### 2020-04-28 papers/intro_paper/intro_paper.tex
updated intro paper

\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers]{revtex4-1}

\begin{document}

\title{Technical Note: pSEOBNRv4HM}

\author{Abhirup Ghosh}
\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), D-14476 Potsdam-Golm, Germany}
\author{Richard Brito}
\affiliation{Dipartimento di Fisica, ``Sapienza" Universit`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185, Roma, Italy}
\author{Alessandra Buonanno}
\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), D-14476 Potsdam-Golm, Germany}

\date{\today}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\section{Method}

\section{Results}

\section{Discussion}

\end{document}

### 2020-06-09 papers/intro_paper/intro_paper.tex
updated paper

@@
 \documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers]{revtex4-1}
+\usepackage{epsfig}
+\usepackage{graphics}
+\usepackage{graphicx}
+\usepackage{bm}
+\usepackage[dvipsnames]{xcolor}
+\usepackage{bm}
+\usepackage{times}
+\usepackage{xspace}
+\usepackage[varg]{txfonts}
+\usepackage[normalem]{ulem} % To get strikethrough (\sout)
+\usepackage[colorlinks]{hyperref}
+\usepackage[caption=false]{subfig}
+\usepackage{booktabs}
+
+\definecolor{LinkColor}{rgb}{0.75, 0, 0}
+\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
+\definecolor{UrlColor}{rgb}{0, 0, 0.75}
+\hypersetup{linkcolor=LinkColor}
+\hypersetup{citecolor=CiteColor}
+\hypersetup{urlcolor=UrlColor}
+\usepackage{perpage}
+\MakePerPage{footnote}
+
+\newcommand{\paperone}{Paper~I\xspace}
+\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
 
@@
 
-\title{Technical Note: pSEOBNRv4HM}
+\title{pSEOBNRv4HM}
 
@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 
-\section{Method}
+\iffalse
+Overview of LIGO-Virgo tests of GR
+No-hair theorem and overview of nohair and ringdown tests with LIGO-Virgo Observations and future detectors
+Describe briefly the test
+Motivate the test: full IMR SNR, t0 definition, flexibility
+highlight importance of spins
+Section breakdown
+\fi
 
-\section{Results}
+The LIGO Scientific Collaboration~\citep{LSC} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave observations~\citep{GWTC-2} from the first half of their third observing run~\citep{O3reference}.
+Combined with the confirmed observations from the first and second observing runs~\citep{GWTC-1}, the Advanced LIGO detectors at Hanford, Washington~\citep{technicaldocument_AdL_H} and Livingston, Louisiana~\citep{technicaldocument_AdL_L}, and the Advanced Virgo detector in Cascina, Italy~\citep{technicaldocument_V} have now detected more than $40$ gravitational wave events from the merger of compact objects like neutron stars and/or black holes (compact binary coalescences/CBCs).
+Alongside independent claims of detections~\citep{Nitz,IAS}, this has firmly established the field of gravitational wave astronomy, five years on from the first ever direct detection of gravitational waves on Earth, on September 14, 2015~\citep{GW150914det}.
+\par
+Observation of gravitational waves have had significant astrophysical and cosmological implications~\citep{LVC:astropapers,H0paper}.
+It has also allowed us to make statements in fundamental physics.
+Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{GW150914TGR,GW170817TGR,GWTC-1TGR}.
+In GR, a CBC involving two black holes (a binary black hole/BBH system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} event marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
+We have performed tests of gravitational wave generation and source dynamics, where we place bounds on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of gravitational wave propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{GW170104det,samajdaretal} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{GW170814det,isietal}.
+We have also checked for consistency between different portions of the signal using estimates of final mass and spin~\citep{IMRCTpapers}, and consistency of the residuals with interferometric noise~\citep{sudarshanetal,GWTC-1TGR}.
+None of these tests report any departure from the predictions of GR.
+\par
+Tests of black hole ringdown and nature of the remnant object is an active field of research at the moment.
+The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical black hole is completely described by two observables: mass and spin angular momentum.
+One consequence of the no-hair conjecture is that the (complex) QNM frequencies of gravitational radiation emitted by a perturbed isolated black hole is uniquely determined by its mass and spin angular momentum.
+Hence a test of the no-hair conjecture would involve checking for consistency between estimates of mass and spin of the remnant object across multiple QNM frequencies.
+An inconsistency would either indicate a non-black hole nature of the remnant object, or an incompleteness of GR as a theory of gravity.
+The consistency between the post-merger signal and the least dampled QNM was first demonstrated in ~\citep{GW150914TGR}, and later extended to include overtones in~\citep{isietal}.
+Consistency of the late-time signal with a single QNM is a test of the ringdown of a BBH coalescence, but not necessarily a test of the no-hair conjecture, which requires the measurement of (atleast) two QNMs (black hole spectroscopy), and checking for consistency between them.
+Recent work in that direction include~\citep{carulloetalpapers,bertipapers}.
+The nature of the remnant object has also been explored through tests of black hole thermodynamics, like the Hawking's area theorem~\citep{Miriametal} or through search for echos in the post-merger signal~\citep{nielsen,abedi,kawa}.
+None of these tests have found evidence for non-black hole nature of the remnant object (as described in GR) in LIGO-Virgo BBH observations.
+\par
+Most of the tests mentioned above focus on analysing the post-merger or late-time ringdown signal in isolation.
+Second generation ground-based interferometric detectors like Advanced LIGO and Virgo are most sensitive to stellar-mass black hole binaries that merge near the minima of their sensitivity band ($\sim 100$Hz).
+As a consequence, the remnant object \textit{rings down} in shot-noise dominated higher frequencies, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
+Furthermore, the post-merger signal of a BBH coalescence transitions from a non-linear to a linear regime where the description of the signal as a QNM spectrum becomes appropriate~\citep{}.
+The ringdown start time isn't a clearly defined quantity and has been explored in detail in~\citep{bhagwatetal}.
+In other works~\citep{carulloetal}, it has been left as a free parameter to be estimated directly from the data.
+Uncertainties in estimates of the ringdown start-time, as well as an overall lack of SNR in the post-merger signal, given typical sensitivities of ground-based detectors result in significant statistical uncertainties in the measurement of the QNM frequencies.
+\par
+An independent approach to black hole spectroscopy, based on a full-signal analysis, was outlined in~\citep{britopaper1} (henceforth referred to as \paperone).
+\abhi{describe underlying GR model; parameterisation; advantages over other methods; highlight spin}
 
-\section{Discussion}
+Unlike methods that focus on the post-merger signal, it describes a framework in which a complete inspiral-merger-ringdown (IMR) waveform model is used to measure the complex QNM frequencies.
+\abhi{It is a spinning multipolar effective-one-body waveform calibrated to numerical relativity simulations (SEOBNRv4HM~\citep{cotesta}})This allows access to the full SNR of the signal, reducing measurement uncertainties.
+Moreover, the definition of the ringdown start time is built into the model and does not need to be either left as an additional free parameter or fixed using alternate definitions.
+While \paperone presented the method in the context of a non-spinning waveform model, we extend the analysis to the case with black holes spins in the current paper.
+All astrophysical black holes are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties.
+\par
+The rest of this paper is organized as follows.
+Section~\ref{sec:model} describes our parametrised IMR waveform model.
+In section~\ref{sec:method}, we define our testing GR framework in which we use that model to measure the complex QNM frequencies in a Bayesian formalism.
+Then in section~\ref{sec:results}, we demonstrate our method on real gravitational wave events, as well as simulated signals.
+Finally we provide a summary of our results and discuss future developments in section  The rest of this paper is organized as follows.
+Section~\ref{sec:model} describes our waveform model, which is then used to perform our test of black hole ringdown using Bayesian framwork, outlined in section~\ref{sec:discussion}.
+
+\section{Waveform Model}\label{sec:model}
+SEOBNRv4HM model + parameterised
+highlight importance of spins
+
+\section{Method/Bayesian PE}\label{sec:method}
+Bayesian inference
+
+\section{Results}\label{sec:results}
+Priors
+LIGO-Virgo results
+Results on injections: modGR, noise systematics
+
+\section{Discussion}\label{sec:discussion}
 

### 2020-06-30 papers/intro_paper/intro_paper.tex
updated the draft with comments and references

@@
 \usepackage{booktabs}
+\usepackage{url}
 
@@
 
-The LIGO Scientific Collaboration~\citep{LSC} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave observations~\citep{GWTC-2} from the first half of their third observing run~\citep{O3reference}.
-Combined with the confirmed observations from the first and second observing runs~\citep{GWTC-1}, the Advanced LIGO detectors at Hanford, Washington~\citep{technicaldocument_AdL_H} and Livingston, Louisiana~\citep{technicaldocument_AdL_L}, and the Advanced Virgo detector in Cascina, Italy~\citep{technicaldocument_V} have now detected more than $40$ gravitational wave events from the merger of compact objects like neutron stars and/or black holes (compact binary coalescences/CBCs).
-Alongside independent claims of detections~\citep{Nitz,IAS}, this has firmly established the field of gravitational wave astronomy, five years on from the first ever direct detection of gravitational waves on Earth, on September 14, 2015~\citep{GW150914det}.
+The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave observations~\citep{GWTC-2} from the first half of their third observing run~\citep{O3reference}.
+Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $40$ gravitational wave events from the merger of compact objects like neutron stars and/or black holes (compact binary coalescences/CBCs).
+Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of gravitational wave astronomy, five years on from the first ever direct detection of gravitational waves on Earth, on September 14, 2015~\citep{abbott2016observation}.
 \par
-Observation of gravitational waves have had significant astrophysical and cosmological implications~\citep{LVC:astropapers,H0paper}.
+Observation of gravitational waves have had significant astrophysical and cosmological implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}.
 It has also allowed us to make statements in fundamental physics.
-Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{GW150914TGR,GW170817TGR,GWTC-1TGR}.
+Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}.
 In GR, a CBC involving two black holes (a binary black hole/BBH system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} event marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
-We have performed tests of gravitational wave generation and source dynamics, where we place bounds on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of gravitational wave propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{GW170104det,samajdaretal} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{GW170814det,isietal}.
-We have also checked for consistency between different portions of the signal using estimates of final mass and spin~\citep{IMRCTpapers}, and consistency of the residuals with interferometric noise~\citep{sudarshanetal,GWTC-1TGR}.
+We have performed tests of gravitational wave generation and source dynamics, where we place bounds on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of gravitational wave propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{gw170104,samajdar2017projected} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{gw170814,isi2017probing}.
+We have also checked for consistency between different portions of the signal using estimates of final mass and spin~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and consistency of the residuals with interferometric noise~\citep{Ghonge:2020suv,gwtc1_tgr}.
 None of these tests report any departure from the predictions of GR.
@@
 An inconsistency would either indicate a non-black hole nature of the remnant object, or an incompleteness of GR as a theory of gravity.
-The consistency between the post-merger signal and the least dampled QNM was first demonstrated in ~\citep{GW150914TGR}, and later extended to include overtones in~\citep{isietal}.
+The consistency between the post-merger signal and the least dampled QNM was first demonstrated in ~\citep{LSC_2016grtests}, and later extended to include overtones in~\citep{Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}.
 Consistency of the late-time signal with a single QNM is a test of the ringdown of a BBH coalescence, but not necessarily a test of the no-hair conjecture, which requires the measurement of (atleast) two QNMs (black hole spectroscopy), and checking for consistency between them.
-Recent work in that direction include~\citep{carulloetalpapers,bertipapers}.
-The nature of the remnant object has also been explored through tests of black hole thermodynamics, like the Hawking's area theorem~\citep{Miriametal} or through search for echos in the post-merger signal~\citep{nielsen,abedi,kawa}.
+Recent work in that direction include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}.
+The nature of the remnant object has also been explored through tests of black hole thermodynamics, like the Hawking's area theorem~\citep{Cabero:2017avf} or through search for echos in the post-merger signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
 None of these tests have found evidence for non-black hole nature of the remnant object (as described in GR) in LIGO-Virgo BBH observations.
@@
 Furthermore, the post-merger signal of a BBH coalescence transitions from a non-linear to a linear regime where the description of the signal as a QNM spectrum becomes appropriate~\citep{}.
-The ringdown start time isn't a clearly defined quantity and has been explored in detail in~\citep{bhagwatetal}.
-In other works~\citep{carulloetal}, it has been left as a free parameter to be estimated directly from the data.
+The ringdown start time isn't a clearly defined quantity and has been explored in detail in~\citep{Bhagwat:2017tkm}.
+In other works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a free parameter to be estimated directly from the data.
 Uncertainties in estimates of the ringdown start-time, as well as an overall lack of SNR in the post-merger signal, given typical sensitivities of ground-based detectors result in significant statistical uncertainties in the measurement of the QNM frequencies.
 \par
-An independent approach to black hole spectroscopy, based on a full-signal analysis, was outlined in~\citep{britopaper1} (henceforth referred to as \paperone).
+An independent approach to black hole spectroscopy, based on a full-signal analysis, was outlined in~\citep{Brito:2018rfr} (henceforth referred to as \paperone).
 \abhi{describe underlying GR model; parameterisation; advantages over other methods; highlight spin}
@@
 \section{Waveform Model}\label{sec:model}
-SEOBNRv4HM model + parameterised
-highlight importance of spins
+
+\abhi{Summary of the section:}
+
+\begin{itemize}
+\item{a description of the SEOBNRv4HM model and it's generalisation to form the pSEOBNRv4HM model}
+\item{highlight the importance of spins in the model, especially with regards to the non-spinning method outlined in Brito et al.}
+\end{itemize}
 
 \section{Method/Bayesian PE}\label{sec:method}
-Bayesian inference
+
+\abhi{This section will basically provide an overview of Bayesian inference.
+Starting from the generalised definition of likelihood, provide an expression for the posterior on the delta QNM parameters.}
 
 \section{Results}\label{sec:results}
-Priors
-LIGO-Virgo results
-Results on injections: modGR, noise systematics
+\subsection{Priors}
+
+\abhi{A small sub-section dedicated to priors used in this analysis. Very common question from referees.}
+
+\subsection{Results on GW150914-like injection}
+
+\abhi{The GW150914-like injections we have:}
+\begin{itemize}
+\item{an SEOBNRv4HM software injection with the 22 mode frequencies estimated}
+\item{an SEOBNRv4HM software injection with the 33 mode frequencies estimated}
+\item{a non-spinning NR injection with parameters close to the real event but higher SNR for which 22 mode frequencies are estimated}
+\item{a non-spinning highly-asymmetric (q=6) NR injection with total mass similar to GW150914 and high SNR for which 22 and 33 mode frequencies are estimated}
+\end{itemize}
+
+\subsection{Results on modGR injection}
+
+\abhi{As part of review we had developed the infrastructure to make non-GR waveforms using pSEOBNRv4HM, and running LALInference on it.
+We had specifically chosen an injection with domega220 = dtau220  = 0.5 in zero-noise, and successfully recovered those frequencies thus demonstrating the robustness of the method in detecting deviations from GR.}
+
+\subsection{Results on actual LIGO-Virgo results}
+
+\abhi{Results obtained as part of the review on GW150914 and other O1-O2 events which are of relevance}
+
+\subsection{Results on noise systematics study}
+
+\abhi{A small summary of the noise systematics study that was done for S190521g to show that the deviations seen were consistent with systematics due to noise.
+The study include 2 separate sections: in Gaussian noise, and in real LIGO-Virgo noise immediately adjacent to the actual event.}
 
@@
 
+%
+\bibliographystyle{apsrev}
+\bibliography{intro_paper}
+
 \end{document}

### 2020-07-22 papers/intro_paper/intro_paper.tex
updated draft
updated paper and figures

@@
 \usepackage{url}
+\usepackage{float}
 
@@
 \newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
+
+\newcommand{\h}{\mathpzc{h}}
+\newcommand{\Hhat}{\hat{\mathpzc{H}}}
+\newcommand{\B}{\mathpzc{B}}
+\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
+\newcommand{\xilm}{\xi_{\ell m}}
+\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
+\newcommand{\Y}{{Y}^{-2}}
+\newcommand{\hc}{h_\times}
+\newcommand{\hp}{h_+}
+\newcommand{\Fc}{F_\times}
+\newcommand{\Fp}{F_+}
+\newcommand{\Mf}{M_f}
+\newcommand{\cA}{\mathpzc{A}}
+\newcommand{\lm}{_{\ell m}}
+\newcommand{\deff}{d_\mathrm{eff}}
+\newcommand{\rmi}{\mathrm{i}}
+\newcommand{\blambda}{\bm{\lambda}}
+\newcommand{\btheta}{\bm{\theta}}
+\newcommand{\bxi}{\bm{\xi}}
+\newcommand{\Mo}{M_{\odot}}
+\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
+\newcommand{\FF}{\mathrm{FF}}
+\newcommand{\e}{\mathrm{e}}
+\newcommand{\rhoopt}{\rho_\mathrm{opt}}
+\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
+\newcommand{\fqnm}{f}
+\newcommand{\sigmaqnm}{\sigma}
+\newcommand{\n}{\mathbf{n}}
+\newcommand*{\skymapscale}{0.5}
+\newcommand*{\paramestscale}{0.455}
 
@@
 
+Each interferometric GW detector $I$ detects a linear combination of the two polarizations $h_+$ and $h_\times$, given by 
+\begin{eqnarray}
+h^I(t) & = \frac{1}{d_L} \, \left [ F^I_+(\alpha, \delta, \psi) \, h_+(t-t_0; \n, \blambda) \right. \\ 
+       & \left. + F^I_{\times}(\alpha, \delta, \psi)\, h_\times(t-t_0; \n, \blambda) \right]
+\label{eq:det_response}
+\end{eqnarray}
+where ${d_L}$ is the luminosity distance to the source, $F^I_+$ and $F^I_\times$ are the antenna pattern functions of the detector $I$, $t_0$ is the time of arrival of the signal at the detector, and $(\alpha, \delta), \psi$ define the sky position and polarisation angle of the GW source, respectively.
+Above, we have neglected the time dependence of the antenna pattern functions, which is a good assumption for the case of the transient signals that we consider in this work.
+
+The noise $n(t)$ in a GW detector can be safely described, over sufficiently short time intervals, as a stationary and Gaussian random process with zero mean and a power spectral density (PSD), $S_n(f)$.
+In the presence of a GW signal $h(t; \btheta)$ from a binary black hole merger described by a parameter set $\btheta$ (which include the intrinsic and extrinsic parameters of the binary as well as the set of parameters describing deviations from GR), we assume that the detector data $d(t)$ is the sum of the noise and the signal, i.e.:
+\begin{equation}
+d(t) = n(t) + h(t; \btheta). 
+\end{equation}
+A (quasi-circular) non-spinning binary black hole coalescence can be completely described by a 11-dimensional parameter set $\btheta = \{ \blambda, \bxi\}$ in GR, where $\blambda = \{ M_c, q, s_{1z}, s_{2z} \}$ is the set of intrinsic parameters consisting of the chirp mass $M_c$ and the asymmetric mass ratio $q = m_2/m_1$ (with the convention $m_2 \leq m_1$) and the aligned spin components $(s_{1z}, s_{2z})$, and $\bxi = \{ d_L, \alpha, \delta, \iota, \psi, t_0, \phi_0 \}$, is the set of extrinsic parameters consisting of the luminosity distance $d_L$, the sky position $\{\alpha, \delta\}$ and orientation $\{\psi, \iota\}$ of the binary, and the time and phase at coalescence $\{t_0, \phi_0\}$ respectively.
+
+We use the Bayesian framework to obtain the posterior probability distribution $P({\btheta} \, | \, d)$ of the parameter set $\btheta$, through the Bayes Theorem:
+\begin{equation}
+P({\btheta} \, | \, d) = \frac{P({\btheta}) \, P (d \, | \, {\btheta})}{P(d)}.
+\label{eq:Bayes_theorem}
+\end{equation} 
+where, $P({\btheta})$ denotes the prior probability distribution of the parameters, and $P (d \, | \, {\btheta})$ is the likelihood function, the probability of observing data $d(t)$ given the model parameters $\btheta$.
+$P(d)$ is a normalization constant, called the marginal likelihood: $P(d) = \int p(d|\btheta) \, p(\btheta) \, d\btheta$.
+Under the assumption of the data mentioned above, the likelihood function $P(d \, | \, {\btheta})$ can be written as:
+\begin{equation}
+P (d \, | \, {\btheta}) \propto \exp \left[ -\frac{1}{2} \langle d - h({\btheta}), d - h({\btheta}) \rangle \right],
+\end{equation}
+where $\langle a, b \rangle$ describes the noise-weighted inner product defined as:
+\begin{equation}
+\langle a, b \rangle := 4 \Re \int_{f_\mathrm{low}}^{f_\mathrm{high}} \frac{\tilde{a}(f) \, \tilde{b}^*(f)}{S_n(f)}df
+\end{equation}
+where $\tilde{a}(f)$ denotes the Fourier transforms of $a(t)$, and the integration limits are defined by the sensitivity bandwidth of the detector, $f_\mathrm{low}$ and $f_\mathrm{high}$.
+
+Assuming that the noise between any two detectors is uncorrelated, the joint likelihood across the three detectors is written as a product of the likelihoods in each detector:
+\begin{equation}
+P (d \, | \, {\btheta}) = \prod_{I \epsilon {H,L,V}} P (d^{I} \, | \, {\btheta}).
+\end{equation}
+
+In this Bayesian framework, we proceed to estimate the posterior probability distribution of $\btheta$ by stochastically sampling over the parameter space, using a python-based affine-invariant ensemble sampler \textsc{emcee}~\cite{foreman2013emcee, goodman2010ensemble}.
+Subsequently, we marginalize over the \textit{nuisance} parameters to obtain the posterior distributions on the non-GR parameter set, ${\Delta \blambda}$ or $c_{\ell m}$.
+If the data is consistent with a binary black hole signal in GR, $P(\Delta \blambda \, | \, d)$ (or $P(\Delta c_{\ell m} \, | \, d)$) is expected to be consistent with zero.
+
 \section{Results}\label{sec:results}
@@
 
+We assume uniform prior probability distributions on the chirp mass and mass ratio in the interval $M_c \in [1,200] M_\odot$ and $q \in [0.05,1.0]$.
+The prior on the location of the source is  assumed to be isotropic on the sphere of  the  sky,  with $P({d_L}) \propto d_{L}^{2}$ where $d_L \in [1,10000]$ Mpc.
+We use an  isotropic  prior  on  the  orientation  of  the  binary: $P({\iota,\varphi_0,\psi}) \propto \sin\iota$ with $\iota \in [0,\pi)$, $\varphi_0 \in [0,2\pi)$ and $\psi \in [0,\pi)$.
+For all other parameters in $\btheta$, we use uniform priors: $\alpha \in [0,2\pi)$, $\delta \in [0,2\pi)$ and $t_0 \in [-15,15]$.
+
 \subsection{Results on GW150914-like injection}
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figures/GW150914_swinj_GR_vs_modGR.png}
+\end{figure*}
 
@@
 \item{an SEOBNRv4HM software injection with the 22 mode frequencies estimated}
-\item{an SEOBNRv4HM software injection with the 33 mode frequencies estimated}
 \item{a non-spinning NR injection with parameters close to the real event but higher SNR for which 22 mode frequencies are estimated}
@@
 
+\begin{figure}
+	\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
+\end{figure}
+
 \abhi{Results obtained as part of the review on GW150914 and other O1-O2 events which are of relevance}
+\abhi{A plot showing the fractional quantities}
+\abhi{A table with absolute quantites similar to GWTC-2 TGR}
+
+\begin{tabular}{llllllll}
+\toprule
+Event & \multicolumn{3}{c}{Redshifted} & \hphantom{X} & \multicolumn{3}{c}{Redshifted} \\
+& \multicolumn{3}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{3}{c}{damping time [ms]} \\[0.075cm]
+\cline{2-4}
+\cline{6-8}
+& IMR & DS & pSEOB & \hphantom{X} & IMR & DS & pSEOB \\
+\midrule
+
+GW150914 &
+$249^{+9}_{-7}$ &
+$247^{+14}_{-16}$ &
+$-$ &
+\hphantom{X} &
+$4.1^{+0.3}_{-0.2}$ &
+$4.8^{+3.7}_{-1.9}$ &
+$-$
+\\[0.075cm]
+
+GW170104 &
+$286^{+16}_{-27}$ &
+$228^{+71}_{-102}$ &
+$-$ &
+\hphantom{X} &
+$3.5^{+0.4}_{-0.3}$ &
+$3.6^{+36.2}_{-2.1}$ &
+$-$
+\\[0.075cm]
+
+GW170729 &
+$161^{+13}_{-14}$ &
+$148^{+11}_{-11}$ &
+$-$ &
+\hphantom{X} &
+$7.8^{+1.8}_{-1.5}$ &
+$10.4^{+8.2}_{-4.7}$ &
+$-$
+\\[0.075cm]
+
+GW170814 &
+$295^{+13}_{-12}$ &
+$527^{+340}_{-332}$ &
+$-$ &
+\hphantom{X} &
+$3.7^{+0.3}_{-0.2}$ &
+$25.1^{+22.2}_{-19.0}$ &
+$-$
+\\[0.075cm]
+
+GW170823 &
+$199^{+14}_{-16}$ &
+$222^{+664}_{-62}$ &
+$-$ &
+\hphantom{X} &
+$5.4^{+1.0}_{-0.6}$ &
+$13.4^{+31.8}_{-9.8}$ &
+$-$
+\\[0.075cm]
+
+\bottomrule
+\end{tabular}
 
@@
 
+\begin{figure}[H]
+	\includegraphics[width=0.4\textwidth]{figures/S190521g_gaussiannoiseinjections.png}
+	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
+\end{figure}
+
+We injected NRSur7dq4 signal using the MaxL parameters from EXP30, in 2.5 hours of data surrounding the event at: t0-1.5 hours, t0-1., t0-0.5, t0+0.5, t0+1.
+For 3 of the 5 noise realisations, corresponding to t0-1 hour, t0+0.5 hours, and t0+1.0 hour we recover a damping time similar to the actual event, whereas for a third case, t0-0.5 hours, we obtain a damping time consistent at the 90\% credible interval.
+L1-SNR goes down by more than 3 in some runs (maximum L1-SNR 12, minimum 9), indicative of how the noise variability is strongly affecting the recovered parameters.
+For some injections the mass ratio is biased, although final spin (most sensitive to mass ratio) is not affected much.
+domega varies quite a lot among runs, instead dtau seems well behaved around zero.
+Effective frequency is a stable parameter (always well measured), while effective tau is much more sensitive to the noise configuration.
+
 \section{Discussion}\label{sec:discussion}
+
+\abhi{A comparison with pyRING}
+\abhi{damped sinusoid results}
 

### 2020-09-08 papers/intro_paper/intro_paper.tex
updated tex

--- 2020-06-30 papers/intro_paper/intro_paper.tex
@@
 \newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
+
+\newcommand{\h}{\mathpzc{h}}
+\newcommand{\Hhat}{\hat{\mathpzc{H}}}
+\newcommand{\B}{\mathpzc{B}}
+\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
+\newcommand{\xilm}{\xi_{\ell m}}
+\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
+\newcommand{\Y}{{Y}^{-2}}
+\newcommand{\hc}{h_\times}
+\newcommand{\hp}{h_+}
+\newcommand{\Fc}{F_\times}
+\newcommand{\Fp}{F_+}
+\newcommand{\Mf}{M_f}
+\newcommand{\cA}{\mathpzc{A}}
+\newcommand{\lm}{_{\ell m}}
+\newcommand{\deff}{d_\mathrm{eff}}
+\newcommand{\rmi}{\mathrm{i}}
+\newcommand{\blambda}{\bm{\lambda}}
+\newcommand{\btheta}{\bm{\theta}}
+\newcommand{\bxi}{\bm{\xi}}
+\newcommand{\bzeta}{\bm{\zeta}}
+\newcommand{\bs}[1]{\bm{\vec{s}_{#1}}}
+\newcommand{\Mo}{M_{\odot}}
+\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
+\newcommand{\FF}{\mathrm{FF}}
+\newcommand{\e}{\mathrm{e}}
+\newcommand{\rhoopt}{\rho_\mathrm{opt}}
+\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
+\newcommand{\fqnm}{f}
+\newcommand{\sigmaqnm}{\sigma}
+\newcommand{\n}{\mathbf{n}}
+\newcommand*{\skymapscale}{0.5}
+\newcommand*{\paramestscale}{0.455}
 
@@
 
-\abhi{This section will basically provide an overview of Bayesian inference.
-Starting from the generalised definition of likelihood, provide an expression for the posterior on the delta QNM parameters.}
+A gravitational waveform from the (quasi-circular) coalescence of two black holes is completely described in GR by a set \textit{intrinsic} parameters, $\bxi$: the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the initial binary and a reference time and phase $t_c, \phi_c$ respectively; and a set of \textit{extrinsic} parameters, $\btheta$: the location of the binary given by the right ascension, $\alpha$, declination,$\delta$ and the luminosity distance, $d_L$, and its orientation described through the inclination of the binary $\iota$ and its polarisation $\psi$.
+Also allowing for additional degrees of freedom $\bzeta$ like the complex QNM frequencies described in section \ref{sec:model}, one can then use a Bayesian formalism to obtain a posterior probability density function on the combined parameter set $\blambda = \{\bxi, \btheta, \bzeta\}$:
+
+\begin{equation}
+p(\blambda | d, H, I) \propto P(\blambda | H,I) \mathcal{L}(d | \blambda, H, I)
+\end{equation}
+
+where $P(\blambda | H,I)$ is the prior probability density function and $\mathcal{L}(d | \blambda, H, I)$ is the likelihood of obtaining the data for a given choice of the parameter set $\blambda$.
+We assume the hypothesis $H$ to be our waveform model described in section \ref{sec:model} and $I$ to be any other information assumed during the analysis.
+
+Given the full-dimensional posterior probability density function $p(\blambda | d, H, I)$, we can marginalise over the \emph{nuisance} parameters, to obtain the marginalised posterior probability density function on our QNM parameters $\bzeta$, as:
+
+\begin{equation}
+p(\bzeta | d, H, I) = \int p(\blambda | d, H, I) d\bxi d\btheta
+\end{equation}
+
+Throughout our analysis, we assume the noise in the detector to be well-approximated by the Gaussian random process with a fixed power spectral density.
+This allows us to define a Gaussian likelihood function $\mathcal{L}(d | \blambda, H, I)$, which we stochastically sample over using either a Markhov-Chain-Monte-Carlo based algorithm implemented in the LIGO Algorithms Library.
 
@@
 
-\abhi{A small sub-section dedicated to priors used in this analysis. Very common question from referees.}
+Throughout our analysis we assume a completely uninformed prior in the component masses $m_1, m_2$, uniformly distributed in the range (XX,YY).
+Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation.
+Our prior on the distance varies as $d_L^2$ upto a distance of XX.
+For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
+2015 LALInference paper).
+For our non-GR ringdown parameters, we assume priors uniform in the range (XX,YY).
+For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
 
 \subsection{Results on GW150914-like injection}
+
+\begin{figure*}
+	\includegraphics[width=\textwidth]{figures/GW150914_swinj_GR_vs_modGR.png}
+	\caption{final figure will contain a third set of contours for modGR recovered assuming GR to show bias. That run is ongoing.}
+\end{figure*}
 
@@
 
+\begin{figure}
+	\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
+	\caption{include contours from pyRING}
+\end{figure}
+
 \abhi{Results obtained as part of the review on GW150914 and other O1-O2 events which are of relevance}
+\abhi{A plot showing the fractional quantities}
+\abhi{A table with absolute quantites similar to GWTC-2 TGR}
+
+\begin{tabular}{llllllll}
+\toprule
+Event & \multicolumn{3}{c}{Redshifted} & \hphantom{X} & \multicolumn{3}{c}{Redshifted} \\
+& \multicolumn{3}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{3}{c}{damping time [ms]} \\[0.075cm]
+\cline{2-4}
+\cline{6-8}
+& IMR & DS & pSEOB & \hphantom{X} & IMR & DS & pSEOB \\
+\midrule
+
+GW150914 &
+$249^{+9}_{-7}$ &
+$247^{+14}_{-16}$ &
+$-$ &
+\hphantom{X} &
+$4.1^{+0.3}_{-0.2}$ &
+$4.8^{+3.7}_{-1.9}$ &
+$-$
+\\[0.075cm]
+
+GW170104 &
+$286^{+16}_{-27}$ &
+$228^{+71}_{-102}$ &
+$-$ &
+\hphantom{X} &
+$3.5^{+0.4}_{-0.3}$ &
+$3.6^{+36.2}_{-2.1}$ &
+$-$
+\\[0.075cm]
+
+GW170729 &
+$161^{+13}_{-14}$ &
+$148^{+11}_{-11}$ &
+$-$ &
+\hphantom{X} &
+$7.8^{+1.8}_{-1.5}$ &
+$10.4^{+8.2}_{-4.7}$ &
+$-$
+\\[0.075cm]
+
+GW170814 &
+$295^{+13}_{-12}$ &
+$527^{+340}_{-332}$ &
+$-$ &
+\hphantom{X} &
+$3.7^{+0.3}_{-0.2}$ &
+$25.1^{+22.2}_{-19.0}$ &
+$-$
+\\[0.075cm]
+
+GW170823 &
+$199^{+14}_{-16}$ &
+$222^{+664}_{-62}$ &
+$-$ &
+\hphantom{X} &
+$5.4^{+1.0}_{-0.6}$ &
+$13.4^{+31.8}_{-9.8}$ &
+$-$
+\\[0.075cm]
+
+\bottomrule
+\end{tabular}
 
@@
 
+\begin{figure}[H]
+	\includegraphics[width=0.4\textwidth]{figures/S190521g_noiseinjections.png}
+	\caption{a single figure for both Gaussian and Real noise injections, color coded, to save space}
+\end{figure}
+
+We injected NRSur7dq4 signal using the MaxL parameters from EXP30, in 2.5 hours of data surrounding the event at: t0-1.5 hours, t0-1., t0-0.5, t0+0.5, t0+1.
+For 3 of the 5 noise realisations, corresponding to t0-1 hour, t0+0.5 hours, and t0+1.0 hour we recover a damping time similar to the actual event, whereas for a third case, t0-0.5 hours, we obtain a damping time consistent at the 90\% credible interval.
+L1-SNR goes down by more than 3 in some runs (maximum L1-SNR 12, minimum 9), indicative of how the noise variability is strongly affecting the recovered parameters.
+For some injections the mass ratio is biased, although final spin (most sensitive to mass ratio) is not affected much.
+domega varies quite a lot among runs, instead dtau seems well behaved around zero.
+Effective frequency is a stable parameter (always well measured), while effective tau is much more sensitive to the noise configuration.
+
 \section{Discussion}\label{sec:discussion}
+
+\abhi{A comparison with pyRING}
+\abhi{damped sinusoid results}
 

### 2020-09-14 papers/intro_paper/intro_paper.tex
started writing sec. II

@@
 \newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
+\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
 
@@
 Unlike methods that focus on the post-merger signal, it describes a framework in which a complete inspiral-merger-ringdown (IMR) waveform model is used to measure the complex QNM frequencies.
-\abhi{It is a spinning multipolar effective-one-body waveform calibrated to numerical relativity simulations (SEOBNRv4HM~\citep{cotesta}})This allows access to the full SNR of the signal, reducing measurement uncertainties.
+\abhi{It is a spinning multipolar effective-one-body waveform calibrated to numerical relativity simulations (SEOBNRv4HM~\citep{Cotesta:2018fcv}})This allows access to the full SNR of the signal, reducing measurement uncertainties.
 Moreover, the definition of the ringdown start time is built into the model and does not need to be either left as an additional free parameter or fixed using alternate definitions.
@@
 \end{itemize}
+
+\rb{work in progress}
+
+As in \paperone, we use an IMR waveform developed within the EOB formalism.
+However, in this work we  extend the results of \paperone by using a waveform model for spinning, nonprecessing binary BHs.
+Namely we use the multipolar waveform developed in Ref.~\citep{Cotesta:2018fcv}.
+In addition to being calibrated to NR simulations, this model also uses information from BH perturbation theory for the merger and ringdown.
+Therefore this waveform model provides a very accurate and faithful semi-analytic description of the inspiral, merger and ringdown phases.
+
+In the observer frame, GWs emitted by a binary can be written as 
+$h_+(\iota,\varphi;t ) - i h_\times(\iota,\varphi;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi)\, h_{\ell m}(t)$, where $\iota$ denotes the inclination angle computed with respect to the direction perpendicular to the orbital, $\varphi$ the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
+The EOBNR model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes.
+For each $(\ell, m)$, the merger-ringdown EOBNR modes read~\citep{Cotesta:2018fcv}
+%
+\begin{equation}
+  \label{RD}
+  h_{\ell m}^\mathrm{merger-RD}(t) = \nu A_{\ell m}(t) e^{i\phi_{\ell m} (t)}\,
+  e^{-i\sigma_{\ell m0} (t-t_\mathrm{match}^{\ell m})} \quad t \geq t_{\rm match}^{\ell m}\,,
+\end{equation}
+%
+where $\sigma_{\ell m0} = \omega_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNM of the final BH,  where the oscillation frequency of the QNM is given by $\omega_{\ell m  0}>0$ and the decay time by $\tau_{\ell m 0}>0$.
+The explicit expressions for the functions $A_{\ell m}(t)$ and $\phi_{\ell m} (t)$ can be found given in Ref.~\citep{Cotesta:2018fcv}, and are chosen such that the functions $A_{\ell  m}$ and $\phi_{\ell  m}$ are of class $C^1$ at $t=  t_{\rm match}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge EOBNR
+waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
+Finally, the inspiral-(plunge-)merger-ringdown EOBNR waveform reads $h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{
+    match}^{\ell m})$, where $\theta(t)$ is the Heaviside step function.
+
+  In the model constructed in Ref.~\cite{Cotesta:2018fcv}, the complex frequencies $\sigma_{\ell m 0}$  are expressed in terms of the final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the latter are related to the BBH's component masses and spins through an
+  NR--fitting-formulas obtained in GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. 
+  Here, to measure the ringdown frequencies and damping times of
+  different QNMs, we relax the assumption that the ringdown signal is
+  fixed by the NR--fitting-formulas, and
+  instead promote the QNM (complex) frequencies to be free
+  parameters (henceforth, pSEOBNR model). 
+  %In the specific applications of this paper, we will only allow $\sigma_{220}$ and $\sigma_{330}$ to vary freely, while all the other mode frequencies present in the merger-ringdown waveform coincide to the GR values.
+We emphasize that $\sigma_{220}$ and $\sigma_{330}$ varying freely implies that the EOBNR waveform at merger (i.e., close to the peak and at $t_\mathrm{match}^{\ell m}$),  {\it does not necessarily} coincide with the GR prediction, since the matching procedure changes the shape of the waveform for $t>  t_\mathrm{match}^{\ell m}$ for $(\ell,m) = (2,2)$ and $(3,3)$.
+Lastly, for $t < t_{\rm match}^{\ell m}$, our EOBNR waveform modes agree with the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ computed in GR.
 
@@
 
-\begin{figure}[H]
-	\includegraphics[width=0.4\textwidth]{figures/S190521g_noiseinjections.png}
-	\caption{a single figure for both Gaussian and Real noise injections, color coded, to save space}
-\end{figure}
+%\begin{figure}[H]
+%	\includegraphics[width=0.4\textwidth]{figures/S190521g_noiseinjections.png}
+%	\caption{a single figure for both Gaussian and Real noise injections, color coded, to save space}
+%\end{figure}
 

### 2020-10-12 papers/intro_paper/intro_paper.tex
updated paper
a bit more text for the waveform model

--- 2020-09-08 papers/intro_paper/intro_paper.tex
@@
 
-\section{Waveform Model}\label{sec:model}
+\section{Method}
+\subsection{Waveform Model}\label{sec:model}
 
-\abhi{Summary of the section:}
+%\abhi{Summary of the section:}
 
-\begin{itemize}
-\item{a description of the SEOBNRv4HM model and it's generalisation to form the pSEOBNRv4HM model}
-\item{highlight the importance of spins in the model, especially with regards to the non-spinning method outlined in Brito et al.}
-\end{itemize}
+%\begin{itemize}
+%\item{a description of the SEOBNRv4HM model and it's generalisation to form the pSEOBNRv4HM model}
+%\item{highlight the importance of spins in the model, especially with regards to the non-spinning method outlined in Brito et al.}
+%\end{itemize}
 
-\section{Method/Bayesian PE}\label{sec:method}
+As in \paperone, we use an IMR waveform model developed within the EOB formalism.
+However, in this work we extend the results of \paperone by using a waveform model for spinning, nonprecessing binary BHs.
+Namely we use as our baseline model the multipolar waveform developed in Ref.~\citep{Cotesta:2018fcv}.
+In addition to being calibrated to NR simulations, this model also uses information from BH perturbation theory for the merger and ringdown phases.
+Therefore this waveform model provides a very accurate and faithful semi-analytic description of the inspiral, merger and ringdown phases.
+Henceforth we will denote this model by SEOBNR for short.
+
+In the observer's frame, the GW polarizations can be written as 
+$h_+(\iota,\varphi;t ) - i h_\times(\iota,\varphi;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi)\, h_{\ell m}(t)$, where $\iota$ denotes the inclination angle computed with respect to the direction perpendicular to the orbital plane, $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
+The SEOBNR model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes.
+For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown SEOBNR waveform is schematically given by $h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{
+    match}^{\ell m})$, where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown phase.
+  %  
+The merger-ringdown SEOBNR modes read~\citep{Bohe:2016gbl,Cotesta:2018fcv}
+%
+\begin{equation}
+  \label{RD}
+  h_{\ell m}^\mathrm{merger-RD}(t) = \nu A_{\ell m}(t) e^{i\phi_{\ell m} (t)}\,
+  e^{-i\sigma_{\ell m0} (t-t_\mathrm{match}^{\ell m})} \quad t \geq t_{\rm match}^{\ell m}\,,
+\end{equation}
+%
+where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = \omega_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
+We denote the oscillation frequencies by $\omega_{\ell m  0}\equiv \Re(\sigma_{\ell m0})$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0})$.
+The explicit expressions for the amplitudes $A_{\ell m}(t)$ and phases $\phi_{\ell m} (t)$ can be found in Ref.~\citep{Cotesta:2018fcv}, and are chosen such that the functions $A_{\ell  m}$ and $\phi_{\ell  m}$ are of class $C^1$ at $t=  t_{\rm match}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge SEOBNR waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
+
+In the SEOBNR model constructed in Ref.~\cite{Cotesta:2018fcv}, the complex frequencies $\sigma_{\ell m 0}$  are expressed in terms of the final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the latter are related to the BBH's component masses and spins through NR--fitting-formulas obtained in GR~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values (henceforth, pSEOBNR model).
+We note that when leaving $\sigma_{\ell m}$ to vary freely, the amplitudes $A_{\ell m}(t)$ and phases $\phi_{\ell m} (t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies (see~\citep{Cotesta:2018fcv}).
+
+For the specific applications of this paper, we will normally only allow either $\sigma_{220}$ or $\sigma_{330}$ to vary, while keeping all the other modes to coincide with GR.
+However the model can be easily used to measure any QNM complex frequency available in the waveform.
+
+\subsection{Bayesian PE}\label{sec:method}
 

### 2020-10-20 papers/intro_paper/intro_paper.tex
updated paper draft

@@
 Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}.
-In GR, a CBC involving two black holes (a binary black hole/BBH system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} event marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
+In GR, a CBC involving two black holes (a binary black hole (BBH) system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
 We have performed tests of gravitational wave generation and source dynamics, where we place bounds on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of gravitational wave propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{gw170104,samajdar2017projected} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{gw170814,isi2017probing}.
@@
 None of these tests report any departure from the predictions of GR.
+\abhi{Perhaps reframe this section in the contect of the O3a TGR companion paper}
 \par
@@
 Hence a test of the no-hair conjecture would involve checking for consistency between estimates of mass and spin of the remnant object across multiple QNM frequencies.
-An inconsistency would either indicate a non-black hole nature of the remnant object, or an incompleteness of GR as a theory of gravity.
+An inconsistency would either indicate a non-black hole nature of the remnant object, or an incompleteness of GR as the underlying theory of gravity.
 The consistency between the post-merger signal and the least dampled QNM was first demonstrated in ~\citep{LSC_2016grtests}, and later extended to include overtones in~\citep{Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}.
@@
 Then in section~\ref{sec:results}, we demonstrate our method on real gravitational wave events, as well as simulated signals.
-Finally we provide a summary of our results and discuss future developments in section  The rest of this paper is organized as follows.
-Section~\ref{sec:model} describes our waveform model, which is then used to perform our test of black hole ringdown using Bayesian framwork, outlined in section~\ref{sec:discussion}.
+Finally we provide a summary of our results and discuss future developments in section~\ref{sec:discussion}.
 
@@
 
-Throughout our analysis, we assume the noise in the detector to be well-approximated by the Gaussian random process with a fixed power spectral density.
+An example of a posterior distribution on $\bzeta$Throughout our analysis, we assume the noise in the detector to be well-approximated by the Gaussian random process with a fixed power spectral density.
 This allows us to define a Gaussian likelihood function $\mathcal{L}(d | \blambda, H, I)$, which we stochastically sample over using either a Markhov-Chain-Monte-Carlo based algorithm implemented in the LIGO Algorithms Library.
@@
 \section{Results}\label{sec:results}
+
+\iffalse
 \subsection{Priors}
@@
 
-\subsection{Results on GW150914-like injection}
+\fi
 
-\begin{figure*}
-	\includegraphics[width=\textwidth]{figures/GW150914_swinj_GR_vs_modGR.png}
+\subsection{Simulations using GR signals}\label{ssec:gr_signal}
+
+We initially demonstrate our method using simulated GR signals, with parameters similar to the two gravitational wave events, GW150914 CITE and GW190521 CITE.
+These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the signal-to-noise ratio pre- and post-merger return reliable parameter estimation results.
+To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, SEOBNRv4HM CITE (without allowing for deviations in the QNM parameters) to simulate our GW signal.
+And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the Advanced LIGO zero-detuned-high-power PSD CITE.
+We find, as expected, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time, $\{d\omega,d\tau\}$ are consistent with zero (the solid curves in left panel of Fig.\ref{fig:gr_simulation}).
+The difference in the size of the posterior is due to the difference in the SNRs of the two events ($\sim 25$ for GW150914 as compared to $\sim 13$ for GW190521).
+One can then convert these fractional quantities into absolute quantities using the relations:
+
+\begin{eqnarray}
+f_{220}^{\text{eff}} &:=& f_{220}^{\text{GR}} (1 + \delta f_{220}) \\
+\tau _{220}^{\text{eff}} &:=& \tau _{220}^{\text{GR}} (1 + \delta \tau_{220})
+\end{eqnarray}
+
+and construct posterior distributions on these effective quantities, $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (solid lines in middle and right panels of Fig.\ref{fig:gr_simulation}).
+The GR quantities $(f_{220}^{\text{GR}}, \tau _{220}^{\text{GR}})$ are constructed using numerical relativity predictions of the mass and spin of the remnant object, starting from estimates of the masses and spins of the initial binary \abhi{add description of the contruction of GR quantities with details of NR fit formula}.
+In each of these cases, recovered posterior are consistent with the GR predictions (as indicated by the plus signs).
+
+\begin{figure*}[h]
+	\includegraphics[width=0.3\textwidth]{figures/GW150914_GW190521_simulated_frac.png}\includegraphics[width=0.56\textwidth]{figures/GW150914_GW190521_simulated_abs.png}\label{fig:gr_simulation}
 	\caption{final figure will contain a third set of contours for modGR recovered assuming GR to show bias. That run is ongoing.}
@@
 
+\iffalse
 \abhi{The GW150914-like injections we have:}
@@
 \end{itemize}
+\fi
 
-\subsection{Results on modGR injection}
+\subsection{Simulations using nonGR signals}
 
+To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger \abhi{be more specific}, and differ in their post-merger description.
+We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $d\omega =d\tau = 0.5$.
+In other words, we assume that the frequency and damping time of our nonGR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}).
+We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}.
+The posterior probability distributions on $\{d\omega,d\tau\}$ or equivalently$(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (dashed lines in Fig.\ref{fig:gr_simulation})) are consistent with the corresponding the values of the injection parameters, indicated by plus signs \abhi{add markers in effective quantity plots}.
+
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms.png}\label{fig:nongr_waveform}
+	\caption{NonGR waveforms}
+\end{figure}
+
+\subsection{Simulations using NR signals}
+
+\iffalse
 \abhi{As part of review we had developed the infrastructure to make non-GR waveforms using pSEOBNRv4HM, and running LALInference on it.
 We had specifically chosen an injection with domega220 = dtau220  = 0.5 in zero-noise, and successfully recovered those frequencies thus demonstrating the robustness of the method in detecting deviations from GR.}
+\fi
 
@@
 
+The LIGO-Virgo Collaboration recently released their testing GR catalog containing results of this test for all events observed during the first half of O3 CITE, which passed a threshold for the total detector frame mass > XX and SNRs in the pre- and post-merger regions to be atleast YY.
+For reasons of computational expense the analyses of the relevant events during the LIGO-Virgo's first and second observing runs could not be included in the catalog, and are being presented here for the first time.
+We conduct analysis on the 5 relevant events that pass the above thresholds from the O1-O2 catalog CITE: GW150914, GW170104, GW170729, GW170814 and GW170823 \abhi{what about GW170809?}.
+Out of these, the analysis of GW170814 and GW170823 return uninformative posteriors.
+This is because of an insufficient SNR In the post-merger signal for these two events.
+For GW170814, this is because the total mass is slightly lower than the rest, thus coalescing in the region of the detector bandwidth dominated by shot-noise, while in the case of GW170823 the overall SNR of the entire signal is too low to reliably estimate $\{d\omega,d\tau\}$.
+For the three remaining signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $\{d\omega,d\tau\}$ in the top panel of Fig.\ref{fig:o1o2_events}.
+We also reconstruct the effective QNM parameters, $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ which are tabulated in Table \ref{tab:qnm_o1o2_results}.
+
+Among all GW signals detected so far, GW150914 is unique in it's loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
+The bottom panel of Fig.\ref{fig:o1o2_events} compares the results we obtain for GW150914 with previously published LIGO-Virgo results using a damped-sinusoid method, as well as the measurement reported using a non-spinning model in \paperone.
+The damped-sinusoid model assumed specific cutoff times (indicated in the curves on the bottom panel of Fig.\ref{fig:o1o2_events}) after the time corresponding to the peak amplitude as predicted by the best-fitting GR template waveform.
+Increasing time, decreasing SNR, wider posteriors, less-precise measurement.
+Compared to that we see when we incorporate the complete IMR version of the test, we utilise more SNR leading to tighter constraints.
+
 \begin{figure}
+	\includegraphics[width=0.4\textwidth]{figures/O1O2_realevents.png}
 	\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
-	\caption{include contours from pyRING}
+	\caption{O1-O2 analysis}\label{fig:o1o2_events}
 \end{figure}
-
-\abhi{Results obtained as part of the review on GW150914 and other O1-O2 events which are of relevance}
-\abhi{A plot showing the fractional quantities}
-\abhi{A table with absolute quantites similar to GWTC-2 TGR}
 
@@
 \bottomrule
-\end{tabular}
+\end{tabular}\label{tab:qnm_o1o2_results}
 
@@
 
+\iffalse
 \abhi{A small summary of the noise systematics study that was done for S190521g to show that the deviations seen were consistent with systematics due to noise.
 The study include 2 separate sections: in Gaussian noise, and in real LIGO-Virgo noise immediately adjacent to the actual event.}
+\fi
 
-%\begin{figure}[H]
-%	\includegraphics[width=0.4\textwidth]{figures/S190521g_noiseinjections.png}
-%	\caption{a single figure for both Gaussian and Real noise injections, color coded, to save space}
-%\end{figure}
+Tests of general relativity
+
+\begin{figure}[H]
+	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
+	\caption{a single figure for both Gaussian and Real noise injections, color coded, to save space}\label{fig:21g_systematics}
+\end{figure}
 
 We injected NRSur7dq4 signal using the MaxL parameters from EXP30, in 2.5 hours of data surrounding the event at: t0-1.5 hours, t0-1., t0-0.5, t0+0.5, t0+1.
-For 3 of the 5 noise realisations, corresponding to t0-1 hour, t0+0.5 hours, and t0+1.0 hour we recover a damping time similar to the actual event, whereas for a third case, t0-0.5 hours, we obtain a damping time consistent at the 90\% credible interval.
+For 3 of the 5 noise realisations, corresponding to t0-1 hour, t0+0.5 hours, and t0+1.0 hour we recover a damping time similar to the actual event, whereas for a third case, t0-0.5 hours, we obtain a damping time consistent at the 90\% credible interval (bottom panel of FIg.\ref{fig:21g_systematics}).
 L1-SNR goes down by more than 3 in some runs (maximum L1-SNR 12, minimum 9), indicative of how the noise variability is strongly affecting the recovered parameters.

### 2020-10-24 papers/intro_paper/intro_paper.tex
updated paper

@@
 
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave observations~\citep{GWTC-2} from the first half of their third observing run~\citep{O3reference}.
-Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $40$ gravitational wave events from the merger of compact objects like neutron stars and/or black holes (compact binary coalescences/CBCs).
-Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of gravitational wave astronomy, five years on from the first ever direct detection of gravitational waves on Earth, on September 14, 2015~\citep{abbott2016observation}.
+The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave (GW) observations~\citep{GWTC-2} from the first half of their third observing run (O3a)~\citep{O3reference}.
+Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $40$ GW events from the merger of compact objects like neutron stars and/or black holes (compact binary coalescences or CBCs).
+Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of GW astronomy, five years on from the first ever direct detection of GWs on Earth, on September 14, 2015~\citep{abbott2016observation}.
 \par
-Observation of gravitational waves have had significant astrophysical and cosmological implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}.
+Observation of GWs have had significant astrophysical and cosmological implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}.
 It has also allowed us to make statements in fundamental physics.
-Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}.
+Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity (GR)~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}.
 In GR, a CBC involving two black holes (a binary black hole (BBH) system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
-We have performed tests of gravitational wave generation and source dynamics, where we place bounds on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of gravitational wave propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{gw170104,samajdar2017projected} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{gw170814,isi2017probing}.
-We have also checked for consistency between different portions of the signal using estimates of final mass and spin~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and consistency of the residuals with interferometric noise~\citep{Ghonge:2020suv,gwtc1_tgr}.
+\par
+The LIGO-Virgo collaborations have also released a companion paper detailing their latest results of tests of GR using events from the catalogue, GWTC-2.
+The results include tests of GW generation and source dynamics, where bounds are placed on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of GW propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{gw170104,samajdar2017projected} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{gw170814,isi2017probing}.
+The paper also checks for consistency between different portions of the signal using estimates of final mass and spin~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and consistency of the residuals with interferometric noise~\citep{Ghonge:2020suv,gwtc1_tgr}.
 None of these tests report any departure from the predictions of GR.
-\abhi{Perhaps reframe this section in the contect of the O3a TGR companion paper}
 \par
-Tests of black hole ringdown and nature of the remnant object is an active field of research at the moment.
+The O3a TGR paper also details results on tests of black hole ringdown and nature of the remnant object, which is an active field of research at the moment.
 The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical black hole is completely described by two observables: mass and spin angular momentum.
@@
 In section~\ref{sec:method}, we define our testing GR framework in which we use that model to measure the complex QNM frequencies in a Bayesian formalism.
-Then in section~\ref{sec:results}, we demonstrate our method on real gravitational wave events, as well as simulated signals.
+Then in section~\ref{sec:results}, we demonstrate our method on real GW events, as well as simulated signals.
 Finally we provide a summary of our results and discuss future developments in section~\ref{sec:discussion}.
@@
 
-We initially demonstrate our method using simulated GR signals, with parameters similar to the two gravitational wave events, GW150914 CITE and GW190521 CITE.
+We initially demonstrate our method using simulated GR signals, with parameters similar to the two GW events, GW150914 CITE and GW190521 CITE.
 These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the signal-to-noise ratio pre- and post-merger return reliable parameter estimation results.
@@
 
-\begin{figure*}[h]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
 	\includegraphics[width=0.3\textwidth]{figures/GW150914_GW190521_simulated_frac.png}\includegraphics[width=0.56\textwidth]{figures/GW150914_GW190521_simulated_abs.png}\label{fig:gr_simulation}
@@
 \end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
 	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms.png}\label{fig:nongr_waveform}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
 	\includegraphics[width=0.4\textwidth]{figures/O1O2_realevents.png}
@@
 
-Tests of general relativity
+In order to investigate the
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[H]

### 2020-10-27 data/S190521g/rync_hypatia.sh
updated scripts/notebooks

@@ -1,4 +1,4 @@
-#pSEOBNRvrHM files
+#pSEOBNRv4HM files
 # C01 files
 ## GR
 rsync -ztave gsissh hypatia1.aei.mpg.de:/home/abhirup.ghosh/Documents/Work/spinqnm/runs/XLALSimInspiralChooseTDWaveformFromCache_runs/ligo_events/S190521g/C01/GR/cbcBayes/posterior_samples.dat pSEOBNRv4HM_GR_c01.dat

### 2020-10-27 data/S190521g/software_injections/copy_pEOB_injections_from_CIT.sh

@@ -1,0 +1,8 @@
+rsync -ztave ssh ldas-grid.ligo.caltech.edu:/home/richard.brito/public_html/LVC/projects/pEOBNRv2HM/O3/S190521g/injections_zeronoise/precession_220/1126259462.39-0/H1L1/posterior_samples.dat pEOB_injprec_zeronoise.dat
+rsync -ztave ssh ldas-grid.ligo.caltech.edu:/home/richard.brito/public_html/LVC/projects/pEOBNRv2HM/O3/S190521g/injections_zeronoise/precession_GR/1126259462.39-0/H1L1/posterior_samples.dat pEOB_injprec_zeronoise_GR.dat
+rsync -ztave ssh ldas-grid.ligo.caltech.edu:/home/richard.brito/public_html/LVC/projects/pEOBNRv2HM/O3/S190521g/injections_zeronoise/v4HM_220/1126259462.39-0/H1L1/posterior_samples.dat pEOB_injnoprec_zeronoise.dat
+rsync -ztave ssh ldas-grid.ligo.caltech.edu:/home/richard.brito/public_html/LVC/projects/pEOBNRv2HM/O3/S190521g/injections_zeronoise/v4HM_GR/1126259462.39-0/H1L1/posterior_samples.dat pEOB_injnoprec_zeronoise_GR.dat
+rsync -ztave ssh ldas-grid.ligo.caltech.edu:/home/richard.brito/public_html/LVC/projects/pEOBNRv2HM/O3/S190521g/injections/precession_220/1126259462.39-0/H1L1/posterior_samples.dat pEOB_injprec_w_noise.dat
+rsync -ztave ssh ldas-grid.ligo.caltech.edu:/home/richard.brito/public_html/LVC/projects/pEOBNRv2HM/O3/S190521g/injections/precession_GR/1126259462.39-0/H1L1/posterior_samples.dat pEOB_injprec_w_noise_GR.dat
+rsync -ztave ssh ldas-grid.ligo.caltech.edu:/home/richard.brito/public_html/LVC/projects/pEOBNRv2HM/O3/S190521g/injections/v4HM_220/1126259462.39-0/H1L1/posterior_samples.dat pEOB_injnoprec_w_noise.dat
[…]

### 2020-10-27 scripts/combine_samples.py

@@ -1,0 +1,260 @@
+#!/usr/bin/env python3
+import argparse
+import configparser
+import glob
+import sys
+import subprocess as sp
+import os
+import numpy as np
+import pandas as pd
+import h5py
+from loguru import logger
+
+
+def get_git_rev():
+    origdir = os.getcwd()
+    os.chdir(os.path.dirname(__file__))
+    git_rev = sp.check_output("git rev-parse HEAD", shell=True).strip().decode()
+    try:
+        sp.check_call("git diff --quiet", shell=True)
+        status = "CLEAN"
+    except sp.CalledProcessError:
+        status = "DIRTY"
+    os.chdir(origdir)
+    return f"{git_rev}__{status}"
+
+
+def grab_webdir(ini_file):
+    config = configparser.ConfigParser(allow_no_value=True)
+    config.optionxform = str
+    config.read(ini_file)
+    return os.path.join(config.get("paths", "webdir"), "production_postproc")
+
+
+def get_extra_dead_chains(path):
+    """Get the extra chains which may have died"""
+    logger.info("Gathering dead or completed chains")
+    dead_chains = glob.glob("{}/*.hdf5".format(path))
+    chain_list = []
+    for chain in dead_chains:
+        try:
+            fp = h5py.File(chain, "r")
+            tmp = fp["/lalinference/lalinference_mcmc/posterior_samples"]
+            len_samples = len(tmp)
+            if len_samples > 400:
+                chain_list.append(chain)
+            fp.close()
+        except:
+            continue
+    logger.info(
+        "We have collected {} dead/completed chains that have >400 samples".format(
+            len(chain_list)
+        )
+    )
+    return chain_list
+
+
+def sanity_check_chains(combined_chains):
+    """Some infinite temp chains occassioanly seem to have a logpost of -np.inf,
+    which casuses the downsampling using deltaLogP to fail. Filter out these 
+    chains here
+    Also check if the length of the chains is below 200 and if it is, reject them.
+    This helps guard against very short chains that failed early on and may cause
+    cbcBayesMCMC2Pos to fail.
+    """
+    logger.info("Sanity checking the chains for infinite logpost")
+    final_list = []
+    for chain in combined_chains:
+        flag = False
+        fp = h5py.File(chain, "r")
+        tmp = fp["/lalinference/lalinference_mcmc"]
[…]

### 2020-10-27 scripts/compute_final_samples.py

@@ -15,6 +15,7 @@ from optparse import OptionParser
 import corner
 import imrtgrutils_final as tgr
 import argparse
+import glob
 
 # Module for confidence calculations
 class confidence(object):
@@ -85,7 +86,10 @@ if __name__ == '__main__':
   ## Read (m1, m2, a1z, a2z, domega, dtau) posterior samples
   ##############################################################################
 
-  data = np.genfromtxt(post_loc + '/posterior_samples.dat', names=True, dtype=None)
+  try:
+  	data = np.genfromtxt(post_loc + '/posterior_samples.dat', names=True, dtype=None)
+  except IOError:
+	data = np.genfromtxt(glob.glob(post_loc + '/*.dat')[0], names=True, dtype=None)
   if ('mf_evol' in data.dtype.names) and ('af_evol' in data.dtype.names):
   	mf, af, m1, m2, a1z, a2z, domega, dtau = data['mf_evol'], data['af_evol'], data['m1'], data['m2'], data['a1z'], data['a2z'], data['domega220'], data['dtau220']
   elif ('mf' in data.dtype.names) and ('af' in data.dtype.names):

### 2020-10-27 scripts/compute_sigmalm0_SimIMREOBGenerateQNMFreqV2.py

@@ -61,13 +61,13 @@ if __name__ == '__main__':
 
     omegalm0SI_GR, taulm0SI_GR = get_sigmalm0SI_GR(m1, m2, a1z, a2z, lm)
 
-    print 'omega_GR (Hz) values:', omegalm0SI_GR
-    print 'freq_GR = omega_GR/2pi (Hz) values', omegalm0SI_GR/(2*pi)
-    print 'tau_GR (ms) values:', taulm0SI_GR*1000.
+    #print 'omega_GR (Hz) values:', omegalm0SI_GR
+    #print 'freq_GR = omega_GR/2pi (Hz) values', omegalm0SI_GR/(2*pi)
+    #print 'tau_GR (ms) values:', taulm0SI_GR*1000.
 
     omegalm0SI_modGR, taulm0SI_modGR = get_sigmalm0SI_modGR(omegalm0SI_GR, taulm0SI_GR, domega220, dtau220)
 
-    print 'omega_modGR (Hz) values:', omegalm0SI_modGR
-    print 'freq_modGR = omega_modGR/2pi (Hz) values', omegalm0SI_modGR/(2*pi)
-    print 'tau_modGR (ms) values:', taulm0SI_modGR*1000.
+    #print 'omega_modGR (Hz) values:', omegalm0SI_modGR
+    #print 'freq_modGR = omega_modGR/2pi (Hz) values', omegalm0SI_modGR/(2*pi)
+    #print 'tau_modGR (ms) values:', taulm0SI_modGR*1000.
 

### 2020-10-27 scripts/sanity_check_chains.py

@@ -1,0 +1,52 @@
+import numpy as np
+import glob
+import h5py
+from optparse import OptionParser
+
+def sanity_check_chains(combined_chains):
+    """Some infinite temp chains occassioanly seem to have a logpost of -np.inf,
+    which casuses the downsampling using deltaLogP to fail. Filter out these
+    chains here
+    Also check if the length of the chains is below 200 and if it is, reject them.
+    This helps guard against very short chains that failed early on and may cause
+    cbcBayesMCMC2Pos to fail.
+    """
+    #logger.info("Sanity checking the chains for infinite logpost")
+    final_list = []
+    rejected_list = []
+    for chain in combined_chains:
+        flag = False
+        fp = h5py.File(chain, "r")
+        tmp = fp["/lalinference/lalinference_mcmc"]
+        cold_samples = fp["/lalinference/lalinference_mcmc/posterior_samples"][()]
+        if len(cold_samples) < 200:
+            continue
+        for i in range(1, 8):
+            data = fp["/lalinference/lalinference_mcmc/chain_{:02d}".format(i)]
+            logpost = data["logpost"]
+            if (len(np.where(logpost > -1e8)[0]) / len(logpost)) < 0.99:
+		rejected_list.append(chain)
+                flag = True
+                break
+        if not flag:
+            final_list.append(chain)
+        fp.close()
+    #logger.info(
+    #    "Out of {} chains we have rejected {} chains due to logpost issues".format(
+    #        len(combined_chains), len(combined_chains) - len(final_list)
+    #    )
+    #)
+    return final_list, rejected_list
+
+
+if __name__ == "__main__":
+
+    parser = OptionParser()
+    parser.add_option("-p", "--post-loc", dest="post_loc", help="path to directory containing the cbcBayesPostProc posterior_samples.dat output")
+    (options, args) = parser.parse_args()
+    post_loc = options.post_loc
+
+    combined_chains = glob.glob(post_loc + "/combine*")
+    final_list, rejected_list = sanity_check_chains(combined_chains)
+
+    print (' '.join(final_list))

### 2020-10-27 papers/intro_paper/intro_paper.tex
updated paper

@@
 
+\subsubsection{Test of the No hair theorem}
+
+We provide a simple demonstration of a test of the no-hair theorem using our model.
+As described in the introduction, any test of the no-hair theorem of black holes would need to involve the independent measurements of (at least) two different QNMs.
+We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning binary black hole with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$.
+We choose an asymmetric system to increase the SNR in the higher modes.
+We also rescale the distance and orientation of the binary such that the total SNR of the signal is 75.
+Based on the LIGO-Virgo observations during  O3, such asymmetric and loud signals are no longer just a theoretical prediction but quite the possibility at design sensitivities CITE of these detectors.
+Using the signal, we attempt to measure the QNM frequencies corresponding to the zeroeth overtone of the $(2,\pm 2)$ and $(3,\pm 3)$ modes~\ref{fig:nohair_sxs}.
+We explore two cases, where we fix either one of the $(2,\pm 2)$ or $(3,\pm 3)$ frequency and damping time, ie, $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ or $(f_{330}^{\text{eff}}, \tau _{330}^{\text{eff}})$ fixed at their GR predictions and estimating the other pair.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+	%\includegraphics[width=0.3\textwidth]{figures/GW150914_GW190521_simulated_frac.png}\includegraphics[width=0.56\textwidth]{figures/GW150914_GW190521_simulated_abs.png}
+	\label{fig:nohair_sxs}
+	\caption{SXS:BBH:0166. 220/330 measurement}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\iffalse
+\abhi{As part of review we had developed the infrastructure to make non-GR waveforms using pSEOBNRv4HM, and running LALInference on it.
+We had specifically chosen an injection with domega220 = dtau220  = 0.5 in zero-noise, and successfully recovered those frequencies thus demonstrating the robustness of the method in detecting deviations from GR.}
+\fi
+
 \subsection{Simulations using nonGR signals}
@@
 We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}.
-The posterior probability distributions on $\{d\omega,d\tau\}$ or equivalently$(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (dashed lines in Fig.\ref{fig:gr_simulation})) are consistent with the corresponding the values of the injection parameters, indicated by plus signs \abhi{add markers in effective quantity plots}.
+The posterior probability distributions on $\{d\omega,d\tau\}$ or equivalently $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (dashed lines in Fig.\ref{fig:gr_simulation})) are consistent with the corresponding the values of the injection parameters, indicated by plus signs \abhi{add markers in effective quantity plots}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Simulations using NR signals}
-
-\iffalse
-\abhi{As part of review we had developed the infrastructure to make non-GR waveforms using pSEOBNRv4HM, and running LALInference on it.
-We had specifically chosen an injection with domega220 = dtau220  = 0.5 in zero-noise, and successfully recovered those frequencies thus demonstrating the robustness of the method in detecting deviations from GR.}
-\fi
 
@@
 
+\iffalse
 \abhi{A comparison with pyRING}
 \abhi{damped sinusoid results}
+\fi
 

### 2020-11-09 papers/intro_paper/intro_paper.tex
more on waveform model

@@
 In the observer's frame, the GW polarizations can be written as 
-$h_+(\iota,\varphi;t ) - i h_\times(\iota,\varphi;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi)\, h_{\ell m}(t)$, where $\iota$ denotes the inclination angle computed with respect to the direction perpendicular to the orbital plane, $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
-The SEOBNR model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown SEOBNR waveform is schematically given by $h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{
-    match}^{\ell m})$, where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown phase.
 %
+\begin{equation}
+h_+(\iota,\varphi;t ) - i h_\times(\iota,\varphi;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi)\, h_{\ell m}(t)\,,
+\end{equation}
+%
+where $\iota$ denotes the inclination angle computed with respect to the direction perpendicular to the orbital plane, $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
+The SEOBNR model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
+For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown SEOBNR waveform is schematically given by
+%
+\begin{equation}
+h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
+\end{equation}
+where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown phase.
 The merger-ringdown SEOBNR modes read~\citep{Bohe:2016gbl,Cotesta:2018fcv}
@@
 \label{RD}
-  h_{\ell m}^\mathrm{merger-RD}(t) = \nu A_{\ell m}(t) e^{i\phi_{\ell m} (t)}\,
-  e^{-i\sigma_{\ell m0} (t-t_\mathrm{match}^{\ell m})} \quad t \geq t_{\rm match}^{\ell m}\,,
+h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
 \end{equation}
 %
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = \omega_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
-We denote the oscillation frequencies by $\omega_{\ell m  0}\equiv \Re(\sigma_{\ell m0})$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0})$.
-The explicit expressions for the amplitudes $A_{\ell m}(t)$ and phases $\phi_{\ell m} (t)$ can be found in Ref.~\citep{Cotesta:2018fcv}, and are chosen such that the functions $A_{\ell  m}$ and $\phi_{\ell  m}$ are of class $C^1$ at $t=  t_{\rm match}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge SEOBNR waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
+where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
+We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
+The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
+%
+\begin{equation}
+\label{eq:ansatz_amp}
+\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
+\end{equation}
+%
+\begin{equation}
+\label{eq:ansatz_phase}
+\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
+\end{equation}
+%
+where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
+The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
+are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge SEOBNR waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
+This allows to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
+% in terms of $c_{1,f}^{\ell   m},\ c_{2,f}^{\ell m},\ \sigma^\textrm{R}_{\ell m},\ |h_{\ell    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell  m})|,\ \partial_t|h_{\ell    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|$ as
+\begin{align} 
+c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
+    m} \nu} \big[ \partial_t|h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
+    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
+    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
+c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
+    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
+    m} \nu} \big[ \partial_t|h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
+    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
+    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber   
+\end{align}
+and $d_{1,c}^{\ell m}$ as
+\begin{align}    
+d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
+      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
+\end{align}
+%
+where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
+The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
+Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
 
@@
 Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values (henceforth, pSEOBNR model).
-We note that when leaving $\sigma_{\ell m}$ to vary freely, the amplitudes $A_{\ell m}(t)$ and phases $\phi_{\ell m} (t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies (see~\citep{Cotesta:2018fcv}).
+We note that when leaving $\sigma_{\ell m}$ to vary freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies, as can be seen from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$.
 
-For the specific applications of this paper, we will normally only allow either $\sigma_{220}$ or $\sigma_{330}$ to vary, while keeping all the other modes to coincide with GR.
+For the specific applications of this paper, we will normally only allow either $\sigma_{220}$ and/or $\sigma_{330}$ to vary, while keeping all the other modes to coincide with GR.
 However the model can be easily used to measure any QNM complex frequency available in the waveform.

### 2020-11-11 papers/intro_paper/intro_paper.tex
added abstract

@@
 \newcommand*{\paramestscale}{0.455}
+\newcommand{\df}[1]{\delta f_{\text{#1}}}
+\newcommand{\dt}[1]{\delta \tau_{\text{#1}}}
+\newcommand{\fngr}[1]{f_{\text{#1}}}
+\newcommand{\tngr}[1]{tau_{\text{#1}}}
+%\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
+%\newcommand{\tgr}[1]{\tau ^{\text{GR}_{\text{#1}}}
 
@@
 
-\title{pSEOBNRv4HM}
+\title{Black hole spectroscopy using gravitational wave signals from the inspiral, merger and ringdown of binary black holes}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+\begin{abstract}
+The no-hair conjecture in general relativity states that the properties of a Kerr black hole are completely described by its mass and spin angular momentum.
+As a consequence, the complex quasi-normal-mode (QNM) frequencies of a binary black hole ringdown can be uniquely determined by the mass and spin of the remnant object.
+Conversely, measurement of the QNM frequencies could be a independent test of the no-hair conjecture.
+This paper outlines a test of the no-hair conjecture by measuring the complex QNM frequencies of a binary black hole ringdown within the framework of, for the first time, a spinning inspiral-merger-ringdown waveform model, thereby using the entire signal power and removing dependency on the predicted or estimated start time of the proposed ringdown.
+We further demonstrate the robustness of the test against modified gravitational wave signals with a ringdown different from what general relativity predicts for Kerr black holes.
+The method was used to analyse the properties of the merger remnants for the events observed by LIGO-Virgo in the first half of their third observing run (O3a) in the latest LIGO-Virgo publication.
+In this paper, for the first time, we analyse the gravitational wave events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a.
+The joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dt{220} = YY \pm$ are the strongest constraints yet using this method.
+Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the gravitational wave event on the results of this test.
+\end{abstract}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 \maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%
-% Abstract
-%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-11-11 papers/intro_paper/intro_paper.tex
updated introduction, waveform model and bayesian PE sections in the paper

@@
 \newcommand{\bxi}{\bm{\xi}}
+\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
+\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
 \newcommand{\bzeta}{\bm{\zeta}}
@@
 \newcommand{\df}[1]{\delta f_{\text{#1}}}
-\newcommand{\dt}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f_{\text{#1}}}
-\newcommand{\tngr}[1]{tau_{\text{#1}}}
-%\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
-%\newcommand{\tgr}[1]{\tau ^{\text{GR}_{\text{#1}}}
+\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
+\newcommand{\fngr}[1]{f ^{\text{nGR}}_{\text{#1}}}
+\newcommand{\taungr}[1]{\tau ^{\text{nGR}}_{\text{#1}}}
+\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
+\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
+\newcommand{\pSEOB}{\texttt{pSEOBNR}}
+\newcommand{\SEOB}{\texttt{SEOBNR}}
 
@@
 
-\title{Black hole spectroscopy using gravitational wave signals from the inspiral, merger and ringdown of binary black holes}
+\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from the inspiral, merger and ringdown of binary black holes}
 
@@
 In this paper, for the first time, we analyse the gravitational wave events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a.
-The joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dt{220} = YY \pm$ are the strongest constraints yet using this method.
+The joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method.
 Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the gravitational wave event on the results of this test.
@@
 The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave (GW) observations~\citep{GWTC-2} from the first half of their third observing run (O3a)~\citep{O3reference}.
-Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $40$ GW events from the merger of compact objects like neutron stars and/or black holes (compact binary coalescences or CBCs).
+Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $50$ GW events from the merger of compact objects like neutron stars and/or black holes, collectively called compact binary coalescences (CBCs).
 Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of GW astronomy, five years on from the first ever direct detection of GWs on Earth, on September 14, 2015~\citep{abbott2016observation}.
@@
 \par
-The LIGO-Virgo collaborations have also released a companion paper detailing their latest results of tests of GR using events from the catalogue, GWTC-2.
+The LIGO-Virgo collaborations have also released a companion paper detailing their latest results of tests of GR using events from the catalogues GWTC-2 CITE and GWTC-1 CITE.
 The results include tests of GW generation and source dynamics, where bounds are placed on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of GW propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{gw170104,samajdar2017projected} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{gw170814,isi2017probing}.
-The paper also checks for consistency between different portions of the signal using estimates of final mass and spin~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and consistency of the residuals with interferometric noise~\citep{Ghonge:2020suv,gwtc1_tgr}.
+The paper also checks for consistency between different portions of the signal using estimates of predicted mass and spin of the remnant object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and consistency of the residuals with interferometric noise~\citep{Ghonge:2020suv,gwtc1_tgr}.
 None of these tests report any departure from the predictions of GR.
 \par
-The O3a TGR paper also details results on tests of black hole ringdown and nature of the remnant object, which is an active field of research at the moment.
+The LIGO-Virgo O3a testing GR paper also details results on tests of black hole ringdown and nature of the remnant object, which is an active field of research at the moment.
 The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical black hole is completely described by two observables: mass and spin angular momentum.
@@
 Furthermore, the post-merger signal of a BBH coalescence transitions from a non-linear to a linear regime where the description of the signal as a QNM spectrum becomes appropriate~\citep{}.
-The ringdown start time isn't a clearly defined quantity and has been explored in detail in~\citep{Bhagwat:2017tkm}.
+The ringdown start time is not a clearly defined quantity and has been explored in detail in~\citep{Bhagwat:2017tkm}.
 In other works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a free parameter to be estimated directly from the data.
@@
 An independent approach to black hole spectroscopy, based on a full-signal analysis, was outlined in~\citep{Brito:2018rfr} (henceforth referred to as \paperone).
-\abhi{describe underlying GR model; parameterisation; advantages over other methods; highlight spin}
-
 Unlike methods that focus on the post-merger signal, it describes a framework in which a complete inspiral-merger-ringdown (IMR) waveform model is used to measure the complex QNM frequencies.
@@
 While \paperone presented the method in the context of a non-spinning waveform model, we extend the analysis to the case with black holes spins in the current paper.
-All astrophysical black holes are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties.
+All astrophysical black holes are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties CITE \cite{paper_showing_systematics_from_ignoring_spin}.
 \par
@@
 Section~\ref{sec:model} describes our parametrised IMR waveform model.
-In section~\ref{sec:method}, we define our testing GR framework in which we use that model to measure the complex QNM frequencies in a Bayesian formalism.
+In section~\ref{sec:method}, we define our testing GR framework in which we use that model to measure the complex QNM frequencies within a Bayesian formalism.
 Then in section~\ref{sec:results}, we demonstrate our method on real GW events, as well as simulated signals.
@@
 Therefore this waveform model provides a very accurate and faithful semi-analytic description of the inspiral, merger and ringdown phases.
-Henceforth we will denote this model by SEOBNR for short.
+Henceforth we will denote this model by $\SEOB$ for short.
 
@@
 where $\iota$ denotes the inclination angle computed with respect to the direction perpendicular to the orbital plane, $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
-The SEOBNR model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown SEOBNR waveform is schematically given by
+The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
+For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
 %
@@
 where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown phase.
-The merger-ringdown SEOBNR modes read~\citep{Bohe:2016gbl,Cotesta:2018fcv}
+The merger-ringdown $\SEOB$ modes read~\citep{Bohe:2016gbl,Cotesta:2018fcv}
 %
@@
 The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge SEOBNR waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
+are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
 This allows to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
@@
 
-In the SEOBNR model constructed in Ref.~\cite{Cotesta:2018fcv}, the complex frequencies $\sigma_{\ell m 0}$  are expressed in terms of the final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the latter are related to the BBH's component masses and spins through NR--fitting-formulas obtained in GR~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values (henceforth, pSEOBNR model).
+In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the complex frequencies $\sigma_{\ell m 0}$  are expressed in terms of the final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the latter are related to the BBH's component masses and spins through NR--fitting-formulas obtained in GR~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values (henceforth, $\pSEOB$ model).
+The $\pSEOB$ model uses a parameterised version of the $\SEOB$ model where the frequency and the damping time of the ${\ell m 0}$ mode, i.e, $(f_{\ell m 0}, \tau _{\ell m 0})$ is defined through fractional deviations from the corresponding GR values, i.e., the predictions of the QNM frequencies obtained using the fits~\cite{Taracchini:2013rva,Hofmann:2016yih}:
+
+\begin{eqnarray}
+f_{\ell m 0}^{\text{nGR}} &:=& f_{\ell m 0}^{\text{GR}} (1 + \delta f_{\ell m 0}) \\
+\tau _{\ell m 0}^{\text{nGR}} &:=& \tau _{\ell m 0}^{\text{GR}} (1 + \delta \tau_{\ell m 0})
+\end{eqnarray}
+
+where $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$ are the fractional deviations in the frequency and damping time, respectively.
 We note that when leaving $\sigma_{\ell m}$ to vary freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies, as can be seen from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$.
-
-For the specific applications of this paper, we will normally only allow either $\sigma_{220}$ and/or $\sigma_{330}$ to vary, while keeping all the other modes to coincide with GR.
-However the model can be easily used to measure any QNM complex frequency available in the waveform.
+\footnote{For the results discussed in this paper, we restrict ourselves to the $(\ell m) = (2,2)$ and $(3,3)$ modes.
+Most of the high-mass events, for which this test is most appropriate, observed by LIGO-Virgo are consistent with nearly-equal-mass face-on/off binaries for which power in the subdominant modes is not enough to attempt to measure more than two QNM frequencies at once.
+Hence, all the other $(\ell m)$ modes are fixed at their GR predictions.}
 
@@
 
-A gravitational waveform from the (quasi-circular) coalescence of two black holes is completely described in GR by a set \textit{intrinsic} parameters, $\bxi$: the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the initial binary and a reference time and phase $t_c, \phi_c$ respectively; and a set of \textit{extrinsic} parameters, $\btheta$: the location of the binary given by the right ascension, $\alpha$, declination,$\delta$ and the luminosity distance, $d_L$, and its orientation described through the inclination of the binary $\iota$ and its polarisation $\psi$.
-Also allowing for additional degrees of freedom $\bzeta$ like the complex QNM frequencies described in section \ref{sec:model}, one can then use a Bayesian formalism to obtain a posterior probability density function on the combined parameter set $\blambda = \{\bxi, \btheta, \bzeta\}$:
+A gravitational wave signal from the (quasi-circular) coalescence of two black holes is completely described in GR by a fixed set of parameters, $\bxigr$.
+These can be grouped into the \emph{intrinsic} parameters: the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the initial binary and a reference time and phase $t_c, \phi_c$ respectively; and the \emph{extrinsic} parameters: the location of the binary given by the right ascension, $\alpha$, declination,$\delta$ and the luminosity distance, $d_L$, and its orientation described through the inclination of the binary $\iota$ and its polarisation $\psi$.
+The parametrised model described in ~\ref{sec:model}, $\pSEOB$, introduces an additional set of non-GR parameters, $\bxingr$, which essentially consist of the fractional deviations in the frequency and damping time corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
+One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$ and any other information used in the analysis $I$:
 
 \begin{equation}
-p(\blambda | d, H, I) \propto P(\blambda | H,I) \mathcal{L}(d | \blambda, H, I)
+P(\blambda | d, \mathcal{H}, I) = \frac{P(\blambda | \mathcal{H}, I) \, \mathcal{L}(d | \blambda, \mathcal{H}, I)}{P(d|\mathcal{H}, I)},
+\label{eq:Bayes_theorem}
+\end{equation}
+where $P(\blambda | \mathcal{H}, I)$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H}, I)$ is called the \emph{likelihood} function.
+The denominator is a normalization constant $P(d|\mathcal{H}, I) := \int P(\blambda | \mathcal{H}, I) \, \mathcal{L}(d | \blambda, \mathcal{H}, I) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
+In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density $S_n(f)$.
+The likelihood function can consequently be defined as:
+
+\begin{equation}
+\mathcal{L}(d | \blambda, \mathcal{H}, I) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
+\label{eq:likelihood}\end{equation}
+where $\langle . | . \rangle$ is the following noise-weighted inner product:
+\begin{equation}
+\langle A | B \rangle := \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
+\label{eq:nwip}
+\end{equation}
+$\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and a $^*$ denotes complex conjugation.
+The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the gravitational wave detector.
+We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas${f_\mathrm{low}}$ is dictated by the response of the gravitational detector to low-frequency seismic noise.
+Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H}, I)$ in equation~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-Chain Monte-Carlo~\cite{xxx} or Nested Sampling~\cite{xxx}.
+For this paper, we use the lalinferencemcmc~\cite{xx} and bilby codes that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
+
+Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H}, I)$, we can marginalise over the \emph{nuisance} parameters, to obtain the marginalised posterior probability density function over the QNM parameters $\bxingr$:
+
+\begin{equation}
+P(\bxingr | d, \mathcal{H}, I)= \int P(\blambda | d, \mathcal{H}, I) d\bxigr
 \end{equation}
 
-where $P(\blambda | H,I)$ is the prior probability density function and $\mathcal{L}(d | \blambda, H, I)$ is the likelihood of obtaining the data for a given choice of the parameter set $\blambda$.
-We assume the hypothesis $H$ to be our waveform model described in section \ref{sec:model} and $I$ to be any other information assumed during the analysis.
-
-Given the full-dimensional posterior probability density function $p(\blambda | d, H, I)$, we can marginalise over the \emph{nuisance} parameters, to obtain the marginalised posterior probability density function on our QNM parameters $\bzeta$, as:
-
-\begin{equation}
-p(\bzeta | d, H, I) = \int p(\blambda | d, H, I) d\bxi d\btheta
-\end{equation}
-
-An example of a posterior distribution on $\bzeta$Throughout our analysis, we assume the noise in the detector to be well-approximated by the Gaussian random process with a fixed power spectral density.
-This allows us to define a Gaussian likelihood function $\mathcal{L}(d | \blambda, H, I)$, which we stochastically sample over using either a Markhov-Chain-Monte-Carlo based algorithm implemented in the LIGO Algorithms Library.
+For most of the results discussed in this paper, we would restrict ourselves to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes.
+In those cases we would assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or  $ \{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes are fixed at their GR predictions, i.e., $\delta f_{\ell m 0}) = \delta \tau_{\ell m 0} = 0$.
+This is because, for most of the high-mass events we find most appropriate for this test, the LIGO-Virgo observations are consistent with nearly-equal-mass face-on/off black hole binaries for which power in the subdominant modes is not enough to attempt to measure more than two QNM frequencies at once.
 

### 2020-11-16 papers/intro_paper/intro_paper.tex
added plots

@@
 \usepackage{float}
+\usepackage[bottom]{footmisc}
 
@@
 \begin{eqnarray}
-f_{\ell m 0}^{\text{nGR}} &:=& f_{\ell m 0}^{\text{GR}} (1 + \delta f_{\ell m 0}) \\
-\tau _{\ell m 0}^{\text{nGR}} &:=& \tau _{\ell m 0}^{\text{GR}} (1 + \delta \tau_{\ell m 0})
+f_{\ell m 0}^{\text{nGR}} &:=& f_{\ell m 0}^{\text{GR}} (1 + \delta f_{\ell m 0})\label{eq:nongr_freqs_a} \\ 
+\tau _{\ell m 0}^{\text{nGR}} &:=& \tau _{\ell m 0}^{\text{GR}} (1 + \delta \tau_{\ell m 0}) \label{eq:nongr_freqs_b}
 \end{eqnarray}
-
-where $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$ are the fractional deviations in the frequency and damping time, respectively.
+where $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$ are the fractional deviations in the frequency and damping time, respectively, from the corresponding GR predictions.
+The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are constructed using numerical relativity predictions of the mass and spin of the remnant object, starting from estimates of the masses and spins of the initial binary:
+\begin{eqnarray}
+f_{\ell m 0}^{GR} = f_{\ell m 0}^{GR}(M_f, a_f) = f_{\ell m 0}^{GR}(m_1, m_2, \bs1, \bs2 ) \\
+\tau_{\ell m 0}^{GR} = \tau_{\ell m 0}^{GR}(M_f, a_f) = \tau_{\ell m 0}^{GR}(m_1, m_2, \bs1, \bs2 )
+\end{eqnarray}
+where we go from the second to the third step in both equation through the numerical relativity fits: $M_f = M_f(m_1, m_2, \bs1, \bs2)$ and $a_f = a_f(m_1, m_2, \bs1, \bs2)$.
+$M_f, a_f$ are the mass and spin of the remnant black while are determined from the initial masses and spins using analytical fits to numerical relativity simulations described above.
 We note that when leaving $\sigma_{\ell m}$ to vary freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies, as can be seen from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$.
@@
 The parametrised model described in ~\ref{sec:model}, $\pSEOB$, introduces an additional set of non-GR parameters, $\bxingr$, which essentially consist of the fractional deviations in the frequency and damping time corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
+Also, since the underlying GR model, $\SEOB$ is aligned-spin, i.e., the black holes are restricted to have spins parallel to the orbital angular momentum, the number of independent spin components reduce from 6 to 2.
+By convention we denote the direction of the orbital angular momentum to be the $z$-axis, and as a consequence, denote the spin components of the two black holes as $s_{1z}$ and $s_{2z}$, respectively.
 One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$ and any other information used in the analysis $I$:
@@
 In those cases we would assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or  $ \{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes are fixed at their GR predictions, i.e., $\delta f_{\ell m 0}) = \delta \tau_{\ell m 0} = 0$.
-This is because, for most of the high-mass events we find most appropriate for this test, the LIGO-Virgo observations are consistent with nearly-equal-mass face-on/off black hole binaries for which power in the subdominant modes is not enough to attempt to measure more than two QNM frequencies at once.
+This is because, for most of the high-mass events we find most appropriate for this test, the LIGO-Virgo observations are consistent with nearly-equal-mass face-on/off black hole binaries for which power in the subdominant modes is not enough to attempt to measure more than one, or at most QNM frequencies at once.
+
+\subsection{Priors}
+
+Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$.
+Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary.
+The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out.
+For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
+2015 LALInference paper).
+For our non-GR ringdown parameters, we assume uniform priors.
+This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}.
+For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
 
@@
 
-\iffalse
-\subsection{Priors}
+\subsection{Simulations using GR signals in Gaussian Noise}\label{ssec:gr_signal}
 
-Throughout our analysis we assume a completely uninformed prior in the component masses $m_1, m_2$, uniformly distributed in the range (XX,YY).
-Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation.
-Our prior on the distance varies as $d_L^2$ upto a distance of XX.
-For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
-2015 LALInference paper).
-For our non-GR ringdown parameters, we assume priors uniform in the range (XX,YY).
-For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
+First, we demonstrate our method on gravitational wave signals from BBH systems that are well described by GR.
+We inject simulated GW signals modellng inspiral, merger and ringdown of BBHs  into coloured Gaussian noise described by Advanced LIGO-Virgo design sensitivity in the high-power, zero-detuning configuration (ZDHP) CITE.
+In particular we choose parameters similar to two specific GW events, GW150914 CITE and GW190521 CITE.
+The details of the injections are provided in Table~\ref{tab:injection_values}.
+These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the signal-to-noise ratio pre- and post-merger return reliable parameter estimation results.
+To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, $\SEOB$ CITE (without allowing for deviations in the QNM parameters) to simulate our GW signal.
+And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the Advanced LIGO zero-detuned-high-power PSD CITE.
+As in the case of the actual detections, we consider a two-detector advanced LIGO network at Hanford and Livingston, having identical PSDs.
+The distance to the two simulated events is rescaled such that the SNR in the detector network is same as the actual event, i.e, 24 (14) for GW150914 (GW190521).
+Since (almost) equal-mass binaries like GW150914 and GW190521 observed at moderate high SNRs are not expected to have a loud ringdown signal, we restrict ourselves to estimating the frequency and damping time of the $(\ell m) = (2,2)$, i.e., $\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to their GR values.
 
-\fi
-
-\subsection{Simulations using GR signals}\label{ssec:gr_signal}
-
-We initially demonstrate our method using simulated GR signals, with parameters similar to the two GW events, GW150914 CITE and GW190521 CITE.
-These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the signal-to-noise ratio pre- and post-merger return reliable parameter estimation results.
-To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, SEOBNRv4HM CITE (without allowing for deviations in the QNM parameters) to simulate our GW signal.
-And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the Advanced LIGO zero-detuned-high-power PSD CITE.
-We find, as expected, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time, $\{d\omega,d\tau\}$ are consistent with zero (the solid curves in left panel of Fig.\ref{fig:gr_simulation}).
-The difference in the size of the posterior is due to the difference in the SNRs of the two events ($\sim 25$ for GW150914 as compared to $\sim 13$ for GW190521).
-One can then convert these fractional quantities into absolute quantities using the relations:
-
-\begin{eqnarray}
-f_{220}^{\text{eff}} &:=& f_{220}^{\text{GR}} (1 + \delta f_{220}) \\
-\tau _{220}^{\text{eff}} &:=& \tau _{220}^{\text{GR}} (1 + \delta \tau_{220})
-\end{eqnarray}
-
-and construct posterior distributions on these effective quantities, $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (solid lines in middle and right panels of Fig.\ref{fig:gr_simulation}).
-The GR quantities $(f_{220}^{\text{GR}}, \tau _{220}^{\text{GR}})$ are constructed using numerical relativity predictions of the mass and spin of the remnant object, starting from estimates of the masses and spins of the initial binary \abhi{add description of the contruction of GR quantities with details of NR fit formula}.
+We find, as one might expect, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time are consistent with zero (the left top panel in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
+The difference in the size of the posterior is due to the difference in the SNRs of the two events.
+One can then convert these fractional quantities into absolute quantities using the relations given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and construct posterior distributions on these effective quantities, $(\fngr{220}, \taungr{220})$ (the right top panel in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
 In each of these cases, recovered posterior are consistent with the GR predictions (as indicated by the plus signs).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Table for Injections
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-	\includegraphics[width=0.3\textwidth]{figures/GW150914_GW190521_simulated_frac.png}\includegraphics[width=0.56\textwidth]{figures/GW150914_GW190521_simulated_abs.png}\label{fig:gr_simulation}
-	\caption{final figure will contain a third set of contours for modGR recovered assuming GR to show bias. That run is ongoing.}
-\end{figure*}
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c| }
+ \hline
+ Event & $m_1 (\Mo)$ &  $m_1 (\Mo)$ & $a_{1z}$ & $a_{2z}$ & SNR \\ 
+ \hline
+ GW150914 & 38.53 & 33.40 & 0.0035 & -0.0440 & 25 \\ \label{tab:injection_values}
+ GW190521 & 152.20 & 120.41 & 0.0230 & -0.3864 & 14 \\ 
+ \hline
+\end{tabular}
+\caption{Details of the injection parameters, chosen to be similar to the actual GW events}
+\label{tab:injection_values}
+\end{center}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GW150914-like simulated signal
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_gr_ngr.png}
+	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (top panel) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (bottom panel) for an injection with initial parameters similar to GW150914 \ref{tab:injection_values}.
+The dark purple and grey points indicate the GR and modified GR signals respectively, when recovered using our $\pSEOB$ model.
+The two contours indicate the 50 and 90 \% credible levels, while the injected values are indicated by the '+' marker.
+The orange posterior probability distribution with the accompanying 90 \% credible level indicated in white corresponds to the biased measurement if our modGR signal had been estimated using the GR waveform model $SEOB$.
+}
+	\label{fig:GW150914_simulated_signal}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GW190521-like simulated signal
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_gr_ngr.png}
+	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (top panel) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (bottom panel) for an injection with initial parameters similar to GW190521 \ref{tab:injection_values}.
+The dark purple and grey points indicate the GR and modified GR signals respectively, when recovered using our $\pSEOB$ model.
+The two contours indicate the 50 and 90 \% credible levels, while the injected values are indicated by the '+' marker.
+The orange posterior probability distribution with the accompanying 90 \% credible level indicated in white corresponds to the biased measurement if our modGR signal had been estimated using the GR waveform model $SEOB$.
+}
+	\label{fig:GW190521_simulated_signal}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsubsection{Test of the No hair theorem}
+\subsection{Simulations using modified GR signals in Gaussian noise}
 
-We provide a simple demonstration of a test of the no-hair theorem using our model.
-As described in the introduction, any test of the no-hair theorem of black holes would need to involve the independent measurements of (at least) two different QNMs.
-We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning binary black hole with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$.
-We choose an asymmetric system to increase the SNR in the higher modes.
-We also rescale the distance and orientation of the binary such that the total SNR of the signal is 75.
-Based on the LIGO-Virgo observations during  O3, such asymmetric and loud signals are no longer just a theoretical prediction but quite the possibility at design sensitivities CITE of these detectors.
-Using the signal, we attempt to measure the QNM frequencies corresponding to the zeroeth overtone of the $(2,\pm 2)$ and $(3,\pm 3)$ modes~\ref{fig:nohair_sxs}.
-We explore two cases, where we fix either one of the $(2,\pm 2)$ or $(3,\pm 3)$ frequency and damping time, ie, $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ or $(f_{330}^{\text{eff}}, \tau _{330}^{\text{eff}})$ fixed at their GR predictions and estimating the other pair.
+To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger, and differ in their post-merger description.
+We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $\df{220} = \dtau{220} = 0.5$.
+In other words, we assume that the frequency and damping time of our non-GR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}).
+We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}.
+The posterior probability distributions on $(\df{220}, \dtau{220})$ or equivalently $(\fngr{220}, \taungr{220})$ (right panels in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}) are consistent with the corresponding the values of the injection parameters, indicated by plus signs.
+
+We additionally investigate the effects of erroneously assuming that an underlying modified GR signal can be well-described using GR.
+We do this by estimating the parameters of our modified GR signals using the GR waveform model $\SEOB$ instead of the parametrised $\pSEOB$.
+In such cases, we run the risk of biased pareameter estimates due to an incomplete understanding of the underlying signal.
+The resulting orange posterior probability distributions are shown in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}) with the corresponding 90 \% credible level in white.
+The results are interesting and distinctly different for the two events.
+For the GW150914-like modified GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (Fig.\ref{fig:GW150914_simulated_signal} lower panel) are consistent with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no deviations.
+In other words, if the actual signal had deviations as large as the 50 \% of the GR prediction, the analysis with $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
+However in the case of the GW190521-like modified GR signal, a simple GR analysis of the modified GR signal would have yielded measurements distinctly different from either of the two parametrised estimates: with and without deviations.
+The fact that the GW190521-like signal has a much lower SNR than GW150914 might be a possible reason for the the measurement of the final quantities to be more susceptible to noise.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-	%\includegraphics[width=0.3\textwidth]{figures/GW150914_GW190521_simulated_frac.png}\includegraphics[width=0.56\textwidth]{figures/GW150914_GW190521_simulated_abs.png}
-	\label{fig:nohair_sxs}
-	\caption{SXS:BBH:0166. 220/330 measurement}
-\end{figure*}
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms.png}
+	\caption{The gravitational strain $h(t)$ in the LIGO Hanford (top panel) and Livingston (bottom panel) detectors, for a GW150914-like event where the ringdown is described by GR (black solid lines), i.e., $\df{220} = \dtau{220} = 0$, and where the ringdown frequencies are modified from GR (dashed red lines), i.e., $\df{220} = \dtau{220} = 0.5$.
+The time is measured with respect to UTC:1126285216, which was assumed to be point at which the event merged.
+The signals are identical up to merger, but show a distinctly different ringdown.}
+	\label{fig:nongr_waveform}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\iffalse
-\abhi{As part of review we had developed the infrastructure to make non-GR waveforms using pSEOBNRv4HM, and running LALInference on it.
-We had specifically chosen an injection with domega220 = dtau220  = 0.5 in zero-noise, and successfully recovered those frequencies thus demonstrating the robustness of the method in detecting deviations from GR.}
-\fi
+\subsection{Test of the No hair theorem}\label{ssec:nohairtheorem}
 
-\subsection{Simulations using nonGR signals}
-
-To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger \abhi{be more specific}, and differ in their post-merger description.
-We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $d\omega =d\tau = 0.5$.
-In other words, we assume that the frequency and damping time of our nonGR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}).
-We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}.
-The posterior probability distributions on $\{d\omega,d\tau\}$ or equivalently $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (dashed lines in Fig.\ref{fig:gr_simulation})) are consistent with the corresponding the values of the injection parameters, indicated by plus signs \abhi{add markers in effective quantity plots}.
+Finally, we provide a simple demonstration of a test of the no-hair theorem using our model.
+As described in the introduction, any test of the no-hair theorem of black holes would need to involve independent measurements of (at least) two different QNMs.
+We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning binary black hole with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$.
+We choose an asymmetric system to increase the SNR in the higher modes.
+We also rescale the distance and orientation of the binary such that the total SNR of the signal in a network of three detectors, LIGO Hanford, Livingston and Virgo, is 75.
+The LIGO detectors are assumed to be in the ZDHP configuration as before, while the Virgo detector is assumed to be at design sensitivity CITE.
+Based on the LIGO-Virgo observations during O3a, such asymmetric and loud signals are no longer just a theoretical prediction but quite plausible at design sensitivities.
+Using the signal, we attempt to measure the QNM frequencies $(2,\pm 2)$ and $(3,\pm 3)$ modes together (Fig.~\ref{fig:nohair_sxs}).
+The fractional deviations in the estimates of the damping time and frequency of either mode is expected to be consistent with 0, as we indeed find in the left panel of Fig.~\ref{fig:nohair_sxs}.
+Consequently we find that the reconstructed quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330}, \taungr{330})$  are also consistent with the corresponding predictions for a BBH merger in GR.
+As a consequence, the information from these two independent measures correspond to a unique remnant object, which is completely described by its mass and spin angular momentum.
+For most of the events observed so far, the power in the $(3,\pm 3)$ has not been sufficient to measure it along with the $(2,\pm 2)$, or in fact, in its place.
+However, it might also be possible to combine information from multiple observation, as is likely over the coming few years of gravitational wave astronomy with the LIGO-Virgo detectors, to obtain meaningful constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[H]
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms.png}\label{fig:nongr_waveform}
-	\caption{NonGR waveforms}
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166_placeholder.png}	
+	\caption{\textcolor{red}{DEMO FIGURE; RUN ONGOING} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) respectively, for a numerical relativity signal corresponding to a BBH merger of $q=6$,  $M=84 \Mo$ and SNR $75$.
+The plus signs mark the GR predictions.}
+	\label{fig:nohair_sxs}
 \end{figure}
@@
 
-The LIGO-Virgo Collaboration recently released their testing GR catalog containing results of this test for all events observed during the first half of O3 CITE, which passed a threshold for the total detector frame mass > XX and SNRs in the pre- and post-merger regions to be atleast YY.
-For reasons of computational expense the analyses of the relevant events during the LIGO-Virgo's first and second observing runs could not be included in the catalog, and are being presented here for the first time.
-We conduct analysis on the 5 relevant events that pass the above thresholds from the O1-O2 catalog CITE: GW150914, GW170104, GW170729, GW170814 and GW170823 \abhi{what about GW170809?}.
-Out of these, the analysis of GW170814 and GW170823 return uninformative posteriors.
-This is because of an insufficient SNR In the post-merger signal for these two events.
-For GW170814, this is because the total mass is slightly lower than the rest, thus coalescing in the region of the detector bandwidth dominated by shot-noise, while in the case of GW170823 the overall SNR of the entire signal is too low to reliably estimate $\{d\omega,d\tau\}$.
-For the three remaining signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $\{d\omega,d\tau\}$ in the top panel of Fig.\ref{fig:o1o2_events}.
-We also reconstruct the effective QNM parameters, $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ which are tabulated in Table \ref{tab:qnm_o1o2_results}.
+The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during the first half of O3 CITE, which passed a threshold for the total detector frame mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$\abhi{confirm}.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template.
+We restricted ourselves to the high-mass events which are expected to be merger-ringdown dominated.
+However, since our method relies on doing a parameter estimation on the entire inspiral-merger-ringdown signal, we require the SNR to be beyond a certain threshold throughout the signal for reliable parameter estimation of the initial and final quantities.
+Fig.~\ref{fig:o1o2_events} contains three events from O3a, GW190519\_ 153544, GW190521\_ 074359, GW190910\_ 112807.
 
-Among all GW signals detected so far, GW150914 is unique in it's loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
+For the first time, in this paper, we present results on the relevant events from LIGO-Virgo's first and second observing runs, alongside the above events.
+Applying the same thresholds as above, we find three additional events which could be included in the analysis: GW150914, GW170104, GW170729 \abhi{would need to confirm the thresholds again, and see if GW170809 qualifies}.
+Regarding the other two high-mass events, GW170814 and GW170823 do not satisfy the SNR thresholds.
+For the three relevant signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $(\df{220}, \dtau{220})$ in Fig.\ref{fig:o1o2_events}.
+We also reconstruct the effective QNM parameters, $(\fngr{220}, \taungr{220})$ which are tabulated in Table~\ref{tab:qnm_o1o2_results}.
+
+Among all GW signals detected so far, GW150914 is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
 The bottom panel of Fig.\ref{fig:o1o2_events} compares the results we obtain for GW150914 with previously published LIGO-Virgo results using a damped-sinusoid method, as well as the measurement reported using a non-spinning model in \paperone.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% O1-O2 events
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[H]
-	\includegraphics[width=0.4\textwidth]{figures/O1O2_realevents.png}
-	\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
-	\caption{O1-O2 analysis}\label{fig:o1o2_events}
+\begin{figure}[h!]
+	\includegraphics[width=0.5\textwidth]{figures/O1O2_realevents.pdf}
+	%\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
+	\caption{The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions.
+We also plot the joint probability distribution obtained by multiplying the likelihoods of the $\{\df{220},\dtau{220}\}$ (black dashed line) \abhi{need to compute the joint likelihood.
+currently contains the hierarchical contour from the O3a TGR paper}}
+	\label{fig:o1o2_events}
 \end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GW150914
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+	\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
+	\caption{The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions.
+We also plot the joint probability distribution obtained by multiplying the likelihoods of the $\{\df{220},\dtau{220}\}$ (black dashed line) \abhi{need to compute the joint likelihood.
+currently contains the hierarchical contour from the O3a TGR paper}}
+	\label{fig:GW150914_real}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Finally, if we assume that the fractional deviations $(\df{220}, \dtau{220})$ take the same values in multiple events, we can assume the posterior of one event to be the prior for the next, and obtain a joint posterior probability distribution.
+For $N$ observations, where $P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j-th$ observation corresponding to the data set $d_j$, $j=1...N$, the joint posterior is given by:
+\begin{equation}
+P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
+\end{equation}
+where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220}, \dtau{220})$.
+However, since we assume the prior on $(\df{220}, \dtau{220})$ to be flat or uniform, the joint posterior is equal to the joint likelihood.
+
+We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalised distributions as black dashed lines in Fig.~\ref{fig:o1o2_events}.
+These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.
+\abhi{perhaps show 2 joint posteriors: only O3a and O3a+O1-O2 to explicitly show the tightening of the joint constraints by adding the O1-O2 events}
+
+\begin{table}
+\begin{center}
 \begin{tabular}{llllllll}
 \toprule
-Event & \multicolumn{3}{c}{Redshifted} & \hphantom{X} & \multicolumn{3}{c}{Redshifted} \\
-& \multicolumn{3}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{3}{c}{damping time [ms]} \\[0.075cm]
+Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
+& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
 \cline{2-4}
 \cline{6-8}
-& IMR & DS & pSEOB & \hphantom{X} & IMR & DS & pSEOB \\
+& IMR  & pSEOB & \hphantom{X} & IMR  & pSEOB \\
 \midrule
@@
 $249^{+9}_{-7}$ &
-$247^{+14}_{-16}$ &
 $-$ &
@@
 $4.1^{+0.3}_{-0.2}$ &
-$4.8^{+3.7}_{-1.9}$ &
 $-$
@@
 $286^{+16}_{-27}$ &
-$228^{+71}_{-102}$ &
 $-$ &
@@
 $3.5^{+0.4}_{-0.3}$ &
-$3.6^{+36.2}_{-2.1}$ &
 $-$
@@
 $161^{+13}_{-14}$ &
-$148^{+11}_{-11}$ &
 $-$ &
@@
 $7.8^{+1.8}_{-1.5}$ &
-$10.4^{+8.2}_{-4.7}$ &
-$-$
-\\[0.075cm]
-
-GW170814 &
-$295^{+13}_{-12}$ &
-$527^{+340}_{-332}$ &
-$-$ &
-\hphantom{X} &
-$3.7^{+0.3}_{-0.2}$ &
-$25.1^{+22.2}_{-19.0}$ &
-$-$
-\\[0.075cm]
-
-GW170823 &
-$199^{+14}_{-16}$ &
-$222^{+664}_{-62}$ &
-$-$ &
-\hphantom{X} &
-$5.4^{+1.0}_{-0.6}$ &
-$13.4^{+31.8}_{-9.8}$ &
 $-$
@@
 \bottomrule
-\end{tabular}\label{tab:qnm_o1o2_results}
+\end{tabular}
+\caption{}
+\label{tab:qnm_o1o2_results}
+\end{center}
+\end{table}
 
-\subsection{Results on noise systematics study}
+\section{Discussion}\label{sec:discussion}
+
+\iffalse
+\abhi{A comparison with pyRING}
+\abhi{damped sinusoid results}
+\fi
+
+\pagebreak
+
+\appendix
+\section{Study of noise syetematics on ringdown measurements}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[H]
+\begin{figure}
 	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
@@
 
-\section{Discussion}\label{sec:discussion}
-
-\iffalse
-\abhi{A comparison with pyRING}
-\abhi{damped sinusoid results}
-\fi
-
 %

### 2020-11-17 papers/intro_paper/intro_paper.tex
updated paper and figures

@@
 
-We find, as one might expect, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time are consistent with zero (the left top panel in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
+We find, as one might expect, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time are consistent with zero (top panels in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
 The difference in the size of the posterior is due to the difference in the SNRs of the two events.
-One can then convert these fractional quantities into absolute quantities using the relations given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and construct posterior distributions on these effective quantities, $(\fngr{220}, \taungr{220})$ (the right top panel in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
+One can then convert these fractional quantities into absolute quantities using the relations given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and construct posterior distributions on these effective quantities, $(\fngr{220}, \taungr{220})$ (bottom panels in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
 In each of these cases, recovered posterior are consistent with the GR predictions (as indicated by the plus signs).
+In Fig.~\ref{fig:GW190521_simulated_GR_signal_corner} we illustrate possible correlations between the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, i.e, $(\df{220}, \dtau{220})$,  the GR predictions $(\fgr{220}, \taugr{220})$ and the reconstructed quantities $(\fngr{220}, \taungr{220})$ using the GW190521-like simulated GR signal as an example.
 
@@
 	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms.png}
-	\caption{The gravitational strain $h(t)$ in the LIGO Hanford (top panel) and Livingston (bottom panel) detectors, for a GW150914-like event where the ringdown is described by GR (black solid lines), i.e., $\df{220} = \dtau{220} = 0$, and where the ringdown frequencies are modified from GR (dashed red lines), i.e., $\df{220} = \dtau{220} = 0.5$.
+	\caption{\textcolor{red}{FINAL RESULT}The gravitational strain $h(t)$ in the LIGO Hanford (top panel) and Livingston (bottom panel) detectors, for a GW150914-like event where the ringdown is described by GR (black solid lines), i.e., $\df{220} = \dtau{220} = 0$, and where the ringdown frequencies are modified from GR (dashed red lines), i.e., $\df{220} = \dtau{220} = 0.5$.
 The time is measured with respect to UTC:1126285216, which was assumed to be point at which the event merged.
@@
 
-The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during the first half of O3 CITE, which passed a threshold for the total detector frame mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$\abhi{confirm}.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template.
+The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during the first half of O3 CITE, which passed a threshold for the total detector frame mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template.
 We restricted ourselves to the high-mass events which are expected to be merger-ringdown dominated.
@@
 
-Among all GW signals detected so far, GW150914 is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
-The bottom panel of Fig.\ref{fig:o1o2_events} compares the results we obtain for GW150914 with previously published LIGO-Virgo results using a damped-sinusoid method, as well as the measurement reported using a non-spinning model in \paperone.
+Among all the GW signals detected so far, GW150914 is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
+Fig.\ref{fig:GW150914_real} compares the results we obtain for GW150914 using $\pSEOB$ with previously published LIGO-Virgo results using a damped-sinusoid method, as well as the measurement reported using a non-spinning model in \paperone.
 The damped-sinusoid model assumed specific cutoff times (indicated in the curves on the bottom panel of Fig.\ref{fig:o1o2_events}) after the time corresponding to the peak amplitude as predicted by the best-fitting GR template waveform.
@@
 	\includegraphics[width=0.5\textwidth]{figures/O1O2_realevents.pdf}
-	%\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
-	\caption{The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions.
+	\caption{\textcolor{red}{FINAL RESULT}The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions.
 We also plot the joint probability distribution obtained by multiplying the likelihoods of the $\{\df{220},\dtau{220}\}$ (black dashed line) \abhi{need to compute the joint likelihood.
@@
 \begin{figure}[h!]
-	\includegraphics[width=0.4\textwidth]{figures/GW150914.png}
-	\caption{The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions.
-We also plot the joint probability distribution obtained by multiplying the likelihoods of the $\{\df{220},\dtau{220}\}$ (black dashed line) \abhi{need to compute the joint likelihood.
-currently contains the hierarchical contour from the O3a TGR paper}}
+	\includegraphics[width=0.4\textwidth]{figures/GW150914.pdf}
+	\caption{\textcolor{red}{FINAL RESULT}The 90\% credible levels of the posterior probability distribution of the frequency and damping time of the $(2,2)$ QNM for GW150914.
+The measurements by fitting damped sinusoids to the signal 1,3,5 milli-seconds after the peak amplitude is given by the black, darkgrey and grey curves.
+The measurement using NR fits is the purple contour, while the $\pSEOB$ and $pEOB$ measurements are indicated by the dark blue and light blue contours respectively.}
 	\label{fig:GW150914_real}
@@
 \end{tabular}
-\caption{}
+\caption{\textcolor{red}{NOT COMPLETE}}
 \label{tab:qnm_o1o2_results}
@@
 	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
-	\caption{a single figure for both Gaussian and Real noise injections, color coded, to save space}\label{fig:21g_systematics}
+	\caption{\textcolor{red}{FINAL RESULT}a single figure for both Gaussian and Real noise injections, color coded, to save space}\label{fig:21g_systematics}
 \end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GW190521-like simulated GR signal: corner plot
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[h!]
+	\includegraphics[width=\textwidth]{figures/GW190521_simulated_signal_gr_corner.pdf}
+	\caption{\textcolor{red}{FINAL RESULT} Corner plot showing the two-dimensional posterior probability distributions and corresponding one-dimensional marginalised distributions of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, i.e, $(\df{220}, \dtau{220})$,  the GR predictions $(\fgr{220}, \taugr{220})$ and the reconstructed quantities $(\fngr{220}, \taungr{220})$ for a GW190521-like simulated GR signal.
+The dashed lines on the one-dimensional marginalised histograms correspond to the median and the 90 \% confidence intervals of the distribution.}
+	\label{fig:GW190521_simulated_GR_signal_corner}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %

### 2020-11-17 papers/intro_paper/intro_paper.tex
minor update
updated noise systematics figure

@@
 And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the Advanced LIGO zero-detuned-high-power PSD CITE.
+A detailed study on noise systematics for one of the GW events is presented in Appendix~\ref{sec:noise_systematics}.
 As in the case of the actual detections, we consider a two-detector advanced LIGO network at Hanford and Livingston, having identical PSDs.
@@
 \appendix
-\section{Study of noise syetematics on ringdown measurements}
+\section{Study of noise syetematics on ringdown measurements}\label{sec:noise_systematics}
 
@@
 	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT}a single figure for both Gaussian and Real noise injections, color coded, to save space}\label{fig:21g_systematics}
+	\caption{\textcolor{red}{FINAL RESULT}90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220}$ from simulations of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
+The GR prediction for the frequency and damping time is indicated by the black cross.
+While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
+For comparison, we also plot the 90 \% credible level for the actual event, GW190521.}
+	\label{fig:21g_systematics}
 \end{figure}

### 2020-11-24 hierarchical_scripts/utils.py
add combined samples + notebooks

@@ -1,0 +1,278 @@
+import os
+import re
+from glob import glob
+import numpy as np
+from collections import OrderedDict
+import json
+import parse
+
+# ----------------------------------------------------------------------------
+# IO and other
+# ----------------------------------------------------------------------------
+
+def load_cache(param, cache_path):
+    cache_exists = all(os.path.isfile(cache_path.format(par=param, hyper=k)) for
+                       k in ['mu', 'sigma', 'pop'])
+    if cache_exists:
+        cache = {k: np.loadtxt(cache_path.format(par=param, hyper=k)) 
+                 for k in ['mu', 'sigma', 'pop']}
+    else:
+        cache = {}
+    return cache
+
+def save_cache(fits, cache_path, paths=None):
+    for param, fit in fits.items():
+        try:
+            post = fit.extract(['mu', 'sigma', 'pop'])
+        except AttributeError:
+            post = fit
+        for k in ['mu', 'sigma', 'pop']:
+            np.savetxt(cache_path.format(par=param, hyper=k), post[k])
+        print("Cached %s"%  param)
+    # record list of events
+    if paths:
+        cache_dir = os.path.dirname(cache_path)
+        log_path = os.path.join(cache_dir, 'events.json')
+        with open(log_path, 'w') as f:
+            json.dump(paths, f, indent=4)
+        print("Events logged: %r" % log_path)
+        
+def load_data(param, data_path, data_dict=None, path_dict=None):
+    ''' Loads posteriors from individual event runs for a given parameter.
+    
+    Arguments
+    ---------
+    param: str
+        parameter name
+    data_path: str
+        posterior sample path template, 'mypath/post_{par}_{event}.dat.gz'
+    data_dict: dict
+        dictionary to which to add loaded samples (opt.)
+    path_dict: dict
+        dictionary to which to add path information (opt.)
+    
+    Returns
+    -------
+    data_dict: dict
+        dictionary with loaded samples.
+    path_dict: dict
+        dictionary with path information.
+    '''
+    if data_dict is None:
+        data_dict = {}
+    if path_dict is None:
+        path_dict = {}
+    paths = glob(data_path.format(par=param, event='*'))
+    for path in paths:
+        try:
+            label = parse.parse(data_path, path)['event']
+            data_dict[label] = np.loadtxt(path)
+            path_dict[label] = path
+        except AttributeError:
+            pass
+    return data_dict, path_dict
+
[…]

### 2020-11-25 papers/intro_paper/code/bounded_1d_kde.py
updated several notebooks and minutes from last week's meeting

@@ -1,0 +1,74 @@
+#!/opt/local/bin/python
+
+####!/usr/bin/env python
+# -*- coding: utf-8 -*-
+"""
+A bounded 1-D KDE class for all of your bounded 1-D KDE needs.
+"""
+
+import numpy as np
+from scipy.stats import gaussian_kde as kde
+
+
+class Bounded_1d_kde(kde):
+    r"""Represents a one-dimensional Gaussian kernel density estimator
+    for a probability distribution function that exists on a bounded
+    domain."""
+
+    def __init__(self, pts, xlow=None, xhigh=None, *args, **kwargs):
+        """Initialize with the given bounds.  Either ``low`` or
+        ``high`` may be ``None`` if the bounds are one-sided.  Extra
+        parameters are passed to :class:`gaussian_kde`.
+
+        :param xlow: The lower x domain boundary.
+
+        :param xhigh: The upper x domain boundary.
+        """
+        pts = np.atleast_1d(pts)
+
+        assert pts.ndim == 1, 'Bounded_1d_kde can only be one-dimensional'
+
+        super(Bounded_1d_kde, self).__init__(pts.T, *args, **kwargs)
+
+        self._xlow = xlow
+        self._xhigh = xhigh
+
+    @property
+    def xlow(self):
+        """The lower bound of the x domain."""
+        return self._xlow
+
+    @property
+    def xhigh(self):
+        """The upper bound of the x domain."""
+        return self._xhigh
+
+    def evaluate(self, pts):
+        """Return an estimate of the density evaluated at the given
+        points."""
+        pts = np.atleast_1d(pts)
+        assert pts.ndim == 1, 'points must be one-dimensional'
+
+        x = pts.T
+        pdf = super(Bounded_1d_kde, self).evaluate(pts.T)
+        if self.xlow is not None:
+            pdf += super(Bounded_1d_kde, self).evaluate(2*self.xlow - x)
+
+        if self.xhigh is not None:
+            pdf += super(Bounded_1d_kde, self).evaluate(2*self.xhigh - x)
+
+        return pdf
+
+    def __call__(self, pts):
+        pts = np.atleast_1d(pts)
+        out_of_bounds = np.zeros(pts.shape[0], dtype='bool')
+
+        if self.xlow is not None:
+            out_of_bounds[pts < self.xlow] = True
+        if self.xhigh is not None:
+            out_of_bounds[pts > self.xhigh] = True
+
+        results = self.evaluate(pts)
+        results[out_of_bounds] = 0.
+        return results
+

### 2020-11-25 papers/intro_paper/code/bounded_2d_kde.py

@@ -1,0 +1,112 @@
+#!/opt/local/bin/python
+
+####!/usr/bin/env python
+# -*- coding: utf-8 -*-
+"""
+A bounded 2-D KDE class for all of your bounded 2-D KDE needs.
+"""
+
+import numpy as np
+from scipy.stats import gaussian_kde as kde
+
+class Bounded_2d_kde(kde):
+    r"""Represents a two-dimensional Gaussian kernel density estimator
+    for a probability distribution function that exists on a bounded
+    domain."""
+
+    def __init__(self, pts, xlow=None, xhigh=None, ylow=None, yhigh=None, *args, **kwargs):
+        """Initialize with the given bounds.  Either ``low`` or
+        ``high`` may be ``None`` if the bounds are one-sided.  Extra
+        parameters are passed to :class:`gaussian_kde`.
+
+        :param xlow: The lower x domain boundary.
+
+        :param xhigh: The upper x domain boundary.
+
+        :param ylow: The lower y domain boundary.
+
+        :param yhigh: The upper y domain boundary.
+        """
+        pts = np.atleast_2d(pts)
+
+        assert pts.ndim == 2, 'Bounded_kde can only be two-dimensional'
+
+        super(Bounded_2d_kde, self).__init__(pts.T, *args, **kwargs)
+
+        self._xlow = xlow
+        self._xhigh = xhigh
+        self._ylow = ylow
+        self._yhigh = yhigh
+
+    @property
+    def xlow(self):
+        """The lower bound of the x domain."""
+        return self._xlow
+
+    @property
+    def xhigh(self):
+        """The upper bound of the x domain."""
+        return self._xhigh
+
+    @property
+    def ylow(self):
+        """The lower bound of the y domain."""
+        return self._ylow
+
+    @property
+    def yhigh(self):
+        """The upper bound of the y domain."""
+        return self._yhigh
+
+    def evaluate(self, pts):
+        """Return an estimate of the density evaluated at the given
+        points."""
+        pts = np.atleast_2d(pts)
+        assert pts.ndim == 2, 'points must be two-dimensional'
+
+        x, y = pts.T
+        pdf = super(Bounded_2d_kde, self).evaluate(pts.T)
+        if self.xlow is not None:
+            pdf += super(Bounded_2d_kde, self).evaluate([2*self.xlow - x, y])
+
+        if self.xhigh is not None:
[…]

### 2020-11-26 papers/intro_paper/intro_paper.tex
updated figures and notebooks for the paper

@@
 
+\section*{ACKNOWLEDGEMENTS}\label{sec:acknowledgements}
+LIGO Clusters
+
 \iffalse
@@
 \appendix
-\section{Study of noise syetematics on ringdown measurements}\label{sec:noise_systematics}
+\section{Study of syetematics on ringdown measurements}\label{sec:noise_systematics}
 
@@
 
-In order to investigate the
+In Section~\ref{sec:method}, we mentioned that the expression of the Bayesian likelihood function outlined in Eqs.~\ref{eq:likelihood} and \ref{eq:nwip} is only valid if the interferometric noise can be described as a stationary Gaussian process.
+LIGO-Virgo noise, however, frequently has non-stationary and/or non-Gaussian features, like glitches, PSD drift, etc, which can affect parameter inferences unless appropriately accounted for.
+
+Here we demonstrate with an example, systematic biases likely originating from an incomplete understanding of the noise using the example of the GW190521.
+In Fig.~\ref{ig:o1o2_events} \abhi{include GW190521A in figure}, we find the estimates of the fractional deviations in the damping time, $\dtau{220}$ does not enclose the GR prediction at the 90 \% credible level, although the fractional deviation in the frequency $\df{220}$ is.
 

### 2020-12-01 papers/intro_paper/intro_paper.tex
updated figures and notebooks in paper

@@
 \usepackage[bottom]{footmisc}
+\usepackage{lineno}
+\linenumbers
 
@@
 \newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f ^{\text{nGR}}_{\text{#1}}}
-\newcommand{\taungr}[1]{\tau ^{\text{nGR}}_{\text{#1}}}
+\newcommand{\fngr}[1]{f_{\text{#1}}}
+\newcommand{\taungr}[1]{\tau_{\text{#1}}}
 \newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
@@
 
-\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from the inspiral, merger and ringdown of binary black holes}
+\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from binary black holes}
 
@@
 \begin{abstract}
-The no-hair conjecture in general relativity states that the properties of a Kerr black hole are completely described by its mass and spin angular momentum.
-As a consequence, the complex quasi-normal-mode (QNM) frequencies of a binary black hole ringdown can be uniquely determined by the mass and spin of the remnant object.
+The no-hair conjecture in General Relativity states that the properties of a Kerr black hole (BH) are completely described by its mass and spin angular momentum.
+As a consequence, the complex quasi-normal-mode (QNM) frequencies of a binary black hole (BBH) ringdown can be uniquely determined by the mass and spin of the remnant object.
 Conversely, measurement of the QNM frequencies could be a independent test of the no-hair conjecture.
-This paper outlines a test of the no-hair conjecture by measuring the complex QNM frequencies of a binary black hole ringdown within the framework of, for the first time, a spinning inspiral-merger-ringdown waveform model, thereby using the entire signal power and removing dependency on the predicted or estimated start time of the proposed ringdown.
-We further demonstrate the robustness of the test against modified gravitational wave signals with a ringdown different from what general relativity predicts for Kerr black holes.
+This paper outlines a test of the no-hair conjecture by measuring the complex QNM frequencies of a BBH ringdown within the framework of, for the first time, a spinning inspiral-merger-ringdown waveform model, thereby using the entire signal power and removing dependency on the predicted or estimated start time of the proposed ringdown.
+We further demonstrate the robustness of the test against modified gravitational wave (GW) signals with a ringdown different from what GR predicts for Kerr BHs.
 The method was used to analyse the properties of the merger remnants for the events observed by LIGO-Virgo in the first half of their third observing run (O3a) in the latest LIGO-Virgo publication.
-In this paper, for the first time, we analyse the gravitational wave events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a.
-The joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method.
-Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the gravitational wave event on the results of this test.
+In this paper, for the first time, we analyse the GW events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a.
+Finally, the joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method.
+%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
 \end{abstract}
@@
 
-\iffalse
-Overview of LIGO-Virgo tests of GR
-No-hair theorem and overview of nohair and ringdown tests with LIGO-Virgo Observations and future detectors
-Describe briefly the test
-Motivate the test: full IMR SNR, t0 definition, flexibility
-highlight importance of spins
-Section breakdown
-\fi
-
 The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave (GW) observations~\citep{GWTC-2} from the first half of their third observing run (O3a)~\citep{O3reference}.
-Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $50$ GW events from the merger of compact objects like neutron stars and/or black holes, collectively called compact binary coalescences (CBCs).
+Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $50$ GW events from the merger of compact objects like neutron stars and/or black holes (BHs), collectively called compact binary coalescences (CBCs).
 Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of GW astronomy, five years on from the first ever direct detection of GWs on Earth, on September 14, 2015~\citep{abbott2016observation}.
@@
 Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity (GR)~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}.
-In GR, a CBC involving two black holes (a binary black hole (BBH) system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
+In GR, a CBC involving two BHs (a binary black hole (BBH) system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
 \par
@@
 \par
-The LIGO-Virgo O3a testing GR paper also details results on tests of black hole ringdown and nature of the remnant object, which is an active field of research at the moment.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical black hole is completely described by two observables: mass and spin angular momentum.
-One consequence of the no-hair conjecture is that the (complex) QNM frequencies of gravitational radiation emitted by a perturbed isolated black hole is uniquely determined by its mass and spin angular momentum.
+The LIGO-Virgo O3a testing GR paper also details results on tests of BH ringdown and nature of the remnant object, which is an active field of research at the moment.
+The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin angular momentum.
+One consequence of the no-hair conjecture is that the (complex) QNM frequencies of gravitational radiation emitted by a perturbed isolated BH is uniquely determined by its mass and spin angular momentum.
 Hence a test of the no-hair conjecture would involve checking for consistency between estimates of mass and spin of the remnant object across multiple QNM frequencies.
-An inconsistency would either indicate a non-black hole nature of the remnant object, or an incompleteness of GR as the underlying theory of gravity.
-The consistency between the post-merger signal and the least dampled QNM was first demonstrated in ~\citep{LSC_2016grtests}, and later extended to include overtones in~\citep{Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}.
-Consistency of the late-time signal with a single QNM is a test of the ringdown of a BBH coalescence, but not necessarily a test of the no-hair conjecture, which requires the measurement of (atleast) two QNMs (black hole spectroscopy), and checking for consistency between them.
+An inconsistency would either indicate a non-BH nature of the remnant object, or an incompleteness of GR as the underlying theory of gravity.
+The consistency between the post-merger signal and the least damped QNM was first demonstrated in ~\citep{LSC_2016grtests} for GW150914, and later extended to include overtones in~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}.
+Consistency of the late-time signal with a single QNM is a test of the ringdown of a BBH coalescence, but not necessarily a test of the no-hair conjecture, which requires the measurement of (at least) two QNMs (BH spectroscopy), and checking for consistency between them.
 Recent work in that direction include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}.
-The nature of the remnant object has also been explored through tests of black hole thermodynamics, like the Hawking's area theorem~\citep{Cabero:2017avf} or through search for echos in the post-merger signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
-None of these tests have found evidence for non-black hole nature of the remnant object (as described in GR) in LIGO-Virgo BBH observations.
+The nature of the remnant object has also been explored through tests of BH thermodynamics, like the Hawking's area theorem~\citep{Cabero:2017avf} or through search for echos in the post-merger signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
+None of these tests have found evidence for non-BH nature of the remnant object (as described in GR) in LIGO-Virgo BBH observations.
 \par
 Most of the tests mentioned above focus on analysing the post-merger or late-time ringdown signal in isolation.
-Second generation ground-based interferometric detectors like Advanced LIGO and Virgo are most sensitive to stellar-mass black hole binaries that merge near the minima of their sensitivity band ($\sim 100$Hz).
+Second generation ground-based interferometric detectors like Advanced LIGO and Virgo are most sensitive to stellar-mass BH binaries that merge near the minima of their sensitivity band ($\sim 100$Hz).
 As a consequence, the remnant object \textit{rings down} in shot-noise dominated higher frequencies, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
-Furthermore, the post-merger signal of a BBH coalescence transitions from a non-linear to a linear regime where the description of the signal as a QNM spectrum becomes appropriate~\citep{}.
 The ringdown start time is not a clearly defined quantity and has been explored in detail in~\citep{Bhagwat:2017tkm}.
@@
 \par
-An independent approach to black hole spectroscopy, based on a full-signal analysis, was outlined in~\citep{Brito:2018rfr} (henceforth referred to as \paperone).
+An independent approach to BH spectroscopy, based on a full-signal analysis, was outlined in~\citep{Brito:2018rfr} (henceforth referred to as \paperone).
 Unlike methods that focus on the post-merger signal, it describes a framework in which a complete inspiral-merger-ringdown (IMR) waveform model is used to measure the complex QNM frequencies.
-\abhi{It is a spinning multipolar effective-one-body waveform calibrated to numerical relativity simulations (SEOBNRv4HM~\citep{Cotesta:2018fcv}})This allows access to the full SNR of the signal, reducing measurement uncertainties.
+This allows access to the full SNR of the signal, reducing measurement uncertainties.
 Moreover, the definition of the ringdown start time is built into the model and does not need to be either left as an additional free parameter or fixed using alternate definitions.
-While \paperone presented the method in the context of a non-spinning waveform model, we extend the analysis to the case with black holes spins in the current paper.
-All astrophysical black holes are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties CITE \cite{paper_showing_systematics_from_ignoring_spin}.
+While \paperone presented the method in the context of a non-spinning waveform model, we extend the analysis to the case with BHs spins in the current paper.
+\abhi{mention other improvements between EOBNRv2 and EOBNv4} All astrophysical BHs are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties CITE \cite{paper_showing_systematics_from_ignoring_spin}.
 \par
@@
 \section{Method}
+
+A GW signal from the (quasi-circular) coalescence of two BHs is completely described in GR by a fixed set of $15$ parameters, $\bxigr$.
+These can be grouped into the \emph{intrinsic} parameters: the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the initial binary and a reference time and phase $t_c, \phi_c$ respectively; and the \emph{extrinsic} parameters: the sky position of the binary ($\alpha$, $\delta$), the luminosity distance, $d_L$, and its orientation described through the inclination of the binary $\iota$ and its polarisation $\psi$.
+If the spins of the individual BHs are assumed to be aligned with the orbital angular momentum of the binary, then GW signal has a reduced dimensionality of $11$ parameters.
+The aligned-spin components are defined as: $a_{iz} = s_{iz}/m_i$, where $i=1,2$ for the two BHs.
+
 \subsection{Waveform Model}\label{sec:model}
 
-%\abhi{Summary of the section:}
-
-%\begin{itemize}
-%\item{a description of the SEOBNRv4HM model and it's generalisation to form the pSEOBNRv4HM model}
-%\item{highlight the importance of spins in the model, especially with regards to the non-spinning method outlined in Brito et al.}
-%\end{itemize}
-
 As in \paperone, we use an IMR waveform model developed within the EOB formalism.
-However, in this work we extend the results of \paperone by using a waveform model for spinning, nonprecessing binary BHs.
-Namely we use as our baseline model the multipolar waveform developed in Ref.~\citep{Cotesta:2018fcv}.
+However, in this work we extend the results of \paperone by using a waveform model for spinning, non-precessing BBHs.
+Namely we use as our baseline model the aligned-spin multipolar waveform developed in Ref.~\citep{Cotesta:2018fcv}.
 In addition to being calibrated to NR simulations, this model also uses information from BH perturbation theory for the merger and ringdown phases.
@@
 %
-where $\iota$ denotes the inclination angle computed with respect to the direction perpendicular to the orbital plane, $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
+where $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
 The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
@@
 In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the complex frequencies $\sigma_{\ell m 0}$  are expressed in terms of the final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the latter are related to the BBH's component masses and spins through NR--fitting-formulas obtained in GR~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values (henceforth, $\pSEOB$ model).
-The $\pSEOB$ model uses a parameterised version of the $\SEOB$ model where the frequency and the damping time of the ${\ell m 0}$ mode, i.e, $(f_{\ell m 0}, \tau _{\ell m 0})$ is defined through fractional deviations from the corresponding GR values, i.e., the predictions of the QNM frequencies obtained using the fits~\cite{Taracchini:2013rva,Hofmann:2016yih}:
+Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values.
+Henceforth called $\pSEOB$, this model uses a parameterised version of the $\SEOB$ model where the frequency and the damping time of the ${\ell m 0}$ mode, i.e, $(f_{\ell m 0}, \tau _{\ell m 0})$ is defined through fractional deviations, ($(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$), from the corresponding GR values, i.e., the predictions of the QNM frequencies obtained using the fits~\cite{Taracchini:2013rva,Hofmann:2016yih}:
 
 \begin{eqnarray}
-f_{\ell m 0}^{\text{nGR}} &:=& f_{\ell m 0}^{\text{GR}} (1 + \delta f_{\ell m 0})\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0}^{\text{nGR}} &:=& \tau _{\ell m 0}^{\text{GR}} (1 + \delta \tau_{\ell m 0}) \label{eq:nongr_freqs_b}
+f_{\ell m 0} &:=& f_{\ell m 0}^{\text{GR}} (1 + \delta f_{\ell m 0})\label{eq:nongr_freqs_a} \\ 
+\tau _{\ell m 0} &:=& \tau _{\ell m 0}^{\text{GR}} (1 + \delta \tau_{\ell m 0}) \label{eq:nongr_freqs_b}
 \end{eqnarray}
-where $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$ are the fractional deviations in the frequency and damping time, respectively, from the corresponding GR predictions.
-The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are constructed using numerical relativity predictions of the mass and spin of the remnant object, starting from estimates of the masses and spins of the initial binary:
-\begin{eqnarray}
-f_{\ell m 0}^{GR} = f_{\ell m 0}^{GR}(M_f, a_f) = f_{\ell m 0}^{GR}(m_1, m_2, \bs1, \bs2 ) \\
-\tau_{\ell m 0}^{GR} = \tau_{\ell m 0}^{GR}(M_f, a_f) = \tau_{\ell m 0}^{GR}(m_1, m_2, \bs1, \bs2 )
-\end{eqnarray}
-where we go from the second to the third step in both equation through the numerical relativity fits: $M_f = M_f(m_1, m_2, \bs1, \bs2)$ and $a_f = a_f(m_1, m_2, \bs1, \bs2)$.
-$M_f, a_f$ are the mass and spin of the remnant black while are determined from the initial masses and spins using analytical fits to numerical relativity simulations described above.
+The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are constructed using the same NR--fitting--formula prescriptiion described above.
 We note that when leaving $\sigma_{\ell m}$ to vary freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies, as can be seen from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$.
-\footnote{For the results discussed in this paper, we restrict ourselves to the $(\ell m) = (2,2)$ and $(3,3)$ modes.
-Most of the high-mass events, for which this test is most appropriate, observed by LIGO-Virgo are consistent with nearly-equal-mass face-on/off binaries for which power in the subdominant modes is not enough to attempt to measure more than two QNM frequencies at once.
-Hence, all the other $(\ell m)$ modes are fixed at their GR predictions.}
 
@@
 
-A gravitational wave signal from the (quasi-circular) coalescence of two black holes is completely described in GR by a fixed set of parameters, $\bxigr$.
-These can be grouped into the \emph{intrinsic} parameters: the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the initial binary and a reference time and phase $t_c, \phi_c$ respectively; and the \emph{extrinsic} parameters: the location of the binary given by the right ascension, $\alpha$, declination,$\delta$ and the luminosity distance, $d_L$, and its orientation described through the inclination of the binary $\iota$ and its polarisation $\psi$.
-The parametrised model described in ~\ref{sec:model}, $\pSEOB$, introduces an additional set of non-GR parameters, $\bxingr$, which essentially consist of the fractional deviations in the frequency and damping time corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-Also, since the underlying GR model, $\SEOB$ is aligned-spin, i.e., the black holes are restricted to have spins parallel to the orbital angular momentum, the number of independent spin components reduce from 6 to 2.
-By convention we denote the direction of the orbital angular momentum to be the $z$-axis, and as a consequence, denote the spin components of the two black holes as $s_{1z}$ and $s_{2z}$, respectively.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$ and any other information used in the analysis $I$:
+The parametrised model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
+One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
 
 \begin{equation}
-P(\blambda | d, \mathcal{H}, I) = \frac{P(\blambda | \mathcal{H}, I) \, \mathcal{L}(d | \blambda, \mathcal{H}, I)}{P(d|\mathcal{H}, I)},
+P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
 \label{eq:Bayes_theorem}
 \end{equation}
-where $P(\blambda | \mathcal{H}, I)$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H}, I)$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}, I) := \int P(\blambda | \mathcal{H}, I) \, \mathcal{L}(d | \blambda, \mathcal{H}, I) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density $S_n(f)$.
+where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
+The denominator is a normalization constant $P(d|\mathcal{H}) := \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
+In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
 The likelihood function can consequently be defined as:
@@
 \begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}, I) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
+\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
 \label{eq:likelihood}\end{equation}
@@
 $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and a $^*$ denotes complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the gravitational wave detector.
+The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
 We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas${f_\mathrm{low}}$ is dictated by the response of the gravitational detector to low-frequency seismic noise.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H}, I)$ in equation~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-Chain Monte-Carlo~\cite{xxx} or Nested Sampling~\cite{xxx}.
-For this paper, we use the lalinferencemcmc~\cite{xx} and bilby codes that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
+Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in equation~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-Chain Monte-Carlo~\cite{xxx} or Nested Sampling~\cite{xxx}.
+For this paper, we use the lalinferencemcmc~\cite{xx} and bilby codes CITE that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
 
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H}, I)$, we can marginalise over the \emph{nuisance} parameters, to obtain the marginalised posterior probability density function over the QNM parameters $\bxingr$:
+Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalise over the \emph{nuisance} parameters, to obtain the marginalised posterior probability density function over the QNM parameters $\bxingr$:
 
 \begin{equation}
-P(\bxingr | d, \mathcal{H}, I)= \int P(\blambda | d, \mathcal{H}, I) d\bxigr
+P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr
 \end{equation}
@@
 For most of the results discussed in this paper, we would restrict ourselves to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes.
-In those cases we would assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or  $ \{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes are fixed at their GR predictions, i.e., $\delta f_{\ell m 0}) = \delta \tau_{\ell m 0} = 0$.
-This is because, for most of the high-mass events we find most appropriate for this test, the LIGO-Virgo observations are consistent with nearly-equal-mass face-on/off black hole binaries for which power in the subdominant modes is not enough to attempt to measure more than one, or at most QNM frequencies at once.
+In those cases we would assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or  $ \{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be fixed at their GR predictions, i.e., $\delta f_{\ell m 0} = \delta \tau_{\ell m 0} = 0$.
+This is because, for most of the high-mass events we find most appropriate for this test, the LIGO-Virgo observations are consistent with nearly-equal-mass face-on/off BH binaries for which power in the subdominant modes is not enough to attempt to measure more than one, or at most QNM frequencies simultaneously.
 
+Throughout our analysis, we assume uniform priors on our non-GR QNM parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$.
+However, since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are derived through NR--fits, from the corresponding priors on the initial masses and spins, this leads to a non-trivial prior on the final reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m 0})$.
+Also, given the definition of the damping time in Sec.~\ref{sec:model}, we realise $\delta \tau_{\ell m 0} = -1$ leads to the imaginary part of the frequency going to infinity.
+We avoid this by restricting the minimum of the prior on $\delta \tau_{\ell m 0}$ to be greater than $-1$.
+
+\iffalse
 \subsection{Priors}
@@
 For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
+\fi
 
@@
 
-First, we demonstrate our method on gravitational wave signals from BBH systems that are well described by GR.
-We inject simulated GW signals modellng inspiral, merger and ringdown of BBHs  into coloured Gaussian noise described by Advanced LIGO-Virgo design sensitivity in the high-power, zero-detuning configuration (ZDHP) CITE.
+First, we demonstrate our method on GW signals from BBH systems that are well described by GR.
+We inject simulated GW signals modellng inspiral, merger and ringdown of BBHs into coloured Gaussian noise with PSDs expected at design sensitivities of Advanced LIGO-Virgo CITE.
 In particular we choose parameters similar to two specific GW events, GW150914 CITE and GW190521 CITE.
 The details of the injections are provided in Table~\ref{tab:injection_values}.
-These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the signal-to-noise ratio pre- and post-merger return reliable parameter estimation results.
-To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, $\SEOB$ CITE (without allowing for deviations in the QNM parameters) to simulate our GW signal.
-And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the Advanced LIGO zero-detuned-high-power PSD CITE.
+These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the SNR pre- and post-merger return reliable parameter estimation results.
+To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, $\SEOB$ (without allowing for deviations in the QNM parameters) to simulate our GW signal.
+And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the noise.
 A detailed study on noise systematics for one of the GW events is presented in Appendix~\ref{sec:noise_systematics}.
@@
 The distance to the two simulated events is rescaled such that the SNR in the detector network is same as the actual event, i.e, 24 (14) for GW150914 (GW190521).
-Since (almost) equal-mass binaries like GW150914 and GW190521 observed at moderate high SNRs are not expected to have a loud ringdown signal, we restrict ourselves to estimating the frequency and damping time of the $(\ell m) = (2,2)$, i.e., $\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to their GR values.
+Since (almost) equal-mass binaries like GW150914 and GW190521 observed at moderately high SNRs are not expected to have a loud ringdown signal, we restrict ourselves to estimating the frequency and damping time of the $(\ell m) = (2,2)$, i.e., $\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to their GR values.
 
-We find, as one might expect, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time are consistent with zero (top panels in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
-The difference in the size of the posterior is due to the difference in the SNRs of the two events.
-One can then convert these fractional quantities into absolute quantities using the relations given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and construct posterior distributions on these effective quantities, $(\fngr{220}, \taungr{220})$ (bottom panels in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}).
-In each of these cases, recovered posterior are consistent with the GR predictions (as indicated by the plus signs).
-In Fig.~\ref{fig:GW190521_simulated_GR_signal_corner} we illustrate possible correlations between the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, i.e, $(\df{220}, \dtau{220})$,  the GR predictions $(\fgr{220}, \taugr{220})$ and the reconstructed quantities $(\fngr{220}, \taungr{220})$ using the GW190521-like simulated GR signal as an example.
+We find, as one might expect, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time are consistent with zero (left panels of Fig.~\ref{fig:simulated_signal_GR}).
+One can then convert these fractional quantities into absolute quantities using the relations given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and construct posterior distributions on these effective quantities, $(\fngr{220}, \taungr{220})$ (right panels of Fig.~\ref{fig:simulated_signal_GR}).
+In each of these cases, recovered posterior are consistent with the GR predictions (black solid lines).
 
+\iffalse
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\fi
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GW150914-like simulated signal
+% Table for Injections
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c| }
+ \hline
+ Event & $m_{1,d} (\Mo)$ &  $m_{2,d} (\Mo)$ & $a_{1z}$ & $a_{2z}$ & SNR \\ 
+ \hline
+ GW150914 & 39 & 31 & 0.0 & 0.0 & 25 \\
+ GW190521 & 150 & 120 & 0.02 & -0.39 & 14 \\ 
+ SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
+ \hline
+\end{tabular}
+\caption{Details of the injection parameters, chosen to be similar to the actual GW events. $(m_{1,d},m_{2,d})$ are the detector-frame masses of the primary and secondary BHs respectively.}
+\label{tab:injection_values}
+\end{center}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Simulated siganl: GR
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_gr_ngr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (top panel) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (bottom panel) for an injection with initial parameters similar to GW150914 \ref{tab:injection_values}.
-The dark purple and grey points indicate the GR and modified GR signals respectively, when recovered using our $\pSEOB$ model.
-The two contours indicate the 50 and 90 \% credible levels, while the injected values are indicated by the '+' marker.
-The orange posterior probability distribution with the accompanying 90 \% credible level indicated in white corresponds to the biased measurement if our modGR signal had been estimated using the GR waveform model $SEOB$.
-}
-	\label{fig:GW150914_simulated_signal}
+	\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
+	\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
+	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
+The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalised distributions mark the 90\% credible levels.
+The black vertical and horizontal lines mark the injection values.}
+	\label{fig:simulated_signal_GR}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Simulations using modified GR signals in Gaussian noise}
+
+To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger, and differ in their post-merger description.
+We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $\df{220} = \dtau{220} = 0.5$ \abhi{deviations=0.1 runs are ongoing and almost done}.
+In other words, we assume that the frequency and damping time of our non-GR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}).
+We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}.
+The posterior probability distributions on $(\df{220}, \dtau{220})$ or equivalently $(\fngr{220}, \taungr{220})$ (Fig.~\ref{simulated_signal_nonGR}) are consistent with the corresponding the values of the injection parameters, indicated by the black solid lines.
+
+We additionally investigate the effects of erroneously assuming that an underlying modified GR signal can be well-described using GR.
+We do this by estimating the parameters of our modified GR signals using the GR waveform model $\SEOB$ instead of the parametrised $\pSEOB$.
+In such cases, we run the risk of biased parameter estimates due to an incomplete understanding of the underlying signal.
+The resulting posterior probability distributions are shown in the right panels of Fig.~\ref{simulated_signal_nonGR} by the pink (GW150914) and grey (GW190521) curves.
+The results are interesting and distinctly different for the two events.
+For the GW150914-like modified GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (Fig.~\ref{simulated_signal_nonGR} top right panel) are consistent with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no deviations (Fig.~\ref{simulated_signal_GR} top right panel).
+In other words, if the actual signal had deviations as large as the 50 \% of the GR prediction, the analysis with $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
+However in the case of the GW190521-like modified GR signal, a simple GR analysis of the modified GR signal would have yielded measurements distinctly different from either of the two parametrised estimates: with and without deviations.
+The fact that the GW190521-like signal has a much lower SNR than GW150914 might be a possible reason for the the measurement of the final quantities to be more susceptible to noise.
+A more detailed comparison of the other parameters, like the masses and spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR signal is shown in the appendix (Fig.~\ref{fig:gr_ngr_comparison}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
+	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarisation of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (solid orange lines), i.e., $\df{220} = \dtau{220} = 0$, and where the merger-ringdown is modified (dashed grey lines), i.e., $\df{220} = \dtau{220} = 0.5$.
+Bottom panel: Comparison of the evolution of the amplitude (left) and phase (right) for the GR and modified GR signal.}
+	\label{fig:nongr_waveform}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GW190521-like simulated signal
+% Simulated siganl: non-GR
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_gr_ngr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (top panel) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (bottom panel) for an injection with initial parameters similar to GW190521 \ref{tab:injection_values}.
-The dark purple and grey points indicate the GR and modified GR signals respectively, when recovered using our $\pSEOB$ model.
-The two contours indicate the 50 and 90 \% credible levels, while the injected values are indicated by the '+' marker.
-The orange posterior probability distribution with the accompanying 90 \% credible level indicated in white corresponds to the biased measurement if our modGR signal had been estimated using the GR waveform model $SEOB$.
-}
-	\label{fig:GW190521_simulated_signal}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\iffalse
-\abhi{The GW150914-like injections we have:}
-\begin{itemize}
-\item{an SEOBNRv4HM software injection with the 22 mode frequencies estimated}
-\item{a non-spinning NR injection with parameters close to the real event but higher SNR for which 22 mode frequencies are estimated}
-\item{a non-spinning highly-asymmetric (q=6) NR injection with total mass similar to GW150914 and high SNR for which 22 and 33 mode frequencies are estimated}
-\end{itemize}
-\fi
-
-\subsection{Simulations using modified GR signals in Gaussian noise}
-
-To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger, and differ in their post-merger description.
-We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $\df{220} = \dtau{220} = 0.5$.
-In other words, we assume that the frequency and damping time of our non-GR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}).
-We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}.
-The posterior probability distributions on $(\df{220}, \dtau{220})$ or equivalently $(\fngr{220}, \taungr{220})$ (right panels in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}) are consistent with the corresponding the values of the injection parameters, indicated by plus signs.
-
-We additionally investigate the effects of erroneously assuming that an underlying modified GR signal can be well-described using GR.
-We do this by estimating the parameters of our modified GR signals using the GR waveform model $\SEOB$ instead of the parametrised $\pSEOB$.
-In such cases, we run the risk of biased pareameter estimates due to an incomplete understanding of the underlying signal.
-The resulting orange posterior probability distributions are shown in Figs.\ref{fig:GW150914_simulated_signal} and \ref{fig:GW190521_simulated_signal}) with the corresponding 90 \% credible level in white.
-The results are interesting and distinctly different for the two events.
-For the GW150914-like modified GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (Fig.\ref{fig:GW150914_simulated_signal} lower panel) are consistent with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no deviations.
-In other words, if the actual signal had deviations as large as the 50 \% of the GR prediction, the analysis with $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
-However in the case of the GW190521-like modified GR signal, a simple GR analysis of the modified GR signal would have yielded measurements distinctly different from either of the two parametrised estimates: with and without deviations.
-The fact that the GW190521-like signal has a much lower SNR than GW150914 might be a possible reason for the the measurement of the final quantities to be more susceptible to noise.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms.png}
-	\caption{\textcolor{red}{FINAL RESULT}The gravitational strain $h(t)$ in the LIGO Hanford (top panel) and Livingston (bottom panel) detectors, for a GW150914-like event where the ringdown is described by GR (black solid lines), i.e., $\df{220} = \dtau{220} = 0$, and where the ringdown frequencies are modified from GR (dashed red lines), i.e., $\df{220} = \dtau{220} = 0.5$.
-The time is measured with respect to UTC:1126285216, which was assumed to be point at which the event merged.
-The signals are identical up to merger, but show a distinctly different ringdown.}
-	\label{fig:nongr_waveform}
+	\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
+	\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
+	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for modGR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
+The underlying signal has a deviation, $\df{220} = \dtau{220} = XX$.
+The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalised distributions mark the 90\% credible levels.
+The black vertical and horizontal lines mark the injection values.
+In the right panels, we additionally show measurements using a GR ($SEOB$) waveform, for GW150914 (grey) and GW190521 (pink), The measurements are visibly biased.}
+	\label{fig:simulated_signal_nonGR}
 \end{figure}
@@
 Finally, we provide a simple demonstration of a test of the no-hair theorem using our model.
-As described in the introduction, any test of the no-hair theorem of black holes would need to involve independent measurements of (at least) two different QNMs.
-We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning binary black hole with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$.
+As described in the introduction, any test of the no-hair theorem of BHs would need to involve independent measurements of (at least) two different QNMs.
+We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning BBH with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$.
 We choose an asymmetric system to increase the SNR in the higher modes.
 We also rescale the distance and orientation of the binary such that the total SNR of the signal in a network of three detectors, LIGO Hanford, Livingston and Virgo, is 75.
-The LIGO detectors are assumed to be in the ZDHP configuration as before, while the Virgo detector is assumed to be at design sensitivity CITE.
 Based on the LIGO-Virgo observations during O3a, such asymmetric and loud signals are no longer just a theoretical prediction but quite plausible at design sensitivities.
-Using the signal, we attempt to measure the QNM frequencies $(2,\pm 2)$ and $(3,\pm 3)$ modes together (Fig.~\ref{fig:nohair_sxs}).
+Using this signal, we attempt to measure the QNM frequencies $(2,\pm 2)$ and $(3,\pm 3)$ modes together (Fig.~\ref{fig:nohair_sxs}).
+The SNR in other sub-dominant modes is too less for us to estimate them reliably.
+
 The fractional deviations in the estimates of the damping time and frequency of either mode is expected to be consistent with 0, as we indeed find in the left panel of Fig.~\ref{fig:nohair_sxs}.
 Consequently we find that the reconstructed quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330}, \taungr{330})$  are also consistent with the corresponding predictions for a BBH merger in GR.
-As a consequence, the information from these two independent measures correspond to a unique remnant object, which is completely described by its mass and spin angular momentum.
+As a consequence, the information from these two independent measures correspond to a unique remnant object, which is completely described by its mass and spin angular momentum \abhi{have the mf-af plot as well as a third panel to show consistency}.
 For most of the events observed so far, the power in the $(3,\pm 3)$ has not been sufficient to measure it along with the $(2,\pm 2)$, or in fact, in its place.
-However, it might also be possible to combine information from multiple observation, as is likely over the coming few years of gravitational wave astronomy with the LIGO-Virgo detectors, to obtain meaningful constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.
+However, it might also be possible to combine information from multiple observation, as is likely over the coming few years of GW astronomy with the LIGO-Virgo detectors, to obtain meaningful constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.
 
@@
 	\label{fig:o1o2_events}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GW150914
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.4\textwidth]{figures/GW150914.pdf}
-	\caption{\textcolor{red}{FINAL RESULT}The 90\% credible levels of the posterior probability distribution of the frequency and damping time of the $(2,2)$ QNM for GW150914.
-The measurements by fitting damped sinusoids to the signal 1,3,5 milli-seconds after the peak amplitude is given by the black, darkgrey and grey curves.
-The measurement using NR fits is the purple contour, while the $\pSEOB$ and $pEOB$ measurements are indicated by the dark blue and light blue contours respectively.}
-	\label{fig:GW150914_real}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GW190521-like simulated GR signal: corner plot
+% modified GR signal: GR vs nonGR recovery comparison
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}[h!]
-	\includegraphics[width=\textwidth]{figures/GW190521_simulated_signal_gr_corner.pdf}
-	\caption{\textcolor{red}{FINAL RESULT} Corner plot showing the two-dimensional posterior probability distributions and corresponding one-dimensional marginalised distributions of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, i.e, $(\df{220}, \dtau{220})$,  the GR predictions $(\fgr{220}, \taugr{220})$ and the reconstructed quantities $(\fngr{220}, \taungr{220})$ for a GW190521-like simulated GR signal.
-The dashed lines on the one-dimensional marginalised histograms correspond to the median and the 90 \% confidence intervals of the distribution.}
-	\label{fig:GW190521_simulated_GR_signal_corner}
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
+	\caption{\textcolor{red}{FINAL RESULT} Right panels: GW50914. Left panels: GW190521. \abhi{describe how we get final mass and spin}}
+	\label{fig:gr_ngr_comparison}
 \end{figure*}

### 2020-12-02 data/rin/compute_sigmalm0_SimIMREOBGenerateQNMFreqV2.py
added rin data

@@ -1,0 +1,51 @@
+import numpy as np
+import lal
+import lalsimulation as lalsim
+
+###########################################################
+# function to compute GR value of sigmalm0 (in SI units)
+# for a single set of m1, m2, a1z, a2z for SEOBNRv4HM
+###########################################################
+def get_sigmalm0SI_GR(m1, m2, a1z, a2z, lm):
+
+  M = m1 + m2
+
+  omegalm0SI = []
+  taulm0SI = []
+
+  for idx in range(len(M)):
+    sigmalm0SI = lal.CreateCOMPLEX16Vector(1)
+    lalsim.SimIMREOBGenerateQNMFreqV2(sigmalm0SI, m1[idx], m2[idx], np.array([0., 0., a1z[idx]]), np.array([0., 0., a2z[idx]]), lm[0], lm[1], 1, lalsim.SEOBNRv4)
+
+    omegalm0SI.append(np.real((sigmalm0SI.data)[0]))
+    taulm0SI.append(1./np.imag((sigmalm0SI.data)[0]))
+
+  return np.asarray(omegalm0SI), np.asarray(taulm0SI)
+
+###########################################################
+# function to compute GR value of sigmalm0 (in SI units)
+# for a single set of m1, m2, a1x, a1y, a1z, a2x, a2y, a2z 
+# for SEOBNRv4PHM
+###########################################################
+def get_sigmalm0SI_GR_prec(m1, m2, a1x, a1y, a1z, a2x, a2y, a2z, lm):
+
+  M = m1 + m2
+
+  omegalm0SI = []
+  taulm0SI = []
+
+  for idx in range(len(M)):
+    sigmalm0SI = lal.CreateCOMPLEX16Vector(1)
+    lalsim.SimIMREOBGenerateQNMFreqV2Prec(sigmalm0SI, m1[idx], m2[idx], np.array([a1x[idx], a1y[idx], a1z[idx]]), np.array([a2x[idx], a2y[idx], a2z[idx]]), lm[0], lm[1], 1, lalsim.SEOBNRv4P)
+
+    omegalm0SI.append(np.real((sigmalm0SI.data)[0]))
+    taulm0SI.append(1./np.imag((sigmalm0SI.data)[0]))
+
+  return np.asarray(omegalm0SI), np.asarray(taulm0SI)
+
+###########################################################
+# function to compute modGR values of sigmalm0 (in SI units)
+###########################################################
[…]

### 2020-12-02 data/rin/utils.py

@@ -1,0 +1,780 @@
+# -*- coding: utf-8 -*-
+#
+#       Copyright 2020
+#       Maximiliano Isi <max.isi@ligo.org>
+#       Ben Farr ... [add me]
+#
+#       This program is free software; you can redistribute it and/or modify
+#       it under the terms of the GNU General Public License as published by
+#       the Free Software Foundation; either version 2 of the License, or
+#       (at your option) any later version.
+#
+#       This program is distributed in the hope that it will be useful,
+#       but WITHOUT ANY WARRANTY; without even the implied warranty of
+#       MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#       GNU General Public License for more details.
+#
+#       You should have received a copy of the GNU General Public License
+#       along with this program; if not, write to the Free Software
+#       Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston,
+#       MA 02110-1301, USA.
+
+import os
+import numpy as np
+from scipy.stats import gaussian_kde 
+from scipy.interpolate import interp1d
+from scipy.integrate import cumtrapz
+import pickle as pkl
+from pylab import *
+import scipy.stats as ss
+import warnings
+with warnings.catch_warnings():
+    warnings.simplefilter('ignore')
+    from pesummary.core.plots.bounded_1d_kde import bounded_1d_kde as Bounded_1d_kde
+
+# ############################################################################
+# rcParams
+
+# make plots fit the LaTex column size but rescale them for ease of display
+scale_factor = 2
+
+# Get columnsize from LaTeX using \showthe\columnwidth
+fig_width_pt = scale_factor*246.0
+# Convert pts to inches
+inches_per_pt = 1.0/72.27               
+# Golden ratio
+fig_ratio = (np.sqrt(5)-1.0)/2.0
+fig_width = fig_width_pt*inches_per_pt
+fig_height =fig_width*fig_ratio
+
+figsize_column = (fig_width, fig_height)
+figsize_square = (fig_width, fig_width)
+
+fig_width_page = scale_factor*inches_per_pt*508.87
+figsize_page = (fig_width_page, fig_height)
+
+rcParams = {'figure.figsize': figsize_column}
+
[…]

### 2020-12-02 papers/intro_paper/intro_paper.tex

@@
 
-\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from binary black holes}
+\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from binary black hole coalescences}
 
@@
 In this paper, for the first time, we analyse the GW events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a.
+We also analyse two events from the O3a list of events that were not considered for the initial analysis.
 Finally, the joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method.
@@
 As described in the introduction, any test of the no-hair theorem of BHs would need to involve independent measurements of (at least) two different QNMs.
-We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning BBH with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$.
+We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning BBH with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$ (Table~\ref{tab:injection_values}).
 We choose an asymmetric system to increase the SNR in the higher modes.
@@
 
-The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during the first half of O3 CITE, which passed a threshold for the total detector frame mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template.
-We restricted ourselves to the high-mass events which are expected to be merger-ringdown dominated.
+The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during O3a ~\cite{Abbott:2020jks}, which passed a threshold for the total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template.
+For the purpose of \cite{Abbott:2020jks}, we used a mass threshold and restricted ourselves to the highest-mass events which were expected to be most promising to study merger-ringdown.
 However, since our method relies on doing a parameter estimation on the entire inspiral-merger-ringdown signal, we require the SNR to be beyond a certain threshold throughout the signal for reliable parameter estimation of the initial and final quantities.
-Fig.~\ref{fig:o1o2_events} contains three events from O3a, GW190519\_ 153544, GW190521\_ 074359, GW190910\_ 112807.
+In fact the SNR threshold alone should be sufficient for the analysis, and for this paper we have relaxed the mass threshold.
+This has added two events, GW190630$\_$185205 and GW190828$\_$063405, to the list of events considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking promising}.
+Fig.~\ref{fig:o1o2_events} shows results from these two events along with GW190519$\_$153544, GW190521$\_$074359, GW190910$\_$112807.
 
 For the first time, in this paper, we present results on the relevant events from LIGO-Virgo's first and second observing runs, alongside the above events.
-Applying the same thresholds as above, we find three additional events which could be included in the analysis: GW150914, GW170104, GW170729 \abhi{would need to confirm the thresholds again, and see if GW170809 qualifies}.
-Regarding the other two high-mass events, GW170814 and GW170823 do not satisfy the SNR thresholds.
-For the three relevant signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $(\df{220}, \dtau{220})$ in Fig.\ref{fig:o1o2_events}.
+Applying the same thresholds as above, we find three additional events which could be included in the analysis: GW150914, GW170104, GW170729.
+The other high-mass events from O1-O2, GW170809, GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the merger-ringdown signal.
+For the three relevant signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}.
 We also reconstruct the effective QNM parameters, $(\fngr{220}, \taungr{220})$ which are tabulated in Table~\ref{tab:qnm_o1o2_results}.
-
-Among all the GW signals detected so far, GW150914 is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
-Fig.\ref{fig:GW150914_real} compares the results we obtain for GW150914 using $\pSEOB$ with previously published LIGO-Virgo results using a damped-sinusoid method, as well as the measurement reported using a non-spinning model in \paperone.
-The damped-sinusoid model assumed specific cutoff times (indicated in the curves on the bottom panel of Fig.\ref{fig:o1o2_events}) after the time corresponding to the peak amplitude as predicted by the best-fitting GR template waveform.
-Increasing time, decreasing SNR, wider posteriors, less-precise measurement.
-Compared to that we see when we incorporate the complete IMR version of the test, we utilise more SNR leading to tighter constraints.
+\footnote{See Table IV of \cite{Abbott:2020jks} for a list of the SNR thresholds.
+The paper quotes them for the purpose of the IMR consistency test, but the same thresholds have been used for the $pSEOB$ test as well.} Among all the GW signals detected so far, GW150914 (solid curve in Fig.~\ref{fig:o1o2_events})is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
 
@@
 \begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/O1O2_realevents.pdf}
-	\caption{\textcolor{red}{FINAL RESULT}The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions.
-We also plot the joint probability distribution obtained by multiplying the likelihoods of the $\{\df{220},\dtau{220}\}$ (black dashed line) \abhi{need to compute the joint likelihood.
-currently contains the hierarchical contour from the O3a TGR paper}}
+	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results.pdf}
+	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+The solid red curve marks the constraint the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
+The joint constraints on $\{\df{220},\dtau{220}\}$ obtained using multiplying the likelihoods from individual events is given by the filled grey contours.\abhi{add curves from joint likelihood}\abhi{add a hierarchical curve if we want to include that analysis}}
 	\label{fig:o1o2_events}
@@
 
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalised distributions as black dashed lines in Fig.~\ref{fig:o1o2_events}.
+We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalised distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
 These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.
-\abhi{perhaps show 2 joint posteriors: only O3a and O3a+O1-O2 to explicitly show the tightening of the joint constraints by adding the O1-O2 events}
+\abhi{perhaps show 2 joint posteriors: only O3a and O3a+O1-O2 to explicitly show the tightening of the joint constraints by adding the O1-O2 events} \abhi{add text on the hierarchical analysis if we want to include that analysis}
 
 \begin{table}
-\begin{center}
+\begin{flushleft}
 \begin{tabular}{llllllll}
@@
 & \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\cline{2-4}
-\cline{6-8}
+\hline
 & IMR  & pSEOB & \hphantom{X} & IMR  & pSEOB \\
-\midrule
+\hline
 
@@
 
+GWGW190630$\_$185205 &
+$-$ &
+$-$ &
+\hphantom{X} &
+$-$ &
+$-$
+\\[0.075cm]
+
+GW190828$\_$063405,170729 &
+$-$ &
+$-$ &
+\hphantom{X} &
+$-$ &
+$-$
+\\[0.075cm]
+\hline
 \bottomrule
@@
 \label{tab:qnm_o1o2_results}
-\end{center}
+\end{flushleft}
 \end{table}
@@
 In Section~\ref{sec:method}, we mentioned that the expression of the Bayesian likelihood function outlined in Eqs.~\ref{eq:likelihood} and \ref{eq:nwip} is only valid if the interferometric noise can be described as a stationary Gaussian process.
-LIGO-Virgo noise, however, frequently has non-stationary and/or non-Gaussian features, like glitches, PSD drift, etc, which can affect parameter inferences unless appropriately accounted for.
-
-Here we demonstrate with an example, systematic biases likely originating from an incomplete understanding of the noise using the example of the GW190521.
-In Fig.~\ref{ig:o1o2_events} \abhi{include GW190521A in figure}, we find the estimates of the fractional deviations in the damping time, $\dtau{220}$ does not enclose the GR prediction at the 90 \% credible level, although the fractional deviation in the frequency $\df{220}$ is.
+LIGO-Virgo noise, however, frequently has non-stationary and/or non-Gaussian features, for example glitches, which can affect parameter inferences unless appropriately accounted for.
+Here we demonstrate with an example of a GW190521-like simulated signal, systematic biases likely originating from an incomplete understanding of the noise.
 
@@
 \begin{figure}
-	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT}90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220}$ from simulations of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
+	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
+	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220}$ from simulations of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
 The GR prediction for the frequency and damping time is indicated by the black cross.
@@
 
-We injected NRSur7dq4 signal using the MaxL parameters from EXP30, in 2.5 hours of data surrounding the event at: t0-1.5 hours, t0-1., t0-0.5, t0+0.5, t0+1.
-For 3 of the 5 noise realisations, corresponding to t0-1 hour, t0+0.5 hours, and t0+1.0 hour we recover a damping time similar to the actual event, whereas for a third case, t0-0.5 hours, we obtain a damping time consistent at the 90\% credible interval (bottom panel of FIg.\ref{fig:21g_systematics}).
-L1-SNR goes down by more than 3 in some runs (maximum L1-SNR 12, minimum 9), indicative of how the noise variability is strongly affecting the recovered parameters.
-For some injections the mass ratio is biased, although final spin (most sensitive to mass ratio) is not affected much.
-domega varies quite a lot among runs, instead dtau seems well behaved around zero.
-Effective frequency is a stable parameter (always well measured), while effective tau is much more sensitive to the noise configuration.
+We use as our underlying GR signal, an NR waveform (using the waveform model \texttt{NRSur7dq4}) with parameters similar to the actual event GW190521 (as reported in Table I of \cite{Abbott:2020tfl}).
+The predictions of the frequency and damping time for the GR signal we choose are indicated by the black cross in Fig.~\ref{fig:21g_systematics}, and for comparison, the results on the actual signal are shown with a black solid curve.
+It would appear that while the measurement of the frequency is consistent with the prediction, we overestimate the damping time.
+
+The underlying NR signal is expected to be precessing, and since the $pSEOB$ model is built on an aligned-spin GR model, a lack of precession could bias measurements.
+We explore effects of possible waveform systematics by injecting the signal is coloured Gaussian noise.
+In this case, since the understanding of the noise realisations is complete, any measurement biases could only arise from incomplete understanding of the underlying signal.
+We find (grey curves in Fig.\ref{fig:21g_systematics}) our results to be consistent with the prediction thus ruling out a lack of precession to be a likely cause for the bias in the damping time measurement of the actual signal.
+
+We subsequently study the effects of possible noise systematics by injecting the same \texttt{NRSur7dq4} GW signal in different realisations of actual interferometric noise around the real event GW190521.
+Since the PSDs of the GW detectors are expected to vary over longer durations of time, we select 5 different noise realisations over a segment of 2.5 hours of coincident data in both the LIGO detectors centred at the time of the actual event.
+The noise properties in this chunk of data, and consequently for all 5 simulated signals, is expected to be the closest to that for the actual event.
+The results are indicated by pink curves in Fig.~\ref{fig:21g_systematics}.
+For 3 of the 5 noise realisations, corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we recover a damping time similar to the actual event, where $t_0$ is the GPS time of the actual event.
+For the other two noise realisations, we estimate the consistent damping time but an off-set frequency, while the fifth noise realisation is consistent with both predictions.
+The SNR in the L1 Livingston detector goes down by more than 3 in some runs, indicative of how a variation in the noise strongly affects our ability to infer parameters.
+This also seems to indicate that a bias in the measurements of the damping time for the actual event can be unaccounted noise systematics.
+
+\section{Correlations between GR and non-GR parameters}\label{sec:correlations}
+\abhi{Do we want a separate appendix to discuss Fig.~\ref{fig:gr_ngr_comparison}? Or is the reference in the main text currently, sufficient?}
 
@@
 	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Right panels: GW50914. Left panels: GW190521. \abhi{describe how we get final mass and spin}}
+	\caption{\textcolor{red}{FINAL RESULT} Comparison of the recovered parameters when the underlying signal is assumed to be a GR signal or a modified GR signal.
+In both cases, the actual underlying signal is a modified GR signal with parameters similar to GW150914 (left panels) and GW190521 (right panels) respectively.
+The initial parameters are given in Table~\ref{tab:injection_values}, with the QNM parameters defined by $\df{220} = \dtau{220} = 0.5$.
+For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.
+The panels (from top to bottom) show the recoveries in (detector-frame) initial masses (first row), z-components of dimensionless initial spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f, a_f$) from the frequency and damping time (obtained by inverting the Berti fits) CITE}
 	\label{fig:gr_ngr_comparison}

### 2020-12-02 papers/intro_paper/intro_paper.tex
updated second draft and notebooks

@@
 The solid red curve marks the constraint the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $\{\df{220},\dtau{220}\}$ obtained using multiplying the likelihoods from individual events is given by the filled grey contours.\abhi{add curves from joint likelihood}\abhi{add a hierarchical curve if we want to include that analysis}}
+The joint constraints on $\{\df{220},\dtau{220}\}$ obtained using multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
 	\label{fig:o1o2_events}
@@
 We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalised distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.
-\abhi{perhaps show 2 joint posteriors: only O3a and O3a+O1-O2 to explicitly show the tightening of the joint constraints by adding the O1-O2 events} \abhi{add text on the hierarchical analysis if we want to include that analysis}
+These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\abhi{add text on the hierarchical analysis if we want to include that analysis}
 

### 2020-12-02 papers/intro_paper/intro_paper.tex
finalised second draft

@@
 
-\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_1 (\Mo)$ &  $m_1 (\Mo)$ & $a_{1z}$ & $a_{2z}$ & SNR \\ 
- \hline
- GW150914 & 38.53 & 33.40 & 0.0035 & -0.0440 & 25 \\ \label{tab:injection_values}
- GW190521 & 152.20 & 120.41 & 0.0230 & -0.3864 & 14 \\ 
- \hline
-\end{tabular}
-\caption{Details of the injection parameters, chosen to be similar to the actual GW events}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\fi
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
-	\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
+\begin{figure*}%[h!]
+\begin{center}
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
+	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
 	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
@@
 	\label{fig:simulated_signal_GR}
-\end{figure}
+\end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.25\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
+\begin{figure*}%[h!]
+\begin{center}
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
+	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
 	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for modGR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
@@
 	\label{fig:simulated_signal_nonGR}
-\end{figure}
+\end{center}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\iffalse
-\abhi{A comparison with pyRING}
-\abhi{damped sinusoid results}
-\fi
-
-\pagebreak
-
 \appendix
 \section{Study of syetematics on ringdown measurements}\label{sec:noise_systematics}
-
-\iffalse
-\abhi{A small summary of the noise systematics study that was done for S190521g to show that the deviations seen were consistent with systematics due to noise.
-The study include 2 separate sections: in Gaussian noise, and in real LIGO-Virgo noise immediately adjacent to the actual event.}
-\fi
 

### 2020-12-07 papers/intro_paper/intro_paper.tex
updated 2 figures
updated paper draft

@@
 
-\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from binary black hole coalescences}
+\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
 
@@
 The fact that the GW190521-like signal has a much lower SNR than GW150914 might be a possible reason for the the measurement of the final quantities to be more susceptible to noise.
-A more detailed comparison of the other parameters, like the masses and spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR signal is shown in the appendix (Fig.~\ref{fig:gr_ngr_comparison}).
+A more detailed comparison of the other parameters, like the masses and spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR signal is shown in Fig.~\ref{fig:gr_ngr_comparison}.
 
@@
 	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarisation of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (solid orange lines), i.e., $\df{220} = \dtau{220} = 0$, and where the merger-ringdown is modified (dashed grey lines), i.e., $\df{220} = \dtau{220} = 0.5$.
-Bottom panel: Comparison of the evolution of the amplitude (left) and phase (right) for the GR and modified GR signal.}
+Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and modified GR signal.}
 	\label{fig:nongr_waveform}
@@
 \end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% modified GR signal: GR vs nonGR recovery comparison
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
+	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
+	\caption{\textcolor{red}{FINAL RESULT} Comparison of the recovered parameters when the underlying signal is assumed to be a GR signal or a modified GR signal.
+In both cases, the actual underlying signal is a modified GR signal with parameters similar to GW150914 (left panels) and GW190521 (right panels) respectively.
+The initial parameters are given in Table~\ref{tab:injection_values}, with the QNM parameters defined by $\df{220} = \dtau{220} = 0.5$.
+For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.
+The panels (from top to bottom) show the recoveries in (detector-frame) initial masses (first row), z-components of dimensionless initial spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f, a_f$) from the frequency and damping time (obtained by inverting the Berti fits) CITE}
+	\label{fig:gr_ngr_comparison}
 \end{figure*}
@@
 \begin{figure}
+\begin{center}
 	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
@@
 	\label{fig:21g_systematics}
+\end{center}	
 \end{figure}
@@
 
-\section{Correlations between GR and non-GR parameters}\label{sec:correlations}
-\abhi{Do we want a separate appendix to discuss Fig.~\ref{fig:gr_ngr_comparison}? Or is the reference in the main text currently, sufficient?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of the recovered parameters when the underlying signal is assumed to be a GR signal or a modified GR signal.
-In both cases, the actual underlying signal is a modified GR signal with parameters similar to GW150914 (left panels) and GW190521 (right panels) respectively.
-The initial parameters are given in Table~\ref{tab:injection_values}, with the QNM parameters defined by $\df{220} = \dtau{220} = 0.5$.
-For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.
-The panels (from top to bottom) show the recoveries in (detector-frame) initial masses (first row), z-components of dimensionless initial spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f, a_f$) from the frequency and damping time (obtained by inverting the Berti fits) CITE}
-	\label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %

### 2021-01-06 papers/intro_paper/intro_paper.tex
changes in title/abstract

@@
 \newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
+\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
+\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
 
@@
 
+\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
+\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
+
 \begin{document}
 
-\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
+%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
+
+\title{\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}}
 
 \author{Abhirup Ghosh}
-\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), D-14476 Potsdam-Golm, Germany}
+\AEI
 \author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185, Roma, Italy}
+\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
 \author{Alessandra Buonanno}
-\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), D-14476 Potsdam-Golm, Germany}
+\AEI
+\UMD
 
@@
 \begin{abstract}
-The no-hair conjecture in General Relativity states that the properties of a Kerr black hole (BH) are completely described by its mass and spin angular momentum.
-As a consequence, the complex quasi-normal-mode (QNM) frequencies of a binary black hole (BBH) ringdown can be uniquely determined by the mass and spin of the remnant object.
-Conversely, measurement of the QNM frequencies could be a independent test of the no-hair conjecture.
-This paper outlines a test of the no-hair conjecture by measuring the complex QNM frequencies of a BBH ringdown within the framework of, for the first time, a spinning inspiral-merger-ringdown waveform model, thereby using the entire signal power and removing dependency on the predicted or estimated start time of the proposed ringdown.
-We further demonstrate the robustness of the test against modified gravitational wave (GW) signals with a ringdown different from what GR predicts for Kerr BHs.
-The method was used to analyse the properties of the merger remnants for the events observed by LIGO-Virgo in the first half of their third observing run (O3a) in the latest LIGO-Virgo publication.
-In this paper, for the first time, we analyse the GW events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a.
-We also analyse two events from the O3a list of events that were not considered for the initial analysis.
-Finally, the joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method.
-%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
+  The no-hair conjecture in General Relativity states that the
+  properties of an \ab{astrophysical} Kerr black hole (BH) are completely described by its
+  mass and spin angular momentum. As a consequence, the complex
+  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
+  ringdown can be uniquely determined by the mass and spin of the
+  remnant object. Conversely, measurement of the QNM frequencies could
+  be an independent test of the no-hair conjecture. This paper \ab{extends to spinning BHs earlier work} 
+ \sout{outlines a} \ab{that proposed to} 
+  test \sout{of} the no-hair conjecture by measuring the complex QNM
+  frequencies of a BBH ringdown \sout{within the framework of, for the first
+  time, a spinning} using inspiral-merger-ringdown waveform\ab{s} \sout{model}, thereby
+  \sout{using} \ab{taking full advantage of} the entire signal power and removing dependency on the
+  predicted or estimated start time of the proposed ringdown. We
+  further demonstrate the robustness of the test against modified
+  gravitational-wave (GW) signals with a ringdown different from what
+  GR predicts for Kerr BHs. \ab{Our} method was used to analyse the
+  properties of the merger remnants for the events observed by
+  LIGO-Virgo in the first half of their third observing run (O3a) in
+  the latest LIGO-Virgo publication. In this paper, for the first
+  time, we analyse the GW events from the first \ab{(O1)} and second \ab{(O2)} LIGO-Virgo
+  observing runs and provide joint constraints with published results
+  from O3a. We also analyse two events from the O3a \ab{catalogue} \sout{list of events} 
+  that were not considered \sout{for} \ab{in}  the initial \ab{LIGO-Virgo} analysis. Finally, the
+  joint measurements of the fractional deviations in the frequency,
+  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
+  constraints yet using this
+  method. %Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
 \end{abstract}

### 2021-01-06 papers/intro_paper/intro_paper.tex
changes in Section I

@@
 \documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers]{revtex4-1}
+
 \usepackage{epsfig}
@@
 \usepackage{lineno}
-\linenumbers
+%\linenumbers
 
@@
 
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave (GW) observations~\citep{GWTC-2} from the first half of their third observing run (O3a)~\citep{O3reference}.
-Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $50$ GW events from the merger of compact objects like neutron stars and/or black holes (BHs), collectively called compact binary coalescences (CBCs).
-Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of GW astronomy, five years on from the first ever direct detection of GWs on Earth, on September 14, 2015~\citep{abbott2016observation}.
+The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
+Collaboration\sout{s}~\citep{Virgo} \ab{have} recently announced their catalogue of
+gravitational-wave (GW) \sout{observations} \ab{signals}~\citep{GWTC-2} from the first
+half of the\sout{ir} third observing run (O3a)~\citep{O3reference}. Combined
+with \sout{the confirmed observations from} the first and second observing-run \ab{catalogues}~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford,
+Washington and Livingston, Louisiana~\citep{aasi2015characterization},
+and the Advanced Virgo detector in Cascina,
+Italy~\citep{acernese2014advanced} have now detected \sout{more than} $50$ GW
+events from the merger of compact objects like neutron stars and/or
+black holes (BHs), collectively called compact binary coalescences
+(CBCs). Alongside independent claims of
+detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020},
+\sout{this} \ab{these results} \sout{has} \ab{have} firmly established the field of GW astronomy, five years \sout{on
+from} \ab{after} the first \sout{ever direct} detection of GWs \ab{passing through the} \sout{on} Earth, on September 14,
+2015~\citep{abbott2016observation}.
 \par

### 2021-01-08 papers/intro_paper/intro_paper.tex
changes in Introduction

--- 2021-01-06 papers/intro_paper/intro_paper.tex
@@
 
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave (GW) observations~\citep{GWTC-2} from the first half of their third observing run (O3a)~\citep{O3reference}.
-Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $50$ GW events from the merger of compact objects like neutron stars and/or black holes (BHs), collectively called compact binary coalescences (CBCs).
-Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of GW astronomy, five years on from the first ever direct detection of GWs on Earth, on September 14, 2015~\citep{abbott2016observation}.
-\par
-Observation of GWs have had significant astrophysical and cosmological implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}.
-It has also allowed us to make statements in fundamental physics.
-Specifically, LIGO-Virgo's observations have allowed us to test predictions of Einstein's theory of General Relativity (GR)~\citep[GR]{}, in previously unexplored regimes of highly relativistic, strong-field regimes of gravity~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}.
-In GR, a CBC involving two BHs (a binary black hole (BBH) system) is described in three distinct phases: an early \textit{inspiral}, where the two compact objects spiral in and \textit{plunge} due to a back-reaction of gravitational-wave-emission, a \textit{merger} marked by the formation of an apparent horizon~\citep{NRpaper}, and a late-time \textit{ringdown}, where the newly formed remnant object settles down to a stable Kerr state through the emission of an exponentially damped quasi-normal-mode (QNM) spectrum of gravitational radiation~\citep{vishu,earlyqnmpapers}.
-\par
-The LIGO-Virgo collaborations have also released a companion paper detailing their latest results of tests of GR using events from the catalogues GWTC-2 CITE and GWTC-1 CITE.
-The results include tests of GW generation and source dynamics, where bounds are placed on parametrised deviations in the Post-Newtonian coefficients describing the early inspiral~\citep{earlydevelopmentpapers}, and phenomenological coefficients describing the intermediate (plunge) and merger regimes of coalescence~\citep{TIGERmethodspapers}, tests of GW propagation, which assume a generalised dispersion relation and place upper bounds on the Compton wavelength and consequently, the mass of the graviton~\citep{gw170104,samajdar2017projected} and tests of the polarisation of gravitational radiation using a multi-gravitational-wave-detector network~\citep{gw170814,isi2017probing}.
-The paper also checks for consistency between different portions of the signal using estimates of predicted mass and spin of the remnant object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and consistency of the residuals with interferometric noise~\citep{Ghonge:2020suv,gwtc1_tgr}.
-None of these tests report any departure from the predictions of GR.
-\par
-The LIGO-Virgo O3a testing GR paper also details results on tests of BH ringdown and nature of the remnant object, which is an active field of research at the moment.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin angular momentum.
-One consequence of the no-hair conjecture is that the (complex) QNM frequencies of gravitational radiation emitted by a perturbed isolated BH is uniquely determined by its mass and spin angular momentum.
-Hence a test of the no-hair conjecture would involve checking for consistency between estimates of mass and spin of the remnant object across multiple QNM frequencies.
-An inconsistency would either indicate a non-BH nature of the remnant object, or an incompleteness of GR as the underlying theory of gravity.
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in ~\citep{LSC_2016grtests} for GW150914, and later extended to include overtones in~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}.
-Consistency of the late-time signal with a single QNM is a test of the ringdown of a BBH coalescence, but not necessarily a test of the no-hair conjecture, which requires the measurement of (at least) two QNMs (BH spectroscopy), and checking for consistency between them.
-Recent work in that direction include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}.
-The nature of the remnant object has also been explored through tests of BH thermodynamics, like the Hawking's area theorem~\citep{Cabero:2017avf} or through search for echos in the post-merger signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
-None of these tests have found evidence for non-BH nature of the remnant object (as described in GR) in LIGO-Virgo BBH observations.
-\par
-Most of the tests mentioned above focus on analysing the post-merger or late-time ringdown signal in isolation.
-Second generation ground-based interferometric detectors like Advanced LIGO and Virgo are most sensitive to stellar-mass BH binaries that merge near the minima of their sensitivity band ($\sim 100$Hz).
-As a consequence, the remnant object \textit{rings down} in shot-noise dominated higher frequencies, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
-The ringdown start time is not a clearly defined quantity and has been explored in detail in~\citep{Bhagwat:2017tkm}.
-In other works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a free parameter to be estimated directly from the data.
-Uncertainties in estimates of the ringdown start-time, as well as an overall lack of SNR in the post-merger signal, given typical sensitivities of ground-based detectors result in significant statistical uncertainties in the measurement of the QNM frequencies.
-\par
-An independent approach to BH spectroscopy, based on a full-signal analysis, was outlined in~\citep{Brito:2018rfr} (henceforth referred to as \paperone).
-Unlike methods that focus on the post-merger signal, it describes a framework in which a complete inspiral-merger-ringdown (IMR) waveform model is used to measure the complex QNM frequencies.
-This allows access to the full SNR of the signal, reducing measurement uncertainties.
-Moreover, the definition of the ringdown start time is built into the model and does not need to be either left as an additional free parameter or fixed using alternate definitions.
-While \paperone presented the method in the context of a non-spinning waveform model, we extend the analysis to the case with BHs spins in the current paper.
-\abhi{mention other improvements between EOBNRv2 and EOBNv4} All astrophysical BHs are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties CITE \cite{paper_showing_systematics_from_ignoring_spin}.
-\par
-The rest of this paper is organized as follows.
-Section~\ref{sec:model} describes our parametrised IMR waveform model.
-In section~\ref{sec:method}, we define our testing GR framework in which we use that model to measure the complex QNM frequencies within a Bayesian formalism.
-Then in section~\ref{sec:results}, we demonstrate our method on real GW events, as well as simulated signals.
-Finally we provide a summary of our results and discuss future developments in section~\ref{sec:discussion}.
+\comment{AB: Please make the citations in the bibliography uniform (I would stick with citations 
+taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please 
+stick with American English.}
+
+The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
+Collaboration\sout{s}~\citep{Virgo} \ab{have} recently announced their catalogue of
+gravitational-wave (GW) \sout{observations} \ab{signals}~\citep{GWTC-2} from the first
+half of the\sout{ir} third observing run (O3a)~\citep{O3reference}. Combined
+with \sout{the confirmed observations from} the first and second observing-run \ab{catalogues}~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford,
+Washington and Livingston, Louisiana~\citep{aasi2015characterization},
+and the Advanced Virgo detector in Cascina,
+Italy~\citep{acernese2014advanced} have now detected \sout{more than} $50$ GW
+events from the merger of compact objects like neutron stars and/or
+black holes (BHs).\sout{, collectively called compact binary coalescences
+(CBCs).} Alongside independent claims of
+detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020},
+\sout{this} \ab{these results} \sout{has} \ab{have} firmly established the field of GW astronomy, five years \sout{on
+from} \ab{after} the first \sout{ever direct} detection of a GW \ab{passing through the} \sout{on} Earth, \ab{notably GW150914} 
+\sout{on September 14,2015}~\citep{abbott2016observation}.
+
+\ab{The observation of GWs has} had significant astrophysical and cosmological
+implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
+has also allowed us to \sout{make statements in} \ab{probe} fundamental
+physics \sout{.Specifically, LIGO-Virgo's observations have allowed us to} and 
+test predictions of Einstein's theory of General Relativity 
+(GR)~\citep{GR} in the previously unexplored \ab{highly-dynamical, and strong field 
+regime} \sout{of highly relativistic, strong-field regimes of
+gravity}~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR\sout{, a CBC
+involving two BHs (}a binary black hole (BBH) system\sout{)} is described \sout{in} \ab{by}
+three \sout{distinct} phases: an early \textit{inspiral}, where the two
+compact objects spiral in \ab{loosing energy because of the emission of GWs} \sout{and \textit{plunge} due to a back-reaction
+of gravitational-wave-emission}, a \textit{merger} marked by the
+formation of a\sout{n} \ab{common} apparent horizon~\citep{NRpaper}, and a \sout{late-time} 
+\textit{ringdown}, \sout{where} \ab{during which} the newly formed remnant object settles down
+to a \sout{stable} Kerr \ab{BH} \sout{state through the emission of} \ab{emitting} an exponentially damped
+quasi-normal-mode (QNM) spectrum of gravitational
+radiation~\citep{vishu,earlyqnmpapers}.
+
+The LIGO-Virgo collaborations \ab{have released companion papers \cite{}} detailing their \sout{latest} results 
+of tests of GR using \sout{events} \ab{GW150914 \cite{} and 
+the first two transient catalogues (TC) (i.e., GWTC-1\cite{}  and GWTC-2 \cite{})}. 
+The results include tests of GW generation and source dynamics, where bounds are placed on
+parametrized deviations in the post-Newtonian \ab{(PN)} coefficients describing
+the early inspiral~\citep{earlydevelopmentpapers}, and
+phenomenological coefficients describing the intermediate (plunge) and
+merger regimes of coalescence~\citep{TIGERmethodspapers}; tests of GW
+propagation, which assume a generalized dispersion relation and place
+upper bounds on the Compton wavelength and consequently, the mass of
+the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
+polarization of gravitational radiation using a
+multi-GW-detector network~\citep{gw170814,isi2017probing}. The \ab{GWTC-1/2} paper\ab{s} also 
+check\sout{s} for consistency between different portions of the signal using estimates
+\sout{of} \ab{for the} predicted mass and spin of the remnant
+object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
+consistency of the residuals with interferometric
+noise~\citep{Ghonge:2020suv,gwtc1_tgr}. None of these tests report any
+departure from the predictions of GR.
+
+\ab{The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
+first measurement of the dominant damped-sinusoidal signal in the ringdown stage of a BBH 
+coalescence.} The LIGO-Virgo O3a testing GR paper~\cite{} \ab{has recently reported} 
+\sout{also details results on tests} \ab{a comprehensive analysis of the properties of the 
+remnant object, including the ringdown stage, for tens of GW events.}   
+\sout{BH ringdown and nature of the remnant object, which is an active field
+of research at the moment.} The no-hair conjecture in GR~\citep{}
+states that an (electrically neutral) astrophysical BH is completely
+described by two observables: mass and spin angular momentum. One
+consequence of the no-hair conjecture is that the (complex) QNM
+frequencies of gravitational radiation emitted by a perturbed isolated
+BH is uniquely determined by its mass and spin angular momentum. Hence
+a test of the no-hair conjecture would involve checking for
+consistency between estimates of mass and spin of the remnant object
+across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
+indicate a non-BH nature of the remnant object, or an incompleteness
+of GR as the underlying theory of gravity.
+
+The consistency between the post-merger signal and the least damped QNM was first demonstrated in 
+Ref.~\citep{LSC_2016grtests} for GW150914, and later extended to include
+overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
+of the late-time \sout{signal} \ab{waveform} with a single QNM is a test of the ringdown of
+a BBH coalescence, but not necessarily a test of the no-hair
+conjecture, which requires the measurement of (at least) two QNMs (BH
+spectroscopy), and checking for consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
+in that direction \comment{AB: which direction? There are papers by Nikhef group and 
+also Brito et al., and many others that have investigated BH spectroscopy.} include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
+nature of the remnant object has also been explored through tests of
+BH thermodynamics, like the Hawking's area
+theorem~\citep{Cabero:2017avf} or through search for echos in the
+post-merger
+signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
+of these tests have found evidence for non-BH nature of the remnant
+object (as described in GR) in LIGO-Virgo BBH observations.
+
+\comment{AB: I don't understand the next senetnce, it looks to me out of context.} 
+Most of the tests mentioned above focus on analysing the post-merger
+or late-time ringdown signal in isolation. \sout{Second generation
+ground-based interferometric detectors like} \ab{Ground-based detectors, 
+such as \sout{Advanced} LIGO and Virgo,} are most sensitive to 
+stellar-mass BH binaries that merge near the
+minim\ab{um}\sout{a} of their sensitivity band ($\sim 100$Hz). As a consequence, the
+remnant object \textit{rings down} \comment{AB: we are not discussing the interferometer noises, 
+so why to give such a detail about the shot noise?} \sout{in shot-noise dominated higher
+frequencies, leaving} \ab{at frequencies where the sensitivity is worse, leaving} 
+very little signal-to-noise ratio (SNR) in the
+post-merger signal. \comment{AB: This discussion about the starting time of the ringdown starts too abruptly, 
+and looks out of context and incomplete. Also, why are we citing only those papers? The matter 
+has a long history. There have been calibrations to NR of damped-sinusoid signals.} 
+The ringdown start time is not a clearly defined
+quantity and has been explored in detail
+in Ref.~\citep{Bhagwat:2017tkm}. In other
+works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a
+free parameter to be estimated directly from the data. Uncertainties
+in estimates of the ringdown start-time, as well as an overall lack of
+SNR in the post-merger signal, given typical sensitivities of
+ground-based detectors result in significant statistical uncertainties
+in the measurement of the QNM frequencies.
+
+An independent approach to BH spectroscopy, based on the full-signal
+analysis, was \sout{outlined} \ab{introduced} in Ref.~\citep{Brito:2018rfr} 
+(henceforth referred to as \paperone). Unlike methods that focus \ab{only} 
+on the post-merger signal, it \sout{describes a framework in which a} 
+\ab{employs the} complete inspiral-merger-ringdown
+(IMR) waveform \sout{model is used} to measure the complex QNM
+frequencies. This \sout{allows} \ab{gives} access to the full SNR of the signal,
+reducing measurement uncertainties. Moreover, the definition of the
+ringdown start time is built into the \ab{merger-ringdown} model and does not need to be
+either left as an additional free parameter or fixed using alternate
+definitions. While \paperone presented the method \ab{and tested it for }\sout{in the context of a
+non-spinning waveform model} \ab{non-spinning BBHs}, \ab{here} we extend the analysis to the \ab{more 
+realistic astrophysical} case in which BHs \ab{carry} spin\sout{s in the current paper}. \ab{Furthermore, 
+the IMR waveform model used in this paper is more accurate than what employed in \paperone, 
+because it contains more information from PN theory and it was calibrated to a much larger set 
+of numerical-relativity waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
+and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the 
+source properties \cite{paper_showing_systematics_from_ignoring_spin}.
+
+The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parametrized IMR
+waveform model. In Sec.~\ref{sec:method}, we define our testing GR  framework in which we use that model 
+to measure the complex QNM frequencies within a Bayesian formalism. Then, in Sec.~\ref{sec:results}, 
+we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze 
+the ... and constrain the QNM frequecies ...} Finally, we provide a summary of
+our results and discuss future developments in Sec.~\ref{sec:discussion}.
 
@@
 
-\section*{ACKNOWLEDGEMENTS}\label{sec:acknowledgements}
-LIGO Clusters
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+LIGO Clusters. \comment{AB: Our cluster!!!}
 
 \appendix
+
 \section{Study of syetematics on ringdown measurements}\label{sec:noise_systematics}

### 2021-01-11 papers/intro_paper/intro_paper.tex
changes in Sec. I and II

@@
-\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers]{revtex4-1}
-
+%\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers,nofootinbib]{revtex4-1}
+\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
 \usepackage{epsfig}
@@
 \newcommand{\bzeta}{\bm{\zeta}}
-\newcommand{\bs}[1]{\bm{\vec{s}_{#1}}}
+\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
 \newcommand{\Mo}{M_{\odot}}
@@
   $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
-  constraints yet using this
-  method. %Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
+  constraints yet using this method.
+%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
 \end{abstract}
@@
 compact objects spiral in \ab{loosing energy because of the emission of GWs} \sout{and \textit{plunge} due to a back-reaction
-of gravitational-wave-emission}, a \textit{merger} marked by the
+of GW-emission}, a \textit{merger} marked by the
 formation of a\sout{n} \ab{common} apparent horizon~\citep{NRpaper}, and a \sout{late-time} 
 \textit{ringdown}, \sout{where} \ab{during which} the newly formed remnant object settles down
-to a \sout{stable} Kerr \ab{BH} \sout{state through the emission of} \ab{emitting} an exponentially damped
-quasi-normal-mode (QNM) spectrum of gravitational
-radiation~\citep{vishu,earlyqnmpapers}.
+to a \sout{stable} Kerr \ab{BH} \sout{state through the emission of} \ab{emitting} \sout{an exponentially damped} 
+quasi-normal-modes (QNMs) \sout{spectrum of gravitational
+radiation}~\citep{vishu,earlyqnmpapers} \ab{(i.e., damped oscillations with specific, discrete 
+frequencies and decay times)}.
 
 The LIGO-Virgo collaborations \ab{have released companion papers \cite{}} detailing their \sout{latest} results 
-of tests of GR using \sout{events} \ab{GW150914 \cite{} and 
-the first two transient catalogues (TC) (i.e., GWTC-1\cite{}  and GWTC-2 \cite{})}. 
+of tests of GR  \sout{using events} \ab{for GW150914} \cite{} and \ab{for several GW events of} 
+the \sout{first} two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
 The results include tests of GW generation and source dynamics, where bounds are placed on
-parametrized deviations in the post-Newtonian \ab{(PN)} coefficients describing
+parameterized deviations in the post-Newtonian \ab{(PN)} coefficients describing
 the early inspiral~\citep{earlydevelopmentpapers}, and
@@
 propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and consequently, the mass of
+upper bounds on the Compton wavelength and, consequently, the mass of
 the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
 polarization of gravitational radiation using a
-multi-GW-detector network~\citep{gw170814,isi2017probing}. The \ab{GWTC-1/2} paper\ab{s} also 
+multi--GW-detector network~\citep{gw170814,isi2017probing}. The \ab{GWTC-1/2} paper\ab{s} also 
 check\sout{s} for consistency between different portions of the signal using estimates
@@
 \ab{The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
-first measurement of the dominant damped-sinusoidal signal in the ringdown stage of a BBH 
+first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH 
 coalescence.} The LIGO-Virgo O3a testing GR paper~\cite{} \ab{has recently reported} 
@@
 frequencies of gravitational radiation emitted by a perturbed isolated
-BH is uniquely determined by its mass and spin angular momentum. Hence
+BH \ab{are} \sout{is} uniquely determined by its mass and spin angular momentum. Hence
 a test of the no-hair conjecture would involve checking for
@@
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and checking for consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
+spectroscopy), and \sout{checking for} consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
 in that direction \comment{AB: which direction? There are papers by Nikhef group and 
@@
 
-\comment{AB: I don't understand the next senetnce, it looks to me out of context.} 
+\comment{AB: I don't understand the next sentence, it looks to me out of context.} 
 Most of the tests mentioned above focus on analysing the post-merger
@@
 and looks out of context and incomplete. Also, why are we citing only those papers? The matter 
-has a long history. There have been calibrations to NR of damped-sinusoid signals.} 
+has a long history. There have been calibrations to NR of damped- oscillation signals.} 
 The ringdown start time is not a clearly defined
@@
 free parameter to be estimated directly from the data. Uncertainties
-in estimates of the ringdown start-time, as well as an overall lack of
+in estimates of the ringdown start-time, as well as, an overall lack of
 SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors result in significant statistical uncertainties
+ground-based detectors, result in significant statistical uncertainties
 in the measurement of the QNM frequencies.
@@
 the IMR waveform model used in this paper is more accurate than what employed in \paperone, 
-because it contains more information from PN theory and it was calibrated to a much larger set 
-of numerical-relativity waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
-and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the 
+because it contains higher-order corrections in PN theory and it was calibrated to a much larger set 
+of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
+and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the 
 source properties \cite{paper_showing_systematics_from_ignoring_spin}.
 
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parametrized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our testing GR  framework in which we use that model 
-to measure the complex QNM frequencies within a Bayesian formalism. Then, in Sec.~\ref{sec:results}, 
+The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
+waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR\ab{, notably how we can measure 
+complex QNM frequencies with our parameterized model within a Bayesian formalism}. Then, in Sec.~\ref{sec:results}, 
 we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze 
-the ... and constrain the QNM frequecies ...} Finally, we provide a summary of
-our results and discuss future developments in Sec.~\ref{sec:discussion}.
+the ... and constrain the QNM frequecies ... Finally, in Sec.~\ref{sec:discussion} we provide a summary of
+our results and discuss future developments.}
 
@@
 
-A GW signal from the (quasi-circular) coalescence of two BHs is completely described in GR by a fixed set of $15$ parameters, $\bxigr$.
-These can be grouped into the \emph{intrinsic} parameters: the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the initial binary and a reference time and phase $t_c, \phi_c$ respectively; and the \emph{extrinsic} parameters: the sky position of the binary ($\alpha$, $\delta$), the luminosity distance, $d_L$, and its orientation described through the inclination of the binary $\iota$ and its polarisation $\psi$.
-If the spins of the individual BHs are assumed to be aligned with the orbital angular momentum of the binary, then GW signal has a reduced dimensionality of $11$ parameters.
-The aligned-spin components are defined as: $a_{iz} = s_{iz}/m_i$, where $i=1,2$ for the two BHs.
+\comment{AB: In teh following, I will not use much the strike-out, but instead I will 
+bracket in color the text that I have changed.}
+
+A GW signal from the (quasi-circular) coalescence of two BHs is
+completely described in GR by a \sout{fixed set of} $15$ parameters,
+$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
+the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the \ab{component 
+objects in the} \sout{initial} binary; and the 
+\emph{extrinsic} parameters: \ab{a reference time $t_c$ and phase 
+$\phi_c$,} the sky position of the binary ($\alpha$,
+$\delta$), the luminosity distance, $d_L$, and \ab{the binary's} orientation
+described through the inclination of the binary $\iota$ and its
+polarization $\psi$. \ab{We also introduce the total mass $M = m_1+m_2$, 
+and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$}.
+
+\ab{Here, we focus on BHs with spins aligned or anti-aligned 
+with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
+the GW signal depends on $11$ parameters. We denote the 
+aligned-spin \ab{(dimensionless)} components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.}
 
@@
 
-As in \paperone, we use an IMR waveform model developed within the EOB formalism.
-However, in this work we extend the results of \paperone by using a waveform model for spinning, non-precessing BBHs.
-Namely we use as our baseline model the aligned-spin multipolar waveform developed in Ref.~\citep{Cotesta:2018fcv}.
-In addition to being calibrated to NR simulations, this model also uses information from BH perturbation theory for the merger and ringdown phases.
-Therefore this waveform model provides a very accurate and faithful semi-analytic description of the inspiral, merger and ringdown phases.
-Henceforth we will denote this model by $\SEOB$ for short.
+As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
+formalism~\cite{}. \ab{However, whereas \paperone was limited to non-spinning multipolar waveforms, 
+here we use as our baseline model the aligned-spin multipolar waveform model 
+developed in Ref.~\citep{Cotesta:2018fcv}}. In addition to being
+calibrated to NR simulations, this model also uses information from BH
+perturbation theory for the merger and ringdown phases. \sout{Therefore this
+waveform model provides a very accurate and faithful semi-analytic
+description of the inspiral, merger and ringdown phases.} \ab{Henceforth we
+will denote this model by $\SEOB$ for short}~\footnote{\ab{In the LIGO Algorithm Library (LAL), this 
+waveform model is called {\tt SEOBNRv4HM}.}}.
 
@@
 %
-where $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics.
+\comment{AB: there is a mismatch of notations for the parameters with respect to what was introduced above.}
+where $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\varphi)$ are the $-2$ spin-weighted spherical harmonics.
 The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
@@
 \end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown phase.
-The merger-ringdown $\SEOB$ modes read~\citep{Bohe:2016gbl,Cotesta:2018fcv}
+where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown \ab{waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}}
 %
@@
 are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
+This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
 % in terms of $c_{1,f}^{\ell   m},\ c_{2,f}^{\ell m},\ \sigma^\textrm{R}_{\ell m},\ |h_{\ell    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell  m})|,\ \partial_t|h_{\ell    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|$ as
 \begin{align} 
+\label{c1}
 c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
@@
     m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
+\label{c2}
 c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
@@
 \begin{align}
+\label{d1}    
 d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
@@
 
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the complex frequencies $\sigma_{\ell m 0}$  are expressed in terms of the final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the latter are related to the BBH's component masses and spins through NR--fitting-formulas obtained in GR~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values.
-Henceforth called $\pSEOB$, this model uses a parameterised version of the $\SEOB$ model where the frequency and the damping time of the ${\ell m 0}$ mode, i.e, $(f_{\ell m 0}, \tau _{\ell m 0})$ is defined through fractional deviations, ($(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$), from the corresponding GR values, i.e., the predictions of the QNM frequencies obtained using the fits~\cite{Taracchini:2013rva,Hofmann:2016yih}:
+In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
+complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
+final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
+latter are related to the BBH's component masses and spins through
+NR--fitting-formulas obtained in
+GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
+spirit of what was done in \paperone, we promote the QNM (complex)
+frequencies to be free parameters of the model, while keeping the
+inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
+to their GR values. \ab{More explicitly, we introduce a parameterized 
+version of the $\SEOB$ model where the frequency and the
+damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
+_{\ell m 0})$) is defined through the fractional deviations, $(\delta
+f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
+values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,} 
+\begin{eqnarray}
+f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
+\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
+\end{eqnarray}
+\ab{We denote such a parameterized waveform model \pSEOB}~\footnote{\ab{This 
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}}.
 
-\begin{eqnarray}
-f_{\ell m 0} &:=& f_{\ell m 0}^{\text{GR}} (1 + \delta f_{\ell m 0})\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &:=& \tau _{\ell m 0}^{\text{GR}} (1 + \delta \tau_{\ell m 0}) \label{eq:nongr_freqs_b}
-\end{eqnarray}
-The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are constructed using the same NR--fitting--formula prescriptiion described above.
-We note that when leaving $\sigma_{\ell m}$ to vary freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies, as can be seen from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$.
+\ab{As said}, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+constructed using the same NR--fitting--formula \sout{prescriptiion} 
+described above. We note that when leaving $\sigma_{\ell m}$ to vary
+freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
+  m}(t)$ \sout{will} in general also differ from the GR prediction\ab{s}, since
+those functions depend on the QNM complex frequencies, as can be seen
+from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ \ab{in Eqs.~(\ref{c1}), 
+(\ref{c2}), and (\ref{d1}).}
 
-\subsection{Bayesian PE}\label{sec:method}
+\subsection{Bayesian Parameter Estimation}\label{sec:method}
 
-The parametrised model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
+The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
 One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) := \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
+The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
 In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
 The likelihood function can consequently be defined as:
+%
+\begin{equation}
+\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
+\label{eq:likelihood}
+\end{equation}
+%
+where $\langle . | . \rangle$ is the following noise-weighted inner product:
+%
+\begin{equation}
+\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
+\label{eq:nwip}
+\end{equation}
+%
+\ab{The quantity} $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
+The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
+We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas${f_\mathrm{low}}$ is dictated by \ab{the performance of the
+GW detector at low-frequency and we assume XXX}. \comment{AB: It isn't just seismic noise. In fact, at low frequency, there are mysterious noises that people have had hard time 
+to control.} \sout{the response of the gravitational detector to low-frequency seismic noise.} Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in equation~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-Chain Monte-Carlo~\cite{xxx} or Nested Sampling~\cite{xxx}.
+For this paper, we use the lalinferencemcmc~\cite{xx} and bilby codes CITE that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
+
+Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
 
 \begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}\end{equation}
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
-\begin{equation}
-\langle A | B \rangle := \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-$\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and a $^*$ denotes complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas${f_\mathrm{low}}$ is dictated by the response of the gravitational detector to low-frequency seismic noise.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in equation~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-Chain Monte-Carlo~\cite{xxx} or Nested Sampling~\cite{xxx}.
-For this paper, we use the lalinferencemcmc~\cite{xx} and bilby codes CITE that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalise over the \emph{nuisance} parameters, to obtain the marginalised posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr
+P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
 \end{equation}
 
-For most of the results discussed in this paper, we would restrict ourselves to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes.
-In those cases we would assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or  $ \{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be fixed at their GR predictions, i.e., $\delta f_{\ell m 0} = \delta \tau_{\ell m 0} = 0$.
-This is because, for most of the high-mass events we find most appropriate for this test, the LIGO-Virgo observations are consistent with nearly-equal-mass face-on/off BH binaries for which power in the subdominant modes is not enough to attempt to measure more than one, or at most QNM frequencies simultaneously.
+For most of the results discussed in this paper, we restrict ourselves
+to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we
+\sout{would} assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
+\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
+fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
+\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH 
+events that we find most appropriate for this test, the LIGO-Virgo
+observations are consistent with nearly--equal-mass face-on/off BBHs 
+for which power in the subdominant modes is not enough to
+attempt to measure more than one, or at most \comment{AB: it seems some wrods are missing 
+to make the senetence meaningful} QNM frequencies, 
+simultaneously.
 
-Throughout our analysis, we assume uniform priors on our non-GR QNM parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$.
-However, since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are derived through NR--fits, from the corresponding priors on the initial masses and spins, this leads to a non-trivial prior on the final reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m 0})$.
-Also, given the definition of the damping time in Sec.~\ref{sec:model}, we realise $\delta \tau_{\ell m 0} = -1$ leads to the imaginary part of the frequency going to infinity.
-We avoid this by restricting the minimum of the prior on $\delta \tau_{\ell m 0}$ to be greater than $-1$.
+\ab{Lastly}, throughout our analysis, we assume uniform priors on our non-GR QNM
+parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. However,
+since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+derived through NR--fits, from the corresponding priors on the initial
+masses and spins, this leads to a non-trivial prior on the final
+reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
+  0})$. Also, given the definition of the damping time in
+Sec.~\ref{sec:model}, we \sout{realize} \ab{note} that $\delta \tau_{\ell m 0} = -1$ leads
+to the imaginary part of the frequency going to infinity. We avoid
+this by restricting the minimum of the prior on $\delta \tau_{\ell m
+  0}$ to be greater than $-1$.
 
@@
 	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalised distributions mark the 90\% credible levels.
+The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
 The black vertical and horizontal lines mark the injection values.}
@@
 We additionally investigate the effects of erroneously assuming that an underlying modified GR signal can be well-described using GR.
-We do this by estimating the parameters of our modified GR signals using the GR waveform model $\SEOB$ instead of the parametrised $\pSEOB$.
+We do this by estimating the parameters of our modified GR signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
 In such cases, we run the risk of biased parameter estimates due to an incomplete understanding of the underlying signal.
@@
 In other words, if the actual signal had deviations as large as the 50 \% of the GR prediction, the analysis with $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
-However in the case of the GW190521-like modified GR signal, a simple GR analysis of the modified GR signal would have yielded measurements distinctly different from either of the two parametrised estimates: with and without deviations.
+However in the case of the GW190521-like modified GR signal, a simple GR analysis of the modified GR signal would have yielded measurements distinctly different from either of the two parameterized estimates: with and without deviations.
 The fact that the GW190521-like signal has a much lower SNR than GW150914 might be a possible reason for the the measurement of the final quantities to be more susceptible to noise.
@@
 The underlying signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalised distributions mark the 90\% credible levels.
+The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
 The black vertical and horizontal lines mark the injection values.
@@
 
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalised distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
+We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
 These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\abhi{add text on the hierarchical analysis if we want to include that analysis}

### 2021-01-11 papers/intro_paper/intro_paper.tex
changes in Sec. I and II

@@
 GW detector at low-frequency and we assume XXX}. \comment{AB: It isn't just seismic noise. In fact, at low frequency, there are mysterious noises that people have had hard time 
-to control.} \sout{the response of the gravitational detector to low-frequency seismic noise.} Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in equation~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-Chain Monte-Carlo~\cite{xxx} or Nested Sampling~\cite{xxx}.
-For this paper, we use the lalinferencemcmc~\cite{xx} and bilby codes CITE that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
+to control.} \sout{the response of the gravitational detector to low-frequency seismic noise.} Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{} or Nested Sampling~\cite{}.
+For this paper, we use the \verb+LALInference+~\cite{} and \verb+Bilby+ codes~\cite{} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
 

### 2021-01-11 papers/intro_paper/intro_paper.tex
changes in Sec. III

@@
 
-\subsection{Waveform Model}\label{sec:model}
+\subsection{Waveform model}\label{sec:model}
 
@@
 
-\subsection{Bayesian Parameter Estimation}\label{sec:method}
+\subsection{Bayesian parameter estimation}\label{sec:method}
 
@@
 
-\subsection{Simulations using GR signals in Gaussian Noise}\label{ssec:gr_signal}
+\subsection{\ab{Synthetic-signal injections in General Relativity with Gaussian noise}}\label{ssec:gr_signal}
 
-First, we demonstrate our method on GW signals from BBH systems that are well described by GR.
-We inject simulated GW signals modellng inspiral, merger and ringdown of BBHs into coloured Gaussian noise with PSDs expected at design sensitivities of Advanced LIGO-Virgo CITE.
-In particular we choose parameters similar to two specific GW events, GW150914 CITE and GW190521 CITE.
-The details of the injections are provided in Table~\ref{tab:injection_values}.
-These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the SNR pre- and post-merger return reliable parameter estimation results.
-To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, $\SEOB$ (without allowing for deviations in the QNM parameters) to simulate our GW signal.
-And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the noise.
-A detailed study on noise systematics for one of the GW events is presented in Appendix~\ref{sec:noise_systematics}.
-As in the case of the actual detections, we consider a two-detector advanced LIGO network at Hanford and Livingston, having identical PSDs.
-The distance to the two simulated events is rescaled such that the SNR in the detector network is same as the actual event, i.e, 24 (14) for GW150914 (GW190521).
-Since (almost) equal-mass binaries like GW150914 and GW190521 observed at moderately high SNRs are not expected to have a loud ringdown signal, we restrict ourselves to estimating the frequency and damping time of the $(\ell m) = (2,2)$, i.e., $\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to their GR values.
-
-We find, as one might expect, that the posterior distribution on the parameters describing fractional deviations in the frequency and damping time are consistent with zero (left panels of Fig.~\ref{fig:simulated_signal_GR}).
-One can then convert these fractional quantities into absolute quantities using the relations given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and construct posterior distributions on these effective quantities, $(\fngr{220}, \taungr{220})$ (right panels of Fig.~\ref{fig:simulated_signal_GR}).
-In each of these cases, recovered posterior are consistent with the GR predictions (black solid lines).
+\ab{We demonstrate our method using synthetic-signal injections describing GWs 
+from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and 
+Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.} 
+For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and 
+GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}. 
+These two binary systems are representative of the kind of systems for which 
+the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the  
+pre- and post-merger SNRs return reliable parameter-estimation results.}
 
@@
  \hline
- Event & $m_{1,d} (\Mo)$ &  $m_{2,d} (\Mo)$ & $a_{1z}$ & $a_{2z}$ & SNR \\ 
+ Event & $m_{1,d} (\Mo)$ &  $m_{2,d} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
  \hline
- GW150914 & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521 & 150 & 120 & 0.02 & -0.39 & 14 \\ 
+ GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
+ GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
  SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
@@
 \end{tabular}
-\caption{Details of the injection parameters, chosen to be similar to the actual GW events. $(m_{1,d},m_{2,d})$ are the detector-frame masses of the primary and secondary BHs respectively.}
+\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in teh first column. The parameters 
+$(m_{1,d},m_{2,d})$ are the detector-frame masses of the primary and secondary BHs, respectively.}
 \label{tab:injection_values}
@@
 
+\comment{AB: Nothing is said in the text about the third mock signal in the Table!}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
+\begin{figure*}[hbt]
 \begin{center}
@@
 The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.}
+The black vertical and horizontal lines mark the injection values.
+\comment{AB: I would use a different color for the bottom figures, e.g., ``green''.
+Please also indicate on the figures:
+GW150914-like and GW190521-like.}}
 	\label{fig:simulated_signal_GR}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\ab{To avoid possible systematic biases in our parameter-estimation analysis 
+due to error in waveform modeling,} we use the GR version of the same waveform,
+$\SEOB$ (without allowing for deviations in the QNM parameters) to
+simulate our GW signal. And to avoid systematic biases due to noise,
+we use an averaged (zero-noise) realization of the noise. A detailed
+study on noise systematics for one of the GW events is presented in
+Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to teh Appendix is out of context. 
+Why should the reader appreciate at this stage of the paper, where we have not yet 
+discussed results with real data, what is in the Appendix?} As in the case of the actual
+detections, we consider a two-detector LIGO network at
+Hanford and Livingston, having identical PSDs. The distance to the two
+\ab{synthetic} events is rescaled such that the SNR in the detector network
+is the same as the actual events (i.e., 24 for GW150914 and 14 
+for GW190521). Since mearly--equal-mass binaries like GW150914 and
+GW190521 observed at moderately high SNRs are not expected to have a
+loud ringdown signal, we restrict ourselves to estimating the
+frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
+$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
+their GR values.
+
+We find, as one might expect, that the posterior distribution on the
+parameters describing fractional deviations in the frequency and
+damping time are consistent with zero (left panels of
+Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
+fractional quantities into absolute quantities using the relations
+given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
+construct posterior distributions on these effective quantities,
+$(\fngr{220}, \taungr{220})$ (right panels of
+Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
+posterior are consistent with the GR predictions (black \sout{solid lines} \ab{dot}).
 

### 2021-01-15 papers/intro_paper/intro_paper.tex
changes in Sec. III

@@
 
-\subsection{Waveform model}\label{sec:model}
+\ab{\subsection{Parameterized waveform model}}\label{sec:model}
 
@@
 
-\section{Results}\label{sec:results}
+\section{Synthetic-signal injection study}\label{sec:results}
 
-\subsection{\ab{Synthetic-signal injections in General Relativity with Gaussian noise}}\label{ssec:gr_signal}
+\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
 
@@
  \hline
- Event & $m_{1,d} (\Mo)$ &  $m_{2,d} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
+ Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
  \hline
@@
 \end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in teh first column. The parameters 
-$(m_{1,d},m_{2,d})$ are the detector-frame masses of the primary and secondary BHs, respectively.}
+\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
+$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
+\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
+The third row is completely ignored in the caption's explanations.}}
 \label{tab:injection_values}
@@
 
-\comment{AB: Nothing is said in the text about the third mock signal in the Table!}
+\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
 
@@
 The black vertical and horizontal lines mark the injection values.
-\comment{AB: I would use a different color for the bottom figures, e.g., ``green''.
-Please also indicate on the figures:
-GW150914-like and GW190521-like.}}
+\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
 	\label{fig:simulated_signal_GR}
@@
 
-\subsection{Simulations using modified GR signals in Gaussian noise}
+\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
 
-To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger, and differ in their post-merger description.
-We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $\df{220} = \dtau{220} = 0.5$ \abhi{deviations=0.1 runs are ongoing and almost done}.
-In other words, we assume that the frequency and damping time of our non-GR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}).
-We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}.
-The posterior probability distributions on $(\df{220}, \dtau{220})$ or equivalently $(\fngr{220}, \taungr{220})$ (Fig.~\ref{simulated_signal_nonGR}) are consistent with the corresponding the values of the injection parameters, indicated by the black solid lines.
+To demonstrate the robustness of the method in detecting possible
+deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
+we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
+the corresponding GR prediction up to merger, and differ in their post-merger
+description. We again choose \sout{systems with initial-}binary-parameters
+similar to GW150914 and GW190521 (as given in Table XXX), but 
+\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
+\ab{set} $\df{220} = \dtau{220} = 0.5$ \abhi{deviations=0.1 runs are ongoing and almost
+  done}. In other words, we assume that the frequency and damping time
+of our non-GR signal is 1.5 times the corresponding GR prediction,
+although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
+we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
+you just clearly refer to thePlease introduce the injected signal and the template, which is used 
+to recover it, and simply say that they belong to the same waweform model.} 
+We also avoid waveform \sout{and noise} systematic biases by choosing 
+a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
+summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
+show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
+$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
+values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
+explaining the results in teh figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
+is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
 
-We additionally investigate the effects of erroneously assuming that an underlying modified GR signal can be well-described using GR.
-We do this by estimating the parameters of our modified GR signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
-In such cases, we run the risk of biased parameter estimates due to an incomplete understanding of the underlying signal.
-The resulting posterior probability distributions are shown in the right panels of Fig.~\ref{simulated_signal_nonGR} by the pink (GW150914) and grey (GW190521) curves.
-The results are interesting and distinctly different for the two events.
-For the GW150914-like modified GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (Fig.~\ref{simulated_signal_nonGR} top right panel) are consistent with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no deviations (Fig.~\ref{simulated_signal_GR} top right panel).
-In other words, if the actual signal had deviations as large as the 50 \% of the GR prediction, the analysis with $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
-However in the case of the GW190521-like modified GR signal, a simple GR analysis of the modified GR signal would have yielded measurements distinctly different from either of the two parameterized estimates: with and without deviations.
-The fact that the GW190521-like signal has a much lower SNR than GW150914 might be a possible reason for the the measurement of the final quantities to be more susceptible to noise.
-A more detailed comparison of the other parameters, like the masses and spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR signal is shown in Fig.~\ref{fig:gr_ngr_comparison}.
+We additionally investigate the effects of erroneously assuming that
+\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
+\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
+signals using the GR waveform model $\SEOB$ instead of the parameterized 
+$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
+In such cases, we run the risk of biased parameter estimates due to an
+incomplete understanding of the underlying signal. The resulting
+posterior probability distributions are shown in the right panels of
+Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
+(GW190521-like) curves.} The results are interesting and distinctly
+different for the two events. For the GW150914-like \comment{AB: I would avoid using 
+``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
+(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
+with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
+deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
+words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
+the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
+reported \emph{no} deviation from the GR prediction. However in the
+case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
+the non-GR signal would have yielded measurements distinctly
+different from either of the two parameterized estimates: with and
+without deviations. \comment{AB: Not clear to me the next sentence. We are working 
+in Gaussian noise, so why are you referring to the noise as the culprit or the 
+source of difference?} The fact that the GW190521-like signal has a much
+lower SNR than GW150914-like signal might be a possible reason for the 
+measurement of the final quantities to be more susceptible to noise. A
+more detailed comparison of the other parameters, like the masses and
+spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR
+signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
+comment the figures. What are the main results? What do we deduce?}
 
@@
 	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarisation of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (solid orange lines), i.e., $\df{220} = \dtau{220} = 0$, and where the merger-ringdown is modified (dashed grey lines), i.e., $\df{220} = \dtau{220} = 0.5$.
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and modified GR signal.}
+Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and modified GR signal.
+\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from teh y-axis labels, but instead provide
+explanations in the caption, and use only $f(t)$.}}
 	\label{fig:nongr_waveform}
@@
 The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($SEOB$) waveform, for GW150914 (grey) and GW190521 (pink), The measurements are visibly biased.}
+In the right panels, we additionally show measurements using a GR (\SEOB) waveform, for GW150914 (grey) and GW190521 (pink), The measurements are visibly biased.
+\comment{AB:The labels of the plots on theright are
+wrong, I believe, because otehrwise I don't understand the results. Please rewrite the caption in a more concise and clear way. It is difficult 
+to understand it. We are not using the notation ``modGR'' anywhere else in the paper. We don't invent new notations each time!}}
 	\label{fig:simulated_signal_nonGR}
@@
 
-\subsection{Test of the No hair theorem}\label{ssec:nohairtheorem}
+\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
 
@@
 
-\subsection{Results on actual LIGO-Virgo results}
+\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
 

### 2021-01-17 papers/intro_paper/intro_paper.tex
changes up to Sec. III

@@
 \end{eqnarray}
-\ab{We denote such a parameterized waveform model \pSEOB}~\footnote{\ab{This 
+\ab{We denote such a parameterized waveform model $\pSEOB$}~\footnote{\ab{This 
 waveform model is called {\tt pSEOBNRv4HM} in LAL.}}.
@@
 	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
+	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
 The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
@@
 Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-posterior are consistent with the GR predictions (black \sout{solid lines} \ab{dot}).
+\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
+(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
+to 1D and 2D posteriors when discussing the figures.}}
 
@@
 \sout{we attach a phenomenological post-merger signal described by deviation parameters} 
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \abhi{deviations=0.1 runs are ongoing and almost
-  done}. In other words, we assume that the frequency and damping time
+\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
+  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
+based on QNM predictions in theories of gravity alternative to GR.}. 
+In other words, we assume that the frequency and damping time
 of our non-GR signal is 1.5 times the corresponding GR prediction,
@@
 more detailed comparison of the other parameters, like the masses and
-spins, between an $pSEOB$ and an $SEOB$ measurement of a modified GR
+spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
 signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
@@
 	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarisation of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (solid orange lines), i.e., $\df{220} = \dtau{220} = 0$, and where the merger-ringdown is modified (dashed grey lines), i.e., $\df{220} = \dtau{220} = 0.5$.
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and modified GR signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from teh y-axis labels, but instead provide
-explanations in the caption, and use only $f(t)$.}}
+	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
+Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
+\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
 	\label{fig:nongr_waveform}
@@
 	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $\{\df{220},\dtau{220}\}$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for modGR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The underlying signal has a deviation, $\df{220} = \dtau{220} = XX$.
+	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
 The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
 The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR (\SEOB) waveform, for GW150914 (grey) and GW190521 (pink), The measurements are visibly biased.
-\comment{AB:The labels of the plots on theright are
-wrong, I believe, because otehrwise I don't understand the results. Please rewrite the caption in a more concise and clear way. It is difficult 
-to understand it. We are not using the notation ``modGR'' anywhere else in the paper. We don't invent new notations each time!}}
+In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
+GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
+switch the red and blue colors.
+The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
+Please indicate on the figures: GW150914-like and GW190521-like.}}
 	\label{fig:simulated_signal_nonGR}
@@
 	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of the recovered parameters when the underlying signal is assumed to be a GR signal or a modified GR signal.
-In both cases, the actual underlying signal is a modified GR signal with parameters similar to GW150914 (left panels) and GW190521 (right panels) respectively.
-The initial parameters are given in Table~\ref{tab:injection_values}, with the QNM parameters defined by $\df{220} = \dtau{220} = 0.5$.
-For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.
-The panels (from top to bottom) show the recoveries in (detector-frame) initial masses (first row), z-components of dimensionless initial spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f, a_f$) from the frequency and damping time (obtained by inverting the Berti fits) CITE}
+	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
+\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
+a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
+(obtained by inverting the Berti fits).
+\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
+Also please specify if the remnant mass is the detector-frame mass.
+Please
+switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
 	\label{fig:gr_ngr_comparison}
@@
 
-Finally, we provide a simple demonstration of a test of the no-hair theorem using our model.
-As described in the introduction, any test of the no-hair theorem of BHs would need to involve independent measurements of (at least) two different QNMs.
-We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning BBH with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$ (Table~\ref{tab:injection_values}).
+Finally, we provide a simple demonstration of a test of the no-hair
+theorem using our model. As described in the introduction, any test of
+the no-hair theorem of BHs would need to involve independent
+measurements of (at least) two different QNMs.
+
+\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
+corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
+\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
 We choose an asymmetric system to increase the SNR in the higher modes. 
-We also rescale the distance and orientation of the binary such that the total SNR of the signal in a network of three detectors, LIGO Hanford, Livingston and Virgo, is 75.
-Based on the LIGO-Virgo observations during O3a, such asymmetric and loud signals are no longer just a theoretical prediction but quite plausible at design sensitivities.
-Using this signal, we attempt to measure the QNM frequencies $(2,\pm 2)$ and $(3,\pm 3)$ modes together (Fig.~\ref{fig:nohair_sxs}).
-The SNR in other sub-dominant modes is too less for us to estimate them reliably.
+We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
+such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
+the three detectors, LIGO Hanford, Livingston and
+Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
+asymmetric and loud signals are no longer just a theoretical
+prediction, but quite plausible at design sensitivities. Using this
+signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
+$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
+our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
+other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
 
-The fractional deviations in the estimates of the damping time and frequency of either mode is expected to be consistent with 0, as we indeed find in the left panel of Fig.~\ref{fig:nohair_sxs}.
-Consequently we find that the reconstructed quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330}, \taungr{330})$  are also consistent with the corresponding predictions for a BBH merger in GR.
-As a consequence, the information from these two independent measures correspond to a unique remnant object, which is completely described by its mass and spin angular momentum \abhi{have the mf-af plot as well as a third panel to show consistency}.
-For most of the events observed so far, the power in the $(3,\pm 3)$ has not been sufficient to measure it along with the $(2,\pm 2)$, or in fact, in its place.
-However, it might also be possible to combine information from multiple observation, as is likely over the coming few years of GW astronomy with the LIGO-Virgo detectors, to obtain meaningful constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.
+The fractional deviations in the estimates of the damping time and
+frequency of either mode is expected to be consistent with 0, as we
+indeed find in the left panel of
+Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
+quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
+\taungr{330})$ are also consistent with the corresponding predictions
+for a BBH merger in GR. As a consequence, the information from these
+two independent measures correspond to a unique remnant object, which
+is completely described by its mass and spin angular momentum
+\abhi{have the mf-af plot as well as a third panel to show
+  consistency}. For most of the events observed so far, the power in
+the $(3,\pm 3)$ has not been sufficient to measure it along with the
+$(2,\pm 2)$, or in fact, in its place. However, it might also be
+possible to combine information from multiple observation\sout{, as is
+likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
+detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
+other sub-dominant QNMs~\cite{}.
 
@@
 	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166_placeholder.png}	
-	\caption{\textcolor{red}{DEMO FIGURE; RUN ONGOING} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) respectively, for a numerical relativity signal corresponding to a BBH merger of $q=6$,  $M=84 \Mo$ and SNR $75$.
+	\caption{\textcolor{red}{DEMO FIGURE; RUN ONGOING} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
 The plus signs mark the GR predictions.}

### 2021-01-17 papers/intro_paper/intro_paper.tex
changes up to Sec. III
updated SXS:BBH:0166 results

@@
 
-\section{Method}
+\ab{\section{Waveform model and statistical strategy to measure quasi-normal modes}}
 
@@
 
-\subsection{Bayesian parameter estimation}\label{sec:method}
+\ab{\subsection{Bayesian parameter-estimation technique}}
+\label{sec:method}
 
@@
 
-\section{Synthetic-signal injection study}\label{sec:results}
+\ab{\section{Synthetic-signal injection study}}
+\label{sec:results}
 
@@
 \begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166_placeholder.png}	
-	\caption{\textcolor{red}{DEMO FIGURE; RUN ONGOING} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
+	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
+	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
 The plus signs mark the GR predictions.}

### 2021-01-17 papers/intro_paper/intro_paper.tex
changes for all sections

--- 2021-01-17 papers/intro_paper/intro_paper.tex
@@
 taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please 
-stick with American English.}
+stick with American English. Also, please be uniform when writing captions, when using colors and style 
+of curves in plots, when building Tables. There is not a lot of discussion in the text on the main results of the paper (Sec. IV). 
+The abstract would need to be tighten and made more crispy once the quantitative results for the 
+bounds are included.}
 
@@
 
-\section{Method}
+\ab{\section{Waveform model and statistical strategy to measure quasi-normal modes}}
 
-\comment{AB: In teh following, I will not use much the strike-out, but instead I will 
+\comment{AB: In the following, I will not use much the strike-out, but instead I will 
 bracket in color the text that I have changed.}
@@
 study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to teh Appendix is out of context. 
+Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context. 
 Why should the reader appreciate at this stage of the paper, where we have not yet 
@@
 values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
-explaining the results in teh figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
+explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
 is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
@@
 
-The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during O3a ~\cite{Abbott:2020jks}, which passed a threshold for the total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template.
-For the purpose of \cite{Abbott:2020jks}, we used a mass threshold and restricted ourselves to the highest-mass events which were expected to be most promising to study merger-ringdown.
-However, since our method relies on doing a parameter estimation on the entire inspiral-merger-ringdown signal, we require the SNR to be beyond a certain threshold throughout the signal for reliable parameter estimation of the initial and final quantities.
-In fact the SNR threshold alone should be sufficient for the analysis, and for this paper we have relaxed the mass threshold.
-This has added two events, GW190630$\_$185205 and GW190828$\_$063405, to the list of events considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking promising}.
-Fig.~\ref{fig:o1o2_events} shows results from these two events along with GW190519$\_$153544, GW190521$\_$074359, GW190910$\_$112807.
+\comment{AB: This is the most important section in the paper, because it contains the 
+main results of the paper, i.e., the constraints on QNMs using real data. It needs to 
+be expanded and results would need to be highlighted much better than in the current version. 
+I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors 
+that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have 
+a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the 
+TGR GWTC-2, but for the 22 QNM frequencies for the different GW events. 
+Figures can be used in talks, and can capture the information much better 
+than a list of numbers in a Table.}
 
-For the first time, in this paper, we present results on the relevant events from LIGO-Virgo's first and second observing runs, alongside the above events.
-Applying the same thresholds as above, we find three additional events which could be included in the analysis: GW150914, GW170104, GW170729.
-The other high-mass events from O1-O2, GW170809, GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the merger-ringdown signal.
-For the three relevant signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}.
-We also reconstruct the effective QNM parameters, $(\fngr{220}, \taungr{220})$ which are tabulated in Table~\ref{tab:qnm_o1o2_results}.
-\footnote{See Table IV of \cite{Abbott:2020jks} for a list of the SNR thresholds.
-The paper quotes them for the purpose of the IMR consistency test, but the same thresholds have been used for the $pSEOB$ test as well.} Among all the GW signals detected so far, GW150914 (solid curve in Fig.~\ref{fig:o1o2_events})is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.
+The LIGO-Virgo Collaboration recently released their testing GR
+catalogue containing results \sout{of this test} for all events observed
+during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
+total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
+post-merger regions $\geq 8$.The pre- and post-merger regions of the
+signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
+signal} before and after the signal reaches \ab{the} peak\ab{'s} 
+amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the} 
+likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
+\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the 
+entire paper, except perhaps the Conclusions section.} 
+For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
+threshold and restrict\sout{ed} ourselves to the highest-mass events which
+\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
+since our method relies on doing a parameter estimation on the entire
+inspiral-merger-ringdown signal, we require the SNR to be beyond a
+certain threshold throughout the signal for reliable parameter
+estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters, 
+there are the component masses of the holes in the binary, and the 
+mass of the remnant formed after merger.} In fact the SNR
+threshold alone should be sufficient for the analysis, and for this
+paper we have relaxed the mass threshold. This has added two events,
+GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
+considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
+  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
+events along with GW190519$\_$153544, GW190521$\_$074359,
+GW190910$\_$112807. \comment{AB: Please improve the above paragraph 
+and make it clearer which choice is made for the SNR threshold and 
+masses, and why.}
+
+\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to 
+measure the QNMs to} \sout{present results on} the relevant
+GW events from LIGO-Virgo's O1 and O2 runs, alongside
+the above events. Applying the same thresholds as above, we find three
+additional events that could be included in the analysis: GW150914,
+GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
+GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
+merger-ringdown signal. For the three relevant signals, GW150914,
+GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
+$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
+reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
+which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
+  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
+  thresholds. The paper quotes them for the purpose of the IMR
+  consistency test, but the same thresholds have been used for the
+  $pSEOB$ test, as well.} Among all the GW signals detected so far,
+GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
+loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what 
+is the ``clarity'' of a signal?} leading to the
+first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
 
@@
 	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results.pdf}
-	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the constraint the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $\{\df{220},\dtau{220}\}$ obtained using multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
+	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
+The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
 	\label{fig:o1o2_events}
@@
 
-Finally, if we assume that the fractional deviations $(\df{220}, \dtau{220})$ take the same values in multiple events, we can assume the posterior of one event to be the prior for the next, and obtain a joint posterior probability distribution.
-For $N$ observations, where $P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j-th$ observation corresponding to the data set $d_j$, $j=1...N$, the joint posterior is given by:
+Finally, if we assume that the fractional deviations $(\df{220},
+\dtau{220})$ take the same values in multiple events, we can assume
+the posterior of one event to be the prior for the next, and obtain a
+joint posterior probability distribution. For $N$ observations, where
+$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
+observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
+posterior is given by:
+%
 \begin{equation}
@@
 \end{equation}
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220}, \dtau{220})$.
-However, since we assume the prior on $(\df{220}, \dtau{220})$ to be flat or uniform, the joint posterior is equal to the joint likelihood.
+%
+where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
+\dtau{220})$. However, since we assume the prior on $(\df{220},
+\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
+the joint likelihood.
 
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\abhi{add text on the hierarchical analysis if we want to include that analysis}
+We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. 
+These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis 
+if we want to include that analysis. AB: we want to include that analysis.}
+
+\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the 
+hierarchically combined methods.}
 
@@
 \hline
-& IMR  & pSEOB & \hphantom{X} & IMR  & pSEOB \\
+& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
 \hline
@@
 
-GWGW190630$\_$185205 &
+GW190630$\_$185205 &
 $-$ &
@@
 
-GW190828$\_$063405,170729 &
+GW190828$\_$063405 &
 $-$ &
@@
 \end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE}}
+\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table 
+also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
 \label{tab:qnm_o1o2_results}
@@
 \section{Discussion}\label{sec:discussion}
+
+\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers 
+about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also 
+EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al. 
+It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with 
+Richard and Vivien.}
 
@@
 
-\section{Study of syetematics on ringdown measurements}\label{sec:noise_systematics}
+\section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
 
-In Section~\ref{sec:method}, we mentioned that the expression of the Bayesian likelihood function outlined in Eqs.~\ref{eq:likelihood} and \ref{eq:nwip} is only valid if the interferometric noise can be described as a stationary Gaussian process.
-LIGO-Virgo noise, however, frequently has non-stationary and/or non-Gaussian features, for example glitches, which can affect parameter inferences unless appropriately accounted for.
-Here we demonstrate with an example of a GW190521-like simulated signal, systematic biases likely originating from an incomplete understanding of the noise.
+\comment{AB: Please improve considerably this Appendix because it is not easy to follow the motivation and the logic. It is written for LIGO people. 
+I have tried to make changes but it is better if you do it. I risk to erase parts that you would consider important. Please write it thinking that your 
+reader is not an LSC reader!}
+
+In Sec.~\ref{sec:method}, we \ab{discussed} \sout{mentioned that} the expression of the
+Bayesian likelihood function \ab{that we use in our analysis} \sout{outlined in} \ab{(see 
+Eq.~\ref{eq:likelihood})} \ab{and stressed that it}\sout{and \ref{eq:nwip}} is only valid if the interferometric noise can be
+described as a stationary Gaussian process. LIGO-Virgo noise, however,
+frequently has non-stationary and/or non-Gaussian features, for
+example glitches, which can affect parameter inferences unless
+appropriately accounted for. Here we demonstrate\ab{, by injecting in real 
+noise a GW190521-like signal} \sout{with an example of a
+GW190521-like simulated signal}, \ab{how} systematic biases \ab{can originate} \sout{likely originating}
+from an incomplete understanding of the noise. \comment{AB: It is confusing to refer to ``systematic'' 
+biases for the noise, generally we refer to systematic biases for the waveform modeling. 
+In fact, below you also, somewhat suddenly, refer to (lack of) precession, as a possible source of systemtcis. 
+I would advice you to clarify from the beginning of this Appendix, what this study is about and what you intend to 
+do below.}
 
@@
 	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220}$ from simulations of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
+	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ from simulations \comment{AB: I have changed this in other places.
+The word ``simulations'' is confusing, because we deal with a paper in which we also refer to NR simulations.
+I suggest to use ``injected synthetic signals'' instead} of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
 The GR prediction for the frequency and damping time is indicated by the black cross.
 While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-For comparison, we also plot the 90 \% credible level for the actual event, GW190521.}
+For comparison, we also plot the 90 \% credible level for the actual event, GW190521.
+\comment{AB: For clarity, please indicate on the plot which waveform model is used to obtain such posteriors, as you did
+in the other plots of the paper. Also, please use something else instead of ``actual event'', which is confusing. The problem is 
+that the first two entries of the legend refer to the noise properties of the PE study done with an injected synthetic signal, whereas I believe ``actual event'' refers to ``real'' not injected signal
+and ``real noise''. All the entries in the legend need to be consistent with each other; you need to specify for each of them the ``signal'' and the ``noise''. I hope is clear what I am saying}}
 	\label{fig:21g_systematics}
@@
 
-We use as our underlying GR signal, an NR waveform (using the waveform model \texttt{NRSur7dq4}) with parameters similar to the actual event GW190521 (as reported in Table I of \cite{Abbott:2020tfl}).
-The predictions of the frequency and damping time for the GR signal we choose are indicated by the black cross in Fig.~\ref{fig:21g_systematics}, and for comparison, the results on the actual signal are shown with a black solid curve.
-It would appear that while the measurement of the frequency is consistent with the prediction, we overestimate the damping time.
+\ab{The spinning, precessing NR-surrogate model \texttt{NRSur7dq4}, valid up to mass ratio 4, was employed 
+(together with the $\SEOB$ model) to analyze the GW190521 signal observed by the LIGO and Virgo detectors. 
+For the injected synthetic signal we use a \texttt{NRSur7dq4} waveform with parameters similar to the ones 
+recovered by this model on the actual GW190521 data (see Table I of Ref.~\cite{Abbott:2020tfl}).}  
+\ab{In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal 
+predicts for the $(2,2)$ frequency and damping time, and for comparison, we also 
+show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$. As seen in the plot, while 
+the measurement of the frequency is consistent with the prediction, we overestimate the damping time.} \comment{AB: it is not clear 
+to me what the figure shows. Is the black line the result when running $\pSEOB$ against real data or the 
+injection in realt data?}
 
-The underlying NR signal is expected to be precessing, and since the $pSEOB$ model is built on an aligned-spin GR model, a lack of precession could bias measurements.
-We explore effects of possible waveform systematics by injecting the signal is coloured Gaussian noise.
-In this case, since the understanding of the noise realisations is complete, any measurement biases could only arise from incomplete understanding of the underlying signal.
-We find (grey curves in Fig.\ref{fig:21g_systematics}) our results to be consistent with the prediction thus ruling out a lack of precession to be a likely cause for the bias in the damping time measurement of the actual signal.
+\comment{AB: What is the ``underlying'' NR signal? I think you are referring to the 
+injected signal. Also, until now you have not discussed precession. 
+} The underlying NR signal is expected to be precessing, and since the
+$\pSEOB$ model is built on an aligned-spin GR model, a lack of
+precession could bias measurements. We explore effects of possible
+waveform systematics by injecting the signal is coloured Gaussian
+noise. In this case, since the understanding of the noise realizations
+is complete, any measurement biases could only arise from incomplete
+understanding of the \sout{underlying} \ab{injected} signal. We find (grey curves in
+Fig.\ref{fig:21g_systematics}) our results to be consistent with the
+prediction thus ruling out a lack of precession to be a likely cause
+for the bias in the damping time measurement of the actual signal.
 
-We subsequently study the effects of possible noise systematics by injecting the same \texttt{NRSur7dq4} GW signal in different realisations of actual interferometric noise around the real event GW190521.
-Since the PSDs of the GW detectors are expected to vary over longer durations of time, we select 5 different noise realisations over a segment of 2.5 hours of coincident data in both the LIGO detectors centred at the time of the actual event.
-The noise properties in this chunk of data, and consequently for all 5 simulated signals, is expected to be the closest to that for the actual event.
-The results are indicated by pink curves in Fig.~\ref{fig:21g_systematics}.
-For 3 of the 5 noise realisations, corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we recover a damping time similar to the actual event, where $t_0$ is the GPS time of the actual event.
-For the other two noise realisations, we estimate the consistent damping time but an off-set frequency, while the fifth noise realisation is consistent with both predictions.
-The SNR in the L1 Livingston detector goes down by more than 3 in some runs, indicative of how a variation in the noise strongly affects our ability to infer parameters.
-This also seems to indicate that a bias in the measurements of the damping time for the actual event can be unaccounted noise systematics.
+We subsequently study the effects of possible noise systematics by
+injecting the same \texttt{NRSur7dq4} GW signal in different
+realizations of actual interferometric noise around the real event
+GW190521. Since the PSDs of the GW detectors are expected to vary over
+longer durations of time, we select 5 different noise realizations
+over a segment of 2.5 hours of coincident data in both the LIGO
+detectors centered at the time of the actual event. The noise
+properties in this chunk of data, and consequently for all 5 simulated
+signals, is expected to be the closest to that for the actual
+event. The results are indicated by \sout{pink} \ab{green} curves in
+Fig.~\ref{fig:21g_systematics}. \ab{As it can be seen from the figure,} 
+for 3 of the 5 noise realizations,
+corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we
+recover a damping time similar to the actual event, where $t_0$ is the
+GPS time of the actual event. For the other two noise realizations, we
+estimate the consistent damping time but an off-set frequency, while
+the fifth noise realization is consistent with both predictions. The
+SNR in the Livingston detector goes down by more than \ab{a factor} 3 in some
+runs, indicative of how a variation in the noise strongly affects our
+ability to infer parameters. This also seems to indicate that a bias
+in the measurements of the damping time for the actual event \comment{AB: not clear 
+what you mean} can be unaccounted noise systematics.
 

### 2021-01-25 papers/intro_paper/intro_paper.tex
updated joint plot
update abstract and acknowledgments

@@
   The no-hair conjecture in General Relativity states that the
-  properties of an \ab{astrophysical} Kerr black hole (BH) are completely described by its
+  properties of an astrophysical Kerr black hole (BH) are completely described by its
   mass and spin angular momentum. As a consequence, the complex
@@
   remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper \ab{extends to spinning BHs earlier work} 
- \sout{outlines a} \ab{that proposed to} 
-  test \sout{of} the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown \sout{within the framework of, for the first
-  time, a spinning} using inspiral-merger-ringdown waveform\ab{s} \sout{model}, thereby
-  \sout{using} \ab{taking full advantage of} the entire signal power and removing dependency on the
+  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to 
+  test the no-hair conjecture by measuring the complex QNM
+  frequencies of a BBH ringdown using inspiral-merger-ringdown waveforms, thereby taking full advantage of the entire signal power and removing dependency on the
   predicted or estimated start time of the proposed ringdown. We
@@
   gravitational-wave (GW) signals with a ringdown different from what
-  GR predicts for Kerr BHs. \ab{Our} method was used to analyse the
+  GR predicts for Kerr BHs. Our method was used to analyse the
   properties of the merger remnants for the events observed by
@@
   the latest LIGO-Virgo publication. In this paper, for the first
-  time, we analyse the GW events from the first \ab{(O1)} and second \ab{(O2)} LIGO-Virgo
+  time, we analyse the GW events from the first (O1) and second (O2) LIGO-Virgo
   observing runs and provide joint constraints with published results
-  from O3a. We also analyse two events from the O3a \ab{catalogue} \sout{list of events} 
-  that were not considered \sout{for} \ab{in}  the initial \ab{LIGO-Virgo} analysis. Finally, the
-  joint measurements of the fractional deviations in the frequency,
+  from O3a. We also analyse two events from the O3a catalogue 
+  that were not considered in the initial LIGO-Virgo analysis. The
+  joint measurements of the fractional deviations in the frequency and damping time,
   $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
@@
 \begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results.pdf}
+	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
 	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
@@
 LIGO Clusters. \comment{AB: Our cluster!!!}
+R.B.
+acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
+792862.
+This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
 

### 2021-01-25 papers/intro_paper/intro_paper.tex
done with Sec. II

@@
 The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
-Collaboration\sout{s}~\citep{Virgo} \ab{have} recently announced their catalogue of
-gravitational-wave (GW) \sout{observations} \ab{signals}~\citep{GWTC-2} from the first
-half of the\sout{ir} third observing run (O3a)~\citep{O3reference}. Combined
-with \sout{the confirmed observations from} the first and second observing-run \ab{catalogues}~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford,
+Collaboration~\citep{Virgo} have recently announced their catalogue of
+gravitational-wave (GW) signals from the first
+half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
+with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
 Washington and Livingston, Louisiana~\citep{aasi2015characterization},
@@
 
-\ab{\section{Waveform model and statistical strategy to measure quasi-normal modes}}
-
-\comment{AB: In the following, I will not use much the strike-out, but instead I will 
-bracket in color the text that I have changed.}
+\section{Waveform model and statistical strategy to measure quasi-normal modes}
 
 A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a \sout{fixed set of} $15$ parameters,
+completely described in GR by a $15$ parameters,
 $\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the \ab{component 
-objects in the} \sout{initial} binary; and the 
-\emph{extrinsic} parameters: \ab{a reference time $t_c$ and phase 
-$\phi_c$,} the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and \ab{the binary's} orientation
+the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component 
+objects in the binary; and the 
+\emph{extrinsic} parameters: a reference time $t_c$ and phase 
+$\phi_c$, the sky position of the binary ($\alpha$,
+$\delta$), the luminosity distance, $d_L$, and the binary's orientation
 described through the inclination of the binary $\iota$ and its
-polarization $\psi$. \ab{We also introduce the total mass $M = m_1+m_2$, 
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$}.
-
-\ab{Here, we focus on BHs with spins aligned or anti-aligned 
+polarization $\psi$. We also introduce the total mass $M = m_1+m_2$, 
+and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
+
+Here, we focus on BHs with spins aligned or anti-aligned 
 with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
 the GW signal depends on $11$ parameters. We denote the 
-aligned-spin \ab{(dimensionless)} components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.}
-
-\ab{\subsection{Parameterized waveform model}}\label{sec:model}
+aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
+
+\subsection{Parameterized waveform model}\label{sec:model}
 
 As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
-formalism~\cite{}. \ab{However, whereas \paperone was limited to non-spinning multipolar waveforms, 
+formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms, 
 here we use as our baseline model the aligned-spin multipolar waveform model 
-developed in Ref.~\citep{Cotesta:2018fcv}}. In addition to being
+developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
 calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. \sout{Therefore this
-waveform model provides a very accurate and faithful semi-analytic
-description of the inspiral, merger and ringdown phases.} \ab{Henceforth we
-will denote this model by $\SEOB$ for short}~\footnote{\ab{In the LIGO Algorithm Library (LAL), this 
-waveform model is called {\tt SEOBNRv4HM}.}}.
+perturbation theory for the merger and ringdown phases. Henceforth we
+will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this 
+waveform model is called {\tt SEOBNRv4HM}.}.
 
@@
 \begin{equation}
-h_+(\iota,\varphi;t ) - i h_\times(\iota,\varphi;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi)\, h_{\ell m}(t)\,,
+h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
 \end{equation}
 %
-\comment{AB: there is a mismatch of notations for the parameters with respect to what was introduced above.}
-where $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\varphi)$ are the $-2$ spin-weighted spherical harmonics.
+where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
 The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
@@
 \end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown \ab{waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}}
+where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
 %
@@
 This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-% in terms of $c_{1,f}^{\ell   m},\ c_{2,f}^{\ell m},\ \sigma^\textrm{R}_{\ell m},\ |h_{\ell    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell  m})|,\ \partial_t|h_{\ell    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|$ as
+%
 \begin{align} 
@@
 inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. \ab{More explicitly, we introduce a parameterized 
+to their GR values. More explicitly, we introduce a parameterized 
 version of the $\SEOB$ model where the frequency and the
@@
 f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,} 
+values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
 \begin{eqnarray}
@@
 \end{eqnarray}
-\ab{We denote such a parameterized waveform model $\pSEOB$}~\footnote{\ab{This 
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}}.
-
-\ab{As said}, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula \sout{prescriptiion} 
+We denote such a parameterized waveform model $\pSEOB$~\footnote{This 
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
+
+As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+constructed using the same NR--fitting--formula 
 described above. We note that when leaving $\sigma_{\ell m}$ to vary
 freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ \sout{will} in general also differ from the GR prediction\ab{s}, since
+  m}(t)$ in general also differ from the GR predictions, since
 those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ \ab{in Eqs.~(\ref{c1}), 
-(\ref{c2}), and (\ref{d1}).}
-
-\ab{\subsection{Bayesian parameter-estimation technique}}
+from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}), 
+(\ref{c2}), and (\ref{d1}).
+
+\subsection{Bayesian parameter-estimation technique}
 \label{sec:method}
@@
 %
-\ab{The quantity} $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
+The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
 The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas${f_\mathrm{low}}$ is dictated by \ab{the performance of the
-GW detector at low-frequency and we assume XXX}. \comment{AB: It isn't just seismic noise. In fact, at low frequency, there are mysterious noises that people have had hard time 
-to control.} \sout{the response of the gravitational detector to low-frequency seismic noise.} Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{} or Nested Sampling~\cite{}.
-For this paper, we use the \verb+LALInference+~\cite{} and \verb+Bilby+ codes~\cite{} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
+We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
+GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
+Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
+For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
 
@@
 For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we
-\sout{would} assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
+to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
 \{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
@@
 for which power in the subdominant modes is not enough to
-attempt to measure more than one, or at most \comment{AB: it seems some wrods are missing 
-to make the senetence meaningful} QNM frequencies, 
-simultaneously.
-
-\ab{Lastly}, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. However,
+attempt to measure more than one QNM complex frequency.
+
+Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
+parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
 since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
@@
   0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we \sout{realize} \ab{note} that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the frequency going to infinity. We avoid
+Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
+to the imaginary part of the QNM complex frequency going to infinity. We avoid
 this by restricting the minimum of the prior on $\delta \tau_{\ell m

### 2021-01-25 papers/intro_paper/intro_paper.tex
edits to intro<

@@
 
-\title{\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}}
+\title{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}
 
@@
 and the Advanced Virgo detector in Cascina,
-Italy~\citep{acernese2014advanced} have now detected \sout{more than} $50$ GW
+Italy~\citep{acernese2014advanced} have now detected $50$ GW
 events from the merger of compact objects like neutron stars and/or
-black holes (BHs).\sout{, collectively called compact binary coalescences
-(CBCs).} Alongside independent claims of
-detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020},
-\sout{this} \ab{these results} \sout{has} \ab{have} firmly established the field of GW astronomy, five years \sout{on
-from} \ab{after} the first \sout{ever direct} detection of a GW \ab{passing through the} \sout{on} Earth, \ab{notably GW150914} 
-\sout{on September 14,2015}~\citep{abbott2016observation}.
+black holes (BHs). Alongside independent claims of
+detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, notably GW150914~\citep{abbott2016observation}.
 
-\ab{The observation of GWs has} had significant astrophysical and cosmological
+The observation of GWs has had significant astrophysical and cosmological
 implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
-has also allowed us to \sout{make statements in} \ab{probe} fundamental
-physics \sout{.Specifically, LIGO-Virgo's observations have allowed us to} and 
-test predictions of Einstein's theory of General Relativity 
-(GR)~\citep{GR} in the previously unexplored \ab{highly-dynamical, and strong field 
-regime} \sout{of highly relativistic, strong-field regimes of
-gravity}~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR\sout{, a CBC
-involving two BHs (}a binary black hole (BBH) system\sout{)} is described \sout{in} \ab{by}
-three \sout{distinct} phases: an early \textit{inspiral}, where the two
-compact objects spiral in \ab{loosing energy because of the emission of GWs} \sout{and \textit{plunge} due to a back-reaction
-of GW-emission}, a \textit{merger} marked by the
-formation of a\sout{n} \ab{common} apparent horizon~\citep{NRpaper}, and a \sout{late-time} 
-\textit{ringdown}, \sout{where} \ab{during which} the newly formed remnant object settles down
-to a \sout{stable} Kerr \ab{BH} \sout{state through the emission of} \ab{emitting} \sout{an exponentially damped} 
-quasi-normal-modes (QNMs) \sout{spectrum of gravitational
-radiation}~\citep{vishu,earlyqnmpapers} \ab{(i.e., damped oscillations with specific, discrete 
-frequencies and decay times)}.
+has also allowed us to probe fundamental
+physics and test predictions of Einstein's theory of General Relativity 
+(GR) in the previously unexplored highly-dynamical, and strong field 
+regime~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR, a binary black hole (BBH) system is described by
+three distinct phases: an early \textit{inspiral}, where the two
+compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
+formation of a common apparent horizon~\citep{NRpaper}, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\citep{vishu,earlyqnmpapers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
 
-The LIGO-Virgo collaborations \ab{have released companion papers \cite{}} detailing their \sout{latest} results 
-of tests of GR  \sout{using events} \ab{for GW150914} \cite{} and \ab{for several GW events of} 
-the \sout{first} two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
+The LIGO-Virgo collaborations have released companion papers \cite{} detailing their results 
+of tests of GR for GW150914 \cite{} and for several GW events of 
+the two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
 The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian \ab{(PN)} coefficients describing
+parameterized deviations in the post-Newtonian (PN) coefficients describing
 the early inspiral~\citep{earlydevelopmentpapers}, and
@@
 polarization of gravitational radiation using a
-multi--GW-detector network~\citep{gw170814,isi2017probing}. The \ab{GWTC-1/2} paper\ab{s} also 
-check\sout{s} for consistency between different portions of the signal using estimates
-\sout{of} \ab{for the} predicted mass and spin of the remnant
+multi--GW-detector network~\citep{gw170814,isi2017probing}. The GWTC-1/2 papers also 
+check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
 object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
@@
 
-\ab{The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
+The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
 first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH 
-coalescence.} The LIGO-Virgo O3a testing GR paper~\cite{} \ab{has recently reported} 
-\sout{also details results on tests} \ab{a comprehensive analysis of the properties of the 
-remnant object, including the ringdown stage, for tens of GW events.}   
-\sout{BH ringdown and nature of the remnant object, which is an active field
-of research at the moment.} The no-hair conjecture in GR~\citep{}
-states that an (electrically neutral) astrophysical BH is completely
+coalescence. The LIGO-Virgo O3a testing GR paper~\cite{} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
+The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely
 described by two observables: mass and spin angular momentum. One
@@
 frequencies of gravitational radiation emitted by a perturbed isolated
-BH \ab{are} \sout{is} uniquely determined by its mass and spin angular momentum. Hence
+BH are uniquely determined by its mass and spin angular momentum. Hence
 a test of the no-hair conjecture would involve checking for

### 2021-01-25 papers/intro_paper/abstract.tex
divided up paper into input segments

--- 2021-01-25 papers/intro_paper/intro_paper.tex
@@
-%\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers,nofootinbib]{revtex4-1}
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
-\usepackage{epsfig}
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{bm}
-\usepackage{times}
-\usepackage{xspace}
-\usepackage[varg]{txfonts}
-\usepackage[normalem]{ulem} % To get strikethrough (\sout)
-\usepackage[colorlinks]{hyperref}
-\usepackage[caption=false]{subfig}
-\usepackage{booktabs}
-\usepackage{url}
-\usepackage{float}
-\usepackage[bottom]{footmisc}
-\usepackage{lineno}
-%\linenumbers
-
-\definecolor{LinkColor}{rgb}{0.75, 0, 0}
-\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
-\definecolor{UrlColor}{rgb}{0, 0, 0.75}
-\hypersetup{linkcolor=LinkColor}
-\hypersetup{citecolor=CiteColor}
-\hypersetup{urlcolor=UrlColor}
-\usepackage{perpage}
-\MakePerPage{footnote}
-
-\newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
-\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
-\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
-\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
-
-\newcommand{\h}{\mathpzc{h}}
-\newcommand{\Hhat}{\hat{\mathpzc{H}}}
-\newcommand{\B}{\mathpzc{B}}
-\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
-\newcommand{\xilm}{\xi_{\ell m}}
-\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
-\newcommand{\Y}{{Y}^{-2}}
-\newcommand{\hc}{h_\times}
-\newcommand{\hp}{h_+}
-\newcommand{\Fc}{F_\times}
-\newcommand{\Fp}{F_+}
-\newcommand{\Mf}{M_f}
-\newcommand{\cA}{\mathpzc{A}}
-\newcommand{\lm}{_{\ell m}}
-\newcommand{\deff}{d_\mathrm{eff}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\blambda}{\bm{\lambda}}
-\newcommand{\btheta}{\bm{\theta}}
-\newcommand{\bxi}{\bm{\xi}}
-\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
-\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
-\newcommand{\bzeta}{\bm{\zeta}}
-\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
-\newcommand{\Mo}{M_{\odot}}
-\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
-\newcommand{\FF}{\mathrm{FF}}
-\newcommand{\e}{\mathrm{e}}
-\newcommand{\rhoopt}{\rho_\mathrm{opt}}
-\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
-\newcommand{\fqnm}{f}
-\newcommand{\sigmaqnm}{\sigma}
-\newcommand{\n}{\mathbf{n}}
-\newcommand*{\skymapscale}{0.5}
-\newcommand*{\paramestscale}{0.455}
-\newcommand{\df}[1]{\delta f_{\text{#1}}}
-\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f_{\text{#1}}}
-\newcommand{\taungr}[1]{\tau_{\text{#1}}}
-\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
-\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
-\newcommand{\pSEOB}{\texttt{pSEOBNR}}
-\newcommand{\SEOB}{\texttt{SEOBNR}}
-
-\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
-\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
-
-\begin{document}
-
-%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
-
-\title{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}
-
-\author{Abhirup Ghosh}
-\AEI
-\author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
-\author{Alessandra Buonanno}
-\AEI
-\UMD
-
-\date{\today}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
   The no-hair conjecture in General Relativity states that the
@@
 %Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
-
-\section{Introduction}\label{sec:intro}
-
-\comment{AB: Please make the citations in the bibliography uniform (I would stick with citations 
-taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please 
-stick with American English. Also, please be uniform when writing captions, when using colors and style 
-of curves in plots, when building Tables. There is not a lot of discussion in the text on the main results of the paper (Sec. IV). 
-The abstract would need to be tighten and made more crispy once the quantitative results for the 
-bounds are included.}
-
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
-Collaboration~\citep{Virgo} have recently announced their catalogue of
-gravitational-wave (GW) signals from the first
-half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
-with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\citep{aasi2015characterization},
-and the Advanced Virgo detector in Cascina,
-Italy~\citep{acernese2014advanced} have now detected $50$ GW
-events from the merger of compact objects like neutron stars and/or
-black holes (BHs). Alongside independent claims of
-detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, notably GW150914~\citep{abbott2016observation}.
-
-The observation of GWs has had significant astrophysical and cosmological
-implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
-has also allowed us to probe fundamental
-physics and test predictions of Einstein's theory of General Relativity 
-(GR) in the previously unexplored highly-dynamical, and strong field 
-regime~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}, where the two
-compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon~\citep{NRpaper}, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\citep{vishu,earlyqnmpapers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
-
-The LIGO-Virgo collaborations have released companion papers \cite{} detailing their results 
-of tests of GR for GW150914 \cite{} and for several GW events of 
-the two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
-The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral~\citep{earlydevelopmentpapers}, and
-phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\citep{TIGERmethodspapers}; tests of GW
-propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
-polarization of gravitational radiation using a
-multi--GW-detector network~\citep{gw170814,isi2017probing}. The GWTC-1/2 papers also 
-check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
-consistency of the residuals with interferometric
-noise~\citep{Ghonge:2020suv,gwtc1_tgr}. None of these tests report any
-departure from the predictions of GR.
-
-The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
-first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH 
-coalescence. The LIGO-Virgo O3a testing GR paper~\cite{} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely
-described by two observables: mass and spin angular momentum. One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin angular momentum. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.
-
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in 
-Ref.~\citep{LSC_2016grtests} for GW150914, and later extended to include
-overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
-of the late-time \sout{signal} \ab{waveform} with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and \sout{checking for} consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
-in that direction \comment{AB: which direction? There are papers by Nikhef group and 
-also Brito et al., and many others that have investigated BH spectroscopy.} include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
-nature of the remnant object has also been explored through tests of
-BH thermodynamics, like the Hawking's area
-theorem~\citep{Cabero:2017avf} or through search for echos in the
-post-merger
-signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
-of these tests have found evidence for non-BH nature of the remnant
-object (as described in GR) in LIGO-Virgo BBH observations.
-
-\comment{AB: I don't understand the next sentence, it looks to me out of context.} 
-Most of the tests mentioned above focus on analysing the post-merger
-or late-time ringdown signal in isolation. \sout{Second generation
-ground-based interferometric detectors like} \ab{Ground-based detectors, 
-such as \sout{Advanced} LIGO and Virgo,} are most sensitive to 
-stellar-mass BH binaries that merge near the
-minim\ab{um}\sout{a} of their sensitivity band ($\sim 100$Hz). As a consequence, the
-remnant object \textit{rings down} \comment{AB: we are not discussing the interferometer noises, 
-so why to give such a detail about the shot noise?} \sout{in shot-noise dominated higher
-frequencies, leaving} \ab{at frequencies where the sensitivity is worse, leaving} 
-very little signal-to-noise ratio (SNR) in the
-post-merger signal. \comment{AB: This discussion about the starting time of the ringdown starts too abruptly, 
-and looks out of context and incomplete. Also, why are we citing only those papers? The matter 
-has a long history. There have been calibrations to NR of damped- oscillation signals.} 
-The ringdown start time is not a clearly defined
-quantity and has been explored in detail
-in Ref.~\citep{Bhagwat:2017tkm}. In other
-works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a
-free parameter to be estimated directly from the data. Uncertainties
-in estimates of the ringdown start-time, as well as, an overall lack of
-SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, result in significant statistical uncertainties
-in the measurement of the QNM frequencies.
-
-An independent approach to BH spectroscopy, based on the full-signal
-analysis, was \sout{outlined} \ab{introduced} in Ref.~\citep{Brito:2018rfr} 
-(henceforth referred to as \paperone). Unlike methods that focus \ab{only} 
-on the post-merger signal, it \sout{describes a framework in which a} 
-\ab{employs the} complete inspiral-merger-ringdown
-(IMR) waveform \sout{model is used} to measure the complex QNM
-frequencies. This \sout{allows} \ab{gives} access to the full SNR of the signal,
-reducing measurement uncertainties. Moreover, the definition of the
-ringdown start time is built into the \ab{merger-ringdown} model and does not need to be
-either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method \ab{and tested it for }\sout{in the context of a
-non-spinning waveform model} \ab{non-spinning BBHs}, \ab{here} we extend the analysis to the \ab{more 
-realistic astrophysical} case in which BHs \ab{carry} spin\sout{s in the current paper}. \ab{Furthermore, 
-the IMR waveform model used in this paper is more accurate than what employed in \paperone, 
-because it contains higher-order corrections in PN theory and it was calibrated to a much larger set 
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
-and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the 
-source properties \cite{paper_showing_systematics_from_ignoring_spin}.
-
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR\ab{, notably how we can measure 
-complex QNM frequencies with our parameterized model within a Bayesian formalism}. Then, in Sec.~\ref{sec:results}, 
-we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze 
-the ... and constrain the QNM frequecies ... Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.}
-
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component 
-objects in the binary; and the 
-\emph{extrinsic} parameters: a reference time $t_c$ and phase 
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$, 
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-
-Here, we focus on BHs with spins aligned or anti-aligned 
-with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
-the GW signal depends on $11$ parameters. We denote the 
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
-formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms, 
-here we use as our baseline model the aligned-spin multipolar waveform model 
-developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this 
-waveform model is called {\tt SEOBNRv4HM}.}.
-
-In the observer's frame, the GW polarizations can be written as 
-%
-\begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
-\end{equation}
-%
-where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
-\begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
-\end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
-\begin{equation}
-\label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
-\end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{equation}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
-\end{equation}
-%
-\begin{equation}
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{equation}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{align} 
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber   
-\end{align}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}    
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
-
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized 
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) is defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This 
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
-
-As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula 
-described above. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}), 
-(\ref{c2}), and (\ref{d1}).
-
-\subsection{Bayesian parameter-estimation technique}
-\label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
-fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH 
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs 
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-\iffalse
-\subsection{Priors}
-
-Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$.
-Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary.
-The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out.
-For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
-2015 LALInference paper).
-For our non-GR ringdown parameters, we assume uniform priors.
-This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}.
-For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
-\fi
-
-\ab{\section{Synthetic-signal injection study}}
-\label{sec:results}
-
-\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
-
-\ab{We demonstrate our method using synthetic-signal injections describing GWs 
-from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and 
-Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.} 
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and 
-GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}. 
-These two binary systems are representative of the kind of systems for which 
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the  
-pre- and post-merger SNRs return reliable parameter-estimation results.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
- \hline
-\end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
-$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
-The third row is completely ignored in the caption's explanations.}}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
-	\label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{To avoid possible systematic biases in our parameter-estimation analysis 
-due to error in waveform modeling,} we use the GR version of the same waveform,
-$\SEOB$ (without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context. 
-Why should the reader appreciate at this stage of the paper, where we have not yet 
-discussed results with real data, what is in the Appendix?} As in the case of the actual
-detections, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs. The distance to the two
-\ab{synthetic} events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14 
-for GW190521). Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
-$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
-(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
-to 1D and 2D posteriors when discussing the figures.}}
-
-\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
-we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
-the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose \sout{systems with initial-}binary-parameters
-similar to GW150914 and GW190521 (as given in Table XXX), but 
-\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
-  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
-based on QNM predictions in theories of gravity alternative to GR.}. 
-In other words, we assume that the frequency and damping time
-of our non-GR signal is 1.5 times the corresponding GR prediction,
-although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
-we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
-you just clearly refer to thePlease introduce the injected signal and the template, which is used 
-to recover it, and simply say that they belong to the same waweform model.} 
-We also avoid waveform \sout{and noise} systematic biases by choosing 
-a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
-summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
-show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
-$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
-values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
-explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
-is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
-
-We additionally investigate the effects of erroneously assuming that
-\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
-\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
-signals using the GR waveform model $\SEOB$ instead of the parameterized 
-$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
-In such cases, we run the risk of biased parameter estimates due to an
-incomplete understanding of the underlying signal. The resulting
-posterior probability distributions are shown in the right panels of
-Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
-(GW190521-like) curves.} The results are interesting and distinctly
-different for the two events. For the GW150914-like \comment{AB: I would avoid using 
-``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
-(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
-deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
-the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working 
-in Gaussian noise, so why are you referring to the noise as the culprit or the 
-source of difference?} The fact that the GW190521-like signal has a much
-lower SNR than GW150914-like signal might be a possible reason for the 
-measurement of the final quantities to be more susceptible to noise. A
-more detailed comparison of the other parameters, like the masses and
-spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
-signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
-comment the figures. What are the main results? What do we deduce?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
-	\label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
-switch the red and blue colors.
-The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
-Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
-\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
-(obtained by inverting the Berti fits).
-\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
-Also please specify if the remnant mass is the detector-frame mass.
-Please
-switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
-\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
-We choose an asymmetric system to increase the SNR in the higher modes. 
-We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
-such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
-the three detectors, LIGO Hanford, Livingston and
-Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
-asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible at design sensitivities. Using this
-signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
-$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
-our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
-
-The fractional deviations in the estimates of the damping time and
-frequency of either mode is expected to be consistent with 0, as we
-indeed find in the left panel of
-Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
-quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
-\taungr{330})$ are also consistent with the corresponding predictions
-for a BBH merger in GR. As a consequence, the information from these
-two independent measures correspond to a unique remnant object, which
-is completely described by its mass and spin angular momentum
-\abhi{have the mf-af plot as well as a third panel to show
-  consistency}. For most of the events observed so far, the power in
-the $(3,\pm 3)$ has not been sufficient to measure it along with the
-$(2,\pm 2)$, or in fact, in its place. However, it might also be
-possible to combine information from multiple observation\sout{, as is
-likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
-detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
-	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
-The plus signs mark the GR predictions.}
-	\label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
-
-\comment{AB: This is the most important section in the paper, because it contains the 
-main results of the paper, i.e., the constraints on QNMs using real data. It needs to 
-be expanded and results would need to be highlighted much better than in the current version. 
-I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors 
-that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have 
-a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the 
-TGR GWTC-2, but for the 22 QNM frequencies for the different GW events. 
-Figures can be used in talks, and can capture the information much better 
-than a list of numbers in a Table.}
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results \sout{of this test} for all events observed
-during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
-total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
-signal} before and after the signal reaches \ab{the} peak\ab{'s} 
-amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the} 
-likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
-\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the 
-entire paper, except perhaps the Conclusions section.} 
-For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
-threshold and restrict\sout{ed} ourselves to the highest-mass events which
-\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
-since our method relies on doing a parameter estimation on the entire
-inspiral-merger-ringdown signal, we require the SNR to be beyond a
-certain threshold throughout the signal for reliable parameter
-estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters, 
-there are the component masses of the holes in the binary, and the 
-mass of the remnant formed after merger.} In fact the SNR
-threshold alone should be sufficient for the analysis, and for this
-paper we have relaxed the mass threshold. This has added two events,
-GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
-  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
-events along with GW190519$\_$153544, GW190521$\_$074359,
-GW190910$\_$112807. \comment{AB: Please improve the above paragraph 
-and make it clearer which choice is made for the SNR threshold and 
-masses, and why.}
-
-\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to 
-measure the QNMs to} \sout{present results on} the relevant
-GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same thresholds as above, we find three
-additional events that could be included in the analysis: GW150914,
-GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
-merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
-reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
-which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
-  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $pSEOB$ test, as well.} Among all the GW signals detected so far,
-GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what 
-is the ``clarity'' of a signal?} leading to the
-first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
-	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
-	\label{fig:o1o2_events}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, if we assume that the fractional deviations $(\df{220},
-\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. 
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis 
-if we want to include that analysis. AB: we want to include that analysis.}
-
-\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the 
-hierarchically combined methods.}
-
-\begin{table}
-\begin{flushleft}
-\begin{tabular}{llllllll}
-\toprule
-Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
-& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\hline
-& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
-\hline
-
-GW150914 &
-$249^{+9}_{-7}$ &
-$-$ &
-\hphantom{X} &
-$4.1^{+0.3}_{-0.2}$ &
-$-$
-\\[0.075cm]
-
-GW170104 &
-$286^{+16}_{-27}$ &
-$-$ &
-\hphantom{X} &
-$3.5^{+0.4}_{-0.3}$ &
-$-$
-\\[0.075cm]
-
-GW170729 &
-$161^{+13}_{-14}$ &
-$-$ &
-\hphantom{X} &
-$7.8^{+1.8}_{-1.5}$ &
-$-$
-\\[0.075cm]
-
-GW190630$\_$185205 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-
-GW190828$\_$063405 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-\hline
-\bottomrule
-\end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table 
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
-\label{tab:qnm_o1o2_results}
-\end{flushleft}
-\end{table}
-
-\section{Discussion}\label{sec:discussion}
-
-\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers 
-about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also 
-EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al. 
-It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with 
-Richard and Vivien.}
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-LIGO Clusters. \comment{AB: Our cluster!!!}
-R.B.
-acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862.
-This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
-
-\appendix
-
-\section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
-
-\comment{AB: Please improve considerably this Appendix because it is not easy to follow the motivation and the logic. It is written for LIGO people. 
-I have tried to make changes but it is better if you do it. I risk to erase parts that you would consider important. Please write it thinking that your 
-reader is not an LSC reader!}
-
-In Sec.~\ref{sec:method}, we \ab{discussed} \sout{mentioned that} the expression of the
-Bayesian likelihood function \ab{that we use in our analysis} \sout{outlined in} \ab{(see 
-Eq.~\ref{eq:likelihood})} \ab{and stressed that it}\sout{and \ref{eq:nwip}} is only valid if the interferometric noise can be
-described as a stationary Gaussian process. LIGO-Virgo noise, however,
-frequently has non-stationary and/or non-Gaussian features, for
-example glitches, which can affect parameter inferences unless
-appropriately accounted for. Here we demonstrate\ab{, by injecting in real 
-noise a GW190521-like signal} \sout{with an example of a
-GW190521-like simulated signal}, \ab{how} systematic biases \ab{can originate} \sout{likely originating}
-from an incomplete understanding of the noise. \comment{AB: It is confusing to refer to ``systematic'' 
-biases for the noise, generally we refer to systematic biases for the waveform modeling. 
-In fact, below you also, somewhat suddenly, refer to (lack of) precession, as a possible source of systemtcis. 
-I would advice you to clarify from the beginning of this Appendix, what this study is about and what you intend to 
-do below.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ from simulations \comment{AB: I have changed this in other places.
-The word ``simulations'' is confusing, because we deal with a paper in which we also refer to NR simulations.
-I suggest to use ``injected synthetic signals'' instead} of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
-The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-For comparison, we also plot the 90 \% credible level for the actual event, GW190521.
-\comment{AB: For clarity, please indicate on the plot which waveform model is used to obtain such posteriors, as you did
-in the other plots of the paper. Also, please use something else instead of ``actual event'', which is confusing. The problem is 
-that the first two entries of the legend refer to the noise properties of the PE study done with an injected synthetic signal, whereas I believe ``actual event'' refers to ``real'' not injected signal
-and ``real noise''. All the entries in the legend need to be consistent with each other; you need to specify for each of them the ``signal'' and the ``noise''. I hope is clear what I am saying}}
-	\label{fig:21g_systematics}
-\end{center}	
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{The spinning, precessing NR-surrogate model \texttt{NRSur7dq4}, valid up to mass ratio 4, was employed 
-(together with the $\SEOB$ model) to analyze the GW190521 signal observed by the LIGO and Virgo detectors. 
-For the injected synthetic signal we use a \texttt{NRSur7dq4} waveform with parameters similar to the ones 
-recovered by this model on the actual GW190521 data (see Table I of Ref.~\cite{Abbott:2020tfl}).}  
-\ab{In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal 
-predicts for the $(2,2)$ frequency and damping time, and for comparison, we also 
-show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$. As seen in the plot, while 
-the measurement of the frequency is consistent with the prediction, we overestimate the damping time.} \comment{AB: it is not clear 
-to me what the figure shows. Is the black line the result when running $\pSEOB$ against real data or the 
-injection in realt data?}
-
-\comment{AB: What is the ``underlying'' NR signal? I think you are referring to the 
-injected signal. Also, until now you have not discussed precession. 
-} The underlying NR signal is expected to be precessing, and since the
-$\pSEOB$ model is built on an aligned-spin GR model, a lack of
-precession could bias measurements. We explore effects of possible
-waveform systematics by injecting the signal is coloured Gaussian
-noise. In this case, since the understanding of the noise realizations
-is complete, any measurement biases could only arise from incomplete
-understanding of the \sout{underlying} \ab{injected} signal. We find (grey curves in
-Fig.\ref{fig:21g_systematics}) our results to be consistent with the
-prediction thus ruling out a lack of precession to be a likely cause
-for the bias in the damping time measurement of the actual signal.
-
-We subsequently study the effects of possible noise systematics by
-injecting the same \texttt{NRSur7dq4} GW signal in different
-realizations of actual interferometric noise around the real event
-GW190521. Since the PSDs of the GW detectors are expected to vary over
-longer durations of time, we select 5 different noise realizations
-over a segment of 2.5 hours of coincident data in both the LIGO
-detectors centered at the time of the actual event. The noise
-properties in this chunk of data, and consequently for all 5 simulated
-signals, is expected to be the closest to that for the actual
-event. The results are indicated by \sout{pink} \ab{green} curves in
-Fig.~\ref{fig:21g_systematics}. \ab{As it can be seen from the figure,} 
-for 3 of the 5 noise realizations,
-corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we
-recover a damping time similar to the actual event, where $t_0$ is the
-GPS time of the actual event. For the other two noise realizations, we
-estimate the consistent damping time but an off-set frequency, while
-the fifth noise realization is consistent with both predictions. The
-SNR in the Livingston detector goes down by more than \ab{a factor} 3 in some
-runs, indicative of how a variation in the noise strongly affects our
-ability to infer parameters. This also seems to indicate that a bias
-in the measurements of the damping time for the actual event \comment{AB: not clear 
-what you mean} can be unaccounted noise systematics.
-
-%
-\bibliographystyle{apsrev}
-\bibliography{intro_paper}
-
-\end{document}

### 2021-01-25 papers/intro_paper/acknowledgements.tex
divided up paper into input segments

--- 2021-01-25 papers/intro_paper/intro_paper.tex
@@
-%\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers,nofootinbib]{revtex4-1}
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
-\usepackage{epsfig}
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{bm}
-\usepackage{times}
-\usepackage{xspace}
-\usepackage[varg]{txfonts}
-\usepackage[normalem]{ulem} % To get strikethrough (\sout)
-\usepackage[colorlinks]{hyperref}
-\usepackage[caption=false]{subfig}
-\usepackage{booktabs}
-\usepackage{url}
-\usepackage{float}
-\usepackage[bottom]{footmisc}
-\usepackage{lineno}
-%\linenumbers
-
-\definecolor{LinkColor}{rgb}{0.75, 0, 0}
-\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
-\definecolor{UrlColor}{rgb}{0, 0, 0.75}
-\hypersetup{linkcolor=LinkColor}
-\hypersetup{citecolor=CiteColor}
-\hypersetup{urlcolor=UrlColor}
-\usepackage{perpage}
-\MakePerPage{footnote}
-
-\newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
-\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
-\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
-\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
-
-\newcommand{\h}{\mathpzc{h}}
-\newcommand{\Hhat}{\hat{\mathpzc{H}}}
-\newcommand{\B}{\mathpzc{B}}
-\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
-\newcommand{\xilm}{\xi_{\ell m}}
-\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
-\newcommand{\Y}{{Y}^{-2}}
-\newcommand{\hc}{h_\times}
-\newcommand{\hp}{h_+}
-\newcommand{\Fc}{F_\times}
-\newcommand{\Fp}{F_+}
-\newcommand{\Mf}{M_f}
-\newcommand{\cA}{\mathpzc{A}}
-\newcommand{\lm}{_{\ell m}}
-\newcommand{\deff}{d_\mathrm{eff}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\blambda}{\bm{\lambda}}
-\newcommand{\btheta}{\bm{\theta}}
-\newcommand{\bxi}{\bm{\xi}}
-\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
-\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
-\newcommand{\bzeta}{\bm{\zeta}}
-\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
-\newcommand{\Mo}{M_{\odot}}
-\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
-\newcommand{\FF}{\mathrm{FF}}
-\newcommand{\e}{\mathrm{e}}
-\newcommand{\rhoopt}{\rho_\mathrm{opt}}
-\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
-\newcommand{\fqnm}{f}
-\newcommand{\sigmaqnm}{\sigma}
-\newcommand{\n}{\mathbf{n}}
-\newcommand*{\skymapscale}{0.5}
-\newcommand*{\paramestscale}{0.455}
-\newcommand{\df}[1]{\delta f_{\text{#1}}}
-\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f_{\text{#1}}}
-\newcommand{\taungr}[1]{\tau_{\text{#1}}}
-\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
-\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
-\newcommand{\pSEOB}{\texttt{pSEOBNR}}
-\newcommand{\SEOB}{\texttt{SEOBNR}}
-
-\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
-\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
-
-\begin{document}
-
-%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
-
-\title{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}
-
-\author{Abhirup Ghosh}
-\AEI
-\author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
-\author{Alessandra Buonanno}
-\AEI
-\UMD
-
-\date{\today}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  The no-hair conjecture in General Relativity states that the
-  properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin angular momentum. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
-  ringdown can be uniquely determined by the mass and spin of the
-  remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to 
-  test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using inspiral-merger-ringdown waveforms, thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the proposed ringdown. We
-  further demonstrate the robustness of the test against modified
-  gravitational-wave (GW) signals with a ringdown different from what
-  GR predicts for Kerr BHs. Our method was used to analyse the
-  properties of the merger remnants for the events observed by
-  LIGO-Virgo in the first half of their third observing run (O3a) in
-  the latest LIGO-Virgo publication. In this paper, for the first
-  time, we analyse the GW events from the first (O1) and second (O2) LIGO-Virgo
-  observing runs and provide joint constraints with published results
-  from O3a. We also analyse two events from the O3a catalogue 
-  that were not considered in the initial LIGO-Virgo analysis. The
-  joint measurements of the fractional deviations in the frequency and damping time,
-  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
-  constraints yet using this method.
-%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
-
-\section{Introduction}\label{sec:intro}
-
-\comment{AB: Please make the citations in the bibliography uniform (I would stick with citations 
-taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please 
-stick with American English. Also, please be uniform when writing captions, when using colors and style 
-of curves in plots, when building Tables. There is not a lot of discussion in the text on the main results of the paper (Sec. IV). 
-The abstract would need to be tighten and made more crispy once the quantitative results for the 
-bounds are included.}
-
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
-Collaboration~\citep{Virgo} have recently announced their catalogue of
-gravitational-wave (GW) signals from the first
-half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
-with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\citep{aasi2015characterization},
-and the Advanced Virgo detector in Cascina,
-Italy~\citep{acernese2014advanced} have now detected $50$ GW
-events from the merger of compact objects like neutron stars and/or
-black holes (BHs). Alongside independent claims of
-detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, notably GW150914~\citep{abbott2016observation}.
-
-The observation of GWs has had significant astrophysical and cosmological
-implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
-has also allowed us to probe fundamental
-physics and test predictions of Einstein's theory of General Relativity 
-(GR) in the previously unexplored highly-dynamical, and strong field 
-regime~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}, where the two
-compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon~\citep{NRpaper}, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\citep{vishu,earlyqnmpapers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
-
-The LIGO-Virgo collaborations have released companion papers \cite{} detailing their results 
-of tests of GR for GW150914 \cite{} and for several GW events of 
-the two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
-The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral~\citep{earlydevelopmentpapers}, and
-phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\citep{TIGERmethodspapers}; tests of GW
-propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
-polarization of gravitational radiation using a
-multi--GW-detector network~\citep{gw170814,isi2017probing}. The GWTC-1/2 papers also 
-check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
-consistency of the residuals with interferometric
-noise~\citep{Ghonge:2020suv,gwtc1_tgr}. None of these tests report any
-departure from the predictions of GR.
-
-The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
-first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH 
-coalescence. The LIGO-Virgo O3a testing GR paper~\cite{} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely
-described by two observables: mass and spin angular momentum. One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin angular momentum. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.
-
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in 
-Ref.~\citep{LSC_2016grtests} for GW150914, and later extended to include
-overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
-of the late-time \sout{signal} \ab{waveform} with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and \sout{checking for} consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
-in that direction \comment{AB: which direction? There are papers by Nikhef group and 
-also Brito et al., and many others that have investigated BH spectroscopy.} include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
-nature of the remnant object has also been explored through tests of
-BH thermodynamics, like the Hawking's area
-theorem~\citep{Cabero:2017avf} or through search for echos in the
-post-merger
-signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
-of these tests have found evidence for non-BH nature of the remnant
-object (as described in GR) in LIGO-Virgo BBH observations.
-
-\comment{AB: I don't understand the next sentence, it looks to me out of context.} 
-Most of the tests mentioned above focus on analysing the post-merger
-or late-time ringdown signal in isolation. \sout{Second generation
-ground-based interferometric detectors like} \ab{Ground-based detectors, 
-such as \sout{Advanced} LIGO and Virgo,} are most sensitive to 
-stellar-mass BH binaries that merge near the
-minim\ab{um}\sout{a} of their sensitivity band ($\sim 100$Hz). As a consequence, the
-remnant object \textit{rings down} \comment{AB: we are not discussing the interferometer noises, 
-so why to give such a detail about the shot noise?} \sout{in shot-noise dominated higher
-frequencies, leaving} \ab{at frequencies where the sensitivity is worse, leaving} 
-very little signal-to-noise ratio (SNR) in the
-post-merger signal. \comment{AB: This discussion about the starting time of the ringdown starts too abruptly, 
-and looks out of context and incomplete. Also, why are we citing only those papers? The matter 
-has a long history. There have been calibrations to NR of damped- oscillation signals.} 
-The ringdown start time is not a clearly defined
-quantity and has been explored in detail
-in Ref.~\citep{Bhagwat:2017tkm}. In other
-works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a
-free parameter to be estimated directly from the data. Uncertainties
-in estimates of the ringdown start-time, as well as, an overall lack of
-SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, result in significant statistical uncertainties
-in the measurement of the QNM frequencies.
-
-An independent approach to BH spectroscopy, based on the full-signal
-analysis, was \sout{outlined} \ab{introduced} in Ref.~\citep{Brito:2018rfr} 
-(henceforth referred to as \paperone). Unlike methods that focus \ab{only} 
-on the post-merger signal, it \sout{describes a framework in which a} 
-\ab{employs the} complete inspiral-merger-ringdown
-(IMR) waveform \sout{model is used} to measure the complex QNM
-frequencies. This \sout{allows} \ab{gives} access to the full SNR of the signal,
-reducing measurement uncertainties. Moreover, the definition of the
-ringdown start time is built into the \ab{merger-ringdown} model and does not need to be
-either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method \ab{and tested it for }\sout{in the context of a
-non-spinning waveform model} \ab{non-spinning BBHs}, \ab{here} we extend the analysis to the \ab{more 
-realistic astrophysical} case in which BHs \ab{carry} spin\sout{s in the current paper}. \ab{Furthermore, 
-the IMR waveform model used in this paper is more accurate than what employed in \paperone, 
-because it contains higher-order corrections in PN theory and it was calibrated to a much larger set 
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
-and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the 
-source properties \cite{paper_showing_systematics_from_ignoring_spin}.
-
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR\ab{, notably how we can measure 
-complex QNM frequencies with our parameterized model within a Bayesian formalism}. Then, in Sec.~\ref{sec:results}, 
-we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze 
-the ... and constrain the QNM frequecies ... Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.}
-
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component 
-objects in the binary; and the 
-\emph{extrinsic} parameters: a reference time $t_c$ and phase 
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$, 
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-
-Here, we focus on BHs with spins aligned or anti-aligned 
-with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
-the GW signal depends on $11$ parameters. We denote the 
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
-formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms, 
-here we use as our baseline model the aligned-spin multipolar waveform model 
-developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this 
-waveform model is called {\tt SEOBNRv4HM}.}.
-
-In the observer's frame, the GW polarizations can be written as 
-%
-\begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
-\end{equation}
-%
-where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
-\begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
-\end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
-\begin{equation}
-\label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
-\end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{equation}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
-\end{equation}
-%
-\begin{equation}
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{equation}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{align} 
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber   
-\end{align}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}    
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
-
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized 
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) is defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This 
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
-
-As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula 
-described above. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}), 
-(\ref{c2}), and (\ref{d1}).
-
-\subsection{Bayesian parameter-estimation technique}
-\label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
-fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH 
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs 
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-\iffalse
-\subsection{Priors}
-
-Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$.
-Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary.
-The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out.
-For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
-2015 LALInference paper).
-For our non-GR ringdown parameters, we assume uniform priors.
-This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}.
-For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
-\fi
-
-\ab{\section{Synthetic-signal injection study}}
-\label{sec:results}
-
-\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
-
-\ab{We demonstrate our method using synthetic-signal injections describing GWs 
-from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and 
-Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.} 
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and 
-GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}. 
-These two binary systems are representative of the kind of systems for which 
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the  
-pre- and post-merger SNRs return reliable parameter-estimation results.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
- \hline
-\end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
-$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
-The third row is completely ignored in the caption's explanations.}}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
-	\label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{To avoid possible systematic biases in our parameter-estimation analysis 
-due to error in waveform modeling,} we use the GR version of the same waveform,
-$\SEOB$ (without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context. 
-Why should the reader appreciate at this stage of the paper, where we have not yet 
-discussed results with real data, what is in the Appendix?} As in the case of the actual
-detections, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs. The distance to the two
-\ab{synthetic} events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14 
-for GW190521). Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
-$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
-(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
-to 1D and 2D posteriors when discussing the figures.}}
-
-\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
-we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
-the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose \sout{systems with initial-}binary-parameters
-similar to GW150914 and GW190521 (as given in Table XXX), but 
-\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
-  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
-based on QNM predictions in theories of gravity alternative to GR.}. 
-In other words, we assume that the frequency and damping time
-of our non-GR signal is 1.5 times the corresponding GR prediction,
-although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
-we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
-you just clearly refer to thePlease introduce the injected signal and the template, which is used 
-to recover it, and simply say that they belong to the same waweform model.} 
-We also avoid waveform \sout{and noise} systematic biases by choosing 
-a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
-summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
-show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
-$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
-values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
-explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
-is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
-
-We additionally investigate the effects of erroneously assuming that
-\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
-\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
-signals using the GR waveform model $\SEOB$ instead of the parameterized 
-$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
-In such cases, we run the risk of biased parameter estimates due to an
-incomplete understanding of the underlying signal. The resulting
-posterior probability distributions are shown in the right panels of
-Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
-(GW190521-like) curves.} The results are interesting and distinctly
-different for the two events. For the GW150914-like \comment{AB: I would avoid using 
-``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
-(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
-deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
-the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working 
-in Gaussian noise, so why are you referring to the noise as the culprit or the 
-source of difference?} The fact that the GW190521-like signal has a much
-lower SNR than GW150914-like signal might be a possible reason for the 
-measurement of the final quantities to be more susceptible to noise. A
-more detailed comparison of the other parameters, like the masses and
-spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
-signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
-comment the figures. What are the main results? What do we deduce?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
-	\label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
-switch the red and blue colors.
-The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
-Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
-\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
-(obtained by inverting the Berti fits).
-\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
-Also please specify if the remnant mass is the detector-frame mass.
-Please
-switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
-\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
-We choose an asymmetric system to increase the SNR in the higher modes. 
-We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
-such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
-the three detectors, LIGO Hanford, Livingston and
-Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
-asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible at design sensitivities. Using this
-signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
-$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
-our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
-
-The fractional deviations in the estimates of the damping time and
-frequency of either mode is expected to be consistent with 0, as we
-indeed find in the left panel of
-Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
-quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
-\taungr{330})$ are also consistent with the corresponding predictions
-for a BBH merger in GR. As a consequence, the information from these
-two independent measures correspond to a unique remnant object, which
-is completely described by its mass and spin angular momentum
-\abhi{have the mf-af plot as well as a third panel to show
-  consistency}. For most of the events observed so far, the power in
-the $(3,\pm 3)$ has not been sufficient to measure it along with the
-$(2,\pm 2)$, or in fact, in its place. However, it might also be
-possible to combine information from multiple observation\sout{, as is
-likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
-detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
-	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
-The plus signs mark the GR predictions.}
-	\label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
-
-\comment{AB: This is the most important section in the paper, because it contains the 
-main results of the paper, i.e., the constraints on QNMs using real data. It needs to 
-be expanded and results would need to be highlighted much better than in the current version. 
-I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors 
-that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have 
-a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the 
-TGR GWTC-2, but for the 22 QNM frequencies for the different GW events. 
-Figures can be used in talks, and can capture the information much better 
-than a list of numbers in a Table.}
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results \sout{of this test} for all events observed
-during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
-total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
-signal} before and after the signal reaches \ab{the} peak\ab{'s} 
-amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the} 
-likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
-\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the 
-entire paper, except perhaps the Conclusions section.} 
-For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
-threshold and restrict\sout{ed} ourselves to the highest-mass events which
-\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
-since our method relies on doing a parameter estimation on the entire
-inspiral-merger-ringdown signal, we require the SNR to be beyond a
-certain threshold throughout the signal for reliable parameter
-estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters, 
-there are the component masses of the holes in the binary, and the 
-mass of the remnant formed after merger.} In fact the SNR
-threshold alone should be sufficient for the analysis, and for this
-paper we have relaxed the mass threshold. This has added two events,
-GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
-  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
-events along with GW190519$\_$153544, GW190521$\_$074359,
-GW190910$\_$112807. \comment{AB: Please improve the above paragraph 
-and make it clearer which choice is made for the SNR threshold and 
-masses, and why.}
-
-\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to 
-measure the QNMs to} \sout{present results on} the relevant
-GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same thresholds as above, we find three
-additional events that could be included in the analysis: GW150914,
-GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
-merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
-reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
-which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
-  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $pSEOB$ test, as well.} Among all the GW signals detected so far,
-GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what 
-is the ``clarity'' of a signal?} leading to the
-first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
-	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
-	\label{fig:o1o2_events}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, if we assume that the fractional deviations $(\df{220},
-\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. 
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis 
-if we want to include that analysis. AB: we want to include that analysis.}
-
-\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the 
-hierarchically combined methods.}
-
-\begin{table}
-\begin{flushleft}
-\begin{tabular}{llllllll}
-\toprule
-Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
-& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\hline
-& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
-\hline
-
-GW150914 &
-$249^{+9}_{-7}$ &
-$-$ &
-\hphantom{X} &
-$4.1^{+0.3}_{-0.2}$ &
-$-$
-\\[0.075cm]
-
-GW170104 &
-$286^{+16}_{-27}$ &
-$-$ &
-\hphantom{X} &
-$3.5^{+0.4}_{-0.3}$ &
-$-$
-\\[0.075cm]
-
-GW170729 &
-$161^{+13}_{-14}$ &
-$-$ &
-\hphantom{X} &
-$7.8^{+1.8}_{-1.5}$ &
-$-$
-\\[0.075cm]
-
-GW190630$\_$185205 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-
-GW190828$\_$063405 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-\hline
-\bottomrule
-\end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table 
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
-\label{tab:qnm_o1o2_results}
-\end{flushleft}
-\end{table}
-
-\section{Discussion}\label{sec:discussion}
-
-\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers 
-about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also 
-EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al. 
-It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with 
-Richard and Vivien.}
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
 LIGO Clusters. \comment{AB: Our cluster!!!}
@@
 This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
-
-\appendix
-
-\section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
-
-\comment{AB: Please improve considerably this Appendix because it is not easy to follow the motivation and the logic. It is written for LIGO people. 
-I have tried to make changes but it is better if you do it. I risk to erase parts that you would consider important. Please write it thinking that your 
-reader is not an LSC reader!}
-
-In Sec.~\ref{sec:method}, we \ab{discussed} \sout{mentioned that} the expression of the
-Bayesian likelihood function \ab{that we use in our analysis} \sout{outlined in} \ab{(see 
-Eq.~\ref{eq:likelihood})} \ab{and stressed that it}\sout{and \ref{eq:nwip}} is only valid if the interferometric noise can be
-described as a stationary Gaussian process. LIGO-Virgo noise, however,
-frequently has non-stationary and/or non-Gaussian features, for
-example glitches, which can affect parameter inferences unless
-appropriately accounted for. Here we demonstrate\ab{, by injecting in real 
-noise a GW190521-like signal} \sout{with an example of a
-GW190521-like simulated signal}, \ab{how} systematic biases \ab{can originate} \sout{likely originating}
-from an incomplete understanding of the noise. \comment{AB: It is confusing to refer to ``systematic'' 
-biases for the noise, generally we refer to systematic biases for the waveform modeling. 
-In fact, below you also, somewhat suddenly, refer to (lack of) precession, as a possible source of systemtcis. 
-I would advice you to clarify from the beginning of this Appendix, what this study is about and what you intend to 
-do below.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ from simulations \comment{AB: I have changed this in other places.
-The word ``simulations'' is confusing, because we deal with a paper in which we also refer to NR simulations.
-I suggest to use ``injected synthetic signals'' instead} of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
-The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-For comparison, we also plot the 90 \% credible level for the actual event, GW190521.
-\comment{AB: For clarity, please indicate on the plot which waveform model is used to obtain such posteriors, as you did
-in the other plots of the paper. Also, please use something else instead of ``actual event'', which is confusing. The problem is 
-that the first two entries of the legend refer to the noise properties of the PE study done with an injected synthetic signal, whereas I believe ``actual event'' refers to ``real'' not injected signal
-and ``real noise''. All the entries in the legend need to be consistent with each other; you need to specify for each of them the ``signal'' and the ``noise''. I hope is clear what I am saying}}
-	\label{fig:21g_systematics}
-\end{center}	
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{The spinning, precessing NR-surrogate model \texttt{NRSur7dq4}, valid up to mass ratio 4, was employed 
-(together with the $\SEOB$ model) to analyze the GW190521 signal observed by the LIGO and Virgo detectors. 
-For the injected synthetic signal we use a \texttt{NRSur7dq4} waveform with parameters similar to the ones 
-recovered by this model on the actual GW190521 data (see Table I of Ref.~\cite{Abbott:2020tfl}).}  
-\ab{In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal 
-predicts for the $(2,2)$ frequency and damping time, and for comparison, we also 
-show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$. As seen in the plot, while 
-the measurement of the frequency is consistent with the prediction, we overestimate the damping time.} \comment{AB: it is not clear 
-to me what the figure shows. Is the black line the result when running $\pSEOB$ against real data or the 
-injection in realt data?}
-
-\comment{AB: What is the ``underlying'' NR signal? I think you are referring to the 
-injected signal. Also, until now you have not discussed precession. 
-} The underlying NR signal is expected to be precessing, and since the
-$\pSEOB$ model is built on an aligned-spin GR model, a lack of
-precession could bias measurements. We explore effects of possible
-waveform systematics by injecting the signal is coloured Gaussian
-noise. In this case, since the understanding of the noise realizations
-is complete, any measurement biases could only arise from incomplete
-understanding of the \sout{underlying} \ab{injected} signal. We find (grey curves in
-Fig.\ref{fig:21g_systematics}) our results to be consistent with the
-prediction thus ruling out a lack of precession to be a likely cause
-for the bias in the damping time measurement of the actual signal.
-
-We subsequently study the effects of possible noise systematics by
-injecting the same \texttt{NRSur7dq4} GW signal in different
-realizations of actual interferometric noise around the real event
-GW190521. Since the PSDs of the GW detectors are expected to vary over
-longer durations of time, we select 5 different noise realizations
-over a segment of 2.5 hours of coincident data in both the LIGO
-detectors centered at the time of the actual event. The noise
-properties in this chunk of data, and consequently for all 5 simulated
-signals, is expected to be the closest to that for the actual
-event. The results are indicated by \sout{pink} \ab{green} curves in
-Fig.~\ref{fig:21g_systematics}. \ab{As it can be seen from the figure,} 
-for 3 of the 5 noise realizations,
-corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we
-recover a damping time similar to the actual event, where $t_0$ is the
-GPS time of the actual event. For the other two noise realizations, we
-estimate the consistent damping time but an off-set frequency, while
-the fifth noise realization is consistent with both predictions. The
-SNR in the Livingston detector goes down by more than \ab{a factor} 3 in some
-runs, indicative of how a variation in the noise strongly affects our
-ability to infer parameters. This also seems to indicate that a bias
-in the measurements of the damping time for the actual event \comment{AB: not clear 
-what you mean} can be unaccounted noise systematics.
-
-%
-\bibliographystyle{apsrev}
-\bibliography{intro_paper}
-
-\end{document}

### 2021-01-25 papers/intro_paper/appendix.tex
divided up paper into input segments

--- 2021-01-25 papers/intro_paper/intro_paper.tex
@@
-%\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers,nofootinbib]{revtex4-1}
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
-\usepackage{epsfig}
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{bm}
-\usepackage{times}
-\usepackage{xspace}
-\usepackage[varg]{txfonts}
-\usepackage[normalem]{ulem} % To get strikethrough (\sout)
-\usepackage[colorlinks]{hyperref}
-\usepackage[caption=false]{subfig}
-\usepackage{booktabs}
-\usepackage{url}
-\usepackage{float}
-\usepackage[bottom]{footmisc}
-\usepackage{lineno}
-%\linenumbers
-
-\definecolor{LinkColor}{rgb}{0.75, 0, 0}
-\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
-\definecolor{UrlColor}{rgb}{0, 0, 0.75}
-\hypersetup{linkcolor=LinkColor}
-\hypersetup{citecolor=CiteColor}
-\hypersetup{urlcolor=UrlColor}
-\usepackage{perpage}
-\MakePerPage{footnote}
-
-\newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
-\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
-\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
-\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
-
-\newcommand{\h}{\mathpzc{h}}
-\newcommand{\Hhat}{\hat{\mathpzc{H}}}
-\newcommand{\B}{\mathpzc{B}}
-\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
-\newcommand{\xilm}{\xi_{\ell m}}
-\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
-\newcommand{\Y}{{Y}^{-2}}
-\newcommand{\hc}{h_\times}
-\newcommand{\hp}{h_+}
-\newcommand{\Fc}{F_\times}
-\newcommand{\Fp}{F_+}
-\newcommand{\Mf}{M_f}
-\newcommand{\cA}{\mathpzc{A}}
-\newcommand{\lm}{_{\ell m}}
-\newcommand{\deff}{d_\mathrm{eff}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\blambda}{\bm{\lambda}}
-\newcommand{\btheta}{\bm{\theta}}
-\newcommand{\bxi}{\bm{\xi}}
-\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
-\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
-\newcommand{\bzeta}{\bm{\zeta}}
-\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
-\newcommand{\Mo}{M_{\odot}}
-\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
-\newcommand{\FF}{\mathrm{FF}}
-\newcommand{\e}{\mathrm{e}}
-\newcommand{\rhoopt}{\rho_\mathrm{opt}}
-\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
-\newcommand{\fqnm}{f}
-\newcommand{\sigmaqnm}{\sigma}
-\newcommand{\n}{\mathbf{n}}
-\newcommand*{\skymapscale}{0.5}
-\newcommand*{\paramestscale}{0.455}
-\newcommand{\df}[1]{\delta f_{\text{#1}}}
-\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f_{\text{#1}}}
-\newcommand{\taungr}[1]{\tau_{\text{#1}}}
-\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
-\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
-\newcommand{\pSEOB}{\texttt{pSEOBNR}}
-\newcommand{\SEOB}{\texttt{SEOBNR}}
-
-\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
-\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
-
-\begin{document}
-
-%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
-
-\title{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}
-
-\author{Abhirup Ghosh}
-\AEI
-\author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
-\author{Alessandra Buonanno}
-\AEI
-\UMD
-
-\date{\today}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  The no-hair conjecture in General Relativity states that the
-  properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin angular momentum. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
-  ringdown can be uniquely determined by the mass and spin of the
-  remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to 
-  test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using inspiral-merger-ringdown waveforms, thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the proposed ringdown. We
-  further demonstrate the robustness of the test against modified
-  gravitational-wave (GW) signals with a ringdown different from what
-  GR predicts for Kerr BHs. Our method was used to analyse the
-  properties of the merger remnants for the events observed by
-  LIGO-Virgo in the first half of their third observing run (O3a) in
-  the latest LIGO-Virgo publication. In this paper, for the first
-  time, we analyse the GW events from the first (O1) and second (O2) LIGO-Virgo
-  observing runs and provide joint constraints with published results
-  from O3a. We also analyse two events from the O3a catalogue 
-  that were not considered in the initial LIGO-Virgo analysis. The
-  joint measurements of the fractional deviations in the frequency and damping time,
-  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
-  constraints yet using this method.
-%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
-
-\section{Introduction}\label{sec:intro}
-
-\comment{AB: Please make the citations in the bibliography uniform (I would stick with citations 
-taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please 
-stick with American English. Also, please be uniform when writing captions, when using colors and style 
-of curves in plots, when building Tables. There is not a lot of discussion in the text on the main results of the paper (Sec. IV). 
-The abstract would need to be tighten and made more crispy once the quantitative results for the 
-bounds are included.}
-
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
-Collaboration~\citep{Virgo} have recently announced their catalogue of
-gravitational-wave (GW) signals from the first
-half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
-with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\citep{aasi2015characterization},
-and the Advanced Virgo detector in Cascina,
-Italy~\citep{acernese2014advanced} have now detected $50$ GW
-events from the merger of compact objects like neutron stars and/or
-black holes (BHs). Alongside independent claims of
-detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, notably GW150914~\citep{abbott2016observation}.
-
-The observation of GWs has had significant astrophysical and cosmological
-implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
-has also allowed us to probe fundamental
-physics and test predictions of Einstein's theory of General Relativity 
-(GR) in the previously unexplored highly-dynamical, and strong field 
-regime~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}, where the two
-compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon~\citep{NRpaper}, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\citep{vishu,earlyqnmpapers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
-
-The LIGO-Virgo collaborations have released companion papers \cite{} detailing their results 
-of tests of GR for GW150914 \cite{} and for several GW events of 
-the two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
-The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral~\citep{earlydevelopmentpapers}, and
-phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\citep{TIGERmethodspapers}; tests of GW
-propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
-polarization of gravitational radiation using a
-multi--GW-detector network~\citep{gw170814,isi2017probing}. The GWTC-1/2 papers also 
-check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
-consistency of the residuals with interferometric
-noise~\citep{Ghonge:2020suv,gwtc1_tgr}. None of these tests report any
-departure from the predictions of GR.
-
-The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
-first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH 
-coalescence. The LIGO-Virgo O3a testing GR paper~\cite{} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely
-described by two observables: mass and spin angular momentum. One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin angular momentum. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.
-
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in 
-Ref.~\citep{LSC_2016grtests} for GW150914, and later extended to include
-overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
-of the late-time \sout{signal} \ab{waveform} with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and \sout{checking for} consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
-in that direction \comment{AB: which direction? There are papers by Nikhef group and 
-also Brito et al., and many others that have investigated BH spectroscopy.} include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
-nature of the remnant object has also been explored through tests of
-BH thermodynamics, like the Hawking's area
-theorem~\citep{Cabero:2017avf} or through search for echos in the
-post-merger
-signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
-of these tests have found evidence for non-BH nature of the remnant
-object (as described in GR) in LIGO-Virgo BBH observations.
-
-\comment{AB: I don't understand the next sentence, it looks to me out of context.} 
-Most of the tests mentioned above focus on analysing the post-merger
-or late-time ringdown signal in isolation. \sout{Second generation
-ground-based interferometric detectors like} \ab{Ground-based detectors, 
-such as \sout{Advanced} LIGO and Virgo,} are most sensitive to 
-stellar-mass BH binaries that merge near the
-minim\ab{um}\sout{a} of their sensitivity band ($\sim 100$Hz). As a consequence, the
-remnant object \textit{rings down} \comment{AB: we are not discussing the interferometer noises, 
-so why to give such a detail about the shot noise?} \sout{in shot-noise dominated higher
-frequencies, leaving} \ab{at frequencies where the sensitivity is worse, leaving} 
-very little signal-to-noise ratio (SNR) in the
-post-merger signal. \comment{AB: This discussion about the starting time of the ringdown starts too abruptly, 
-and looks out of context and incomplete. Also, why are we citing only those papers? The matter 
-has a long history. There have been calibrations to NR of damped- oscillation signals.} 
-The ringdown start time is not a clearly defined
-quantity and has been explored in detail
-in Ref.~\citep{Bhagwat:2017tkm}. In other
-works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a
-free parameter to be estimated directly from the data. Uncertainties
-in estimates of the ringdown start-time, as well as, an overall lack of
-SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, result in significant statistical uncertainties
-in the measurement of the QNM frequencies.
-
-An independent approach to BH spectroscopy, based on the full-signal
-analysis, was \sout{outlined} \ab{introduced} in Ref.~\citep{Brito:2018rfr} 
-(henceforth referred to as \paperone). Unlike methods that focus \ab{only} 
-on the post-merger signal, it \sout{describes a framework in which a} 
-\ab{employs the} complete inspiral-merger-ringdown
-(IMR) waveform \sout{model is used} to measure the complex QNM
-frequencies. This \sout{allows} \ab{gives} access to the full SNR of the signal,
-reducing measurement uncertainties. Moreover, the definition of the
-ringdown start time is built into the \ab{merger-ringdown} model and does not need to be
-either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method \ab{and tested it for }\sout{in the context of a
-non-spinning waveform model} \ab{non-spinning BBHs}, \ab{here} we extend the analysis to the \ab{more 
-realistic astrophysical} case in which BHs \ab{carry} spin\sout{s in the current paper}. \ab{Furthermore, 
-the IMR waveform model used in this paper is more accurate than what employed in \paperone, 
-because it contains higher-order corrections in PN theory and it was calibrated to a much larger set 
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
-and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the 
-source properties \cite{paper_showing_systematics_from_ignoring_spin}.
-
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR\ab{, notably how we can measure 
-complex QNM frequencies with our parameterized model within a Bayesian formalism}. Then, in Sec.~\ref{sec:results}, 
-we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze 
-the ... and constrain the QNM frequecies ... Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.}
-
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component 
-objects in the binary; and the 
-\emph{extrinsic} parameters: a reference time $t_c$ and phase 
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$, 
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-
-Here, we focus on BHs with spins aligned or anti-aligned 
-with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
-the GW signal depends on $11$ parameters. We denote the 
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
-formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms, 
-here we use as our baseline model the aligned-spin multipolar waveform model 
-developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this 
-waveform model is called {\tt SEOBNRv4HM}.}.
-
-In the observer's frame, the GW polarizations can be written as 
-%
-\begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
-\end{equation}
-%
-where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
-\begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
-\end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
-\begin{equation}
-\label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
-\end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{equation}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
-\end{equation}
-%
-\begin{equation}
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{equation}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{align} 
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber   
-\end{align}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}    
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
-
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized 
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) is defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This 
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
-
-As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula 
-described above. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}), 
-(\ref{c2}), and (\ref{d1}).
-
-\subsection{Bayesian parameter-estimation technique}
-\label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
-fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH 
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs 
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-\iffalse
-\subsection{Priors}
-
-Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$.
-Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary.
-The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out.
-For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
-2015 LALInference paper).
-For our non-GR ringdown parameters, we assume uniform priors.
-This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}.
-For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
-\fi
-
-\ab{\section{Synthetic-signal injection study}}
-\label{sec:results}
-
-\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
-
-\ab{We demonstrate our method using synthetic-signal injections describing GWs 
-from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and 
-Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.} 
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and 
-GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}. 
-These two binary systems are representative of the kind of systems for which 
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the  
-pre- and post-merger SNRs return reliable parameter-estimation results.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
- \hline
-\end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
-$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
-The third row is completely ignored in the caption's explanations.}}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
-	\label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{To avoid possible systematic biases in our parameter-estimation analysis 
-due to error in waveform modeling,} we use the GR version of the same waveform,
-$\SEOB$ (without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context. 
-Why should the reader appreciate at this stage of the paper, where we have not yet 
-discussed results with real data, what is in the Appendix?} As in the case of the actual
-detections, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs. The distance to the two
-\ab{synthetic} events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14 
-for GW190521). Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
-$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
-(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
-to 1D and 2D posteriors when discussing the figures.}}
-
-\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
-we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
-the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose \sout{systems with initial-}binary-parameters
-similar to GW150914 and GW190521 (as given in Table XXX), but 
-\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
-  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
-based on QNM predictions in theories of gravity alternative to GR.}. 
-In other words, we assume that the frequency and damping time
-of our non-GR signal is 1.5 times the corresponding GR prediction,
-although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
-we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
-you just clearly refer to thePlease introduce the injected signal and the template, which is used 
-to recover it, and simply say that they belong to the same waweform model.} 
-We also avoid waveform \sout{and noise} systematic biases by choosing 
-a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
-summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
-show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
-$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
-values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
-explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
-is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
-
-We additionally investigate the effects of erroneously assuming that
-\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
-\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
-signals using the GR waveform model $\SEOB$ instead of the parameterized 
-$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
-In such cases, we run the risk of biased parameter estimates due to an
-incomplete understanding of the underlying signal. The resulting
-posterior probability distributions are shown in the right panels of
-Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
-(GW190521-like) curves.} The results are interesting and distinctly
-different for the two events. For the GW150914-like \comment{AB: I would avoid using 
-``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
-(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
-deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
-the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working 
-in Gaussian noise, so why are you referring to the noise as the culprit or the 
-source of difference?} The fact that the GW190521-like signal has a much
-lower SNR than GW150914-like signal might be a possible reason for the 
-measurement of the final quantities to be more susceptible to noise. A
-more detailed comparison of the other parameters, like the masses and
-spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
-signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
-comment the figures. What are the main results? What do we deduce?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
-	\label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
-switch the red and blue colors.
-The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
-Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
-\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
-(obtained by inverting the Berti fits).
-\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
-Also please specify if the remnant mass is the detector-frame mass.
-Please
-switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
-\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
-We choose an asymmetric system to increase the SNR in the higher modes. 
-We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
-such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
-the three detectors, LIGO Hanford, Livingston and
-Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
-asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible at design sensitivities. Using this
-signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
-$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
-our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
-
-The fractional deviations in the estimates of the damping time and
-frequency of either mode is expected to be consistent with 0, as we
-indeed find in the left panel of
-Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
-quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
-\taungr{330})$ are also consistent with the corresponding predictions
-for a BBH merger in GR. As a consequence, the information from these
-two independent measures correspond to a unique remnant object, which
-is completely described by its mass and spin angular momentum
-\abhi{have the mf-af plot as well as a third panel to show
-  consistency}. For most of the events observed so far, the power in
-the $(3,\pm 3)$ has not been sufficient to measure it along with the
-$(2,\pm 2)$, or in fact, in its place. However, it might also be
-possible to combine information from multiple observation\sout{, as is
-likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
-detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
-	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
-The plus signs mark the GR predictions.}
-	\label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
-
-\comment{AB: This is the most important section in the paper, because it contains the 
-main results of the paper, i.e., the constraints on QNMs using real data. It needs to 
-be expanded and results would need to be highlighted much better than in the current version. 
-I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors 
-that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have 
-a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the 
-TGR GWTC-2, but for the 22 QNM frequencies for the different GW events. 
-Figures can be used in talks, and can capture the information much better 
-than a list of numbers in a Table.}
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results \sout{of this test} for all events observed
-during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
-total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
-signal} before and after the signal reaches \ab{the} peak\ab{'s} 
-amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the} 
-likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
-\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the 
-entire paper, except perhaps the Conclusions section.} 
-For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
-threshold and restrict\sout{ed} ourselves to the highest-mass events which
-\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
-since our method relies on doing a parameter estimation on the entire
-inspiral-merger-ringdown signal, we require the SNR to be beyond a
-certain threshold throughout the signal for reliable parameter
-estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters, 
-there are the component masses of the holes in the binary, and the 
-mass of the remnant formed after merger.} In fact the SNR
-threshold alone should be sufficient for the analysis, and for this
-paper we have relaxed the mass threshold. This has added two events,
-GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
-  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
-events along with GW190519$\_$153544, GW190521$\_$074359,
-GW190910$\_$112807. \comment{AB: Please improve the above paragraph 
-and make it clearer which choice is made for the SNR threshold and 
-masses, and why.}
-
-\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to 
-measure the QNMs to} \sout{present results on} the relevant
-GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same thresholds as above, we find three
-additional events that could be included in the analysis: GW150914,
-GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
-merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
-reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
-which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
-  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $pSEOB$ test, as well.} Among all the GW signals detected so far,
-GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what 
-is the ``clarity'' of a signal?} leading to the
-first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
-	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
-	\label{fig:o1o2_events}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, if we assume that the fractional deviations $(\df{220},
-\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. 
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis 
-if we want to include that analysis. AB: we want to include that analysis.}
-
-\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the 
-hierarchically combined methods.}
-
-\begin{table}
-\begin{flushleft}
-\begin{tabular}{llllllll}
-\toprule
-Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
-& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\hline
-& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
-\hline
-
-GW150914 &
-$249^{+9}_{-7}$ &
-$-$ &
-\hphantom{X} &
-$4.1^{+0.3}_{-0.2}$ &
-$-$
-\\[0.075cm]
-
-GW170104 &
-$286^{+16}_{-27}$ &
-$-$ &
-\hphantom{X} &
-$3.5^{+0.4}_{-0.3}$ &
-$-$
-\\[0.075cm]
-
-GW170729 &
-$161^{+13}_{-14}$ &
-$-$ &
-\hphantom{X} &
-$7.8^{+1.8}_{-1.5}$ &
-$-$
-\\[0.075cm]
-
-GW190630$\_$185205 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-
-GW190828$\_$063405 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-\hline
-\bottomrule
-\end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table 
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
-\label{tab:qnm_o1o2_results}
-\end{flushleft}
-\end{table}
-
-\section{Discussion}\label{sec:discussion}
-
-\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers 
-about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also 
-EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al. 
-It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with 
-Richard and Vivien.}
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-LIGO Clusters. \comment{AB: Our cluster!!!}
-R.B.
-acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862.
-This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
-
-\appendix
-
 \section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
@@
 what you mean} can be unaccounted noise systematics.
-
-%
-\bibliographystyle{apsrev}
-\bibliography{intro_paper}
-
-\end{document}

### 2021-01-25 papers/intro_paper/discussion.tex
divided up paper into input segments

--- 2021-01-25 papers/intro_paper/intro_paper.tex
@@
-%\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers,nofootinbib]{revtex4-1}
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
-\usepackage{epsfig}
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{bm}
-\usepackage{times}
-\usepackage{xspace}
-\usepackage[varg]{txfonts}
-\usepackage[normalem]{ulem} % To get strikethrough (\sout)
-\usepackage[colorlinks]{hyperref}
-\usepackage[caption=false]{subfig}
-\usepackage{booktabs}
-\usepackage{url}
-\usepackage{float}
-\usepackage[bottom]{footmisc}
-\usepackage{lineno}
-%\linenumbers
-
-\definecolor{LinkColor}{rgb}{0.75, 0, 0}
-\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
-\definecolor{UrlColor}{rgb}{0, 0, 0.75}
-\hypersetup{linkcolor=LinkColor}
-\hypersetup{citecolor=CiteColor}
-\hypersetup{urlcolor=UrlColor}
-\usepackage{perpage}
-\MakePerPage{footnote}
-
-\newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
-\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
-\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
-\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
-
-\newcommand{\h}{\mathpzc{h}}
-\newcommand{\Hhat}{\hat{\mathpzc{H}}}
-\newcommand{\B}{\mathpzc{B}}
-\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
-\newcommand{\xilm}{\xi_{\ell m}}
-\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
-\newcommand{\Y}{{Y}^{-2}}
-\newcommand{\hc}{h_\times}
-\newcommand{\hp}{h_+}
-\newcommand{\Fc}{F_\times}
-\newcommand{\Fp}{F_+}
-\newcommand{\Mf}{M_f}
-\newcommand{\cA}{\mathpzc{A}}
-\newcommand{\lm}{_{\ell m}}
-\newcommand{\deff}{d_\mathrm{eff}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\blambda}{\bm{\lambda}}
-\newcommand{\btheta}{\bm{\theta}}
-\newcommand{\bxi}{\bm{\xi}}
-\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
-\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
-\newcommand{\bzeta}{\bm{\zeta}}
-\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
-\newcommand{\Mo}{M_{\odot}}
-\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
-\newcommand{\FF}{\mathrm{FF}}
-\newcommand{\e}{\mathrm{e}}
-\newcommand{\rhoopt}{\rho_\mathrm{opt}}
-\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
-\newcommand{\fqnm}{f}
-\newcommand{\sigmaqnm}{\sigma}
-\newcommand{\n}{\mathbf{n}}
-\newcommand*{\skymapscale}{0.5}
-\newcommand*{\paramestscale}{0.455}
-\newcommand{\df}[1]{\delta f_{\text{#1}}}
-\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f_{\text{#1}}}
-\newcommand{\taungr}[1]{\tau_{\text{#1}}}
-\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
-\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
-\newcommand{\pSEOB}{\texttt{pSEOBNR}}
-\newcommand{\SEOB}{\texttt{SEOBNR}}
-
-\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
-\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
-
-\begin{document}
-
-%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
-
-\title{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}
-
-\author{Abhirup Ghosh}
-\AEI
-\author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
-\author{Alessandra Buonanno}
-\AEI
-\UMD
-
-\date{\today}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  The no-hair conjecture in General Relativity states that the
-  properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin angular momentum. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
-  ringdown can be uniquely determined by the mass and spin of the
-  remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to 
-  test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using inspiral-merger-ringdown waveforms, thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the proposed ringdown. We
-  further demonstrate the robustness of the test against modified
-  gravitational-wave (GW) signals with a ringdown different from what
-  GR predicts for Kerr BHs. Our method was used to analyse the
-  properties of the merger remnants for the events observed by
-  LIGO-Virgo in the first half of their third observing run (O3a) in
-  the latest LIGO-Virgo publication. In this paper, for the first
-  time, we analyse the GW events from the first (O1) and second (O2) LIGO-Virgo
-  observing runs and provide joint constraints with published results
-  from O3a. We also analyse two events from the O3a catalogue 
-  that were not considered in the initial LIGO-Virgo analysis. The
-  joint measurements of the fractional deviations in the frequency and damping time,
-  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
-  constraints yet using this method.
-%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
-
-\section{Introduction}\label{sec:intro}
-
-\comment{AB: Please make the citations in the bibliography uniform (I would stick with citations 
-taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please 
-stick with American English. Also, please be uniform when writing captions, when using colors and style 
-of curves in plots, when building Tables. There is not a lot of discussion in the text on the main results of the paper (Sec. IV). 
-The abstract would need to be tighten and made more crispy once the quantitative results for the 
-bounds are included.}
-
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
-Collaboration~\citep{Virgo} have recently announced their catalogue of
-gravitational-wave (GW) signals from the first
-half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
-with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\citep{aasi2015characterization},
-and the Advanced Virgo detector in Cascina,
-Italy~\citep{acernese2014advanced} have now detected $50$ GW
-events from the merger of compact objects like neutron stars and/or
-black holes (BHs). Alongside independent claims of
-detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, notably GW150914~\citep{abbott2016observation}.
-
-The observation of GWs has had significant astrophysical and cosmological
-implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
-has also allowed us to probe fundamental
-physics and test predictions of Einstein's theory of General Relativity 
-(GR) in the previously unexplored highly-dynamical, and strong field 
-regime~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}, where the two
-compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon~\citep{NRpaper}, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\citep{vishu,earlyqnmpapers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
-
-The LIGO-Virgo collaborations have released companion papers \cite{} detailing their results 
-of tests of GR for GW150914 \cite{} and for several GW events of 
-the two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
-The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral~\citep{earlydevelopmentpapers}, and
-phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\citep{TIGERmethodspapers}; tests of GW
-propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
-polarization of gravitational radiation using a
-multi--GW-detector network~\citep{gw170814,isi2017probing}. The GWTC-1/2 papers also 
-check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
-consistency of the residuals with interferometric
-noise~\citep{Ghonge:2020suv,gwtc1_tgr}. None of these tests report any
-departure from the predictions of GR.
-
-The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
-first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH 
-coalescence. The LIGO-Virgo O3a testing GR paper~\cite{} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely
-described by two observables: mass and spin angular momentum. One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin angular momentum. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.
-
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in 
-Ref.~\citep{LSC_2016grtests} for GW150914, and later extended to include
-overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
-of the late-time \sout{signal} \ab{waveform} with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and \sout{checking for} consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
-in that direction \comment{AB: which direction? There are papers by Nikhef group and 
-also Brito et al., and many others that have investigated BH spectroscopy.} include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
-nature of the remnant object has also been explored through tests of
-BH thermodynamics, like the Hawking's area
-theorem~\citep{Cabero:2017avf} or through search for echos in the
-post-merger
-signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
-of these tests have found evidence for non-BH nature of the remnant
-object (as described in GR) in LIGO-Virgo BBH observations.
-
-\comment{AB: I don't understand the next sentence, it looks to me out of context.} 
-Most of the tests mentioned above focus on analysing the post-merger
-or late-time ringdown signal in isolation. \sout{Second generation
-ground-based interferometric detectors like} \ab{Ground-based detectors, 
-such as \sout{Advanced} LIGO and Virgo,} are most sensitive to 
-stellar-mass BH binaries that merge near the
-minim\ab{um}\sout{a} of their sensitivity band ($\sim 100$Hz). As a consequence, the
-remnant object \textit{rings down} \comment{AB: we are not discussing the interferometer noises, 
-so why to give such a detail about the shot noise?} \sout{in shot-noise dominated higher
-frequencies, leaving} \ab{at frequencies where the sensitivity is worse, leaving} 
-very little signal-to-noise ratio (SNR) in the
-post-merger signal. \comment{AB: This discussion about the starting time of the ringdown starts too abruptly, 
-and looks out of context and incomplete. Also, why are we citing only those papers? The matter 
-has a long history. There have been calibrations to NR of damped- oscillation signals.} 
-The ringdown start time is not a clearly defined
-quantity and has been explored in detail
-in Ref.~\citep{Bhagwat:2017tkm}. In other
-works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a
-free parameter to be estimated directly from the data. Uncertainties
-in estimates of the ringdown start-time, as well as, an overall lack of
-SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, result in significant statistical uncertainties
-in the measurement of the QNM frequencies.
-
-An independent approach to BH spectroscopy, based on the full-signal
-analysis, was \sout{outlined} \ab{introduced} in Ref.~\citep{Brito:2018rfr} 
-(henceforth referred to as \paperone). Unlike methods that focus \ab{only} 
-on the post-merger signal, it \sout{describes a framework in which a} 
-\ab{employs the} complete inspiral-merger-ringdown
-(IMR) waveform \sout{model is used} to measure the complex QNM
-frequencies. This \sout{allows} \ab{gives} access to the full SNR of the signal,
-reducing measurement uncertainties. Moreover, the definition of the
-ringdown start time is built into the \ab{merger-ringdown} model and does not need to be
-either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method \ab{and tested it for }\sout{in the context of a
-non-spinning waveform model} \ab{non-spinning BBHs}, \ab{here} we extend the analysis to the \ab{more 
-realistic astrophysical} case in which BHs \ab{carry} spin\sout{s in the current paper}. \ab{Furthermore, 
-the IMR waveform model used in this paper is more accurate than what employed in \paperone, 
-because it contains higher-order corrections in PN theory and it was calibrated to a much larger set 
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
-and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the 
-source properties \cite{paper_showing_systematics_from_ignoring_spin}.
-
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR\ab{, notably how we can measure 
-complex QNM frequencies with our parameterized model within a Bayesian formalism}. Then, in Sec.~\ref{sec:results}, 
-we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze 
-the ... and constrain the QNM frequecies ... Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.}
-
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component 
-objects in the binary; and the 
-\emph{extrinsic} parameters: a reference time $t_c$ and phase 
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$, 
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-
-Here, we focus on BHs with spins aligned or anti-aligned 
-with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
-the GW signal depends on $11$ parameters. We denote the 
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
-formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms, 
-here we use as our baseline model the aligned-spin multipolar waveform model 
-developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this 
-waveform model is called {\tt SEOBNRv4HM}.}.
-
-In the observer's frame, the GW polarizations can be written as 
-%
-\begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
-\end{equation}
-%
-where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
-\begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
-\end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
-\begin{equation}
-\label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
-\end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{equation}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
-\end{equation}
-%
-\begin{equation}
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{equation}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{align} 
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber   
-\end{align}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}    
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
-
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized 
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) is defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This 
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
-
-As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula 
-described above. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}), 
-(\ref{c2}), and (\ref{d1}).
-
-\subsection{Bayesian parameter-estimation technique}
-\label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
-fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH 
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs 
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-\iffalse
-\subsection{Priors}
-
-Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$.
-Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary.
-The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out.
-For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
-2015 LALInference paper).
-For our non-GR ringdown parameters, we assume uniform priors.
-This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}.
-For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
-\fi
-
-\ab{\section{Synthetic-signal injection study}}
-\label{sec:results}
-
-\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
-
-\ab{We demonstrate our method using synthetic-signal injections describing GWs 
-from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and 
-Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.} 
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and 
-GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}. 
-These two binary systems are representative of the kind of systems for which 
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the  
-pre- and post-merger SNRs return reliable parameter-estimation results.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
- \hline
-\end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
-$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
-The third row is completely ignored in the caption's explanations.}}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
-	\label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{To avoid possible systematic biases in our parameter-estimation analysis 
-due to error in waveform modeling,} we use the GR version of the same waveform,
-$\SEOB$ (without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context. 
-Why should the reader appreciate at this stage of the paper, where we have not yet 
-discussed results with real data, what is in the Appendix?} As in the case of the actual
-detections, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs. The distance to the two
-\ab{synthetic} events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14 
-for GW190521). Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
-$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
-(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
-to 1D and 2D posteriors when discussing the figures.}}
-
-\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
-we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
-the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose \sout{systems with initial-}binary-parameters
-similar to GW150914 and GW190521 (as given in Table XXX), but 
-\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
-  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
-based on QNM predictions in theories of gravity alternative to GR.}. 
-In other words, we assume that the frequency and damping time
-of our non-GR signal is 1.5 times the corresponding GR prediction,
-although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
-we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
-you just clearly refer to thePlease introduce the injected signal and the template, which is used 
-to recover it, and simply say that they belong to the same waweform model.} 
-We also avoid waveform \sout{and noise} systematic biases by choosing 
-a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
-summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
-show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
-$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
-values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
-explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
-is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
-
-We additionally investigate the effects of erroneously assuming that
-\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
-\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
-signals using the GR waveform model $\SEOB$ instead of the parameterized 
-$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
-In such cases, we run the risk of biased parameter estimates due to an
-incomplete understanding of the underlying signal. The resulting
-posterior probability distributions are shown in the right panels of
-Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
-(GW190521-like) curves.} The results are interesting and distinctly
-different for the two events. For the GW150914-like \comment{AB: I would avoid using 
-``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
-(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
-deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
-the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working 
-in Gaussian noise, so why are you referring to the noise as the culprit or the 
-source of difference?} The fact that the GW190521-like signal has a much
-lower SNR than GW150914-like signal might be a possible reason for the 
-measurement of the final quantities to be more susceptible to noise. A
-more detailed comparison of the other parameters, like the masses and
-spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
-signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
-comment the figures. What are the main results? What do we deduce?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
-	\label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
-switch the red and blue colors.
-The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
-Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
-\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
-(obtained by inverting the Berti fits).
-\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
-Also please specify if the remnant mass is the detector-frame mass.
-Please
-switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
-\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
-We choose an asymmetric system to increase the SNR in the higher modes. 
-We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
-such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
-the three detectors, LIGO Hanford, Livingston and
-Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
-asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible at design sensitivities. Using this
-signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
-$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
-our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
-
-The fractional deviations in the estimates of the damping time and
-frequency of either mode is expected to be consistent with 0, as we
-indeed find in the left panel of
-Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
-quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
-\taungr{330})$ are also consistent with the corresponding predictions
-for a BBH merger in GR. As a consequence, the information from these
-two independent measures correspond to a unique remnant object, which
-is completely described by its mass and spin angular momentum
-\abhi{have the mf-af plot as well as a third panel to show
-  consistency}. For most of the events observed so far, the power in
-the $(3,\pm 3)$ has not been sufficient to measure it along with the
-$(2,\pm 2)$, or in fact, in its place. However, it might also be
-possible to combine information from multiple observation\sout{, as is
-likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
-detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
-	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
-The plus signs mark the GR predictions.}
-	\label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
-
-\comment{AB: This is the most important section in the paper, because it contains the 
-main results of the paper, i.e., the constraints on QNMs using real data. It needs to 
-be expanded and results would need to be highlighted much better than in the current version. 
-I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors 
-that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have 
-a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the 
-TGR GWTC-2, but for the 22 QNM frequencies for the different GW events. 
-Figures can be used in talks, and can capture the information much better 
-than a list of numbers in a Table.}
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results \sout{of this test} for all events observed
-during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
-total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
-signal} before and after the signal reaches \ab{the} peak\ab{'s} 
-amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the} 
-likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
-\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the 
-entire paper, except perhaps the Conclusions section.} 
-For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
-threshold and restrict\sout{ed} ourselves to the highest-mass events which
-\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
-since our method relies on doing a parameter estimation on the entire
-inspiral-merger-ringdown signal, we require the SNR to be beyond a
-certain threshold throughout the signal for reliable parameter
-estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters, 
-there are the component masses of the holes in the binary, and the 
-mass of the remnant formed after merger.} In fact the SNR
-threshold alone should be sufficient for the analysis, and for this
-paper we have relaxed the mass threshold. This has added two events,
-GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
-  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
-events along with GW190519$\_$153544, GW190521$\_$074359,
-GW190910$\_$112807. \comment{AB: Please improve the above paragraph 
-and make it clearer which choice is made for the SNR threshold and 
-masses, and why.}
-
-\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to 
-measure the QNMs to} \sout{present results on} the relevant
-GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same thresholds as above, we find three
-additional events that could be included in the analysis: GW150914,
-GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
-merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
-reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
-which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
-  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $pSEOB$ test, as well.} Among all the GW signals detected so far,
-GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what 
-is the ``clarity'' of a signal?} leading to the
-first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
-	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
-	\label{fig:o1o2_events}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, if we assume that the fractional deviations $(\df{220},
-\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. 
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis 
-if we want to include that analysis. AB: we want to include that analysis.}
-
-\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the 
-hierarchically combined methods.}
-
-\begin{table}
-\begin{flushleft}
-\begin{tabular}{llllllll}
-\toprule
-Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
-& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\hline
-& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
-\hline
-
-GW150914 &
-$249^{+9}_{-7}$ &
-$-$ &
-\hphantom{X} &
-$4.1^{+0.3}_{-0.2}$ &
-$-$
-\\[0.075cm]
-
-GW170104 &
-$286^{+16}_{-27}$ &
-$-$ &
-\hphantom{X} &
-$3.5^{+0.4}_{-0.3}$ &
-$-$
-\\[0.075cm]
-
-GW170729 &
-$161^{+13}_{-14}$ &
-$-$ &
-\hphantom{X} &
-$7.8^{+1.8}_{-1.5}$ &
-$-$
-\\[0.075cm]
-
-GW190630$\_$185205 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-
-GW190828$\_$063405 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-\hline
-\bottomrule
-\end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table 
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
-\label{tab:qnm_o1o2_results}
-\end{flushleft}
-\end{table}
-
-\section{Discussion}\label{sec:discussion}
-
 \comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers
@@
 Richard and Vivien.}
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-LIGO Clusters. \comment{AB: Our cluster!!!}
-R.B.
-acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862.
-This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
-
-\appendix
-
-\section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
-
-\comment{AB: Please improve considerably this Appendix because it is not easy to follow the motivation and the logic. It is written for LIGO people. 
-I have tried to make changes but it is better if you do it. I risk to erase parts that you would consider important. Please write it thinking that your 
-reader is not an LSC reader!}
-
-In Sec.~\ref{sec:method}, we \ab{discussed} \sout{mentioned that} the expression of the
-Bayesian likelihood function \ab{that we use in our analysis} \sout{outlined in} \ab{(see 
-Eq.~\ref{eq:likelihood})} \ab{and stressed that it}\sout{and \ref{eq:nwip}} is only valid if the interferometric noise can be
-described as a stationary Gaussian process. LIGO-Virgo noise, however,
-frequently has non-stationary and/or non-Gaussian features, for
-example glitches, which can affect parameter inferences unless
-appropriately accounted for. Here we demonstrate\ab{, by injecting in real 
-noise a GW190521-like signal} \sout{with an example of a
-GW190521-like simulated signal}, \ab{how} systematic biases \ab{can originate} \sout{likely originating}
-from an incomplete understanding of the noise. \comment{AB: It is confusing to refer to ``systematic'' 
-biases for the noise, generally we refer to systematic biases for the waveform modeling. 
-In fact, below you also, somewhat suddenly, refer to (lack of) precession, as a possible source of systemtcis. 
-I would advice you to clarify from the beginning of this Appendix, what this study is about and what you intend to 
-do below.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ from simulations \comment{AB: I have changed this in other places.
-The word ``simulations'' is confusing, because we deal with a paper in which we also refer to NR simulations.
-I suggest to use ``injected synthetic signals'' instead} of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
-The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-For comparison, we also plot the 90 \% credible level for the actual event, GW190521.
-\comment{AB: For clarity, please indicate on the plot which waveform model is used to obtain such posteriors, as you did
-in the other plots of the paper. Also, please use something else instead of ``actual event'', which is confusing. The problem is 
-that the first two entries of the legend refer to the noise properties of the PE study done with an injected synthetic signal, whereas I believe ``actual event'' refers to ``real'' not injected signal
-and ``real noise''. All the entries in the legend need to be consistent with each other; you need to specify for each of them the ``signal'' and the ``noise''. I hope is clear what I am saying}}
-	\label{fig:21g_systematics}
-\end{center}	
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{The spinning, precessing NR-surrogate model \texttt{NRSur7dq4}, valid up to mass ratio 4, was employed 
-(together with the $\SEOB$ model) to analyze the GW190521 signal observed by the LIGO and Virgo detectors. 
-For the injected synthetic signal we use a \texttt{NRSur7dq4} waveform with parameters similar to the ones 
-recovered by this model on the actual GW190521 data (see Table I of Ref.~\cite{Abbott:2020tfl}).}  
-\ab{In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal 
-predicts for the $(2,2)$ frequency and damping time, and for comparison, we also 
-show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$. As seen in the plot, while 
-the measurement of the frequency is consistent with the prediction, we overestimate the damping time.} \comment{AB: it is not clear 
-to me what the figure shows. Is the black line the result when running $\pSEOB$ against real data or the 
-injection in realt data?}
-
-\comment{AB: What is the ``underlying'' NR signal? I think you are referring to the 
-injected signal. Also, until now you have not discussed precession. 
-} The underlying NR signal is expected to be precessing, and since the
-$\pSEOB$ model is built on an aligned-spin GR model, a lack of
-precession could bias measurements. We explore effects of possible
-waveform systematics by injecting the signal is coloured Gaussian
-noise. In this case, since the understanding of the noise realizations
-is complete, any measurement biases could only arise from incomplete
-understanding of the \sout{underlying} \ab{injected} signal. We find (grey curves in
-Fig.\ref{fig:21g_systematics}) our results to be consistent with the
-prediction thus ruling out a lack of precession to be a likely cause
-for the bias in the damping time measurement of the actual signal.
-
-We subsequently study the effects of possible noise systematics by
-injecting the same \texttt{NRSur7dq4} GW signal in different
-realizations of actual interferometric noise around the real event
-GW190521. Since the PSDs of the GW detectors are expected to vary over
-longer durations of time, we select 5 different noise realizations
-over a segment of 2.5 hours of coincident data in both the LIGO
-detectors centered at the time of the actual event. The noise
-properties in this chunk of data, and consequently for all 5 simulated
-signals, is expected to be the closest to that for the actual
-event. The results are indicated by \sout{pink} \ab{green} curves in
-Fig.~\ref{fig:21g_systematics}. \ab{As it can be seen from the figure,} 
-for 3 of the 5 noise realizations,
-corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we
-recover a damping time similar to the actual event, where $t_0$ is the
-GPS time of the actual event. For the other two noise realizations, we
-estimate the consistent damping time but an off-set frequency, while
-the fifth noise realization is consistent with both predictions. The
-SNR in the Livingston detector goes down by more than \ab{a factor} 3 in some
-runs, indicative of how a variation in the noise strongly affects our
-ability to infer parameters. This also seems to indicate that a bias
-in the measurements of the damping time for the actual event \comment{AB: not clear 
-what you mean} can be unaccounted noise systematics.
-
-%
-\bibliographystyle{apsrev}
-\bibliography{intro_paper}
-
-\end{document}

### 2021-01-25 papers/intro_paper/intro.tex
divided up paper into input segments

--- 2021-01-25 papers/intro_paper/intro_paper.tex
@@
-%\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers,nofootinbib]{revtex4-1}
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
-\usepackage{epsfig}
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{bm}
-\usepackage{times}
-\usepackage{xspace}
-\usepackage[varg]{txfonts}
-\usepackage[normalem]{ulem} % To get strikethrough (\sout)
-\usepackage[colorlinks]{hyperref}
-\usepackage[caption=false]{subfig}
-\usepackage{booktabs}
-\usepackage{url}
-\usepackage{float}
-\usepackage[bottom]{footmisc}
-\usepackage{lineno}
-%\linenumbers
-
-\definecolor{LinkColor}{rgb}{0.75, 0, 0}
-\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
-\definecolor{UrlColor}{rgb}{0, 0, 0.75}
-\hypersetup{linkcolor=LinkColor}
-\hypersetup{citecolor=CiteColor}
-\hypersetup{urlcolor=UrlColor}
-\usepackage{perpage}
-\MakePerPage{footnote}
-
-\newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
-\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
-\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
-\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
-
-\newcommand{\h}{\mathpzc{h}}
-\newcommand{\Hhat}{\hat{\mathpzc{H}}}
-\newcommand{\B}{\mathpzc{B}}
-\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
-\newcommand{\xilm}{\xi_{\ell m}}
-\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
-\newcommand{\Y}{{Y}^{-2}}
-\newcommand{\hc}{h_\times}
-\newcommand{\hp}{h_+}
-\newcommand{\Fc}{F_\times}
-\newcommand{\Fp}{F_+}
-\newcommand{\Mf}{M_f}
-\newcommand{\cA}{\mathpzc{A}}
-\newcommand{\lm}{_{\ell m}}
-\newcommand{\deff}{d_\mathrm{eff}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\blambda}{\bm{\lambda}}
-\newcommand{\btheta}{\bm{\theta}}
-\newcommand{\bxi}{\bm{\xi}}
-\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
-\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
-\newcommand{\bzeta}{\bm{\zeta}}
-\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
-\newcommand{\Mo}{M_{\odot}}
-\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
-\newcommand{\FF}{\mathrm{FF}}
-\newcommand{\e}{\mathrm{e}}
-\newcommand{\rhoopt}{\rho_\mathrm{opt}}
-\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
-\newcommand{\fqnm}{f}
-\newcommand{\sigmaqnm}{\sigma}
-\newcommand{\n}{\mathbf{n}}
-\newcommand*{\skymapscale}{0.5}
-\newcommand*{\paramestscale}{0.455}
-\newcommand{\df}[1]{\delta f_{\text{#1}}}
-\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f_{\text{#1}}}
-\newcommand{\taungr}[1]{\tau_{\text{#1}}}
-\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
-\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
-\newcommand{\pSEOB}{\texttt{pSEOBNR}}
-\newcommand{\SEOB}{\texttt{SEOBNR}}
-
-\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
-\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
-
-\begin{document}
-
-%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
-
-\title{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}
-
-\author{Abhirup Ghosh}
-\AEI
-\author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
-\author{Alessandra Buonanno}
-\AEI
-\UMD
-
-\date{\today}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  The no-hair conjecture in General Relativity states that the
-  properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin angular momentum. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
-  ringdown can be uniquely determined by the mass and spin of the
-  remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to 
-  test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using inspiral-merger-ringdown waveforms, thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the proposed ringdown. We
-  further demonstrate the robustness of the test against modified
-  gravitational-wave (GW) signals with a ringdown different from what
-  GR predicts for Kerr BHs. Our method was used to analyse the
-  properties of the merger remnants for the events observed by
-  LIGO-Virgo in the first half of their third observing run (O3a) in
-  the latest LIGO-Virgo publication. In this paper, for the first
-  time, we analyse the GW events from the first (O1) and second (O2) LIGO-Virgo
-  observing runs and provide joint constraints with published results
-  from O3a. We also analyse two events from the O3a catalogue 
-  that were not considered in the initial LIGO-Virgo analysis. The
-  joint measurements of the fractional deviations in the frequency and damping time,
-  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
-  constraints yet using this method.
-%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
-
-\section{Introduction}\label{sec:intro}
-
 \comment{AB: Please make the citations in the bibliography uniform (I would stick with citations
@@
 our results and discuss future developments.}
-
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component 
-objects in the binary; and the 
-\emph{extrinsic} parameters: a reference time $t_c$ and phase 
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$, 
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-
-Here, we focus on BHs with spins aligned or anti-aligned 
-with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
-the GW signal depends on $11$ parameters. We denote the 
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
-formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms, 
-here we use as our baseline model the aligned-spin multipolar waveform model 
-developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this 
-waveform model is called {\tt SEOBNRv4HM}.}.
-
-In the observer's frame, the GW polarizations can be written as 
-%
-\begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
-\end{equation}
-%
-where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
-\begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
-\end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
-\begin{equation}
-\label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
-\end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{equation}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
-\end{equation}
-%
-\begin{equation}
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{equation}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{align} 
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber   
-\end{align}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}    
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
-
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized 
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) is defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This 
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
-
-As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula 
-described above. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}), 
-(\ref{c2}), and (\ref{d1}).
-
-\subsection{Bayesian parameter-estimation technique}
-\label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
-fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH 
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs 
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-\iffalse
-\subsection{Priors}
-
-Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$.
-Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary.
-The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out.
-For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
-2015 LALInference paper).
-For our non-GR ringdown parameters, we assume uniform priors.
-This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}.
-For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
-\fi
-
-\ab{\section{Synthetic-signal injection study}}
-\label{sec:results}
-
-\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
-
-\ab{We demonstrate our method using synthetic-signal injections describing GWs 
-from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and 
-Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.} 
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and 
-GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}. 
-These two binary systems are representative of the kind of systems for which 
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the  
-pre- and post-merger SNRs return reliable parameter-estimation results.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
- \hline
-\end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
-$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
-The third row is completely ignored in the caption's explanations.}}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
-	\label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{To avoid possible systematic biases in our parameter-estimation analysis 
-due to error in waveform modeling,} we use the GR version of the same waveform,
-$\SEOB$ (without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context. 
-Why should the reader appreciate at this stage of the paper, where we have not yet 
-discussed results with real data, what is in the Appendix?} As in the case of the actual
-detections, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs. The distance to the two
-\ab{synthetic} events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14 
-for GW190521). Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
-$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
-(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
-to 1D and 2D posteriors when discussing the figures.}}
-
-\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
-we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
-the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose \sout{systems with initial-}binary-parameters
-similar to GW150914 and GW190521 (as given in Table XXX), but 
-\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
-  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
-based on QNM predictions in theories of gravity alternative to GR.}. 
-In other words, we assume that the frequency and damping time
-of our non-GR signal is 1.5 times the corresponding GR prediction,
-although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
-we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
-you just clearly refer to thePlease introduce the injected signal and the template, which is used 
-to recover it, and simply say that they belong to the same waweform model.} 
-We also avoid waveform \sout{and noise} systematic biases by choosing 
-a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
-summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
-show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
-$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
-values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
-explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
-is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
-
-We additionally investigate the effects of erroneously assuming that
-\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
-\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
-signals using the GR waveform model $\SEOB$ instead of the parameterized 
-$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
-In such cases, we run the risk of biased parameter estimates due to an
-incomplete understanding of the underlying signal. The resulting
-posterior probability distributions are shown in the right panels of
-Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
-(GW190521-like) curves.} The results are interesting and distinctly
-different for the two events. For the GW150914-like \comment{AB: I would avoid using 
-``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
-(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
-deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
-the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working 
-in Gaussian noise, so why are you referring to the noise as the culprit or the 
-source of difference?} The fact that the GW190521-like signal has a much
-lower SNR than GW150914-like signal might be a possible reason for the 
-measurement of the final quantities to be more susceptible to noise. A
-more detailed comparison of the other parameters, like the masses and
-spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
-signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
-comment the figures. What are the main results? What do we deduce?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
-	\label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
-switch the red and blue colors.
-The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
-Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
-\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
-(obtained by inverting the Berti fits).
-\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
-Also please specify if the remnant mass is the detector-frame mass.
-Please
-switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
-\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
-We choose an asymmetric system to increase the SNR in the higher modes. 
-We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
-such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
-the three detectors, LIGO Hanford, Livingston and
-Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
-asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible at design sensitivities. Using this
-signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
-$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
-our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
-
-The fractional deviations in the estimates of the damping time and
-frequency of either mode is expected to be consistent with 0, as we
-indeed find in the left panel of
-Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
-quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
-\taungr{330})$ are also consistent with the corresponding predictions
-for a BBH merger in GR. As a consequence, the information from these
-two independent measures correspond to a unique remnant object, which
-is completely described by its mass and spin angular momentum
-\abhi{have the mf-af plot as well as a third panel to show
-  consistency}. For most of the events observed so far, the power in
-the $(3,\pm 3)$ has not been sufficient to measure it along with the
-$(2,\pm 2)$, or in fact, in its place. However, it might also be
-possible to combine information from multiple observation\sout{, as is
-likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
-detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
-	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
-The plus signs mark the GR predictions.}
-	\label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
-
-\comment{AB: This is the most important section in the paper, because it contains the 
-main results of the paper, i.e., the constraints on QNMs using real data. It needs to 
-be expanded and results would need to be highlighted much better than in the current version. 
-I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors 
-that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have 
-a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the 
-TGR GWTC-2, but for the 22 QNM frequencies for the different GW events. 
-Figures can be used in talks, and can capture the information much better 
-than a list of numbers in a Table.}
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results \sout{of this test} for all events observed
-during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
-total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
-signal} before and after the signal reaches \ab{the} peak\ab{'s} 
-amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the} 
-likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
-\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the 
-entire paper, except perhaps the Conclusions section.} 
-For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
-threshold and restrict\sout{ed} ourselves to the highest-mass events which
-\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
-since our method relies on doing a parameter estimation on the entire
-inspiral-merger-ringdown signal, we require the SNR to be beyond a
-certain threshold throughout the signal for reliable parameter
-estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters, 
-there are the component masses of the holes in the binary, and the 
-mass of the remnant formed after merger.} In fact the SNR
-threshold alone should be sufficient for the analysis, and for this
-paper we have relaxed the mass threshold. This has added two events,
-GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
-  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
-events along with GW190519$\_$153544, GW190521$\_$074359,
-GW190910$\_$112807. \comment{AB: Please improve the above paragraph 
-and make it clearer which choice is made for the SNR threshold and 
-masses, and why.}
-
-\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to 
-measure the QNMs to} \sout{present results on} the relevant
-GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same thresholds as above, we find three
-additional events that could be included in the analysis: GW150914,
-GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
-merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
-reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
-which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
-  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $pSEOB$ test, as well.} Among all the GW signals detected so far,
-GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what 
-is the ``clarity'' of a signal?} leading to the
-first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
-	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
-	\label{fig:o1o2_events}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, if we assume that the fractional deviations $(\df{220},
-\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. 
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis 
-if we want to include that analysis. AB: we want to include that analysis.}
-
-\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the 
-hierarchically combined methods.}
-
-\begin{table}
-\begin{flushleft}
-\begin{tabular}{llllllll}
-\toprule
-Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
-& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\hline
-& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
-\hline
-
-GW150914 &
-$249^{+9}_{-7}$ &
-$-$ &
-\hphantom{X} &
-$4.1^{+0.3}_{-0.2}$ &
-$-$
-\\[0.075cm]
-
-GW170104 &
-$286^{+16}_{-27}$ &
-$-$ &
-\hphantom{X} &
-$3.5^{+0.4}_{-0.3}$ &
-$-$
-\\[0.075cm]
-
-GW170729 &
-$161^{+13}_{-14}$ &
-$-$ &
-\hphantom{X} &
-$7.8^{+1.8}_{-1.5}$ &
-$-$
-\\[0.075cm]
-
-GW190630$\_$185205 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-
-GW190828$\_$063405 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-\hline
-\bottomrule
-\end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table 
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
-\label{tab:qnm_o1o2_results}
-\end{flushleft}
-\end{table}
-
-\section{Discussion}\label{sec:discussion}
-
-\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers 
-about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also 
-EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al. 
-It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with 
-Richard and Vivien.}
-
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-LIGO Clusters. \comment{AB: Our cluster!!!}
-R.B.
-acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862.
-This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
-
-\appendix
-
-\section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
-
-\comment{AB: Please improve considerably this Appendix because it is not easy to follow the motivation and the logic. It is written for LIGO people. 
-I have tried to make changes but it is better if you do it. I risk to erase parts that you would consider important. Please write it thinking that your 
-reader is not an LSC reader!}
-
-In Sec.~\ref{sec:method}, we \ab{discussed} \sout{mentioned that} the expression of the
-Bayesian likelihood function \ab{that we use in our analysis} \sout{outlined in} \ab{(see 
-Eq.~\ref{eq:likelihood})} \ab{and stressed that it}\sout{and \ref{eq:nwip}} is only valid if the interferometric noise can be
-described as a stationary Gaussian process. LIGO-Virgo noise, however,
-frequently has non-stationary and/or non-Gaussian features, for
-example glitches, which can affect parameter inferences unless
-appropriately accounted for. Here we demonstrate\ab{, by injecting in real 
-noise a GW190521-like signal} \sout{with an example of a
-GW190521-like simulated signal}, \ab{how} systematic biases \ab{can originate} \sout{likely originating}
-from an incomplete understanding of the noise. \comment{AB: It is confusing to refer to ``systematic'' 
-biases for the noise, generally we refer to systematic biases for the waveform modeling. 
-In fact, below you also, somewhat suddenly, refer to (lack of) precession, as a possible source of systemtcis. 
-I would advice you to clarify from the beginning of this Appendix, what this study is about and what you intend to 
-do below.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ from simulations \comment{AB: I have changed this in other places.
-The word ``simulations'' is confusing, because we deal with a paper in which we also refer to NR simulations.
-I suggest to use ``injected synthetic signals'' instead} of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
-The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-For comparison, we also plot the 90 \% credible level for the actual event, GW190521.
-\comment{AB: For clarity, please indicate on the plot which waveform model is used to obtain such posteriors, as you did
-in the other plots of the paper. Also, please use something else instead of ``actual event'', which is confusing. The problem is 
-that the first two entries of the legend refer to the noise properties of the PE study done with an injected synthetic signal, whereas I believe ``actual event'' refers to ``real'' not injected signal
-and ``real noise''. All the entries in the legend need to be consistent with each other; you need to specify for each of them the ``signal'' and the ``noise''. I hope is clear what I am saying}}
-	\label{fig:21g_systematics}
-\end{center}	
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{The spinning, precessing NR-surrogate model \texttt{NRSur7dq4}, valid up to mass ratio 4, was employed 
-(together with the $\SEOB$ model) to analyze the GW190521 signal observed by the LIGO and Virgo detectors. 
-For the injected synthetic signal we use a \texttt{NRSur7dq4} waveform with parameters similar to the ones 
-recovered by this model on the actual GW190521 data (see Table I of Ref.~\cite{Abbott:2020tfl}).}  
-\ab{In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal 
-predicts for the $(2,2)$ frequency and damping time, and for comparison, we also 
-show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$. As seen in the plot, while 
-the measurement of the frequency is consistent with the prediction, we overestimate the damping time.} \comment{AB: it is not clear 
-to me what the figure shows. Is the black line the result when running $\pSEOB$ against real data or the 
-injection in realt data?}
-
-\comment{AB: What is the ``underlying'' NR signal? I think you are referring to the 
-injected signal. Also, until now you have not discussed precession. 
-} The underlying NR signal is expected to be precessing, and since the
-$\pSEOB$ model is built on an aligned-spin GR model, a lack of
-precession could bias measurements. We explore effects of possible
-waveform systematics by injecting the signal is coloured Gaussian
-noise. In this case, since the understanding of the noise realizations
-is complete, any measurement biases could only arise from incomplete
-understanding of the \sout{underlying} \ab{injected} signal. We find (grey curves in
-Fig.\ref{fig:21g_systematics}) our results to be consistent with the
-prediction thus ruling out a lack of precession to be a likely cause
-for the bias in the damping time measurement of the actual signal.
-
-We subsequently study the effects of possible noise systematics by
-injecting the same \texttt{NRSur7dq4} GW signal in different
-realizations of actual interferometric noise around the real event
-GW190521. Since the PSDs of the GW detectors are expected to vary over
-longer durations of time, we select 5 different noise realizations
-over a segment of 2.5 hours of coincident data in both the LIGO
-detectors centered at the time of the actual event. The noise
-properties in this chunk of data, and consequently for all 5 simulated
-signals, is expected to be the closest to that for the actual
-event. The results are indicated by \sout{pink} \ab{green} curves in
-Fig.~\ref{fig:21g_systematics}. \ab{As it can be seen from the figure,} 
-for 3 of the 5 noise realizations,
-corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we
-recover a damping time similar to the actual event, where $t_0$ is the
-GPS time of the actual event. For the other two noise realizations, we
-estimate the consistent damping time but an off-set frequency, while
-the fifth noise realization is consistent with both predictions. The
-SNR in the Livingston detector goes down by more than \ab{a factor} 3 in some
-runs, indicative of how a variation in the noise strongly affects our
-ability to infer parameters. This also seems to indicate that a bias
-in the measurements of the damping time for the actual event \comment{AB: not clear 
-what you mean} can be unaccounted noise systematics.
-
-%
-\bibliographystyle{apsrev}
-\bibliography{intro_paper}
-
-\end{document}

### 2021-01-25 papers/intro_paper/intro_paper.tex
divided up paper into input segments

@@
 \begin{abstract}
-  The no-hair conjecture in General Relativity states that the
-  properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin angular momentum. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
-  ringdown can be uniquely determined by the mass and spin of the
-  remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to 
-  test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using inspiral-merger-ringdown waveforms, thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the proposed ringdown. We
-  further demonstrate the robustness of the test against modified
-  gravitational-wave (GW) signals with a ringdown different from what
-  GR predicts for Kerr BHs. Our method was used to analyse the
-  properties of the merger remnants for the events observed by
-  LIGO-Virgo in the first half of their third observing run (O3a) in
-  the latest LIGO-Virgo publication. In this paper, for the first
-  time, we analyse the GW events from the first (O1) and second (O2) LIGO-Virgo
-  observing runs and provide joint constraints with published results
-  from O3a. We also analyse two events from the O3a catalogue 
-  that were not considered in the initial LIGO-Virgo analysis. The
-  joint measurements of the fractional deviations in the frequency and damping time,
-  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
-  constraints yet using this method.
-%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
+\input{abstract}
 \end{abstract}
@@
 
-\section{Introduction}\label{sec:intro}
+%%%%%%%%%%%%%%%%%
+\section{Introduction}
+\label{sec:intro}
+\input{intro}
+%%%%%%%%%%%%%%%%%
 
-\comment{AB: Please make the citations in the bibliography uniform (I would stick with citations 
-taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please 
-stick with American English. Also, please be uniform when writing captions, when using colors and style 
-of curves in plots, when building Tables. There is not a lot of discussion in the text on the main results of the paper (Sec. IV). 
-The abstract would need to be tighten and made more crispy once the quantitative results for the 
-bounds are included.}
+%%%%%%%%%%%%%%%%%
+\section{Waveform model and statistical strategy to measure quasi-normal modes}
+\input{model_method}
+%%%%%%%%%%%%%%%%%
 
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
-Collaboration~\citep{Virgo} have recently announced their catalogue of
-gravitational-wave (GW) signals from the first
-half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
-with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\citep{aasi2015characterization},
-and the Advanced Virgo detector in Cascina,
-Italy~\citep{acernese2014advanced} have now detected $50$ GW
-events from the merger of compact objects like neutron stars and/or
-black holes (BHs). Alongside independent claims of
-detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, notably GW150914~\citep{abbott2016observation}.
-
-The observation of GWs has had significant astrophysical and cosmological
-implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
-has also allowed us to probe fundamental
-physics and test predictions of Einstein's theory of General Relativity 
-(GR) in the previously unexplored highly-dynamical, and strong field 
-regime~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}, where the two
-compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon~\citep{NRpaper}, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\citep{vishu,earlyqnmpapers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
-
-The LIGO-Virgo collaborations have released companion papers \cite{} detailing their results 
-of tests of GR for GW150914 \cite{} and for several GW events of 
-the two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}. 
-The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral~\citep{earlydevelopmentpapers}, and
-phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\citep{TIGERmethodspapers}; tests of GW
-propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
-polarization of gravitational radiation using a
-multi--GW-detector network~\citep{gw170814,isi2017probing}. The GWTC-1/2 papers also 
-check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
-consistency of the residuals with interferometric
-noise~\citep{Ghonge:2020suv,gwtc1_tgr}. None of these tests report any
-departure from the predictions of GR.
-
-The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the 
-first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH 
-coalescence. The LIGO-Virgo O3a testing GR paper~\cite{} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely
-described by two observables: mass and spin angular momentum. One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin angular momentum. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.
-
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in 
-Ref.~\citep{LSC_2016grtests} for GW150914, and later extended to include
-overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
-of the late-time \sout{signal} \ab{waveform} with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and \sout{checking for} consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
-in that direction \comment{AB: which direction? There are papers by Nikhef group and 
-also Brito et al., and many others that have investigated BH spectroscopy.} include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
-nature of the remnant object has also been explored through tests of
-BH thermodynamics, like the Hawking's area
-theorem~\citep{Cabero:2017avf} or through search for echos in the
-post-merger
-signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
-of these tests have found evidence for non-BH nature of the remnant
-object (as described in GR) in LIGO-Virgo BBH observations.
-
-\comment{AB: I don't understand the next sentence, it looks to me out of context.} 
-Most of the tests mentioned above focus on analysing the post-merger
-or late-time ringdown signal in isolation. \sout{Second generation
-ground-based interferometric detectors like} \ab{Ground-based detectors, 
-such as \sout{Advanced} LIGO and Virgo,} are most sensitive to 
-stellar-mass BH binaries that merge near the
-minim\ab{um}\sout{a} of their sensitivity band ($\sim 100$Hz). As a consequence, the
-remnant object \textit{rings down} \comment{AB: we are not discussing the interferometer noises, 
-so why to give such a detail about the shot noise?} \sout{in shot-noise dominated higher
-frequencies, leaving} \ab{at frequencies where the sensitivity is worse, leaving} 
-very little signal-to-noise ratio (SNR) in the
-post-merger signal. \comment{AB: This discussion about the starting time of the ringdown starts too abruptly, 
-and looks out of context and incomplete. Also, why are we citing only those papers? The matter 
-has a long history. There have been calibrations to NR of damped- oscillation signals.} 
-The ringdown start time is not a clearly defined
-quantity and has been explored in detail
-in Ref.~\citep{Bhagwat:2017tkm}. In other
-works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a
-free parameter to be estimated directly from the data. Uncertainties
-in estimates of the ringdown start-time, as well as, an overall lack of
-SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, result in significant statistical uncertainties
-in the measurement of the QNM frequencies.
-
-An independent approach to BH spectroscopy, based on the full-signal
-analysis, was \sout{outlined} \ab{introduced} in Ref.~\citep{Brito:2018rfr} 
-(henceforth referred to as \paperone). Unlike methods that focus \ab{only} 
-on the post-merger signal, it \sout{describes a framework in which a} 
-\ab{employs the} complete inspiral-merger-ringdown
-(IMR) waveform \sout{model is used} to measure the complex QNM
-frequencies. This \sout{allows} \ab{gives} access to the full SNR of the signal,
-reducing measurement uncertainties. Moreover, the definition of the
-ringdown start time is built into the \ab{merger-ringdown} model and does not need to be
-either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method \ab{and tested it for }\sout{in the context of a
-non-spinning waveform model} \ab{non-spinning BBHs}, \ab{here} we extend the analysis to the \ab{more 
-realistic astrophysical} case in which BHs \ab{carry} spin\sout{s in the current paper}. \ab{Furthermore, 
-the IMR waveform model used in this paper is more accurate than what employed in \paperone, 
-because it contains higher-order corrections in PN theory and it was calibrated to a much larger set 
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning, 
-and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the 
-source properties \cite{paper_showing_systematics_from_ignoring_spin}.
-
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR\ab{, notably how we can measure 
-complex QNM frequencies with our parameterized model within a Bayesian formalism}. Then, in Sec.~\ref{sec:results}, 
-we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze 
-the ... and constrain the QNM frequecies ... Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.}
-
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component 
-objects in the binary; and the 
-\emph{extrinsic} parameters: a reference time $t_c$ and phase 
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$, 
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-
-Here, we focus on BHs with spins aligned or anti-aligned 
-with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,  
-the GW signal depends on $11$ parameters. We denote the 
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB) 
-formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms, 
-here we use as our baseline model the aligned-spin multipolar waveform model 
-developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this 
-waveform model is called {\tt SEOBNRv4HM}.}.
-
-In the observer's frame, the GW polarizations can be written as 
-%
-\begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
-\end{equation}
-%
-where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
-\begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
-\end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
-\begin{equation}
-\label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
-\end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{equation}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
-\end{equation}
-%
-\begin{equation}
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{equation}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{align} 
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber   
-\end{align}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}    
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
-
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized 
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) is defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This 
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
-
-As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula 
-described above. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}), 
-(\ref{c2}), and (\ref{d1}).
-
-\subsection{Bayesian parameter-estimation technique}
-\label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
-fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH 
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs 
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-\iffalse
-\subsection{Priors}
-
-Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$.
-Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary.
-The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out.
-For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al.
-2015 LALInference paper).
-For our non-GR ringdown parameters, we assume uniform priors.
-This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}.
-For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
-\fi
-
+%%%%%%%%%%%%%%%%%
 \ab{\section{Synthetic-signal injection study}}
 \label{sec:results}
+\input{results_synthetic}
+%%%%%%%%%%%%%%%%%
 
-\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
+%%%%%%%%%%%%%%%%%
+\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
+\input{results_lvc}
+%%%%%%%%%%%%%%%%%
 
-\ab{We demonstrate our method using synthetic-signal injections describing GWs 
-from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and 
-Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.} 
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and 
-GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}. 
-These two binary systems are representative of the kind of systems for which 
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the  
-pre- and post-merger SNRs return reliable parameter-estimation results.}
+%%%%%%%%%%%%%%%%%
+\section{Discussion}
+\label{sec:discussion}
+\input{discussion}
+%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\ 
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\ 
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
- \hline
-\end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters 
-$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
-The third row is completely ignored in the caption's explanations.}}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}		
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
-	\label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{To avoid possible systematic biases in our parameter-estimation analysis 
-due to error in waveform modeling,} we use the GR version of the same waveform,
-$\SEOB$ (without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context. 
-Why should the reader appreciate at this stage of the paper, where we have not yet 
-discussed results with real data, what is in the Appendix?} As in the case of the actual
-detections, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs. The distance to the two
-\ab{synthetic} events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14 
-for GW190521). Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
-$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-\ab{2D} posterior{\ab{s} are consistent with the GR predictions 
-(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring 
-to 1D and 2D posteriors when discussing the figures.}}
-
-\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations \sout{of the underlying GW signal from predictions of} \ab{from GR}, 
-we inject \sout{simulated} \ab{synthetic} GW signals which are identical to 
-the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose \sout{systems with initial-}binary-parameters
-similar to GW150914 and GW190521 (as given in Table XXX), but 
-\sout{we attach a phenomenological post-merger signal described by deviation parameters} 
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
-  done. AB: I would show results that include the $10\%$ case, which is more realistic, 
-based on QNM predictions in theories of gravity alternative to GR.}. 
-In other words, we assume that the frequency and damping time
-of our non-GR signal is 1.5 times the corresponding GR prediction,
-although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform} 
-we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl 
-you just clearly refer to thePlease introduce the injected signal and the template, which is used 
-to recover it, and simply say that they belong to the same waweform model.} 
-We also avoid waveform \sout{and noise} systematic biases by choosing 
-a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We 
-summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we 
-show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
-$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding 
-values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when 
-explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal 
-is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
-
-We additionally investigate the effects of erroneously assuming that
-\sout{an underlying modified} \ab{a non-GR} signal can be well-described 
-\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR} 
-signals using the GR waveform model $\SEOB$ instead of the parameterized 
-$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.} 
-In such cases, we run the risk of biased parameter estimates due to an
-incomplete understanding of the underlying signal. The resulting
-posterior probability distributions are shown in the right panels of
-Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue 
-(GW190521-like) curves.} The results are interesting and distinctly
-different for the two events. For the GW150914-like \comment{AB: I would avoid using 
-``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
-(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
-deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
-the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working 
-in Gaussian noise, so why are you referring to the noise as the culprit or the 
-source of difference?} The fact that the GW190521-like signal has a much
-lower SNR than GW150914-like signal might be a possible reason for the 
-measurement of the final quantities to be more susceptible to noise. A
-more detailed comparison of the other parameters, like the masses and
-spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
-signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please 
-comment the figures. What are the main results? What do we deduce?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-	\caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
-	\label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-	\caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please 
-switch the red and blue colors.
-The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
-Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-	\caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
-\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
-(obtained by inverting the Berti fits).
-\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
-Also please specify if the remnant mass is the detector-frame mass.
-Please
-switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
-	\label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{} 
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166), 
-\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}). 
-We choose an asymmetric system to increase the SNR in the higher modes. 
-We also \sout{rescale} \ab{choose} the distance and orientation of the binary 
-such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of 
-the three detectors, LIGO Hanford, Livingston and
-Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
-asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible at design sensitivities. Using this
-signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
-$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize 
-our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
-
-The fractional deviations in the estimates of the damping time and
-frequency of either mode is expected to be consistent with 0, as we
-indeed find in the left panel of
-Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
-quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
-\taungr{330})$ are also consistent with the corresponding predictions
-for a BBH merger in GR. As a consequence, the information from these
-two independent measures correspond to a unique remnant object, which
-is completely described by its mass and spin angular momentum
-\abhi{have the mf-af plot as well as a third panel to show
-  consistency}. For most of the events observed so far, the power in
-the $(3,\pm 3)$ has not been sufficient to measure it along with the
-$(2,\pm 2)$, or in fact, in its place. However, it might also be
-possible to combine information from multiple observation\sout{, as is
-likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
-detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}	
-	\caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
-The plus signs mark the GR predictions.}
-	\label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
-
-\comment{AB: This is the most important section in the paper, because it contains the 
-main results of the paper, i.e., the constraints on QNMs using real data. It needs to 
-be expanded and results would need to be highlighted much better than in the current version. 
-I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors 
-that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have 
-a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the 
-TGR GWTC-2, but for the 22 QNM frequencies for the different GW events. 
-Figures can be used in talks, and can capture the information much better 
-than a list of numbers in a Table.}
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results \sout{of this test} for all events observed
-during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
-total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
-signal} before and after the signal reaches \ab{the} peak\ab{'s} 
-amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the} 
-likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
-\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the 
-entire paper, except perhaps the Conclusions section.} 
-For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
-threshold and restrict\sout{ed} ourselves to the highest-mass events which
-\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
-since our method relies on doing a parameter estimation on the entire
-inspiral-merger-ringdown signal, we require the SNR to be beyond a
-certain threshold throughout the signal for reliable parameter
-estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters, 
-there are the component masses of the holes in the binary, and the 
-mass of the remnant formed after merger.} In fact the SNR
-threshold alone should be sufficient for the analysis, and for this
-paper we have relaxed the mass threshold. This has added two events,
-GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
-  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
-events along with GW190519$\_$153544, GW190521$\_$074359,
-GW190910$\_$112807. \comment{AB: Please improve the above paragraph 
-and make it clearer which choice is made for the SNR threshold and 
-masses, and why.}
-
-\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to 
-measure the QNMs to} \sout{present results on} the relevant
-GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same thresholds as above, we find three
-additional events that could be included in the analysis: GW150914,
-GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
-merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
-reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
-which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
-  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $pSEOB$ test, as well.} Among all the GW signals detected so far,
-GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what 
-is the ``clarity'' of a signal?} leading to the
-first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
-	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
-	\label{fig:o1o2_events}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, if we assume that the fractional deviations $(\df{220},
-\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. 
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis 
-if we want to include that analysis. AB: we want to include that analysis.}
-
-\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the 
-hierarchically combined methods.}
-
-\begin{table}
-\begin{flushleft}
-\begin{tabular}{llllllll}
-\toprule
-Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
-& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\hline
-& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
-\hline
-
-GW150914 &
-$249^{+9}_{-7}$ &
-$-$ &
-\hphantom{X} &
-$4.1^{+0.3}_{-0.2}$ &
-$-$
-\\[0.075cm]
-
-GW170104 &
-$286^{+16}_{-27}$ &
-$-$ &
-\hphantom{X} &
-$3.5^{+0.4}_{-0.3}$ &
-$-$
-\\[0.075cm]
-
-GW170729 &
-$161^{+13}_{-14}$ &
-$-$ &
-\hphantom{X} &
-$7.8^{+1.8}_{-1.5}$ &
-$-$
-\\[0.075cm]
-
-GW190630$\_$185205 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-
-GW190828$\_$063405 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-\hline
-\bottomrule
-\end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table 
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
-\label{tab:qnm_o1o2_results}
-\end{flushleft}
-\end{table}
-
-\section{Discussion}\label{sec:discussion}
-
-\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers 
-about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also 
-EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al. 
-It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with 
-Richard and Vivien.}
-
+%%%%%%%%%%%%%%%%%
 \section*{Acknowledgements}
 \label{sec:acknowledgements}
-LIGO Clusters. \comment{AB: Our cluster!!!}
-R.B.
-acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862.
-This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
+\input{acknowledgements}
+%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%
 \appendix
-
-\section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
-
-\comment{AB: Please improve considerably this Appendix because it is not easy to follow the motivation and the logic. It is written for LIGO people. 
-I have tried to make changes but it is better if you do it. I risk to erase parts that you would consider important. Please write it thinking that your 
-reader is not an LSC reader!}
-
-In Sec.~\ref{sec:method}, we \ab{discussed} \sout{mentioned that} the expression of the
-Bayesian likelihood function \ab{that we use in our analysis} \sout{outlined in} \ab{(see 
-Eq.~\ref{eq:likelihood})} \ab{and stressed that it}\sout{and \ref{eq:nwip}} is only valid if the interferometric noise can be
-described as a stationary Gaussian process. LIGO-Virgo noise, however,
-frequently has non-stationary and/or non-Gaussian features, for
-example glitches, which can affect parameter inferences unless
-appropriately accounted for. Here we demonstrate\ab{, by injecting in real 
-noise a GW190521-like signal} \sout{with an example of a
-GW190521-like simulated signal}, \ab{how} systematic biases \ab{can originate} \sout{likely originating}
-from an incomplete understanding of the noise. \comment{AB: It is confusing to refer to ``systematic'' 
-biases for the noise, generally we refer to systematic biases for the waveform modeling. 
-In fact, below you also, somewhat suddenly, refer to (lack of) precession, as a possible source of systemtcis. 
-I would advice you to clarify from the beginning of this Appendix, what this study is about and what you intend to 
-do below.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
-	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ from simulations \comment{AB: I have changed this in other places.
-The word ``simulations'' is confusing, because we deal with a paper in which we also refer to NR simulations.
-I suggest to use ``injected synthetic signals'' instead} of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
-The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-For comparison, we also plot the 90 \% credible level for the actual event, GW190521.
-\comment{AB: For clarity, please indicate on the plot which waveform model is used to obtain such posteriors, as you did
-in the other plots of the paper. Also, please use something else instead of ``actual event'', which is confusing. The problem is 
-that the first two entries of the legend refer to the noise properties of the PE study done with an injected synthetic signal, whereas I believe ``actual event'' refers to ``real'' not injected signal
-and ``real noise''. All the entries in the legend need to be consistent with each other; you need to specify for each of them the ``signal'' and the ``noise''. I hope is clear what I am saying}}
-	\label{fig:21g_systematics}
-\end{center}	
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ab{The spinning, precessing NR-surrogate model \texttt{NRSur7dq4}, valid up to mass ratio 4, was employed 
-(together with the $\SEOB$ model) to analyze the GW190521 signal observed by the LIGO and Virgo detectors. 
-For the injected synthetic signal we use a \texttt{NRSur7dq4} waveform with parameters similar to the ones 
-recovered by this model on the actual GW190521 data (see Table I of Ref.~\cite{Abbott:2020tfl}).}  
-\ab{In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal 
-predicts for the $(2,2)$ frequency and damping time, and for comparison, we also 
-show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$. As seen in the plot, while 
-the measurement of the frequency is consistent with the prediction, we overestimate the damping time.} \comment{AB: it is not clear 
-to me what the figure shows. Is the black line the result when running $\pSEOB$ against real data or the 
-injection in realt data?}
-
-\comment{AB: What is the ``underlying'' NR signal? I think you are referring to the 
-injected signal. Also, until now you have not discussed precession. 
-} The underlying NR signal is expected to be precessing, and since the
-$\pSEOB$ model is built on an aligned-spin GR model, a lack of
-precession could bias measurements. We explore effects of possible
-waveform systematics by injecting the signal is coloured Gaussian
-noise. In this case, since the understanding of the noise realizations
-is complete, any measurement biases could only arise from incomplete
-understanding of the \sout{underlying} \ab{injected} signal. We find (grey curves in
-Fig.\ref{fig:21g_systematics}) our results to be consistent with the
-prediction thus ruling out a lack of precession to be a likely cause
-for the bias in the damping time measurement of the actual signal.
-
-We subsequently study the effects of possible noise systematics by
-injecting the same \texttt{NRSur7dq4} GW signal in different
-realizations of actual interferometric noise around the real event
-GW190521. Since the PSDs of the GW detectors are expected to vary over
-longer durations of time, we select 5 different noise realizations
-over a segment of 2.5 hours of coincident data in both the LIGO
-detectors centered at the time of the actual event. The noise
-properties in this chunk of data, and consequently for all 5 simulated
-signals, is expected to be the closest to that for the actual
-event. The results are indicated by \sout{pink} \ab{green} curves in
-Fig.~\ref{fig:21g_systematics}. \ab{As it can be seen from the figure,} 
-for 3 of the 5 noise realizations,
-corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we
-recover a damping time similar to the actual event, where $t_0$ is the
-GPS time of the actual event. For the other two noise realizations, we
-estimate the consistent damping time but an off-set frequency, while
-the fifth noise realization is consistent with both predictions. The
-SNR in the Livingston detector goes down by more than \ab{a factor} 3 in some
-runs, indicative of how a variation in the noise strongly affects our
-ability to infer parameters. This also seems to indicate that a bias
-in the measurements of the damping time for the actual event \comment{AB: not clear 
-what you mean} can be unaccounted noise systematics.
+\input{appendix}
 

### 2021-01-25 papers/intro_paper/model_method.tex
divided up paper into input segments

A GW signal from the (quasi-circular) coalescence of two BHs is
completely described in GR by a $15$ parameters,
$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
objects in the binary; and the
\emph{extrinsic} parameters: a reference time $t_c$ and phase
$\phi_c$, the sky position of the binary ($\alpha$,
$\delta$), the luminosity distance, $d_L$, and the binary's orientation
described through the inclination of the binary $\iota$ and its
polarization $\psi$. We also introduce the total mass $M = m_1+m_2$,
and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.

Here, we focus on BHs with spins aligned or anti-aligned
with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,
the GW signal depends on $11$ parameters. We denote the
aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.

\subsection{Parameterized waveform model}\label{sec:model}

As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB)
formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms,
here we use as our baseline model the aligned-spin multipolar waveform model
developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
calibrated to NR simulations, this model also uses information from BH
perturbation theory for the merger and ringdown phases. Henceforth we
will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this
waveform model is called {\tt SEOBNRv4HM}.}.

In the observer's frame, the GW polarizations can be written as
%
\begin{equation}
h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
\end{equation}
%
where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics. The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}. For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
%
\begin{equation}
h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
\end{equation}
where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
%
\begin{equation}
\label{RD}
h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
\end{equation}
%
where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH. We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
%
\begin{equation}
\label{eq:ansatz_amp}
\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
\end{equation}
%
\begin{equation}
\label{eq:ansatz_phase}
\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
\end{equation}
%
where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$. The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$. This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
%
\begin{align}
\label{c1}
c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
    m} \nu} \big[ \partial_t|h_{\ell
    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
\label{c2}
c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
    m} \nu} \big[ \partial_t|h_{\ell
    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber
\end{align}
and $d_{1,c}^{\ell m}$ as
\begin{align}
\label{d1}
d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
\end{align}
%
where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode. The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.

In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
latter are related to the BBH's component masses and spins through
NR--fitting-formulas obtained in
GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
spirit of what was done in \paperone, we promote the QNM (complex)
frequencies to be free parameters of the model, while keeping the
inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
to their GR values. More explicitly, we introduce a parameterized
version of the $\SEOB$ model where the frequency and the
damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
_{\ell m 0})$) is defined through the fractional deviations, $(\delta
f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
\begin{eqnarray}
f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
\end{eqnarray}
We denote such a parameterized waveform model $\pSEOB$~\footnote{This
waveform model is called {\tt pSEOBNRv4HM} in LAL.}.

As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
constructed using the same NR--fitting--formula
described above. We note that when leaving $\sigma_{\ell m}$ to vary
freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
  m}(t)$ in general also differ from the GR predictions, since
those functions depend on the QNM complex frequencies, as can be seen
from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
(\ref{c2}), and (\ref{d1}).

\subsection{Bayesian parameter-estimation technique}
\label{sec:method}

The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$. One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
%
\begin{equation}
P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
\label{eq:Bayes_theorem}
\end{equation}
%
where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function. The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$. In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$. The likelihood function can consequently be defined as:
%
\begin{equation}
\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
\label{eq:likelihood}
\end{equation}
%
where $\langle . | . \rangle$ is the following noise-weighted inner product:
%
\begin{equation}
\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
\label{eq:nwip}
\end{equation}
%
The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation. The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector. We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}. Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}. For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.

Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:

\begin{equation}
P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
\end{equation}

For most of the results discussed in this paper, we restrict ourselves
to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH
events that we find most appropriate for this test, the LIGO-Virgo
observations are consistent with nearly--equal-mass face-on/off BBHs
for which power in the subdominant modes is not enough to
attempt to measure more than one QNM complex frequency.

Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
derived through NR--fits, from the corresponding priors on the initial
masses and spins, this leads to a non-trivial prior on the final
reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
  0})$. Also, given the definition of the damping time in
Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
to the imaginary part of the QNM complex frequency going to infinity. We avoid
this by restricting the minimum of the prior on $\delta \tau_{\ell m
  0}$ to be greater than $-1$.

\iffalse
\subsection{Priors}

Throughout our analysis we assume a completely prior uniform in the component masses $m_1, m_2$. Our prior on the spins are uniform in the magnitude between (0,1) and isotropic in spin orientation, but finally restricted to the component parallel to the orbital angular momentum of the binary. The prior on the distance varies as $d_L^2$ giving more weightage to binaries farther out. For the rest of the parameters we use standard priors as defined in the documentation (CITE Vietch et al. 2015 LALInference paper). For our non-GR ringdown parameters, we assume uniform priors. This of course leads to a non-trivial prior on the reconstructed frequency and damping time, because of the prior on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$, which itself depend on the prior on the initial masses and spins through NR fits \abhi{perhaps figure on priors on QNM quantities}. For $d\tau = -1$, we encounter a singularity (the imaginary part of the frequency goes to infinity), which we avoid by restricting the minimum of the prior on $d\tau$ to be greater than $-1$.
\fi

### 2021-01-25 papers/intro_paper/results_lvc.tex
divided up paper into input segments

\comment{AB: This is the most important section in the paper, because it contains the
main results of the paper, i.e., the constraints on QNMs using real data. It needs to
be expanded and results would need to be highlighted much better than in the current version.
I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors
that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have
a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the
TGR GWTC-2, but for the 22 QNM frequencies for the different GW events.
Figures can be used in talks, and can capture the information much better
than a list of numbers in a Table.}

The LIGO-Virgo Collaboration recently released their testing GR
catalogue containing results \sout{of this test} for all events observed
during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
post-merger regions $\geq 8$.The pre- and post-merger regions of the
signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
signal} before and after the signal reaches \ab{the} peak\ab{'s}
amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the}
likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the
entire paper, except perhaps the Conclusions section.}
For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
threshold and restrict\sout{ed} ourselves to the highest-mass events which
\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
since our method relies on doing a parameter estimation on the entire
inspiral-merger-ringdown signal, we require the SNR to be beyond a
certain threshold throughout the signal for reliable parameter
estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters,
there are the component masses of the holes in the binary, and the
mass of the remnant formed after merger.} In fact the SNR
threshold alone should be sufficient for the analysis, and for this
paper we have relaxed the mass threshold. This has added two events,
GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
events along with GW190519$\_$153544, GW190521$\_$074359,
GW190910$\_$112807. \comment{AB: Please improve the above paragraph
and make it clearer which choice is made for the SNR threshold and
masses, and why.}

\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to
measure the QNMs to} \sout{present results on} the relevant
GW events from LIGO-Virgo's O1 and O2 runs, alongside
the above events. Applying the same thresholds as above, we find three
additional events that could be included in the analysis: GW150914,
GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
merger-ringdown signal. For the three relevant signals, GW150914,
GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
  thresholds. The paper quotes them for the purpose of the IMR
  consistency test, but the same thresholds have been used for the
  $pSEOB$ test, as well.} Among all the GW signals detected so far,
GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what
is the ``clarity'' of a signal?} leading to the
first, and to date, best attempt in measuring the QNM frequencies~\cite{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% O1-O2 events
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
        \caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal. The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves. The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
        \label{fig:o1o2_events}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Finally, if we assume that the fractional deviations $(\df{220},
\dtau{220})$ take the same values in multiple events, we can assume
the posterior of one event to be the prior for the next, and obtain a
joint posterior probability distribution. For $N$ observations, where
$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
posterior is given by:
%
\begin{equation}
P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
\end{equation}
%
where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
\dtau{220})$. However, since we assume the prior on $(\df{220},
\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
the joint likelihood.

We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis
if we want to include that analysis. AB: we want to include that analysis.}

\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the
hierarchically combined methods.}

\begin{table}
\begin{flushleft}
\begin{tabular}{llllllll}
\toprule
Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
\hline
& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
\hline

GW150914 &
$249^{+9}_{-7}$ &
$-$ &
\hphantom{X} &
$4.1^{+0.3}_{-0.2}$ &
$-$
\\[0.075cm]

GW170104 &
$286^{+16}_{-27}$ &
$-$ &
\hphantom{X} &
$3.5^{+0.4}_{-0.3}$ &
$-$
\\[0.075cm]

GW170729 &
$161^{+13}_{-14}$ &
$-$ &
\hphantom{X} &
$7.8^{+1.8}_{-1.5}$ &
$-$
\\[0.075cm]

GW190630$\_$185205 &
$-$ &
$-$ &
\hphantom{X} &
$-$ &
$-$
\\[0.075cm]

GW190828$\_$063405 &
$-$ &
$-$ &
\hphantom{X} &
$-$ &
$-$
\\[0.075cm]
\hline
\bottomrule
\end{tabular}
\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table
also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
\label{tab:qnm_o1o2_results}
\end{flushleft}
\end{table}

### 2021-01-25 papers/intro_paper/results_synthetic.tex
divided up paper into input segments

\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}

\ab{We demonstrate our method using synthetic-signal injections describing GWs
from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and
Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.}
For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and
GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}.
These two binary systems are representative of the kind of systems for which
the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the
pre- and post-merger SNRs return reliable parameter-estimation results.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for Injections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c| }
 \hline
 Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\
 \hline
 GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
 GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\
 SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
 \hline
\end{tabular}
\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters
$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively. \comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages. The third row is completely ignored in the caption's explanations.}}
\label{tab:injection_values}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbt]
\begin{center}
        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}
        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}
        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}). The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. \comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
        \label{fig:simulated_signal_GR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ab{To avoid possible systematic biases in our parameter-estimation analysis
due to error in waveform modeling,} we use the GR version of the same waveform,
$\SEOB$ (without allowing for deviations in the QNM parameters) to
simulate our GW signal. And to avoid systematic biases due to noise,
we use an averaged (zero-noise) realization of the noise. A detailed
study on noise systematics for one of the GW events is presented in
Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context.
Why should the reader appreciate at this stage of the paper, where we have not yet
discussed results with real data, what is in the Appendix?} As in the case of the actual
detections, we consider a two-detector LIGO network at
Hanford and Livingston, having identical PSDs. The distance to the two
\ab{synthetic} events is rescaled such that the SNR in the detector network
is the same as the actual events (i.e., 24 for GW150914 and 14
for GW190521). Since mearly--equal-mass binaries like GW150914 and
GW190521 observed at moderately high SNRs are not expected to have a
loud ringdown signal, we restrict ourselves to estimating the
frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
their GR values.

We find, as one might expect, that the posterior distribution on the
parameters describing fractional deviations in the frequency and
damping time are consistent with zero (left panels of
Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
fractional quantities into absolute quantities using the relations
given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
construct posterior distributions on these effective quantities,
$(\fngr{220}, \taungr{220})$ (right panels of
Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
\ab{2D} posterior{\ab{s} are consistent with the GR predictions
(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring
to 1D and 2D posteriors when discussing the figures.}}

\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}

To demonstrate the robustness of the method in detecting possible
deviations \sout{of the underlying GW signal from predictions of} \ab{from GR},
we inject \sout{simulated} \ab{synthetic} GW signals which are identical to
the corresponding GR prediction up to merger, and differ in their post-merger
description. We again choose \sout{systems with initial-}binary-parameters
similar to GW150914 and GW190521 (as given in Table XXX), but
\sout{we attach a phenomenological post-merger signal described by deviation parameters}
\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
  done. AB: I would show results that include the $10\%$ case, which is more realistic,
based on QNM predictions in theories of gravity alternative to GR.}.
In other words, we assume that the frequency and damping time
of our non-GR signal is 1.5 times the corresponding GR prediction,
although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform}
we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl
you just clearly refer to thePlease introduce the injected signal and the template, which is used
to recover it, and simply say that they belong to the same waweform model.}
We also avoid waveform \sout{and noise} systematic biases by choosing
a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We
summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding
values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when
explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal
is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}

We additionally investigate the effects of erroneously assuming that
\sout{an underlying modified} \ab{a non-GR} signal can be well-described
\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR}
signals using the GR waveform model $\SEOB$ instead of the parameterized
$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.}
In such cases, we run the risk of biased parameter estimates due to an
incomplete understanding of the underlying signal. The resulting
posterior probability distributions are shown in the right panels of
Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue
(GW190521-like) curves.} The results are interesting and distinctly
different for the two events. For the GW150914-like \comment{AB: I would avoid using
``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
reported \emph{no} deviation from the GR prediction. However in the
case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
the non-GR signal would have yielded measurements distinctly
different from either of the two parameterized estimates: with and
without deviations. \comment{AB: Not clear to me the next sentence. We are working
in Gaussian noise, so why are you referring to the noise as the culprit or the
source of difference?} The fact that the GW190521-like signal has a much
lower SNR than GW150914-like signal might be a possible reason for the
measurement of the final quantities to be more susceptible to noise. A
more detailed comparison of the other parameters, like the masses and
spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please
comment the figures. What are the main results? What do we deduce?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
        \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$). Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal. \comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
        \label{fig:nongr_waveform}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Simulated siganl: non-GR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$. The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels. The black vertical and horizontal lines mark the injection values. In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please
switch the red and blue colors. The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots. Please indicate on the figures: GW150914-like and GW190521-like.}}
        \label{fig:simulated_signal_nonGR}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% modified GR signal: GR vs nonGR recovery comparison
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}%[h!]
        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}
        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
        \caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}. \sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
(obtained by inverting the Berti fits). \comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption. Also please specify if the remnant mass is the detector-frame mass. Please
switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
        \label{fig:gr_ngr_comparison}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}

Finally, we provide a simple demonstration of a test of the no-hair
theorem using our model. As described in the introduction, any test of
the no-hair theorem of BHs would need to involve independent
measurements of (at least) two different QNMs.

\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{}
corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166),
\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
We choose an asymmetric system to increase the SNR in the higher modes.
We also \sout{rescale} \ab{choose} the distance and orientation of the binary
such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of
the three detectors, LIGO Hanford, Livingston and
Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
asymmetric and loud signals are no longer just a theoretical
prediction, but quite plausible at design sensitivities. Using this
signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize
our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}

The fractional deviations in the estimates of the damping time and
frequency of either mode is expected to be consistent with 0, as we
indeed find in the left panel of
Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
\taungr{330})$ are also consistent with the corresponding predictions
for a BBH merger in GR. As a consequence, the information from these
two independent measures correspond to a unique remnant object, which
is completely described by its mass and spin angular momentum
\abhi{have the mf-af plot as well as a third panel to show
  consistency}. For most of the events observed so far, the power in
the $(3,\pm 3)$ has not been sufficient to measure it along with the
$(2,\pm 2)$, or in fact, in its place. However, it might also be
possible to combine information from multiple observation\sout{, as is
likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
other sub-dominant QNMs~\cite{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
        \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
        \caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}. The plus signs mark the GR predictions.}
        \label{fig:nohair_sxs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-25 papers/intro_paper/results_synthetic.tex
updated results_synthetic section

@@
-\subsection{\ab{Simulations using GR signals in Gaussian noise}} \label{ssec:gr_signal}
+\subsection{Simulations using GR signals in Gaussian noise} \label{ssec:gr_signal}
 
-\ab{We demonstrate our method using synthetic-signal injections describing GWs
+We demonstrate our method using synthetic-signal injections describing GWs
 from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and
-Virgo detectors at design sensitivities~\cite{}. \comment{AB: Please cite which PSD you used.}
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{} and
-GW190521~\cite{}. We list them in Table~\ref{tab:injection_values}.
+Virgo detectors at design sensitivities~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
+For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
+GW190521~\cite{Abbott:2020tfl}. We list them in Table~\ref{tab:injection_values}.
 These two binary systems are representative of the kind of systems for which
 the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the
-pre- and post-merger SNRs return reliable parameter-estimation results.}
+pre- and post-merger SNRs return reliable parameter-estimation results.
 

### 2021-01-27 papers/intro_paper/results_lvc.tex
updated results section

@@
 
-\begin{table}
-\begin{flushleft}
-\begin{tabular}{llllllll}
-\toprule
-Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
-& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
-\hline
-& IMR  & \pSEOB & \hphantom{X} & IMR  & \pSEOB \\
-\hline
-
-GW150914 &
-$249^{+9}_{-7}$ &
-$-$ &
-\hphantom{X} &
-$4.1^{+0.3}_{-0.2}$ &
-$-$
-\\[0.075cm]
-
-GW170104 &
-$286^{+16}_{-27}$ &
-$-$ &
-\hphantom{X} &
-$3.5^{+0.4}_{-0.3}$ &
-$-$
-\\[0.075cm]
-
-GW170729 &
-$161^{+13}_{-14}$ &
-$-$ &
-\hphantom{X} &
-$7.8^{+1.8}_{-1.5}$ &
-$-$
-\\[0.075cm]
-
-GW190630$\_$185205 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-
-GW190828$\_$063405 &
-$-$ &
-$-$ &
-\hphantom{X} &
-$-$ &
-$-$
-\\[0.075cm]
-\hline
-\bottomrule
-\end{tabular}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
-\label{tab:qnm_o1o2_results}
-\end{flushleft}
-\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Table for LVC values
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{table_lvc_results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-27 papers/intro_paper/results_synthetic.tex
updated results section

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c| }
- \hline
- Event & $m_{\rm 1,det} (\Mo)$ &  $m_{\rm 2,det} (\Mo)$ & $\chi_{1}$ & $\chi_{2}$ & SNR \\
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 \\
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 \\
- \hline
-\end{tabular}
-\caption{\ab{Parameters of the synthetic-signal injections}, chosen to be similar to the actual GW events indicated in the first column. The parameters
-$(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-\comment{AB: I would suggest to give in the Table also the SNR in the pre- and post-merger stages.
-The third row is completely ignored in the caption's explanations.}}
-\label{tab:injection_values}
-\end{center}
-\end{table}
+\input{table_injection_values}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-27 papers/intro_paper/table_injection_values.tex
updated results section

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c| }
 \hline
 Event & \makecell{$m_{\rm 1,det}$ \\ $(\Mo)$} &  \makecell{$m_{\rm 2,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & SNR & \makecell{SNR \\ (pre-merger)} & \makecell{SNR \\(post-merger)} \\
 \hline
 GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 & XX & XX \\
 GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 & XX & XX \\
 SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 & XX & XX \\
 \hline
\end{tabular}
\caption{Parameters of the synthetic-signal injections, chosen to be similar to the actual GW events indicated in the first column (first two rows). The parameters $(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively. The third row indicates the parameters of the SXS BBH waveform used in Sec.~\ref{ssec:nohairtheorem}. \abhi{Fill in values; define pre/post-merger somewhere in the text}}
\label{tab:injection_values}
\end{center}
\end{table}

### 2021-01-27 papers/intro_paper/discussion.tex
add sometext to conclusions and update bib

@@
 Richard and Vivien.}
+
+\rb{Work in progress (most of this was taken from \paperone}
+We investigated the advantages of using IMR waveforms, with respect to 
+damped-sinusoid models, to measure ringdown frequencies and damping times in the post-merger 
+signal of a compact-object coalescence. To address this goal, we built a parameterized multipolar IMR waveform model within 
+the EOB formalism (pEOBNR), and investigated its ability in measuring the QNM complex frequencies in GW150914, and 
+in several synthetic GW signals injected in Gaussian noise.
+
+We found the following important advantages: (i) using an IMR model, 
+calibrated to NR waveforms, one does not need to define an \emph{a priori} unknown starting time at
+which the signal can be described as a sum of exponentially damped
+sinusoids~\cite{Gossan:2011ha,Meidam:2014jpa,Cabero:2017avf,Bhagwat:2017tkm,Baibhav:2017jhs,London:2018gaq}, therefore avoiding potential biases due to a non-optimal
+choice of the ringdown starting time~\cite{Thrane:2017lqn}; (ii) the IMR model avoids technical
+issues inherent to assuming a waveform with a cutoff at a particular
+time, namely the need to know in advance the sky position and time at
+coalescence~\cite{TheLIGOScientific:2016src,Cabero:2017avf}; (iii) the IMR model naturally includes important physics,
+such as phase shifts between different modes, their relative
+amplitudes and the presence of overtones~\cite{Buonanno:2006ui,Pan:2011gk}; and (iv) the IMR model
+generically leads to stronger constraints on the QNM frequencies
+compared to what can be achieved with a damped-sinusoid model.
+
+The approach that we here presented should also be seen as
+complementary to previous works on the subject. Besides directly
+measuring the ringdown frequencies, our IMR model 
+can also be used to validate the results obtained with the more agnostic
+damped-sinusoid models. In particular, as we showed, the pEOBNR model already
+provides very interesting constraints on the frequency and damping time of the dominant QNM of GW150914~\cite{Abbott:2016blz}.
+
+This work can be improved in several fronts... The IMR model here presented could also be
+extended to allow GR deviations in the inspiral phase.
+
+QNM frequencies of spherically symmetric solutions were computed in theories such as
+Einstein-Maxwell-dilaton~\cite{Ferrari:2000ep}, dynamical
+Chern-Simons gravity~\cite{Molina:2010fb}, Einstein-dilaton-Gauss-Bonnet
+gravity~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk}
+and for some solutions in massive
+(bi)gravity~\cite{Brito:2013wya,Brito:2013yxa,Babichev:2015zub}. On
+the other hand, not much progress has been made to compute QNMs for
+spinning BHs in alternative theories to GR, the only exception
+being the Kerr-Newman case in Einstein-Maxwell
+theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa}. Most
+of the estimates for QNMs of spinning BHs in modified gravity have
+instead used the connection between the light ring and
+QNMs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo,Glampedakis:2017cgd},
+which is formally only valid in the eikonal $\ell \to \infty$ limit
+and known to fail to describe some families of QNMs when additional
+degrees of freedom are present~\cite{Blazquez-Salcedo:2016enn}.

### 2021-01-28 papers/intro_paper/results_synthetic.tex
updated synthetic results section

@@
 
-\comment{AB: Nothing is said in the text and the caption of the Table about the third mock signal in the Table!}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-\comment{AB: Please indicate on the figures: GW150914-like and GW190521-like.} \comment{AB: Please be consistent and use the label pSEOBNR, as in the text, instead of pSEOB.}}
+The black vertical and horizontal lines mark the injection values.}
         \label{fig:simulated_signal_GR}
@@
 
-\ab{To avoid possible systematic biases in our parameter-estimation analysis
-due to error in waveform modeling,} we use the GR version of the same waveform,
+To avoid possible systematic biases in our parameter-estimation analysis
+due to error in waveform modeling, we use the GR version of the same waveform,
 $\SEOB$ (without allowing for deviations in the QNM parameters) to
 simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. A detailed
+we use an averaged (zero-noise) realization of the noise. \footnote{A detailed
 study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}. \comment{AB: This reference to the Appendix is out of context.
-Why should the reader appreciate at this stage of the paper, where we have not yet
-discussed results with real data, what is in the Appendix?} As in the case of the actual
+Appendix~\ref{sec:noise_systematics}.}  As in the case of the actual
 detections, we consider a two-detector LIGO network at
 Hanford and Livingston, having identical PSDs. The distance to the two 
-\ab{synthetic} events is rescaled such that the SNR in the detector network
+synthetic events is rescaled such that the SNR in the detector network
 is the same as the actual events (i.e., 24 for GW150914 and 14
@@
 loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of \ab{only one QNM} $(\ell m) = (2,2)$, i.e.,
+frequency and damping time of only one QNM $(\ell m) = (2,2)$, i.e.,
 $\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
@@
 Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-\ab{2D} posterior{\ab{s} are consistent with the GR predictions
-(black \sout{solid lines} \ab{dot}). \comment{AB: please be precise in referring
-to 1D and 2D posteriors when discussing the figures.}}
+two-dimensional posteriors are consistent with the GR predictions
+(black dashed lines).
 
-\subsection{\ab{Simulations using non-GR signals in Gaussian noise}} \label{ssec:ngr_signal}
+\subsection{Simulations using non-GR signals in Gaussian noise} \label{ssec:ngr_signal}
 
 To demonstrate the robustness of the method in detecting possible
-deviations \sout{of the underlying GW signal from predictions of} \ab{from GR},
-we inject \sout{simulated} \ab{synthetic} GW signals which are identical to
+deviations from GR, we inject synthetic GW signals which are identical to
 the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose \sout{systems with initial-}binary-parameters
-similar to GW150914 and GW190521 (as given in Table XXX), but
-\sout{we attach a phenomenological post-merger signal described by deviation parameters}
-\ab{set} $\df{220} = \dtau{220} = 0.5$ \comment{AG: deviations=0.1 runs are ongoing and almost
-  done. AB: I would show results that include the $10\%$ case, which is more realistic,
-based on QNM predictions in theories of gravity alternative to GR.}.
+description. We again choose binary-parameters
+similar to GW150914 and GW190521 (as given in Table ~\ref{tab:injection_values}), but
+set $\df{220} = \dtau{220} = 0.1 $.
 In other words, we assume that the frequency and damping time
-of our non-GR signal is 1.5 times the corresponding GR prediction,
-although the pre-merger signal is identical to GR. \ab{In Fig.~\ref{fig:nongr_waveform}
-we show ...}  \comment{AB: Not clear to me what the next sentence says. Coudl
-you just clearly refer to thePlease introduce the injected signal and the template, which is used
-to recover it, and simply say that they belong to the same waweform model.}
-We also avoid waveform \sout{and noise} systematic biases by choosing
-a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. \ab{We
-summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
+of our non-GR signal is 10\% more than the corresponding GR prediction,
+although the pre-merger signal is identical to GR. In Fig.~\ref{fig:nongr_waveform}
+we show this non-GR waveform, \texttt{pSEOBNR} with respect to the 
+original GR template, \texttt{SEOBNR}. We see that the waveforms are identical in amplitude
+and instanteneous frequency upto the merger (lower panel) , beyond which the 
+red (GR template) and blue (non-GR template) diverge. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
 show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
 $(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding
-values of the injection parameters, indicated by the black solid lines.} \comment{AB: Please be more quantitative when
-explaining the results in the figure. Which black lines are you referring to? In the main 2-D figure the injected signal
-is a point not a line. I think you are referring to the 1D posteriors, but it needs to be explained.}
+values of the injection parameters, indicated by the black dashed lines.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
+        \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
+Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
+        \label{fig:nongr_waveform}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Simulated siganl: non-GR
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+\begin{center}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
+        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
+The non-GR signal has a deviation, $\df{220} = \dtau{220} = XX$.
+The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
+The black vertical and horizontal lines mark the injection values.
+In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
+GW150914-like (upper panel) and GW190521-like (lower panel) injections. The measurements with $\SEOB$ waveforms are visibly biased.}
+        \label{fig:simulated_signal_nonGR}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 We additionally investigate the effects of erroneously assuming that
-\sout{an underlying modified} \ab{a non-GR} signal can be well-described
-\ab{by a GR one}. We do this by estimating the parameters of our \ab{non-GR}
-signals using the GR waveform model $\SEOB$ instead of the parameterized
-$\pSEOB$. \comment{AB: Not clear what the next senetnce wants to say.}
-In such cases, we run the risk of biased parameter estimates due to an
-incomplete understanding of the underlying signal. The resulting
-posterior probability distributions are shown in the right panels of
-Fig.~\ref{fig:simulated_signal_nonGR} by the \ab{red (GW150914-like) and blue
-(GW190521-like) curves.} The results are interesting and distinctly
-different for the two events. For the GW150914-like \comment{AB: I would avoid using
-``modified'' GR, but istsead non-GR.} \ab{non-GR} signal, the measurements of $(\fgr{220}, \taugr{220})$
-(see top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fgr{220}, \taugr{220})$ measurements for a signal with no
-deviations from GR (see top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations \ab{from GR} as large as the $50\%$ \sout{of
-the GR prediction}, the analysis with \ab{the GR signal} $\SEOB$ would likely have
+an underlying non-GR signal can be well-described
+by a GR one. We do this by estimating the parameters of our non-GR
+signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
+The resulting one- and two-dimensional posteriors are shown in the right panels of Fig.~\ref{fig:simulated_signal_nonGR} by red curves for the GW150914-like (top) and GW190521-like (bottom) signals respectively.
+For both signals, we find the $\SEOB$ estimates are markedly biased with respect to the $\pSEOB$ estimates.
+This can be explained by the inability of the $\SEOB$ template waveform to capture all the physics in the $\pSEOB$ signal.
+We also notice that the results are distinctly
+different for the two events. For the GW150914-like non-GR signal, the measurements of $(\fgr{220}, \taugr{220})$
+(top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
+with the $(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no
+deviations} from GR (top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
+words, if the actual signal had deviations from GR as large as the $10\%$, the analysis with the GR signal $\SEOB$ would likely have
 reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like \ab{non-GR} signal, a simple GR analysis of
+case of the GW190521-like non-GR signal, a simple GR analysis of
 the non-GR signal would have yielded measurements distinctly
@@
 comment the figures. What are the main results? What do we deduce?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-        \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR \sout{(solid orange lines)} (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified \sout{(dashed grey lines)} (i.e., $\df{220} = \dtau{220} = 0.5$).
-Bottom panel: Comparison of the evolution of the amplitude (left) and instantaneous frequency (right) for the GR and \sout{modified} \ab{non-GR} signal.
-\comment{AB: Please remove ``Amplitudes'' and ``Instantaneous Frequency'' from the $y$-axis labels, but instead provide explanations in the caption, and use only $f(t)$ as label.}}
-        \label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fngrtaungr.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for \sout{modGR} \ab{non-GR} injections with \sout{initia}l parameters \sout{similar to} \ab{of GW150914-like} (top panels) and \ab{GW190521-like} (bottom panels) \ab{as given in Table~\ref{tab:injection_values}.} The \sout{underlying} \ab{non-GR} signal has a deviation, $\df{220} = \dtau{220} = XX$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like \sout{(grey)} \ab{(upper panel)} and GW190521-like \sout{(pink)} \ab{(lower panel) injections}. The measurements \ab{with $\SEOB$ waveforms} are visibly biased. \comment{AB: please
-switch the red and blue colors.
-The blue colors should always refer to the same waveform model, which is shown in the left panels, otherwise it is very confusing to understand those plots.
-Please indicate on the figures: GW150914-like and GW190521-like.}}
-        \label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\ab{Here, we} use a \sout{simulated} NR GW signal from the SXS catalog~\cite{}
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166),
-\sout{rescaled to a} total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
+Here, we use an NR GW signal from the SXS catalog~\cite{Mroue:2013xna}
+corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166) and 
+total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
 We choose an asymmetric system to increase the SNR in the higher modes.
-We also \sout{rescale} \ab{choose} the distance and orientation of the binary
-such that the total SNR \sout{of the signal} in \sout{a} \ab{the} network of
-the three detectors, LIGO Hanford, Livingston and
-Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such
-asymmetric and loud signals are no longer just a theoretical
+We also choose the distance and orientation of the binary
+such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
+Virgo, is \macro{$\sim$ 70}. Based on the LIGO-Virgo observations during during the first three observing runs, 
+such asymmetric and loud signals are no longer just a theoretical
 prediction, but quite plausible at design sensitivities. Using this
-signal, we attempt to measure \ab{both} the \sout{QNM frequencies} $(2,\pm 2)$ and
-$(3,\pm 3)$ \sout{modes} \ab{QNMs} \sout{together}. \ab{We summarize
-our results in Fig.~\ref{fig:nohair_sxs}. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.} \sout{less for us to estimate them reliably.}
+signal, we attempt to measure both the $(2,\pm 2)$ and
+$(3,\pm 3)$ QNMs. For this injected signal the SNR in
+other sub-dominant modes is too low to be able to measure them.
 
-The fractional deviations in the estimates of the damping time and
-frequency of either mode is expected to be consistent with 0, as we
-indeed find in the left panel of
-Fig.~\ref{fig:nohair_sxs}. Consequently we find that the reconstructed
-quantities $(\fngr{220}, \taungr{220})$ and $(\fngr{330},
-\taungr{330})$ are also consistent with the corresponding predictions
-for a BBH merger in GR. As a consequence, the information from these
-two independent measures correspond to a unique remnant object, which
-is completely described by its mass and spin angular momentum
-\abhi{have the mf-af plot as well as a third panel to show
-  consistency}. For most of the events observed so far, the power in
-the $(3,\pm 3)$ has not been sufficient to measure it along with the
-$(2,\pm 2)$, or in fact, in its place. However, it might also be
-possible to combine information from multiple observation\sout{, as is
-likely} over the coming few years \sout{of GW astronomy with the LIGO-Virgo
-detectors,} to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs~\cite{}.
+We summarize our results in Fig.~\ref{fig:nohair_sxs}.
+Given the injection parameters, the predicted values of the $(2,\pm 2)$ and $(3,\pm 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68 ms)}  and \macro{(271.21 Hz, 4.50 ms)} respectively.
+The left panel of Fig.~\ref{fig:nohair_sxs} shows that the two-dimensional posteriors on the $(2,\pm 2)$ and $(3,\pm 3)$ QNMs are consistent with the predictions for a BBH merger in GR, indicated by the black plus sign.
+Using fitting formulae provided in ~\cite{Berti:2005ys}, specifically,  Eqs.
+2.1, E1, E3 and tables VIII and IX for the fitting coefficients, we infer the two-dimensional posterior probability distirbution on the final mass and spin for the $(2,\pm 2)$ (blue) and $(3,\pm 3)$ (red) QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}.
+The two independent estimates are consistent with each other and correspond to a unique mass and spin for the remnant BH \macro{(83.08 $\Mo$, 0.37)} indicated by the plus sign.
+As a consequence, this may be considered as a test of the no-hair conjecture.
+For most of the events observed so far, the power in the $(3,\pm 3)$ has not been sufficient to measure it along with the $(2,\pm 2)$, or in fact, in its place.
+However, it might also be possible to combine information from multiple observation over the coming few years to obtain meaningful constraints on the $(3,\pm 3)$ and
+other sub-dominant QNMs.
 
@@
         \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
-        \caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) \ab{QNM,} respectively, \sout{for a numerical relativity signal corresponding to a BBH merger of} \ab{when a NR signal with parameters} $q=6$,  $M=84 \Mo$ and SNR $=75$ \ab{is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model}.
+        \caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) QNM, respectively, when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
 The plus signs mark the GR predictions.}

### 2021-01-28 papers/intro_paper/table_injection_values.tex
updated synthetic results section

@@
 \begin{center}
-\begin{tabular}{ |c|c|c|c|c|c|c|c| }
+\begin{tabular}{ c|c|c|c|c|c|c|c }
+
+ Event & \makecell{$m_{\rm 1,det}$ \\ $(\Mo)$} &  \makecell{$m_{\rm 2,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
  \hline
- Event & \makecell{$m_{\rm 1,det}$ \\ $(\Mo)$} &  \makecell{$m_{\rm 2,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & SNR & \makecell{SNR \\ (pre-merger)} & \makecell{SNR \\(post-merger)} \\
- \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 & XX & XX \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 14 & XX & XX \\
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 75 & XX & XX \\
- \hline
+ GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 & 22 & 12 \\
+ GW190521-like & 150 & 120 & 0.02 & -0.39 & 20 & 8 & 18 \\
+ SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 71 & 58 & 41 \\
+
 \end{tabular}
@@
 The third row indicates the parameters of the SXS BBH waveform used in Sec.~\ref{ssec:nohairtheorem}.
-\abhi{Fill in values; define pre/post-merger somewhere in the text}}
+$\rho_\text{IMR}$, $\rho_\text{insp}$ and $\rho_\text{postinsp}$ are the SNR of the full IMR signal, SNR upto a certain cutoff frequency, and SNR after the cutoff frequency respectively.
+The cutoff frequency is assumed to be the frequency at the innermost circular stable orbit (ISCO) corresponding to the remnant Kerr black hole in each case.}
 \label{tab:injection_values}

### 2021-01-28 papers/intro_paper/results_synthetic.tex
updated paper

@@
 
+\abhi{Divided up this section into three clear indepenent segments. each segment has a plot associated with it.}
+
+\abhi{segment 1: discuss the recovery of nonGR signals to establish the robustness of the pipeline}
+
 To demonstrate the robustness of the method in detecting possible
@@
 
-We additionally investigate the effects of erroneously assuming that
-an underlying non-GR signal can be well-described
-by a GR one. We do this by estimating the parameters of our non-GR
-signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
+\abhi{segment 2: discuss possible systematics by recoving a nonGR signal using a GR template}
+We additionally investigate the effects of erroneously assuming that an underlying non-GR signal can be well-described
+by a GR one.
+We do this by estimating the parameters of our non-GR signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
 The resulting one- and two-dimensional posteriors are shown in the right panels of Fig.~\ref{fig:simulated_signal_nonGR} by red curves for the GW150914-like (top) and GW190521-like (bottom) signals respectively.
@@
 This can be explained by the inability of the $\SEOB$ template waveform to capture all the physics in the $\pSEOB$ signal.
-We also notice that the results are distinctly
-different for the two events. For the GW150914-like non-GR signal, the measurements of $(\fgr{220}, \taugr{220})$
-(top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no
-deviations} from GR (top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations from GR as large as the $10\%$, the analysis with the GR signal $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like non-GR signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working
+We also notice that the results are distinctly different for the two events.
+For the GW150914-like non-GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent with the $(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no deviations} from GR (top right panel in Fig.~\ref{fig:simulated_signal_GR}).
+In other words, if the actual signal had deviations from GR as large as the $10\%$, the analysis with the GR signal $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
+However in the case of the GW190521-like non-GR signal, a simple GR analysis of the non-GR signal would have yielded measurements distinctly different from either of the two parameterized estimates: with and without deviations.
+
+\abhi{segment 3: discuss possible correlations between GR and nonGR quantities as you increase deviation. Also discuss the SNRs recovered}.
+Finally, we investigate the impact on the estimation of GR parameters discussed in Sec.~\ref{sec:method}, $\bxigr$  as we change the magnitude of deviation in the non-GR parameters.
+For comparison, we also consider a synthetic signal with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, along with the 10\% non-GR signal and a signal with no deviation (essentially GR) mentioned above.
+
+\comment{AB: Not clear to me the next sentence. We are working
 in Gaussian noise, so why are you referring to the noise as the culprit or the
@@
 \begin{figure*}%[h!]
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fngrtaungr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_0p1_0p5_gr_fngrtaungr.png}
         \caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.

### 2021-01-28 papers/intro_paper/results_lvc.tex
started to go through LVC results section

@@
 
-\ab{Furthermore}, for the first time, in this paper, we \ab{apply our method to
-measure the QNMs to} \sout{present results on} the relevant
+Furthermore, for the first time, in this paper, we apply our method to
+measure the QNMs to the relevant
 GW events from LIGO-Virgo's O1 and O2 runs, alongside
@@
 merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we \sout{provide} \ab{show} the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also
-reconstruct the \sout{effective} QNM parameters, $(\fngr{220}, \taungr{220})$
+GW170104 and GW170729, we show the posterior distributions in
+$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also reconstruct the QNM parameters, $(\fngr{220}, \taungr{220})$
 which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
@@
   consistency test, but the same thresholds have been used for the
-  $pSEOB$ test, as well.} Among all the GW signals detected so far,
+  $\pSEOB$ test, as well.} Among all the GW signals detected so far,
 GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, \sout{mass as well as the clarity of the signal,} \comment{AB: what
-is the ``clarity'' of a signal?} leading to the
-first, and to date, best attempt in measuring the QNM frequencies~\cite{}.
+loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{LSC_2016grtests,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
 

### 2021-01-28 papers/intro_paper/results_synthetic.tex
updated results synthetic section

--- 2021-01-28 papers/intro_paper/results_synthetic.tex
@@
 
+\abhi{I have slightly modified this subsection. I have divided up the three main results we want to show here:\\
+1. the robustness of the pipeline to detect devations. This segment includes the 10\% deviation results.\\
+2. the systematic biases if one uses a GR template to measure a nonGR signal. This also uses the 10\% deviation results.\\
+3.
+highlight the fact that for a nonGR signal, not only does pSEOB correctly recover the frequencies, unlike SEOB, it also correctly recovers the masses and spins.
+For this we needed to show a comparison of a SEOB vs pSEOB recovery of a signal with and without deviation, i.e, at least 4 cases.
+The easiest way to show this, I thought, would be to restrict to one event, GW150914-like, and create three signals with deviationsn = 0, 0.1 and 0.5.
+Then in two columns we show the SEOB vs pSEOB recoveries.
+There are several things that can be higlighted in this figure: a) for GR recoveries, greater the deviation, greater the biases.
+b) pSEOB measurements for all quantities are unbiased, c) this behaviour is unchanged irrespective of the magnitude of the deviation.
+Consequently, I have replaced the earlier Fig 4 with a new figure.}
+
 To demonstrate the robustness of the method in detecting possible
@@
 
-We additionally investigate the effects of erroneously assuming that
-an underlying non-GR signal can be well-described
-by a GR one. We do this by estimating the parameters of our non-GR
-signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
+We additionally investigate the effects of erroneously assuming that an underlying non-GR signal can be well-described
+by a GR one.
+We do this by estimating the parameters of our non-GR signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
 The resulting one- and two-dimensional posteriors are shown in the right panels of Fig.~\ref{fig:simulated_signal_nonGR} by red curves for the GW150914-like (top) and GW190521-like (bottom) signals respectively.
@@
 This can be explained by the inability of the $\SEOB$ template waveform to capture all the physics in the $\pSEOB$ signal.
-We also notice that the results are distinctly
-different for the two events. For the GW150914-like non-GR signal, the measurements of $(\fgr{220}, \taugr{220})$
-(top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent
-with the $(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no
-deviations} from GR (top right panel in Fig.~\ref{fig:simulated_signal_GR}). In other
-words, if the actual signal had deviations from GR as large as the $10\%$, the analysis with the GR signal $\SEOB$ would likely have
-reported \emph{no} deviation from the GR prediction. However in the
-case of the GW190521-like non-GR signal, a simple GR analysis of
-the non-GR signal would have yielded measurements distinctly
-different from either of the two parameterized estimates: with and
-without deviations. \comment{AB: Not clear to me the next sentence. We are working
-in Gaussian noise, so why are you referring to the noise as the culprit or the
-source of difference?} The fact that the GW190521-like signal has a much
-lower SNR than GW150914-like signal might be a possible reason for the
-measurement of the final quantities to be more susceptible to noise. A
-more detailed comparison of the other parameters, like the masses and
-spins, between an $\pSEOB$ and an $\SEOB$ measurement of a modified GR
-signal is shown in Fig.~\ref{fig:gr_ngr_comparison}. \comment{AB: Please
-comment the figures. What are the main results? What do we deduce?}
+We also notice that the results are distinctly different for the two events.
+For the GW150914-like non-GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent with the $(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no deviations} from GR (top right panel in Fig.~\ref{fig:simulated_signal_GR}).
+In other words, if the actual signal had deviations from GR as large as the $10\%$, the analysis with the GR signal $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
+However in the case of the GW190521-like non-GR signal, a simple GR analysis of the non-GR signal would have yielded measurements distinctly different from either of the two parameterized estimates: with and without deviations.
 
+Finally, we investigate the impact on the estimation of GR parameters discussed in Sec.~\ref{sec:method}, $\bxigr$  as we change the magnitude of deviation in the non-GR parameters.
+We restrict oursel es to a GW150914-like event, and for comparison, add a synthetic signal with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the 10\% non-GR signal and a signal with no deviation (essentially GR) mentioned above.
+We summarise the results in Fig.~\ref{fig:gr_ngr_comparison}.
+The left (right) panels show the posterior probability distributions of the three signals using the GR, $\SEOB$ (non-GR, $\pSEOB$) waveform model.
+The first difference we note is the $\SEOB$ recoveries yield biased estimates when the underlying signal is non-GR, while the $\pSEOB$ recoveries do not.
+Furthermore, as we increase the deviations, while the $\SEOB$ recoveries expectedly get more biased, the $\pSEOB$ measurements are robust is consistently recovering the injected value.
+Since the measurement of the frequency and damping time in the $\pSEOB$ model incorporate information from the masses and spins through the NR fitting formulae (as shown in Eqs.~\ref{eq:nongr_freqs_a}-~\ref{eq:nongr_freqs_b}), one might have expected correlations between the mass, spins and the QNM frequencies, leading to biased estimates in the masses and spins.
+We confirm here that is not the case.
+
+\iffalse
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure*}%[h!]
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
-        \caption{\textcolor{red}{FINAL RESULT} Comparison of \sout{the recovered} \ab{binary's} parameters when \sout{the underlying signal is assumed to be a GR signal or a modified GR signal} \ab{a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model}.
-\sout{In both cases, the actual underlying signal is a modified GR signal with parameters similar to} \ab{The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.5$.} \sout{For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively.} The panels (from top to bottom) show the recoveries in (detector-frame) \sout{initial} masses (first row), \sout{z-components of dimensionless initial} \ab(dimensionless) spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time
-(obtained by inverting the Berti fits).
-\comment{AB: I would write those details about the ``Berti's fits, etc.'' in the text, not in the caption.
-Also please specify if the remnant mass is the detector-frame mass.
-Please
-switch the red and blue colors. The blue colors should always refer to the same waveform model, i.e., $\pSEOB$. Please indicate on the figures: GW150914-like and GW190521-like.}}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_m1m2.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_a1za2z.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fgrtaugr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_Mfaf.png}
+        \caption{\textcolor{red}{FINAL RESULT} Comparison of binary's parameters when a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model.
+The left (right) panels refer to
+a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.1$.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
+In each case, the injection values are indicated by the black dashed lines.}
+        \label{fig:gr_ngr_comparison}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GW150914-like signal with different deviations: GR vs nonGR recovery
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_m1m2.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_a1za2z.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_fgrtaugr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
+        \caption{\textcolor{red}{FINAL RESULT}  Comparison of a GW150914-like injection's parameters when signals with no, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
+In each case, the injection values are indicated by the black dashed lines.
+In the lowermost panel, the injection values of the final mass and spin, correspond to the injection with no deviations.
+The $\df{220} = \dtau{220} = 0.1$ signal is identical to the results shown in Fig.~\ref{fig:simulated_signal_nonGR}.}
         \label{fig:gr_ngr_comparison}

### 2021-01-28 scripts/compare_snr_nonGR_runs.py
updated snr computing script

@@ -1,0 +1,24 @@
+# Copyright 2021, Abhirup Ghosh <abhirup.ghosh.184098@gmail.com>
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+event_list = ["GW150914", "GW190521" ]
+run_list = ["0p0_GR", "0p0", "0p1_GR", "0p1", "0p5_GR", "0p5"]
+label_list = [np.char.replace(label,"_",":") for label in run_list]
+
+plt.figure(figsize=(10,5))
+
+for event in event_list:
+  plt.figure(figsize=(10,5))
+  for (label,run) in zip(label_list,run_list):
+    data = np.genfromtxt(f"/Users/abhirupghosh/Documents/Work/spinqnm/runs/nonGR/{event}-like/domega220_dtau220_{run}_widerdist/cbcBayes/posterior_samples.dat", dtype=None, names=True)
+    
+    plt.hist(data["matched_filter_snr"], histtype="step", bins=50, density=True, label=f"{event}:{label}")
+
+  #plt.xlim(left=15)
+  plt.xlabel("$\\rho_{SNR}$")
+  plt.ylabel("P($\\rho_{SNR}$)")
+  plt.legend(loc="best")
+  plt.savefig(f"./compare_snr_nonGR_runs_{event}.png")
+    

### 2021-01-29 papers/intro_paper/appendix.tex
updated appendix
updated appendix figure

@@
-\section{Study of systematics on ringdown measurements \ab{in real , non-Gaussian noise}}\label{sec:noise_systematics}
+\section{Study of systematics in ringdown measurements in real, non-Gaussian noise}\label{sec:noise_systematics}
 
-\comment{AB: Please improve considerably this Appendix because it is not easy to follow the motivation and the logic. It is written for LIGO people.
-I have tried to make changes but it is better if you do it. I risk to erase parts that you would consider important. Please write it thinking that your
-reader is not an LSC reader!}
+\abhi{completely re-written this section to make it more readable and less technical.}
 
-In Sec.~\ref{sec:method}, we \ab{discussed} \sout{mentioned that} the expression of the
-Bayesian likelihood function \ab{that we use in our analysis} \sout{outlined in} \ab{(see
-Eq.~\ref{eq:likelihood})} \ab{and stressed that it}\sout{and \ref{eq:nwip}} is only valid if the interferometric noise can be
-described as a stationary Gaussian process. LIGO-Virgo noise, however,
-frequently has non-stationary and/or non-Gaussian features, for
-example glitches, which can affect parameter inferences unless
-appropriately accounted for. Here we demonstrate\ab{, by injecting in real
-noise a GW190521-like signal} \sout{with an example of a
-GW190521-like simulated signal}, \ab{how} systematic biases \ab{can originate} \sout{likely originating}
-from an incomplete understanding of the noise. \comment{AB: It is confusing to refer to ``systematic''
-biases for the noise, generally we refer to systematic biases for the waveform modeling.
-In fact, below you also, somewhat suddenly, refer to (lack of) precession, as a possible source of systemtcis.
-I would advice you to clarify from the beginning of this Appendix, what this study is about and what you intend to
-do below.}
+Inferences of all parameters in this paper have been done under the assumption that the noise in the detectors is stationary and Gaussian.
+In other words, detector noise follows a normal distrubution with zero mean and a PSD, $S_n(f)$, that is not a function of time, at least during the internal of the gravitational wave signal.
+This allows us to write the Bayesian likelihood function in the form given in Eqs.~\ref{eq:likelihood}-~\ref{eq:nwip}, and perform all the parameter estimation that follows in the results sections.
+However,, LIGO-Virgo noise can often have features that deviate from stationarity and Gaussianity.
+If such features are not taken into account appropriately, final estimates of parameters can get biased.
+We demonstrate one such case by injecting in real noise a GW190521-like signal and showing how parameter estimates can be biased by our understanding of detector noise is not complete.
 
@@
         \includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-        \caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ from simulations \comment{AB: I have changed this in other places.
-The word ``simulations'' is confusing, because we deal with a paper in which we also refer to NR simulations.
-I suggest to use ``injected synthetic signals'' instead} of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines).
+        \caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur7dq4} GW signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
 The GR prediction for the frequency and damping time is indicated by the black cross.
 While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-For comparison, we also plot the 90 \% credible level for the actual event, GW190521.
-\comment{AB: For clarity, please indicate on the plot which waveform model is used to obtain such posteriors, as you did
-in the other plots of the paper. Also, please use something else instead of ``actual event'', which is confusing. The problem is
-that the first two entries of the legend refer to the noise properties of the PE study done with an injected synthetic signal, whereas I believe ``actual event'' refers to ``real'' not injected signal
-and ``real noise''. All the entries in the legend need to be consistent with each other; you need to specify for each of them the ``signal'' and the ``noise''. I hope is clear what I am saying}}
+The black curve corresponds to the measurements of the real event GW190521 reported in~\ref{Abbott:2020jks}.
+All signals are recovered using the $\pSEOB$ waveform model.}
         \label{fig:21g_systematics}
@@
 
-\ab{The spinning, precessing NR-surrogate model \texttt{NRSur7dq4}, valid up to mass ratio 4, was employed
-(together with the $\SEOB$ model) to analyze the GW190521 signal observed by the LIGO and Virgo detectors.
-For the injected synthetic signal we use a \texttt{NRSur7dq4} waveform with parameters similar to the ones
-recovered by this model on the actual GW190521 data (see Table I of Ref.~\cite{Abbott:2020tfl}).}
-\ab{In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal
-predicts for the $(2,2)$ frequency and damping time, and for comparison, we also
-show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$. As seen in the plot, while
-the measurement of the frequency is consistent with the prediction, we overestimate the damping time.} \comment{AB: it is not clear
-to me what the figure shows. Is the black line the result when running $\pSEOB$ against real data or the
-injection in realt data?}
+We choose a spinning, precessing NR-surrogate model \texttt{NRSur7dq4} (valid up to mass ratio 4) to simulate the actual GW190521 signal observed by the LIGO and Virgo detectors~\cite{Abbott:2020tfl} (see Table I of Ref.~\cite{Abbott:2020tfl})).
+The choice of the  NR-surrogate model is motivated by the fact that they are the most accurate in the parameter range described by GW190521.
+In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal predicts for the $(2,2)$ frequency and damping time,, and for comparison, we also show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$.
+As seen in the plot, while the measurement of the frequency is consistent with the prediction, we overestimate the damping time.
 
-\comment{AB: What is the ``underlying'' NR signal? I think you are referring to the
-injected signal. Also, until now you have not discussed precession.
-} The underlying NR signal is expected to be precessing, and since the
-$\pSEOB$ model is built on an aligned-spin GR model, a lack of
-precession could bias measurements. We explore effects of possible
-waveform systematics by injecting the signal is coloured Gaussian
-noise. In this case, since the understanding of the noise realizations
-is complete, any measurement biases could only arise from incomplete
-understanding of the \sout{underlying} \ab{injected} signal. We find (grey curves in
-Fig.\ref{fig:21g_systematics}) our results to be consistent with the
-prediction thus ruling out a lack of precession to be a likely cause
-for the bias in the damping time measurement of the actual signal.
+The actual GW190521 event was observed at a GPS time, 1242442967.61 seconds (roughly 03:02:49 UTC, May 21, 2019).
+We select a time period of about 2.5 hours around this GPS time and create synthetic signals by injecting the \texttt{NRSur7dq4} GW signal in different stretches of real detector noise around the time of the actual GW event.
+The PSDs of GW detectors are expected to vary over
+longer durations of time, and hence the 2.5 hour stretch of noise we consider can be assumed to have noise-properties similar to the time of the actual event.
+The results are indicated by green curves in Fig.~\ref{fig:21g_systematics}.
+As it can be seen from the figure, for 3 of the 5 noise realizations, corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we recover a damping time similar to the actual event, where $t_0$ is the GPS time of the actual event.
+For the other two noise realizations, we estimate the consistent damping time but an off-set frequency, while the fifth noise realization is consistent with both predictions.
+This seems to indicate that a bias in the measurements of the damping time for the actual event can be explained on account of an incomplete understanding of the noise at the time of the event.
 
-We subsequently study the effects of possible noise systematics by
-injecting the same \texttt{NRSur7dq4} GW signal in different
-realizations of actual interferometric noise around the real event
-GW190521. Since the PSDs of the GW detectors are expected to vary over
-longer durations of time, we select 5 different noise realizations
-over a segment of 2.5 hours of coincident data in both the LIGO
-detectors centered at the time of the actual event. The noise
-properties in this chunk of data, and consequently for all 5 simulated
-signals, is expected to be the closest to that for the actual
-event. The results are indicated by \sout{pink} \ab{green} curves in
-Fig.~\ref{fig:21g_systematics}. \ab{As it can be seen from the figure,}
-for 3 of the 5 noise realizations,
-corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we
-recover a damping time similar to the actual event, where $t_0$ is the
-GPS time of the actual event. For the other two noise realizations, we
-estimate the consistent damping time but an off-set frequency, while
-the fifth noise realization is consistent with both predictions. The
-SNR in the Livingston detector goes down by more than \ab{a factor} 3 in some
-runs, indicative of how a variation in the noise strongly affects our
-ability to infer parameters. This also seems to indicate that a bias
-in the measurements of the damping time for the actual event \comment{AB: not clear
-what you mean} can be unaccounted noise systematics.
+The reader might question the judiciousness of using an aligned-spin waveform model, like $\pSEOB$ to measure a signal like GW190521 which appears to be precessing, especially because an incomplete understanding of the underlying signal can also lead to biases in measured quantities, as we have already demonstrated in Sec.~\ref{ssec:ngr_signal}.
+In order to explore possible effects of missing information about in-plane spins in $\pSEOB$, we repeat the above study of injecting synthetic signals using \texttt{NRSur7dq4} and recovering using the $\pSEOB$ template.
+But this time, instead of using real detector noise, we use Gaussian noise, i.e., realisations of noise sampled from a predicted detector PSD.
+Since the properties of the noise is completely understood in this case, any residual measurement biases can be completely attributed to diffferences in the waveform model.
+The 2D posterior distributions of the frequency and damping time measured using these Gaussian-noise signals is shown by the grey curves in Fig.~\ref{fig:21g_systematics}.
+We find the measurements to be completely consistent with the predictions of the frequency and damping time, thus concluding that a lack of in-plane spins in the $\pSEOB$ model does not affect our measurements of the QNM properties.
+The fact that the measurement of ringdown quantities are robust against an incomplete understanding of the inspral of a GW signal, is indeed one of the most strong points of our model.

### 2021-01-31 papers/intro_paper/results_lvc.tex
updated figure caption

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}
-        \caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+\begin{figure*}
+        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.25\textwidth]{figures/rin_all_events_bounds.pdf}
+        \caption{\emph{Left panel}: The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
 The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.}
+The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
+\emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $(\df{220},\dtau{220})$, colored by the median redshifted chirp mass $(1 + z)M$, inferred assuming GR.
+Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).}
         \label{fig:o1o2_events}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
 \input{table_lvc_results}
+\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table
+also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
+\label{tab:qnm_o1o2_results}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-31 papers/intro_paper/results_lvc.tex
updated all figures

@@
 \begin{figure*}
-        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.25\textwidth]{figures/rin_all_events_bounds.pdf}
-        \caption{\emph{Left panel}: The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.3\textwidth]{figures/rin_all_events_bounds.pdf}
+        \caption{\emph{Top panel}: The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
 The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
 The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
-\emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $(\df{220},\dtau{220})$, colored by the median redshifted chirp mass $(1 + z)M$, inferred assuming GR.
+\emph{Bottom panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted chirp mass $(1 + z)M$, inferred assuming GR.
 Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).}

### 2021-02-01 papers/intro_paper/results_lvc.tex
edits to lvc section

@@
 post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified \sout{as} \ab{from} the \ab{signal's} power \sout{in the frequency content of the
-signal} before and after the signal reaches \ab{the} peak\ab{'s}
-amplitude, \sout{as} \ab{which is} determined by the maximum \ab{of the}
-likelihood \ab{function}  \ab{from the} parameter-estimation \ab{analysis} \sout{template}.
+signal are identified from the signal's power before and after the signal reaches the peak's
+amplitude, which is determined by the maximum of the
+likelihood function from the parameter-estimation analysis.
 \comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the
@@
 GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking
-  promising}. Fig.~\ref{fig:o1o2_events} shows results from these two
+considered in \cite{Abbott:2020jks}. Fig.~\ref{fig:o1o2_events} shows results from these two
 events along with GW190519$\_$153544, GW190521$\_$074359,
@@
 loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{LSC_2016grtests,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
+Within 90\% credibility we obtain from GW150914:
+%
+\begin{equation}
+\df{220}=0.04^{+0.06}_{-0.04}\,\quad \dtau{220}=0.09^{+0.18}_{-0.18}\,.
+\end{equation}
 
@@
 The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
-\emph{Bottom panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted chirp mass $(1 + z)M$, inferred assuming GR.
+\emph{Bottom panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
 Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).}
@@
 
-Finally, if we assume that the fractional deviations $(\df{220},
-\dtau{220})$ take the same values in multiple events, we can assume
+Stronger constraints can be obtained by combining information from all the events~\cite{Abbott:2020jks}.
+If we assume that the fractional deviations $(\df{220},\dtau{220})$ take the same values in multiple events, we can assume
 the posterior of one event to be the prior for the next, and obtain a
@@
 where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since we assume the prior on $(\df{220},
+\dtau{220})$. However, since here we assume the prior on $(\df{220},
 \dtau{220})$ to be flat (or uniform), the joint posterior is equal to
 the joint likelihood.
+We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding 1D marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
+From the joint likelihood we obtain within 90\% credibility:
+%
+\begin{equation}
+\df{220}=0.02^{+0.03}_{-0.03}\,,\quad \dtau{220}=0.11^{+0.12}_{-0.12}\,.
+\end{equation}
+%
 
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding \ab{1D} marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
-These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method.\comment{AG: add text on the hierarchical analysis
-if we want to include that analysis. AB: we want to include that analysis.}
-
-\comment{AB: Please write in the text (equations) the results for $(\df{220}, \dtau{220})$ for GW150914, the joint likelihood and the
-hierarchically combined methods.}
+As described in~\cite{Abbott:2020jks}, we can relax the assumption of a shared deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
+The general idea behind this technique is to assume that the non-GR parameters $(\df{220},\dtau{220})$ are drawn from a common underlying distribution, whose properties can be inferred from the population of events.
+Following~\cite{Zimmerman:2019wzo,Isi:2019asy,Abbott:2020jks} we model the population distribution with a Gaussian  $\mathcal{N}(\mu,\sigma)$ of unknown mean $\mu$ and standard deviation $\sigma$.
+Through a joint analysis of all the GW events, one can then obtain a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for the hyperparameters $\mu$ and $\sigma$~\cite{Isi:2019asy} and a distribution for a given non-GR parameter $\xi_{\text{nGR}}$ by computing~\cite{Isi:2019asy}
+%
+\begin{equation}
+P(\xi_{\text{nGR}} | \{d_j\}) = \int P(\xi_{\text{nGR}} |\, \mu, \sigma)\,P(\mu, \sigma |  \{d_j\})\,d\mu\,d\sigma \,,
+\end{equation}
+%
+where $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$ by construction.
+The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained through this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
+%
+\begin{equation}
+\df{220}=0.02^{+0.09}_{-0.09}\,,\quad \dtau{220}=0.13^{+0.42}_{-0.40}\,.
+\end{equation}
+Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ stronger for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$. \rb{give results for $\mu$ and $\sigma$ as well?}
 

### 2021-02-01 papers/intro_paper/results_lvc.tex
edits lvc section

@@
 The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results \sout{of this test} for all events observed
-during O3a~\cite{Abbott:2020jks}, which passed a threshold for the
-total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$.The pre- and post-merger regions of the
-signal are identified from the signal's power before and after the signal reaches the peak's
-amplitude, which is determined by the maximum of the
-likelihood function from the parameter-estimation analysis.
-\comment{AB: What does it mean ``for the purpose of Ref.''? We are using present tense in the
-entire paper, except perhaps the Conclusions section.}
-For the purpose of Ref.~\cite{Abbott:2020jks}, we use\sout{d} a mass
-threshold and restrict\sout{ed} ourselves to the highest-mass events which
-\sout{were} \ab{are} expected to be most promising to study merger-ringdown. However,
-since our method relies on doing a parameter estimation on the entire
-inspiral-merger-ringdown signal, we require the SNR to be beyond a
-certain threshold throughout the signal for reliable parameter
-estimation of the initial and final quantities. \comment{AB: there are not ``initial'' and ``final'' parameters,
-there are the component masses of the holes in the binary, and the
-mass of the remnant formed after merger.} In fact the SNR
-threshold alone should be sufficient for the analysis, and for this
-paper we have relaxed the mass threshold. This has added two events,
-GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events
-considered in \cite{Abbott:2020jks}. Fig.~\ref{fig:o1o2_events} shows results from these two
-events along with GW190519$\_$153544, GW190521$\_$074359,
-GW190910$\_$112807. \comment{AB: Please improve the above paragraph
-and make it clearer which choice is made for the SNR threshold and
-masses, and why.}
+catalogue containing results for events observed
+during O3a~\cite{Abbott:2020jks}.
+For the test that we here present, the results shown in~\cite{Abbott:2020jks} only include events which pass a threshold for the median redshifted total mass $\geq 90 \Mo$ and SNRs in the pre- and
+post-merger regions $\geq 8$\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.}.
+%
+The SNR threshold ensures that the signal contains sufficient information in both the inspiral and merger stages to break the degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$.
+Such strong degeneracy is present for low-SNR events with negligible higher-modes and for which only the post-merger is detectable rendering the measurement of $(\df{220}, \dtau{220})$ impossible for those cases.\rb{should we show an example where this degeneracy happens in the appendix?
+We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example.
+And perhaps also for GW150914 for comparison.}
+On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies.
+However, since the SNR threshold alone should be sufficient for the analysis, for this paper we run the test on all the events listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and post-merger regions $\geq 8$, without imposing any mass threshold.
 
+Imposing this threshold adds two events, GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in \cite{Abbott:2020jks}.
 Furthermore, for the first time, in this paper, we apply our method to
-measure the QNMs to the relevant
-GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same thresholds as above, we find three
+measure the QNMs to the relevant GW events from LIGO-Virgo's O1 and O2 runs, alongside
+the above events. Applying the same threshold as above, we find two
 additional events that could be included in the analysis: GW150914,
-GW170104, GW170729. The other high-mass events from O1-O2, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the
-merger-ringdown signal. For the three relevant signals, GW150914,
-GW170104 and GW170729, we show the posterior distributions in
-$(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also reconstruct the QNM parameters, $(\fngr{220}, \taungr{220})$
-which are tabulated in Table~\ref{tab:qnm_o1o2_results} \footnote{See
-  Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
+GW170104. The other high-mass events from O1-O2, GW170729, GW170809,
+GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
+merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}\footnote{See Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
   thresholds. The paper quotes them for the purpose of the IMR
   consistency test, but the same thresholds have been used for the
-  $\pSEOB$ test, as well.} Among all the GW signals detected so far,
-GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its
-loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{LSC_2016grtests,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
-Within 90\% credibility we obtain from GW150914:
-%
-\begin{equation}
-\df{220}=0.04^{+0.06}_{-0.04}\,\quad \dtau{220}=0.09^{+0.18}_{-0.18}\,.
-\end{equation}
+  $\pSEOB$ test, as well.}.
 
@@
         \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.3\textwidth]{figures/rin_all_events_bounds.pdf}
-        \caption{\emph{Top panel}: The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+        \caption{\emph{Top panel}:\rb{should this be left and right panel?} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
 The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For all the relevant signals, we show the posterior distributions $(\df{220}, \dtau{220})$ in the left panel \rb{the caption says "top panel" but the current figure is in the left panel} of Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM parameters, $(\fngr{220}, \taungr{220})$ in Table~\ref{tab:qnm_o1o2_results}.
+In the right panel \rb{the caption says "bottom panel" but the current figure is in the right panel} of Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\% credible intervals on the one-dimensional marginalised posteriors highlighting the dependence of the constraints with respect to the total mass of the system.
+In general the tightest bounds come from the most massive systems, as would be expected given that more massive events tend to have larger post-merger SNR \rb{check if this is true when plot is updated}.
+
+Among all the GW signals detected so far, GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{LSC_2016grtests,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
+Within 90\% credibility we obtain from GW150914:
+%
+\begin{equation}
+\df{220}=0.04^{+0.06}_{-0.04}\,\quad \dtau{220}=0.09^{+0.18}_{-0.18}\,.
+\end{equation}
 
@@
 \end{equation}
-Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ stronger for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$. \rb{give results for $\mu$ and $\sigma$ as well?}
+Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ stronger for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$.
+Similar improvements hold for the hyperparameters: $\df{220}\,(\mu=0.02^{+0.05}_{-0.05},\,\sigma<0.09)$ and $\dtau{220}\,(\mu=0.13^{+0.20}_{-0.18},\,\sigma<0.38)$.
 

### 2021-02-02 papers/intro_paper/results_lvc.tex
lvc results

@@
 Following~\cite{Zimmerman:2019wzo,Isi:2019asy,Abbott:2020jks} we model the population distribution with a Gaussian  $\mathcal{N}(\mu,\sigma)$ of unknown mean $\mu$ and standard deviation $\sigma$.
-Through a joint analysis of all the GW events, one can then obtain a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for the hyperparameters $\mu$ and $\sigma$~\cite{Isi:2019asy} and a distribution for a given non-GR parameter $\xi_{\text{nGR}}$ by computing~\cite{Isi:2019asy}
+We can then obtain a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for the hyperparameters $\mu$ and $\sigma$ from a joint analysis of all the GW events~\cite{Isi:2019asy}.
+We use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $.
+%
+Finally, the distribution for a given non-GR parameter $\xi_{\text{nGR}}$ is then be obtained by computing~\cite{Isi:2019asy}
 %
@@
 %
-where $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$ by construction.
+where $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$.
 The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained through this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
@@
 \end{equation}
-Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ stronger for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$.
+Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ more stringent for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$.
 Similar improvements hold for the hyperparameters: $\df{220}\,(\mu=0.02^{+0.05}_{-0.05},\,\sigma<0.09)$ and $\dtau{220}\,(\mu=0.13^{+0.20}_{-0.18},\,\sigma<0.38)$.

### 2021-02-02 papers/intro_paper/abstract.tex
updated abstract and introduction; added references

@@
   joint measurements of the fractional deviations in the frequency and damping time,
-  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
+  \macro{$\df{220} = 0.02^{+0.03}_{-0.03}$} and \macro{$\dtau{220} = 0.11 ^{+0.12} _{-0.12}$} are the strongest
   constraints yet using this method.

### 2021-02-02 papers/intro_paper/intro.tex
updated abstract and introduction; added references

@@
 
-The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
-Collaboration~\citep{Virgo} have recently announced their catalogue of
+\abhi{The main body can now be considered stable in terms of text and results. Some of the fine tuning mentioned above,eg, reference formatting, cosmetic changes, etc are currently ongoing.}
+
+\abhi{All macros in the paper are currently highlighted in orange, and would require one final check before final draft.}
+
+The LIGO Scientific Collaboration~\cite{lsc} and the Virgo
+Collaboration~\cite{Virgo} have recently announced their catalogue of
 gravitational-wave (GW) signals from the first
@@
 with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\citep{aasi2015characterization},
+Washington and Livingston, Louisiana~\cite{Aasi:2014mqd},
 and the Advanced Virgo detector in Cascina,
-Italy~\citep{acernese2014advanced} have now detected $50$ GW
+Italy~\cite{TheVirgo:2014hva} have now detected $50$ GW
 events from the merger of compact objects like neutron stars and/or
 black holes (BHs). Alongside independent claims of
-detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, notably GW150914~\citep{abbott2016observation}.
+detections~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, GW150914~\cite{Abbott:2016blz}.
 
 The observation of GWs has had significant astrophysical and cosmological
-implications~\citep{LSC_2016astroph,gw170817_mma,gw170817_joint,gw170817_hubble}. It
+implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
 has also allowed us to probe fundamental
@@
 (GR) in the previously unexplored highly-dynamical, and strong field
-regime~\citep{LSC_2016grtests,GW170817_TGR,gwtc1_tgr}. In GR, a binary black hole (BBH) system is described by
+regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa}. In GR, a binary black hole (BBH) system is described by
 three distinct phases: an early \textit{inspiral}, where the two
 compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon~\citep{NRpaper}, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\citep{vishu,earlyqnmpapers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
+formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970cc}\abhi{cite some of the other early QNM papers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
 
-The LIGO-Virgo collaborations have released companion papers \cite{} detailing their results
-of tests of GR for GW150914 \cite{} and for several GW events of
-the two transient catalogues (TC): GWTC-1\cite{}  and GWTC-2 \cite{}.
+The LIGO-Virgo collaborations have released companion papers detailing their results
+of tests of GR for GW150914 \cite{TheLIGOScientific:2016src} and for several GW events of
+the two transient catalogues (TC): GWTC-1 \cite{LIGOScientific:2018mvr,LIGOScientific:2019fpa}  and GWTC-2 \cite{Abbott:2020niy,Abbott:2020jks}.
 The results include tests of GW generation and source dynamics, where bounds are placed on
 parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral~\citep{earlydevelopmentpapers}, and
+the early inspiral and
 phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\citep{TIGERmethodspapers}; tests of GW
+merger regimes of coalescence~\cite{Arun:2006hn,Arun:2006yw,Agathos:2013upa,Abbott:2018lct}; tests of GW
 propagation, which assume a generalized dispersion relation and place
 upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\citep{gw170104,samajdar2017projected}, and tests of the
+the graviton~\cite{Abbott:2017vtc,Samajdar:2017mka}, and tests of the
 polarization of gravitational radiation using a
-multi--GW-detector network~\citep{gw170814,isi2017probing}. The GWTC-1/2 papers also
+multi--GW-detector network~\cite{Abbott:2017oio,Isi:2017fbj}. The GWTC-1/2 papers also
 check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\citep{Ghosh:2016xx,Ghosh:2017gfp,LSC_2016grtests}, and
+object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
 consistency of the residuals with interferometric
-noise~\citep{Ghonge:2020suv,gwtc1_tgr}. None of these tests report any
+noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
 departure from the predictions of GR.
 
-The first paper on tests of GR by the LIGO Collaboration~\cite{} provided us with the
+The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} provided us with the
 first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
-coalescence. The LIGO-Virgo O3a testing GR paper~\cite{} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
-The no-hair conjecture in GR~\citep{} states that an (electrically neutral) astrophysical BH is completely
+coalescence.
+The LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
+The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely
 described by two observables: mass and spin angular momentum. One
@@
 The consistency between the post-merger signal and the least damped QNM was first demonstrated in
-Ref.~\citep{LSC_2016grtests} for GW150914, and later extended to include
+Ref.~\citep{LIGOScientific:2019fp} for GW150914, and later extended to include
 overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
-of the late-time \sout{signal} \ab{waveform} with a single QNM is a test of the ringdown of
+of the late-time waveform with a single QNM is a test of the ringdown of
 a BBH coalescence, but not necessarily a test of the no-hair
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and \sout{checking for} consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
-in that direction \comment{AB: which direction? There are papers by Nikhef group and
-also Brito et al., and many others that have investigated BH spectroscopy.} include~\citep{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
+also include~\cite{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
 nature of the remnant object has also been explored through tests of
@@
 
-\comment{AB: I don't understand the next sentence, it looks to me out of context.}
-Most of the tests mentioned above focus on analysing the post-merger
-or late-time ringdown signal in isolation. \sout{Second generation
-ground-based interferometric detectors like} \ab{Ground-based detectors,
-such as \sout{Advanced} LIGO and Virgo,} are most sensitive to
+Most of the tests mentioned above restrict the data to the post-merger signal and then analyse it.
+Ground-based detectors, such as LIGO and Virgo, are most sensitive to
 stellar-mass BH binaries that merge near the
-minim\ab{um}\sout{a} of their sensitivity band ($\sim 100$Hz). As a consequence, the
-remnant object \textit{rings down} \comment{AB: we are not discussing the interferometer noises,
-so why to give such a detail about the shot noise?} \sout{in shot-noise dominated higher
-frequencies, leaving} \ab{at frequencies where the sensitivity is worse, leaving}
+minimum of their sensitivity band ($\sim 100$Hz). As a consequence, the
+remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
 very little signal-to-noise ratio (SNR) in the
@@
 An independent approach to BH spectroscopy, based on the full-signal
-analysis, was \sout{outlined} \ab{introduced} in Ref.~\citep{Brito:2018rfr}
-(henceforth referred to as \paperone). Unlike methods that focus \ab{only}
-on the post-merger signal, it \sout{describes a framework in which a}
-\ab{employs the} complete inspiral-merger-ringdown
-(IMR) waveform \sout{model is used} to measure the complex QNM
-frequencies. This \sout{allows} \ab{gives} access to the full SNR of the signal,
+analysis, was introduced in Ref.~\citep{Brito:2018rfr}
+(henceforth referred to as \paperone). Unlike methods that focus only
+on the post-merger signal, it employs the
+complete inspiral-merger-ringdown
+(IMR) waveform to measure the complex QNM
+frequencies. This gives access to the full SNR of the signal,
 reducing measurement uncertainties. Moreover, the definition of the
-ringdown start time is built into the \ab{merger-ringdown} model and does not need to be
+ringdown start time is built into the merger-ringdown model and does not need to be
 either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method \ab{and tested it for }\sout{in the context of a
-non-spinning waveform model} \ab{non-spinning BBHs}, \ab{here} we extend the analysis to the \ab{more
-realistic astrophysical} case in which BHs \ab{carry} spin\sout{s in the current paper}. \ab{Furthermore,
+definitions. While \paperone presented the method and tested it for non-spinning BBHs, here we extend the analysis to the more
+realistic astrophysical case in which BHs carr spin. Furthermore,
 the IMR waveform model used in this paper is more accurate than what employed in \paperone,
 because it contains higher-order corrections in PN theory and it was calibrated to a much larger set
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}.}  All astrophysical BHs are expected to be spinning,
+of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}. All astrophysical BHs are expected to be spinning,
 and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the
-source properties \cite{paper_showing_systematics_from_ignoring_spin}.
+source properties.
 
 The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR\ab{, notably how we can measure
-complex QNM frequencies with our parameterized model within a Bayesian formalism}. Then, in Sec.~\ref{sec:results},
-we demonstrate our method on real GW events, as well as simulated signals. \ab{In particular, we analyze
-the ... and constrain the QNM frequecies ... Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.}
+waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
+complex QNM frequencies with our parameterized model within a Bayesian formalism. Then, in Sec.~\ref{sec:results},
+we demonstrate our method on real GW events, as well as simulated signals. In particular, we analyze
+the GWTC 1/2  events and constrain the QNM frequecies to be \macro{$\df{220} = 0.02^{+0.03}_{-0.03}$} and \macro{$\dtau{220} = 0.11 ^{+0.12} _{-0.12}$}.
+Finally, in Sec.~\ref{sec:discussion} we provide a summary of
+our results and discuss future developments.

### 2021-02-02 papers/intro_paper/model_method.tex
updated method/model section

@@
 As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB)
-formalism~\cite{Brito:2018rfr}. However, whereas \paperone was limited to non-spinning multipolar waveforms,
+formalism. However, whereas \paperone was limited to non-spinning multipolar waveforms,
 here we use as our baseline model the aligned-spin multipolar waveform model
-developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being
+developed in Ref.~\cite{Cotesta:2018fcv}. In addition to being
 calibrated to NR simulations, this model also uses information from BH
@@
 %
-where $\varphi_0$ is the azimuthal direction to the observer \rb{Perhaps to clarify that $\varphi_0$ does not add another parameter we can say: "(note that without loss of generality we can take $\phi_c\equiv\varphi_0$)"}, ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
+where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
 The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
@@
 We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy} \rb{Abhirup, can you check that indeed we followed the LIGO-Virgo analysis?}.
+GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
 Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.

### 2021-02-02 papers/intro_paper/results_lvc.tex
addressed remaining comments in results sections

@@
 We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example.
-And perhaps also for GW150914 for comparison.}
+And perhaps also for GW150914 for comparison.}\abhi{I would be fine with this.
+Perhaps we should have a discussion about how best to put it in the appendix, if we decide to.}
 On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies.
@@
         \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.3\textwidth]{figures/rin_all_events_bounds.pdf}
-        \caption{\emph{Top panel}:\rb{should this be left and right panel?} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+        \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
 The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
 The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
-\emph{Bottom panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
+\emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
 Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).}
@@
 
-For all the relevant signals, we show the posterior distributions $(\df{220}, \dtau{220})$ in the left panel \rb{the caption says "top panel" but the current figure is in the left panel} of Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM parameters, $(\fngr{220}, \taungr{220})$ in Table~\ref{tab:qnm_o1o2_results}.
-In the right panel \rb{the caption says "bottom panel" but the current figure is in the right panel} of Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\% credible intervals on the one-dimensional marginalised posteriors highlighting the dependence of the constraints with respect to the total mass of the system.
-In general the tightest bounds come from the most massive systems, as would be expected given that more massive events tend to have larger post-merger SNR \rb{check if this is true when plot is updated}.
+For all the relevant signals, we show the posterior distributions $(\df{220}, \dtau{220})$ in the left panel of Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM parameters, $(\fngr{220}, \taungr{220})$ in Table~\ref{tab:qnm_o1o2_results}.
+In the right panel  of Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\% credible intervals on the one-dimensional marginalised posteriors highlighting the dependence of the constraints with respect to the total mass of the system.
+In general the tightest bounds are expected to come from the most massive systems, as they tend to have larger post-merger SNR.
+We find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.
 
-Among all the GW signals detected so far, GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{LSC_2016grtests,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
+Among all the GW signals detected so far, GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{TheLIGOScientific:2016src,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
 Within 90\% credibility we obtain from GW150914:
@@
 \input{table_lvc_results}
-\caption{\textcolor{red}{NOT COMPLETE} \comment{AB: We would need to give also the final mass and spins. I would suggest that we list in the Table
-also the results from the TGR GWTC-2 paper, obtained with our method, so that all the results are in one Table.}}
+\caption{The median, and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from the measurements of the QNM frequencies.}
 \label{tab:qnm_o1o2_results}

### 2021-02-02 papers/intro_paper/intro.tex
udpated introduction

@@
 The consistency between the post-merger signal and the least damped QNM was first demonstrated in
-Ref.~\citep{LIGOScientific:2019fp} for GW150914, and later extended to include
-overtones in Refs.~\citep{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
+Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and later extended to include
+overtones in Refs.~\cite{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
 of the late-time waveform with a single QNM is a test of the ringdown of
@@
 BH thermodynamics, like the Hawking's area
-theorem~\citep{Cabero:2017avf} or through search for echos in the
+theorem~\cite{Cabero:2017avf} or through search for echos in the
 post-merger
-signal~\citep{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
+signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
 of these tests have found evidence for non-BH nature of the remnant
@@
 
-Most of the tests mentioned above restrict the data to the post-merger signal and then analyse it.
 Ground-based detectors, such as LIGO and Virgo, are most sensitive to
 stellar-mass BH binaries that merge near the
-minimum of their sensitivity band ($\sim 100$Hz). As a consequence, the
+minimum of their sensitivity band ($\sim100$Hz). As a consequence, the
 remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
 very little signal-to-noise ratio (SNR) in the
-post-merger signal. \comment{AB: This discussion about the starting time of the ringdown starts too abruptly,
-and looks out of context and incomplete. Also, why are we citing only those papers? The matter
-has a long history. There have been calibrations to NR of damped- oscillation signals.}
-The ringdown start time is not a clearly defined
-quantity and has been explored in detail
-in Ref.~\citep{Bhagwat:2017tkm}. In other
-works~\citep{Carullo:2018gah,Carullo:2019flw}, it has been left as a
-free parameter to be estimated directly from the data. Uncertainties
-in estimates of the ringdown start-time, as well as, an overall lack of
+post-merger signal.
+Most of the tests mentioned above restrict the data to this post-merger signal, which signficantly reduces parameter estimation capabilities.
+However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example in \cite{Bhagwat:2017tkm}).
+In some tests, for example \cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time have been left as a
+free parameter to be estimated directly from the data.
+Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter estimation analyses (see \texttt{PyRING} analysis in \cite{Abbott:2020jks}).
+Uncertainties
+in estimates of the ringdown start-time, as well as an overall lack of
 SNR in the post-merger signal, given typical sensitivities of
 ground-based detectors, result in significant statistical uncertainties
-in the measurement of the QNM frequencies.
+in the measurement of the QNM frequencies. And hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
 
 An independent approach to BH spectroscopy, based on the full-signal
-analysis, was introduced in Ref.~\citep{Brito:2018rfr}
+analysis, was introduced in Ref.~\cite{Brito:2018rfr}
 (henceforth referred to as \paperone). Unlike methods that focus only

### 2021-02-02 papers/intro_paper/results_lvc.tex
added reference to SNRs in GWTC-2 TGR

@@
 For the test that we here present, the results shown in~\cite{Abbott:2020jks} only include events which pass a threshold for the median redshifted total mass $\geq 90 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.}.
+post-merger regions $\geq 8$\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
+The SNR values are listed in Table 4 of \cite{Abbott:2020jks}}.
 %

### 2021-02-03 papers/intro_paper/acknowledgements.tex
updated appendix
cite some early QNM papers and reviews

@@
-LIGO Clusters. \comment{AB: Our cluster!!!}
+The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
+We would like to acknowledge the computing resources at the AEI and the LIGO Scientific Collaboration, specifically the Hypatia and CIT clusters.
 R.B.
 acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862.
-This research was supported by the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
+792862, the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001).
+We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).

### 2021-02-03 papers/intro_paper/intro.tex
cite some early QNM papers and reviews

@@
 compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970cc}\abhi{cite some of the other early QNM papers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
+formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Teukolsky:1973ha,Press:1973zz,Chandrasekhar:1975zza,Detweiler:1980gk,Kokkotas:1999bd,Berti:2009kk}\abhi{cite some of the other early QNM papers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
 

### 2021-02-03 papers/intro_paper/acknowledgements.tex
small edit

@@
 acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862, the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001).
+792862, from the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001).
 We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).

### 2021-02-03 papers/intro_paper/intro.tex
a couple or more refs for intro

--- 2021-02-02 papers/intro_paper/intro.tex
@@
 (GR) in the previously unexplored highly-dynamical, and strong field
-regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa}. In GR, a binary black hole (BBH) system is described by
+regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks}. In GR, a binary black hole (BBH) system is described by
 three distinct phases: an early \textit{inspiral}, where the two
 compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970cc}\abhi{cite some of the other early QNM papers} (i.e., damped oscillations with specific, discrete frequencies and decay times).
+formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Teukolsky:1973ha,Press:1973zz,Chandrasekhar:1975zza,Detweiler:1980gk,Buonanno:2000ef,Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv,Kokkotas:1999bd,Berti:2009kk}\abhi{cite some of the other early QNM papers}\rb{added a couple of important early QNM papers but also the NR breakthrough papers and Alessandra's paper on the transition form inspiral to plunge.
+} (i.e., damped oscillations with specific, discrete frequencies and decay times).
 
@@
 first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
-coalescence.
-The LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
+coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}.
+This set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.\rb{slightly modified the previous two sentences to include also cite the GW190521 papers}
 The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely

### 2021-02-03 papers/intro_paper/intro.tex
small edits

@@
 
-The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} provided us with the
-first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
+The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} also provided us with the first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
 coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}.

### 2021-02-05 papers/intro_paper/intro.tex
more refs

@@
 compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Teukolsky:1973ha,Press:1973zz,Chandrasekhar:1975zza,Detweiler:1980gk,Buonanno:2000ef,Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv,Kokkotas:1999bd,Berti:2009kk}\abhi{cite some of the other early QNM papers}\rb{added a couple of important early QNM papers but also the NR breakthrough papers and Alessandra's paper on the transition form inspiral to plunge.
-} (i.e., damped oscillations with specific, discrete frequencies and decay times).
+formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk,Kokkotas:1999bd,Berti:2009kk}\abhi{cite some of the other early QNM papers}\rb{added a couple of important early QNM papers plus standard reviews on QNMs} (i.e., damped oscillations with specific, discrete frequencies and decay times).
 
@@
 coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}.
-This set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.\rb{slightly modified the previous two sentences to include also cite the GW190521 papers}
-The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely
+The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.\rb{slightly modified the previous two sentences to also include the GW190521 papers}
+Measurements of the BH ringdown are particularly important in view the no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} which states that an (electrically neutral) astrophysical BH is completely
 described by two observables: mass and spin angular momentum. One
@@
 consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
+across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}. An inconsistency would either
 indicate a non-BH nature of the remnant object, or an incompleteness
@@
 The consistency between the post-merger signal and the least damped QNM was first demonstrated in
-Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and later extended to include
-overtones in Refs.~\cite{Brito:2018rfr,Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw}. Consistency
-of the late-time waveform with a single QNM is a test of the ringdown of
+Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analysis~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}.
+This was later extended to include
+overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw,Abbott:2020jks}. Consistency of the late-time waveform with a single QNM is a test of the ringdown of
 a BBH coalescence, but not necessarily a test of the no-hair
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work
-also include~\cite{Carullo:2018gah,Carullo:2019flw,Bhagwat:2019bwv}. The
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work on the subject
+also include~\cite{Carullo:2018sfu,Carullo:2018gah,Bhagwat:2019bwv,Cabero:2019zyt}. The
 nature of the remnant object has also been explored through tests of
 BH thermodynamics, like the Hawking's area
-theorem~\cite{Cabero:2017avf} or through search for echos in the
-post-merger
-signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}. None
-of these tests have found evidence for non-BH nature of the remnant
+theorem~\cite{Cabero:2017avf,Isi:2020tac} or through search for echos in the
+post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.  None of these tests have found evidence for non-BH nature of the remnant
 object (as described in GR) in LIGO-Virgo BBH observations.
@@
 definitions. While \paperone presented the method and tested it for non-spinning BBHs, here we extend the analysis to the more
-realistic astrophysical case in which BHs carr spin. Furthermore,
+realistic astrophysical case in which BHs carry spin. Furthermore,
 the IMR waveform model used in this paper is more accurate than what employed in \paperone,

### 2021-02-05 papers/intro_paper/discussion.tex
more refs and writing some ideas in conclusions

--- 2021-01-25 papers/intro_paper/discussion.tex
@@
 Richard and Vivien.}
+
+\rb{Work in progress}
+We extended previous work by building a parameterized IMR waveform model that can be used to measure the QNM complex frequencies of the remnant object formed in BBH mergers with (aligned-)spinning components.
+
+This model had been previously used to analyze BBHs from the GWTC-2~\cite{Abbott:2020jks}.
+Here, we extended those results by also analyzing GW events from the first and second LIGO-Virgo observing runs.
+Our results are the strongest constraints on the frequency and damping time of least-damped QNM obtained so far.
+
+These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects.
+\rb{this is taken from \paperone, needs to be updated:}QNM frequencies of spherically symmetric solutions were computed in theories such as Einstein-Maxwell-dilaton~\cite{Ferrari:2000ep}, dynamical Chern-Simons gravity~\cite{Molina:2010fb}, Einstein-dilaton-Gauss-Bonnet gravity~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk} and for some solutions in massive (bi)gravity~\cite{Brito:2013wya,Brito:2013yxa,Babichev:2015zub}.
+On
+the other hand, not much progress has been made to compute QNMs for
+spinning BHs in alternative theories to GR, the only exception
+being the Kerr-Newman case in Einstein-Maxwell
+theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa}. Most
+of the estimates for QNMs of spinning BHs in modified gravity have
+instead used the connection between the light ring and
+QNMs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo,Glampedakis:2017cgd},
+which is formally only valid in the eikonal $\ell \to \infty$ limit
+and known to fail to describe some families of QNMs when additional
+degrees of freedom are present~\cite{Blazquez-Salcedo:2016enn}.
+
+This work can be improved in several fronts...
+It could be easily extended to generic precessing waveforms.
+Interesting future studies include using this model using waveforms obtained in recent numerical relativity simulations of non-GR theories.

### 2021-02-05 papers/intro_paper/intro.tex
more refs and writing some ideas in conclusions

@@
 The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.\rb{slightly modified the previous two sentences to also include the GW190521 papers}
-Measurements of the BH ringdown are particularly important in view the no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} which states that an (electrically neutral) astrophysical BH is completely
+The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely
 described by two observables: mass and spin angular momentum. One
@@
 The consistency between the post-merger signal and the least damped QNM was first demonstrated in
-Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analysis~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}.
+Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analyses~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}.
 This was later extended to include
@@
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Berti:2005ys}. Recent work on the subject
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv}. Recent work on the subject
 also include~\cite{Carullo:2018sfu,Carullo:2018gah,Bhagwat:2019bwv,Cabero:2019zyt}. The
@@
 Most of the tests mentioned above restrict the data to this post-merger signal, which signficantly reduces parameter estimation capabilities.
-However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example in \cite{Bhagwat:2017tkm}).
+However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in \cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
 In some tests, for example \cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time have been left as a

### 2021-02-15 runs/O3b/TGR/release/utils.py
Revert "added release folder"
This reverts commit 5bd69e1c3acc6cf6d888d1e05f9efa9a50b42d1b

@@ -1,278 +1,0 @@
-import os
-import re
-from glob import glob
-import numpy as np
-from collections import OrderedDict
-import json
-import parse
-
-# ----------------------------------------------------------------------------
-# IO and other
-# ----------------------------------------------------------------------------
-
-def load_cache(param, cache_path):
-    cache_exists = all(os.path.isfile(cache_path.format(par=param, hyper=k)) for
-                       k in ['mu', 'sigma', 'pop'])
-    if cache_exists:
-        cache = {k: np.loadtxt(cache_path.format(par=param, hyper=k)) 
-                 for k in ['mu', 'sigma', 'pop']}
-    else:
-        cache = {}
-    return cache
-
-def save_cache(fits, cache_path, paths=None):
-    for param, fit in fits.items():
-        try:
-            post = fit.extract(['mu', 'sigma', 'pop'])
-        except AttributeError:
-            post = fit
-        for k in ['mu', 'sigma', 'pop']:
-            np.savetxt(cache_path.format(par=param, hyper=k), post[k])
-        print("Cached %s"%  param)
-    # record list of events
-    if paths:
-        cache_dir = os.path.dirname(cache_path)
-        log_path = os.path.join(cache_dir, 'events.json')
-        with open(log_path, 'w') as f:
-            json.dump(paths, f, indent=4)
-        print("Events logged: %r" % log_path)
-        
-def load_data(param, data_path, data_dict=None, path_dict=None):
-    ''' Loads posteriors from individual event runs for a given parameter.
-    
-    Arguments
-    ---------
-    param: str
-        parameter name
-    data_path: str
-        posterior sample path template, 'mypath/post_{par}_{event}.dat.gz'
-    data_dict: dict
-        dictionary to which to add loaded samples (opt.)
-    path_dict: dict
-        dictionary to which to add path information (opt.)
-    
-    Returns
-    -------
-    data_dict: dict
-        dictionary with loaded samples.
-    path_dict: dict
-        dictionary with path information.
-    '''
-    if data_dict is None:
-        data_dict = {}
-    if path_dict is None:
-        path_dict = {}
-    paths = glob(data_path.format(par=param, event='*'))
-    for path in paths:
-        try:
-            label = parse.parse(data_path, path)['event']
-            data_dict[label] = np.loadtxt(path)
-            path_dict[label] = path
-        except AttributeError:
-            pass
-    return data_dict, path_dict
-
[…]

### 2021-02-15 papers/intro_paper/discussion.tex
a bit more conclusions

@@
 \rb{Work in progress}
-We extended previous work by building a parameterized IMR waveform model that can be used to measure the QNM complex frequencies of the remnant object formed in BBH mergers with (aligned-)spinning components.
+In this work, we used a parameterized IMR waveform model to measure the QNM complex frequencies of the remnant object formed in BBH mergers with (aligned-)spinning components, extending previous work where only non-spinning components had been considered~\cite{Brito:2018rfr}.
+We demonstrated that the model can accurately recover the QNM complex frequencies for a selection of simulated GW signals, including a case more than one mode is measurable, and also showed that this test can be used to detect possible deviations from GR in the ringdown part of the signal.
 
-This model had been previously used to analyze BBHs from the GWTC-2~\cite{Abbott:2020jks}.
-Here, we extended those results by also analyzing GW events from the first and second LIGO-Virgo observing runs.
-Our results are the strongest constraints on the frequency and damping time of least-damped QNM obtained so far.
+This model had been previously used to analyze BBHs from the GWTC-2~\cite{Abbott:2020jks}, and we here extended those results by also analyzing GW events from the first and second LIGO-Virgo observing runs.
+We not find any evidence for deviations from GR and even in the most agnostic and conservative scenario, where we combine the information using an hierarchical approach, we constrain the frequency of the least damped QNM to be within $\sim 9\%$ of the GR prediction, whereas the damping time is constrained to be within $\sim 40\%$ of the GR prediction.
+These results provide the most-up-to-date and strongest constraints on the frequency and damping time of least-damped QNM obtained with this model.
+The order-of-magnitude of the constraints we obtain is largely compatible with the ones recently reported in Ref.~\cite{Carullo:2021dui}, where only the post-merger part of the ringdown was analyzed.
 
@@
 
+To constrain the deviations from GR we decided to use the most generic and conservative parametrization, Eqs.~\eqref{eq:nongr_freqs_a} and~\eqref{eq:nongr_freqs_b}, where the fractional deviations $(\delta f_{\ell m0,\delta \tau_{\ell m0}$ are taken to be completely free parameters.
+In principle, this model can also be used with more restricted parametrizations, such as the one proposed in Ref.~\cite{Maselli:2019mjd} and recently applied on LIGO-Virgo events in Ref.
+~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters.
+Other examples also include proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Suvorov:2021amy,Volkel:2020daa} which, as proposed in ~\cite{Volkel:2020daa,Volkel:2020xlc} could be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx}.
+
 This work can be improved in several fronts...

### 2021-02-15 papers/intro_paper/discussion.tex
more conclusions

@@
-\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers
-about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also
-EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al.
-It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with
-Richard and Vivien.}
-
 \rb{Work in progress}
@@
 These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects.
-\rb{this is taken from \paperone, needs to be updated:}QNM frequencies of spherically symmetric solutions were computed in theories such as Einstein-Maxwell-dilaton~\cite{Ferrari:2000ep}, dynamical Chern-Simons gravity~\cite{Molina:2010fb}, Einstein-dilaton-Gauss-Bonnet gravity~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk} and for some solutions in massive (bi)gravity~\cite{Brito:2013wya,Brito:2013yxa,Babichev:2015zub}.
+\rb{this is taken from \paperone, needs to be updated:}
+QNM frequencies of spherically symmetric solutions were computed in theories such as Einstein-Maxwell-dilaton~\cite{Ferrari:2000ep}, dynamical Chern-Simons gravity~\cite{Molina:2010fb}, Einstein-dilaton-Gauss-Bonnet gravity~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk} and for some solutions in massive (bi)gravity~\cite{Brito:2013wya,Brito:2013yxa,Babichev:2015zub}.
 On
@@
 degrees of freedom are present~\cite{Blazquez-Salcedo:2016enn}.  
+EFT~\cite{Franciolini:2018uyq,Cano:2020cao,Cardoso:2018ptl}, ECO~\cite{Maggio:2020jml}
 
-To constrain the deviations from GR we decided to use the most generic and conservative parametrization, Eqs.~\eqref{eq:nongr_freqs_a} and~\eqref{eq:nongr_freqs_b}, where the fractional deviations $(\delta f_{\ell m0,\delta \tau_{\ell m0}$ are taken to be completely free parameters.
-In principle, this model can also be used with more restricted parametrizations, such as the one proposed in Ref.~\cite{Maselli:2019mjd} and recently applied on LIGO-Virgo events in Ref.
+To constrain the deviations from GR we decided to use the most generic and conservative parametrization, Eqs.~\eqref{eq:nongr_freqs_a} and~\eqref{eq:nongr_freqs_b}, where the fractional deviations $(\delta f_{\ell m0},\delta \tau_{\ell m0})$ are taken to be completely free parameters.
+In principle, this model can also be used with other, more restricted, parametrizations that could help to map constraints on the QNM complex frequencies to constraints in specific beyond-GR theories.
+This includes for example the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently applied to LIGO-Virgo GW events in Ref.
 ~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters.
-Other examples also include proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Suvorov:2021amy,Volkel:2020daa} which, as proposed in ~\cite{Volkel:2020daa,Volkel:2020xlc} could be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx}.
+Other examples also include proposals to write the deviations from GR in terms of a small parametrized deviations of the perturbation equations~\cite{Cardoso:2019mqo,McManus:2019ulj} or proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Suvorov:2021amy,Volkel:2020daa}.
+As proposed in~\cite{Volkel:2020daa,Volkel:2020xlc} constraints on the BH metric using QNM measurements could then also be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx}.
 
-This work can be improved in several fronts...
-It could be easily extended to generic precessing waveforms.
-Interesting future studies include using this model using waveforms obtained in recent numerical relativity simulations of non-GR theories.
+Generalization to generic precessing waveforms is straightforward and could be done using the recently developed model reported in Ref.~\cite{Ossokine:2020kjp}.
+
+Finally, it would also be important to test our model against waveforms obtained with numerical relativity simulations of specific beyond-GR theories.
+Such simulations are however extremely challenging to do (when at all possible), and have so far only been done for a handful of theories, focusing mostly on proof-of-concept simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}.
+Nonetheless, given the recent efforts put forward in order to simulate BBHs in beyond-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.

### 2021-02-16 data/rin/S190521r/read_hdf5.py
added notebook to compute mtotal,qnm params degeneracy

@@ -1,0 +1,5 @@
+import h5py as h5
+
+data = "rin_S190521r_pseobnrv4hm.h5"
+
+f = h5.File(data)

### 2021-02-16 papers/intro_paper/discussion.tex
conclusions

@@
 \rb{Work in progress}
-In this work, we used a parameterized IMR waveform model to measure the QNM complex frequencies of the remnant object formed in BBH mergers with (aligned-)spinning components, extending previous work where only non-spinning components had been considered~\cite{Brito:2018rfr}.
-We demonstrated that the model can accurately recover the QNM complex frequencies for a selection of simulated GW signals, including a case more than one mode is measurable, and also showed that this test can be used to detect possible deviations from GR in the ringdown part of the signal.
+We demonstrated how a parameterized IMR waveform model can be used to measure the QNM complex frequencies of the remnant object formed in BBH mergers.
+Our model can be used for BBHs with (aligned-)spinning components, which extends previous work where a similar model for non-spinning components had been considered~\cite{Brito:2018rfr}.
+We showed that this model can accurately recover the QNM complex frequencies of simulated GW signals in the LIGO and Virgo detectors.
+Our results also demonstrate that this model can be used to perform tests of the no-hair conjecture and can also be used to detect possible deviations from GR in the ringdown part of the signal.
 
-This model had been previously used to analyze BBHs from the GWTC-2~\cite{Abbott:2020jks}, and we here extended those results by also analyzing GW events from the first and second LIGO-Virgo observing runs.
-We not find any evidence for deviations from GR and even in the most agnostic and conservative scenario, where we combine the information using an hierarchical approach, we constrain the frequency of the least damped QNM to be within $\sim 9\%$ of the GR prediction, whereas the damping time is constrained to be within $\sim 40\%$ of the GR prediction.
-These results provide the most-up-to-date and strongest constraints on the frequency and damping time of least-damped QNM obtained with this model.
-The order-of-magnitude of the constraints we obtain is largely compatible with the ones recently reported in Ref.~\cite{Carullo:2021dui}, where only the post-merger part of the ringdown was analyzed.
+This model had been previously used to analyze BBHs from the first half of LIGO-Virgo's third observing run~\cite{Abbott:2020jks}.
+We extended these results by analyzing GW events from the first and second LIGO-Virgo observing runs and updated the joint measurements on the fractional deviations in the frequency and damping time of the least-damped QNM.
+As expected, the event providing the best constraint on the least-damped QNM to be date continues to be GW150914 [see \eqref{GW150914_delta}].
+In addition, even in the most agnostic and conservative scenario where we combine the information from different events using an hierarchical approach, at $90\%$ credibility, we constrain the frequency of the least damped QNM to be within $\sim 9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$ over the results reported in~\cite{Abbott:2020jks}.
+The order-of-magnitude of the constraints we obtain is largely compatible with the ones recently reported in Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done using only the post-merger part of the ringdown was analyzed.
 
-These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects.
-\rb{this is taken from \paperone, needs to be updated:}
-QNM frequencies of spherically symmetric solutions were computed in theories such as Einstein-Maxwell-dilaton~\cite{Ferrari:2000ep}, dynamical Chern-Simons gravity~\cite{Molina:2010fb}, Einstein-dilaton-Gauss-Bonnet gravity~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk} and for some solutions in massive (bi)gravity~\cite{Brito:2013wya,Brito:2013yxa,Babichev:2015zub}.
-On
-the other hand, not much progress has been made to compute QNMs for
-spinning BHs in alternative theories to GR, the only exception
-being the Kerr-Newman case in Einstein-Maxwell
-theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa}. Most
-of the estimates for QNMs of spinning BHs in modified gravity have
-instead used the connection between the light ring and
-QNMs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo,Glampedakis:2017cgd},
-which is formally only valid in the eikonal $\ell \to \infty$ limit
-and known to fail to describe some families of QNMs when additional
-degrees of freedom are present~\cite{Blazquez-Salcedo:2016enn}.  
-EFT~\cite{Franciolini:2018uyq,Cano:2020cao,Cardoso:2018ptl}, ECO~\cite{Maggio:2020jml}
+These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects (see e.g.~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}).
+However, QNM computations in beyond-GR theories have only been done in an handful of case, mostly focusing on non-rotating or slowly-rotating BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao} or relied on the eikonal/geometric optics approximation to obtain estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}.
+The only exceptions to this rule are computations of the QNM of Kerr-Newman BHs in Einstein-Maxwell theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} and estimates of the BBH ringdown in beyond-GR theories obtained through numerical simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}.
 
@@
 ~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters.
-Other examples also include proposals to write the deviations from GR in terms of a small parametrized deviations of the perturbation equations~\cite{Cardoso:2019mqo,McManus:2019ulj} or proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Suvorov:2021amy,Volkel:2020daa}.
-As proposed in~\cite{Volkel:2020daa,Volkel:2020xlc} constraints on the BH metric using QNM measurements could then also be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx}.
+Other examples also include proposals to write the deviations from GR in terms of a small parametrized deviations of the perturbation equations~\cite{Cardoso:2019mqo,McManus:2019ulj} or proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa}.
+As proposed in~\cite{Volkel:2020daa,Volkel:2020xlc} constraints on the BH metric using QNM measurements could then also be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
 
-Generalization to generic precessing waveforms is straightforward and could be done using the recently developed model reported in Ref.~\cite{Ossokine:2020kjp}.
-
-Finally, it would also be important to test our model against waveforms obtained with numerical relativity simulations of specific beyond-GR theories.
+It would also be important to test our model against waveforms obtained with numerical relativity simulations of specific beyond-GR theories.
 Such simulations are however extremely challenging to do (when at all possible), and have so far only been done for a handful of theories, focusing mostly on proof-of-concept simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}.
 Nonetheless, given the recent efforts put forward in order to simulate BBHs in beyond-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.
+
+Finally, an obvious generalization of this work would be to extend the parameterized IMR model to generic precessing BBHs, which can in principle be easily done using the recently developed multipolar EOB model reported in Ref.~\cite{Ossokine:2020kjp}.

### 2021-02-16 papers/intro_paper/appendix.tex
updated appendix
finished first draft of conclusions

@@
 While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-The black curve corresponds to the measurements of the real event GW190521 reported in~\ref{Abbott:2020jks}.
+The black curve corresponds to the measurements of the real event GW190521 reported in~\cite{Abbott:2020jks}.
 All signals are recovered using the $\pSEOB$ waveform model.}
@@
 The fact that the measurement of ringdown quantities are robust against an incomplete understanding of the inspral of a GW signal, is indeed one of the most strong points of our model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+        \includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_GW150914.pdf}\includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_S190521g.pdf}
+        \caption{Left panel: GW150914, Right panel: GW190521. Describe the correlations in this caption}
+        \label{fig:correlations}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-02-16 papers/intro_paper/discussion.tex
finished first draft of conclusions

@@
-\rb{Work in progress}
-We demonstrated how a parameterized IMR waveform model can be used to measure the QNM complex frequencies of the remnant object formed in BBH mergers.
-Our model can be used for BBHs with (aligned-)spinning components, which extends previous work where a similar model for non-spinning components had been considered~\cite{Brito:2018rfr}.
-We showed that this model can accurately recover the QNM complex frequencies of simulated GW signals in the LIGO and Virgo detectors.
-Our results also demonstrate that this model can be used to perform tests of the no-hair conjecture and can also be used to detect possible deviations from GR in the ringdown part of the signal.
+We built a parameterized IMR waveform model that can be used to measure the QNM complex frequencies of the remnant object formed in BBH mergers.
+This model can be used to analyze any BBH with (aligned-)spinning components, which constitute an important extension of previous work where a similar model for non-spinning components had been considered~\cite{Brito:2018rfr}.
+We showed that this test can be used to accurately recover the QNM complex frequencies of simulated GW signals in the LIGO and Virgo detectors.
+We also demonstrated that this model can be used to perform tests of the no-hair conjecture and can also be used to detect possible small deviations from GR in the ringdown part of the signal.
 
@@
 In addition, even in the most agnostic and conservative scenario where we combine the information from different events using an hierarchical approach, at $90\%$ credibility, we constrain the frequency of the least damped QNM to be within $\sim 9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$ over the results reported in~\cite{Abbott:2020jks}.
-The order-of-magnitude of the constraints we obtain is largely compatible with the ones recently reported in Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done using only the post-merger part of the ringdown was analyzed.
+The constraints we obtain on the frequencies and damping time of the least damped QNM are compatible with the ones recently reported in Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done using only the post-merger part of the signal was analyzed.
 
 These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects (see e.g.~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}).
-However, QNM computations in beyond-GR theories have only been done in an handful of case, mostly focusing on non-rotating or slowly-rotating BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao} or relied on the eikonal/geometric optics approximation to obtain estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}.
-The only exceptions to this rule are computations of the QNM of Kerr-Newman BHs in Einstein-Maxwell theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} and estimates of the BBH ringdown in beyond-GR theories obtained through numerical simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}.
+However, QNM computations in beyond-GR theories have only been done in an handful of cases, mostly focusing on non-rotating or slowly-rotating BH solutions (see e.g.~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao}) or relying on the eikonal/geometric optics approximation to obtain estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}.
+The only exceptions to this rule, that we are aware of, are computations of the QNM of Kerr-Newman BHs in Einstein-Maxwell theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} and estimates of the BBH ringdown in beyond-GR theories obtained through a limited number of numerical simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}.
+Given these limitations, our ability of going beyond a  null test of GR and use our results to impose precise constraints on beyond-GR theories with QNM measurements is at this moment quite limited.
 
-To constrain the deviations from GR we decided to use the most generic and conservative parametrization, Eqs.~\eqref{eq:nongr_freqs_a} and~\eqref{eq:nongr_freqs_b}, where the fractional deviations $(\delta f_{\ell m0},\delta \tau_{\ell m0})$ are taken to be completely free parameters.
-In principle, this model can also be used with other, more restricted, parametrizations that could help to map constraints on the QNM complex frequencies to constraints in specific beyond-GR theories.
+Despite these limitations there has been some recent effort to develop parametrizations that could help mapping measurements of the parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0}))$ onto constraints to specific beyond-GR theories.
 This includes for example the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently applied to LIGO-Virgo GW events in Ref.
-~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters.
-Other examples also include proposals to write the deviations from GR in terms of a small parametrized deviations of the perturbation equations~\cite{Cardoso:2019mqo,McManus:2019ulj} or proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa}.
-As proposed in~\cite{Volkel:2020daa,Volkel:2020xlc} constraints on the BH metric using QNM measurements could then also be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
+~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters, or the proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where deviations from the GR QNMs are mapped onto generic small modifications of the perturbation equations describing the QNMs.
+Other examples also include proposals to map deviations from the GR QNMs to coefficients in generic effective field theory actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to directly relate measurements of the QNM complex frequencies to a parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which could be used jointly with measurements coming from the Event Horizon Telescope to obtain stronger constraints on deviations from GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
+We should note, however, that all these parametrizations are either limited to non-spinning BHs or make use of a series expansion in the BH spin which might limit their accuracy for highly-spinning BHs.
 
-It would also be important to test our model against waveforms obtained with numerical relativity simulations of specific beyond-GR theories.
-Such simulations are however extremely challenging to do (when at all possible), and have so far only been done for a handful of theories, focusing mostly on proof-of-concept simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}.
+In the future, it would also be important to test whether this model could be used to detect deviations in waveforms obtained through numerical relativity simulations of specific beyond-GR theories.
+Such simulations are still at their infancy and have so far only been done for a handful of theories, focusing mostly on proof-of-concept simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}.
 Nonetheless, given the recent efforts put forward in order to simulate BBHs in beyond-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.

### 2021-02-16 papers/intro_paper/discussion.tex
conclusions

@@
 
-Despite these limitations there has been some recent effort to develop parametrizations that could help mapping measurements of the parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0}))$ onto constraints to specific beyond-GR theories.
+Despite these limitations there has been some recent effort to develop parametrizations that could help mapping measurements of the parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto constraints to specific beyond-GR theories.
 This includes for example the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently applied to LIGO-Virgo GW events in Ref.
 ~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters, or the proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where deviations from the GR QNMs are mapped onto generic small modifications of the perturbation equations describing the QNMs.
-Other examples also include proposals to map deviations from the GR QNMs to coefficients in generic effective field theory actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to directly relate measurements of the QNM complex frequencies to a parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which could be used jointly with measurements coming from the Event Horizon Telescope to obtain stronger constraints on deviations from GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
+Other examples also include proposals to map deviations from the GR QNMs to coefficients in generic effective field theory actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to directly relate measurements of the QNM complex frequencies to a parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which could be then used jointly with measurements coming from the Event Horizon Telescope to obtain stronger constraints on deviations from GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
 We should note, however, that all these parametrizations are either limited to non-spinning BHs or make use of a series expansion in the BH spin which might limit their accuracy for highly-spinning BHs.

### 2021-03-01 papers/intro_paper/results_lvc.tex
conclusions
more text about hierarchical method

@@
 %
-\begin{equation}
+\begin{equation}\label{GW150914_delta}
 \df{220}=0.04^{+0.06}_{-0.04}\,\quad \dtau{220}=0.09^{+0.18}_{-0.18}\,.
@@
 Following~\cite{Zimmerman:2019wzo,Isi:2019asy,Abbott:2020jks} we model the population distribution with a Gaussian  $\mathcal{N}(\mu,\sigma)$ of unknown mean $\mu$ and standard deviation $\sigma$.
-We can then obtain a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for the hyperparameters $\mu$ and $\sigma$ from a joint analysis of all the GW events~\cite{Isi:2019asy}.
-We use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $.
-%
-Finally, the distribution for a given non-GR parameter $\xi_{\text{nGR}}$ is then be obtained by computing~\cite{Isi:2019asy}
+Under those assumptions, the goal is then to directly measure a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for $\mu$ and $\sigma$ from a joint analysis of all the GW events.
+If GR is correct, then this posterior should be consistent with $\mu=0$ and $\sigma=0$.
+From Bayes' theorem it follows that~\cite{Isi:2019asy}:
 %
 \begin{equation}
-P(\xi_{\text{nGR}} | \{d_j\}) = \int P(\xi_{\text{nGR}} |\, \mu, \sigma)\,P(\mu, \sigma |  \{d_j\})\,d\mu\,d\sigma \,,
+P(\mu, \sigma |  \{d_j\}) \propto P(\mu,\sigma)\prod _{j=1}^N P(d_j |\, \mu, \sigma) \,,
 \end{equation}
 %
-where $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$.
+where $P(\mu,\sigma)$ is the prior (also known as hyperprior) on ($\mu,\sigma$), and $P(d_j | \mu, \sigma) $ can be written in terms of the individual likelihoods of a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}
+%
+\begin{equation}
+P(d_j | \mu, \sigma) = \int P(d_j |\, \xi_{\text{nGR}})  P(\xi_{\text{nGR}} |\, \mu, \sigma) \,d\xi_{\text{nGR}} \,.
+\end{equation}
+%
+Here $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$ by construction and $P(d_j |\, \xi_{\text{nGR}})$ is the likelihood for the parameter $\xi_{\text{nGR}}$ for a given event $d_j$ that is computed from the standard parameter estimation analysis.
+After obtaining $P(\mu, \sigma |  \{d_j\})$, we can then infer a population distribution for a given non-GR parameter $\xi_{\text{nGR}}$ using:~\cite{Isi:2019asy}
+%
+\begin{equation}\label{hier_combine}
+P(\xi_{\text{nGR}} | \{d_j\}) = \int P(\xi_{\text{nGR}} |\, \mu, \sigma)\,P(\mu, \sigma |  \{d_j\})\,d\mu\,d\sigma \,.
+\end{equation}
+%
+Notice that, if we fix $\sigma=0$, this approach is equivalent to assume that all events share the same non-GR parameter $\xi_{\text{nGR}} =\mu$ and~\eqref{hier_combine} reduces to the joint likelihood~\cite{Zimmerman:2019wzo}.
+In practice, we use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $ and compute $P(\xi_{\text{nGR}} | \{d_j\})$.
+
 The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained through this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:

### 2021-03-08 papers/intro_paper/PA_paper_section/pa_tgr_section.tex
added first draft for PA TGR section

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{times}
\usepackage{xspace}
\usepackage[varg]{txfonts}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{makecell}

\definecolor{LinkColor}{rgb}{0.75, 0, 0}
\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
\definecolor{UrlColor}{rgb}{0, 0, 0.75}
\hypersetup{linkcolor=LinkColor}
\hypersetup{citecolor=CiteColor}
\hypersetup{urlcolor=UrlColor}
\usepackage{perpage}
\MakePerPage{footnote}

\newcommand{\paperone}{Paper~I\xspace}
\newcommand{\abhi}[1]{\textcolor{Emerald}{[AG: #1]}}
\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
\newcommand{\macro}[1]{\textcolor{orange}{\textbf{#1}}}

\newcommand{\h}{\mathpzc{h}}
\newcommand{\Hhat}{\hat{\mathpzc{H}}}
\newcommand{\B}{\mathpzc{B}}
\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
\newcommand{\xilm}{\xi_{\ell m}}
\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
\newcommand{\Y}{{Y}^{-2}}
\newcommand{\hc}{h_\times}
\newcommand{\hp}{h_+}
\newcommand{\Fc}{F_\times}
\newcommand{\Fp}{F_+}
\newcommand{\Mf}{M_f}
\newcommand{\cA}{\mathpzc{A}}
\newcommand{\lm}{_{\ell m}}
\newcommand{\deff}{d_\mathrm{eff}}
\newcommand{\rmi}{\mathrm{i}}
\newcommand{\blambda}{\bm{\lambda}}
\newcommand{\btheta}{\bm{\theta}}
\newcommand{\bxi}{\bm{\xi}}
\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
\newcommand{\bzeta}{\bm{\zeta}}
\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
\newcommand{\Mo}{M_{\odot}}
\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
\newcommand{\FF}{\mathrm{FF}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\rhoopt}{\rho_\mathrm{opt}}
\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
\newcommand{\fqnm}{f}
\newcommand{\sigmaqnm}{\sigma}
\newcommand{\n}{\mathbf{n}}
\newcommand*{\skymapscale}{0.5}
\newcommand*{\paramestscale}{0.455}
\newcommand{\df}[1]{\delta f_{\text{#1}}}
\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
\newcommand{\fngr}[1]{f_{\text{#1}}}
\newcommand{\taungr}[1]{\tau_{\text{#1}}}
\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
\newcommand{\pSEOB}{\texttt{pSEOBNR}}
\newcommand{\SEOB}{\texttt{SEOBNR}}

\begin{document}

%%%%%%%%%%%%%%%%%
\section{TGR: The \textsc{pSEOBNRv4HM} analysis}
\label{sec:pa_tgr}
Optimisations in waveform generation presented in this paper not only benefit gravitational wave detection and parameter estimation, but would also speed up downstream inferences in astrophysics, cosmology and fundamental physics. We demonstrate this expedition on one of the ringdown tests of general relativity previously discussed in ~\cite{Ghosh:2016xx:prep,Abbott:2020jks,Brito:2018rfr}. The $\pSEOB$ ringdown analysis uses a parameterised version of a full inspiral-merger-ringdown gravitational wave signal model to measure and constrain the (complex) QNM frequencies. Consequently, unlike other ringdown studies restricted to the post-merger signal, the $\pSEOB$ analysis makes use of the entire signal power and does not suffer from the ambiguity of a ringdown start-time definition. However, the current implementation of the test uses the time-domain \texttt{SEOBNRv4HM}~\cite{Cotesta:2018fcv} waveform model and is computationally expensive, especially since every iteration of the parameter estimation sampler requires the generation of a complete inspiral-merger-ringdown waveform. This also makes the $\pSEOB$ analysis an ideal candidate for testing post-adaibatic optimisations.
\par
In the \texttt{SEOBNRv4HM} model, starting from estimates of the initial binary's masses and spins, numerical relativity fits~\cite{Taracchini:2013rva,Hofmann:2016yih} are used to predict the mass and spin of the remnant object, which are then used to predict the ringdown frequencies and damping times, $(f_{\ell m 0}^{\text{GR}}, \tau _{\ell m 0}^{\text{GR}})$~\cite{Berti:2005ys,Berti:2009kk}. In the parameteretised model, (\texttt{pSEOBNRv4HM}), the frequency and damping times, $(f_{\ell m 0}, \tau _{\ell m 0})$ are described through fractional deviations, $(\delta
\hat{f}_{\ell m 0},\delta \hat{\tau}_{\ell m 0})$, from the corresponding GR predictions as:
\begin{eqnarray}
f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta \hat{f}_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \hat{\tau}_{\ell m 0})\,. \label{eq:nongr_freqs_b}
\end{eqnarray}
and left as free parameters in the model, to be directly estimated from the data instead of being predicted using NR fits. A comparison of the measurements of the frequency and damping time for the least-damped QNM for GW150914, $(f_{220},\tau_{220})$, using a version of \texttt{pSEOBNRv4HM} with ("PA") and without ("non-PA") post-adaibatic optimisations is shown in the left panel of Fig.~\ref{fig:pa_nonpa_tgr}. The \texttt{pSEOBNRv4HM} waveform model contains information from $(l,m)=(2,2), (2,1),(3,3), (4,,4)$ and $(5,5)$ modes. For a quasi-equal high-mass binary like GW150914, contributions from higher multipoles of the GW signal are expected to be negligible. Hence, we restrict our analysis to just the least-damped dominant QNM, i.e., $(f_{220},\tau_{220})$, keeping the other QNMs fixed at their nominal GR values. We find that the model with post-adiabatic optimisations faithfully reproduces results without them. However, as shown in the right panel of Fig.~\ref{fig:pa_nonpa_tgr}, the speed-up is significant. Fitting a straight line through the points in the period between when each run started accumulating samples and/or was terminated, the slope of the PA run is roughly 8 times steeper than the non-PA run. In other words, the PA run accumulated samples at a rate 8 times faster than then non-PA run.
\par
With focus shifting from analyses of individual events to population studies, demands on computational resources and person-power are ever-increasing, as demonstrated by large-scale studies in LVK catalog papers CITE(PE/astro-imp/TGR catalog papers). Hence, such increases in computational efficiency is immensely important for the future of GW data analysis.

% Figure for pSEOBNR
\begin{figure*}
  \centering
  \includegraphics[height=5cm]{GW150914_actual_PA_nonPA_fngrtaungr}\includegraphics[height=5cm]{GW150914_actual_PA_nonPA_benchmarking}
  \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the frequency and damping time of the $(2,\pm 2)$ QNM, $(f_{220},\tau_{220})$ and their corresponding one-dimensional marginalized posterior distributions, for GW150914. \emph{Right panel}: Accumulation of samples over time, usng the PA and non-PA models. The black vertical dashed line indicates the point at which the PA run was terminated. The magenta (green) dashed line represents a straight line fitted to the PA (non-PA) points, restricted to the period over which the run accummulated samples. The PA run accumulated samples roughly 8 times faster than the non-PA run.}
  \label{fig:pa_nonpa_tgr}
\end{figure*}

%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%
\bibliographystyle{apsrev}
\bibliography{pa_tgr_section}
%%%%%%%%%%%%%%%%%

\end{document}

### 2021-03-17 papers/intro_paper/intro.tex
changes in title and Sec. I

@@
-\comment{AB: Please make the citations in the bibliography uniform (I would stick with citations
-taken from InSpires and remove the URL links). We will be submitting to Physical Review D, so please
-stick with American English. Also, please be uniform when writing captions, when using colors and style
-of curves in plots, when building Tables. There is not a lot of discussion in the text on the main results of the paper (Sec. IV).
-The abstract would need to be tighten and made more crispy once the quantitative results for the
-bounds are included.}
-
-\abhi{The main body can now be considered stable in terms of text and results. Some of the fine tuning mentioned above,eg, reference formatting, cosmetic changes, etc are currently ongoing.}
-
-\abhi{All macros in the paper are currently highlighted in orange, and would require one final check before final draft.}
-
 The LIGO Scientific Collaboration~\cite{lsc} and the Virgo
@@
 regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}, where the two
-compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
-formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk,Kokkotas:1999bd,Berti:2009kk}\abhi{cite some of the other early QNM papers}\rb{added a couple of important early QNM papers plus standard reviews on QNMs} (i.e., damped oscillations with specific, discrete frequencies and decay times).
+three distinct phases: an early \textit{inspiral}~\cite{Blanchet:2013haa}, where the two
+compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger}~\cite{Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv} marked by the
+formation of a common apparent horizon, and a \textit{ringdown}~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs) (i.e., damped oscillations with specific, discrete frequencies and decay times).
+\comment{AB: I have left only  the QNM refs until 80s, and added the main refs for ``inspiral'' and ``merger''.
+I found the citation unbalanced.}
 
 The LIGO-Virgo collaborations have released companion papers detailing their results
-of tests of GR for GW150914 \cite{TheLIGOScientific:2016src} and for several GW events of
+of tests of GR for GW150914 \cite{TheLIGOScientific:2016src}, and for several GW events of
 the two transient catalogues (TC): GWTC-1 \cite{LIGOScientific:2018mvr,LIGOScientific:2019fpa}  and GWTC-2 \cite{Abbott:2020niy,Abbott:2020jks}.
@@
 parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral and
+the early inspiral, and
 phenomenological coefficients describing the intermediate (plunge) and
@@
 coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}.
-The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.\rb{slightly modified the previous two sentences to also include the GW190521 papers}
-The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely
-described by two observables: mass and spin angular momentum. One
+The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
+The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin angular momentum \ab{(for short spin)}.
+One
 consequence of the no-hair conjecture is that the (complex) QNM
 frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin angular momentum. Hence
+BH are uniquely determined by its mass and spin. Hence
 a test of the no-hair conjecture would involve checking for
@@
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv}. Recent work on the subject
-also include~\cite{Carullo:2018sfu,Carullo:2018gah,Bhagwat:2019bwv,Cabero:2019zyt}. The
+spectroscopy), and consistency between \ab{them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}}. The
 nature of the remnant object has also been explored through tests of
@@
 stellar-mass BH binaries that merge near the
-minimum of their sensitivity band ($\sim100$Hz). As a consequence, the
+minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the
 remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
@@
 post-merger signal.
-Most of the tests mentioned above restrict the data to this post-merger signal, which signficantly reduces parameter estimation capabilities.
-However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in \cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
-In some tests, for example \cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time have been left as a
+Most of the tests mentioned above restrict the data to this post-merger signal, which signficantly reduces parameter-estimation capabilities.
+However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
+In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a
 free parameter to be estimated directly from the data.
-Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter estimation analyses (see \texttt{PyRING} analysis in \cite{Abbott:2020jks}).
+Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{PyRING} analysis in Ref.~\cite{Abbott:2020jks}).
 Uncertainties
@@
 waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
-complex QNM frequencies with our parameterized model within a Bayesian formalism. Then, in Sec.~\ref{sec:results},
-we demonstrate our method on real GW events, as well as simulated signals. In particular, we analyze
-the GWTC 1/2  events and constrain the QNM frequecies to be \macro{$\df{220} = 0.02^{+0.03}_{-0.03}$} and \macro{$\dtau{220} = 0.11 ^{+0.12} _{-0.12}$}.
-Finally, in Sec.~\ref{sec:discussion} we provide a summary of
+complex QNM frequencies with our parameterized model within a Bayesian formalism\ab{, and validate it using 
+several synthetic-signal injection studies in Gaussian noise}. Then, in Sec.~\ref{sec:results},
+we \sout{demonstrate} \ab{apply}  our method on real GW events \ab{using LIGO and Virgo data}.\sout{, as well as simulated signals}. In particular, we analyze
+the GWTC 1/2  events and \ab{obtain the most stringent constraints on the dominant (complex)} QNM frequecies \ab{with our method}\sout{to be \macro{$\df{220} = 0.02^{+0.03}_{-0.03}$} and \macro{$\dtau{220} = 0.11 ^{+0.12} _{-0.12}$}}.
+\comment{AB: I think it is too early to give the results here.} Finally, in Sec.~\ref{sec:discussion} we provide a summary of
 our results and discuss future developments.

### 2021-03-17 papers/intro_paper/intro_paper.tex
updated results_synthetic section
updated results section
updated synthetic results section
updated abstract and introduction; added references
udpated introduction
changes in title and Sec. I

@@
 %\linenumbers
+\usepackage{makecell}
 
@@
 \newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{red}{[\textit{AG: #1}]}}
+\newcommand{\abhi}[1]{\textcolor{Emerald}{[AG: #1]}}
 \newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
@@
 \newcommand{\comment}[1]{\textcolor{red}{[#1]}}
+\newcommand{\macro}[1]{\textcolor{orange}{\textbf{#1}}}
 
@@
 
-\title{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}
+\title{\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}} 
+%by making full use of gravitational-wave modeling}
 
@@
 %%%%%%%%%%%%%%%%%
-\ab{\section{Synthetic-signal injection study}}
+\section{Synthetic-signal injection study}
 \label{sec:results}
@@
 %%%%%%%%%%%%%%%%%
-\ab{\section{Constraints on QNM frequencies using LIGO-Virgo data}}
+\section{Constraints on QNM frequencies using LIGO-Virgo data}
 \input{results_lvc}

### 2021-03-17 papers/intro_paper/model_method.tex
more refs
changes in title and Sec. IIa

@@
 A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by a $15$ parameters,
+completely described in GR by $15$ parameters,
 $\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
@@
 Here, we focus on BHs with spins aligned or anti-aligned
-with the orbital angular momentum (henceforth, ``aligned-spin''). In this case,
+with the orbital angular momentum (henceforth, aligned-spin). In this case,
 the GW signal depends on $11$ parameters. We denote the
@@
 As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB)
-formalism. However, whereas \paperone was limited to non-spinning multipolar waveforms,
+formalism~\cite{Buonanno:1998gg,Buonanno:2000ef}. However, whereas \paperone was limited to non-spinning multipolar waveforms,
 here we use as our baseline model the aligned-spin multipolar waveform model
@@
 %
-where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
+where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
 The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
@@
 damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) is defined through the fractional deviations, $(\delta
+_{\ell m 0})$) are defined through the fractional deviations, $(\delta
 f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values, which are obtained using NR fits~\cite{Taracchini:2013rva,Hofmann:2016yih}. Thus,
+values.\sout{, which are obtained using NR fits}
+Thus~\cite{Gossan:2011ha,Meidam:2014jpa},
 \begin{eqnarray}
@@
 
-As said, the GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the same NR--fitting--formula
-described above. We note that when leaving $\sigma_{\ell m}$ to vary
+\sout{As said,} The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+constructed using the \sout{same} NR--fitting--formula \ab{from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}}.
+\sout{described above.} We note that when leaving $\sigma_{\ell m}$ to vary
 freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
@@
 from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
-(\ref{c2}), and (\ref{d1}).
+(\ref{c2}), and (\ref{d1}). \ab{As a consequence, the ringdown signal (amplitude and phase) 
+soon after merger deviates from the one predicted by GR.}
 

### 2021-03-17 papers/intro_paper/model_method.tex
changes in title and Sec. II

@@
 %
-\begin{equation}
+\begin{subequations}
+\begin{eqnarray}
 \label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) = c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},
-\end{equation}
-%
-\begin{equation}
+\tilde{A}_{\ell m}(t) &=& c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},\\
 \label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) = \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{equation}
+\tilde{\phi}_{\ell m}(t) &=& \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
+\end{eqnarray}
+\end{subequations}
 %
@@
 %
+\begin{subequations}
 \begin{align}
@@
 \end{align}
+\end{subequations}
 and $d_{1,c}^{\ell m}$ as
@@
 Thus~\cite{Gossan:2011ha,Meidam:2014jpa},
+\begin{subequations}
 \begin{eqnarray}
@@
 \end{eqnarray}
+\end{subequations}
 We denote such a parameterized waveform model $\pSEOB$~\footnote{This
@@
 %
-where $\langle . | . \rangle$ is the following noise-weighted inner product:
+where $\langle . | . \rangle$ is the usual noise-weighted inner product:
 %
@@
 We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency and we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
+GW detector at low-frequency.
+Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
 Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
@@
 to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and all the other $(\ell m)$ modes to be
-fixed at their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
+\{\df{330},\dtau{330}\}$, and \ab{fix} all the other $(\ell m)$ modes to \sout{be
+fixed at} their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
 \tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH

### 2021-03-17 papers/intro_paper/model_method.tex
changes in Sec. I

@@
 $\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
+the \ab{(source)} masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
 objects in the binary; and the
@@
 described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$,
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
+polarization $\psi$. We also introduce the total \ab{(source)} mass $M = m_1+m_2$,
+and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$. \ab{When needed, 
+we shall denote the detector masses as $m_{1,\rm det}= (1+z)\,m_1$ and $m_{2,\rm det} = (1+z)\,m_2$, 
+where $z$ is the redshift.}
 

### 2021-03-17 papers/intro_paper/results_synthetic.tex
minor update
changes in Sec. IIIB

@@
 
-We demonstrate our method using synthetic-signal injections describing GWs
-from BBHs in GR. We employ coloured Gaussian noise with PSDs expected for LIGO and
-Virgo detectors at design sensitivities~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
+We \ab{now} demonstrate our method using synthetic-signal injections describing GWs
+from BBHs in GR. We employ coloured Gaussian noise with PSDs for LIGO and
+Virgo detectors \ab{during the fourth observing (O4) run} (i.e., at design sensitivity)\ab{, which 
+is expected to start yin the second half of 2022}~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
 For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
@@
         \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for GR injections with initial parameters similar to GW150914 (top panels) and GW190521 (bottom panels) (Table~\ref{tab:injection_values}).
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.}
+        \caption{\textcolor{red}{FINAL RESULT} Posterior probability
+          distribution on the fractional deviations in the frequency
+          and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$
+          (left panels) and the reconstructed quantities,
+          $(\fngr{220}, \taungr{220})$ (right panels) for GR
+          injections \ab{($\SEOB$)} with initial parameters similar to GW150914 (top
+          panels) and GW190521 (bottom panels)
+          (see Table~\ref{tab:injection_values}). The 2D contour marks the
+          90\% credible region, while the dashed lines on the 1D
+          marginalized distributions mark the 90\% credible
+          levels. The black vertical and horizontal lines mark the
+          injection values.}
         \label{fig:simulated_signal_GR}
@@
 due to error in waveform modeling, we use the GR version of the same waveform,
-$\SEOB$ (without allowing for deviations in the QNM parameters) to
+$\SEOB$ (i.e., without allowing for deviations in the QNM parameters) to
 simulate our GW signal. And to avoid systematic biases due to noise,
@@
 Appendix~\ref{sec:noise_systematics}.}  As in the case of the actual
-detections, we consider a two-detector LIGO network at
+detections \ab{of GW150914 and GW190521}, we consider a two-detector LIGO network at
 Hanford and Livingston, having identical PSDs. The distance to the two 
@@
 loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of only one QNM $(\ell m) = (2,2)$, i.e.,
-$\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to
+frequency and damping time of only one QNM $(\ell m) = (2,2)$ (i.e.,
+$\{\df{220},\dtau{220}\}$), while fixing the other QNM frequencies to
 their GR values.
@@
 
-\abhi{I have slightly modified this subsection. I have divided up the three main results we want to show here:\\
-1. the robustness of the pipeline to detect devations. This segment includes the 10\% deviation results.\\
-2. the systematic biases if one uses a GR template to measure a nonGR signal. This also uses the 10\% deviation results.\\
-3.
-highlight the fact that for a nonGR signal, not only does pSEOB correctly recover the frequencies, unlike SEOB, it also correctly recovers the masses and spins.
-For this we needed to show a comparison of a SEOB vs pSEOB recovery of a signal with and without deviation, i.e, at least 4 cases.
-The easiest way to show this, I thought, would be to restrict to one event, GW150914-like, and create three signals with deviationsn = 0, 0.1 and 0.5.
-Then in two columns we show the SEOB vs pSEOB recoveries.
-There are several things that can be higlighted in this figure: a) for GR recoveries, greater the deviation, greater the biases.
-b) pSEOB measurements for all quantities are unbiased, c) this behaviour is unchanged irrespective of the magnitude of the deviation.
-Consequently, I have replaced the earlier Fig 4 with a new figure.}
-
 To demonstrate the robustness of the method in detecting possible
@@
 description. We again choose binary-parameters
-similar to GW150914 and GW190521 (as given in Table ~\ref{tab:injection_values}), but
+similar to GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but
 set $\df{220} = \dtau{220} = 0.1 $.
@@
 and instanteneous frequency upto the merger (lower panel) , beyond which the 
-red (GR template) and blue (non-GR template) diverge. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
+red (GR template) and blue (non-GR template) \sout{diverge} \ab{differ}. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
 show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
@@
         \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
-The non-GR signal has a deviation, $\df{220} = \dtau{220} = XX$.
+        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections \ab{($\pSEOB$)} with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
+The non-GR signal has a deviation, $\df{220} = \dtau{220} = 0.1$.
 The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
@@
 
-We additionally investigate the effects of erroneously assuming that an underlying non-GR signal can be well-described
-by a GR one.
-We do this by estimating the parameters of our non-GR signals using the GR waveform model $\SEOB$ instead of the parameterized $\pSEOB$.
-The resulting one- and two-dimensional posteriors are shown in the right panels of Fig.~\ref{fig:simulated_signal_nonGR} by red curves for the GW150914-like (top) and GW190521-like (bottom) signals respectively.
-For both signals, we find the $\SEOB$ estimates are markedly biased with respect to the $\pSEOB$ estimates.
-This can be explained by the inability of the $\SEOB$ template waveform to capture all the physics in the $\pSEOB$ signal.
-We also notice that the results are distinctly different for the two events.
-For the GW150914-like non-GR signal, the measurements of $(\fgr{220}, \taugr{220})$ (top right panel in Fig.~\ref{fig:simulated_signal_nonGR}) are consistent with the $(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no deviations} from GR (top right panel in Fig.~\ref{fig:simulated_signal_GR}).
-In other words, if the actual signal had deviations from GR as large as the $10\%$, the analysis with the GR signal $\SEOB$ would likely have reported \emph{no} deviation from the GR prediction.
-However in the case of the GW190521-like non-GR signal, a simple GR analysis of the non-GR signal would have yielded measurements distinctly different from either of the two parameterized estimates: with and without deviations.
+We additionally investigate the effects of erroneously assuming that
+an underlying non-GR signal can be well-described by a GR one. We do
+this by estimating the parameters of our non-GR signals using the GR
+waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
+resulting one- and two-dimensional posteriors are shown in the right
+panels of Fig.~\ref{fig:simulated_signal_nonGR} by red curves for the
+GW150914-like (top) and GW190521-like (bottom) signals
+respectively. For both signals, we find the $\SEOB$ estimates are
+markedly biased with respect to the $\pSEOB$ estimates. \sout{This can be
+explained by the inability of the $\SEOB$ template waveform to capture
+all the physics in the $\pSEOB$ signal.} \comment{AB: I erased the previous sentence because 
+$\pSEOB$ has not ``more'' physics. We varied the QNMs by 10\% with respect GR, we have a different gravity theory 
+which we cannot match with a GR template. I don't think we need to give any explanation of the results, 
+they are self-evident to me.} We also notice that the
+results are distinctly different for the two events. For the
+GW150914-like non-GR signal, the measurements of $(\fgr{220},
+\taugr{220})$ (top right panel in
+Fig.~\ref{fig:simulated_signal_nonGR}) are consistent with the
+$(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no
+  deviations} from GR (top right panel in
+Fig.~\ref{fig:simulated_signal_GR}). In other words, if the actual
+signal had deviations from GR as large as the $10\%$, the analysis
+with the GR signal $\SEOB$ would likely have reported \emph{no}
+deviation from the GR prediction. However in the case of the
+GW190521-like non-GR signal, a simple GR analysis of the non-GR signal
+would have yielded measurements distinctly different from either of
+the two parameterized estimates: with and without deviations.
 
-Finally, we investigate the impact on the estimation of GR parameters discussed in Sec.~\ref{sec:method}, $\bxigr$  as we change the magnitude of deviation in the non-GR parameters.
-We restrict oursel es to a GW150914-like event, and for comparison, add a synthetic signal with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the 10\% non-GR signal and a signal with no deviation (essentially GR) mentioned above.
-We summarise the results in Fig.~\ref{fig:gr_ngr_comparison}.
-The left (right) panels show the posterior probability distributions of the three signals using the GR, $\SEOB$ (non-GR, $\pSEOB$) waveform model.
-The first difference we note is the $\SEOB$ recoveries yield biased estimates when the underlying signal is non-GR, while the $\pSEOB$ recoveries do not.
-Furthermore, as we increase the deviations, while the $\SEOB$ recoveries expectedly get more biased, the $\pSEOB$ measurements are robust is consistently recovering the injected value.
-Since the measurement of the frequency and damping time in the $\pSEOB$ model incorporate information from the masses and spins through the NR fitting formulae (as shown in Eqs.~\ref{eq:nongr_freqs_a}-~\ref{eq:nongr_freqs_b}), one might have expected correlations between the mass, spins and the QNM frequencies, leading to biased estimates in the masses and spins.
-We confirm here that is not the case.
+Finally, we investigate the impact on the estimation of \ab{the} GR parameters
+\sout{discussed in Sec.~\ref{sec:method},} $\bxigr$ as we change the
+magnitude of deviation in the non-GR parameters. We restrict ourselves 
+to a GW150914-like event, and for comparison, add a synthetic signal
+with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
+10\% non-GR signal and a signal with no deviation (essentially GR)
+mentioned above. We summarise the results in
+Fig.~\ref{fig:gr_ngr_comparison}. The left (right) panels show the
+posterior probability distributions of the three signals using the GR,
+$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
+note is the $\SEOB$ recoveries yield biased estimates when the
+underlying signal is non-GR, while the $\pSEOB$ recoveries do
+not. Furthermore, as we increase the deviations, while the $\SEOB$
+recoveries expectedly get more biased, the $\pSEOB$ measurements are
+robust in consistently recovering the injected value. Since the
+measurement of the frequency and damping time in the $\pSEOB$ model
+incorporate information from the masses and spins through the NR
+fitting formulae (as shown in
+Eqs.~(\ref{eq:nongr_freqs_a})---(\ref{eq:nongr_freqs_b})), one might have
+expected correlations between the mass, spins and the QNM frequencies,
+leading to biased estimates in the masses and spins. We confirm here
+that is not the case.
 
@@
         \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
-        \caption{\textcolor{red}{FINAL RESULT}  Comparison of a GW150914-like injection's parameters when signals with no, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
+        \caption{\textcolor{red}{FINAL RESULT}  Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
 The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.

### 2021-03-17 papers/intro_paper/results_synthetic.tex
changes in Sec. IIIB

@@
         \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
-Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
+Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) \comment{AB: what is the amplitude $h$?
+How is it obtained from the polarizations?} and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
         \label{fig:nongr_waveform}
@@
 leading to biased estimates in the masses and spins. We confirm here
-that is not the case.
+that is not the case. \comment{AB: I don't see how from the figure O 
+conclude that there are no correlations between masses/spins and QNMs.}
 

### 2021-03-17 papers/intro_paper/results_synthetic.tex
changes up to Sec. III

@@
 leading to biased estimates in the masses and spins. We confirm here
-that is not the case. \comment{AB: I don't see how from the figure O 
+that is not the case. \comment{AB: I don't see how from the figure I can  
 conclude that there are no correlations between masses/spins and QNMs.}
@@
 such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
-Virgo, is \macro{$\sim$ 70}. Based on the LIGO-Virgo observations during during the first three observing runs, 
+Virgo, is \macro{$\sim$ 70}. Based on the LIGO-Virgo observations during the first three observing runs, 
 such asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible at design sensitivities. Using this
+prediction, but quite plausible \ab{during O4.} \sout{at design sensitivities.} Using this
 signal, we attempt to measure both the $(2,\pm 2)$ and
@@
 
-We summarize our results in Fig.~\ref{fig:nohair_sxs}.
-Given the injection parameters, the predicted values of the $(2,\pm 2)$ and $(3,\pm 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68 ms)}  and \macro{(271.21 Hz, 4.50 ms)} respectively.
-The left panel of Fig.~\ref{fig:nohair_sxs} shows that the two-dimensional posteriors on the $(2,\pm 2)$ and $(3,\pm 3)$ QNMs are consistent with the predictions for a BBH merger in GR, indicated by the black plus sign.
-Using fitting formulae provided in ~\cite{Berti:2005ys}, specifically,  Eqs.
-2.1, E1, E3 and tables VIII and IX for the fitting coefficients, we infer the two-dimensional posterior probability distirbution on the final mass and spin for the $(2,\pm 2)$ (blue) and $(3,\pm 3)$ (red) QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}.
-The two independent estimates are consistent with each other and correspond to a unique mass and spin for the remnant BH \macro{(83.08 $\Mo$, 0.37)} indicated by the plus sign.
-As a consequence, this may be considered as a test of the no-hair conjecture.
-For most of the events observed so far, the power in the $(3,\pm 3)$ has not been sufficient to measure it along with the $(2,\pm 2)$, or in fact, in its place.
-However, it might also be possible to combine information from multiple observation over the coming few years to obtain meaningful constraints on the $(3,\pm 3)$ and
-other sub-dominant QNMs.
+We summarize our results in Fig.~\ref{fig:nohair_sxs}.  Given the
+injection parameters, the predicted values of the $(2,\pm 2)$ and
+$(3,\pm 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68
+  ms)} and \macro{(271.21 Hz, 4.50 ms)} respectively. The left panel
+of Fig.~\ref{fig:nohair_sxs} shows that the 2D posteriors
+on the $(2,\pm 2)$ and $(3,\pm 3)$ QNMs are consistent with the
+predictions for a BBH merger in GR, indicated by the black plus sign.
+Using fitting formulae provided in Ref.~\cite{Berti:2005ys}, specifically,
+Eq.~(2.1), Eq.~(E1) and Eq.~(E3) and Tables VIII and IX for the fitting coefficients,
+we infer the 2D posterior probability distribution on the
+final mass and spin for the $(2,\pm 2)$ (blue) and $(3,\pm 3)$ (red)
+QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
+independent estimates are consistent with each other and correspond to
+a unique mass and spin for the remnant BH \macro{(83.08 $\Mo$, 0.37)}
+indicated by the plus sign. As a consequence, this may be considered
+as a test of the no-hair conjecture. For most of the events observed
+so far, the power in the $(3,\pm 3)$ has not been sufficient to
+measure it along with the $(2,\pm 2)$, or in fact, in its
+place. However, it might also be possible to combine information from
+multiple observation over the coming few years to obtain meaningful
+constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.
 

### 2021-03-17 papers/intro_paper/results_synthetic.tex
changes up to Sec. III

@@
 
+\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% modified GR signal: GR vs nonGR recovery comparison
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_m1m2.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_a1za2z.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fgrtaugr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_Mfaf.png}
+        \caption{\textcolor{red}{FINAL RESULT} Comparison of binary's parameters when a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model.
+The left (right) panels refer to
+a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.1$.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
+In each case, the injection values are indicated by the black dashed lines.}
+        \label{fig:gr_ngr_comparison}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GW150914-like signal with different deviations: GR vs nonGR recovery
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_m1m2.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_a1za2z.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_fgrtaugr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
+        \caption{\textcolor{red}{FINAL RESULT}  Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
+In each case, the injection values are indicated by the black dashed lines.
+In the lowermost panel, the injection values of the final mass and spin, correspond to the injection with no deviations.
+The $\df{220} = \dtau{220} = 0.1$ signal is identical to the results shown in Fig.~\ref{fig:simulated_signal_nonGR}.}
+        \label{fig:gr_ngr_comparison}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 We additionally investigate the effects of erroneously assuming that
@@
 conclude that there are no correlations between masses/spins and QNMs.}
-
-\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_m1m2.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_a1za2z.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fgrtaugr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_Mfaf.png}
-        \caption{\textcolor{red}{FINAL RESULT} Comparison of binary's parameters when a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model.
-The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.1$.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
-In each case, the injection values are indicated by the black dashed lines.}
-        \label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\fi
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GW150914-like signal with different deviations: GR vs nonGR recovery
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_m1m2.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_a1za2z.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_fgrtaugr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
-        \caption{\textcolor{red}{FINAL RESULT}  Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
-In each case, the injection values are indicated by the black dashed lines.
-In the lowermost panel, the injection values of the final mass and spin, correspond to the injection with no deviations.
-The $\df{220} = \dtau{220} = 0.1$ signal is identical to the results shown in Fig.~\ref{fig:simulated_signal_nonGR}.}
-        \label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-03-17 papers/intro_paper/results_lvc.tex
changes up to Sec. IV

@@
-\comment{AB: This is the most important section in the paper, because it contains the
-main results of the paper, i.e., the constraints on QNMs using real data. It needs to
-be expanded and results would need to be highlighted much better than in the current version.
-I would like to suggest that besides the Table and the figure with the 2D- and 1D-posteriors
-that you made (which can be contrasted with Fig. 14 of the TGR GWTC-2 paper), we could have
-a new figure that is either a combination of Figs. 5 and 6 or only Fig. 5 of the
-TGR GWTC-2, but for the 22 QNM frequencies for the different GW events.
-Figures can be used in talks, and can capture the information much better
-than a list of numbers in a Table.}
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results for events observed
-during O3a~\cite{Abbott:2020jks}.
-For the test that we here present, the results shown in~\cite{Abbott:2020jks} only include events which pass a threshold for the median redshifted total mass $\geq 90 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
-The SNR values are listed in Table 4 of \cite{Abbott:2020jks}}.
-%
-The SNR threshold ensures that the signal contains sufficient information in both the inspiral and merger stages to break the degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$.
-Such strong degeneracy is present for low-SNR events with negligible higher-modes and for which only the post-merger is detectable rendering the measurement of $(\df{220}, \dtau{220})$ impossible for those cases.\rb{should we show an example where this degeneracy happens in the appendix?
-We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example.
-And perhaps also for GW150914 for comparison.}\abhi{I would be fine with this.
-Perhaps we should have a discussion about how best to put it in the appendix, if we decide to.}
-On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies.
-However, since the SNR threshold alone should be sufficient for the analysis, for this paper we run the test on all the events listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and post-merger regions $\geq 8$, without imposing any mass threshold.
-
-Imposing this threshold adds two events, GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in \cite{Abbott:2020jks}.
-Furthermore, for the first time, in this paper, we apply our method to
-measure the QNMs to the relevant GW events from LIGO-Virgo's O1 and O2 runs, alongside
-the above events. Applying the same threshold as above, we find two
-additional events that could be included in the analysis: GW150914,
-GW170104. The other high-mass events from O1-O2, GW170729, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
-merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}\footnote{See Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $\pSEOB$ test, as well.}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-For all the relevant signals, we show the posterior distributions $(\df{220}, \dtau{220})$ in the left panel of Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM parameters, $(\fngr{220}, \taungr{220})$ in Table~\ref{tab:qnm_o1o2_results}.
-In the right panel  of Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\% credible intervals on the one-dimensional marginalised posteriors highlighting the dependence of the constraints with respect to the total mass of the system.
-In general the tightest bounds are expected to come from the most massive systems, as they tend to have larger post-merger SNR.
-We find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.
+The LIGO-Virgo Collaboration recently released their testing GR
+catalogue containing results for events observed
+during O3a~\cite{Abbott:2020jks}.
+For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median \sout{redshifted} \ab{detector} total mass $\geq 90 \Mo$ and SNRs in the pre- and
+post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
+The SNR values are listed in Table 4 of Ref.~\cite{Abbott:2020jks}}.
+%
+The SNR threshold ensures that the signal contains sufficient information in both the inspiral and merger stages to break the degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$.
+Such strong degeneracy is present for low-SNR events with negligible higher-modes and for which only the post-merger is detectable rendering the measurement of $(\df{220}, \dtau{220})$ impossible for those cases.\rb{should we show an example where this degeneracy happens in the appendix?
+We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example.
+And perhaps also for GW150914 for comparison.}\abhi{I would be fine with this.
+Perhaps we should have a discussion about how best to put it in the appendix, if we decide to.} \comment{AB: I would agree in showing the two plots that are at the end of the paper in a short Appendix B.}
+On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies.
+However, since the SNR threshold alone should be sufficient for the analysis, for this paper we run the test on all the events listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and post-merger regions $\geq 8$, without imposing any mass threshold.
 
-Among all the GW signals detected so far, GW150914 (solid curve in Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the first, and to date, best attempt in measuring the QNM frequencies~\cite{TheLIGOScientific:2016src,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}.
-Within 90\% credibility we obtain from GW150914:
+\ab{Given the above we add the signals}  GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in Ref.~\cite{Abbott:2020jks}. \ab{Furthermore, for the first time, 
+we apply our method to measure the QNMs to GW events from O1 and O2, notably GW150914 and GW170104.} The other high-mass events from O1 and O2, GW170729, GW170809,
+GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
+merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}~\footnote{See Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
+  thresholds. The paper quotes them for the purpose of the IMR
+  consistency test, but the same thresholds have been used for the
+  $\pSEOB$ test, as well.}.
+
+For all the relevant signals, we show the posterior distributions
+$(\df{220}, \dtau{220})$ in the left panel of
+Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM
+parameters, $(\fngr{220}, \taungr{220})$ in
+Table~\ref{tab:qnm_o1o2_results}. In the right panel of
+Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%
+credible intervals on the 1D marginalized posteriors. We highlight the
+dependence of the constraints on the total mass of the
+system. In general, the tightest bounds are set by the 
+most massive systems, as they tend to have larger post-merger SNR. We
+find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.
+
+Among all the GW signals detected so far, GW150914 (solid curve in
+Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the
+first, and to date, best attempt in measuring the QNM
+frequencies~\cite{TheLIGOScientific:2016src,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}. Within
+90\% credibility we obtain from GW150914:
 %
@@
 
-As described in~\cite{Abbott:2020jks}, we can relax the assumption of a shared deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
+\ab{However, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so they are not constant across the GW signals observed by LIGO and Virgo.}
+As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a \sout{shared} \ab{constant} deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
 The general idea behind this technique is to assume that the non-GR parameters $(\df{220},\dtau{220})$ are drawn from a common underlying distribution, whose properties can be inferred from the population of events.
@@
 Here $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$ by construction and $P(d_j |\, \xi_{\text{nGR}})$ is the likelihood for the parameter $\xi_{\text{nGR}}$ for a given event $d_j$ that is computed from the standard parameter estimation analysis.
-After obtaining $P(\mu, \sigma |  \{d_j\})$, we can then infer a population distribution for a given non-GR parameter $\xi_{\text{nGR}}$ using:~\cite{Isi:2019asy}
+After obtaining $P(\mu, \sigma |  \{d_j\})$, we can then infer a population distribution for a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}:
 %
@@
 %
-Notice that, if we fix $\sigma=0$, this approach is equivalent to assume that all events share the same non-GR parameter $\xi_{\text{nGR}} =\mu$ and~\eqref{hier_combine} reduces to the joint likelihood~\cite{Zimmerman:2019wzo}.
+Notice that, if we fix $\sigma=0$, this approach is equivalent to assume that all events share the same non-GR parameter $\xi_{\text{nGR}} =\mu$ and Eq.~\eqref{hier_combine} reduces to the joint likelihood~\cite{Zimmerman:2019wzo}.
 In practice, we use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $ and compute $P(\xi_{\text{nGR}} | \{d_j\})$.
 
-The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained through this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
+The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained with this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
 %

### 2021-03-17 papers/intro_paper/results_lvc.tex
changes up to Sec. IV

@@
 \input{table_lvc_results}
-\caption{The median, and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from the measurements of the QNM frequencies.}
+\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from 
+the QNM frequencies \ab{using the $\pSEOB$ model}.}
 \label{tab:qnm_o1o2_results}

### 2021-03-17 papers/intro_paper/results_lvc.tex
changes up to Sec. IV

--- 2021-03-17 papers/intro_paper/results_lvc.tex
@@
 \input{table_lvc_results}
-\caption{The median, and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from the measurements of the QNM frequencies.}
+\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from 
+the QNM frequencies \ab{using the $\pSEOB$ model.} \comment{AB: I would add the mass and spin of the remnant from NR fits, as well. The final mass should be multiplied by $(1+z)$. Correct?}}
 \label{tab:qnm_o1o2_results}

### 2021-03-17 papers/intro_paper/results_lvc.tex
changes up to Sec. IV

@@
 parameters, $(\fngr{220}, \taungr{220})$ in
-Table~\ref{tab:qnm_o1o2_results}. In the right panel of
+Table~\ref{tab:qnm_o1o2_results}. \comment{AB: could you explain how the mass 
+and spin in Table II are computed? I think we should also list the mass and 
+spin fron NR fits.} In the right panel of
 Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%

### 2021-03-17 papers/intro_paper/discussion.tex
changes in Sec. V

@@
-We built a parameterized IMR waveform model that can be used to measure the QNM complex frequencies of the remnant object formed in BBH mergers.
-This model can be used to analyze any BBH with (aligned-)spinning components, which constitute an important extension of previous work where a similar model for non-spinning components had been considered~\cite{Brito:2018rfr}.
-We showed that this test can be used to accurately recover the QNM complex frequencies of simulated GW signals in the LIGO and Virgo detectors.
-We also demonstrated that this model can be used to perform tests of the no-hair conjecture and can also be used to detect possible small deviations from GR in the ringdown part of the signal.
+\ab{We built a parameterized IMR waveform model, $\pSEOB$, that can 
+measure the QNM complex frequencies of the remnant object formed \ab{through 
+the merger of BHs with aligned or antialigned spins, thus extending  
+previous work, which was limited} to non-spinning BHs~\cite{Brito:2018rfr}. 
+The $\pSEOB$ model was recently used to infer the QNMs of some of the 
+BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.}
 
-This model had been previously used to analyze BBHs from the first half of LIGO-Virgo's third observing run~\cite{Abbott:2020jks}.
-We extended these results by analyzing GW events from the first and second LIGO-Virgo observing runs and updated the joint measurements on the fractional deviations in the frequency and damping time of the least-damped QNM.
-As expected, the event providing the best constraint on the least-damped QNM to be date continues to be GW150914 [see \eqref{GW150914_delta}].
-In addition, even in the most agnostic and conservative scenario where we combine the information from different events using an hierarchical approach, at $90\%$ credibility, we constrain the frequency of the least damped QNM to be within $\sim 9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$ over the results reported in~\cite{Abbott:2020jks}.
-The constraints we obtain on the frequencies and damping time of the least damped QNM are compatible with the ones recently reported in Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done using only the post-merger part of the signal was analyzed.
+We extended these results by analyzing GW events from the first and
+second LIGO-Virgo observing runs and updated the joint measurements on
+the fractional deviations in the frequency and damping time of the
+least-damped QNM. As expected, the event providing the best constraint
+on the least-damped QNM to be date continues to be GW150914 [see
+\eqref{GW150914_delta}]. In addition, even in the most agnostic and
+conservative scenario where we combine the information from different
+events using an hierarchical approach, at $90\%$ credibility, we
+constrain the frequency of the least damped QNM to be within $\sim
+9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$
+over the results reported in~\cite{Abbott:2020jks}. The constraints we
+obtain on the frequencies and damping time of the least damped QNM are
+compatible with the ones recently reported in
+Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done
+using only the post-merger part of the signal was analyzed.
 
-These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects (see e.g.~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}).
-However, QNM computations in beyond-GR theories have only been done in an handful of cases, mostly focusing on non-rotating or slowly-rotating BH solutions (see e.g.~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao}) or relying on the eikonal/geometric optics approximation to obtain estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}.
-The only exceptions to this rule, that we are aware of, are computations of the QNM of Kerr-Newman BHs in Einstein-Maxwell theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} and estimates of the BBH ringdown in beyond-GR theories obtained through a limited number of numerical simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}.
-Given these limitations, our ability of going beyond a  null test of GR and use our results to impose precise constraints on beyond-GR theories with QNM measurements is at this moment quite limited.
+These constraints could in principle be used to constrain specific
+non-GR theories and exotic compact objects (see
+e.g.~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}). However,
+QNM computations in beyond-GR theories have only been done in an
+handful of cases, mostly focusing on non-rotating or slowly-rotating
+BH solutions (see
+e.g.~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao})
+or relying on the eikonal/geometric optics approximation to obtain
+estimates of the QNMs for spinning
+BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}. The
+only exceptions to this rule, that we are aware of, are computations
+of the QNM of Kerr-Newman BHs in Einstein-Maxwell
+theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} and
+estimates of the BBH ringdown in beyond-GR theories obtained through a
+limited number of numerical
+simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
+limitations, our ability of going beyond a null test of GR and use our
+results to impose precise constraints on beyond-GR theories with QNM
+measurements is at this moment quite limited.
 
-Despite these limitations there has been some recent effort to develop parametrizations that could help mapping measurements of the parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto constraints to specific beyond-GR theories.
-This includes for example the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently applied to LIGO-Virgo GW events in Ref.
-~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters, or the proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where deviations from the GR QNMs are mapped onto generic small modifications of the perturbation equations describing the QNMs.
-Other examples also include proposals to map deviations from the GR QNMs to coefficients in generic effective field theory actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to directly relate measurements of the QNM complex frequencies to a parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which could be then used jointly with measurements coming from the Event Horizon Telescope to obtain stronger constraints on deviations from GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
-We should note, however, that all these parametrizations are either limited to non-spinning BHs or make use of a series expansion in the BH spin which might limit their accuracy for highly-spinning BHs.
+Despite these limitations there has been some recent effort to develop
+parametrizations that could help mapping measurements of the
+parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto
+constraints to specific beyond-GR theories. This includes for example
+the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently
+applied to LIGO-Virgo GW events in Ref. ~\cite{Carullo:2021dui}, where
+deviations from the GR QNMs explicitly depend on a perturbative
+expansion in the BH spin and possible extra non-GR parameters, or the
+proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where
+deviations from the GR QNMs are mapped onto generic small
+modifications of the perturbation equations describing the QNMs. Other
+examples also include proposals to map deviations from the GR QNMs to
+coefficients in generic effective field theory
+actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to
+directly relate measurements of the QNM complex frequencies to a
+parametrized non-GR BH
+metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which
+could be then used jointly with measurements coming from the Event
+Horizon Telescope to obtain stronger constraints on deviations from
+GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
+We should note, however, that all these parametrizations are either
+limited to non-spinning BHs or make use of a series expansion in the
+BH spin which might limit their accuracy for highly-spinning BHs.
 
-In the future, it would also be important to test whether this model could be used to detect deviations in waveforms obtained through numerical relativity simulations of specific beyond-GR theories.
-Such simulations are still at their infancy and have so far only been done for a handful of theories, focusing mostly on proof-of-concept simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}.
-Nonetheless, given the recent efforts put forward in order to simulate BBHs in beyond-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.
+In the future, it would also be important to test whether this model
+could be used to detect deviations in waveforms obtained through
+numerical relativity simulations of specific beyond-GR theories. Such
+simulations are still at their infancy and have so far only been done
+for a handful of theories, focusing mostly on proof-of-concept
+simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}. Nonetheless,
+given the recent efforts put forward in order to simulate BBHs in
+beyond-GR theories, we hope that accurate non-GR IMR waveforms will
+become available in the near future.
 
-Finally, an obvious generalization of this work would be to extend the parameterized IMR model to generic precessing BBHs, which can in principle be easily done using the recently developed multipolar EOB model reported in Ref.~\cite{Ossokine:2020kjp}.
+Finally, an obvious generalization of this work would be to extend the
+parameterized IMR model to generic precessing BBHs, which can in
+principle be easily done using the recently developed multipolar EOB
+model reported in Ref.~\cite{Ossokine:2020kjp}.

### 2021-03-18 papers/intro_paper/discussion.tex
changes in Table II, Sec. IV and V

@@
-\ab{We built a parameterized IMR waveform model, $\pSEOB$, that can 
+\ab{We have built a parameterized IMR waveform model, $\pSEOB$, that can 
 measure the QNM complex frequencies of the remnant object formed \ab{through 
@@
 
-We extended these results by analyzing GW events from the first and
-second LIGO-Virgo observing runs and updated the joint measurements on
-the fractional deviations in the frequency and damping time of the
-least-damped QNM. As expected, the event providing the best constraint
+\ab{After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
+injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
+We have analysed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
+with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
+results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
+we have obtained more stringent bounds on the dominant QNM $(\ell=2,m=2)$.}
+
+\ab{More specifically,} as expected, the event providing the best constraint
 on the least-damped QNM to be date continues to be GW150914 [see

### 2021-03-18 papers/intro_paper/results_lvc.tex
changes in Table II, Sec. IV and V

@@
 %
-The SNR threshold ensures that the signal contains sufficient information in both the inspiral and merger stages to break the degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$.
-Such strong degeneracy is present for low-SNR events with negligible higher-modes and for which only the post-merger is detectable rendering the measurement of $(\df{220}, \dtau{220})$ impossible for those cases.\rb{should we show an example where this degeneracy happens in the appendix?
-We can show a corner plot with $(\df{220}, \dtau{220}, M_{\rm total })$ for 21g in the appendix for example.
-And perhaps also for GW150914 for comparison.}\abhi{I would be fine with this.
-Perhaps we should have a discussion about how best to put it in the appendix, if we decide to.} \comment{AB: I would agree in showing the two plots that are at the end of the paper in a short Appendix B.}
-On the other hand the total mass threshold $\geq 90 \Mo$ was employed due to the fact that this analysis is computationally expensive, and also because we expected these events to be the most promising for ringdown studies.
-However, since the SNR threshold alone should be sufficient for the analysis, for this paper we run the test on all the events listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and post-merger regions $\geq 8$, without imposing any mass threshold.
+The SNR threshold ensures that the signal contains sufficient
+information in both the inspiral and merger stages to break the
+degeneracy between the binary's total mass and the non-GR deviations
+$(\df{220}, \dtau{220})$. Such strong degeneracy is present for
+low-SNR events with negligible higher-modes and for which only the
+post-merger is detectable rendering the measurement of $(\df{220},
+\dtau{220})$ impossible for those cases. On the other hand the
+total mass threshold $\geq 90 \Mo$ was employed due to the fact that
+this analysis is computationally expensive, and also because we
+expected these events to be the most promising for ringdown
+studies. However, since the SNR threshold alone should be sufficient
+for the analysis, for this paper we run the test on all the events
+listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and
+post-merger regions $\geq 8$, without imposing any mass threshold.
 
@@
 \input{table_lvc_results}
-\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from 
-the QNM frequencies \ab{using the $\pSEOB$ model.} \comment{AB: I would add the mass and spin of the remnant from NR fits, as well. The final mass should be multiplied by $(1+z)$. Correct?}}
+\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM \comment{AB: I believe it should be just $(2,2)$.}, and the mass and spin of the remnant object estimated from
+the QNM frequencies \ab{using the $\pSEOB$ model. We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}.} 
+\comment{AB: I would add the mass and spin of the remnant from NR fits, as well. The final mass should be multiplied by $(1+z)$. Correct?}}
 \label{tab:qnm_o1o2_results}

### 2021-03-18 papers/intro_paper/table_injection_values.tex
changes in Sec. III
changes in Table II, Sec. IV and V

@@
 
- Event & \makecell{$m_{\rm 1,det}$ \\ $(\Mo)$} &  \makecell{$m_{\rm 2,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
+ \ab{synthetic signal} & \makecell{$m_{\rm 1\,det}$ \\$(\Mo)$} &  \makecell{$m_{\rm 2\,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
  \hline
@@
 \caption{Parameters of the synthetic-signal injections, chosen to be similar to the actual GW events indicated in the first column (first two rows).
-The parameters $(m_{\rm 1,det},m_{\rm 2,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
+The parameters $(m_{\rm 1\,det},m_{\rm 2 \,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
 The third row indicates the parameters of the SXS BBH waveform used in Sec.~\ref{ssec:nohairtheorem}.
-$\rho_\text{IMR}$, $\rho_\text{insp}$ and $\rho_\text{postinsp}$ are the SNR of the full IMR signal, SNR upto a certain cutoff frequency, and SNR after the cutoff frequency respectively.
-The cutoff frequency is assumed to be the frequency at the innermost circular stable orbit (ISCO) corresponding to the remnant Kerr black hole in each case.}
+The quantities $\rho_\text{IMR}$, $\rho_\text{insp}$ and $\rho_\text{postinsp}$ are the SNR of the full IMR signal, SNR upto a certain cutoff frequency, and SNR after the cutoff frequency respectively.
+In each case, the cutoff frequency is assumed to be the frequency at the innermost circular stable orbit (ISCO) corresponding to the remnant Kerr BH.}
 \label{tab:injection_values}

### 2021-03-18 papers/intro_paper/discussion.tex
changes in Sec. V

@@
 injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
-We have analysed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
+We have analyzed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
 with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
 results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
-we have obtained more stringent bounds on the dominant QNM $(\ell=2,m=2)$.}
+we have obtained more stringent bounds on the dominant (or least-damped) QNM $(\ell=2,m=2)$.}
 
-\ab{More specifically,} as expected, the event providing the best constraint
-on the least-damped QNM to be date continues to be GW150914 [see
-\eqref{GW150914_delta}]. In addition, even in the most agnostic and
+\ab{More specifically, as expected, the single GW event providing the best constraint
+on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.04^{+0.06}_{-0.04}, 
+\dtau{220}=0.09^{+0.18}_{-0.18})$. In addition, in the most agnostic and
 conservative scenario where we combine the information from different
-events using an hierarchical approach, at $90\%$ credibility, we
-constrain the frequency of the least damped QNM to be within $\sim
-9\%$ of the GR prediction -- an improvement of a factor of $\sim 4$
-over the results reported in~\cite{Abbott:2020jks}. The constraints we
-obtain on the frequencies and damping time of the least damped QNM are
-compatible with the ones recently reported in
-Ref.~\cite{Carullo:2021dui}, where measurements on QNMs were done
-using only the post-merger part of the signal was analyzed.
+events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
+at $90\%$ credibility $(\df{220}=0.02^{+0.09}_{-0.09}, \dtau{220}=0.13^{+0.42}_{-0.40})$. Thus, 
+our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
+9\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
+over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.}
+
+\ab{Furthermore, when assuming that the deviations from GR do not vary appreciably over the GW events 
+that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
+on the dominant QNM $(\df{220}=0.02^{+0.03}_{-0.03}, \dtau{220}=0.11^{+0.12}_{-0.12})$. Those 
+constraints are compatible, but sligthly better (especially for the decay time) that the ones recently reported in Ref.~\cite{Carullo:2021dui} 
+(see first row in Table II therein), where measurements on QNMs were done using only the post-merger part of 
+the signal, and included a larger set of GW events from O1, O2 and O3a.}
 

### 2021-03-18 papers/intro_paper/discussion.tex
changes in Sec. V

@@
 on the dominant QNM $(\df{220}=0.02^{+0.03}_{-0.03}, \dtau{220}=0.11^{+0.12}_{-0.12})$. Those 
-constraints are compatible, but sligthly better (especially for the decay time) that the ones recently reported in Ref.~\cite{Carullo:2021dui} 
-(see first row in Table II therein), where measurements on QNMs were done using only the post-merger part of 
-the signal, and included a larger set of GW events from O1, O2 and O3a.}
+constraints are compatible, but sligthly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 
+(see first row in Table II therein), where QNM frequencies were inferred using only the post-merger part of 
+the signal. We note that Ref.~\cite{Carullo:2021dui} used a larger set of GW events from O1, O2 and O3a than we did, although we expect 
+that the extra GW events will not contribute significantly to the combined bound since they have lower SNRs.}
 

### 2021-03-18 papers/intro_paper/discussion.tex
changes in Sec. V

@@
 
-These constraints could in principle be used to constrain specific
-non-GR theories and exotic compact objects (see
-e.g.~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}). However,
-QNM computations in beyond-GR theories have only been done in an
+\ab{These constraints could in principle be used to constrain specific
+non-GR theories and exotic compact objects~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}. 
+However, QNM computations in non-GR theories have only been done in an
 handful of cases, mostly focusing on non-rotating or slowly-rotating
-BH solutions (see
-e.g.~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao})
+BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao},
 or relying on the eikonal/geometric optics approximation to obtain
-estimates of the QNMs for spinning
-BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}. The
+estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}. The
 only exceptions to this rule, that we are aware of, are computations
 of the QNM of Kerr-Newman BHs in Einstein-Maxwell
-theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} and
-estimates of the BBH ringdown in beyond-GR theories obtained through a
-limited number of numerical
-simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
+theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} or 
+estimates of the BBH in non-GR theories obtained through a limited number of 
+NR simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
 limitations, our ability of going beyond a null test of GR and use our
-results to impose precise constraints on beyond-GR theories with QNM
-measurements is at this moment quite limited.
+results to impose precise constraints on non-GR theories with QNM
+measurements is currently quite limited.}
 
-Despite these limitations there has been some recent effort to develop
+Despite these \ab{theoretical} limitations there has been some recent effort to develop
 parametrizations that could help mapping measurements of the
 parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto
-constraints to specific beyond-GR theories. This includes for example
+constraints to specific non-GR theories. This includes for example
 the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently
-applied to LIGO-Virgo GW events in Ref. ~\cite{Carullo:2021dui}, where
+applied to LIGO-Virgo GW events in Ref.~\cite{Carullo:2021dui}, where
 deviations from the GR QNMs explicitly depend on a perturbative
@@
 examples also include proposals to map deviations from the GR QNMs to
-coefficients in generic effective field theory
+coefficients in generic effective--field-theory
 actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to
 directly relate measurements of the QNM complex frequencies to a
-parametrized non-GR BH
-metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which
-could be then used jointly with measurements coming from the Event
+parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa}, 
+which could be then used jointly with measurements from the Event
 Horizon Telescope to obtain stronger constraints on deviations from
@@
 limited to non-spinning BHs or make use of a series expansion in the
-BH spin which might limit their accuracy for highly-spinning BHs.
+BH spin which might limit their accuracy for highly-spinning BHs\ab{, unless 
+the sensitivity of GW detectors will not allow us to access the higher 
+coefficients in the spin series.}
 
-In the future, it would also be important to test whether this model
-could be used to detect deviations in waveforms obtained through
-numerical relativity simulations of specific beyond-GR theories. Such
-simulations are still at their infancy and have so far only been done
-for a handful of theories, focusing mostly on proof-of-concept
+In the future, it would be important to test whether the $\pSEOB$  model
+could be used to detect deviations in waveforms obtained through NR 
+simulations of specific non-GR theories. Such results are still at their 
+infancy and have so far only been done for a handful of theories, focusing mostly on proof-of-concept
 simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}. Nonetheless,
 given the recent efforts put forward in order to simulate BBHs in
-beyond-GR theories, we hope that accurate non-GR IMR waveforms will
-become available in the near future.
+non-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.
 
-Finally, an obvious generalization of this work would be to extend the
-parameterized IMR model to generic precessing BBHs, which can in
+\ab{Finally, an obvious generalization of this work would be to extend the
+parameterized $\pSEOB$ model to generic precessing BBHs, which can in
 principle be easily done using the recently developed multipolar EOB
-model reported in Ref.~\cite{Ossokine:2020kjp}.
+model reported in Ref.~\cite{Ossokine:2020kjp}. Lastly, it will be relevant 
+to include GR deviations in the $\pSEOB$ model also during the late inspiral 
+and plunge stages of the BBH coalescence. On the other hand, GR deviations (notably 
+deviations from PN theory) for the long inspiral stage are currently 
+available in the $\pSEOB$ model and have been used to set bounds on the 
+PN parameters in the GW phasing using LIGO and Virgo observations~\cite{Abbott:2018lct,
+LIGOScientific:2019fpa,Abbott:2020jks}.}

### 2021-03-18 papers/intro_paper/appendix.tex
changes in Sec. V

@@
 
-\abhi{completely re-written this section to make it more readable and less technical.}
-
-Inferences of all parameters in this paper have been done under the assumption that the noise in the detectors is stationary and Gaussian.
-In other words, detector noise follows a normal distrubution with zero mean and a PSD, $S_n(f)$, that is not a function of time, at least during the internal of the gravitational wave signal.
-This allows us to write the Bayesian likelihood function in the form given in Eqs.~\ref{eq:likelihood}-~\ref{eq:nwip}, and perform all the parameter estimation that follows in the results sections.
-However,, LIGO-Virgo noise can often have features that deviate from stationarity and Gaussianity.
-If such features are not taken into account appropriately, final estimates of parameters can get biased.
-We demonstrate one such case by injecting in real noise a GW190521-like signal and showing how parameter estimates can be biased by our understanding of detector noise is not complete.
+Inferences of all parameters in this paper have been done under the
+assumption that the noise in the detectors is stationary and
+Gaussian. In other words, detector noise follows a normal distrubution
+with zero mean and a PSD, $S_n(f)$, that is not a function of time, at
+least during the internal of the GW signal. This
+allows us to write the Bayesian likelihood function in the form given
+in Eqs.~(\ref{eq:likelihood}) and ~(\ref{eq:nwip}), and perform all the
+parameter estimation that follows in the results sections. However,,
+LIGO-Virgo noise can often have features that deviate from
+stationarity and Gaussianity. If such features are not taken into
+account appropriately, final estimates of parameters can get
+biased. Here we demonstrate one such case by injecting in real noise a
+GW190521-like signal and showing how parameter estimates can be biased
+\ab{when} our \sout{understanding} \ab{description} of detector noise is not complete.
 
@@
 \begin{center}
-        \includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
-        \caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur7dq4} GW signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
+        \includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
+        \caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
 The GR prediction for the frequency and damping time is indicated by the black cross.
 While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
-The black curve corresponds to the measurements of the real event GW190521 reported in~\cite{Abbott:2020jks}.
-All signals are recovered using the $\pSEOB$ waveform model.}
+The black curve corresponds to the measurements of the real event GW190521 reported in Ref.~\cite{Abbott:2020jks}.
+All signals are recovered using the $\pSEOB$ model.}
         \label{fig:21g_systematics}
@@
 
-We choose a spinning, precessing NR-surrogate model \texttt{NRSur7dq4} (valid up to mass ratio 4) to simulate the actual GW190521 signal observed by the LIGO and Virgo detectors~\cite{Abbott:2020tfl} (see Table I of Ref.~\cite{Abbott:2020tfl})).
-The choice of the  NR-surrogate model is motivated by the fact that they are the most accurate in the parameter range described by GW190521.
-In Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what the injected \texttt{NRSur7dq4} signal predicts for the $(2,2)$ frequency and damping time,, and for comparison, we also show with a black solid curve the results obtained when recovering the the actual signal GW190521 with the waveform model $\pSEOB$.
-As seen in the plot, while the measurement of the frequency is consistent with the prediction, we overestimate the damping time.
+We choose a spin, precessing NR-surrogate model \ab{\texttt{NRSur}~\footnote{This waveform model is 
+called \texttt{NRSur7dq4} in LAL.}} (valid up to mass ratio 4) to simulate the actual GW190521 signal
+observed by the LIGO and Virgo detectors~\cite{Abbott:2020tfl} (see
+Table I of Ref.~\cite{Abbott:2020tfl})). The choice of the
+\texttt{NRSur} model is motivated by the fact that it is the most
+accurate model in the parameter range described by GW190521\ab{, because 
+it is built by directly interpolating NR waveforms.} In
+Fig.~\ref{fig:21g_systematics}, we indicate with a black cross \comment{AB: I am 
+confused, a model doesn't predict one value by a posterior distribution. What do you 
+mean?} what
+the injected \texttt{NRSur} signal predicts for the QNM $(\ell=2,m=2)$
+frequency and damping time. For comparison, we also show with a
+black solid curve the results obtained when recovering the actual
+signal GW190521 with the $\pSEOB$ model. As seen in the plot,
+while the measurement of the frequency is consistent with the
+prediction, we overestimate the damping time.
 
-The actual GW190521 event was observed at a GPS time, 1242442967.61 seconds (roughly 03:02:49 UTC, May 21, 2019).
-We select a time period of about 2.5 hours around this GPS time and create synthetic signals by injecting the \texttt{NRSur7dq4} GW signal in different stretches of real detector noise around the time of the actual GW event.
-The PSDs of GW detectors are expected to vary over
-longer durations of time, and hence the 2.5 hour stretch of noise we consider can be assumed to have noise-properties similar to the time of the actual event.
-The results are indicated by green curves in Fig.~\ref{fig:21g_systematics}.
-As it can be seen from the figure, for 3 of the 5 noise realizations, corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we recover a damping time similar to the actual event, where $t_0$ is the GPS time of the actual event.
-For the other two noise realizations, we estimate the consistent damping time but an off-set frequency, while the fifth noise realization is consistent with both predictions.
-This seems to indicate that a bias in the measurements of the damping time for the actual event can be explained on account of an incomplete understanding of the noise at the time of the event.
+\ab{To understand such offset in the decay time, we proceed as follows.} 
+The actual GW190521 event was observed at a GPS time, 1242442967.61
+seconds (roughly 03:02:49 UTC, May 21, 2019). We select a time period
+of about 2.5 hours around this GPS time\ab{, create synthetic signals 
+with the \texttt{NRSur} model and inject them in different stretches
+of the real detector noise} around the time of the actual GW event. The
+PSDs of GW detectors are expected to vary over longer durations of
+time, and hence the 2.5 hour stretch of noise we consider can be
+assumed to have noise-properties similar to the time of the actual
+event. \ab{Then, we perform Bayesian analysis against those injections 
+using the $\pSEOB$ model.} The results are indicated by green curves in
+Fig.~\ref{fig:21g_systematics}. As it can be seen from the figure, for
+3 of the 5 noise realizations, corresponding to $t_0-1$ hour,
+$t_0+0.5$ hours, and $t_0+1$ hour, we recover a damping time similar to
+the \ab{one obtained when using the $\pSEOB$ model against the actual event GW190521 
+(black curve)}, where $t_0$ is the GPS time of the actual event. For
+the other two noise realizations, \ab{the $\pSEOB$ model estimates 
+consistently} the damping time, but \ab{has} an off-set frequency, 
+while the fifth noise realization is consistent with both predictions.  
+\ab{This study suggests} that a bias in the measurements of the damping time 
+for the actual event GW190521 can be explained \ab{as due to} an incomplete 
+description of the noise at the time of the event.
 
-The reader might question the judiciousness of using an aligned-spin waveform model, like $\pSEOB$ to measure a signal like GW190521 which appears to be precessing, especially because an incomplete understanding of the underlying signal can also lead to biases in measured quantities, as we have already demonstrated in Sec.~\ref{ssec:ngr_signal}.
-In order to explore possible effects of missing information about in-plane spins in $\pSEOB$, we repeat the above study of injecting synthetic signals using \texttt{NRSur7dq4} and recovering using the $\pSEOB$ template.
-But this time, instead of using real detector noise, we use Gaussian noise, i.e., realisations of noise sampled from a predicted detector PSD.
-Since the properties of the noise is completely understood in this case, any residual measurement biases can be completely attributed to diffferences in the waveform model.
-The 2D posterior distributions of the frequency and damping time measured using these Gaussian-noise signals is shown by the grey curves in Fig.~\ref{fig:21g_systematics}.
-We find the measurements to be completely consistent with the predictions of the frequency and damping time, thus concluding that a lack of in-plane spins in the $\pSEOB$ model does not affect our measurements of the QNM properties.
-The fact that the measurement of ringdown quantities are robust against an incomplete understanding of the inspral of a GW signal, is indeed one of the most strong points of our model.
+The reader might question the judiciousness of using an aligned-spin
+waveform model, like $\pSEOB$, to measure a signal like GW190521 which
+appears to be precessing, especially because an incomplete
+understanding of the underlying signal can also lead to biases in
+measured quantities, as we have already demonstrated in
+Sec.~\ref{ssec:ngr_signal}. In order to explore possible effects of
+missing information about in-plane spins in the $\pSEOB$ model, we repeat the
+above study of injecting synthetic signals using \texttt{NRSur}
+and recovering using the $\pSEOB$ model, \ab{but this time, instead of
+using real detector noise, we use Gaussian noise (i.e., realizations
+of noise sampled from a predicted detector PSD).} Since the properties
+of the noise are completely understood in this case, any residual
+measurement biases can be completely attributed to diffferences in the
+waveform model. The 2D posterior distributions of the frequency and
+damping time measured using these Gaussian-noise signals are shown by
+the grey curves in Fig.~\ref{fig:21g_systematics}. We find the
+measurements to be completely consistent with the predictions of the
+frequency and damping time, thus concluding that a lack of in-plane
+spins in the $\pSEOB$ model does not affect our measurements of the
+QNM properties. The fact that the measurement of ringdown quantities
+are robust against an incomplete description of \ab{the inspiral signal 
+is a crucial property of our method.}
 

### 2021-03-19 papers/intro_paper/abstract.tex
changes in the abstract

--- 2021-01-25 papers/intro_paper/abstract.tex
@@
-  The no-hair conjecture in General Relativity states that the
+  The no-hair conjecture in General Relativity (GR) states that the
   properties of an astrophysical Kerr black hole (BH) are completely described by its
   mass and spin angular momentum. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary black hole (BBH)
+  quasi-normal-mode (QNM) frequencies of a binary--black-hole (BBH)
   ringdown can be uniquely determined by the mass and spin of the
@@
   test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using inspiral-merger-ringdown waveforms, thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the proposed ringdown. We
-  further demonstrate the robustness of the test against modified
-  gravitational-wave (GW) signals with a ringdown different from what
-  GR predicts for Kerr BHs. Our method was used to analyse the
-  properties of the merger remnants for the events observed by
-  LIGO-Virgo in the first half of their third observing run (O3a) in
-  the latest LIGO-Virgo publication. In this paper, for the first
-  time, we analyse the GW events from the first (O1) and second (O2) LIGO-Virgo
-  observing runs and provide joint constraints with published results
-  from O3a. We also analyse two events from the O3a catalogue
-  that were not considered in the initial LIGO-Virgo analysis. The
-  joint measurements of the fractional deviations in the frequency and damping time,
-  $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest
-  constraints yet using this method.
-%Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
+  frequencies of a BBH ringdown using parameterized inspiral-merger-ringdown waveforms in the effective-one-body formalism, 
+thereby taking full advantage of the entire signal power and removing dependency on the
+  predicted or estimated start time of the ringdown. \ab{Our method was used to analyse the
+  properties of the merger remnants for four BBHs observed by
+  LIGO-Virgo in the first half of their third observing (O3a) run in
+  the latest LIGO-Virgo publication. After testing our method with GR and non-GR synthetic-signal injections in Gaussian noise, 
+we analyse for the first time four other GW events: two BBHs from the first (O1) and second (O2) LIGO-Virgo 
+  observing runs, and two BBHs from the O3a run. We then provide joint constraints with published results
+  from the O3a run. In the most agnostic and conservative scenario where we combine the information from different
+events using a hierarchical approach, we obtain, at $90\%$ credibility, that 
+the fractional deviations in the frequency (damping time) of the dominant QNM are 
+$\df{220}=0.02^{+0.09}_{-0.09}$ ($\dtau{220}=0.13^{+0.42}_{-0.40}$), respectively, an improvement of a factor of $\sim 4$ ($\sim 2$) 
+over the results obtained with our model in the LIGO-Virgo publication. The single-event most-stringent constraint to date continues to be 
+GW150914 for which we obtain $\df{220}=0.04^{+0.06}_{-0.04}$ and $\dtau{220}=0.09^{+0.18}_{-0.18}$.}

### 2021-03-19 papers/intro_paper/model_method.tex
changes in Table II, Sec. IV and V
changes in the Sec. II

@@
 and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$. \ab{When needed, 
-we shall denote the detector masses as $m_{1,\rm det}= (1+z)\,m_1$ and $m_{2,\rm det} = (1+z)\,m_2$, 
+we shall denote the detector masses as $m_{1\,\rm det}= (1+z)\,m_1$ and $m_{2 \,\rm det} = (1+z)\,m_2$, 
 where $z$ is the redshift.}
@@
 \end{subequations}
+\comment{AB: as discussed, please expalin very clearly how the GR frequency and decay times are computed, and mark in the equation above 
+their dependence on the mass and spin parameters.}
 We denote such a parameterized waveform model $\pSEOB$~\footnote{This

### 2021-03-24 papers/intro_paper/appendix.tex
add appendix with corner plots

@@
 
+\section{Correlation of the binary's total mass with the non-GR parameters}\label{sec:correlation}
+As mentioned in the main text, for low-SNR events with negligible higher-modes and for which only the post-merger is detectable, there is a strong degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$.
+For those cases, only the reconstructed frequency and damping time $(f_{220},\tau _{220})$ can be independently measured from the data.
+
+To justify this statement, in Fig.~\ref{fig:correlations} we show corner plots that illustrate the correlations between the non-GR parameters $(\df{220}, \dtau{220})$, the detector-frame total mass $M(1+z)$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an event for which both the pre- and post-merger phase are measurable, and for GW190521 (right panel), an event in which the post-merger has ${\rm SNR}> 8$ but the pre-merger has an SNR below 8.
+For GW190521, due the strong degeneracy between $\df{220}$ and the $M(1+z)$, the 1D posterior for $M(1+z)$ is pushed towards the upper boundary of its prior, despite the very wide prior employed in the analysis.
+This in turn renders the measurement of $\df{220}$ (and to a smaller degree of $\dtau{220}$) highly dependent on the upper boundary of the total mass prior.
+On the other hand, this issue does not significantly affect the posteriors for the reconstructed quantities $(f_{220},\tau _{220})$ which are well measured and nearly independent on the upper prior boundary for $M(1+z)$.
+%
+This is to be contrasted with the results for GW150914.
+In this case, the extra information coming from the pre-merger phase allows to break the degeneracy between the non-GR parameters and the total mass, and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can be measured at the same time.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_GW150914.pdf}\includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_S190521g.pdf}
-        \caption{Left panel: GW150914, Right panel: GW190521. Describe the correlations in this caption}
+        \caption{Corner plots showing the correlations between the detector-frame total $(1+z)M$, the non-GR deviations $(\df{220}, \dtau{220})$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$.
+The left panel shows results for GW150914, for which ${\rm SNR}> 8$ in both the pre- and
+post-merger phase of the signal, whereas the right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase but not in the pre-merger phase.}
         \label{fig:correlations}

### 2021-03-25 papers/intro_paper/intro.tex
committed all remaining changes

@@
 formation of a common apparent horizon, and a \textit{ringdown}~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs) (i.e., damped oscillations with specific, discrete frequencies and decay times).
-\comment{AB: I have left only  the QNM refs until 80s, and added the main refs for ``inspiral'' and ``merger''.
-I found the citation unbalanced.}
 
@@
 The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
-The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin angular momentum \ab{(for short spin)}.
+The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin angular momentum \ab{(for short spin)}\abhi{small?}.
 One
@@
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between \ab{them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}}. The
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}. The
 nature of the remnant object has also been explored through tests of
@@
 waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
-complex QNM frequencies with our parameterized model within a Bayesian formalism\ab{, and validate it using 
-several synthetic-signal injection studies in Gaussian noise}. Then, in Sec.~\ref{sec:results},
-we \sout{demonstrate} \ab{apply}  our method on real GW events \ab{using LIGO and Virgo data}.\sout{, as well as simulated signals}. In particular, we analyze
-the GWTC 1/2  events and \ab{obtain the most stringent constraints on the dominant (complex)} QNM frequecies \ab{with our method}\sout{to be \macro{$\df{220} = 0.02^{+0.03}_{-0.03}$} and \macro{$\dtau{220} = 0.11 ^{+0.12} _{-0.12}$}}.
-\comment{AB: I think it is too early to give the results here.} Finally, in Sec.~\ref{sec:discussion} we provide a summary of
+complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
+several synthetic-signal injection studies in Gaussian noise. Then, in Sec.~\ref{sec:results},
+we apply our method on real GW events using LIGO and Virgo data. In particular, we analyze
+the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
 our results and discuss future developments.

### 2021-03-25 papers/intro_paper/model_method.tex
committed all remaining changes

--- 2021-03-17 papers/intro_paper/model_method.tex
@@
 $\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
+the (source) masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
 objects in the binary; and the
@@
 described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total mass $M = m_1+m_2$,
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
+polarization $\psi$. We also introduce the total (source) mass $M = m_1+m_2$,
+and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$. When needed, 
+we shall denote the detector masses as $m_{1\,\rm det}= (1+z)\,m_1$ and $m_{2 \,\rm det} = (1+z)\,m_2$, 
+where $z$ is the redshift. \abhi{We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$.}
 
@@
 f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values.\sout{, which are obtained using NR fits}
-Thus~\cite{Gossan:2011ha,Meidam:2014jpa},
+values~\cite{Gossan:2011ha,Meidam:2014jpa}.
+
+Thus,
 \begin{subequations}
@@
 \end{subequations}
+
+\comment{AB: as discussed, please expalin very clearly how the GR frequency and decay times are computed, and mark in the equation above 
+their dependence on the mass and spin parameters.}\abhi{The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$.
+For every single instance of waveform generation, we choose a value for $(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})$.
+While the mass and spin value go into the construction of $( f_{\ell m 0}^{\text{GR}}, \tau _{\ell m 0}^{\text{GR}})$, these GR quantities and then combined with the values of $(\delta f_{\ell m 0}, \delta \tau_{\ell m 0})$ as shown in the Eqs.~\ref{eq:nongr_freqs_a}-~\ref{eq:nongr_freqs_b}..
+Hence,
+\begin{subequations}
+\begin{eqnarray}
+f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\\ 
+\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})
+\end{eqnarray}
+\end{subequations}
 We denote such a parameterized waveform model $\pSEOB$~\footnote{This
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.
-
-\sout{As said,} The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the \sout{same} NR--fitting--formula \ab{from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}}.
-\sout{described above.} We note that when leaving $\sigma_{\ell m}$ to vary
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}.} We note that when leaving $\sigma_{\ell m}$ to vary
 freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
@@
 from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
-(\ref{c2}), and (\ref{d1}). \ab{As a consequence, the ringdown signal (amplitude and phase) 
-soon after merger deviates from the one predicted by GR.}
+(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 
+soon after merger deviates from the one predicted by GR.
 

### 2021-03-25 papers/intro_paper/results_lvc.tex
add appendix with corner plots
minor changes

@@
         \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.3\textwidth]{figures/rin_all_events_bounds.pdf}
-        \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+        \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2, 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
 The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
@@
 during O3a~\cite{Abbott:2020jks}.
-For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median \sout{redshifted} \ab{detector} total mass $\geq 90 \Mo$ and SNRs in the pre- and
+For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median detector-frame total mass $\geq 90 \Mo$ and SNRs in the pre- and
 post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
@@
 post-merger is detectable rendering the measurement of $(\df{220},
-\dtau{220})$ impossible for those cases. On the other hand the
+\dtau{220})$ impossible for those cases \rb{(see Appendix~\ref{sec:correlation} for more details)}. On the other hand the
 total mass threshold $\geq 90 \Mo$ was employed due to the fact that
@@
 
-\ab{Given the above we add the signals}  GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in Ref.~\cite{Abbott:2020jks}. \ab{Furthermore, for the first time, 
-we apply our method to measure the QNMs to GW events from O1 and O2, notably GW150914 and GW170104.} The other high-mass events from O1 and O2, GW170729, GW170809,
+Given the above we add the signals  GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in Ref.~\cite{Abbott:2020jks}. Furthermore, for the first time, 
+we apply our method to measure the QNMs to GW events from O1 and O2, notably GW150914 and GW170104. The other high-mass events from O1 and O2, GW170729, GW170809,
 GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
@@
 parameters, $(\fngr{220}, \taungr{220})$ in
-Table~\ref{tab:qnm_o1o2_results}. \comment{AB: could you explain how the mass 
-and spin in Table II are computed? I think we should also list the mass and 
-spin fron NR fits.} In the right panel of
+Table~\ref{tab:qnm_o1o2_results}. In the right panel of
 Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%
@@
 
-\ab{However, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so they are not constant across the GW signals observed by LIGO and Virgo.}
-As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a \sout{shared} \ab{constant} deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
+However, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so they are not constant across the GW signals observed by LIGO and Virgo.
+As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a constant deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
 The general idea behind this technique is to assume that the non-GR parameters $(\df{220},\dtau{220})$ are drawn from a common underlying distribution, whose properties can be inferred from the population of events.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
+\begin{table*}
 \input{table_lvc_results}
-\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM \comment{AB: I believe it should be just $(2,2)$.}, and the mass and spin of the remnant object estimated from
-the QNM frequencies \ab{using the $\pSEOB$ model. We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}.} 
-\comment{AB: I would add the mass and spin of the remnant from NR fits, as well. The final mass should be multiplied by $(1+z)$. Correct?}}
+\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,2)$ QNM, and the mass and spin of the remnant object estimated from 
+the QNM frequencies using the $\pSEOB$ model. We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}. }
 \label{tab:qnm_o1o2_results}
-\end{table}
+\end{table*}
 

### 2021-03-25 papers/intro_paper/results_synthetic.tex
minor changes

@@
 
-We \ab{now} demonstrate our method using synthetic-signal injections describing GWs
+We now demonstrate our method using synthetic-signal injections describing GWs
 from BBHs in GR. We employ coloured Gaussian noise with PSDs for LIGO and
-Virgo detectors \ab{during the fourth observing (O4) run} (i.e., at design sensitivity)\ab{, which 
-is expected to start yin the second half of 2022}~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
+Virgo detectors during the fourth observing (O4) run (i.e., at design sensitivity), which 
+is expected to start yin the second half of 2022~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
 For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
@@
           $(\fngr{220}, \taungr{220})$ (right panels) for GR
-          injections \ab{($\SEOB$)} with initial parameters similar to GW150914 (top
+          injections ($\SEOB$) with initial parameters similar to GW150914 (top
           panels) and GW190521 (bottom panels)
@@
 Appendix~\ref{sec:noise_systematics}.}  As in the case of the actual
-detections \ab{of GW150914 and GW190521}, we consider a two-detector LIGO network at
+detections of GW150914 and GW190521, we consider a two-detector LIGO network at
 Hanford and Livingston, having identical PSDs. The distance to the two 
@@
 and instanteneous frequency upto the merger (lower panel) , beyond which the 
-red (GR template) and blue (non-GR template) \sout{diverge} \ab{differ}. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
+red (GR template) and blue (non-GR template) differ. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
 show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
@@
         \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
-Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) \comment{AB: what is the amplitude $h$?
-How is it obtained from the polarizations?} and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
+Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
         \label{fig:nongr_waveform}
@@
         \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections \ab{($\pSEOB$)} with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
+        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections ($\pSEOB$) with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
 The non-GR signal has a deviation, $\df{220} = \dtau{220} = 0.1$.
@@
 respectively. For both signals, we find the $\SEOB$ estimates are
-markedly biased with respect to the $\pSEOB$ estimates. \sout{This can be
-explained by the inability of the $\SEOB$ template waveform to capture
-all the physics in the $\pSEOB$ signal.} \comment{AB: I erased the previous sentence because 
-$\pSEOB$ has not ``more'' physics. We varied the QNMs by 10\% with respect GR, we have a different gravity theory 
-which we cannot match with a GR template. I don't think we need to give any explanation of the results, 
-they are self-evident to me.} We also notice that the
+markedly biased with respect to the $\pSEOB$ estimates. We also notice that the
 results are distinctly different for the two events. For the
@@
 
-Finally, we investigate the impact on the estimation of \ab{the} GR parameters
-\sout{discussed in Sec.~\ref{sec:method},} $\bxigr$ as we change the
+Finally, we investigate the impact on the estimation of the GR parameters $\bxigr$ as we change the
 magnitude of deviation in the non-GR parameters. We restrict ourselves 
@@
 such asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible \ab{during O4.} \sout{at design sensitivities.} Using this
-signal, we attempt to measure both the $(2,\pm 2)$ and
-$(3,\pm 3)$ QNMs. For this injected signal the SNR in
+prediction, but quite plausible during O4. Using this
+signal, we attempt to measure both the $(2,2)$ and
+$(3,3)$ QNMs. For this injected signal the SNR in
 other sub-dominant modes is too low to be able to measure them.
@@
 We summarize our results in Fig.~\ref{fig:nohair_sxs}.  Given the
-injection parameters, the predicted values of the $(2,\pm 2)$ and
-$(3,\pm 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68
+injection parameters, the predicted values of the $(2, 2)$ and
+$(3, 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68
   ms)} and \macro{(271.21 Hz, 4.50 ms)} respectively. The left panel
 of Fig.~\ref{fig:nohair_sxs} shows that the 2D posteriors
-on the $(2,\pm 2)$ and $(3,\pm 3)$ QNMs are consistent with the
+on the $(2, 2)$ and $(3, 3)$ QNMs are consistent with the
 predictions for a BBH merger in GR, indicated by the black plus sign.
@@
 we infer the 2D posterior probability distribution on the
-final mass and spin for the $(2,\pm 2)$ (blue) and $(3,\pm 3)$ (red)
+final mass and spin for the $(2, 2)$ (blue) and $(3, 3)$ (red)
 QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
@@
 as a test of the no-hair conjecture. For most of the events observed
-so far, the power in the $(3,\pm 3)$ has not been sufficient to
-measure it along with the $(2,\pm 2)$, or in fact, in its
+so far, the power in the $(3, 3)$ has not been sufficient to
+measure it along with the $(2, 2)$, or in fact, in its
 place. However, it might also be possible to combine information from
 multiple observation over the coming few years to obtain meaningful
-constraints on the $(3,\pm 3)$ and other sub-dominant QNMs.
+constraints on the $(3, 3)$ and other sub-dominant QNMs.
 
@@
         \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
-        \caption{\textcolor{red}{PRELIMINARY} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2,\pm 2)$ (blue curves) and $(3,\pm 3)$ (red curves) QNM, respectively, when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
+        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2, 2)$ (blue curves) and $(3, 3)$ (red curves) QNM, respectively, when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
 The plus signs mark the GR predictions.}

### 2021-03-25 papers/intro_paper/appendix.tex
updated a_f --> \chi_f

@@
 GW190521-like signal and showing how parameter estimates can be biased
-\ab{when} our \sout{understanding} \ab{description} of detector noise is not complete.
+when our description of detector noise is not complete.
 
@@
 
-We choose a spin, precessing NR-surrogate model \ab{\texttt{NRSur}~\footnote{This waveform model is 
-called \texttt{NRSur7dq4} in LAL.}} (valid up to mass ratio 4) to simulate the actual GW190521 signal
+We choose a spin, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
+called \texttt{NRSur7dq4} in LAL.} (valid up to mass ratio 4) to simulate the actual GW190521 signal
 observed by the LIGO and Virgo detectors~\cite{Abbott:2020tfl} (see
@@
 \texttt{NRSur} model is motivated by the fact that it is the most
-accurate model in the parameter range described by GW190521\ab{, because 
-it is built by directly interpolating NR waveforms.} In
-Fig.~\ref{fig:21g_systematics}, we indicate with a black cross \comment{AB: I am 
-confused, a model doesn't predict one value by a posterior distribution. What do you 
-mean?} what
+accurate model in the parameter range described by GW190521, because 
+it is built by directly interpolating NR waveforms. In
+Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what
 the injected \texttt{NRSur} signal predicts for the QNM $(\ell=2,m=2)$
@@
 
-\ab{To understand such offset in the decay time, we proceed as follows.} 
+To understand such offset in the decay time, we proceed as follows.
 The actual GW190521 event was observed at a GPS time, 1242442967.61
 seconds (roughly 03:02:49 UTC, May 21, 2019). We select a time period
-of about 2.5 hours around this GPS time\ab{, create synthetic signals 
+of about 2.5 hours around this GPS time, create synthetic signals 
 with the \texttt{NRSur} model and inject them in different stretches
-of the real detector noise} around the time of the actual GW event. The
+of the real detector noise around the time of the actual GW event. The
 PSDs of GW detectors are expected to vary over longer durations of
@@
 assumed to have noise-properties similar to the time of the actual
-event. \ab{Then, we perform Bayesian analysis against those injections 
-using the $\pSEOB$ model.} The results are indicated by green curves in
+event. Then, we perform Bayesian analysis against those injections 
+using the $\pSEOB$ model. The results are indicated by green curves in
 Fig.~\ref{fig:21g_systematics}. As it can be seen from the figure, for
@@
 $t_0+0.5$ hours, and $t_0+1$ hour, we recover a damping time similar to
-the \ab{one obtained when using the $\pSEOB$ model against the actual event GW190521 
-(black curve)}, where $t_0$ is the GPS time of the actual event. For
-the other two noise realizations, \ab{the $\pSEOB$ model estimates 
-consistently} the damping time, but \ab{has} an off-set frequency, 
+the one obtained when using the $\pSEOB$ model against the actual event GW190521 
+(black curve), where $t_0$ is the GPS time of the actual event. For
+the other two noise realizations, the $\pSEOB$ model estimates 
+consistently the damping time, but has an off-set frequency, 
 while the fifth noise realization is consistent with both predictions.  
-\ab{This study suggests} that a bias in the measurements of the damping time 
-for the actual event GW190521 can be explained \ab{as due to} an incomplete 
+This study suggests that a bias in the measurements of the damping time 
+for the actual event GW190521 can be explained as due to an incomplete 
 description of the noise at the time of the event.
@@
 above study of injecting synthetic signals using \texttt{NRSur}
-and recovering using the $\pSEOB$ model, \ab{but this time, instead of
+and recovering using the $\pSEOB$ model, but this time, instead of
 using real detector noise, we use Gaussian noise (i.e., realizations
-of noise sampled from a predicted detector PSD).} Since the properties
+of noise sampled from a predicted detector PSD). Since the properties
 of the noise are completely understood in this case, any residual
@@
 QNM properties. The fact that the measurement of ringdown quantities
-are robust against an incomplete description of \ab{the inspiral signal 
-is a crucial property of our method.}
+are robust against an incomplete description of the inspiral signal 
+is a crucial property of our method.
 

### 2021-03-25 papers/intro_paper/results_synthetic.tex
updated a_f --> \chi_f

@@
 a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.1$.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) from the frequency and damping time.
 In each case, the injection values are indicated by the black dashed lines.}
@@
         \caption{\textcolor{red}{FINAL RESULT}  Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $a_f$) from the frequency and damping time.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) from the frequency and damping time.
 In each case, the injection values are indicated by the black dashed lines.

### 2021-03-25 papers/intro_paper/intro.tex
minor updates

@@
 The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
-The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin angular momentum \ab{(for short spin)}\abhi{small?}.
+The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
 One

### 2021-03-25 papers/intro_paper/model_method.tex
minor changes
minor updates

@@
 polarization $\psi$. We also introduce the total (source) mass $M = m_1+m_2$,
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$. When needed, 
+and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$. \abhi{We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$.} When needed, 
 we shall denote the detector masses as $m_{1\,\rm det}= (1+z)\,m_1$ and $m_{2 \,\rm det} = (1+z)\,m_2$, 
-where $z$ is the redshift. \abhi{We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$.}
+where $z$ is the redshift.
 
@@
 their dependence on the mass and spin parameters.}\abhi{The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$.
-For every single instance of waveform generation, we choose a value for $(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})$.
-While the mass and spin value go into the construction of $( f_{\ell m 0}^{\text{GR}}, \tau _{\ell m 0}^{\text{GR}})$, these GR quantities and then combined with the values of $(\delta f_{\ell m 0}, \delta \tau_{\ell m 0})$ as shown in the Eqs.~\ref{eq:nongr_freqs_a}-~\ref{eq:nongr_freqs_b}..
-Hence,
+constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
 \begin{subequations}
@@
 to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and \ab{fix} all the other $(\ell m)$ modes to \sout{be
+\{\df{330},\dtau{330}\}$, and fix all the other $(\ell m)$ modes to \sout{be
 fixed at} their GR predictions (i.e., $\delta f_{\ell m 0} = \delta

### 2021-03-25 papers/intro_paper/results_synthetic.tex
updated caption of Fig 5

@@
         \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations (left panel) and the reconstructed (right panel) frequency and damping time of the $(2, 2)$ (blue curves) and $(3, 3)$ (red curves) QNM, respectively, when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
+        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the frequency and damping time of the $(2, 2)$ and $(3, 3)$ QNM (left panel), and the final mass and spin inferred from the complex frequencies (right panel), when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
 The plus signs mark the GR predictions.}

### 2021-03-25 papers/intro_paper/results_lvc.tex
minor updated
In Fig.6, Made GW150914 contour color consistent with bounds plot on right

@@
 \emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
-Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).}
+Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).
+The purple square marker indicates constraints from the single most-prominent event, GW150914.}
         \label{fig:o1o2_events}
@@
 \caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,2)$ QNM, and the mass and spin of the remnant object estimated from 
-the QNM frequencies using the $\pSEOB$ model. We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}. }
+the QNM frequencies using the $\pSEOB$ model.
+We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}.
+\abhi{[AG: There aren't Mf-chif-IMR results for 0630 in the GWTC-2 TGR paper, probably because PyRING did not run on it.
+The current values are from the GWTC-2 catalog paper.
+The numbre is red is source-frame; needs to be converted to detector-frame.]}}
 \label{tab:qnm_o1o2_results}

### 2021-03-25 papers/intro_paper/results_lvc.tex
updated Table-II to include IMR values of Mf,af from our GR runs, and not the LVC publications

@@
 \input{table_lvc_results}
-\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,2)$ QNM, and the mass and spin of the remnant object estimated from 
-the QNM frequencies using the $\pSEOB$ model.
-We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}.
-\abhi{[AG: There aren't Mf-chif-IMR results for 0630 in the GWTC-2 TGR paper, probably because PyRING did not run on it.
-The current values are from the GWTC-2 catalog paper.
-The numbre is red is source-frame; needs to be converted to detector-frame.]}}
+\caption{The median and symmetric 90\% credible intervals of the remnant properties.
+The first two columns represent the frequency and damping time of the $(2,2)$ QNM measured using the $\pSEOB$ model.
+The next two columns are the mass and spin of the remnant object estimated from the complex QNM frequencies by inverting the fitting formula in~\cite{Berti:2005ys}.
+The last two columns represent final mass and spin estimates predicted using NR fitting formulae from a $\SEOB$ (GR) parameter estimation.}
 \label{tab:qnm_o1o2_results}

### 2021-03-25 papers/intro_paper/table2_gr_constraints.py
added script to compute the constraints in Table-II

@@ -1,0 +1,30 @@
+import numpy as np
+
+data_dict = {
+	'GW150914':'/home/abhirup.ghosh/Documents/Work/spinqnm/runs/O1O2/GW150914/GR/cbcBayes/posterior_samples.dat',
+	'GW170104':'/home/abhirup.ghosh/Documents/Work/spinqnm/runs/O1O2/GW170104/GR/cbcBayes/posterior_samples.dat',
+	'GW190519a': '/home/abhirup.ghosh/Documents/Work/spinqnm/runs/O3a/GR_runs_posterior_samples/GW190519a_posterior_samples.dat',
+	'GW190521b': '/home/abhirup.ghosh/Documents/Work/spinqnm/runs/O3a/GR_runs_posterior_samples/GW190521b_posterior_samples.dat',
+	'S190630ag':'/home/abhirup.ghosh/Documents/Work/spinqnm/runs/O3a/S190630ag/GR/cbcBayes/posterior_samples.dat',
+	'S190828j':'/home/abhirup.ghosh/Documents/Work/spinqnm/runs/O3a/S190828j/GR/cbcBayes/posterior_samples.dat',
+	'GW190910a': '/home/abhirup.ghosh/Documents/Work/spinqnm/runs/O3a/GR_runs_posterior_samples/GW190910a_posterior_samples.dat'
+}
+
+for event in data_dict.keys():
+	data = np.genfromtxt(data_dict[event], dtype=None, names=True)
+
+	print(event)
+	for param in ['mf_evol', 'af_evol']:
+	
+		xf = data[param]
+		xf_med = np.median(xf)
+
+		xf_lower = xf_med - np.percentile(xf, 5)
+		xf_upper = np.percentile(xf, 95) - xf_med
+
+		if param == 'mf_evol':
+			print("$%.1f^{+%0.1f}_{-%0.1f}$ &"%(xf_med, xf_upper, xf_lower))
+		else:
+			print("$%.2f^{+%0.2f}_{-%0.2f}$"%(xf_med, xf_upper, xf_lower))
+
+	

### 2021-03-25 papers/intro_paper/abstract.tex
added comment colour from abstract

@@
 thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the ringdown. \ab{Our method was used to analyse the
+  predicted or estimated start time of the ringdown. Our method was used to analyse the
   properties of the merger remnants for four BBHs observed by
@@
 over the results obtained with our model in the LIGO-Virgo publication. The single-event most-stringent constraint to date continues to be 
-GW150914 for which we obtain $\df{220}=0.04^{+0.06}_{-0.04}$ and $\dtau{220}=0.09^{+0.18}_{-0.18}$.}
+GW150914 for which we obtain $\df{220}=0.04^{+0.06}_{-0.04}$ and $\dtau{220}=0.09^{+0.18}_{-0.18}$.

### 2021-03-25 papers/intro_paper/model_method.tex
removed comment from methods section

@@
 
-\comment{AB: as discussed, please expalin very clearly how the GR frequency and decay times are computed, and mark in the equation above 
-their dependence on the mass and spin parameters.}\abhi{The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
 constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
@@
 We denote such a parameterized waveform model $\pSEOB$~\footnote{This
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}.} We note that when leaving $\sigma_{\ell m}$ to vary
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
 freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell

### 2021-03-25 papers/intro_paper/abstract.tex
minor changes to abstract and intro

@@
   predicted or estimated start time of the ringdown. Our method was used to analyse the
-  properties of the merger remnants for four BBHs observed by
+  properties of the merger remnants for BBHs observed by
   LIGO-Virgo in the first half of their third observing (O3a) run in
@@
 we analyse for the first time four other GW events: two BBHs from the first (O1) and second (O2) LIGO-Virgo 
-  observing runs, and two BBHs from the O3a run. We then provide joint constraints with published results
+  observing runs, and two additional BBHs from the O3a run. We then provide joint constraints with published results
   from the O3a run. In the most agnostic and conservative scenario where we combine the information from different

### 2021-03-25 papers/intro_paper/intro.tex
minor changes to abstract and intro

@@
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}. The
-nature of the remnant object has also been explored through tests of
-BH thermodynamics, like the Hawking's area
-theorem~\cite{Cabero:2017avf,Isi:2020tac} or through search for echos in the
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
+The nature of the remnant object has also been explored through tests of BH thermodynamics, like the Hawking's area
+theorem~\cite{Cabero:2017avf,Isi:2020tac} \rb{and the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, by looking for possible signatures from the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}}, or through search for echos in the
 post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.  None of these tests have found evidence for non-BH nature of the remnant
@@
 post-merger signal.
-Most of the tests mentioned above restrict the data to this post-merger signal, which signficantly reduces parameter-estimation capabilities.
+Most of the tests mentioned above restrict the data to this post-merger signal, which significantly reduces parameter-estimation capabilities.
 However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).

### 2021-03-25 papers/intro_paper/intro.tex
minor corrections up to end of sec. II

@@
 complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
-several synthetic-signal injection studies in Gaussian noise. Then, in Sec.~\ref{sec:results},
+several synthetic-signal injection studies in Gaussian noise \rb{in Sec.~\ref{sec:results}}. Then, in Sec.~\ref{sec:results_lvc},
 we apply our method on real GW events using LIGO and Virgo data. In particular, we analyze

### 2021-03-25 papers/intro_paper/acknowledgements.tex
minor changes through the text and added some comments

@@
-The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
+\rb{The authors thank Max Isi for generously allowing us to use the code developed in Ref.~\cite{Isi:2019asy} for the hierarchical inference analysis.} The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
 We would like to acknowledge the computing resources at the AEI and the LIGO Scientific Collaboration, specifically the Hypatia and CIT clusters.

### 2021-03-25 papers/intro_paper/appendix.tex
minor changes through the text and added some comments

@@
 assumption that the noise in the detectors is stationary and
-Gaussian. In other words, detector noise follows a normal distrubution
+Gaussian. In other words, detector noise follows a normal distribution
 with zero mean and a PSD, $S_n(f)$, that is not a function of time, at
-least during the internal of the GW signal. This
+least during the duration of the GW signal. This
 allows us to write the Bayesian likelihood function in the form given
 in Eqs.~(\ref{eq:likelihood}) and ~(\ref{eq:nwip}), and perform all the
-parameter estimation that follows in the results sections. However,,
+parameter estimation that follows in the results sections. However,
 LIGO-Virgo noise can often have features that deviate from
@@
 The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not.
+While the Gaussian noise simulations are consistent with the prediction, at least 3 of the 5 real noise simulation are not.
 The black curve corresponds to the measurements of the real event GW190521 reported in Ref.~\cite{Abbott:2020jks}.
@@
 To justify this statement, in Fig.~\ref{fig:correlations} we show corner plots that illustrate the correlations between the non-GR parameters $(\df{220}, \dtau{220})$, the detector-frame total mass $M(1+z)$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an event for which both the pre- and post-merger phase are measurable, and for GW190521 (right panel), an event in which the post-merger has ${\rm SNR}> 8$ but the pre-merger has an SNR below 8.
-For GW190521, due the strong degeneracy between $\df{220}$ and the $M(1+z)$, the 1D posterior for $M(1+z)$ is pushed towards the upper boundary of its prior, despite the very wide prior employed in the analysis.
-This in turn renders the measurement of $\df{220}$ (and to a smaller degree of $\dtau{220}$) highly dependent on the upper boundary of the total mass prior.
+For GW190521, due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D posterior for $M(1+z)$ is pushed towards the upper boundary of its prior, despite the very wide prior employed in the analysis.
+This in turn renders the measurement of $\df{220}$ (and to a lesser degree of $\dtau{220}$) highly dependent on the upper boundary of the total mass prior.
 On the other hand, this issue does not significantly affect the posteriors for the reconstructed quantities $(f_{220},\tau _{220})$ which are well measured and nearly independent on the upper prior boundary for $M(1+z)$.

### 2021-03-25 papers/intro_paper/discussion.tex
minor changes through the text and added some comments

@@
-\ab{We have built a parameterized IMR waveform model, $\pSEOB$, that can 
-measure the QNM complex frequencies of the remnant object formed \ab{through 
+We have built a parameterized IMR waveform model, $\pSEOB$, that can 
+measure the QNM complex frequencies of the remnant object formed through 
 the merger of BHs with aligned or antialigned spins, thus extending  
-previous work, which was limited} to non-spinning BHs~\cite{Brito:2018rfr}. 
+previous work, which was limited to non-spinning BHs~\cite{Brito:2018rfr}. 
 The $\pSEOB$ model was recently used to infer the QNMs of some of the 
-BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.}
+BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.
 
-\ab{After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
+After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
 injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
@@
 results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
-we have obtained more stringent bounds on the dominant (or least-damped) QNM $(\ell=2,m=2)$.}
+we have obtained more stringent bounds on the dominant (or least-damped) QNM $(\ell=2,m=2)$.
 
-\ab{More specifically, as expected, the single GW event providing the best constraint
+More specifically, as expected, the single GW event providing the best constraint
 on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.04^{+0.06}_{-0.04}, 
@@
 9\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
-over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.}
+over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.
 
@@
 
-\ab{These constraints could in principle be used to constrain specific
+These constraints could in principle be used to constrain specific
 non-GR theories and exotic compact objects~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}. 
@@
 handful of cases, mostly focusing on non-rotating or slowly-rotating
-BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao},
+BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao,Wagle:2021tam,Pierini:2021jxd},
 or relying on the eikonal/geometric optics approximation to obtain
@@
 of the QNM of Kerr-Newman BHs in Einstein-Maxwell
-theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} or 
-estimates of the BBH in non-GR theories obtained through a limited number of 
-NR simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
+theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} or estimates of the BBH in non-GR theories obtained
+through a limited number of NR simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
 limitations, our ability of going beyond a null test of GR and use our
 results to impose precise constraints on non-GR theories with QNM
-measurements is currently quite limited.}
+measurements is currently quite limited.
 
-Despite these \ab{theoretical} limitations there has been some recent effort to develop
+Despite these theoretical limitations there has been some recent effort to develop
 parametrizations that could help mapping measurements of the
@@
 
-\ab{Finally, an obvious generalization of this work would be to extend the
+Finally, an obvious generalization of this work would be to extend the
 parameterized $\pSEOB$ model to generic precessing BBHs, which can in
@@
 PN parameters in the GW phasing using LIGO and Virgo observations~\cite{Abbott:2018lct,
-LIGOScientific:2019fpa,Abbott:2020jks}.}
+LIGOScientific:2019fpa,Abbott:2020jks}.

### 2021-03-25 papers/intro_paper/results_lvc.tex
minor changes through the text and added some comments

@@
         \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2, 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
+The solid red \textcolor{red}{RB: I guess it's more purple?} curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
 The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
@@
 post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
-The SNR values are listed in Table 4 of Ref.~\cite{Abbott:2020jks}}.
+The SNR values are listed in Table IV of Ref.~\cite{Abbott:2020jks}}.
 %
@@
 GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
-merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}~\footnote{See Table IV of Ref.~\cite{Abbott:2020jks} for a list of the SNR
-  thresholds. The paper quotes them for the purpose of the IMR
-  consistency test, but the same thresholds have been used for the
-  $\pSEOB$ test, as well.}.
+merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}.
 
@@
 \begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}
+P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}\,,
 \end{equation}
@@
 
-However, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so they are not constant across the GW signals observed by LIGO and Virgo.
+However, \rb{in most non-GR theories,} the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so \rb{if GR were to be wrong, one should expect their value to vary} across the GW signals observed by LIGO and Virgo.
 As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a constant deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.

### 2021-03-25 papers/intro_paper/results_synthetic.tex
minor changes through the text and added some comments

@@
 Virgo detectors during the fourth observing (O4) run (i.e., at design sensitivity), which 
-is expected to start yin the second half of 2022~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
+is expected to start in the second half of 2022~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
 For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
@@
 detections of GW150914 and GW190521, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs. The distance to the two 
+Hanford and Livingston, having identical PSDs \textcolor{red}{RB:did we use Virgo? here it seems not, but above we say we used Virgo}. The distance to the two 
 synthetic events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14
+is the same as the actual events (i.e., 24 for GW150914 and 14 \textcolor{red}{RB: $\rho_{\rm IMR}$ for the GW190521-like injection shown in the table is larger than this...}
 for GW190521). Since mearly--equal-mass binaries like GW150914 and
@@
 with the GR signal $\SEOB$ would likely have reported \emph{no}
-deviation from the GR prediction. However in the case of the
+deviation from the GR prediction \textcolor{red}{RB: not sure what this means, since a GR waveform by itself cannot detect a non-GR deviation}. However in the case of the
 GW190521-like non-GR signal, a simple GR analysis of the non-GR signal
 would have yielded measurements distinctly different from either of
-the two parameterized estimates: with and without deviations.
+the two parameterized estimates: with and without deviations\textcolor{red}{RB: I don't understand this previous sentence. Discuss with Abhirup}.
 
@@
 we infer the 2D posterior probability distribution on the
-final mass and spin for the $(2, 2)$ (blue) and $(3, 3)$ (red)
+final mass and spin \rb{as predicted independently by} the $(2, 2)$ (blue) and $(3, 3)$ (red)
 QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
@@
 measure it along with the $(2, 2)$, or in fact, in its
-place. However, it might also be possible to combine information from
+place \textcolor{red}{RB:"in its place" is weird, since the (2,2) is always louder than the (3,3) mode (unless you're thinking about very high mass BHs for which the (2,2) mode would be out-of-band, but the (3,3) still in band.
+But in any case, I would finish the sentence at "has not been sufficient to measure it along with the $(2, 2)$"}.
+However, it might also be possible to combine information from
 multiple observation over the coming few years to obtain meaningful
-constraints on the $(3, 3)$ and other sub-dominant QNMs.
+constraints on the $(3, 3)$ and other sub-dominant QNMs. \textcolor{red}{reminder: citations needed here}
 

### 2021-03-26 papers/intro_paper/results_synthetic.tex
updated draft to address Richard's comments

@@
 study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}.}  As in the case of the actual
-detections of GW150914 and GW190521, we consider a two-detector LIGO network at
-Hanford and Livingston, having identical PSDs \textcolor{red}{RB:did we use Virgo? here it seems not, but above we say we used Virgo}. The distance to the two 
-synthetic events is rescaled such that the SNR in the detector network
-is the same as the actual events (i.e., 24 for GW150914 and 14 \textcolor{red}{RB: $\rho_{\rm IMR}$ for the GW190521-like injection shown in the table is larger than this...}
-for GW190521). Since mearly--equal-mass binaries like GW150914 and
+Appendix~\ref{sec:noise_systematics}.}  Since mearly--equal-mass binaries like GW150914 and
 GW190521 observed at moderately high SNRs are not expected to have a
@@
 respectively. For both signals, we find the $\SEOB$ estimates are
-markedly biased with respect to the $\pSEOB$ estimates. We also notice that the
-results are distinctly different for the two events. For the
-GW150914-like non-GR signal, the measurements of $(\fgr{220},
-\taugr{220})$ (top right panel in
-Fig.~\ref{fig:simulated_signal_nonGR}) are consistent with the
-$(\fngr{220}, \taungr{220})$ measurements for a signal with \emph{no
-  deviations} from GR (top right panel in
-Fig.~\ref{fig:simulated_signal_GR}). In other words, if the actual
-signal had deviations from GR as large as the $10\%$, the analysis
-with the GR signal $\SEOB$ would likely have reported \emph{no}
-deviation from the GR prediction \textcolor{red}{RB: not sure what this means, since a GR waveform by itself cannot detect a non-GR deviation}. However in the case of the
-GW190521-like non-GR signal, a simple GR analysis of the non-GR signal
-would have yielded measurements distinctly different from either of
-the two parameterized estimates: with and without deviations\textcolor{red}{RB: I don't understand this previous sentence. Discuss with Abhirup}.
-
-Finally, we investigate the impact on the estimation of the GR parameters $\bxigr$ as we change the
-magnitude of deviation in the non-GR parameters. We restrict ourselves 
+markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
+this impact on the estimation of the GR parameters $\bxigr$ by changing the
+magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
 to a GW150914-like event, and for comparison, add a synthetic signal
@@
 10\% non-GR signal and a signal with no deviation (essentially GR)
-mentioned above. We summarise the results in
-Fig.~\ref{fig:gr_ngr_comparison}. The left (right) panels show the
+mentioned above. The left (right) panels show the
 posterior probability distributions of the three signals using the GR,
@@
 recoveries expectedly get more biased, the $\pSEOB$ measurements are
-robust in consistently recovering the injected value. Since the
-measurement of the frequency and damping time in the $\pSEOB$ model
-incorporate information from the masses and spins through the NR
-fitting formulae (as shown in
-Eqs.~(\ref{eq:nongr_freqs_a})---(\ref{eq:nongr_freqs_b})), one might have
-expected correlations between the mass, spins and the QNM frequencies,
-leading to biased estimates in the masses and spins. We confirm here
-that is not the case. \comment{AB: I don't see how from the figure I can  
-conclude that there are no correlations between masses/spins and QNMs.}
+robust in consistently recovering the injected value. \abhi{This gives us 
+confidence that the $\pSEOB$ model can accurately measure QNM 
+properties without biasing measurements of inspiral quantities, like masses and spins.}
 
@@
 so far, the power in the $(3, 3)$ has not been sufficient to
-measure it along with the $(2, 2)$, or in fact, in its
-place \textcolor{red}{RB:"in its place" is weird, since the (2,2) is always louder than the (3,3) mode (unless you're thinking about very high mass BHs for which the (2,2) mode would be out-of-band, but the (3,3) still in band.
-But in any case, I would finish the sentence at "has not been sufficient to measure it along with the $(2, 2)$"}.
-However, it might also be possible to combine information from
+measure it along with the $(2, 2)$. However, it might also be possible to combine information from
 multiple observation over the coming few years to obtain meaningful
-constraints on the $(3, 3)$ and other sub-dominant QNMs. \textcolor{red}{reminder: citations needed here}
+constraints on the $(3, 3)$ and other sub-dominant QNMs~\cite{Gossan:2011ha,Meidam:2014jpa,Yang:2017zxs}.
 

### 2021-03-26 papers/intro_paper/table_injection_values.tex
changes in Table II, Sec. IV and V
minor changes
minor updates
updated draft to address Richard's comments

@@
 \begin{center}
-\begin{tabular}{ c|c|c|c|c|c|c|c }
+\begin{tabular}{ c|c|c|c|c|c|c|c|c }
 
- \ab{synthetic signal} & \makecell{$m_{\rm 1\,det}$ \\$(\Mo)$} &  \makecell{$m_{\rm 2\,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
+Injection &  Network & \makecell{$m_{\rm 1\,det}$ \\$(\Mo)$} &  \makecell{$m_{\rm 2\,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
  \hline
- GW150914-like & 39 & 31 & 0.0 & 0.0 & 25 & 22 & 12 \\
- GW190521-like & 150 & 120 & 0.02 & -0.39 & 20 & 8 & 18 \\
- SXS:BBH:0166 & 72 & 12  & 0.0 & 0.0 & 71 & 58 & 41 \\
+ GW150914-like & HL &39 & 31 & 0.0 & 0.0 & 25 & 22 & 12 \\
+ GW190521-like & HL & 150 & 120 & 0.02 & -0.39 & 20 & 8 & 18 \\
+ SXS:BBH:0166 & HLV &72 & 12  & 0.0 & 0.0 & 71 & 58 & 41 \\
 
@@
 \caption{Parameters of the synthetic-signal injections, chosen to be similar to the actual GW events indicated in the first column (first two rows).
-The parameters $(m_{\rm 1\,det},m_{\rm 2 \,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
+The parameters $(m_{\rm 1 \,det}, m_{\rm 2 \,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
 The third row indicates the parameters of the SXS BBH waveform used in Sec.~\ref{ssec:nohairtheorem}.
+The second column refers to the detector-network used, with H,L,V, referring to LIGO-Hanford, LIGO-Livingston and Virgo, respectively.
 The quantities $\rho_\text{IMR}$, $\rho_\text{insp}$ and $\rho_\text{postinsp}$ are the SNR of the full IMR signal, SNR upto a certain cutoff frequency, and SNR after the cutoff frequency respectively.

### 2021-03-26 papers/intro_paper/results_lvc.tex
updated references of curve colours since changing color scheme

@@
         \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2, 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid red \textcolor{red}{RB: I guess it's more purple?} curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
+The solid purple curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
 The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.

### 2021-03-26 papers/intro_paper/results_synthetic.tex
updated references of curve colours since changing color scheme

@@
 resulting one- and two-dimensional posteriors are shown in the right
-panels of Fig.~\ref{fig:simulated_signal_nonGR} by red curves for the
+panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
 GW150914-like (top) and GW190521-like (bottom) signals

### 2021-03-26 papers/intro_paper/lvc_results_standard_form.py
made a final update of all data files; added script to compute the deltas and absolutes

@@ -1,0 +1,46 @@
+import numpy as np
+import h5py
+
+import sys
+sys.path.append("../../scripts")
+
+import compute_sigmalm0_SimIMREOBGenerateQNMFreqV2 as calcqnm
+
+data_loc_full_pe_dict = {"S190519bj":"../../data/rin/S190519bj/rin_S190519bj_pseobnrv4hm.h5", 
+              "S190521r":"../../data/rin/S190521r/rin_S190521r_pseobnrv4hm.h5",
+              "S190630ag":"../../runs/O3a/S190630ag/220/cbcBayes/posterior_samples.dat",
+              "S190828j":"../../runs/O3a/S190828j/220/cbcBayes/posterior_samples.dat",
+              "S190910s":"../../data/rin/S190910s/rin_S190910s_pseobnrv4hm.h5",
+              "GW150914":"../../runs/O1O2/GW150914/220/cbcBayes/posterior_samples.dat",
+              "GW170104":"../../runs/O1O2/GW170104/220/cbcBayes/posterior_samples.dat",
+              "GW170729":"../../runs/O1O2/GW170729/220/cbcBayes/posterior_samples.dat"}
+
+for event in data_loc_full_pe_dict.keys():
+
+	if data_loc_full_pe_dict[event].endswith('.h5'):
+
+		pos_file = h5py.File(data_loc_full_pe_dict[event], "r")
+		samples = pos_file["pSEOBNRv4HM"]["posterior_samples"]
+
+		m1, m2, a1z, a2z, domega, dtau = samples["mass_1"], samples["mass_2"],\
+                                         samples["spin_1z"], samples["spin_2z"],\
+                                         samples["domega220"], samples["dtau220"]
+
+	else:
+		samples = np.genfromtxt(data_loc_full_pe_dict[event], dtype=None, names=True)
+		m1, m2, a1z, a2z, domega, dtau = samples["m1"], samples["m2"],\
+                                         samples["a1z"], samples["a2z"],\
+                                         samples["domega220"], samples["dtau220"]
+    
+	omega_GR, tau_GR = calcqnm.get_sigmalm0SI_GR(m1, m2, a1z, a2z, [2,2])
+	freq_GR = omega_GR/(2.*np.pi)
+        
[…]

### 2021-03-26 papers/intro_paper/intro.tex
made a couple of minor cosmetic changes to the instroduction

@@
 object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
-consistency of the residuals with interferometric
+consistency of the residuals with \abhi{detector}
 noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
@@
 several synthetic-signal injection studies in Gaussian noise \rb{in Sec.~\ref{sec:results}}. Then, in Sec.~\ref{sec:results_lvc},
-we apply our method on real GW events using LIGO and Virgo data. In particular, we analyze
+we apply our method on real GW events \abhi{in} LIGO and Virgo data. In particular, we analyze
 the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of

### 2021-03-26 papers/intro_paper/model_method.tex
minor corrections up to end of sec. II
minor change

@@
 polarization $\psi$. We also introduce the total (source) mass $M = m_1+m_2$,
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$. \abhi{We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$.} When needed, 
+and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$. We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$. When needed, 
 we shall denote the detector masses as $m_{1\,\rm det}= (1+z)\,m_1$ and $m_{2 \,\rm det} = (1+z)\,m_2$, 
@@
 to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and fix all the other $(\ell m)$ modes to \sout{be
-fixed at} their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
+\{\df{330},\dtau{330}\}$, and fix all the other $(\ell m)$ modes to their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
 \tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH

### 2021-03-26 papers/intro_paper/abstract.tex
update numbers for delta's

@@
 the fractional deviations in the frequency (damping time) of the dominant QNM are 
-$\df{220}=0.02^{+0.09}_{-0.09}$ ($\dtau{220}=0.13^{+0.42}_{-0.40}$), respectively, an improvement of a factor of $\sim 4$ ($\sim 2$) 
+$\df{220}=0.03^{+0.10}_{-0.09}$ ($\dtau{220}=0.10^{+0.44}_{-0.39}$), respectively, an improvement of a factor of $\sim 4$ ($\sim 2$) 
 over the results obtained with our model in the LIGO-Virgo publication. The single-event most-stringent constraint to date continues to be 
-GW150914 for which we obtain $\df{220}=0.04^{+0.06}_{-0.04}$ and $\dtau{220}=0.09^{+0.18}_{-0.18}$.
+GW150914 for which we obtain $\df{220}=0.05^{+0.11}_{-0.07}$ and $\dtau{220}=0.07^{+0.26}_{-0.23}$.

### 2021-03-26 papers/intro_paper/discussion.tex
update numbers for delta's

@@
 More specifically, as expected, the single GW event providing the best constraint
-on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.04^{+0.06}_{-0.04}, 
-\dtau{220}=0.09^{+0.18}_{-0.18})$. In addition, in the most agnostic and
+on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.05^{+0.11}_{-0.07}, 
+\dtau{220}=0.07^{+0.26}_{-0.23})$. In addition, in the most agnostic and
 conservative scenario where we combine the information from different
 events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
-at $90\%$ credibility $(\df{220}=0.02^{+0.09}_{-0.09}, \dtau{220}=0.13^{+0.42}_{-0.40})$. Thus, 
+at $90\%$ credibility $(\df{220}=0.03^{+0.10}_{-0.09}, \dtau{220}=0.10^{+0.44}_{-0.39})$. Thus, 
 our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
-9\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
+10\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
 over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.
@@
 that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
-on the dominant QNM $(\df{220}=0.02^{+0.03}_{-0.03}, \dtau{220}=0.11^{+0.12}_{-0.12})$. Those 
+on the dominant QNM $(\df{220}=0.02^{+0.04}_{-0.04}, \dtau{220}=0.10^{+0.14}_{-0.14})$. Those 
 constraints are compatible, but sligthly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 

### 2021-03-26 papers/intro_paper/results_lvc.tex
update numbers for delta's

@@
 \begin{equation}\label{GW150914_delta}
-\df{220}=0.04^{+0.06}_{-0.04}\,\quad \dtau{220}=0.09^{+0.18}_{-0.18}\,.
+\df{220}=0.05^{+0.11}_{-0.07}\,\quad \dtau{220}=0.07^{+0.26}_{-0.23}\,.
 \end{equation}
@@
 joint posterior probability distribution. For $N$ observations, where
-$P_j(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
+$P(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
 observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
@@
 \begin{equation}
-\df{220}=0.02^{+0.03}_{-0.03}\,,\quad \dtau{220}=0.11^{+0.12}_{-0.12}\,.
+\df{220}=0.02^{+0.04}_{-0.04}\,,\quad \dtau{220}=0.10^{+0.14}_{-0.14}\,.
 \end{equation}
@@
 \begin{equation}
-\df{220}=0.02^{+0.09}_{-0.09}\,,\quad \dtau{220}=0.13^{+0.42}_{-0.40}\,.
+\df{220}=0.03^{+0.10}_{-0.09}\,,\quad \dtau{220}=0.10^{+0.44}_{-0.39}\,.
 \end{equation}
 Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ more stringent for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$.
-Similar improvements hold for the hyperparameters: $\df{220}\,(\mu=0.02^{+0.05}_{-0.05},\,\sigma<0.09)$ and $\dtau{220}\,(\mu=0.13^{+0.20}_{-0.18},\,\sigma<0.38)$.
+Similar improvements hold for the hyperparameters: $\df{220}\,(\mu=0.03^{+0.06}_{-0.05},\,\sigma<0.09)$ and $\dtau{220}\,(\mu=0.11^{+0.21}_{-0.19},\,\sigma<0.39)$.
 

### 2021-03-26 papers/intro_paper/abstract.tex
changes in abstract

@@
   properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin angular momentum. As a consequence, the complex
+  mass and spin. As a consequence, the complex
   quasi-normal-mode (QNM) frequencies of a binary--black-hole (BBH)
@@
   properties of the merger remnants for BBHs observed by
-  LIGO-Virgo in the first half of their third observing (O3a) run in
-  the latest LIGO-Virgo publication. After testing our method with GR and non-GR synthetic-signal injections in Gaussian noise, 
-we analyse for the first time four other GW events: two BBHs from the first (O1) and second (O2) LIGO-Virgo 
+  LIGO-Virgo in the first half of their third observing (O3a) run.
+ After testing our method with GR and non-GR synthetic-signal injections in Gaussian noise, 
+we analyse, for the first time, two BBHs from the first (O1) and second (O2) LIGO-Virgo 
   observing runs, and two additional BBHs from the O3a run. We then provide joint constraints with published results

### 2021-03-26 papers/intro_paper/intro.tex
changes in Sec. I

@@
 spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
-The nature of the remnant object has also been explored through tests of BH thermodynamics, like the Hawking's area
-theorem~\cite{Cabero:2017avf,Isi:2020tac} \rb{and the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, by looking for possible signatures from the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}}, or through search for echos in the
-post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.  None of these tests have found evidence for non-BH nature of the remnant
+The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
+theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
+None of these tests have found evidence for non-BH nature of the remnant
 object (as described in GR) in LIGO-Virgo BBH observations.
@@
 complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
-several synthetic-signal injection studies in Gaussian noise \rb{in Sec.~\ref{sec:results}}. Then, in Sec.~\ref{sec:results_lvc},
+several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
 we apply our method on real GW events \abhi{in} LIGO and Virgo data. In particular, we analyze

### 2021-03-26 papers/intro_paper/results_synthetic.tex
changes in Sec. III

@@
         \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability
+        \caption{Posterior probability
           distribution on the fractional deviations in the frequency
@@
         \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-        \caption{\textcolor{red}{FINAL RESULT} Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
+        \caption{Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
 Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
@@
         \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections ($\pSEOB$) with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
+        \caption{Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections ($\pSEOB$) with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
 The non-GR signal has a deviation, $\df{220} = \dtau{220} = 0.1$.
@@
         \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_Mfaf.png}
-        \caption{\textcolor{red}{FINAL RESULT} Comparison of binary's parameters when a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model.
-The left (right) panels refer to
+        \caption{Comparison of binary's parameters when a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model. The left (right) panels refer to
 a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.1$.
@@
         \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
-        \caption{\textcolor{red}{FINAL RESULT}  Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
+        \caption{Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
 The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) from the frequency and damping time.
@@
 recoveries expectedly get more biased, the $\pSEOB$ measurements are
-robust in consistently recovering the injected value. \abhi{This gives us 
+robust in consistently recovering the injected value. This gives us 
 confidence that the $\pSEOB$ model can accurately measure QNM 
-properties without biasing measurements of inspiral quantities, like masses and spins.}
+properties without biasing measurements of inspiral quantities, like masses and spins.
 
@@
 such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
-Virgo, is \macro{$\sim$ 70}. Based on the LIGO-Virgo observations during the first three observing runs, 
+Virgo, is {$\sim$ 70}. Based on the LIGO-Virgo observations during the first three observing runs, 
 such asymmetric and loud signals are no longer just a theoretical
@@
 injection parameters, the predicted values of the $(2, 2)$ and
-$(3, 3)$ frequency and damping time are \macro{(169.45 Hz, 4.68
-  ms)} and \macro{(271.21 Hz, 4.50 ms)} respectively. The left panel
+$(3, 3)$ frequency and damping time are {(169.45 Hz, 4.68
+  ms)} and {(271.21 Hz, 4.50 ms)} respectively. The left panel
 of Fig.~\ref{fig:nohair_sxs} shows that the 2D posteriors
@@
 we infer the 2D posterior probability distribution on the
-final mass and spin \rb{as predicted independently by} the $(2, 2)$ (blue) and $(3, 3)$ (red)
+final mass and spin as predicted independently by the $(2, 2)$ (blue) and $(3, 3)$ (red)
 QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
 independent estimates are consistent with each other and correspond to
-a unique mass and spin for the remnant BH \macro{(83.08 $\Mo$, 0.37)}
+a unique mass and spin for the remnant BH {(83.08 $\Mo$, 0.37)}
 indicated by the plus sign. As a consequence, this may be considered
@@
         \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
-        \caption{\textcolor{red}{FINAL RESULT} Posterior probability distribution on the frequency and damping time of the $(2, 2)$ and $(3, 3)$ QNM (left panel), and the final mass and spin inferred from the complex frequencies (right panel), when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
+        \caption{Posterior probability distribution on the frequency and damping time of the $(2, 2)$ and $(3, 3)$ QNM (left panel), and the final mass and spin inferred from the complex frequencies (right panel), when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
 The plus signs mark the GR predictions.}

### 2021-03-26 papers/intro_paper/results_synthetic.tex
changes in Sec. III

@@
 simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise. \footnote{A detailed
+we use an averaged (zero-noise) realization of the noise~\footnote{A detailed
 study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}.}  Since mearly--equal-mass binaries like GW150914 and
+Appendix~\ref{sec:noise_systematics}.}.  Since mearly--equal-mass binaries like GW150914 and
 GW190521 observed at moderately high SNRs are not expected to have a
@@
 fractional quantities into absolute quantities using the relations
-given in Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b}, and
+given in Eqs.~(\ref{eq:nongr_freqs_a}) and ~(\ref{eq:nongr_freqs_b}), and
 construct posterior distributions on these effective quantities,

### 2021-03-26 papers/intro_paper/results_lvc.tex
changes in Sec. IV

@@
 post-merger is detectable rendering the measurement of $(\df{220},
-\dtau{220})$ impossible for those cases \rb{(see Appendix~\ref{sec:correlation} for more details)}. On the other hand the
+\dtau{220})$ impossible for those cases (see Appendix~\ref{sec:correlation} for more details). On the other hand the
 total mass threshold $\geq 90 \Mo$ was employed due to the fact that
@@
 
-However, \rb{in most non-GR theories,} the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so \rb{if GR were to be wrong, one should expect their value to vary} across the GW signals observed by LIGO and Virgo.
+However, in most non-GR theories, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so if GR were to be wrong, one should expect their value to vary across the GW signals observed by LIGO and Virgo.
 As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a constant deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.

### 2021-03-26 papers/intro_paper/abstract.tex
changes in abstract

@@
 thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the ringdown. Our method was used to analyse the
+  predicted or estimated start time of the ringdown. Our method was used to analyze the
   properties of the merger remnants for BBHs observed by
@@
  After testing our method with GR and non-GR synthetic-signal injections in Gaussian noise, 
-we analyse, for the first time, two BBHs from the first (O1) and second (O2) LIGO-Virgo 
+we analyze, for the first time, two BBHs from the first (O1) and second (O2) LIGO-Virgo 
   observing runs, and two additional BBHs from the O3a run. We then provide joint constraints with published results

### 2021-03-26 papers/intro_paper/appendix.tex
changes in Appendices

@@
         \includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
-        \caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
+        \caption{90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
 The GR prediction for the frequency and damping time is indicated by the black cross.
@@
 \section{Correlation of the binary's total mass with the non-GR parameters}\label{sec:correlation}
-As mentioned in the main text, for low-SNR events with negligible higher-modes and for which only the post-merger is detectable, there is a strong degeneracy between the binary's total mass and the non-GR deviations $(\df{220}, \dtau{220})$.
-For those cases, only the reconstructed frequency and damping time $(f_{220},\tau _{220})$ can be independently measured from the data.
 
-To justify this statement, in Fig.~\ref{fig:correlations} we show corner plots that illustrate the correlations between the non-GR parameters $(\df{220}, \dtau{220})$, the detector-frame total mass $M(1+z)$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an event for which both the pre- and post-merger phase are measurable, and for GW190521 (right panel), an event in which the post-merger has ${\rm SNR}> 8$ but the pre-merger has an SNR below 8.
-For GW190521, due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D posterior for $M(1+z)$ is pushed towards the upper boundary of its prior, despite the very wide prior employed in the analysis.
-This in turn renders the measurement of $\df{220}$ (and to a lesser degree of $\dtau{220}$) highly dependent on the upper boundary of the total mass prior.
-On the other hand, this issue does not significantly affect the posteriors for the reconstructed quantities $(f_{220},\tau _{220})$ which are well measured and nearly independent on the upper prior boundary for $M(1+z)$.
+As mentioned in the main text, for low-SNR events with negligible
+higher-modes and for which only the post-merger is detectable, there
+is a strong degeneracy between the binary's total mass and the non-GR
+deviations $(\df{220}, \dtau{220})$. For those cases, only the
+reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
+be independently measured from the data.
+
+To justify this statement, in Fig.~\ref{fig:correlations} we show
+corner plots that illustrate the correlations between the non-GR
+parameters $(\df{220}, \dtau{220})$, the detector-frame total mass
+$M(1+z)$ and the reconstructed frequency and damping time
+$(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an
+event for which both the pre- and post-merger phase are measurable,
+and for GW190521 (right panel), an event in which the post-merger has
+${\rm SNR}> 8$, but the pre-merger has an SNR below 8. For GW190521,
+due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D
+posterior for $M(1+z)$ is pushed towards the upper boundary of its
+prior, despite the very wide prior employed in the analysis. This in
+turn renders the measurement of $\df{220}$ (and to a lesser degree of
+$\dtau{220}$) highly dependent on the upper boundary of the total mass
+prior. On the other hand, this issue does not significantly affect the
+posteriors for the reconstructed quantities $(f_{220},\tau _{220})$
+which are well measured and nearly independent on the upper prior
+boundary for $M(1+z)$.
 %
-This is to be contrasted with the results for GW150914.
-In this case, the extra information coming from the pre-merger phase allows to break the degeneracy between the non-GR parameters and the total mass, and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can be measured at the same time.
+This is to be contrasted with the results for GW150914. In this case, 
+the extra information coming from the pre-merger phase allows to break 
+the degeneracy between the non-GR parameters and the total mass, 
+and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can 
+be measured at the same time.
 
@@
 The left panel shows results for GW150914, for which ${\rm SNR}> 8$ in both the pre- and
-post-merger phase of the signal, whereas the right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase but not in the pre-merger phase.}
+post-merger phase of the signal, and the correlations are absent.
+The right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase, but not in the pre-merger phase, and the correlations are present.}
         \label{fig:correlations}

### 2021-03-26 papers/intro_paper/intro.tex
changes in Sec. I

@@
 object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
-consistency of the residuals with \abhi{detector}
-noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
+consistency of the residuals with detector noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
 departure from the predictions of GR.
@@
 several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
-we apply our method on real GW events \abhi{in} LIGO and Virgo data. In particular, we analyze
+we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
 the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of

### 2021-03-26 papers/intro_paper/intro_paper.tex
committed all remaining changes
minor updates
minor corrections up to end of sec. II
collated everything back to a single tex

@@
 \newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{Emerald}{[AG: #1]}}
-\newcommand{\rb}[1]{\textcolor{blue}{[\textit{RB: #1}]}}
+\newcommand{\abhi}[1]{\textcolor{Emerald}{#1}}
+\newcommand{\rb}[1]{\textcolor{blue}{#1}}
 \newcommand{\ab}[1]{\textcolor{cyan}{#1}}
@@
 
-\title{\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}} 
+\title{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations} 
 %by making full use of gravitational-wave modeling}
@@
 \begin{abstract}
-\input{abstract}
+  The no-hair conjecture in General Relativity (GR) states that the
+  properties of an astrophysical Kerr black hole (BH) are completely described by its
+  mass and spin. As a consequence, the complex
+  quasi-normal-mode (QNM) frequencies of a binary--black-hole (BBH)
+  ringdown can be uniquely determined by the mass and spin of the
+  remnant object. Conversely, measurement of the QNM frequencies could
+  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to
+  test the no-hair conjecture by measuring the complex QNM
+  frequencies of a BBH ringdown using parameterized inspiral-merger-ringdown waveforms in the effective-one-body formalism, 
+thereby taking full advantage of the entire signal power and removing dependency on the
+  predicted or estimated start time of the ringdown. Our method was used to analyze the
+  properties of the merger remnants for BBHs observed by
+  LIGO-Virgo in the first half of their third observing (O3a) run.
+ After testing our method with GR and non-GR synthetic-signal injections in Gaussian noise, 
+we analyze, for the first time, two BBHs from the first (O1) and second (O2) LIGO-Virgo 
+  observing runs, and two additional BBHs from the O3a run. We then provide joint constraints with published results
+  from the O3a run. In the most agnostic and conservative scenario where we combine the information from different
+events using a hierarchical approach, we obtain, at $90\%$ credibility, that 
+the fractional deviations in the frequency (damping time) of the dominant QNM are 
+$\df{220}=0.03^{+0.10}_{-0.09}$ ($\dtau{220}=0.10^{+0.44}_{-0.39}$), respectively, an improvement of a factor of $\sim 4$ ($\sim 2$) 
+over the results obtained with our model in the LIGO-Virgo publication. The single-event most-stringent constraint to date continues to be 
+GW150914 for which we obtain $\df{220}=0.05^{+0.11}_{-0.07}$ and $\dtau{220}=0.07^{+0.26}_{-0.23}$.
 \end{abstract}
@@
 \label{sec:intro}
-\input{intro}
+The LIGO Scientific Collaboration~\cite{lsc} and the Virgo
+Collaboration~\cite{Virgo} have recently announced their catalogue of
+gravitational-wave (GW) signals from the first
+half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
+with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
+Washington and Livingston, Louisiana~\cite{Aasi:2014mqd},
+and the Advanced Virgo detector in Cascina,
+Italy~\cite{TheVirgo:2014hva} have now detected $50$ GW
+events from the merger of compact objects like neutron stars and/or
+black holes (BHs). Alongside independent claims of
+detections~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, GW150914~\cite{Abbott:2016blz}.
+
+The observation of GWs has had significant astrophysical and cosmological
+implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
+has also allowed us to probe fundamental
+physics and test predictions of Einstein's theory of General Relativity
+(GR) in the previously unexplored highly-dynamical, and strong field
+regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks}. In GR, a binary black hole (BBH) system is described by
+three distinct phases: an early \textit{inspiral}~\cite{Blanchet:2013haa}, where the two
+compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger}~\cite{Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv} marked by the
+formation of a common apparent horizon, and a \textit{ringdown}~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs) (i.e., damped oscillations with specific, discrete frequencies and decay times).
+
+The LIGO-Virgo collaborations have released companion papers detailing their results
+of tests of GR for GW150914 \cite{TheLIGOScientific:2016src}, and for several GW events of
+the two transient catalogues (TC): GWTC-1 \cite{LIGOScientific:2018mvr,LIGOScientific:2019fpa}  and GWTC-2 \cite{Abbott:2020niy,Abbott:2020jks}.
+The results include tests of GW generation and source dynamics, where bounds are placed on
+parameterized deviations in the post-Newtonian (PN) coefficients describing
+the early inspiral, and
+phenomenological coefficients describing the intermediate (plunge) and
+merger regimes of coalescence~\cite{Arun:2006hn,Arun:2006yw,Agathos:2013upa,Abbott:2018lct}; tests of GW
+propagation, which assume a generalized dispersion relation and place
+upper bounds on the Compton wavelength and, consequently, the mass of
+the graviton~\cite{Abbott:2017vtc,Samajdar:2017mka}, and tests of the
+polarization of gravitational radiation using a
+multi--GW-detector network~\cite{Abbott:2017oio,Isi:2017fbj}. The GWTC-1/2 papers also
+check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
+object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
+consistency of the residuals with detector noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
+departure from the predictions of GR.
+
+The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} also provided us with the first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
+coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}.
+The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
+The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
+One
+consequence of the no-hair conjecture is that the (complex) QNM
+frequencies of gravitational radiation emitted by a perturbed isolated
+BH are uniquely determined by its mass and spin. Hence
+a test of the no-hair conjecture would involve checking for
+consistency between estimates of mass and spin of the remnant object
+across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}. An inconsistency would either
+indicate a non-BH nature of the remnant object, or an incompleteness
+of GR as the underlying theory of gravity.
+
+The consistency between the post-merger signal and the least damped QNM was first demonstrated in
+Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analyses~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}.
+This was later extended to include
+overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw,Abbott:2020jks}. Consistency of the late-time waveform with a single QNM is a test of the ringdown of
+a BBH coalescence, but not necessarily a test of the no-hair
+conjecture, which requires the measurement of (at least) two QNMs (BH
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
+The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
+theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
+None of these tests have found evidence for non-BH nature of the remnant
+object (as described in GR) in LIGO-Virgo BBH observations.
+
+Ground-based detectors, such as LIGO and Virgo, are most sensitive to
+stellar-mass BH binaries that merge near the
+minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the
+remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
+very little signal-to-noise ratio (SNR) in the
+post-merger signal.
+Most of the tests mentioned above restrict the data to this post-merger signal, which significantly reduces parameter-estimation capabilities.
+However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
+In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a
+free parameter to be estimated directly from the data.
+Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{PyRING} analysis in Ref.~\cite{Abbott:2020jks}).
+Uncertainties
+in estimates of the ringdown start-time, as well as an overall lack of
+SNR in the post-merger signal, given typical sensitivities of
+ground-based detectors, result in significant statistical uncertainties
+in the measurement of the QNM frequencies. And hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
+
+An independent approach to BH spectroscopy, based on the full-signal
+analysis, was introduced in Ref.~\cite{Brito:2018rfr}
+(henceforth referred to as \paperone). Unlike methods that focus only
+on the post-merger signal, it employs the
+complete inspiral-merger-ringdown
+(IMR) waveform to measure the complex QNM
+frequencies. This gives access to the full SNR of the signal,
+reducing measurement uncertainties. Moreover, the definition of the
+ringdown start time is built into the merger-ringdown model and does not need to be
+either left as an additional free parameter or fixed using alternate
+definitions. While \paperone presented the method and tested it for non-spinning BBHs, here we extend the analysis to the more
+realistic astrophysical case in which BHs carry spin. Furthermore,
+the IMR waveform model used in this paper is more accurate than what employed in \paperone,
+because it contains higher-order corrections in PN theory and it was calibrated to a much larger set
+of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}. All astrophysical BHs are expected to be spinning,
+and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the
+source properties.
+
+The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
+waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
+complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
+several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
+we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
+the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
+our results and discuss future developments.
+
 %%%%%%%%%%%%%%%%%
@@
 \section{Waveform model and statistical strategy to measure quasi-normal modes}
-\input{model_method}
+A GW signal from the (quasi-circular) coalescence of two BHs is
+completely described in GR by $15$ parameters,
+$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
+the (source) masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
+objects in the binary; and the
+\emph{extrinsic} parameters: a reference time $t_c$ and phase
+$\phi_c$, the sky position of the binary ($\alpha$,
+$\delta$), the luminosity distance, $d_L$, and the binary's orientation
+described through the inclination of the binary $\iota$ and its
+polarization $\psi$. We also introduce the total (source) mass $M = m_1+m_2$,
+and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
+We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$.
+We also introduce the detector masses $m_{1\,\rm det}= (1+z)\,m_1$ and $m_{2 \,\rm det} = (1+z)\,m_2$,
+where $z$ is the redshift.
+
+Here, we focus on BHs with spins aligned or anti-aligned
+with the orbital angular momentum (henceforth, aligned-spin). In this case,
+the GW signal depends on $11$ parameters. We denote the
+aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
+
+\subsection{Parameterized waveform model}\label{sec:model}
+
+As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB)
+formalism~\cite{Buonanno:1998gg,Buonanno:2000ef}. However, whereas \paperone was limited to non-spinning multipolar waveforms,
+here we use as our baseline model the aligned-spin multipolar waveform model
+developed in Ref.~\cite{Cotesta:2018fcv}. In addition to being
+calibrated to NR simulations, this model also uses information from BH
+perturbation theory for the merger and ringdown phases. Henceforth we
+will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this
+waveform model is called {\tt SEOBNRv4HM}.}.
+
+In the observer's frame, the GW polarizations can be written as
+%
+\begin{equation}
+h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
+\end{equation}
+%
+where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
+The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
+For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
+%
+\begin{equation}
+h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
+\end{equation}
+where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
+%
+\begin{equation}
+\label{RD}
+h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
+\end{equation}
+%
+where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
+We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
+The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
+%
+\begin{subequations}
+\begin{eqnarray}
+\label{eq:ansatz_amp}
+\tilde{A}_{\ell m}(t) &=& c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},\\
+\label{eq:ansatz_phase}
+\tilde{\phi}_{\ell m}(t) &=& \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
+\end{eqnarray}
+\end{subequations}
+%
+where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
+The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
+are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
+This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
+%
+\begin{subequations}
+\begin{align}
+\label{c1}
+c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
+    m} \nu} \big[ \partial_t|h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
+    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
+    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
+\label{c2}
+c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
+    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
+    m} \nu} \big[ \partial_t|h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
+    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
+    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
+    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber
+\end{align}
+\end{subequations}
+and $d_{1,c}^{\ell m}$ as
+\begin{align}
+\label{d1}
+d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
+      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
+\end{align}
+%
+where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
+The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
+Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
+
+In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
+complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
+final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
+latter are related to the BBH's component masses and spins through
+NR--fitting-formulas obtained in
+GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
+spirit of what was done in \paperone, we promote the QNM (complex)
+frequencies to be free parameters of the model, while keeping the
+inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
+to their GR values. More explicitly, we introduce a parameterized
+version of the $\SEOB$ model where the frequency and the
+damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
+_{\ell m 0})$) are defined through the fractional deviations, $(\delta
+f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
+values~\cite{Gossan:2011ha,Meidam:2014jpa}.
+
+Thus,
+\begin{subequations}
+\begin{eqnarray}
+f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
+\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
+\end{eqnarray}
+\end{subequations}
+
+The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
+\begin{subequations}
+\begin{eqnarray}
+f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\\ 
+\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})
+\end{eqnarray}
+\end{subequations}
+We denote such a parameterized waveform model $\pSEOB$~\footnote{This
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
+freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
+  m}(t)$ in general also differ from the GR predictions, since
+those functions depend on the QNM complex frequencies, as can be seen
+from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
+(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 
+soon after merger deviates from the one predicted by GR.
+
+\subsection{Bayesian parameter-estimation technique}
+\label{sec:method}
+
+The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
+One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
+%
+\begin{equation}
+P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
+\label{eq:Bayes_theorem}
+\end{equation}
+%
+where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
+The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
+In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
+The likelihood function can consequently be defined as:
+%
+\begin{equation}
+\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
+\label{eq:likelihood}
+\end{equation}
+%
+where $\langle . | . \rangle$ is the usual noise-weighted inner product:
+%
+\begin{equation}
+\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
+\label{eq:nwip}
+\end{equation}
+%
+The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
+The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
+We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
+GW detector at low-frequency.
+Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
+Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
+For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
+
+Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
+
+\begin{equation}
+P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
+\end{equation}
+
+For most of the results discussed in this paper, we restrict ourselves
+to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
+\{\df{330},\dtau{330}\}$, and fix all the other $(\ell m)$ modes to their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
+\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH
+events that we find most appropriate for this test, the LIGO-Virgo
+observations are consistent with nearly--equal-mass face-on/off BBHs
+for which power in the subdominant modes is not enough to
+attempt to measure more than one QNM complex frequency.
+
+Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
+parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
+since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+derived through NR--fits, from the corresponding priors on the initial
+masses and spins, this leads to a non-trivial prior on the final
+reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
+  0})$. Also, given the definition of the damping time in
+Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
+to the imaginary part of the QNM complex frequency going to infinity. We avoid
+this by restricting the minimum of the prior on $\delta \tau_{\ell m
+  0}$ to be greater than $-1$.
+
 %%%%%%%%%%%%%%%%%
@@
 \label{sec:results}
-\input{results_synthetic}
+\subsection{Simulations using GR signals in Gaussian noise} \label{ssec:gr_signal}
+
+We now demonstrate our method using synthetic-signal injections describing GWs
+from BBHs in GR. We employ coloured Gaussian noise with PSDs for LIGO and
+Virgo detectors during the fourth observing (O4) run (i.e., at design sensitivity), which 
+is expected to start in the second half of 2022~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
+For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
+GW190521~\cite{Abbott:2020tfl}. We list them in Table~\ref{tab:injection_values}.
+These two binary systems are representative of the kind of systems for which
+the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the
+pre- and post-merger SNRs return reliable parameter-estimation results.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Table for Injections
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{ c|c|c|c|c|c|c|c|c }
+
+Injection &  Network & \makecell{$m_{\rm 1\,det}$ \\$(\Mo)$} &  \makecell{$m_{\rm 2\,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
+ \hline
+ GW150914-like & HL &39 & 31 & 0.0 & 0.0 & 25 & 22 & 12 \\
+ GW190521-like & HL & 150 & 120 & 0.02 & -0.39 & 20 & 8 & 18 \\
+ SXS:BBH:0166 & HLV &72 & 12  & 0.0 & 0.0 & 71 & 58 & 41 \\
+
+\end{tabular}
+\caption{Parameters of the synthetic-signal injections, chosen to be similar to the actual GW events indicated in the first column (first two rows).
+The parameters $(m_{\rm 1 \,det}, m_{\rm 2 \,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
+The third row indicates the parameters of the SXS BBH waveform used in Sec.~\ref{ssec:nohairtheorem}.
+The second column refers to the detector-network used, with H,L,V, referring to LIGO-Hanford, LIGO-Livingston and Virgo, respectively.
+The quantities $\rho_\text{IMR}$, $\rho_\text{insp}$ and $\rho_\text{postinsp}$ are the SNR of the full IMR signal, SNR upto a certain cutoff frequency, and SNR after the cutoff frequency respectively.
+In each case, the cutoff frequency is assumed to be the frequency at the innermost circular stable orbit (ISCO) corresponding to the remnant Kerr BH.}
+\label{tab:injection_values}
+\end{center}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Simulated siganl: GR
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[hbt]
+\begin{center}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}
+        \caption{Posterior probability
+          distribution on the fractional deviations in the frequency
+          and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$
+          (left panels) and the reconstructed quantities,
+          $(\fngr{220}, \taungr{220})$ (right panels) for GR
+          injections ($\SEOB$) with initial parameters similar to GW150914 (top
+          panels) and GW190521 (bottom panels)
+          (see Table~\ref{tab:injection_values}). The 2D contour marks the
+          90\% credible region, while the dashed lines on the 1D
+          marginalized distributions mark the 90\% credible
+          levels. The black vertical and horizontal lines mark the
+          injection values.}
+        \label{fig:simulated_signal_GR}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To avoid possible systematic biases in our parameter-estimation analysis
+due to error in waveform modeling, we use the GR version of the same waveform,
+$\SEOB$ (i.e., without allowing for deviations in the QNM parameters) to
+simulate our GW signal. And to avoid systematic biases due to noise,
+we use an averaged (zero-noise) realization of the noise~\footnote{A detailed
+study on noise systematics for one of the GW events is presented in
+Appendix~\ref{sec:noise_systematics}.}.  Since mearly--equal-mass binaries like GW150914 and
+GW190521 observed at moderately high SNRs are not expected to have a
+loud ringdown signal, we restrict ourselves to estimating the
+frequency and damping time of only one QNM $(\ell m) = (2,2)$ (i.e.,
+$\{\df{220},\dtau{220}\}$), while fixing the other QNM frequencies to
+their GR values.
+
+We find, as one might expect, that the posterior distribution on the
+parameters describing fractional deviations in the frequency and
+damping time are consistent with zero (left panels of
+Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
+fractional quantities into absolute quantities using the relations
+given in Eqs.~(\ref{eq:nongr_freqs_a}) and ~(\ref{eq:nongr_freqs_b}), and
+construct posterior distributions on these effective quantities,
+$(\fngr{220}, \taungr{220})$ (right panels of
+Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
+two-dimensional posteriors are consistent with the GR predictions
+(black dashed lines).
+
+\subsection{Simulations using non-GR signals in Gaussian noise} \label{ssec:ngr_signal}
+
+To demonstrate the robustness of the method in detecting possible
+deviations from GR, we inject synthetic GW signals which are identical to
+the corresponding GR prediction up to merger, and differ in their post-merger
+description. We again choose binary-parameters
+similar to GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but
+set $\df{220} = \dtau{220} = 0.1 $.
+In other words, we assume that the frequency and damping time
+of our non-GR signal is 10\% more than the corresponding GR prediction,
+although the pre-merger signal is identical to GR. In Fig.~\ref{fig:nongr_waveform}
+we show this non-GR waveform, \texttt{pSEOBNR} with respect to the 
+original GR template, \texttt{SEOBNR}. We see that the waveforms are identical in amplitude
+and instanteneous frequency upto the merger (lower panel) , beyond which the 
+red (GR template) and blue (non-GR template) differ. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
+show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
+$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding
+values of the injection parameters, indicated by the black dashed lines.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
+        \caption{Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
+Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
+        \label{fig:nongr_waveform}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Simulated siganl: non-GR
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+\begin{center}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
+        \caption{Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections ($\pSEOB$) with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
+The non-GR signal has a deviation, $\df{220} = \dtau{220} = 0.1$.
+The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
+The black vertical and horizontal lines mark the injection values.
+In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
+GW150914-like (upper panel) and GW190521-like (lower panel) injections. The measurements with $\SEOB$ waveforms are visibly biased.}
+        \label{fig:simulated_signal_nonGR}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% modified GR signal: GR vs nonGR recovery comparison
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_m1m2.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_a1za2z.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fgrtaugr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_Mfaf.png}
+        \caption{Comparison of binary's parameters when a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model. The left (right) panels refer to
+a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.1$.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) from the frequency and damping time.
+In each case, the injection values are indicated by the black dashed lines.}
+        \label{fig:gr_ngr_comparison}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\fi
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% GW150914-like signal with different deviations: GR vs nonGR recovery
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}%[h!]
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_m1m2.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_a1za2z.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_fgrtaugr.png}
+        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
+        \caption{Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) from the frequency and damping time.
+In each case, the injection values are indicated by the black dashed lines.
+In the lowermost panel, the injection values of the final mass and spin, correspond to the injection with no deviations.
+The $\df{220} = \dtau{220} = 0.1$ signal is identical to the results shown in Fig.~\ref{fig:simulated_signal_nonGR}.}
+        \label{fig:gr_ngr_comparison}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We additionally investigate the effects of erroneously assuming that
+an underlying non-GR signal can be well-described by a GR one. We do
+this by estimating the parameters of our non-GR signals using the GR
+waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
+resulting one- and two-dimensional posteriors are shown in the right
+panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
+GW150914-like (top) and GW190521-like (bottom) signals
+respectively. For both signals, we find the $\SEOB$ estimates are
+markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
+this impact on the estimation of the GR parameters $\bxigr$ by changing the
+magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
+to a GW150914-like event, and for comparison, add a synthetic signal
+with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
+10\% non-GR signal and a signal with no deviation (essentially GR)
+mentioned above. The left (right) panels show the
+posterior probability distributions of the three signals using the GR,
+$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
+note is the $\SEOB$ recoveries yield biased estimates when the
+underlying signal is non-GR, while the $\pSEOB$ recoveries do
+not. Furthermore, as we increase the deviations, while the $\SEOB$
+recoveries expectedly get more biased, the $\pSEOB$ measurements are
+robust in consistently recovering the injected value. This gives us 
+confidence that the $\pSEOB$ model can accurately measure QNM 
+properties without biasing measurements of inspiral quantities, like masses and spins.
+
+\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
+
+Finally, we provide a simple demonstration of a test of the no-hair
+theorem using our model. As described in the introduction, any test of
+the no-hair theorem of BHs would need to involve independent
+measurements of (at least) two different QNMs.
+
+Here, we use an NR GW signal from the SXS catalog~\cite{Mroue:2013xna}
+corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166) and 
+total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
+We choose an asymmetric system to increase the SNR in the higher modes.
+We also choose the distance and orientation of the binary
+such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
+Virgo, is {$\sim$ 70}. Based on the LIGO-Virgo observations during the first three observing runs, 
+such asymmetric and loud signals are no longer just a theoretical
+prediction, but quite plausible during O4. Using this
+signal, we attempt to measure both the $(2,2)$ and
+$(3,3)$ QNMs. For this injected signal the SNR in
+other sub-dominant modes is too low to be able to measure them.
+
+We summarize our results in Fig.~\ref{fig:nohair_sxs}.  Given the
+injection parameters, the predicted values of the $(2, 2)$ and
+$(3, 3)$ frequency and damping time are {(169.45 Hz, 4.68
+  ms)} and {(271.21 Hz, 4.50 ms)} respectively. The left panel
+of Fig.~\ref{fig:nohair_sxs} shows that the 2D posteriors
+on the $(2, 2)$ and $(3, 3)$ QNMs are consistent with the
+predictions for a BBH merger in GR, indicated by the black plus sign.
+Using fitting formulae provided in Ref.~\cite{Berti:2005ys}, specifically,
+Eq.~(2.1), Eq.~(E1) and Eq.~(E3) and Tables VIII and IX for the fitting coefficients,
+we infer the 2D posterior probability distribution on the
+final mass and spin as predicted independently by the $(2, 2)$ (blue) and $(3, 3)$ (red)
+QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
+independent estimates are consistent with each other and correspond to
+a unique mass and spin for the remnant BH {(83.08 $\Mo$, 0.37)}
+indicated by the plus sign. As a consequence, this may be considered
+as a test of the no-hair conjecture. For most of the events observed
+so far, the power in the $(3, 3)$ has not been sufficient to
+measure it along with the $(2, 2)$. However, it might also be possible to combine information from
+multiple observation over the coming few years to obtain meaningful
+constraints on the $(3, 3)$ and other sub-dominant QNMs~\cite{Gossan:2011ha,Meidam:2014jpa,Yang:2017zxs}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+        \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
+        \caption{Posterior probability distribution on the frequency and damping time of the $(2, 2)$ and $(3, 3)$ QNM (left panel), and the final mass and spin inferred from the complex frequencies (right panel), when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
+The plus signs mark the GR predictions.}
+        \label{fig:nohair_sxs}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%
@@
 \section{Constraints on QNM frequencies using LIGO-Virgo data}
-\input{results_lvc}
+\label{sec:results_lvc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% O1-O2 events
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.3\textwidth]{figures/rin_all_events_bounds.pdf}
+        \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2, 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
+The solid purple curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
+The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
+\emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
+Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).
+The purple square marker indicates constraints from the single most-prominent event, GW150914.}
+        \label{fig:o1o2_events}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The LIGO-Virgo Collaboration recently released their testing GR
+catalogue containing results for events observed
+during O3a~\cite{Abbott:2020jks}.
+For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median detector-frame total mass $\geq 90 \Mo$ and SNRs in the pre- and
+post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
+The SNR values are listed in Table IV of Ref.~\cite{Abbott:2020jks}}.
+%
+The SNR threshold ensures that the signal contains sufficient
+information in both the inspiral and merger stages to break the
+degeneracy between the binary's total mass and the non-GR deviations
+$(\df{220}, \dtau{220})$. Such strong degeneracy is present for
+low-SNR events with negligible higher-modes and for which only the
+post-merger is detectable rendering the measurement of $(\df{220},
+\dtau{220})$ impossible for those cases (see Appendix~\ref{sec:correlation} for more details). On the other hand the
+total mass threshold $\geq 90 \Mo$ was employed due to the fact that
+this analysis is computationally expensive, and also because we
+expected these events to be the most promising for ringdown
+studies. However, since the SNR threshold alone should be sufficient
+for the analysis, for this paper we run the test on all the events
+listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and
+post-merger regions $\geq 8$, without imposing any mass threshold.
+
+Given the above we add the signals  GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in Ref.~\cite{Abbott:2020jks}. Furthermore, for the first time, 
+we apply our method to measure the QNMs to GW events from O1 and O2, notably GW150914 and GW170104. The other high-mass events from O1 and O2, GW170729, GW170809,
+GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
+merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}.
+
+For all the relevant signals, we show the posterior distributions
+$(\df{220}, \dtau{220})$ in the left panel of
+Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM
+parameters, $(\fngr{220}, \taungr{220})$ in
+Table~\ref{tab:qnm_o1o2_results}. In the right panel of
+Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%
+credible intervals on the 1D marginalized posteriors. We highlight the
+dependence of the constraints on the total mass of the
+system. In general, the tightest bounds are set by the 
+most massive systems, as they tend to have larger post-merger SNR. We
+find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.
+
+Among all the GW signals detected so far, GW150914 (solid curve in
+Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the
+first, and to date, best attempt in measuring the QNM
+frequencies~\cite{TheLIGOScientific:2016src,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}. Within
+90\% credibility we obtain from GW150914:
+%
+\begin{equation}\label{GW150914_delta}
+\df{220}=0.05^{+0.11}_{-0.07}\,\quad \dtau{220}=0.07^{+0.26}_{-0.23}\,.
+\end{equation}
+
+Stronger constraints can be obtained by combining information from all the events~\cite{Abbott:2020jks}.
+If we assume that the fractional deviations $(\df{220},\dtau{220})$ take the same values in multiple events, we can assume
+the posterior of one event to be the prior for the next, and obtain a
+joint posterior probability distribution. For $N$ observations, where
+$P(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
+observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
+posterior is given by:
+%
+\begin{equation}
+P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}\,,
+\end{equation}
+%
+where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
+\dtau{220})$. However, since here we assume the prior on $(\df{220},
+\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
+the joint likelihood.
+We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding 1D marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
+From the joint likelihood we obtain within 90\% credibility:
+%
+\begin{equation}
+\df{220}=0.02^{+0.04}_{-0.04}\,,\quad \dtau{220}=0.10^{+0.14}_{-0.14}\,.
+\end{equation}
+%
+
+However, in most non-GR theories, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so if GR were to be wrong, one should expect their value to vary across the GW signals observed by LIGO and Virgo.
+As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a constant deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
+The general idea behind this technique is to assume that the non-GR parameters $(\df{220},\dtau{220})$ are drawn from a common underlying distribution, whose properties can be inferred from the population of events.
+Following~\cite{Zimmerman:2019wzo,Isi:2019asy,Abbott:2020jks} we model the population distribution with a Gaussian  $\mathcal{N}(\mu,\sigma)$ of unknown mean $\mu$ and standard deviation $\sigma$.
+Under those assumptions, the goal is then to directly measure a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for $\mu$ and $\sigma$ from a joint analysis of all the GW events.
+If GR is correct, then this posterior should be consistent with $\mu=0$ and $\sigma=0$.
+From Bayes' theorem it follows that~\cite{Isi:2019asy}:
+%
+\begin{equation}
+P(\mu, \sigma |  \{d_j\}) \propto P(\mu,\sigma)\prod _{j=1}^N P(d_j |\, \mu, \sigma) \,,
+\end{equation}
+%
+where $P(\mu,\sigma)$ is the prior (also known as hyperprior) on ($\mu,\sigma$), and $P(d_j | \mu, \sigma) $ can be written in terms of the individual likelihoods of a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}
+%
+\begin{equation}
+P(d_j | \mu, \sigma) = \int P(d_j |\, \xi_{\text{nGR}})  P(\xi_{\text{nGR}} |\, \mu, \sigma) \,d\xi_{\text{nGR}} \,.
+\end{equation}
+%
+Here $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$ by construction and $P(d_j |\, \xi_{\text{nGR}})$ is the likelihood for the parameter $\xi_{\text{nGR}}$ for a given event $d_j$ that is computed from the standard parameter estimation analysis.
+After obtaining $P(\mu, \sigma |  \{d_j\})$, we can then infer a population distribution for a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}:
+%
+\begin{equation}\label{hier_combine}
+P(\xi_{\text{nGR}} | \{d_j\}) = \int P(\xi_{\text{nGR}} |\, \mu, \sigma)\,P(\mu, \sigma |  \{d_j\})\,d\mu\,d\sigma \,.
+\end{equation}
+%
+Notice that, if we fix $\sigma=0$, this approach is equivalent to assume that all events share the same non-GR parameter $\xi_{\text{nGR}} =\mu$ and Eq.~\eqref{hier_combine} reduces to the joint likelihood~\cite{Zimmerman:2019wzo}.
+In practice, we use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $ and compute $P(\xi_{\text{nGR}} | \{d_j\})$.
+
+The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained with this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
+%
+\begin{equation}
+\df{220}=0.03^{+0.10}_{-0.09}\,,\quad \dtau{220}=0.10^{+0.44}_{-0.39}\,.
+\end{equation}
+Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ more stringent for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$.
+Similar improvements hold for the hyperparameters: $\df{220}\,(\mu=0.03^{+0.06}_{-0.05},\,\sigma<0.09)$ and $\dtau{220}\,(\mu=0.11^{+0.21}_{-0.19},\,\sigma<0.39)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Table for LVC values
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}
+
+\begin{tabular}{l|c|c|c|c|c|c}
+\toprule
+Event & $\fngr{220}$ (Hz) & $\taungr{220}$ (ms) & $(1+z)M_f/\Mo$ & $\chi_f$ & $(1+z)M_{\text{f}}^{\rm IMR}/\Mo$ & $\chi_{\text{f}}^{\rm IMR}$ \\[0.075cm]
+\midrule
+\hline
+
+GW150914 &
+$257.6^{+17.0}_{-12.8}$ &
+$4.49^{+1.09}_{-0.95}$ &
+$71.0^{+8.7}_{-10.3}$ &
+$0.77^{+0.09}_{-0.18}$ &
+$67.3^{+2.7}_{-2.6}$ &
+$0.67^{+0.03}_{-0.04}$
+\\[0.075cm]
+
+GW170104 &
+$291.4^{+14.7}_{-30.1}$ &
+$5.53^{+3.47}_{-2.40}$ &
+$73.8^{+11.1}_{-19.8}$ &
+$0.89^{+0.07}_{-0.36}$ &
+$56.9^{+3.0}_{-3.0}$ &
+$0.65^{+0.05}_{-0.07}$
+\\[0.075cm]
+
+GW190519\_153544 &
+$123.6^{+11.9}_{-13.0}$ &
+$10.33^{+3.56}_{-3.07}$ &
+$155.5^{+24.0}_{-29.9}$ &
+$0.81^{+0.10}_{-0.28}$ &
+$144.1^{+14.5}_{-16.2}$ &
+$0.78^{+0.08}_{-0.14}$
+\\[0.075cm]
+
+GW190521\_074359 &
+$204.6^{+14.6}_{-11.7}$ &
+$5.32^{+1.48}_{-1.21}$ &
+$86.4^{+12.2}_{-14.3}$ &
+$0.73^{+0.12}_{-0.26}$ &
+$87.1^{+3.3}_{-3.8}$ &
+$0.70^{+0.03}_{-0.05}$
+\\[0.075cm]
+
+GW190630\_185205 &
+$247.8^{+31.8}_{-52.8}$ &
+$3.87^{+2.37}_{-1.80}$ &
+$65.6^{+18.8}_{-41.5}$ &
+$0.62^{+0.27}_{-0.62}$ &
+$66.2^{+4.0}_{-3.2}$ &
+$0.70^{+0.05}_{-0.08}$
+\\[0.075cm]
+
+GW190828\_063405 &
+$257.8^{+201.3}_{-27.8}$ &
+$4.23^{+4.17}_{-1.92}$ &
+$67.4^{+25.7}_{-30.0}$ &
+$0.76^{+0.20}_{-0.73}$ &
+$75.8^{+5.0}_{-5.0}$ &
+$0.74^{+0.04}_{-0.06}$
+\\[0.075cm]
+
+GW190910\_112807 &
+$174.2^{+11.7}_{-7.5}$ &
+$9.52^{+3.13}_{-2.68}$ &
+$123.5^{+14.7}_{-18.1}$ &
+$0.90^{+0.05}_{-0.11}$ &
+$94.9^{+7.6}_{-8.6}$ &
+$0.72^{+0.08}_{-0.04}$
+\\[0.075cm]
+
+\bottomrule
+\end{tabular}
+\caption{The median and symmetric 90\% credible intervals of the remnant properties.
+The first two columns represent the frequency and damping time of the $(2,2)$ QNM measured using the $\pSEOB$ model.
+The next two columns are the mass and spin of the remnant object estimated from the complex QNM frequencies by inverting the fitting formula in~\cite{Berti:2005ys}.
+The last two columns represent final mass and spin estimates predicted using NR fitting formulae from a $\SEOB$ parameter estimation.}
+\label{tab:qnm_o1o2_results}
+\end{table*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%
@@
 \label{sec:discussion}
-\input{discussion}
+We have built a parameterized IMR waveform model, $\pSEOB$, that can 
+measure the QNM complex frequencies of the remnant object formed through 
+the merger of BHs with aligned or antialigned spins, thus extending  
+previous work, which was limited to non-spinning BHs~\cite{Brito:2018rfr}. 
+The $\pSEOB$ model was recently used to infer the QNMs of some of the 
+BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.
+
+After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
+injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
+We have analyzed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
+with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
+results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
+we have obtained more stringent bounds on the dominant (or least-damped) QNM $(\ell=2,m=2)$.
+
+More specifically, as expected, the single GW event providing the best constraint
+on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.05^{+0.11}_{-0.07}, 
+\dtau{220}=0.07^{+0.26}_{-0.23})$. In addition, in the most agnostic and
+conservative scenario where we combine the information from different
+events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
+at $90\%$ credibility $(\df{220}=0.03^{+0.10}_{-0.09}, \dtau{220}=0.10^{+0.44}_{-0.39})$. Thus, 
+our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
+10\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
+over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.
+
+Furthermore, when assuming that the deviations from GR do not vary appreciably over the GW events 
+that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
+on the dominant QNM $(\df{220}=0.02^{+0.04}_{-0.04}, \dtau{220}=0.10^{+0.14}_{-0.14})$. Those 
+constraints are compatible, but sligthly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 
+(see first row in Table II therein), where QNM frequencies were inferred using only the post-merger part of 
+the signal. We note that Ref.~\cite{Carullo:2021dui} used a larger set of GW events from O1, O2 and O3a than we did, although we expect 
+that the extra GW events will not contribute significantly to the combined bound since they have lower SNRs.
+
+These constraints could in principle be used to constrain specific
+non-GR theories and exotic compact objects~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}. 
+However, QNM computations in non-GR theories have only been done in an
+handful of cases, mostly focusing on non-rotating or slowly-rotating
+BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao,Wagle:2021tam,Pierini:2021jxd},
+or relying on the eikonal/geometric optics approximation to obtain
+estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}. The
+only exceptions to this rule, that we are aware of, are computations
+of the QNM of Kerr-Newman BHs in Einstein-Maxwell
+theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} or estimates of the BBH in non-GR theories obtained
+through a limited number of NR simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
+limitations, our ability of going beyond a null test of GR and use our
+results to impose precise constraints on non-GR theories with QNM
+measurements is currently quite limited.
+
+Despite these theoretical limitations there has been some recent effort to develop
+parametrizations that could help mapping measurements of the
+parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto
+constraints to specific non-GR theories. This includes for example
+the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently
+applied to LIGO-Virgo GW events in Ref.~\cite{Carullo:2021dui}, where
+deviations from the GR QNMs explicitly depend on a perturbative
+expansion in the BH spin and possible extra non-GR parameters, or the
+proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where
+deviations from the GR QNMs are mapped onto generic small
+modifications of the perturbation equations describing the QNMs. Other
+examples also include proposals to map deviations from the GR QNMs to
+coefficients in generic effective--field-theory
+actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to
+directly relate measurements of the QNM complex frequencies to a
+parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa}, 
+which could be then used jointly with measurements from the Event
+Horizon Telescope to obtain stronger constraints on deviations from
+GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
+We should note, however, that all these parametrizations are either
+limited to non-spinning BHs or make use of a series expansion in the
+BH spin which might limit their accuracy for highly-spinning BHs, unless 
+the sensitivity of GW detectors will not allow us to access the higher 
+coefficients in the spin series.
+
+In the future, it would be important to test whether the $\pSEOB$  model
+could be used to detect deviations in waveforms obtained through NR 
+simulations of specific non-GR theories. Such results are still at their 
+infancy and have so far only been done for a handful of theories, focusing mostly on proof-of-concept
+simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}. Nonetheless,
+given the recent efforts put forward in order to simulate BBHs in
+non-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.
+
+Finally, an obvious generalization of this work would be to extend the
+parameterized $\pSEOB$ model to generic precessing BBHs, which can in
+principle be easily done using the recently developed multipolar EOB
+model reported in Ref.~\cite{Ossokine:2020kjp}. Lastly, it will be relevant 
+to include GR deviations in the $\pSEOB$ model also during the late inspiral 
+and plunge stages of the BBH coalescence. On the other hand, GR deviations (notably 
+deviations from PN theory) for the long inspiral stage are currently 
+available in the $\pSEOB$ model and have been used to set bounds on the 
+PN parameters in the GW phasing using LIGO and Virgo observations~\cite{Abbott:2018lct,
+LIGOScientific:2019fpa,Abbott:2020jks}.
+
 %%%%%%%%%%%%%%%%%
@@
 \label{sec:acknowledgements}
-\input{acknowledgements}
+The authors thank Max Isi for generously allowing us to use the code developed in Ref.~\cite{Isi:2019asy} for the hierarchical inference analysis.
+The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
+We would like to acknowledge the computing resources at the AEI and the LIGO Scientific Collaboration, specifically the Hypatia and CIT clusters.
+R.B.
+acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
+792862, from the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001).
+We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
 %%%%%%%%%%%%%%%%%
@@
 \appendix
-\input{appendix}
+\section{Study of systematics in ringdown measurements in real, non-Gaussian noise}\label{sec:noise_systematics}
+
+Inferences of all parameters in this paper have been done under the
+assumption that the noise in the detectors is stationary and
+Gaussian. In other words, detector noise follows a normal distribution
+with zero mean and a PSD, $S_n(f)$, that is not a function of time, at
+least during the duration of the GW signal. This
+allows us to write the Bayesian likelihood function in the form given
+in Eqs.~(\ref{eq:likelihood}) and ~(\ref{eq:nwip}), and perform all the
+parameter estimation that follows in the results sections. However,
+LIGO-Virgo noise can often have features that deviate from
+stationarity and Gaussianity. If such features are not taken into
+account appropriately, final estimates of parameters can get
+biased. Here we demonstrate one such case by injecting in real noise a
+GW190521-like signal and showing how parameter estimates can be biased
+when our description of detector noise is not complete.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\begin{center}
+        \includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
+        \caption{90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2, 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
+The GR prediction for the frequency and damping time is indicated by the black cross.
+While the Gaussian noise simulations are consistent with the prediction, at least 3 of the 5 real noise simulation are not.
+The black curve corresponds to the measurements of the real event GW190521 reported in Ref.~\cite{Abbott:2020jks}.
+All signals are recovered using the $\pSEOB$ model.}
+        \label{fig:21g_systematics}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We choose a spin, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
+called \texttt{NRSur7dq4} in LAL.} (valid up to mass ratio 4) to simulate the actual GW190521 signal
+observed by the LIGO and Virgo detectors~\cite{Abbott:2020tfl} (see
+Table I of Ref.~\cite{Abbott:2020tfl})). The choice of the
+\texttt{NRSur} model is motivated by the fact that it is the most
+accurate model in the parameter range described by GW190521, because 
+it is built by directly interpolating NR waveforms. In
+Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what
+the injected \texttt{NRSur} signal predicts for the QNM $(\ell=2,m=2)$
+frequency and damping time. For comparison, we also show with a
+black solid curve the results obtained when recovering the actual
+signal GW190521 with the $\pSEOB$ model. As seen in the plot,
+while the measurement of the frequency is consistent with the
+prediction, we overestimate the damping time.
+
+To understand such offset in the decay time, we proceed as follows.
+The actual GW190521 event was observed at a GPS time, 1242442967.61
+seconds (roughly 03:02:49 UTC, May 21, 2019). We select a time period
+of about 2.5 hours around this GPS time, create synthetic signals 
+with the \texttt{NRSur} model and inject them in different stretches
+of the real detector noise around the time of the actual GW event. The
+PSDs of GW detectors are expected to vary over longer durations of
+time, and hence the 2.5 hour stretch of noise we consider can be
+assumed to have noise-properties similar to the time of the actual
+event. Then, we perform Bayesian analysis against those injections 
+using the $\pSEOB$ model. The results are indicated by green curves in
+Fig.~\ref{fig:21g_systematics}. As it can be seen from the figure, for
+3 of the 5 noise realizations, corresponding to $t_0-1$ hour,
+$t_0+0.5$ hours, and $t_0+1$ hour, we recover a damping time similar to
+the one obtained when using the $\pSEOB$ model against the actual event GW190521 
+(black curve), where $t_0$ is the GPS time of the actual event. For
+the other two noise realizations, the $\pSEOB$ model estimates 
+consistently the damping time, but has an off-set frequency, 
+while the fifth noise realization is consistent with both predictions.  
+This study suggests that a bias in the measurements of the damping time 
+for the actual event GW190521 can be explained as due to an incomplete 
+description of the noise at the time of the event.
+
+The reader might question the judiciousness of using an aligned-spin
+waveform model, like $\pSEOB$, to measure a signal like GW190521 which
+appears to be precessing, especially because an incomplete
+understanding of the underlying signal can also lead to biases in
+measured quantities, as we have already demonstrated in
+Sec.~\ref{ssec:ngr_signal}. In order to explore possible effects of
+missing information about in-plane spins in the $\pSEOB$ model, we repeat the
+above study of injecting synthetic signals using \texttt{NRSur}
+and recovering using the $\pSEOB$ model, but this time, instead of
+using real detector noise, we use Gaussian noise (i.e., realizations
+of noise sampled from a predicted detector PSD). Since the properties
+of the noise are completely understood in this case, any residual
+measurement biases can be completely attributed to diffferences in the
+waveform model. The 2D posterior distributions of the frequency and
+damping time measured using these Gaussian-noise signals are shown by
+the grey curves in Fig.~\ref{fig:21g_systematics}. We find the
+measurements to be completely consistent with the predictions of the
+frequency and damping time, thus concluding that a lack of in-plane
+spins in the $\pSEOB$ model does not affect our measurements of the
+QNM properties. The fact that the measurement of ringdown quantities
+are robust against an incomplete description of the inspiral signal 
+is a crucial property of our method.
+
+\section{Correlation of the binary's total mass with the non-GR parameters}\label{sec:correlation}
+
+As mentioned in the main text, for low-SNR events with negligible
+higher-modes and for which only the post-merger is detectable, there
+is a strong degeneracy between the binary's total mass and the non-GR
+deviations $(\df{220}, \dtau{220})$. For those cases, only the
+reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
+be independently measured from the data.
+
+To justify this statement, in Fig.~\ref{fig:correlations} we show
+corner plots that illustrate the correlations between the non-GR
+parameters $(\df{220}, \dtau{220})$, the detector-frame total mass
+$M(1+z)$ and the reconstructed frequency and damping time
+$(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an
+event for which both the pre- and post-merger phase are measurable,
+and for GW190521 (right panel), an event in which the post-merger has
+${\rm SNR}> 8$, but the pre-merger has an SNR below 8. For GW190521,
+due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D
+posterior for $M(1+z)$ is pushed towards the upper boundary of its
+prior, despite the very wide prior employed in the analysis. This in
+turn renders the measurement of $\df{220}$ (and to a lesser degree of
+$\dtau{220}$) highly dependent on the upper boundary of the total mass
+prior. On the other hand, this issue does not significantly affect the
+posteriors for the reconstructed quantities $(f_{220},\tau _{220})$
+which are well measured and nearly independent on the upper prior
+boundary for $M(1+z)$.
+%
+This is to be contrasted with the results for GW150914. In this case, 
+the extra information coming from the pre-merger phase allows to break 
+the degeneracy between the non-GR parameters and the total mass, 
+and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can 
+be measured at the same time.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{center}
+        \includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_GW150914.pdf}\includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_S190521g.pdf}
+        \caption{Corner plots showing the correlations between the detector-frame total $(1+z)M$, the non-GR deviations $(\df{220}, \dtau{220})$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$.
+The left panel shows results for GW150914, for which ${\rm SNR}> 8$ in both the pre- and
+post-merger phase of the signal, and the correlations are absent.
+The right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase, but not in the pre-merger phase, and the correlations are present.}
+        \label{fig:correlations}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2021-03-26 papers/intro_paper/intro_paper.tex
mention the comparable bounds on dtau220 between 21r and 150914
minor update
minor typesetting change in appendix

@@
 on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.05^{+0.11}_{-0.07}, 
-\dtau{220}=0.07^{+0.26}_{-0.23})$. In addition, in the most agnostic and
+\dtau{220}=0.07^{+0.26}_{-0.23})$, although the bounds on 
+$\dtau{220}$ from GW150914 are comparable to GW190521\_074359, 
+the second-most precisely measured event in our list.
+In addition, in the most agnostic and
 conservative scenario where we combine the information from different
@@
 
-\section{Correlation of the binary's total mass with the non-GR parameters}\label{sec:correlation}
+\section{Correlation of the binary's total mass with the non-GR parameters}
+\label{sec:correlation}
 
@@
 reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
-be independently measured from the data.
-
-To justify this statement, in Fig.~\ref{fig:correlations} we show
+be independently measured from the data. To justify this statement, 
+in Fig.~\ref{fig:correlations} we show
 corner plots that illustrate the correlations between the non-GR
@@
 which are well measured and nearly independent on the upper prior
-boundary for $M(1+z)$.
-%
-This is to be contrasted with the results for GW150914. In this case, 
+boundary for $M(1+z)$. This is to be contrasted with the results for GW150914. In this case, 
 the extra information coming from the pre-merger phase allows to break 

### 2021-03-31 papers/intro_paper/intro_paper.tex
added responses to referee comments in section III B

@@
 values of the injection parameters, indicated by the black dashed lines. 
+\abhi{We also note that at the SNRs we consider, since statistical uncertainties dominate systematic biases, the measurement excludes, at the 90\% credible level, the GR prediction on the frequency ($\df{220}=0$), but includes the prediction on the damping time ($\dtau{220}=0$).
+However, with louder events, one would expect these measurement errors to shrink and the $\taungr{220}$ measurement to be inconsistent with the GR prediction as well.}
 

### 2021-03-31 papers/intro_paper/intro_paper.tex
added responses to referee comments
going through gregorio's commetns sec I and II

@@
 The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
-The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
+The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
 One
@@
 This was later extended to include
-overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw,Abbott:2020jks}. Consistency of the late-time waveform with a single QNM is a test of the ringdown of
+overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Abbott:2020jks}. Consistency of the late-time waveform with a single QNM is a test of the ringdown of
 a BBH coalescence, but not necessarily a test of the no-hair
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd,Bhagwat:2019dtm,Forteza:2020hbw}.
 The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
-theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
+theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, \rb{the consistency of the merger frequency with predictions from NR simulations~\cite{Carullo:2018gah}} or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
 None of these tests have found evidence for non-BH nature of the remnant
@@
 post-merger signal.
-Most of the tests mentioned above restrict the data to this post-merger signal, which significantly reduces parameter-estimation capabilities.
+Most of the tests mentioned above restrict the data to this post-merger signal \rb{which, while being agnostic to deviations in the pre-merger dynamics, significantly} reduces parameter-estimation capabilities.
 However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
@@
 free parameter to be estimated directly from the data.
-Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{PyRING} analysis in Ref.~\cite{Abbott:2020jks}).
+Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{pyRing} analysis in Ref.~\cite{Abbott:2020jks}).
 Uncertainties
@@
 SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, result in significant statistical uncertainties
-in the measurement of the QNM frequencies. And hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
+ground-based detectors, \rb{can result in significant statistical uncertainties in the measurement of some of the QNM properties.
+This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data}.
+Hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
 
@@
 (IMR) waveform to measure the complex QNM
-frequencies. This gives access to the full SNR of the signal,
-reducing measurement uncertainties. Moreover, the definition of the
+frequencies.
+\rb{This method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies, which allows us to access to the full SNR of the signal and
+reduce measurement uncertainties}. Moreover, the definition of the
 ringdown start time is built into the merger-ringdown model and does not need to be
@@
 we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
-the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
+the GWTC-2 events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
 our results and discuss future developments.
@@
 \begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})
+f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,,\\ 
+\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,.
 \end{eqnarray}
@@
 The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
+One then proceeds to use the Bayes' theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
 %
@@
 GW150914-like (top) and GW190521-like (bottom) signals
-respectively. For both signals, we find the $\SEOB$ estimates are
+respectively. For both signals, we find the \abhi{2D} $\SEOB$ estimates are
 markedly biased with respect to the $\pSEOB$ estimates.  We investigate 

### 2021-03-31 papers/intro_paper/intro_paper.tex
minor changes

@@
 Most of the tests mentioned above restrict the data to this post-merger signal \rb{which, while being agnostic to deviations in the pre-merger dynamics, significantly} reduces parameter-estimation capabilities.
-However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
+Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
 In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a
@@
 frequencies.
-\rb{This method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies, which allows us to access to the full SNR of the signal and
-reduce measurement uncertainties}. Moreover, the definition of the
+\rb{This method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies.
+This allows to access the full SNR of the signal, reducing
+measurement uncertainties.} Moreover, the definition of the
 ringdown start time is built into the merger-ringdown model and does not need to be

### 2021-03-31 papers/intro_paper/intro_paper.tex
added responses for comments in section 3 and 4

@@
 with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\cite{Aasi:2014mqd},
+Washington and Livingston, Louisiana~\cite{TheLIGOScientific:2014jea},
 and the Advanced Virgo detector in Cascina,
@@
 conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd,Bhagwat:2019dtm,Forteza:2020hbw}.
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Gossan:2011ha, Meidam:2014jpa,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
 The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
@@
 Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
+For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc,Speagle_2020} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
 
@@
 
-\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% modified GR signal: GR vs nonGR recovery comparison
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_m1m2.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_a1za2z.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fgrtaugr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_Mfaf.png}
-        \caption{Comparison of binary's parameters when a non-GR signal ($\pSEOB$) is injected and recovered with a GR ($\SEOB$) or a non-GR ($\pSEOB$) waveform model. The left (right) panels refer to
-a GW150914-like (GW190521- like) injected signal (see Table~\ref{tab:injection_values}) with QNM deviation parameters of $\df{220} = \dtau{220} = 0.1$.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) from the frequency and damping time.
-In each case, the injection values are indicated by the black dashed lines.}
-        \label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\fi
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
          \caption{Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) from the frequency and damping time.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) \abhi{(fourth row)} from the frequency and damping time.
 In each case, the injection values are indicated by the black dashed lines.
@@
 properties without biasing measurements of inspiral quantities, like masses and spins.
+\abhi{For the samples of the final mass and spin in the last row, we start from the samples
+of the complex QNM frequencies $(\fngr{220}, \taungr{220})$ that are obtained from the 
+fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
+$(\fgr{220},\taugr{220})$ using Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b},
+and then invert them $(\fngr{220}, \taungr{220})$ using the fitting formula in~\cite{Berti:2005ys}.
+The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
+three unique sets of values for $(M_f,\chi_f)$. These predicted values are correctly 
+recovered by the $\pSEOB$ waveform (bottom-right plot in Fig.~\ref{fig:gr_ngr_comparison}),
+leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
+analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$. }
 

### 2021-03-31 papers/intro_paper/intro_paper.tex
added responses to comments in appendix

@@
 The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
-We would like to acknowledge the computing resources at the AEI and the LIGO Scientific Collaboration, specifically the Hypatia and CIT clusters.
-R.B.
+\abhi{The authors are grateful for computational resources provided by the LIGO Laboratory and supported by the National Science Foundation Grants PHY-0757058 and PHY-0823459, as well as computational resources at the AEI, specifically the Hypatia cluster.} R.B.
 acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
@@
 
-We choose a spin, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
+We choose a \abhi{spinning}, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
 called \texttt{NRSur7dq4} in LAL.} (valid up to mass ratio 4) to simulate the actual GW190521 signal

### 2021-03-31 papers/intro_paper/intro_paper.tex
address comment in intro

@@
 Ground-based detectors, such as LIGO and Virgo, are most sensitive to
-stellar-mass BH binaries that merge near the
+stellar-mass BH binaries \rb{that form remnants with mass $\gtrsim 50 M_{\odot}$ and} merge near the
 minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the

### 2021-03-31 papers/intro_paper/intro_paper.tex
minor comment

@@
 \label{sec:acknowledgements}
-The authors thank Max Isi for generously allowing us to use the code developed in Ref.~\cite{Isi:2019asy} for the hierarchical inference analysis.
+The authors thank Max Isi for generously allowing us to use the code developed in Ref.~\cite{Isi:2019asy} for the hierarchical inference analysis, and Gregorio Carullo for carefully reading the manuscript and providing useful comments.
 The authors would like to thank everyone at the frontline of the Covid-19 pandemic.

### 2021-03-31 papers/intro_paper/intro_paper.tex
some changes

@@
 frequencies.
-\rb{This method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies.
+\ab{In the current version, this method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies.
 This allows to access the full SNR of the signal, reducing
-measurement uncertainties.} Moreover, the definition of the
+measurement uncertainties. However, we note that this method can incorporate deviations from GR, notably from the (known) PN coefficients,  
+also during the long inspiral stage~\cite{Abbott:2018lct,
+LIGOScientific:2019fpa,Abbott:2020jks}, and can in principle incorporate deviations from GR, notably from the parameters calibrated to NR simulations,  
+in the late inspiral and plunge.} Moreover, in this method, the definition of the
 ringdown start time is built into the merger-ringdown model and does not need to be
@@
 To demonstrate the robustness of the method in detecting possible
-deviations from GR, we inject synthetic GW signals which are identical to
-the corresponding GR prediction up to merger, and differ in their post-merger
-description. We again choose binary-parameters
-similar to GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but
-set $\df{220} = \dtau{220} = 0.1 $.
-In other words, we assume that the frequency and damping time
-of our non-GR signal is 10\% more than the corresponding GR prediction,
-although the pre-merger signal is identical to GR. In Fig.~\ref{fig:nongr_waveform}
-we show this non-GR waveform, \texttt{pSEOBNR} with respect to the 
-original GR template, \texttt{SEOBNR}. We see that the waveforms are identical in amplitude
-and instanteneous frequency upto the merger (lower panel) , beyond which the 
-red (GR template) and blue (non-GR template) differ. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
-show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
-$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding
-values of the injection parameters, indicated by the black dashed lines. 
-\abhi{We also note that at the SNRs we consider, since statistical uncertainties dominate systematic biases, the measurement excludes, at the 90\% credible level, the GR prediction on the frequency ($\df{220}=0$), but includes the prediction on the damping time ($\dtau{220}=0$).
-However, with louder events, one would expect these measurement errors to shrink and the $\taungr{220}$ measurement to be inconsistent with the GR prediction as well.}
+deviations from GR, we inject synthetic GW signals which are identical
+to the corresponding GR prediction up to merger, and differ in their
+post-merger description. We again choose binary-parameters similar to
+GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but set
+$\df{220} = \dtau{220} = 0.1 $.  In other words, we assume that the
+frequency and damping time of our non-GR signal is 10\% more than the
+corresponding GR prediction, although the pre-merger signal is
+identical to GR. In Fig.~\ref{fig:nongr_waveform} we show this non-GR
+waveform, \texttt{pSEOBNR} with respect to the original GR template,
+\texttt{SEOBNR}. We see that the waveforms are identical in amplitude
+and instanteneous frequency upto the merger (lower panel) , beyond
+which the red (GR template) and blue (non-GR template) differ. We
+summarize the results of the Bayesian analysis in
+Fig.~\ref{fig:simulated_signal_nonGR} where we show the posterior
+probability distributions for $(\df{220}, \dtau{220})$, or
+equivalently $(\fngr{220}, \taungr{220})$. We find that they are
+consistent with the corresponding values of the injection parameters,
+indicated by the black dashed lines.  \abhi{We also note that at the
+  SNRs we consider, since statistical uncertainties dominate
+  systematic biases, the measurement excludes, at the 90\% credible
+  level, the GR prediction \ab{of} the frequency ($\df{220}=0$), but
+  includes the prediction \ab{of} the damping time
+  ($\dtau{220}=0$). However, with louder events, one would expect
+  these measurement errors to shrink and the $\taungr{220}$
+  measurement to be inconsistent with the GR prediction, as well.}
 
@@
 properties without biasing measurements of inspiral quantities, like masses and spins.
-\abhi{For the samples of the final mass and spin in the last row, we start from the samples
-of the complex QNM frequencies $(\fngr{220}, \taungr{220})$ that are obtained from the 
+\ab{To compute the samples of the final mass and spin in the last row, we start from the samples
+of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
 fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
-$(\fgr{220},\taugr{220})$ using Eqs.~\ref{eq:nongr_freqs_a} and ~\ref{eq:nongr_freqs_b},
-and then invert them $(\fngr{220}, \taungr{220})$ using the fitting formula in~\cite{Berti:2005ys}.
+$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b})},
+\abhi{and then invert them \sout{$(\fngr{220}, \taungr{220})$} using the fitting formula in Ref.~\cite{Berti:2005ys}.
 The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to

### 2021-04-01 papers/intro_paper/intro_paper.tex
removed colour from responses; cleaned remaining comments from tex

@@
-%\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers,nofootinbib]{revtex4-1}
 \documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
@@
 \newcommand{\paperone}{Paper~I\xspace}
-\newcommand{\abhi}[1]{\textcolor{Emerald}{#1}}
-\newcommand{\rb}[1]{\textcolor{blue}{#1}}
-\newcommand{\ab}[1]{\textcolor{cyan}{#1}}
-\newcommand{\comment}[1]{\textcolor{red}{[#1]}}
-\newcommand{\macro}[1]{\textcolor{orange}{\textbf{#1}}}
 
@@
 
-%\title{Black hole spectroscopy using a complete gravitational wave signal from a binary black coalescence}
-
 \title{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}
-%by making full use of gravitational-wave modeling}
 
@@
 The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
-theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, \rb{the consistency of the merger frequency with predictions from NR simulations~\cite{Carullo:2018gah}} or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
+theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, the consistency of the merger frequency with predictions from NR simulations~\cite{Carullo:2018gah} or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
 None of these tests have found evidence for non-BH nature of the remnant
@@
 Ground-based detectors, such as LIGO and Virgo, are most sensitive to
-stellar-mass BH binaries \rb{that form remnants with mass $\gtrsim 50 M_{\odot}$ and} merge near the
+stellar-mass BH binaries that form remnants with mass $\gtrsim 50 M_{\odot}$ and merge near the
 minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the
@@
 post-merger signal.
-Most of the tests mentioned above restrict the data to this post-merger signal \rb{which, while being agnostic to deviations in the pre-merger dynamics, significantly} reduces parameter-estimation capabilities.
+Most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities.
 Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
@@
 SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, \rb{can result in significant statistical uncertainties in the measurement of some of the QNM properties.
-This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data}.
+ground-based detectors, can result in significant statistical uncertainties in the measurement of some of the QNM properties.
+This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data.
 Hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
@@
 frequencies.
-\ab{In the current version, this method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies.
+In the current version, this method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies.
 This allows to access the full SNR of the signal, reducing
@@
 LIGOScientific:2019fpa,Abbott:2020jks}, and can in principle incorporate deviations from GR, notably from the parameters calibrated to NR simulations,  
-in the late inspiral and plunge.} Moreover, in this method, the definition of the
+in the late inspiral and plunge. Moreover, in this method, the definition of the
 ringdown start time is built into the merger-ringdown model and does not need to be
@@
 consistent with the corresponding values of the injection parameters,
-indicated by the black dashed lines.  \abhi{We also note that at the
+indicated by the black dashed lines.  We also note that at the
   SNRs we consider, since statistical uncertainties dominate
   systematic biases, the measurement excludes, at the 90\% credible
-  level, the GR prediction \ab{of} the frequency ($\df{220}=0$), but
-  includes the prediction \ab{of} the damping time
+  level, the GR prediction of the frequency ($\df{220}=0$), but
+  includes the prediction of the damping time
   ($\dtau{220}=0$). However, with louder events, one would expect
   these measurement errors to shrink and the $\taungr{220}$
-  measurement to be inconsistent with the GR prediction, as well.}
+  measurement to be inconsistent with the GR prediction, as well.
 
@@
          \caption{Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) \abhi{(fourth row)} from the frequency and damping time.
+The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) (fourth row) from the frequency and damping time.
 In each case, the injection values are indicated by the black dashed lines.
@@
 GW150914-like (top) and GW190521-like (bottom) signals
-respectively. For both signals, we find the \abhi{2D} $\SEOB$ estimates are
+respectively. For both signals, we find the 2D $\SEOB$ estimates are
 markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
@@
 properties without biasing measurements of inspiral quantities, like masses and spins.
-\ab{To compute the samples of the final mass and spin in the last row, we start from the samples
+To compute the samples of the final mass and spin in the last row, we start from the samples
 of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
 fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
-$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b})},
-\abhi{and then invert them \sout{$(\fngr{220}, \taungr{220})$} using the fitting formula in Ref.~\cite{Berti:2005ys}.
+$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b}),
+and then invert them using the fitting formula in Ref.~\cite{Berti:2005ys}.
 The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
@@
 leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
-analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$. }
+analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$.
 
@@
 The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
-\abhi{The authors are grateful for computational resources provided by the LIGO Laboratory and supported by the National Science Foundation Grants PHY-0757058 and PHY-0823459, as well as computational resources at the AEI, specifically the Hypatia cluster.} R.B.
+The authors are grateful for computational resources provided by the LIGO Laboratory and supported by the National Science Foundation Grants PHY-0757058 and PHY-0823459, as well as computational resources at the AEI, specifically the Hypatia cluster.
+R.B.
 acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
@@
 
-We choose a \abhi{spinning}, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
+We choose a spinning, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
 called \texttt{NRSur7dq4} in LAL.} (valid up to mass ratio 4) to simulate the actual GW190521 signal

### 2021-05-03 papers/intro_paper/intro_paper.tex
small changes

@@
 three distinct phases: an early \textit{inspiral}~\cite{Blanchet:2013haa}, where the two
-compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger}~\cite{Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv} marked by the
+compact objects spiral in losing energy because of the emission of GWs, a \textit{merger}~\cite{Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv} marked by the
 formation of a common apparent horizon, and a \textit{ringdown}~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs) (i.e., damped oscillations with specific, discrete frequencies and decay times).
@@
 from BBHs in GR. We employ coloured Gaussian noise with PSDs for LIGO and
-Virgo detectors during the fourth observing (O4) run (i.e., at design sensitivity), which 
+Virgo detectors during the fourth observing (O4) run~\cite{Abbott:2020qfu}, which 
 is expected to start in the second half of 2022~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
@@
 on the dominant QNM $(\df{220}=0.02^{+0.04}_{-0.04}, \dtau{220}=0.10^{+0.14}_{-0.14})$. Those 
-constraints are compatible, but sligthly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 
+constraints are compatible, but slightly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 
 (see first row in Table II therein), where QNM frequencies were inferred using only the post-merger part of 

### 2021-05-06 papers/intro_paper/intro_paper.tex
minor changes

@@
 %
-where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics.
+where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics \textcolor{blue}{where $(\ell,m)$ are the usual indices that describe the angular dependence of the spin-weighted spherical harmonics, with $\ell\geq 2$, $-\ell\leq m\leq \ell$}.
 The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
@@
 %
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH.
+where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH, \textcolor{blue}{i.e.
+QNMs with overtone index $n=0$}.
 We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.

### 2021-05-06 papers/intro_paper/intro_paper.tex
shuffle intro

@@
 
+\textcolor{blue}{The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
+One
+consequence of the no-hair conjecture is that the (complex) QNM
+frequencies of gravitational radiation emitted by a perturbed isolated
+BH are uniquely determined by its mass and spin. Hence
+a test of the no-hair conjecture would involve checking for
+consistency between estimates of mass and spin of the remnant object
+across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}.  Consistency of the late-time waveform with a single QNM is a test of the ringdown of
+a BBH coalescence, but not necessarily a test of the no-hair
+conjecture, which requires the measurement of (at least) two QNMs (BH
+spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Gossan:2011ha, Meidam:2014jpa,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
+An inconsistency would either
+indicate a non-BH nature of the remnant object, or an incompleteness
+of GR as the underlying theory of gravity.}
+
 The LIGO-Virgo collaborations have released companion papers detailing their results
@@
 The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
-The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
-One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}. An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.
-
 The consistency between the post-merger signal and the least damped QNM was first demonstrated in
@@
 This was later extended to include
-overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Abbott:2020jks}. Consistency of the late-time waveform with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Gossan:2011ha, Meidam:2014jpa,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
-The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
+overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Abbott:2020jks}.  The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
 theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, the consistency of the merger frequency with predictions from NR simulations~\cite{Carullo:2018gah} or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.

### 2021-05-07 papers/intro_paper/intro_paper.tex
added comments for Section III

@@
 properties without biasing measurements of inspiral quantities, like masses and spins. 
+\textcolor{blue}{As we increase the deviation, the remnant object rings down at a higher frequency and damping time.
+The resulting $\pSEOB$ signal is longer than the GR ($\SEOB$) prediction.
+When we try to fit the $\SEOB$ model to this signal (left column of Fig.~\ref{fig:gr_ngr_comparison}), the template tries to fit parameters appropriate for a longer signal, i.e., smaller masses and spins.
+Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.}
 To compute the samples of the final mass and spin in the last row, we start from the samples

### 2021-05-07 papers/intro_paper/intro_paper.tex
added comments for Section III

@@
 degeneracy between the binary's total mass and the non-GR deviations
-$(\df{220}, \dtau{220})$. Such strong degeneracy is present for
+$(\df{220}, \dtau{220})$.
+Such strong degeneracy \textcolor{blue}{(which arises from the fact that the frequency and damping time inverse are proportional to the total mass such that one can always obtain the same frequency or damping time by appropriately increasing the total mass and the deviation parameters in the same direction)} is present for
 low-SNR events with negligible higher-modes and for which only the

### 2021-05-07 papers/intro_paper/intro_paper.tex
added flow

@@
 Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
+\textcolor{blue}{Namely, for all events and injections we consider, we set ${f_\mathrm{low}}=20$ Hz, except for the GW190521-like injection and the real GW190521 event for which use ${f_\mathrm{low}}=11$ Hz~\cite{Abbott:2020tfl,Abbott:2020mjq}.} Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
 For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc,Speagle_2020} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.

### 2021-05-10 papers/intro_paper/intro_paper.tex
added sentence about ringdown starting time

@@
 Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
-In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a
-free parameter to be estimated directly from the data.
+\textcolor{blue}{Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to apply perturbation theory in a regime where non-linearities are still important}.
+In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a free parameter to be estimated directly from the data.
 Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{pyRing} analysis in Ref.~\cite{Abbott:2020jks}).
@@
 $(\df{220}, \dtau{220})$.
-Such strong degeneracy \textcolor{blue}{(which arises from the fact that the frequency and damping time inverse are proportional to the total mass such that one can always obtain the same frequency or damping time by appropriately increasing the total mass and the deviation parameters in the same direction)} is present for
+Such strong degeneracy \textcolor{blue}{, which arises from the fact that the frequency and damping time inverse are inversely proportional to the total mass~\cite{Berti:2005ys} such that one can always obtain the same frequency or damping time by appropriately increasing (or decreasing) the total mass and the deviation parameters in the same direction,} is present for
 low-SNR events with negligible higher-modes and for which only the

### 2021-05-10 papers/intro_paper/intro_paper.tex
changes

@@
 
-Ground-based detectors, such as LIGO and Virgo, are most sensitive to
-stellar-mass BH binaries that form remnants with mass $\gtrsim 50 M_{\odot}$ and merge near the
-minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the
-remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
-very little signal-to-noise ratio (SNR) in the
-post-merger signal.
-Most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities.
+%Ground-based detectors, such as LIGO and Virgo, are most sensitive to stellar-mass BH binaries that form remnants with mass $\gtrsim 50 M_{\odot}$ and merge near the minimum of their sensitivity band ($\sim 100$ Hz).
+As a consequence, the remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
+\textcolor{blue}{With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}.
+This is likely to remain the case in the near future~\cite{Berti:2016lat}.}
+%
+\textcolor{blue}{This is particularly important, given that} most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities.
 Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).

### 2021-05-11 papers/intro_paper/intro_paper.tex
minor

@@
 leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
-analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$.
+analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$).
 

### 2021-05-24 papers/intro_paper/intro_paper.tex
edits following Alessandra's comments

@@
 As a consequence, the remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
-\textcolor{blue}{With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}.
-This is likely to remain the case in the near future~\cite{Berti:2016lat}.}
+\textcolor{blue}{With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}.}
 %
@@
 Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
-\textcolor{blue}{Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to apply perturbation theory in a regime where non-linearities are still important}.
+\textcolor{blue}{Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to extract the fundamental QNMs too early after merger, since the higher-order overtones dominate the ringdown signal closer to merger~\cite{Buonanno:2006ui,Giesler:2019uxc}}.
 In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a free parameter to be estimated directly from the data.
@@
 The solid purple curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
+The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves (\textcolor{blue}{only shown in the 1D posteriors plots}).
 \emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
@@
 $(\df{220}, \dtau{220})$.
-Such strong degeneracy \textcolor{blue}{, which arises from the fact that the frequency and damping time inverse are inversely proportional to the total mass~\cite{Berti:2005ys} such that one can always obtain the same frequency or damping time by appropriately increasing (or decreasing) the total mass and the deviation parameters in the same direction,} is present for
+Such strong degeneracy \textcolor{blue}{arises from the fact that the complex QNM frequencies are inversely proportional to the total mass~\cite{Berti:2005ys} such that one can always obtain the same fundamental frequency or damping time by appropriately increasing (or decreasing) the total mass and the deviation parameters in the same direction.
+This degeneracy is especially important} in
 low-SNR events with negligible higher-modes and for which only the
-post-merger is detectable rendering the measurement of $(\df{220},
+post-merger is detectable, rendering the measurement of $(\df{220},
 \dtau{220})$ impossible for those cases  (see Appendix~\ref{sec:correlation} for more details). On the other hand the
@@
 In practice, we use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $ and compute $P(\xi_{\text{nGR}} | \{d_j\})$.
-
-The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained with this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
+\textcolor{blue}{We note that the current implementation of this analysis, as originally defined in~\cite{Isi:2019asy}, is only defined for 1D posteriors, therefore below we only show 1D posteriors for the hierarchical analysis.}
+
+The posteriors for $\df{220}$ and $ \dtau{220}$ obtained with this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
 %

### 2021-06-16 papers/intro_paper/intro_paper.tex
removed colored comments for arxiv update

@@
 
-\textcolor{blue}{The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
+The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
 One
@@
 indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.}
+of GR as the underlying theory of gravity.
 
@@
 As a consequence, the remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
-\textcolor{blue}{With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}.}
-%
-\textcolor{blue}{This is particularly important, given that} most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities.
+With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}.
+%
+This is particularly important, given that most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities.
 Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
-\textcolor{blue}{Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to extract the fundamental QNMs too early after merger, since the higher-order overtones dominate the ringdown signal closer to merger~\cite{Buonanno:2006ui,Giesler:2019uxc}}.
+Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to extract the fundamental QNMs too early after merger, since the higher-order overtones dominate the ringdown signal closer to merger~\cite{Buonanno:2006ui,Giesler:2019uxc}.
 In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a free parameter to be estimated directly from the data.
@@
 %
-where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics \textcolor{blue}{where $(\ell,m)$ are the usual indices that describe the angular dependence of the spin-weighted spherical harmonics, with $\ell\geq 2$, $-\ell\leq m\leq \ell$}.
+where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics where $(\ell,m)$ are the usual indices that describe the angular dependence of the spin-weighted spherical harmonics, with $\ell\geq 2$, $-\ell\leq m\leq \ell$.
 The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
@@
 %
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH, \textcolor{blue}{i.e.
-QNMs with overtone index $n=0$}.
+where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH, i.e.
+QNMs with overtone index $n=0$.
 We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
@@
 Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
-\textcolor{blue}{Namely, for all events and injections we consider, we set ${f_\mathrm{low}}=20$ Hz, except for the GW190521-like injection and the real GW190521 event for which use ${f_\mathrm{low}}=11$ Hz~\cite{Abbott:2020tfl,Abbott:2020mjq}.} Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
+Namely, for all events and injections we consider, we set ${f_\mathrm{low}}=20$ Hz, except for the GW190521-like injection and the real GW190521 event for which use ${f_\mathrm{low}}=11$ Hz~\cite{Abbott:2020tfl,Abbott:2020mjq}.
+Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
 For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc,Speagle_2020} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
@@
 properties without biasing measurements of inspiral quantities, like masses and spins. 
-\textcolor{blue}{As we increase the deviation, the remnant object rings down at a higher frequency and damping time.
+As we increase the deviation, the remnant object rings down at a higher frequency and damping time.
 The resulting $\pSEOB$ signal is longer than the GR ($\SEOB$) prediction.
 When we try to fit the $\SEOB$ model to this signal (left column of Fig.~\ref{fig:gr_ngr_comparison}), the template tries to fit parameters appropriate for a longer signal, i.e., smaller masses and spins.
-Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.}
+Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.
 To compute the samples of the final mass and spin in the last row, we start from the samples
@@
 The solid purple curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves (\textcolor{blue}{only shown in the 1D posteriors plots}).
+The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves only shown in the 1D posteriors plots).
 \emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
@@
 $(\df{220}, \dtau{220})$.
-Such strong degeneracy \textcolor{blue}{arises from the fact that the complex QNM frequencies are inversely proportional to the total mass~\cite{Berti:2005ys} such that one can always obtain the same fundamental frequency or damping time by appropriately increasing (or decreasing) the total mass and the deviation parameters in the same direction.
-This degeneracy is especially important} in
+Such strong degeneracy arises from the fact that the complex QNM frequencies are inversely proportional to the total mass~\cite{Berti:2005ys} such that one can always obtain the same fundamental frequency or damping time by appropriately increasing (or decreasing) the total mass and the deviation parameters in the same direction.
+This degeneracy is especially important in
 low-SNR events with negligible higher-modes and for which only the
@@
 In practice, we use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $ and compute $P(\xi_{\text{nGR}} | \{d_j\})$.
-\textcolor{blue}{We note that the current implementation of this analysis, as originally defined in~\cite{Isi:2019asy}, is only defined for 1D posteriors, therefore below we only show 1D posteriors for the hierarchical analysis.}
+We note that the current implementation of this analysis, as originally defined in~\cite{Isi:2019asy}, is only defined for 1D posteriors, therefore below we only show 1D posteriors for the hierarchical analysis.
 

### 2021-07-21 notes/hector_qnms/qnms.tex
HS: added my qnm notes

\documentclass[aps,10pt,preprint,
               notitlepage,onecolumn,superscriptaddress,
               eqsecnum,
               nofootinbib,tightenlines,floatfix]{revtex4-1}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{anyfontsize}
\usepackage{mathtools}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[linktocpage,breaklinks]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}

% Comment this out if want to use times font
% \usepackage{txfonts}
\usepackage{tensor}
\usepackage{bm}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{epstopdf}

\usepackage{natbib}

\hypersetup{colorlinks=true,
            citecolor=NavyBlue,
            linkcolor=NavyBlue,
            urlcolor=NavyBlue}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Add collaborators here
\newcommand{\hs}[1]{{\color{magenta}[HS: #1]}}

\newcommand{\dd}{{\rm d}}
\newcommand{\ii}{{\rm i}}
\newcommand{\xp}{x^{\prime}}
\newcommand{\rp}{r^{\prime}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\lt}{\left}
\newcommand{\rt}{\right}
\newcommand{\pd}{\partial}
\newcommand{\df}{\coloneqq}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{Some notes on quasinormal mode tests}

\begin{abstract}
Terse.
\end{abstract}

\author{Hector O. Silva}
\email{hector.silva@aei.mpg.de}
\affiliation{Max Planck Institute for Gravitational Physics,
(Albert Einstein Institute), Am M\"uhlenberg 1, 14476 Potsdam, Germany}

\date{{\today}}

\maketitle

\tableofcontents

\section{Introduction}

Here is a collection of thoughts on QNMs tests.
%
We follow the notations used in~\cite{Ghosh:2021mrv}.

\section{Test of the Kerr metric}

\subsection{Basic idea}

The idea here is to use the post-Kerr formalism~\cite{Glampedakis:2017dvb} as a null test of
the Kerr nature of the remnant BH.
%
Let us start by reviewing what was proposed there.

According to the geometrical optics (eikonal limit)-null geodesic
correspondence, the fundamental quasinormal mode frequencies are
(see~e.g.~\cite{Ferrari:1984zz,Cardoso:2008bp}) related to the orbital frequency and Lyapunov
exponent of a null particle (or a bundle of them for the later) at the black
hole's light ring.

The idea of the post-Kerr test is to write the true Kerr quasinormal mode as
%
\begin{equation}
    \sigma_{\ell m 0}^{\rm Kerr} = \sigma_{\ell m 0}^{\rm eik.} + \beta_{\ell m 0}^{\rm off-set}\,,
    \label{eq:qnm_kerr_exact}
\end{equation}
%
where $\sigma_{\ell m 0}^{\rm eik.}$ is the result predicted by the eikonal
calculation and $\beta_{\ell m 0}^{\rm off-set}$ is a known
(\cite{Glampedakis:2017dvb}, Appendix A) off-set function that encapsulates the
mismatch between eikonal and exact quasinormal frequencies.

Next, suppose that from data we inferred a frequency $\sigma_{\ell m 0}^{\rm obs.}$
which we decompose as
%
\begin{equation}
    \sigma_{\ell m 0}^{\rm obs.} = \kappa_{\ell m 0} + \beta_{\ell m 0}^{\rm off-set}\,,
\end{equation}
%
where $\beta$ is the same off-set function appearing
in~\eqref{eq:qnm_kerr_exact} and $\kappa$ is an eikonal quasinormal frequency
whose value is determined in practice subtracting off $\beta$ from the inferred
$\sigma^{\rm obs.}$.

Then, if both the spacetime and the light ring are non-Kerr
we would expect that
%
\begin{equation}
    \sigma_{\ell m 0}^{\rm obs} - \sigma_{\ell m 0}^{\rm Kerr} = \kappa_{\ell m 0} - \sigma^{\rm eik.}_{\ell m 0} \neq 0 \,.
    \label{eq:qnm_obs}
\end{equation}
%
If we assume that the `non-Kerrness' is small, we can write
%
\begin{equation}
    \delta \sigma_{\ell m 0} \equiv  \sigma_{\ell m 0}^{\rm obs} - \sigma_{\ell m 0}^{\rm Kerr}
\end{equation}
%
where the terms in the right-hand side differ, by construction, only through their eikonal contributions.
%
The good point about this `post-Kerr' approach is that $\kappa$ can be
calculated analytically given a perturbed Kerr black hole spacetime and we can
thus quantify the amount of non-Kerr of the remnant black hole.
%
Being more specific, we can quote how different is the light ring relative to Kerr.

Let us elaborate on this last point some more. In the eikonal limit we propose:
%
\begin{equation}
    {\rm Re}[\sigma] = m (\Omega_{\rm ph} + \epsilon \delta \Omega_0)
\end{equation}
%
where $\Omega_{\rm ph}$ is the known Kerr light ring orbital frequency
%
\begin{align}
    \Omega_{\rm ph} &= \pm \frac{M^{1/2}}{r_{\rm ph}^{3/2} \pm a M^{1/2}} \,,
    \\
    r_{\rm ph} &= 2M \left\{
    1 + \cos\left[ \frac{2}{3} \cos^{-1} \left( \mp \frac{a}{M} \right)\right]
    \right\}\,,
\end{align}
%
with $r_{\rm ph}$ being the equatorial light ring for prograde (upper sign) and
retrograde (lower sign) orbits. Also, $\delta \Omega_0$ is a small deviation
which can be expressed in terms of the perturbations to the $\varphi\varphi$,
$t\varphi$ and $tt$ components of the Kerr metric.
%
\hs{I thought that we could learn something about the black hole metric
following this route, but maybe this is not worth pursuing because:
%
(i) if we were able to obtain information on the $\delta g^{\rm Kerr}$
it would still be at a single point and it seems unclear how to generically reconstructed
the deformed metric (see however~\cite{Volkel:2020daa});
%
(ii) the expressions for the post-Kerr modifications depend on quite a few
metric components (three for the real part), meaning that to break the degeneracy of
them we would need quite a number of $\sigma_{\ell m 0}$.
%
Perhaps then, it is more instructive to try to constraint some coordinate independent
parameters.}
%

\subsection{An eikonal consistency check?}

There is something simpler that could be applied right away.
\hs{Not very sure about this. Discuss.}

Suppose that from out parameter estimation we are given an
%
$\sigma_{\ell m 0}^{\rm obs.}$.
%
Further assume that we have two of such modes detected (as one would require
for a no-hair test). Since we work in the eikonal limit we do cannot predict the
overtone (see~\cite{Dolan:2009nk} for an alternative approach however), so say we know the fundamental $n=0$
quasinormal modes of multipole $\ell = m = 2$.

Then, from the decomposition~\eqref{eq:qnm_obs} we can write:
%
\begin{subequations}
\begin{align}
    2 \pi f_{220} &= 2 \left( \Omega_{\rm ph} + \epsilon \delta \Omega_{0} \right) + {\rm  Re}[\beta^{\rm off-set}_{\ell m 0}]\,,
    \\
    \tau^{-1}_{220} &= (1/2) |\gamma_{\rm ph} + \epsilon \delta \gamma_{0}| + {\rm  Im}[\beta^{\rm off-set}_{\ell m 0}]\,.
\end{align}
\end{subequations}
%
These equations can be cast in the form used in~\cite{Ghosh:2021mrv}, where $\delta f_{220}$
and $\delta \tau_{220}$ now depend on $(\delta \Omega_0,\, \delta \gamma_0)$.
%
This allows us to translate the posterior distributions of~\cite{Ghosh:2021mrv} into posteriors of more
physical observables.
%
\hs{TODO: can this be translated onto shadow properties~\cite{Yang:2021zqy}?}

Another possibility is to simply test within GR the validity of the geometrical optics / null
geodesic correspondence. The idea is as follows. First write:
%
\begin{equation}
    \sigma_{\ell m 0} = 2 \pi f_{\ell m 0} + \ii / \tau_{\ell m 0}\,.
\end{equation}
%
where in GR,
%
\begin{subequations}
\begin{align}
    2 \pi f_{\ell m 0} &= m \Omega_{\rm ph} + {\rm  Re}[\beta^{\rm off-set}_{\ell m 0}]\,,
    \\
    \tau^{-1}_{\ell m 0} &= (1/2) |\gamma_{\rm ph}|+ {\rm  Im}[\beta^{\rm off-set}_{\ell m 0}]\,,
\label{eq:re_im_eikonal}
\end{align}
\end{subequations}
%
where $\beta^{\rm off-set}_{\ell m 0} = \beta^{\rm off-set}_{\ell m 0}(M_f, \chi_f)$ are known for $\ell = m $.
%
We can then promote ($\Omega_{\rm ph}$, $\gamma_{\rm ph}$) to free parameters in the
doing parameter estimation together with $M_f(m_1, m_2, \chi_1, \chi_2)$ and $\chi_f(m_1, m_2, \chi_1, \chi_2)$.
%
\emph{If the geometrical optics / null geodesic picture is correct}:
%
\begin{itemize}
    \item from a single QNM detection we would expect that the $(\Omega_{\rm ph}, \gamma_{\rm ph})$ joint posterior contour will be consistent
    with the joint posterior obtained by transforming $(M_f, \chi_f) \mapsto (\Omega_{\rm ph}, \gamma_{\rm ph})$.
    \item from two QNM detections we would expect that the posteriors of $\gamma_{\rm ph}$ (since
    the eikonal formula is independent on $\ell$ and $m$) and of $\Omega_{\rm ph} / m$ would be consistent. (There would be three posteriors: two from each mode
    and a third from $(M_f, \chi_f) \mapsto (\Omega_{\rm ph}, \gamma_{\rm ph})$).
\end{itemize}

In practice, this is not different from the usual no-hair test, but it allows us to test a \emph{physical image
on how we interpret the QNMs}.

\subsection{Assumptions and caveats}
%
There are two caveats that we need to keep in mind:
%
\begin{itemize}
\item We assume that the off-set function $\beta$ is the same in the Kerr and
non-Kerr spacetimes. This may not be the case in general and therefore any
bound on the deviation parameters would at best \emph{be conservative} (one can
imagine that knowing exactly $\beta$ for a given theory would only strengthen
the constraints;
%
\item The quasinormal mode formulas of~\cite{Glampedakis:2017dvb} does not
capture coupling between gravitational and extra degrees of freedom which
are ubiquitous in beyond-GR theories.
%
However, one can imagine that if a beyond-GR theory is perturbatively away from
GR there is a regime where the equation almost decouple the results are a
good first approximation to be used in absence of exact quasinormal mode
frequencies calculations.
\end{itemize}

\section{Theory-specific calculations}

Here we summarize some classes of theories for which quasinormal modes
of black holes have been computed in the past. We use the acronyms NR (nonrotating),
SR (slowly-rotating) and RR (rapidly-rotating).

\begin{itemize}
    \item Einstein-dilaton-Gauss-Bonnet -- (NR)~\cite{Blazquez-Salcedo:2016enn},
        (SR)~\cite{Pierini:2021jxd}.~\hs{Having results at both NR and SR approximations
        could be useful to assess {\sc parSpec} truncated at different spin-orders};
    \item dynamical Chern-Simons -- (NR)~\cite{Molina:2010fb}, (SR)~\cite{Wagle:2021tam,Srivastava:2021imr};
    \item Einstein-Maxwell-dilaton -- (NR)~\cite{Ferrari:1984zz}, (SR)~\cite{Brito:2018hjh};
\end{itemize}

\section{Effective hydrodynamical properties of exotic matter}

In~\cite{Yunes:2016jcc}, a few order-of-magnitude estimates were places on the effective
viscosity of an `exotic matter alternative to BH' was placed.
%
The starting point is a Newtonian, quasi-incompressible star with a density $\rho$,
radius $R$ and which perturbed by a spherical harmonic mode $Y_{\ell m}$.
%
From~\cite{Cutler:1987ApJ314}, the shear $\bar{\eta}$ and bulk $\bar{\zeta}$ viscosities of the oscillations are related to their
respective damping times as $\tau_{\bar{\eta}}$ and $\tau_{\bar{\zeta}}$ as
%
\begin{align}
    \bar{\eta}  &= \frac{1}{(\ell - 1) (2\ell + 1)} \frac{\rho R^2}{\tau_{\bar{\eta}}}\,,
    \\
    \bar{\zeta} &= \left(\frac{5}{4}\right)^{4} \frac{2 (2\ell +3)}{\ell^3} \frac{\rho R^2}{\tau_{\bar{\zeta}}}\,.
\end{align}
%

Given these expressions, Ref.~\cite{Yunes:2016jcc} focuses of $\ell = 2$ and eliminates the density by using
$\rho = m / [(4 \pi / 3) R^3]$, to obtain
%
\begin{align}
    \bar{\eta}_{\rm eff} &\sim 4 \cdot 10^{28} \frac{{\rm g}}{{\rm cm} \cdot {\rm s}}
    \left( \frac{m}{65 M_{\odot}} \right)
    \left( \frac{370 \, {\rm km}}{R} \right)
    \left( \frac{4 \, {\rm ms}}{\tau_{\bar{\eta}}} \right)
    \\
    \bar{\zeta}_{\rm eff} &\sim 3 \cdot 10^{30} \frac{{\rm g}}{{\rm cm} \cdot {\rm s}}
    \left( \frac{m}{65 M_{\odot}} \right)
    \left( \frac{370 \, {\rm km}}{R} \right)
    \left( \frac{4 \, {\rm ms}}{\tau_{\bar{\eta}}} \right)
\end{align}
%
where the expressions where rescalled by a fiducial damping times of $\tau = 4 ms$~\hs{Now we have posteriors on
this can could be used.}, a total mass of $m = 65~M_{\odot}$ and a radius of $R = 370~{\rm km}$ (corresponding to
the orbital separation at the end of the inspiral~\hs{Determined how?}).
%
These orders of magnitude are comparable with those of black holes (in the context of the membrane paradigm), but
larger than other compact objects such as boson stars and neutron stars. See~\cite{Yunes:2016jcc}, Table V.

\section{Others}

\subsection{Overtones}
%
Can we include overtones to the pSEOBNR~\cite{Brito:2018rfr,Ghosh:2021mrv}?

% \subsection{Isospectrality}
% %
% A firm prediction of GR is that the quasinormal modes

\subsection{QNMs and multipole moments}
%
The Refs.~\cite{Krishnendu:2017shb,Krishnendu:2019tjp} binary black hole
inspirals were used to constraint the spin-induced quadrupole moment by
parametrizing it is as $M_2 = - (1 + \delta q) \chi^2 M^3 \equiv \kappa \chi^2 M^3$ (where we follow the
notation of~\cite{Glampedakis:2017cgd}).
%
In~\cite{Glampedakis:2017cgd} the quasinormal mode in the eikonal limit were computed
for a generic ultracompact objects (such that it has a light ring).
%
The final formulas for $\sigma_{220}$ depend on two deformation parameters:
$\delta q$ (which null for Kerr) and a spin-octupole $\delta s_{3}$.
%
It seems possible to extend~\cite{Krishnendu:2017shb,Krishnendu:2019tjp}
into a `inspiral-ringdown' consistency check now that $\delta q$ can be inferred
both from the ringdown and from the inspiral. The spin-octupole would be something new.

\subsection{Final spin and mass fits}
%
In obtaining the modes in~\cite{Ghosh:2021mrv}, we final mass $M_f$ and spin
$\chi_f$ are obtained by a fit to the numerical relativity (NR) simulations, in
particular, from~\cite{Taracchini:2013rva,Hofmann:2016yih}.
%
These papers are about five years old. Can we update these fits and/or use
larger NR catalogs?
%
\hs{These references seem to have a done a very comprehensive work so the
gain-by-effort ratio is probably small. Opinions?}

Some works have followed Ref.~\cite{Buonanno:2007sv} to estimate the remnant black hole spin
in both theory specific~\cite{Jai-akson:2017ldo} and generic set-ups.
%
Since $\chi_f$ in~\cite{Ghosh:2021mrv} is predicted using fits obtained in GR
could we modify them a bit and perhaps related $\delta f$, $\delta \tau$ with
some non-GR parameter $x$ building upon~\cite{Buonanno:2007sv}?
%
Imagining that $\chi_f$ could change dramatically due to $x$;
could we use stack the posteriors on $\chi_f$ of all binary-black-hole events so far
to constraint $x$?

\section{A full parametrized inspiral-merger-ringdown template}

The waveform model used in~\cite{Brito:2018rfr,Ghosh:2021mrv} assumes that
only the merger-ringdown phase for the coalescence has significant GR deviations.
%
On the other hand, we know that the most of the waveform's SNR is contained in the
inspiral.
%
Could include changes to the inspiral as well?

It could be useful to remember that late-inspiral-ringdown waveforms which emulate
GW150914 (examined in~\cite{Ghosh:2021mrv}) are publicly available for
Einstein-dilaton-Gauss-Bonnet and dynamical-Chern-Simons
theories~\cite{Okounkova:2019zjf,Okounkova:2020rqw}.

\bibliography{biblio}

\end{document}

### 2021-07-26 scripts/generate_waveforms.py
updated parspec notebook

@@ -37,8 +37,8 @@ def generate_waveform(domega220, dtau220, alphaNGR, pNGR):
 
 # Define binary parameters
 nqcCoeffsInput=lal.CreateREAL8Vector(10) ##This will be unused, but it is necessary
-m1 = 50.0*lal.MSUN_SI
-m2 = 50.0*lal.MSUN_SI
+m1 = 35.0*lal.MSUN_SI
+m2 = 35.0*lal.MSUN_SI
 phi_c = 0.
 f_start22 = 20. #Frequency of the 22 mode at which the signal starts
 distance = 500e6*lal.PC_SI
@@ -52,6 +52,10 @@ domega440, dtau440 = 0., 0.
 domega550, dtau550 = 0., 0.
 
 pNGR = 2.
+alphaNGR = 100.
+
+z = distance * 70000.0 / 1.0e6 / lal.PC_SI / lal.C_SI
+gamma = (alphaNGR * lal.C_SI * lal.C_SI * (1. + z)/ lal.G_SI/ (m1+m2))**pNGR
 
 plt.figure()
 
@@ -63,13 +67,16 @@ plt.plot(t, hp, color='r')
 # plot data with no deviation
 t, hp, hc = generate_waveform(0, 0, 100, pNGR)
 plt.plot(t, hp, color='g', ls='dashdot')
+"""
+for idx in range(10000):
 
-for idx in range(100):
+	domega220 =  np.random.uniform(0.,1.)
+	dtau220 =  np.random.uniform(0.,1.)
 
-	domega220 =  np.random.rand()*20000. - 10000.
-	#print(domega220)
-	t, hp, hc = generate_waveform(domega220, 0, 1, pNGR)
+	t, hp, hc = generate_waveform(domega220, dtau220, 100, pNGR)
+	#t, hp, hc = generate_waveform(0.394314, -0.888588, 100, pNGR)
 	plt.plot(t, hp, alpha=0.1, color='k', lw=0.1)
 
 plt.xlim([0.32, 0.38])
-plt.savefig('../plots/parspec/pSEOB_parspec-no-dev_comparison_p2_df0.png')
+plt.savefig('../plots/parspec/pSEOB_parspec-no-dev_comparison_p2_df0_dtau0.png')
+"""

### 2021-08-31 notes/hector_qnms/qnms.tex
HS: upd theory specific list with EFTofGR
HS: added Einstein-Aether paper reference

@@
-\documentclass[aps,10pt,preprint,
+\documentclass[aps,prd,10pt,preprint,
                notitlepage,onecolumn,superscriptaddress,
                eqsecnum,
-               nofootinbib,tightenlines,floatfix]{revtex4-1}
+               nofootinbib,tightenlines,floatfix]{revtex4-2}
 
@@
         (SR)~\cite{Pierini:2021jxd}.~\hs{Having results at both NR and SR approximations
-        could be useful to assess {\sc parSpec} truncated at different spin-orders};
-    \item dynamical Chern-Simons -- (NR)~\cite{Molina:2010fb}, (SR)~\cite{Wagle:2021tam,Srivastava:2021imr};
-    \item Einstein-Maxwell-dilaton -- (NR)~\cite{Ferrari:1984zz}, (SR)~\cite{Brito:2018hjh};
+        could be useful to assess {\sc parSpec} truncated at different spin-orders}.
+    \item dynamical Chern-Simons -- (NR)~\cite{Molina:2010fb}, (SR)~\cite{Wagle:2021tam,Srivastava:2021imr}.
+    \item Einstein-Maxwell-dilaton -- (NR)~\cite{Ferrari:1984zz}, (SR)~\cite{Brito:2018hjh}.
+    \item EFTofGR -- (NR, cubic)~\cite{deRham:2020ejn} and (NR, quadratic)~\cite{Cardoso:2018ptl}.
+    \item Einstein-Aether -- (NR, odd/axial parity)~\cite{Tsujikawa:2021typ}. Analysis of quadratic Lagrangian only; no mode calculation.
 \end{itemize}

### 2021-11-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added a preliminary skeleton for follow-up paper

--- 2021-05-11 papers/intro_paper/intro_paper.tex
@@
 
-\title{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}
+\title{Super-awesome paper with super-cool results}
 
-\author{Abhirup Ghosh}
-\AEI
-\author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
-\author{Alessandra Buonanno}
-\AEI
-\UMD
+\author{TBD}
 
@@
 \begin{abstract}
-  The no-hair conjecture in General Relativity (GR) states that the
-  properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary--black-hole (BBH)
-  ringdown can be uniquely determined by the mass and spin of the
-  remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to
-  test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using parameterized inspiral-merger-ringdown waveforms in the effective-one-body formalism, 
-thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the ringdown. Our method was used to analyze the
-  properties of the merger remnants for BBHs observed by
-  LIGO-Virgo in the first half of their third observing (O3a) run.
- After testing our method with GR and non-GR synthetic-signal injections in Gaussian noise, 
-we analyze, for the first time, two BBHs from the first (O1) and second (O2) LIGO-Virgo 
-  observing runs, and two additional BBHs from the O3a run. We then provide joint constraints with published results
-  from the O3a run. In the most agnostic and conservative scenario where we combine the information from different
-events using a hierarchical approach, we obtain, at $90\%$ credibility, that 
-the fractional deviations in the frequency (damping time) of the dominant QNM are 
-$\df{220}=0.03^{+0.10}_{-0.09}$ ($\dtau{220}=0.10^{+0.44}_{-0.39}$), respectively, an improvement of a factor of $\sim 4$ ($\sim 2$) 
-over the results obtained with our model in the LIGO-Virgo publication. The single-event most-stringent constraint to date continues to be 
-GW150914 for which we obtain $\df{220}=0.05^{+0.11}_{-0.07}$ and $\dtau{220}=0.07^{+0.26}_{-0.23}$.
 \end{abstract}
@@
 \label{sec:intro}
-The LIGO Scientific Collaboration~\cite{lsc} and the Virgo
-Collaboration~\cite{Virgo} have recently announced their catalogue of
-gravitational-wave (GW) signals from the first
-half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
-with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\cite{TheLIGOScientific:2014jea},
-and the Advanced Virgo detector in Cascina,
-Italy~\cite{TheVirgo:2014hva} have now detected $50$ GW
-events from the merger of compact objects like neutron stars and/or
-black holes (BHs). Alongside independent claims of
-detections~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, GW150914~\cite{Abbott:2016blz}.
-
-The observation of GWs has had significant astrophysical and cosmological
-implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
-has also allowed us to probe fundamental
-physics and test predictions of Einstein's theory of General Relativity
-(GR) in the previously unexplored highly-dynamical, and strong field
-regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}~\cite{Blanchet:2013haa}, where the two
-compact objects spiral in losing energy because of the emission of GWs, a \textit{merger}~\cite{Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv} marked by the
-formation of a common apparent horizon, and a \textit{ringdown}~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs) (i.e., damped oscillations with specific, discrete frequencies and decay times).
-
-\textcolor{blue}{The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
-One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}.  Consistency of the late-time waveform with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Gossan:2011ha, Meidam:2014jpa,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
-An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.}
-
-The LIGO-Virgo collaborations have released companion papers detailing their results
-of tests of GR for GW150914 \cite{TheLIGOScientific:2016src}, and for several GW events of
-the two transient catalogues (TC): GWTC-1 \cite{LIGOScientific:2018mvr,LIGOScientific:2019fpa}  and GWTC-2 \cite{Abbott:2020niy,Abbott:2020jks}.
-The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral, and
-phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\cite{Arun:2006hn,Arun:2006yw,Agathos:2013upa,Abbott:2018lct}; tests of GW
-propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\cite{Abbott:2017vtc,Samajdar:2017mka}, and tests of the
-polarization of gravitational radiation using a
-multi--GW-detector network~\cite{Abbott:2017oio,Isi:2017fbj}. The GWTC-1/2 papers also
-check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
-consistency of the residuals with detector noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
-departure from the predictions of GR.
-
-The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} also provided us with the first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
-coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}.
-The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in
-Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analyses~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}.
-This was later extended to include
-overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Abbott:2020jks}.  The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
-theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, the consistency of the merger frequency with predictions from NR simulations~\cite{Carullo:2018gah} or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
-None of these tests have found evidence for non-BH nature of the remnant
-object (as described in GR) in LIGO-Virgo BBH observations.
-
-%Ground-based detectors, such as LIGO and Virgo, are most sensitive to stellar-mass BH binaries that form remnants with mass $\gtrsim 50 M_{\odot}$ and merge near the minimum of their sensitivity band ($\sim 100$ Hz).
-As a consequence, the remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
-\textcolor{blue}{With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}.
-This is likely to remain the case in the near future~\cite{Berti:2016lat}.}
-%
-\textcolor{blue}{This is particularly important, given that} most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities.
-Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
-\textcolor{blue}{Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to apply perturbation theory in a regime where non-linearities are still important}.
-In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a free parameter to be estimated directly from the data.
-Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{pyRing} analysis in Ref.~\cite{Abbott:2020jks}).
-Uncertainties
-in estimates of the ringdown start-time, as well as an overall lack of
-SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, can result in significant statistical uncertainties in the measurement of some of the QNM properties.
-This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data.
-Hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
-
-An independent approach to BH spectroscopy, based on the full-signal
-analysis, was introduced in Ref.~\cite{Brito:2018rfr}
-(henceforth referred to as \paperone). Unlike methods that focus only
-on the post-merger signal, it employs the
-complete inspiral-merger-ringdown
-(IMR) waveform to measure the complex QNM
-frequencies.
-In the current version, this method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies.
-This allows to access the full SNR of the signal, reducing
-measurement uncertainties. However, we note that this method can incorporate deviations from GR, notably from the (known) PN coefficients,  
-also during the long inspiral stage~\cite{Abbott:2018lct,
-LIGOScientific:2019fpa,Abbott:2020jks}, and can in principle incorporate deviations from GR, notably from the parameters calibrated to NR simulations,  
-in the late inspiral and plunge. Moreover, in this method, the definition of the
-ringdown start time is built into the merger-ringdown model and does not need to be
-either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method and tested it for non-spinning BBHs, here we extend the analysis to the more
-realistic astrophysical case in which BHs carry spin. Furthermore,
-the IMR waveform model used in this paper is more accurate than what employed in \paperone,
-because it contains higher-order corrections in PN theory and it was calibrated to a much larger set
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}. All astrophysical BHs are expected to be spinning,
-and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the
-source properties.
-
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
-complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
-several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
-we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
-the GWTC-2 events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.
-
 %%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the (source) masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
-objects in the binary; and the
-\emph{extrinsic} parameters: a reference time $t_c$ and phase
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total (source) mass $M = m_1+m_2$,
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$.
-We also introduce the detector masses $m_{1\,\rm det}= (1+z)\,m_1$ and $m_{2 \,\rm det} = (1+z)\,m_2$,
-where $z$ is the redshift.
-
-Here, we focus on BHs with spins aligned or anti-aligned
-with the orbital angular momentum (henceforth, aligned-spin). In this case,
-the GW signal depends on $11$ parameters. We denote the
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB)
-formalism~\cite{Buonanno:1998gg,Buonanno:2000ef}. However, whereas \paperone was limited to non-spinning multipolar waveforms,
-here we use as our baseline model the aligned-spin multipolar waveform model
-developed in Ref.~\cite{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this
-waveform model is called {\tt SEOBNRv4HM}.}.
-
-In the observer's frame, the GW polarizations can be written as
-%
-\begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
-\end{equation}
-%
-where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics \textcolor{blue}{where $(\ell,m)$ are the usual indices that describe the angular dependence of the spin-weighted spherical harmonics, with $\ell\geq 2$, $-\ell\leq m\leq \ell$}.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
-\begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
-\end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
-\begin{equation}
-\label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
-\end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH, \textcolor{blue}{i.e.
-QNMs with overtone index $n=0$}.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{subequations}
-\begin{eqnarray}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) &=& c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},\\
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) &=& \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{eqnarray}
-\end{subequations}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{subequations}
-\begin{align}
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber
-\end{align}
-\end{subequations}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
-
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) are defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values~\cite{Gossan:2011ha,Meidam:2014jpa}.
-
-Thus,
-\begin{subequations}
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-\end{subequations}
-
-The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
-\begin{subequations}
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,,\\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,.
-\end{eqnarray}
-\end{subequations}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
-(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 
-soon after merger deviates from the one predicted by GR.
-
-\subsection{Bayesian parameter-estimation technique}
+\section{Method}
 \label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes' theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the usual noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency.
-Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
-\textcolor{blue}{Namely, for all events and injections we consider, we set ${f_\mathrm{low}}=20$ Hz, except for the GW190521-like injection and the real GW190521 event for which use ${f_\mathrm{low}}=11$ Hz~\cite{Abbott:2020tfl,Abbott:2020mjq}.} Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc,Speagle_2020} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and fix all the other $(\ell m)$ modes to their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\section{Synthetic-signal injection study}
-\label{sec:results}
-\subsection{Simulations using GR signals in Gaussian noise} \label{ssec:gr_signal}
-
-We now demonstrate our method using synthetic-signal injections describing GWs
-from BBHs in GR. We employ coloured Gaussian noise with PSDs for LIGO and
-Virgo detectors during the fourth observing (O4) run~\cite{Abbott:2020qfu}, which 
-is expected to start in the second half of 2022~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
-GW190521~\cite{Abbott:2020tfl}. We list them in Table~\ref{tab:injection_values}.
-These two binary systems are representative of the kind of systems for which
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the
-pre- and post-merger SNRs return reliable parameter-estimation results.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ c|c|c|c|c|c|c|c|c }
-
-Injection &  Network & \makecell{$m_{\rm 1\,det}$ \\$(\Mo)$} &  \makecell{$m_{\rm 2\,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
- \hline
- GW150914-like & HL &39 & 31 & 0.0 & 0.0 & 25 & 22 & 12 \\
- GW190521-like & HL & 150 & 120 & 0.02 & -0.39 & 20 & 8 & 18 \\
- SXS:BBH:0166 & HLV &72 & 12  & 0.0 & 0.0 & 71 & 58 & 41 \\
-
-\end{tabular}
-\caption{Parameters of the synthetic-signal injections, chosen to be similar to the actual GW events indicated in the first column (first two rows).
-The parameters $(m_{\rm 1 \,det}, m_{\rm 2 \,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-The third row indicates the parameters of the SXS BBH waveform used in Sec.~\ref{ssec:nohairtheorem}.
-The second column refers to the detector-network used, with H,L,V, referring to LIGO-Hanford, LIGO-Livingston and Virgo, respectively.
-The quantities $\rho_\text{IMR}$, $\rho_\text{insp}$ and $\rho_\text{postinsp}$ are the SNR of the full IMR signal, SNR upto a certain cutoff frequency, and SNR after the cutoff frequency respectively.
-In each case, the cutoff frequency is assumed to be the frequency at the innermost circular stable orbit (ISCO) corresponding to the remnant Kerr BH.}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}
-        \caption{Posterior probability
-          distribution on the fractional deviations in the frequency
-          and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$
-          (left panels) and the reconstructed quantities,
-          $(\fngr{220}, \taungr{220})$ (right panels) for GR
-          injections ($\SEOB$) with initial parameters similar to GW150914 (top
-          panels) and GW190521 (bottom panels)
-          (see Table~\ref{tab:injection_values}). The 2D contour marks the
-          90\% credible region, while the dashed lines on the 1D
-          marginalized distributions mark the 90\% credible
-          levels. The black vertical and horizontal lines mark the
-          injection values.}
-        \label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To avoid possible systematic biases in our parameter-estimation analysis
-due to error in waveform modeling, we use the GR version of the same waveform,
-$\SEOB$ (i.e., without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise~\footnote{A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}.}.  Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of only one QNM $(\ell m) = (2,2)$ (i.e.,
-$\{\df{220},\dtau{220}\}$), while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~(\ref{eq:nongr_freqs_a}) and ~(\ref{eq:nongr_freqs_b}), and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-two-dimensional posteriors are consistent with the GR predictions
-(black dashed lines).
-
-\subsection{Simulations using non-GR signals in Gaussian noise} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations from GR, we inject synthetic GW signals which are identical
-to the corresponding GR prediction up to merger, and differ in their
-post-merger description. We again choose binary-parameters similar to
-GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but set
-$\df{220} = \dtau{220} = 0.1 $.  In other words, we assume that the
-frequency and damping time of our non-GR signal is 10\% more than the
-corresponding GR prediction, although the pre-merger signal is
-identical to GR. In Fig.~\ref{fig:nongr_waveform} we show this non-GR
-waveform, \texttt{pSEOBNR} with respect to the original GR template,
-\texttt{SEOBNR}. We see that the waveforms are identical in amplitude
-and instanteneous frequency upto the merger (lower panel) , beyond
-which the red (GR template) and blue (non-GR template) differ. We
-summarize the results of the Bayesian analysis in
-Fig.~\ref{fig:simulated_signal_nonGR} where we show the posterior
-probability distributions for $(\df{220}, \dtau{220})$, or
-equivalently $(\fngr{220}, \taungr{220})$. We find that they are
-consistent with the corresponding values of the injection parameters,
-indicated by the black dashed lines.  We also note that at the
-  SNRs we consider, since statistical uncertainties dominate
-  systematic biases, the measurement excludes, at the 90\% credible
-  level, the GR prediction of the frequency ($\df{220}=0$), but
-  includes the prediction of the damping time
-  ($\dtau{220}=0$). However, with louder events, one would expect
-  these measurement errors to shrink and the $\taungr{220}$
-  measurement to be inconsistent with the GR prediction, as well.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-        \caption{Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
-Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
-        \label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
-        \caption{Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections ($\pSEOB$) with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
-The non-GR signal has a deviation, $\df{220} = \dtau{220} = 0.1$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like (upper panel) and GW190521-like (lower panel) injections. The measurements with $\SEOB$ waveforms are visibly biased.}
-        \label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GW150914-like signal with different deviations: GR vs nonGR recovery
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_m1m2.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_a1za2z.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_fgrtaugr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
-         \caption{Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) (fourth row) from the frequency and damping time.
-In each case, the injection values are indicated by the black dashed lines.
-In the lowermost panel, the injection values of the final mass and spin, correspond to the injection with no deviations.
-The $\df{220} = \dtau{220} = 0.1$ signal is identical to the results shown in Fig.~\ref{fig:simulated_signal_nonGR}.}
-        \label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We additionally investigate the effects of erroneously assuming that
-an underlying non-GR signal can be well-described by a GR one. We do
-this by estimating the parameters of our non-GR signals using the GR
-waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
-resulting one- and two-dimensional posteriors are shown in the right
-panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
-GW150914-like (top) and GW190521-like (bottom) signals
-respectively. For both signals, we find the 2D $\SEOB$ estimates are
-markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
-this impact on the estimation of the GR parameters $\bxigr$ by changing the
-magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
-to a GW150914-like event, and for comparison, add a synthetic signal
-with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
-10\% non-GR signal and a signal with no deviation (essentially GR)
-mentioned above. The left (right) panels show the
-posterior probability distributions of the three signals using the GR,
-$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
-note is the $\SEOB$ recoveries yield biased estimates when the
-underlying signal is non-GR, while the $\pSEOB$ recoveries do
-not. Furthermore, as we increase the deviations, while the $\SEOB$
-recoveries expectedly get more biased, the $\pSEOB$ measurements are
-robust in consistently recovering the injected value. This gives us 
-confidence that the $\pSEOB$ model can accurately measure QNM 
-properties without biasing measurements of inspiral quantities, like masses and spins. 
-\textcolor{blue}{As we increase the deviation, the remnant object rings down at a higher frequency and damping time.
-The resulting $\pSEOB$ signal is longer than the GR ($\SEOB$) prediction.
-When we try to fit the $\SEOB$ model to this signal (left column of Fig.~\ref{fig:gr_ngr_comparison}), the template tries to fit parameters appropriate for a longer signal, i.e., smaller masses and spins.
-Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.}
-To compute the samples of the final mass and spin in the last row, we start from the samples
-of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
-fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
-$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b}),
-and then invert them using the fitting formula in Ref.~\cite{Berti:2005ys}.
-The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
-three unique sets of values for $(M_f,\chi_f)$. These predicted values are correctly 
-recovered by the $\pSEOB$ waveform (bottom-right plot in Fig.~\ref{fig:gr_ngr_comparison}),
-leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
-analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$).
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-Here, we use an NR GW signal from the SXS catalog~\cite{Mroue:2013xna}
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166) and 
-total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
-We choose an asymmetric system to increase the SNR in the higher modes.
-We also choose the distance and orientation of the binary
-such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
-Virgo, is {$\sim$ 70}. Based on the LIGO-Virgo observations during the first three observing runs, 
-such asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible during O4. Using this
-signal, we attempt to measure both the $(2,2)$ and
-$(3,3)$ QNMs. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.
-
-We summarize our results in Fig.~\ref{fig:nohair_sxs}.  Given the
-injection parameters, the predicted values of the $(2, 2)$ and
-$(3, 3)$ frequency and damping time are {(169.45 Hz, 4.68
-  ms)} and {(271.21 Hz, 4.50 ms)} respectively. The left panel
-of Fig.~\ref{fig:nohair_sxs} shows that the 2D posteriors
-on the $(2, 2)$ and $(3, 3)$ QNMs are consistent with the
-predictions for a BBH merger in GR, indicated by the black plus sign.
-Using fitting formulae provided in Ref.~\cite{Berti:2005ys}, specifically,
-Eq.~(2.1), Eq.~(E1) and Eq.~(E3) and Tables VIII and IX for the fitting coefficients,
-we infer the 2D posterior probability distribution on the
-final mass and spin as predicted independently by the $(2, 2)$ (blue) and $(3, 3)$ (red)
-QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
-independent estimates are consistent with each other and correspond to
-a unique mass and spin for the remnant BH {(83.08 $\Mo$, 0.37)}
-indicated by the plus sign. As a consequence, this may be considered
-as a test of the no-hair conjecture. For most of the events observed
-so far, the power in the $(3, 3)$ has not been sufficient to
-measure it along with the $(2, 2)$. However, it might also be possible to combine information from
-multiple observation over the coming few years to obtain meaningful
-constraints on the $(3, 3)$ and other sub-dominant QNMs~\cite{Gossan:2011ha,Meidam:2014jpa,Yang:2017zxs}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-        \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
-        \caption{Posterior probability distribution on the frequency and damping time of the $(2, 2)$ and $(3, 3)$ QNM (left panel), and the final mass and spin inferred from the complex frequencies (right panel), when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
-The plus signs mark the GR predictions.}
-        \label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\section{Constraints on QNM frequencies using LIGO-Virgo data}
-\label{sec:results_lvc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.3\textwidth]{figures/rin_all_events_bounds.pdf}
-        \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2, 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid purple curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves.
-\emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
-Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).
-The purple square marker indicates constraints from the single most-prominent event, GW150914.}
-        \label{fig:o1o2_events}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results for events observed
-during O3a~\cite{Abbott:2020jks}.
-For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median detector-frame total mass $\geq 90 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
-The SNR values are listed in Table IV of Ref.~\cite{Abbott:2020jks}}.
-%
-The SNR threshold ensures that the signal contains sufficient
-information in both the inspiral and merger stages to break the
-degeneracy between the binary's total mass and the non-GR deviations
-$(\df{220}, \dtau{220})$.
-Such strong degeneracy \textcolor{blue}{, which arises from the fact that the frequency and damping time inverse are inversely proportional to the total mass~\cite{Berti:2005ys} such that one can always obtain the same frequency or damping time by appropriately increasing (or decreasing) the total mass and the deviation parameters in the same direction,} is present for
-low-SNR events with negligible higher-modes and for which only the
-post-merger is detectable rendering the measurement of $(\df{220},
-\dtau{220})$ impossible for those cases (see Appendix~\ref{sec:correlation} for more details). On the other hand the
-total mass threshold $\geq 90 \Mo$ was employed due to the fact that
-this analysis is computationally expensive, and also because we
-expected these events to be the most promising for ringdown
-studies. However, since the SNR threshold alone should be sufficient
-for the analysis, for this paper we run the test on all the events
-listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and
-post-merger regions $\geq 8$, without imposing any mass threshold.
-
-Given the above we add the signals  GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in Ref.~\cite{Abbott:2020jks}. Furthermore, for the first time, 
-we apply our method to measure the QNMs to GW events from O1 and O2, notably GW150914 and GW170104. The other high-mass events from O1 and O2, GW170729, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
-merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}.
-
-For all the relevant signals, we show the posterior distributions
-$(\df{220}, \dtau{220})$ in the left panel of
-Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM
-parameters, $(\fngr{220}, \taungr{220})$ in
-Table~\ref{tab:qnm_o1o2_results}. In the right panel of
-Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%
-credible intervals on the 1D marginalized posteriors. We highlight the
-dependence of the constraints on the total mass of the
-system. In general, the tightest bounds are set by the 
-most massive systems, as they tend to have larger post-merger SNR. We
-find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.
-
-Among all the GW signals detected so far, GW150914 (solid curve in
-Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the
-first, and to date, best attempt in measuring the QNM
-frequencies~\cite{TheLIGOScientific:2016src,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}. Within
-90\% credibility we obtain from GW150914:
-%
-\begin{equation}\label{GW150914_delta}
-\df{220}=0.05^{+0.11}_{-0.07}\,\quad \dtau{220}=0.07^{+0.26}_{-0.23}\,.
-\end{equation}
-
-Stronger constraints can be obtained by combining information from all the events~\cite{Abbott:2020jks}.
-If we assume that the fractional deviations $(\df{220},\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}\,,
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since here we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding 1D marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
-From the joint likelihood we obtain within 90\% credibility:
-%
-\begin{equation}
-\df{220}=0.02^{+0.04}_{-0.04}\,,\quad \dtau{220}=0.10^{+0.14}_{-0.14}\,.
-\end{equation}
-%
-
-However, in most non-GR theories, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so if GR were to be wrong, one should expect their value to vary across the GW signals observed by LIGO and Virgo.
-As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a constant deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
-The general idea behind this technique is to assume that the non-GR parameters $(\df{220},\dtau{220})$ are drawn from a common underlying distribution, whose properties can be inferred from the population of events.
-Following~\cite{Zimmerman:2019wzo,Isi:2019asy,Abbott:2020jks} we model the population distribution with a Gaussian  $\mathcal{N}(\mu,\sigma)$ of unknown mean $\mu$ and standard deviation $\sigma$.
-Under those assumptions, the goal is then to directly measure a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for $\mu$ and $\sigma$ from a joint analysis of all the GW events.
-If GR is correct, then this posterior should be consistent with $\mu=0$ and $\sigma=0$.
-From Bayes' theorem it follows that~\cite{Isi:2019asy}:
-%
-\begin{equation}
-P(\mu, \sigma |  \{d_j\}) \propto P(\mu,\sigma)\prod _{j=1}^N P(d_j |\, \mu, \sigma) \,,
-\end{equation}
-%
-where $P(\mu,\sigma)$ is the prior (also known as hyperprior) on ($\mu,\sigma$), and $P(d_j | \mu, \sigma) $ can be written in terms of the individual likelihoods of a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}
-%
-\begin{equation}
-P(d_j | \mu, \sigma) = \int P(d_j |\, \xi_{\text{nGR}})  P(\xi_{\text{nGR}} |\, \mu, \sigma) \,d\xi_{\text{nGR}} \,.
-\end{equation}
-%
-Here $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$ by construction and $P(d_j |\, \xi_{\text{nGR}})$ is the likelihood for the parameter $\xi_{\text{nGR}}$ for a given event $d_j$ that is computed from the standard parameter estimation analysis.
-After obtaining $P(\mu, \sigma |  \{d_j\})$, we can then infer a population distribution for a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}:
-%
-\begin{equation}\label{hier_combine}
-P(\xi_{\text{nGR}} | \{d_j\}) = \int P(\xi_{\text{nGR}} |\, \mu, \sigma)\,P(\mu, \sigma |  \{d_j\})\,d\mu\,d\sigma \,.
-\end{equation}
-%
-Notice that, if we fix $\sigma=0$, this approach is equivalent to assume that all events share the same non-GR parameter $\xi_{\text{nGR}} =\mu$ and Eq.~\eqref{hier_combine} reduces to the joint likelihood~\cite{Zimmerman:2019wzo}.
-In practice, we use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $ and compute $P(\xi_{\text{nGR}} | \{d_j\})$.
-
-The 1D posteriors for $\df{220}$ and $ \dtau{220}$ obtained with this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
-%
-\begin{equation}
-\df{220}=0.03^{+0.10}_{-0.09}\,,\quad \dtau{220}=0.10^{+0.44}_{-0.39}\,.
-\end{equation}
-Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ more stringent for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$.
-Similar improvements hold for the hyperparameters: $\df{220}\,(\mu=0.03^{+0.06}_{-0.05},\,\sigma<0.09)$ and $\dtau{220}\,(\mu=0.11^{+0.21}_{-0.19},\,\sigma<0.39)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for LVC values
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}
-
-\begin{tabular}{l|c|c|c|c|c|c}
-\toprule
-Event & $\fngr{220}$ (Hz) & $\taungr{220}$ (ms) & $(1+z)M_f/\Mo$ & $\chi_f$ & $(1+z)M_{\text{f}}^{\rm IMR}/\Mo$ & $\chi_{\text{f}}^{\rm IMR}$ \\[0.075cm]
-\midrule
-\hline
-
-GW150914 &
-$257.6^{+17.0}_{-12.8}$ &
-$4.49^{+1.09}_{-0.95}$ &
-$71.0^{+8.7}_{-10.3}$ &
-$0.77^{+0.09}_{-0.18}$ &
-$67.3^{+2.7}_{-2.6}$ &
-$0.67^{+0.03}_{-0.04}$
-\\[0.075cm]
-
-GW170104 &
-$291.4^{+14.7}_{-30.1}$ &
-$5.53^{+3.47}_{-2.40}$ &
-$73.8^{+11.1}_{-19.8}$ &
-$0.89^{+0.07}_{-0.36}$ &
-$56.9^{+3.0}_{-3.0}$ &
-$0.65^{+0.05}_{-0.07}$
-\\[0.075cm]
-
-GW190519\_153544 &
-$123.6^{+11.9}_{-13.0}$ &
-$10.33^{+3.56}_{-3.07}$ &
-$155.5^{+24.0}_{-29.9}$ &
-$0.81^{+0.10}_{-0.28}$ &
-$144.1^{+14.5}_{-16.2}$ &
-$0.78^{+0.08}_{-0.14}$
-\\[0.075cm]
-
-GW190521\_074359 &
-$204.6^{+14.6}_{-11.7}$ &
-$5.32^{+1.48}_{-1.21}$ &
-$86.4^{+12.2}_{-14.3}$ &
-$0.73^{+0.12}_{-0.26}$ &
-$87.1^{+3.3}_{-3.8}$ &
-$0.70^{+0.03}_{-0.05}$
-\\[0.075cm]
-
-GW190630\_185205 &
-$247.8^{+31.8}_{-52.8}$ &
-$3.87^{+2.37}_{-1.80}$ &
-$65.6^{+18.8}_{-41.5}$ &
-$0.62^{+0.27}_{-0.62}$ &
-$66.2^{+4.0}_{-3.2}$ &
-$0.70^{+0.05}_{-0.08}$
-\\[0.075cm]
-
-GW190828\_063405 &
-$257.8^{+201.3}_{-27.8}$ &
-$4.23^{+4.17}_{-1.92}$ &
-$67.4^{+25.7}_{-30.0}$ &
-$0.76^{+0.20}_{-0.73}$ &
-$75.8^{+5.0}_{-5.0}$ &
-$0.74^{+0.04}_{-0.06}$
-\\[0.075cm]
-
-GW190910\_112807 &
-$174.2^{+11.7}_{-7.5}$ &
-$9.52^{+3.13}_{-2.68}$ &
-$123.5^{+14.7}_{-18.1}$ &
-$0.90^{+0.05}_{-0.11}$ &
-$94.9^{+7.6}_{-8.6}$ &
-$0.72^{+0.08}_{-0.04}$
-\\[0.075cm]
-
-\bottomrule
-\end{tabular}
-\caption{The median and symmetric 90\% credible intervals of the remnant properties.
-The first two columns represent the frequency and damping time of the $(2,2)$ QNM measured using the $\pSEOB$ model.
-The next two columns are the mass and spin of the remnant object estimated from the complex QNM frequencies by inverting the fitting formula in~\cite{Berti:2005ys}.
-The last two columns represent final mass and spin estimates predicted using NR fitting formulae from a $\SEOB$ parameter estimation.}
-\label{tab:qnm_o1o2_results}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%
@@
 \label{sec:discussion}
-We have built a parameterized IMR waveform model, $\pSEOB$, that can 
-measure the QNM complex frequencies of the remnant object formed through 
-the merger of BHs with aligned or antialigned spins, thus extending  
-previous work, which was limited to non-spinning BHs~\cite{Brito:2018rfr}. 
-The $\pSEOB$ model was recently used to infer the QNMs of some of the 
-BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.
-
-After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
-injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
-We have analyzed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
-with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
-results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
-we have obtained more stringent bounds on the dominant (or least-damped) QNM $(\ell=2,m=2)$.
-
-More specifically, as expected, the single GW event providing the best constraint
-on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.05^{+0.11}_{-0.07}, 
-\dtau{220}=0.07^{+0.26}_{-0.23})$, although the bounds on 
-$\dtau{220}$ from GW150914 are comparable to GW190521\_074359, 
-the second-most precisely measured event in our list.
-In addition, in the most agnostic and
-conservative scenario where we combine the information from different
-events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
-at $90\%$ credibility $(\df{220}=0.03^{+0.10}_{-0.09}, \dtau{220}=0.10^{+0.44}_{-0.39})$. Thus, 
-our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
-10\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
-over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.
-
-Furthermore, when assuming that the deviations from GR do not vary appreciably over the GW events 
-that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
-on the dominant QNM $(\df{220}=0.02^{+0.04}_{-0.04}, \dtau{220}=0.10^{+0.14}_{-0.14})$. Those 
-constraints are compatible, but slightly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 
-(see first row in Table II therein), where QNM frequencies were inferred using only the post-merger part of 
-the signal. We note that Ref.~\cite{Carullo:2021dui} used a larger set of GW events from O1, O2 and O3a than we did, although we expect 
-that the extra GW events will not contribute significantly to the combined bound since they have lower SNRs.
-
-These constraints could in principle be used to constrain specific
-non-GR theories and exotic compact objects~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}. 
-However, QNM computations in non-GR theories have only been done in an
-handful of cases, mostly focusing on non-rotating or slowly-rotating
-BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao,Wagle:2021tam,Pierini:2021jxd},
-or relying on the eikonal/geometric optics approximation to obtain
-estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}. The
-only exceptions to this rule, that we are aware of, are computations
-of the QNM of Kerr-Newman BHs in Einstein-Maxwell
-theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} or estimates of the BBH in non-GR theories obtained
-through a limited number of NR simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
-limitations, our ability of going beyond a null test of GR and use our
-results to impose precise constraints on non-GR theories with QNM
-measurements is currently quite limited.
-
-Despite these theoretical limitations there has been some recent effort to develop
-parametrizations that could help mapping measurements of the
-parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto
-constraints to specific non-GR theories. This includes for example
-the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently
-applied to LIGO-Virgo GW events in Ref.~\cite{Carullo:2021dui}, where
-deviations from the GR QNMs explicitly depend on a perturbative
-expansion in the BH spin and possible extra non-GR parameters, or the
-proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where
-deviations from the GR QNMs are mapped onto generic small
-modifications of the perturbation equations describing the QNMs. Other
-examples also include proposals to map deviations from the GR QNMs to
-coefficients in generic effective--field-theory
-actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to
-directly relate measurements of the QNM complex frequencies to a
-parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa}, 
-which could be then used jointly with measurements from the Event
-Horizon Telescope to obtain stronger constraints on deviations from
-GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
-We should note, however, that all these parametrizations are either
-limited to non-spinning BHs or make use of a series expansion in the
-BH spin which might limit their accuracy for highly-spinning BHs, unless 
-the sensitivity of GW detectors will not allow us to access the higher 
-coefficients in the spin series.
-
-In the future, it would be important to test whether the $\pSEOB$  model
-could be used to detect deviations in waveforms obtained through NR 
-simulations of specific non-GR theories. Such results are still at their 
-infancy and have so far only been done for a handful of theories, focusing mostly on proof-of-concept
-simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}. Nonetheless,
-given the recent efforts put forward in order to simulate BBHs in
-non-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.
-
-Finally, an obvious generalization of this work would be to extend the
-parameterized $\pSEOB$ model to generic precessing BBHs, which can in
-principle be easily done using the recently developed multipolar EOB
-model reported in Ref.~\cite{Ossokine:2020kjp}. Lastly, it will be relevant 
-to include GR deviations in the $\pSEOB$ model also during the late inspiral 
-and plunge stages of the BBH coalescence. On the other hand, GR deviations (notably 
-deviations from PN theory) for the long inspiral stage are currently 
-available in the $\pSEOB$ model and have been used to set bounds on the 
-PN parameters in the GW phasing using LIGO and Virgo observations~\cite{Abbott:2018lct,
-LIGOScientific:2019fpa,Abbott:2020jks}.
-
 %%%%%%%%%%%%%%%%%
@@
 \label{sec:acknowledgements}
-The authors thank Max Isi for generously allowing us to use the code developed in Ref.~\cite{Isi:2019asy} for the hierarchical inference analysis, and Gregorio Carullo for carefully reading the manuscript and providing useful comments.
-The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
-The authors are grateful for computational resources provided by the LIGO Laboratory and supported by the National Science Foundation Grants PHY-0757058 and PHY-0823459, as well as computational resources at the AEI, specifically the Hypatia cluster.
-R.B.
-acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862, from the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001).
-We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
 %%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\appendix
-\section{Study of systematics in ringdown measurements in real, non-Gaussian noise}\label{sec:noise_systematics}
-
-Inferences of all parameters in this paper have been done under the
-assumption that the noise in the detectors is stationary and
-Gaussian. In other words, detector noise follows a normal distribution
-with zero mean and a PSD, $S_n(f)$, that is not a function of time, at
-least during the duration of the GW signal. This
-allows us to write the Bayesian likelihood function in the form given
-in Eqs.~(\ref{eq:likelihood}) and ~(\ref{eq:nwip}), and perform all the
-parameter estimation that follows in the results sections. However,
-LIGO-Virgo noise can often have features that deviate from
-stationarity and Gaussianity. If such features are not taken into
-account appropriately, final estimates of parameters can get
-biased. Here we demonstrate one such case by injecting in real noise a
-GW190521-like signal and showing how parameter estimates can be biased
-when our description of detector noise is not complete.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
-        \includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
-        \caption{90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2, 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
-The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 of the 5 real noise simulation are not.
-The black curve corresponds to the measurements of the real event GW190521 reported in Ref.~\cite{Abbott:2020jks}.
-All signals are recovered using the $\pSEOB$ model.}
-        \label{fig:21g_systematics}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We choose a spinning, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
-called \texttt{NRSur7dq4} in LAL.} (valid up to mass ratio 4) to simulate the actual GW190521 signal
-observed by the LIGO and Virgo detectors~\cite{Abbott:2020tfl} (see
-Table I of Ref.~\cite{Abbott:2020tfl})). The choice of the
-\texttt{NRSur} model is motivated by the fact that it is the most
-accurate model in the parameter range described by GW190521, because 
-it is built by directly interpolating NR waveforms. In
-Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what
-the injected \texttt{NRSur} signal predicts for the QNM $(\ell=2,m=2)$
-frequency and damping time. For comparison, we also show with a
-black solid curve the results obtained when recovering the actual
-signal GW190521 with the $\pSEOB$ model. As seen in the plot,
-while the measurement of the frequency is consistent with the
-prediction, we overestimate the damping time.
-
-To understand such offset in the decay time, we proceed as follows.
-The actual GW190521 event was observed at a GPS time, 1242442967.61
-seconds (roughly 03:02:49 UTC, May 21, 2019). We select a time period
-of about 2.5 hours around this GPS time, create synthetic signals 
-with the \texttt{NRSur} model and inject them in different stretches
-of the real detector noise around the time of the actual GW event. The
-PSDs of GW detectors are expected to vary over longer durations of
-time, and hence the 2.5 hour stretch of noise we consider can be
-assumed to have noise-properties similar to the time of the actual
-event. Then, we perform Bayesian analysis against those injections 
-using the $\pSEOB$ model. The results are indicated by green curves in
-Fig.~\ref{fig:21g_systematics}. As it can be seen from the figure, for
-3 of the 5 noise realizations, corresponding to $t_0-1$ hour,
-$t_0+0.5$ hours, and $t_0+1$ hour, we recover a damping time similar to
-the one obtained when using the $\pSEOB$ model against the actual event GW190521 
-(black curve), where $t_0$ is the GPS time of the actual event. For
-the other two noise realizations, the $\pSEOB$ model estimates 
-consistently the damping time, but has an off-set frequency, 
-while the fifth noise realization is consistent with both predictions.  
-This study suggests that a bias in the measurements of the damping time 
-for the actual event GW190521 can be explained as due to an incomplete 
-description of the noise at the time of the event.
-
-The reader might question the judiciousness of using an aligned-spin
-waveform model, like $\pSEOB$, to measure a signal like GW190521 which
-appears to be precessing, especially because an incomplete
-understanding of the underlying signal can also lead to biases in
-measured quantities, as we have already demonstrated in
-Sec.~\ref{ssec:ngr_signal}. In order to explore possible effects of
-missing information about in-plane spins in the $\pSEOB$ model, we repeat the
-above study of injecting synthetic signals using \texttt{NRSur}
-and recovering using the $\pSEOB$ model, but this time, instead of
-using real detector noise, we use Gaussian noise (i.e., realizations
-of noise sampled from a predicted detector PSD). Since the properties
-of the noise are completely understood in this case, any residual
-measurement biases can be completely attributed to diffferences in the
-waveform model. The 2D posterior distributions of the frequency and
-damping time measured using these Gaussian-noise signals are shown by
-the grey curves in Fig.~\ref{fig:21g_systematics}. We find the
-measurements to be completely consistent with the predictions of the
-frequency and damping time, thus concluding that a lack of in-plane
-spins in the $\pSEOB$ model does not affect our measurements of the
-QNM properties. The fact that the measurement of ringdown quantities
-are robust against an incomplete description of the inspiral signal 
-is a crucial property of our method.
-
-\section{Correlation of the binary's total mass with the non-GR parameters}
-\label{sec:correlation}
-
-As mentioned in the main text, for low-SNR events with negligible
-higher-modes and for which only the post-merger is detectable, there
-is a strong degeneracy between the binary's total mass and the non-GR
-deviations $(\df{220}, \dtau{220})$. For those cases, only the
-reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
-be independently measured from the data. To justify this statement, 
-in Fig.~\ref{fig:correlations} we show
-corner plots that illustrate the correlations between the non-GR
-parameters $(\df{220}, \dtau{220})$, the detector-frame total mass
-$M(1+z)$ and the reconstructed frequency and damping time
-$(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an
-event for which both the pre- and post-merger phase are measurable,
-and for GW190521 (right panel), an event in which the post-merger has
-${\rm SNR}> 8$, but the pre-merger has an SNR below 8. For GW190521,
-due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D
-posterior for $M(1+z)$ is pushed towards the upper boundary of its
-prior, despite the very wide prior employed in the analysis. This in
-turn renders the measurement of $\df{220}$ (and to a lesser degree of
-$\dtau{220}$) highly dependent on the upper boundary of the total mass
-prior. On the other hand, this issue does not significantly affect the
-posteriors for the reconstructed quantities $(f_{220},\tau _{220})$
-which are well measured and nearly independent on the upper prior
-boundary for $M(1+z)$. This is to be contrasted with the results for GW150914. In this case, 
-the extra information coming from the pre-merger phase allows to break 
-the degeneracy between the non-GR parameters and the total mass, 
-and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can 
-be measured at the same time.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_GW150914.pdf}\includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_S190521g.pdf}
-        \caption{Corner plots showing the correlations between the detector-frame total $(1+z)M$, the non-GR deviations $(\df{220}, \dtau{220})$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$.
-The left panel shows results for GW150914, for which ${\rm SNR}> 8$ in both the pre- and
-post-merger phase of the signal, and the correlations are absent.
-The right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase, but not in the pre-merger phase, and the correlations are present.}
-        \label{fig:correlations}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \bibliographystyle{apsrev}
-\bibliography{intro_paper}
+\bibliography{paper_alt_theor_bounds}
 

### 2021-11-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added a skeleton to the proposed paper
hs: small edits

@@
 \usepackage{times}
+% \usepackage[varg]{txfonts}
+\usepackage{txfonts}
 \usepackage{xspace}
-\usepackage[varg]{txfonts}
 \usepackage[normalem]{ulem} % To get strikethrough (\sout)
@@
 \usepackage{makecell}
+\usepackage{microtype}
 
@@
 
+\newcommand{\pd}{\partial}
+\newcommand{\dd}{{\rm d}}
+\newcommand{\dV}{{\rm d}^{4}x \, \sqrt{-g} \,}
+\newcommand{\lame}{\lambda_{\rm e}}
+\newcommand{\lamo}{\lambda_{\rm o}}
+
+% Comment commands
+\newcommand{\ag}[1]{{\textcolor{cyan}{{[AG: #1]}} }}
+\newcommand{\hs}[1]{{\textcolor{blue}{{[HS: #1]}} }}
+\newcommand{\ab}[1]{{\textcolor{green}{{[AB: #1]}} }}
+
 \newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
-\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
+\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, Maryland 20742, USA}}
 
@@
 
-\author{TBD}
+\author{Abhirup Ghosh}
+\author{Hector O. Silva}
+\AEI
+\author{Alessandra Buonanno}
+\AEI
+\UMD
 
@@
 %%%%%%%%%%%%%%%%%
-\section{Method}
+\section{Methods}
 \label{sec:method}
+
+\subsection{The parametrized waveform model}
+\label{sec:review_pSEOB}
+
+\subsection{The parametrized ringdown spin expansion coefficients}
+\label{sec:review_parspec}
+
+\subsection{Overview of modified gravity theories}
+\label{sec:review_theories}
+
+A broad class modified gravity theories are capture by the action
+%
+\begin{align}
+S &= \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
+\left[ R + \dots \right.
+\nonumber \\
+&\quad
+\left.
+\right]
+\end{align}
+%
+
+\begin{table}[t]
+\begin{tabular}{c c c c c}
+\hline
+\hline
+Theory & $p$ & $\delta \omega$ & $\delta \tau$ & Refs. \\
+\hline
+\dots & \dots & \dots & \dots & \dots \\
+\hline
+\hline
+\end{tabular}
+\caption{Summary of theories consider in this paper.
+\hs{Add a column with the constraint (if any) that we placed.}}
+\label{tab:ref_stars}
+\end{table}
+
+%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%
+\section{Results}
+\label{sec:results}
 %%%%%%%%%%%%%%%%%
@@
 \label{sec:acknowledgements}
+%
+We thank Emanuele Berti and Andrea Maselli for discussions.
+%
+The authors are grateful for the computational resources provided by the AEI,
+specifically the {\sc Hypatia} cluster.
+%
+The authors would like to thank everyone at the frontline of the Covid-19
+pandemic.
 %%%%%%%%%%%%%%%%%
 
-%
-\bibliographystyle{apsrev}
+% \bibliographystyle{apsrev}
 \bibliography{paper_alt_theor_bounds}

### 2021-11-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: generic title added
hs: added description of sections and todos

@@
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
+\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-2}
 \usepackage{epsfig}
@@
 \usepackage{bm}
-\usepackage{times}
+% \usepackage{times}
 % \usepackage[varg]{txfonts}
@@
 
-\title{Super-awesome paper with super-cool results}
+% HS: temporary title. Feel free to add suggestions
+\title{Constraints on higher-curvature gravity theories from binary black hole ringdown signals}
+% \title{Black-hole ringdown as probe of higher-curvature gravity theories}
 
@@
 
+\subsection{The parametrized ringdown spin expansion coefficients}
+\label{sec:review_parspec}
+
+\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
+
 \subsection{The parametrized waveform model}
@@
 
-\subsection{The parametrized ringdown spin expansion coefficients}
-\label{sec:review_parspec}
+\hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
+explain how we modified it to include the {\sc Parspec} parametrisation.}
 
@@
 \label{sec:review_theories}
+
+\hs{Here we review class of gravity theories we will consider.
+They all have higher-curvature terms, hence the `higher-curvature gravity theories'
+in the title.}
 
@@
 \end{align}
-%
 
-\begin{table}[t]
+%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%
+\section{Methods}
+\label{sec:methods}
+%%%%%%%%%%%%%%%%%
+
+\begin{table}[th]
 \begin{tabular}{c c c c c}
@@
 \caption{Summary of theories consider in this paper.
-\hs{Add a column with the constraint (if any) that we placed.}}
-\label{tab:ref_stars}
+\hs{Add a column with the constraint (if any) that we placed.}
+\hs{TODO: add which runs are done and which need to be done.}
+}
+\label{tab:ref_theories}
 \end{table}
 
-%%%%%%%%%%%%%%%%%
+\hs{We {\it must very explicitly} state our working hypothesis here:
+%
+\begin{itemize}
+    \item That we include only the nonrotating, non-GR correction to the QNMs.
+    \item That due to absence of isospectrality, when translating to the theory specific result,
+    we {\it chose} to use the lowest damping, gravitational QNM of the theory.
+\end{itemize}
+%
+We can come back to these in the Sec.~\ref{sec:discussion} as things that we
+might want to revisit in the future.
+}
+
+\hs{In Table~\ref{tab:ref_theories} we summarize the relevant parameters for
+the {\sc Parspec} implementation of each theory and give credit to the papers
+which calculated the QNMs.}
+
+\hs{Say which GW event we will consider and justify why.}
 
@@
 
+\hs{Here we summarise the results of our PE runs. Combine the posteriors on the
+the non-GR parameter coming from different events. We could have a short
+subsection for each theory. We should quote two thresholds for claiming
+that we placed a bound, one using the secondary BH mass and another with
+the final BH mass.}
+
 %%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%
+
+\hs{I think an important message of the paper is that we give indication that
+there are theories of gravity (such as dCS) which can by-pass observational
+constraints from the inspiral phase alone, {\it yet} they do not, if we
+analyse the ringdown. This is quite important because I've frequently heard
+that the ``inspiral is what will constrain theories''. I think this might be
+the most important message.}
 
@@
 %
-The authors are grateful for the computational resources provided by the AEI,
-specifically the {\sc Hypatia} cluster.
+\hs{Anyone else? Serguei, Deyan?}
+%
+We thank the computational resources provided by the AEI, specifically the
+{\sc Hypatia} cluster.
 %

### 2021-12-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: upd to modified grav section

@@
 \usepackage{lineno}
+\usepackage{mathrsfs}
 %\linenumbers
@@
 % HS: temporary title. Feel free to add suggestions
-\title{Constraints on higher-curvature gravity theories from binary black hole ringdown signals}
-% \title{Black-hole ringdown as probe of higher-curvature gravity theories}
+% \title{Probing higher-curvature gravity theories from binary black hole ringdown signals}
+\title{Black-hole ringdown as probe of higher-curvature gravity theories}
 
@@
 \maketitle
+\tableofcontents
 
@@
 
-\subsection{The parametrized ringdown spin expansion coefficients}
+\subsection{The parametrized ringdown spin expansion coefficients formalism}
 \label{sec:review_parspec}
@@
 \hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
+
+The formalism modifies the Kerr quasinormal mode frequency as
+%
+\begin{subequations}
+\begin{align}
+\omega_{\iota} &= \omega^{\rm K}_{\iota} \, (1 + \delta \omega_{\iota}), \\
+\tau_{\iota}   &= \tau^{\rm K}_{\iota}   \, (1 + \delta \tau_{\iota}),
+\end{align}
+\label{eq:general_deviation}
+\end{subequations}
+%
+where the $\iota$ collectively represents the QNM labels $\{l,\, m,\, n\}$.
+
+Further expand the Kerr expression as:
+%
+\begin{subequations}
+\begin{align}
+\omega_{\iota} &= (1/M) \sum_{j = 0}^{N} \, \chi^{j} \omega^{(j)}_{k} \, \left( 1 + \gamma \delta \omega^{(j)}_{k} \right), \\
+\tau_{\iota}   &= M     \sum_{j = 0}^{N} \, \chi^{j} \tau^{(j)}_{k}   \, \left( 1 + \gamma \delta \tau^{(j)}_{k} \right),
+\end{align}
+\label{eq:kerr_expansion}
+\end{subequations}
+
+Also,
+%
+\begin{equation}
+\gamma = \frac{\kappa}{M_{\rm s}^{p}} = \frac{\kappa (1 + z)^{p}}{M^{p}}
+= \left[
+\frac{\ell c^2 (1 + z)}{G M}
+\right]^{p}
+\end{equation}
+%
 
@@
 
-A broad class modified gravity theories are capture by the action
+A broad class modified gravity theories are described by the action
 %
+\begin{equation}
+S = \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
+\left[ R
+- \tfrac{1}{2}(\nabla \varphi)^2
+\right]
++
+\sum_{n \geqslant 2} \frac{\ell^{2n - 2}}{16 \pi G} S^{(2n)},
+\end{equation}
+%
+where $\varphi$ is a dynamical scalar field, $\ell$ some length scale, assumed
+to be small compares to the length scale associated with a black hole, i.e.,
+$GM \gg \ell$, and $S^{(2n)}$ are corrections to the Einstein-Klein-Gordon
+action that introduce involving higher-order curvature tensors (with $2n$
+metric derivatives) and scalar field.
+
+More specifically, we work up to dimension-eight operators (i.e., $n=4$),
+%
+\begin{subequations}
 \begin{align}
-S &= \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
-\left[ R + \dots \right.
-\nonumber \\
-&\quad
-\left.
-\right]
+S^{(4)} &= \alpha_{\rm GB} R^{2}_{\rm GB} + \alpha_{\rm CS} {}^{*}RR,
+\label{eq:s_4}
+\\
+S^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
++ \lamo \ell^4 R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
+\label{eq:s_6}
+\\
+S^{(8)} &= \epsilon_{1} \mathcal{C}^2  + \epsilon_{2} \tilde{\mathcal{C}}^{2}
++ \epsilon_{3} \mathcal{C} \tilde{\mathcal{C}},
+\label{eq:s_8}
 \end{align}
+\label{eq:action_mods}
+\end{subequations}
+%
+where we defined the Gauss-Bonnet and Pontryagin densities, respectively,
+%
+\begin{subequations}
+\begin{align}
+    R^{2}_{\rm GB} &= R_{\mu\nu\rho\sigma}R^{\mu\nu\rho\sigma} - 4 R_{\mu\nu} R^{\mu\nu} + R^2,
+    \\
+    {}^{*}RR &= \tfrac{1}{2} R_{\nu\mu\rho\sigma} {}^{*}R^{\mu\nu\rho\sigma},
+\end{align}
+\end{subequations}
+%
+and where $R_{\mu\nu\rho\sigma}$ is the Riemann tensor
+and $\tilde{R}_{\mu\nu\rho\sigma}$ its dual, defined as
+%
+\begin{equation}
+\tilde{R}_{\mu\nu\alpha\beta} = \tfrac{1}{2} \epsilon_{\mu\nu\rho\sigma} R^{\rho\sigma}{}_{\alpha\beta},
+\end{equation}
+%
+with $\epsilon_{\mu\nu\rho\sigma}$ being the Levi-Civita tensor.
+
+This action encapsulates various modified gravity theories, which often are studied on their own,
+namely,
+%
+\begin{itemize}
+    \item scalar Gauss-Bonnet gravity (sGB): corresponds to $\alpha_{\rm GB}$
+          nonzero and all other dimensionless coupling constants equal to zero.
+    \item dynamical Chern-Simons (dCS): this corresponds to $\alpha_{\rm CS}$
+          nonzero and all other dimensionless coupling constants equal to zero.
+    \item cubic effective field theory of GR (cEFTofGR): this corresponds to $\lame$, $\lamo$ nonzero
+          and all other dimensionless coupling constants equal to zero.
+    \item quartic effective field theory of GR (qEFTofGR): this corresponds to $\varepsilon_{i}$
+          ($i = 1,2,3$) nonzero and all other dimensionless coupling constants equal to zero.
+\end{itemize}
+
+In each of these theories, slowly-rotating black hole and their quasinormal mode spectra
+to leading order in spin have been calculated.
+%
+We can use this results to establish a mapping between theory-specific calculations and
+the theory-agnostic {\sc Parspec} parametrization.
+%
+We discuss how we do this in the section.
+
+In Eqs.~\eqref{eq:action_mods}, $\alpha_{\rm GB}$, $\alpha_{\rm CS}$, $\lame$,
+$\lamo$ and $\varepsilon_{i}$ are dimensionless constants.
 
@@
 
-\begin{table}[th]
-\begin{tabular}{c c c c c}
+\subsection{From theory-agnostic to theory-specific QNM results}
+
+\begin{table*}[th]
+\begin{tabular}{c c c c c c}
 \hline
 \hline
-Theory & $p$ & $\delta \omega$ & $\delta \tau$ & Refs. \\
+Theory & $p$ & $\delta \omega$ & $\delta \tau$ & QNM & Constraint \\
 \hline
-\dots & \dots & \dots & \dots & \dots \\
+sGB      & 4 & \dots & \dots & \cite{Pierini:2021jxd} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 1.7$~km~\cite{Perkins:2021mhb} \\
+dCS      & 4 & \dots & \dots & \cite{Wagle:2021tam} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 8.5$~km~\cite{Silva:2020acr} \\
+cEFTofGR & 4 & \dots & \dots & \cite{Cano:2021myl} & -- \\
+qEFTofGR & 6 & \dots & \dots & \cite{Cano:2021myl} & -- \\
 \hline
@@
 \end{tabular}
-\caption{Summary of theories consider in this paper.
+\caption{Summary of the quasinormal modes calculations.
+%
+We summarize each theory we have considered together with: the exponent $p$ at
+which their QNM-modification enters, the corresponding modifications to the
+oscillation frequency $\delta \omega$ and decay time $\delta \tau$, the
+references from which we used the results from and the current best constraint
+(if applicable).
+%
 \hs{Add a column with the constraint (if any) that we placed.}
@@
 }
-\label{tab:ref_theories}
-\end{table}
+\label{tab:ref_theories_qnms}
+\end{table*}
 
@@
 
-\hs{In Table~\ref{tab:ref_theories} we summarize the relevant parameters for
+\hs{In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
 the {\sc Parspec} implementation of each theory and give credit to the papers
@@
 
-\hs{Say which GW event we will consider and justify why.}
+\subsection{Gravitational events used}
+
+\hs{Say that we use GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp} and justify why.}
+
+\subsection{Parameter estimation}
 
@@
 
-\hs{Here we summarise the results of our PE runs. Combine the posteriors on the
+\hs{Here we summarize the results of our PE runs. Combine the posteriors on the
 the non-GR parameter coming from different events. We could have a short
@@
 constraints from the inspiral phase alone, {\it yet} they do not, if we
-analyse the ringdown. This is quite important because I've frequently heard
+analyze the ringdown. This is quite important because I've frequently heard
 that the ``inspiral is what will constrain theories''. I think this might be
@@
 %
-We thank Emanuele Berti and Andrea Maselli for discussions.
-%
-\hs{Anyone else? Serguei, Deyan?}
+We thank Emanuele~Berti, Andrea~Maselli, Deyan~Mihailov and Serguei~Ossokine
+for discussions.
 %

### 2021-12-21 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: removed duplicate bib entry; added package for slanted signs
hs: filling more details of table/re-organizing subsections

@@
 \usepackage{bm}
-% \usepackage{times}
-% \usepackage[varg]{txfonts}
 \usepackage{txfonts}
+\usepackage{amssymb}
 \usepackage{xspace}
@@
 \usepackage{mathrsfs}
-%\linenumbers
 \usepackage{makecell}
@@
 \definecolor{UrlColor}{rgb}{0, 0, 0.75}
-\hypersetup{linkcolor=LinkColor}
-\hypersetup{citecolor=CiteColor}
-\hypersetup{urlcolor=UrlColor}
+\hypersetup{linkcolor=NavyBlue}
+\hypersetup{citecolor=NavyBlue}
+\hypersetup{urlcolor=NavyBlue}
 \usepackage{perpage}
@@
 % \title{Probing higher-curvature gravity theories from binary black hole ringdown signals}
-\title{Black-hole ringdown as probe of higher-curvature gravity theories}
+\title{The black-hole ringdown as a probe of higher-curvature gravity theories}
 
+\author{Hector O. Silva}
 \author{Abhirup Ghosh}
-\author{Hector O. Silva}
 \AEI
@@
 \maketitle
-\tableofcontents
+% \tableofcontents
 
@@
 %%%%%%%%%%%%%%%%%
+
+\hs{AB will do this.}
 
@@
 
+\hs{HS will do this.}
 \hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
@@
 
+\hs{AG will do this.}
 \hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
@@
 
-\hs{Here we review class of gravity theories we will consider.
-They all have higher-curvature terms, hence the `higher-curvature gravity theories'
-in the title.}
+\hs{HS will do this.}
+
+% \hs{Here we review class of gravity theories we will consider.
+% They all have higher-curvature terms, hence the `higher-curvature gravity theories'
+% in the title.}
 
@@
 \left[ R
-- \tfrac{1}{2}(\nabla \varphi)^2
+- \tfrac{\beta}{2}(\nabla \varphi)^2
 \right]
@@
 
-%%%%%%%%%%%%%%%%%
-\section{Methods}
-\label{sec:methods}
-%%%%%%%%%%%%%%%%%
-
 \subsection{From theory-agnostic to theory-specific QNM results}
 
+\hs{HS will do this.}
+
 \begin{table*}[th]
-\begin{tabular}{c c c c c c}
+\begin{tabular}{c | c c c c c c c c}
 \hline
 \hline
-Theory & $p$ & $\delta \omega$ & $\delta \tau$ & QNM & Constraint \\
+Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
 \hline
-sGB      & 4 & \dots & \dots & \cite{Pierini:2021jxd} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 1.7$~km~\cite{Perkins:2021mhb} \\
-dCS      & 4 & \dots & \dots & \cite{Wagle:2021tam} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 8.5$~km~\cite{Silva:2020acr} \\
-cEFTofGR & 4 & \dots & \dots & \cite{Cano:2021myl} & -- \\
-qEFTofGR & 6 & \dots & \dots & \cite{Cano:2021myl} & -- \\
+sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots & \cite{Pierini:2021jxd} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
+dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam} & $\alpha^{1/2}_{\rm CS} \ell \leqslant 8.5$~km~\cite{Silva:2020acr} & \dots \\
+cEFTofGR & 4 & $-0.3680$ / $-0.5131$  & 1.9242 / 1.7000 & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
+qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
 \hline
@@
 which their QNM-modification enters, the corresponding modifications to the
-oscillation frequency $\delta \omega$ and decay time $\delta \tau$, the
+oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
 references from which we used the results from and the current best constraint
 (if applicable).
+%
+In the entries for cEFTofGR, the first entries in the $\delta
+\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
+\emph{only parity-even correnctions} and the second entries by considering
+\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
+$\lambda_{\rm e,o}$ are degenerate with the lengthscale $\ell$.
 %
@@
 
-\subsection{Gravitational events used}
+%%%%%%%%%%%%%%%%%
+\section{Analysis using LIGO-Virgo data}
+\label{sec:results}
+%%%%%%%%%%%%%%%%%
 
 \hs{Say that we use GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp} and justify why.}
-
-\subsection{Parameter estimation}
-
-%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-%%%%%%%%%%%%%%%%%
 
@@
 %
-We thank Emanuele~Berti, Andrea~Maselli, Deyan~Mihailov and Serguei~Ossokine
-for discussions.
+We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihailov, and
+Serguei~Ossokine for discussions.
 %

### 2022-01-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: reorganization of mod. grav. sec.

@@
 \usepackage{graphicx}
-\usepackage{bm}
 \usepackage[dvipsnames]{xcolor}
 \usepackage{bm}
-\usepackage{txfonts}
+% \usepackage{txfonts}
 \usepackage{amssymb}
@@
 
+\usepackage{tikz}
+
 \definecolor{LinkColor}{rgb}{0.75, 0, 0}
@@
 \definecolor{UrlColor}{rgb}{0, 0, 0.75}
+\definecolor{rred}{RGB}{218,41,28}
 \hypersetup{linkcolor=NavyBlue}
@@
 \hypersetup{urlcolor=NavyBlue}
+
 \usepackage{perpage}
@@
 
+% Modified gravity related
 \newcommand{\pd}{\partial}
@@
 \newcommand{\dV}{{\rm d}^{4}x \, \sqrt{-g} \,}
+
 \newcommand{\lame}{\lambda_{\rm e}}
 \newcommand{\lamo}{\lambda_{\rm o}}
+\newcommand{\acs}{\ell_{\rm CS}}
+\newcommand{\agb}{\ell_{\rm GB}}
 
@@
 % \title{Probing higher-curvature gravity theories from binary black hole ringdown signals}
-\title{The black-hole ringdown as a probe of higher-curvature gravity theories}
+\title{Black-hole ringdown as a probe of higher-curvature gravity theories}
 
@@
 
-\hs{HS will do this.}
+We will consider several modified gravity theories as applications of the \pSEOB{}
+waveform model presented in Sec.~\ref{sec:review_pSEOB}.
+%
+In the following, we briefly review which theories we consider, what are the
+currents observational constraints in each of them and what we known about the
+QNMs of black holes in each of them.
 
-% \hs{Here we review class of gravity theories we will consider.
-% They all have higher-curvature terms, hence the `higher-curvature gravity theories'
-% in the title.}
+\subsubsection{scalar-Gauss-Bonnet gravity}
+%
+This theory is given by the following action,
+%
+\begin{equation} \label{eq:action_sgb}
+    S_{\rm GB} = \frac{1}{16 \pi}
+    \int \dV
+    \left[
+    R - \tfrac{1}{2}(\nabla \varphi)^2
+    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \mathscr{G}
+    \right],
+\end{equation}
+%
+where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
+$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
+invariant $\mathscr{G}$,
+%
+\begin{equation} \label{eq:def_gb}
+    \mathscr{G} =
+    R^{\mu\nu\rho\sigma}R_{\mu\nu\rho\sigma}
+    - 4 R^{\mu\nu}R_{\mu\nu}
+    + R^2,
+\end{equation}
+%
+with strength set by the dimensionful coupling constant $\agb$ with dimensions
+of length.
 
-A broad class modified gravity theories are described by the action
+Different subclasses of this theory are determined by the function $f(\varphi)$
+and they can be classified into two classes based on the properties of their black hole solutions.
+%
+In the first class, the first derivative of the coupling
+function $f'(\varphi) = \dd f  / \dd \varphi$ is always nonzero and black holes
+are known to always support (secondary) scalar hair.
+%
+Examples include the shift-symmetric $f \propto \varphi$ and dilatonic
+$f \propto \exp(\varphi)$ couplings.
+%
+In the second class, $f'(\varphi) = 0$ can vanish for some constant $\varphi_0$.
+%
+In this case, one can show that theory admits the same stationary,
+asymptotically flat black hole solution of GR and scalarized black
+holes~\cite{Doneva:2017bvd,Silva:2017uqg,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
+%
+Examples include the quadratic $f \propto \varphi^2$~\cite{Silva:2017uqg}
+and Gaussian $f \propto \exp(-\varphi^2)$~\cite{Doneva:2017bvd} couplings.
+%
+Here will consider only the dilatonic theory.
+
+Black holes in both classes support monopolar scalar hair and thus, when in binaries,
+can source scalar dipole radiation and are therefore prone to be constrained with
+GWs observations of compact binaries~\cite{Nair:2019iur,Perkins:2021mhb}.
+%
+\dots
+
+The calculation of the QNMs in this theory is more complicated than in GR already for
+nonrotating black holes. The reason is due to the coupling between scalar field and
+the Gauss-Bonnet invariant, which manifests into a coupling between scalar perturbation
+and gravitational perturbations of polar parity \dots
+
+\begin{figure}
+\begin{tikzpicture}[baseline,>=stealth]
+    % \draw[help lines, gray] (-4, -2) grid (4, 2);
+    \draw[->] (-2.5, 0) -- (-1.75, +0.5);
+    \draw[->] (-2.5, 0) -- (-1.75, -0.5);
+
+    \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \varphi\}$};
+
+    \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
+    \node at (-1, +0.5) {$\{ \textcolor{rred}{h^{\rm p}_{\alpha\beta}}, \, \varphi\}$};
+    \node at (-1, -0.5) {$h^{\rm a}_{\alpha\beta}$};
+
+    \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
+    \node at (+1, +0.5) {\dots};
+    \node at (+1, -0.5) {\dots};
+\end{tikzpicture}
+\caption{Quasinormal modes of black holes in scalar-Gauss-Bonnet gravity.}
+\end{figure}
+
+\subsubsection{dynamical Chern-Simons}
+
+This theory is given by the following action,
+%
+\begin{equation} \label{eq:action_dcs}
+    S_{\rm CS} = \frac{1}{16 \pi}
+    \int \dV
+    \left[
+    R - \tfrac{1}{2}(\nabla \vartheta)^2
+    + \tfrac{1}{4} \ell^{2}_{\rm CS} \, \vartheta \, {}^{*}RR
+    \right],
+\end{equation}
+%
+where $\vartheta$ is a pseudo-scalar field, which couples
+to the Pontryagin density,
 %
 \begin{equation}
-S = \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
-\left[ R
-- \tfrac{\beta}{2}(\nabla \varphi)^2
-\right]
-+
-\sum_{n \geqslant 2} \frac{\ell^{2n - 2}}{16 \pi G} S^{(2n)},
+    {}^{*}RR = {}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} R^{\nu}_{\mu\rho\sigma},
 \end{equation}
 %
-where $\varphi$ is a dynamical scalar field, $\ell$ some length scale, assumed
-to be small compares to the length scale associated with a black hole, i.e.,
-$GM \gg \ell$, and $S^{(2n)}$ are corrections to the Einstein-Klein-Gordon
-action that introduce involving higher-order curvature tensors (with $2n$
-metric derivatives) and scalar field.
+where ${}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma}$ is the dual of the Riemann tensor,
+defined as
+%
+${}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} =
+\tfrac{1}{2} \epsilon^{\mu}{}_{\nu\gamma\delta}
+R^{\gamma\delta\rho\sigma}$,
+%
+and where $\epsilon^{\mu}{}_{\nu\gamma\delta}$ is the Levi-Civita tensor.
+%
+The coupling between scalar field and the Pontryagin density is set by the
+$\ell_{\rm CS}$ with dimensions of length.
 
-More specifically, we work up to dimension-eight operators (i.e., $n=4$),
+The theory admits the Schwarzschild black hole solution of GR, but predicts
+that spinning black holes have (secondary) scalar hair, which, unlike in
+scalar-Gauss-Bonnet gravity, is dipolar~\cite{Yunes:2009hc,Konno:2009kg}.
+%
+Consequently, the leading-scalar radiation channel is quadrupolar making this
+theory presently unconstrained by from the GWs from the inspiral of black hole
+binaries alone~\cite{Nair:2019iur,Perkins:2021mhb}.
+%
+However, the theory has been constrained by Ref~\cite{Silva:2020acr} through a
+combination information of x-ray observations of the isolated neutron star PSR
+J0030+0451~\cite{Lommen:2000yt,NANOGrav:2017wvv} by the
+NICER~\cite{Riley:2019yda,Miller:2019cac} and gravitational-wave observation of
+the binary neutron star event GW170817~\cite{TheLIGOScientific:2017qsa}.
+
+Similarly to the case of scalar-Gauss-Bonnet gravity, the perturbations of nonrotating
+black holes in dynamical Chern-Simons gravity also have a coupling between scalar and
+metric perturbations. However, the coupling is between the scalar and gravitational perturbations
+of axial parity~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb,Wagle:2021tam}.
+
+\begin{figure}
+\begin{tikzpicture}[baseline,>=stealth]
+    % \draw[help lines, gray] (-4, -2) grid (4, 2);
+    \draw[->] (-2.5, 0) -- (-1.75, +0.5);
+    \draw[->] (-2.5, 0) -- (-1.75, -0.5);
+
+    \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \vartheta\}$};
+
+    \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
+    \node at (-1, +0.5) {$h^{\rm p}_{\alpha\beta}$};
+    \node at (-1, -0.5) {$\{ \textcolor{rred}{h^{\rm a}_{\alpha\beta}}, \, \vartheta\}$};
+
+    \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
+    \node at (+1, +0.5) {\dots};
+    \node at (+1, -0.5) {\dots};
+\end{tikzpicture}
+\caption{Quasinormal modes of black holes in dynamical Chern-Simons gravity.}
+\end{figure}
+
+\subsubsection{Effective-field-theory of GR}
+
+This theory is given by the following action,
+%
+\begin{equation} \label{eq:action_eft}
+    S_{\rm EFT} = \frac{1}{16 \pi}
+    \int \dd^4x \sqrt{-g}
+    \left[ R
+    +
+    \footnotesize{\sum}_{n \geqslant 2} \ell^{2n - 2} L^{(2n)}
+    \right],
+\end{equation}
+%
+where $\ell$ is some length scale, assumed to be small compares to the length
+scale associated with a black hole, i.e., $\ell / M \ll 1$, and
+$L^{(2n)}$ are corrections to the Einstein-Hilbert term action that
+introduce involving higher-order curvature tensors (with $2n$ metric
+derivatives).
+
+More specifically, we follow Refs.~\cite{Cano:2020cao,Cano:2021myl} and work up
+to dimension-eight operators (i.e., $n=4$),
 %
 \begin{subequations}
+\label{eq:action_mods}
 \begin{align}
-S^{(4)} &= \alpha_{\rm GB} R^{2}_{\rm GB} + \alpha_{\rm CS} {}^{*}RR,
-\label{eq:s_4}
-\\
-S^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
-+ \lamo \ell^4 R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
+    L^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
+    \nonumber \\
+            &\quad + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
     \label{eq:s_6}
     \\
-S^{(8)} &= \epsilon_{1} \mathcal{C}^2  + \epsilon_{2} \tilde{\mathcal{C}}^{2}
-+ \epsilon_{3} \mathcal{C} \tilde{\mathcal{C}},
+    L^{(8)} &= \varepsilon_{1} \mathcal{C}^2
+    + \varepsilon_{2} \tilde{\mathcal{C}}^{2}
+    + \varepsilon_{3} \mathcal{C} \tilde{\mathcal{C}},
 \label{eq:s_8}
-\end{align}
-\label{eq:action_mods}
-\end{subequations}
-%
-where we defined the Gauss-Bonnet and Pontryagin densities, respectively,
-%
-\begin{subequations}
-\begin{align}
-    R^{2}_{\rm GB} &= R_{\mu\nu\rho\sigma}R^{\mu\nu\rho\sigma} - 4 R_{\mu\nu} R^{\mu\nu} + R^2,
-    \\
-    {}^{*}RR &= \tfrac{1}{2} R_{\nu\mu\rho\sigma} {}^{*}R^{\mu\nu\rho\sigma},
 \end{align}
@@
 %
-and where $R_{\mu\nu\rho\sigma}$ is the Riemann tensor
-and $\tilde{R}_{\mu\nu\rho\sigma}$ its dual, defined as
+where $\lambda_{\rm o, e}$ and $\varepsilon_{i}$ ($i=1,2,3$) are dimensionless parameters.
+
+Black holes in these theories were studied in \dots
+
+% where we defined the Gauss-Bonnet and Pontryagin densities, respectively,
+% %
+% \begin{subequations}
+% \begin{align}
+%     R^{2}_{\rm GB} &= R_{\mu\nu\rho\sigma}R^{\mu\nu\rho\sigma} - 4 R_{\mu\nu} R^{\mu\nu} + R^2,
+%     \\
+%     {}^{*}RR &= \tfrac{1}{2} R_{\nu\mu\rho\sigma} {}^{*}R^{\mu\nu\rho\sigma},
+% \end{align}
+% \end{subequations}
+% %
+% and where $R_{\mu\nu\rho\sigma}$ is the Riemann tensor
+% and $\tilde{R}_{\mu\nu\rho\sigma}$ its dual, defined as
+% %
+% \begin{equation}
+% \tilde{R}_{\mu\nu\alpha\beta} = \tfrac{1}{2} \epsilon_{\mu\nu\rho\sigma} R^{\rho\sigma}{}_{\alpha\beta},
+% \end{equation}
+% %
+% with $\epsilon_{\mu\nu\rho\sigma}$ being the Levi-Civita tensor.
+
+% This action encapsulates various modified gravity theories, which often are studied on their own,
+% namely,
+% %
+% \begin{itemize}
+%     \item scalar Gauss-Bonnet gravity (sGB): corresponds to $\alpha_{\rm GB}$
+%           nonzero and all other dimensionless coupling constants equal to zero.
+%     \item dynamical Chern-Simons (dCS): this corresponds to $\alpha_{\rm CS}$
+%           nonzero and all other dimensionless coupling constants equal to zero.
+%     \item cubic effective field theory of GR (cEFTofGR): this corresponds to $\lame$, $\lamo$ nonzero
+%           and all other dimensionless coupling constants equal to zero.
+%     \item quartic effective field theory of GR (qEFTofGR): this corresponds to $\varepsilon_{i}$
+%           ($i = 1,2,3$) nonzero and all other dimensionless coupling constants equal to zero.
+% \end{itemize}
 %
-\begin{equation}
-\tilde{R}_{\mu\nu\alpha\beta} = \tfrac{1}{2} \epsilon_{\mu\nu\rho\sigma} R^{\rho\sigma}{}_{\alpha\beta},
-\end{equation}
+% In each of these theories, slowly-rotating black hole and their quasinormal mode spectra
+% to leading order in spin have been calculated.
+% %
+% We can use this results to establish a mapping between theory-specific calculations and
+% the theory-agnostic {\sc Parspec} parametrization.
+% %
+% We discuss how we do this in the section.
 %
-with $\epsilon_{\mu\nu\rho\sigma}$ being the Levi-Civita tensor.
-
-This action encapsulates various modified gravity theories, which often are studied on their own,
-namely,
-%
-\begin{itemize}
-    \item scalar Gauss-Bonnet gravity (sGB): corresponds to $\alpha_{\rm GB}$
-          nonzero and all other dimensionless coupling constants equal to zero.
-    \item dynamical Chern-Simons (dCS): this corresponds to $\alpha_{\rm CS}$
-          nonzero and all other dimensionless coupling constants equal to zero.
-    \item cubic effective field theory of GR (cEFTofGR): this corresponds to $\lame$, $\lamo$ nonzero
-          and all other dimensionless coupling constants equal to zero.
-    \item quartic effective field theory of GR (qEFTofGR): this corresponds to $\varepsilon_{i}$
-          ($i = 1,2,3$) nonzero and all other dimensionless coupling constants equal to zero.
-\end{itemize}
-
-In each of these theories, slowly-rotating black hole and their quasinormal mode spectra
-to leading order in spin have been calculated.
-%
-We can use this results to establish a mapping between theory-specific calculations and
-the theory-agnostic {\sc Parspec} parametrization.
-%
-We discuss how we do this in the section.
-
-In Eqs.~\eqref{eq:action_mods}, $\alpha_{\rm GB}$, $\alpha_{\rm CS}$, $\lame$,
-$\lamo$ and $\varepsilon_{i}$ are dimensionless constants.
+% In Eqs.~\eqref{eq:action_mods}, $\alpha_{\rm GB}$, $\alpha_{\rm CS}$, $\lame$,
+% $\lamo$ and $\varepsilon_{i}$ are dimensionless constants.
 

### 2022-01-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: adjusted order of sections

@@
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-2}
+\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-1}
 \usepackage{epsfig}
@@
 \usepackage{tikz}
+
+% -----------
+% Bibligraphy
+% -----------
+\AtBeginDocument{%
+    \newwrite\bibnotes
+    \def\bibnotesext{Notes.bib}
+    \immediate\openout\bibnotes=\jobname\bibnotesext
+    \immediate\write\bibnotes{@CONTROL{REVTEX41Control}}
+    \immediate\write\bibnotes{@CONTROL{%
+    apsrev41Control,author="08",editor="1",pages="1",title="0",year="1"}}
+    \if@filesw
+    \immediate\write\@auxout{\string\citation{apsrev41Control}}%
+    \fi
+}
 
@@
 
-%%%%%%%%%%%%%%%%%
-\section{Methods}
-\label{sec:method}
-
-\subsection{The parametrized ringdown spin expansion coefficients formalism}
-\label{sec:review_parspec}
-
-\hs{HS will do this.}
-\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
-
-The formalism modifies the Kerr quasinormal mode frequency as
-%
-\begin{subequations}
-\begin{align}
-\omega_{\iota} &= \omega^{\rm K}_{\iota} \, (1 + \delta \omega_{\iota}), \\
-\tau_{\iota}   &= \tau^{\rm K}_{\iota}   \, (1 + \delta \tau_{\iota}),
-\end{align}
-\label{eq:general_deviation}
-\end{subequations}
-%
-where the $\iota$ collectively represents the QNM labels $\{l,\, m,\, n\}$.
-
-Further expand the Kerr expression as:
-%
-\begin{subequations}
-\begin{align}
-\omega_{\iota} &= (1/M) \sum_{j = 0}^{N} \, \chi^{j} \omega^{(j)}_{k} \, \left( 1 + \gamma \delta \omega^{(j)}_{k} \right), \\
-\tau_{\iota}   &= M     \sum_{j = 0}^{N} \, \chi^{j} \tau^{(j)}_{k}   \, \left( 1 + \gamma \delta \tau^{(j)}_{k} \right),
-\end{align}
-\label{eq:kerr_expansion}
-\end{subequations}
-
-Also,
-%
-\begin{equation}
-\gamma = \frac{\kappa}{M_{\rm s}^{p}} = \frac{\kappa (1 + z)^{p}}{M^{p}}
-= \left[
-\frac{\ell c^2 (1 + z)}{G M}
-\right]^{p}
-\end{equation}
-%
-
-\subsection{The parametrized waveform model}
-\label{sec:review_pSEOB}
-
-\hs{AG will do this.}
-\hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
-explain how we modified it to include the {\sc Parspec} parametrisation.}
-
-\subsection{Overview of modified gravity theories}
+\section{Overview of modified gravity theories}
 \label{sec:review_theories}
@@
 
-\subsubsection{scalar-Gauss-Bonnet gravity}
+\subsection{scalar-Gauss-Bonnet gravity}
 %
@@
 
-\subsubsection{dynamical Chern-Simons}
+\subsection{dynamical Chern-Simons}
 
@@
 
-\subsubsection{Effective-field-theory of GR}
+\subsection{Effective-field-theory of GR}
 
@@
 % $\lamo$ and $\varepsilon_{i}$ are dimensionless constants.
+
+%%%%%%%%%%%%%%%%%
+\section{Methods}
+\label{sec:method}
+
+\subsection{The parametrized ringdown spin expansion coefficients formalism}
+\label{sec:review_parspec}
+
+\hs{HS will do this.}
+\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
+
+The formalism modifies the Kerr quasinormal mode frequency as
+%
+\begin{subequations}
+\begin{align}
+\omega_{\iota} &= \omega^{\rm K}_{\iota} \, (1 + \delta \omega_{\iota}), \\
+\tau_{\iota}   &= \tau^{\rm K}_{\iota}   \, (1 + \delta \tau_{\iota}),
+\end{align}
+\label{eq:general_deviation}
+\end{subequations}
+%
+where the $\iota$ collectively represents the QNM labels $\{l,\, m,\, n\}$.
+
+Further expand the Kerr expression as:
+%
+\begin{subequations}
+\begin{align}
+\omega_{\iota} &= (1/M) \sum_{j = 0}^{N} \, \chi^{j} \omega^{(j)}_{k} \, \left( 1 + \gamma \delta \omega^{(j)}_{k} \right), \\
+\tau_{\iota}   &= M     \sum_{j = 0}^{N} \, \chi^{j} \tau^{(j)}_{k}   \, \left( 1 + \gamma \delta \tau^{(j)}_{k} \right),
+\end{align}
+\label{eq:kerr_expansion}
+\end{subequations}
+
+Also,
+%
+\begin{equation}
+\gamma = \frac{\kappa}{M_{\rm s}^{p}} = \frac{\kappa (1 + z)^{p}}{M^{p}}
+= \left[
+\frac{\ell c^2 (1 + z)}{G M}
+\right]^{p}
+\end{equation}
+
+\subsection{The parametrized waveform model}
+\label{sec:review_pSEOB}
+
+\hs{AG will do this.}
+\hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
+explain how we modified it to include the {\sc Parspec} parametrisation.}
 

### 2022-01-20 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: added eft bh refs.

@@
 % \usepackage{txfonts}
+\usepackage{natbib}
 \usepackage{amssymb}
@@
 \newcommand{\lamo}{\lambda_{\rm o}}
-\newcommand{\acs}{\ell_{\rm CS}}
-\newcommand{\agb}{\ell_{\rm GB}}
 
@@
 
-We will consider several modified gravity theories as applications of the \pSEOB{}
-waveform model presented in Sec.~\ref{sec:review_pSEOB}.
+% We will consider several modified gravity theories as applications of the \pSEOB{}
+% waveform model presented in Sec.~\ref{sec:review_pSEOB}.
 %
-In the following, we briefly review which theories we consider, what are the
-currents observational constraints in each of them and what we known about the
-QNMs of black holes in each of them.
+We briefly review which theories we consider, what are the currents
+observational constraints in each of them and what we known about the QNMs of
+black holes in each of them.
 
@@
 %
-with strength set by the dimensionful coupling constant $\agb$ with dimensions
+with strength set by the dimensionful coupling constant $\ell_{\rm GB}$ with dimensions
 of length.
@@
 
-Black holes in these theories were studied in \dots
+Black holes in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} for the dimension-six EFT
+and in Refs.~\cite{Cardoso:2018ptl} for the dimension-eight EFT.
 
@@
 % \bibliographystyle{apsrev}
-\bibliography{paper_alt_theor_bounds}
+\bibliography{biblio}
 

### 2022-01-28 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: preliminary plot

@@
 
-\subsection{dynamical Chern-Simons}
+\subsection{dynamical Chern-Simons gravity}
 
@@
 \hline
-sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots & \cite{Pierini:2021jxd} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
-dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam} & $\alpha^{1/2}_{\rm CS} \ell \leqslant 8.5$~km~\cite{Silva:2020acr} & \dots \\
+sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
+dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr}   & \dots \\
 cEFTofGR & 4 & $-0.3680$ / $-0.5131$  & 1.9242 / 1.7000 & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
@@
 
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
+\caption{Preliminary plot.}
+\label{fig:dCS_bounds}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%
@@
 %
-We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihailov, and
+We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov, and
 Serguei~Ossokine for discussions.
@@
 We thank the computational resources provided by the AEI, specifically the
-{\sc Hypatia} cluster.
+{\sc Hypatia} cluster and Steffen Grunewald for assistance.
 %
@@
 % \bibliographystyle{apsrev}
-\bibliography{biblio}
+\bibliography{paper_alt_theor_bounds}
 

### 2022-02-02 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: updated figures with the latests samples

@@
 \begin{equation}
-\gamma = \frac{\kappa}{M_{\rm s}^{p}} = \frac{\kappa (1 + z)^{p}}{M^{p}}
+\gamma
+%
+= \frac{\ell^{p}}{M_{\rm s}^{p}}
+%
+% = \frac{\ell^{p} (1 + z)^{p}}{M^{p}}
+%
 = \left[
@@
 \right]^{p}
+\label{eq:def_gamma}
 \end{equation}
@@
 \includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
-\caption{Preliminary plot.}
+\caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
+The posterior shows that information was gained on this parameter relative to
+the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
+%
+The vertical lines represent two threshold for the validity of the theory as
+an EFT.
+%
+The dotted line (labelled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
+given by the median value of the secondary's mass $\epsilon \, (G m_2 / c^2)$.
+%
+The dot-dashed line (labelled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
+given by the median value of the remnant's mass $\epsilon \, (G M_{f} / c^2)$.
+%
+For both, we used $\epsilon = 0.5$.
+%
+If we take the latter as a lengthscale for the validity of dCS as an EFT, we
+have place upper bound on $\ell_{\rm CS} \leqslant 43.8$, within the
+approximation of our formalism.
+}
 \label{fig:dCS_bounds}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
+\caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
+The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
+in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
+}
+\label{fig:dCS_gamma_plot}
 \end{figure}

### 2022-02-06 papers/paper_alt_theor_bounds/pseob_review.tex
updated pseob revie

--- 2021-06-16 papers/intro_paper/intro_paper.tex
@@
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
-\usepackage{epsfig}
-\usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{bm}
-\usepackage{times}
-\usepackage{xspace}
-\usepackage[varg]{txfonts}
-\usepackage[normalem]{ulem} % To get strikethrough (\sout)
-\usepackage[colorlinks]{hyperref}
-\usepackage[caption=false]{subfig}
-\usepackage{booktabs}
-\usepackage{url}
-\usepackage{float}
-\usepackage[bottom]{footmisc}
-\usepackage{lineno}
-%\linenumbers
-\usepackage{makecell}
+In this section we describe the waveform model used in this paper to measure properties of the underlying GW signal.
+As in \cite{Brito:2018rfr,Ghosh:2021mrv}, we use an inspiral-merger-ringdown (IMR) BBH waveform model where the parameters describing the remnant object are left additionally free and estimated directly from the data.
 
-\definecolor{LinkColor}{rgb}{0.75, 0, 0}
-\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
-\definecolor{UrlColor}{rgb}{0, 0, 0.75}
-\hypersetup{linkcolor=LinkColor}
-\hypersetup{citecolor=CiteColor}
-\hypersetup{urlcolor=UrlColor}
-\usepackage{perpage}
-\MakePerPage{footnote}
-
-\newcommand{\paperone}{Paper~I\xspace}
-
-\newcommand{\h}{\mathpzc{h}}
-\newcommand{\Hhat}{\hat{\mathpzc{H}}}
-\newcommand{\B}{\mathpzc{B}}
-\newcommand{\hlm}{\mathpzc{h}_{\ell m}}
-\newcommand{\xilm}{\xi_{\ell m}}
-\newcommand{\Ylm}{{Y}^{-2}_{\ell m}}
-\newcommand{\Y}{{Y}^{-2}}
-\newcommand{\hc}{h_\times}
-\newcommand{\hp}{h_+}
-\newcommand{\Fc}{F_\times}
-\newcommand{\Fp}{F_+}
-\newcommand{\Mf}{M_f}
-\newcommand{\cA}{\mathpzc{A}}
-\newcommand{\lm}{_{\ell m}}
-\newcommand{\deff}{d_\mathrm{eff}}
-\newcommand{\rmi}{\mathrm{i}}
-\newcommand{\blambda}{\bm{\lambda}}
-\newcommand{\btheta}{\bm{\theta}}
-\newcommand{\bxi}{\bm{\xi}}
-\newcommand{\bxigr}{\bm{\xi}_{\text{GR}}}
-\newcommand{\bxingr}{\bm{\xi}_{\text{nGR}}}
-\newcommand{\bzeta}{\bm{\zeta}}
-\newcommand{\bs}[1]{\bm{\vec{S}_{#1}}}
-\newcommand{\Mo}{M_{\odot}}
-\newcommand{\FFe}{\mathrm{FF}_\mathrm{eff}}
-\newcommand{\FF}{\mathrm{FF}}
-\newcommand{\e}{\mathrm{e}}
-\newcommand{\rhoopt}{\rho_\mathrm{opt}}
-\newcommand{\rhosubopt}{\rho_\mathrm{subopt}}
-\newcommand{\fqnm}{f}
-\newcommand{\sigmaqnm}{\sigma}
-\newcommand{\n}{\mathbf{n}}
-\newcommand*{\skymapscale}{0.5}
-\newcommand*{\paramestscale}{0.455}
-\newcommand{\df}[1]{\delta f_{\text{#1}}}
-\newcommand{\dtau}[1]{\delta \tau_{\text{#1}}}
-\newcommand{\fngr}[1]{f_{\text{#1}}}
-\newcommand{\taungr}[1]{\tau_{\text{#1}}}
-\newcommand{\fgr}[1]{f ^{\text{GR}}_{\text{#1}}}
-\newcommand{\taugr}[1]{\tau ^{\text{GR}}_{\text{#1}}}
-\newcommand{\pSEOB}{\texttt{pSEOBNR}}
-\newcommand{\SEOB}{\texttt{SEOBNR}}
-
-\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
-\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}
-
-\begin{document}
-
-\title{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}
-
-\author{Abhirup Ghosh}
-\AEI
-\author{Richard Brito}
-\affiliation{Dipartimento di Fisica, ``Sapienza" Universit\`a di Roma $\&$ Sezione INFN Roma1, Piazzale Aldo Moro 5, 00185 Roma, Italia}
-\author{Alessandra Buonanno}
-\AEI
-\UMD
-
-\date{\today}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  The no-hair conjecture in General Relativity (GR) states that the
-  properties of an astrophysical Kerr black hole (BH) are completely described by its
-  mass and spin. As a consequence, the complex
-  quasi-normal-mode (QNM) frequencies of a binary--black-hole (BBH)
-  ringdown can be uniquely determined by the mass and spin of the
-  remnant object. Conversely, measurement of the QNM frequencies could
-  be an independent test of the no-hair conjecture. This paper extends to spinning BHs earlier work that proposed to
-  test the no-hair conjecture by measuring the complex QNM
-  frequencies of a BBH ringdown using parameterized inspiral-merger-ringdown waveforms in the effective-one-body formalism, 
-thereby taking full advantage of the entire signal power and removing dependency on the
-  predicted or estimated start time of the ringdown. Our method was used to analyze the
-  properties of the merger remnants for BBHs observed by
-  LIGO-Virgo in the first half of their third observing (O3a) run.
- After testing our method with GR and non-GR synthetic-signal injections in Gaussian noise, 
-we analyze, for the first time, two BBHs from the first (O1) and second (O2) LIGO-Virgo 
-  observing runs, and two additional BBHs from the O3a run. We then provide joint constraints with published results
-  from the O3a run. In the most agnostic and conservative scenario where we combine the information from different
-events using a hierarchical approach, we obtain, at $90\%$ credibility, that 
-the fractional deviations in the frequency (damping time) of the dominant QNM are 
-$\df{220}=0.03^{+0.10}_{-0.09}$ ($\dtau{220}=0.10^{+0.44}_{-0.39}$), respectively, an improvement of a factor of $\sim 4$ ($\sim 2$) 
-over the results obtained with our model in the LIGO-Virgo publication. The single-event most-stringent constraint to date continues to be 
-GW150914 for which we obtain $\df{220}=0.05^{+0.11}_{-0.07}$ and $\dtau{220}=0.07^{+0.26}_{-0.23}$.
-\end{abstract}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
-
-%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:intro}
-The LIGO Scientific Collaboration~\cite{lsc} and the Virgo
-Collaboration~\cite{Virgo} have recently announced their catalogue of
-gravitational-wave (GW) signals from the first
-half of the third observing run (O3a)~\cite{Abbott:2020niy}. Combined
-with the first and second observing-run catalogues~\cite{LIGOScientific:2018mvr}, the Advanced LIGO detectors at Hanford,
-Washington and Livingston, Louisiana~\cite{TheLIGOScientific:2014jea},
-and the Advanced Virgo detector in Cascina,
-Italy~\cite{TheVirgo:2014hva} have now detected $50$ GW
-events from the merger of compact objects like neutron stars and/or
-black holes (BHs). Alongside independent claims of
-detections~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq}, these results have firmly established the field of GW astronomy, five years after the first detection of a GW passing through Earth, GW150914~\cite{Abbott:2016blz}.
-
-The observation of GWs has had significant astrophysical and cosmological
-implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
-has also allowed us to probe fundamental
-physics and test predictions of Einstein's theory of General Relativity
-(GR) in the previously unexplored highly-dynamical, and strong field
-regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks}. In GR, a binary black hole (BBH) system is described by
-three distinct phases: an early \textit{inspiral}~\cite{Blanchet:2013haa}, where the two
-compact objects spiral in losing energy because of the emission of GWs, a \textit{merger}~\cite{Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv} marked by the
-formation of a common apparent horizon, and a \textit{ringdown}~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza,Detweiler:1980gk}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs) (i.e., damped oscillations with specific, discrete frequencies and decay times).
-
-The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin.
-One
-consequence of the no-hair conjecture is that the (complex) QNM
-frequencies of gravitational radiation emitted by a perturbed isolated
-BH are uniquely determined by its mass and spin. Hence
-a test of the no-hair conjecture would involve checking for
-consistency between estimates of mass and spin of the remnant object
-across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}.  Consistency of the late-time waveform with a single QNM is a test of the ringdown of
-a BBH coalescence, but not necessarily a test of the no-hair
-conjecture, which requires the measurement of (at least) two QNMs (BH
-spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Gossan:2011ha, Meidam:2014jpa,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}.
-An inconsistency would either
-indicate a non-BH nature of the remnant object, or an incompleteness
-of GR as the underlying theory of gravity.
-
-The LIGO-Virgo collaborations have released companion papers detailing their results
-of tests of GR for GW150914 \cite{TheLIGOScientific:2016src}, and for several GW events of
-the two transient catalogues (TC): GWTC-1 \cite{LIGOScientific:2018mvr,LIGOScientific:2019fpa}  and GWTC-2 \cite{Abbott:2020niy,Abbott:2020jks}.
-The results include tests of GW generation and source dynamics, where bounds are placed on
-parameterized deviations in the post-Newtonian (PN) coefficients describing
-the early inspiral, and
-phenomenological coefficients describing the intermediate (plunge) and
-merger regimes of coalescence~\cite{Arun:2006hn,Arun:2006yw,Agathos:2013upa,Abbott:2018lct}; tests of GW
-propagation, which assume a generalized dispersion relation and place
-upper bounds on the Compton wavelength and, consequently, the mass of
-the graviton~\cite{Abbott:2017vtc,Samajdar:2017mka}, and tests of the
-polarization of gravitational radiation using a
-multi--GW-detector network~\cite{Abbott:2017oio,Isi:2017fbj}. The GWTC-1/2 papers also
-check for consistency between different portions of the signal using estimates for the predicted mass and spin of the remnant
-object~\cite{Ghosh:2016xx,Ghosh:2017gfp,TheLIGOScientific:2016src}, and
-consistency of the residuals with detector noise~\cite{Ghonge:2020suv,LIGOScientific:2019fpa}. None of these tests report any
-departure from the predictions of GR.
-
-The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} also provided us with the first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
-coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}.
-The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.
-The consistency between the post-merger signal and the least damped QNM was first demonstrated in
-Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analyses~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}.
-This was later extended to include
-overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Abbott:2020jks}.  The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
-theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, the consistency of the merger frequency with predictions from NR simulations~\cite{Carullo:2018gah} or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.
-None of these tests have found evidence for non-BH nature of the remnant
-object (as described in GR) in LIGO-Virgo BBH observations.
-
-%Ground-based detectors, such as LIGO and Virgo, are most sensitive to stellar-mass BH binaries that form remnants with mass $\gtrsim 50 M_{\odot}$ and merge near the minimum of their sensitivity band ($\sim 100$ Hz).
-As a consequence, the remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving very little signal-to-noise ratio (SNR) in the post-merger signal.
-With current ground-based detectors, only a small fraction of BBH coalescences lead to a detectable post-merger GW signal and, even for these events, the signal-to-noise ratio (SNR) in the post-merger signal is, in most cases, only slightly above threshold for detection~\cite{LIGOScientific:2019fpa,Abbott:2020jks}.
-%
-This is particularly important, given that most of the tests mentioned above restrict the data to this post-merger signal which, while being agnostic to deviations in the pre-merger dynamics, significantly reduces parameter-estimation capabilities.
-Added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}).
-Defining such a time is particularly important in order to avoid possible systematic errors that may occur if one tries to extract the fundamental QNMs too early after merger, since the higher-order overtones dominate the ringdown signal closer to merger~\cite{Buonanno:2006ui,Giesler:2019uxc}.
-In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a free parameter to be estimated directly from the data.
-Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{pyRing} analysis in Ref.~\cite{Abbott:2020jks}).
-Uncertainties
-in estimates of the ringdown start-time, as well as an overall lack of
-SNR in the post-merger signal, given typical sensitivities of
-ground-based detectors, can result in significant statistical uncertainties in the measurement of some of the QNM properties.
-This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data.
-Hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.
-
-An independent approach to BH spectroscopy, based on the full-signal
-analysis, was introduced in Ref.~\cite{Brito:2018rfr}
-(henceforth referred to as \paperone). Unlike methods that focus only
-on the post-merger signal, it employs the
-complete inspiral-merger-ringdown
-(IMR) waveform to measure the complex QNM
-frequencies.
-In the current version, this method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies.
-This allows to access the full SNR of the signal, reducing
-measurement uncertainties. However, we note that this method can incorporate deviations from GR, notably from the (known) PN coefficients,  
-also during the long inspiral stage~\cite{Abbott:2018lct,
-LIGOScientific:2019fpa,Abbott:2020jks}, and can in principle incorporate deviations from GR, notably from the parameters calibrated to NR simulations,  
-in the late inspiral and plunge. Moreover, in this method, the definition of the
-ringdown start time is built into the merger-ringdown model and does not need to be
-either left as an additional free parameter or fixed using alternate
-definitions. While \paperone presented the method and tested it for non-spinning BBHs, here we extend the analysis to the more
-realistic astrophysical case in which BHs carry spin. Furthermore,
-the IMR waveform model used in this paper is more accurate than what employed in \paperone,
-because it contains higher-order corrections in PN theory and it was calibrated to a much larger set
-of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}. All astrophysical BHs are expected to be spinning,
-and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the
-source properties.
-
-The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
-waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
-complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
-several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
-we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
-the GWTC-2 events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
-our results and discuss future developments.
-
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\section{Waveform model and statistical strategy to measure quasi-normal modes}
-A GW signal from the (quasi-circular) coalescence of two BHs is
-completely described in GR by $15$ parameters,
-$\bxigr$. These can be grouped into the \emph{intrinsic} parameters:
-the (source) masses, $m_1, m_2$ and spins, $\bs1, \bs2$ of the component
-objects in the binary; and the
-\emph{extrinsic} parameters: a reference time $t_c$ and phase
-$\phi_c$, the sky position of the binary ($\alpha$,
-$\delta$), the luminosity distance, $d_L$, and the binary's orientation
-described through the inclination of the binary $\iota$ and its
-polarization $\psi$. We also introduce the total (source) mass $M = m_1+m_2$,
-and the (dimensionless) symmetric mass ratio $\nu = m_1m_2/M^2$.
-We also follow the convention $m_1 > m_2$, and hence the asymmetric mass ratio, $q = m_1/m_2 \geq1$.
-We also introduce the detector masses $m_{1\,\rm det}= (1+z)\,m_1$ and $m_{2 \,\rm det} = (1+z)\,m_2$,
-where $z$ is the redshift.
-
-Here, we focus on BHs with spins aligned or anti-aligned
-with the orbital angular momentum (henceforth, aligned-spin). In this case,
-the GW signal depends on $11$ parameters. We denote the
-aligned-spin (dimensionless) components as $\chi_{i} = |\vec{\bm{S}}_i|/m^2_i$, where $i=1,2$ for the two BHs.
-
-\subsection{Parameterized waveform model}\label{sec:model}
-
-As in \paperone, we use an IMR waveform model developed within the effective-one-body (EOB)
-formalism~\cite{Buonanno:1998gg,Buonanno:2000ef}. However, whereas \paperone was limited to non-spinning multipolar waveforms,
-here we use as our baseline model the aligned-spin multipolar waveform model
-developed in Ref.~\cite{Cotesta:2018fcv}. In addition to being
-calibrated to NR simulations, this model also uses information from BH
-perturbation theory for the merger and ringdown phases. Henceforth we
-will denote this model by $\SEOB$ for short~\footnote{In the LIGO Algorithm Library (LAL), this
-waveform model is called {\tt SEOBNRv4HM}.}.
+We use, as our baseline model, the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf},  henceforth referred to as \SEOB{} \footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.} in this paper.
+The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral.
+An accurate description of the merger is incorporated through calibration with NR simulations, as described in~\cite{Cotesta:2018fcv}, along with information for the merger and ringdown phases, from BH perturbation theory.
 
@@
 where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics where $(\ell,m)$ are the usual indices that describe the angular dependence of the spin-weighted spherical harmonics, with $\ell\geq 2$, $-\ell\leq m\leq \ell$.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv}.
+The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
 For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
@@
 
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
+In the $\SEOB$ model constructed in Ref.~\cite{Mihaylov:2021bpf}, the
 complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
@@
 NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) are defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
-values~\cite{Gossan:2011ha,Meidam:2014jpa}.
-
-Thus,
-\begin{subequations}
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-\end{subequations}
-
-The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
-\begin{subequations}
-\begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,,\\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,.
-\end{eqnarray}
-\end{subequations}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
-(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 
-soon after merger deviates from the one predicted by GR.
-
-\subsection{Bayesian parameter-estimation technique}
-\label{sec:method}
-
-The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$.
-One then proceeds to use the Bayes' theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
-%
-\begin{equation}
-P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
-\label{eq:Bayes_theorem}
-\end{equation}
-%
-where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function.
-The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$.
-In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$.
-The likelihood function can consequently be defined as:
-%
-\begin{equation}
-\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
-\label{eq:likelihood}
-\end{equation}
-%
-where $\langle . | . \rangle$ is the usual noise-weighted inner product:
-%
-\begin{equation}
-\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
-\label{eq:nwip}
-\end{equation}
-%
-The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation.
-The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector.
-We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
-GW detector at low-frequency.
-Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}.
-Namely, for all events and injections we consider, we set ${f_\mathrm{low}}=20$ Hz, except for the GW190521-like injection and the real GW190521 event for which use ${f_\mathrm{low}}=11$ Hz~\cite{Abbott:2020tfl,Abbott:2020mjq}.
-Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}.
-For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc,Speagle_2020} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.
-
-Given the full-dimensional posterior probability density function $P(\blambda | d, \mathcal{H})$, we can marginalize over the \emph{nuisance} parameters, to obtain the marginalized posterior probability density function over the QNM parameters $\bxingr$:
-
-\begin{equation}
-P(\bxingr | d, \mathcal{H})= \int P(\blambda | d, \mathcal{H}) d\bxigr\,.
-\end{equation}
-
-For most of the results discussed in this paper, we restrict ourselves
-to the $(\ell m) = (2,2)$ and/or $(3,3)$ modes. In those cases we assume $\bxingr = \{\df{220},\dtau{220}\}$ and/or $
-\{\df{330},\dtau{330}\}$, and fix all the other $(\ell m)$ modes to their GR predictions (i.e., $\delta f_{\ell m 0} = \delta
-\tau_{\ell m 0} = 0$). This is because, for most of the high-mass BH
-events that we find most appropriate for this test, the LIGO-Virgo
-observations are consistent with nearly--equal-mass face-on/off BBHs
-for which power in the subdominant modes is not enough to
-attempt to measure more than one QNM complex frequency.
-
-Lastly, throughout our analysis, we assume uniform priors on our non-GR QNM
-parameters, $(\delta f_{\ell m 0},\delta \tau_{\ell m 0})$. We note that
-since the priors on $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
-derived through NR--fits, from the corresponding priors on the initial
-masses and spins, this leads to a non-trivial prior on the final
-reconstructed frequency and damping time, $( f_{\ell m 0},\tau_{\ell m
-  0})$. Also, given the definition of the damping time in
-Sec.~\ref{sec:model}, we note that $\delta \tau_{\ell m 0} = -1$ leads
-to the imaginary part of the QNM complex frequency going to infinity. We avoid
-this by restricting the minimum of the prior on $\delta \tau_{\ell m
-  0}$ to be greater than $-1$.
-
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\section{Synthetic-signal injection study}
-\label{sec:results}
-\subsection{Simulations using GR signals in Gaussian noise} \label{ssec:gr_signal}
-
-We now demonstrate our method using synthetic-signal injections describing GWs
-from BBHs in GR. We employ coloured Gaussian noise with PSDs for LIGO and
-Virgo detectors during the fourth observing (O4) run~\cite{Abbott:2020qfu}, which 
-is expected to start in the second half of 2022~\cite{AdvLIGOPSD,TheVirgo:2014hva}.
-For the mock BBH signals, we choose parameters similar to two specific GW events, GW150914~\cite{Abbott:2016blz} and
-GW190521~\cite{Abbott:2020tfl}. We list them in Table~\ref{tab:injection_values}.
-These two binary systems are representative of the kind of systems for which
-the QNM measurement is most suitable, notably high-mass BBH events which are loud enough that the
-pre- and post-merger SNRs return reliable parameter-estimation results.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for Injections
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ c|c|c|c|c|c|c|c|c }
-
-Injection &  Network & \makecell{$m_{\rm 1\,det}$ \\$(\Mo)$} &  \makecell{$m_{\rm 2\,det}$ \\ $(\Mo)$} & $\chi_{1}$ & $\chi_{2}$ & $\rho_\text{IMR}$ & $\rho_\text{insp}$ & $\rho_\text{postinsp}$ \\
- \hline
- GW150914-like & HL &39 & 31 & 0.0 & 0.0 & 25 & 22 & 12 \\
- GW190521-like & HL & 150 & 120 & 0.02 & -0.39 & 20 & 8 & 18 \\
- SXS:BBH:0166 & HLV &72 & 12  & 0.0 & 0.0 & 71 & 58 & 41 \\
-
-\end{tabular}
-\caption{Parameters of the synthetic-signal injections, chosen to be similar to the actual GW events indicated in the first column (first two rows).
-The parameters $(m_{\rm 1 \,det}, m_{\rm 2 \,det})$ are the detector-frame masses of the primary and secondary BHs, respectively.
-The third row indicates the parameters of the SXS BBH waveform used in Sec.~\ref{ssec:nohairtheorem}.
-The second column refers to the detector-network used, with H,L,V, referring to LIGO-Hanford, LIGO-Livingston and Virgo, respectively.
-The quantities $\rho_\text{IMR}$, $\rho_\text{insp}$ and $\rho_\text{postinsp}$ are the SNR of the full IMR signal, SNR upto a certain cutoff frequency, and SNR after the cutoff frequency respectively.
-In each case, the cutoff frequency is assumed to be the frequency at the innermost circular stable orbit (ISCO) corresponding to the remnant Kerr BH.}
-\label{tab:injection_values}
-\end{center}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[hbt]
-\begin{center}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_f220_tau220.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p0_f220_tau220.png}
-        \caption{Posterior probability
-          distribution on the fractional deviations in the frequency
-          and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$
-          (left panels) and the reconstructed quantities,
-          $(\fngr{220}, \taungr{220})$ (right panels) for GR
-          injections ($\SEOB$) with initial parameters similar to GW150914 (top
-          panels) and GW190521 (bottom panels)
-          (see Table~\ref{tab:injection_values}). The 2D contour marks the
-          90\% credible region, while the dashed lines on the 1D
-          marginalized distributions mark the 90\% credible
-          levels. The black vertical and horizontal lines mark the
-          injection values.}
-        \label{fig:simulated_signal_GR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To avoid possible systematic biases in our parameter-estimation analysis
-due to error in waveform modeling, we use the GR version of the same waveform,
-$\SEOB$ (i.e., without allowing for deviations in the QNM parameters) to
-simulate our GW signal. And to avoid systematic biases due to noise,
-we use an averaged (zero-noise) realization of the noise~\footnote{A detailed
-study on noise systematics for one of the GW events is presented in
-Appendix~\ref{sec:noise_systematics}.}.  Since mearly--equal-mass binaries like GW150914 and
-GW190521 observed at moderately high SNRs are not expected to have a
-loud ringdown signal, we restrict ourselves to estimating the
-frequency and damping time of only one QNM $(\ell m) = (2,2)$ (i.e.,
-$\{\df{220},\dtau{220}\}$), while fixing the other QNM frequencies to
-their GR values.
-
-We find, as one might expect, that the posterior distribution on the
-parameters describing fractional deviations in the frequency and
-damping time are consistent with zero (left panels of
-Fig.~\ref{fig:simulated_signal_GR}). One can then convert these
-fractional quantities into absolute quantities using the relations
-given in Eqs.~(\ref{eq:nongr_freqs_a}) and ~(\ref{eq:nongr_freqs_b}), and
-construct posterior distributions on these effective quantities,
-$(\fngr{220}, \taungr{220})$ (right panels of
-Fig.~\ref{fig:simulated_signal_GR}). In each of these cases, the recovered
-two-dimensional posteriors are consistent with the GR predictions
-(black dashed lines).
-
-\subsection{Simulations using non-GR signals in Gaussian noise} \label{ssec:ngr_signal}
-
-To demonstrate the robustness of the method in detecting possible
-deviations from GR, we inject synthetic GW signals which are identical
-to the corresponding GR prediction up to merger, and differ in their
-post-merger description. We again choose binary-parameters similar to
-GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but set
-$\df{220} = \dtau{220} = 0.1 $.  In other words, we assume that the
-frequency and damping time of our non-GR signal is 10\% more than the
-corresponding GR prediction, although the pre-merger signal is
-identical to GR. In Fig.~\ref{fig:nongr_waveform} we show this non-GR
-waveform, \texttt{pSEOBNR} with respect to the original GR template,
-\texttt{SEOBNR}. We see that the waveforms are identical in amplitude
-and instanteneous frequency upto the merger (lower panel) , beyond
-which the red (GR template) and blue (non-GR template) differ. We
-summarize the results of the Bayesian analysis in
-Fig.~\ref{fig:simulated_signal_nonGR} where we show the posterior
-probability distributions for $(\df{220}, \dtau{220})$, or
-equivalently $(\fngr{220}, \taungr{220})$. We find that they are
-consistent with the corresponding values of the injection parameters,
-indicated by the black dashed lines.  We also note that at the
-  SNRs we consider, since statistical uncertainties dominate
-  systematic biases, the measurement excludes, at the 90\% credible
-  level, the GR prediction of the frequency ($\df{220}=0$), but
-  includes the prediction of the damping time
-  ($\dtau{220}=0$). However, with louder events, one would expect
-  these measurement errors to shrink and the $\taungr{220}$
-  measurement to be inconsistent with the GR prediction, as well.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-        \includegraphics[width=0.5\textwidth]{figures/modGR_waveforms_amplitudephase.png}
-        \caption{Top panel: The `+'--polarization of the gravitational waveform $h_+(t)$ from a GW150914-like event where the post-merger is described by GR (i.e., $\df{220} = \dtau{220} = 0$), and where the merger-ringdown is modified (i.e., $\df{220} = \dtau{220} = 0.1$).
-Bottom panel: Comparison of the evolution of the amplitude, $\tilde{h}(t)$ (left) and instantaneous frequency, $f(t)$ (right) for the GR and non-GR signal.}
-        \label{fig:nongr_waveform}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Simulated siganl: non-GR
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-\begin{center}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_deltaf220_deltatau220.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p1_gr_ngr_fngrtaungr.png}
-        \caption{Posterior probability distribution on the fractional deviations in the frequency and damping time of the $(2,2)$ QNM, $(\df{220},\dtau{220})$ (left panels) and the reconstructed quantities, $(\fngr{220}, \taungr{220})$ (right panels) for non-GR injections ($\pSEOB$) with parameters of GW150914-like (top panels) and GW190521-like (bottom panels) as given in Table~\ref{tab:injection_values}.
-The non-GR signal has a deviation, $\df{220} = \dtau{220} = 0.1$.
-The 2D contour marks the 90\% credible region, while the dashed lines on the 1D marginalized distributions mark the 90\% credible levels.
-The black vertical and horizontal lines mark the injection values.
-In the right panels, we additionally show measurements using a GR ($\SEOB$) waveform, for the
-GW150914-like (upper panel) and GW190521-like (lower panel) injections. The measurements with $\SEOB$ waveforms are visibly biased.}
-        \label{fig:simulated_signal_nonGR}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% GW150914-like signal with different deviations: GR vs nonGR recovery
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}%[h!]
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_m1m2.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_a1za2z.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_fgrtaugr.png}
-        \includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_gr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p0_0p1_0p5_ngr_Mfaf.png}
-         \caption{Comparison of a GW150914-like injection's parameters when signals with zero, 10\% and 50\% deviations ($\df{220} = \dtau{220} = 0, 0.1, 0.5$) are recovered using a GR ($\SEOB$) (left panels) or a non-GR ($\pSEOB$) (right panels) waveform model.
-The panels (from top to bottom) show the 2D posteriors (with 90\% credible levels) and corresponding marginalised 1D posteriors (with 90\% credible levels) in (detector-frame) masses (first row), dimensionless spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f$, $\chi_f$) (fourth row) from the frequency and damping time.
-In each case, the injection values are indicated by the black dashed lines.
-In the lowermost panel, the injection values of the final mass and spin, correspond to the injection with no deviations.
-The $\df{220} = \dtau{220} = 0.1$ signal is identical to the results shown in Fig.~\ref{fig:simulated_signal_nonGR}.}
-        \label{fig:gr_ngr_comparison}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We additionally investigate the effects of erroneously assuming that
-an underlying non-GR signal can be well-described by a GR one. We do
-this by estimating the parameters of our non-GR signals using the GR
-waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
-resulting one- and two-dimensional posteriors are shown in the right
-panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
-GW150914-like (top) and GW190521-like (bottom) signals
-respectively. For both signals, we find the 2D $\SEOB$ estimates are
-markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
-this impact on the estimation of the GR parameters $\bxigr$ by changing the
-magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
-to a GW150914-like event, and for comparison, add a synthetic signal
-with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
-10\% non-GR signal and a signal with no deviation (essentially GR)
-mentioned above. The left (right) panels show the
-posterior probability distributions of the three signals using the GR,
-$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
-note is the $\SEOB$ recoveries yield biased estimates when the
-underlying signal is non-GR, while the $\pSEOB$ recoveries do
-not. Furthermore, as we increase the deviations, while the $\SEOB$
-recoveries expectedly get more biased, the $\pSEOB$ measurements are
-robust in consistently recovering the injected value. This gives us 
-confidence that the $\pSEOB$ model can accurately measure QNM 
-properties without biasing measurements of inspiral quantities, like masses and spins. 
-As we increase the deviation, the remnant object rings down at a higher frequency and damping time.
-The resulting $\pSEOB$ signal is longer than the GR ($\SEOB$) prediction.
-When we try to fit the $\SEOB$ model to this signal (left column of Fig.~\ref{fig:gr_ngr_comparison}), the template tries to fit parameters appropriate for a longer signal, i.e., smaller masses and spins.
-Hence, with increasing deviations, the recovered masses and spins have a tendency to shift towards lower values.
-To compute the samples of the final mass and spin in the last row, we start from the samples
-of the complex QNM frequencies $(\fngr{220}, \taungr{220})$, which are obtained from the 
-fractional deviation samples $(\df{220},\dtau{220})$ and the GR-quantities
-$(\fgr{220},\taugr{220})$ using Eqs.~(\ref{eq:nongr_freqs_a}) and Eq.~(\ref{eq:nongr_freqs_b}),
-and then invert them using the fitting formula in Ref.~\cite{Berti:2005ys}.
-The three BBH signals, $\df{220} = \dtau{220} = 0, 0.1, 0.5$, correspond to
-three unique sets of values for $(M_f,\chi_f)$. These predicted values are correctly 
-recovered by the $\pSEOB$ waveform (bottom-right plot in Fig.~\ref{fig:gr_ngr_comparison}),
-leading to three distinct and disjointed 2D posteriors on $(M_f,\chi_f)$, unlike the $\SEOB$
-analysis (to reduce clutter in the plot, we just plot the injection values for $\df{220} = \dtau{220} = 0$).
-
-\subsection{Test of the no-hair conjecture}\label{ssec:nohairtheorem}
-
-Finally, we provide a simple demonstration of a test of the no-hair
-theorem using our model. As described in the introduction, any test of
-the no-hair theorem of BHs would need to involve independent
-measurements of (at least) two different QNMs.
-
-Here, we use an NR GW signal from the SXS catalog~\cite{Mroue:2013xna}
-corresponding to a non-spinning BBH with mass-ratio $q=6$ (SXS:BBH:0166) and 
-total mass $M=84 \Mo$ (see Table~\ref{tab:injection_values}).
-We choose an asymmetric system to increase the SNR in the higher modes.
-We also choose the distance and orientation of the binary
-such that the total SNR in the three-detector network of LIGO Hanford, Livingston and
-Virgo, is {$\sim$ 70}. Based on the LIGO-Virgo observations during the first three observing runs, 
-such asymmetric and loud signals are no longer just a theoretical
-prediction, but quite plausible during O4. Using this
-signal, we attempt to measure both the $(2,2)$ and
-$(3,3)$ QNMs. For this injected signal the SNR in
-other sub-dominant modes is too low to be able to measure them.
-
-We summarize our results in Fig.~\ref{fig:nohair_sxs}.  Given the
-injection parameters, the predicted values of the $(2, 2)$ and
-$(3, 3)$ frequency and damping time are {(169.45 Hz, 4.68
-  ms)} and {(271.21 Hz, 4.50 ms)} respectively. The left panel
-of Fig.~\ref{fig:nohair_sxs} shows that the 2D posteriors
-on the $(2, 2)$ and $(3, 3)$ QNMs are consistent with the
-predictions for a BBH merger in GR, indicated by the black plus sign.
-Using fitting formulae provided in Ref.~\cite{Berti:2005ys}, specifically,
-Eq.~(2.1), Eq.~(E1) and Eq.~(E3) and Tables VIII and IX for the fitting coefficients,
-we infer the 2D posterior probability distribution on the
-final mass and spin as predicted independently by the $(2, 2)$ (blue) and $(3, 3)$ (red)
-QNMs in the right panel of Fig.~\ref{fig:nohair_sxs}. The two
-independent estimates are consistent with each other and correspond to
-a unique mass and spin for the remnant BH {(83.08 $\Mo$, 0.37)}
-indicated by the plus sign. As a consequence, this may be considered
-as a test of the no-hair conjecture. For most of the events observed
-so far, the power in the $(3, 3)$ has not been sufficient to
-measure it along with the $(2, 2)$. However, it might also be possible to combine information from
-multiple observation over the coming few years to obtain meaningful
-constraints on the $(3, 3)$ and other sub-dominant QNMs~\cite{Gossan:2011ha,Meidam:2014jpa,Yang:2017zxs}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-        \includegraphics[width=0.5\textwidth]{figures/nohair_sxs_0166.png}
-        \caption{Posterior probability distribution on the frequency and damping time of the $(2, 2)$ and $(3, 3)$ QNM (left panel), and the final mass and spin inferred from the complex frequencies (right panel), when a NR signal with parameters $q=6$,  $M=84 \Mo$ and SNR $=75$ is injected in Gaussian noise and recovered with the $\pSEOB$ waveform model.
-The plus signs mark the GR predictions.}
-        \label{fig:nohair_sxs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\section{Constraints on QNM frequencies using LIGO-Virgo data}
-\label{sec:results_lvc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% O1-O2 events
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-        \includegraphics[width=0.5\textwidth]{figures/rin_pseob_results_v2.pdf}\includegraphics[width=0.3\textwidth]{figures/rin_all_events_bounds.pdf}
-        \caption{\emph{Left panel}:The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2, 2)$ QNM, $(\df{220},\dtau{220})$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal.
-The solid purple curve marks the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves.
-The joint constraints on $(\df{220},\dtau{220})$ obtained multiplying the likelihoods from individual events is given by the filled grey contours, while the hierarchical method of combination yields the black dot dashed curves only shown in the 1D posteriors plots).
-\emph{Right panel}: 90\% credible interval on the one-dimensional marginalised posteriors on $\delta \sigma_i=(\df{220},\dtau{220})$, colored by the median redshifted total mass $(1 + z)M$, inferred assuming GR.
-Filled gray (unfilled black) triangles mark the constraints obtained when all the events are combined by multiplying likelihoods (hierarchically).
-The purple square marker indicates constraints from the single most-prominent event, GW150914.}
-        \label{fig:o1o2_events}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The LIGO-Virgo Collaboration recently released their testing GR
-catalogue containing results for events observed
-during O3a~\cite{Abbott:2020jks}.
-For the test that we here present, the results shown in Ref.~\cite{Abbott:2020jks} only include events which pass a threshold for the median detector-frame total mass $\geq 90 \Mo$ and SNRs in the pre- and
-post-merger regions $\geq 8$~\footnote{The pre- and post-merger regions of the signal are identified from the signal's power before and after the signal reaches the peak's amplitude, which is determined from the maximum of the likelihood function obtained with the parameter-estimation analysis.
-The SNR values are listed in Table IV of Ref.~\cite{Abbott:2020jks}}.
-%
-The SNR threshold ensures that the signal contains sufficient
-information in both the inspiral and merger stages to break the
-degeneracy between the binary's total mass and the non-GR deviations
-$(\df{220}, \dtau{220})$.
-Such strong degeneracy arises from the fact that the complex QNM frequencies are inversely proportional to the total mass~\cite{Berti:2005ys} such that one can always obtain the same fundamental frequency or damping time by appropriately increasing (or decreasing) the total mass and the deviation parameters in the same direction.
-This degeneracy is especially important in
-low-SNR events with negligible higher-modes and for which only the
-post-merger is detectable, rendering the measurement of $(\df{220},
-\dtau{220})$ impossible for those cases  (see Appendix~\ref{sec:correlation} for more details). On the other hand the
-total mass threshold $\geq 90 \Mo$ was employed due to the fact that
-this analysis is computationally expensive, and also because we
-expected these events to be the most promising for ringdown
-studies. However, since the SNR threshold alone should be sufficient
-for the analysis, for this paper we run the test on all the events
-listed in Ref.~\cite{Abbott:2020jks} that have SNRs in the pre- and
-post-merger regions $\geq 8$, without imposing any mass threshold.
-
-Given the above we add the signals  GW190630$\_$185205 and GW190828$\_$063405, to the list of GW events considered in Ref.~\cite{Abbott:2020jks}. Furthermore, for the first time, 
-we apply our method to measure the QNMs to GW events from O1 and O2, notably GW150914 and GW170104. The other high-mass events from O1 and O2, GW170729, GW170809,
-GW170814, GW170818 and GW170823 do not have an SNR $\geq 8$ in the
-merger-ringdown signal. The list of the signals for which we run the analysis is given in Table~\ref{tab:qnm_o1o2_results}.
-
-For all the relevant signals, we show the posterior distributions
-$(\df{220}, \dtau{220})$ in the left panel of
-Fig.~\ref{fig:o1o2_events} and also provide the reconstructed QNM
-parameters, $(\fngr{220}, \taungr{220})$ in
-Table~\ref{tab:qnm_o1o2_results}. In the right panel of
-Fig.~\ref{fig:o1o2_events} we also provide a summary of the 90\%
-credible intervals on the 1D marginalized posteriors. We highlight the
-dependence of the constraints on the total mass of the
-system. In general, the tightest bounds are set by the 
-most massive systems, as they tend to have larger post-merger SNR. We
-find a similar trend in the right panel of Fig.~\ref{fig:o1o2_events}.
-
-Among all the GW signals detected so far, GW150914 (solid curve in
-Fig.~\ref{fig:o1o2_events}) is unique in its loudness, leading to the
-first, and to date, best attempt in measuring the QNM
-frequencies~\cite{TheLIGOScientific:2016src,Brito:2018rfr,Carullo:2019flw,Isi:2019aib}. Within
-90\% credibility we obtain from GW150914:
-%
-\begin{equation}\label{GW150914_delta}
-\df{220}=0.05^{+0.11}_{-0.07}\,\quad \dtau{220}=0.07^{+0.26}_{-0.23}\,.
-\end{equation}
-
-Stronger constraints can be obtained by combining information from all the events~\cite{Abbott:2020jks}.
-If we assume that the fractional deviations $(\df{220},\dtau{220})$ take the same values in multiple events, we can assume
-the posterior of one event to be the prior for the next, and obtain a
-joint posterior probability distribution. For $N$ observations, where
-$P(\df{220}, \dtau{220} | d_j)$ is the posterior for the $j$-th
-observation corresponding to the data set $d_j$, $j=1,\dots,N$, the joint
-posterior is given by:
-%
-\begin{equation}
-P(\df{220}, \dtau{220} | \{d_j\}) = P(\df{220}, \dtau{220}) \prod _{j=1}^N \frac{P(\df{220}, \dtau{220} | d_j) }{P(\df{220}, \dtau{220})}\,,
-\end{equation}
-%
-where $P(\df{220}, \dtau{220})$ is the prior on $(\df{220},
-\dtau{220})$. However, since here we assume the prior on $(\df{220},
-\dtau{220})$ to be flat (or uniform), the joint posterior is equal to
-the joint likelihood.
-We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as, the corresponding 1D marginalized distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}.
-From the joint likelihood we obtain within 90\% credibility:
-%
-\begin{equation}
-\df{220}=0.02^{+0.04}_{-0.04}\,,\quad \dtau{220}=0.10^{+0.14}_{-0.14}\,.
-\end{equation}
-%
-
-However, in most non-GR theories, the deviations parameters $(\df{220},\dtau{220})$ depend in general on the source's parameters, so if GR were to be wrong, one should expect their value to vary across the GW signals observed by LIGO and Virgo.
-As described in Ref.~\cite{Abbott:2020jks}, we can relax the assumption of a constant deviation across all events by using the hierarchical inference technique originally proposed in Refs.~\cite{Zimmerman:2019wzo,Isi:2019asy}.
-The general idea behind this technique is to assume that the non-GR parameters $(\df{220},\dtau{220})$ are drawn from a common underlying distribution, whose properties can be inferred from the population of events.
-Following~\cite{Zimmerman:2019wzo,Isi:2019asy,Abbott:2020jks} we model the population distribution with a Gaussian  $\mathcal{N}(\mu,\sigma)$ of unknown mean $\mu$ and standard deviation $\sigma$.
-Under those assumptions, the goal is then to directly measure a posterior distribution $P(\mu, \sigma |  \{d_j\}) $ for $\mu$ and $\sigma$ from a joint analysis of all the GW events.
-If GR is correct, then this posterior should be consistent with $\mu=0$ and $\sigma=0$.
-From Bayes' theorem it follows that~\cite{Isi:2019asy}:
-%
-\begin{equation}
-P(\mu, \sigma |  \{d_j\}) \propto P(\mu,\sigma)\prod _{j=1}^N P(d_j |\, \mu, \sigma) \,,
-\end{equation}
-%
-where $P(\mu,\sigma)$ is the prior (also known as hyperprior) on ($\mu,\sigma$), and $P(d_j | \mu, \sigma) $ can be written in terms of the individual likelihoods of a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}
-%
-\begin{equation}
-P(d_j | \mu, \sigma) = \int P(d_j |\, \xi_{\text{nGR}})  P(\xi_{\text{nGR}} |\, \mu, \sigma) \,d\xi_{\text{nGR}} \,.
-\end{equation}
-%
-Here $P(\xi_{\text{nGR}} | \,\mu, \sigma) = \mathcal{N}(\mu,\sigma)$ by construction and $P(d_j |\, \xi_{\text{nGR}})$ is the likelihood for the parameter $\xi_{\text{nGR}}$ for a given event $d_j$ that is computed from the standard parameter estimation analysis.
-After obtaining $P(\mu, \sigma |  \{d_j\})$, we can then infer a population distribution for a given non-GR parameter $\xi_{\text{nGR}}$ using~\cite{Isi:2019asy}:
-%
-\begin{equation}\label{hier_combine}
-P(\xi_{\text{nGR}} | \{d_j\}) = \int P(\xi_{\text{nGR}} |\, \mu, \sigma)\,P(\mu, \sigma |  \{d_j\})\,d\mu\,d\sigma \,.
-\end{equation}
-%
-Notice that, if we fix $\sigma=0$, this approach is equivalent to assume that all events share the same non-GR parameter $\xi_{\text{nGR}} =\mu$ and Eq.~\eqref{hier_combine} reduces to the joint likelihood~\cite{Zimmerman:2019wzo}.
-In practice, we use the \texttt{stan}-based code~\cite{stan} developed and used in Refs.~\cite{Isi:2019asy,Abbott:2020jks} to obtain $P(\mu, \sigma |  \{d_j\}) $ and compute $P(\xi_{\text{nGR}} | \{d_j\})$.
-We note that the current implementation of this analysis, as originally defined in~\cite{Isi:2019asy}, is only defined for 1D posteriors, therefore below we only show 1D posteriors for the hierarchical analysis.
-
-The posteriors for $\df{220}$ and $ \dtau{220}$ obtained with this technique are shown in Fig.~\ref{fig:o1o2_events} (dash-dotted curves) with corresponding median and 90\% credible interval given by:
-%
-\begin{equation}
-\df{220}=0.03^{+0.10}_{-0.09}\,,\quad \dtau{220}=0.10^{+0.44}_{-0.39}\,.
-\end{equation}
-Compared to Ref.~\cite{Abbott:2020jks} these constraints are almost a factor $\sim 4$ more stringent for $\df{220}$ and a factor $\sim 2$ for $\dtau{220}$.
-Similar improvements hold for the hyperparameters: $\df{220}\,(\mu=0.03^{+0.06}_{-0.05},\,\sigma<0.09)$ and $\dtau{220}\,(\mu=0.11^{+0.21}_{-0.19},\,\sigma<0.39)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Table for LVC values
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}
-
-\begin{tabular}{l|c|c|c|c|c|c}
-\toprule
-Event & $\fngr{220}$ (Hz) & $\taungr{220}$ (ms) & $(1+z)M_f/\Mo$ & $\chi_f$ & $(1+z)M_{\text{f}}^{\rm IMR}/\Mo$ & $\chi_{\text{f}}^{\rm IMR}$ \\[0.075cm]
-\midrule
-\hline
-
-GW150914 &
-$257.6^{+17.0}_{-12.8}$ &
-$4.49^{+1.09}_{-0.95}$ &
-$71.0^{+8.7}_{-10.3}$ &
-$0.77^{+0.09}_{-0.18}$ &
-$67.3^{+2.7}_{-2.6}$ &
-$0.67^{+0.03}_{-0.04}$
-\\[0.075cm]
-
-GW170104 &
-$291.4^{+14.7}_{-30.1}$ &
-$5.53^{+3.47}_{-2.40}$ &
-$73.8^{+11.1}_{-19.8}$ &
-$0.89^{+0.07}_{-0.36}$ &
-$56.9^{+3.0}_{-3.0}$ &
-$0.65^{+0.05}_{-0.07}$
-\\[0.075cm]
-
-GW190519\_153544 &
-$123.6^{+11.9}_{-13.0}$ &
-$10.33^{+3.56}_{-3.07}$ &
-$155.5^{+24.0}_{-29.9}$ &
-$0.81^{+0.10}_{-0.28}$ &
-$144.1^{+14.5}_{-16.2}$ &
-$0.78^{+0.08}_{-0.14}$
-\\[0.075cm]
-
-GW190521\_074359 &
-$204.6^{+14.6}_{-11.7}$ &
-$5.32^{+1.48}_{-1.21}$ &
-$86.4^{+12.2}_{-14.3}$ &
-$0.73^{+0.12}_{-0.26}$ &
-$87.1^{+3.3}_{-3.8}$ &
-$0.70^{+0.03}_{-0.05}$
-\\[0.075cm]
-
-GW190630\_185205 &
-$247.8^{+31.8}_{-52.8}$ &
-$3.87^{+2.37}_{-1.80}$ &
-$65.6^{+18.8}_{-41.5}$ &
-$0.62^{+0.27}_{-0.62}$ &
-$66.2^{+4.0}_{-3.2}$ &
-$0.70^{+0.05}_{-0.08}$
-\\[0.075cm]
-
-GW190828\_063405 &
-$257.8^{+201.3}_{-27.8}$ &
-$4.23^{+4.17}_{-1.92}$ &
-$67.4^{+25.7}_{-30.0}$ &
-$0.76^{+0.20}_{-0.73}$ &
-$75.8^{+5.0}_{-5.0}$ &
-$0.74^{+0.04}_{-0.06}$
-\\[0.075cm]
-
-GW190910\_112807 &
-$174.2^{+11.7}_{-7.5}$ &
-$9.52^{+3.13}_{-2.68}$ &
-$123.5^{+14.7}_{-18.1}$ &
-$0.90^{+0.05}_{-0.11}$ &
-$94.9^{+7.6}_{-8.6}$ &
-$0.72^{+0.08}_{-0.04}$
-\\[0.075cm]
-
-\bottomrule
-\end{tabular}
-\caption{The median and symmetric 90\% credible intervals of the remnant properties.
-The first two columns represent the frequency and damping time of the $(2,2)$ QNM measured using the $\pSEOB$ model.
-The next two columns are the mass and spin of the remnant object estimated from the complex QNM frequencies by inverting the fitting formula in~\cite{Berti:2005ys}.
-The last two columns represent final mass and spin estimates predicted using NR fitting formulae from a $\SEOB$ parameter estimation.}
-\label{tab:qnm_o1o2_results}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
-We have built a parameterized IMR waveform model, $\pSEOB$, that can 
-measure the QNM complex frequencies of the remnant object formed through 
-the merger of BHs with aligned or antialigned spins, thus extending  
-previous work, which was limited to non-spinning BHs~\cite{Brito:2018rfr}. 
-The $\pSEOB$ model was recently used to infer the QNMs of some of the 
-BBH's remnants detected by LIGO and Virgo during O3a~\cite{Abbott:2020jks}.
-
-After testing our method to infer the QNM frequencies with GR and non-GR synthetic-signal 
-injections in Gaussian noise, we have applied it to LIGO and Virgo real data. 
-We have analyzed GW events in O1, O2 and O3a (a total of 4 new events) that were not examined in Ref.~\cite{Abbott:2020jks} 
-with the $\pSEOB$ model (see Table~\ref{tab:qnm_o1o2_results}). After combining our new 
-results with the other GW events in O3a investigated with our method~\cite{Abbott:2020jks}, 
-we have obtained more stringent bounds on the dominant (or least-damped) QNM $(\ell=2,m=2)$.
-
-More specifically, as expected, the single GW event providing the best constraint
-on the least-damped QNM to date continues to be GW150914 $(\df{220}=0.05^{+0.11}_{-0.07}, 
-\dtau{220}=0.07^{+0.26}_{-0.23})$, although the bounds on 
-$\dtau{220}$ from GW150914 are comparable to GW190521\_074359, 
-the second-most precisely measured event in our list.
-In addition, in the most agnostic and
-conservative scenario where we combine the information from different
-events using a hierarchical approach~\cite{Zimmerman:2019wzo,Isi:2019asy}, we obtain 
-at $90\%$ credibility $(\df{220}=0.03^{+0.10}_{-0.09}, \dtau{220}=0.10^{+0.44}_{-0.39})$. Thus, 
-our results constrain the frequency (decay time) of the least damped QNM to be within $\sim
-10\%$ ($\sim 40\%$) of the GR prediction --- an improvement of a factor of $\sim 4$ ($\sim 2$) 
-over the results obtained with the $\pSEOB$ model in Ref.~\cite{Abbott:2020jks}.
-
-Furthermore, when assuming that the deviations from GR do not vary appreciably over the GW events 
-that we have analyzed, and combine the likelihood functions, we have obtained the most stringent bounds  
-on the dominant QNM $(\df{220}=0.02^{+0.04}_{-0.04}, \dtau{220}=0.10^{+0.14}_{-0.14})$. Those 
-constraints are compatible, but slightly better (especially for the decay time) than the ones recently reported in Ref.~\cite{Carullo:2021dui} 
-(see first row in Table II therein), where QNM frequencies were inferred using only the post-merger part of 
-the signal. We note that Ref.~\cite{Carullo:2021dui} used a larger set of GW events from O1, O2 and O3a than we did, although we expect 
-that the extra GW events will not contribute significantly to the combined bound since they have lower SNRs.
-
-These constraints could in principle be used to constrain specific
-non-GR theories and exotic compact objects~\cite{Glampedakis:2017cgd,Cardoso:2019rvt,Maggio:2020jml}. 
-However, QNM computations in non-GR theories have only been done in an
-handful of cases, mostly focusing on non-rotating or slowly-rotating
-BH solutions~\cite{Ferrari:2000ep,Molina:2010fb,Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk,Brito:2018hjh,Franciolini:2018uyq,Cardoso:2018ptl,Tattersall:2018nve,Tattersall:2019nmh,Blazquez-Salcedo:2019nwd,Silva:2019scu,Glampedakis:2019dqh,Blazquez-Salcedo:2020jee,Blazquez-Salcedo:2020caw,Cano:2020cao,Wagle:2021tam,Pierini:2021jxd},
-or relying on the eikonal/geometric optics approximation to obtain
-estimates of the QNMs for spinning BHs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo}. The
-only exceptions to this rule, that we are aware of, are computations
-of the QNM of Kerr-Newman BHs in Einstein-Maxwell
-theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa} or estimates of the BBH in non-GR theories obtained
-through a limited number of NR simulations~\cite{Okounkova:2019dfo,Okounkova:2019zjf}. Given these
-limitations, our ability of going beyond a null test of GR and use our
-results to impose precise constraints on non-GR theories with QNM
-measurements is currently quite limited.
-
-Despite these theoretical limitations there has been some recent effort to develop
-parametrizations that could help mapping measurements of the
-parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto
-constraints to specific non-GR theories. This includes for example
-the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently
-applied to LIGO-Virgo GW events in Ref.~\cite{Carullo:2021dui}, where
-deviations from the GR QNMs explicitly depend on a perturbative
-expansion in the BH spin and possible extra non-GR parameters, or the
-proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where
-deviations from the GR QNMs are mapped onto generic small
-modifications of the perturbation equations describing the QNMs. Other
-examples also include proposals to map deviations from the GR QNMs to
-coefficients in generic effective--field-theory
-actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to
-directly relate measurements of the QNM complex frequencies to a
-parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa}, 
-which could be then used jointly with measurements from the Event
-Horizon Telescope to obtain stronger constraints on deviations from
-GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
-We should note, however, that all these parametrizations are either
-limited to non-spinning BHs or make use of a series expansion in the
-BH spin which might limit their accuracy for highly-spinning BHs, unless 
-the sensitivity of GW detectors will not allow us to access the higher 
-coefficients in the spin series.
-
-In the future, it would be important to test whether the $\pSEOB$  model
-could be used to detect deviations in waveforms obtained through NR 
-simulations of specific non-GR theories. Such results are still at their 
-infancy and have so far only been done for a handful of theories, focusing mostly on proof-of-concept
-simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}. Nonetheless,
-given the recent efforts put forward in order to simulate BBHs in
-non-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.
-
-Finally, an obvious generalization of this work would be to extend the
-parameterized $\pSEOB$ model to generic precessing BBHs, which can in
-principle be easily done using the recently developed multipolar EOB
-model reported in Ref.~\cite{Ossokine:2020kjp}. Lastly, it will be relevant 
-to include GR deviations in the $\pSEOB$ model also during the late inspiral 
-and plunge stages of the BBH coalescence. On the other hand, GR deviations (notably 
-deviations from PN theory) for the long inspiral stage are currently 
-available in the $\pSEOB$ model and have been used to set bounds on the 
-PN parameters in the GW phasing using LIGO and Virgo observations~\cite{Abbott:2018lct,
-LIGOScientific:2019fpa,Abbott:2020jks}.
-
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-The authors thank Max Isi for generously allowing us to use the code developed in Ref.~\cite{Isi:2019asy} for the hierarchical inference analysis, and Gregorio Carullo for carefully reading the manuscript and providing useful comments.
-The authors would like to thank everyone at the frontline of the Covid-19 pandemic.
-The authors are grateful for computational resources provided by the LIGO Laboratory and supported by the National Science Foundation Grants PHY-0757058 and PHY-0823459, as well as computational resources at the AEI, specifically the Hypatia cluster.
-R.B.
-acknowledges financial support from the European Union's Horizon 2020 research and innovation programme under the Marie Sk\l odowska-Curie grant agreement No.
-792862, from the European Union's H2020 ERC, Starting Grant agreement no.~DarkGRA--757480, and from the MIUR PRIN and FARE programmes (GW-NEXT, CUP:~B84I20000100001).
-We also acknowledge support from the Amaldi Research Center funded by the MIUR program ``Dipartimento di Eccellenza'' (CUP:~B81I18001170001).
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%
-\appendix
-\section{Study of systematics in ringdown measurements in real, non-Gaussian noise}\label{sec:noise_systematics}
-
-Inferences of all parameters in this paper have been done under the
-assumption that the noise in the detectors is stationary and
-Gaussian. In other words, detector noise follows a normal distribution
-with zero mean and a PSD, $S_n(f)$, that is not a function of time, at
-least during the duration of the GW signal. This
-allows us to write the Bayesian likelihood function in the form given
-in Eqs.~(\ref{eq:likelihood}) and ~(\ref{eq:nwip}), and perform all the
-parameter estimation that follows in the results sections. However,
-LIGO-Virgo noise can often have features that deviate from
-stationarity and Gaussianity. If such features are not taken into
-account appropriately, final estimates of parameters can get
-biased. Here we demonstrate one such case by injecting in real noise a
-GW190521-like signal and showing how parameter estimates can be biased
-when our description of detector noise is not complete.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
-        \includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
-        \caption{90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2, 2)$ mode, $(\fgr{220}, \taugr{220})$ using synthetic \texttt{NRSur} signals with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (green dot dashed lines).
-The GR prediction for the frequency and damping time is indicated by the black cross.
-While the Gaussian noise simulations are consistent with the prediction, at least 3 of the 5 real noise simulation are not.
-The black curve corresponds to the measurements of the real event GW190521 reported in Ref.~\cite{Abbott:2020jks}.
-All signals are recovered using the $\pSEOB$ model.}
-        \label{fig:21g_systematics}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We choose a spinning, precessing NR-surrogate model \texttt{NRSur}~\footnote{This waveform model is 
-called \texttt{NRSur7dq4} in LAL.} (valid up to mass ratio 4) to simulate the actual GW190521 signal
-observed by the LIGO and Virgo detectors~\cite{Abbott:2020tfl} (see
-Table I of Ref.~\cite{Abbott:2020tfl})). The choice of the
-\texttt{NRSur} model is motivated by the fact that it is the most
-accurate model in the parameter range described by GW190521, because 
-it is built by directly interpolating NR waveforms. In
-Fig.~\ref{fig:21g_systematics}, we indicate with a black cross what
-the injected \texttt{NRSur} signal predicts for the QNM $(\ell=2,m=2)$
-frequency and damping time. For comparison, we also show with a
-black solid curve the results obtained when recovering the actual
-signal GW190521 with the $\pSEOB$ model. As seen in the plot,
-while the measurement of the frequency is consistent with the
-prediction, we overestimate the damping time.
-
-To understand such offset in the decay time, we proceed as follows.
-The actual GW190521 event was observed at a GPS time, 1242442967.61
-seconds (roughly 03:02:49 UTC, May 21, 2019). We select a time period
-of about 2.5 hours around this GPS time, create synthetic signals 
-with the \texttt{NRSur} model and inject them in different stretches
-of the real detector noise around the time of the actual GW event. The
-PSDs of GW detectors are expected to vary over longer durations of
-time, and hence the 2.5 hour stretch of noise we consider can be
-assumed to have noise-properties similar to the time of the actual
-event. Then, we perform Bayesian analysis against those injections 
-using the $\pSEOB$ model. The results are indicated by green curves in
-Fig.~\ref{fig:21g_systematics}. As it can be seen from the figure, for
-3 of the 5 noise realizations, corresponding to $t_0-1$ hour,
-$t_0+0.5$ hours, and $t_0+1$ hour, we recover a damping time similar to
-the one obtained when using the $\pSEOB$ model against the actual event GW190521 
-(black curve), where $t_0$ is the GPS time of the actual event. For
-the other two noise realizations, the $\pSEOB$ model estimates 
-consistently the damping time, but has an off-set frequency, 
-while the fifth noise realization is consistent with both predictions.  
-This study suggests that a bias in the measurements of the damping time 
-for the actual event GW190521 can be explained as due to an incomplete 
-description of the noise at the time of the event.
-
-The reader might question the judiciousness of using an aligned-spin
-waveform model, like $\pSEOB$, to measure a signal like GW190521 which
-appears to be precessing, especially because an incomplete
-understanding of the underlying signal can also lead to biases in
-measured quantities, as we have already demonstrated in
-Sec.~\ref{ssec:ngr_signal}. In order to explore possible effects of
-missing information about in-plane spins in the $\pSEOB$ model, we repeat the
-above study of injecting synthetic signals using \texttt{NRSur}
-and recovering using the $\pSEOB$ model, but this time, instead of
-using real detector noise, we use Gaussian noise (i.e., realizations
-of noise sampled from a predicted detector PSD). Since the properties
-of the noise are completely understood in this case, any residual
-measurement biases can be completely attributed to diffferences in the
-waveform model. The 2D posterior distributions of the frequency and
-damping time measured using these Gaussian-noise signals are shown by
-the grey curves in Fig.~\ref{fig:21g_systematics}. We find the
-measurements to be completely consistent with the predictions of the
-frequency and damping time, thus concluding that a lack of in-plane
-spins in the $\pSEOB$ model does not affect our measurements of the
-QNM properties. The fact that the measurement of ringdown quantities
-are robust against an incomplete description of the inspiral signal 
-is a crucial property of our method.
-
-\section{Correlation of the binary's total mass with the non-GR parameters}
-\label{sec:correlation}
-
-As mentioned in the main text, for low-SNR events with negligible
-higher-modes and for which only the post-merger is detectable, there
-is a strong degeneracy between the binary's total mass and the non-GR
-deviations $(\df{220}, \dtau{220})$. For those cases, only the
-reconstructed frequency and damping time $(f_{220},\tau _{220})$ can
-be independently measured from the data. To justify this statement, 
-in Fig.~\ref{fig:correlations} we show
-corner plots that illustrate the correlations between the non-GR
-parameters $(\df{220}, \dtau{220})$, the detector-frame total mass
-$M(1+z)$ and the reconstructed frequency and damping time
-$(f_{220},\tau _{220})$ for GW150914 (left panel), corresponding to an
-event for which both the pre- and post-merger phase are measurable,
-and for GW190521 (right panel), an event in which the post-merger has
-${\rm SNR}> 8$, but the pre-merger has an SNR below 8. For GW190521,
-due the strong degeneracy between $\df{220}$ and $M(1+z)$, the 1D
-posterior for $M(1+z)$ is pushed towards the upper boundary of its
-prior, despite the very wide prior employed in the analysis. This in
-turn renders the measurement of $\df{220}$ (and to a lesser degree of
-$\dtau{220}$) highly dependent on the upper boundary of the total mass
-prior. On the other hand, this issue does not significantly affect the
-posteriors for the reconstructed quantities $(f_{220},\tau _{220})$
-which are well measured and nearly independent on the upper prior
-boundary for $M(1+z)$. This is to be contrasted with the results for GW150914. In this case, 
-the extra information coming from the pre-merger phase allows to break 
-the degeneracy between the non-GR parameters and the total mass, 
-and therefore both $(\df{220}, \dtau{220})$ and $M(1+z)$ can 
-be measured at the same time.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{center}
-        \includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_GW150914.pdf}\includegraphics[width=0.45\textwidth]{figures/mtotal_qnm_params_degeneracy_S190521g.pdf}
-        \caption{Corner plots showing the correlations between the detector-frame total $(1+z)M$, the non-GR deviations $(\df{220}, \dtau{220})$ and the reconstructed frequency and damping time $(f_{220},\tau _{220})$.
-The left panel shows results for GW150914, for which ${\rm SNR}> 8$ in both the pre- and
-post-merger phase of the signal, and the correlations are absent.
-The right panel shows the results for GW190521,  which has ${\rm SNR}> 8$ in the post-merger phase, but not in the pre-merger phase, and the correlations are present.}
-        \label{fig:correlations}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-\bibliographystyle{apsrev}
-\bibliography{intro_paper}
-
-\end{document}
+GR~\cite{Taracchini:2013rva,Hofmann:2016yih}.

### 2022-02-07 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
updated main tex/bib
hs: to merge

@@
 dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr}   & \dots \\
-cEFTofGR & 4 & $-0.3680$ / $-0.5131$  & 1.9242 / 1.7000 & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
+cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
 qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
@@
 \omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
-\emph{only parity-even correnctions} and the second entries by considering
+\emph{only parity-even corrections} and the second entries by considering
 \emph{only parity-odd corrections}. In these cases, the dimensionless parameters
-$\lambda_{\rm e,o}$ are degenerate with the lengthscale $\ell$.
+$\lambda_{\rm e,o}$ are degenerate with the length scale $\ell$.
 %
@@
 The dotted line (labelled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
-given by the median value of the secondary's mass $\epsilon \, (G m_2 / c^2)$.
+given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
 %
 The dot-dashed line (labelled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
-given by the median value of the remnant's mass $\epsilon \, (G M_{f} / c^2)$.
+given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
 %
-For both, we used $\epsilon = 0.5$.
+For both, we used $\varepsilon = 0.5$.
 %
-If we take the latter as a lengthscale for the validity of dCS as an EFT, we
-have place upper bound on $\ell_{\rm CS} \leqslant 43.8$, within the
+If we take the latter as a length scale for the validity of dCS as an EFT, we
+have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
 approximation of our formalism.

### 2022-02-07 papers/paper_alt_theor_bounds/pseob_review.tex
updated pseob_review.tex

@@
-In this section we describe the waveform model used in this paper to measure properties of the underlying GW signal.
-As in \cite{Brito:2018rfr,Ghosh:2021mrv}, we use an inspiral-merger-ringdown (IMR) BBH waveform model where the parameters describing the remnant object are left additionally free and estimated directly from the data.
+In this section we describe the waveform model used in this paper to measure properties of a BBH ringdown.
+As in \cite{Brito:2018rfr,Ghosh:2021mrv}, we use an inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model where the parameters describing the remnant object are left additionally free and estimated directly from the data.
 
-We use, as our baseline model, the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf},  henceforth referred to as \SEOB{} \footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.} in this paper.
-The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral.
-An accurate description of the merger is incorporated through calibration with NR simulations, as described in~\cite{Cotesta:2018fcv}, along with information for the merger and ringdown phases, from BH perturbation theory.
+The GW signal from a BBH merger can be determined in GR by a unique set of parameters -- the masses and spins of the two BHs, $(m_1.
+m_2.
+\vec{s}_1, \vec{s}_2)$, the sky location determined by the luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$, and the orientation of the binary given by the inclination and polarisation angles, $(\iota, \psi)$.
+The set is completed by the choice of a reference time and phase, $(t_0.
+\phi_0)$.
+If we further assume that the spins of the individual BHs are restricted to be parallel to the orbital angular momentum, then we reduce the 6 components of spin to just 2, $(\chi_1, \chi_2)$ and our entire parameter set from 15 to 11.
+We define some additional parameters and set some conventions that will be useful in our analysis later, namely, the totat mass $M=m_1+m_2$, the chirp mass $\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$, the asymmetric mass ratio $q=m_1/m_2$ with the convention $m_1 \geq m_2; q \geq 1$ and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
 
-In the observer's frame, the GW polarizations can be written as
+The polarisations of the GW signal (in the observer's frame) are,
 %
@@
 %
-where $\varphi_0$ is the azimuthal direction to the observer (note that without loss of generality we can take $\phi_c\equiv\varphi_0$), while ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics where $(\ell,m)$ are the usual indices that describe the angular dependence of the spin-weighted spherical harmonics, with $\ell\geq 2$, $-\ell\leq m\leq \ell$.
-The $\SEOB$ model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
-For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown $\SEOB$ waveform is schematically given by
-%
+where ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(\ell,m)$.
+As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{} \footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
+The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{\ell m}^\mathrm{insp-plunge}$.
+An accurate description of the merger is incorporated through calibration with NR simulations, as described in~\cite{Cotesta:2018fcv}, along with information for the merger and ringdown phases, from BH perturbation theory.
+The merger-ringdown waveform, $h_{\ell m}^\mathrm{merger-RD}$, is then stitched to inspiral-plunge waveform, $h_{\ell m}^\mathrm{insp-plunge}$ at a certain time $t = t_{\textrm{match}}^{\ell m}$, as
 \begin{equation}
@@
 \end{equation}
-where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown waveform, which reads~\citep{Bohe:2016gbl,Cotesta:2018fcv}
-%
+where $\theta(t)$ is the Heaviside step function. The merger-ringdown waveform is expressed as an exponentially damped sinusoid ~\citep{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
 \begin{equation}
@@
 \end{equation}
-%
-where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH, i.e.
-QNMs with overtone index $n=0$.
-We denote the oscillation frequencies by $f_{\ell m  0}\equiv \Re(\sigma_{\ell m0})/(2\pi)$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0}) $.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are given by~\cite{Bohe:2016gbl,Cotesta:2018fcv}:
-%
-\begin{subequations}
-\begin{eqnarray}
-\label{eq:ansatz_amp}
-\tilde{A}_{\ell m}(t) &=& c_{1,c}^{\ell m} \tanh[c_{1,f}^{\ell m}\ (t-t_{\textrm{match}}^{\ell m}) \ +\ c_{2,f}^{\ell m}] \ + \ c_{2,c}^{\ell m},\\
-\label{eq:ansatz_phase}
-\tilde{\phi}_{\ell m}(t) &=& \phi_{\textrm{match}}^{\ell m} - d_{1,c}^{\ell m} \log\left[\frac{1+d_{2,f}^{\ell m} e^{-d_{1,f}^{\ell m}(t-t_{\textrm{match}}^{\ell m})}}{1+d_{2,f}^{\ell m}}\right],
-\end{eqnarray}
-\end{subequations}
-%
-where $ \phi_{\textrm{match}}^{\ell m}$ is the phase of the inspiral-plunge mode $(\ell, m)$ computed at $t = t_{\textrm{match}}^{\ell m}$.
-The coefficients $d_{1,c}^{\ell m}$ and $c_{i,c}^{\ell m}$ with $i = 1,2$
-are fixed by imposing that the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are of class $C^1$ at $t = t_{\textrm{match}}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge $\SEOB$ waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.
-This allows us to write the coefficients $c_{i,c}^{\ell m}$ as~\cite{Cotesta:2018fcv}:
-%
-\begin{subequations}
-\begin{align}
-\label{c1}
-c_{1,c}^{\ell m} &= \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})| \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh^2{(c_{2,f}^{\ell m})}, \\
-\label{c2}
-c_{2,c}^{\ell m} &= -\frac{ |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|}{\nu} + \frac{1}{c_{1,f}^{\ell
-    m} \nu} \big[ \partial_t|h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m})|  \nonumber \\
-    &- \sigma^\textrm{R}_{\ell m} |h_{\ell
-    m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell
-    m})|\big] \cosh{(c_{2,f}^{\ell m})}\sinh{(c_{2,f}^{\ell m})}, \\ \nonumber
-\end{align}
-\end{subequations}
-and $d_{1,c}^{\ell m}$ as
-\begin{align}
-\label{d1}
-d_{1,c}^{\ell m} &= \left[\omega_{\ell m}^{\textrm{insp-plunge}}(t_{\textrm{match}}^{\ell m}) -  \sigma^\textrm{I}_{\ell
-      m}\right]\frac{1+ d_{2,f}^{\ell m}}{d_{1,f}^{\ell m}d_{2,f}^{\ell m}}\,,
-\end{align}
-%
-where we denoted $\sigma_{\ell m}^\textrm{R} \equiv \Im (\sigma_{\ell m0}) < 0$ and  $\sigma_{\ell m}^\textrm{I} \equiv -\Re (\sigma_{\ell m0})$, and $\omega_{\ell m}^{\textrm{insp-plunge}}(t)$ is the frequency of the inspiral-plunge EOB mode.
-The coefficients $c_{i,f}^{\ell m}$ and $d_{i,f}^{\ell m}$ are obtained through fits to NR and
-Teukolsky-equation--based waveforms and can be found in Appendix C of Ref.~\cite{Cotesta:2018fcv}.
+where $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
+The frequencies $f_{\ell m}$ and damping times $/\tau_{\ell m}$ of the $(\ell m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{\ell m0}$ respetively.
+The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are defined in~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
 
-In the $\SEOB$ model constructed in Ref.~\cite{Mihaylov:2021bpf}, the
+\subsection{Construction of the merger-ringdown signal}
+In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies $\sigma_{\ell m 0}$ are computed by first determining the final mass and spin from estimates oof the initial masses and spins through NR--fitting--formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+and then converting these estimates of the final mass and spin to the complex frequencies using BH perturbation theory--inspiral analytical fits outlined in~\cite{Berti:2005ys,Berti:2009kk}.
+
+\iffalse
+In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
 complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
@@
 NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
+spirit of what was done in \paperone, we promote the QNM (complex)
+frequencies to be free parameters of the model, while keeping the
+inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
+to their GR values. More explicitly, we introduce a parameterized
+version of the $\SEOB$ model where the frequency and the
+damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
+_{\ell m 0})$) are defined through the fractional deviations, $(\delta
+f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
+values~\cite{Gossan:2011ha,Meidam:2014jpa}.
+
+Thus,
+\begin{subequations}
+\begin{eqnarray}
+f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
+\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
+\end{eqnarray}
+\end{subequations}
+
+The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
+\begin{subequations}
+\begin{eqnarray}
+f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,,\\ 
+\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,.
+\end{eqnarray}
+\end{subequations}
+We denote such a parameterized waveform model $\pSEOB$~\footnote{This
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
+freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
+  m}(t)$ in general also differ from the GR predictions, since
+those functions depend on the QNM complex frequencies, as can be seen
+from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
+(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 
+soon after merger deviates from the one predicted by GR.
+\fi

### 2022-02-07 papers/paper_alt_theor_bounds/pseob_review.tex
updated pseob_review.tex

@@
 where $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
-The frequencies $f_{\ell m}$ and damping times $/\tau_{\ell m}$ of the $(\ell m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{\ell m0}$ respetively.
+The frequencies $f_{\ell m 0}$ and damping times $\tau_{\ell m 0}$ of the $(\ell m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{\ell m0}$ respetively.
 The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are defined in~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
 
-\subsection{Construction of the merger-ringdown signal}
-In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies $\sigma_{\ell m 0}$ are computed by first determining the final mass and spin from estimates oof the initial masses and spins through NR--fitting--formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-and then converting these estimates of the final mass and spin to the complex frequencies using BH perturbation theory--inspiral analytical fits outlined in~\cite{Berti:2005ys,Berti:2009kk}.
+\subsection{The PARSPEC formalism and the construction of the merger-ringdown signal}
+In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies $\sigma_{\ell m 0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ are computed by first determining the final mass and spin from estimates of the initial masses and spins through NR--fitting--formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+and then converting these estimates of the final mass and spin to the complex frequencies using BH perturbation theory--inspiral analytical fits outlined in~\cite{Berti:2005ys,Berti:2009kk}.Hence,
+
+\begin{subequations}
+\begin{eqnarray}
+f_{\ell m 0}^{\text{GR}} &=& f_{\ell m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,\\ 
+\tau _{\ell m 0}^{\text{GR}} &=& \tau _{\ell m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,.
+\end{eqnarray}
+\end{subequations}
+
+Instead, for our parameterised model, we replace the above ringdown prescription with one introduced in~\cite{Maselli:2019mjd} and followed up by~\cite{Carullo:2021dui}.
+
+\ag{Copied over current content of III A.
+We can follow this plan: HS writes the small PARSPEC overview, after which AG goes back to how that formalism was actually coded up in the model.
+We might need to adapt the PARSPEC notation to be uniform with the $\ell m 0$ notations used above.}
+\hs{HS will do this.}
+\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
+
+The formalism modifies the Kerr quasinormal mode frequency as
+%
+\begin{subequations}
+\begin{align}
+\omega_{\iota} &= \omega^{\rm K}_{\iota} \, (1 + \delta \omega_{\iota}), \\
+\tau_{\iota}   &= \tau^{\rm K}_{\iota}   \, (1 + \delta \tau_{\iota}),
+\end{align}
+\label{eq:general_deviation}
+\end{subequations}
+%
+where the $\iota$ collectively represents the QNM labels $\{l,\, m,\, n\}$.
+
+Further expand the Kerr expression as:
+%
+\begin{subequations}
+\begin{align}
+\omega_{\iota} &= (1/M) \sum_{j = 0}^{N} \, \chi^{j} \omega^{(j)}_{k} \, \left( 1 + \gamma \delta \omega^{(j)}_{k} \right), \\
+\tau_{\iota}   &= M     \sum_{j = 0}^{N} \, \chi^{j} \tau^{(j)}_{k}   \, \left( 1 + \gamma \delta \tau^{(j)}_{k} \right),
+\end{align}
+\label{eq:kerr_expansion}
+\end{subequations}
+
+Also,
+%
+\begin{equation}
+\gamma
+%
+= \frac{\ell^{p}}{M_{\rm s}^{p}}
+%
+% = \frac{\ell^{p} (1 + z)^{p}}{M^{p}}
+%
+= \left[
+\frac{\ell c^2 (1 + z)}{G M}
+\right]^{p}
+\label{eq:def_gamma}
+\end{equation}
 

### 2022-02-14 papers/paper_alt_theor_bounds/pseob_review.tex
updated pseob_review.tex

--- 2022-02-07 papers/paper_alt_theor_bounds/pseob_review.tex
@@
-In this section we describe the waveform model used in this paper to measure properties of a BBH ringdown.
+In this section we describe the waveform model used in our paper to measure properties of a BBH ringdown.
 As in \cite{Brito:2018rfr,Ghosh:2021mrv}, we use an inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model where the parameters describing the remnant object are left additionally free and estimated directly from the data.
@@
 \begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi_0)\, h_{\ell m}(t)\,,
+h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{l, m} {}_{-\!2}Y_{l m}(\iota,\varphi_0)\, h_{l m}(t)\,,
 \end{equation}
 %
-where ${}_{-\!2}Y_{\ell m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(\ell,m)$.
-As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{} \footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
-The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{\ell m}^\mathrm{insp-plunge}$.
+where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(l,m)$.\footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.} As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{} \footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
+The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
 An accurate description of the merger is incorporated through calibration with NR simulations, as described in~\cite{Cotesta:2018fcv}, along with information for the merger and ringdown phases, from BH perturbation theory.
-The merger-ringdown waveform, $h_{\ell m}^\mathrm{merger-RD}$, is then stitched to inspiral-plunge waveform, $h_{\ell m}^\mathrm{insp-plunge}$ at a certain time $t = t_{\textrm{match}}^{\ell m}$, as
+The merger-ringdown waveform, $h_{l m}^\mathrm{merger-RD}$, is then stitched to inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$ at a certain time $t = t^{\textrm{match}}_{l m}$, as
 \begin{equation}
-h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{\ell m})\,,
+h_{l m}(t) = h_{l m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{l m} - t) + h_{l m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{l m})\,,
 \end{equation}
@@
 \label{RD}
-h_{\ell m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{\ell m}(t)\ e^{i \tilde{\phi}_{\ell m}(t)} \ e^{-i \sigma_{\ell m 0}(t-t_{\textrm{match}}^{\ell m})},
+h_{l m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{l m}(t)\ e^{i \tilde{\phi}_{l m}(t)} \ e^{-i \sigma_{l m 0}(t-t^{\textrm{match}}_{l m})},
 \end{equation}
-where $\sigma_{\ell m0} = 2\pi f_{\ell m 0} -i/\tau_{\ell m 0}$ are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
-The frequencies $f_{\ell m}$ and damping times $/\tau_{\ell m}$ of the $(\ell m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{\ell m0}$ respetively.
-The functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell m}(t)$ are defined in~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
+where $\sigma_{l m0} = \omega_{l m 0} -i/\tau_{l m 0}$ are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
+The frequencies $\omega_{l m 0}$ and damping times $\tau_{l m 0}$ of the $(l, m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{l m0}$ respetively.
+The functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l m}(t)$ are defined in~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
 
-\subsection{Construction of the merger-ringdown signal}
-In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies $\sigma_{\ell m 0}$ are computed by first determining the final mass and spin from estimates oof the initial masses and spins through NR--fitting--formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-and then converting these estimates of the final mass and spin to the complex frequencies using BH perturbation theory--inspiral analytical fits outlined in~\cite{Berti:2005ys,Berti:2009kk}.
+In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies $\sigma_{l m 0}$ are computed by first determining the final mass and spin from estimates of the initial masses and spins through NR--fitting--formulas~\cite{Taracchini:2013rva,Hofmann:2016yih} and then converting them to the complex frequencies using BH perturbation theory--inspiral analytical fits outlined in~\cite{Berti:2005ys,Berti:2009kk}.
+Hence,
+
+\begin{subequations}
+\begin{eqnarray}
+\omega_{l m 0}^{\text{GR}} &=& \omega_{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,\\ 
+\tau _{l m 0}^{\text{GR}} &=& \tau _{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,.
+\end{eqnarray}
+\end{subequations}
+where $(\omega_{l m 0}^{\text{GR}}, \tau _{l m 0}^{\text{GR}} )$ refer to the QNM predictions in baseline \SEOB{} model.
+In this paper, however, we introduce a completely different expression of the QNM frequencies $(\omega_{l m 0}, \tau _{l m 0})$, as a series expansion on the spin of the remnant object $\chi_f$ (Eqs.~\ref{eq:kerr_expansion}).
+For the rest of the paper, in keeping with the conventions introduced in Sec.~\ref{sec:review_parspec}, we are going to use the index $k$ to refer to $(l, m,n=0)$ mode.
+Accordingly, we are going to use $(\omega_k, \tau _k)$ to refer to $(\omega_{l m 0}, \tau _{l m 0})$ respectively.
+
+In this formalism our QNM frequencies are expressed through functions,
+\begin{subequations}
+\begin{eqnarray}
+\omega_k &=& \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\})\\ 
+\tau _k &=& \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\})
+\end{eqnarray}
+\end{subequations}
+where the estimates of $(m_1.
+m_2.
+\chi_1, \chi_1)$ are used to predict the final mass and spin $(M_f,  \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+Additionally, $(\omega_k, \tau_k)$ depend on the coupling constant $\ell$ defined in Eq.~\ref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$, where $j$ ranges from 0 to the power of spin in Eqs.~\ref{eq:kerr_expansion} upto which we include corrections.
+For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$ terms, then we just have two additional degrees of freedom, $(\omega_k^{(0)}, \tau_k^{(0)})$ per mode $k$.
+We will call this parametrized waveform model $\pSEOB$ in this paper.
+In this paper, we will restrict ourselves to the $k=(2,2,0)$ QNM and corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
+Assuming a prior which is uniform on the beyond-GR parameters, $(\ell, \{\delta \omega_k^{(j)}\},\{\delta \tau_k^{(j)}\})$, we employ a Bayesian framework to stochastically sample over the parameter space using the \texttt{LALInference} algorithm.~\cite{lallsuite}.
+The bounds on these beyond-GR parameters, for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}, are provided in Sec.~\ref{sec:results}.
 
@@
 In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{\ell m 0}$ are expressed in terms of the
+complex frequencies $\sigma_{l m 0}$ are expressed in terms of the
 final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
@@
 frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed
+inspiral-plunge modes $h_{l m}^\mathrm{inspiral-plunge}(t)$ fixed
 to their GR values. More explicitly, we introduce a parameterized
 version of the $\SEOB$ model where the frequency and the
-damping time of the ${\ell m 0}$ mode (i.e, $(f_{\ell m 0}, \tau
-_{\ell m 0})$) are defined through the fractional deviations, $(\delta
-f_{\ell m 0},\delta \tau_{\ell m 0})$, from the corresponding GR
+damping time of the ${l m 0}$ mode (i.e, $(\omega_{l m 0}, \tau
+_{l m 0})$) are defined through the fractional deviations, $(\delta
+\omega_{l m 0},\delta \tau_{l m 0})$, from the corresponding GR
 values~\cite{Gossan:2011ha,Meidam:2014jpa}.
@@
 \begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}^{\text{GR}}\, (1 + \delta f_{\ell m 0})\,,\label{eq:nongr_freqs_a} \\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}^{\text{GR}}\, (1 + \delta \tau_{\ell m 0})\,. \label{eq:nongr_freqs_b}
+\omega_{l m 0} &=& \omega_{l m 0}^{\text{GR}}\, (1 + \delta \omega_{l m 0})\,,\label{eq:nongr_freqs_a} \\ 
+\tau _{l m 0} &=& \tau _{l m 0}^{\text{GR}}\, (1 + \delta \tau_{l m 0})\,. \label{eq:nongr_freqs_b}
 \end{eqnarray}
@@
 
-The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
+The GR quantities $( \omega_{l m 0}^{GR},\tau_{l m 0}^{GR})$ are
 constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
@@
 \begin{eqnarray}
-f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,,\\ 
-\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,.
+\omega_{l m 0} &=& \omega_{l m 0}(m_1, m_2, \chi_1, \chi_2, \delta \omega_{l m 0}, \delta \tau_{l m 0})\,,\\ 
+\tau _{l m 0} &=& \tau _{l m 0}(m_1, m_2, \chi_1, \chi_2, \delta \omega_{l m 0}, \delta \tau_{l m 0})\,.
 \end{eqnarray}
@@
 We denote such a parameterized waveform model $\pSEOB$~\footnote{This
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
-freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{l m}$ to vary
+freely, the functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l
   m}(t)$ in general also differ from the GR predictions, since
 those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
+from the expressions for $c_{i,c}^{l m}$ and $d_{1,c}^{l m}$ in Eqs.~(\ref{c1}),
 (\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 

### 2022-02-14 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: terse text about qnm translation

@@
 \newcommand{\dd}{{\rm d}}
+\newcommand{\ii}{{\rm i}}
 \newcommand{\dV}{{\rm d}^{4}x \, \sqrt{-g} \,}
@@
 explain how we modified it to include the {\sc Parspec} parametrisation.}
+\input{pseob_review}
 
@@
 
-\hs{HS will do this.}
+Let us now establish the connection between theory-agnostic framework of the
+$\pSEOB$ waveform model and the theory-specific QNM calculations.
+%
+We begin by expanding $\omega$ and $\tau$, given by Eqs.~\eqref{eq:kerr_expansion} as,
+%
+\begin{subequations}
+\begin{align}
+M \omega_{220} &= \gamma (\delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)})
++ \sum_{j=0}^{N} \chi^{j} \omega^{j}\,,
+\\
+\tau_{220}/M   &= \gamma (\delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)})
++ \sum_{j=0}^{N} \chi^{j} \tau^{j}\,,
+\end{align}
+\label{eq:qnm_nongr_iso}
+\end{subequations}
+%
+where we are already focusing on the dominant $\ell = m = 2$, $n=0$ QNM and
+pulled out of the sum all beyond-GR corrections, rescriting ourselves to the nonspinning ($j=0$) and linear-order in spin ($j=1$)
+corrections to the Kerr QNMs, encoded in the coefficients $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$.
+
+Just as in GR where the coefficients $\omega^{j}$, $\tau^{j}$ are determined by
+comparison against the Kerr QNMs, a theory-specific calculation predicts the
+numerical values of $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$
+%
+This means that using the $\pSEOB$ waveform model with theory-specific informed
+QNMs we reduce the parameters space of beyond-GR parameters to one, i.e., to
+only $\gamma$, which in turn contains information about the length scale $\ell$.
+
+Now as we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating black holes
+is modified gravity theories come in two families depending on their transformation upon a parity
+transformation: axial and polar. Which is the one we use to match against Eqs.~\eqref{eq:qnm_nongr_iso}?
+%
+To answer this question one has to work on a theory-by-theory case and in each theory perform a
+a translation between the metric perturbations $h_{\mu\nu}$ in the Regger-Wheeler-Zerilli gauge and
+connect it with the transverse-traceless gauge used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
+%
+In GR, both axial and polar QNMs are the same (a property known as \emph{isospectrality}) and therefore which
+QNM we use to model the ringdown makes no difference.
+%
+In beyond-GR theories, isospectrality is in general broken (see the discussion in Ref.~\cite{Hui:2021cpm} for a counterexample).
+and thus how axial and polar gravitational QNMs appear in the GW signal has to be answered in theory-by-theory.
+%
+This is outside the scope of this paper and here we take the more pragmatic approach
+of simply choosing the \emph{least damped gravitational mode between the two parities.}
+%
+The justification is this is the mode which, if excited during the merger, is
+the most likely to appear in the signal.
+
+In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
+the {\sc Parspec} implementation of each theory and give credit to the papers
+which calculated the QNMs.
 
@@
 \hline
-sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
-dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr}   & \dots \\
+sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.7$~km~\cite{Perkins:2021mhb} (GW) & \dots \\
+dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr} (EM+GW)  & \dots \\
 cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
@@
 
-\hs{We {\it must very explicitly} state our working hypothesis here:
-%
-\begin{itemize}
-    \item That we include only the nonrotating, non-GR correction to the QNMs.
-    \item That due to absence of isospectrality, when translating to the theory specific result,
-    we {\it chose} to use the lowest damping, gravitational QNM of the theory.
-\end{itemize}
-%
-We can come back to these in the Sec.~\ref{sec:discussion} as things that we
-might want to revisit in the future.
-}
+% \hs{We {\it must very explicitly} state our working hypothesis here:
+% %
+% \begin{itemize}
+%     \item That we include only the nonrotating, non-GR correction to the QNMs.
+%     \item That due to absence of isospectrality, when translating to the theory specific result,
+%     we {\it chose} to use the lowest damping, gravitational QNM of the theory.
+% \end{itemize}
+% %
+% We can come back to these in the Sec.~\ref{sec:discussion} as things that we
+% might want to revisit in the future.
+% }
 
-\hs{In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
-the {\sc Parspec} implementation of each theory and give credit to the papers
-which calculated the QNMs.}
+% \hs{In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
+% the {\sc Parspec} implementation of each theory and give credit to the papers
+% which calculated the QNMs.}
 

### 2022-02-14 papers/paper_alt_theor_bounds/pseob_review.tex
hs: added refs, small changes

@@
 
-The GW signal from a BBH merger can be determined in GR by a unique set of parameters -- the masses and spins of the two BHs, $(m_1.
-m_2.
-\vec{s}_1, \vec{s}_2)$, the sky location determined by the luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$, and the orientation of the binary given by the inclination and polarisation angles, $(\iota, \psi)$.
-The set is completed by the choice of a reference time and phase, $(t_0.
-\phi_0)$.
+The GW signal from a BBH merger can be determined in GR by a unique set of parameters -- the masses and spins of the two BHs, $(m_1,\, m_2,\, \vec{s}_1,\, \vec{s}_2)$, the sky location determined by the luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$, and the orientation of the binary given by the inclination and polarisation angles, $(\iota, \psi)$.
+The set is completed by the choice of a reference time and phase, $(t_0,\, \phi_0)$.
 If we further assume that the spins of the individual BHs are restricted to be parallel to the orbital angular momentum, then we reduce the 6 components of spin to just 2, $(\chi_1, \chi_2)$ and our entire parameter set from 15 to 11.
-We define some additional parameters and set some conventions that will be useful in our analysis later, namely, the totat mass $M=m_1+m_2$, the chirp mass $\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$, the asymmetric mass ratio $q=m_1/m_2$ with the convention $m_1 \geq m_2; q \geq 1$ and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
+We define some additional parameters and set some conventions that will be useful in our analysis later, namely, the totat mass $M=m_1+m_2$, the chirp mass $\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$, the asymmetric mass ratio $q=m_1/m_2$ with the convention $m_1 \geqslant m_2; q \geqslant 1$ and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
 
@@
 The merger-ringdown waveform, $h_{l m}^\mathrm{merger-RD}$, is then stitched to inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$ at a certain time $t = t^{\textrm{match}}_{l m}$, as
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $\theta(t)$ is the Heaviside step function. The merger-ringdown waveform is expressed as an exponentially damped sinusoid ~\citep{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
+%
 \begin{equation}
@@
 \end{equation}
-where $\sigma_{l m0} = \omega_{l m 0} -i/\tau_{l m 0}$ are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
+%
+where
+%
+\begin{equation}
+\sigma_{l m0} = \omega_{l m 0} - i / \tau_{l m 0}\,,
+\end{equation}
+%
+are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
 The frequencies $\omega_{l m 0}$ and damping times $\tau_{l m 0}$ of the $(l, m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{l m0}$ respetively.
@@
 where $(\omega_{l m 0}^{\text{GR}}, \tau _{l m 0}^{\text{GR}} )$ refer to the QNM predictions in baseline \SEOB{} model.
-In this paper, however, we introduce a completely different expression of the QNM frequencies $(\omega_{l m 0}, \tau _{l m 0})$, as a series expansion on the spin of the remnant object $\chi_f$ (Eqs.~\ref{eq:kerr_expansion}).
+In this paper, however, we introduce a completely different expression of the QNM frequencies $(\omega_{l m 0}, \tau _{l m 0})$, as a series expansion on the spin of the remnant object $\chi_f$ [see Eqs.~\eqref{eq:kerr_expansion}].
 For the rest of the paper, in keeping with the conventions introduced in Sec.~\ref{sec:review_parspec}, we are going to use the index $k$ to refer to $(l, m,n=0)$ mode.
@@
 In this formalism our QNM frequencies are expressed through functions,
+%
 \begin{subequations}
-\begin{eqnarray}
-\omega_k &=& \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\})\\ 
-\tau _k &=& \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\})
-\end{eqnarray}
+\begin{align}
+\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\})\\
+\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\})
+\end{align}
 \end{subequations}
-where the estimates of $(m_1.
-m_2.
-\chi_1, \chi_1)$ are used to predict the final mass and spin $(M_f,  \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-Additionally, $(\omega_k, \tau_k)$ depend on the coupling constant $\ell$ defined in Eq.~\ref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$, where $j$ ranges from 0 to the power of spin in Eqs.~\ref{eq:kerr_expansion} upto which we include corrections.
+%
+where the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict the final mass and spin $(M_f,\, \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+%
+Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$ defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$, where $j$ ranges from 0 to the power of spin in Eqs.~\ref{eq:kerr_expansion} upto which we include corrections.
+%
 For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$ terms, then we just have two additional degrees of freedom, $(\omega_k^{(0)}, \tau_k^{(0)})$ per mode $k$.
 We will call this parametrized waveform model $\pSEOB$ in this paper.
+%
 In this paper, we will restrict ourselves to the $k=(2,2,0)$ QNM and corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
 Assuming a prior which is uniform on the beyond-GR parameters, $(\ell, \{\delta \omega_k^{(j)}\},\{\delta \tau_k^{(j)}\})$, we employ a Bayesian framework to stochastically sample over the parameter space using the \texttt{LALInference} algorithm.~\cite{lallsuite}.
+%
 The bounds on these beyond-GR parameters, for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}, are provided in Sec.~\ref{sec:results}.

### 2022-02-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: explained mapping in concrete example; terse

@@
 \usepackage{bm}
-% \usepackage{txfonts}
+\usepackage{txfonts}
 \usepackage{natbib}
@@
 \begin{align}
-M \omega_{220} &= \gamma (\delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)})
+M \omega_{220} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
 + \sum_{j=0}^{N} \chi^{j} \omega^{j}\,,
 \\
-\tau_{220}/M   &= \gamma (\delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)})
+\tau_{220}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
 + \sum_{j=0}^{N} \chi^{j} \tau^{j}\,,
@@
 only $\gamma$, which in turn contains information about the length scale $\ell$.
+%
+It is important to emphasize that our procedure is different from that of~\cite{Carullo:2021dui}
+which, for a given value of $p$, varied all $\ell$, $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ parameters.
+%
+% As we will see later, our theory-informed approach can result to stronger constraints to certain modified ....
 
@@
 the most likely to appear in the signal.
+
+% ---------------------------
+% CONCRETE EXAMPLE OF MAPPING
+% ---------------------------
+Let us show one concrete example of how this mapping is done.
+%
+In Ref.~\cite{Wagle:2021tam} the QNMs of slow-rotating BHs in dCS gravity were calculated
+and it was found that the axial gravitational modes have their damping time increased as we
+increase the Chern-Simons coupling $\ell_{\rm CS}$ at fixed spin $\chi$ of the BH.
+%
+Having selected this mode we can now obtain $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
+%
+Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
+%
+\begin{equation}
+    M \omega^{\rm CS}_{220} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+    \label{eq:omega_dsc_eg}
+\end{equation}
+%
+and similarly for the imaginary part ${\rm Im}(\sigma_{220}) = \omega^{\rm CS}_{220} = 1 / \tau^{\rm CS}_{220}$.
+%
+Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [such that $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
+and $c_{i}$ are fitting coefficients.
+%
+In the context of a binary BH merger, $M$ is interpreted as the remnant mass $\Mf$.
+
+We can now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm CS}$, and
+gather the terms proportional to $\ell_{\rm CS}$.
+%
+Doing so, we find,
+%
+\begin{align}
+    \Mf \, \omega^{\rm CS}_{220} &=
+    \left[ 0.3722 + 1.1945 (\ell_{\rm CS} / \Mf)^4 \right]
+    \nonumber \\
+    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm CS} / \Mf)^4 \right] \, \chi\,,
+\end{align}
+%
+where we made use of the numerical value of the coefficients $c_{i}$ and,
+reassuringly, the nonrotating and linear-in-spin coefficients above agree with those
+of~\cite{Maselli:2019mjd} to xx\%.
+%
+We now isolate the dCS corrections and compare against Eq.~\eqref{eq:qnm_nongr_iso}.
+%
+Doing so, we can make the identifications,
+%
+\begin{equation}
+p_{\rm cs} = 4\,, \quad \delta \omega^{(0)}_{\rm cs} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm cs} = 41.199\,.
+\label{eq:cs_omega_coefs}
+\end{equation}
+%
+The same procedure can be made for $\tau^{(i)}$, which results in,
+%
+\begin{equation}
+\delta \tau^{(0)}_{\rm cs} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm cs} = 794.66\,.
+\label{eq:cs_tau_coefs}
+\end{equation}
+%
+which completes the set of fixed parameters beyond-GR parameters in the ringdown of the \pSEOB waveform model.
+%
+As we said before, the only free beyond-GR parameter left is now $\ell_{\rm CS}$.
 

### 2022-02-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: started super terse text on data analysis

@@
 \usepackage{txfonts}
+% \usepackage{newtxtext}
+% \usepackage{newtxmath}
 \usepackage{natbib}
-\usepackage{amssymb}
+% \usepackage{amssymb}
 \usepackage{xspace}
@@
 %
-Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [such that $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
+Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [thus $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
 and $c_{i}$ are fitting coefficients.
@@
 %
-The same procedure can be made for $\tau^{(i)}$, which results in,
+The same procedure can be carried for $\tau^{(i)}$, which results in,
 %
@@
 %
-which completes the set of fixed parameters beyond-GR parameters in the ringdown of the \pSEOB waveform model.
+which completes the set of fixed parameters beyond-GR parameters in the ringdown of the \pSEOB{} waveform model.
 %
@@
 
-\hs{Say that we use GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp} and justify why.}
+% \hs{Say that we use GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp} and justify why.}
+
+We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
+%
+They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
+
+\begin{equation}
+P(\bm{\lambda} \vert d, \mathcal{H}) =
+\frac{P(\bm{\lambda} \vert \mathcal{H}) P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
+\label{eq:bayes}
+\end{equation}
+%
+where $d$ is the data and $\bm{\lambda}$ is a set of vectors that fully
+characterize the waveform.
+%
+$P(\bm{\lambda} \vert \mathcal{H})$ is prior probability distribution,
+$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
+$P(d \vert \mathcal{H})$ the evidence.
+
+Our set of parameters is $\bm{\lambda} = \bm{\theta}_{\rm GR} \cup \bm{\theta}_{\rm nGR}$, where
+$\bm{\theta}_{\rm nGR} = \{\ell_{i}\}$ is a set of beyond-GR coupling constants.
+%
+As discussed in Sec.~\ref{sec:review_theories} there is a single coupling
+constants in the cases of EdGB and dCS theories, but two in the cubic and
+quartic EFTofGR.
+
+Assuming Gaussian and stationary noise, we can write the (log) likelihood function as,
+%
+\begin{equation}
+\ln \mathcal{L}(d \vert \bm{\lambda},\mathcal{H}) \propto
+- \tfrac{1}{2}
+\langle
+d - h(\bm{\lambda}) \vert d - h(\bm{\lambda})
+\rangle\,,
+\end{equation}
+%
+with noise-weighted inner product $\langle \cdot | \cdot \rangle$ defined as,
+%
+\begin{equation}
+\langle A | B \rangle =
+\int_{f_{\rm low}}^{f_{\rm high}} \, \dd f \,
+\frac{\tilde{A}^{\ast}(f) \tilde{B}(f) + \tilde{A}(f) \tilde{B}^{\ast}(f)}{S_{n}(f)}
+\end{equation}
+%
+where $\tilde{A}(f)$ is the Fourier transform of $A(t)$, the asterisk
+denotes complex conjugation and $S_{n}(f)$ is the power spectrum density
+of the detector.
+
+With the posterior distribution function $P(\bm{\lambda} | d, \mathcal{H})$ determined, we can then
+marginalize over all nuisance parameters to obtain the posterior
+distribution function the $i$-th beyond-GR coupling constants $\ell_{i}$,
+%
+\begin{equation}
+P(\ell_{i} | d, \mathcal{H}) =
+\int \dd \xi_{\rm GR} \,
+P(\bm{\lambda} | d, \mathcal{H}) \,.
+\label{eq:marg_posterior}
+\end{equation}
+%
 
@@
 the final BH mass.}
+
+\subsection{Einstein-dilaton-Gauss-Bonnet}
+\label{sec:results_edgb}
+
+\subsection{Dynamical Chern-Simons}
+\label{sec:results_dcs}
+
+\subsection{Effective-field-theory of general relativity}
+\label{sec:results_efts}
 

### 2022-02-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs:removed comments
transfered content of pseob_review.tex to the main.tex

@@
 
-\hs{AG will do this.}
-\hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
-explain how we modified it to include the {\sc Parspec} parametrisation.}
-\input{pseob_review}
+In this section we describe the waveform model used in our paper to measure properties of a BBH ringdown.
+As in \cite{Brito:2018rfr,Ghosh:2021mrv}, we use an inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model where the parameters describing the remnant object are left additionally free and estimated directly from the data.
+
+The GW signal from a BBH merger can be determined in GR by a unique set of parameters -- the masses and spins of the two BHs, $(m_1,\, m_2,\, \vec{s}_1,\, \vec{s}_2)$, the sky location determined by the luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$, and the orientation of the binary given by the inclination and polarisation angles, $(\iota, \psi)$.
+The set is completed by the choice of a reference time and phase, $(t_0,\, \phi_0)$.
+If we further assume that the spins of the individual BHs are restricted to be parallel to the orbital angular momentum, then we reduce the 6 components of spin to just 2, $(\chi_1, \chi_2)$ and our entire parameter set from 15 to 11.
+We define some additional parameters and set some conventions that will be useful in our analysis later, namely, the totat mass $M=m_1+m_2$, the chirp mass $\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$, the asymmetric mass ratio $q=m_1/m_2$ with the convention $m_1 \geqslant m_2; q \geqslant 1$ and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
+
+The polarisations of the GW signal (in the observer's frame) are,
+%
+\begin{equation}
+h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{l, m} {}_{-\!2}Y_{l m}(\iota,\varphi_0)\, h_{l m}(t)\,,
+\end{equation}
+%
+where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(l,m)$.\footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.} As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{} \footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
+The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
+An accurate description of the merger is incorporated through calibration with NR simulations, as described in~\cite{Cotesta:2018fcv}, along with information for the merger and ringdown phases, from BH perturbation theory.
+The merger-ringdown waveform, $h_{l m}^\mathrm{merger-RD}$, is then stitched to inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$ at a certain time $t = t^{\textrm{match}}_{l m}$, as
+%
+\begin{equation}
+h_{l m}(t) = h_{l m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{l m} - t) + h_{l m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{l m})\,,
+\end{equation}
+%
+where $\theta(t)$ is the Heaviside step function. The merger-ringdown waveform is expressed as an exponentially damped sinusoid ~\citep{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
+%
+\begin{equation}
+\label{RD}
+h_{l m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{l m}(t)\ e^{i \tilde{\phi}_{l m}(t)} \ e^{-i \sigma_{l m 0}(t-t^{\textrm{match}}_{l m})},
+\end{equation}
+%
+where
+%
+\begin{align}
+\sigma_{l m 0} &= {\rm Re}(\sigma_{l m 0}) + i \, {\rm Im}(\sigma_{l m 0})\,,
+\nonumber \\
+&= \omega_{l m 0} - i / \tau_{l m 0}\,,
+\end{align}
+%
+are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
+The frequencies $\omega_{l m 0}$ and damping times $\tau_{l m 0}$ of the $(l, m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{l m0}$ respetively.
+The functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l m}(t)$ are defined in~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
+
+In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies $\sigma_{l m 0}$ are computed by first determining the final mass and spin from estimates of the initial masses and spins through NR--fitting--formulas~\cite{Taracchini:2013rva,Hofmann:2016yih} and then converting them to the complex frequencies using BH perturbation theory--inspiral analytical fits outlined in~\cite{Berti:2005ys,Berti:2009kk}.
+Hence,
+
+\begin{subequations}
+\begin{eqnarray}
+\omega_{l m 0}^{\text{GR}} &=& \omega_{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,\\
+\tau _{l m 0}^{\text{GR}} &=& \tau _{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,.
+\end{eqnarray}
+\end{subequations}
+where $(\omega_{l m 0}^{\text{GR}}, \tau _{l m 0}^{\text{GR}} )$ refer to the QNM predictions in baseline \SEOB{} model.
+In this paper, however, we introduce a completely different expression of the QNM frequencies $(\omega_{l m 0}, \tau _{l m 0})$, as a series expansion on the spin of the remnant object $\chi_f$ [see Eqs.~\eqref{eq:kerr_expansion}].
+For the rest of the paper, in keeping with the conventions introduced in Sec.~\ref{sec:review_parspec}, we are going to use the index $k$ to refer to $(l, m,n=0)$ mode.
+Accordingly, we are going to use $(\omega_k, \tau _k)$ to refer to $(\omega_{l m 0}, \tau _{l m 0})$ respectively.
+
+In this formalism our QNM frequencies are expressed through functions,
+%
+\begin{subequations}
+\begin{align}
+\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\})\\
+\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\})
+\end{align}
+\end{subequations}
+%
+where the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict the final mass and spin $(M_f,\, \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+%
+Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$ defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$, where $j$ ranges from 0 to the power of spin in Eqs.~\ref{eq:kerr_expansion} upto which we include corrections.
+%
+For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$ terms, then we just have two additional degrees of freedom, $(\omega_k^{(0)}, \tau_k^{(0)})$ per mode $k$.
+We will call this parametrized waveform model $\pSEOB$ in this paper.
+%
+In this paper, we will restrict ourselves to the $k=(2,2,0)$ QNM and corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
+Assuming a prior which is uniform on the beyond-GR parameters, $(\ell, \{\delta \omega_k^{(j)}\},\{\delta \tau_k^{(j)}\})$, we employ a Bayesian framework to stochastically sample over the parameter space using the \texttt{LALInference} algorithm.~\cite{lallsuite}.
+%
+The bounds on these beyond-GR parameters, for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}, are provided in Sec.~\ref{sec:results}.
+
+\iffalse
+In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
+complex frequencies $\sigma_{l m 0}$ are expressed in terms of the
+final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
+latter are related to the BBH's component masses and spins through
+NR--fitting-formulas obtained in
+GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
+spirit of what was done in \paperone, we promote the QNM (complex)
+frequencies to be free parameters of the model, while keeping the
+inspiral-plunge modes $h_{l m}^\mathrm{inspiral-plunge}(t)$ fixed
+to their GR values. More explicitly, we introduce a parameterized
+version of the $\SEOB$ model where the frequency and the
+damping time of the ${l m 0}$ mode (i.e, $(\omega_{l m 0}, \tau
+_{l m 0})$) are defined through the fractional deviations, $(\delta
+\omega_{l m 0},\delta \tau_{l m 0})$, from the corresponding GR
+values~\cite{Gossan:2011ha,Meidam:2014jpa}.
+
+Thus,
+\begin{subequations}
+\begin{eqnarray}
+\omega_{l m 0} &=& \omega_{l m 0}^{\text{GR}}\, (1 + \delta \omega_{l m 0})\,,\label{eq:nongr_freqs_a} \\
+\tau _{l m 0} &=& \tau _{l m 0}^{\text{GR}}\, (1 + \delta \tau_{l m 0})\,. \label{eq:nongr_freqs_b}
+\end{eqnarray}
+\end{subequations}
+
+The GR quantities $( \omega_{l m 0}^{GR},\tau_{l m 0}^{GR})$ are
+constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
+\begin{subequations}
+\begin{eqnarray}
+\omega_{l m 0} &=& \omega_{l m 0}(m_1, m_2, \chi_1, \chi_2, \delta \omega_{l m 0}, \delta \tau_{l m 0})\,,\\
+\tau _{l m 0} &=& \tau _{l m 0}(m_1, m_2, \chi_1, \chi_2, \delta \omega_{l m 0}, \delta \tau_{l m 0})\,.
+\end{eqnarray}
+\end{subequations}
+We denote such a parameterized waveform model $\pSEOB$~\footnote{This
+waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{l m}$ to vary
+freely, the functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l
+  m}(t)$ in general also differ from the GR predictions, since
+those functions depend on the QNM complex frequencies, as can be seen
+from the expressions for $c_{i,c}^{l m}$ and $d_{1,c}^{l m}$ in Eqs.~(\ref{c1}),
+(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase)
+soon after merger deviates from the one predicted by GR.
+\fi
 
@@
 \begin{equation}
-p_{\rm cs} = 4\,, \quad \delta \omega^{(0)}_{\rm cs} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm cs} = 41.199\,.
+p_{\rm CS} = 4\,, \quad \delta \omega^{(0)}_{\rm CS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm CS} = 41.199\,.
 \label{eq:cs_omega_coefs}
@@
 \begin{equation}
-\delta \tau^{(0)}_{\rm cs} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm cs} = 794.66\,.
+\delta \tau^{(0)}_{\rm CS} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm CS} = 794.66\,.
 \label{eq:cs_tau_coefs}
@@
 
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/posteriors_for_exs.pdf}
+\caption{Summary of our results.
+\hs{Maybe have some like this for an `executive summary'?}
+}
+\label{fig:dCS_exec_sum}
+\end{figure}
+
 \subsection{Effective-field-theory of general relativity}

### 2022-02-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added to the bayesian section

@@
 % HS: temporary title. Feel free to add suggestions
-% \title{Probing higher-curvature gravity theories from binary black hole ringdown signals}
+% \title{Probing higher-curvature gravity theories from binary BH ringdown signals}
 \title{Black-hole ringdown as a probe of higher-curvature gravity theories}
@@
 %
-We briefly review which theories we consider, what are the currents
-observational constraints in each of them and what we known about the QNMs of
-black holes in each of them.
+We briefly review the theories we consider in this paper, what the currents
+observational constraints are in each of them and what we know about BH QNMs in each of them.
 
@@
 where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
-$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
+%$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
 invariant $\mathscr{G}$,
@@
 with strength set by the dimensionful coupling constant $\ell_{\rm GB}$ with dimensions
-of length.
-
-Different subclasses of this theory are determined by the function $f(\varphi)$
-and they can be classified into two classes based on the properties of their black hole solutions.
+of length. Different subclasses of this theory are determined by the function $f(\varphi)$
+and they can be classified into two classes based on the properties of their BH solutions.
 %
 In the first class, the first derivative of the coupling
-function $f'(\varphi) = \dd f  / \dd \varphi$ is always nonzero and black holes
+function $f'(\varphi) = \dd f  / \dd \varphi$ is always nonzero and BHs
 are known to always support (secondary) scalar hair.
@@
 In this case, one can show that theory admits the same stationary,
-asymptotically flat black hole solution of GR and scalarized black
-holes~\cite{Doneva:2017bvd,Silva:2017uqg,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
+asymptotically flat BH solution of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
 %
@@
 %
-Here will consider only the dilatonic theory.
+Here we will consider only the dilatonic theory.
 
-Black holes in both classes support monopolar scalar hair and thus, when in binaries,
+BHs in both classes support monopolar scalar hair and thus, when in binaries,
 can source scalar dipole radiation and are therefore prone to be constrained with
@@
 The calculation of the QNMs in this theory is more complicated than in GR already for
-nonrotating black holes. The reason is due to the coupling between scalar field and
+nonrotating BHs. The reason is due to the coupling between scalar field and
 the Gauss-Bonnet invariant, which manifests into a coupling between scalar perturbation
@@
 \end{tikzpicture}
-\caption{Quasinormal modes of black holes in scalar-Gauss-Bonnet gravity.}
+\caption{Quasinormal modes of BHs in scalar-Gauss-Bonnet gravity.}
 \end{figure}
@@
 
-The theory admits the Schwarzschild black hole solution of GR, but predicts
-that spinning black holes have (secondary) scalar hair, which, unlike in
+The theory admits the Schwarzschild BH solution of GR, but predicts
+that spinning BHs have (secondary) scalar hair, which, unlike in
 scalar-Gauss-Bonnet gravity, is dipolar~\cite{Yunes:2009hc,Konno:2009kg}.
@@
 Consequently, the leading-scalar radiation channel is quadrupolar making this
-theory presently unconstrained by from the GWs from the inspiral of black hole
+theory presently unconstrained by from the GWs from the inspiral of BH
 binaries alone~\cite{Nair:2019iur,Perkins:2021mhb}.
@@
 Similarly to the case of scalar-Gauss-Bonnet gravity, the perturbations of nonrotating
-black holes in dynamical Chern-Simons gravity also have a coupling between scalar and
+BHs in dynamical Chern-Simons gravity also have a coupling between scalar and
 metric perturbations. However, the coupling is between the scalar and gravitational perturbations
@@
 \end{tikzpicture}
-\caption{Quasinormal modes of black holes in dynamical Chern-Simons gravity.}
+\caption{Quasinormal modes of BHs in dynamical Chern-Simons gravity.}
 \end{figure}
@@
 where $\ell$ is some length scale, assumed to be small compares to the length
-scale associated with a black hole, i.e., $\ell / M \ll 1$, and
+scale associated with a BH, i.e., $\ell / M \ll 1$, and
 $L^{(2n)}$ are corrections to the Einstein-Hilbert term action that
@@
 
-Black holes in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} for the dimension-six EFT
+BHs in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} for the dimension-six EFT
 and in Refs.~\cite{Cardoso:2018ptl} for the dimension-eight EFT.
@@
 %
-% In each of these theories, slowly-rotating black hole and their quasinormal mode spectra
+% In each of these theories, slowly-rotating BH and their quasinormal mode spectra
 % to leading order in spin have been calculated.
@@
 %
-For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$ terms, then we just have two additional degrees of freedom, $(\omega_k^{(0)}, \tau_k^{(0)})$ per mode $k$.
-We will call this parametrized waveform model $\pSEOB$ in this paper.
+For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$, terms for just the $k=(2,2,0)$ mode, then we would just have two additional degrees of freedom, $(\delta \omega_0^{(0)}, \delta \tau_0^{(0)})$.
+In this paper, we would restrict ourselves to corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
 %
-In this paper, we will restrict ourselves to the $k=(2,2,0)$ QNM and corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
+
+Using this parameterized waveform model, which we will call $\pSEOB$ in this paper, we infer bounds on our beyond-GR parameters for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}.
+We detail these results in Sec.~\ref{sec:results}.
+%
+%In this paper, we will restrict ourselves to the $k=(2,2,0)$ QNM and corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
 Assuming a prior which is uniform on the beyond-GR parameters, $(\ell, \{\delta \omega_k^{(j)}\},\{\delta \tau_k^{(j)}\})$, we employ a Bayesian framework to stochastically sample over the parameter space using the \texttt{LALInference} algorithm.~\cite{lallsuite}.
 %
-The bounds on these beyond-GR parameters, for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}, are provided in Sec.~\ref{sec:results}.
-
-\iffalse
-In the $\SEOB$ model constructed in Ref.~\cite{Cotesta:2018fcv}, the
-complex frequencies $\sigma_{l m 0}$ are expressed in terms of the
-final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the
-latter are related to the BBH's component masses and spins through
-NR--fitting-formulas obtained in
-GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the
-spirit of what was done in \paperone, we promote the QNM (complex)
-frequencies to be free parameters of the model, while keeping the
-inspiral-plunge modes $h_{l m}^\mathrm{inspiral-plunge}(t)$ fixed
-to their GR values. More explicitly, we introduce a parameterized
-version of the $\SEOB$ model where the frequency and the
-damping time of the ${l m 0}$ mode (i.e, $(\omega_{l m 0}, \tau
-_{l m 0})$) are defined through the fractional deviations, $(\delta
-\omega_{l m 0},\delta \tau_{l m 0})$, from the corresponding GR
-values~\cite{Gossan:2011ha,Meidam:2014jpa}.
-
-Thus,
-\begin{subequations}
-\begin{eqnarray}
-\omega_{l m 0} &=& \omega_{l m 0}^{\text{GR}}\, (1 + \delta \omega_{l m 0})\,,\label{eq:nongr_freqs_a} \\
-\tau _{l m 0} &=& \tau _{l m 0}^{\text{GR}}\, (1 + \delta \tau_{l m 0})\,. \label{eq:nongr_freqs_b}
-\end{eqnarray}
-\end{subequations}
-
-The GR quantities $( \omega_{l m 0}^{GR},\tau_{l m 0}^{GR})$ are
-constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
-\begin{subequations}
-\begin{eqnarray}
-\omega_{l m 0} &=& \omega_{l m 0}(m_1, m_2, \chi_1, \chi_2, \delta \omega_{l m 0}, \delta \tau_{l m 0})\,,\\
-\tau _{l m 0} &=& \tau _{l m 0}(m_1, m_2, \chi_1, \chi_2, \delta \omega_{l m 0}, \delta \tau_{l m 0})\,.
-\end{eqnarray}
-\end{subequations}
-We denote such a parameterized waveform model $\pSEOB$~\footnote{This
-waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{l m}$ to vary
-freely, the functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l
-  m}(t)$ in general also differ from the GR predictions, since
-those functions depend on the QNM complex frequencies, as can be seen
-from the expressions for $c_{i,c}^{l m}$ and $d_{1,c}^{l m}$ in Eqs.~(\ref{c1}),
-(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase)
-soon after merger deviates from the one predicted by GR.
-\fi
+%The bounds on these beyond-GR parameters, for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}, are detailed in Sec.~\ref{sec:results}.
 
@@
 \subsection{From theory-agnostic to theory-specific QNM results}
+\label{sec:theory_specific_qnm}
 
@@
 
-Now as we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating black holes
+Now as we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating BHs
 is modified gravity theories come in two families depending on their transformation upon a parity
@@
 %%%%%%%%%%%%%%%%%
-\section{Analysis using LIGO-Virgo data}
+\section{Results using LIGO-Virgo events}
 \label{sec:results}
@@
 
-% \hs{Say that we use GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp} and justify why.}
-
-We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
+\subsection{Bayesian formalism}
+If we assume that a GW signal observed in detector data $d$ is accurately described by our waveform model \pSEOB{}, we can infer the parameters of the model, $\bm{\lambda}$, given the hypotheis $\mathcal{H}$, using the Bayes theorem,
 %
-They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
-
 \begin{equation}
@@
 %
-where $d$ is the data and $\bm{\lambda}$ is a set of vectors that fully
-characterize the waveform.
+where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
+$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
+$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
+$P(d \vert \mathcal{H})$ the evidence. The set of parameters, $\bm{\lambda}$, detailed in Sec.~\ref{sec:review_pSEOB}
+include the set of beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$.
 %
-$P(\bm{\lambda} \vert \mathcal{H})$ is prior probability distribution,
-$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
-$P(d \vert \mathcal{H})$ the evidence.
-
-Our set of parameters is $\bm{\lambda} = \bm{\theta}_{\rm GR} \cup \bm{\theta}_{\rm nGR}$, where
-$\bm{\theta}_{\rm nGR} = \{\ell_{i}\}$ is a set of beyond-GR coupling constants.
+As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
+constants in the cases of EdGB and dCS theories, but two in the cubic and
+quartic EFTofGR. We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
+fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
 %
-As discussed in Sec.~\ref{sec:review_theories} there is a single coupling
-constants in the cases of EdGB and dCS theories, but two in the cubic and
-quartic EFTofGR.
 
@@
 denotes complex conjugation and $S_{n}(f)$ is the power spectrum density
-of the detector.
+of the detector. Assuming a speicifc prior distribution for our parameters, 
+we stochastically sample over the parameter space 
+using a \texttt{LALInference} Markhov Chain Monte Carlo 
+algorithm.~\cite{lallsuite}. We subsequently marginalise over the 
+remaining parameters to obtain the posterior probability distribution on $\ell$. 
+An example of this is shown in Fig. XX.
 
-With the posterior distribution function $P(\bm{\lambda} | d, \mathcal{H})$ determined, we can then
-marginalize over all nuisance parameters to obtain the posterior
-distribution function the $i$-th beyond-GR coupling constants $\ell_{i}$,
+\subsection{Event selection}
+
+% \hs{Say that we use GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp} and justify why.}
+
+%We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
 %
-\begin{equation}
-P(\ell_{i} | d, \mathcal{H}) =
-\int \dd \xi_{\rm GR} \,
-P(\bm{\lambda} | d, \mathcal{H}) \,.
-\label{eq:marg_posterior}
-\end{equation}
-%
+%They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
+Although the LIGO-Virgo detectors have observed 90 GW signals, we select, for our analyses in this paper, the ones that are likely to be the most promising probes of the BH ringdown using our method.
+In~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis in Sec.VIII A.2 (which is most similar to the \pSEOB{} model presented in this paper) identified two events which provided the strongest bounds on the dominant QNM measuments -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
+
+\ag{event selection, noise, PE settings, priors}
 

### 2022-02-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added a section on priors

@@
 %%%%%%%%%%%%%%%%%
+\subsection{Parameter Inference}
 
-\subsection{Bayesian formalism}
+\subsubsection{Bayesian formalism}
 If we assume that a GW signal observed in detector data $d$ is accurately described by our waveform model \pSEOB{}, we can infer the parameters of the model, $\bm{\lambda}$, given the hypotheis $\mathcal{H}$, using the Bayes theorem,
@@
 $P(d \vert \mathcal{H})$ the evidence. The set of parameters, $\bm{\lambda}$, detailed in Sec.~\ref{sec:review_pSEOB}
-include the set of beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$.
+include the set of beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}, \delta \tau_k^{(j)}\}$.
 %
@@
 
-\subsection{Event selection}
+\subsubsection{Priors}
+
+The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \text{sin} \iota$.
+For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the z-components~\footnote{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.} The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
+
+Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$, as already mentioned in the previous section, we would mostly hold $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$ to freely vary.
+For such cases, we assume a prior uniform between appropriate ranges on $\ell$.
+
+\subsubsection{Event selection}
 
@@
 
-\subsection{Einstein-dilaton-Gauss-Bonnet}
+\subsection{Results}
+
+\subsubsection{Einstein-dilaton-Gauss-Bonnet}
 \label{sec:results_edgb}
 
-\subsection{Dynamical Chern-Simons}
+\subsubsection{Dynamical Chern-Simons}
 \label{sec:results_dcs}
@@
 
-\subsection{Effective-field-theory of general relativity}
+\subsubsection{Effective-field-theory of general relativity}
 \label{sec:results_efts}

### 2022-02-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added short intro to section IV

@@
 \label{sec:results}
+
+In this section, we provide a basic outline of the Bayesian formalism we use to infer the properties of the underlying GW signal, identify the most promising events from the catalog of GW observations to base our analyses on, and discuss the key insights they provide in constraining predictions of momdified gravity theories.
+
 %%%%%%%%%%%%%%%%%
@@
 %They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
-Although the LIGO-Virgo detectors have observed 90 GW signals, we select, for our analyses in this paper, the ones that are likely to be the most promising probes of the BH ringdown using our method.
+
+%Although the LIGO-Virgo detectors have observed 90 GW signals, we select, for our analyses in this paper, the ones that are likely to be the most promising probes of the BH ringdown using our method.
 In~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis in Sec.VIII A.2 (which is most similar to the \pSEOB{} model presented in this paper) identified two events which provided the strongest bounds on the dominant QNM measuments -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
 
-\ag{event selection, noise, PE settings, priors}
+\ag{event selection, noise, PE settings}
 

### 2022-02-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added section on event selection

@@
 %They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
+The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an \emph{IMR} model which infers the properties of the underlying GW signal, including independently its ringdown properties, using the Bayesian formalism above.
+Naturally, the most promising candidates for our analyses are high-mass \emph{and} loud GW observations with a significant signal-to-noise ratio (SNR) in the post-merger signal.
+The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed signals not all of which are relevant for a BH ringdown analysis.
+In fact, in an accompanying paper~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis~\footnote{Sec.VIII A.2 in ~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model presented in this paper, identified two events which provided the strongest bounds on measurements of the dominant $(220)$ QNM -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
+These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are extremely similar in their source properties.
+These are also two of the loudest BBH signals observed to date with a total network SNR of XX and XX respectively.
+Moreover, and what is most relevant for our analysis, is that their SNRs in the just the post-inspiral (merger-ringdown) part of the signal are the loudest to date, XX and XX respectively (corresponding tables in TGR GWTC-1/3) making them significantly promising as probes of the BH ringdown.
 

### 2022-02-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
finished section on event selection; completed sec iv.A for now

@@
 
-% \hs{Say that we use GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp} and justify why.}
-
-%We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
-%
-%They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
-The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an \emph{IMR} model which infers the properties of the underlying GW signal, including independently its ringdown properties, using the Bayesian formalism above.
-Naturally, the most promising candidates for our analyses are high-mass \emph{and} loud GW observations with a significant signal-to-noise ratio (SNR) in the post-merger signal.
+The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an \emph{IMR} model which infers the properties of the underlying GW signal, including (independently) its ringdown properties, using the Bayesian formalism above.
+Naturally, the most promising candidates for our analyses are high-mass \emph{and} loud GW observations with a significant signal-to-noise ratio (SNR) in the post-merger part of the signal.
 The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed signals not all of which are relevant for a BH ringdown analysis.
@@
 These are also two of the loudest BBH signals observed to date with a total network SNR of XX and XX respectively.
-Moreover, and what is most relevant for our analysis, is that their SNRs in the just the post-inspiral (merger-ringdown) part of the signal are the loudest to date, XX and XX respectively (corresponding tables in TGR GWTC-1/3) making them significantly promising as probes of the BH ringdown.
+Moreover, and what is more relevant for our analysis, is their post-inspiral (merger-ringdown) SNRs, which at XX and XX respectively (see the columns for $\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and Table IV of ~\cite{LIGOScientific:2021sio}).
+In this paper, we are going to focus on these two GW events as our probes of the BH ringdown in alternative theories of gravity.
 
-%Although the LIGO-Virgo detectors have observed 90 GW signals, we select, for our analyses in this paper, the ones that are likely to be the most promising probes of the BH ringdown using our method.
-In~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis in Sec.VIII A.2 (which is most similar to the \pSEOB{} model presented in this paper) identified two events which provided the strongest bounds on the dominant QNM measuments -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
-
-\ag{event selection, noise, PE settings}
+The parameter inference in this paper follow configurations identical to the ones used on these events for the \textit{pSEOBNRv4HM} analysis in~\cite{LIGOScientific:2021sio}.
+GW150914 was a 2-detector event (HL) while GW200129 was 3-detector (HLV).
+We consequently use the same strain data $h(t)$, detector power-spectral-densities $S_n(f)$ and calibration envelopes as were used for the analyses in~\cite{LIGOScientific:2021sio}.
+The only difference between the sampling configurations is that we do not sample over the fractional deviations in the $(220)$ QNM frequencies and damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions.
+In the section to follow, we enumerate through the different theories and outline the highlight results.
+Wherever possible, we also combine results from multiple events to obtain the strongest possible bound on $\ell$.
 

### 2022-02-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added todo and spell-checked

@@
 % HS: temporary title. Feel free to add suggestions
-% \title{Probing higher-curvature gravity theories from binary BH ringdown signals}
 \title{Black-hole ringdown as a probe of higher-curvature gravity theories}
@@
 \begin{align}
-\omega_{\iota} &= \omega^{\rm K}_{\iota} \, (1 + \delta \omega_{\iota}), \\
-\tau_{\iota}   &= \tau^{\rm K}_{\iota}   \, (1 + \delta \tau_{\iota}),
+\omega_{J} &= \omega^{\rm K}_{J} \, (1 + \delta \omega_{J}), \\
+\tau_{J}   &= \tau^{\rm K}_{J}   \, (1 + \delta \tau_{J}),
 \end{align}
@@
 %
-where the $\iota$ collectively represents the QNM labels $\{l,\, m,\, n\}$.
+where the $J$ collectively represents the QNM labels $\{l,\, m,\, n\}$.
 
@@
 %
-Having selected this mode we can now obtain $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
+Having selected this branch of QNMs we can proceed to determine $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
 %
@@
 \hline
-sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.7$~km~\cite{Perkins:2021mhb} (GW) & \dots \\
-dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr} (EM+GW)  & \dots \\
+sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
+dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & \dots \\
 cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
@@
 
-In this section, we provide a basic outline of the Bayesian formalism we use to infer the properties of the underlying GW signal, identify the most promising events from the catalog of GW observations to base our analyses on, and discuss the key insights they provide in constraining predictions of momdified gravity theories.
+In this section, we provide a basic outline of the Bayesian formalism we use to
+infer the properties of the underlying GW signal, identify the most promising
+events from the catalog of GW observations to base our analyses on, and discuss
+the key insights they provide in constraining predictions of modified gravity
+theories.
 
@@
 \subsubsection{Bayesian formalism}
-If we assume that a GW signal observed in detector data $d$ is accurately described by our waveform model \pSEOB{}, we can infer the parameters of the model, $\bm{\lambda}$, given the hypotheis $\mathcal{H}$, using the Bayes theorem,
+If we assume that a GW signal observed in detector data $d$ is accurately
+described by our waveform model \pSEOB{}, we can infer the parameters of the
+model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using the Bayes
+theorem,
 %
@@
 \begin{equation}
-\ln \mathcal{L}(d \vert \bm{\lambda},\mathcal{H}) \propto
+\ln P(d \vert \bm{\lambda},\mathcal{H}) \propto
 - \tfrac{1}{2}
@@
 %
-where $\tilde{A}(f)$ is the Fourier transform of $A(t)$, the asterisk
-denotes complex conjugation and $S_{n}(f)$ is the power spectrum density
-of the detector. Assuming a speicifc prior distribution for our parameters, 
-we stochastically sample over the parameter space 
-using a \texttt{LALInference} Markhov Chain Monte Carlo 
-algorithm.~\cite{lallsuite}. We subsequently marginalise over the 
-remaining parameters to obtain the posterior probability distribution on $\ell$. 
-An example of this is shown in Fig. XX.
+where $\tilde{A}(f)$ is the Fourier transform of $A(t)$, the asterisk denotes
+complex conjugation and $S_{n}(f)$ is the power spectrum density of the
+detector.
+%
+Assuming a specific prior distribution for our parameters, we stochastically
+sample over the parameter space using a \texttt{LALInference} Markov Chain
+Monte Carlo algorithm.~\cite{lalsuite}. We subsequently marginalize over the
+remaining parameters to obtain the posterior probability distribution on
+$\ell$. An example of this is shown in Fig. XX.
 
@@
 
+\hs{Note to ourselves: as mentioned in~\cite{Maselli:2019mjd}:
+%
+``As customary in parametrized approaches, we focus on perturbative corrections by assuming $\gamma_{i} \delta \omega^{(n)} \ll 1$, $\gamma_{i} \delta \tau^{(n)} \ll 1$ and GR is recovered in the limit $\gamma_{i} \to 0$.''
+We should check this \emph{in addition} to the small-coupling approximation to argue whether we placed a bound or not.
+}
+
 \subsubsection{Einstein-dilaton-Gauss-Bonnet}
@@
 %
-The dotted line (labelled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
+The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
 given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
 %
-The dot-dashed line (labelled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
+The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
 given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.

### 2022-02-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: small changes

@@
 \begin{align}
-\omega_{\iota} &= (1/M) \sum_{j = 0}^{N} \, \chi^{j} \omega^{(j)}_{k} \, \left( 1 + \gamma \delta \omega^{(j)}_{k} \right), \\
-\tau_{\iota}   &= M     \sum_{j = 0}^{N} \, \chi^{j} \tau^{(j)}_{k}   \, \left( 1 + \gamma \delta \tau^{(j)}_{k} \right),
+\omega_{J} &= (1/M) \sum_{j = 0}^{N} \, \chi^{j} \omega^{(j)}_{k} \, \left( 1 + \gamma \delta \omega^{(j)}_{k} \right), \\
+\tau_{J}   &= M     \sum_{j = 0}^{N} \, \chi^{j} \tau^{(j)}_{k}   \, \left( 1 + \gamma \delta \tau^{(j)}_{k} \right),
 \end{align}
@@
 = \frac{\ell^{p}}{M_{\rm s}^{p}}
-%
-% = \frac{\ell^{p} (1 + z)^{p}}{M^{p}}
 %
@@
 %
-Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$ defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$, where $j$ ranges from 0 to the power of spin in Eqs.~\ref{eq:kerr_expansion} upto which we include corrections.
+Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$
+defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and
+$\{\delta \tau_k^{(j)}\}$, where $j$ ranges from zero to the power of spin in Eqs.~\eqref{eq:kerr_expansion}
+up to which we include corrections.
 %
@@
 %
-It is important to emphasize that our procedure is different from that of~\cite{Carullo:2021dui}
+It is important to emphasize that our procedure is different from that of Ref.~\cite{Carullo:2021dui}
 which, for a given value of $p$, varied all $\ell$, $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ parameters.
@@
 
-Now as we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating BHs
+As we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating BHs
 is modified gravity theories come in two families depending on their transformation upon a parity
@@
 Assuming a specific prior distribution for our parameters, we stochastically
-sample over the parameter space using a \texttt{LALInference} Markov Chain
+sample over the parameter space using a \texttt{LALInference} Markov-Chain
 Monte Carlo algorithm.~\cite{lalsuite}. We subsequently marginalize over the
-remaining parameters to obtain the posterior probability distribution on
-$\ell$. An example of this is shown in Fig. XX.
+remaining parameters to obtain the posterior probability distribution
+function~(PDF) on $\ell$. An example of this is shown in Fig. XX.
 

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: small updates
hs: upd figures
upd to results section

@@
 \usepackage{natbib}
-% \usepackage{amssymb}
+\usepackage{amssymb}
 \usepackage{xspace}
@@
     +
-    \footnotesize{\sum}_{n \geqslant 2} \ell^{2n - 2} L^{(2n)}
+    {\sum}_{n \geqslant 2} \ell^{2n - 2} L^{(2n)}
     \right],
@@
 The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed signals not all of which are relevant for a BH ringdown analysis.
-In fact, in an accompanying paper~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis~\footnote{Sec.VIII A.2 in ~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model presented in this paper, identified two events which provided the strongest bounds on measurements of the dominant $(220)$ QNM -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
+In fact, in an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM} analysis~\footnote{Sec.VIII A.2 in ~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model presented in this paper, identified two events which provided the strongest bounds on measurements of the dominant $(220)$ QNM -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
 These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are extremely similar in their source properties.
@@
 
-The parameter inference in this paper follow configurations identical to the ones used on these events for the \textit{pSEOBNRv4HM} analysis in~\cite{LIGOScientific:2021sio}.
-GW150914 was a 2-detector event (HL) while GW200129 was 3-detector (HLV).
-We consequently use the same strain data $h(t)$, detector power-spectral-densities $S_n(f)$ and calibration envelopes as were used for the analyses in~\cite{LIGOScientific:2021sio}.
-The only difference between the sampling configurations is that we do not sample over the fractional deviations in the $(220)$ QNM frequencies and damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions.
-In the section to follow, we enumerate through the different theories and outline the highlight results.
-Wherever possible, we also combine results from multiple events to obtain the strongest possible bound on $\ell$.
+The parameter inference in this paper follows configurations identical to the
+ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
+Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector event (HL) while
+GW200129 was 3-detector (HLV).
+%
+We consequently use the same strain data $h(t)$, detector
+power-spectral-densities $S_n(f)$ and calibration envelopes as were used for
+the analyses in Ref.~\cite{LIGOScientific:2021sio}.
+%
+The only difference between the sampling configurations is that we do not
+sample over the fractional deviations in the $(220)$ QNM frequencies and
+damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
+and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions.
+%
+In the section to follow, we enumerate through the different theories and
+outline the highlight results. Wherever possible, we also combine results from
+multiple events to obtain the strongest possible bound on $\ell$.
 
-\hs{Here we summarize the results of our PE runs. Combine the posteriors on the
-the non-GR parameter coming from different events. We could have a short
-subsection for each theory. We should quote two thresholds for claiming
-that we placed a bound, one using the secondary BH mass and another with
-the final BH mass.}
+% -----------------
+% Corner plots here
+% -----------------
+
+As a first test ...
 
@@
 
-\hs{Note to ourselves: as mentioned in~\cite{Maselli:2019mjd}:
+% -----------------
+% Explain threshold
+% -----------------
+
+\subsubsection{General remarks for the interpretation of our results}
+\label{sec:remaks}
+
+There are two requirements that we must take into account before
+we can confidently claim to have placed a constraint, with our model assumptions,
+with our parameter estimation study.
+
+First, as described in Sec.~\ref{sec:review_theories}, all theories that we consider must be considered as an
+effective field theory, meaning it has a sensible description only below an energy, or equivalently an length scale.
 %
-``As customary in parametrized approaches, we focus on perturbative corrections by assuming $\gamma_{i} \delta \omega^{(n)} \ll 1$, $\gamma_{i} \delta \tau^{(n)} \ll 1$ and GR is recovered in the limit $\gamma_{i} \to 0$.''
-We should check this \emph{in addition} to the small-coupling approximation to argue whether we placed a bound or not.
-}
+As a threshold for the validity of the EFT we use
+%
+\begin{equation}
+T_{\rm EFT} (\varepsilon; \, \mathfrak{m}) = \varepsilon \,  (G \mathfrak{m} / c^2)\,,
+\end{equation}
+%
+where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ the median value of one of the
+masses involved in the problem.
+%
+We also momentarily restored factor of $c$ and $G$ to emphasize that this is a quantity
+with dimensions of length and can hence be compared with the coupling strength $\ell$.
+%
+The parameter $T_{\rm EFT}$ was used in both
+Refs.~\cite{Nair:2019iur,Perkins:2021mhb} with $\varepsilon = 1/2$,
+but here we will assume $\varepsilon \in [0, 1]$.
+%
+We will say that a bound has been placed on $\ell$, if most of the support of
+the posterior distribution function $P(\ell)$ is in the interval $[0, \, T_{\rm EFT}(\varepsilon; \, \mathfrak{m})]$.
+%
+In practice, this can be quantified by the cumulative distribution function
+(CDF) associated to the marginalized posterior distribution $P(\ell)$,
+%
+\begin{equation}
+P(\ell \leqslant x) = \int_{-\infty}^{x} P(x) \, \dd x\,.
+\end{equation}
+%
+We will demand, for instance, that for a bound with 90\% credibility to be meaningfully placed that,
+%
+\begin{equation}
+% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
+P(\ell \leqslant T_{\rm EFT}) \leqslant 0.9 \,.
+\end{equation}
+
+%
+Another question to consider is: what is the mass $\mathfrak{m}$ that we should use?
+%
+In Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which attempted to constrain dCS and shift-symmetric sGB theories with the \emph{inspiral}
+signal alone, it was natural to chose the secondary's mass $m_2$ as the most conservative choice, since it is by definition the smallest mass
+and hence places the lowest threshold for the validity of either theory as an EFT.
+%
+In our problem, the answer is not as clear. On the one hand, since we are
+interested in the ringdown portion of the signal, it is natural to use the
+final mass $M_f$ to compute the threshold $T_{\rm EFT}$.
+%
+On the other hand, one may argue that the modified gravity theory under study
+should be be able to predict a full inspiral, merger, and ringdown of the black
+hole binary, and thus the same most conservative $m_2$ should be used.
+%
+Here we take an agnostic approach and consider both masses, $m_2$ and $M_f$, to
+establish $T_{\rm EFT}$, and we will compare how different assumptions yield
+different interpretations of the results of our parameter estimations.
+
+There is a second criteria we must also take into account. As already emphasized in Ref.~\cite{Maselli:2019mjd},
+the {\sc Parspec} is by construction perturbative. This means that the non-GR deformation parameters are small,
+i.e.,
+%
+\begin{equation}
+\gamma \delta \omega^{(j)} \ll 1 \,, \quad \textrm{and} \quad \gamma \delta \tau^{(j)} \ll 1 \,.
+\end{equation}
+%
+for all indices $j$ in the expansion in dimensionless spin $\chi$.
+%
+We will also construct posterior distributions on the parameters and check if most of their support
+is constrained to be much less than unity.
+
+% \hs{Note to ourselves: as mentioned in~\cite{Maselli:2019mjd}:
+% %
+% ``As customary in parametrized approaches, we focus on perturbative corrections by assuming $\gamma_{i} \delta \omega^{(n)} \ll 1$, $\gamma_{i} \delta \tau^{(n)} \ll 1$ and GR is recovered in the limit $\gamma_{i} \to 0$.''
+% We should check this \emph{in addition} to the small-coupling approximation to argue whether we placed a bound or not.
+% }
 
@@
 \label{sec:results_edgb}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/ssgb_posteriors.pdf}
+\caption{Template.}
+\label{fig:sGB_exec_sum}
+\end{figure}
 
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/posteriors_for_exs.pdf}
-\caption{Summary of our results.
-\hs{Maybe have some like this for an `executive summary'?}
+\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
+GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
+in spin QNM correction.
 }
 \label{fig:dCS_exec_sum}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
+\caption{(Color online).~The cumulative distribution function evaluated at the threshold $T(\varepsilon;\, m)$
+as a function of the parameter $\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source mass,
+and (orange curves) $m = M_{f}$, the remnant's source mass, without (solid curve) and with (dashed curves)
+linear in spin QNM corrections.
+}
+\label{fig:dcs_cdf}
 \end{figure}
@@
 %
-We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov, and
-Serguei~Ossokine for discussions.
+We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov,
+Serguei~Ossokine, and Helvi~Witek for discussions.
 %
-We thank the computational resources provided by the AEI, specifically the
+We also thank the computational resources provided by the AEI, specifically the
 {\sc Hypatia} cluster and Steffen Grunewald for assistance.

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: discussion on cs results

@@
 \newcommand{\SEOB}{\texttt{SEOBNR}}
+\newcommand{\gm}{\mathfrak{m}}
 
@@
 
-There are two requirements that we must take into account before
-we can confidently claim to have placed a constraint, with our model assumptions,
+There are two conditions that we must take into account before
+we can confidently claim to have placed a constraint, within our model's assumptions,
 with our parameter estimation study.
 
-First, as described in Sec.~\ref{sec:review_theories}, all theories that we consider must be considered as an
-effective field theory, meaning it has a sensible description only below an energy, or equivalently an length scale.
-%
-As a threshold for the validity of the EFT we use
-%
-\begin{equation}
-T_{\rm EFT} (\varepsilon; \, \mathfrak{m}) = \varepsilon \,  (G \mathfrak{m} / c^2)\,,
-\end{equation}
-%
-where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ the median value of one of the
-masses involved in the problem.
-%
-We also momentarily restored factor of $c$ and $G$ to emphasize that this is a quantity
-with dimensions of length and can hence be compared with the coupling strength $\ell$.
-%
-The parameter $T_{\rm EFT}$ was used in both
-Refs.~\cite{Nair:2019iur,Perkins:2021mhb} with $\varepsilon = 1/2$,
-but here we will assume $\varepsilon \in [0, 1]$.
+First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
+consider must be considered as an effective field theory, meaning it should be
+considered valid only below an energy scale, or equivalently, a length scale.
+%
+As a cut-off length scale for the validity of the EFT we use,
+%
+\begin{equation}
+\Lambda_{\rm EFT} (\varepsilon; \, \mathfrak{m}) = \varepsilon \,  (G \mathfrak{m} / c^2)\,,
+\end{equation}
+%
+where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
+value of one of the masses involved in the problem.
+%
+We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
+dimensions of length and hence can be compared to the coupling strength $\ell$.
+%
+The parameter $\Lambda_{\rm EFT}$ was used
+Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} with $\varepsilon = 1/2$,
+but here we  $\varepsilon \in [0, 1]$.
 %
 We will say that a bound has been placed on $\ell$, if most of the support of
-the posterior distribution function $P(\ell)$ is in the interval $[0, \, T_{\rm EFT}(\varepsilon; \, \mathfrak{m})]$.
+the posterior distribution function $P(\ell)$ is in the interval $[0, \, \Lambda_{\rm EFT}(\varepsilon; \, \mathfrak{m})]$.
 %
@@
 \begin{equation}
-P(\ell \leqslant x) = \int_{-\infty}^{x} P(x) \, \dd x\,.
-\end{equation}
-%
-We will demand, for instance, that for a bound with 90\% credibility to be meaningfully placed that,
+P(\ell \leqslant \ell') = \int_{-\infty}^{\,\ell'} P(\ell') \, \dd \ell'\,.
+\label{eq:def_cdf}
+\end{equation}
+%
+For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
 %
@@
 % \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
-P(\ell \leqslant T_{\rm EFT}) \leqslant 0.9 \,.
-\end{equation}
-
-%
-Another question to consider is: what is the mass $\mathfrak{m}$ that we should use?
-%
-In Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which attempted to constrain dCS and shift-symmetric sGB theories with the \emph{inspiral}
-signal alone, it was natural to chose the secondary's mass $m_2$ as the most conservative choice, since it is by definition the smallest mass
-and hence places the lowest threshold for the validity of either theory as an EFT.
+P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,.
+\label{eq:eft_bound}
+\end{equation}
+
+%
+Another question to consider is the following: what is the mass $\mathfrak{m}$ that we should use?
+%
+In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, which attempted to
+constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
+signal alone, it was natural to chose the secondary's mass $m_2$ as the most
+conservative choice, for it is by definition the smallest mass and hence
+places the lowest threshold for the validity of either theory as an EFT.
 %
 In our problem, the answer is not as clear. On the one hand, since we are
-interested in the ringdown portion of the signal, it is natural to use the
-final mass $M_f$ to compute the threshold $T_{\rm EFT}$.
+interested in the ringdown part of the signal, it is natural to use the
+final mass $M_f$ to compute the cut-off $\Lambda_{\rm EFT}$.
 %
 On the other hand, one may argue that the modified gravity theory under study
-should be be able to predict a full inspiral, merger, and ringdown of the black
+should be able to predict a full inspiral, merger, and ringdown of the black
 hole binary, and thus the same most conservative $m_2$ should be used.
 %
-Here we take an agnostic approach and consider both masses, $m_2$ and $M_f$, to
-establish $T_{\rm EFT}$, and we will compare how different assumptions yield
-different interpretations of the results of our parameter estimations.
-
-There is a second criteria we must also take into account. As already emphasized in Ref.~\cite{Maselli:2019mjd},
-the {\sc Parspec} is by construction perturbative. This means that the non-GR deformation parameters are small,
-i.e.,
-%
-\begin{equation}
-\gamma \delta \omega^{(j)} \ll 1 \,, \quad \textrm{and} \quad \gamma \delta \tau^{(j)} \ll 1 \,.
-\end{equation}
-%
-for all indices $j$ in the expansion in dimensionless spin $\chi$.
-%
-We will also construct posterior distributions on the parameters and check if most of their support
-is constrained to be much less than unity.
+Here we adopt an agnostic view and consider both masses, $m_2$ and $M_f$, to
+determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
+yield to different interpretations of the results of our parameter estimations.
+
+There is a second criteria we must also consider.
+%
+As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc Parspec}
+formalism is by construction perturbative. This means that the non-GR
+deformation parameters are small, i.e.,
+%
+\begin{equation}
+\gamma \, \delta \omega^{(j)} \ll 1 \,,
+\quad \textrm{and} \quad
+\gamma \, \delta \tau^{(j)} \ll 1 \,.
+\end{equation}
+%
+for all $j$ of the expansion in dimensionless spin $\chi$.
+%
+We will also construct posterior distributions on the parameters and check if
+most of their support is concentrated to a domain with values much smaller than
+unity.
 
@@
 \label{sec:results_dcs}
+
+We now turn our attention to dCS gravity.
+%
+In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
+function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
+(middle panel), with (dashed line) and without (solid line) spin corrections to
+dominant $l = m = 2$,~$n=0$~QNM.
+%
+Perhaps the most salient feature of these posteriors is that they are not
+peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
+deviation from GR. This is not the case. We must remember that in the {\sc
+Parspec} formalism the GR deviations are controlled by $\gamma \, \delta
+\omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$, and these, indeed, do peak at
+zero. (See Fig. xx discussed below.)
+%
+We also see that in both cases, that the inclusion leading-order-in-spin
+correction to the mode, displaces the posteriors towards smaller values of
+$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
+posterior peaks.
+%
+Finally, in the bottom panel, we show the combined result for both events.
+
+In Fig.~\ref{fig:dcs_cdf} we show the cumulative distribution function (CDF) as
+evaluates with Eq.~\eqref{eq:def_cdf}, with $\ell' = \Lambda_{\rm EFT}$,
+for both GW150914 (top panel) and GW200129 (bottom panel), where $\Lambda_{\rm EFT}$
+is calculated with either $\mathfrak{m} = m_2$ (blue curves) or $M_{f}$ (orange curves),
+and with $\varepsilon \in [0,\, 1]$.
+%
+For GW150914, we see that with $\gm = m_2$ that Eq.~\eqref{eq:eft_bound} is not
+satisfied unless $\varepsilon \approx 0.9$ (with only $j=0$ corrections) and
+$\varepsilon \approx 0.7$ (with both $j=0$ and $1$ corrections).
+%
+The situation is different if we use $\gm = M_f$. We find that with or without spin corrections
+that Eq.~\eqref{eq:eft_bound} can be satisfied with $\varepsilon \leq 1/2$, i.e., below the criteria
+used Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+%
+This means that with our model's assumptions and using the remnant's source mass $M_f$ to set the
+cut-off scale that we can claim an upper bound
+%
+\begin{equation}
+\ell_{\rm CS} \leqslant \Lambda_{\rm EFT}(1/2; \, M_{f}) = \dots \,.
+\quad \textrm{at 90\% credibility},
+\end{equation}
+%
+on dCS gravity and would constitute the first bound on this theory with
+gravitational-wave observations alone.
+%
+Let us consider GW200129 now.
 
@@
 
+\hs{Try to draw some conclusions that apply to all theories.}
+
 \hs{I think an important message of the paper is that we give indication that
@@
 
+\hs{Say that the fact we spin correction look important reinforces the
+importance of calculation QNMs of spinning black holes beyond-GR.}
+
+\hs{Say it is important to go beyond mode calculation and actually understand
+how the QNM appear in the GW signal.}
+
 %%%%%%%%%%%%%%%%%

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
upd to dcs section

@@
 In the section to follow, we enumerate through the different theories and
-outline the highlight results. Wherever possible, we also combine results from
+outline the highlight results. Whenever possible, we also combine results from
 multiple events to obtain the strongest possible bound on $\ell$.
@@
 
-\subsubsection{General remarks for the interpretation of our results}
+\subsubsection{General remarks on the interpretation of our results}
 \label{sec:remaks}
@@
 unity.
+
+When possible, we also combine the marginalized posterior distribution on
+$\ell$ for both event GW150914 and GW200129. To do so, we employ the same
+approach as Ref.~\cite{Perkins:2021mhb} which relies in obtaining a kerneld
+density estimator (KDE) as an approximation for the posterior distribution on
+$\ell$ for each individual events which are then multiplied together to yield
+the cumulative posterior.
+%
+This method can have difficulties in dealing with hard cut-offs in the
+distribution, such as the one we impose at $\ell = 0$. We address this issue as
+done in Ref.~\cite{Perkins:2021mhb}, by first doubling our number of samples as
+$\{ s_i \} \cup \{ - s_i \}$, i.e., mirroring the samples across $\ell = 0$.
+%
+We then renormalize the associated KDE numerically in the range $\ell = [0,
+\infty]$.
 
@@
 %
-The situation is different if we use $\gm = M_f$. We find that with or without spin corrections
-that Eq.~\eqref{eq:eft_bound} can be satisfied with $\varepsilon \leq 1/2$, i.e., below the criteria
-used Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+The situation is different if we use $\gm = M_f$. In this case, we find that
+with or without spin corrections that Eq.~\eqref{eq:eft_bound} can be satisfied
+with $\varepsilon \leq 1/2$, i.e., below the criteria used
+Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
 %
@@
 %
-Let us consider GW200129 now.
+These conclusions for GW150914 are shared with GW200129.
 
@@
 and (orange curves) $m = M_{f}$, the remnant's source mass, without (solid curve) and with (dashed curves)
-linear in spin QNM corrections.
+linear in spin QNM corrections. The horizontal lines lay at 0.68 and 0.90.
 }

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: template figures

@@
 
-\subsection{Results}
-
-% -----------------
-% Explain threshold
-% -----------------
-
-\subsubsection{General remarks on the interpretation of our results}
-\label{sec:remaks}
-
-There are two conditions that we must take into account before
-we can confidently claim to have placed a constraint, within our model's assumptions,
-with our parameter estimation study.
-
-First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
-consider must be considered as an effective field theory, meaning it should be
-considered valid only below an energy scale, or equivalently, a length scale.
-%
-As a cut-off length scale for the validity of the EFT we use,
-%
-\begin{equation}
-\Lambda_{\rm EFT} (\varepsilon; \, \mathfrak{m}) = \varepsilon \,  (G \mathfrak{m} / c^2)\,,
-\end{equation}
-%
-where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
-value of one of the masses involved in the problem.
-%
-We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
-dimensions of length and hence can be compared to the coupling strength $\ell$.
-%
-The parameter $\Lambda_{\rm EFT}$ was used
-Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} with $\varepsilon = 1/2$,
-but here we  $\varepsilon \in [0, 1]$.
-%
-We will say that a bound has been placed on $\ell$, if most of the support of
-the posterior distribution function $P(\ell)$ is in the interval $[0, \, \Lambda_{\rm EFT}(\varepsilon; \, \mathfrak{m})]$.
-%
-In practice, this can be quantified by the cumulative distribution function
-(CDF) associated to the marginalized posterior distribution $P(\ell)$,
-%
-\begin{equation}
-P(\ell \leqslant \ell') = \int_{-\infty}^{\,\ell'} P(\ell') \, \dd \ell'\,.
-\label{eq:def_cdf}
-\end{equation}
-%
-For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
-%
-\begin{equation}
-% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
-P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,.
-\label{eq:eft_bound}
-\end{equation}
-
-%
-Another question to consider is the following: what is the mass $\mathfrak{m}$ that we should use?
-%
-In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, which attempted to
-constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
-signal alone, it was natural to chose the secondary's mass $m_2$ as the most
-conservative choice, for it is by definition the smallest mass and hence
-places the lowest threshold for the validity of either theory as an EFT.
-%
-In our problem, the answer is not as clear. On the one hand, since we are
-interested in the ringdown part of the signal, it is natural to use the
-final mass $M_f$ to compute the cut-off $\Lambda_{\rm EFT}$.
-%
-On the other hand, one may argue that the modified gravity theory under study
-should be able to predict a full inspiral, merger, and ringdown of the black
-hole binary, and thus the same most conservative $m_2$ should be used.
-%
-Here we adopt an agnostic view and consider both masses, $m_2$ and $M_f$, to
-determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
-yield to different interpretations of the results of our parameter estimations.
-
-There is a second criteria we must also consider.
-%
-As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc Parspec}
-formalism is by construction perturbative. This means that the non-GR
-deformation parameters are small, i.e.,
-%
-\begin{equation}
-\gamma \, \delta \omega^{(j)} \ll 1 \,,
-\quad \textrm{and} \quad
-\gamma \, \delta \tau^{(j)} \ll 1 \,.
-\end{equation}
-%
-for all $j$ of the expansion in dimensionless spin $\chi$.
-%
-We will also construct posterior distributions on the parameters and check if
-most of their support is concentrated to a domain with values much smaller than
-unity.
+\subsubsection{Stacking posteriors}
+\label{sec:stack}
 
@@
 
+\subsubsection{General remarks on the interpretation of our results}
+\label{sec:remaks}
+
+There are two conditions that we must take into account before
+we can confidently claim to have placed a constraint, within our model's assumptions,
+with our parameter estimation study.
+
+First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
+consider must be considered as an effective field theory, meaning it should be
+considered valid only below an energy scale, or equivalently, a length scale.
+%
+As a cut-off length scale for the validity of the EFT we use,
+%
+\begin{equation}
+\Lambda_{\rm EFT} (\varepsilon; \, \mathfrak{m}) = \varepsilon \,  (G \mathfrak{m} / c^2)\,,
+\end{equation}
+%
+where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
+value of one of the masses involved in the problem.
+%
+We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
+dimensions of length and hence can be compared to the coupling strength $\ell$.
+%
+The parameter $\Lambda_{\rm EFT}$ was used
+Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} with $\varepsilon = 1/2$,
+but here we  $\varepsilon \in [0, 1]$.
+%
+We will say that a bound has been placed on $\ell$, if most of the support of
+the posterior distribution function $P(\ell)$ is in the interval $[0, \, \Lambda_{\rm EFT}(\varepsilon; \, \mathfrak{m})]$.
+%
+In practice, this can be quantified by the cumulative distribution function
+(CDF) associated to the marginalized posterior distribution $P(\ell)$,
+%
+\begin{equation}
+P(\ell \leqslant \ell') = \int_{-\infty}^{\,\ell'} P(\ell') \, \dd \ell'\,.
+\label{eq:def_cdf}
+\end{equation}
+%
+For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
+%
+\begin{equation}
+% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
+P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,.
+\label{eq:eft_bound}
+\end{equation}
+
+%
+Another question to consider is the following: what is the mass $\mathfrak{m}$ that we should use?
+%
+In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, which attempted to
+constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
+signal alone, it was natural to chose the secondary's mass $m_2$ as the most
+conservative choice, for it is by definition the smallest mass and hence
+places the lowest threshold for the validity of either theory as an EFT.
+%
+In our problem, the answer is not as clear. On the one hand, since we are
+interested in the ringdown part of the signal, it is natural to use the
+final mass $M_f$ to compute the cut-off $\Lambda_{\rm EFT}$.
+%
+On the other hand, one may argue that the modified gravity theory under study
+should be able to predict a full inspiral, merger, and ringdown of the black
+hole binary, and thus the same most conservative $m_2$ should be used.
+%
+Here we adopt an agnostic view and consider both masses, $m_2$ and $M_f$, to
+determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
+yield to different interpretations of the results of our parameter estimations.
+
+There is a second criteria we must also consider.
+%
+As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc Parspec}
+formalism is by construction perturbative. This means that the non-GR
+deformation parameters are small, i.e.,
+%
+\begin{equation}
+\gamma \, \delta \omega^{(j)} \ll 1 \,,
+\quad \textrm{and} \quad
+\gamma \, \delta \tau^{(j)} \ll 1 \,.
+\end{equation}
+%
+for all $j$ of the expansion in dimensionless spin $\chi$.
+%
+We will also construct posterior distributions on the parameters and check if
+most of their support is concentrated to a domain with values much smaller than
+unity.
+
+\subsection{Results}
+
+% -----------------
+% Explain threshold
+% -----------------
+
 % \hs{Note to ourselves: as mentioned in~\cite{Maselli:2019mjd}:
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/ssgb_posteriors.pdf}
-\caption{Template.}
+\includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function in EdGB gravity
+for the coupling constant $\ell_{\rm GB}$ for GW150914 (top panel), GW200129 (middle panel)
+and combined events (bottom panel).
+%
+In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
+in spin QNM correction.}
 \label{fig:sGB_exec_sum}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
+\caption{(Color online).~The cumulative distribution function evaluated at the
+threshold $T(\varepsilon;\, m)$ EdGB gravity as a function of the parameter
+$\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source
+mass, and (orange curves) $m = M_{f}$, the remnant's source mass, without
+(solid curve) and with (dashed curves) linear in spin QNM corrections. The
+horizontal lines lay at 0.68 and 0.90.
+}
+\label{fig:dcs_cdf}
 \end{figure}

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: polishing text

@@
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-1}
+\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,amsfonts,amsmath,longbibliography]{revtex4-1}
 \usepackage{epsfig}
@@
 \newcommand{\gm}{\mathfrak{m}}
+\newcommand{\msun}{~{\rm M}_{\odot}}
 
@@
 %
-where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(l,m)$.\footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.} As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{} \footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
+where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(l,m)$.\footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.} As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
 The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
@@
 Moreover, and what is more relevant for our analysis, is their post-inspiral (merger-ringdown) SNRs, which at XX and XX respectively (see the columns for $\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and Table IV of ~\cite{LIGOScientific:2021sio}).
-In this paper, we are going to focus on these two GW events as our probes of the BH ringdown in alternative theories of gravity.
+In this paper, we are going to focus on these two GW events as our probes of the BH ringdown in modified theories of gravity.
 
@@
 \begin{equation}
-\Lambda_{\rm EFT} (\varepsilon; \, \mathfrak{m}) = \varepsilon \,  (G \mathfrak{m} / c^2)\,,
+\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, G \mathfrak{m} / c^2 \,,
+\label{eq:def_cutoff}
 \end{equation}
@@
 %
-The parameter $\Lambda_{\rm EFT}$ was used
-Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} with $\varepsilon = 1/2$,
-but here we  $\varepsilon \in [0, 1]$.
+In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
+but here we consider $\varepsilon \in [0, 1]$.
 %
 We will say that a bound has been placed on $\ell$, if most of the support of
-the posterior distribution function $P(\ell)$ is in the interval $[0, \, \Lambda_{\rm EFT}(\varepsilon; \, \mathfrak{m})]$.
-%
-In practice, this can be quantified by the cumulative distribution function
+the posterior distribution function $P(\ell)$ is in the interval
+$[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
+%
+In practice, this can be quantified through the cumulative distribution function
 (CDF) associated to the marginalized posterior distribution $P(\ell)$,
@@
 % \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
-P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,.
+P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
 \label{eq:eft_bound}
 \end{equation}
-
-%
-Another question to consider is the following: what is the mass $\mathfrak{m}$ that we should use?
+%
+and likewise for other percentiles.
+
+Another question we must consider is the following: what is the mass $\mathfrak{m}$ that we should use
+in Eq.~\eqref{eq:def_cutoff}?
 %
@@
 constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
-signal alone, it was natural to chose the secondary's mass $m_2$ as the most
+the GW signal alone, it was natural to chose the secondary's mass $m_2$ as the most
 conservative choice, for it is by definition the smallest mass and hence
@@
 should be able to predict a full inspiral, merger, and ringdown of the black
-hole binary, and thus the same most conservative $m_2$ should be used.
-%
-Here we adopt an agnostic view and consider both masses, $m_2$ and $M_f$, to
+hole binary before we can even make such a test, and thus the same, more conservative choice
+$\gm = m_2$ should be used.
+%
+Here we adopt an agnostic view to this question and consider \emph{both} masses, $m_2$ and $M_f$, to
 determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
@@
 \caption{(Color online).~The cumulative distribution function evaluated at the
-threshold $T(\varepsilon;\, m)$ EdGB gravity as a function of the parameter
+cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
 $\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant \Lambda_{\rm EFT}(1/2; \, M_{f}) = \dots \,.
+\ell_{\rm CS} \leqslant 46.5~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
 \quad \textrm{at 90\% credibility},
@@
 %
-These conclusions for GW150914 are shared with GW200129.
+We also note that since the CDF grows fast in approximate domain $\varepsilon = [0.2, 0.4]$,
+that a stronger, albeit at lower credibility,
+%
+\begin{equation}
+\ell_{\rm CS} \leqslant 27.4~\textrm{km}~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
+\quad \textrm{at 68\% credibility},
+\end{equation}
+%
+can also be placed, when we include the $j=1$ QNM correction.
+
+We can draw qualitatively similar conclusions from the GW200129 event.
+In particular, we find,
+%
+\begin{equation}
+\ell_{\rm CS} \leqslant 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
+\quad \textrm{at 90\% credibility},
+\end{equation}
+%
+and
+%
+\begin{equation}
+\ell_{\rm CS} \leqslant 19.3~\textrm{km}~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
+\quad \textrm{at 68\% credibility},
+\end{equation}
+%
+when we include the $j=1$ QNM correction.
+
+These slightly stronger bound are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
+for GW200129 (compare the top and middle panels in Fig.~\ref{fig:dCS_exec_sum}), and in part due to
+the smaller median remmant ($M_{f} \approx 59.5\msun$ versus $M_{f} \approx 61.8\msun$ for GW150914).
 
@@
 \includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
-\caption{(Color online).~The cumulative distribution function evaluated at the threshold $T(\varepsilon;\, m)$
+\caption{(Color online).~The cumulative distribution function evaluated at the cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$
 as a function of the parameter $\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source mass,
@@
 linear in spin QNM corrections. The horizontal lines lay at 0.68 and 0.90.
+%
+We see that the CDF at $\varepsilon = 1/2$ is approximately one when $\gm =
+M_{f}$ for both events, with and without including the $j = 1$ dCS corrections
+to the dominat QNM.
 }

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more text

@@
 %
-\hs{Add a column with the constraint (if any) that we placed.}
-\hs{TODO: add which runs are done and which need to be done.}
+% \hs{Add a column with the constraint (if any) that we placed.}
+% \hs{TODO: add which runs are done and which need to be done.}
 }
@@
 \gamma \, \delta \tau^{(j)} \ll 1 \,.
+\label{eq:parspec_bound}
 \end{equation}
@@
 cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
-$\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source
-mass, and (orange curves) $m = M_{f}$, the remnant's source mass, without
+$\varepsilon$ for both (blue curves) $\gm = m_2$, the secondary's source
+mass, and (orange curves) $\gm = M_{f}$, the remnant's source mass, without
 (solid curve) and with (dashed curves) linear in spin QNM corrections. The
@@
 \caption{(Color online).~The cumulative distribution function evaluated at the cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$
-as a function of the parameter $\varepsilon$ for both (blue curves) $m = m_2$, the secondary's source mass,
-and (orange curves) $m = M_{f}$, the remnant's source mass, without (solid curve) and with (dashed curves)
+as a function of the parameter $\varepsilon$ for both $\gm = m_2$ (blue curves), the secondary's source mass,
+and $\gm = M_{f}$ (orange curves), the remnant's source mass, without (solid curve) and with (dashed curves)
 linear in spin QNM corrections. The horizontal lines lay at 0.68 and 0.90.
@@
 \end{figure}
+
+\begin{table}[h]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound \\
+\hline
+GW150914 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
+GW150914 & $j = 0, 1$ & Yes & No  & --                                 \\
+GW200129 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
+GW200129 & $j = 0, 1$ & Yes & No  & --                                 \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results for dCS gravity.
+%
+We assume $\varepsilon = 1/2$.}
+\end{table}
 

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: included combined constraint to dcs section and table

@@
 \usepackage{graphicx}
-\usepackage[dvipsnames]{xcolor}
+\usepackage[dvipsnames,table]{xcolor}
 \usepackage{bm}
@@
 sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
-dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & \dots \\
+EdGB      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
 cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
@@
 \omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
-\emph{only parity-even corrections} and the second entries by considering
-\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
-$\lambda_{\rm e,o}$ are degenerate with the length scale $\ell$.
-%
-% \hs{Add a column with the constraint (if any) that we placed.}
-% \hs{TODO: add which runs are done and which need to be done.}
+only parity-even corrections and the second entries by considering
+only parity-odd corrections.
+%
+In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
+with the length scale $\ell$.
+%
 }
@@
 \begin{equation}
-P(\ell \leqslant \ell') = \int_{-\infty}^{\,\ell'} P(\ell') \, \dd \ell'\,.
+P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} P(\ell') \, \dd \ell'\,.
 \label{eq:def_cdf}
@@
 
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
+GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
+in spin QNM correction.
+%
+We stress that posteriors obtained including $j=1$ corrections, violated conditions~\eqref{eq:parspec_bound}
+and therefore should not be used to draw meaningful conclusions. We show them for illustrative purposes
+and also to emphasize the importance of taking conditions~\eqref{eq:eft_bound} and~\eqref{eq:parspec_bound}
+simultaneously into consideration when analyzing the results of the parameter estimation.
+}
+\label{fig:dCS_exec_sum}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
+\caption{(Color online).~The cumulative distribution function evaluated at the
+cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$ as a function of the parameter $\varepsilon$ for both
+$\gm = m_2$ (solid and dashed lines) and $\gm = M_{f}$ (dot-dashed and dotted lines) without
+(blue lines) and with (orange lines) linear-in-spin QNM corrections.
+The horizontal lines lay at 0.68 and 0.90.
+%
+We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
+1/2$ for both events, with and without including the $j = 1$ dCS corrections to
+the dominant QNM.
+}
+\label{fig:dcs_cdf}
+\end{figure}
+
 We now turn our attention to dCS gravity.
@@
 In Fig.~\ref{fig:dcs_cdf} we show the cumulative distribution function (CDF) as
-evaluates with Eq.~\eqref{eq:def_cdf}, with $\ell' = \Lambda_{\rm EFT}$,
+evaluates with Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT}$,
 for both GW150914 (top panel) and GW200129 (bottom panel), where $\Lambda_{\rm EFT}$
@@
 with or without spin corrections that Eq.~\eqref{eq:eft_bound} can be satisfied
-with $\varepsilon \leq 1/2$, i.e., below the criteria used
+with $\varepsilon \leqslant 1/2$, i.e., below the criteria used
 Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 46.5~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
-\quad \textrm{at 90\% credibility},
+\ell_{\rm CS} \leqslant 42.6~\textrm{km}
+% ~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
+\quad \textrm{(90\% credibility)},
 \end{equation}
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 27.4~\textrm{km}~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
+\ell_{\rm CS} \leqslant 37.4~\textrm{km}
+% ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
 \quad \textrm{at 68\% credibility},
@@
 %
-can also be placed, when we include the $j=1$ QNM correction.
+can also be placed, when $j=0$.
 
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
-\quad \textrm{at 90\% credibility},
+\ell_{\rm CS} \leqslant 36.6~\textrm{km}
+% 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
+\quad \textrm{(90\% credibility)},
 \end{equation}
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 19.3~\textrm{km}~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
-\quad \textrm{at 68\% credibility},
-\end{equation}
-%
-when we include the $j=1$ QNM correction.
-
-These slightly stronger bound are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
+\ell_{\rm CS} \leqslant 29.1~\textrm{km}
+% ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
+\quad \textrm{(68\% credibility)},
+\end{equation}
+%
+when $j=0$.
+%
+These stronger bound are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
 for GW200129 (compare the top and middle panels in Fig.~\ref{fig:dCS_exec_sum}), and in part due to
-the smaller median remmant ($M_{f} \approx 59.5\msun$ versus $M_{f} \approx 61.8\msun$ for GW150914).
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
-GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-%
-In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
-in spin QNM correction.
-}
-\label{fig:dCS_exec_sum}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
-\caption{(Color online).~The cumulative distribution function evaluated at the cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$
-as a function of the parameter $\varepsilon$ for both $\gm = m_2$ (blue curves), the secondary's source mass,
-and $\gm = M_{f}$ (orange curves), the remnant's source mass, without (solid curve) and with (dashed curves)
-linear in spin QNM corrections. The horizontal lines lay at 0.68 and 0.90.
-%
-We see that the CDF at $\varepsilon = 1/2$ is approximately one when $\gm =
-M_{f}$ for both events, with and without including the $j = 1$ dCS corrections
-to the dominat QNM.
-}
-\label{fig:dcs_cdf}
-\end{figure}
+the smaller median remnant ($M_{f} \approx 59.5\msun$ versus $M_{f} \approx 61.8\msun$ for GW150914).
+
+We also found for both GW events, that the
+perturbative-conditions~\ref{eq:parspec_bound} imposed by the {\sc Parspec}
+formalism are violated for the $\gamma_{\rm CS} \delta \tau^{(1)}$ coefficient.
+%
+This means that we cannot use these posterior to infer any meaningful bound on dCS gravity.
+%
+Now, since both event individually led to a bound on $\ell_{\rm CS}$ (assuming a cut-off scale for $\gm = M_{f}$
+and $j = 0$), we can combine the posteriors to obtain the cumulative bound,
+%
+\begin{equation}
+\ell_{\rm CS} \leqslant 34.5~\textrm{km}
+\quad \textrm{(90\% credibility)},
+\end{equation}
+%
+which is the main result of this section.
+%
+This bound is approximately a factor of four weaker than that placed by
+Ref.~\cite{Silva:2020acr}, but
+%
+(i) relies only on GW observations and
+%
+(ii) suggests that a ringdown analysis can potentially place constraints on
+theories which evade GW tests using inspiral information alone, such as the
+case of dCS gravity~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+%
+In Table~\ref{tab:summary_dcs} we summarize our findings of this section.
 
@@
 \hline
-Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound \\
+Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound ($\gm = M_{f}$) \\
 \hline
-GW150914 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
+GW150914 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant 46.5$~km \\
 GW150914 & $j = 0, 1$ & Yes & No  & --                                 \\
-GW200129 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant \dots$~km \\
+GW200129 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant 43.9$~km \\
 GW200129 & $j = 0, 1$ & Yes & No  & --                                 \\
+Combined & $j = 0$    & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
+Combined & $j = 0, 1$ & Yes & No  & --                                 \\
 \hline
@@
 \end{tabular}
-\caption{Detailed summary of our results for dCS gravity.
-%
-We assume $\varepsilon = 1/2$.}
+\caption{Detailed summary of our results for dCS gravity for GW150914, GW200129, and
+combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+%
+We found that while our posteriors satisfy the condition~\eqref{eq:eft_bound} (with $\varepsilon = 1/2$),
+they do not obey the condition~\eqref{eq:parspec_bound} for $j = 1$. This means
+that our results for $j=0$ are the only ones we can confidently quote.
+%
+The combined bound, which is also quoted in Table~\ref{tab:ref_theories_qnms},
+is $\ell_{\rm CS} \leqslant 34.5$~km.
+}
+\label{tab:summary_dcs}
 \end{table}
@@
 
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
-\caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
-The posterior shows that information was gained on this parameter relative to
-the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
-%
-The vertical lines represent two threshold for the validity of the theory as
-an EFT.
-%
-The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
-given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
-%
-The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
-given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
-%
-For both, we used $\varepsilon = 0.5$.
-%
-If we take the latter as a length scale for the validity of dCS as an EFT, we
-have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
-approximation of our formalism.
-}
-\label{fig:dCS_bounds}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
-\caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
-The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
-in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
-}
-\label{fig:dCS_gamma_plot}
-\end{figure}
+% \begin{figure}[t]
+% \includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
+% \caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
+% The posterior shows that information was gained on this parameter relative to
+% the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
+% %
+% The vertical lines represent two threshold for the validity of the theory as
+% an EFT.
+% %
+% The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
+% given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
+% %
+% The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
+% given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
+% %
+% For both, we used $\varepsilon = 0.5$.
+% %
+% If we take the latter as a length scale for the validity of dCS as an EFT, we
+% have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
+% approximation of our formalism.
+% }
+% \label{fig:dCS_bounds}
+% \end{figure}
+%
+% \begin{figure}[t]
+% \includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
+% \caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
+% The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
+% in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
+% }
+% \label{fig:dCS_gamma_plot}
+% \end{figure}
 
@@
 We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov,
-Serguei~Ossokine, and Helvi~Witek for discussions.
+Serguei~Ossokine, Scott~E.~Perkins, and Helvi~Witek for discussions.
 %

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: organizing a bit

@@
 peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
-deviation from GR. This is not the case. We must remember that in the {\sc
-Parspec} formalism the GR deviations are controlled by $\gamma \, \delta
-\omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$, and these, indeed, do peak at
-zero. (See Fig. xx discussed below.)
+deviation from GR. This is not the case.
+%
+We must remember that in the {\sc Parspec} formalism that the GR deviations
+are controlled by $\gamma \, \delta \omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$.
+We verified that these quantities do indeed peak at zero indicating consistency with GR.
 %
@@
 We also found for both GW events, that the
-perturbative-conditions~\ref{eq:parspec_bound} imposed by the {\sc Parspec}
-formalism are violated for the $\gamma_{\rm CS} \delta \tau^{(1)}$ coefficient.
-%
-This means that we cannot use these posterior to infer any meaningful bound on dCS gravity.
-%
-Now, since both event individually led to a bound on $\ell_{\rm CS}$ (assuming a cut-off scale for $\gm = M_{f}$
-and $j = 0$), we can combine the posteriors to obtain the cumulative bound,
+perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc Parspec}
+formalism is violated for the $\gamma_{\rm CS} \delta \tau^{(1)}$ coefficient.
+%
+This means that we cannot use these posterior to infer any meaningful bound on dCS gravity
+and that is why we quoted only the $j=0$ bound above.
+
+Finally, since both event individually led to a bound on $\ell_{\rm CS}$
+(assuming a cut-off scale for $\gm = M_{f}$ and $j = 0$), we can combine the
+posteriors to obtain the cumulative bound,
 %

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more refs

@@
 \begin{abstract}
+% General
+% Motivation
+% What we do
+% Main conclusion
 \end{abstract}
@@
 
-\begin{figure}
-\begin{tikzpicture}[baseline,>=stealth]
-    % \draw[help lines, gray] (-4, -2) grid (4, 2);
-    \draw[->] (-2.5, 0) -- (-1.75, +0.5);
-    \draw[->] (-2.5, 0) -- (-1.75, -0.5);
-
-    \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \varphi\}$};
-
-    \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
-    \node at (-1, +0.5) {$\{ \textcolor{rred}{h^{\rm p}_{\alpha\beta}}, \, \varphi\}$};
-    \node at (-1, -0.5) {$h^{\rm a}_{\alpha\beta}$};
-
-    \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
-    \node at (+1, +0.5) {\dots};
-    \node at (+1, -0.5) {\dots};
-\end{tikzpicture}
-\caption{Quasinormal modes of BHs in scalar-Gauss-Bonnet gravity.}
-\end{figure}
+% \begin{figure}
+% \begin{tikzpicture}[baseline,>=stealth]
+%     % \draw[help lines, gray] (-4, -2) grid (4, 2);
+%     \draw[->] (-2.5, 0) -- (-1.75, +0.5);
+%     \draw[->] (-2.5, 0) -- (-1.75, -0.5);
+%
+%     \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \varphi\}$};
+%
+%     \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
+%     \node at (-1, +0.5) {$\{ \textcolor{rred}{h^{\rm p}_{\alpha\beta}}, \, \varphi\}$};
+%     \node at (-1, -0.5) {$h^{\rm a}_{\alpha\beta}$};
+%
+%     \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
+%     \node at (+1, +0.5) {\dots};
+%     \node at (+1, -0.5) {\dots};
+% \end{tikzpicture}
+% \caption{Quasinormal modes of BHs in scalar-Gauss-Bonnet gravity.}
+% \end{figure}
 
@@
 
-\begin{figure}
-\begin{tikzpicture}[baseline,>=stealth]
-    % \draw[help lines, gray] (-4, -2) grid (4, 2);
-    \draw[->] (-2.5, 0) -- (-1.75, +0.5);
-    \draw[->] (-2.5, 0) -- (-1.75, -0.5);
-
-    \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \vartheta\}$};
-
-    \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
-    \node at (-1, +0.5) {$h^{\rm p}_{\alpha\beta}$};
-    \node at (-1, -0.5) {$\{ \textcolor{rred}{h^{\rm a}_{\alpha\beta}}, \, \vartheta\}$};
-
-    \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
-    \node at (+1, +0.5) {\dots};
-    \node at (+1, -0.5) {\dots};
-\end{tikzpicture}
-\caption{Quasinormal modes of BHs in dynamical Chern-Simons gravity.}
-\end{figure}
+% \begin{figure}
+% \begin{tikzpicture}[baseline,>=stealth]
+%     % \draw[help lines, gray] (-4, -2) grid (4, 2);
+%     \draw[->] (-2.5, 0) -- (-1.75, +0.5);
+%     \draw[->] (-2.5, 0) -- (-1.75, -0.5);
+%
+%     \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \vartheta\}$};
+%
+%     \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
+%     \node at (-1, +0.5) {$h^{\rm p}_{\alpha\beta}$};
+%     \node at (-1, -0.5) {$\{ \textcolor{rred}{h^{\rm a}_{\alpha\beta}}, \, \vartheta\}$};
+%
+%     \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
+%     \node at (+1, +0.5) {\dots};
+%     \node at (+1, -0.5) {\dots};
+% \end{tikzpicture}
+% \caption{Quasinormal modes of BHs in dynamical Chern-Simons gravity.}
+% \end{figure}
 
@@
 %
+We remark that the alarmingly large values of $\delta \omega_{\rm CS}^{(1)}$ and $\delta \tau_{\rm CS}^{(1)}$
+are compensated by the assumptions that $(\ell_{\rm CS} / M_f)^2$ and $\chi$ are much less than unity. These
+are the assumptions use to calculate the QNM frequencies both in Ref.~\cite{Wagle:2021tam} and also in
+other gravity considered here~\cite{Pierini:2021jxd,Cano:2021myl}.
+%
 As we said before, the only free beyond-GR parameter left is now $\ell_{\rm CS}$.
@@
 \hline
-sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
-EdGB      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
+EdGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
+dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
 cEFTofGR & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
-qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
+% qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
 \hline
@@
 Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$, as already mentioned in the previous section, we would mostly hold $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$ to freely vary.
-For such cases, we assume a prior uniform between appropriate ranges on $\ell$.
+For such cases, we assume a prior uniform between appropriate ranges on $\ell$, making sure that our marginalized posterior distributions on $\ell$ do not rail over the maximum prior value on $\ell$.
 
@@
 
-\subsubsection{Stacking posteriors}
-\label{sec:stack}
-
-When possible, we also combine the marginalized posterior distribution on
-$\ell$ for both event GW150914 and GW200129. To do so, we employ the same
-approach as Ref.~\cite{Perkins:2021mhb} which relies in obtaining a kerneld
-density estimator (KDE) as an approximation for the posterior distribution on
-$\ell$ for each individual events which are then multiplied together to yield
-the cumulative posterior.
-%
-This method can have difficulties in dealing with hard cut-offs in the
-distribution, such as the one we impose at $\ell = 0$. We address this issue as
-done in Ref.~\cite{Perkins:2021mhb}, by first doubling our number of samples as
-$\{ s_i \} \cup \{ - s_i \}$, i.e., mirroring the samples across $\ell = 0$.
-%
-We then renormalize the associated KDE numerically in the range $\ell = [0,
-\infty]$.
-
 \subsubsection{General remarks on the interpretation of our results}
@@
 unity.
+
+\subsubsection{Stacking posteriors}
+\label{sec:stack}
+
+If we find that our posterior obey both conditions~\eqref{eq:eft_bound}
+and~\eqref{eq:parspec_bound}, we combine individual posteriors on $\ell$ from
+each event.
+%
+% When possible, we also combine the marginalized posterior distribution on
+% $\ell$ for both event GW150914 and GW200129.
+%
+To do so, we employ one of the approaches of Ref.~\cite{Perkins:2021mhb} which
+is based on obtaining a kernel density estimator (KDE) as an approximation for
+the posterior distribution on $\ell$ for each individual events. These are then
+multiplied together to yield the cumulative posterior.
+%
+(See also Refs.~\cite{DelPozzo:2011pg,Cardenas-Avendano:2019zxd,Carullo:2021dui}.)
+%
+This method can have difficulties in dealing with hard cut-offs in the
+distribution, such as the one we impose at $\ell = 0$. We address this issue as
+done in Ref.~\cite{Perkins:2021mhb}, by first doubling our number of samples as
+$\{ s_i \} \cup \{ - s_i \}$, i.e., mirroring the samples across $\ell = 0$.
+%
+We then renormalize the associated KDE numerically in the range $\ell = [0,
+\infty]$.
 
@@
 perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc Parspec}
-formalism is violated for the $\gamma_{\rm CS} \delta \tau^{(1)}$ coefficient.
+formalism is violated for the $\gamma_{\rm CS} \, \delta \tau^{(1)}$ coefficient.
 %

### 2022-03-02 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: upd figs

@@
 
+% ---------------------------------------------------
+% Template. Complete when we have the main text done.
+% ---------------------------------------------------
+% This paper is organized as follows.
+% %
+% In Sec.~\ref{sec:review_theories} we present a short overview of the modified gravity theories
+% which we will consider and (if any) the current constraints on them.
+% %
+% In Sec.~\ref{sec:method} we review the two frameworks we combine in our work: the {\sc Parspec}
+% parametrization for the QNMs and the {\sc pSEOBNR} waveform model. We also explain how the
+% theory-specific QNM calculation can be mapped onto the theory-agnostic {\sc Parspec} framework.
+% %
+% In Sec.~\ref{sec:results} we explain how we carry ...
+% %
+% Finally, we present our conclusion in Sec.~\ref{sec:discussion} and point directions for future work.
+% %
+% Unless stated otherwise, we use geometrical unit $c = G = 1$.
+
 \section{Overview of modified gravity theories}
@@
 %
-We now isolate the dCS corrections and compare against Eq.~\eqref{eq:qnm_nongr_iso}.
-%
-Doing so, we can make the identifications,
+We now isolate the dCS corrections and compare against Eq.~\eqref{eq:qnm_nongr_iso},
+whcih yields,
 %
@@
 are the assumptions use to calculate the QNM frequencies both in Ref.~\cite{Wagle:2021tam} and also in
-other gravity considered here~\cite{Pierini:2021jxd,Cano:2021myl}.
+other gravity theories considered here~\cite{Pierini:2021jxd,Cano:2021myl}.
 %
@@
 \hline
-EdGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & \dots \\
-dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
+EdGB      & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
+dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
 cEFTofGR  & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
@@
 %
-for all $j$ of the expansion in dimensionless spin $\chi$.
-%
-We will also construct posterior distributions on the parameters and check if
+for all $j$ in the expansion in dimensionless spin $\chi$.
+%
+We will also construct posterior distributions for these parameters and check if
 most of their support is concentrated to a domain with values much smaller than
@@
 To do so, we employ one of the approaches of Ref.~\cite{Perkins:2021mhb} which
-is based on obtaining a kernel density estimator (KDE) as an approximation for
-the posterior distribution on $\ell$ for each individual events. These are then
-multiplied together to yield the cumulative posterior.
+is relies on first obtaining a kernel density estimator (KDE) as an approximation for
+the posterior distribution on $\ell$ for each individual events. Next, we multiply
+these posteriors together to obtain the cumulative posterior.
 %
@@
 (solid curve) and with (dashed curves) linear in spin QNM corrections. The
-horizontal lines lay at 0.68 and 0.90.
+horizontal lines lay at 0.68 and 0.90. We see that in no situation the curves pass
+through the 0.68 or 0.90 lines even at $\varepsilon = 1$. This means that no bound on $\ell_{\rm GB}$
+can be placed with the event we analyzed.
 }
@@
 \end{figure}
+
+\begin{table}[h]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound ($\gm = M_{f}$) \\
+\hline
+GW150914 & $j = 0$    & No  & Yes & -- \\
+GW150914 & $j = 0, 1$ & No  & Yes & -- \\
+GW200129 & $j = 0$    & No  & Yes & -- \\
+GW200129 & $j = 0, 1$ & No  & Yes & -- \\
+Combined & $j = 0$    & --  & Yes & -- \\
+Combined & $j = 0, 1$ & --  & Yes & -- \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results for EdGB gravity for GW150914, GW200129, and
+combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+%
+We conclude that we cannot place any constraint on $\ell_{\rm GB}$ with any of the GW events
+studied here.~\hs{TODO: update when completed.}
+}
+\label{tab:summary_edgb}
+\end{table}
 
@@
 %%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
+\section{Conclusions}
+\label{sec:conclusions}
 %%%%%%%%%%%%%%%%%
 
-\hs{Try to draw some conclusions that apply to all theories.}
-
-\hs{I think an important message of the paper is that we give indication that
-there are theories of gravity (such as dCS) which can by-pass observational
-constraints from the inspiral phase alone, {\it yet} they do not, if we
-analyze the ringdown. This is quite important because I've frequently heard
-that the ``inspiral is what will constrain theories''. I think this might be
-the most important message.}
-
-\hs{Say that the fact we spin correction look important reinforces the
-importance of calculation QNMs of spinning black holes beyond-GR.}
-
-\hs{Say it is important to go beyond mode calculation and actually understand
-how the QNM appear in the GW signal.}
+% -------------------------------------------------------------
+% \hs{Try to draw some conclusions that apply to all theories.}
+% -------------------------------------------------------------
+
+We presented an unified framework to combine the parametrized formalism introduced
+to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model.
+%
+We showed through concrete examples how theory-specific calculations QNM of
+slowly-rotating BHs in modified gravity theories can be mapped upon the
+theory-agnostic beyond-GR parameters of the {\sc ParSpec} formalism.
+%
+Together this allowed us to apply the \pSEOB~waveform model to test three
+modified gravity theories (EdGB, dCS and cubic EFTofGR) using real
+observational data from the GW events GW150914 and GW200129.
+%
+We found, in particular that, within the assumptions of our model and by
+stacking posteriors, that the coupling constant of dCS gravity is bound to
+$\ell_{\rm CS} \leqslant 34.5$~km.
+%
+In contrast, we could place any constraint of the coupling constants in EdGB gravity $\ell_{\rm GB}$.
+%
+This dichotomy between these theories has an analogy with works that considered the inspiral part of the GW signal alone.
+%
+There it is dCS which is unconstrained, while EdGB, in principle can be constrained, based on results for the closely
+related shift-symmetric version of this theory.
+
+Our work shows that there are theories of gravity (such as dCS) which can by-pass observational
+constraints from the inspiral phase alone, {\it yet} would not, if we
+analyze the ringdown.
+%
+We hope that our result thus serve as additional motivation for future work
+modeling the late-inspiral, merger and ringdown of coalescing BHs in modified
+gravity theories.
+
+Let us discuss some avenues for future work \dots
+
+% -----------------------------------------------------------------------------
+% \hs{Say that the fact we spin correction look important reinforces the
+% importance of calculation QNMs of spinning black holes beyond-GR.}
+%
+% \hs{Say it is important to go beyond mode calculation and actually understand
+% how the QNM appear in the GW signal.}
+% -----------------------------------------------------------------------------
 

### 2022-03-03 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: corner plot
hs: which eft subset we work with

@@
     L^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
-    \nonumber \\
-            &\quad + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
+    % \nonumber \\
+    %         &\quad
+    + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
     \label{eq:s_6}
@@
 and in Refs.~\cite{Cardoso:2018ptl} for the dimension-eight EFT.
+
+Here we will consider $\lame = \lamo = 1$ for simplicity in the cubic EFT, while in quartic,
+we will $\varepsilon_{1} = 1$ and $\varepsilon_{1,\,2} = 0$. This is the same subset of the EFT's parameter
+space studied in~\cite{Sennett:2019bpc}.
 
@@
 
-The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an \emph{IMR} model which infers the properties of the underlying GW signal, including (independently) its ringdown properties, using the Bayesian formalism above.
-Naturally, the most promising candidates for our analyses are high-mass \emph{and} loud GW observations with a significant signal-to-noise ratio (SNR) in the post-merger part of the signal.
-The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed signals not all of which are relevant for a BH ringdown analysis.
-In fact, in an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM} analysis~\footnote{Sec.VIII A.2 in ~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model presented in this paper, identified two events which provided the strongest bounds on measurements of the dominant $(220)$ QNM -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
-These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are extremely similar in their source properties.
-These are also two of the loudest BBH signals observed to date with a total network SNR of XX and XX respectively.
-Moreover, and what is more relevant for our analysis, is their post-inspiral (merger-ringdown) SNRs, which at XX and XX respectively (see the columns for $\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and Table IV of ~\cite{LIGOScientific:2021sio}).
-In this paper, we are going to focus on these two GW events as our probes of the BH ringdown in modified theories of gravity.
+The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an
+\emph{IMR} model which infers the properties of the underlying GW signal,
+including (independently) its ringdown properties, using the Bayesian formalism
+above. Naturally, the most promising candidates for our analyses are high-mass
+\emph{and} loud GW observations with a significant signal-to-noise ratio (SNR)
+in the post-merger part of the signal.
+%
+The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
+signals not all of which are relevant for a BH ringdown analysis. In fact, in
+an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM}
+analysis\footnote{See, in particular, Sec.VIII A.2
+in~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model
+presented in this paper, identified two events which provided the strongest
+bounds on measurements of the dominant $(220)$ QNM --
+GW150914~\cite{LIGOScientific:2016aoc} and
+GW200129~\cite{LIGOScientific:2021djp}.
+%
+These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are
+extremely similar in their source properties. These are also two of the loudest
+BBH signals observed to date with a total network SNR of XX and XX
+respectively.
+%
+Moreover, and what is more relevant for our analysis, is their post-inspiral
+(merger-ringdown) SNRs, which at XX and XX respectively (see the columns for
+$\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
+Table IV of~\cite{LIGOScientific:2021sio}).
+%
+In this paper, we are going to focus on these two GW events as our probes of
+the BH ringdown in modified theories of gravity.
 
@@
 As a first test ...
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/tmp_corner_plot.pdf}
+\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$ and remnant mass $M_f$
+in our non-GR parameter estimation run is consistent with an equivalent GR run.~\hs{Complete.}}
+\label{fig:corner_plot}
+\end{figure}
 

### 2022-03-03 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
upd table and bib

@@
 %
-and similarly for the imaginary part ${\rm Im}(\sigma_{220}) = \omega^{\rm CS}_{220} = 1 / \tau^{\rm CS}_{220}$.
+and similarly for the imaginary part ${\rm Im}(\sigma_{220}) =  - 1 / \tau^{\rm CS}_{220}$.
 %
@@
 dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
-cEFTofGR  & 4 & $-0.3680$ $(-0.5131)$  & 1.9242 (1.7000) & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
-% qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
+cEFT  & 4 & -0.5812  & 1.3234 & \dots & \dots & \cite{Cano:2021myl} & \dots  & \dots \\
+qEFT  & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl} & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
 \hline
@@
 %
-In the entries for cEFTofGR, the first entries in the $\delta
-\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
-only parity-even corrections and the second entries by considering
-only parity-odd corrections.
+% In the entries for cEFTofGR, the first entries in the $\delta
+% \omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
+% only parity-even corrections and the second entries by considering
+% only parity-odd corrections.
 %

### 2022-03-03 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
cEFT params

@@
 dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
-cEFT  & 4 & -0.5812  & 1.3234 & \dots & \dots & \cite{Cano:2021myl} & \dots  & \dots \\
+cEFT  & 4 & -0.5813  & 1.3234 & \dots & \dots & \cite{Cano:2021myl} & \dots  & \dots \\
 qEFT  & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl} & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs:percentile reminder

@@
 In this paper, we would restrict ourselves to corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
-%
 
@@
 which, for a given value of $p$, varied all $\ell$, $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ parameters.
-%
-% As we will see later, our theory-informed approach can result to stronger constraints to certain modified ....
 
@@
 %
-In beyond-GR theories, isospectrality is in general broken (see the discussion in Ref.~\cite{Hui:2021cpm} for a counterexample).
-and thus how axial and polar gravitational QNMs appear in the GW signal has to be answered in theory-by-theory.
-%
-This is outside the scope of this paper and here we take the more pragmatic approach
-of simply choosing the \emph{least damped gravitational mode between the two parities.}
+In beyond-GR theories, isospectrality is in general broken (see the discussion
+in Ref.~\cite{Hui:2021cpm} for a counterexample). and thus how axial and polar
+gravitational QNMs appear in the GW signal has to be answered in
+theory-by-theory.
+%
+This is outside the scope of this paper and here we take the more pragmatic
+approach of simply choosing the \emph{least damped gravitational mode between
+the two parities.}
 %
@@
 
-Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$, as already mentioned in the previous section, we would mostly hold $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$ to freely vary.
-For such cases, we assume a prior uniform between appropriate ranges on $\ell$, making sure that our marginalized posterior distributions on $\ell$ do not rail over the maximum prior value on $\ell$.
+Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$,
+as already mentioned in the previous section, we hold $\{\delta \omega_k^{(j)}\},$
+and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$
+to freely vary.
+%
+For such cases, we assume a prior uniform between appropriate ranges on $\ell$,
+making sure that our marginalized posterior distributions on $\ell$ do not rail
+over the maximum prior value on $\ell$.
 
@@
 \subsection{Results}
+
+\hs{Quote 90\% credibility results.}
 

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: making notation a bit uniform across sections

@@
 
-The GW signal from a BBH merger can be determined in GR by a unique set of parameters -- the masses and spins of the two BHs, $(m_1,\, m_2,\, \vec{s}_1,\, \vec{s}_2)$, the sky location determined by the luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$, and the orientation of the binary given by the inclination and polarisation angles, $(\iota, \psi)$.
+The GW signal from a BBH merger can be determined in GR by a unique set of parameters $\bm{\theta}$, that
+includes the masses and spins of the two BHs, $(m_1,\, m_2,\, \vec{s}_1,\, \vec{s}_2)$, the sky location determined by the luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$, and the orientation of the binary given by the inclination and polarization angles, $(\iota, \psi)$.
 The set is completed by the choice of a reference time and phase, $(t_0,\, \phi_0)$.
@@
 
-The polarisations of the GW signal (in the observer's frame) are,
+The polarization of the GW signal (in the observer's frame) are,
 %
@@
 P(\bm{\lambda} \vert d, \mathcal{H}) =
-\frac{P(\bm{\lambda} \vert \mathcal{H}) P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
+\frac{P(\bm{\lambda} \vert \mathcal{H}) \, P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
 \label{eq:bayes}
@@
 $P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
-$P(d \vert \mathcal{H})$ the evidence. The set of parameters, $\bm{\lambda}$, detailed in Sec.~\ref{sec:review_pSEOB}
-include the set of beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}, \delta \tau_k^{(j)}\}$.
-%
-As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
-constants in the cases of EdGB and dCS theories, but two in the cubic and
-quartic EFTofGR. We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
-fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
-%
+$P(d \vert \mathcal{H})$ the evidence.
+%
+The set of parameters, $\bm{\lambda}$ is the union between the GR waveform
+model parameters~$\bm{\theta}$, detailed in Sec.~\ref{sec:review_pSEOB}, and
+the non-GR parameter of $\ell$, i.e.,
+%
+\begin{equation}
+\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
+\end{equation}
+%
+which, we recall, set the characteristic lengthscale in which deviations from
+GR become relevant in each of the theories described in
+Sec.~\ref{sec:review_theories}.
+
+% As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
+% constants in the cases of EdGB and dCS theories, but two in the cubic and
+% quartic EFTofGR.
+% %
+% We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
+% fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
+% %
 
@@
 sample over the parameter space using a \texttt{LALInference} Markov-Chain
-Monte Carlo algorithm.~\cite{lalsuite}. We subsequently marginalize over the
-remaining parameters to obtain the posterior probability distribution
-function~(PDF) on $\ell$. An example of this is shown in Fig. XX.
+Monte Carlo algorithm~\cite{lalsuite}.
+%
+We subsequently marginalize over the remaining parameters to obtain the
+posterior probability distribution function~(PDF) on $\ell$.
+%
+An example of this is shown in Fig. XX.
 
@@
 each event.
+
+Suppose we have a set of $N$ GW signals $\{D_{i}\}$, described by the ...
 %

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: formated table header
hs: added lalinferencemcmc refs

@@
-\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,amsfonts,amsmath,longbibliography]{revtex4-1}
+\documentclass[twocolumn,
+               prd,
+               aps,
+               superscriptaddress,
+               tightenlines,
+               nofootinbib,
+               eqsecnum,
+               amsfonts,
+               amsmath,
+               longbibliography]{revtex4-1}
+
 \usepackage{epsfig}
@@
 
-\hs{HS will do this.}
-\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
+% \hs{HS will do this.}
+% \hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
 
@@
 sample over the parameter space using a \texttt{LALInference} Markov-Chain
-Monte Carlo algorithm~\cite{lalsuite}.
+Monte Carlo algorithm~\cite{Rover:2006ni,vanderSluys:2008qx,Veitch:2014wba,lalsuite}.
 %
@@
 P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
+\quad \textrm{(EFT bound)},
 \label{eq:eft_bound}
@@
 %
-As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc Parspec}
+As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc ParSpec}
 formalism is by construction perturbative. This means that the non-GR
-deformation parameters are small, i.e.,
+deformation parameters are small, that is,
+% $\gamma \, \delta \omega^{(j)} \ll 1$ and
+% $\gamma \, \delta \tau^{(j)} \ll 1$
 %
@@
 \quad \textrm{and} \quad
-\gamma \, \delta \tau^{(j)} \ll 1 \,.
+\gamma \, \delta \tau^{(j)} \ll 1 \, \quad \textrm{(ParSpec bound)},
 \label{eq:parspec_bound}
@@
 
-Suppose we have a set of $N$ GW signals $\{D_{i}\}$, described by the ...
+Suppose we have a set of $N$ GW detections $\{D_{i}\}$ described by model parameters $\bm{\lambda}$.
 %
@@
 \hline
-Event & $j$ & Eq.~\eqref{eq:eft_bound}? & Eq.~\eqref{eq:parspec_bound}?  & Bound ($\gm = M_{f}$) \\
+Event & $j$ & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+      &     & bound? & bound?  &                            \\
 \hline

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added cumulative dist discussion

@@
 \bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
+\label{eq:def_params}
 \end{equation}
@@
 Assuming a specific prior distribution for our parameters, we stochastically
-sample over the parameter space using a \texttt{LALInference} Markov-Chain
-Monte Carlo algorithm~\cite{Rover:2006ni,vanderSluys:2008qx,Veitch:2014wba,lalsuite}.
+sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
+\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx},
+which is part of \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
 %
@@
 deformation parameters are small, that is,
-% $\gamma \, \delta \omega^{(j)} \ll 1$ and
-% $\gamma \, \delta \tau^{(j)} \ll 1$
 %
@@
 
-If we find that our posterior obey both conditions~\eqref{eq:eft_bound}
-and~\eqref{eq:parspec_bound}, we combine individual posteriors on $\ell$ from
-each event.
-
-Suppose we have a set of $N$ GW detections $\{D_{i}\}$ described by model parameters $\bm{\lambda}$.
-%
-% When possible, we also combine the marginalized posterior distribution on
-% $\ell$ for both event GW150914 and GW200129.
-%
+If, for each event, we find that the constraints~\eqref{eq:eft_bound}
+and~\eqref{eq:parspec_bound} are satisfied, we further combine the individual
+posteriors distribution on $\ell$, allowing us to place a stronger bound on this parameter.
+%
+Let us review how do we calculate this \emph{cumulative posterior distribution} on $\ell$.
+
+% 1. Description of data and assumption o \ell being shared
+Suppose we have a set of $N$ GW events $\{d_{i}\}$ that are described by
+model parameters $\bm{\lambda}_{i}$, where $i$ labels each event.
+%
+We assume that the value of the coupling constant $\ell$, given a specific theory,
+is common to all events.
+%
+% 2. Define joint posterior
+%
+The joint posterior for the parameters $\bm{\lambda}_{i}$, that describe the
+data $\{d_{i}\}$, is
+%
+\begin{equation}
+P(\ell, \{\btheta_i\} | \{d_{i}\})
+= \frac{ P(\ell_i, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) }.
+\label{eq:def_joint_posterior}
+\end{equation}
+%
+where we separated $\ell$ from the GR waveform model parameters $\btheta$ [cf.~Eq.~\eqref{eq:def_params}].
+%
+% 3. Marginalisation to obtain the cumulative posterior
+%
+To obtain the cumulative posterior distribution on $\ell$, we marginalize
+the joint posterior~\eqref{eq:def_joint_posterior} over
+all parameters $\{ \btheta_i \}$, i.e.,
+%
+\begin{align}
+P(\ell | \{d_i\}) &= \int \dd \{\btheta_i\} \, P(\ell, \{\btheta_i\} | \{d_{i}\}),
+\nonumber \\
+                  &= \int \dd \{\btheta_i\} \, \frac{ P(\ell_i, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) },
+\nonumber \\
+                  &= \frac{P(\ell_i)}{P(\{d_i\})} \int \dd \{\btheta_i\} \, P(\{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ),
+\end{align}
+%
+where we have assumed that the prior on $\ell$, $P(\ell)$, is independent of
+the other parameters $\{\btheta_i\}$.
+%
+This allow us to factor $P(\lambda, \{\btheta_i\} = P(\ell) P(\{\btheta\})$
+and then move $P(\ell)$ out of the integral
+%
+We also moved out integral the evidence $P(\{d_i\})$, which is a normalization constant.
+%
+% 4. Factor the integrals in a product due to statistical independence
+We can now factor the probabilities inside the integral, because each event is independent from one another:
+%
+\begin{equation}
+P(\ell | \{d_i\}) = \frac{P(\ell_i)}{P(\{d_i\})}
+\prod_{i=1}^{N}
+\int \dd \btheta_i \, P(\btheta_i) \, P( d_i | \ell_i, \btheta_i ).
+\end{equation}
+%
+% 5. Final formula
+We can now identify the integral as the marginalized likelihood for each individual event
+%
+\begin{equation}
+P(\ell | \{d_i\}) = \frac{P(\ell_i)}{P(\{d_i\})}
+\prod_{i=1}^{N} P( d_i | \ell_i ),
+\end{equation}
+%
+which we can rewritte as
+%
+\begin{equation}
+P(\ell | \{d_i\}) = \frac{P(\ell_i)}{P(\{d_i\})}
+\prod_{i=1}^{N} \frac{P(d_i)}{P(\ell_i)} P(\ell_i | d_i).
+\label{eq:cumulative_dist_ell}
+\end{equation}
+%
+using Bayes' theorem. This is our final result.
+
+In our parameter estimation studies, we found that depending on which event and
+on which theory we adopt for our parameter estimation, that we had to adjust
+the prior on $\ell$.
+%
+The reasons are twofold. First, we found that depending on the source parameters $\btheta$,
+certain large values of $\ell$ could result in unphysical waveforms in the frequency band we considered.
+For instance, they could feature a ringdown multiple times longer than the inspiral-merger part.
+%
+Such waveform are perhaps not surprising since we are, by construction, adding corrections to the GR QNM
+which \emph{delay} its damping.
+%
+%
+In practice, we found these edge cases were problematic to deal with \texttt{LALInferenceMCMC}.
+%
+We addressed this issue, by reducing the prior range on $\ell$, which does not pose a problem to our parameter
+estimation runs because these edge-case waveforms differ grossly from the true signal and thus have
+negligible likelihood
+%
+However, we cannot reduce the prior on $\ell$ too much. If we do so,
+to the individual posterior to rail against the prior and to result in GW
+waveform which are physical.
+%
+Altogether, this means that the priors $P(\ell)$ are not shared between events and
+they must be taken into account when calculation the cumulative posterior function~\eqref{eq:cumulative_dist_ell}.
+
 To do so, we employ one of the approaches of Ref.~\cite{Perkins:2021mhb} which

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: tried to improve stacking discussion

@@
 % 1. Description of data and assumption o \ell being shared
-Suppose we have a set of $N$ GW events $\{d_{i}\}$ that are described by
+Suppose we have a data set $\{d_{i}\}$ of $N$ events which is described by
 model parameters $\bm{\lambda}_{i}$, where $i$ labels each event.
@@
 P(\ell, \{\btheta_i\} | \{d_{i}\})
-= \frac{ P(\ell_i, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) }.
+= \frac{ P(\ell, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) }.
 \label{eq:def_joint_posterior}
@@
 \nonumber \\
-                  &= \int \dd \{\btheta_i\} \, \frac{ P(\ell_i, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) },
+                  &= \int \dd \{\btheta_i\} \, \frac{ P(\ell, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) },
 \nonumber \\
-                  &= \frac{P(\ell_i)}{P(\{d_i\})} \int \dd \{\btheta_i\} \, P(\{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ),
+                  &= \frac{P(\ell)}{P(\{d_i\})} \int \dd \{\btheta_i\} \, P(\{\btheta_i\}) \, P( \{d_i\} | \ell, \{\btheta_i\} ),
 \end{align}
@@
 %
-This allow us to factor $P(\lambda, \{\btheta_i\} = P(\ell) P(\{\btheta\})$
+This allow us to write $P(\ell, \{\btheta_i\} = P(\ell) P(\{\btheta_i\})$
 and then move $P(\ell)$ out of the integral
@@
 % 4. Factor the integrals in a product due to statistical independence
-We can now factor the probabilities inside the integral, because each event is independent from one another:
-%
-\begin{equation}
-P(\ell | \{d_i\}) = \frac{P(\ell_i)}{P(\{d_i\})}
+%
+We can now factor the probabilities inside the integral, since each event is independent from another:
+%
+\begin{equation}
+P(\ell | \{d_i\}) = \frac{P(\ell)}{P(\{d_i\})}
 \prod_{i=1}^{N}
@@
 \begin{equation}
-P(\ell | \{d_i\}) = \frac{P(\ell_i)}{P(\{d_i\})}
+P(\ell | \{d_i\}) = \frac{P(\ell)}{P(\{d_i\})}
 \prod_{i=1}^{N} P( d_i | \ell_i ),
@@
 %
-which we can rewritte as
-%
-\begin{equation}
-P(\ell | \{d_i\}) = \frac{P(\ell_i)}{P(\{d_i\})}
-\prod_{i=1}^{N} \frac{P(d_i)}{P(\ell_i)} P(\ell_i | d_i).
+which we can rewrite as
+%
+\begin{align}
+P(\ell | \{d_i\}) &= \frac{P(\ell)}{P(\{d_i\})}
+\prod_{i=1}^{N} \frac{P(d_i)}{P(\ell_i)} P(\ell_i | d_i)
+\nonumber \\
+&= P(\ell)
+\prod_{i=1}^{N} \frac{P(\ell_i | d_i)}{P(\ell_i)}.
 \label{eq:cumulative_dist_ell}
-\end{equation}
-%
-using Bayes' theorem. This is our final result.
-
-In our parameter estimation studies, we found that depending on which event and
-on which theory we adopt for our parameter estimation, that we had to adjust
-the prior on $\ell$.
-%
-The reasons are twofold. First, we found that depending on the source parameters $\btheta$,
-certain large values of $\ell$ could result in unphysical waveforms in the frequency band we considered.
-For instance, they could feature a ringdown multiple times longer than the inspiral-merger part.
-%
-Such waveform are perhaps not surprising since we are, by construction, adding corrections to the GR QNM
-which \emph{delay} its damping.
-%
-%
-In practice, we found these edge cases were problematic to deal with \texttt{LALInferenceMCMC}.
-%
-We addressed this issue, by reducing the prior range on $\ell$, which does not pose a problem to our parameter
-estimation runs because these edge-case waveforms differ grossly from the true signal and thus have
-negligible likelihood
+\end{align}
+%
+by using Bayes' theorem in the first line and cancelling the evidences in the
+second line. This is our final result.
+
+%
+\hs{Abhirup, maybe move this to the prior subsection?}
+In our parameter estimation runs that we had to adjust our prior on $\ell$ depending on which event and
+on which theory we examined.
+%
+The reasons are twofold.
+%
+% Describe problem 1
+%
+First, we found that depending on the source parameters $\btheta$,
+large values of $\ell$ could result in unphysical waveforms in the frequency
+band we considered. More specifically, these waveforms have a ringdown which is
+considerable longer than the inspiral-merger part in the detector frequency band.
+%
+The fact that our sampled over these waveforms is perhaps not surprising,
+because, after all, we are by construction adding corrections to the GR QNM
+which \emph{increase} the damping timescale.
+%
+In practice, we found that these edge-cases were problematic to deal with
+\texttt{LALInferenceMCMC}.
+%
+We overcome this problem, we reduced the prior upper-value of our prior on $\ell$.
+%
+This choice does not pose a problem to our parameter estimations, because these
+waveforms differ grossly from the data and thus have negligible likelihood.
+%
+% Describe problem 2
 %
 However, we cannot reduce the prior on $\ell$ too much. If we do so,
-to the individual posterior to rail against the prior and to result in GW
-waveform which are physical.
+to the marginalized posterior distribution on $\ell$ would rail against
+the prior or, in a more extreme case, even be a uninformative, flat posterior.
+%
+% Summary
 %
@@
 
-To do so, we employ one of the approaches of Ref.~\cite{Perkins:2021mhb} which
-is relies on first obtaining a kernel density estimator (KDE) as an approximation for
-the posterior distribution on $\ell$ for each individual events. Next, we multiply
-these posteriors together to obtain the cumulative posterior.
+Finally, we use one of the approaches of Ref.~\cite{Perkins:2021mhb} to
+compute the product in Eq.~\eqref{eq:cumulative_dist_ell}.
+%
+It method relies on first obtaining a kernel density estimator (KDE) for
+the posterior distribution on $\ell$ for each individual event.
+%
+Next, we multiply these posteriors according to Eq.~\eqref{eq:cumulative_dist_ell}.
 %
@@
 %
-This method can have difficulties in dealing with hard cut-offs in the
+This approach based on the KDE can have difficulties in dealing with hard cut-offs in the
 distribution, such as the one we impose at $\ell = 0$. We address this issue as
@@
 %
-We then renormalize the associated KDE numerically in the range $\ell = [0,
-\infty]$.
+We then renormalize the associated KDE numerically in the range $\ell = [0, \infty]$.
 

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: contour plot

@@
 \usepackage[caption=false]{subfig}
-\usepackage{booktabs}
 \usepackage{url}
@@
 
-\usepackage{tikz}
+% \usepackage{tikz}
 
@@
 }
-
-\definecolor{LinkColor}{rgb}{0.75, 0, 0}
-\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
-\definecolor{UrlColor}{rgb}{0, 0, 0.75}
+% -----------
+
 \definecolor{rred}{RGB}{218,41,28}
@@
 
-\author{Hector O. Silva}
-\author{Abhirup Ghosh}
-\AEI
-\author{Alessandra Buonanno}
-\AEI
-\UMD
+\author{Hector O. Silva}     \AEI
+\author{Abhirup Ghosh}       \AEI
+\author{Alessandra Buonanno} \AEI \UMD
 
@@
 \maketitle
-% \tableofcontents
-
-%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
 \label{sec:intro}
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Overview of modified gravity theories}
 \label{sec:review_theories}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%
 \section{Methods}
 \label{sec:method}
+%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results using LIGO-Virgo events}
 \label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 As a first test ...
+\hs{Move to an appendix.}
 
@@
 \includegraphics[width=\columnwidth]{figs/tmp_corner_plot.pdf}
-\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$ and remnant mass $M_f$
-in our non-GR parameter estimation run is consistent with an equivalent GR run.~\hs{Complete.}}
+\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
+detector-frame remnant mass $M_f$, and redshift $z$ for GW150915, using the same waveform model,
+but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
+dCS gravity and $j=0$). The contours represent 90\% credible regions.
+%
+We see that the introduction of the non-GR parameters does not bias the inference on the source parameters.}
 \label{fig:corner_plot}
@@
 
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
 \label{sec:conclusions}
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: fig frames

@@
 In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
-the {\sc Parspec} implementation of each theory and give credit to the papers
+the {\sc ParSpec} implementation of each theory and give credit to the papers
 which calculated the QNMs.
@@
 %
-We must remember that in the {\sc Parspec} formalism that the GR deviations
+We must remember that in the {\sc ParSpec} formalism that the GR deviations
 are controlled by $\gamma \, \delta \omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$.
@@
 We also found for both GW events, that the
-perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc Parspec}
+perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc ParSpec}
 formalism is violated for the $\gamma_{\rm CS} \, \delta \tau^{(1)}$ coefficient.
@@
 
-\subsubsection{Effective-field-theory of general relativity}
-\label{sec:results_efts}
+\subsubsection{cubic effective-field-theory of general relativity}
+\label{sec:results_ceft}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm cEFT}$ for
+GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
+in spin QNM correction.
+%
+\hs{TODO}
+}
+\label{fig:cEFT_exec_sum}
+\end{figure}
+
+\subsubsection{quartic effective-field-theory of general relativity}
+\label{sec:results_qeft}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
+GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
+in spin QNM correction.
+%
+\hs{TODO}
+}
+\label{fig:qEFT_exec_sum}
+\end{figure}
 

### 2022-03-09 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: additional histograms

@@
 %
-We see that the introduction of the non-GR parameters does not bias the inference on the source parameters.}
+We see that the introduction of the non-GR parameters does not bias the inference on the source parameters.
+%
+\hs{TODO: increase font size and move it to an Appendix.}
+}
 \label{fig:corner_plot}
@@
 %
-\hs{Abhirup, maybe move this to the prior subsection?}
+\hs{Abhirup, maybe move this to the subsection on priors?}
 In our parameter estimation runs that we had to adjust our prior on $\ell$ depending on which event and
@@
 
-\hs{Quote 90\% credibility results.}
+\hs{Convention: us 90\% credibility for the final bounds.}
 
@@
 
+\begin{table}[h]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+Event & $j$ & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+      &     & bound? & bound?  &                            \\
+\hline
+GW150914 & $j = 0$    &     &     &    \\
+GW150914 & $j = 0, 1$ &     &     &    \\
+GW200129 & $j = 0$    &     &     &    \\
+GW200129 & $j = 0, 1$ &     &     &    \\
+Combined & $j = 0$    &     &     &    \\
+Combined & $j = 0, 1$ &     &     &    \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results the cubic EFT of GR for GW150914, GW200129, and
+combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+%
+\hs{TODO: update when completed.}
+}
+\label{tab:summary_ceft}
+\end{table}
+
 \subsubsection{quartic effective-field-theory of general relativity}
@@
 \end{figure}
+
+\begin{table}[h]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+Event & $j$ & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+      &     & bound? & bound?  &                            \\
+\hline
+GW150914 & $j = 0$    &     &     &    \\
+GW150914 & $j = 0, 1$ &     &     &    \\
+GW200129 & $j = 0$    &     &     &    \\
+GW200129 & $j = 0, 1$ &     &     &    \\
+Combined & $j = 0$    &     &     &    \\
+Combined & $j = 0, 1$ &     &     &    \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results the quartic EFT of GR for GW150914, GW200129, and
+combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+%
+\hs{TODO: update when completed.}
+}
+\label{tab:summary_qeft}
+\end{table}
 
@@
 %
-Together this allowed us to apply the \pSEOB~waveform model to test three
-modified gravity theories (EdGB, dCS and cubic EFTofGR) using real
-observational data from the GW events GW150914 and GW200129.
+Together this allowed us to apply the \pSEOB~waveform model to test four
+modified gravity theories (EdGB, dCS, cubic, and quartic
+effective-field-theories of GR) using data from the GW events GW150914 and GW200129.
 %

### 2022-03-09 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: terse text on parspec formalism

@@
 
-Further expand the Kerr expression as:
+We expand the Kerr expression as:
 %
 \begin{subequations}
+\label{eq:kerr_expansion}
 \begin{align}
-\omega_{J} &= (1/M) \sum_{j = 0}^{N} \, \chi^{j} \omega^{(j)}_{k} \, \left( 1 + \gamma \delta \omega^{(j)}_{k} \right), \\
-\tau_{J}   &= M     \sum_{j = 0}^{N} \, \chi^{j} \tau^{(j)}_{k}   \, \left( 1 + \gamma \delta \tau^{(j)}_{k} \right),
+\omega_{J} &= \frac{1}{M} \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \omega^{(n)}_{J} \, \left( 1 + \gamma \delta \omega^{(n)}_{J} \right), \\
+\tau_{J}   &= M     \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \tau^{(n)}_{J}   \, \left( 1 + \gamma \delta \tau^{(n)}_{J} \right),
 \end{align}
-\label{eq:kerr_expansion}
 \end{subequations}
-
-Also,
+%
+where $M$ and $\chi$ are the detector-frame mass and dimensionless spin of the
+remnant black hole; $\omega_{K}^{n}$, $\tau_{K}^{n}$ are dimensionless coefficients
+of the spin expansion for Kerr QNMs; $\delta\omega_{K}^{n}$, $\delta\tau_{K}^{n}$ are
+source-independent dimensionless coefficients that characterize the corrections to the Kerr QNM at each spin-order;
+and finally $N_{\rm max}$ is the order of the spin expansion.
+%
+All source dependence on the beyond-GR modification is encapsulated in the dimensionless
+parameter $\gamma$,
 %
@@
 %
-= \frac{\ell^{p}}{M_{\rm s}^{p}}
+= \left(\frac{\ell}{M_{\rm s}}\right)^{p}
 %
@@
 \end{equation}
+%
+which depends on the parameter $\ell$, with dimensions of lenght, which sets the
+lenghtscale in which beyond-GR modification become important and the exponent $p$
+which is related to how the beyond-GR modifications are included to the Einstein-Hilbert action.
+%
+In Eq.~\eqref{eq:def_gamma} we made $\ell$ dimensionless by the other
+lenghtscale associated to the remnant black hole, i.e., its source-frame mass
+$M_{\rm s}$, which we can also in terms of the detector-frame mass $M$ through
+a the redshift $z$.
+
+In principle, a modification to GR would also affect $M$ and $\chi$ and the expansion should be written
+in terms of non-GR mass and spin, say $\bar{M}$ and $\bar{\chi}$. If we assume that the beyond-GR corrections
+are included perturbatively, the modifications to the BH mass and spin can be absorved into the deviations
+parameters $\delta\omega$ and $\delta\tau$.
+%
+This means we can identify the $M$ and $\chi$ with their corresponding GR values.
+
+\hs{TODO: in figures and tables use $N_{\rm max} = 0$ ($N_{\rm max} = 1$) instead of $j=0$ ($j=0,1$).}
+\hs{TODO: say that we check a posteriori if our PE runs agree with this.}
 
@@
 The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \text{sin} \iota$.
-For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the z-components~\footnote{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.} The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
+For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
+This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.
+%
+The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
 
@@
 %
+(See also Refs.~\cite{DelPozzo:2011pg,Cardenas-Avendano:2019zxd,Carullo:2021dui}.)
+%
 Next, we multiply these posteriors according to Eq.~\eqref{eq:cumulative_dist_ell}.
-%
-(See also Refs.~\cite{DelPozzo:2011pg,Cardenas-Avendano:2019zxd,Carullo:2021dui}.)
 %
@@
 %
-This dichotomy between these theories has an analogy with works that considered the inspiral part of the GW signal alone.
-%
-There it is dCS which is unconstrained, while EdGB, in principle can be constrained, based on results for the closely
-related shift-symmetric version of this theory.
+This dichotomy between these theories has an analogy with works that considered
+the inspiral part of the GW signal alone.
+%
+In that case, it is dCS which is unconstrained, while EdGB, in principle can be
+constrained, based on results for the closely related shift-symmetric version
+of this theory.
 

### 2022-03-09 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: reorganize subsub and subsection

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results using LIGO-Virgo events}
-\label{sec:results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%
+\section{Parameter Inference}
 
@@
 
-%%%%%%%%%%%%%%%%%
-\subsection{Parameter Inference}
-
-\subsubsection{Bayesian formalism}
+\subsection{Bayesian formalism}
 If we assume that a GW signal observed in detector data $d$ is accurately
@@
 
-\subsubsection{Priors}
+\subsection{Priors}
 
@@
 
-\subsubsection{Event selection}
+\subsection{Event selection}
 
@@
 
-\subsubsection{General remarks on the interpretation of our results}
+\subsection{General remarks on the interpretation of our results}
 \label{sec:remaks}
@@
 
-\subsubsection{Stacking posteriors}
+\subsection{Stacking posteriors}
 \label{sec:stack}
@@
 
-\subsection{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results using LIGO-Virgo events}
+\label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsubsection{Einstein-dilaton-Gauss-Bonnet}
+\subsection{Einstein-dilaton-Gauss-Bonnet}
 \label{sec:results_edgb}
@@
 
-\subsubsection{Dynamical Chern-Simons}
+\subsection{Dynamical Chern-Simons}
 \label{sec:results_dcs}
@@
 
-\subsubsection{cubic effective-field-theory of general relativity}
+\subsection{cubic effective-field-theory of general relativity}
 \label{sec:results_ceft}
@@
 
-\subsubsection{quartic effective-field-theory of general relativity}
+\subsection{quartic effective-field-theory of general relativity}
 \label{sec:results_qeft}

### 2022-03-14 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small changes

@@
 
-% \hs{HS will do this.}
-% \hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}
-
-The formalism modifies the Kerr quasinormal mode frequency as
+We start by reviewing the parametrized ringdown spin expansion coefficients formalism (ParSpec)
+introduced in Ref.~\cite{Maselli:2019mjd}, but following some of the notation of Ref.~\cite{Carullo:2021dui}.
+%
+The formalism modifies the Kerr quasinormal mode frequency $\omega_{J}^{\rm K}$ and
+damping time $\tau_{J}^{\rm K}$ as
 %
 \begin{subequations}
+\label{eq:general_deviation}
 \begin{align}
@@
 \end{align}
-\label{eq:general_deviation}
 \end{subequations}
 %
-where the $J$ collectively represents the QNM labels $\{l,\, m,\, n\}$.
+where the $J$ collectively represents the QNM labels $\{l,\, m,\, n\}$, where $l$ is
+the , $m$ and $n$ the ove
 
@@
 In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
-the {\sc ParSpec} implementation of each theory and give credit to the papers
+the ParSpec implementation of each theory and give credit to the papers
 which calculated the QNMs.
@@
 dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
-cEFT  & 4 & -0.5813  & 1.3234 & \dots & \dots & \cite{Cano:2021myl} & \dots  & \dots \\
+cEFT  & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} & \dots  & \dots \\
 qEFT  & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl} & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
@@
 %
-% In the entries for cEFTofGR, the first entries in the $\delta
-% \omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
-% only parity-even corrections and the second entries by considering
-% only parity-odd corrections.
-%
 In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
@@
 \end{table*}
-
-% \hs{We {\it must very explicitly} state our working hypothesis here:
-% %
-% \begin{itemize}
-%     \item That we include only the nonrotating, non-GR correction to the QNMs.
-%     \item That due to absence of isospectrality, when translating to the theory specific result,
-%     we {\it chose} to use the lowest damping, gravitational QNM of the theory.
-% \end{itemize}
-% %
-% We can come back to these in the Sec.~\ref{sec:discussion} as things that we
-% might want to revisit in the future.
-% }
-
-% \hs{In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
-% the {\sc Parspec} implementation of each theory and give credit to the papers
-% which calculated the QNMs.}
 
@@
 %
-As already emphasized in Ref.~\cite{Maselli:2019mjd}, the {\sc ParSpec}
+As already emphasized in Ref.~\cite{Maselli:2019mjd}, the ParSpec
 formalism is by construction perturbative. This means that the non-GR
@@
 %
-We must remember that in the {\sc ParSpec} formalism that the GR deviations
+We must remember that in the ParSpec formalism that the GR deviations
 are controlled by $\gamma \, \delta \omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$.
@@
 We also found for both GW events, that the
-perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc ParSpec}
+perturbative-conditions~\eqref{eq:parspec_bound} required by the ParSpec
 formalism is violated for the $\gamma_{\rm CS} \, \delta \tau^{(1)}$ coefficient.
@@
 slowly-rotating BHs in modified gravity theories can be mapped upon the
-theory-agnostic beyond-GR parameters of the {\sc ParSpec} formalism.
+theory-agnostic beyond-GR parameters of the ParSpec formalism.
 %

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
working on parspec section; new refs

@@
 
-We start by reviewing the parametrized ringdown spin expansion coefficients formalism (ParSpec)
-introduced in Ref.~\cite{Maselli:2019mjd}, but following some of the notation of Ref.~\cite{Carullo:2021dui}.
-%
-The formalism modifies the Kerr quasinormal mode frequency $\omega_{J}^{\rm K}$ and
-damping time $\tau_{J}^{\rm K}$ as
+We start by reviewing the parametrized ringdown spin expansion coefficients
+formalism (ParSpec) introduced in Ref.~\cite{Maselli:2019mjd}, but following
+some of the notation of Ref.~\cite{Carullo:2021dui}.
+%
+A general procedure to describe deviations from the Kerr quasinormal mode frequencies $\omega_{J}^{\rm K}$ and
+damping time $\tau_{J}^{\rm K}$ is to write them as,
 %
@@
 %
-where the $J$ collectively represents the QNM labels $\{l,\, m,\, n\}$, where $l$ is
-the , $m$ and $n$ the ove
+as done e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
+%
+Here we use $J$ to collectively represents the QNM labels $\{l,\, m,\, n\}$,
+where $l$ and $m$ are the multipole indices, and $n$ the overtone number.
+%
+We work exclusively with $\ell = m = 2$ and $n = 0$ (fundamental mode) in this work.
 
@@
 where $M$ and $\chi$ are the detector-frame mass and dimensionless spin of the
-remnant black hole; $\omega_{K}^{n}$, $\tau_{K}^{n}$ are dimensionless coefficients
+black hole; $\omega_{K}^{n}$, $\tau_{K}^{n}$ are dimensionless coefficients
 of the spin expansion for Kerr QNMs; $\delta\omega_{K}^{n}$, $\delta\tau_{K}^{n}$ are
@@
 All source dependence on the beyond-GR modification is encapsulated in the dimensionless
-parameter $\gamma$,
+parameter $\gamma$ given by,
 %
@@
 \frac{\ell c^2 (1 + z)}{G M}
-\right]^{p}
+\right]^{p},
 \label{eq:def_gamma}
@@
 %
-which depends on the parameter $\ell$, with dimensions of lenght, which sets the
-lenghtscale in which beyond-GR modification become important and the exponent $p$
-which is related to how the beyond-GR modifications are included to the Einstein-Hilbert action.
-%
-In Eq.~\eqref{eq:def_gamma} we made $\ell$ dimensionless by the other
+which depends on the parameter $\ell$, with dimensions of length (and sets the
+lengthscale at which beyond-GR modifications become important), and
+the exponent $p$ which is related to how the beyond-GR modifications are
+included to the Einstein-Hilbert action.
+%
+In Eq.~\eqref{eq:def_gamma} we made $\ell$ dimensionless by using the other
 lenghtscale associated to the remnant black hole, i.e., its source-frame mass
-$M_{\rm s}$, which we can also in terms of the detector-frame mass $M$ through
-a the redshift $z$.
+$M_{\rm s}$, which we can also write in terms of the detector-frame mass $M$ through
+the redshift $z$~\cite{Krolak:1987ofj}.
 
@@
 This means we can identify the $M$ and $\chi$ with their corresponding GR values.
+%
 

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: parspec section; reinstated mathcal L for likelihood

@@
 
-We start by reviewing the parametrized ringdown spin expansion coefficients
-formalism (ParSpec) introduced in Ref.~\cite{Maselli:2019mjd}, but following
-some of the notation of Ref.~\cite{Carullo:2021dui}.
-%
-A general procedure to describe deviations from the Kerr quasinormal mode frequencies $\omega_{J}^{\rm K}$ and
-damping time $\tau_{J}^{\rm K}$ is to write them as,
+We start by reviewing the parametrized ringdown spin expansion coefficients (ParSpec)
+framework introduced in Ref.~\cite{Maselli:2019mjd}, but following
+some of the notation used in Ref.~\cite{Carullo:2021dui}.
+
+A general procedure to describe deviations from the Kerr QNM frequencies $\omega_{J}^{\rm K}$ and
+damping times $\tau_{J}^{\rm K}$ is to write,
 %
@@
 %
-as done e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
-%
-Here we use $J$ to collectively represents the QNM labels $\{l,\, m,\, n\}$,
+where $\delta\omega_{J}$ and $\delta\tau_{J}$ are the deformation parameters.
+%
+Here we use the subscript $J$ to represent the QNM labels $\{l,\, m,\, n\}$,
 where $l$ and $m$ are the multipole indices, and $n$ the overtone number.
 %
-We work exclusively with $\ell = m = 2$ and $n = 0$ (fundamental mode) in this work.
-
-We expand the Kerr expression as:
+We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
+QNM in this work, that is, $J = \{2,\, 2,\, 0\}$.
+%
+This approach was adopted, e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
+
+A caveat of the parametrizations of the form~\eqref{eq:general_deviation}, is that
+$\delta\omega_{J}$ and $\delta\tau_{J}$ depend, in general, on the BH's source mass and spin.
+%
+Ideally, one would like to explicitly reinstate the dependence the source-frame
+BH mass and spin for it would
+%
+%
+(i) introduce deformation parameters which can be determined, once and for
+all, from a specific gravity theory, and
+%
+(ii) make it easy to combine constraints from multiple source.
+
+In the ParSpec framework this is accomplished by performing a bivariate
+expansion of Eq.~\eqref{eq:general_deviation} in the detector-frame mass and
+spin, namely
 %
@@
 %
-This means we can identify the $M$ and $\chi$ with their corresponding GR values.
-%
-
-\hs{TODO: in figures and tables use $N_{\rm max} = 0$ ($N_{\rm max} = 1$) instead of $j=0$ ($j=0,1$).}
+This means we can identify the $M$ and $\chi$ with their \emph{corresponding GR values}.
+
+% \hs{TODO: in figures and tables use $N_{\rm max} = 0$ ($N_{\rm max} = 1$) instead of $j=0$ ($j=0,1$).}
 \hs{TODO: say that we check a posteriori if our PE runs agree with this.}
@@
 \begin{subequations}
+\label{eq:qnm_nongr_iso}
 \begin{align}
 M \omega_{220} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
-+ \sum_{j=0}^{N} \chi^{j} \omega^{j}\,,
++ \sum_{n=0}^{N_{\rm max}} \chi^{j} \omega^{j}\,,
 \\
 \tau_{220}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
-+ \sum_{j=0}^{N} \chi^{j} \tau^{j}\,,
++ \sum_{n=0}^{N_{\rm max}} \chi^{j} \tau^{j}\,,
 \end{align}
-\label{eq:qnm_nongr_iso}
 \end{subequations}
 %
-where we are already focusing on the dominant $\ell = m = 2$, $n=0$ QNM and
-pulled out of the sum all beyond-GR corrections, rescriting ourselves to the nonspinning ($j=0$) and linear-order in spin ($j=1$)
-corrections to the Kerr QNMs, encoded in the coefficients $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$.
+where, recall, we focus on the $\ell = m = 2$, $n=0$ QNM and have pulled out of
+the sum all beyond-GR corrections, restricting ourselves to the nonspinning
+($n=0$) and linear-order in spin ($n=1$) corrections to the Kerr QNMs.
+%
+These corrections are encoded in the coefficients $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$.
 
@@
 P(\bm{\lambda} \vert d, \mathcal{H}) =
-\frac{P(\bm{\lambda} \vert \mathcal{H}) \, P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
+\frac{P(\bm{\lambda} \vert \mathcal{H}) \, \mathcal{L}(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
 \label{eq:bayes}
@@
 $P(\bm{\lambda} \vert \mathcal{H})$ the prior,
-$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
+$\mathcal{L}(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
 $P(d \vert \mathcal{H})$ the evidence.

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more parspec section

@@
 %
-We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
-QNM in this work, that is, $J = \{2,\, 2,\, 0\}$.
-%
 This approach was adopted, e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
@@
 This means we can identify the $M$ and $\chi$ with their \emph{corresponding GR values}.
+
+We remark that in the GR limit, where $\delta\omega_{J}^{(n)} = \delta\tau_{J}^{(n)} = 0$ $\forall\, n$,
+the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
+the Kerr QNMs for spins $\chi \lesssim 0.7$.
+%
+The values of the fitting coefficients $\omega_{J}^{(n)}$ and $\tau_{J}^{(n)}$
+can be found in Ref.~\cite{Maselli:2019mjd}, Table I.
 
@@
 %
-where, recall, we focus on the $\ell = m = 2$, $n=0$ QNM and have pulled out of
+We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
+QNM in this work, that is, $J = \{2,\, 2,\, 0\}$, and we  have pulled out of
 the sum all beyond-GR corrections, restricting ourselves to the nonspinning

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
many updates; summary table split

--- 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
@@
 
-% ---------------------------------------------------
-% Template. Complete when we have the main text done.
-% ---------------------------------------------------
-% This paper is organized as follows.
-% %
-% In Sec.~\ref{sec:review_theories} we present a short overview of the modified gravity theories
-% which we will consider and (if any) the current constraints on them.
-% %
-% In Sec.~\ref{sec:method} we review the two frameworks we combine in our work: the {\sc Parspec}
-% parametrization for the QNMs and the {\sc pSEOBNR} waveform model. We also explain how the
-% theory-specific QNM calculation can be mapped onto the theory-agnostic {\sc Parspec} framework.
-% %
-% In Sec.~\ref{sec:results} we explain how we carry ...
-% %
-% Finally, we present our conclusion in Sec.~\ref{sec:discussion} and point directions for future work.
-% %
-% Unless stated otherwise, we use geometrical unit $c = G = 1$.
+\begin{table}[th]
+\begin{tabular}{c | c c}
+\hline \hline
+Theory & Constraint & This work \\
+\hline
+EdGB        & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
+dCS         & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
+cubic EFT   & \dots & \dots \\
+quartic EFT & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
+\hline \hline
+\end{tabular}
+\caption{\hs{Mention it in the Introduction later, in a sort of `executive summary'.}}
+\label{tab:bound_summary}
+\end{table}
 
@@
 
-A general procedure to describe deviations from the Kerr QNM frequencies $\omega_{J}^{\rm K}$ and
-damping times $\tau_{J}^{\rm K}$ is to write,
+A general procedure to describe deviations from the Kerr QNM frequencies $\omega_{k}^{\rm Kerr}$ and
+damping times $\tau_{k}^{\rm Kerr}$ is to write,
 %
@@
 \begin{align}
-\omega_{J} &= \omega^{\rm K}_{J} \, (1 + \delta \omega_{J}), \\
-\tau_{J}   &= \tau^{\rm K}_{J}   \, (1 + \delta \tau_{J}),
+\omega_{k} &= \omega^{\rm Kerr}_{k} \, (1 + \delta \omega_{k}), \\
+\tau_{k}   &= \tau^{\rm Kerr}_{k}   \, (1 + \delta \tau_{k}),
 \end{align}
@@
 %
-where $\delta\omega_{J}$ and $\delta\tau_{J}$ are the deformation parameters.
-%
-Here we use the subscript $J$ to represent the QNM labels $\{l,\, m,\, n\}$,
+where $\delta\omega_{k}$ and $\delta\tau_{k}$ are the deformation parameters.
+%
+Here we use the subscript $k$ to represent the QNM labels $\{l,\, m,\, n\}$,
 where $l$ and $m$ are the multipole indices, and $n$ the overtone number.
 %
-We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
-QNM in this work, that is, $J = \{2,\, 2,\, 0\}$.
-%
 This approach was adopted, e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
 
-A caveat of the parametrizations of the form~\eqref{eq:general_deviation}, is that
-$\delta\omega_{J}$ and $\delta\tau_{J}$ depend, in general, on the BH's source mass and spin.
+A caveat of parametrizations of the form~\eqref{eq:general_deviation}, is that
+$\delta\omega_{k}$ and $\delta\tau_{k}$ depend, in general, on the BH's source mass and spin.
 %
@@
 \begin{align}
-\omega_{J} &= \frac{1}{M} \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \omega^{(n)}_{J} \, \left( 1 + \gamma \delta \omega^{(n)}_{J} \right), \\
-\tau_{J}   &= M     \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \tau^{(n)}_{J}   \, \left( 1 + \gamma \delta \tau^{(n)}_{J} \right),
+\omega_{k} &= \frac{1}{M} \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \omega^{(n)}_{k} \, \left( 1 + \gamma \delta \omega^{(n)}_{k} \right), \\
+\tau_{k}   &= M     \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \tau^{(n)}_{k}   \, \left( 1 + \gamma \delta \tau^{(n)}_{k} \right),
 \end{align}
@@
 where $M$ and $\chi$ are the detector-frame mass and dimensionless spin of the
-black hole; $\omega_{K}^{n}$, $\tau_{K}^{n}$ are dimensionless coefficients
-of the spin expansion for Kerr QNMs; $\delta\omega_{K}^{n}$, $\delta\tau_{K}^{n}$ are
+black hole; $\omega_{k}^{n}$, $\tau_{k}^{n}$ are dimensionless coefficients
+of the spin expansion for Kerr QNMs; $\delta\omega_{k}^{(n)}$, $\delta\tau_{k}^{(n)}$ are
 source-independent dimensionless coefficients that characterize the corrections to the Kerr QNM at each spin-order;
@@
 This means we can identify the $M$ and $\chi$ with their \emph{corresponding GR values}.
+
+We remark that in the GR limit, where $\delta\omega_{k}^{(n)} = \delta\tau_{k}^{(n)} = 0$ $\forall\, n$,
+the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
+the Kerr QNMs for spins $\chi \lesssim 0.7$.
+%
+The values of the fitting coefficients $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$
+can be found in Ref.~\cite{Maselli:2019mjd}, Table I.
 
@@
 %
-where $\theta(t)$ is the Heaviside step function. The merger-ringdown waveform is expressed as an exponentially damped sinusoid ~\citep{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
+where $\theta(t)$ is the Heaviside step function. The merger-ringdown waveform is expressed as an exponentially damped sinusoid~\citep{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
 %
@@
 %
-are the complex frequencies of the fundamental (n=0 overtone) QNMs of the remnant BH.
-The frequencies $\omega_{l m 0}$ and damping times $\tau_{l m 0}$ of the $(l, m)$ QNM can be read off from the real and imaginary parts of  $\sigma_{l m0}$ respetively.
+are the complex frequencies of the fundamental ($n=0$ overtone) QNMs of the remnant BH.
+%
+The frequencies $\omega_{l m 0}$ and damping times $\tau_{l m 0}$ of the $(l,
+m)$ QNM can be read off from the real and imaginary parts of $\sigma_{l m 0}$
+respectively.
+%
 The functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l m}(t)$ are defined in~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
@@
 Hence,
-
-\begin{subequations}
-\begin{eqnarray}
-\omega_{l m 0}^{\text{GR}} &=& \omega_{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,\\
-\tau _{l m 0}^{\text{GR}} &=& \tau _{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,.
-\end{eqnarray}
-\end{subequations}
-where $(\omega_{l m 0}^{\text{GR}}, \tau _{l m 0}^{\text{GR}} )$ refer to the QNM predictions in baseline \SEOB{} model.
-In this paper, however, we introduce a completely different expression of the QNM frequencies $(\omega_{l m 0}, \tau _{l m 0})$, as a series expansion on the spin of the remnant object $\chi_f$ [see Eqs.~\eqref{eq:kerr_expansion}].
-For the rest of the paper, in keeping with the conventions introduced in Sec.~\ref{sec:review_parspec}, we are going to use the index $k$ to refer to $(l, m,n=0)$ mode.
-Accordingly, we are going to use $(\omega_k, \tau _k)$ to refer to $(\omega_{l m 0}, \tau _{l m 0})$ respectively.
-
-In this formalism our QNM frequencies are expressed through functions,
 %
@@
 \begin{align}
-\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\})\\
-\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\})
+\omega_{l m 0}^{\text{GR}} &= \omega_{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,\\
+\tau _{l m 0}^{\text{GR}} &= \tau _{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,.
 \end{align}
@@
 %
-where the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict the final mass and spin $(M_f,\, \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+where $(\omega_{l m 0}^{\text{GR}}, \tau_{l m 0}^{\text{GR}} )$ refer to the
+QNM predictions in baseline \SEOB{} model.
+%
+In this paper, however, we introduce a completely different expression of the
+QNM frequencies $(\omega_{l m 0}, \tau_{l m 0})$, as a series expansion on the
+spin of the remnant object $\chi_f$ [see Eqs.~\eqref{eq:kerr_expansion}].
+%
+For the rest of the paper, in keeping with the conventions introduced in
+Sec.~\ref{sec:review_parspec}, we are going to use the index $k$ to refer to
+$(l, m,n=0)$ mode. Accordingly, we are going to use $(\omega_k, \tau _k)$ to
+refer to $(\omega_{l m 0}, \tau _{l m 0})$ respectively.
+
+In this formalism our QNM frequencies are expressed through functions,
+%
+\begin{subequations}
+\begin{align}
+\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\}),\\
+\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\}),
+\end{align}
+\end{subequations}
+%
+where we fixed a certain value of $p$, and the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict
+the final mass and spin $(M_f,\, \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+%
+% HS: we implicitly fixed p here. Could we leave it free in PE study. This is similar
+% to the 'number of dimensions'-like studies. Here it would tells us quite generically
+% what is the dimension of the modification to the EH-action we include!
 %
 Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$
-defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and
-$\{\delta \tau_k^{(j)}\}$, where $j$ ranges from zero to the power of spin in Eqs.~\eqref{eq:kerr_expansion}
-up to which we include corrections.
-%
-For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$, terms for just the $k=(2,2,0)$ mode, then we would just have two additional degrees of freedom, $(\delta \omega_0^{(0)}, \delta \tau_0^{(0)})$.
-In this paper, we would restrict ourselves to corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
-
-Using this parameterized waveform model, which we will call $\pSEOB$ in this paper, we infer bounds on our beyond-GR parameters for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}.
-We detail these results in Sec.~\ref{sec:results}.
+defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta
+\omega_k^{(n)}\},$ and $\{\delta \tau_k^{(n)}\}$, where $n$ ranges from zero to
+the power of spin in Eqs.~\eqref{eq:kerr_expansion} up to which we include
+corrections.
+%
+For example, if we restrict ourselves to corrections with $n=0$, or
+$\chi_f^0$, to the $k=(2,2,0)$ mode only, then we would just have two
+additional parameters, $(\delta \omega_0^{(0)}, \delta \tau_0^{(0)})$.
+%
+In this paper, we will restrict ourselves to corrections to the $n=0$ and
+$n=1$ terms, i.e., leading and next-to-leading order corrections to the spin,
+$\chi_f$.
+
+Using this parameterized waveform model, which we will call $\pSEOB$ in this
+paper, we infer bounds on our beyond-GR parameters for specific cases of
+modified gravity theories outlined in Sec.~\ref{sec:review_theories}. We detail
+these results in Sec.~\ref{sec:results}.
+%
+\hs{Should we call this waveform differently to distinguish it from your previous papers?}
 %
@@
 %
-We begin by expanding $\omega$ and $\tau$, given by Eqs.~\eqref{eq:kerr_expansion} as,
+We begin by rewriting $\omega_{k}$ and $\tau_{k}$, given by Eqs.~\eqref{eq:kerr_expansion} as,
 %
@@
 \begin{align}
-M \omega_{220} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
+M \omega_{k} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
 + \sum_{n=0}^{N_{\rm max}} \chi^{j} \omega^{j}\,,
 \\
-\tau_{220}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
-+ \sum_{n=0}^{N_{\rm max}} \chi^{j} \tau^{j}\,,
+\tau_{k}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
++ \sum_{n=0}^{N_{\rm max}} \chi^{(n)} \tau^{(n)}\,,
 \end{align}
@@
 %
-where, recall, we focus on the $\ell = m = 2$, $n=0$ QNM and have pulled out of
-the sum all beyond-GR corrections, restricting ourselves to the nonspinning
-($n=0$) and linear-order in spin ($n=1$) corrections to the Kerr QNMs.
-%
-These corrections are encoded in the coefficients $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$.
-
-Just as in GR where the coefficients $\omega^{j}$, $\tau^{j}$ are determined by
-comparison against the Kerr QNMs, a theory-specific calculation predicts the
-numerical values of $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$
-%
+We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
+QNM, i.e., $k = \{2,\, 2,\, 0\}$. For this reason we will omit the subcripts
+$k$ hereafter and no ambiguity in notation between the overtone index and the
+subscript $n$ in the series should arise.
+%
+We have also pulled out from the sum all beyond-GR corrections, restricting
+ourselves to the nonspinning ($n=0$) and linear-order in spin ($n=1$)
+corrections to the Kerr QNMs.
+%
+% These corrections are encoded in the coefficients $\delta\omega^{(n)}$ and $\delta\tau^{(n)}$.
+
+How can we determine the beyond-GR corrections? In GR, comparison between the numerically determined
+Kerr QNMs against the fitting formula~\eqref{eq:qnm_nongr_iso} fixes the GR expansion coefficients
+$\omega^{(n)}$, $\tau^{(n)}$.
+%
+We can proceed in a similar way with QNMs calculated in the context of a beyond-GR theory.
+%
+In particular, in the literature, we can already find fitting formulas relating
+the QNMs to the BHs mass, spin and coupling constant $\ell$, the latter being
+specific to each theory, up to $n=1$ in the spin expansion.
+%
+The idea is then to compare these formulas against Eq.~\eqref{eq:qnm_nongr_iso}
+to fix $p$, $\delta\omega^{(n)}$, and $\delta\tau^{(n)}$.
+
 This means that using the $\pSEOB$ waveform model with theory-specific informed
-QNMs we reduce the parameters space of beyond-GR parameters to one, i.e., to
-only $\gamma$, which in turn contains information about the length scale $\ell$.
-%
-It is important to emphasize that our procedure is different from that of Ref.~\cite{Carullo:2021dui}
-which, for a given value of $p$, varied all $\ell$, $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ parameters.
-
-As we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating BHs
-is modified gravity theories come in two families depending on their transformation upon a parity
-transformation: axial and polar. Which is the one we use to match against Eqs.~\eqref{eq:qnm_nongr_iso}?
-%
-To answer this question one has to work on a theory-by-theory case and in each theory perform a
-a translation between the metric perturbations $h_{\mu\nu}$ in the Regger-Wheeler-Zerilli gauge and
-connect it with the transverse-traceless gauge used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
+QNMs we reduce the parameter space of beyond-GR parameters to $\ell$ alone.
+%
+We emphasize that our procedure is different from that of
+Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell$,
+$\delta\omega^{(n)}$ and $\delta\tau^{(n)}$ parameters.
+
+As we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating
+BHs is modified gravity theories come in two families depending on their
+transformation upon a parity transformation: axial and polar. Which is the one
+we use to match against Eqs.~\eqref{eq:qnm_nongr_iso}?
+%
+To answer this question one has to work on a theory-by-theory case and in each
+theory perform a translation between the metric perturbations $h_{\mu\nu}$ in
+the Regger-Wheeler-Zerilli gauge and connect it with the transverse-traceless
+gauge used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
 %
@@
 
-% ---------------------------
-% CONCRETE EXAMPLE OF MAPPING
-% ---------------------------
-Let us show one concrete example of how this mapping is done.
-%
-In Ref.~\cite{Wagle:2021tam} the QNMs of slow-rotating BHs in dCS gravity were calculated
-and it was found that the axial gravitational modes have their damping time increased as we
-increase the Chern-Simons coupling $\ell_{\rm CS}$ at fixed spin $\chi$ of the BH.
-%
-Having selected this branch of QNMs we can proceed to determine $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
-%
-Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
-%
-\begin{equation}
-    M \omega^{\rm CS}_{220} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
-    \label{eq:omega_dsc_eg}
-\end{equation}
-%
-and similarly for the imaginary part ${\rm Im}(\sigma_{220}) =  - 1 / \tau^{\rm CS}_{220}$.
-%
-Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [thus $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
-and $c_{i}$ are fitting coefficients.
-%
-In the context of a binary BH merger, $M$ is interpreted as the remnant mass $\Mf$.
-
-We can now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm CS}$, and
-gather the terms proportional to $\ell_{\rm CS}$.
-%
-Doing so, we find,
-%
-\begin{align}
-    \Mf \, \omega^{\rm CS}_{220} &=
-    \left[ 0.3722 + 1.1945 (\ell_{\rm CS} / \Mf)^4 \right]
-    \nonumber \\
-    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm CS} / \Mf)^4 \right] \, \chi\,,
-\end{align}
-%
-where we made use of the numerical value of the coefficients $c_{i}$ and,
-reassuringly, the nonrotating and linear-in-spin coefficients above agree with those
-of~\cite{Maselli:2019mjd} to xx\%.
-%
-We now isolate the dCS corrections and compare against Eq.~\eqref{eq:qnm_nongr_iso},
-whcih yields,
-%
-\begin{equation}
-p_{\rm CS} = 4\,, \quad \delta \omega^{(0)}_{\rm CS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm CS} = 41.199\,.
-\label{eq:cs_omega_coefs}
-\end{equation}
-%
-The same procedure can be carried for $\tau^{(i)}$, which results in,
-%
-\begin{equation}
-\delta \tau^{(0)}_{\rm CS} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm CS} = 794.66\,.
-\label{eq:cs_tau_coefs}
-\end{equation}
-%
-which completes the set of fixed parameters beyond-GR parameters in the ringdown of the \pSEOB{} waveform model.
-%
-We remark that the alarmingly large values of $\delta \omega_{\rm CS}^{(1)}$ and $\delta \tau_{\rm CS}^{(1)}$
-are compensated by the assumptions that $(\ell_{\rm CS} / M_f)^2$ and $\chi$ are much less than unity. These
-are the assumptions use to calculate the QNM frequencies both in Ref.~\cite{Wagle:2021tam} and also in
-other gravity theories considered here~\cite{Pierini:2021jxd,Cano:2021myl}.
-%
-As we said before, the only free beyond-GR parameter left is now $\ell_{\rm CS}$.
+We performed the mapping between theory-specific QNM calculation and the ParSpec framework
+under the hypothesis above for the theories listed in Sec.~\ref{sec:review_theories}.
+%
+We leave the details of our calculation to Appendix~\ref{app:map_details} and
+summarize our result in Table~\ref{tab:ref_theories_qnms}.
 
@@
 
-\begin{table*}[th]
-\begin{tabular}{c | c c c c c c c c}
-\hline
-\hline
-Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
-\hline
-EdGB      & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
-dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
-cEFT  & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} & \dots  & \dots \\
-qEFT  & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl} & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
+% \begin{table*}[th]
+% \begin{tabular}{c | c c c c c c c c}
+% \hline
+% \hline
+% Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
+% \hline
+% EdGB      & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
+% dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
+% cEFT  & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} & \dots  & \dots \\
+% qEFT  & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl} & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
+% \hline
+% \hline
+% \end{tabular}
+% \caption{Summary of the quasinormal modes calculations.
+% %
+% We summarize each theory we have considered together with: the exponent $p$ at
+% which their QNM-modification enters, the corresponding modifications to the
+% oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
+% references from which we used the results from and the current best constraint
+% (if applicable).
+% %
+% In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
+% with the length scale $\ell$.
+% %
+% }
+% \label{tab:ref_theories_qnms}
+% \end{table*}
+
+\begin{table}[t]
+\begin{tabular}{c | c c c c c c}
+\hline
+\hline
+Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
+\hline
+EdGB        & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
+dCS         & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}  \\
+cubic EFT   & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} \\
+quartic EFT & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl}  \\
 \hline
@@
 \end{tabular}
-\caption{Summary of the quasinormal modes calculations.
+\caption{Summary of theory-specific QNM calculations.
 %
@@
 (if applicable).
-%
-In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
-with the length scale $\ell$.
-%
 }
 \label{tab:ref_theories_qnms}
-\end{table*}
+\end{table}
 
@@
 
+\appendix
+
+\section{Details of the determination of the theory-specific
+ParSpec coefficients}
+\label{app:map_details}
+
+\subsection{dynamical Chern-Simons}
+\label{app:map_dcs}
+
+Let us show one concrete example of how this mapping is done.
+%
+In Ref.~\cite{Wagle:2021tam} the QNMs of slow-rotating BHs in dCS gravity were calculated
+and it was found that the axial gravitational modes have their damping time increased as we
+increase the Chern-Simons coupling $\ell_{\rm CS}$ at fixed spin $\chi$ of the BH.
+%
+Having selected this branch of QNMs we can proceed to determine $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
+%
+Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
+%
+\begin{equation}
+    M \omega^{\rm CS}_{220} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+    \label{eq:omega_dsc_eg}
+\end{equation}
+%
+and similarly for the imaginary part ${\rm Im}(\sigma_{220}) =  - 1 / \tau^{\rm CS}_{220}$.
+%
+Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [thus $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
+and $c_{i}$ are fitting coefficients.
+%
+In the context of a binary BH merger, $M$ is interpreted as the remnant mass $\Mf$.
+
+We can now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm CS}$, and
+gather the terms proportional to $\ell_{\rm CS}$.
+%
+Doing so, we find,
+%
+\begin{align}
+    \Mf \, \omega^{\rm CS}_{220} &=
+    \left[ 0.3722 + 1.1945 (\ell_{\rm CS} / \Mf)^4 \right]
+    \nonumber \\
+    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm CS} / \Mf)^4 \right] \, \chi\,,
+\end{align}
+%
+where we made use of the numerical value of the coefficients $c_{i}$ and,
+reassuringly, the nonrotating and linear-in-spin coefficients above agree with those
+of~\cite{Maselli:2019mjd} to xx\%.
+%
+We now isolate the dCS corrections and compare against Eq.~\eqref{eq:qnm_nongr_iso},
+whcih yields,
+%
+\begin{equation}
+p_{\rm CS} = 4\,, \quad \delta \omega^{(0)}_{\rm CS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm CS} = 41.199\,.
+\label{eq:cs_omega_coefs}
+\end{equation}
+%
+The same procedure can be carried for $\tau^{(i)}$, which results in,
+%
+\begin{equation}
+\delta \tau^{(0)}_{\rm CS} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm CS} = 794.66\,.
+\label{eq:cs_tau_coefs}
+\end{equation}
+%
+which completes the set of fixed parameters beyond-GR parameters in the ringdown of the \pSEOB{} waveform model.
+%
+We remark that the alarmingly large values of $\delta \omega_{\rm CS}^{(1)}$ and $\delta \tau_{\rm CS}^{(1)}$
+are compensated by the assumptions that $(\ell_{\rm CS} / M_f)^2$ and $\chi$ are much less than unity. These
+are the assumptions use to calculate the QNM frequencies both in Ref.~\cite{Wagle:2021tam} and also in
+other gravity theories considered here~\cite{Pierini:2021jxd,Cano:2021myl}.
+%
+As we said before, the only free beyond-GR parameter left is now $\ell_{\rm CS}$.
+
 %%%%%%%%%%%%%%%%%

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: updated detailed summary table styles for clarity

@@
 which their QNM-modification enters, the corresponding modifications to the
-oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
-references from which we used the results from and the current best constraint
-(if applicable).
+oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
+references from which we used the results from.
 }
@@
 \hline
-Event & $j$ & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+$N_{\rm max}$ & Event &  EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
               &       &  bound? & bound?  &                            \\
 \hline
-GW150914 & $j = 0$    & No  & Yes & -- \\
-GW150914 & $j = 0, 1$ & No  & Yes & -- \\
-GW200129 & $j = 0$    & No  & Yes & -- \\
-GW200129 & $j = 0, 1$ & No  & Yes & -- \\
-Combined & $j = 0$    & --  & Yes & -- \\
-Combined & $j = 0, 1$ & --  & Yes & -- \\
+  & GW150914 & No  & Yes & -- \\
+0 & GW200129 & No  & Yes & -- \\
+  & Combined & --  & Yes & -- \\
+\hline
+  & GW150914 & No  & Yes & -- \\
+1 & GW200129 & No  & Yes & -- \\
+  & Combined & --  & Yes & -- \\
 \hline
@@
 \hline
-Event & $j$ & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
               &       & bound? & bound?  &                            \\
 \hline
-GW150914 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant 46.5$~km \\
-GW150914 & $j = 0, 1$ & Yes & No  & --                                 \\
-GW200129 & $j = 0$    & Yes & Yes & $\ell_{\rm CS} \leqslant 43.9$~km \\
-GW200129 & $j = 0, 1$ & Yes & No  & --                                 \\
-Combined & $j = 0$    & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
-Combined & $j = 0, 1$ & Yes & No  & --                                 \\
+      & GW150914 & Yes & Yes & $\ell_{\rm CS} \leqslant 46.5$~km \\
+0     & GW200129 & Yes & Yes & $\ell_{\rm CS} \leqslant 43.9$~km \\
+      & Combined & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
+\hline
+      & GW150914 & Yes & No  & --                                 \\
+1     & GW200129 & Yes & No  & --                                 \\
+      & Combined & Yes & No  & --                                 \\
 \hline
@@
 \hline
-Event & $j$ & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
               &       & bound? & bound?  &                            \\
 \hline
-GW150914 & $j = 0$    &     &     &    \\
-GW150914 & $j = 0, 1$ &     &     &    \\
-GW200129 & $j = 0$    &     &     &    \\
-GW200129 & $j = 0, 1$ &     &     &    \\
-Combined & $j = 0$    &     &     &    \\
-Combined & $j = 0, 1$ &     &     &    \\
+  & GW150914 &  &     &    \\
+0 & GW200129 &  &     &    \\
+  & Combined &  &     &    \\
+\hline
+  & GW150914 &  &     &    \\
+1 & GW200129 &  &     &    \\
+  & Combined &  &     &    \\
 \hline
@@
 We now isolate the dCS corrections and compare against Eq.~\eqref{eq:qnm_nongr_iso},
-whcih yields,
+which yields,
 %
@@
 %
-The same procedure can be carried for $\tau^{(i)}$, which results in,
+We carry the same steps for $\tau^{(i)}$, which results in,
 %

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: example waveform

@@
 
-In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
-the ParSpec implementation of each theory and give credit to the papers
-which calculated the QNMs.
+\begin{table}[t]
+\begin{tabular}{c | c c c c c c}
+\hline
+\hline
+Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
+\hline
+EdGB        & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
+dCS         & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}  \\
+cubic EFT   & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} \\
+quartic EFT & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl}  \\
+\hline
+\hline
+\end{tabular}
+\caption{Summary of theory-specific QNM calculations.
+%
+We summarize each theory we have considered together with: the exponent $p$ at
+which their QNM-modification enters, the corresponding modifications to the
+oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
+references from which we used the results from.
+}
+\label{tab:ref_theories_qnms}
+\end{table}
+
+In Fig.~\ref{fig:example_waveform} we show an illustrative waveform for the case of the cubic EFT
+of gravity include the leading-order $n = 0$ deformations to the fundamental QNM.
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
+\caption{(Color online).~Example of an waveform.}
+\label{fig:example_waveform}
+\end{figure}
 
@@
 
-\begin{table}[t]
-\begin{tabular}{c | c c c c c c}
-\hline
-\hline
-Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
-\hline
-EdGB        & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
-dCS         & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}  \\
-cubic EFT   & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} \\
-quartic EFT & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl}  \\
-\hline
-\hline
-\end{tabular}
-\caption{Summary of theory-specific QNM calculations.
-%
-We summarize each theory we have considered together with: the exponent $p$ at
-which their QNM-modification enters, the corresponding modifications to the
-oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
-references from which we used the results from.
-}
-\label{tab:ref_theories_qnms}
-\end{table}
-
 %%%%%%%%%%%%%%%%%

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: minor changes

@@
 \int_{f_{\rm low}}^{f_{\rm high}} \, \dd f \,
-\frac{\tilde{A}^{\ast}(f) \tilde{B}(f) + \tilde{A}(f) \tilde{B}^{\ast}(f)}{S_{n}(f)}
+\frac{\tilde{A}^{\ast}(f) \tilde{B}(f) + \tilde{A}(f) \tilde{B}^{\ast}(f)}{S_{n}(f)}\,,
 \end{equation}
@@
 \texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx},
-which is part of \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
+which is part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
 %

### 2022-03-15 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
upd

@@
 %
-To answer this question one has to work on a theory-by-theory case and in each
-theory perform a translation between the metric perturbations $h_{\mu\nu}$ in
-the Regger-Wheeler-Zerilli gauge and connect it with the transverse-traceless
-gauge used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
+To answer this question one has to work with a chosen theory and perform a
+translation between the metric perturbations $h_{\mu\nu}$ in the
+Regger-Wheeler-Zerilli gauge and connect it with the transverse-traceless gauge
+used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
 %
@@
 In beyond-GR theories, isospectrality is in general broken (see the discussion
-in Ref.~\cite{Hui:2021cpm} for a counterexample). and thus how axial and polar
-gravitational QNMs appear in the GW signal has to be answered in
-theory-by-theory.
+in Ref.~\cite{Hui:2021cpm} for a counterexample).
+%
+Thus, how axial and polar gravitational QNMs appear in the GW signal has to be
+answered on theory-by-theory basis.
 %
@@
 %
-The justification is this is the mode which, if excited during the merger, is
+The justification is this is the mode (if excited during the merger) which is
 the most likely to appear in the signal.
@@
 %
-We leave the details of our calculation to Appendix~\ref{app:map_details} and
-summarize our result in Table~\ref{tab:ref_theories_qnms}.
+We summarize our result in Table~\ref{tab:ref_theories_qnms} and
+leave the details of our calculations to Appendix~\ref{app:map_details}.
 
@@
 
-In Fig.~\ref{fig:example_waveform} we show an illustrative waveform for the case of the cubic EFT
-of gravity include the leading-order $n = 0$ deformations to the fundamental QNM.
+In Fig.~\ref{fig:example_waveform} we show an illustrative waveform for GR (solid line; using the \texttt{SEOBNR} model) and in the cubic EFT of gravity (dashed line; using the \pSEOB{} model),
+including the leading-order $n = 0$ deformations to the fundamental QNM (see Table~\ref{tab:ref_theories_qnms}).
+%
+We chose binary parameters similar to GW150914, consisting of a quasicircular,
+nonspinning binary with detector-frame masses
+$m_1^{\rm dec} = 39\msun$ and $m_2^{\rm dec} = 31\msun$.
+%
+The top panel shows the $+$ polarization of the GW $h_{+}$ in both theories,
+while the bottom panel shows the amplitude $|h| = \sqrt{h_{+}^2 + h_{\times}^2}$
+and instantaneous frequency $f$, all as functions of time $t$.
+%
+The signal are identical up to the merger, after which they differ during the ringdown.
+%
+By construction, the ringdown is lasts longer for the cubic EFT of GR waveform and
+with a smaller instantaneous frequency (see the bottom panel) due to the negative value of the
+$\delta\omega^{(0)}$ coefficient in this theory.
 
@@
 
+\hs{I suspect that by construction the $N_{\rm max} = 1$ will fail to satisfy our
+perturbative bounds. If so, add explanation here.}
+
 % -----------------------------------------------------------------------------

### 2022-03-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: cleaned dcs appendix

@@
 the QNMs to the BHs mass, spin and coupling constant $\ell$, the latter being
-specific to each theory, up to $n=1$ in the spin expansion.
+specific to each theory, up to $n=1$ in the spin expansion (see Table~\ref{tab:ref_theories_qnms}).
 %
@@
 The top panel shows the $+$ polarization of the GW $h_{+}$ in both theories,
-while the bottom panel shows the amplitude $|h| = \sqrt{h_{+}^2 + h_{\times}^2}$
+while the bottom panel shows the amplitude $|h| = (h_{+}^2 + h_{\times}^2)^{1/2}$
 and instantaneous frequency $f$, all as functions of time $t$.
@@
 \includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
-\caption{(Color online).~Example of an waveform.}
+\caption{(Color online).~Example GW signal with GW1509140-like parameters
+for both GR (solid line) and cubic EFT of GR (dashed line) with the leading-order
+$n=0$ modifications to the fundamental QNM.
+%
+The former is computed with the \SEOB{} model, while the latter with the
+\pSEOB{} model, with ringdown modifications according to the results in
+Table~\ref{tab:ref_theories_qnms}.
+%
+Top panel: the $+$ polarization $h_{+}(t)$. Bottom panel: the GW amplitude
+$|\tilde{h}(t)|$ (left axes) and the instantaneous frequency $f(t)$ (right axes).
+}
 \label{fig:example_waveform}
@@
 We subsequently marginalize over the remaining parameters to obtain the
-posterior probability distribution function~(PDF) on $\ell$.
-%
-An example of this is shown in Fig. XX.
+posterior probability distribution function~(PDF) on $\ell$, our main quantity of interest.
+%
+% An example of this is shown in Fig. XX.
 
@@
 
-Let us show one concrete example of how this mapping is done.
+% Let us show one concrete example of how this mapping is done.
 %
@@
 %
-Having selected this branch of QNMs we can proceed to determine $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ as follows.
+Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm}, this is the branch of QNMs we will select.
+
+We can now proceed to determine $\delta\omega^{(n)}$ and $\delta\tau^{(n)}$ as follows.
 %
@@
 \begin{equation}
-    M \omega^{\rm CS}_{220} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+    M \omega_{\rm CS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
     \label{eq:omega_dsc_eg}
@@
 %
-and similarly for the imaginary part ${\rm Im}(\sigma_{220}) =  - 1 / \tau^{\rm CS}_{220}$.
-%
-Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$ [thus $\kappa \zeta = (\ell_{\rm CS} / M)^4$]
-and $c_{i}$ are fitting coefficients.
+and similarly for the imaginary part ${\rm Im}(\sigma_{\rm CS}) =  - 1 / \tau_{\rm CS}$.
+%
+Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$, and thus
+%
+\begin{equation}
+\kappa \zeta = (\ell_{\rm CS} / M)^4 \,,
+\end{equation}
+%
+and $c_{i}$ are fitting coefficients which can be found in Ref.~\cite{Wagle:2021tam}, Table II.
 %
@@
 %
-Doing so, we find,
+We obtain
 %
@@
     &\quad + \left[0.1861 + 5.1828 (\ell_{\rm CS} / \Mf)^4 \right] \, \chi\,,
+    \label{eq:omega_dcs_interm}
 \end{align}
 %
-where we made use of the numerical value of the coefficients $c_{i}$ and,
-reassuringly, the nonrotating and linear-in-spin coefficients above agree with those
-of~\cite{Maselli:2019mjd} to xx\%.
-%
-We now isolate the dCS corrections and compare against Eq.~\eqref{eq:qnm_nongr_iso},
-which yields,
+where we made use of the numerical value of the coefficients $c_{i}$.
+%
+We find that (reassuringly) that the nonrotating GR part of the expression above agree with $\omega^{(0)}$ of Ref.~\cite{Maselli:2019mjd}
+to 0.5\% relative percent error. The same error estimate is larger ($\approx 20$\%) for the linear-in-spin coefficient;
+0.1861 in comparison to 0.1258 of Ref.~\cite{Maselli:2019mjd}.
+%
+We attribute this difference to Ref.~\cite{Wagle:2021tam} having fitted Eq.~\eqref{eq:omega_dsc_eg} to QNM data compute to linear-order in spin, whereas~\cite{Maselli:2019mjd}
+fitted Eq.~\eqref{eq:kerr_expansion} to Kerr QNM valid to all orders in spin.
+
+We can now isolate the dCS corrections from Eq.~\eqref{eq:omega_dcs_interm} and
+compare against Eq.~\eqref{eq:qnm_nongr_iso}, to find
 %
@@
 \end{equation}
-%
-We carry the same steps for $\tau^{(i)}$, which results in,
+
+We can carry the same steps for $\tau_{\rm CS}$ and find
 %
@@
 are compensated by the assumptions that $(\ell_{\rm CS} / M_f)^2$ and $\chi$ are much less than unity. These
-are the assumptions use to calculate the QNM frequencies both in Ref.~\cite{Wagle:2021tam} and also in
-other gravity theories considered here~\cite{Pierini:2021jxd,Cano:2021myl}.
-%
-As we said before, the only free beyond-GR parameter left is now $\ell_{\rm CS}$.
+are the assumptions use to calculate the QNM frequencies both in Ref.~\cite{Wagle:2021tam}.
 

### 2022-03-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: updated corner plot

@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/tmp_corner_plot.pdf}
+\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
 \caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $M_f$, and redshift $z$ for GW150915, using the same waveform model,
+detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
 but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
@@
 We see that the introduction of the non-GR parameters does not bias the inference on the source parameters.
-%
-\hs{TODO: increase font size and move it to an Appendix.}
 }

### 2022-03-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: morning updates

@@
 %
-We see that the introduction of the non-GR parameters does not bias the inference on the source parameters.
+We see that the introduction of the non-GR parameters does not bias the
+inference on the source parameters.
 }
@@
 
-\hs{I suspect that by construction the $N_{\rm max} = 1$ will fail to satisfy our
+\hs{I suspect that by construction the $N_{\rm max} = 1$ cases will often fail to satisfy our
 perturbative bounds. If so, add explanation here.}
@@
 
+\subsection{Einstein-dilaton-Gauss-Bonnet}
+\label{app:map_edgb}
+
 \subsection{dynamical Chern-Simons}
@@
 
-We can now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm CS}$, and
+We now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm CS}$, and
 gather the terms proportional to $\ell_{\rm CS}$.
@@
 \begin{align}
-    \Mf \, \omega^{\rm CS}_{220} &=
+    \Mf \, \omega_{\rm CS} &=
     \left[ 0.3722 + 1.1945 (\ell_{\rm CS} / \Mf)^4 \right]
@@
 
+\subsection{Effective-field-theories GR}
+\label{app:map_eftofgr}
+
 %%%%%%%%%%%%%%%%%

### 2022-03-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
separated the pe sec

@@
 \section{Parameter Inference}
-
-In this section, we provide a basic outline of the Bayesian formalism we use to
-infer the properties of the underlying GW signal, identify the most promising
-events from the catalog of GW observations to base our analyses on, and discuss
-the key insights they provide in constraining predictions of modified gravity
-theories.
-
-\subsection{Bayesian formalism}
-If we assume that a GW signal observed in detector data $d$ is accurately
-described by our waveform model \pSEOB{}, we can infer the parameters of the
-model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using the Bayes
-theorem,
-%
-\begin{equation}
-P(\bm{\lambda} \vert d, \mathcal{H}) =
-\frac{P(\bm{\lambda} \vert \mathcal{H}) \, \mathcal{L}(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
-\label{eq:bayes}
-\end{equation}
-%
-where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
-$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
-$\mathcal{L}(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
-$P(d \vert \mathcal{H})$ the evidence.
-%
-The set of parameters, $\bm{\lambda}$ is the union between the GR waveform
-model parameters~$\bm{\theta}$, detailed in Sec.~\ref{sec:review_pSEOB}, and
-the non-GR parameter of $\ell$, i.e.,
-%
-\begin{equation}
-\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
-\label{eq:def_params}
-\end{equation}
-%
-which, we recall, set the characteristic lengthscale in which deviations from
-GR become relevant in each of the theories described in
-Sec.~\ref{sec:review_theories}.
-
-% As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
-% constants in the cases of EdGB and dCS theories, but two in the cubic and
-% quartic EFTofGR.
-% %
-% We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
-% fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
-% %
-
-Assuming Gaussian and stationary noise, we can write the (log) likelihood function as,
-%
-\begin{equation}
-\ln P(d \vert \bm{\lambda},\mathcal{H}) \propto
-- \tfrac{1}{2}
-\langle
-d - h(\bm{\lambda}) \vert d - h(\bm{\lambda})
-\rangle\,,
-\end{equation}
-%
-with noise-weighted inner product $\langle \cdot | \cdot \rangle$ defined as,
-%
-\begin{equation}
-\langle A | B \rangle =
-\int_{f_{\rm low}}^{f_{\rm high}} \, \dd f \,
-\frac{\tilde{A}^{\ast}(f) \tilde{B}(f) + \tilde{A}(f) \tilde{B}^{\ast}(f)}{S_{n}(f)}\,,
-\end{equation}
-%
-where $\tilde{A}(f)$ is the Fourier transform of $A(t)$, the asterisk denotes
-complex conjugation and $S_{n}(f)$ is the power spectrum density of the
-detector.
-%
-Assuming a specific prior distribution for our parameters, we stochastically
-sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
-\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx},
-which is part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
-%
-We subsequently marginalize over the remaining parameters to obtain the
-posterior probability distribution function~(PDF) on $\ell$, our main quantity of interest.
-%
-% An example of this is shown in Fig. XX.
-
-\subsection{Priors}
-
-The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \text{sin} \iota$.
-For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
-This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.
-%
-The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
-
-Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$,
-as already mentioned in the previous section, we hold $\{\delta \omega_k^{(j)}\},$
-and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$
-to freely vary.
-%
-For such cases, we assume a prior uniform between appropriate ranges on $\ell$,
-making sure that our marginalized posterior distributions on $\ell$ do not rail
-over the maximum prior value on $\ell$.
-
-\subsection{Event selection}
-
-The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an
-\emph{IMR} model which infers the properties of the underlying GW signal,
-including (independently) its ringdown properties, using the Bayesian formalism
-above. Naturally, the most promising candidates for our analyses are high-mass
-\emph{and} loud GW observations with a significant signal-to-noise ratio (SNR)
-in the post-merger part of the signal.
-%
-The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
-signals not all of which are relevant for a BH ringdown analysis. In fact, in
-an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM}
-analysis\footnote{See, in particular, Sec.VIII A.2
-in~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model
-presented in this paper, identified two events which provided the strongest
-bounds on measurements of the dominant $(220)$ QNM --
-GW150914~\cite{LIGOScientific:2016aoc} and
-GW200129~\cite{LIGOScientific:2021djp}.
-%
-These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are
-extremely similar in their source properties. These are also two of the loudest
-BBH signals observed to date with a total network SNR of XX and XX
-respectively.
-%
-Moreover, and what is more relevant for our analysis, is their post-inspiral
-(merger-ringdown) SNRs, which at XX and XX respectively (see the columns for
-$\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
-Table IV of~\cite{LIGOScientific:2021sio}).
-%
-In this paper, we are going to focus on these two GW events as our probes of
-the BH ringdown in modified theories of gravity.
-
-The parameter inference in this paper follows configurations identical to the
-ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
-Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector event (HL) while
-GW200129 was 3-detector (HLV).
-%
-We consequently use the same strain data $h(t)$, detector
-power-spectral-densities $S_n(f)$ and calibration envelopes as were used for
-the analyses in Ref.~\cite{LIGOScientific:2021sio}.
-%
-The only difference between the sampling configurations is that we do not
-sample over the fractional deviations in the $(220)$ QNM frequencies and
-damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
-and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions.
-%
-In the section to follow, we enumerate through the different theories and
-outline the highlight results. Whenever possible, we also combine results from
-multiple events to obtain the strongest possible bound on $\ell$.
-
-% -----------------
-% Corner plots here
-% -----------------
-
-As a first test ...
-\hs{Move to an appendix.}
-
-\begin{figure}[t]
-\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
-\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
-but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
-dCS gravity and $j=0$). The contours represent 90\% credible regions.
-%
-We see that the introduction of the non-GR parameters does not bias the
-inference on the source parameters.
-}
-\label{fig:corner_plot}
-\end{figure}
-
-\subsection{General remarks on the interpretation of our results}
-\label{sec:remaks}
-
-There are two conditions that we must take into account before
-we can confidently claim to have placed a constraint, within our model's assumptions,
-with our parameter estimation study.
-
-First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
-consider must be considered as an effective field theory, meaning it should be
-considered valid only below an energy scale, or equivalently, a length scale.
-%
-As a cut-off length scale for the validity of the EFT we use,
-%
-\begin{equation}
-\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, G \mathfrak{m} / c^2 \,,
-\label{eq:def_cutoff}
-\end{equation}
-%
-where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
-value of one of the masses involved in the problem.
-%
-We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
-dimensions of length and hence can be compared to the coupling strength $\ell$.
-%
-In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
-but here we consider $\varepsilon \in [0, 1]$.
-%
-We will say that a bound has been placed on $\ell$, if most of the support of
-the posterior distribution function $P(\ell)$ is in the interval
-$[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
-%
-In practice, this can be quantified through the cumulative distribution function
-(CDF) associated to the marginalized posterior distribution $P(\ell)$,
-%
-\begin{equation}
-P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} P(\ell') \, \dd \ell'\,.
-\label{eq:def_cdf}
-\end{equation}
-%
-For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
-%
-\begin{equation}
-% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
-P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
-\quad \textrm{(EFT bound)},
-\label{eq:eft_bound}
-\end{equation}
-%
-and likewise for other percentiles.
-
-Another question we must consider is the following: what is the mass $\mathfrak{m}$ that we should use
-in Eq.~\eqref{eq:def_cutoff}?
-%
-In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, which attempted to
-constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
-the GW signal alone, it was natural to chose the secondary's mass $m_2$ as the most
-conservative choice, for it is by definition the smallest mass and hence
-places the lowest threshold for the validity of either theory as an EFT.
-%
-In our problem, the answer is not as clear. On the one hand, since we are
-interested in the ringdown part of the signal, it is natural to use the
-final mass $M_f$ to compute the cut-off $\Lambda_{\rm EFT}$.
-%
-On the other hand, one may argue that the modified gravity theory under study
-should be able to predict a full inspiral, merger, and ringdown of the black
-hole binary before we can even make such a test, and thus the same, more conservative choice
-$\gm = m_2$ should be used.
-%
-Here we adopt an agnostic view to this question and consider \emph{both} masses, $m_2$ and $M_f$, to
-determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
-yield to different interpretations of the results of our parameter estimations.
-
-There is a second criteria we must also consider.
-%
-As already emphasized in Ref.~\cite{Maselli:2019mjd}, the ParSpec
-formalism is by construction perturbative. This means that the non-GR
-deformation parameters are small, that is,
-%
-\begin{equation}
-\gamma \, \delta \omega^{(j)} \ll 1 \,,
-\quad \textrm{and} \quad
-\gamma \, \delta \tau^{(j)} \ll 1 \, \quad \textrm{(ParSpec bound)},
-\label{eq:parspec_bound}
-\end{equation}
-%
-for all $j$ in the expansion in dimensionless spin $\chi$.
-%
-We will also construct posterior distributions for these parameters and check if
-most of their support is concentrated to a domain with values much smaller than
-unity.
-
-\subsection{Stacking posteriors}
-\label{sec:stack}
-
-If, for each event, we find that the constraints~\eqref{eq:eft_bound}
-and~\eqref{eq:parspec_bound} are satisfied, we further combine the individual
-posteriors distribution on $\ell$, allowing us to place a stronger bound on this parameter.
-%
-Let us review how do we calculate this \emph{cumulative posterior distribution} on $\ell$.
-
-% 1. Description of data and assumption o \ell being shared
-Suppose we have a data set $\{d_{i}\}$ of $N$ events which is described by
-model parameters $\bm{\lambda}_{i}$, where $i$ labels each event.
-%
-We assume that the value of the coupling constant $\ell$, given a specific theory,
-is common to all events.
-%
-% 2. Define joint posterior
-%
-The joint posterior for the parameters $\bm{\lambda}_{i}$, that describe the
-data $\{d_{i}\}$, is
-%
-\begin{equation}
-P(\ell, \{\btheta_i\} | \{d_{i}\})
-= \frac{ P(\ell, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) }.
-\label{eq:def_joint_posterior}
-\end{equation}
-%
-where we separated $\ell$ from the GR waveform model parameters $\btheta$ [cf.~Eq.~\eqref{eq:def_params}].
-%
-% 3. Marginalisation to obtain the cumulative posterior
-%
-To obtain the cumulative posterior distribution on $\ell$, we marginalize
-the joint posterior~\eqref{eq:def_joint_posterior} over
-all parameters $\{ \btheta_i \}$, i.e.,
-%
-\begin{align}
-P(\ell | \{d_i\}) &= \int \dd \{\btheta_i\} \, P(\ell, \{\btheta_i\} | \{d_{i}\}),
-\nonumber \\
-                  &= \int \dd \{\btheta_i\} \, \frac{ P(\ell, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) },
-\nonumber \\
-                  &= \frac{P(\ell)}{P(\{d_i\})} \int \dd \{\btheta_i\} \, P(\{\btheta_i\}) \, P( \{d_i\} | \ell, \{\btheta_i\} ),
-\end{align}
-%
-where we have assumed that the prior on $\ell$, $P(\ell)$, is independent of
-the other parameters $\{\btheta_i\}$.
-%
-This allow us to write $P(\ell, \{\btheta_i\} = P(\ell) P(\{\btheta_i\})$
-and then move $P(\ell)$ out of the integral
-%
-We also moved out integral the evidence $P(\{d_i\})$, which is a normalization constant.
-%
-% 4. Factor the integrals in a product due to statistical independence
-%
-We can now factor the probabilities inside the integral, since each event is independent from another:
-%
-\begin{equation}
-P(\ell | \{d_i\}) = \frac{P(\ell)}{P(\{d_i\})}
-\prod_{i=1}^{N}
-\int \dd \btheta_i \, P(\btheta_i) \, P( d_i | \ell_i, \btheta_i ).
-\end{equation}
-%
-% 5. Final formula
-We can now identify the integral as the marginalized likelihood for each individual event
-%
-\begin{equation}
-P(\ell | \{d_i\}) = \frac{P(\ell)}{P(\{d_i\})}
-\prod_{i=1}^{N} P( d_i | \ell_i ),
-\end{equation}
-%
-which we can rewrite as
-%
-\begin{align}
-P(\ell | \{d_i\}) &= \frac{P(\ell)}{P(\{d_i\})}
-\prod_{i=1}^{N} \frac{P(d_i)}{P(\ell_i)} P(\ell_i | d_i)
-\nonumber \\
-&= P(\ell)
-\prod_{i=1}^{N} \frac{P(\ell_i | d_i)}{P(\ell_i)}.
-\label{eq:cumulative_dist_ell}
-\end{align}
-%
-by using Bayes' theorem in the first line and cancelling the evidences in the
-second line. This is our final result.
-
-%
-\hs{Abhirup, maybe move this to the subsection on priors?}
-In our parameter estimation runs that we had to adjust our prior on $\ell$ depending on which event and
-on which theory we examined.
-%
-The reasons are twofold.
-%
-% Describe problem 1
-%
-First, we found that depending on the source parameters $\btheta$,
-large values of $\ell$ could result in unphysical waveforms in the frequency
-band we considered. More specifically, these waveforms have a ringdown which is
-considerable longer than the inspiral-merger part in the detector frequency band.
-%
-The fact that our sampled over these waveforms is perhaps not surprising,
-because, after all, we are by construction adding corrections to the GR QNM
-which \emph{increase} the damping timescale.
-%
-In practice, we found that these edge-cases were problematic to deal with
-\texttt{LALInferenceMCMC}.
-%
-We overcome this problem, we reduced the prior upper-value of our prior on $\ell$.
-%
-This choice does not pose a problem to our parameter estimations, because these
-waveforms differ grossly from the data and thus have negligible likelihood.
-%
-% Describe problem 2
-%
-However, we cannot reduce the prior on $\ell$ too much. If we do so,
-to the marginalized posterior distribution on $\ell$ would rail against
-the prior or, in a more extreme case, even be a uninformative, flat posterior.
-%
-% Summary
-%
-Altogether, this means that the priors $P(\ell)$ are not shared between events and
-they must be taken into account when calculation the cumulative posterior function~\eqref{eq:cumulative_dist_ell}.
-
-Finally, we use one of the approaches of Ref.~\cite{Perkins:2021mhb} to
-compute the product in Eq.~\eqref{eq:cumulative_dist_ell}.
-%
-It method relies on first obtaining a kernel density estimator (KDE) for
-the posterior distribution on $\ell$ for each individual event.
-%
-(See also Refs.~\cite{DelPozzo:2011pg,Cardenas-Avendano:2019zxd,Carullo:2021dui}.)
-%
-Next, we multiply these posteriors according to Eq.~\eqref{eq:cumulative_dist_ell}.
-%
-This approach based on the KDE can have difficulties in dealing with hard cut-offs in the
-distribution, such as the one we impose at $\ell = 0$. We address this issue as
-done in Ref.~\cite{Perkins:2021mhb}, by first doubling our number of samples as
-$\{ s_i \} \cup \{ - s_i \}$, i.e., mirroring the samples across $\ell = 0$.
-%
-We then renormalize the associated KDE numerically in the range $\ell = [0, \infty]$.
+\input{sec_pe}
 

### 2022-03-16 papers/paper_alt_theor_bounds/sec_pe.tex
separated the pe sec

In this section, we provide a basic outline of the Bayesian formalism we use to
infer the properties of the underlying GW signal, identify the most promising
events from the catalog of GW observations to base our analyses on, and discuss
the key insights they provide in constraining predictions of modified gravity
theories.

\subsection{Bayesian formalism}
If we assume that a GW signal observed in detector data $d$ is accurately
described by our waveform model \pSEOB{}, we can infer the parameters of the
model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using the Bayes
theorem,
%
\begin{equation}
P(\bm{\lambda} \vert d, \mathcal{H}) =
\frac{P(\bm{\lambda} \vert \mathcal{H}) \, \mathcal{L}(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
\label{eq:bayes}
\end{equation}
%
where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
$\mathcal{L}(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
$P(d \vert \mathcal{H})$ the evidence.
%
The set of parameters, $\bm{\lambda}$ is the union between the GR waveform
model parameters~$\bm{\theta}$, detailed in Sec.~\ref{sec:review_pSEOB}, and
the non-GR parameter of $\ell$, i.e.,
%
\begin{equation}
\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
\label{eq:def_params}
\end{equation}
%
which, we recall, set the characteristic lengthscale in which deviations from
GR become relevant in each of the theories described in
Sec.~\ref{sec:review_theories}.

% As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
% constants in the cases of EdGB and dCS theories, but two in the cubic and
% quartic EFTofGR.
% %
% We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
% fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
% %

Assuming Gaussian and stationary noise, we can write the (log) likelihood function as,
%
\begin{equation}
\ln P(d \vert \bm{\lambda},\mathcal{H}) \propto
- \tfrac{1}{2}
\langle
d - h(\bm{\lambda}) \vert d - h(\bm{\lambda})
\rangle\,,
\end{equation}
%
with noise-weighted inner product $\langle \cdot | \cdot \rangle$ defined as,
%
\begin{equation}
\langle A | B \rangle =
\int_{f_{\rm low}}^{f_{\rm high}} \, \dd f \,
\frac{\tilde{A}^{\ast}(f) \tilde{B}(f) + \tilde{A}(f) \tilde{B}^{\ast}(f)}{S_{n}(f)}\,,
\end{equation}
%
where $\tilde{A}(f)$ is the Fourier transform of $A(t)$, the asterisk denotes
complex conjugation and $S_{n}(f)$ is the power spectrum density of the
detector.
%
Assuming a specific prior distribution for our parameters, we stochastically
sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx},
which is part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
%
We subsequently marginalize over the remaining parameters to obtain the
posterior probability distribution function~(PDF) on $\ell$, our main quantity of interest.
%
% An example of this is shown in Fig. XX.

\subsection{Priors}

The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \text{sin} \iota$. For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.
%
The prior on $t_0$ is uniform and its range is informed by our detection pipelines.

Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$,
as already mentioned in the previous section, we hold $\{\delta \omega_k^{(j)}\},$
and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$
to freely vary.
%
For such cases, we assume a prior uniform between appropriate ranges on $\ell$,
making sure that our marginalized posterior distributions on $\ell$ do not rail
over the maximum prior value on $\ell$.

\subsection{Event selection}

The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an
\emph{IMR} model which infers the properties of the underlying GW signal,
including (independently) its ringdown properties, using the Bayesian formalism
above. Naturally, the most promising candidates for our analyses are high-mass
\emph{and} loud GW observations with a significant signal-to-noise ratio (SNR)
in the post-merger part of the signal.
%
The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
signals not all of which are relevant for a BH ringdown analysis. In fact, in
an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM}
analysis\footnote{See, in particular, Sec.VIII A.2
in~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model
presented in this paper, identified two events which provided the strongest
bounds on measurements of the dominant $(220)$ QNM --
GW150914~\cite{LIGOScientific:2016aoc} and
GW200129~\cite{LIGOScientific:2021djp}.
%
These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are
extremely similar in their source properties. These are also two of the loudest
BBH signals observed to date with a total network SNR of XX and XX
respectively.
%
Moreover, and what is more relevant for our analysis, is their post-inspiral
(merger-ringdown) SNRs, which at XX and XX respectively (see the columns for
$\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
Table IV of~\cite{LIGOScientific:2021sio}).
%
In this paper, we are going to focus on these two GW events as our probes of
the BH ringdown in modified theories of gravity.

The parameter inference in this paper follows configurations identical to the
ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector event (HL) while
GW200129 was 3-detector (HLV).
%
We consequently use the same strain data $h(t)$, detector
power-spectral-densities $S_n(f)$ and calibration envelopes as were used for
the analyses in Ref.~\cite{LIGOScientific:2021sio}.
%
The only difference between the sampling configurations is that we do not
sample over the fractional deviations in the $(220)$ QNM frequencies and
damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions.
%
In the section to follow, we enumerate through the different theories and
outline the highlight results. Whenever possible, we also combine results from
multiple events to obtain the strongest possible bound on $\ell$.

% -----------------
% Corner plots here
% -----------------

As a first test ...
\hs{Move to an appendix.}

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $j=0$). The contours represent 90\% credible regions.
%
We see that the introduction of the non-GR parameters does not bias the
inference on the source parameters.
}
\label{fig:corner_plot}
\end{figure}

\subsection{General remarks on the interpretation of our results}
\label{sec:remaks}

There are two conditions that we must take into account before
we can confidently claim to have placed a constraint, within our model's assumptions,
with our parameter estimation study.

First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
consider must be considered as an effective field theory, meaning it should be
considered valid only below an energy scale, or equivalently, a length scale.
%
As a cut-off length scale for the validity of the EFT we use,
%
\begin{equation}
\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, G \mathfrak{m} / c^2 \,,
\label{eq:def_cutoff}
\end{equation}
%
where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
value of one of the masses involved in the problem.
%
We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
dimensions of length and hence can be compared to the coupling strength $\ell$.
%
In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
but here we consider $\varepsilon \in [0, 1]$.
%
We will say that a bound has been placed on $\ell$, if most of the support of
the posterior distribution function $P(\ell)$ is in the interval
$[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
%
In practice, this can be quantified through the cumulative distribution function
(CDF) associated to the marginalized posterior distribution $P(\ell)$,
%
\begin{equation}
P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} P(\ell') \, \dd \ell'\,.
\label{eq:def_cdf}
\end{equation}
%
For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
%
\begin{equation}
% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
\quad \textrm{(EFT bound)},
\label{eq:eft_bound}
\end{equation}
%
and likewise for other percentiles.

Another question we must consider is the following: what is the mass $\mathfrak{m}$ that we should use
in Eq.~\eqref{eq:def_cutoff}?
%
In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, which attempted to
constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
the GW signal alone, it was natural to chose the secondary's mass $m_2$ as the most
conservative choice, for it is by definition the smallest mass and hence
places the lowest threshold for the validity of either theory as an EFT.
%
In our problem, the answer is not as clear. On the one hand, since we are
interested in the ringdown part of the signal, it is natural to use the
final mass $M_f$ to compute the cut-off $\Lambda_{\rm EFT}$.
%
On the other hand, one may argue that the modified gravity theory under study
should be able to predict a full inspiral, merger, and ringdown of the black
hole binary before we can even make such a test, and thus the same, more conservative choice
$\gm = m_2$ should be used.
%
Here we adopt an agnostic view to this question and consider \emph{both} masses, $m_2$ and $M_f$, to
determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
yield to different interpretations of the results of our parameter estimations.

There is a second criteria we must also consider.
%
As already emphasized in Ref.~\cite{Maselli:2019mjd}, the ParSpec
formalism is by construction perturbative. This means that the non-GR
deformation parameters are small, that is,
%
\begin{equation}
\gamma \, \delta \omega^{(j)} \ll 1 \,,
\quad \textrm{and} \quad
\gamma \, \delta \tau^{(j)} \ll 1 \, \quad \textrm{(ParSpec bound)},
\label{eq:parspec_bound}
\end{equation}
%
for all $j$ in the expansion in dimensionless spin $\chi$.
%
We will also construct posterior distributions for these parameters and check if
most of their support is concentrated to a domain with values much smaller than
unity.

\subsection{Stacking posteriors}
\label{sec:stack}

If, for each event, we find that the constraints~\eqref{eq:eft_bound}
and~\eqref{eq:parspec_bound} are satisfied, we further combine the individual
posteriors distribution on $\ell$, allowing us to place a stronger bound on this parameter.
%
Let us review how do we calculate this \emph{cumulative posterior distribution} on $\ell$.

% 1. Description of data and assumption o \ell being shared
Suppose we have a data set $\{d_{i}\}$ of $N$ events which is described by
model parameters $\bm{\lambda}_{i}$, where $i$ labels each event.
%
We assume that the value of the coupling constant $\ell$, given a specific theory,
is common to all events.
%
% 2. Define joint posterior
%
The joint posterior for the parameters $\bm{\lambda}_{i}$, that describe the
data $\{d_{i}\}$, is
%
\begin{equation}
P(\ell, \{\btheta_i\} | \{d_{i}\})
= \frac{ P(\ell, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) }.
\label{eq:def_joint_posterior}
\end{equation}
%
where we separated $\ell$ from the GR waveform model parameters $\btheta$ [cf.~Eq.~\eqref{eq:def_params}].
%
% 3. Marginalisation to obtain the cumulative posterior
%
To obtain the cumulative posterior distribution on $\ell$, we marginalize
the joint posterior~\eqref{eq:def_joint_posterior} over
all parameters $\{ \btheta_i \}$, i.e.,
%
\begin{align}
P(\ell | \{d_i\}) &= \int \dd \{\btheta_i\} \, P(\ell, \{\btheta_i\} | \{d_{i}\}),
\nonumber \\
                  &= \int \dd \{\btheta_i\} \, \frac{ P(\ell, \{\btheta_i\}) \, P( \{d_i\} | \ell_i, \{\btheta_i\} ) }{ P(\{d_i\}) },
\nonumber \\
                  &= \frac{P(\ell)}{P(\{d_i\})} \int \dd \{\btheta_i\} \, P(\{\btheta_i\}) \, P( \{d_i\} | \ell, \{\btheta_i\} ),
\end{align}
%
where we have assumed that the prior on $\ell$, $P(\ell)$, is independent of
the other parameters $\{\btheta_i\}$.
%
This allow us to write $P(\ell, \{\btheta_i\} = P(\ell) P(\{\btheta_i\})$
and then move $P(\ell)$ out of the integral
%
We also moved out integral the evidence $P(\{d_i\})$, which is a normalization constant.
%
% 4. Factor the integrals in a product due to statistical independence
%
We can now factor the probabilities inside the integral, since each event is independent from another:
%
\begin{equation}
P(\ell | \{d_i\}) = \frac{P(\ell)}{P(\{d_i\})}
\prod_{i=1}^{N}
\int \dd \btheta_i \, P(\btheta_i) \, P( d_i | \ell_i, \btheta_i ).
\end{equation}
%
% 5. Final formula
We can now identify the integral as the marginalized likelihood for each individual event
%
\begin{equation}
P(\ell | \{d_i\}) = \frac{P(\ell)}{P(\{d_i\})}
\prod_{i=1}^{N} P( d_i | \ell_i ),
\end{equation}
%
which we can rewrite as
%
\begin{align}
P(\ell | \{d_i\}) &= \frac{P(\ell)}{P(\{d_i\})}
\prod_{i=1}^{N} \frac{P(d_i)}{P(\ell_i)} P(\ell_i | d_i)
\nonumber \\
&= P(\ell)
\prod_{i=1}^{N} \frac{P(\ell_i | d_i)}{P(\ell_i)}.
\label{eq:cumulative_dist_ell}
\end{align}
%
by using Bayes' theorem in the first line and cancelling the evidences in the
second line. This is our final result.

%
\hs{Abhirup, maybe move this to the subsection on priors?}
In our parameter estimation runs that we had to adjust our prior on $\ell$ depending on which event and
on which theory we examined.
%
The reasons are twofold.
%
% Describe problem 1
%
First, we found that depending on the source parameters $\btheta$,
large values of $\ell$ could result in unphysical waveforms in the frequency
band we considered. More specifically, these waveforms have a ringdown which is
considerable longer than the inspiral-merger part in the detector frequency band.
%
The fact that our sampled over these waveforms is perhaps not surprising,
because, after all, we are by construction adding corrections to the GR QNM
which \emph{increase} the damping timescale.
%
In practice, we found that these edge-cases were problematic to deal with
\texttt{LALInferenceMCMC}.
%
We overcome this problem, we reduced the prior upper-value of our prior on $\ell$.
%
This choice does not pose a problem to our parameter estimations, because these
waveforms differ grossly from the data and thus have negligible likelihood.
%
% Describe problem 2
%
However, we cannot reduce the prior on $\ell$ too much. If we do so,
to the marginalized posterior distribution on $\ell$ would rail against
the prior or, in a more extreme case, even be a uninformative, flat posterior.
%
% Summary
%
Altogether, this means that the priors $P(\ell)$ are not shared between events and
they must be taken into account when calculation the cumulative posterior function~\eqref{eq:cumulative_dist_ell}.

Finally, we use one of the approaches of Ref.~\cite{Perkins:2021mhb} to
compute the product in Eq.~\eqref{eq:cumulative_dist_ell}.
%
It method relies on first obtaining a kernel density estimator (KDE) for
the posterior distribution on $\ell$ for each individual event.
%
(See also Refs.~\cite{DelPozzo:2011pg,Cardenas-Avendano:2019zxd,Carullo:2021dui}.)
%
Next, we multiply these posteriors according to Eq.~\eqref{eq:cumulative_dist_ell}.
%
This approach based on the KDE can have difficulties in dealing with hard cut-offs in the
distribution, such as the one we impose at $\ell = 0$. We address this issue as
done in Ref.~\cite{Perkins:2021mhb}, by first doubling our number of samples as
$\{ s_i \} \cup \{ - s_i \}$, i.e., mirroring the samples across $\ell = 0$.
%
We then renormalize the associated KDE numerically in the range $\ell = [0, \infty]$.

### 2022-03-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added qEFT coefs.

@@
 Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
-\hline
+\hlin
 EdGB        & 4 & 0.0107    & 0.0044    & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
 dCS         & 4 & 3.1964    & 6.3619    & 41.199    & 794.66   &  \cite{Wagle:2021tam}  \\
-cubic EFT   & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} \\
-quartic EFT & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl}  \\
+cubic EFT   & 4 & $-$0.5813 & 2.6469    & $-$3.8620 & 265.12   & \cite{Cano:2021myl} \\
+quartic EFT & 6 & $-$0.2114 & $-$0.6070 & $-$1.5263 & 171.35   & \cite{Cano:2021myl}  \\
 \hline

### 2022-03-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
finished changes to the PE section

--- 2022-03-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
@@
 dCS         & 4 & 3.1964    & 6.3619    & 41.199    & 794.66   &  \cite{Wagle:2021tam}  \\
-cubic EFT   & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} \\
-quartic EFT & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl}  \\
+cubic EFT   & 4 & $-$0.5813 & 2.6469    & $-$3.8620 & 265.12   & \cite{Cano:2021myl} \\
+quartic EFT & 6 & $-$0.2114 & $-$0.6070 & $-$1.5263 & 171.35   & \cite{Cano:2021myl}  \\
 \hline

### 2022-03-23 papers/paper_alt_theor_bounds/sec_pe.tex

@@
 P(\bm{\lambda} \vert d, \mathcal{H}) =
-\frac{P(\bm{\lambda} \vert \mathcal{H}) \, \mathcal{L}(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
+\frac{p(\bm{\lambda} \vert \mathcal{H}) \, \mathcal{L}(d \vert \bm{\lambda},\mathcal{H})}{E(d \vert \mathcal{H})}\,,
 \label{eq:bayes}
@@
 where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
-$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
+$p(\bm{\lambda} \vert \mathcal{H})$ the prior,
 $\mathcal{L}(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
-$P(d \vert \mathcal{H})$ the evidence.
+$E(d \vert \mathcal{H})$ the evidence.
 %
-The set of parameters, $\bm{\lambda}$ is the union between the GR waveform
-model parameters~$\bm{\theta}$, detailed in Sec.~\ref{sec:review_pSEOB}, and
-the non-GR parameter of $\ell$, i.e.,
+The set of parameters, $\bm{\lambda}$ is a union of the GR waveform
+model parameters~$\bm{\theta}$ (c.f.  Sec.~\ref{sec:review_pSEOB}), and
+$\ell$,  the only non-GR parameter in this problem which, we recall, set 
+the characteristic length-scale in which deviations from
+GR become relevant in each of the theories described in
+Sec.~\ref{sec:review_theories}. Hence, 
 %
@@
 \end{equation}
-%
-which, we recall, set the characteristic lengthscale in which deviations from
-GR become relevant in each of the theories described in
-Sec.~\ref{sec:review_theories}.
 
@@
 
-Assuming Gaussian and stationary noise, we can write the (log) likelihood function as,
+Assuming stationary Gaussian noise, we can write the (log) likelihood function as,
 %
 \begin{equation}
-\ln P(d \vert \bm{\lambda},\mathcal{H}) \propto
+\ln \mathcal{L}(d \vert \bm{\lambda},\mathcal{H}) \propto
 - \tfrac{1}{2}
@@
 %
-Assuming a specific prior distribution for our parameters, we stochastically
+Assuming a specific prior distribution for our parameters (discussed further in the subsequent section), we stochastically
 sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
 \texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx},
-which is part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
+a package part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
 %
 We subsequently marginalize over the remaining parameters to obtain the
-posterior probability distribution function~(PDF) on $\ell$, our main quantity of interest.
+posterior probability distribution function~(PDF) on $\ell$,  $P_j(\ell \vert d_j,\mathcal{H})$, our main parameter of interest.
 %
 % An example of this is shown in Fig. XX.
+
+For $N$ independent GW observations $\{d_j\}, j=1,...N$, each characterised by a posterior probability distribution $P_j(\ell \vert d_j,\mathcal{H})$, the joint posterior can be written as:
+%
+\begin{equation}
+P(\ell | \{d_j\}) = p(\ell) \prod_{j=1}^{N} \frac{P_j(\ell | d_j)}{p_j(\ell)}.
+\label{eq:cumulative_dist_ell}
+\end{equation}
+%
+where $p_j(\ell)$ are the priors used for each observation, and $p(\ell)$ is an overall prior.  Since we assume a uniform prior on $\ell$, joint posterior is identically equal to the joint likelihood.
 
@@
 
+\iffalse
 \subsection{Stacking posteriors}
@@
 We then renormalize the associated KDE numerically in the range $\ell = [0, \infty]$.
+\fi

### 2022-03-28 papers/paper_alt_theor_bounds/jnb/postprocessing_tools.py
hs: joint likelihood function included

@@ -196,3 +196,46 @@ def do_posterior_combine(x1, y1, prior_limits1,
         ax.legend(loc='best', fontsize=8)
     
     return x12_vals, yx12_combined(np.array(x1)) / yx12_normalisation
+
+def joint_likelihood_and_posterior(df1, df2, pr1max, pr2max):
+
+    # priors ranges
+    pr1range = [0, pr1max]
+    pr2range = [0, pr2max]
+
+    Nbins = 50
+    
+    lbins1 = np.linspace(pr1range[0], pr1range[1], Nbins)
+    lintp1 = (lbins1[:-1] + lbins1[1:])/2.
+
+    lbins2 = np.linspace(pr2range[0], pr2range[1], Nbins)
+    lintp2 = (lbins2[:-1] + lbins2[1:])/2.
+
+    dl1 = np.mean(np.diff(lbins1))
+    dl2 = np.mean(np.diff(lbins2))
+    
+    # prior histograms
+    prl1, lbins1 = np.histogram(np.random.uniform(pr1range[0], pr1range[1], 100000), bins=lbins1, density=True)
+    prl2, lbins2 = np.histogram(np.random.uniform(pr2range[0], pr2range[1], 100000), bins=lbins1, density=True)
+    
+    # posterior histograms
+    Pl1, lbins1 = np.histogram(df1['alphangr'], bins=lbins1, density=True)
+    Pl2, lbins2 = np.histogram(df2['alphangr'], bins=lbins2, density=True)
+    
+    # likelihoods
+    likel1 = Pl1/prl1
+    likel2 = Pl2/prl2
+
+    likel1 /= np.sum(likel1) * dl1
+    likel2 /= np.sum(likel2) * dl2
+    
+    # HS: Abhirup, if dl1 \neq dl2, which one should we use?
+    # joint likelihood
+    likel = likel1*likel2
+    likel /= np.sum(likel) * dl1 # chose dl1 because dl1=dl2
+
+    # joint posterior
+    Pl = likel * prl1 # chose one of the priors because they were identical
+    Pl /= np.sum(Pl) * dl1 # chose dl1 because dl1=dl2
+    
+    return lintp1, lintp2, likel, Pl

### 2022-03-28 papers/paper_alt_theor_bounds/jnb/tools.py

@@ -47,3 +47,46 @@ def combined_posterior(x1, x2):
     print(yx_combined.integral(0, max(x1_post)))
     
     return np.array(x_vals), np.array(y_vals) / yx_combined.integral(0, max(x1_post))
+
+def joint_likelihood_and_posterior(df1, df2, pr1max, pr2max):
+
+    # priors ranges
+    pr1range = [0, pr1max]
+    pr2range = [0, pr2max]
+
+    Nbins = 50
+    
+    lbins1 = np.linspace(pr1range[0], pr1range[1], Nbins)
+    lintp1 = (lbins1[:-1] + lbins1[1:])/2.
+
+    lbins2 = np.linspace(pr2range[0], pr2range[1], Nbins)
+    lintp2 = (lbins2[:-1] + lbins2[1:])/2.
+
+    dl1 = np.mean(np.diff(lbins1))
+    dl2 = np.mean(np.diff(lbins2))
+    
+    # prior histograms
+    prl1, lbins1 = np.histogram(np.random.uniform(pr1range[0], pr1range[1], 100000), bins=lbins1, density=True)
+    prl2, lbins2 = np.histogram(np.random.uniform(pr2range[0], pr2range[1], 100000), bins=lbins1, density=True)
+    
+    # posterior histograms
+    Pl1, lbins1 = np.histogram(df1['alphangr'], bins=lbins1, density=True)
+    Pl2, lbins2 = np.histogram(df2['alphangr'], bins=lbins2, density=True)
+    
+    # likelihoods
+    likel1 = Pl1/prl1
+    likel2 = Pl2/prl2
+
+    likel1 /= np.sum(likel1) * dl1
+    likel2 /= np.sum(likel2) * dl2
+    
+    # HS: Abhirup, if dl1 \neq dl2, which one should we use?
+    # joint likelihood
+    likel = likel1*likel2
+    likel /= np.sum(likel) * dl1 # chose dl1 because dl1=dl2
+
+    # joint posterior
+    Pl = likel * prl1 # chose one of the priors because they were identical
+    Pl /= np.sum(Pl) * dl1 # chose dl1 because dl1=dl2
+    
+    return lintp1, lintp2, likel, Pl

### 2022-03-28 papers/paper_alt_theor_bounds/jnb/postprocessing_tools.py
added convention of choosing the widest prior range for combined posteriors

@@ -231,11 +231,18 @@ def joint_likelihood_and_posterior(df1, df2, pr1max, pr2max):
     
     # HS: Abhirup, if dl1 \neq dl2, which one should we use?
     # joint likelihood
+    if (pr1max > pr2max) or (pr2max == pr2max):
+        dl = dl1
+        pr = prl1
+    else:        
+        dl = dl2
+        pr = prl2
+        
     likel = likel1*likel2
-    likel /= np.sum(likel) * dl1 # chose dl1 because dl1=dl2
+    likel /= np.sum(likel) * dl # chose dl1 because dl1=dl2
 
     # joint posterior
-    Pl = likel * prl1 # chose one of the priors because they were identical
-    Pl /= np.sum(Pl) * dl1 # chose dl1 because dl1=dl2
+    Pl = likel * pr # chose one of the priors because they were identical
+    Pl /= np.sum(Pl) * dl # chose dl1 because dl1=dl2
     
     return lintp1, lintp2, likel, Pl

### 2022-03-28 papers/paper_alt_theor_bounds/jnb/postprocessing_tools.py
hs: notebooks with final figs

@@ -43,7 +43,7 @@ def get_threshold(smp_mass, thr_coef=1/2.):
     
     smp_mass_geo = np.median(smp_mass) * Msun_to_km
     
-    return thr_coef * m_in_km
+    return thr_coef * smp_mass_geo
 
 def get_kde_l(smp_l, l_min = 0, l_max = 60, vis=False):
     """
@@ -199,6 +199,12 @@ def do_posterior_combine(x1, y1, prior_limits1,
 
 def joint_likelihood_and_posterior(df1, df2, pr1max, pr2max):
 
+    import scipy.ndimage.filters as filter
+    from scipy.interpolate import InterpolatedUnivariateSpline as ius
+    
+    def gf(P):
+        return filter.gaussian_filter(P, sigma=2.0)
+    
     # priors ranges
     pr1range = [0, pr1max]
     pr2range = [0, pr2max]
@@ -229,14 +235,15 @@ def joint_likelihood_and_posterior(df1, df2, pr1max, pr2max):
     likel1 /= np.sum(likel1) * dl1
     likel2 /= np.sum(likel2) * dl2
     
-    # HS: Abhirup, if dl1 \neq dl2, which one should we use?
     # joint likelihood
     if (pr1max > pr2max) or (pr2max == pr2max):
         dl = dl1
         pr = prl1
+        lintp = lintp1
     else:        
         dl = dl2
         pr = prl2
+        lintp = lintp2
         
     likel = likel1*likel2
     likel /= np.sum(likel) * dl # chose dl1 because dl1=dl2
@@ -245,4 +252,22 @@ def joint_likelihood_and_posterior(df1, df2, pr1max, pr2max):
     Pl = likel * pr # chose one of the priors because they were identical
     Pl /= np.sum(Pl) * dl # chose dl1 because dl1=dl2
     
-    return lintp1, lintp2, likel, Pl
+    # return lintp1, lintp2, likel, Pl
+
+    l_vals = np.arange(0, pr.max() + 1)
+    jlike = gf(likel)
+    jpost = gf(Pl)
+    
+    jlike_interp = ius(lintp, jlike, k=1)
+    jpost_interp = ius(lintp, jpost, k=1)
+    
+#     plt.plot(lintp, gf(likel))
+#     plt.plot(l_vals, jlike_interp(l_vals))
+    
+#     plt.plot(lintp, gf(Pl))
+#     plt.plot(l_vals, jpost_interp(l_vals))
[…]

### 2022-03-28 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: commit for merge
hs: summary included

@@
 EdGB        & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
-dCS         & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
-cubic EFT   & \dots & \dots \\
-quartic EFT & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
+dCS         & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 38.7$~km \\
+cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
+quartic EFT & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km \\
 \hline \hline
@@
 for both GR (solid line) and cubic EFT of GR (dashed line) with the leading-order
-$n=0$ modifications to the fundamental QNM.
+$n=0$ modifications to the fundamental QNM, for $\ell_{\rm cEFT} = 65$~km.
 %
@@
 We conclude that we cannot place any constraint on $\ell_{\rm GB}$ with any of the GW events
-studied here.~\hs{TODO: update when completed.}
+studied here.
 }
@@
 %
-can also be placed, when $j=0$.
+can also be placed, when $N_{\rm max}=0$.
 
@@
 %
-when $j=0$.
+when $N_{\rm max}=0$.
 %
@@
 This means that we cannot use these posterior to infer any meaningful bound on dCS gravity
-and that is why we quoted only the $j=0$ bound above.
+and that is why we quoted only the $N_{\rm max}=0$ bound above.
 
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 34.5~\textrm{km}
+\ell_{\rm CS} \leqslant 38.7~\textrm{km}
 \quad \textrm{(90\% credibility)},
@@
 \hline
-      & GW150914 & Yes & Yes & $\ell_{\rm CS} \leqslant 46.5$~km \\
-0     & GW200129 & Yes & Yes & $\ell_{\rm CS} \leqslant 43.9$~km \\
-      & Combined & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
+%       & GW150914 & Yes & Yes & $\ell_{\rm CS} \leqslant 46.5$~km \\
+% 0     & GW200129 & Yes & Yes & $\ell_{\rm CS} \leqslant 43.9$~km \\
+%       & Combined & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
+      & GW150914 & Yes & Yes & $\ell_{\rm CS} \leqslant 41.9$~km \\
+0     & GW200129 & Yes & Yes & $\ell_{\rm CS} \leqslant 35.8$~km \\
+      & Combined &     &     & \cellcolor{black!10}$\ell_{\rm CS} \leqslant 38.7$~km \\
 \hline
@@
 1     & GW200129 & Yes & No  & --                                 \\
-      & Combined & Yes & No  & --                                 \\
+      & Combined &     &     & --                                 \\
 \hline
@@
 they do not obey the condition~\eqref{eq:parspec_bound} for $j = 1$. This means
-that our results for $j=0$ are the only ones we can confidently quote.
+that our results for $N_{\rm max}=0$ are the only ones we can confidently quote.
 %
 The combined bound, which is also quoted in Table~\ref{tab:ref_theories_qnms},
-is $\ell_{\rm CS} \leqslant 34.5$~km.
+is $\ell_{\rm CS} \leqslant 38.7$~km.
 }
@@
 \hline
-  & GW150914 &  &     &    \\
-0 & GW200129 &  &     &    \\
-  & Combined &  &     &    \\
-\hline
-  & GW150914 &  &     &    \\
-1 & GW200129 &  &     &    \\
-  & Combined &  &     &    \\
+  & GW150914  & Yes & Yes &  $38.2$~km \\
+0 & GW200129  & Yes & Yes &  $42.5$~km \\
+  & Combined  &     &     &  \cellcolor{black!10}$38.2$~km \\
+\hline
+  & GW150914  & Yes  & No  &  -- \\
+1 & GW200129  & Yes  & No  &  -- \\
+  & Combined  &      &     &  -- \\
 \hline
@@
 combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
-%
-\hs{TODO: update when completed.}
 }
@@
 \hline
-  & GW150914 &  &     &    \\
-0 & GW200129 &  &     &    \\
-  & Combined &  &     &    \\
+  & GW150914 & Yes & Yes  & $51.7$~km \\
+0 & GW200129 & Yes & Yes  & $54.8$~km \\
+  & Combined &     &      & \cellcolor{black!10}$51.3$~km \\
 \hline
@@
 %
-\hs{TODO: update when completed.}
 }

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: make tables uniform and cosmetics to the contour plot

@@
 \hline
-  & GW150914  & Yes & Yes &  $38.2$~km \\
-0 & GW200129  & Yes & Yes &  $42.5$~km \\
-  & Combined  &     &     &  \cellcolor{black!10}$38.2$~km \\
+  & GW150914  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 38.2$~km \\
+0 & GW200129  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 42.5$~km \\
+  & Combined  &     &     &  \cellcolor{black!10}$\ell_{\rm cEFT} \leqslant 38.2$~km \\
 \hline
@@
 \hline
-  & GW150914 & Yes & Yes  & $51.7$~km \\
-0 & GW200129 & Yes & Yes  & $54.8$~km \\
-  & Combined &     &      & \cellcolor{black!10}$51.3$~km \\
+  & GW150914 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 51.7$~km \\
+0 & GW200129 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 54.8$~km \\
+  & Combined &     &      & \cellcolor{black!10}$\ell_{\rm qEFT} \leqslant 51.3$~km \\
 \hline
@@
 combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+%
+\hs{Need to debug $N_{\rm max} = 1$ runs.}
 %

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: news refs started editing edgb section

@@
 
-\subsection{The parametrized ringdown spin expansion coefficients formalism}
+\subsection{The parametrized ringdown spin expansion coefficients framework}
 \label{sec:review_parspec}
@@
 $\chi_f^0$, to the $k=(2,2,0)$ mode only, then we would just have two
-additional parameters, $(\delta \omega_0^{(0)}, \delta \tau_0^{(0)})$.
+additional parameters, $\{\delta \omega_0^{(0)}, \delta \tau_0^{(0)}\}$.
 %
@@
 translation between the metric perturbations $h_{\mu\nu}$ in the
-Regger-Wheeler-Zerilli gauge and connect it with the transverse-traceless gauge
+Regger-Wheeler-Zerilli gauge~\cite{Regge:1957td,Zerilli:1970se} and connect it with the transverse-traceless gauge
 used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
@@
 
-\hs{Convention: us 90\% credibility for the final bounds.}
+% ----------------------------------------------------------
+% \hs{Convention: us 90\% credibility for the final bounds.}
+% ----------------------------------------------------------
 
@@
 \label{sec:results_edgb}
+
+We start by presenting our result for EdGB gravity.
+%
+In Fig.~\ref{fig:edgb_exec_sum} we show the margelized posteriors of the coupling constant $\ell_{\rm GB}$,
+for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
+QNM.
 
@@
 in spin QNM correction.}
-\label{fig:sGB_exec_sum}
+\label{fig:edgb_exec_sum}
 \end{figure}
@@
 }
-\label{fig:dcs_cdf}
+\label{fig:edgb_cdf}
 \end{figure}

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more writing in the edgb section

@@
 
-We start by presenting our result for EdGB gravity.
+We start by presenting our results for EdGB gravity.
 %
@@
 for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
-QNM.
+QNM. The bottom panel panel shows the joint posterior combining both events.
+%
+We see for both events events the $N_{\rm max} = 0$ posteriors are characterized by a peak away from zero.
+%
+This does not mean that we are observing a deviantion from GR. We recall that the deviations from GR in the ParSpec framework
+are controlled by $\gamma$, which here reads,
+%
+\begin{equation}
+    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{\rm s}}\right)^4\,.
+\end{equation}
+%
+As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior with maximum support near zero, indicating consistency
+of our data with GR.
+%
+We also observe that the inclusion of the spin corrections (i.e., $N_{\rm max} = 1$) displaces the posteriors towards
+smaller values of $\ell_{\rm GB}$.
+
+As we stressed in Sec.~\ref{sec:remarks}, before we can draw any conclusions on
+the allowed values for $\ell_{\rm GB}$ from our parameter estimation study, we
+must first check whether the ``EFT''~\eqref{eq:eft_bound} and
+``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
+%
+We do the former in Fig.~\ref{fig:edgb_cdf}.
 
@@
 We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
-1/2$ for both events, with and without including the $j = 1$ dCS corrections to
+1/2$ for both events, with and without including the $n = 1$ dCS corrections to
 the dominant QNM.

### 2022-03-29 papers/paper_alt_theor_bounds/sec_pe.tex
hs: making notation uniform in pe section; upd refs.

@@
 
-For $N$ independent GW observations $\{d_j\}, j=1,...N$, each characterised by a posterior probability distribution $P_j(\ell \vert d_j,\mathcal{H})$, the joint posterior can be written as:
+For $N$ independent GW observations $\{d_j\}$, $j=1,...,N$, each characterised by a posterior probability distribution $P_j(\ell \vert d_j,\mathcal{H})$, the joint posterior can be written as:
 %
 \begin{equation}
-P(\ell | \{d_j\}) = p(\ell) \prod_{j=1}^{N} \frac{P_j(\ell | d_j)}{p_j(\ell)}.
+P(\ell | \{d_j\}) = p(\ell) \prod_{j=1}^{N} \frac{P_j(\ell | d_j)}{p_j(\ell)}\,.
 \label{eq:cumulative_dist_ell}
@@
 %
-where $p_j(\ell)$ are the priors used for each observation, and $p(\ell)$ is an overall prior.  Since we assume a uniform prior on $\ell$, joint posterior is identically equal to the joint likelihood.
+where $p_j(\ell)$ are the priors used for each observation, and $p(\ell)$ is an overall prior.
+%
+Since we assume a uniform prior on $\ell$, the joint posterior is identically
+equal to the joint likelihood.
+%
+In some cases, we found it necessary to work with different prior ranges across
+different events, within the context of a given theory.
+%
+In this situation, when combining the posteriors we use chose as our overall
+prior the widest one among the individual events.
 
@@
 
-The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \text{sin} \iota$.
+The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \sin\iota$.
 For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
@@
 
-Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$,
-as already mentioned in the previous section, we hold $\{\delta \omega_k^{(j)}\},$
-and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$
+Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(n)}\delta \tau_k^{(n)}\}$,
+as already mentioned in the previous section, we hold $\{\delta \omega_k^{(n)}\}$
+and $\{\delta \tau_k^{(n)}\}$ fixed to theory-specific predictions, and allow only $\ell$
 to freely vary.
@@
 \subsection{Event selection}
+
+\begin{figure}[t]
+\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
+\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
+detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
+but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
+dCS gravity and $j=0$). The contours represent 90\% credible regions.
+%
+We see that the introduction of the non-GR parameters does not bias the
+inference on the source parameters.
+}
+\label{fig:corner_plot}
+\end{figure}
 
@@
 
-\begin{figure}[t]
-\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
-\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
-but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
-dCS gravity and $j=0$). The contours represent 90\% credible regions.
-%
-We see that the introduction of the non-GR parameters does not bias the
-inference on the source parameters.
-}
-\label{fig:corner_plot}
-\end{figure}
-
 \subsection{General remarks on the interpretation of our results}
-\label{sec:remaks}
+\label{sec:remarks}
 
@@
 where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
-value of one of the masses involved in the problem.
+value of one of the mass scales involved in the problem.
 %
@@
 
+Second, as already emphasized in Ref.~\cite{Maselli:2019mjd}, the ParSpec
+formalism is by construction perturbative. This means that the non-GR
+deformation parameters are small, that is,
+%
+\begin{equation}
+\gamma \, \delta \omega^{(n)} \ll 1 \,,
+\,\, \textrm{and} \,\,
+\gamma \, \delta \tau^{(n)} \ll 1 \,, \quad \textrm{(ParSpec bound)},
+\label{eq:parspec_bound}
+\end{equation}
+%
+for all orders $n$ in the expansion in dimensionless spin $\chi$ and where $\gamma$
+is given by Eq.~\eqref{eq:def_gamma}.
+%
+We will also construct posterior distributions for these parameters and check if
+most of their support is concentrated to a domain with values much smaller than
+unity.
+
 Another question we must consider is the following: what is the mass $\mathfrak{m}$ that we should use
@@
 the GW signal alone, it was natural to chose the secondary's mass $m_2$ as the most
-conservative choice, for it is by definition the smallest mass and hence
-places the lowest threshold for the validity of either theory as an EFT.
-%
+conservative choice, since it is (by definition) the smallest mass and hence
+places the lowest cut-off scale $\Lambda_{\rm EFT}$ for the validity of either of these theories as an EFT.
+
 In our problem, the answer is not as clear. On the one hand, since we are
 interested in the ringdown part of the signal, it is natural to use the
-final mass $M_f$ to compute the cut-off $\Lambda_{\rm EFT}$.
+final mass $M_f$ to compute $\Lambda_{\rm EFT}$.
 %
@@
 yield to different interpretations of the results of our parameter estimations.
-
-There is a second criteria we must also consider.
-%
-As already emphasized in Ref.~\cite{Maselli:2019mjd}, the ParSpec
-formalism is by construction perturbative. This means that the non-GR
-deformation parameters are small, that is,
-%
-\begin{equation}
-\gamma \, \delta \omega^{(j)} \ll 1 \,,
-\quad \textrm{and} \quad
-\gamma \, \delta \tau^{(j)} \ll 1 \, \quad \textrm{(ParSpec bound)},
-\label{eq:parspec_bound}
-\end{equation}
-%
-for all $j$ in the expansion in dimensionless spin $\chi$.
-%
-We will also construct posterior distributions for these parameters and check if
-most of their support is concentrated to a domain with values much smaller than
-unity.
 

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more editing

@@
 As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior with maximum support near zero, indicating consistency
-of our data with GR.
+between data and GR.
 %
@@
 %
-We do the former in Fig.~\ref{fig:edgb_cdf}.
+We verify the former in Fig.~\ref{fig:edgb_cdf}. In top (bottom) panel we shown the cumulative density function
+of the $\ell_{\rm GB}$ posteriors, obtained evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
+with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or the remnant's mass ($\mathfrak{m} = M_f$, solid lines), with varying $\epsilon$.
 

### 2022-03-29 papers/paper_alt_theor_bounds/sec_pe.tex
hs: more editing

@@
 In practice, this can be quantified through the cumulative distribution function
-(CDF) associated to the marginalized posterior distribution $P(\ell)$,
+(CDF) associated with the marginalized posterior distribution $P(\ell)$,
 %
@@
 %
-For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
+For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that
+up to $\ell_{\rm max} = \Lambda_{\rm EFT}$ we have,
 %
@@
 %
-and likewise for other percentiles.
+and likewise for other credibility percentiles.
 

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: edgb section first version done

@@
 %
-We verify the former in Fig.~\ref{fig:edgb_cdf}. In top (bottom) panel we shown the cumulative density function
-of the $\ell_{\rm GB}$ posteriors, obtained evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
-with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or the remnant's mass ($\mathfrak{m} = M_f$, solid lines), with varying $\epsilon$.
+We verify the former in Fig.~\ref{fig:edgb_cdf}. In top (bottom) panel we shown
+the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
+evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
+with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
+the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$.
+%
+For GW150914, we see that for the $N_{\rm max} = 0$ that the CDF never goes past $0.2$, regardless of the mass scale $\mathfrak{m}$,
+even at $\varepsilon = 1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is never met
+at a significant credilibity and thus that we cannot place a bound on $\ell_{\rm GB}$.
+%
+The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not change when we include spin corrections to the EdGB QNM.
+%
+Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our present model}.
 
@@
 through the 0.68 or 0.90 lines even at $\varepsilon = 1$. This means that no bound on $\ell_{\rm GB}$
-can be placed with the event we analyzed.
+can be placed with the events we analyzed.
 }

### 2022-03-29 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: correcting typos

@@
 %
-In Fig.~\ref{fig:edgb_exec_sum} we show the margelized posteriors of the coupling constant $\ell_{\rm GB}$,
+In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized posteriors of the coupling constant $\ell_{\rm GB}$,
 for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
@@
 %
-This does not mean that we are observing a deviantion from GR. We recall that the deviations from GR in the ParSpec framework
-are controlled by $\gamma$, which here reads,
+This does not mean that we are observing a deviation from GR. We recall that
+the deviations from GR in the ParSpec framework are controlled by $\gamma$,
+which here reads,
 %
@@
 %
-We verify the former in Fig.~\ref{fig:edgb_cdf}. In top (bottom) panel we shown
+We check the validity of the EFT bound in Fig.~\ref{fig:edgb_cdf}. In the top (bottom) panel we show
 the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
@@
 %
-For GW150914, we see that for the $N_{\rm max} = 0$ that the CDF never goes past $0.2$, regardless of the mass scale $\mathfrak{m}$,
-even at $\varepsilon = 1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is never met
-at a significant credilibity and thus that we cannot place a bound on $\ell_{\rm GB}$.
-%
-The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not change when we include spin corrections to the EdGB QNM.
-%
-Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our present model}.
+For GW150914, we see that for the $N_{\rm max} = 0$ that the CDF never goes
+past $0.2$, regardless of the mass scale $\mathfrak{m}$, even at $\varepsilon =
+1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
+never met at a significant credibility and thus that we cannot place a bound on
+$\ell_{\rm GB}$.
+%
+The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not
+change when we include spin corrections to the EdGB QNM.
+%
+Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our
+present model}.
+%
+These conclusions are summarized in Table~\ref{tab:summary_edgb}.
 
@@
 %
-We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov,
-Serguei~Ossokine, Scott~E.~Perkins, and Helvi~Witek for discussions.
-%
-We also thank the computational resources provided by the AEI, specifically the
-{\sc Hypatia} cluster and Steffen Grunewald for assistance.
+We thank Emanuele Berti, Andrea Maselli, Caio F. B. Macedo, Deyan Mihaylov,
+Serguei Ossokine, Scott E. Perkins, and Helvi Witek for discussions.
+%
+We are grateful for the computational resources provided by the Max Planck
+Institute for Gravitational Physics in Potsdam, specifically the
+high-performace computing cluster Hypatia and to Steffen Grunewald for
+assistance.
 %

### 2022-03-30 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: text on edgb and included missing cdf figs for eft

@@
 
-\subsection{Einstein-dilaton-Gauss-Bonnet}
+\subsection{Einstein-dilaton-Gauss-Bonnet gravity}
 \label{sec:results_edgb}
 
-We start by presenting our results for EdGB gravity.
-%
-In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized posteriors of the coupling constant $\ell_{\rm GB}$,
-for GW150914 (top panel) and GW200129 (middle panel), with and without the spin correction to the $(2,2,0)$
-QNM. The bottom panel panel shows the joint posterior combining both events.
-%
-We see for both events events the $N_{\rm max} = 0$ posteriors are characterized by a peak away from zero.
-%
-This does not mean that we are observing a deviation from GR. We recall that
-the deviations from GR in the ParSpec framework are controlled by $\gamma$,
-which here reads,
+We start by showing our results for EdGB gravity.
+%
+In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized posteriors of the
+coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
+(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
+%
+The bottom panel panel shows the joint posterior combining both events.
+%
+We see that for both events events, the $N_{\rm max} = 0$ posteriors are
+characterized by a peak away from zero.
+%
+This does not mean that we are inferring a deviation from GR from data.
+%
+Recall that the deviations from GR in the ParSpec framework are controlled
+by $\gamma$, which here reads,
 %
@@
 %
-As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior with maximum support near zero, indicating consistency
-between data and GR.
-%
-We also observe that the inclusion of the spin corrections (i.e., $N_{\rm max} = 1$) displaces the posteriors towards
-smaller values of $\ell_{\rm GB}$.
-
-As we stressed in Sec.~\ref{sec:remarks}, before we can draw any conclusions on
-the allowed values for $\ell_{\rm GB}$ from our parameter estimation study, we
+As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior
+distribution with largest support at zero, indicating consistency between data
+and GR.
+%
+We also observe that the inclusion of the spin corrections (i.e., curves with $N_{\rm max} = 1$)
+displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$.
+
+As we emphasized in Sec.~\ref{sec:remarks}, before drawing any conclusions on
+the allowed values for $\ell_{\rm GB}$ from our parameter estimations, we
 must first check whether the ``EFT''~\eqref{eq:eft_bound} and
@@
 %
-For GW150914, we see that for the $N_{\rm max} = 0$ that the CDF never goes
-past $0.2$, regardless of the mass scale $\mathfrak{m}$, even at $\varepsilon =
+For GW150914, we see that for the $N_{\rm max} = 0$ curves, that the CDF never goes
+past $0.2$, regardless of the mass scale $\mathfrak{m}$ used and even at $\varepsilon =
 1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
@@
 The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not
-change when we include spin corrections to the EdGB QNM.
+change for either event when we include spin corrections to the EdGB QNM.
 %
@@
 These conclusions are summarized in Table~\ref{tab:summary_edgb}.
+
+Let us contrast our results with those of Ref.~\cite{Lyu:2022gdr} which placed
+the bound
+%
+$\ell_{\rm GB} \leqslant 1.33$~km
+%
+using the inspiral portion of the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt} or
+of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound $\ell_{\rm GB} \leqslant 1.7$~km, by considering
+a selection of black hole binaries from the GWTC-1 and GWTC-1 catalogs~\cite{}\footnote{These bounds
+are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and take into consideration only the leading-order
+scalar field contribution arising from the dilatonic coupling.}
+%
+
+% which relies on post-Newtonian calculations of the GW phase shift in this theory~\cite{Yagi:2011xp,Shiralilou:2020gah,Shiralilou:2021mfl}
+% combined with parametrized post-Einsteinian (ppE) framework~\cite{Yunes:2009ke,Chatziioannou:2012rf,Tahura:2019dgr}.
+
+Based on the later, but now here confirmed, within the assumptions of our waveform model,
+in the case of comparable mass binaries.
 
@@
 
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold.pdf}
+\caption{
+}
+\label{fig:cEFT_cdf}
+\end{figure}
+
 \begin{table}[h]
@@
 \label{fig:qEFT_exec_sum}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
+\caption{
+}
+\label{fig:qEFT_cdf}
 \end{figure}

### 2022-03-30 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: updated edgb caption to match new plot style

@@
 with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
-the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$.
+the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$ between 0 and 1.
 %
@@
 The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not
-change for either event when we include spin corrections to the EdGB QNM.
+change for either event when we add spin corrections to the EdGB QNM.
 %
@@
 scalar field contribution arising from the dilatonic coupling.}
-%
 
@@
 %
-In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
-in spin QNM correction.}
+In all panels, different line colors correspond to the inclusion ($N_{\rm max} = 1$) or not ($N_{\rm max} = 0$)
+of the linear-in-spin QNM correction.}
 \label{fig:edgb_exec_sum}
@@
 cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
-$\varepsilon$ for both (blue curves) $\gm = m_2$, the secondary's source
-mass, and (orange curves) $\gm = M_{f}$, the remnant's source mass, without
-(solid curve) and with (dashed curves) linear in spin QNM corrections. The
+$\varepsilon$ for both (dashed curves) $\gm = m_2$, the secondary's source
+mass, and (solid curves) $\gm = M_{f}$, the remnant's source mass, without
+(black curves) and with (purple curves) linear in spin QNM corrections. The
 horizontal lines lay at 0.68 and 0.90. We see that in no situation the curves pass
@@
 \hline
-$N_{\rm max}$ & Event &  EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
-              &       &  bound? & bound?  &                            \\
+$N_{\rm max}$ & Event &  EFT    & ParSpec & Constraint      \\
+              &       &  bound? & bound?  & ($\gm = M_{f}$) \\
 \hline
@@
 %
-We conclude that we cannot place any constraint on $\ell_{\rm GB}$ with any of the GW events
-studied here.
+We find that we cannot place any constraint on $\ell_{\rm GB}$ with our waveform model from either GW event.
 }

### 2022-03-30 papers/paper_alt_theor_bounds/sec_pe.tex
hs: change to cdf description

--- 2022-03-29 papers/paper_alt_theor_bounds/sec_pe.tex
@@
 In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
-but here we consider $\varepsilon \in [0, 1]$.
+but here we consider $\varepsilon \in [0, 1]$ for generality.
 %
@@
 In practice, this can be quantified through the cumulative distribution function
-(CDF) associated to the marginalized posterior distribution $P(\ell)$,
+(CDF) associated with the marginalized posterior distribution $P(\ell)$, namely
 %
@@
 %
-For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed that,
+For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed on $\ell$ that
 %
@@
 %
-and likewise for other percentiles.
+where we let $\ell_{\rm max} = \Lambda_{\rm EFT}$ in Eq.~\eqref{eq:def_cdf}, and
+likewise for other credibility percentiles.
 

### 2022-03-30 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: still editing edgb section

@@
 where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
-%$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
+$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
 invariant $\mathscr{G}$,
@@
 
-As we emphasized in Sec.~\ref{sec:remarks}, before drawing any conclusions on
-the allowed values for $\ell_{\rm GB}$ from our parameter estimations, we
-must first check whether the ``EFT''~\eqref{eq:eft_bound} and
-``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
-%
-We check the validity of the EFT bound in Fig.~\ref{fig:edgb_cdf}. In the top (bottom) panel we show
-the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
-evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
-with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
-the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$ between 0 and 1.
-%
-For GW150914, we see that for the $N_{\rm max} = 0$ curves, that the CDF never goes
-past $0.2$, regardless of the mass scale $\mathfrak{m}$ used and even at $\varepsilon =
-1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
-never met at a significant credibility and thus that we cannot place a bound on
-$\ell_{\rm GB}$.
-%
-The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not
-change for either event when we add spin corrections to the EdGB QNM.
-%
-Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our
-present model}.
-%
-These conclusions are summarized in Table~\ref{tab:summary_edgb}.
-
-Let us contrast our results with those of Ref.~\cite{Lyu:2022gdr} which placed
-the bound
-%
-$\ell_{\rm GB} \leqslant 1.33$~km
-%
-using the inspiral portion of the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt} or
-of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound $\ell_{\rm GB} \leqslant 1.7$~km, by considering
-a selection of black hole binaries from the GWTC-1 and GWTC-1 catalogs~\cite{}\footnote{These bounds
-are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and take into consideration only the leading-order
-scalar field contribution arising from the dilatonic coupling.}
-
-% which relies on post-Newtonian calculations of the GW phase shift in this theory~\cite{Yagi:2011xp,Shiralilou:2020gah,Shiralilou:2021mfl}
-% combined with parametrized post-Einsteinian (ppE) framework~\cite{Yunes:2009ke,Chatziioannou:2012rf,Tahura:2019dgr}.
-
-Based on the later, but now here confirmed, within the assumptions of our waveform model,
-in the case of comparable mass binaries.
-
 \begin{figure}[t]
@@
 
+As we emphasized in Sec.~\ref{sec:remarks}, before drawing any conclusions on
+the allowed values for $\ell_{\rm GB}$ from our parameter estimations, we
+must first check whether the ``EFT''~\eqref{eq:eft_bound} and
+``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
+%
+We check the validity of the EFT bound in Fig.~\ref{fig:edgb_cdf}. In the top (bottom) panel we show
+the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
+evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
+with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
+the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$ between 0 and 1.
+%
+For GW150914, we see that for the $N_{\rm max} = 0$ curves, that the CDF never goes
+past $0.2$, regardless of the mass scale $\mathfrak{m}$ used and even at $\varepsilon =
+1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
+never met at a significant credibility and thus that we cannot place a bound on
+$\ell_{\rm GB}$.
+%
+The situation is similar for GW200129 with $N_{\rm max} = 0$ and does not
+change for either event when we add spin corrections to the EdGB QNM.
+%
+Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our
+present model}.
+%
+These conclusions are summarized in Table~\ref{tab:summary_edgb}.
+
+Let us contrast our results with those of Ref.~\cite{Lyu:2022gdr} which placed
+the bound
+%
+$\ell_{\rm GB} \leqslant 1.33$~km
+%
+using the \emph{inspiral} portion of the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt} or
+of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound $\ell_{\rm GB} \leqslant 1.7$~km, by considering
+a selection of black hole binaries from the GWTC-1 and GWTC-1 catalogs~\cite{}\footnote{These bounds
+are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and
+take into consideration only the leading-order scalar field contribution arising from the dilatonic coupling.}
+%
+In this cases
+
+% which relies on post-Newtonian calculations of the GW phase shift in this theory~\cite{Yagi:2011xp,Shiralilou:2020gah,Shiralilou:2021mfl}
+% combined with parametrized post-Einsteinian (ppE) framework~\cite{Yunes:2009ke,Chatziioannou:2012rf,Tahura:2019dgr}.
+
+Based on the later, but now here confirmed, within the assumptions of our waveform model,
+in the case of comparable mass binaries.
+
+Hence, here we have an example of a theory in which the inspiral portion of the signal
+is more constraining then the ringdown portion of the signal.
+%
+As we will next, the situation is the opposite for dCS gravity.
+
 \subsection{Dynamical Chern-Simons}
@@
 
+\hs{TODO: say that we could try to expand the waveform model to include modification to
+the inspiral part too; maybe through FTI~\cite{Mehta:2022pcn}?}
+
+\hs{TODO: add that we could try to parametrize the final black hole mass and spin estimates formulas we
+use at the moment~\cite{Hofmann:2016yih}. Maybe comment that a possible first attempt could follow~\cite{Buonanno:2007sv},
+as done in~\cite{Jai-akson:2017ldo,Li:2020wse}. Say that ultimately we will need to informed by NR in beyond-GR.}
+
 \hs{I suspect that by construction the $N_{\rm max} = 1$ cases will often fail to satisfy our

### 2022-03-30 papers/paper_alt_theor_bounds/sec_pe.tex
hs: still editing edgb section

@@
 described by our waveform model \pSEOB{}, we can infer the parameters of the
-model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using the Bayes
-theorem,
+model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using Bayes' theorem,
 %
@@
 We subsequently marginalize over the remaining parameters to obtain the
-posterior probability distribution function~(PDF) on $\ell$,  $P_j(\ell \vert d_j,\mathcal{H})$, our main parameter of interest.
-%
-% An example of this is shown in Fig. XX.
+posterior probability distribution function~(PDF) on $\ell$,  i.e., $P_j(\ell \vert d_j,\mathcal{H})$,
+our main parameter of interest.
 

### 2022-03-30 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: moving to the eft sections

@@
 in terms of non-GR mass and spin, say $\bar{M}$ and $\bar{\chi}$. If we assume that the beyond-GR corrections
-are included perturbatively, the modifications to the BH mass and spin can be absorved into the deviations
+are included perturbatively, the modifications to the BH mass and spin can be absorbed into the deviations
 parameters $\delta\omega$ and $\delta\tau$.
@@
 This means we can identify the $M$ and $\chi$ with their \emph{corresponding GR values}.
-
-We remark that in the GR limit, where $\delta\omega_{k}^{(n)} = \delta\tau_{k}^{(n)} = 0$ $\forall\, n$,
+%
+\hs{TODO: say that we check a posteriori if our PE runs agree with this.}
+
+We remark that in the GR limit ($\gamma \to 0$)
+% where $\delta\omega_{k}^{(n)} = \delta\tau_{k}^{(n)} = 0$ $\forall\, n$,
 the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
@@
 % \hs{TODO: in figures and tables use $N_{\rm max} = 0$ ($N_{\rm max} = 1$) instead of $j=0$ ($j=0,1$).}
-\hs{TODO: say that we check a posteriori if our PE runs agree with this.}
 
@@
 In all panels, different line colors correspond to the inclusion ($N_{\rm max} = 1$) or not ($N_{\rm max} = 0$)
-of the linear-in-spin QNM correction.}
+of the linear-in-spin QNM correction.
+%
+The joint posteriors are shown for illustrative purposes only. As we explain in Fig.~\ref{fig:edgb_cdf} and
+in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}.
+}
 \label{fig:edgb_exec_sum}
@@
 %
-Altogether, \emph{we conclude that we cannot constrain EdGB gravity with our
+Taken together we are led to \emph{conclude that we cannot constrain EdGB gravity with our
 present model}.
 %
-These conclusions are summarized in Table~\ref{tab:summary_edgb}.
-
-Let us contrast our results with those of Ref.~\cite{Lyu:2022gdr} which placed
-the bound
+We summarize our findings in Table~\ref{tab:summary_edgb}.
+
+Let us place our results in a broader context. In particular, let us contrast
+them against those of Ref.~\cite{Lyu:2022gdr} which placed the bound
 %
@@
 %
-using the \emph{inspiral} portion of the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt} or
-of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound $\ell_{\rm GB} \leqslant 1.7$~km, by considering
-a selection of black hole binaries from the GWTC-1 and GWTC-1 catalogs~\cite{}\footnote{These bounds
+using the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt}, and
+of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound
+%
+$\ell_{\rm GB} \leqslant 1.7$~km,
+%
+by stacking the posterior of $\ell_{\rm GB}$ from a  selection of black hole binaries from the GWTC-1 and GWTC-2 catalogs
+with at least one relatively low-mass binary component~\cite{}\footnote{These bounds
 are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and
-take into consideration only the leading-order scalar field contribution arising from the dilatonic coupling.}
-%
-In this cases
-
-% which relies on post-Newtonian calculations of the GW phase shift in this theory~\cite{Yagi:2011xp,Shiralilou:2020gah,Shiralilou:2021mfl}
-% combined with parametrized post-Einsteinian (ppE) framework~\cite{Yunes:2009ke,Chatziioannou:2012rf,Tahura:2019dgr}.
-
-Based on the later, but now here confirmed, within the assumptions of our waveform model,
-in the case of comparable mass binaries.
-
+take into consideration only the leading-order scalar field contribution arising from the dilatonic coupling.}.
+%
+These works use the \emph{inspiral} portion of GW event only and a constraint
+on EdGB gravity can be obtained because black holes in this theory carry a
+monopole scalar charge which in turn can source dipolar scalar radiation,
+that affects the GW phase at $-1$PN order, relative to the dominant GR contribution, and
+is proportional to the difference between the charges of binary components.
+%
+Now, the magnitude of the scalar charge scales roughly with the inverse of the black hole's mass squared, that is,
+smaller (larger) back holes carry large (smaller) scalar charges. Qualitatively, this is because the scalar field
+is sourced by the Gauss-Bonnet curvature invariant, which is large for black holes with small masses.
+%
+Beyond-GR corrections to the inspiral are, by construction, not present in our
+waveform model and constitutes a important ingredient to be added in forthcoming
+versions of the model.
+%
+In addition to the larger mass (which suppresses the black hole's charge), the
+QNM of EdGB gravity differ very little from GR as observed in~\cite{Blazquez-Salcedo:2016enn}.
+%
 Hence, here we have an example of a theory in which the inspiral portion of the signal
@@
 %
-We stress that posteriors obtained including $j=1$ corrections, violated conditions~\eqref{eq:parspec_bound}
+We stress that posteriors obtained including $n=1$ corrections, violated conditions~\eqref{eq:parspec_bound}
 and therefore should not be used to draw meaningful conclusions. We show them for illustrative purposes
@@
 (middle panel), with (dashed line) and without (solid line) spin corrections to
-dominant $l = m = 2$,~$n=0$~QNM.
+dominant $(2,2,0)$~QNM.
 %
@@
 peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
-deviation from GR. This is not the case.
-%
-We must remember that in the ParSpec formalism that the GR deviations
-are controlled by $\gamma \, \delta \omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$.
-We verified that these quantities do indeed peak at zero indicating consistency with GR.
+deviation from GR. This is not the case and the situation is that same as the
+one we discussed in the previous section for EdGB gravity.
+%
+We verified that
+%
+\begin{equation}
+    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm CS}}{G M_{\rm s}} \right)^{4}\,,
+\end{equation}
+%
+does indeed peak at zero indicating consistency with GR, similarly to what is shown in Fig.~\ref{} for $\gamma_{\rm GB}$.
 %
@@
 
-In Fig.~\ref{fig:dcs_cdf} we show the cumulative distribution function (CDF) as
-evaluates with Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT}$,
+In Fig.~\ref{fig:dcs_cdf} we show the cumulative distribution function,
+obtained from Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT} (\varepsilon, \gm)$,
 for both GW150914 (top panel) and GW200129 (bottom panel), where $\Lambda_{\rm EFT}$
-is calculated with either $\mathfrak{m} = m_2$ (blue curves) or $M_{f}$ (orange curves),
-and with $\varepsilon \in [0,\, 1]$.
+is calculated with either $\gm = m_2$ (dashed lines) or $M_{f}$ (solid lines),
+and in the range $\varepsilon \in [0,1]$.
 %
 For GW150914, we see that with $\gm = m_2$ that Eq.~\eqref{eq:eft_bound} is not
-satisfied unless $\varepsilon \approx 0.9$ (with only $j=0$ corrections) and
-$\varepsilon \approx 0.7$ (with both $j=0$ and $1$ corrections).
+satisfied unless $\varepsilon \approx 0.9$ (with only $n=0$ corrections) and
+$\varepsilon \approx 0.7$ (with both $n=0$ and $1$ corrections).
 %
@@
 \ell_{\rm CS} \leqslant 42.6~\textrm{km}
-% ~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
 \quad \textrm{(90\% credibility)},

### 2022-03-30 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more edits

@@
 
+We now consider the cubic EFT of GR, a case in which our results bear
+similarity with what we found in dCS.
+
 \begin{figure}[t]
@@
 \label{sec:results_qeft}
+
+Finally, let us consider the quartic EFT of GR.
 
@@
 
-We presented an unified framework to combine the parametrized formalism introduced
-to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model.
-%
-We showed through concrete examples how theory-specific calculations QNM of
-slowly-rotating BHs in modified gravity theories can be mapped upon the
+We presented an unified framework to combine the framework introduced
+to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
+%
+We showed with concrete examples how theory-specific calculations QNM of
+slowly-rotating BHs in modified gravity theories can be mapped onto the
 theory-agnostic beyond-GR parameters of the ParSpec formalism.
 %
-Together this allowed us to apply the \pSEOB~waveform model to test four
-modified gravity theories (EdGB, dCS, cubic, and quartic
-effective-field-theories of GR) using data from the GW events GW150914 and GW200129.
+Put together this allowed us to use the \pSEOB~waveform model to test four
+modified gravity theories (EdGB, dCS, cubic, and quartic EFTs of GR) using
+observational data from the GW events GW150914 and GW200129.
 %

### 2022-03-30 papers/paper_alt_theor_bounds/sec_pe.tex
hs: edits to pe

@@
 %
-Assuming a specific prior distribution for our parameters (discussed further in the subsequent section), we stochastically
+Assuming a specific prior distribution for our parameters (discussed further in the next section), we stochastically
 sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
@@
 
-For $N$ independent GW observations $\{d_j\}$, $j=1,...,N$, each characterised by a posterior probability distribution $P_j(\ell \vert d_j,\mathcal{H})$, the joint posterior can be written as:
+For $N$ independent GW observations $\{d_j\}$, $j=1,...,N$, each characterised
+by a posterior probability distribution $P_j(\ell \vert d_j,\mathcal{H})$, the
+joint posterior can be written as:
 %
@@
 presented in this paper, identified two events which provided the strongest
-bounds on measurements of the dominant $(220)$ QNM --
+bounds on measurements of the dominant $(220)$ QNM:
 GW150914~\cite{LIGOScientific:2016aoc} and

### 2022-03-30 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: going over again the theory summary

@@
 
-% We will consider several modified gravity theories as applications of the \pSEOB{}
-% waveform model presented in Sec.~\ref{sec:review_pSEOB}.
-%
-We briefly review the theories we consider in this paper, what the currents
-observational constraints are in each of them and what we know about BH QNMs in each of them.
-
-\subsection{scalar-Gauss-Bonnet gravity}
-%
-This theory is given by the following action,
+We start by briefly reviewing the modified gravity theories we consider in this
+paper, what are the currents observational constraints and what we do know
+about BH QNMs in each of them.
+
+\subsection{Einstein-dilaton-Gauss-Bonnet gravity}
+\label{sec:review_edgb}
+
+This theory belongs to the class of scalar-Gauss-Bonnet theories, described by
+the action
 %
@@
     R - \tfrac{1}{2}(\nabla \varphi)^2
-    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \mathscr{G}
-    \right],
-\end{equation}
-%
-where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
-$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
-invariant $\mathscr{G}$,
-%
-\begin{equation} \label{eq:def_gb}
-    \mathscr{G} =
+    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \, \mathcal{G}
+    \right]\,,
+\end{equation}
+%
+where $g = \textrm{det} \, g$ is the metric determinant, $R$ is the Ricci
+scalar and $\varphi$ is a dynamical, massless scalar field that couples to the
+Gauss-Bonnet invariant
+%
+% \begin{equation} \label{eq:def_gb}
+$ \mathcal{G} =
 R^{\mu\nu\rho\sigma}R_{\mu\nu\rho\sigma}
 - 4 R^{\mu\nu}R_{\mu\nu}
-    + R^2,
-\end{equation}
-%
-with strength set by the dimensionful coupling constant $\ell_{\rm GB}$ with dimensions
-of length. Different subclasses of this theory are determined by the function $f(\varphi)$
-and they can be classified into two classes based on the properties of their BH solutions.
-%
-In the first class, the first derivative of the coupling
-function $f'(\varphi) = \dd f  / \dd \varphi$ is always nonzero and BHs
-are known to always support (secondary) scalar hair.
-%
-Examples include the shift-symmetric $f \propto \varphi$ and dilatonic
-$f \propto \exp(\varphi)$ couplings.
++ R^2$,
+% \end{equation}
+%
+where $R_{\mu\nu\rho\sigma}$ and $R_{\mu\nu}$ are respectively the Riemann and Ricci tensors.
+%
+By itself, $\int \dV \mathcal{G}$ is a boundary term in four dimensions
+and hence does not contribute to the field equations~\cite{Myers:1987yn}.
+%
+It can however contribute to the field equation when coupled to $\varphi$, as
+done through function $f(\varphi)$. The strength of the coupling is
+set by $\ell_{\rm GB}$, with dimensions of length.
+
+Different subclasses of this theory are determined by the function $f(\varphi)$
+and they can be classified into two classes based on the properties of their BH
+solutions.
+%
+In the first class, the first derivative of the coupling function $f'(\varphi) = \dd f  / \dd \varphi$
+is always nonzero and BHs are known to always support scalar hair.
+%
+This is the case of Einstein-dilaton-Gauss-Bonnet (EdGB) gravity, for which $f = \exp(\varphi)$.
+%
+% Examples include the shift-symmetric $f \propto \varphi$ and dilatonic
+% $f \propto \exp(\varphi)$ couplings.
 %
@@
 %
-In this case, one can show that theory admits the same stationary,
-asymptotically flat BH solution of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
+In this case, the theory admits the same stationary, asymptotically flat BH
+solution of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
 %
 Examples include the quadratic $f \propto \varphi^2$~\cite{Silva:2017uqg}
-and Gaussian $f \propto \exp(-\varphi^2)$~\cite{Doneva:2017bvd} couplings.
-%
-Here we will consider only the dilatonic theory.
-
-BHs in both classes support monopolar scalar hair and thus, when in binaries,
-can source scalar dipole radiation and are therefore prone to be constrained with
-GWs observations of compact binaries~\cite{Nair:2019iur,Perkins:2021mhb}.
-%
-\dots
+and Gaussian $f \propto \exp(-\varphi^2)$~\cite{Doneva:2017bvd} coupling functions.
+
+BHs in both classes of theories have hair, to which we can associate a (monopole) scalar charge,
+related to the asymptotic $1/r$ decay of the scalar field.
+%
+This charge is not an independent parameter, and depends on the BH's mass and spin,
+thus being a ``secondary charge''~\cite{Coleman:1991ku,Herdeiro:2015waa}.
+%
+Since the scalar field is coupled to a curvature invariant, the scalar charge is larger (smaller)
+the smaller (larger) the BH's mass is.
+
+These properties are not mere theoretical curiosities, but have important observational consequences.
+%
+First, the presence of the scalar charge implies that when in binaries, BHs can source
+scalar dipole radiation~\cite{Yagi:2011xp,Julie:2019sab,Shiralilou:2020gah,Shiralilou:2021mfl,Julie:2022huo} making
+the theory prone to be constraint with present
+GWs observations of BH binaries (BBH)~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+%
+Second, the scalar field does influence the response of BHs to linearized perturbations in this theory,
+affecting their QNM spectra.
 
@@
 the Gauss-Bonnet invariant, which manifests into a coupling between scalar perturbation
-and gravitational perturbations of polar parity \dots
+and gravitational perturbations of polar parity.
+%
+BH QNMs in EdGB gravity were first computed in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and these calculations
+were extended to leading-order in BH spin effects in Ref.~\cite{Pierini:2021jxd}.
 
@@
 
-\subsection{dynamical Chern-Simons gravity}
+\subsection{Dynamical Chern-Simons gravity}
+\label{sec:review_dcs}
 

### 2022-03-31 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: theory section and new refs

@@
 
-This theory belongs to the class of scalar-Gauss-Bonnet theories, described by
-the action
+This theory belongs to the class of scalar-Gauss-Bonnet theories, which are
+described by the action
 %
@@
 where $g = \textrm{det} \, g$ is the metric determinant, $R$ is the Ricci
-scalar and $\varphi$ is a dynamical, massless scalar field that couples to the
+scalar and $\varphi$ is a dynamical scalar field that couples to the
 Gauss-Bonnet invariant
@@
 It can however contribute to the field equation when coupled to $\varphi$, as
-done through function $f(\varphi)$. The strength of the coupling is
+done through the coupling function $f(\varphi)$. The strength of the coupling is
 set by $\ell_{\rm GB}$, with dimensions of length.
@@
 %
-This is the case of Einstein-dilaton-Gauss-Bonnet (EdGB) gravity, for which $f = \exp(\varphi)$.
+This is the case of Einstein-dilaton-Gauss-Bonnet (EdGB) gravity, for which $f(\varphi) = \exp(\varphi)$~\cite{Kanti:1995vq}.
+%
+% \begin{equation}
+% f = \exp(\varphi)\,,
+% \end{equation}
+%
 %
@@
 In this case, the theory admits the same stationary, asymptotically flat BH
-solution of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
-%
-Examples include the quadratic $f \propto \varphi^2$~\cite{Silva:2017uqg}
-and Gaussian $f \propto \exp(-\varphi^2)$~\cite{Doneva:2017bvd} coupling functions.
-
-BHs in both classes of theories have hair, to which we can associate a (monopole) scalar charge,
-related to the asymptotic $1/r$ decay of the scalar field.
-%
-This charge is not an independent parameter, and depends on the BH's mass and spin,
-thus being a ``secondary charge''~\cite{Coleman:1991ku,Herdeiro:2015waa}.
-%
-Since the scalar field is coupled to a curvature invariant, the scalar charge is larger (smaller)
+solution of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
+%
+Examples include the Gaussian $f(\varphi) \propto \exp(-\varphi^2)$~\cite{Doneva:2017bvd} and
+the quadratic $f(\varphi) \propto \varphi^2$~\cite{Silva:2017uqg} coupling functions.
+
+BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
+related to the asymptotic $1/r$ fall-off of the scalar field.
+%
+This charge is not an independent parameter, and depends on the BH's mass and spin, %~\cite{Berti:2018cxi},
+thus being a ``secondary hair''~\cite{Coleman:1991ku,Herdeiro:2015waa}.
+%
+Since the scalar field is coupled to a curvature scalar, the $Q$ is larger (smaller)
 the smaller (larger) the BH's mass is.
 
-These properties are not mere theoretical curiosities, but have important observational consequences.
+These properties are not mere theoretical curiosities; they have important observational consequences.
 %
 First, the presence of the scalar charge implies that when in binaries, BHs can source
-scalar dipole radiation~\cite{Yagi:2011xp,Julie:2019sab,Shiralilou:2020gah,Shiralilou:2021mfl,Julie:2022huo} making
-the theory prone to be constraint with present
-GWs observations of BH binaries (BBH)~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
-%
-Second, the scalar field does influence the response of BHs to linearized perturbations in this theory,
-affecting their QNM spectra.
-
-The calculation of the QNMs in this theory is more complicated than in GR already for
-nonrotating BHs. The reason is due to the coupling between scalar field and
-the Gauss-Bonnet invariant, which manifests into a coupling between scalar perturbation
-and gravitational perturbations of polar parity.
-%
-BH QNMs in EdGB gravity were first computed in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and these calculations
-were extended to leading-order in BH spin effects in Ref.~\cite{Pierini:2021jxd}.
+scalar dipole radiation (see e.g., Refs.~\cite{Yagi:2011xp,Julie:2019sab,Shiralilou:2020gah,Shiralilou:2021mfl,Julie:2022huo})
+which affects the GW phase at $-1$PN order (relative to the dominant GR
+contribution), with magnitude proportional to the difference between the
+charges of binary components. This makes EdGB gravity testable with present GWs
+observations of compact binaries where at least one component is a BH.
+%
+More specifically, Ref.~\cite{Lyu:2022gdr} placed the bound
+%
+$\ell_{\rm GB} \leqslant 1.33$~km
+%
+using the neutron star-black hole binaries GW200105 and
+GW200115~\cite{LIGOScientific:2021qlt} while Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, obtained
+%
+$\ell_{\rm GB} \leqslant 1.7$~km,
+%
+by stacking the posteriors of $\ell_{\rm GB}$ from a selection of black hole binaries (BBH)
+from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}\footnote{These bounds
+are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and
+take into account only the leading-order scalar field contribution arising from the dilatonic coupling.}.
+%
+% These works use the \emph{inspiral} portion of GW event only and a constraint
+% on EdGB gravity can be obtained because black holes in this theory carry a
+% monopole scalar charge which in turn can source dipolar scalar radiation,
+% that affects the GW phase at $-1$PN order, relative to the dominant GR contribution, and
+% is proportional to the difference between the charges of binary components.
+
+Second, the scalar field does influence the response of BHs to linearized perturbations and thus
+affects the BH's QNM spectra.
+%
+% The calculation of the QNMs in this theory is more complicated than in GR already for
+% nonrotating BHs. The reason is due to
+The coupling between scalar field and the Gauss-Bonnet invariant, which
+manifests into a coupling between scalar perturbation and gravitational
+perturbations of polar parity, which, e.g., breaks the familiar equivalence
+between the QNM spectra of polar and axial gravitational perturbations of
+Schwarzschild BHs in GR.
+%
+The QNMs on nonrotating BHs in EdGB gravity were first computed in
+Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and these calculations were
+extended to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
 
@@
 
-This theory is given by the following action,
+This theory is described by the action~\cite{Jackiw:2003pm},
 %
@@
 where $\vartheta$ is a pseudo-scalar field, which couples
-to the Pontryagin density,
-%
-\begin{equation}
-    {}^{*}RR = {}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} R^{\nu}_{\mu\rho\sigma},
-\end{equation}
+to the Pontryagin density
+${}^{*}RR = {}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} R^{\nu}_{\mu\rho\sigma}$,
+%
+% \begin{equation}
+%     {}^{*}RR = {}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} R^{\nu}_{\mu\rho\sigma},
+% \end{equation}
 %
@@
 ${}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} =
-\tfrac{1}{2} \epsilon^{\mu}{}_{\nu\gamma\delta}
-R^{\gamma\delta\rho\sigma}$,
+\epsilon^{\mu}{}_{\nu\gamma\delta}
+R^{\gamma\delta\rho\sigma} / 2$,
 %
@@
 %
-The coupling between scalar field and the Pontryagin density is set by the
-$\ell_{\rm CS}$ with dimensions of length.
+The coupling strength between scalar field and the Pontryagin density is set by the
+coupling constant $\ell_{\rm CS}$, with dimensions of length.
 

### 2022-03-31 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: edited dcs section; move to eft section

@@
 perturbations of polar parity, which, e.g., breaks the familiar equivalence
-between the QNM spectra of polar and axial gravitational perturbations of
+between the QNM spectra of polar and axial gravitational perturbations (isospectrality) of
 Schwarzschild BHs in GR.
@@
 %
-where $\vartheta$ is a pseudo-scalar field, which couples
-to the Pontryagin density
+where $\vartheta$ is a pseudoscalar field, which couples to the Pontryagin
+density
 ${}^{*}RR = {}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} R^{\nu}_{\mu\rho\sigma}$,
@@
 %
-The coupling strength between scalar field and the Pontryagin density is set by the
-coupling constant $\ell_{\rm CS}$, with dimensions of length.
-
-The theory admits the Schwarzschild BH solution of GR, but predicts
-that spinning BHs have (secondary) scalar hair, which, unlike in
-scalar-Gauss-Bonnet gravity, is dipolar~\cite{Yunes:2009hc,Konno:2009kg}.
-%
-Consequently, the leading-scalar radiation channel is quadrupolar making this
-theory presently unconstrained by from the GWs from the inspiral of BH
-binaries alone~\cite{Nair:2019iur,Perkins:2021mhb}.
-%
-However, the theory has been constrained by Ref~\cite{Silva:2020acr} through a
-combination information of x-ray observations of the isolated neutron star PSR
-J0030+0451~\cite{Lommen:2000yt,NANOGrav:2017wvv} by the
-NICER~\cite{Riley:2019yda,Miller:2019cac} and gravitational-wave observation of
-the binary neutron star event GW170817~\cite{TheLIGOScientific:2017qsa}.
-
-Similarly to the case of scalar-Gauss-Bonnet gravity, the perturbations of nonrotating
-BHs in dynamical Chern-Simons gravity also have a coupling between scalar and
-metric perturbations. However, the coupling is between the scalar and gravitational perturbations
-of axial parity~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb,Wagle:2021tam}.
+As in scalar-Gauss-Bonnet theories, $\int \dV {}^{*}RR$ alone is a boundary term~\cite{Jackiw:2003pm},
+hence cannot contribute to the field equations in four-dimensions.
+%
+However, this terms can modify the theory's field equation by coupling it to
+$\vartheta$.
+%
+The coupling strength set by the coupling constant $\ell_{\rm CS}$, with
+dimensions of length.
+
+The theory admits same the garden-variety Schwarzschild BH solution of
+GR~\cite{Jackiw:2003pm}, but admits non-Kerr solutions for spinning BHs~\cite{Yunes:2009hc,Konno:2009kg}.
+%
+These BHs carry secondary scalar hair, which, unlike in EdGB gravity, is
+dipolar.
+%
+As a consequence, the leading-scalar radiative channel of BBH to lose energy is quadrupolar,
+which affects the GW phase at 2PN order.
+%
+Deviations from GR at this PN order are poorly constrained with present GW
+observations~\cite{LIGOScientific:2021sio}, making dCS gravity unconstrained by
+analyses that rely on the inspiral portion of GWs from BBH
+binaries~\cite{Nair:2019iur,Perkins:2021mhb}.
+%
+However, the theory has been constrained by Ref.~\cite{Silva:2020acr}, that found
+%
+$\ell_{\rm CS} \leqslant 8.5$~km,
+%
+by folding data from the x-ray observations of the isolated neutron star (NS)
+PSR~J0030+0451~\cite{Lommen:2000yt,NANOGrav:2017wvv} by
+NICER~\cite{Riley:2019yda,Miller:2019cac} and from the GW observation of the binary
+neutron star (BNS) GW170817~\cite{TheLIGOScientific:2017qsa}.
+
+The QNMs of the Schwarzschild BH in dCS gravity where studied in Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb},
+that found that scalar perturbations and gravitational perturbations of axial parity couple. (Contrast with EdGB gravity).
+%
+This yields in a breakdown of isospectrality. The QNM spectra of slowly-rotating BHs in dCS gravity was
+studied in Ref.~\cite{Wagle:2021tam}.
 
@@
 
-This theory is given by the following action,
+Our last example of modified gravity theories are the so-called effective field theories (EFT) of GR.
+They are described by the action
 %
@@
     +
-    {\sum}_{n \geqslant 2} \ell^{2n - 2} L^{(2n)}
-    \right],
-\end{equation}
-%
-where $\ell$ is some length scale, assumed to be small compares to the length
-scale associated with a BH, i.e., $\ell / M \ll 1$, and
-$L^{(2n)}$ are corrections to the Einstein-Hilbert term action that
-introduce involving higher-order curvature tensors (with $2n$ metric
-derivatives).
+    \sum_{n \geqslant 2} \ell^{2n - 2} L^{(2n)}
+    \right]\,,
+\end{equation}
+%
+where $\ell$ is a lengthscale, assumed to be small compares to the lengthscale
+associated with a BH, i.e., $\ell / M \ll 1$, and $L^{(2n)}$ are corrections to
+that introduce higher-order curvature tensors (with $2n$ metric derivatives).
 
@@
 where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(l,m)$.\footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.} As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
-The model uses an effective-one-body approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
+%
+The model uses an effective-one-body (EOB) approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
 An accurate description of the merger is incorporated through calibration with NR simulations, as described in~\cite{Cotesta:2018fcv}, along with information for the merger and ringdown phases, from BH perturbation theory.

### 2022-03-31 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: work on eft section, new refs

@@
 cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
-quartic EFT & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km \\
+quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km \\
 \hline \hline
@@
 BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
-related to the asymptotic $1/r$ fall-off of the scalar field.
+related to the asymptotic $r^{-1}$ fall-off of the scalar field.
 %
@@
 
-This theory is described by the action~\cite{Jackiw:2003pm},
+This theory is described by the action~\cite{Jackiw:2003pm,Alexander:2009tp},
 %
@@
 %
-These BHs carry secondary scalar hair, which, unlike in EdGB gravity, is
-dipolar.
+These BHs support a scalar field which asymptotically falls-off as $r^{-2}$, to which we can associate
+a scalar dipole charge.
 %
@@
 
-Our last example of modified gravity theories are the so-called effective field theories (EFT) of GR.
+Our last example of modified gravity theories are the so-called effective field
+theories (EFT) of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
+%
 They are described by the action

### 2022-03-31 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more writing and refs

@@
 %
-% \begin{equation} \label{eq:def_gb}
-$ \mathcal{G} =
+$\mathcal{G} =
 R^{\mu\nu\rho\sigma}R_{\mu\nu\rho\sigma}
@@
 + R^2$,
-% \end{equation}
 %
@@
 % \end{equation}
-%
-%
-% Examples include the shift-symmetric $f \propto \varphi$ and dilatonic
-% $f \propto \exp(\varphi)$ couplings.
 %
@@
 take into account only the leading-order scalar field contribution arising from the dilatonic coupling.}.
-%
-% These works use the \emph{inspiral} portion of GW event only and a constraint
-% on EdGB gravity can be obtained because black holes in this theory carry a
-% monopole scalar charge which in turn can source dipolar scalar radiation,
-% that affects the GW phase at $-1$PN order, relative to the dominant GR contribution, and
-% is proportional to the difference between the charges of binary components.
 
@@
 %
-% The calculation of the QNMs in this theory is more complicated than in GR already for
-% nonrotating BHs. The reason is due to
 The coupling between scalar field and the Gauss-Bonnet invariant, which
@@
 perturbations of polar parity, which, e.g., breaks the familiar equivalence
-between the QNM spectra of polar and axial gravitational perturbations (isospectrality) of
-Schwarzschild BHs in GR.
+between the QNM spectra of polar and axial gravitational perturbations
+(isospectrality) of Schwarzschild BHs in GR.
 %
@@
 extended to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
-
-% \begin{figure}
-% \begin{tikzpicture}[baseline,>=stealth]
-%     % \draw[help lines, gray] (-4, -2) grid (4, 2);
-%     \draw[->] (-2.5, 0) -- (-1.75, +0.5);
-%     \draw[->] (-2.5, 0) -- (-1.75, -0.5);
-%
-%     \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \varphi\}$};
-%
-%     \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
-%     \node at (-1, +0.5) {$\{ \textcolor{rred}{h^{\rm p}_{\alpha\beta}}, \, \varphi\}$};
-%     \node at (-1, -0.5) {$h^{\rm a}_{\alpha\beta}$};
-%
-%     \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
-%     \node at (+1, +0.5) {\dots};
-%     \node at (+1, -0.5) {\dots};
-% \end{tikzpicture}
-% \caption{Quasinormal modes of BHs in scalar-Gauss-Bonnet gravity.}
-% \end{figure}
 
@@
 %
-% \begin{equation}
-%     {}^{*}RR = {}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} R^{\nu}_{\mu\rho\sigma},
-% \end{equation}
-%
 where ${}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma}$ is the dual of the Riemann tensor,
@@
 %
-As in scalar-Gauss-Bonnet theories, $\int \dV {}^{*}RR$ alone is a boundary term~\cite{Jackiw:2003pm},
-hence cannot contribute to the field equations in four-dimensions.
+As in scalar-Gauss-Bonnet theories, $\int \dV {}^{*}RR$ alone is a boundary
+term~\cite{Jackiw:2003pm}, thus does not contribute to the field equations in
+four-dimensions.
 %
@@
 As a consequence, the leading-scalar radiative channel of BBH to lose energy is quadrupolar,
-which affects the GW phase at 2PN order.
+which affects the GW phase at 2PN order~\cite{Yagi:2011xp,Alexander:2017jmt}.
 %
@@
 studied in Ref.~\cite{Wagle:2021tam}.
-
-% \begin{figure}
-% \begin{tikzpicture}[baseline,>=stealth]
-%     % \draw[help lines, gray] (-4, -2) grid (4, 2);
-%     \draw[->] (-2.5, 0) -- (-1.75, +0.5);
-%     \draw[->] (-2.5, 0) -- (-1.75, -0.5);
-%
-%     \node at (-3.25, 0) {$\{h_{\alpha\beta}, \, \vartheta\}$};
-%
-%     \node at (-1, 1.25) {${\cal O}(\chi^{0})$};
-%     \node at (-1, +0.5) {$h^{\rm p}_{\alpha\beta}$};
-%     \node at (-1, -0.5) {$\{ \textcolor{rred}{h^{\rm a}_{\alpha\beta}}, \, \vartheta\}$};
-%
-%     \node at (+1, 1.25) {${\cal O}(\chi^{1})$};
-%     \node at (+1, +0.5) {\dots};
-%     \node at (+1, -0.5) {\dots};
-% \end{tikzpicture}
-% \caption{Quasinormal modes of BHs in dynamical Chern-Simons gravity.}
-% \end{figure}
 
@@
     L^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
-    % \nonumber \\
-    %         &\quad
     + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
@@
 space studied in~\cite{Sennett:2019bpc}.
-
-% where we defined the Gauss-Bonnet and Pontryagin densities, respectively,
-% %
-% \begin{subequations}
-% \begin{align}
-%     R^{2}_{\rm GB} &= R_{\mu\nu\rho\sigma}R^{\mu\nu\rho\sigma} - 4 R_{\mu\nu} R^{\mu\nu} + R^2,
-%     \\
-%     {}^{*}RR &= \tfrac{1}{2} R_{\nu\mu\rho\sigma} {}^{*}R^{\mu\nu\rho\sigma},
-% \end{align}
-% \end{subequations}
-% %
-% and where $R_{\mu\nu\rho\sigma}$ is the Riemann tensor
-% and $\tilde{R}_{\mu\nu\rho\sigma}$ its dual, defined as
-% %
-% \begin{equation}
-% \tilde{R}_{\mu\nu\alpha\beta} = \tfrac{1}{2} \epsilon_{\mu\nu\rho\sigma} R^{\rho\sigma}{}_{\alpha\beta},
-% \end{equation}
-% %
-% with $\epsilon_{\mu\nu\rho\sigma}$ being the Levi-Civita tensor.
-
-% This action encapsulates various modified gravity theories, which often are studied on their own,
-% namely,
-% %
-% \begin{itemize}
-%     \item scalar Gauss-Bonnet gravity (sGB): corresponds to $\alpha_{\rm GB}$
-%           nonzero and all other dimensionless coupling constants equal to zero.
-%     \item dynamical Chern-Simons (dCS): this corresponds to $\alpha_{\rm CS}$
-%           nonzero and all other dimensionless coupling constants equal to zero.
-%     \item cubic effective field theory of GR (cEFTofGR): this corresponds to $\lame$, $\lamo$ nonzero
-%           and all other dimensionless coupling constants equal to zero.
-%     \item quartic effective field theory of GR (qEFTofGR): this corresponds to $\varepsilon_{i}$
-%           ($i = 1,2,3$) nonzero and all other dimensionless coupling constants equal to zero.
-% \end{itemize}
-%
-% In each of these theories, slowly-rotating BH and their quasinormal mode spectra
-% to leading order in spin have been calculated.
-% %
-% We can use this results to establish a mapping between theory-specific calculations and
-% the theory-agnostic {\sc Parspec} parametrization.
-% %
-% We discuss how we do this in the section.
-%
-% In Eqs.~\eqref{eq:action_mods}, $\alpha_{\rm GB}$, $\alpha_{\rm CS}$, $\lame$,
-% $\lamo$ and $\varepsilon_{i}$ are dimensionless constants.
 

### 2022-03-31 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more edits to dcs section

@@
 density
-${}^{*}RR = {}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} R^{\nu}_{\mu\rho\sigma}$,
-%
-where ${}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma}$ is the dual of the Riemann tensor,
+${}^{*}RR = {}^{*}R_{\mu\nu}{}^{\rho\sigma} R^{\nu\mu}{}_{\rho\sigma}$,
+%
+where ${}^{*}R^{\mu\nu\rho\sigma}$ is the dual of the Riemann tensor,
 defined as
 %
-${}^{*}R^{\mu}{}_{\nu}{}^{\rho\sigma} =
-\epsilon^{\mu}{}_{\nu\gamma\delta}
+${}^{*}R^{\mu\nu\rho\sigma} =
+\epsilon^{\mu\nu}{}_{\gamma\delta}
 R^{\gamma\delta\rho\sigma} / 2$,
 %
-and where $\epsilon^{\mu}{}_{\nu\gamma\delta}$ is the Levi-Civita tensor.
+and where $\epsilon_{\mu\nu\gamma\delta}$ is the Levi-Civita tensor.
 %
@@
 %
-The coupling strength set by the coupling constant $\ell_{\rm CS}$, with
+The coupling strength is set by the coupling constant $\ell_{\rm CS}$, with
 dimensions of length.
 
-The theory admits same the garden-variety Schwarzschild BH solution of
-GR~\cite{Jackiw:2003pm}, but admits non-Kerr solutions for spinning BHs~\cite{Yunes:2009hc,Konno:2009kg}.
-%
-These BHs support a scalar field which asymptotically falls-off as $r^{-2}$, to which we can associate
-a scalar dipole charge.
+The theory admits as solution the garden-variety Schwarzschild BH of GR. This
+is not case when rotation is included and the Kerr metric is not a solution of
+the theory~\cite{Jackiw:2003pm}.
+%
+These rotating BHs support a scalar field which falls-off as
+$r^{-2}$ asymptically, to which we can associate a scalar dipole
+charge~\cite{Yunes:2009hc,Konno:2009kg}.
 %
@@
 %
-However, the theory has been constrained by Ref.~\cite{Silva:2020acr}, that found
+Nonetheless, the theory has been constrained by Ref.~\cite{Silva:2020acr}, that found
 %
@@
 NICER~\cite{Riley:2019yda,Miller:2019cac} and from the GW observation of the binary
-neutron star (BNS) GW170817~\cite{TheLIGOScientific:2017qsa}.
+neutron star (BNS) GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}.
 

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: eft theory section in progress

@@
 %
-Nonetheless, the theory has been constrained by Ref.~\cite{Silva:2020acr}, that found
+Nonetheless, the theory has been constrained in Ref.~\cite{Silva:2020acr}, that found
 %
@@
 studied in Ref.~\cite{Wagle:2021tam}.
+%
+They were also extracted from numerical relativity (NR) simulations of head-on BH collisions
+in Ref.~\cite{Okounkova:2019dfo}.
 
@@
 More specifically, we follow Refs.~\cite{Cano:2020cao,Cano:2021myl} and work up
-to dimension-eight operators (i.e., $n=4$),
+to dimension-eight operators ($n=4$),
 %
@@
     L^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
-    + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
+    + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu}\,,
     \label{eq:s_6}
@@
     + \varepsilon_{2} \tilde{\mathcal{C}}^{2}
-    + \varepsilon_{3} \mathcal{C} \tilde{\mathcal{C}},
+    + \varepsilon_{3} \mathcal{C} \tilde{\mathcal{C}}\,,
 \label{eq:s_8}
@@
 %
-where $\lambda_{\rm o, e}$ and $\varepsilon_{i}$ ($i=1,2,3$) are dimensionless parameters.
-
-BHs in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} for the dimension-six EFT
-and in Refs.~\cite{Cardoso:2018ptl} for the dimension-eight EFT.
-
-Here we will consider $\lame = \lamo = 1$ for simplicity in the cubic EFT, while in quartic,
-we will $\varepsilon_{1} = 1$ and $\varepsilon_{1,\,2} = 0$. This is the same subset of the EFT's parameter
-space studied in~\cite{Sennett:2019bpc}.
+where ${\cal C} = R_{\mu\nu\rho\sigma} R^{\mu\nu\rho\sigma}$,
+$\tilde{\cal C} = R_{\mu\nu\gamma\delta} \epsilon^{\mu\nu}{}_{\rho\sigma} R^{\rho\sigma\gamma\delta}$,
+and where $\lambda_{\rm o, e}$ and $\varepsilon_{i}$ ($i=1,2,3$) are dimensionless parameters.
+%
+Due to the large number of free parameters in this theory, we will work only with a subset of the theory's
+parameter space.
+%
+In particular, we will consider dimension-six and dimension-eight operators separately.
+%
+In the dimension-six case we further assume that $\lame = \lamo = 1$, leaving us with $\ell = \ell_{\rm cEFT}$
+as our single free parameter.
+%
+In the dimension-eight case, we will set $\varepsilon_{1} = 1$ and $\varepsilon_{2} = \varepsilon_{3} = 0$,
+as done in Ref.~\cite{Sennett:2019bpc}.
+%
+This leaves us with $\ell = \ell_{\rm qEFT}$ as our single free parameter.
+
+BHs in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} in the dimension-six EFT
+and in Refs.~\cite{Cardoso:2018ptl} in the dimension-eight EFT.
+%
+In general
 
@@
 BH mass and spin for it would
-%
 %

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: opening paragraph to methods sec

@@
 %
-Since the scalar field is coupled to a curvature scalar, the $Q$ is larger (smaller)
+Since the scalar field is coupled to a curvature scalar, $Q$ is larger (smaller)
 the smaller (larger) the BH's mass is.
@@
 
-BHs in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} in the dimension-six EFT
-and in Refs.~\cite{Cardoso:2018ptl} in the dimension-eight EFT.
-%
-In general
+In general \dots
+%
+\hs{Describe PN works.}
+
+The QNMs of nonrotating BHs where calculated in in Refs.~\cite{deRham:2020ejn,Cano:2020cao} in the dimension-six EFT
+and in Refs.~\cite{Cardoso:2018ptl,Cano:2020cao} in the dimension-eight EFT.
+%
+Ref.~\cite{Cano:2020cao} calculated the leading-order in BH spin corrections to the QNM spectra.
 
@@
 
+Having reviewed the modified gravity theories we will consider, we now present
+the frameworks upon which we will build our waveform model to confront these
+theories against GW observations.
+%
+We will start by reviewing the theory-agnostic parametrized ringdown
+spin-expansion coefficients (ParSpec) expansion in
+Sec.~\ref{sec:review_parspec}.
+%
+Next, in Sec.~\ref{sec:review_pSEOB}, we will review our full
+inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model we
+use~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we include the ParSpec
+expansion into it.
+%
+Finally, in Sec.~\ref{sec:theory_specific_qnm}, we show how we can map
+theory-specific QNM calculations in modified gravity theories onto the
+theory-agnostic free coefficients in the ParSpec expansion.
+%
+Ultimately, this provides with an IMR BBH waveform model, with the ringdown
+informed with QNM calculations in specific beyond-GR theories.
+
 \subsection{The parametrized ringdown spin expansion coefficients framework}
@@
 
-We start by reviewing the parametrized ringdown spin expansion coefficients (ParSpec)
+We start by reviewing the ParSpec
 framework introduced in Ref.~\cite{Maselli:2019mjd}, but following

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: cleaning text a bit

@@
 We will start by reviewing the theory-agnostic parametrized ringdown
-spin-expansion coefficients (ParSpec) expansion in
-Sec.~\ref{sec:review_parspec}.
-%
-Next, in Sec.~\ref{sec:review_pSEOB}, we will review our full
-inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model we
-use~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we include the ParSpec
-expansion into it.
+spin-expansion coefficients (ParSpec) expansion in Sec.~\ref{sec:review_parspec}.
+%
+Next, in Sec.~\ref{sec:review_pSEOB}, we will review the
+inspiral-(plunge)-merger-ringdown (IMR) BBH waveform
+model~\cite{Brito:2018rfr,Ghosh:2021mrv} we will use and explain how we modify
+it to include the ParSpec expansion.
 %
@@
 %
-Ultimately, this provides with an IMR BBH waveform model, with the ringdown
-informed with QNM calculations in specific beyond-GR theories.
+Ultimately, this provides us with an IMR BBH waveform model, with the ringdown
+portion of the model informed by QNM calculations in specific beyond-GR
+theories.
 

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
working on parspec section

@@
 some of the notation used in Ref.~\cite{Carullo:2021dui}.
-
-A general procedure to describe deviations from the Kerr QNM frequencies $\omega_{k}^{\rm Kerr}$ and
-damping times $\tau_{k}^{\rm Kerr}$ is to write,
+%
+A general procedure to describe deviations to the QNM frequencies $\omega_{k}^{\rm Kerr}$ and
+damping times $\tau_{k}^{\rm Kerr}$ of the GR Kerr BH is to write,
 %
@@
 %
-This approach was adopted, e.g., in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
+This type of parametrization was adopted, for instance, in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
 
@@
 (i) introduce deformation parameters which can be determined, once and for
-all, from a specific gravity theory, and
-%
-(ii) make it easy to combine constraints from multiple source.
-
-In the ParSpec framework this is accomplished by performing a bivariate
-expansion of Eq.~\eqref{eq:general_deviation} in the detector-frame mass and
-spin, namely
+all, from a specific gravity theory (GR included), and
+%
+(ii) make it simpler to combine constraints coming from multiple source.
+
+In the ParSpec expansion this is accomplished by performing a bivariate
+expansion of Eq.~\eqref{eq:general_deviation} in the detector-frame BH's mass
+$M$ and spin $\chi$, namely
 %
@@
 %
-where $M$ and $\chi$ are the detector-frame mass and dimensionless spin of the
-black hole; $\omega_{k}^{n}$, $\tau_{k}^{n}$ are dimensionless coefficients
-of the spin expansion for Kerr QNMs; $\delta\omega_{k}^{(n)}$, $\delta\tau_{k}^{(n)}$ are
-source-independent dimensionless coefficients that characterize the corrections to the Kerr QNM at each spin-order;
+where $\omega_{k}^{n}$ and $\tau_{k}^{n}$ are dimensionless coefficients of the
+expansion in spin for Kerr QNMs;
+%
+$\delta\omega_{k}^{(n)}$ and $\delta\tau_{k}^{(n)}$ are source-independent
+dimensionless coefficients that characterize the corrections to the Kerr QNM at
+each spin-order;
+%
 and finally $N_{\rm max}$ is the order of the spin expansion.

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: parspec review section

@@
 %
-Since the scalar field is coupled to a curvature scalar, $Q$ is larger (smaller)
+Since the scalar field is sourced by a curvature scalar, $Q$ is larger (smaller)
 the smaller (larger) the BH's mass is.
@@
 contribution), with magnitude proportional to the difference between the
-charges of binary components. This makes EdGB gravity testable with present GWs
+charges of binary components. This makes EdGB gravity testable with present GW
 observations of compact binaries where at least one component is a BH.
@@
 
-More specifically, we follow Refs.~\cite{Cano:2020cao,Cano:2021myl} and work up
-to dimension-eight operators ($n=4$),
+More specifically, we follow the notation of
+Refs.~\cite{Cano:2020cao,Cano:2021myl} and work up to dimension-eight operators
+($n=4$),
 %
@@
 %
-Due to the large number of free parameters in this theory, we will work only with a subset of the theory's
+Due to the large number of free parameters in this theory, we will focus on a subset of the theory's
 parameter space.
@@
 %
-All source dependence on the beyond-GR modification is encapsulated in the dimensionless
-parameter $\gamma$ given by,
+All source dependence on a given modified gravity theory is encapsulated in the
+dimensionless parameter $\gamma$, given by
 %
@@
 %
-which depends on the parameter $\ell$, with dimensions of length (and sets the
+which depends on a parameter $\ell$, with dimensions of length (and sets the
 lengthscale at which beyond-GR modifications become important), and
 the exponent $p$ which is related to how the beyond-GR modifications are
-included to the Einstein-Hilbert action.
+added to the Einstein-Hilbert action.
 %
@@
 
-In principle, a modification to GR would also affect $M$ and $\chi$ and the expansion should be written
-in terms of non-GR mass and spin, say $\bar{M}$ and $\bar{\chi}$. If we assume that the beyond-GR corrections
-are included perturbatively, the modifications to the BH mass and spin can be absorbed into the deviations
+In principle, a modification to GR would also affect $M$ and $\chi$ and the
+expansion should be written in terms of non-GR mass and spin, say $\bar{M}$ and
+$\bar{\chi}$. If we assume that the beyond-GR corrections are included perturbatively
+(as is the case for all theories described in Sec.~\ref{sec:review_theories}),
+the modifications to the BH mass and spin can be absorbed into the deviations
 parameters $\delta\omega$ and $\delta\tau$.
@@
 %
-\hs{TODO: say that we check a posteriori if our PE runs agree with this.}
-
-We remark that in the GR limit ($\gamma \to 0$)
-% where $\delta\omega_{k}^{(n)} = \delta\tau_{k}^{(n)} = 0$ $\forall\, n$,
+We will see that in Sec.~\ref{sec:pe} that this is assumption is indeed
+satisfied in our parameter estimation studies (cf.~Fig.~\ref{fig:corner_plot}).
+
+Finally, we remark that in the GR limit ($\gamma \to 0$)
 the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
@@
 can be found in Ref.~\cite{Maselli:2019mjd}, Table I.
+%
+The fitting coefficients for $N_{\rm max} = 9$, which extend the validity of
+the spin-expansion up to $\chi \lesssim 0.99$ where obtained in
+Ref.~\cite{Carullo:2021dui}.
 
@@
 translation between the metric perturbations $h_{\mu\nu}$ in the
-Regger-Wheeler-Zerilli gauge~\cite{Regge:1957td,Zerilli:1970se} and connect it with the transverse-traceless gauge
+Regge-Wheeler-Zerilli gauge~\cite{Regge:1957td,Zerilli:1970se} and connect it with the transverse-traceless gauge
 used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
@@
 \section{Parameter Inference}
+\label{sec:pe}
 \input{sec_pe}

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added pe section back to main tex file

@@
 
-%%%%%%%%%%%%%%%%%%%%%%
+% --------------------------------------------------------------------------------- %
 \section{Introduction}
 \label{sec:intro}
-%%%%%%%%%%%%%%%%%%%%%%
+% --------------------------------------------------------------------------------- %
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% --------------------------------------------------------------------------------- %
 \section{Overview of modified gravity theories}
 \label{sec:review_theories}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% --------------------------------------------------------------------------------- %
 
@@
 
-%%%%%%%%%%%%%%%%%%
+% --------------------------------------------------------------------------------- %
 \section{Methods}
 \label{sec:method}
-%%%%%%%%%%%%%%%%%%
+% --------------------------------------------------------------------------------- %
 
@@
 
-%%%%%%%%%%%%%%%%%
+% --------------------------------------------------------------------------------- %
 \section{Parameter Inference}
 \label{sec:pe}
-\input{sec_pe}
+% \input{sec_pe}
+% --------------------------------------------------------------------------------- %
+
+In this section, we provide a basic outline of the Bayesian formalism we use to
+infer the properties of the underlying GW signal, identify the most promising
+events from the catalog of GW observations to base our analyses on, and discuss
+the key insights they provide in constraining predictions of modified gravity
+theories.
+
+\subsection{Bayesian formalism}
+If we assume that a GW signal observed in detector data $d$ is accurately
+described by our waveform model \pSEOB{}, we can infer the parameters of the
+model, $\bm{\lambda}$, given the hypothesis $\mathcal{H}$, using Bayes' theorem,
+%
+\begin{equation}
+P(\bm{\lambda} \vert d, \mathcal{H}) =
+\frac{p(\bm{\lambda} \vert \mathcal{H}) \, \mathcal{L}(d \vert \bm{\lambda},\mathcal{H})}{E(d \vert \mathcal{H})}\,,
+\label{eq:bayes}
+\end{equation}
+%
+where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
+$p(\bm{\lambda} \vert \mathcal{H})$ the prior,
+$\mathcal{L}(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
+$E(d \vert \mathcal{H})$ the evidence.
+%
+The set of parameters, $\bm{\lambda}$ is a union of the GR waveform
+model parameters~$\bm{\theta}$ (c.f.  Sec.~\ref{sec:review_pSEOB}), and
+$\ell$,  the only non-GR parameter in this problem which, we recall, set
+the characteristic length-scale in which deviations from
+GR become relevant in each of the theories described in
+Sec.~\ref{sec:review_theories}. Hence,
+%
+\begin{equation}
+\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
+\label{eq:def_params}
+\end{equation}
+
+% As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
+% constants in the cases of EdGB and dCS theories, but two in the cubic and
+% quartic EFTofGR.
+% %
+% We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
+% fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
+% %
+
+Assuming stationary Gaussian noise, we can write the (log) likelihood function as,
+%
+\begin{equation}
+\ln \mathcal{L}(d \vert \bm{\lambda},\mathcal{H}) \propto
+- \tfrac{1}{2}
+\langle
+d - h(\bm{\lambda}) \vert d - h(\bm{\lambda})
+\rangle\,,
+\end{equation}
+%
+with noise-weighted inner product $\langle \cdot | \cdot \rangle$ defined as,
+%
+\begin{equation}
+\langle A | B \rangle =
+\int_{f_{\rm low}}^{f_{\rm high}} \, \dd f \,
+\frac{\tilde{A}^{\ast}(f) \tilde{B}(f) + \tilde{A}(f) \tilde{B}^{\ast}(f)}{S_{n}(f)}\,,
+\end{equation}
+%
+where $\tilde{A}(f)$ is the Fourier transform of $A(t)$, the asterisk denotes
+complex conjugation and $S_{n}(f)$ is the power spectrum density of the
+detector.
+%
+Assuming a specific prior distribution for our parameters (discussed further in the next section), we stochastically
+sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
+\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx},
+a package part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
+%
+We subsequently marginalize over the remaining parameters to obtain the
+posterior probability distribution function~(PDF) on $\ell$,  i.e., $P_j(\ell \vert d_j,\mathcal{H})$,
+our main parameter of interest.
+
+For $N$ independent GW observations $\{d_j\}$, $j=1,...,N$, each characterised
+by a posterior probability distribution $P_j(\ell \vert d_j,\mathcal{H})$, the
+joint posterior can be written as:
+%
+\begin{equation}
+P(\ell | \{d_j\}) = p(\ell) \prod_{j=1}^{N} \frac{P_j(\ell | d_j)}{p_j(\ell)}\,.
+\label{eq:cumulative_dist_ell}
+\end{equation}
+%
+where $p_j(\ell)$ are the priors used for each observation, and $p(\ell)$ is an overall prior.
+%
+Since we assume a uniform prior on $\ell$, the joint posterior is identically
+equal to the joint likelihood.
+%
+In some cases, we found it necessary to work with different prior ranges across
+different events, within the context of a given theory.
+%
+In this situation, when combining the posteriors we use chose as our overall
+prior the widest one among the individual events.
+
+\subsection{Priors}
+
+The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \sin\iota$.
+For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
+This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.
+%
+The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
+
+Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(n)}\delta \tau_k^{(n)}\}$,
+as already mentioned in the previous section, we hold $\{\delta \omega_k^{(n)}\}$
+and $\{\delta \tau_k^{(n)}\}$ fixed to theory-specific predictions, and allow only $\ell$
+to freely vary.
+%
+For such cases, we assume a prior uniform between appropriate ranges on $\ell$,
+making sure that our marginalized posterior distributions on $\ell$ do not rail
+over the maximum prior value on $\ell$.
+
+\subsection{Event selection}
+
+\begin{figure}[t]
+\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
+\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
+detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
+but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
+dCS gravity and $j=0$). The contours represent 90\% credible regions.
+%
+We see that the introduction of the non-GR parameters does not bias the
+inference on the source parameters.
+}
+\label{fig:corner_plot}
+\end{figure}
+
+The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an
+\emph{IMR} model which infers the properties of the underlying GW signal,
+including (independently) its ringdown properties, using the Bayesian formalism
+above. Naturally, the most promising candidates for our analyses are high-mass
+\emph{and} loud GW observations with a significant signal-to-noise ratio (SNR)
+in the post-merger part of the signal.
+%
+The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
+signals not all of which are relevant for a BH ringdown analysis. In fact, in
+an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM}
+analysis\footnote{See, in particular, Sec.VIII A.2
+in~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model
+presented in this paper, identified two events which provided the strongest
+bounds on measurements of the dominant $(220)$ QNM:
+GW150914~\cite{LIGOScientific:2016aoc} and
+GW200129~\cite{LIGOScientific:2021djp}.
+%
+These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are
+extremely similar in their source properties. These are also two of the loudest
+BBH signals observed to date with a total network SNR of XX and XX
+respectively.
+%
+Moreover, and what is more relevant for our analysis, is their post-inspiral
+(merger-ringdown) SNRs, which at XX and XX respectively (see the columns for
+$\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
+Table IV of~\cite{LIGOScientific:2021sio}).
+%
+In this paper, we are going to focus on these two GW events as our probes of
+the BH ringdown in modified theories of gravity.
+
+The parameter inference in this paper follows configurations identical to the
+ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
+Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector event (HL) while
+GW200129 was 3-detector (HLV).
+%
+We consequently use the same strain data $h(t)$, detector
+power-spectral-densities $S_n(f)$ and calibration envelopes as were used for
+the analyses in Ref.~\cite{LIGOScientific:2021sio}.
+%
+The only difference between the sampling configurations is that we do not
+sample over the fractional deviations in the $(220)$ QNM frequencies and
+damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
+and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions.
+%
+In the section to follow, we enumerate through the different theories and
+outline the highlight results. Whenever possible, we also combine results from
+multiple events to obtain the strongest possible bound on $\ell$.
+
+% -----------------
+% Corner plots here
+% -----------------
+
+As a first test ...
+\hs{Move to an appendix.}
+
+\subsection{General remarks on the interpretation of our results}
+\label{sec:remarks}
+
+There are two conditions that we must take into account before
+we can confidently claim to have placed a constraint, within our model's assumptions,
+with our parameter estimation study.
+
+First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
+consider must be considered as an effective field theory, meaning it should be
+considered valid only below an energy scale, or equivalently, a length scale.
+%
+As a cut-off length scale for the validity of the EFT we use,
+%
+\begin{equation}
+\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, G \mathfrak{m} / c^2 \,,
+\label{eq:def_cutoff}
+\end{equation}
+%
+where $\varepsilon$ is a dimensionless number and $\mathfrak{m}$ is the median
+value of one of the mass scales involved in the problem.
+%
+We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
+dimensions of length and hence can be compared to the coupling strength $\ell$.
+%
+In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
+but here we consider $\varepsilon \in [0, 1]$ for generality.
+%
+We will say that a bound has been placed on $\ell$, if most of the support of
+the posterior distribution function $P(\ell)$ is in the interval
+$[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
+%
+In practice, this can be quantified through the cumulative distribution function
+(CDF) associated with the marginalized posterior distribution $P(\ell)$, namely
+%
+\begin{equation}
+P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} P(\ell') \, \dd \ell'\,.
+\label{eq:def_cdf}
+\end{equation}
+%
+For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed on $\ell$ that
+%
+\begin{equation}
+% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
+P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
+\quad \textrm{(EFT bound)},
+\label{eq:eft_bound}
+\end{equation}
+%
+where we let $\ell_{\rm max} = \Lambda_{\rm EFT}$ in Eq.~\eqref{eq:def_cdf}, and
+likewise for other credibility percentiles.
+
+Second, as already emphasized in Ref.~\cite{Maselli:2019mjd}, the ParSpec
+formalism is by construction perturbative. This means that the non-GR
+deformation parameters are small, that is,
+%
+\begin{equation}
+\gamma \, \delta \omega^{(n)} \ll 1 \,,
+\,\, \textrm{and} \,\,
+\gamma \, \delta \tau^{(n)} \ll 1 \,, \quad \textrm{(ParSpec bound)},
+\label{eq:parspec_bound}
+\end{equation}
+%
+for all orders $n$ in the expansion in dimensionless spin $\chi$ and where $\gamma$
+is given by Eq.~\eqref{eq:def_gamma}.
+%
+We will also construct posterior distributions for these parameters and check if
+most of their support is concentrated to a domain with values much smaller than
+unity.
+
+Another question we must consider is the following: what is the mass $\mathfrak{m}$ that we should use
+in Eq.~\eqref{eq:def_cutoff}?
+%
+In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, which attempted to
+constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
+the GW signal alone, it was natural to chose the secondary's mass $m_2$ as the most
+conservative choice, since it is (by definition) the smallest mass and hence
+places the lowest cut-off scale $\Lambda_{\rm EFT}$ for the validity of either of these theories as an EFT.
+
+In our problem, the answer is not as clear. On the one hand, since we are
+interested in the ringdown part of the signal, it is natural to use the
+final mass $M_f$ to compute $\Lambda_{\rm EFT}$.
+%
+On the other hand, one may argue that the modified gravity theory under study
+should be able to predict a full inspiral, merger, and ringdown of the black
+hole binary before we can even make such a test, and thus the same, more conservative choice
+$\gm = m_2$ should be used.
+%
+Here we adopt an agnostic view to this question and consider \emph{both} masses, $m_2$ and $M_f$, to
+determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
+yield to different interpretations of the results of our parameter estimations.
 

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added comment on Nmax

@@
 %
-The fitting coefficients for $N_{\rm max} = 9$, which extend the validity of
-the spin-expansion up to $\chi \lesssim 0.99$ where obtained in
-Ref.~\cite{Carullo:2021dui}.
+In Ref.~\cite{Carullo:2021dui}, the fitting coefficients were calculated up to $N_{\rm max} = 9$,
+which extend the validity of the spin-expansion up to $\chi \lesssim 0.99$.
+%
+As we will discuss in Sec.~\ref{sec:pe}, the expansion to $N_{\rm max} = 4$ is
+sufficient for our purposes.
 

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: editing waveform model section

@@
 
-In this section we describe the waveform model used in our paper to measure properties of a BBH ringdown.
-As in \cite{Brito:2018rfr,Ghosh:2021mrv}, we use an inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model where the parameters describing the remnant object are left additionally free and estimated directly from the data.
-
-The GW signal from a BBH merger can be determined in GR by a unique set of parameters $\bm{\theta}$, that
-includes the masses and spins of the two BHs, $(m_1,\, m_2,\, \vec{s}_1,\, \vec{s}_2)$, the sky location determined by the luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$, and the orientation of the binary given by the inclination and polarization angles, $(\iota, \psi)$.
-The set is completed by the choice of a reference time and phase, $(t_0,\, \phi_0)$.
-If we further assume that the spins of the individual BHs are restricted to be parallel to the orbital angular momentum, then we reduce the 6 components of spin to just 2, $(\chi_1, \chi_2)$ and our entire parameter set from 15 to 11.
-We define some additional parameters and set some conventions that will be useful in our analysis later, namely, the totat mass $M=m_1+m_2$, the chirp mass $\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$, the asymmetric mass ratio $q=m_1/m_2$ with the convention $m_1 \geqslant m_2; q \geqslant 1$ and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
-
-The polarization of the GW signal (in the observer's frame) are,
+We now describe the waveform model used in our paper to measure properties of a
+BBH ringdown.
+%
+As in Refs.~\cite{Brito:2018rfr,Ghosh:2021mrv}, we use an IMR BBH waveform
+model where the parameters describing the remnant object are left additionally
+free and estimated directly from the data.
+
+The GW signal from a BBH merger can be determined in GR by a unique set of
+parameters $\bm{\theta}$, that includes the masses and spins of the two BHs,
+$(m_1,\, m_2,\, \vec{s}_1,\, \vec{s}_2)$, the sky location determined by the
+luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$,
+and the orientation of the binary given by the inclination $\iota$ and polarization $\psi$
+angles.
+%
+The set is completed by the choice of a reference time $t_0$ and phase
+$\phi_0$. If we further assume that the spins of the individual BHs are
+restricted to be parallel to the orbital angular momentum, we reduce the six
+components of spin to just two, $(\chi_1, \chi_2)$ and our entire parameter set
+from 15 to 11.
+%
+Let us also define some additional parameters and set some conventions that
+will be useful in our analysis later, namely, the total mass
+%
+$M=m_1+m_2$,
+%
+the chirp mass
+%
+$\mathcal {M}=(m_{1}m_{2})^{3/5}/(m_{1}+m_{2})^{1/5}$,
+%
+the asymmetric mass ratio $q=m_1/m_2$, with the convention $m_1 \geqslant m_2$ (thus $q \geqslant 1$),
+and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
+
+The polarization of the GW signal (in the observer's frame) is,
 %
@@
 %
-where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical harmonics described by standard angular dependence indices $(l,m)$.\footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.} As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in \cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform model is available in \texttt{LALSuite} \cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
-%
-The model uses an effective-one-body (EOB) approach combined with a post-adiabatic solution of the equations of motion to describe the inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
-An accurate description of the merger is incorporated through calibration with NR simulations, as described in~\cite{Cotesta:2018fcv}, along with information for the merger and ringdown phases, from BH perturbation theory.
-The merger-ringdown waveform, $h_{l m}^\mathrm{merger-RD}$, is then stitched to inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$ at a certain time $t = t^{\textrm{match}}_{l m}$, as
-%
-\begin{equation}
-h_{l m}(t) = h_{l m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{l m} - t) + h_{l m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{match}^{l m})\,,
-\end{equation}
-%
-where $\theta(t)$ is the Heaviside step function. The merger-ringdown waveform is expressed as an exponentially damped sinusoid~\citep{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
+where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical
+harmonics described by standard angular dependence indices $l$ and $m$.
+%
+% --------------------------------
+% HS: maybe not necessary anymore:
+% \footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.}
+% --------------------------------
+%
+As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in Ref.~\cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
+%
+The model uses an effective-one-body (EOB) approach combined with a
+post-adiabatic solution of the equations of motion to describe the
+inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
+%
+An accurate description of the merger is incorporated through calibration with
+NR simulations, as described in Ref.~\cite{Cotesta:2018fcv}, along with
+information for the merger and ringdown phases, from BH perturbation theory.
+The merger-ringdown waveform, $h_{l m}^\mathrm{merger-RD}$, is then stitched to
+inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$ at a certain time $t = t^{\textrm{match}}_{l m}$, as
+%
+\begin{equation}
+h_{l m}(t) =
+h_{l m}^\textrm{insp-plunge}\, \theta(t_\textrm{match}^{l m} - t)
++ h_{l m}^\textrm{merger-RD}\,\theta(t-t_\textrm{match}^{l m})\,,
+\end{equation}
+%
+where $\theta(t)$ is the Heaviside step function.
+%
+The merger-ringdown waveform is expressed as an exponentially damped
+sinusoid~\cite{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
 %
@@
 \label{RD}
-h_{l m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{l m}(t)\ e^{i \tilde{\phi}_{l m}(t)} \ e^{-i \sigma_{l m 0}(t-t^{\textrm{match}}_{l m})},
+h_{l m}^{\textrm{merger-RD}}(t) = \nu \ \tilde{A}_{l m}(t)\ e^{i \tilde{\phi}_{l m}(t)} \ e^{-i \sigma_{l m 0}(t-t^{\textrm{match}}_{l m})}\,,
 \end{equation}
@@
 \begin{align}
-\sigma_{l m 0} &= {\rm Re}(\sigma_{l m 0}) + i \, {\rm Im}(\sigma_{l m 0})\,,
-\nonumber \\
-&= \omega_{l m 0} - i / \tau_{l m 0}\,,
+\sigma_{l m 0} = {\rm Re}(\sigma_{l m 0}) + i \, {\rm Im}(\sigma_{l m 0})
+= \omega_{l m 0} - i / \tau_{l m 0}\,,
 \end{align}
@@
 %
-The functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l m}(t)$ are defined in~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
-
-In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies $\sigma_{l m 0}$ are computed by first determining the final mass and spin from estimates of the initial masses and spins through NR--fitting--formulas~\cite{Taracchini:2013rva,Hofmann:2016yih} and then converting them to the complex frequencies using BH perturbation theory--inspiral analytical fits outlined in~\cite{Berti:2005ys,Berti:2009kk}.
+The functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l m}(t)$ are defined
+in Ref.~\cite{Bohe:2016gbl,Cotesta:2018fcv}.
+
+In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies
+$\sigma_{l m 0}$ are computed by first determining the final mass and spin from
+estimates of the initial masses and spins through NR-fitting-formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}
+and then converting them to the complex frequencies using BH perturbation
+theory-inspiral analytical fits~\cite{Berti:2005ys,Berti:2009kk}.
+%
 Hence,
@@
 QNM predictions in baseline \SEOB{} model.
-%
+
 In this paper, however, we introduce a completely different expression of the
 QNM frequencies $(\omega_{l m 0}, \tau_{l m 0})$, as a series expansion on the
-spin of the remnant object $\chi_f$ [see Eqs.~\eqref{eq:kerr_expansion}].
+spin of the remnant object $\chi_f$ as we described in Sec.~\ref{sec:review_parspec}; cf.~Eqs.~\eqref{eq:kerr_expansion}.
 %
@@
 
-In this formalism our QNM frequencies are expressed through functions,
+Following the ParSpec expansion, our QNM frequencies are expressed through functions,
 %
@@
 where we fixed a certain value of $p$, and the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict
-the final mass and spin $(M_f,\, \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
+the final BH mass $M_f$ and spin $\chi_f$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
 %
@@
 %
-Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$
+Additionally, both $\omega_k$ and $\tau_k$ depend on the coupling constant $\ell$
 defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: a bit more text

@@
 paper, we infer bounds on our beyond-GR parameters for specific cases of
-modified gravity theories outlined in Sec.~\ref{sec:review_theories}. We detail
-these results in Sec.~\ref{sec:results}.
+modified gravity theories presented Sec.~\ref{sec:review_theories}.
+%
+We detail these results in Sec.~\ref{sec:results}.
 %

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added comment to ab; moved variable-p idea to conclusions

@@
 In this case, the theory admits the same stationary, asymptotically flat BH
-solution of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
+solutions of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
 %
@@
 %
-\hs{Describe PN works.}
+\hs{Alessandra, can you include a short description of~\cite{Sennett:2019bpc} for the quartic EFT?}
 
@@
 %
-All source dependence on a given modified gravity theory is encapsulated in the
+All source dependence on a given modified gravity theory is contained in the
 dimensionless parameter $\gamma$, given by
@@
 
-% \hs{TODO: in figures and tables use $N_{\rm max} = 0$ ($N_{\rm max} = 1$) instead of $j=0$ ($j=0,1$).}
-
 \subsection{The parametrized waveform model}
@@
 
-We now describe the waveform model used in our paper to measure properties of a
+We now describe the waveform model used in our paper to infer properties of a
 BBH ringdown.
@@
 %
-As our baseline model, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in Ref.~\cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
+As our baseline model, that is, the GR model upon which non-GR modifications will be added to, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in Ref.~\cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
 %
@@
 information for the merger and ringdown phases, from BH perturbation theory.
-The merger-ringdown waveform, $h_{l m}^\mathrm{merger-RD}$, is then stitched to
-inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$ at a certain time $t = t^{\textrm{match}}_{l m}$, as
+The merger-ringdown waveform, $h_{l m}^\textrm{merger-RD}$, is then stitched to
+inspiral-plunge waveform, $h_{l m}^\textrm{insp-plunge}$ at a certain time $t = t^{\textrm{match}}_{l m}$, as
 %
@@
 \begin{align}
-\omega_{l m 0}^{\text{GR}} &= \omega_{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,\\
-\tau _{l m 0}^{\text{GR}} &= \tau _{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,.
+\omega_{l m 0}^{\text{GR}} &= \omega_{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
+\\
+\tau _{l m 0}^{\text{GR}} &= \tau _{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
 \end{align}
@@
 the final BH mass $M_f$ and spin $\chi_f$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-%
-% HS: we implicitly fixed p here. Could we leave it free in PE study. This is similar
-% to the 'number of dimensions'-like studies. Here it would tells us quite generically
-% what is the dimension of the modification to the EH-action we include!
 %
@@
 
+% ------------------------------------------------------------------------------------
+% HS: we fixed p in our work. We could leave it free in future studies study.
+% This is similar to the 'number of dimensions'-like studies. Here it would
+% tells us quite generically what is the dimension of the modification to the
+% EH-action we include!
+% ------------------------------------------------------------------------------------
+
 \appendix

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: editing result section for cubic eft

@@
 function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
-(middle panel), with (dashed line) and without (solid line) spin corrections to
+(middle panel), with (purple line) and without (black line) spin corrections to
 dominant $(2,2,0)$~QNM.
@@
 
-We now consider the cubic EFT of GR, a case in which our results bear
-similarity with what we found in dCS.
+We now consider the cubic EFT of GR.
+%
+In Fig.~\ref{fig:cEFT_exec_sum} we show the marginalized posterior distributions
+functions of $\ell_{\rm cEFT}$ for GW150914 (top panel) and GW200129 (middle panel),
+with black (purple) curve corresponding to $N_{\rm max} = 0$ ($N_{\rm max} = 1$) in
+the spin expansion.
+%
+We find that in this theory, the posterior distributions are mostly uniform for
+$\ell_{\rm cEFT} \lesssim 40$~km (contrast this with the EdGB and dCS gravity
+cases; cf.~Figs.~\ref{fig:edgb_exec_sum} and~\ref{fig:dCS_exec_sum}).
+%
+For values $\ell_{\rm cEFT} \gtrsim 40$~km, the posteriors smoothly approach zero.
+
+In Fig.~\ref{fig:cEFT_cdf} we show the cumulative distribution functions for
+both events, calculated as done in EdGB and dCS cases.
+%
+We see that curves are very similar to those of dCS gravity for GW200129 (cf.
+bottom panel in Fig.~\ref{fig:cEFT_cdf}).
+%
+We find that for both events both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound}
+bounds are satisfied for $\mathfrak{m} = M_f$ and $N_{\rm max} = 1/2$, allowing us to obtain the
+combined bound from both events
+%
+\begin{equation}
+    \ell_{\rm cEFT} \leqslant 51.3~\textrm{km},
+\end{equation}
+%
+at 90\% credibility. As also happened for our study for dCS, the find that for
+the cubic EFT that the ParSpec bound is violated by the $n = 1$ corrections to
+the QNMs, implying that we cannot use the associated posterior distributions on
+$\ell_{\rm cEFT}$ to draw any meaningful constraint on this parameter.
 
@@
 %
-In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
+In all panels, we use purple (black) lines correspond to the inclusion (or not) of the linear
 in spin QNM correction.
-%
-\hs{TODO}
 }
@@
 
-\begin{table}[h]
+\begin{table}[b]
 \begin{tabular}{l l c c c}

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: emphasized diff between us and carullo

@@
 In this paper, we will restrict ourselves to corrections to the $n=0$ and
-$n=1$ terms, i.e., leading and next-to-leading order corrections to the spin,
-$\chi_f$.
+$n=1$ terms, that is, only up to the leading-order in spin $\chi_f$ term.
 
@@
 %
-\hs{Should we call this waveform differently to distinguish it from your previous papers?}
+\hs{Alessandra, Abhirup, should we call this waveform differently to distinguish it from your previous papers?}
 %
@@
 M \omega_{k} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
-+ \sum_{n=0}^{N_{\rm max}} \chi^{j} \omega^{j}\,,
++ \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)}\,,
 \\
 \tau_{k}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
-+ \sum_{n=0}^{N_{\rm max}} \chi^{(n)} \tau^{(n)}\,,
++ \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}\,,
 \end{align}
@@
 Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell$,
-$\delta\omega^{(n)}$ and $\delta\tau^{(n)}$ parameters.
+$\delta\omega^{(n)}$, and $\delta\tau^{(n)}$ parameters, and then proceeded
+to use the posteriors on $\ell$ to draw conclusions to any theory that predict
+corrections at a given $p$.
+%
+This is a critical different between our study and Ref.~\cite{Carullo:2021dui}.
+In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
+information to the ParSpec expansion \emph{can lead to different interpretation
+of the final results, even for different theories which predict modifications
+with the exponent $p$.}
 
@@
 function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
-(middle panel), with (purple line) and without (black line) spin corrections to
+(middle panel), with different colors distinguishing cases with and without spin corrections to
 dominant $(2,2,0)$~QNM.

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more editing on comp with gc

@@
 %
-This is a critical different between our study and Ref.~\cite{Carullo:2021dui}.
+This is a critical difference between our work and Ref.~\cite{Carullo:2021dui}.
 In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
-information to the ParSpec expansion \emph{can lead to different interpretation
-of the final results, even for different theories which predict modifications
-with the exponent $p$.}
-
-As we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating
-BHs is modified gravity theories come in two families depending on their
-transformation upon a parity transformation: axial and polar. Which is the one
-we use to match against Eqs.~\eqref{eq:qnm_nongr_iso}?
-%
-To answer this question one has to work with a chosen theory and perform a
-translation between the metric perturbations $h_{\mu\nu}$ in the
-Regge-Wheeler-Zerilli gauge~\cite{Regge:1957td,Zerilli:1970se} and connect it with the transverse-traceless gauge
-used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
-%
-In GR, both axial and polar QNMs are the same (a property known as \emph{isospectrality}) and therefore which
-QNM we use to model the ringdown makes no difference.
-%
-In beyond-GR theories, isospectrality is in general broken (see the discussion
-in Ref.~\cite{Hui:2021cpm} for a counterexample).
-%
-Thus, how axial and polar gravitational QNMs appear in the GW signal has to be
-answered on theory-by-theory basis.
-%
-This is outside the scope of this paper and here we take the more pragmatic
-approach of simply choosing the \emph{least damped gravitational mode between
-the two parities.}
-%
-The justification is this is the mode (if excited during the merger) which is
-the most likely to appear in the signal.
-
-We performed the mapping between theory-specific QNM calculation and the ParSpec framework
-under the hypothesis above for the theories listed in Sec.~\ref{sec:review_theories}.
-%
-We summarize our result in Table~\ref{tab:ref_theories_qnms} and
-leave the details of our calculations to Appendix~\ref{app:map_details}.
+information to the ParSpec expansion coefficients \emph{can lead to different interpretations
+of the final bounds on $\ell$, even for different theories which predict value of the exponent $p$.}
 
@@
 \end{table}
+
+As we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating
+BHs is modified gravity theories come in two families depending on their
+transformation upon a parity transformation: axial and polar. Which is the one
+we use to match against Eqs.~\eqref{eq:qnm_nongr_iso}?
+%
+To answer this question one has to work with a chosen theory and perform a
+translation between the metric perturbations $h_{\mu\nu}$ in the
+Regge-Wheeler-Zerilli gauge~\cite{Regge:1957td,Zerilli:1970se} and connect it with the transverse-traceless gauge
+used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
+%
+In GR, both axial and polar QNMs are the same (a property known as \emph{isospectrality}) and therefore which
+QNM we use to model the ringdown makes no difference.
+%
+In beyond-GR theories, isospectrality is in general broken (see the discussion
+in Ref.~\cite{Hui:2021cpm} for a counterexample).
+%
+Thus, how axial and polar gravitational QNMs appear in the GW signal has to be
+answered on theory-by-theory basis.
+%
+This is outside the scope of this paper and here we take the more pragmatic
+approach of simply choosing the \emph{least damped gravitational mode between
+the two parities.}
+%
+The justification is this is the mode (if excited during the merger) which is
+the most likely to appear in the signal.
+
+We performed the mapping between theory-specific QNM calculation and the ParSpec framework
+under the hypothesis above for the theories listed in Sec.~\ref{sec:review_theories}.
+%
+We summarize our result in Table~\ref{tab:ref_theories_qnms} and
+leave the details of our calculations to Appendix~\ref{app:map_details}.
 

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more edits

@@
 %
-On the other hand, one may argue that the modified gravity theory under study
-should be able to predict a full inspiral, merger, and ringdown of the black
-hole binary before we can even make such a test, and thus the same, more conservative choice
-$\gm = m_2$ should be used.
+On the other hand, one may argue that the modified gravity theory being
+consideration should be able to predict a full inspiral, merger, and ringdown
+of the black hole binary before we can even make such a test, and thus the
+same, more conservative choice $\gm = m_2$ should be used.
 %
@@
 
-\subsection{cubic effective-field-theory of general relativity}
+\subsection{Cubic Effective-Field-Theory of General Relativity}
 \label{sec:results_ceft}
@@
 
-\subsection{quartic effective-field-theory of general relativity}
+\subsection{Quartic Effective-Field-Theory of General Relativity}
 \label{sec:results_qeft}

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: minor corrections

@@
 functions of $\ell_{\rm cEFT}$ for GW150914 (top panel) and GW200129 (middle panel),
-with black (purple) curve corresponding to $N_{\rm max} = 0$ ($N_{\rm max} = 1$) in
+with different curve colors corresponding to different $N_{\rm max}$ in
 the spin expansion.
@@
 In Fig.~\ref{fig:cEFT_cdf} we show the cumulative distribution functions for
-both events, calculated as done in EdGB and dCS cases.
+both events, calculated as already described for the EdGB and dCS cases.
 %
@@
 %
-We find that for both events both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound}
-bounds are satisfied for $\mathfrak{m} = M_f$ and $N_{\rm max} = 1/2$, allowing us to obtain the
-combined bound from both events
+Moreover, we find that for both events both the EFT~\eqref{eq:eft_bound} and
+ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for $\mathfrak{m} = M_f$
+and $N_{\rm max} = 1/2$, allowing us to obtain the combined bound
 %

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: filled xx in events description; improved prior discussion

@@
 %
-For such cases, we assume a prior uniform between appropriate ranges on $\ell$,
-making sure that our marginalized posterior distributions on $\ell$ do not rail
-over the maximum prior value on $\ell$.
+We assume an uniform prior between appropriate ranges on $\ell$,
+say $\ell \in [0, \ell_{\rm max}]$.
+%
+The lower limit is set by the fact the modified gravity theories we consider
+all have $p$ even and hence we can assume $\ell > 0$ without loss of
+generality.
+%
+The upper limit is chosen as to make sure that our marginalized posterior
+distributions on $\ell$ do not rail against $\ell_{\rm max}$.
 
@@
 %
-These two events, with a total mass of $XX \Mo$ and $XX \Mo$ respectively, are
+These two events, with a total mass of $65 \Mo$ and $63.4 \Mo$ respectively, are
 extremely similar in their source properties. These are also two of the loudest
-BBH signals observed to date with a total network SNR of XX and XX
+BBH signals observed to date with a total network SNR of 24 and 26.8
 respectively.
@@
 Moreover, and what is more relevant for our analysis, is their post-inspiral
-(merger-ringdown) SNRs, which at XX and XX respectively (see the columns for
+(merger-ringdown) SNRs, which at 16.1 and 16 respectively (see the columns for
 $\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
@@
 \begin{equation}
-P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} P(\ell') \, \dd \ell'\,.
+P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
 \label{eq:def_cdf}
@@
 \includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
-\caption{(Color online).~The cumulative distribution function evaluated at the
+\caption{(Color online).~The CDF evaluated at the
 cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
@@
 horizontal lines lay at 0.68 and 0.90. We see that in no situation the curves pass
-through the 0.68 or 0.90 lines even at $\varepsilon = 1$. This means that no bound on $\ell_{\rm GB}$
-can be placed with the events we analyzed.
+through the 0.68 or 0.90 lines even at $\varepsilon = 1$.
+%
+This means that no bound on $\ell_{\rm GB}$ can be placed with the events we
+analyzed.
 }
@@
 
-As we emphasized in Sec.~\ref{sec:remarks}, before drawing any conclusions on
-the allowed values for $\ell_{\rm GB}$ from our parameter estimations, we
-must first check whether the ``EFT''~\eqref{eq:eft_bound} and
-``ParSpec''~\eqref{eq:parspec_bound} bounds are satisfied.
+As we emphasized in Sec.~\ref{sec:remarks}, we must first check whether the
+``EFT''~\eqref{eq:eft_bound} and ``ParSpec''~\eqref{eq:parspec_bound} bounds
+are satisfied, before drawing any conclusions on the allowed values for
+$\ell_{\rm GB}$ from our parameter estimations
 %
 We check the validity of the EFT bound in Fig.~\ref{fig:edgb_cdf}. In the top (bottom) panel we show
-the cumulative density function of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
-evaluating the integral~\eqref{eq:def_cdf} with $\Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
+the CDF of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
+by evaluating the integral~\eqref{eq:def_cdf} with $\ell_{\rm max} = \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
 with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
@@
 past $0.2$, regardless of the mass scale $\mathfrak{m}$ used and even at $\varepsilon =
-1$. This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
+1$, at which the EFT description of the theory would not be valid anyway.
+%
+This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
 never met at a significant credibility and thus that we cannot place a bound on
@@
 
-Let us place our results in a broader context. In particular, let us contrast
-them against those of Ref.~\cite{Lyu:2022gdr} which placed the bound
-%
-$\ell_{\rm GB} \leqslant 1.33$~km
-%
-using the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt}, and
-of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound
-%
-$\ell_{\rm GB} \leqslant 1.7$~km,
-%
-by stacking the posterior of $\ell_{\rm GB}$ from a  selection of black hole binaries from the GWTC-1 and GWTC-2 catalogs
-with at least one relatively low-mass binary component~\cite{}\footnote{These bounds
-are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and
-take into consideration only the leading-order scalar field contribution arising from the dilatonic coupling.}.
-%
-These works use the \emph{inspiral} portion of GW event only and a constraint
-on EdGB gravity can be obtained because black holes in this theory carry a
-monopole scalar charge which in turn can source dipolar scalar radiation,
-that affects the GW phase at $-1$PN order, relative to the dominant GR contribution, and
-is proportional to the difference between the charges of binary components.
-%
-Now, the magnitude of the scalar charge scales roughly with the inverse of the black hole's mass squared, that is,
-smaller (larger) back holes carry large (smaller) scalar charges. Qualitatively, this is because the scalar field
-is sourced by the Gauss-Bonnet curvature invariant, which is large for black holes with small masses.
-%
-Beyond-GR corrections to the inspiral are, by construction, not present in our
-waveform model and constitutes a important ingredient to be added in forthcoming
-versions of the model.
-%
-In addition to the larger mass (which suppresses the black hole's charge), the
-QNM of EdGB gravity differ very little from GR as observed in~\cite{Blazquez-Salcedo:2016enn}.
-%
-Hence, here we have an example of a theory in which the inspiral portion of the signal
-is more constraining then the ringdown portion of the signal.
+Our result contrasts with those of Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}
+which relied on the BBH inspiral to constrain $\ell_{\rm GB}$, as discussed in Sec.~\ref{sec:review_edgb}.
+%
+We see that EdGB provides an example of a theory in which the inspiral portion
+of the signal is more constraining then the ringdown portion of the signal.
+%
+Two reasons together can explain our negative results. First, as observed by
+Ref.~\cite{Blazquez-Salcedo:2016enn}, the QNMs of EdGB BHs only differ slightly
+from their Schwarzschild counterparts. Second, the larger mass $M_f$ of the
+remnant BH, suppresses scalar field's charge relatively to the initial binary
+components.~\hs{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
+Point this out in the conclusions after all specific theories are discussed.}
 %
 As we will next, the situation is the opposite for dCS gravity.
+
+% Let us place our results in a broader context. In particular, let us contrast
+% them against those of Ref.~\cite{Lyu:2022gdr} which placed the bound
+% %
+% $\ell_{\rm GB} \leqslant 1.33$~km
+% %
+% using the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt}, and
+% of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound
+% %
+% $\ell_{\rm GB} \leqslant 1.7$~km,
+% %
+% by stacking the posterior of $\ell_{\rm GB}$ from a  selection of black hole binaries from the GWTC-1 and GWTC-2 catalogs
+% with at least one relatively low-mass binary component~\cite{}\footnote{These bounds
+% are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and
+% take into consideration only the leading-order scalar field contribution arising from the dilatonic coupling.}.
+% %
+% These works use the \emph{inspiral} portion of GW event only and a constraint
+% on EdGB gravity can be obtained because black holes in this theory carry a
+% monopole scalar charge which in turn can source dipolar scalar radiation,
+% that affects the GW phase at $-1$PN order, relative to the dominant GR contribution, and
+% is proportional to the difference between the charges of binary components.
+% %
+% Now, the magnitude of the scalar charge scales roughly with the inverse of the black hole's mass squared, that is,
+% smaller (larger) back holes carry large (smaller) scalar charges. Qualitatively, this is because the scalar field
+% is sourced by the Gauss-Bonnet curvature invariant, which is large for black holes with small masses.
+% %
+% Beyond-GR corrections to the inspiral are, by construction, not present in our
+% waveform model and constitutes a important ingredient to be added in forthcoming
+% versions of the model.
+% %
+% In addition to the larger mass (which suppresses the black hole's charge), the
+% QNM of EdGB gravity differ very little from GR as observed in~\cite{Blazquez-Salcedo:2016enn}.
+% %
+% Hence, here we have an example of a theory in which the inspiral portion of the signal
+% is more constraining then the ringdown portion of the signal.
+%
+% As we will next, the situation is the opposite for dCS gravity.
 
@@
 \includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
-\caption{(Color online).~The cumulative distribution function evaluated at the
-cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$ as a function of the parameter $\varepsilon$ for both
-$\gm = m_2$ (solid and dashed lines) and $\gm = M_{f}$ (dot-dashed and dotted lines) without
-(blue lines) and with (orange lines) linear-in-spin QNM corrections.
-The horizontal lines lay at 0.68 and 0.90.
+\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for dCS gravity.
+% The cumulative distribution function evaluated at the
+% cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$ as a function of the parameter $\varepsilon$ for both
+% $\gm = m_2$ (solid and dashed lines) and $\gm = M_{f}$ (dot-dashed and dotted lines) without
+% (blue lines) and with (orange lines) linear-in-spin QNM corrections.
+% The horizontal lines lay at 0.68 and 0.90.
 %
@@
 
-We now turn our attention to dCS gravity.
+We now consider dCS gravity.
 %
@@
 
-In Fig.~\ref{fig:dcs_cdf} we show the cumulative distribution function,
+In Fig.~\ref{fig:dcs_cdf} we show the CDF
 obtained from Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT} (\varepsilon, \gm)$,
@@
 
-In Fig.~\ref{fig:cEFT_cdf} we show the cumulative distribution functions for
+In Fig.~\ref{fig:cEFT_cdf} we show the CDF for
 both events, calculated as already described for the EdGB and dCS cases.
@@
 %
-In all panels, we use purple (black) lines correspond to the inclusion (or not) of the linear
-in spin QNM correction.
+The colors distinguish different $N_{\rm max}$ in the spin expansion.
 }
@@
 \includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold.pdf}
-\caption{
+\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for the cubic EFT of GR.
+We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
+1/2$ for both events, with and without including the $n = 1$ corrections to
+the dominant QNM.
 }

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: comment on corner plot in event selection sec

@@
 manifests into a coupling between scalar perturbation and gravitational
-perturbations of polar parity, which, e.g., breaks the familiar equivalence
+perturbations of polar parity, which, e.g., breaks the equivalence
 between the QNM spectra of polar and axial gravitational perturbations
-(isospectrality) of Schwarzschild BHs in GR.
+(isospectrality~\cite{Chandrasekhar:1985kt}) of Schwarzschild BHs in GR.
 %
@@
 
-The QNMs of the Schwarzschild BH in dCS gravity where studied in Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb},
-that found that scalar perturbations and gravitational perturbations of axial parity couple. (Contrast with EdGB gravity).
+The QNMs of the Schwarzschild BH in dCS gravity where studied in
+Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb}, that found that scalar
+perturbations and gravitational perturbations of axial parity couple. (Contrast
+with EdGB gravity).
 %
@@
 information to the ParSpec expansion coefficients \emph{can lead to different interpretations
-of the final bounds on $\ell$, even for different theories which predict value of the exponent $p$.}
+of the final bounds on $\ell$, even for different theories which predict the same value of the exponent $p$.}
 
@@
 Regge-Wheeler-Zerilli gauge~\cite{Regge:1957td,Zerilli:1970se} and connect it with the transverse-traceless gauge
-used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Sec. xxx),
+used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Chapter~12),
 %
@@
 %
-In beyond-GR theories, isospectrality is in general broken (see the discussion
+In beyond-GR theories, isospectrality is in general broken (see
 in Ref.~\cite{Hui:2021cpm} for a counterexample).
@@
 Thus, how axial and polar gravitational QNMs appear in the GW signal has to be
-answered on theory-by-theory basis.
+answered on a theory-by-theory basis.
 %
@@
 as already mentioned in the previous section, we hold $\{\delta \omega_k^{(n)}\}$
-and $\{\delta \tau_k^{(n)}\}$ fixed to theory-specific predictions, and allow only $\ell$
-to freely vary.
+and $\{\delta \tau_k^{(n)}\}$ fixed to theory-specific predictions, and allow only $\ell$ to freely vary.
 %
@@
 damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
-and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions.
-%
-In the section to follow, we enumerate through the different theories and
+and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions, summarized
+in Table~\ref{tab:ref_theories_qnms}.
+%
+In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
+detector-frame remnant mass $(1 + z) M_f$ for GW150914 for GR and the
+illustrative case of dCS gravity. We see that our waveform models does not
+introduce a substantial change to the GR estimates on this parameters, as
+required by the ParSpec expansion (see discussion in
+Sec.~\ref{sec:review_parspec}).
+
+In Sec.~\ref{sec:results}, we will enumerate through the different theories and
 outline the highlight results. Whenever possible, we also combine results from
@@
 
-As a first test ...
-\hs{Move to an appendix.}
+% As a first test ...
+% \hs{Move to an appendix.}
 
@@
 
-There are two conditions that we must take into account before
-we can confidently claim to have placed a constraint, within our model's assumptions,
-with our parameter estimation study.
+There are two conditions that we must verify before we can confidently claim to
+have placed a constraint, within our model's assumptions, with our parameter
+estimation study.
 
@@
 consider must be considered as an effective field theory, meaning it should be
-considered valid only below an energy scale, or equivalently, a length scale.
-%
-As a cut-off length scale for the validity of the EFT we use,
+considered valid only below an energy scale, or equivalently, a lengthscale.
+%
+As a cut-off lengthscale for the validity of the EFT we use,
 %
@@
 \begin{equation}
-P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
+% P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
+% HS: changed lower limit to zero since we don't have support for negative \ell-values
+P(\ell \leqslant \ell_{\rm max}) = \int_{0}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
 \label{eq:def_cdf}
@@
 %
-For instance, we will demand that for a bound with 90\% credibility to be meaningfully placed on $\ell$ that
+For instance, we will require that for a bound with 90\% credibility to be placed on $\ell$ that
 %
@@
 for all orders $n$ in the expansion in dimensionless spin $\chi$ and where $\gamma$
-is given by Eq.~\eqref{eq:def_gamma}.
+was defined in Eq.~\eqref{eq:def_gamma}.
 %
@@
 In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, which attempted to
-constrain dCS and shift-symmetric sGB theories with the \emph{inspiral} part of
+constrain dCS and EdGB theories with the \emph{inspiral} part of
 the GW signal alone, it was natural to chose the secondary's mass $m_2$ as the most
-conservative choice, since it is (by definition) the smallest mass and hence
+conservative choice, since it is by definition the smallest component mass and hence
 places the lowest cut-off scale $\Lambda_{\rm EFT}$ for the validity of either of these theories as an EFT.
@@
 %
-Here we adopt an agnostic view to this question and consider \emph{both} masses, $m_2$ and $M_f$, to
-determine $\Lambda_{\rm EFT}$. We will then compare how different assumptions
-yield to different interpretations of the results of our parameter estimations.
+Here we adopt a pragmatic approach to this issue and consider \emph{both}
+masses, $m_2$ and $M_f$, to determine $\Lambda_{\rm EFT}$.
+%
+We will then compare how different assumptions yield to different
+interpretations of the results of our parameter estimations.
 

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs:terse text on qeft

@@
 \includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
-GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-%
-In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
-in spin QNM correction.
+\caption{(Color online).~Similar to Fig.~\ref{fig:dCS_exec_sum}, but for dCS gravity.
+%
+% ~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
+% GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+% %
+% In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
+% in spin QNM correction.
 %
@@
 %
-These stronger bound are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
+These stronger bounds are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
 for GW200129 (compare the top and middle panels in Fig.~\ref{fig:dCS_exec_sum}), and in part due to
 the smaller median remnant ($M_{f} \approx 59.5\msun$ versus $M_{f} \approx 61.8\msun$ for GW150914).
+%
+\hs{Should we remove these and just quote the 90\% results?}
 
@@
 
-Finally, let us consider the quartic EFT of GR.
+At last, let us consider the quartic EFT of GR.
+%
+In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
+GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR
+%
+We find that both the ``EFT''~\eqref{eq:eft_bound} and ``ParSpec''~\eqref{eq:parspec_bound} are satisfied,
+hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
+%
+As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_f$ before $\varepsilon = 1/2$.
+%
+Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
+%
+\begin{equation}
+    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km}\,.
+\end{equation}
+%
 
@@
 GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-%
-In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
-in spin QNM correction.
-%
-\hs{TODO}
 }
@@
 combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
-%
-\hs{Need to debug $N_{\rm max} = 1$ runs.}
-%
 }
@@
 %
-In contrast, we could place any constraint of the coupling constants in EdGB gravity $\ell_{\rm GB}$.
+In contrast, we could not place any constraint of the coupling constants in EdGB gravity $\ell_{\rm GB}$.
 %

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: removed waveform name comment

@@
 %
-\hs{Alessandra, Abhirup, should we call this waveform differently to distinguish it from your previous papers?}
+% \hs{Alessandra, Abhirup, should we call this waveform differently to distinguish it from your previous papers?}
 %
@@
 %
-In GR, both axial and polar QNMs are the same (a property known as \emph{isospectrality}) and therefore which
-QNM we use to model the ringdown makes no difference.
+In GR, both axial and polar QNMs are isospectral and hence which QNM we use to
+model the ringdown makes no difference.
 %

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: darboux refs and quartic eft text

@@
 The coupling between scalar field and the Gauss-Bonnet invariant, which
-manifests into a coupling between scalar perturbation and gravitational
+result into a coupling between scalar perturbation and gravitational
 perturbations of polar parity, which, e.g., breaks the equivalence
 between the QNM spectra of polar and axial gravitational perturbations
-(isospectrality~\cite{Chandrasekhar:1985kt}) of Schwarzschild BHs in GR.
+(isospectrality~\cite{Chandrasekhar:1985kt}, see also Refs.~\cite{Glampedakis:2017rar,Lenzi:2021njy}) of Schwarzschild BHs in GR.
 %
@@
 \begin{equation}
-    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{\rm s}}\right)^4\,.
+    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{f}}\right)^4\,.
 \end{equation}
@@
 \begin{equation}
-    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm CS}}{G M_{\rm s}} \right)^{4}\,,
+    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm CS}}{G M_{f}} \right)^{4}\,,
 \end{equation}
@@
 %
-We also see that in both cases, that the inclusion leading-order-in-spin
-correction to the mode, displaces the posteriors towards smaller values of
+We also see that in both cases that the inclusion leading-order-in-spin
+correction to the mode displaces the posteriors towards smaller values of
 $\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
@@
 $\ell_{\rm cEFT}$ to draw any meaningful constraint on this parameter.
+%
+We summarize our results in Table~\ref{tab:summary_ceft}.
 
@@
 
+In this theory, we considered only $N_{\rm max} = 0$. We found that the
+inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 50$~km
+with ringdowns portions of the larger than the inspiral-plunge part \dots
+%
+To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but at doing so we obtained which
+were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
+%
+Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
+
 \begin{figure}[t]
@@
   & Combined &     &      & \cellcolor{black!10}$\ell_{\rm qEFT} \leqslant 51.3$~km \\
-\hline
-  & GW150914 &  &     &    \\
-1 & GW200129 &  &     &    \\
-  & Combined &  &     &    \\
+% \hline
+%   & GW150914 &  &     &    \\
+% 1 & GW200129 &  &     &    \\
+%   & Combined &  &     &    \\
 \hline

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: small edits on qeft
hs: edits in results section

@@
 Using this parameterized waveform model, which we will call $\pSEOB$ in this
-paper, we infer bounds on our beyond-GR parameters for specific cases of
+paper, we infer bounds on our non-GR parameter $\ell$ for specific cases of
 modified gravity theories presented Sec.~\ref{sec:review_theories}.
@@
 
-Our result contrasts with those of Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}
+We can compare this conclusion with that of Ref.~\cite{Carullo:2021dui}, which obtained $\ell_{\rm GB} \lesssim 35$~km,
+by setting $p=4$, \emph{but not} including theory-specific QNM information on $\delta \omega^{(n)}$ and $\delta \tau^{(n)}$.
+%
+Our results provide a concrete example of the importance of including
+theory-specific QNM calculations information into the parameter estimation
+and how this can dramatically change the outcome of the results.
+
+Let us also contrasts our results with those of Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}
 which relied on the BBH inspiral to constrain $\ell_{\rm GB}$, as discussed in Sec.~\ref{sec:review_edgb}.
@@
 
-In Fig.~\ref{fig:cEFT_cdf} we show the CDF for
-both events, calculated as already described for the EdGB and dCS cases.
+In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
+same way as already described for the EdGB and dCS theories.
 %
@@
 %
-Moreover, we find that for both events both the EFT~\eqref{eq:eft_bound} and
-ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for $\mathfrak{m} = M_f$
-and $N_{\rm max} = 1/2$, allowing us to obtain the combined bound
-%
-\begin{equation}
-    \ell_{\rm cEFT} \leqslant 51.3~\textrm{km},
+Moreover, we find that the EFT~\eqref{eq:eft_bound} and
+ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
+$\mathfrak{m} = M_f$ and $N_{\rm max} = 1/2$.
+%
+This allows us to place the combined bound of
+%
+\begin{equation}
+    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km}\,,
 \end{equation}
@@
 the cubic EFT that the ParSpec bound is violated by the $n = 1$ corrections to
-the QNMs, implying that we cannot use the associated posterior distributions on
-$\ell_{\rm cEFT}$ to draw any meaningful constraint on this parameter.
+the QNMs, meaning that we cannot use this case to draw any meaningful
+constraint on this parameter.
 %
@@
 
-At last, let us consider the quartic EFT of GR.
+Let us now consider the quartic EFT of GR as our final example.
 %
@@
 \end{equation}
-%
 
@@
 %
-To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but at doing so we obtained which
-were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
+To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
+which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
 %
@@
 \includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
-\caption{
+\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
+We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
+can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_f$ for both events at 90\% credibility.
 }
@@
 \caption{Detailed summary of our results the quartic EFT of GR for GW150914, GW200129, and
-combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+combined events using $\gm = M_{f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$. The quoted
+result correspond to 90\% credible values.
 }

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: gamma gb plot

@@
     \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{f}}\right)^4\,.
-\end{equation}
-%
-As shown in Fig.~xxx, $\gamma_{\rm GB}$ does indeed have a posterior
+    \label{eq:def_gamma_gb}
+\end{equation}
+%
+As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm GB}$ does indeed have a posterior
 distribution with largest support at zero, indicating consistency between data
@@
 \label{fig:edgb_exec_sum}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{figs/edgb_gamma.pdf}
+\caption{(Color online).~Posterior distribution function on the dimensionless parameter $\gamma_{\rm GB}$,
+defined in Eq.~\eqref{eq:def_gamma_gb}. We see that this parameter controls the ParSpec expansion in EdGB gravity
+does have maximum support at $\gamma_{\rm GB} = 0$. This shows that our model is consistent with GR.
+}
+\label{fig:gamma_gb}
 \end{figure}
@@
 %
-does indeed peak at zero indicating consistency with GR, similarly to what is shown in Fig.~\ref{} for $\gamma_{\rm GB}$.
+does indeed peak at zero indicating consistency with GR, similarly to what is shown in Fig.~\ref{fig:gamma_gb} for $\gamma_{\rm GB}$.
 %
@@
 In this theory, we considered only $N_{\rm max} = 0$. We found that the
-inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 50$~km
-with ringdowns portions of the larger than the inspiral-plunge part \dots
+inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
+for which the ringdown portions of the larger than the inspiral-plunge part \dots
 %
@@
 Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
+%
+\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ are breaking down other than
+we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}
 

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: fig refing

@@
 \includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
-\caption{(Color online).~Similar to Fig.~\ref{fig:dCS_exec_sum}, but for dCS gravity.
+\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for dCS gravity.
 %
@@
 %
-We stress that posteriors obtained including $n=1$ corrections, violated conditions~\eqref{eq:parspec_bound}
+We stress that posteriors obtained including $n=1$ corrections, violate conditions~\eqref{eq:parspec_bound}
 and therefore should not be used to draw meaningful conclusions. We show them for illustrative purposes
@@
 In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
-GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR
-%
-We find that both the ``EFT''~\eqref{eq:eft_bound} and ``ParSpec''~\eqref{eq:parspec_bound} are satisfied,
+GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR.
+%
+We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
 hence allowing us to infer bounds on $\ell_{\rm qEFT}$.

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: missing k subs

@@
 \begin{align}
-M \omega_{k} &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
-+ \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)}\,,
+    M \omega_{k} &= \gamma \left( \delta\omega^{(0)}_{k} \omega^{(0)}_{k} + \chi \delta\omega^{(1)}_{k} \omega^{(1)}_{k} \right)
+    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)}_{k} \,,
 \\
-\tau_{k}/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
-+ \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}\,,
+    \tau_{k}/M   &= \gamma \left( \delta\tau^{(0)}_{k} \tau^{(0)}_{k} + \chi \delta\tau^{(1)}_{k} \tau^{(1)}_{k} \right)
+    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}_{k}\,,
 \end{align}
@@
 %
-\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ are breaking down other than
+\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ simulations are breaking down other than
 we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: comment on robustness of n=0 results

@@
 to fix $p$, $\delta\omega^{(n)}$, and $\delta\tau^{(n)}$.
+%
+Because QNMs of rotating BHs in modified gravity theories are not known to
+all spin values, we can expect that the $n=1$ coefficients to be susceptible to
+changes as calculations beyond-leading order in spin are accomplished.
+%
+That is not the case for the $n=0$ coefficients and the situation is the same as in GR,
+in which the $n=0$ coefficients are simply the QNMs of the Schwarzschild BH.
 

### 2022-04-05 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: minor change
hs: txt

@@
 
-This means that using the $\pSEOB$ waveform model with theory-specific informed
-QNMs we reduce the parameter space of beyond-GR parameters to $\ell$ alone.
+In the end, the $\pSEOB$ waveform model with theory-specific informed
+QNMs has only $\ell$ as a free beyond-GR parameter.
 %
@@
 are compensated by the assumptions that $(\ell_{\rm CS} / M_f)^2$ and $\chi$ are much less than unity. These
-are the assumptions use to calculate the QNM frequencies both in Ref.~\cite{Wagle:2021tam}.
+are the assumptions used to calculate the QNM frequencies in Ref.~\cite{Wagle:2021tam}.
 

### 2022-04-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section II.B

@@
 % Comment commands
-\newcommand{\ag}[1]{{\textcolor{cyan}{{[AG: #1]}} }}
+\usepackage{xcolor}
+\newcommand{\agcomm}[1]{{\textcolor{red}{{[AG: #1]}} }}
+\newcommand{\ag}[1]{{\textcolor{Maroon}{{#1}} }}
 \newcommand{\hs}[1]{{\textcolor{blue}{{[HS: #1]}} }}
@@
 We start by briefly reviewing the modified gravity theories we consider in this
-paper, what are the currents observational constraints and what we do know
-about BH QNMs in each of them.
+paper, what the current observational constraints are and what we know
+about BH QNMs in each of these theories.
 
@@
 - 4 R^{\mu\nu}R_{\mu\nu}
-+ R^2$,
-%
-where $R_{\mu\nu\rho\sigma}$ and $R_{\mu\nu}$ are respectively the Riemann and Ricci tensors.
++ R^2$.
+%
+$R_{\mu\nu\rho\sigma}$ and $R_{\mu\nu}$ are the Riemann and Ricci tensors respectively.
 %
@@
 %
-It can however contribute to the field equation when coupled to $\varphi$, as
-done through the coupling function $f(\varphi)$. The strength of the coupling is
+However,  when coupled to $\varphi$, it can contribute to the field equation
+through the coupling function $f(\varphi)$. The strength of the coupling is
 set by $\ell_{\rm GB}$, with dimensions of length.
@@
 Different subclasses of this theory are determined by the function $f(\varphi)$
-and they can be classified into two classes based on the properties of their BH
+and can be divided into two classes based on the properties of their BH
 solutions.
@@
 In this case, the theory admits the same stationary, asymptotically flat BH
-solutions of GR and scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
+solutions as GR and those of scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
 %
@@
 the quadratic $f(\varphi) \propto \varphi^2$~\cite{Silva:2017uqg} coupling functions.
-
 BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
-related to the asymptotic $r^{-1}$ fall-off of the scalar field.
+related to the asymptotic $r^{-1}$\agcomm{In most of these cases $r$ might be intuitive, but just wanted to leave this comment to remind myself that we never define it explicitly.} fall-off of the scalar field.
 %
@@
 %
-Since the scalar field is sourced by a curvature scalar, $Q$ is larger (smaller)
-the smaller (larger) the BH's mass is.
+Since the scalar field is sourced by a curvature scalar, $Q$ is larger (smaller), 
+ smaller (larger) the BH mass is.
 
@@
 take into account only the leading-order scalar field contribution arising from the dilatonic coupling.}.
-
-Second, the scalar field does influence the response of BHs to linearized perturbations and thus
-affects the BH's QNM spectra.
+Secondly, the scalar field does influence the response of BHs to linearized perturbations and thus
+affects the BH QNM spectra.
 %
 The coupling between scalar field and the Gauss-Bonnet invariant, which
-result into a coupling between scalar perturbation and gravitational
-perturbations of polar parity, which, e.g., breaks the equivalence
+result in a coupling between scalar perturbations and gravitational
+perturbations of polar parity can, for example break the equivalence
 between the QNM spectra of polar and axial gravitational perturbations
-(isospectrality~\cite{Chandrasekhar:1985kt}, see also Refs.~\cite{Glampedakis:2017rar,Lenzi:2021njy}) of Schwarzschild BHs in GR.
-%
-The QNMs on nonrotating BHs in EdGB gravity were first computed in
-Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and these calculations were
+(isospectrality~\cite{Chandrasekhar:1985kt}, see also Refs.~\cite{Glampedakis:2017rar,Lenzi:2021njy}) for Schwarzschild BHs in GR.
+%
+
+The QNMs for nonrotating BHs in EdGB gravity were first computed in
+Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and were
 extended to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
@@
 %
-where $\vartheta$ is a pseudoscalar field, which couples to the Pontryagin
+where $\vartheta$ is a pseudoscalar field which couples to the Pontryagin
 density
@@
 %
-where ${}^{*}R^{\mu\nu\rho\sigma}$ is the dual of the Riemann tensor,
+where ${}^{*}R^{\mu\nu\rho\sigma}$ is the dual of the Riemann tensor
 defined as
@@
 %
-and where $\epsilon_{\mu\nu\gamma\delta}$ is the Levi-Civita tensor.
-%
-As in scalar-Gauss-Bonnet theories, $\int \dV {}^{*}RR$ alone is a boundary
-term~\cite{Jackiw:2003pm}, thus does not contribute to the field equations in
+and $\epsilon_{\mu\nu\gamma\delta}$ is the Levi-Civita tensor.
+%
+As in scalar-Gauss-Bonnet theories, $\int \dV {}^{*}RR$ by itself is a boundary
+term~\cite{Jackiw:2003pm} that does not contribute to the field equations in
 four-dimensions.
 %
-However, this terms can modify the theory's field equation by coupling it to
-$\vartheta$.
+However, a coupling with $\vartheta$ can modify the field equations.
 %
@@
 
-The theory admits as solution the garden-variety Schwarzschild BH of GR. This
-is not case when rotation is included and the Kerr metric is not a solution of
+The theory admits as a solution, the garden-variety Schwarzschild BH of GR. This
+is not the case when rotation is included and the Kerr metric is not a solution of
 the theory~\cite{Jackiw:2003pm}.
 %
-These rotating BHs support a scalar field which falls-off as
+These rotating BHs support a scalar field which fall off as
 $r^{-2}$ asymptically, to which we can associate a scalar dipole
@@
 As a consequence, the leading-scalar radiative channel of BBH to lose energy is quadrupolar,
-which affects the GW phase at 2PN order~\cite{Yagi:2011xp,Alexander:2017jmt}.
+which affects the GW phase at 2PN order~\cite{Yagi:2011xp,Alexander:2017jmt}.\agcomm{I am not sure I understand this sentence.}
 %
 Deviations from GR at this PN order are poorly constrained with present GW
-observations~\cite{LIGOScientific:2021sio}, making dCS gravity unconstrained by
+observations~\cite{LIGOScientific:2021sio}\agcomm{might want to quantify what we mean by poor.
+Looking at Table VI of the reference, I see that the 90\% credible bounds are $\sim 1-0\%$ using the hierarchical approach and $\sim 50\%$ using the restricted approach for $\varphi_4$.
+Perhaps we want to mention this?}, making dCS gravity unconstrained by
 analyses that rely on the inspiral portion of GWs from BBH
@@
 %
-by folding data from the x-ray observations of the isolated neutron star (NS)
+by folding data from the X-ray observations of the isolated neutron star (NS)
 PSR~J0030+0451~\cite{Lommen:2000yt,NANOGrav:2017wvv} by
@@
 
-The QNMs of the Schwarzschild BH in dCS gravity where studied in
+The QNMs of the Schwarzschild BH in dCS gravity were studied in
 Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb}, that found that scalar

### 2022-04-07 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section II.C

@@
 Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb}, that found that scalar
-perturbations and gravitational perturbations of axial parity couple. (Contrast
-with EdGB gravity).
-%
-This yields in a breakdown of isospectrality. The QNM spectra of slowly-rotating BHs in dCS gravity was
+perturbations couple to gravitational perturbations of axial parity. (Contrast
+with EdGB gravity)\agcomm{Is the text in parenthesis a comment?}.
+%
+This leads to a breakdown of isospectrality. The QNM spectra of slowly-rotating BHs in dCS gravity was
 studied in Ref.~\cite{Wagle:2021tam}.
@@
 %
-where $\ell$ is a lengthscale, assumed to be small compares to the lengthscale
-associated with a BH, i.e., $\ell / M \ll 1$, and $L^{(2n)}$ are corrections to
+where $\ell$ is a length-scale assumed to be small compared to the length-scale
+$\ell / M \ll 1$ associated with a BH and $L^{(2n)}$ are corrections 
 that introduce higher-order curvature tensors (with $2n$ metric derivatives).
@@
 $\tilde{\cal C} = R_{\mu\nu\gamma\delta} \epsilon^{\mu\nu}{}_{\rho\sigma} R^{\rho\sigma\gamma\delta}$,
-and where $\lambda_{\rm o, e}$ and $\varepsilon_{i}$ ($i=1,2,3$) are dimensionless parameters.
-%
-Due to the large number of free parameters in this theory, we will focus on a subset of the theory's
-parameter space.
+and $(\lambda_{\rm o, e},\varepsilon_{i})$,  $i=1,2,3$, are dimensionless parameters.
+%
+Due to the large number of free parameters in this theory, we will focus on a subset of the parameter space.
 %
@@
 %
-This leaves us with $\ell = \ell_{\rm qEFT}$ as our single free parameter.
+This leaves us with $\ell = \ell_{\rm qEFT}$ as our single free parameter \agcomm{Perhaps a bit of motivation about why we make these choices, even if it is to say that it is a simple first choice?}.
 
@@
 
-The QNMs of nonrotating BHs where calculated in in Refs.~\cite{deRham:2020ejn,Cano:2020cao} in the dimension-six EFT
+The QNMs of nonrotating BHs where calculated in Refs.~\cite{deRham:2020ejn,Cano:2020cao} in the dimension-six EFT
 and in Refs.~\cite{Cardoso:2018ptl,Cano:2020cao} in the dimension-eight EFT.
 %
-Ref.~\cite{Cano:2020cao} calculated the leading-order in BH spin corrections to the QNM spectra.
+Ref.~\cite{Cano:2020cao} calculated the leading-order BH spin corrections to the QNM spectra.
 

### 2022-04-07 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section III.A

@@
 Having reviewed the modified gravity theories we will consider, we now present
-the frameworks upon which we will build our waveform model to confront these
-theories against GW observations.
-%
-We will start by reviewing the theory-agnostic parametrized ringdown
-spin-expansion coefficients (ParSpec) expansion in Sec.~\ref{sec:review_parspec}.
-%
-Next, in Sec.~\ref{sec:review_pSEOB}, we will review the
-inspiral-(plunge)-merger-ringdown (IMR) BBH waveform
-model~\cite{Brito:2018rfr,Ghosh:2021mrv} we will use and explain how we modify
+the sequential building blocks for the waveform model we use to test these theories
+against GW observations.
+%
+We start by reviewing the theory-agnostic parametrized ringdown
+spin-expansion coefficients (ParSpec) \sout{expansion} \ag{framework} \agcomm{replaced `framework' to prevent duplication.
+The original parspec authors call this a data-analysis framework, so I think it would be safe to use it.
+I have left the term ``ParSpec expansion" in other places, because ParSpec is always abbreviated in those places.} in Sec.~\ref{sec:review_parspec}.
+%
+Next, in Sec.~\ref{sec:review_pSEOB}, we review our baseline
+parametrized inspiral-(plunge)-merger-ringdown (IMR) BBH waveform
+model~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we modify
 it to include the ParSpec expansion.
@@
 %
-where $\delta\omega_{k}$ and $\delta\tau_{k}$ are the deformation parameters.
+where $\delta\omega_{k}$ and $\delta\tau_{k}$ are the fractional deformation parameters.
 %
@@
 
-A caveat of parametrizations of the form~\eqref{eq:general_deviation}, is that
-$\delta\omega_{k}$ and $\delta\tau_{k}$ depend, in general, on the BH's source mass and spin.
-%
-Ideally, one would like to explicitly reinstate the dependence the source-frame
-BH mass and spin for it would
+\ag{The current LIGO-Virgo-Kagra tests of BH ringdown (see Sec.VII.A of~\cite{LIGOScientific:2020tif} or Sec.VIII.A of~\cite{LIGOScientific:2021sio}) take a restrictive theory-agnostic approach towards the inference of $\delta\omega_{k}$ and $\delta\tau_{k}$.
+These deviations are either assumed to occur identically across all observed sources or belong to a generic underlying Gaussian population.
+A more realistic scenario, however, is that these parameters depend on the source BH's mass and spin.}
+\sout{A caveat of parametrizations of the form~\eqref{eq:general_deviation}, is that
+$\delta\omega_{k}$ and $\delta\tau_{k}$ depend, in general, on the BH's source mass and spin.}
+%
+Ideally, one would like to explicitly reinstate \sout{the dependence the source-frame
+BH mass and spin} \ag{this dependence} for it would
 %
@@
 %
-(ii) make it simpler to combine constraints coming from multiple source.
-
-In the ParSpec expansion this is accomplished by performing a bivariate
+(ii) make it simpler to combine constraints coming from multiple \ag{(independently observed)} sources.
+
+ParSpec is such an observable-based
+\sout{In the ParSpec expansion this is accomplished by performing a} bivariate
 expansion of Eq.~\eqref{eq:general_deviation} in the detector-frame BH's mass
-$M$ and spin $\chi$, namely
+$M$ and spin $\chi$, \sout{namely}
 %
@@
 %
-where $\omega_{k}^{n}$ and $\tau_{k}^{n}$ are dimensionless coefficients of the
+where $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$ are dimensionless coefficients of the
 expansion in spin for Kerr QNMs;
@@
 %
-and finally $N_{\rm max}$ is the order of the spin expansion.
+and $N_{\rm max}$ is the order of the spin expansion.
 %
@@
 which depends on a parameter $\ell$, with dimensions of length (and sets the
-lengthscale at which beyond-GR modifications become important), and
+length-scale at which beyond-GR modifications become important), and
 the exponent $p$ which is related to how the beyond-GR modifications are
@@
 %
-In Eq.~\eqref{eq:def_gamma} we made $\ell$ dimensionless by using the other
-lenghtscale associated to the remnant black hole, i.e., its source-frame mass
+In Eq.~\eqref{eq:def_gamma} we made \sout{$\ell$} \ag{$\gamma$} dimensionless  by using the other
+length-scale associated with the remnant black hole, i.e., its source-frame mass
 $M_{\rm s}$, which we can also write in terms of the detector-frame mass $M$ through
-the redshift $z$~\cite{Krolak:1987ofj}.
+the redshift $z$~\cite{Krolak:1987ofj}. \ag{Also, dividing by the factor $G/c^2$ allows us to
+express $\ell$ in physically intuitive metric units.}
 
 In principle, a modification to GR would also affect $M$ and $\chi$ and the
-expansion should be written in terms of non-GR mass and spin, say $\bar{M}$ and
+expansion should be written in terms of the non-GR mass and spin, say $\bar{M}$ and
 $\bar{\chi}$. If we assume that the beyond-GR corrections are included perturbatively
-(as is the case for all theories described in Sec.~\ref{sec:review_theories}),
+(as is the case of all theories described in Sec.~\ref{sec:review_theories}),
 the modifications to the BH mass and spin can be absorbed into the deviations
@@
 %
-This means we can identify the $M$ and $\chi$ with their \emph{corresponding GR values}.
-%
-We will see that in Sec.~\ref{sec:pe} that this is assumption is indeed
+This means we can identify the $M$ and $\chi$ with their \emph{corresponding GR values}
+\footnote{\ag{For a more detailed discussion, see Appendix A in ~\cite{Maselli:2019mjd}.}}.
+%
+We will see that in Sec.~\ref{sec:pe} that this assumption is indeed
 satisfied in our parameter estimation studies (cf.~Fig.~\ref{fig:corner_plot}).
@@
 The values of the fitting coefficients $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$
-can be found in Ref.~\cite{Maselli:2019mjd}, Table I.
+can be found in Ref.~\cite{Maselli:2019mjd}, Table I\agcomm{This sentence would need
+to be adapted if we put the GR coefficients in our current Table II.}.
 %

### 2022-04-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section III

@@
 where $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$ are dimensionless coefficients of the
-expansion in spin for Kerr QNMs;
+expansion in spin for Kerr QNMs\footnote{\ag{From this point onwards, to prevent ambiguity,
+we will use $n$ to denote the series expansion index, and not the spherical 
+harmonic overtone.}};
 %
@@
 length-scale associated with the remnant black hole, i.e., its source-frame mass
-$M_{\rm s}$, which we can also write in terms of the detector-frame mass $M$ through
+$M_{\rm s}$\footnote{\ag{Throughout this paper, we maintain the convention of 
+using the subscript ``s" to denote source-frame quantities and plain baseline 
+symbols for detector-frame measurements.}} which we can also write in terms of the detector-frame mass $M$ through
 the redshift $z$~\cite{Krolak:1987ofj}. \ag{Also, dividing by the factor $G/c^2$ allows us to
@@
 %
-the asymmetric mass ratio $q=m_1/m_2$, with the convention $m_1 \geqslant m_2$ (thus $q \geqslant 1$),
+the asymmetric mass ratio $q=m_1/m_2$, with the convention $m_1 \geqslant m_2$ (and thus $q \geqslant 1$),
 and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
@@
 where ${}_{-\!2}Y_{l m}(\iota,\varphi_0)$ are the $-2$ spin-weighted spherical
-harmonics described by standard angular dependence indices $l$ and $m$.
+harmonics.
 %
@@
 %
-As our baseline model, that is, the GR model upon which non-GR modifications will be added to, we use the computationally efficient (time-domain) multipolar waveform model for quasicircular spin-aligned BBH mergers described in Ref.~\cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
+As our baseline model, that is, the GR model upon which non-GR modifications 
+will be added, we use the computationally efficient (time-domain) multipolar 
+waveform model for quasicircular spin-aligned BBH mergers described in 
+Ref.~\cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform 
+model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA} 
+waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, 
+and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
 %
@@
 h_{l m}(t) =
-h_{l m}^\textrm{insp-plunge}\, \theta(t_\textrm{match}^{l m} - t)
-+ h_{l m}^\textrm{merger-RD}\,\theta(t-t_\textrm{match}^{l m})\,,
-\end{equation}
-%
-where $\theta(t)$ is the Heaviside step function.
+h_{l m}^\textrm{insp-plunge}\, \Theta(t_\textrm{match}^{l m} - t)
++ h_{l m}^\textrm{merger-RD}\,\Theta(t-t_\textrm{match}^{l m})\,,
+\end{equation}
+%
+where $\Theta(t)$ is the Heaviside step function \agcomm{Changed $\theta(t)$ to $\Theta(t)$,
+because $\theta$ was already used to denote the parameter space.}.
 %
@@
 %
-are the complex frequencies of the fundamental ($n=0$ overtone) QNMs of the remnant BH.
-%
-The frequencies $\omega_{l m 0}$ and damping times $\tau_{l m 0}$ of the $(l,
-m)$ QNM can be read off from the real and imaginary parts of $\sigma_{l m 0}$
-respectively.
+are the complex frequencies of the fundamental ($0$-th overtone) QNMs of the remnant BH.
+%
+\ag{Going back to the convention established above to use the index $k$ to now denote the $(l, m,0)$
+mode,  the frequencies $\omega_k$ and damping times $\tau_k$ can be read off from the 
+real and imaginary parts of $\sigma_k$ respectively.}
 %
@@
 In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies
-$\sigma_{l m 0}$ are computed by first determining the final mass and spin from
+$\sigma_k$ are computed by first determining the final mass and spin from
 estimates of the initial masses and spins through NR-fitting-formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}
 and then converting them to the complex frequencies using BH perturbation
-theory-inspiral analytical fits~\cite{Berti:2005ys,Berti:2009kk}.
+theory-inspired analytical fits~\cite{Berti:2005ys,Berti:2009kk}.
 %
@@
 \begin{align}
-\omega_{l m 0}^{\text{GR}} &= \omega_{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
+\omega_k^{\text{GR}} &= \omega_k^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
 \\
-\tau _{l m 0}^{\text{GR}} &= \tau _{l m 0}^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
+\tau _k^{\text{GR}} &= \tau _k^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
 \end{align}
@@
 %
-where $(\omega_{l m 0}^{\text{GR}}, \tau_{l m 0}^{\text{GR}} )$ refer to the
-QNM predictions in baseline \SEOB{} model.
-
-In this paper, however, we introduce a completely different expression of the
-QNM frequencies $(\omega_{l m 0}, \tau_{l m 0})$, as a series expansion on the
-spin of the remnant object $\chi_f$ as we described in Sec.~\ref{sec:review_parspec}; cf.~Eqs.~\eqref{eq:kerr_expansion}.
-%
-For the rest of the paper, in keeping with the conventions introduced in
-Sec.~\ref{sec:review_parspec}, we are going to use the index $k$ to refer to
-$(l, m,n=0)$ mode. Accordingly, we are going to use $(\omega_k, \tau _k)$ to
-refer to $(\omega_{l m 0}, \tau _{l m 0})$ respectively.
-
-Following the ParSpec expansion, our QNM frequencies are expressed through functions,
+where $(\omega_k^{\text{GR}}, \tau_k^{\text{GR}} )$ refer to the
+GR QNM predictions in the baseline \SEOB{} model.
+
+\ag{In this paper, we replace these GR predictions with QNM 
+frequencies defined through the ParSpec expansion introduced in 
+Sec.~\ref{sec:review_parspec}; cf.~Eqs.~\eqref{eq:kerr_expansion}. Hence,}
 %
@@
 \begin{align}
-\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\}),\\
-\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\}),
+\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(n)}\}),\\
+\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(n)}\}),
 \end{align}
@@
 %
-where we fixed a certain value of $p$, and the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict
-the final BH mass $M_f$ and spin $\chi_f$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
-%
-Additionally, both $\omega_k$ and $\tau_k$ depend on the coupling constant $\ell$
-defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta
-\omega_k^{(n)}\},$ and $\{\delta \tau_k^{(n)}\}$, where $n$ ranges from zero to
-the power of spin in Eqs.~\eqref{eq:kerr_expansion} up to which we include
-corrections.
-%
-For example, if we restrict ourselves to corrections with $n=0$, or
+\ag{where the mass and spin of the remnant object $(M_f,\chi_f)$ are themselves functions of
+$(m_1,\, m_2,\, \chi_1,\, \chi_2)$ (through~\cite{Taracchini:2013rva,Hofmann:2016yih}), and we fix $p$
+to a certain theory-specific value. Additionally,  the frequencies depend on the ParSpec coefficients $\{\delta
+\omega_k^{(n)},\delta \tau_k^{(n)}\}$,  and the coupling constant $\ell$.}
+
+\sout{For example, if we restrict ourselves to corrections with $n=0$, or
 $\chi_f^0$, to the $k=(2,2,0)$ mode only, then we would just have two
@@
 In this paper, we will restrict ourselves to corrections to the $n=0$ and
-$n=1$ terms, that is, only up to the leading-order in spin $\chi_f$ term.
+$n=1$ terms, that is, only up to the leading-order in spin $\chi_f$ term.}
 
@@
 
-Let us now establish the connection between theory-agnostic framework of the
-$\pSEOB$ waveform model and the theory-specific QNM calculations.
-%
-We begin by rewriting $\omega_{k}$ and $\tau_{k}$, given by Eqs.~\eqref{eq:kerr_expansion} as,
+Let us now establish the connection between the theory-agnostic \agcomm{or independent?} framework of the
+$\pSEOB$ waveform model and the theory-specific QNM calculations.  \ag{In this paper we will restrict ourselves to
+corrections to the leading and next-to-leading order terms in the ParSpec expansion, as well as the fundamental 
+$k = \{2,\, 2,\, 0\}$ QNM. For this reason,  we will omit the subscripts $k$ hereafter 
+and rewrite $\omega$ and $\tau$, given by} Eqs.~\eqref{eq:kerr_expansion} as,
 %
@@
 \begin{align}
-    M \omega_{k} &= \gamma \left( \delta\omega^{(0)}_{k} \omega^{(0)}_{k} + \chi \delta\omega^{(1)}_{k} \omega^{(1)}_{k} \right)
-    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)}_{k} \,,
+    M \omega &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
+    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)} \,,
 \\
-    \tau_{k}/M   &= \gamma \left( \delta\tau^{(0)}_{k} \tau^{(0)}_{k} + \chi \delta\tau^{(1)}_{k} \tau^{(1)}_{k} \right)
-    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}_{k}\,,
+    \tau/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
+    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}\,,
 \end{align}
@@
 %
-We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
+\sout{We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
 QNM, i.e., $k = \{2,\, 2,\, 0\}$. For this reason we will omit the subcripts
 $k$ hereafter and no ambiguity in notation between the overtone index and the
-subscript $n$ in the series should arise.
-%
-We have also pulled out from the sum all beyond-GR corrections, restricting
+subscript $n$ in the series should arise.}
+%
+We have \sout{also} pulled out from the sum all beyond-GR corrections, restricting
 ourselves to the nonspinning ($n=0$) and linear-order in spin ($n=1$)
@@
 
-In the end, the $\pSEOB$ waveform model with theory-specific informed
+In the end, the $\pSEOB$ waveform model with theory-specific
 QNMs has only $\ell$ as a free beyond-GR parameter.
@@
 oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
-references from which we used the results from.
+references from which we used the results from.\agcomm{Just leaving this comment 
+as a reminder to expand this table to include the GR values from Maselli et al.}
 }
@@
 
-As we have seen in Sec.~\ref{sec:review_theories}, the QNM of slowly-rotating
-BHs is modified gravity theories come in two families depending on their
-transformation upon a parity transformation: axial and polar. Which is the one
-we use to match against Eqs.~\eqref{eq:qnm_nongr_iso}?
+As we have seen in Sec.~\ref{sec:review_theories}, QNMs of slowly-rotating
+BHs in modified gravity theories can belong to two families depending on how 
+they behave under a parity transformation: axial and polar. Which one do
+we use to match with Eqs.~\eqref{eq:qnm_nongr_iso}?
 %
@@
 the most likely to appear in the signal.
-
-We performed the mapping between theory-specific QNM calculation and the ParSpec framework
-under the hypothesis above for the theories listed in Sec.~\ref{sec:review_theories}.
-%
-We summarize our result in Table~\ref{tab:ref_theories_qnms} and
+We performed the mapping between theory-specific QNM calculations and the ParSpec framework
+under the hypothesis above, for the theories listed in Sec.~\ref{sec:review_theories}.
+%
+We summarize our results in Table~\ref{tab:ref_theories_qnms} and
 leave the details of our calculations to Appendix~\ref{app:map_details}.
@@
 %
-We chose binary parameters similar to GW150914, consisting of a quasicircular,
-nonspinning binary with detector-frame masses
-$m_1^{\rm dec} = 39\msun$ and $m_2^{\rm dec} = 31\msun$.
-%
-The top panel shows the $+$ polarization of the GW $h_{+}$ in both theories,
+We chose binary parameters similar to GW150914,  but non-spinning, with detector-frame masses
+\sout{$m_1^{\rm dec} = 39\msun$ and $m_2^{\rm dec} = 31\msun$}
+\ag{$m_1 = 39\msun$ and $m_2 = 31\msun$} \agcomm{My suggestion would be to follow what
+I have written in footnote 2, and use unsubscripted symbols to denote detector frame quantities throughout.}.
+%
+The top panel shows the $+$ GW polarization $h_{+}$ in both theories,
 while the bottom panel shows the amplitude $|h| = (h_{+}^2 + h_{\times}^2)^{1/2}$
@@
 %
-The signal are identical up to the merger, after which they differ during the ringdown.
-%
-By construction, the ringdown is lasts longer for the cubic EFT of GR waveform and
+The signals are identical up to the merger,  \ag{specifically, the time $t_\textrm{match}$ 
+defined in Sec.~\ref{sec:review_pSEOB}}, after which they differ during the ringdown.
+%
+By construction, the ringdown lasts longer for the cubic EFT of GR waveform and
 with a smaller instantaneous frequency (see the bottom panel) due to the negative value of the
@@
 \includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
-\caption{(Color online).~Example GW signal with GW1509140-like parameters
+\caption{(Color online).~Example GW signal with GW150914-like parameters
 for both GR (solid line) and cubic EFT of GR (dashed line) with the leading-order

### 2022-04-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section IV

@@
 model parameters~$\bm{\theta}$ (c.f.  Sec.~\ref{sec:review_pSEOB}), and
-$\ell$,  the only non-GR parameter in this problem which, we recall, set
+$\ell$,  the only non-GR parameter in this problem which, we recall, sets
 the characteristic length-scale in which deviations from
 GR become relevant in each of the theories described in
-Sec.~\ref{sec:review_theories}. Hence,
-%
-\begin{equation}
-\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
-\label{eq:def_params}
-\end{equation}
+Sec.~\ref{sec:review_theories}. %Hence,
+%
+%\begin{equation}
+%\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
+%\label{eq:def_params}
+%\end{equation}
 
@@
 %
-with noise-weighted inner product $\langle \cdot | \cdot \rangle$ defined as,
+with the noise-weighted inner product $\langle \cdot | \cdot \rangle$ defined as,
 %
@@
 where $\tilde{A}(f)$ is the Fourier transform of $A(t)$, the asterisk denotes
-complex conjugation and $S_{n}(f)$ is the power spectrum density of the
-detector.
+complex conjugation, $S_{n}(f)$ is the power spectrum density of the
+detector \ag{and $[f_{\rm low}, f_{\rm high}]$ span the detector sensitivity band.}
 %
@@
 sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
-\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx},
-a package part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
+\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx} as part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
 %
 We subsequently marginalize over the remaining parameters to obtain the
-posterior probability distribution function~(PDF) on $\ell$,  i.e., $P_j(\ell \vert d_j,\mathcal{H})$,
+posterior probability distribution function~(PDF) on $\ell$,  i.e., $P(\ell \vert d,\mathcal{H})$,
 our main parameter of interest.
@@
 For $N$ independent GW observations $\{d_j\}$, $j=1,...,N$, each characterised
-by a posterior probability distribution $P_j(\ell \vert d_j,\mathcal{H})$, the
+by a PDF $P_j(\ell \vert d_j,\mathcal{H})$, the
 joint posterior can be written as:
@@
 \begin{equation}
-P(\ell | \{d_j\}) = p(\ell) \prod_{j=1}^{N} \frac{P_j(\ell | d_j)}{p_j(\ell)}\,.
+P(\ell | \{d_j\},\mathcal{H}) = p(\ell) \prod_{j=1}^{N} \frac{P_j(\ell | d_j,\mathcal{H})}{p_j(\ell|\mathcal{H})}\,.
 \label{eq:cumulative_dist_ell}
@@
 %
-where $p_j(\ell)$ are the priors used for each observation, and $p(\ell)$ is an overall prior.
-%
-Since we assume a uniform prior on $\ell$, the joint posterior is identically
-equal to the joint likelihood.
-%
-In some cases, we found it necessary to work with different prior ranges across
-different events, within the context of a given theory.
-%
-In this situation, when combining the posteriors we use chose as our overall
-prior the widest one among the individual events.
+where $p_j(\ell | \mathcal{H})$ are the priors used for each observation, and $p(\ell | \mathcal{H})$ is an overall prior.
+%
+Since we assume a uniform prior on $\ell$, the joint posterior is 
+equal to the joint likelihood. Hereafter, we will drop the explicit usage of
+$\mathcal{H}$.
+%
+%In some cases, we found it necessary to work with different prior ranges across
+%different events, within the context of a given theory.
+%
+%In this situation, when combining the posteriors we use chose as our overall
+%prior the widest one among the individual events.
 
@@
 
-The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \sin\iota$.
-For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
-This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.
-%
-The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
-
-Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(n)}\delta \tau_k^{(n)}\}$,
-as already mentioned in the previous section, we hold $\{\delta \omega_k^{(n)}\}$
-and $\{\delta \tau_k^{(n)}\}$ fixed to theory-specific predictions, and allow only $\ell$ to freely vary.
-%
-We assume an uniform prior between appropriate ranges on $\ell$,
+The prior distribution functions on the GR parameters are assumed to be 
+uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a 
+sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic 
+on the binary orientation, $p(\iota, \psi, \phi_0) \propto \sin\iota$. For the spins 
+$(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
+\footnote{\ag{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.}}
+%
+%The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
+
+Among our beyond-GR parameters $\{\ell, \delta \omega^{(n)}\delta \tau^{(n)}\}$,
+as already mentioned in the previous section, we hold $\{\delta \omega^{(n)},\delta \tau^{(n)}\}$ 
+fixed to theory-specific predictions, and only allow $\ell$ to vary freely.
+%
+We assume an uniform prior on $\ell$ between appropriate ranges,
 say $\ell \in [0, \ell_{\rm max}]$.
@@
 %
-The upper limit is chosen as to make sure that our marginalized posterior
-distributions on $\ell$ do not rail against $\ell_{\rm max}$.
+%The upper limit is chosen as to make sure that our marginalized posterior
+%distributions on $\ell$ do not rail against $\ell_{\rm max}$.
 
@@
 %
-These two events, with a total mass of $65 \Mo$ and $63.4 \Mo$ respectively, are
+These two events, with a total (source-frame) mass of $65 \Mo$ and $63.4 \Mo$ respectively, are
 extremely similar in their source properties. These are also two of the loudest
@@
 %
-Moreover, and what is more relevant for our analysis, is their post-inspiral
-(merger-ringdown) SNRs, which at 16.1 and 16 respectively (see the columns for
+Moreover, and what is more relevant for our analysis, are their post-inspiral
+(merger-ringdown) SNRs which are both $\sim `6$ (see the columns for
 $\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
@@
 ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
-Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector event (HL) while
+Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector  (HL) event while
 GW200129 was 3-detector (HLV).
@@
 %
-The only difference between the sampling configurations is that we do not
-sample over the fractional deviations in the $(220)$ QNM frequencies and
-damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
-and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions, summarized
-in Table~\ref{tab:ref_theories_qnms}.
-%
-In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
+%The only difference between the sampling configurations is that we do not
+%sample over the fractional deviations in the $(220)$ QNM frequencies and
+%damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
+%and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions, summarized
+%in Table~\ref{tab:ref_theories_qnms}.
+%
+\sout{In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
 detector-frame remnant mass $(1 + z) M_f$ for GW150914 for GR and the
@@
 required by the ParSpec expansion (see discussion in
-Sec.~\ref{sec:review_parspec}).
-
+Sec.~\ref{sec:review_parspec}).}\agcomm{This reference to Fig.2 appears misplaced here.
+IMO, Fig 2.
+has two purposes.
+1) to show that we do not need the high-spin version of the fits Carullo used, because our spin posteriors are well-localised around 0.7, and 2) to assure the reader that we were right in using the GR values of the final mass and spin in the ParSpec expansion, because introducing nonGR parameters has not ended up biasing our estimates of Mf-chif.
+I think those are the points at which we need to refer to this figure.}
+%
 In Sec.~\ref{sec:results}, we will enumerate through the different theories and
@@
 There are two conditions that we must verify before we can confidently claim to
-have placed a constraint, within our model's assumptions, with our parameter
-estimation study.
-
-First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
+have placed a constraint on $\ell$. First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
 consider must be considered as an effective field theory, meaning it should be
-considered valid only below an energy scale, or equivalently, a lengthscale.
-%
-As a cut-off lengthscale for the validity of the EFT we use,
+considered valid only below an energy scale, or equivalently, a length-scale.
+%
+As a cut-off length-scale for the validity of the EFT we use,
 %
@@
 We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
-dimensions of length and hence can be compared to the coupling strength $\ell$.
+dimensions of length and hence can be compared to the coupling strength $\ell$ \agcomm{Note, that we have also restored G,c factors in Eq.3.3}.
 %
@@
 %
-We will say that a bound has been placed on $\ell$, if most of the support of
-the posterior distribution function $P(\ell)$ is in the interval
+We will say that a bound has been placed on $\ell$, if most of the PDF $P(\ell | d)$ support is in the interval
 $[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
@@
 In practice, this can be quantified through the cumulative distribution function
-(CDF) associated with the marginalized posterior distribution $P(\ell)$, namely
+(CDF) associated with the marginalized posterior distribution $P(\ell | d)$, namely
 %
@@
 % HS: changed lower limit to zero since we don't have support for negative \ell-values
-P(\ell \leqslant \ell_{\rm max}) = \int_{0}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
+P(\ell \leqslant \ell_{\rm max} | d) = \int_{0}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell' | d) \,.
 \label{eq:def_cdf}
@@
 % \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
-P(\ell \leqslant \Lambda_{\rm EFT}) \leqslant 0.9 \,,
+P(\ell \leqslant \Lambda_{\rm EFT} | d) \leqslant 0.9 \,,
 \quad \textrm{(EFT bound)},
@@
 where we let $\ell_{\rm max} = \Lambda_{\rm EFT}$ in Eq.~\eqref{eq:def_cdf}, and
-likewise for other credibility percentiles.
+likewise for other credibility percentiles\agcomm{Note that we were using $\ell_{\rm max}$
+in the previous section to denote the upper end of the prior. I suggest that we remove the 
+$\ell_{\rm max}$ reference from the previous section. No need to go into details about prior
+boundaries.}.
 
@@
 constrain dCS and EdGB theories with the \emph{inspiral} part of
-the GW signal alone, it was natural to chose the secondary's mass $m_2$ as the most
-conservative choice, since it is by definition the smallest component mass and hence
+the GW signal alone, it was natural to choose the secondary's mass $m_2$ as the most
+conservative choice, since it is by definition the smaller component mass and hence
 places the lowest cut-off scale $\Lambda_{\rm EFT}$ for the validity of either of these theories as an EFT.
@@
 %
-On the other hand, one may argue that the modified gravity theory being
+On the other hand, one may argue that the modified gravity theory under
 consideration should be able to predict a full inspiral, merger, and ringdown
@@
 We will then compare how different assumptions yield to different
-interpretations of the results of our parameter estimations.
+interpretations of the results of our parameter estimation.
 
@@
 does have maximum support at $\gamma_{\rm GB} = 0$. This shows that our model is consistent with GR.
-}
+\agcomm{I was thinking a bit more about the colors we choose for the plots, and I think Figs.
+1-2 should have a different set of colors from Figs.
+3-10.
+That is because the former have GR-nonGR comparisons, while the latter has comparisons between different spin corrections.
+Casual readers sometimes make an unconscious connection of quantities with colors.
+}}
 \label{fig:gamma_gb}

### 2022-04-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section V.A

@@
 
-We start by showing our results for EdGB gravity.
-%
-In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized posteriors of the
+We start \sout{by showing our results for} \ag{with} EdGB gravity.
+%
+In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized PDFs of the
 coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
@@
 %
-The bottom panel panel shows the joint posterior combining both events.
-%
-We see that for both events events, the $N_{\rm max} = 0$ posteriors are
+The bottom panel shows the joint posterior from combining both events.
+%
+We see, for both events events, the $N_{\rm max} = 0$ posteriors are
 characterized by a peak away from zero.
 %
-This does not mean that we are inferring a deviation from GR from data.
+This does not mean that we are inferring a deviation from GR.
 %
@@
 As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm GB}$ does indeed have a posterior
-distribution with largest support at zero, indicating consistency between data
+distribution with largest support at zero, indicating consistency between \sout{data} 
+\ag{the underlying signal} \agcomm{whenever possible, I replaced ``data" when we 
+meant signal, simply because earlier we defined data to also include noise, and by a
+GR prediction we conventionally refer to the signal. }
 and GR.
@@
 We also observe that the inclusion of the spin corrections (i.e., curves with $N_{\rm max} = 1$)
-displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$.
+displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$ \ag{(Fig.~\ref{fig:edgb_exec_sum}).
+and larger values of $\gamma_{\rm GB}$ (Fig.~\ref{fig:gamma_gb}).}
 
@@
 \includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function in EdGB gravity
-for the coupling constant $\ell_{\rm GB}$ for GW150914 (top panel), GW200129 (middle panel)
-and combined events (bottom panel).
+\caption{(Color online).~Posterior distribution function on coupling constant $\ell_{\rm GB}$ in EdGB gravity
+for GW150914 (top panel), GW200129 (middle panel)
+and from combining results (bottom panel).
 %
@@
 \caption{(Color online).~The CDF evaluated at the
-cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ EdGB gravity as a function of the parameter
+cut-off $\Lambda_{\rm EFT}(\varepsilon,\gm)$ for EdGB gravity as a function of the parameter
 $\varepsilon$ for both (dashed curves) $\gm = m_2$, the secondary's source
@@
 (black curves) and with (purple curves) linear in spin QNM corrections. The
-horizontal lines lay at 0.68 and 0.90. We see that in no situation the curves pass
+horizontal lines \sout{lay at 0.68 and 0.90}\ag{mark the 68\% and 90\% credible levels}. 
+We see that in no situation the curves pass
 through the 0.68 or 0.90 lines even at $\varepsilon = 1$.
+\agcomm{Am I missing something something? The Nmax=1 lines for GW150914 does 
+cross the credible levels, as well as the m2 Nmax=1 line for GW200129.}
 %
@@
 are satisfied, before drawing any conclusions on the allowed values for
-$\ell_{\rm GB}$ from our parameter estimations
+$\ell_{\rm GB}$ from our parameter estimations.
 %

### 2022-04-11 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section IV.C (added comment)

@@
 1) to show that we do not need the high-spin version of the fits Carullo used, because our spin posteriors are well-localised around 0.7, and 2) to assure the reader that we were right in using the GR values of the final mass and spin in the ParSpec expansion, because introducing nonGR parameters has not ended up biasing our estimates of Mf-chif.
-I think those are the points at which we need to refer to this figure.}
+I think both of these points can be addressed in the discussions section.
+That is also where we can put the other corner plot with the remaining intrinsic parameters.
+One side-advantage of this is that the figures would then also appear slightly later in the paper, as we had originally planned.}
 %

### 2022-04-11 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section V.B

@@
 
-We now consider dCS gravity.
-%
-In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
+We now consider dCS gravity \ag{where the main results are summarised in Fig.~\ref{fig:dCS_exec_sum}}.
+%
+\sout{In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
 function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
 (middle panel), with different colors distinguishing cases with and without spin corrections to
-dominant $(2,2,0)$~QNM.
-%
-Perhaps the most salient feature of these posteriors is that they are not
+dominant $(2,2,0)$~QNM.}\agcomm{A lot of the language here is a repetition of the previous section.}
+%
+\sout{Perhaps the most salient feature of these posteriors is that they are not
 peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
 deviation from GR. This is not the case and the situation is that same as the
-one we discussed in the previous section for EdGB gravity.
-%
-We verified that
+one we discussed in the previous section for EdGB gravity.}
+\ag{As with EdGB gravity (Sec.~\ref{sec:results_edgb}) although the PDF of $\ell_{\rm CS}$
+is peaked away from 0, this does not signify a deviation from GR, as we have verified that,}
+%
+\sout{We verified that}
 %
@@
 Finally, in the bottom panel, we show the combined result for both events.
+\agcomm{Just a thought.  Since, Figs 3,6,8,10 and Figs.4,6,9,11 show the same basic thing,
+should we have one description at the top of the section for each figure? We can follow this up
+by what is special for each theory in each section? Currently, we are repeating a lot of the 
+language to describe these figures for each theory?}
 
 In Fig.~\ref{fig:dcs_cdf} we show the CDF
-obtained from Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT} (\varepsilon, \gm)$,
+\sout{obtained from Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT} (\varepsilon, \gm)$,
 for both GW150914 (top panel) and GW200129 (bottom panel), where $\Lambda_{\rm EFT}$
 is calculated with either $\gm = m_2$ (dashed lines) or $M_{f}$ (solid lines),
-and in the range $\varepsilon \in [0,1]$.
-%
-For GW150914, we see that with $\gm = m_2$ that Eq.~\eqref{eq:eft_bound} is not
+and in the range $\varepsilon \in [0,1]$.}
+%
+\sout{For}\ag{for} GW150914, we see that with $\gm = m_2$ that Eq.~\eqref{eq:eft_bound} is not
 satisfied unless $\varepsilon \approx 0.9$ (with only $n=0$ corrections) and
@@
 \end{equation}
-%
-on dCS gravity and would constitute the first bound on this theory with
-gravitational-wave observations alone.
+\agcomm{I am not familiar with the term ``credibility", and am more used to the phrase, ``at X\% credible level". 
+Are they the same thing?}
+%
+on dCS gravity and would constitute \emph{the first bound on this theory with
+gravitational-wave observations alone}.\agcomm{Since this is an extremely important
+result, would it make sense to reorder the theories such that dCS comes first among results?}
 %
@@
 %
-\hs{Should we remove these and just quote the 90\% results?}
+\hs{Should we remove these and just quote the 90\% results?}\agcomm{I think
+it's fine to give point estimates, because it's easier for reader to interpret results 
+rather than having to make sense of error bars.}
 
@@
 
-Finally, since both event individually led to a bound on $\ell_{\rm CS}$
-(assuming a cut-off scale for $\gm = M_{f}$ and $j = 0$), we can combine the
+Finally, since both events individually led to a bound on $\ell_{\rm CS}$
+(assuming a cut-off scale for $\gm = M_{f}$ and $N_{\rm max}=0$), we can combine the
 posteriors to obtain the cumulative bound,
@@
 \caption{Detailed summary of our results for dCS gravity for GW150914, GW200129, and
-combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible bounds.
 %
 We found that while our posteriors satisfy the condition~\eqref{eq:eft_bound} (with $\varepsilon = 1/2$),
-they do not obey the condition~\eqref{eq:parspec_bound} for $j = 1$. This means
+they do not obey the condition~\eqref{eq:parspec_bound} for $N_{\rm max} = 1$. This means
 that our results for $N_{\rm max}=0$ are the only ones we can confidently quote.

### 2022-04-11 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section V.D

@@
 in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}.
-}
+\agcomm{In all the figures of this kind, would it make sense to add grey vertical lines to
+mark the 68\% and 90\% upper credible intervals? This will help the reader to quickly cross check the numbers
+that are currently only mentioned in the text.}}
 \label{fig:edgb_exec_sum}
@@
 ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
-$\mathfrak{m} = M_f$ and $N_{\rm max} = 1/2$.
+$\mathfrak{m} = M_f$ and $\epsilon = 1/2$.
 %
@@
 at 90\% credibility. As also happened for our study for dCS, the find that for
-the cubic EFT that the ParSpec bound is violated by the $n = 1$ corrections to
+the cubic EFT that the ParSpec bound is violated by the $N_{\rm max} = 1$ corrections to
 the QNMs, meaning that we cannot use this case to draw any meaningful
@@
 we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}
+\agcomm{At the point of me going through this para, I am yet to figure out what's happening inside the code.
+Hence I have not modified this text, but hopefully will have something over the coming days 
+to sure up this point.}
 

### 2022-04-11 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section VI

@@
 \caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
-but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
-dCS gravity and $j=0$). The contours represent 90\% credible regions.
+detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
+but without (blue contours) \agcomm{colors are not up to date; needs to be 
+finalised after we finalise the color scheme} and with the non-GR parameters 
+different from zero (orange contours, for
+dCS gravity and $N_{\rm max}=0$).
+The contours represent 90\% credible \sout{regions}\ag{levels}\agcomm{we have to be particular about the use of credible regions.
+If its 2D they are ``levels", if they are 1D then ``intervals".
+If we are quoting the difference of the 1D intervals, then we say ``credible bounds"}.
 %
@@
 
+\agcomm{Mention that we do not use the high-spin version of the fits, and refer to the 
+chif measurements Fig.~\ref{fig:corner_plot} (which should be near the text here).}
+
+\agcomm{Mention that our alternate ringdown formalism does not bias estimates of GR quantities 
+and refer to Fig.~\ref{fig:corner_plot_all}}
+
+\begin{figure*}[t]
+\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
+\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
+detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
+but without (blue contours)\agcomm{colors to be updated.} and with the non-GR parameters different from zero (orange contours, for
+dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
+%
+We see that the introduction of the non-GR parameters does not bias the
+inference on the source parameters.
+}
+\label{fig:corner_plot_all}
+\end{figure*}
+
 % -----------------------------------------------------------------------------
@@
 \label{app:map_details}
+\agcomm{Reorder sections, such that the appendix comes after the Acknowledgments?}
+
+\agcomm{Have not gone through the appendices, because there might be sections that still
+need to be completed.}
 

### 2022-04-12 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: swapped acknowledgements / appendix order
hs: added a first version of the abstract

@@
 \begin{abstract}
-% General
-% Motivation
-% What we do
-% Main conclusion
+% General:
+The detection of gravitational waves produced by coalescing compact binaries
+allows us to explore the dynamical, nonlinear regime of general relativity
+and to constrain modifications to it.
+%
+Some of these gravitational-wave events are detected with sufficiently high
+signal-to-noise ratio, allowing us to probe the relaxation of the remnant black
+hole to its final, stationary state -- the so-called black-hole ringdown,
+characterized by a set of quasinormal modes.
+% Main question:
+Can we use the ringdown to constrain deviations to general relativity,
+as predicted by several of its contenders?
+% What we do:
+Here, we take a first step to address this question, by using an
+inspiral-merger-ringdown waveform model in the effective-one-body formalism,
+augmented with a parametrization of the ringdown based on an expansion on the
+final black hole's spin.
+%
+We give a prescription on to include to this waveform model the quasinormal mode frequencies
+calculated on a theory-by-theory basis, in particular, for theories that deviate
+from general relativity through higher-curvature corrections, namely,
+Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
+effective-field-theories of general relativity.
+%
+% Main conclusion:
+We confront the resultant waveform models against GW150914 and GW200129 data,
+finding that while Einstein-dilaton-Gauss-Bonnet cannot be constrained with
+these events, we can place upper bounds on the coupling constants of cubic-
+($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order ($\ell_{\rm qEFT}
+\leqslant 51.3$~km) effective-field-theories of general relativity, and
+of dynamical Chern-Simons gravity ($\ell_{\rm CS} \leqslant 38.7$~km).
+%
+The latter result constitutes a concrete example of a theory presently
+unconstrained by inspiral-only analyses which, however, can be constrained by
+merger-ringdown studies.
 \end{abstract}
@@
 
+% --------------------------
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+%
+We thank Emanuele Berti, Andrea Maselli, Caio F. B. Macedo, Deyan Mihaylov,
+Serguei Ossokine, Scott E. Perkins, and Helvi Witek for discussions.
+%
+We are grateful for the computational resources provided by the Max Planck
+Institute for Gravitational Physics in Potsdam, specifically the
+high-performace computing cluster Hypatia and to Steffen Grunewald for
+assistance.
+%
+The authors would like to thank everyone at the frontline of the Covid-19
+pandemic.
+% --------------------------
+
 \appendix
@@
 \label{app:map_details}
-\agcomm{Reorder sections, such that the appendix comes after the Acknowledgments?}
+% HS: done.
+% \agcomm{Reorder sections, such that the appendix comes after the Acknowledgments?}
 
@@
 
-%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
-%
-We thank Emanuele Berti, Andrea Maselli, Caio F. B. Macedo, Deyan Mihaylov,
-Serguei Ossokine, Scott E. Perkins, and Helvi Witek for discussions.
-%
-We are grateful for the computational resources provided by the Max Planck
-Institute for Gravitational Physics in Potsdam, specifically the
-high-performace computing cluster Hypatia and to Steffen Grunewald for
-assistance.
-%
-The authors would like to thank everyone at the frontline of the Covid-19
-pandemic.
-%%%%%%%%%%%%%%%%%
-
 % \bibliographystyle{apsrev}

### 2022-04-12 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added comment to abhi on tick labels

@@
 %
-We give a prescription on to include to this waveform model the quasinormal mode frequencies
+We give a prescription on how to include to this waveform model the quasinormal mode frequencies
 calculated on a theory-by-theory basis, in particular, for theories that deviate
@@
 %
-The latter result constitutes a concrete example of a theory presently
+The latter result is a concrete example of a theory presently
 unconstrained by inspiral-only analyses which, however, can be constrained by
@@
 inference on the source parameters.
+%
+\hs{We also need to fix overlapping tick labels.}
 }

### 2022-04-12 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
udpated acknowledgements

@@
 %
+The material presented in this manuscript is based upon work supported by NSF’s LIGO Laboratory,
+which is a major facility fully funded by the NSF.
+%
+This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open
+Science Center (https://www.gw-openscience.org), a service of LIGO Laboratory, the LIGO Scientific Collaboration 
+and the Virgo Collaboration, and Zenodo (https://zenodo.org/record/5172704).
+%
 The authors would like to thank everyone at the frontline of the Covid-19

### 2022-04-13 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex

@@
 % -----------
-% Bibligraphy
+% Bibliography
 % -----------
@@
 \newcommand{\hs}[1]{{\textcolor{blue}{{[HS: #1]}} }}
-\newcommand{\ab}[1]{{\textcolor{green}{{[AB: #1]}} }}
+\newcommand{\ab}[1]{{\textcolor{cyan}{{#1}} }}
+\newcommand{\abcomm}[1]{{\textcolor{red}{{[AB: #1]}} }}
 
@@
 Some of these gravitational-wave events are detected with sufficiently high
-signal-to-noise ratio, allowing us to probe the relaxation of the remnant black
-hole to its final, stationary state -- the so-called black-hole ringdown,
+signal-to-noise ratio \ab{in the merger}, allowing us to probe the relaxation of the remnant black
+hole to its final, stationary state --- the so-called black-hole ringdown,
 characterized by a set of quasinormal modes.
@@
 % What we do:
-Here, we take a first step to address this question, by using an
+Here, we \sout{take a first step to} address this question by using an
 inspiral-merger-ringdown waveform model in the effective-one-body formalism,
@@
 %
-We give a prescription on how to include to this waveform model the quasinormal mode frequencies
-calculated on a theory-by-theory basis, in particular, for theories that deviate
-from general relativity through higher-curvature corrections, namely,
+We give a prescription on how to include \ab{in} this waveform model the quasinormal mode frequencies
+calculated on a theory-by-theory basis. \ab{In particular, we focus on gravity} theories that deviate
+from general relativity through higher-order curvature corrections, namely,
 Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
@@
 % Main conclusion:
-We confront the resultant waveform models against GW150914 and GW200129 data,
-finding that while Einstein-dilaton-Gauss-Bonnet cannot be constrained with
+We confront the resultant waveform models against \ab{the two loudest gravitational-wave ringdown signals,
+  notably, GW150914 and GW200129, and we find} that while the Einstein-dilaton-Gauss-Bonnet theory cannot be constrained with
 these events, we can place upper bounds on the coupling constants of cubic-
@@
 unconstrained by inspiral-only analyses which, however, can be constrained by
-merger-ringdown studies.
+merger-ringdown studies \ab{with current gravitational-wave data}.
 \end{abstract}

### 2022-04-14 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
some changes in Sec. III

@@
 %
-where $g = \textrm{det} \, g$ is the metric determinant, $R$ is the Ricci
+where $g = \textrm{det}(g)$ is the metric determinant, $R$ is the Ricci
 scalar and $\varphi$ is a dynamical scalar field that couples to the
@@
 
-Having reviewed the modified gravity theories we will consider, we now present
+\ab{Having reviewed the modified gravity theories we will consider, we now present
 the sequential building blocks for the waveform model we use to test these theories
@@
 %
-We start by reviewing the theory-agnostic parametrized ringdown
-spin-expansion coefficients (ParSpec) \sout{expansion} \ag{framework} \agcomm{replaced `framework' to prevent duplication.
-The original parspec authors call this a data-analysis framework, so I think it would be safe to use it.
-I have left the term ``ParSpec expansion" in other places, because ParSpec is always abbreviated in those places.} in Sec.~\ref{sec:review_parspec}.
+We start by reviewing the parametrized ringdown spin-expansion coefficients (ParSpec) framework in Sec.~\ref{sec:review_parspec}.
 %
 Next, in Sec.~\ref{sec:review_pSEOB}, we review our baseline
-parametrized inspiral-(plunge)-merger-ringdown (IMR) BBH waveform
-model~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we modify
-it to include the ParSpec expansion.
+parametrized inspiral(--plunge)-merger-ringdown (IMR) BBH waveform
+model~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we extend 
+it to include the ParSpec.
 %
@@
 theory-specific QNM calculations in modified gravity theories onto the
-theory-agnostic free coefficients in the ParSpec expansion.
+free coefficients in the ParSpec framework.}
 %
@@
 
-We start by reviewing the ParSpec
-framework introduced in Ref.~\cite{Maselli:2019mjd}, but following
-some of the notation used in Ref.~\cite{Carullo:2021dui}.
-%
-A general procedure to describe deviations to the QNM frequencies $\omega_{k}^{\rm Kerr}$ and
-damping times $\tau_{k}^{\rm Kerr}$ of the GR Kerr BH is to write,
+\ab{A general procedure to describe deviations to the QNM frequencies $\omega_{\ell m n}^{\rm Kerr}$ and
+damping times $\tau_{\ell m n}^{\rm Kerr}$ of the GR Kerr BH is to write,}
 %
@@
 \begin{align}
-\omega_{k} &= \omega^{\rm Kerr}_{k} \, (1 + \delta \omega_{k}), \\
-\tau_{k}   &= \tau^{\rm Kerr}_{k}   \, (1 + \delta \tau_{k}),
+\omega_{\ell m n} &= \omega^{\rm Kerr}_{\ell m n} \, (1 + \delta \omega_{\ell m n}), \\
+\tau_{\ell m n }   &= \tau^{\rm Kerr}_{\ell m  n}   \, (1 + \delta \tau_{\ell m n }),
 \end{align}
@@
 %
-where $\delta\omega_{k}$ and $\delta\tau_{k}$ are the fractional deformation parameters.
-%
-Here we use the subscript $k$ to represent the QNM labels $\{l,\, m,\, n\}$,
-where $l$ and $m$ are the multipole indices, and $n$ the overtone number.
-%
-This type of parametrization was adopted, for instance, in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Carullo:2018sfu}.
-
-\ag{The current LIGO-Virgo-Kagra tests of BH ringdown (see Sec.VII.A of~\cite{LIGOScientific:2020tif} or Sec.VIII.A of~\cite{LIGOScientific:2021sio}) take a restrictive theory-agnostic approach towards the inference of $\delta\omega_{k}$ and $\delta\tau_{k}$.
-These deviations are either assumed to occur identically across all observed sources or belong to a generic underlying Gaussian population.
-A more realistic scenario, however, is that these parameters depend on the source BH's mass and spin.}
-\sout{A caveat of parametrizations of the form~\eqref{eq:general_deviation}, is that
-$\delta\omega_{k}$ and $\delta\tau_{k}$ depend, in general, on the BH's source mass and spin.}
-%
-Ideally, one would like to explicitly reinstate \sout{the dependence the source-frame
-BH mass and spin} \ag{this dependence} for it would
-%
-(i) introduce deformation parameters which can be determined, once and for
+\ab{where $\delta\omega_{\ell m n}$ and $\delta\tau_{\ell m  n}$ are the fractional deformation parameters,
+$l$ and $m$ are the multipole indices, and $n$ the overtone number.}
+%
+This type of parametrization was adopted, for instance, in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Brito:2018rfr,Carullo:2018sfu,Ghosh:2021mrv}.
+
+The current LIGO-Virgo-Kagra tests of BH ringdown (see Sec.VII.A
+of Ref.~\cite{LIGOScientific:2020tif} or Sec.VIII.A
+of Ref.~\cite{LIGOScientific:2021sio}) take a restrictive theory-agnostic
+approach towards the inference of $\delta\omega_{\ell m n}$ and
+$\delta\tau_{\ell m n}$. These deviations are either assumed to occur
+identically across all observed sources or belong to a generic
+underlying Gaussian population. A more realistic scenario, however, is
+that these parameters depend on the source BH's mass and spin.
+%
+Ideally, one would like to explicitly reinstate this dependence, by 
+%
+(i) introducing deformation parameters which can be determined, once and for
 all, from a specific gravity theory (GR included), and
 %
-(ii) make it simpler to combine constraints coming from multiple \ag{(independently observed)} sources.
-
-ParSpec is such an observable-based
-\sout{In the ParSpec expansion this is accomplished by performing a} bivariate
-expansion of Eq.~\eqref{eq:general_deviation} in the detector-frame BH's mass
-$M$ and spin $\chi$, \sout{namely}
+(ii) making it simpler to combine constraints coming from multiple (independently observed) sources.
+
+\ab{The ParSpec framework was introduced in Ref.~\cite{Maselli:2019mjd}. It is} an observable-based
+bivariate expansion of Eq.~\eqref{eq:general_deviation}, given by
 %
@@
 \begin{align}
-\omega_{k} &= \frac{1}{M} \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \omega^{(n)}_{k} \, \left( 1 + \gamma \delta \omega^{(n)}_{k} \right), \\
-\tau_{k}   &= M     \sum_{n = 0}^{N_{\rm max}} \, \chi^{n} \tau^{(n)}_{k}   \, \left( 1 + \gamma \delta \tau^{(n)}_{k} \right),
+\omega_{\ell m n} &= \frac{1}{M_{\rm f}} \sum_{j = 0}^{N_{\rm max}} \, \chi_{\rm f}^{j} \omega^{(j)}_{\ell m n} \, \left( 1 + \gamma\, \delta \omega^{(j)}_{\ell m n} \right), \\
+\tau_{\ell m n}   &= M_{\rm f}     \sum_{j = 0}^{N_{\rm max}} \, \chi_{\rm f}^{j} \tau^{(j)}_{\ell m n}   \, \left( 1 + \gamma\, \delta \tau^{(j)}_{\ell m n} \right),
 \end{align}
@@
 %
-where $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$ are dimensionless coefficients of the
-expansion in spin for Kerr QNMs\footnote{\ag{From this point onwards, to prevent ambiguity,
-we will use $n$ to denote the series expansion index, and not the spherical
-harmonic overtone.}};
-%
-$\delta\omega_{k}^{(n)}$ and $\delta\tau_{k}^{(n)}$ are source-independent
+\ab{where $M_{\rm f}$ and $\chi_{\rm f}$ are the detector-frame final mass and spin, respectively;}
+$\omega_{\ell m n}^{(j)}$ and $\tau_{\ell m n}^{(j)}$ are dimensionless coefficients of the
+expansion in spin for Kerr QNMs; $\delta\omega_{\ell m n}^{(j)}$ and $\delta\tau_{\ell m n}^{(j)}$ are source-independent
 dimensionless coefficients that characterize the corrections to the Kerr QNM at
-each spin-order;
+each spin-order, 
 %
@@
 %
-All source dependence on a given modified gravity theory is contained in the
-dimensionless parameter $\gamma$, given by
+All source dependence for a given modified gravity theory is contained in the
+dimensionless parameter $\gamma$, which reads
 %
@@
 %
-= \left(\frac{\ell}{M_{\rm s}}\right)^{p}
+= \left(\frac{\ell}{M_{\rm f}}\right)^{p}
 %
 = \left[
-\frac{\ell c^2 (1 + z)}{G M}
+\frac{\ell c^2 (1 + z)}{G M_{\rm f}}
 \right]^{p},
@@
 %
-which depends on a parameter $\ell$, with dimensions of length (and sets the
-length-scale at which beyond-GR modifications become important), and
+which depends on \ab{the length-scale parameter $\ell$ (non-GR modifications will become
+important at distances $\lesssim \ell$) and 
 the exponent $p$ which is related to how the beyond-GR modifications are
-added to the Einstein-Hilbert action.
+added to the Einstein-Hilbert action.}
 %

### 2022-04-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: upd caption in corner plot in appendix

@@
 \caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
-but without (blue contours)\agcomm{colors to be updated.} and with the non-GR parameters different from zero (orange contours, for
+detector-frame remnant mass $M_f$ for GW150914, using the same waveform model,
+but without (purple contours) and with the non-GR parameters different from zero (blue contours, for
 dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
@@
 %
-\hs{We also need to fix overlapping tick labels.}
+We observe the same qualitative behavior in the posteriors for the other modified gravity theories
+studied in the main text.
 }

### 2022-04-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: maselli coeff. added to table up to j = 1, upd table caption

@@
 
-\begin{table}[t]
-\begin{tabular}{c | c c c c c c}
-\hline
-\hline
-Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
-\hline
-EdGB        & 4 & 0.0107    & 0.0044    & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
-dCS         & 4 & 3.1964    & 6.3619    & 41.199    & 794.66   &  \cite{Wagle:2021tam}  \\
-cubic EFT   & 4 & $-$0.5813 & 2.6469    & $-$3.8620 & 265.12   & \cite{Cano:2021myl} \\
-quartic EFT & 6 & $-$0.2114 & $-$0.6070 & $-$1.5263 & 171.35   & \cite{Cano:2021myl}  \\
+\begin{table*}[t]
+\begin{tabular}{c | c c c c c c c c c c}
+\hline
+\hline
+Theory      & $\omega^{(0)}_{220}$ & $\tau^{(0)}_{220}$ & $\omega^{(1)}_{220}$ & $\tau^{(1)}_{220}$ & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.
+\\
+\hline
+GR          & 0.3737               & 11.2407            &  0.1258              & 0.2522             & --  & --                          & --                        & --                          & --                        & \cite{Maselli:2019mjd} \\
+\hline
+EdGB        & --                   & --                 &  --                  &                    & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
+dCS         & --                   & --                 &  --                  &                    & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
+cubic EFT   & --                   & --                 &  --                  &                    & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
+quartic EFT & --                   & --                 &  --                  &                    & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
 \hline
@@
 oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
-references from which we used the results from.\agcomm{Just leaving this comment
-as a reminder to expand this table to include the GR values from Maselli et al.}
+references from which we used the results from.
+%
+We also included for comparison the GR coefficients, up to $j=1$, obtained in Ref.~\cite{Maselli:2019mjd}.
+%
+The remaining GR coefficients for $1< j \leqslant 4$, for which their non-GR counterpart cannot be determined as of yet for
+the theories under consideration, can be found in Table~I of Ref.~\cite{Maselli:2019mjd}.
 }
 \label{tab:ref_theories_qnms}
-\end{table}
+\end{table*}
 
@@
 
-\section{Details of the determination of the theory-specific
-ParSpec coefficients}
+\section{Details of the determination of the theory-specific ParSpec coefficients}
 \label{app:map_details}
@@
 
-\agcomm{Have not gone through the appendices, because there might be sections that still
-need to be completed.}
+% \agcomm{Have not gone through the appendices, because there might be sections that still
+% need to be completed.}
+
+In this Appendix, we show how we fixed the coefficients in the ParSpec using
+QNM calculations found in the literature for the theories described in
+Sec.~\ref{sec:review_theories}.
 
@@
 \label{app:map_edgb}
+
+We start by considering EdGB gravity, for which the QNMs of nonrotating and
+slowly-rotating BHs where calculated in
+Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and~\cite{Pierini:2021jxd},
+respectively.
 

### 2022-04-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: added pani et al to table

@@
 \hline
-EdGB        & --                   & --                 &  --                  &                    & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
+EdGB        & --                   & --                 &  --                  &                    & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
 dCS         & --                   & --                 &  --                  &                    & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\

### 2022-04-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
chnages in Secs. III & IV

@@
 %
-Some of these gravitational-wave events are detected with sufficiently high
-signal-to-noise ratio \ab{in the merger}, allowing us to probe the relaxation of the remnant black
-hole to its final, stationary state --- the so-called black-hole ringdown,
+\ab{Some of these gravitational-wave events have sufficiently high
+signal-to-noise ratio in the merger, allowing us to probe the relaxation of the remnant black
+hole to its final, stationary state --- the so-called black-hole ringdown, which is}
 characterized by a set of quasinormal modes.
@@
 inspiral-merger-ringdown waveform model in the effective-one-body formalism,
-augmented with a parametrization of the ringdown based on an expansion on the
+augmented with a parametrization of the ringdown based on an expansion \ab{in} the
 final black hole's spin.
@@
 % Main conclusion:
-We confront the resultant waveform models against \ab{the two loudest gravitational-wave ringdown signals,
-  notably, GW150914 and GW200129, and we find} that while the Einstein-dilaton-Gauss-Bonnet theory cannot be constrained with
+We confront the resultant waveform models against \ab{the two loudest gravitational-wave ringdown signals, so far, 
+  notably, GW150914 and GW200129. We find} that while the Einstein-dilaton-Gauss-Bonnet theory cannot be constrained with
 these events, we can place upper bounds on the coupling constants of cubic-
@@
 \end{table}
+
+\ab{Unless otherwise specified, we will work in geometric units $G = 1 = c$.}
 
@@
 
-\ab{Having reviewed the modified gravity theories we will consider, we now present
+\ab{Having reviewed the modified gravity theories that we will consider, we now present
 the sequential building blocks for the waveform model we use to test these theories
@@
 Next, in Sec.~\ref{sec:review_pSEOB}, we review our baseline
-parametrized inspiral(--plunge)-merger-ringdown (IMR) BBH waveform
-model~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we extend
+parametrized inspiral(--plunge)-merger-ringdown (IMR) waveform
+model~\cite{Brito:2018rfr,Ghosh:2021mrv}, and explain how we extend
 it to include the ParSpec.
@@
 %
-Ultimately, this provides us with an IMR BBH waveform model, with the ringdown
+Ultimately, this provides us with an IMR waveform model, with the ringdown
 portion of the model informed by QNM calculations in specific beyond-GR
@@
 
-\ab{A general procedure to describe deviations to the QNM frequencies $\omega_{\ell m n}^{\rm Kerr}$ and
-damping times $\tau_{\ell m n}^{\rm Kerr}$ of the GR Kerr BH is to write,}
+\ab{A general procedure to describe deviations to the QNM frequencies $\omega^{\rm GR}_{\ell m n}$ and
+damping times $\tau^{\rm GR}_{\ell m n}$ of the GR BH is to write,}
 %
@@
 \begin{align}
-\omega_{\ell m n} &= \omega^{\rm Kerr}_{\ell m n} \, (1 + \delta \omega_{\ell m n}), \\
-\tau_{\ell m n }   &= \tau^{\rm Kerr}_{\ell m  n}   \, (1 + \delta \tau_{\ell m n }),
+\omega_{\ell m n} &= \omega_{\ell m n}^{\rm GR} \, (1 + \delta \omega_{\ell m n}), \\
+\tau_{\ell m n }   &= \tau_{\ell m  n}^{\rm GR}   \, (1 + \delta \tau_{\ell m n }),
 \end{align}
@@
 \ab{where $\delta\omega_{\ell m n}$ and $\delta\tau_{\ell m  n}$ are the fractional deformation parameters,
-$l$ and $m$ are the multipole indices, and $n$ the overtone number.}
+$\ell$ and $m$ are the multipole indices, and $n$ the overtone number.}
 %
@@
 
-The current LIGO-Virgo-Kagra tests of BH ringdown (see Sec.VII.A
+The current LIGO-Virgo-KAGRA tests of BH ringdown (see Sec.VII.A
 of Ref.~\cite{LIGOScientific:2020tif} or Sec.VIII.A
-of Ref.~\cite{LIGOScientific:2021sio}) take a restrictive theory-agnostic
+of Ref.~\cite{LIGOScientific:2021sio}) take a restrictive \ab{theory-independent} 
 approach towards the inference of $\delta\omega_{\ell m n}$ and
@@
 
-\ab{The ParSpec framework was introduced in Ref.~\cite{Maselli:2019mjd}. It is} an observable-based
+\ab{The ParSpec framework was introduced in Ref.~\cite{Maselli:2019mjd} and can be used to our purpose. It is} an observable-based
 bivariate expansion of Eq.~\eqref{eq:general_deviation}, given by
@@
 \ab{where $M_{\rm f}$ and $\chi_{\rm f}$ are the detector-frame final mass and spin, respectively;}
-$\omega_{\ell m n}^{(j)}$ and $\tau_{\ell m n}^{(j)}$ are dimensionless coefficients of the
-expansion in spin for Kerr QNMs; $\delta\omega_{\ell m n}^{(j)}$ and $\delta\tau_{\ell m n}^{(j)}$ are source-independent
-dimensionless coefficients that characterize the corrections to the Kerr QNM at
+the quantities $\omega_{\ell m n}^{(j)}$ and $\tau_{\ell m n}^{(j)}$ are dimensionless coefficients of the
+expansion in spin for BH QNMs in GR, while $\delta\omega_{\ell m n}^{(j)}$ and $\delta\tau_{\ell m n}^{(j)}$ are 
+source-independent dimensionless coefficients that characterize the corrections to the GR QNM at
 each spin-order,
@@
 %
-= \left(\frac{\ell}{M_{\rm f}}\right)^{p}
+= \left(\frac{\ell_{\rm th}}{M^{\rm s}_{\rm f}}\right)^{p}
 %
@@
 %
-which depends on \ab{the length-scale parameter $\ell$ (non-GR modifications will become
-important at distances $\lesssim \ell$) and
-the exponent $p$ which is related to how the beyond-GR modifications are
+which depends on \ab{the length-scale parameter $\ell_{\rm th}$ of the specific gravity theory 
+(non-GR modifications become important at distances $\lesssim \ell_{\rm th}$), and
+the exponent $p$ is related to how the non-GR modifications are
 added to the Einstein-Hilbert action.}
 %
-In Eq.~\eqref{eq:def_gamma} we made \sout{$\ell$} \ag{$\gamma$} dimensionless  by using the other
-length-scale associated with the remnant black hole, i.e., its source-frame mass
-$M_{\rm s}$\footnote{\ag{Throughout this paper, we maintain the convention of
-using the subscript ``s" to denote source-frame quantities and plain baseline
-symbols for detector-frame measurements.}} which we can also write in terms of the detector-frame mass $M$ through
-the redshift $z$~\cite{Krolak:1987ofj}. \ag{Also, dividing by the factor $G/c^2$ allows us to
-express $\ell$ in physically intuitive metric units.}
-
-In principle, a modification to GR would also affect $M$ and $\chi$ and the
-expansion should be written in terms of the non-GR mass and spin, say $\bar{M}$ and
-$\bar{\chi}$. If we assume that the beyond-GR corrections are included perturbatively
-(as is the case of all theories described in Sec.~\ref{sec:review_theories}),
+In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by using the other
+length-scale associated with the remnant black hole (i.e., its source-frame mass
+$M^{\rm s}_{\rm f}$\footnote{Throughout this paper, we maintain the convention of
+using the upperscript ``s" to denote source-frame quantities and plain baseline
+symbols for detector-frame measurements.}), which we can also write in terms of the detector-frame mass $M_{\rm f}$ 
+through the redshift $z$~\cite{Krolak:1987ofj}. Also, dividing by the factor $G/c^2$ allows us to
+express $\ell$ in physically intuitive metric units.
+
+In principle, a modification to GR would also affect $M_{\rm f}$ and $\chi_{\rm f}$ and the
+expansion should be written in terms of the non-GR mass and spin, say $\bar{M}_{\rm f}$ and
+$\bar{\chi}_{\rm f}$. If we assume that the non-GR corrections are included perturbatively
+(as it is the case with all the theories described in Sec.~\ref{sec:review_theories}),
 the modifications to the BH mass and spin can be absorbed into the deviations
-parameters $\delta\omega$ and $\delta\tau$.
-%
-This means we can identify the $M$ and $\chi$ with their \emph{corresponding GR values}
-\footnote{\ag{For a more detailed discussion, see Appendix A in ~\cite{Maselli:2019mjd}.}}.
-%
-We will see that in Sec.~\ref{sec:pe} that this assumption is indeed
-satisfied in our parameter estimation studies (cf.~Fig.~\ref{fig:corner_plot}).
+parameters $\delta\omega^{(j)}_{\ell m n}$ and $\delta\tau^{(j)}_{\ell m n}$.
+%
+This means we can identify the $M_{\rm f}$ and $\chi_{\rm f}$ with their \emph{corresponding {\rm GR} values}
+\footnote{For a more detailed discussion, see Appendix A in Ref.~\cite{Maselli:2019mjd}.}.
+%
+We will see in Sec.~\ref{sec:pe}  that this assumption is indeed
+satisfied in our parameter estimation studies (e.g., see Fig.~\ref{fig:corner_plot}).
 
@@
 the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
-the Kerr QNMs for spins $\chi \lesssim 0.7$.
-%
-The values of the fitting coefficients $\omega_{k}^{(n)}$ and $\tau_{k}^{(n)}$
-can be found in Ref.~\cite{Maselli:2019mjd}, Table I\agcomm{This sentence would need
-to be adapted if we put the GR coefficients in our current Table II.}.
+the GR QNMs for BH's spins $\chi \lesssim 0.7$.
+%
+The values of the fitting coefficients $\omega_{\ell m n}^{(j)}$ and $\tau_{\ell m n}^{(j)}$
+can be found in Ref.~\cite{Maselli:2019mjd}. 
 %
@@
 As we will discuss in Sec.~\ref{sec:pe}, the expansion to $N_{\rm max} = 4$ is
-sufficient for our purposes.
+sufficient for our purposes. \ab{For convenience we list the coefficients in the case of 
+GR in Table~\ref{tab:ref_theories_qnms}.}
 
@@
 As in Refs.~\cite{Brito:2018rfr,Ghosh:2021mrv}, we use an IMR BBH waveform
-model where the parameters describing the remnant object are left additionally
-free and estimated directly from the data.
-
-The GW signal from a BBH merger can be determined in GR by a unique set of
+model where the \ab{(complex) frequencies} \sout{parameters} describing the remnant object 
+are left additionally free and estimated directly from the data.
+
+The GW signal from a \ab{quasicircular} BBH can be \ab{described} \sout{determined} in GR by a unique set of
 parameters $\bm{\theta}$, that includes the masses and spins of the two BHs,
-$(m_1,\, m_2,\, \vec{s}_1,\, \vec{s}_2)$, the sky location determined by the
-luminosity distance $d_L$, right ascension $\alpha$ and declination $\delta$,
+$(m_1,\, m_2,\, \mathbf{S}_1,\, \mathbf{S}_2)$, the sky location determined by the
+luminosity distance $D_L$\abcomm{I cchanged to capital d because later we call the 
+data ``d''.}, right ascension $\alpha$ and declination $\delta$,
 and the orientation of the binary given by the inclination $\iota$ and polarization $\psi$
@@
 $\phi_0$. If we further assume that the spins of the individual BHs are
-restricted to be parallel to the orbital angular momentum, we reduce the six
-components of spin to just two, $(\chi_1, \chi_2)$ and our entire parameter set
-from 15 to 11.
+restricted to be \sout{parallel} \ab{aligned or anti-aligned (for short, aligned)} to the unit vector 
+perpendicular to the orbital plane ($\mathbf{\hat{L}}$), we reduce the six
+components of the spins to just two, $\chi_i \equiv \mathbf{S}_i\cdot \mathbf{\hat{L}} /m_i^2$ with $i = 1,2$, 
+and our entire parameter set from 15 to 11.
 %
@@
 the asymmetric mass ratio $q=m_1/m_2$, with the convention $m_1 \geqslant m_2$ (and thus $q \geqslant 1$),
-and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$.
-
-The polarization of the GW signal (in the observer's frame) is,
+and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$. \ab{Note that for BHs $-1 \leq \chi_i \leq 1$.}
+
+For the polarizations of the GW signal (in the observer's frame) we have
 %
@@
 As our baseline model, that is, the GR model upon which non-GR modifications
-will be added, we use the computationally efficient (time-domain) multipolar
-waveform model for quasicircular spin-aligned BBH mergers described in
-Ref.~\cite{Mihaylov:2021bpf} (henceforth referred to as \SEOB{}\footnote{This waveform
+are added, we use the computationally efficient (time-domain) multipolar
+waveform model for quasicircular spin-aligned BBHs described in
+Ref.~\cite{Mihaylov:2021bpf}, which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$,
+and $(5,5)$. \ab{Such a model was built by applying the post-adiabatic approximation~\cite{Nagar:2018gnk} 
+to the multipolar spin-aligned effective-one-body (EOB) waveform model of Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv} 
+(henceforth we refer to our baseline model as \SEOB{}~\footnote{This waveform
 model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA}
-waveform approximant.}) which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$,
-and $(5,5)$~\cite{Cotesta:2018fcv,Mihaylov:2021bpf}.
-%
-The model uses an effective-one-body (EOB) approach combined with a
-post-adiabatic solution of the equations of motion to describe the
-inspiral-plunge waveform, $h_{l m}^\mathrm{insp-plunge}$.
+waveform approximant.}).}
+
 %
 An accurate description of the merger is incorporated through calibration with
-NR simulations, as described in Ref.~\cite{Cotesta:2018fcv}, along with
+NR simulations, as described in Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv}, along with
 information for the merger and ringdown phases, from BH perturbation theory.
@@
 %
-where $\Theta(t)$ is the Heaviside step function \agcomm{Changed $\theta(t)$ to $\Theta(t)$,
-because $\theta$ was already used to denote the parameter space.}.
+where $\Theta(t)$ is the Heaviside step function. 
 %
 The merger-ringdown waveform is expressed as an exponentially damped
-sinusoid~\cite{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}
+sinusoid~\cite{Bohe:2016gbl,Cotesta:2018fcv} 
 %
@@
 \begin{align}
-\sigma_{l m 0} = {\rm Re}(\sigma_{l m 0}) + i \, {\rm Im}(\sigma_{l m 0})
-= \omega_{l m 0} - i / \tau_{l m 0}\,,
+\sigma_{l m 0} \equiv {\rm Re}(\sigma_{l m 0}) + i \, {\rm Im}(\sigma_{l m 0})
+= \omega_{l m 0} - \frac{i}{\tau_{l m 0}}\,,
 \end{align}
@@
 %
-\ag{Going back to the convention established above to use the index $k$ to now denote the $(l, m,0)$
-mode,  the frequencies $\omega_k$ and damping times $\tau_k$ can be read off from the
-real and imaginary parts of $\sigma_k$ respectively.}
+%\ag{Going back to the convention established above to use the index $k$ to now denote the $(l, m,0)$
+%mode,  the frequencies $\omega_k$ and damping times $\tau_k$ can be read off from the
+%real and imaginary parts of $\sigma_k$ respectively.}
 %
@@
 
-In the $\SEOB$ model~\cite{Mihaylov:2021bpf}, the complex frequencies
-$\sigma_k$ are computed by first determining the final mass and spin from
-estimates of the initial masses and spins through NR-fitting-formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}
+In the $\SEOB$ model~\cite{Bohe:2016gbl,Cotesta:2018fcv}, the complex frequencies
+$\sigma_{\ell m 0}$ are computed by first determining the final mass and spin from
+estimates of the initial masses and spins through NR-fitting-formulas~\cite{Taracchini:2013rva,Hofmann:2016yih}, 
 and then converting them to the complex frequencies using BH perturbation
@@
 \begin{align}
-\omega_k^{\text{GR}} &= \omega_k^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
+\omega_{\ell m 0}^{\rm GR} &\equiv \omega^{\rm GR}_{\ell m 0}(m_1, m_2, \chi_1, \chi_2)\,,
 \\
-\tau _k^{\text{GR}} &= \tau _k^{\text{GR}}(m_1, m_2, \chi_1, \chi_2)\,,
+\tau _{\ell m 0}^{\rm GR} & \equiv \tau^{\rm GR}_{\ell m 0}(m_1, m_2, \chi_1, \chi_2)\,,
 \end{align}
@@
 %
-where $(\omega_k^{\text{GR}}, \tau_k^{\text{GR}} )$ refer to the
-GR QNM predictions in the baseline \SEOB{} model.
-
-\ag{In this paper, we replace these GR predictions with QNM
-frequencies defined through the ParSpec expansion introduced in
-Sec.~\ref{sec:review_parspec}; cf.~Eqs.~\eqref{eq:kerr_expansion}. Hence,}
+where $(\omega^{\rm GR}_{\ell m 0}, \tau^{\rm GR}_{\ell m 0})$ refer to the GR QNM predictions in the baseline \SEOB{} model. 
+In this paper, we replace these GR predictions with QNM
+frequencies defined through the ParSpec framework introduced in
+Sec.~\ref{sec:review_parspec} (see Eqs.~\eqref{eq:kerr_expansion}). Hence,
 %
@@
 \begin{align}
-\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(n)}\}),\\
-\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(n)}\}),
+\omega_{\ell m 0} & \equiv  \omega_{\ell m 0}(m_1, m_2, \chi_1, \chi_2,\ell_{\rm th}, \{\delta \omega_{\ell m 0}^{(j)}\}),\\
+\tau_{\ell m 0}   & \equiv \tau_{\ell m 0} (m_1, m_2, \chi_1, \chi_2, \ell_{\rm th}, \{\delta \tau_{\ell m 0}^{(j)}\}),
 \end{align}
@@
 %
-\ag{where the mass and spin of the remnant object $(M_f,\chi_f)$ are themselves functions of
-$(m_1,\, m_2,\, \chi_1,\, \chi_2)$ (through~\cite{Taracchini:2013rva,Hofmann:2016yih}), and we fix $p$
+where the mass and spin of the remnant object $(M_f,\chi_f)$ are themselves functions of
+$(m_1,\, m_2,\, \chi_1,\, \chi_2)$~\cite{Taracchini:2013rva,Hofmann:2016yih}, and we fix $p$
 to a certain theory-specific value. Additionally,  the frequencies depend on the ParSpec coefficients $\{\delta
-\omega_k^{(n)},\delta \tau_k^{(n)}\}$,  and the coupling constant $\ell$.}
-
-\sout{For example, if we restrict ourselves to corrections with $n=0$, or
-$\chi_f^0$, to the $k=(2,2,0)$ mode only, then we would just have two
-additional parameters, $\{\delta \omega_0^{(0)}, \delta \tau_0^{(0)}\}$.
-%
-In this paper, we will restrict ourselves to corrections to the $n=0$ and
-$n=1$ terms, that is, only up to the leading-order in spin $\chi_f$ term.}
-
-Using this parameterized waveform model, which we will call $\pSEOB$ in this
-paper, we infer bounds on our non-GR parameter $\ell$ for specific cases of
+\omega_{\ell m 0}^{(j)},\delta \tau_{\ell m 0}^{(j)}\}$,  and the \ab{length-scale} $\ell_{\rm th}$.
+
+Using this parameterized waveform model, which we denote $\pSEOB$, 
+we infer bounds on our non-GR parameter $\ell_{\rm th}$ for the specific cases of
 modified gravity theories presented Sec.~\ref{sec:review_theories}.
 %
-We detail these results in Sec.~\ref{sec:results}.
+We detail our results in Sec.~\ref{sec:results}.
 %
@@
 
-\subsection{From theory-agnostic to theory-specific QNM results}
+\subsection{From theory-independent to theory-specific QNM results}
 \label{sec:theory_specific_qnm}
 
-Let us now establish the connection between the theory-agnostic \agcomm{or independent?} framework of the
-$\pSEOB$ waveform model and the theory-specific QNM calculations.  \ag{In this paper we will restrict ourselves to
-corrections to the leading and next-to-leading order terms in the ParSpec expansion, as well as the fundamental
-$k = \{2,\, 2,\, 0\}$ QNM. For this reason,  we will omit the subscripts $k$ hereafter
-and rewrite $\omega$ and $\tau$, given by} Eqs.~\eqref{eq:kerr_expansion} as,
+Let us now establish the connection between the theory-\ab{independent} framework of the
+$\pSEOB$ waveform model and the theory-specific QNM calculations. In this paper we restrict ourselves 
+\ab{to the leading and next-to-leading order terms} in the ParSpec expansion, as well as to the fundamental QNM 
+$(\ell, m, n) = (2,\, 2,\, 0)$. For this reason, \ab{for simplicity}, we omit the subscripts hereafter
+and rewrite $\omega_{\ell m n}$ and $\tau_{\ell m n}$, given by Eqs.~\eqref{eq:kerr_expansion} as,
 %
@@
 \begin{align}
-    M \omega &= \gamma \left( \delta\omega^{(0)} \omega^{(0)} + \chi \delta\omega^{(1)} \omega^{(1)} \right)
-    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \omega^{(n)} \,,
+    M_{\rm f}\, \omega &= \gamma \left [ \delta\omega^{(0)} \omega^{(0)} + \chi_{\rm f} \delta\omega^{(1)} \omega^{(1)} \right ]
+    + \sum_{j=0}^{N_{\rm max}} \chi^{j}_{\rm f}\, \omega^{(j)} \,,
 \\
-    \tau/M   &= \gamma \left( \delta\tau^{(0)} \tau^{(0)} + \chi \delta\tau^{(1)} \tau^{(1)} \right)
-    + \sum_{n=0}^{N_{\rm max}} \chi^{n} \tau^{(n)}\,,
+    \frac{\tau}{M_{\rm f}}   &= \gamma \left [ \delta\tau^{(0)} \tau^{(0)} + \chi_{\rm f} \delta\tau^{(1)} \tau^{(1)} \right ]
+    + \sum_{j=0}^{N_{\rm max}} \chi^{n}_{\rm f}\, \tau^{(j)}\,,
 \end{align}
@@
 %
-\sout{We will work exclusively with the $\ell = m = 2$ and $n = 0$ (fundamental mode)
-QNM, i.e., $k = \{2,\, 2,\, 0\}$. For this reason we will omit the subcripts
-$k$ hereafter and no ambiguity in notation between the overtone index and the
-subscript $n$ in the series should arise.}
-%
-We have \sout{also} pulled out from the sum all beyond-GR corrections, restricting
-ourselves to the nonspinning ($n=0$) and linear-order in spin ($n=1$)
-corrections to the Kerr QNMs.
+\ab{where we pull out from the sum all non-GR corrections, restricting
+ourselves to the nonspinning ($j=0$) and linear-order in spin ($j=1$)
+corrections to the GR QNMs.}
 %
 % These corrections are encoded in the coefficients $\delta\omega^{(n)}$ and $\delta\tau^{(n)}$.
-
-How can we determine the beyond-GR corrections? In GR, comparison between the numerically determined
-Kerr QNMs against the fitting formula~\eqref{eq:qnm_nongr_iso} fixes the GR expansion coefficients
-$\omega^{(n)}$, $\tau^{(n)}$.
-%
-We can proceed in a similar way with QNMs calculated in the context of a beyond-GR theory.
-%
-In particular, in the literature, we can already find fitting formulas relating
-the QNMs to the BHs mass, spin and coupling constant $\ell$, the latter being
-specific to each theory, up to $n=1$ in the spin expansion (see Table~\ref{tab:ref_theories_qnms}).
-%
-The idea is then to compare these formulas against Eq.~\eqref{eq:qnm_nongr_iso}
-to fix $p$, $\delta\omega^{(n)}$, and $\delta\tau^{(n)}$.
-%
-Because QNMs of rotating BHs in modified gravity theories are not known to
-all spin values, we can expect that the $n=1$ coefficients to be susceptible to
-changes as calculations beyond-leading order in spin are accomplished.
-%
-That is not the case for the $n=0$ coefficients and the situation is the same as in GR,
-in which the $n=0$ coefficients are simply the QNMs of the Schwarzschild BH.
-
-In the end, the $\pSEOB$ waveform model with theory-specific
-QNMs has only $\ell$ as a free beyond-GR parameter.
-%
-We emphasize that our procedure is different from that of
-Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell$,
-$\delta\omega^{(n)}$, and $\delta\tau^{(n)}$ parameters, and then proceeded
-to use the posteriors on $\ell$ to draw conclusions to any theory that predict
-corrections at a given $p$.
-%
-This is a critical difference between our work and Ref.~\cite{Carullo:2021dui}.
-In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
-information to the ParSpec expansion coefficients \emph{can lead to different interpretations
-of the final bounds on $\ell$, even for different theories which predict the same value of the exponent $p$.}
 
@@
 
+How can we determine the beyond-GR corrections? In GR, comparison between the numerically determined
+Kerr QNMs against the fitting formula~\eqref{eq:qnm_nongr_iso} fixes the GR expansion coefficients
+$\omega^{(j)}$, $\tau^{(j)}$.
+%
+We can proceed in a similar way with QNMs calculated in the context of a non-GR theory.
+%
+In particular, in the literature, we can already find fitting formulas relating
+the QNMs to the BHs mass, spin and coupling constant $\ell_{\rm thh}$, the latter being
+specific to each theory, up to $j=1$ in the spin expansion (see Table~\ref{tab:ref_theories_qnms}).
+%
+The idea is then to compare these formulas against Eq.~\eqref{eq:qnm_nongr_iso}
+to fix $p$, $\delta\omega^{(j)}$, and $\delta\tau^{(j)}$.
+%
+Because QNMs of rotating BHs in modified gravity theories are not known to
+all spin values, we can expect that the $j=1$ coefficients to be susceptible to
+changes as calculations beyond-leading order in spin are accomplished \ab{in the future}.
+%
+That is not the case for the $j=0$ coefficients and the situation is the same as in GR,
+in which the $j=0$ coefficients are simply the QNMs of the Schwarzschild BH.
+
+In the end, the $\pSEOB$ waveform model with theory-specific
+QNMs has only $\ell_{\rm th}$ as a free beyond-GR parameter.
+%
+We emphasize that our procedure is different from that of
+Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell_{\rm th}$,
+$\delta\omega^{(j)}$, and $\delta\tau^{(j)}$ parameters, and then proceeded
+to use the posteriors on $\ell_{\rm th}$ to draw conclusions to any theory that predict
+corrections at a given $p$.
+%
+This is a critical difference between our work and Ref.~\cite{Carullo:2021dui}.
+In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
+information to the ParSpec coefficients \emph{can lead to different interpretations
+of the final bounds on $\ell_{\rm th}$, even for different theories that predict the same 
+value of the exponent $p$.}
+
 As we have seen in Sec.~\ref{sec:review_theories}, QNMs of slowly-rotating
@@
 %
-In beyond-GR theories, isospectrality is in general broken (see
+In non-GR theories, isospectrality is in general broken (see
 in Ref.~\cite{Hui:2021cpm} for a counterexample).
@@
 %
-The justification is this is the mode (if excited during the merger) which is
+The justification is that this is the mode (if excited during the merger) which is
 the most likely to appear in the signal.
@@
 In Fig.~\ref{fig:example_waveform} we show an illustrative waveform for GR (solid line; using the \texttt{SEOBNR} model) and in the cubic EFT of gravity (dashed line; using the \pSEOB{} model),
-including the leading-order $n = 0$ deformations to the fundamental QNM (see Table~\ref{tab:ref_theories_qnms}).
-%
-We chose binary parameters similar to GW150914,  but non-spinning, with detector-frame masses
-\sout{$m_1^{\rm dec} = 39\msun$ and $m_2^{\rm dec} = 31\msun$}
-\ag{$m_1 = 39\msun$ and $m_2 = 31\msun$} \agcomm{My suggestion would be to follow what
-I have written in footnote 2, and use unsubscripted symbols to denote detector frame quantities throughout.}.
+including the leading-order $j = 0$ deformations to the fundamental QNM (see Table~\ref{tab:ref_theories_qnms}).
+%
+We choose binary parameters similar to GW150914,  but non-spinning, with detector-frame masses 
+$m_1 = 39\msun$ and $m_2 = 31\msun$. 
 %
@@
 %
-The signals are identical up to the merger,  \ag{specifically, the time $t_\textrm{match}$
-defined in Sec.~\ref{sec:review_pSEOB}}, after which they differ during the ringdown.
+The signals are identical up to the merger, specifically, the time $t_\textrm{match}$
+defined in Sec.~\ref{sec:review_pSEOB}, after which they differ during the ringdown.
 %
@@
 \includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
-\caption{(Color online).~Example GW signal with GW150914-like parameters
+\caption{(Color online). Gravitational-wave signal with GW150914-like parameters
 for both GR (solid line) and cubic EFT of GR (dashed line) with the leading-order
@@
 % --------------------------------------------------------------------------------- %
-\section{Parameter Inference}
+\section{Parameter Inference and validity of our analysis}
 \label{sec:pe}
@@
 
-In this section, we provide a basic outline of the Bayesian formalism we use to
-infer the properties of the underlying GW signal, identify the most promising
-events from the catalog of GW observations to base our analyses on, and discuss
-the key insights they provide in constraining predictions of modified gravity
-theories.
+In this section, we \ab{first} provide a basic outline of the Bayesian formalism that we use to
+infer the properties of the underlying GW signal; \ab{then, we} identify the most promising
+events from the catalog of \ab{LIGO-Virgo-KAGRA} GW observations to base our analyses on. \ab{Finally, 
+we discuss how we can interpret our results after taking into account the region of validity of 
+the non-GR theories that we are considering, which are EFTs.}
 
@@
 The set of parameters, $\bm{\lambda}$ is a union of the GR waveform
-model parameters~$\bm{\theta}$ (c.f.  Sec.~\ref{sec:review_pSEOB}), and
-$\ell$,  the only non-GR parameter in this problem which, we recall, sets
+model parameters~$\bm{\theta}$ (see Sec.~\ref{sec:review_pSEOB}) \abcomm{It seems to 
+me that PRD does not use ``c.f.''. Does it? I am replacing it with ''see''.}, and
+$\ell_{\rm th}$,  the only non-GR parameter in this problem which, we recall, sets
 the characteristic length-scale in which deviations from
@@
 complex conjugation, $S_{n}(f)$ is the power spectrum density of the
-detector \ag{and $[f_{\rm low}, f_{\rm high}]$ span the detector sensitivity band.}
+detector, and $[f_{\rm low}, f_{\rm high}]$ span the detector sensitivity \ab{frequency} band.
 %
@@
 sample over the parameter space using a Markov-Chain Monte Carlo algorithm as implemented in
-\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx} as part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
+\texttt{LALInferenceMCMC}~\cite{Rover:2006ni,vanderSluys:2008qx}, as part of the \texttt{LALInference} software suite~\cite{Veitch:2014wba,lalsuite}.
 %
 We subsequently marginalize over the remaining parameters to obtain the
-posterior probability distribution function~(PDF) on $\ell$,  i.e., $P(\ell \vert d,\mathcal{H})$,
+posterior probability distribution function~(PDF) on $\ell_{\rm th}$ (i.e., $P(\ell_{\rm th} \vert d,\mathcal{H})$),
 our main parameter of interest.
 
-For $N$ independent GW observations $\{d_j\}$, $j=1,...,N$, each characterised
-by a PDF $P_j(\ell \vert d_j,\mathcal{H})$, the
+For $N$ independent GW observations $\{d_j\}$, $j=1,...,N$, each characterized
+by a PDF $P_j(\ell_{\rm th} \vert d_j,\mathcal{H})$, the
 joint posterior can be written as:
@@
 \begin{equation}
-P(\ell | \{d_j\},\mathcal{H}) = p(\ell) \prod_{j=1}^{N} \frac{P_j(\ell | d_j,\mathcal{H})}{p_j(\ell|\mathcal{H})}\,.
+P(\ell_{\rm th} | \{d_j\},\mathcal{H}) = p(\ell_{\rm th}) \prod_{j=1}^{N} \frac{P_j(\ell_{\rm th} | d_j,\mathcal{H})}{p_j(\ell_{\rm th}|\mathcal{H})}\,.
 \label{eq:cumulative_dist_ell}
@@
 %
-where $p_j(\ell | \mathcal{H})$ are the priors used for each observation, and $p(\ell | \mathcal{H})$ is an overall prior.
-%
-Since we assume a uniform prior on $\ell$, the joint posterior is
+where $p_j(\ell_{\rm th} | \mathcal{H})$ are the priors used for each observation, and $p(\ell_{\rm th} | \mathcal{H})$ is an overall prior.
+%
+Since we assume a uniform prior on $\ell_{\rm th}$, the joint posterior is
 equal to the joint likelihood. Hereafter, we will drop the explicit usage of
@@
 uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a
-sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic
+sphere in the sky for the source location with $p(D_L) \propto D_L^2$, and isotropic
 on the binary orientation, $p(\iota, \psi, \phi_0) \propto \sin\iota$. For the spins
-$(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the $z$-components.
-\footnote{\ag{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.}}
+$(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes.\sout{ and restrict ourselves to the $z$-components.} \footnote{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior.}}.
 %
@@
 
-Among our beyond-GR parameters $\{\ell, \delta \omega^{(n)}\delta \tau^{(n)}\}$,
-as already mentioned in the previous section, we hold $\{\delta \omega^{(n)},\delta \tau^{(n)}\}$
-fixed to theory-specific predictions, and only allow $\ell$ to vary freely.
-%
-We assume an uniform prior on $\ell$ between appropriate ranges,
-say $\ell \in [0, \ell_{\rm max}]$.
-%
-The lower limit is set by the fact the modified gravity theories we consider
-all have $p$ even and hence we can assume $\ell > 0$ without loss of
+Among our non-GR parameters $\{\ell_{\rm th}, \delta \omega^{(j)}\delta \tau^{(j)}\}$,
+as already mentioned in the previous section, we hold $\{\delta \omega^{(j)},\delta \tau^{(j)}\}$
+fixed to theory-specific predictions, and only allow $\ell_{\rm th}$ to vary freely.
+%
+We assume an uniform prior on $\ell_{\rm th}$ between appropriate ranges\sout{,
+say $\ell_{\rm th} \in [0, \ell_{\rm max}]$}.
+%
+The lower limit is set by the fact that the modified gravity theories we consider
+all have $p$ even and hence we can assume $\ell_{\rm th} > 0$ without loss of
 generality.
@@
 The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an
-\emph{IMR} model which infers the properties of the underlying GW signal,
+IMR model that infers the properties of the underlying GW signal,
 including (independently) its ringdown properties, using the Bayesian formalism
@@
 %
-The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
-signals not all of which are relevant for a BH ringdown analysis. In fact, in
-an accompanying paper~\cite{LIGOScientific:2021sio}, the \textsc{pSEOBNRv4HM}
-analysis\footnote{See, in particular, Sec.VIII A.2
-in~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model
+The latest LIGO-Virgo-KAGRA GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
+signals not all of which are relevant for \ab{our} BH ringdown analysis. In fact, in
+the accompanying paper~\cite{LIGOScientific:2021sio} on tests of GR, the \texttt{pSEOBNRv4HM}
+~\cite{Brito:2018rfr,Ghosh:2021mrv} analysis~\footnote{See, in particular, Sec.VIII A.2
+in Ref.~\cite{LIGOScientific:2021sio}}, which is most similar to the \pSEOB{} model
 presented in this paper, identified two events which provided the strongest
-bounds on measurements of the dominant $(220)$ QNM:
+bounds on the measurements of the dominant $(220)$ QNM:
 GW150914~\cite{LIGOScientific:2016aoc} and
@@
 extremely similar in their source properties. These are also two of the loudest
-BBH signals observed to date with a total network SNR of 24 and 26.8
+BBH signals observed to date with a total network SNR of 24 and 26.8, 
 respectively.
@@
 (merger-ringdown) SNRs which are both $\sim `6$ (see the columns for
-$\rho_{\text{post-insp}}$ in Table III of~\cite{LIGOScientific:2019fpa} and
-Table IV of~\cite{LIGOScientific:2021sio}).
+$\rho_{\text{post-insp}}$ in Table III of Ref.~\cite{LIGOScientific:2019fpa} and
+Table IV of Ref.~\cite{LIGOScientific:2021sio}).
 %
@@
 The parameter inference in this paper follows configurations identical to the
-ones used on these events for the \textsc{pSEOBNRv4HM} analysis in
-Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector  (HL) event while
-GW200129 was 3-detector (HLV).
+ones used on these events for the \texttt{pSEOBNRv4HM} analysis in
+Ref.~\cite{LIGOScientific:2021sio}. GW150914 was a 2-detector (Hanford-Livingston) event while
+GW200129 was 3-detector (Hanford-Livingston-Virgo).
 %
@@
 %
-\sout{In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
-detector-frame remnant mass $(1 + z) M_f$ for GW150914 for GR and the
-illustrative case of dCS gravity. We see that our waveform models does not
-introduce a substantial change to the GR estimates on this parameters, as
-required by the ParSpec expansion (see discussion in
-Sec.~\ref{sec:review_parspec}).}\agcomm{This reference to Fig.2 appears misplaced here.
-IMO, Fig 2.
-has two purposes.
-1) to show that we do not need the high-spin version of the fits Carullo used, because our spin posteriors are well-localised around 0.7, and 2) to assure the reader that we were right in using the GR values of the final mass and spin in the ParSpec expansion, because introducing nonGR parameters has not ended up biasing our estimates of Mf-chif.
-I think both of these points can be addressed in the discussions section.
-That is also where we can put the other corner plot with the remaining intrinsic parameters.
-One side-advantage of this is that the figures would then also appear slightly later in the paper, as we had originally planned.}
-%
-In Sec.~\ref{sec:results}, we will enumerate through the different theories and
-outline the highlight results. Whenever possible, we also combine results from
-multiple events to obtain the strongest possible bound on $\ell$.
+
+In Sec.~\ref{sec:results}, we enumerate through the different theories and
+outline the main results. Whenever possible, we also combine results from
+multiple events to obtain the strongest possible bound on $\ell_{\rm th}$.
 
@@
 
-\subsection{General remarks on the interpretation of our results}
+\subsection{Interpretation of our results}
 \label{sec:remarks}
@@
 There are two conditions that we must verify before we can confidently claim to
-have placed a constraint on $\ell$. First, as we explained in Sec.~\ref{sec:review_theories}, all theories that we
-consider must be considered as an effective field theory, meaning it should be
+have placed a constraint on $\ell_{\rm th}$. First, as we have explained in Sec.~\ref{sec:review_theories}, all theories that we
+consider must be \ab{interpreted} as an effective field theory, meaning that it should be
 considered valid only below an energy scale, or equivalently, a length-scale.
@@
 \begin{equation}
-\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, G \mathfrak{m} / c^2 \,,
+\Lambda_{\rm EFT} (\varepsilon, \mathfrak{m}) = \varepsilon \, \frac{G \mathfrak{m}}{c^2} \,,
 \label{eq:def_cutoff}
@@
 %
-We also momentarily restored factors of $c$ and $G$ to emphasize that $\Lambda_{\rm EFT}$ has
-dimensions of length and hence can be compared to the coupling strength $\ell$ \agcomm{Note, that we have also restored G,c factors in Eq.3.3}.
+We note that $\Lambda_{\rm EFT}$ has dimensions of length and hence can be compared to the coupling strength $\ell_{\rm th}$.
 %
@@
 %
-We will say that a bound has been placed on $\ell$, if most of the PDF $P(\ell | d)$ support is in the interval
+We say that a bound has been placed on $\ell_{\rm th}$, if most of the PDF $P(\ell_{\rm th} | d)$ support is in the interval
 $[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
@@
 In practice, this can be quantified through the cumulative distribution function
-(CDF) associated with the marginalized posterior distribution $P(\ell | d)$, namely
-%
-\begin{equation}
-% P(\ell \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
+(CDF) associated with the marginalized posterior distribution $P(\ell_{\rm th} | d)$, namely
+%
+\begin{equation}
+% P(\ell_{\rm th} \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
 % HS: changed lower limit to zero since we don't have support for negative \ell-values
-P(\ell \leqslant \ell_{\rm max} | d) = \int_{0}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell' | d) \,.
+P(\ell_{\rm th} \leqslant \ell_{\rm max} | d) = \int_{0}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell' | d) \,.
 \label{eq:def_cdf}
@@
 %
-For instance, we will require that for a bound with 90\% credibility to be placed on $\ell$ that
+For instance, we require that for a bound \ab{at 90\% credible level} to be placed on $\ell_{\rm th}$ that
 %
@@
 % \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
-P(\ell \leqslant \Lambda_{\rm EFT} | d) \leqslant 0.9 \,,
+P(\ell_{\rm th} \leqslant \Lambda_{\rm EFT} | d) \leqslant 0.9 \,,
 \quad \textrm{(EFT bound)},
@@
 where we let $\ell_{\rm max} = \Lambda_{\rm EFT}$ in Eq.~\eqref{eq:def_cdf}, and
-likewise for other credibility percentiles\agcomm{Note that we were using $\ell_{\rm max}$
-in the previous section to denote the upper end of the prior. I suggest that we remove the
-$\ell_{\rm max}$ reference from the previous section. No need to go into details about prior
-boundaries.}.
+likewise for other credibility percentiles.
 
@@
 \begin{equation}
-\gamma \, \delta \omega^{(n)} \ll 1 \,,
+\gamma \, \delta \omega^{(j)} \ll 1 \,,
 \,\, \textrm{and} \,\,
-\gamma \, \delta \tau^{(n)} \ll 1 \,, \quad \textrm{(ParSpec bound)},
+\gamma \, \delta \tau^{(j)} \ll 1 \,, \quad \textrm{(ParSpec bound)},
 \label{eq:parspec_bound}
@@
 %
-for all orders $n$ in the expansion in dimensionless spin $\chi$ and where $\gamma$
+for all orders $j$ in the expansion in dimensionless spin $\chi_{\rm f}$ and where $\gamma$
 was defined in Eq.~\eqref{eq:def_gamma}.
 %
-We will also construct posterior distributions for these parameters and check if
+We also construct posterior distributions for these parameters and check if
 most of their support is concentrated to a domain with values much smaller than
@@
 interested in the ringdown part of the signal, it is natural to use the
-final mass $M_f$ to compute $\Lambda_{\rm EFT}$.
+final mass $M_{\rm f}$ to compute $\Lambda_{\rm EFT}$.
 %
@@
 consideration should be able to predict a full inspiral, merger, and ringdown
-of the black hole binary before we can even make such a test, and thus the
+of the BBH before we can even make such a test, and thus the
 same, more conservative choice $\gm = m_2$ should be used.
@@
 Here we adopt a pragmatic approach to this issue and consider \emph{both}
-masses, $m_2$ and $M_f$, to determine $\Lambda_{\rm EFT}$.
-%
-We will then compare how different assumptions yield to different
+masses, $m_2$ and $M_{\rm f}$, to determine $\Lambda_{\rm EFT}$.
+%
+We then compare how different assumptions yield to different
 interpretations of the results of our parameter estimation.
@@
 
+\sout{In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
+detector-frame remnant mass $(1 + z) M_f$ for GW150914 for GR and the
+illustrative case of dCS gravity. We see that our waveform models does not
+introduce a substantial change to the GR estimates on this parameters, as
+required by the ParSpec expansion (see discussion in
+Sec.~\ref{sec:review_parspec}).}\agcomm{This reference to Fig.2 appears misplaced here.
+IMO, Fig 2.
+has two purposes.
+1) to show that we do not need the high-spin version of the fits Carullo used, because our spin posteriors are well-localised around 0.7, and 2) to assure the reader that we were right in using the GR values of the final mass and spin in the ParSpec expansion, because introducing nonGR parameters has not ended up biasing our estimates of Mf-chif.
+I think both of these points can be addressed in the discussions section.
+That is also where we can put the other corner plot with the remaining intrinsic parameters.
+One side-advantage of this is that the figures would then also appear slightly later in the paper, as we had originally planned.}
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%

### 2022-04-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: commiting local changes to be able to pull
hs" fixed caption in the appendix plot

@@
 \includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
-\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $M_f$ for GW150914, using the same waveform model,
-but without (purple contours) and with the non-GR parameters different from zero (blue contours, for
-dCS gravity and $N_{\rm max}=0$). The contours represent 90\% credible levels.
+\caption{(Color online).~Corner plot showing that the inferred source binary parameters for GW150914,
+using the same waveform model \pSEOB, but with (purple contours) and without setting the non-GR parameters different
+from zero (blue contours), having as an illustrative example dCS gravity and $N_{\rm max}=0$.
+%
+All contours correspond to 90\% credible levels.
 %
 We see that the introduction of the non-GR parameters does not bias the
-inference on the source parameters.
-%
-We observe the same qualitative behavior in the posteriors for the other modified gravity theories
-studied in the main text.
+inference of the source parameters.
+%
+We found the same qualitative behavior in the posteriors distributions of the
+source binary parameters for the other modified gravity theories studied in the
+main text.
+%
+The same conclusions apply for the other GW event studied here, GW200129.
 }
@@
 
-In this Appendix, we show how we fixed the coefficients in the ParSpec using
-QNM calculations found in the literature for the theories described in
+In this Appendix, we show how we determined the coefficients in the ParSpec
+using QNM calculations found in the literature for the theories described in
 Sec.~\ref{sec:review_theories}.

### 2022-04-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
changes in Sec. I, IV, V, VI

@@
 %
-where $g = \textrm{det}(g)$ is the metric determinant, $R$ is the Ricci
-scalar and $\varphi$ is a dynamical scalar field that couples to the
+where \ab{$g \equiv \textrm{det}(g_{\mu \nu})$} is the metric determinant, $R$ is the Ricci
+scalar, $\varphi$ is a dynamical scalar field that couples to the
 Gauss-Bonnet invariant
@@
 - 4 R^{\mu\nu}R_{\mu\nu}
-+ R^2$.
-%
-$R_{\mu\nu\rho\sigma}$ and $R_{\mu\nu}$ are the Riemann and Ricci tensors respectively.
++ R^2$,
+%
+and $R_{\mu\nu\rho\sigma}$ and $R_{\mu\nu}$ are the Riemann and Ricci tensors respectively.
 %
@@
 %
-In the first class, the first derivative of the coupling function $f'(\varphi) = \dd f  / \dd \varphi$
+In the first class, the first derivative of the coupling function $f'(\varphi) \equiv \dd f  / \dd \varphi$
 is always nonzero and BHs are known to always support scalar hair.
@@
 BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
-related to the asymptotic $r^{-1}$\agcomm{In most of these cases $r$ might be intuitive, but just wanted to leave this comment to remind myself that we never define it explicitly.} fall-off of the scalar field.
+related to the asymptotic $r^{-1}$ fall-off of the scalar field, \ab{where $r$ is the distance from the BH.}
 %
@@
 Since the scalar field is sourced by a curvature scalar, $Q$ is larger (smaller),
- smaller (larger) the BH mass is.
+\ab{the} smaller (larger) the BH mass is.
 
@@
 First, the presence of the scalar charge implies that when in binaries, BHs can source
-scalar dipole radiation (see e.g., Refs.~\cite{Yagi:2011xp,Julie:2019sab,Shiralilou:2020gah,Shiralilou:2021mfl,Julie:2022huo})
-which affects the GW phase at $-1$PN order (relative to the dominant GR
+scalar-dipole radiation (see, e.g., Refs.~\cite{Yagi:2011xp,Julie:2019sab,Shiralilou:2020gah,Shiralilou:2021mfl,Julie:2022huo})
+which affects the GW phase at $-1$PN order (relative to the dominant \ab{quadrupolar} GR
 contribution), with magnitude proportional to the difference between the
 charges of binary components. This makes EdGB gravity testable with present GW
-observations of compact binaries where at least one component is a BH.
+observations of compact binaries where at least \ab{if} one component is a BH.
 %
@@
 %
-using the neutron star-black hole binaries GW200105 and
+using the neutron-star--black-hole binaries GW200105 and
 GW200115~\cite{LIGOScientific:2021qlt} while Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, obtained
@@
 %
-by stacking the posteriors of $\ell_{\rm GB}$ from a selection of black hole binaries (BBH)
-from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}\footnote{These bounds
-are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and
+by stacking the posteriors of $\ell_{\rm GB}$ from a selection of binary BHs (BBH)
+from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}~\footnote{These bounds
+are, strictly speaking, valid only when the scalar field $\varphi$ is small (i.e., $\varphi \ll 1$), and
 take into account only the leading-order scalar field contribution arising from the dilatonic coupling.}.
@@
 perturbations of polar parity can, for example break the equivalence
-between the QNM spectra of polar and axial gravitational perturbations
-(isospectrality~\cite{Chandrasekhar:1985kt}, see also Refs.~\cite{Glampedakis:2017rar,Lenzi:2021njy}) for Schwarzschild BHs in GR.
+between the QNM spectra of polar and axial gravitational \ab{perturbations~\cite{Glampedakis:2017rar,Lenzi:2021njy} 
+(i.e., the isospectrality~\cite{Chandrasekhar:1985kt}) for Schwarzschild BHs in GR.}
 %
@@
 These rotating BHs support a scalar field which fall off as
-$r^{-2}$ asymptically, to which we can associate a scalar dipole
+$r^{-2}$ asymptotically, to which we can associate a scalar dipole
 charge~\cite{Yunes:2009hc,Konno:2009kg}.
@@
 As a consequence, the leading-scalar radiative channel of BBH to lose energy is quadrupolar,
-which affects the GW phase at 2PN order~\cite{Yagi:2011xp,Alexander:2017jmt}.\agcomm{I am not sure I understand this sentence.}
-%
-Deviations from GR at this PN order are poorly constrained with present GW
-observations~\cite{LIGOScientific:2021sio}\agcomm{might want to quantify what we mean by poor.
-Looking at Table VI of the reference, I see that the 90\% credible bounds are $\sim 1-0\%$ using the hierarchical approach and $\sim 50\%$ using the restricted approach for $\varphi_4$.
-Perhaps we want to mention this?}, making dCS gravity unconstrained by
-analyses that rely on the inspiral portion of GWs from BBH
-binaries~\cite{Nair:2019iur,Perkins:2021mhb}.
-%
-Nonetheless, the theory has been constrained in Ref.~\cite{Silva:2020acr}, that found
+which affects the GW phase at 2PN order~\cite{Yagi:2011xp,Alexander:2017jmt}. 
+%
+Deviations from GR at this PN order are constrained with present GW observations~\cite{LIGOScientific:2021sio} 
+\ab{only at the level of $\sim 50\%$ (see the constraint on the 2PN parameter $\varphi_4$ in Fig.XXX of 
+Ref.~\cite{LIGOScientific:2021sio}). Thus, dCS gravity is poorly constrained by
+analyses that rely on the inspiral portion of GWs when using current BBH observations are used~\cite{Nair:2019iur,Perkins:2021mhb}.}
+%
+Nonetheless, the theory has been constrained in Ref.~\cite{Silva:2020acr}, which found
 %
@@
 %
-by folding data from the X-ray observations of the isolated neutron star (NS)
+by folding data from the X-ray observations of the isolated neutron star 
 PSR~J0030+0451~\cite{Lommen:2000yt,NANOGrav:2017wvv} by
 NICER~\cite{Riley:2019yda,Miller:2019cac} and from the GW observation of the binary
-neutron star (BNS) GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}.
+neutron star GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}.
 
 The QNMs of the Schwarzschild BH in dCS gravity were studied in
-Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb}, that found that scalar
-perturbations couple to gravitational perturbations of axial parity. (Contrast
-with EdGB gravity)\agcomm{Is the text in parenthesis a comment?}.
+Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb}, which found that scalar
+perturbations couple to gravitational perturbations of axial parity, \ab{in contrast
+with EdGB gravity.}
 %
@@
 %
-They were also extracted from numerical relativity (NR) simulations of head-on BH collisions
+They were also extracted from numerical-relativity simulations of head-on BH collisions
 in Ref.~\cite{Okounkova:2019dfo}.
 
-\subsection{Effective-field-theory of GR}
+\subsection{Effective-field-theory of General Relativity}
 
@@
     +
-    \sum_{n \geqslant 2} \ell^{2n - 2} L^{(2n)}
+    \sum_{n \geqslant 2} \ell_{\rm EFT}^{2n - 2}\, L^{(2n)}
     \right]\,,
@@
 %
-where $\ell$ is a length-scale assumed to be small compared to the length-scale
-$\ell / M \ll 1$ associated with a BH and $L^{(2n)}$ are corrections
+where $\ell_{\rm EFT}$ is a length-scale assumed to be small compared to the \ab{length-scale $M$ 
+associated with a BH (i.e., $\ell_{\rm EFT} / M \ll 1$),} and $L^{(2n)}$ are corrections
 that introduce higher-order curvature tensors (with $2n$ metric derivatives).
@@
 More specifically, we follow the notation of
-Refs.~\cite{Cano:2020cao,Cano:2021myl} and work up to dimension-eight operators
+Refs.~\cite{Cano:2020cao,Cano:2021myl} and \sout{work up} \ab{consider up} to dimension-eight operators
 ($n=4$),
@@
 %
-Due to the large number of free parameters in this theory, we will focus on a subset of the parameter space.
-%
-In particular, we will consider dimension-six and dimension-eight operators separately.
-%
-In the dimension-six case we further assume that $\lame = \lamo = 1$, leaving us with $\ell = \ell_{\rm cEFT}$
+Due to the large number of free parameters in this theory, we focus on a subset of the parameter space.
+%
+In particular, we consider dimension-six and dimension-eight operators separately.
+%
+\ab{For simplicity,} in the dimension-six case we further assume that $\lame = \lamo = 1$, leaving us with $\ell = \ell_{\rm cEFT}$
 as our single free parameter.
 %
-In the dimension-eight case, we will set $\varepsilon_{1} = 1$ and $\varepsilon_{2} = \varepsilon_{3} = 0$,
+\ab{Similarly,} in the dimension-eight case, we set $\varepsilon_{1} = 1$ and $\varepsilon_{2} = \varepsilon_{3} = 0$,
 as done in Ref.~\cite{Sennett:2019bpc}.
 %
-This leaves us with $\ell = \ell_{\rm qEFT}$ as our single free parameter \agcomm{Perhaps a bit of motivation about why we make these choices, even if it is to say that it is a simple first choice?}.
+This leaves us with $\ell = \ell_{\rm qEFT}$ as our single free parameter.
 
@@
 %
-Ref.~\cite{Cano:2020cao} calculated the leading-order BH spin corrections to the QNM spectra.
+Reference~\cite{Cano:2020cao} calculated the leading-order BH spin corrections to the QNM spectra.
 
@@
 $(m_1,\, m_2,\, \mathbf{S}_1,\, \mathbf{S}_2)$, the sky location determined by the
-luminosity distance $D_L$\abcomm{I cchanged to capital d because later we call the
+luminosity distance $D_L$\abcomm{I changed to capital $d$ because later we call the
 data ``d''.}, right ascension $\alpha$ and declination $\delta$,
@@
 %
-where the mass and spin of the remnant object $(M_f,\chi_f)$ are themselves functions of
+where the mass and spin of the remnant object $(M_{\rm f},\chi_{\rm f})$ are themselves functions of
 $(m_1,\, m_2,\, \chi_1,\, \chi_2)$~\cite{Taracchini:2013rva,Hofmann:2016yih}, and we fix $p$
@@
 % --------------------------------------------------------------------------------- %
-\section{Parameter Inference and validity of our analysis}
+\section{Parameter inference and validity of our bounds}
 \label{sec:pe}
@@
 \caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $(1 + z) \, M_f$ for GW150914, using the same waveform model,
+detector-frame remnant mass $(1 + z) \, M_{\rm f}$ for GW150914, using the same waveform model,
 but without (blue contours) \agcomm{colors are not up to date; needs to be
@@
 
-We start \sout{by showing our results for} \ag{with} EdGB gravity.
+We start with EdGB gravity.
 %
@@
 %
-The bottom panel shows the joint posterior from combining both events.
-%
-We see, for both events events, the $N_{\rm max} = 0$ posteriors are
+The bottom panel shows the joint posterior \ab{obtained by} combining both events.
+%
+We see, for both events, the $N_{\rm max} = 0$ posteriors are
 characterized by a peak away from zero.
@@
 %
-Recall that the deviations from GR in the ParSpec framework are controlled
-by $\gamma$, which here reads,
+\ab{We recall} that the deviations from GR in the ParSpec framework are controlled
+by \ab{the dimensionless parameter} $\gamma$, which here reads,
 %
@@
 As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm GB}$ does indeed have a posterior
-distribution with largest support at zero, indicating consistency between \sout{data}
-\ag{the underlying signal} \agcomm{whenever possible, I replaced ``data" when we
-meant signal, simply because earlier we defined data to also include noise, and by a
-GR prediction we conventionally refer to the signal. }
-and GR.
-%
-We also observe that the inclusion of the spin corrections (i.e., curves with $N_{\rm max} = 1$)
-displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$ \ag{(Fig.~\ref{fig:edgb_exec_sum}).
-and larger values of $\gamma_{\rm GB}$ (Fig.~\ref{fig:gamma_gb}).}
+distribution with largest support at zero, indicating consistency between 
+the underlying signal and GR.
+%
+We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
+displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$ (see Fig.~\ref{fig:edgb_exec_sum}), 
+and larger values of $\gamma_{\rm GB}$ (see Fig.~\ref{fig:gamma_gb}).
 
@@
 The joint posteriors are shown for illustrative purposes only. As we explain in Fig.~\ref{fig:edgb_cdf} and
-in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}.
-\agcomm{In all the figures of this kind, would it make sense to add grey vertical lines to
-mark the 68\% and 90\% upper credible intervals? This will help the reader to quickly cross check the numbers
-that are currently only mentioned in the text.}}
+in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}. \ab{We mark 
+with vertical lines theh $90\%$ upper credible intervals.}}
 \label{fig:edgb_exec_sum}
@@
 defined in Eq.~\eqref{eq:def_gamma_gb}. We see that this parameter controls the ParSpec expansion in EdGB gravity
-does have maximum support at $\gamma_{\rm GB} = 0$. This shows that our model is consistent with GR.
-\agcomm{I was thinking a bit more about the colors we choose for the plots, and I think Figs.
-1-2 should have a different set of colors from Figs.
-3-10.
-That is because the former have GR-nonGR comparisons, while the latter has comparisons between different spin corrections.
-Casual readers sometimes make an unconscious connection of quantities with colors.
-}}
+does have maximum support at $\gamma_{\rm GB} = 0$. This shows that our model is consistent with GR.}
 \label{fig:gamma_gb}
@@
 (black curves) and with (purple curves) linear in spin QNM corrections. The
-horizontal lines \sout{lay at 0.68 and 0.90}\ag{mark the 68\% and 90\% credible levels}.
-We see that in no situation the curves pass
-through the 0.68 or 0.90 lines even at $\varepsilon = 1$.
-\agcomm{Am I missing something something? The Nmax=1 lines for GW150914 does
-cross the credible levels, as well as the m2 Nmax=1 line for GW200129.}
-%
-This means that no bound on $\ell_{\rm GB}$ can be placed with the events we
-analyzed.
+horizontal lines mark the $90\%$ credible levels. \ab{Having set the maximum value 
+of $\varepsilon$ to be 1/2, we see} that in no situation the curves pass
+through the 0.90 lines. This means that no bound on $\ell_{\rm GB}$ can be placed 
+with the events we analyzed.
 }
@@
 
-As we emphasized in Sec.~\ref{sec:remarks}, we must first check whether the
+As we have emphasized in Sec.~\ref{sec:remarks}, we must first check whether the
 ``EFT''~\eqref{eq:eft_bound} and ``ParSpec''~\eqref{eq:parspec_bound} bounds
@@
 with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
-the remnant's mass ($\mathfrak{m} = M_f$, solid lines), while varying $\varepsilon$ between 0 and 1.
+the remnant's mass ($\mathfrak{m} = M_{\rm f}$, solid lines), while varying $\varepsilon$ between 0 and 1. 
 %
@@
 %
-Taken together we are led to \emph{conclude that we cannot constrain EdGB gravity with our
+\ab{For the case with $N_{\rm max} = 1$, we find that the ``EFT bound'' is satisfied 
+only for $\varepsilon \approx 0.8$ and $\approx1$ for GW150914 aand GW200129, respectively. 
+However, we set the maximum value of $\varepsilon$ to be 1/2, thus,} 
+taken together we are led to \emph{conclude that we cannot constrain EdGB gravity with our 
 present model}.
@@
 We can compare this conclusion with that of Ref.~\cite{Carullo:2021dui}, which obtained $\ell_{\rm GB} \lesssim 35$~km,
-by setting $p=4$, \emph{but not} including theory-specific QNM information on $\delta \omega^{(n)}$ and $\delta \tau^{(n)}$.
+by setting $p=4$, \emph{but not} including theory-specific QNM information on $\delta \omega^{(j)}$ and $\delta \tau^{(j)}$.
 %
@@
 %
-We see that EdGB provides an example of a theory in which the inspiral portion
-of the signal is more constraining then the ringdown portion of the signal.
+We see that EdGB provides an example of a theory in which, \ab{with current GW events,} the inspiral portion
+of the signal \ab{can be} more constraining than the ringdown portion of the signal.
 %
@@
 Ref.~\cite{Blazquez-Salcedo:2016enn}, the QNMs of EdGB BHs only differ slightly
-from their Schwarzschild counterparts. Second, the larger mass $M_f$ of the
+from their Schwarzschild counterparts. Second, the larger mass $M_{\rm f}$ of the
 remnant BH, suppresses scalar field's charge relatively to the initial binary
@@
 
-\subsection{Dynamical Chern-Simons}
+\subsection{Dynamical Chern-Simons gravity}
 \label{sec:results_dcs}
@@
 
-We now consider dCS gravity \ag{where the main results are summarised in Fig.~\ref{fig:dCS_exec_sum}}.
-%
-\sout{In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
-function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
-(middle panel), with different colors distinguishing cases with and without spin corrections to
-dominant $(2,2,0)$~QNM.}\agcomm{A lot of the language here is a repetition of the previous section.}
-%
-\sout{Perhaps the most salient feature of these posteriors is that they are not
-peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
-deviation from GR. This is not the case and the situation is that same as the
-one we discussed in the previous section for EdGB gravity.}
-\ag{As with EdGB gravity (Sec.~\ref{sec:results_edgb}) although the PDF of $\ell_{\rm CS}$
-is peaked away from 0, this does not signify a deviation from GR, as we have verified that,}
-%
-\sout{We verified that}
+We now consider dCS gravity where the main results are summarized in Fig.~\ref{fig:dCS_exec_sum}.
+%
+As with EdGB gravity (see Sec.~\ref{sec:results_edgb}) although the PDF of $\ell_{\rm CS}$
+is peaked away from 0, this does not signify a deviation from GR, as we have verified that,
 %
@@
 %
-We also see that in both cases that the inclusion leading-order-in-spin
-correction to the mode displaces the posteriors towards smaller values of
+We also see that in both cases the inclusion of leading-order--in-spin
+correction to the QNM displaces the posteriors towards smaller values of
 $\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
@@
 
-In Fig.~\ref{fig:dcs_cdf} we show the CDF
-\sout{obtained from Eq.~\eqref{eq:def_cdf}, with $\ell_{\rm max} = \Lambda_{\rm EFT} (\varepsilon, \gm)$,
-for both GW150914 (top panel) and GW200129 (bottom panel), where $\Lambda_{\rm EFT}$
-is calculated with either $\gm = m_2$ (dashed lines) or $M_{f}$ (solid lines),
-and in the range $\varepsilon \in [0,1]$.}
-%
-\sout{For}\ag{for} GW150914, we see that with $\gm = m_2$ that Eq.~\eqref{eq:eft_bound} is not
-satisfied unless $\varepsilon \approx 0.9$ (with only $n=0$ corrections) and
-$\varepsilon \approx 0.7$ (with both $n=0$ and $1$ corrections).
-%
-The situation is different if we use $\gm = M_f$. In this case, we find that
-with or without spin corrections that Eq.~\eqref{eq:eft_bound} can be satisfied
-with $\varepsilon \leqslant 1/2$, i.e., below the criteria used
-Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
-%
-This means that with our model's assumptions and using the remnant's source mass $M_f$ to set the
+In Fig.~\ref{fig:dcs_cdf} we show the CDF for GW150914, we see that with $\gm = m_2$, 
+Eq.~\eqref{eq:eft_bound} is not satisfied unless $\varepsilon \approx 0.9$ (with only $j=0$ corrections) and
+$\varepsilon \approx 0.7$ (with both $j=0$ and $1$ corrections).
+%
+The situation is different if we use $\gm = M_{\rm f}$. In this case, we find that
+with or without spin corrections Eq.~\eqref{eq:eft_bound} can be satisfied
+with $\varepsilon \leqslant 1/2$ (i.e., below the criteria used
+Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}).
+%
+This means that with our model's assumptions and using the remnant's source mass $M_{\rm f}$ to set the
 cut-off scale that we can claim an upper bound
@@
 \ell_{\rm CS} \leqslant 42.6~\textrm{km}
-\quad \textrm{(90\% credibility)},
-\end{equation}
-\agcomm{I am not familiar with the term ``credibility", and am more used to the phrase, ``at X\% credible level".
-Are they the same thing?}
-%
-on dCS gravity and would constitute \emph{the first bound on this theory with
-gravitational-wave observations alone}.\agcomm{Since this is an extremely important
-result, would it make sense to reorder the theories such that dCS comes first among results?}
+\quad \textrm{at 90\% credible level},
+\end{equation}
+%
+on dCS gravity and would constitute \emph{the first bound on this theory with GW 
+observations alone}. 
 %
@@
 % ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
-\quad \textrm{at 68\% credibility},
+\quad \textrm{at 68\% credible level},
 \end{equation}
@@
 % 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
-\quad \textrm{(90\% credibility)},
+\quad \textrm{at 90\% credible level},
 \end{equation}
@@
 % ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
-\quad \textrm{(68\% credibility)},
+\quad \textrm{at 68\% credible level},
 \end{equation}
@@
 for GW200129 (compare the top and middle panels in Fig.~\ref{fig:dCS_exec_sum}), and in part due to
-the smaller median remnant ($M_{f} \approx 59.5\msun$ versus $M_{f} \approx 61.8\msun$ for GW150914).
-%
-\hs{Should we remove these and just quote the 90\% results?}\agcomm{I think
-it's fine to give point estimates, because it's easier for reader to interpret results
-rather than having to make sense of error bars.}
-
-We also found for both GW events, that the
-perturbative-conditions~\eqref{eq:parspec_bound} required by the ParSpec
+the smaller median remnant ($M_{\rm f} \approx 59.5\msun$ versus $M_{\rm f} \approx 61.8\msun$ for GW150914).
+%
+We also found for both GW events, that the perturbative-conditions~\eqref{eq:parspec_bound} required by the ParSpec
 formalism is violated for the $\gamma_{\rm CS} \, \delta \tau^{(1)}$ coefficient.
 %
-This means that we cannot use these posterior to infer any meaningful bound on dCS gravity
+This means that we cannot use this posterior to infer any meaningful bound on dCS gravity
 and that is why we quoted only the $N_{\rm max}=0$ bound above.
 
-Finally, since both events individually led to a bound on $\ell_{\rm CS}$
-(assuming a cut-off scale for $\gm = M_{f}$ and $N_{\rm max}=0$), we can combine the
+Finally, since both events individually lead to a bound on $\ell_{\rm CS}$
+(assuming a cut-off scale for $\gm = M_{\rm f}$ and $N_{\rm max}=0$), we can combine the
 posteriors to obtain the cumulative bound,
@@
 \ell_{\rm CS} \leqslant 38.7~\textrm{km}
-\quad \textrm{(90\% credibility)},
+\quad \textrm{ at 90\% credible level},
 \end{equation}
@@
 This bound is approximately a factor of four weaker than that placed by
-Ref.~\cite{Silva:2020acr}, but
-%
-(i) relies only on GW observations and
+Ref.~\cite{Silva:2020acr}, but \ab{it}
+%
+(i) relies only on GW observations, and
 %
 (ii) suggests that a ringdown analysis can potentially place constraints on
-theories which evade GW tests using inspiral information alone, such as the
+theories \ab{that, with current GW events, can evade GR tests} using inspiral information alone, such as the
 case of dCS gravity~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
@@
 \caption{Detailed summary of our results for dCS gravity for GW150914, GW200129, and
-combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible bounds.
+combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$ and quoting only 90\% credible bounds.
 %
@@
 The combined bound, which is also quoted in Table~\ref{tab:ref_theories_qnms},
-is $\ell_{\rm CS} \leqslant 38.7$~km.
+is $\ell_{\rm CS} \leqslant 38.7$~km \ab{at 90\% credible level}.
 }
@@
 
-\subsection{Cubic Effective-Field-Theory of General Relativity}
-\label{sec:results_ceft}
-
-We now consider the cubic EFT of GR.
-%
-In Fig.~\ref{fig:cEFT_exec_sum} we show the marginalized posterior distributions
-functions of $\ell_{\rm cEFT}$ for GW150914 (top panel) and GW200129 (middle panel),
-with different curve colors corresponding to different $N_{\rm max}$ in
-the spin expansion.
-%
-We find that in this theory, the posterior distributions are mostly uniform for
-$\ell_{\rm cEFT} \lesssim 40$~km (contrast this with the EdGB and dCS gravity
-cases; cf.~Figs.~\ref{fig:edgb_exec_sum} and~\ref{fig:dCS_exec_sum}).
-%
-For values $\ell_{\rm cEFT} \gtrsim 40$~km, the posteriors smoothly approach zero.
-
-In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
-same way as already described for the EdGB and dCS theories.
-%
-We see that curves are very similar to those of dCS gravity for GW200129 (cf.
-bottom panel in Fig.~\ref{fig:cEFT_cdf}).
-%
-Moreover, we find that the EFT~\eqref{eq:eft_bound} and
-ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
-$\mathfrak{m} = M_f$ and $\epsilon = 1/2$.
-%
-This allows us to place the combined bound of
-%
-\begin{equation}
-    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km}\,,
-\end{equation}
-%
-at 90\% credibility. As also happened for our study for dCS, the find that for
-the cubic EFT that the ParSpec bound is violated by the $N_{\rm max} = 1$ corrections to
-the QNMs, meaning that we cannot use this case to draw any meaningful
-constraint on this parameter.
-%
-We summarize our results in Table~\ref{tab:summary_ceft}.
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm cEFT}$ for
-GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-%
-The colors distinguish different $N_{\rm max}$ in the spin expansion.
-}
-\label{fig:cEFT_exec_sum}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold.pdf}
-\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for the cubic EFT of GR.
-We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
-1/2$ for both events, with and without including the $n = 1$ corrections to
-the dominant QNM.
-}
-\label{fig:cEFT_cdf}
-\end{figure}
-
-\begin{table}[b]
-\begin{tabular}{l l c c c}
-\hline
-\hline
-$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
-              &       & bound? & bound?  &                            \\
-\hline
-  & GW150914  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 38.2$~km \\
-0 & GW200129  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 42.5$~km \\
-  & Combined  &     &     &  \cellcolor{black!10}$\ell_{\rm cEFT} \leqslant 38.2$~km \\
-\hline
-  & GW150914  & Yes  & No  &  -- \\
-1 & GW200129  & Yes  & No  &  -- \\
-  & Combined  &      &     &  -- \\
-\hline
-\hline
-\end{tabular}
-\caption{Detailed summary of our results the cubic EFT of GR for GW150914, GW200129, and
-combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
-}
-\label{tab:summary_ceft}
-\end{table}
-
-\subsection{Quartic Effective-Field-Theory of General Relativity}
-\label{sec:results_qeft}
-
-Let us now consider the quartic EFT of GR as our final example.
-%
-In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
-GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR.
-%
-We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
-hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
-%
-As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_f$ before $\varepsilon = 1/2$.
-%
-Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
-%
-\begin{equation}
-    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km}\,.
-\end{equation}
-
-In this theory, we considered only $N_{\rm max} = 0$. We found that the
-inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
-for which the ringdown portions of the larger than the inspiral-plunge part \dots
-%
-To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
-which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
-%
-Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
-%
-\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ simulations are breaking down other than
-we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}
-\agcomm{At the point of me going through this para, I am yet to figure out what's happening inside the code.
-Hence I have not modified this text, but hopefully will have something over the coming days
-to sure up this point.}
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
-GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-}
-\label{fig:qEFT_exec_sum}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
-\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
-We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
-can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_f$ for both events at 90\% credibility.
-}
-\label{fig:qEFT_cdf}
-\end{figure}
-
-\begin{table}[h]
-\begin{tabular}{l l c c c}
-\hline
-\hline
-$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
-              &       & bound? & bound?  &                            \\
-\hline
-  & GW150914 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 51.7$~km \\
-0 & GW200129 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 54.8$~km \\
-  & Combined &     &      & \cellcolor{black!10}$\ell_{\rm qEFT} \leqslant 51.3$~km \\
-% \hline
-%   & GW150914 &  &     &    \\
-% 1 & GW200129 &  &     &    \\
-%   & Combined &  &     &    \\
-\hline
-\hline
-\end{tabular}
-\caption{Detailed summary of our results the quartic EFT of GR for GW150914, GW200129, and
-combined events using $\gm = M_{f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$. The quoted
-result correspond to 90\% credible values.
-}
-\label{tab:summary_qeft}
-\end{table}
-
-% \begin{figure}[t]
-% \includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
-% \caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
-% The posterior shows that information was gained on this parameter relative to
-% the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
-% %
-% The vertical lines represent two threshold for the validity of the theory as
-% an EFT.
-% %
-% The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
-% given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
-% %
-% The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
-% given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
-% %
-% For both, we used $\varepsilon = 0.5$.
-% %
-% If we take the latter as a length scale for the validity of dCS as an EFT, we
-% have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
-% approximation of our formalism.
-% }
-% \label{fig:dCS_bounds}
-% \end{figure}
-%
-% \begin{figure}[t]
-% \includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
-% \caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
-% The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
-% in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
-% }
-% \label{fig:dCS_gamma_plot}
-% \end{figure}
-
 \sout{In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
-detector-frame remnant mass $(1 + z) M_f$ for GW150914 for GR and the
+detector-frame remnant mass $(1 + z) M_{\rm f}$ for GW150914 for GR and the
 illustrative case of dCS gravity. We see that our waveform models does not
@@
 
+\subsection{Cubic Effective-FieXld-Theory of General Relativity}
+\label{sec:results_ceft}
+
+We now consider the cubic EFT of GR.
+%
+In Fig.~\ref{fig:cEFT_exec_sum} we show the marginalized posterior distributions
+functions of $\ell_{\rm cEFT}$ for GW150914 (top panel) and GW200129 (middle panel),
+with different curve colors corresponding to different $N_{\rm max}$ in
+the spin expansion.
+%
+We find that in this theory, the posterior distributions are mostly uniform for
+$\ell_{\rm cEFT} \lesssim 40$~km (contrast this with the EdGB and dCS gravity
+cases in Figs.~\ref{fig:edgb_exec_sum} and~\ref{fig:dCS_exec_sum}).
+%
+For values $\ell_{\rm cEFT} \gtrsim 40$~km, the posteriors smoothly approach zero.
+
+In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
+same way as already described for the EdGB and dCS theories.
+%
+We see that curves are very similar to those of dCS gravity for GW200129 (see 
+bottom panel in Fig.~\ref{fig:cEFT_cdf}).
+%
+Moreover, we find that the EFT~\eqref{eq:eft_bound} and
+ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
+$\mathfrak{m} = M_{\rm f}$ and $\varepsilon = 1/2$.
+%
+This allows us to place the combined bound of
+%
+\begin{equation}
+    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km} \quad \textrm{at 90\% credible level}\,.
+\end{equation}
+%
+As also happened for our study for dCS, the find that, for
+the cubic EFT, the ParSpec bound is violated by the $N_{\rm max} = 1$ corrections to
+the QNMs, meaning that we cannot use this case to draw any meaningful
+constraint on this parameter.
+%
+We summarize our results in Table~\ref{tab:summary_ceft}.
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm cEFT}$ for
+GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+The colors distinguish different $N_{\rm max}$ in the spin expansion.
+}
+\label{fig:cEFT_exec_sum}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold.pdf}
+\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for the cubic EFT of GR.
+We see that the CDF curves for $\gm = M_{\rm f}$ are above 90\% for $\varepsilon =
+1/2$ for both events, with and without including the $j = 1$ corrections to
+the dominant QNM.
+}
+\label{fig:cEFT_cdf}
+\end{figure}
+
+\begin{table}[b]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+              &       & bound? & bound?  &                            \\
+\hline
+  & GW150914  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 38.2$~km \\
+0 & GW200129  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 42.5$~km \\
+  & Combined  &     &     &  \cellcolor{black!10}$\ell_{\rm cEFT} \leqslant 38.2$~km \\
+\hline
+  & GW150914  & Yes  & No  &  -- \\
+1 & GW200129  & Yes  & No  &  -- \\
+  & Combined  &      &     &  -- \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results the cubic EFT of GR for GW150914, GW200129, and
+combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+}
+\label{tab:summary_ceft}
+\end{table}
+
+\subsection{Quartic Effective-Field-Theory of General Relativity}
+\label{sec:results_qeft}
+
+Let us now consider the quartic EFT of GR, as our final example.
+%
+In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
+GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR.
+%
+We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
+hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
+%
+As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_{\rm f}$ before $\varepsilon = 1/2$.
+%
+Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
+%
+\begin{equation}
+    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level}\,.
+\end{equation}
+%
+\abcomm{Please update the paragraph below.} 
+In this theory, we have considered only $N_{\rm max} = 0$. We found that the
+inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
+for which the ringdown portions of the larger than the inspiral-plunge part \dots
+%
+To avoid this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
+which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
+%
+Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
+%
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
+GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+}
+\label{fig:qEFT_exec_sum}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
+\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
+We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
+can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 90\% credibility.
+}
+\label{fig:qEFT_cdf}
+\end{figure}
+
+\begin{table}[h]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+              &       & bound? & bound?  &                            \\
+\hline
+  & GW150914 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 51.7$~km \\
+0 & GW200129 & Yes & Yes  & $\ell_{\rm qEFT} \leqslant 54.8$~km \\
+  & Combined &     &      & \cellcolor{black!10}$\ell_{\rm qEFT} \leqslant 51.3$~km \\
+% \hline
+%   & GW150914 &  &     &    \\
+% 1 & GW200129 &  &     &    \\
+%   & Combined &  &     &    \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results the quartic EFT of GR for GW150914, GW200129, and
+combined events using $\gm = M_{f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$. The quoted
+result correspond to 90\% credible values.
+}
+\label{tab:summary_qeft}
+\end{table}
+
+% \begin{figure}[t]
+% \includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
+% \caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
+% The posterior shows that information was gained on this parameter relative to
+% the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
+% %
+% The vertical lines represent two threshold for the validity of the theory as
+% an EFT.
+% %
+% The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
+% given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
+% %
+% The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
+% given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
+% %
+% For both, we used $\varepsilon = 0.5$.
+% %
+% If we take the latter as a length scale for the validity of dCS as an EFT, we
+% have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
+% approximation of our formalism.
+% }
+% \label{fig:dCS_bounds}
+% \end{figure}
+%
+% \begin{figure}[t]
+% \includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
+% \caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
+% The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
+% in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
+% }
+% \label{fig:dCS_gamma_plot}
+% \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We presented an unified framework to combine the framework introduced
+We presented an \ab{unified framework to combine the ParSpec formalism} introduced
 to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
 %
-We showed with concrete examples how theory-specific calculations QNM of
+We showed with concrete examples, \ab{how theory-specific QNM calculations of
 slowly-rotating BHs in modified gravity theories can be mapped onto the
-theory-agnostic beyond-GR parameters of the ParSpec formalism.
+non-GR parameters of the ParSpec formalism}.
 %
@@
 modified gravity theories (EdGB, dCS, cubic, and quartic EFTs of GR) using
-observational data from the GW events GW150914 and GW200129.
-%
-We found, in particular that, within the assumptions of our model and by
-stacking posteriors, that the coupling constant of dCS gravity is bound to
-$\ell_{\rm CS} \leqslant 34.5$~km.
+observational data from the LIGO-Virgo-KAGRA's events GW150914 and GW200129.
+%
+We found, in particular that, \ab{within the interpretation of our non-GR theories as EFTs and the 
+region of validity of the ParSpec framework, the coupling constant of dCS gravity is bound to
+$\ell_{\rm CS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors 
+of GW150914 and GW200129.}
 %
@@
 
-We can now proceed to determine $\delta\omega^{(n)}$ and $\delta\tau^{(n)}$ as follows.
+We can now proceed to determine $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$ as follows.
 %
@@
 We remark that the alarmingly large values of $\delta \omega_{\rm CS}^{(1)}$ and $\delta \tau_{\rm CS}^{(1)}$
-are compensated by the assumptions that $(\ell_{\rm CS} / M_f)^2$ and $\chi$ are much less than unity. These
+are compensated by the assumptions that $(\ell_{\rm CS} / M_{\rm f})^2$ and $\chi$ are much less than unity. These
 are the assumptions used to calculate the QNM frequencies in Ref.~\cite{Wagle:2021tam}.

### 2022-04-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: change to contour plot caption
hs: added missing dashed to parspec table

@@
 \hline
-EdGB        & --                   & --                 &  --                  &                    & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
-dCS         & --                   & --                 &  --                  &                    & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
-cubic EFT   & --                   & --                 &  --                  &                    & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
-quartic EFT & --                   & --                 &  --                  &                    & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
+EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
+dCS         & --                   & --                 &  --                  & --                 & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
+cubic EFT   & --                   & --                 &  --                  & --                 & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
+quartic EFT & --                   & --                 &  --                  & --                 & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
 \hline
@@
 %
-We see that the introduction of the non-GR parameters does not bias the
+We see that the addition of the non-GR parameters does not introduce biases in the
 inference of the source parameters.

### 2022-04-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
zenodo bib info

@@
 \label{app:map_details}
-% HS: done.
-% \agcomm{Reorder sections, such that the appendix comes after the Acknowledgments?}
-
-% \agcomm{Have not gone through the appendices, because there might be sections that still
-% need to be completed.}
 
@@
 %
-In Ref.~\cite{Wagle:2021tam} the QNMs of slow-rotating BHs in dCS gravity were calculated
+In Ref.~\cite{Wagle:2021tam} the QNMs of slowly-rotating BHs in dCS gravity were numerically determined
 and it was found that the axial gravitational modes have their damping time increased as we
@@
 \begin{equation}
-    M \omega_{\rm CS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+    M_{\rm f} \omega_{\rm CS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
     \label{eq:omega_dsc_eg}
@@
 %
-Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M^4 \kappa)$, and thus
-%
-\begin{equation}
-\kappa \zeta = (\ell_{\rm CS} / M)^4 \,,
+Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M_{\rm f}^4 \kappa)$, and thus
+%
+\begin{equation}
+    \kappa \zeta = (\ell_{\rm CS} / M_{\rm f})^4 \,,
 \end{equation}
@@
 and $c_{i}$ are fitting coefficients which can be found in Ref.~\cite{Wagle:2021tam}, Table II.
-%
-In the context of a binary BH merger, $M$ is interpreted as the remnant mass $\Mf$.
 
@@
 \begin{align}
-    \Mf \, \omega_{\rm CS} &=
-    \left[ 0.3722 + 1.1945 (\ell_{\rm CS} / \Mf)^4 \right]
+    M_{\rm f} \, \omega_{\rm CS} &=
+    \left[ 0.3722 + 1.1945 (\ell_{\rm CS} / M_{\rm f})^4 \right]
     \nonumber \\
-    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm CS} / \Mf)^4 \right] \, \chi\,,
+    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm CS} / M_{\rm f})^4 \right] \, \chi\,,
     \label{eq:omega_dcs_interm}
@@
 
-% \bibliographystyle{apsrev}
+The QNMs of slowly-rotating BHs in both cubic and quartic EFT of GR where calculated in Ref.~\cite{Cano:2021myl}.
+
 \bibliography{paper_alt_theor_bounds}

### 2022-04-19 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
fixing  typos

@@
 = \left[
-\frac{\ell c^2 (1 + z)}{G M_{\rm f}}
+\frac{\ell_{\rm th} c^2 (1 + z)}{G M_{\rm f}}
 \right]^{p},
@@
 $\phi_0$. If we further assume that the spins of the individual BHs are
-restricted to be \sout{parallel} \ab{aligned or anti-aligned (for short, aligned)} to the unit vector
+restricted to be \sout{parallel} \ab{aligned or anti-aligned (for short, aligned) to the unit vector
 perpendicular to the orbital plane ($\mathbf{\hat{L}}$), we reduce the six
 components of the spins to just two, $\chi_i \equiv \mathbf{S}_i\cdot \mathbf{\hat{L}} /m_i^2$ with $i = 1,2$,
-and our entire parameter set from 15 to 11.
+and our entire parameter set from 15 to 11.}
 %

### 2022-04-20 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: night revisions

@@
 \usepackage{xspace}
+
 \usepackage[normalem]{ulem} % To get strikethrough (\sout)
+\newcommand\redsout{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{8pt}{1pt}}}\ULon} % To get a red strikethrough
+% (which is easier to spot)
+
 \usepackage[colorlinks]{hyperref}
@@
 \usepackage{xcolor}
-\newcommand{\agcomm}[1]{{\textcolor{red}{{[AG: #1]}} }}
-\newcommand{\ag}[1]{{\textcolor{Maroon}{{#1}} }}
-\newcommand{\hs}[1]{{\textcolor{blue}{{[HS: #1]}} }}
-\newcommand{\ab}[1]{{\textcolor{cyan}{{#1}} }}
-\newcommand{\abcomm}[1]{{\textcolor{red}{{[AB: #1]}} }}
+\newcommand{\agcomm}[1]{{\textcolor{red}{{[AG: #1]}}}}
+\newcommand{\ag}[1]{{\textcolor{Maroon}{{#1}}}}
+\newcommand{\hs}[1]{{\textcolor{TealBlue}{{#1}}}}
+\newcommand{\hscomm}[1]{{\textcolor{TealBlue}{{[HS: #1]}}}}
+\newcommand{\ab}[1]{{\textcolor{cyan}{{#1}}}}
+\newcommand{\abcomm}[1]{{\textcolor{red}{{[AB: #1]}}}}
 
@@
 %
-\ab{Some of these gravitational-wave events have sufficiently high
+Some of these gravitational-wave events have sufficiently high
 signal-to-noise ratio in the merger, allowing us to probe the relaxation of the remnant black
-hole to its final, stationary state --- the so-called black-hole ringdown, which is}
+hole to its final, stationary state --- the so-called black-hole ringdown, which is
 characterized by a set of quasinormal modes.
@@
 % What we do:
-Here, we \sout{take a first step to} address this question by using an
-inspiral-merger-ringdown waveform model in the effective-one-body formalism,
-augmented with a parametrization of the ringdown based on an expansion \ab{in} the
-final black hole's spin.
-%
-We give a prescription on how to include \ab{in} this waveform model the quasinormal mode frequencies
-calculated on a theory-by-theory basis. \ab{In particular, we focus on gravity} theories that deviate
+Here, we  address this question by using an inspiral-merger-ringdown waveform
+model in the effective-one-body formalism, augmented with a parametrization of
+the ringdown based on an expansion in the final black hole's spin.
+%
+We give a prescription on how to include in this waveform model the quasinormal mode frequencies
+calculated on a theory-by-theory basis. In particular, we focus on gravity theories that deviate
 from general relativity through higher-order curvature corrections, namely,
@@
 % Main conclusion:
-We confront the resultant waveform models against \ab{the two loudest gravitational-wave ringdown signals, so far,
-  notably, GW150914 and GW200129. We find} that while the Einstein-dilaton-Gauss-Bonnet theory cannot be constrained with
-these events, we can place upper bounds on the coupling constants of cubic-
-($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order ($\ell_{\rm qEFT}
-\leqslant 51.3$~km) effective-field-theories of general relativity, and
-of dynamical Chern-Simons gravity ($\ell_{\rm CS} \leqslant 38.7$~km).
-%
-The latter result is a concrete example of a theory presently
-unconstrained by inspiral-only analyses which, however, can be constrained by
-merger-ringdown studies \ab{with current gravitational-wave data}.
+We confront the resultant waveform models against the two loudest
+gravitational-wave ringdown signals, so far, notably, GW150914 and GW200129.
+%
+We find that while the Einstein-dilaton-Gauss-Bonnet theory cannot be
+constrained with these events, we can place upper bounds on the coupling
+constants of cubic- ($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order
+($\ell_{\rm qEFT} \leqslant 51.3$~km) effective-field-theories of general
+relativity, and of dynamical Chern-Simons gravity ($\ell_{\rm dCS} \leqslant 38.7$~km).
+%
+The latter result is a concrete example of a theory presently unconstrained by
+inspiral-only analyses which, however, can be constrained by merger-ringdown
+studies with current gravitational-wave data.
+%
 \end{abstract}
@@
 \begin{equation} \label{eq:action_sgb}
-    S_{\rm GB} = \frac{1}{16 \pi}
+    S_{\rm EdGB} = \frac{1}{16 \pi}
     \int \dV
@@
     R - \tfrac{1}{2}(\nabla \varphi)^2
-    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \, \mathcal{G}
+    + \tfrac{1}{4} \ell^{2}_{\rm EdGB} f(\varphi) \, \mathcal{G}
     \right]\,,
@@
 %
-where \ab{$g \equiv \textrm{det}(g_{\mu \nu})$} is the metric determinant, $R$ is the Ricci
+where $g \equiv \textrm{det}(g_{\mu \nu})$ is the metric determinant, $R$ is the Ricci
 scalar, $\varphi$ is a dynamical scalar field that couples to the
@@
 %
-In the first class, the first derivative of the coupling function $f'(\varphi) \equiv \dd f  / \dd \varphi$
-is always nonzero and BHs are known to always support scalar hair.
-%
-This is the case of Einstein-dilaton-Gauss-Bonnet (EdGB) gravity, for which $f(\varphi) = \exp(\varphi)$~\cite{Kanti:1995vq}.
-%
-% \begin{equation}
-% f = \exp(\varphi)\,,
-% \end{equation}
+In the first class, the first derivative of the coupling function $f'(\varphi)
+\equiv \dd f  / \dd \varphi$ is always nonzero and BHs are known to always
+support scalar hair.
+%
+This is the case of Einstein-dilaton-Gauss-Bonnet (EdGB) gravity, for which
+$f(\varphi) = \exp(\varphi)$~\cite{Kanti:1995vq}.
 %
@@
 In this case, the theory admits the same stationary, asymptotically flat BH
-solutions as GR and those of scalarized BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
+solutions as GR and those of scalarized
+BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
 %
@@
 BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
-related to the asymptotic $r^{-1}$ fall-off of the scalar field, \ab{where $r$ is the distance from the BH.}
-%
-This charge is not an independent parameter, and depends on the BH's mass and spin, %~\cite{Berti:2018cxi},
+related to the asymptotic $r^{-1}$ fall-off of the scalar field, where $r$ is the distance from the BH.
+%
+This charge is not an independent parameter, and depends on the BH's mass and spin,
 thus being a ``secondary hair''~\cite{Coleman:1991ku,Herdeiro:2015waa}.
@@
 Since the scalar field is sourced by a curvature scalar, $Q$ is larger (smaller),
-\ab{the} smaller (larger) the BH mass is.
+the smaller (larger) the BH mass is.
 
@@
 scalar-dipole radiation (see, e.g., Refs.~\cite{Yagi:2011xp,Julie:2019sab,Shiralilou:2020gah,Shiralilou:2021mfl,Julie:2022huo})
-which affects the GW phase at $-1$PN order (relative to the dominant \ab{quadrupolar} GR
+which affects the GW phase at $-1$PN order (relative to the dominant quadrupolar GR
 contribution), with magnitude proportional to the difference between the
 charges of binary components. This makes EdGB gravity testable with present GW
-observations of compact binaries where at least \ab{if} one component is a BH.
+observations of compact binaries where at least if one component is a BH.
 %
@@
 %
-$\ell_{\rm GB} \leqslant 1.33$~km
+$\ell_{\rm EdGB} \leqslant 1.33$~km
 %
@@
 %
-$\ell_{\rm GB} \leqslant 1.7$~km,
-%
-by stacking the posteriors of $\ell_{\rm GB}$ from a selection of binary BHs (BBH)
+$\ell_{\rm EdGB} \leqslant 1.7$~km,
+%
+by stacking the posteriors of $\ell_{\rm EdGB}$ from a selection of binary BHs (BBH)
 from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}~\footnote{These bounds
@@
 perturbations of polar parity can, for example break the equivalence
-between the QNM spectra of polar and axial gravitational \ab{perturbations~\cite{Glampedakis:2017rar,Lenzi:2021njy}
-(i.e., the isospectrality~\cite{Chandrasekhar:1985kt}) for Schwarzschild BHs in GR.}
+between the QNM spectra of polar and axial gravitational perturbations~\cite{Glampedakis:2017rar,Lenzi:2021njy}
+(i.e., the isospectrality~\cite{Chandrasekhar:1985kt}) for Schwarzschild BHs in GR.
 %
@@
 %
-\begin{equation} \label{eq:action_dcs}
-    S_{\rm CS} = \frac{1}{16 \pi}
+\begin{align} \label{eq:action_dcs}
+    S_{\rm dCS} = \frac{1}{16 \pi}
     \int \dV
@@
     R - \tfrac{1}{2}(\nabla \vartheta)^2
-    + \tfrac{1}{4} \ell^{2}_{\rm CS} \, \vartheta \, {}^{*}RR
+    + \tfrac{1}{4} \ell^{2}_{\rm dCS} \, \vartheta \, {}^{*}RR
     \right],
-\end{equation}
+    \nonumber \\
+\end{align}
 %
@@
 %
-The coupling strength is set by the coupling constant $\ell_{\rm CS}$, with
+The coupling strength is set by the coupling constant $\ell_{\rm dCS}$, with
 dimensions of length.
@@
 %
-$\ell_{\rm CS} \leqslant 8.5$~km,
+$\ell_{\rm dCS} \leqslant 8.5$~km,
 %
@@
 Refs.~\cite{Yunes:2007ss,Cardoso:2009pk,Molina:2010fb}, which found that scalar
-perturbations couple to gravitational perturbations of axial parity, \ab{in contrast
-with EdGB gravity.}
+perturbations couple to gravitational perturbations of axial parity, in contrast
+with EdGB gravity.
 %
 This leads to a breakdown of isospectrality. The QNM spectra of slowly-rotating BHs in dCS gravity was
-studied in Ref.~\cite{Wagle:2021tam}.
+studied in Ref.~\cite{Srivastava:2021imr,Wagle:2021tam}.
 %
@@
 %
-where $\ell_{\rm EFT}$ is a length-scale assumed to be small compared to the \ab{length-scale $M$
-associated with a BH (i.e., $\ell_{\rm EFT} / M \ll 1$),} and $L^{(2n)}$ are corrections
+where $\ell_{\rm EFT}$ is a length-scale assumed to be small compared to the length-scale $M$
+associated with a BH (i.e., $\ell_{\rm EFT} / M \ll 1$), and $L^{(2n)}$ are corrections
 that introduce higher-order curvature tensors (with $2n$ metric derivatives).
@@
 More specifically, we follow the notation of
-Refs.~\cite{Cano:2020cao,Cano:2021myl} and \sout{work up} \ab{consider up} to dimension-eight operators
-($n=4$),
+Refs.~\cite{Cano:2020cao,Cano:2021myl} and consider up to dimension-eight
+operators ($n=4$),
 %
@@
 $\tilde{\cal C} = R_{\mu\nu\gamma\delta} \epsilon^{\mu\nu}{}_{\rho\sigma} R^{\rho\sigma\gamma\delta}$,
-and $(\lambda_{\rm o, e},\varepsilon_{i})$,  $i=1,2,3$, are dimensionless parameters.
+and $(\lambda_{\rm o, e},\varepsilon_{i})$, $i=$~1, 2, 3, are dimensionless parameters.
 %
@@
 %
-\ab{For simplicity,} in the dimension-six case we further assume that $\lame = \lamo = 1$, leaving us with $\ell = \ell_{\rm cEFT}$
-as our single free parameter.
-%
-\ab{Similarly,} in the dimension-eight case, we set $\varepsilon_{1} = 1$ and $\varepsilon_{2} = \varepsilon_{3} = 0$,
+In addition, in the dimension-six case we further assume that $\lame = \lamo = 1$,
+leaving us with \redsout{$\ell =$} $\ell_{\rm cEFT}$ as our single free parameter.
+%
+Similarly, in the dimension-eight case, we set $\varepsilon_{1} = 1$ and $\varepsilon_{2} = \varepsilon_{3} = 0$,
 as done in Ref.~\cite{Sennett:2019bpc}.
 %
-This leaves us with $\ell = \ell_{\rm qEFT}$ as our single free parameter.
+This leaves us with \redsout{$\ell =$} $\ell_{\rm qEFT}$ as our single free parameter.
 
@@
 %
-\hs{Alessandra, can you include a short description of~\cite{Sennett:2019bpc} for the quartic EFT?}
+\hscomm{Alessandra, can you include a short description of~\cite{Sennett:2019bpc} for the quartic EFT?}
 
@@
 
-\ab{Having reviewed the modified gravity theories that we will consider, we now present
+Having reviewed the modified gravity theories that we will consider, we now present
 the sequential building blocks for the waveform model we use to test these theories
@@
 %
-We start by reviewing the parametrized ringdown spin-expansion coefficients (ParSpec) framework in Sec.~\ref{sec:review_parspec}.
+We start by reviewing the parametrized ringdown spin-expansion coefficients
+(ParSpec) framework~\cite{Maselli:2019mjd} in Sec.~\ref{sec:review_parspec}.
 %
@@
 theory-specific QNM calculations in modified gravity theories onto the
-free coefficients in the ParSpec framework.}
+free coefficients in the ParSpec framework.
 %
@@
 
-\ab{A general procedure to describe deviations to the QNM frequencies $\omega^{\rm GR}_{\ell m n}$ and
-damping times $\tau^{\rm GR}_{\ell m n}$ of the GR BH is to write,}
+A general procedure to describe deviations to the QNM frequencies $\omega^{\rm GR}_{\ell m n}$ and
+damping times $\tau^{\rm GR}_{\ell m n}$ of BHs of GR is to write,
 %
@@
 %
-\ab{where $\delta\omega_{\ell m n}$ and $\delta\tau_{\ell m  n}$ are the fractional deformation parameters,
-$\ell$ and $m$ are the multipole indices, and $n$ the overtone number.}
-%
-This type of parametrization was adopted, for instance, in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Brito:2018rfr,Carullo:2018sfu,Ghosh:2021mrv}.
+where $\delta\omega_{\ell m n}$ and $\delta\tau_{\ell m  n}$ are the fractional deformation parameters,
+$\ell$ and $m$ are the multipole indices, and $n$ the overtone number.
+%
+This type of parametrization\footnote{\hs{See also
+Refs.~\cite{Glampedakis:2017dvb,Glampedakis:2019dqh,Silva:2019scu} and
+Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj,Kimura:2020mrh} for alternative parametrizations.}}
+was adopted, for instance, in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Brito:2018rfr,Carullo:2018sfu,Ghosh:2021mrv}.
 
@@
 of Ref.~\cite{LIGOScientific:2020tif} or Sec.VIII.A
-of Ref.~\cite{LIGOScientific:2021sio}) take a restrictive \ab{theory-independent}
+of Ref.~\cite{LIGOScientific:2021sio}) take a restrictive theory-independent
 approach towards the inference of $\delta\omega_{\ell m n}$ and
@@
 
-\ab{The ParSpec framework was introduced in Ref.~\cite{Maselli:2019mjd} and can be used to our purpose. It is} an observable-based
-bivariate expansion of Eq.~\eqref{eq:general_deviation}, given by
+The ParSpec framework was introduced in Ref.~\cite{Maselli:2019mjd} and can be
+used to our purpose. It is an observable-based bivariate expansion of
+Eq.~\eqref{eq:general_deviation}, given by
 %
@@
 %
-\ab{where $M_{\rm f}$ and $\chi_{\rm f}$ are the detector-frame final mass and spin, respectively;}
+where $M_{\rm f}$ and $\chi_{\rm f}$ are the detector-frame final mass and spin, respectively;
 the quantities $\omega_{\ell m n}^{(j)}$ and $\tau_{\ell m n}^{(j)}$ are dimensionless coefficients of the
-expansion in spin for BH QNMs in GR, while $\delta\omega_{\ell m n}^{(j)}$ and $\delta\tau_{\ell m n}^{(j)}$ are
+expansion in spin for the QNMs of BHs in GR, while $\delta\omega_{\ell m n}^{(j)}$ and $\delta\tau_{\ell m n}^{(j)}$ are
 source-independent dimensionless coefficients that characterize the corrections to the GR QNM at
@@
 %
-All source dependence for a given modified gravity theory is contained in the
+All source dependence due to a given modified gravity theory is contained in the
 dimensionless parameter $\gamma$, which reads
@@
 %
-which depends on \ab{the length-scale parameter $\ell_{\rm th}$ of the specific gravity theory
+which depends on the length-scale parameter $\ell_{\rm th}$ of the specific gravity theory
 (non-GR modifications become important at distances $\lesssim \ell_{\rm th}$), and
 the exponent $p$ is related to how the non-GR modifications are
-added to the Einstein-Hilbert action.}
-%
-In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by using the other
+added to the Einstein-Hilbert action.
+%
+In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by \redsout{using} the \redsout{other}
 length-scale associated with the remnant black hole (i.e., its source-frame mass
@@
 through the redshift $z$~\cite{Krolak:1987ofj}. Also, dividing by the factor $G/c^2$ allows us to
-express $\ell$ in physically intuitive metric units.
+express $\ell_{\rm th}$ in physically intuitive metric units.
 
@@
 %
-This means we can identify the $M_{\rm f}$ and $\chi_{\rm f}$ with their \emph{corresponding {\rm GR} values}
-\footnote{For a more detailed discussion, see Appendix A in Ref.~\cite{Maselli:2019mjd}.}.
+This means we can identify the $M_{\rm f}$ and $\chi_{\rm f}$ with their
+\emph{corresponding {\rm GR} values}\footnote{For a more detailed discussion, see Appendix A in Ref.~\cite{Maselli:2019mjd}.}.
 %
 We will see in Sec.~\ref{sec:pe}  that this assumption is indeed
-satisfied in our parameter estimation studies (e.g., see Fig.~\ref{fig:corner_plot}).
+satisfied in our parameter estimation studies (see, for instance, Fig.~\ref{fig:corner_plot}).
 
@@
 As we will discuss in Sec.~\ref{sec:pe}, the expansion to $N_{\rm max} = 4$ is
-sufficient for our purposes. \ab{For convenience we list the coefficients in the case of
-GR in Table~\ref{tab:ref_theories_qnms}.}
+sufficient for our purposes. For convenience we list the coefficients in the case of
+GR in Table~\ref{tab:ref_theories_qnms}.
 
@@
 As in Refs.~\cite{Brito:2018rfr,Ghosh:2021mrv}, we use an IMR BBH waveform
-model where the \ab{(complex) frequencies} \sout{parameters} describing the remnant object
+model where the (complex\hs{-valued}) frequencies describing the remnant object
 are left additionally free and estimated directly from the data.
 
-The GW signal from a \ab{quasicircular} BBH can be \ab{described} \sout{determined} in GR by a unique set of
+The GW signal from a quasicircular BBH can be described  in GR by a unique set of
 parameters $\bm{\theta}$, that includes the masses and spins of the two BHs,
 $(m_1,\, m_2,\, \mathbf{S}_1,\, \mathbf{S}_2)$, the sky location determined by the
-luminosity distance $D_L$\abcomm{I changed to capital $d$ because later we call the
-data ``d''.}, right ascension $\alpha$ and declination $\delta$,
+luminosity distance $D_L$,
+% \abcomm{I changed to capital $d$ because later we call the
+% data ``d''.},
+right ascension $\alpha$ and declination $\delta$,
 and the orientation of the binary given by the inclination $\iota$ and polarization $\psi$
@@
 $\phi_0$. If we further assume that the spins of the individual BHs are
-restricted to be \sout{parallel} \ab{aligned or anti-aligned (for short, aligned) to the unit vector
+restricted to be aligned or anti-aligned (for short, aligned) to the unit vector
 perpendicular to the orbital plane ($\mathbf{\hat{L}}$), we reduce the six
 components of the spins to just two, $\chi_i \equiv \mathbf{S}_i\cdot \mathbf{\hat{L}} /m_i^2$ with $i = 1,2$,
-and our entire parameter set from 15 to 11.}
+and our entire parameter set from 15 to 11.
 %
@@
 the asymmetric mass ratio $q=m_1/m_2$, with the convention $m_1 \geqslant m_2$ (and thus $q \geqslant 1$),
-and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$. \ab{Note that for BHs $-1 \leq \chi_i \leq 1$.}
+and the symmetric mass ratio of the binary, $\nu = m_1m_2/(m_1+m_2)^2$. Note that for BHs $-1 \leqslant \chi_i \leqslant 1$.
 
@@
 \begin{equation}
-h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{l, m} {}_{-\!2}Y_{l m}(\iota,\varphi_0)\, h_{l m}(t)\,,
+h_+(\iota,\varphi_0;t ) - i h_\times(\iota,\varphi_0;t) = \sum_{l, m} {}_{-\!2}Y_{l m}(\iota,\varphi_0)\, h_{l m}(t),
 \end{equation}
@@
 Ref.~\cite{Mihaylov:2021bpf}, which contains the modes, $(l, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$,
-and $(5,5)$. \ab{Such a model was built by applying the post-adiabatic approximation~\cite{Nagar:2018gnk}
+and $(5,5)$. Such a model was built by applying the post-adiabatic approximation~\cite{Nagar:2018gnk}
 to the multipolar spin-aligned effective-one-body (EOB) waveform model of Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv}
-(henceforth we refer to our baseline model as \SEOB{}~\footnote{This waveform
+(henceforth we refer to our baseline model as \SEOB{}\footnote{This waveform
 model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA}
-waveform approximant.}).}
-
-%
+waveform approximant.}).
+
 An accurate description of the merger is incorporated through calibration with
-NR simulations, as described in Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv}, along with
+numerical relativity (NR) simulations, as described in Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv}, along with
 information for the merger and ringdown phases, from BH perturbation theory.
@@
 to a certain theory-specific value. Additionally, the frequencies depend on the ParSpec coefficients $\{\delta
-\omega_{\ell m 0}^{(j)},\delta \tau_{\ell m 0}^{(j)}\}$,  and the \ab{length-scale} $\ell_{\rm th}$.
-
-Using this parameterized waveform model, which we denote $\pSEOB$,
+\omega_{\ell m 0}^{(j)},\delta \tau_{\ell m 0}^{(j)}\}$, and the length-scale $\ell_{\rm th}$.
+
+Using this parameterized waveform model, which we call $\pSEOB$,
 we infer bounds on our non-GR parameter $\ell_{\rm th}$ for the specific cases of
@@
 
-Let us now establish the connection between the theory-\ab{independent} framework of the
+Let us now establish the connection between the theory-independent framework of the
 $\pSEOB$ waveform model and the theory-specific QNM calculations. In this paper we restrict ourselves
-\ab{to the leading and next-to-leading order terms} in the ParSpec expansion, as well as to the fundamental QNM
-$(\ell, m, n) = (2,\, 2,\, 0)$. For this reason, \ab{for simplicity}, we omit the subscripts hereafter
+to the leading and next-to-leading order terms in the ParSpec expansion, as well as to the fundamental QNM
+$(\ell, m, n) = (2,\, 2,\, 0)$. For this reason, for simplicity, we omit the subscripts hereafter
 and rewrite $\omega_{\ell m n}$ and $\tau_{\ell m n}$, given by Eqs.~\eqref{eq:kerr_expansion} as,
@@
 %
-\ab{where we pull out from the sum all non-GR corrections, restricting
+where we pull out from the sum all non-GR corrections, restricting
 ourselves to the nonspinning ($j=0$) and linear-order in spin ($j=1$)
-corrections to the GR QNMs.}
-%
-% These corrections are encoded in the coefficients $\delta\omega^{(n)}$ and $\delta\tau^{(n)}$.
+corrections to the GR QNMs.
 
@@
 Kerr QNMs against the fitting formula~\eqref{eq:qnm_nongr_iso} fixes the GR expansion coefficients
-$\omega^{(j)}$, $\tau^{(j)}$.
+$\omega^{(j)}$ and $\tau^{(j)}$.
 %
@@
 In particular, in the literature, we can already find fitting formulas relating
-the QNMs to the BHs mass, spin and coupling constant $\ell_{\rm thh}$, the latter being
+the QNMs to the BHs mass, spin and coupling constant $\ell_{\rm th}$, the latter being
 specific to each theory, up to $j=1$ in the spin expansion (see Table~\ref{tab:ref_theories_qnms}).
@@
 all spin values, we can expect that the $j=1$ coefficients to be susceptible to
-changes as calculations beyond-leading order in spin are accomplished \ab{in the future}.
+changes as calculations beyond-leading order in spin are accomplished in the future.
 %
@@
 %
-This is a critical difference between our work and Ref.~\cite{Carullo:2021dui}.
+This is a important difference between our work and Ref.~\cite{Carullo:2021dui}.
 In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
@@
 \label{sec:pe}
-% \input{sec_pe}
 % --------------------------------------------------------------------------------- %
 
-In this section, we \ab{first} provide a basic outline of the Bayesian formalism that we use to
-infer the properties of the underlying GW signal; \ab{then, we} identify the most promising
-events from the catalog of \ab{LIGO-Virgo-KAGRA} GW observations to base our analyses on. \ab{Finally,
+In this section, we first provide a basic outline of the Bayesian formalism that we use to
+infer the properties of the underlying GW signal; then, we identify the most promising
+events from the catalog of LIGO-Virgo-KAGRA GW observations to base our analyses on. Finally,
 we discuss how we can interpret our results after taking into account the region of validity of
-the non-GR theories that we are considering, which are EFTs.}
+the non-GR theories that we are considering, which are EFTs.
 
@@
 The set of parameters, $\bm{\lambda}$ is a union of the GR waveform
-model parameters~$\bm{\theta}$ (see Sec.~\ref{sec:review_pSEOB}) \abcomm{It seems to
-me that PRD does not use ``c.f.''. Does it? I am replacing it with ''see''.}, and
-$\ell_{\rm th}$,  the only non-GR parameter in this problem which, we recall, sets
+model parameters~$\bm{\theta}$ (see Sec.~\ref{sec:review_pSEOB})
+% \abcomm{It seems to
+% me that PRD does not use ``c.f.''. Does it? I am replacing it with ''see''.},
+and $\ell_{\rm th}$, the only non-GR parameter in this problem which, we recall, sets
 the characteristic length-scale in which deviations from
@@
 complex conjugation, $S_{n}(f)$ is the power spectrum density of the
-detector, and $[f_{\rm low}, f_{\rm high}]$ span the detector sensitivity \ab{frequency} band.
+detector, and $[f_{\rm low}, f_{\rm high}]$ span the detector sensitivity frequency band.
 %
@@
 on the binary orientation, $p(\iota, \psi, \phi_0) \propto \sin\iota$. For the spins
-$(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes.\sout{ and restrict ourselves to the $z$-components.} \footnote{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior.}}.
+$(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes\footnote{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior.}}.
 %
@@
 %
-We assume an uniform prior on $\ell_{\rm th}$ between appropriate ranges\sout{,
-say $\ell_{\rm th} \in [0, \ell_{\rm max}]$}.
+We assume an uniform prior on $\ell_{\rm th}$ between appropriate ranges.
+% \sout{, say $\ell_{\rm th} \in [0, \ell_{\rm max}]$}.
 %
@@
 \caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-detector-frame remnant mass $(1 + z) \, M_{\rm f}$ for GW150914, using the same waveform model,
-but without (blue contours) \agcomm{colors are not up to date; needs to be
-finalised after we finalise the color scheme} and with the non-GR parameters
-different from zero (orange contours, for
-dCS gravity and $N_{\rm max}=0$).
-The contours represent 90\% credible \sout{regions}\ag{levels}\agcomm{we have to be particular about the use of credible regions.
-If its 2D they are ``levels", if they are 1D then ``intervals".
-If we are quoting the difference of the 1D intervals, then we say ``credible bounds"}.
+remnant mass $M_{\rm f}$ for GW150914, using the same waveform model,
+but without (purple contours) and with the non-GR parameters
+different from zero (blue contours), for
+dCS gravity and $N_{\rm max}=0$ as an example.
+%
+The contours represent 90\% credible levels.
 %
@@
 The latest LIGO-Virgo-KAGRA GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
-signals not all of which are relevant for \ab{our} BH ringdown analysis. In fact, in
+signals not all of which are relevant for our BH ringdown analysis. In fact, in
 the accompanying paper~\cite{LIGOScientific:2021sio} on tests of GR, the \texttt{pSEOBNRv4HM}
@@
 
-% -----------------
-% Corner plots here
-% -----------------
-
-% As a first test ...
-% \hs{Move to an appendix.}
-
 \subsection{Interpretation of our results}
@@
 have placed a constraint on $\ell_{\rm th}$. First, as we have explained in Sec.~\ref{sec:review_theories}, all theories that we
-consider must be \ab{interpreted} as an effective field theory, meaning that it should be
+consider must be interpreted as an effective field theory, meaning that it should be
 considered valid only below an energy scale, or equivalently, a length-scale.
@@
 %
-In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
-but here we consider $\varepsilon \in [0, 1]$ for generality.
-%
+\hs{Here we explore the range $\varepsilon \in [0, 1]$, but following
+the Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} we quote our final results using
+$\varepsilon = 1/2$.}
+% %
+% In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
+% but here we explore $\varepsilon \in [0, 1]$ for generality.
+% %
 We say that a bound has been placed on $\ell_{\rm th}$, if most of the PDF $P(\ell_{\rm th} | d)$ support is in the interval
-$[0, \, \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})]$.
+$[0, \, \Lambda_{\rm EFT}(\hs{1/2}, \mathfrak{m})]$.
 %
@@
 \begin{equation}
-% P(\ell_{\rm th} \leqslant \ell_{\rm max}) = \int_{-\infty}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell') \,.
-% HS: changed lower limit to zero since we don't have support for negative \ell-values
-P(\ell_{\rm th} \leqslant \ell_{\rm max} | d) = \int_{0}^{\,\ell_{\rm max}} \dd \ell'\, P(\ell' | d) \,.
+P(\ell_{\rm th} \leqslant \ell^{\rm max}_{\rm th} | d) = \int_{0}^{\,\ell^{\rm max}_{\rm th}} \dd \ell'\, P(\ell' | d).
 \label{eq:def_cdf}
@@
 %
-For instance, we require that for a bound \ab{at 90\% credible level} to be placed on $\ell_{\rm th}$ that
+For instance, we require that for a bound at 90\% credible level to be placed on $\ell_{\rm th}$ that
 %
@@
 % \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
-P(\ell_{\rm th} \leqslant \Lambda_{\rm EFT} | d) \leqslant 0.9 \,,
+P(\ell_{\rm th} \leqslant \Lambda_{\rm EFT} | d) \leqslant 0.9,
 \quad \textrm{(EFT bound)},
@@
 %
-where we let $\ell_{\rm max} = \Lambda_{\rm EFT}$ in Eq.~\eqref{eq:def_cdf}, and
+where we let $\ell^{\rm max}_{\rm th} = \Lambda_{\rm EFT}$ in Eq.~\eqref{eq:def_cdf}, and
 likewise for other credibility percentiles.
@@
 \begin{equation}
-\gamma \, \delta \omega^{(j)} \ll 1 \,,
+\gamma \, \delta \omega^{(j)} \ll 1,
 \,\, \textrm{and} \,\,
-\gamma \, \delta \tau^{(j)} \ll 1 \,, \quad \textrm{(ParSpec bound)},
+\gamma \, \delta \tau^{(j)} \ll 1, \quad \textrm{(ParSpec bound)},
 \label{eq:parspec_bound}
@@
 %
-The bottom panel shows the joint posterior \ab{obtained by} combining both events.
+The bottom panel shows the joint posterior obtained by combining both events.
 %
@@
 %
-\ab{We recall} that the deviations from GR in the ParSpec framework are controlled
-by \ab{the dimensionless parameter} $\gamma$, which here reads,
-%
-\begin{equation}
-    \gamma_{\rm GB} = \left(\frac{c^2 \ell_{\rm GB}}{ G M_{f}}\right)^4\,.
+We recall that the deviations from GR in the ParSpec framework are controlled
+by the dimensionless parameter $\gamma$, which here reads,
+%
+\begin{equation}
+    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M_{f}}\right)^4\,.
     \label{eq:def_gamma_gb}
@@
 %
-As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm GB}$ does indeed have a posterior
+As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm EdGB}$ does indeed have a posterior
 distribution with largest support at zero, indicating consistency between
@@
 We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
-displaces the posteriors distributions towards smaller values of $\ell_{\rm GB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
-and larger values of $\gamma_{\rm GB}$ (see Fig.~\ref{fig:gamma_gb}).
+displaces the posteriors distributions towards smaller values of $\ell_{\rm EdGB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
+and larger values of $\gamma_{\rm EdGB}$ (see Fig.~\ref{fig:gamma_gb}).
 
@@
 \includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function on coupling constant $\ell_{\rm GB}$ in EdGB gravity
+\caption{(Color online).~Posterior distribution function on coupling constant $\ell_{\rm EdGB}$ in EdGB gravity
 for GW150914 (top panel), GW200129 (middle panel)
@@
 The joint posteriors are shown for illustrative purposes only. As we explain in Fig.~\ref{fig:edgb_cdf} and
-in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}. \ab{We mark
-with vertical lines theh $90\%$ upper credible intervals.}}
+in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}. We mark
+with vertical lines theh $90\%$ upper credible intervals.}
 \label{fig:edgb_exec_sum}
@@
 \includegraphics[width=\columnwidth]{figs/edgb_gamma.pdf}
-\caption{(Color online).~Posterior distribution function on the dimensionless parameter $\gamma_{\rm GB}$,
+\caption{(Color online).~Posterior distribution function on the dimensionless parameter $\gamma_{\rm EdGB}$,
 defined in Eq.~\eqref{eq:def_gamma_gb}. We see that this parameter controls the ParSpec expansion in EdGB gravity
-does have maximum support at $\gamma_{\rm GB} = 0$. This shows that our model is consistent with GR.}
+does have maximum support at $\gamma_{\rm EdGB} = 0$. This shows that our model is consistent with GR.}
 \label{fig:gamma_gb}
@@
 $\varepsilon$ for both (dashed curves) $\gm = m_2$, the secondary's source
-mass, and (solid curves) $\gm = M_{f}$, the remnant's source mass, without
+mass, and (solid curves) $\gm = M_{\rm f}$, the remnant's source mass, without
 (black curves) and with (purple curves) linear in spin QNM corrections. The
-horizontal lines mark the $90\%$ credible levels. \ab{Having set the maximum value
-of $\varepsilon$ to be 1/2, we see} that in no situation the curves pass
-through the 0.90 lines. This means that no bound on $\ell_{\rm GB}$ can be placed
+horizontal lines mark the $90\%$ credible levels. Having set the maximum value
+of $\varepsilon$ to be 1/2, we see that in no situation the curves pass
+through the 0.90 lines. This means that no bound on $\ell_{\rm EdGB}$ can be placed
 with the events we analyzed.
@@
 \caption{Detailed summary of our results for EdGB gravity for GW150914, GW200129, and
-combined events using $\gm = M_{f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
-%
-We find that we cannot place any constraint on $\ell_{\rm GB}$ with our waveform model from either GW event.
+combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+%
+We find that we cannot place any constraint on $\ell_{\rm EdGB}$ with our waveform model from either GW event.
 }
@@
 are satisfied, before drawing any conclusions on the allowed values for
-$\ell_{\rm GB}$ from our parameter estimations.
+$\ell_{\rm EdGB}$ from our parameter estimations.
 %
 We check the validity of the EFT bound in Fig.~\ref{fig:edgb_cdf}. In the top (bottom) panel we show
-the CDF of the $\ell_{\rm GB}$ posteriors for GW150914 (GW200129), obtained
-by evaluating the integral~\eqref{eq:def_cdf} with $\ell_{\rm max} = \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
+the CDF of the $\ell_{\rm EdGB}$ posteriors for GW150914 (GW200129), obtained
+by evaluating the integral~\eqref{eq:def_cdf} with $\ell^{\rm max}_{\rm th} = \Lambda_{\rm EFT}(\varepsilon, \mathfrak{m})$,
 with the mass scale set by the secondary's mass (i.e., $\mathfrak{m} = m_2$, dashed lines) or
@@
 never met at a significant credibility and thus that we cannot place a bound on
-$\ell_{\rm GB}$.
+$\ell_{\rm EdGB}$.
 %
@@
 %
-\ab{For the case with $N_{\rm max} = 1$, we find that the ``EFT bound'' is satisfied
-only for $\varepsilon \approx 0.8$ and $\approx1$ for GW150914 aand GW200129, respectively.
-However, we set the maximum value of $\varepsilon$ to be 1/2, thus,}
+For the case with $N_{\rm max} = 1$, we find that the ``EFT bound'' is satisfied
+only for $\varepsilon \approx 0.8$ and $\approx1$ for GW150914 and GW200129, respectively.
+However, we set the maximum value of $\varepsilon$ to be 1/2, thus,
 taken together we are led to \emph{conclude that we cannot constrain EdGB gravity with our
@@
 
-We can compare this conclusion with that of Ref.~\cite{Carullo:2021dui}, which obtained $\ell_{\rm GB} \lesssim 35$~km,
+We can compare this conclusion with that of Ref.~\cite{Carullo:2021dui}, which obtained $\ell_{\rm EdGB} \lesssim 35$~km,
 by setting $p=4$, \emph{but not} including theory-specific QNM information on $\delta \omega^{(j)}$ and $\delta \tau^{(j)}$.
@@
 Let us also contrasts our results with those of Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}
-which relied on the BBH inspiral to constrain $\ell_{\rm GB}$, as discussed in Sec.~\ref{sec:review_edgb}.
-%
-We see that EdGB provides an example of a theory in which, \ab{with current GW events,} the inspiral portion
-of the signal \ab{can be} more constraining than the ringdown portion of the signal.
+which relied on the BBH inspiral to constrain $\ell_{\rm EdGB}$, as discussed in Sec.~\ref{sec:review_edgb}.
+%
+We see that EdGB gravity provides an example of a theory in which, with current GW events, the inspiral portion
+of the signal can be more constraining than the ringdown portion of the signal.
 %
@@
 remnant BH, suppresses scalar field's charge relatively to the initial binary
-components.~\hs{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
+components.~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
 Point this out in the conclusions after all specific theories are discussed.}
@@
 %
-As with EdGB gravity (see Sec.~\ref{sec:results_edgb}) although the PDF of $\ell_{\rm CS}$
+As with EdGB gravity (see Sec.~\ref{sec:results_edgb}) although the PDF of $\ell_{\rm dCS}$
 is peaked away from 0, this does not signify a deviation from GR, as we have verified that,
@@
 \begin{equation}
-    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm CS}}{G M_{f}} \right)^{4}\,,
-\end{equation}
-%
-does indeed peak at zero indicating consistency with GR, similarly to what is shown in Fig.~\ref{fig:gamma_gb} for $\gamma_{\rm GB}$.
+    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm dCS}}{G M_{f}} \right)^{4}\,,
+\end{equation}
+%
+does indeed peak at zero indicating consistency with GR, similarly to what is
+shown in Fig.~\ref{fig:gamma_gb} for $\gamma_{\rm EdGB}$.
 %
@@
 correction to the QNM displaces the posteriors towards smaller values of
-$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
+$\ell_{\rm dCS}$. This can be seen more evidently by looking at the location of
 posterior peaks.
@@
 Finally, in the bottom panel, we show the combined result for both events.
-\agcomm{Just a thought.  Since, Figs 3,6,8,10 and Figs.4,6,9,11 show the same basic thing,
-should we have one description at the top of the section for each figure? We can follow this up
-by what is special for each theory in each section? Currently, we are repeating a lot of the
-language to describe these figures for each theory?}
+% \agcomm{Just a thought.  Since, Figs 3,6,8,10 and Figs.4,6,9,11 show the same basic thing,
+% should we have one description at the top of the section for each figure? We can follow this up
+% by what is special for each theory in each section? Currently, we are repeating a lot of the
+% language to describe these figures for each theory?}
 
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 42.6~\textrm{km}
+\ell_{\rm dCS} \leqslant 42.6~\textrm{km}
 \quad \textrm{at 90\% credible level},
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 37.4~\textrm{km}
+\ell_{\rm dCS} \leqslant 37.4~\textrm{km}
 % ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 36.6~\textrm{km}
+\ell_{\rm dCS} \leqslant 36.6~\textrm{km}
 % 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 29.1~\textrm{km}
+\ell_{\rm dCS} \leqslant 29.1~\textrm{km}
 % ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
@@
 %
-These stronger bounds are a consequence of the larger support for $\ell_{\rm CS} \lessapprox 15$~km
+These stronger bounds are a consequence of the larger support for $\ell_{\rm dCS} \lessapprox 15$~km
 for GW200129 (compare the top and middle panels in Fig.~\ref{fig:dCS_exec_sum}), and in part due to
@@
 We also found for both GW events, that the perturbative-conditions~\eqref{eq:parspec_bound} required by the ParSpec
-formalism is violated for the $\gamma_{\rm CS} \, \delta \tau^{(1)}$ coefficient.
+is violated for the $\gamma_{\rm dCS} \, \delta \tau^{(1)}$ coefficient.
 %
@@
 
-Finally, since both events individually lead to a bound on $\ell_{\rm CS}$
+Finally, since both events individually lead to a bound on $\ell_{\rm dCS}$
 (assuming a cut-off scale for $\gm = M_{\rm f}$ and $N_{\rm max}=0$), we can combine the
@@
 \begin{equation}
-\ell_{\rm CS} \leqslant 38.7~\textrm{km}
+\ell_{\rm dCS} \leqslant 38.7~\textrm{km}
 \quad \textrm{ at 90\% credible level},
@@
 This bound is approximately a factor of four weaker than that placed by
-Ref.~\cite{Silva:2020acr}, but \ab{it}
+Ref.~\cite{Silva:2020acr}, but it
 %
@@
 (ii) suggests that a ringdown analysis can potentially place constraints on
-theories \ab{that, with current GW events, can evade GR tests} using inspiral information alone, such as the
-case of dCS gravity~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+theories that, with current GW events, can evade GR tests using inspiral information
+alone, such as the case of dCS gravity~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
 %
@@
 %       & Combined & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
-      & GW150914 & Yes & Yes & $\ell_{\rm CS} \leqslant 41.9$~km \\
-0     & GW200129 & Yes & Yes & $\ell_{\rm CS} \leqslant 35.8$~km \\
-      & Combined &     &     & \cellcolor{black!10}$\ell_{\rm CS} \leqslant 38.7$~km \\
+      & GW150914 & Yes & Yes & $\ell_{\rm dCS} \leqslant 41.9$~km \\
+0     & GW200129 & Yes & Yes & $\ell_{\rm dCS} \leqslant 35.8$~km \\
+      & Combined &     &     & \cellcolor{black!10}$\ell_{\rm dCS} \leqslant 38.7$~km \\
 \hline
@@
 The combined bound, which is also quoted in Table~\ref{tab:ref_theories_qnms},
-is $\ell_{\rm CS} \leqslant 38.7$~km \ab{at 90\% credible level}.
+is $\ell_{\rm dCS} \leqslant 38.7$~km at 90\% credible level.
 }
@@
 
-\subsection{Cubic Effective-FieXld-Theory of General Relativity}
+\subsection{Cubic Effective-Field-Theory of General Relativity}
 \label{sec:results_ceft}
@@
 %
-\abcomm{Please update the paragraph below.}
+% \abcomm{Please update the paragraph below.}
+\hs{
 In this theory, we have considered only $N_{\rm max} = 0$. We found that the
 inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
-for which the ringdown portions of the larger than the inspiral-plunge part \dots
+for which the ringdown portions of the larger than the inspiral-plunge part.
 %
 To avoid this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
-which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
+which were essentially uniform, as our prior, and thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
+}
 %
@@
 
-We presented an \ab{unified framework to combine the ParSpec formalism} introduced
+We presented an unified framework to combine the ParSpec formalism introduced
 to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
 %
-We showed with concrete examples, \ab{how theory-specific QNM calculations of
+We showed with concrete examples, how theory-specific QNM calculations of
 slowly-rotating BHs in modified gravity theories can be mapped onto the
-non-GR parameters of the ParSpec formalism}.
+non-GR parameters of the ParSpec formalism.
 %
@@
 %
-We found, in particular that, \ab{within the interpretation of our non-GR theories as EFTs and the
+We found, in particular that, within the interpretation of our non-GR theories as EFTs and the
 region of validity of the ParSpec framework, the coupling constant of dCS gravity is bound to
 $\ell_{\rm CS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
-of GW150914 and GW200129.}
+of GW150914 and GW200129.
 %
@@
 %
-In that case, it is dCS which is unconstrained, while EdGB, in principle can be
-constrained, based on results for the closely related shift-symmetric version
-of this theory.
+In that case, it is dCS which is unconstrained \hs{with already observed GW
+events}, while EdGB can be constrained, as shown in Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+%
+\hscomm{I will a sentence here on Refs.~\cite{Alexander:2017jmt,Loutrel:2018ydv,Loutrel:2018rxs}.}
 
@@
 
-\hs{TODO: say that we could try to expand the waveform model to include modification to
+\hscomm{TODO: say that we could try to expand the waveform model to include modification to
 the inspiral part too; maybe through FTI~\cite{Mehta:2022pcn}?}
 
-\hs{TODO: add that we could try to parametrize the final black hole mass and spin estimates formulas we
+\hscomm{TODO: add that we could try to parametrize the final black hole mass and spin estimates formulas we
 use at the moment~\cite{Hofmann:2016yih}. Maybe comment that a possible first attempt could follow~\cite{Buonanno:2007sv},
@@
 
-\hs{I suspect that by construction the $N_{\rm max} = 1$ cases will often fail to satisfy our
+\hscomm{I suspect that by construction the $N_{\rm max} = 1$ cases will often fail to satisfy our
 perturbative bounds. If so, add explanation here.}
@@
 from zero (blue contours), having as an illustrative example dCS gravity and $N_{\rm max}=0$.
+%
+\hs{Here, $\chi_{\rm eff}$ is the dimensionless effective-spin parameter, related to the individual spins $\chi_{i}$
+and masses $m_{i}$ of each binary component as $\chi_{\rm eff} \equiv (m_1 \chi_1 + m_2 \chi_2) / (m_1 + m_2)$.}
 %
@@
 
-\subsection{Einstein-dilaton-Gauss-Bonnet}
+\subsection{Einstein-dilaton-Gauss-Bonnet gravity}
 \label{app:map_edgb}
@@
 
-\subsection{dynamical Chern-Simons}
+\subsection{Dynamical Chern-Simons gravity}
 \label{app:map_dcs}
@@
 
-\subsection{Effective-field-theories GR}
+\subsection{Effective-field-theory of General Relativity}
 \label{app:map_eftofgr}

### 2022-04-20 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
updates to appendices and fig captions

@@
 \caption{(Color online).~Posterior distribution function on the dimensionless parameter $\gamma_{\rm EdGB}$,
-defined in Eq.~\eqref{eq:def_gamma_gb}. We see that this parameter controls the ParSpec expansion in EdGB gravity
-does have maximum support at $\gamma_{\rm EdGB} = 0$. This shows that our model is consistent with GR.}
+defined in Eq.~\eqref{eq:def_gamma_gb}. Different line colors distinguish between events, while
+different line styles distinguish between different $N_{\rm max}$.
+%
+We see that this parameter which controls the ParSpec expansion in EdGB gravity
+does have maximum support at $\gamma_{\rm EdGB} = 0$. This shows that our model is consistent with GR.
+\hs{The right panel shows the PDFs in the range $0 \leqslant \gamma_{\rm EdGB} \leqslant 1$. Note how
+the curves are flat in this range for both events and when $N_{\rm max} = 1$.}
+}
 \label{fig:gamma_gb}
@@
 In this Appendix, we show how we determined the coefficients in the ParSpec
+and summarized in Table~\ref{tab:ref_theories_qnms},
 using QNM calculations found in the literature for the theories described in
 Sec.~\ref{sec:review_theories}.
+%
+Here, we consider only the fundamental QNM $(\ell, m, n) = (2, 2, 0)$ and
+hence we omit the QNM subscript ``$(2,2,0)$'' for brevity.
 
@@
 We start by considering EdGB gravity, for which the QNMs of nonrotating and
-slowly-rotating BHs where calculated in
-Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and~\cite{Pierini:2021jxd},
-respectively.
+slowly-rotating BHs where calculated in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk}
+and~\cite{Pierini:2021jxd}, respectively.
+%
+In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
+of the polar gravitational-led modes increases as the coupling constant
+$\ell_{\rm EdGB}$ is increased.
+%
+Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
+this is the gravitational-led branch of QNMs we select.
+
+For the nonrotating QNMs we used the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
+generated a new quartic in $\ell_{\rm EdCS}$ fit to the data valid for small
+values of the coupling constant [see, in particular, Eq.~(27) and Fig.~2 of~\cite{Blazquez-Salcedo:2016enn}].
+%
+We find,
+%
+\begin{subequations}
+\begin{align}
+    M {\rm Re}(\sigma)_{\rm EdGB} &= M {\rm Re}(\sigma)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
+    \\
+    M {\rm Im}(\sigma)_{\rm EdGB} &= M {\rm Im}(\sigma)_{\rm GR} \, \left[ 1 - 0.0044 (\ell_{\rm EdGB} / M)^4 \right].
+\end{align}
+\end{subequations}
+%
+The smallness of the numerical prefactors of $\ell_{\rm EdGB}^4$ are a consequence of the how weakly the QNMs
+of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $(\ell_{\rm EdGB} / M)^4 \approx 0.3$.
+
+The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
+which for consistency, with our previous discussion, we truncated at quartic-order in $\ell_{\rm EdGB}$.
+%
+Taken together, all use as our fitting expressions for the QNM is EdGB gravity
+%
+\begin{subequations}
+\begin{align}
+    M {\rm Re}(\sigma)_{\rm EdGB} &= \dots % {\rm Re}(\omega)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
+    \\
+    M {\rm Im}(\sigma)_{\rm EdGB} &= \dots % {\rm Im}(\omega)_{\rm GR} \, \left[ 1 - 0.0044 (\ell_{\rm EdGB} / M)^4 \right].
+\end{align}
+\end{subequations}
+
+\dots
 
@@
 
-% Let us show one concrete example of how this mapping is done.
-%
-In Ref.~\cite{Wagle:2021tam} the QNMs of slowly-rotating BHs in dCS gravity were numerically determined
-and it was found that the axial gravitational modes have their damping time increased as we
-increase the Chern-Simons coupling $\ell_{\rm CS}$ at fixed spin $\chi$ of the BH.
-%
-Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm}, this is the branch of QNMs we will select.
+For dCS gravity, we follow Ref.~\cite{Wagle:2021tam} which numerically calculated the QNMs of slowly-rotating BHs in this theory
+and found that the axial gravitational modes have their damping time increased as we
+increase the Chern-Simons coupling $\ell_{\rm dCS}$ at fixed spin $\chi$ of the BH.
+%
+Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
+this is the branch of QNMs we will select.
 
@@
 \begin{equation}
-    M_{\rm f} \omega_{\rm CS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+    M \omega_{\rm CS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
     \label{eq:omega_dsc_eg}
@@
 %
-and similarly for the imaginary part ${\rm Im}(\sigma_{\rm CS}) =  - 1 / \tau_{\rm CS}$.
-%
-Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm CS}^{4} / (M_{\rm f}^4 \kappa)$, and thus
-%
-\begin{equation}
-    \kappa \zeta = (\ell_{\rm CS} / M_{\rm f})^4 \,,
+and similarly for the imaginary part ${\rm Im}(\sigma_{\rm dCS}) =  - 1 / \tau_{\rm dCS}$.
+%
+Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm dCS}^{4} / (M^4 \kappa)$, and thus
+%
+\begin{equation}
+    \kappa \zeta = (\ell_{\rm dCS} / M)^4 \,,
 \end{equation}
@@
 
-We now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm CS}$, and
-gather the terms proportional to $\ell_{\rm CS}$.
+We now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm dCS}$, and
+gather the terms proportional to $\ell_{\rm dCS}$.
 %
@@
 \begin{align}
-    M_{\rm f} \, \omega_{\rm CS} &=
-    \left[ 0.3722 + 1.1945 (\ell_{\rm CS} / M_{\rm f})^4 \right]
+    M \, \omega_{\rm dCS} &=
+    \left[ 0.3722 + 1.1945 (\ell_{\rm dCS} / M)^4 \right]
     \nonumber \\
-    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm CS} / M_{\rm f})^4 \right] \, \chi\,,
+    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm dCS} / M)^4 \right] \, \chi\,,
     \label{eq:omega_dcs_interm}
@@
 \begin{equation}
-p_{\rm CS} = 4\,, \quad \delta \omega^{(0)}_{\rm CS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm CS} = 41.199\,.
+p_{\rm dCS} = 4\,, \quad \delta \omega^{(0)}_{\rm dCS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm dCS} = 41.199\,.
 \label{eq:cs_omega_coefs}
@@
 
-We can carry the same steps for $\tau_{\rm CS}$ and find
-%
-\begin{equation}
-\delta \tau^{(0)}_{\rm CS} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm CS} = 794.66\,.
+We can carry the same steps for $\tau_{\rm dCS}$ and find
+%
+\begin{equation}
+\delta \tau^{(0)}_{\rm dCS} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm dCS} = 794.66\,.
 \label{eq:cs_tau_coefs}
@@
 %
-We remark that the alarmingly large values of $\delta \omega_{\rm CS}^{(1)}$ and $\delta \tau_{\rm CS}^{(1)}$
-are compensated by the assumptions that $(\ell_{\rm CS} / M_{\rm f})^2$ and $\chi$ are much less than unity. These
-are the assumptions used to calculate the QNM frequencies in Ref.~\cite{Wagle:2021tam}.
+We remark that the alarmingly large values of $\delta \omega_{\rm dCS}^{(1)}$ and $\delta \tau_{\rm dCS}^{(1)}$
+are compensated by the assumptions that $(\ell_{\rm dCS} / M_{\rm f})^2$ and $\chi$ are much less than unity,
+which are the assumptions in Ref.~\cite{Wagle:2021tam}.
 

### 2022-04-20 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
draft intro + new refs

--- 2022-04-20 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
@@
 
-\hs{AB will do this.}
+Since the first detection of gravitational waves (GWs) from a binary black-hole (BBH) merger in 2015~\cite{LIGOScientific:2016aoc}, 
+the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GWs signals \cite{LIGOScientific:2021djp} from mergers
+of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2020aai} and their mixture \cite{LIGOScientific:2021qlt}. These results have been confirmed 
+by independent analyses, which have also identified a few new GW signals~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq,Nitz:2021zwj,Olsen:2022pin}.
+
+The large number of GW observations has allowed to infer relevant astrophysical~\cite{LIGOScientific:2021aug} and cosmological~\cite{LIGOScientific:2021psn} information on the compact-object population in our local Universe, and also to probe General Relativity (GR) in the high-velocity, dynamical and strong-field regime of gravity~\cite{LIGOScientific:2021sio}.
+The latter complement tests of GR in the low-velocity, quasi-static or linear regimes available with Solar-System experiments~\cite{Will:2014kxa}, binary-pulsar~\cite{Wex:2014nva} and galactic center~\cite{GRAVITY:2018ofz,Do:2019txf,EventHorizonTelescope:2019ths} observations,
+and cosmological measurements~\cite{Clifton:2011jh}.
+
+The coalescence of two BHs in GR is characterized by a long \textit{inspiral} stage, during which the 
+holes adiabatically and steadly come closer and closer to each other, loosing energy because of the emission 
+of GWs.
+Then, they \textit{merge}, forming a common apparent horizon.
+Subsequently, during the \textit{ringdown} stage, the newly formed remnant object settles down to a Kerr BH emitting quasi-normal modes (QNMs)~\cite{Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza}.
+Because of the no-hair conjecture in GR~\cite{Carter:1971zc,Israel:1967wq,Hawking:1971vc,Robinson:1975bv}, the QNM (complex) frequencies of (electrically neutral) astrophysical BHs are only described by the BH's mass and spin.
+In GR, the QNM frequencies are labeled by the harmonic indices $(\ell,m)$ and the overtone number $n$.
+
+Several null tests have been proposed to probe the nature of gravity with GW signals~\cite{TheLIGOScientific:2016src,Yunes:2016jcc,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks,LIGOScientific:2021sio}.
+They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the intermediate (plunge) and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow to set upper limit on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
+mass of the graviton; tests of the polarization of gravitational radiation~
+\cite{Will:2014kxa}, for which more than 
+two GW detectors are needed to set statistically significant bounds, and tests of the remnant properties~\cite{Meidam:2014jpa,Carullo:2018sfu,Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui}
+during the post-merger stage. So far, none of these null tests have reported any deviation from GR.
+
+Probing the gravitational properties of the remnant object during the
+ringdown, has attracted a lot of attention in the last twenty years. 
+Reference~\cite{Dreyer:2003bv} proposed the idea of employing spectroscopy
+of the ringdown stage to rule out (or constrain) either modified theories of 
+gravity or exotic compact objects (in GR) rather than BHs, thus 
+testing the no-hair conjecture. Since then, many studies have quantified the accuracy 
+with which the QNM (complex) frequencies can be measured for
+GW sources detectable with ground- and space-based detectors (see, e.g., Refs.~\cite{Berti:2005ys,Baibhav:2020tma,Bhagwat:2021kwv}). Several analyses~\cite{Carullo:2018sfu,
+Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui}  
+have used the GW observations of the LIGO-Virgo-KAGRA (LVK) collaboration to set upper 
+limits on deviations in the QNM (complex) frequencies of BHs in GR. Others have claimed 
+the measurements of QNMs beyond the dominant $(2,2,0)$ mode~\cite{Capano:2021etf}, 
+or overtones --- for example the $(2,2,1)$ ymode~\cite{Isi:2019aib,Cotesta:2022pci,Isi:2022mhy}. These studies have been pursued either using a superposition 
+of damped sinusoids~\cite{Giesler:2019uxc,Carullo:2019flw}, in some cases augmemted with QNM amplitudes calibrated to 
+numerical-relativity simulations, or with parameterized inspiral-merger-ringdown (IMR) 
+waveform models, where the QNM (complex) frequencies are not necessarily fixed 
+to the GR values for BHs, but kept free~\cite{Brito:2018rfr,Ghosh:2021mrv}.
+
+Here, we will employ the parameterized IMR model of Ref.~\cite{Ghosh:2021mrv}, constructed from a nonprecessing-spin effective-one-body (EOB) waveform model~\cite{Bohe:2016gbl,Cotesta:2018fcv,Mihaylov:2021bpf}, to carry out theory-specific tests of the
+ringdown using four high-curvature gravity theories. Previously, such parameterized 
+waveform model was employed in Refs.~\cite{Abbott:2020jks,LIGOScientific:2021sio} for theory-independent tests of the ringdown.
+More specifically, here we will focus on four modified gravity theories, Einstein-dilaton Gauss-Bonnet gravity, dynamical
+Chern-Simon gravity, cubic and quartic effective-field theories of GR, and 
+express the QNM (complex) frequencies using the parametrized ringdown spin-expansion coefficients (ParSpec) 
+of Ref.~\cite{Maselli:2019mjd}. In such a framework, the non-GR QNM frequencies are  
+recast as deviations from the GR QNM values, and are expressed in terms of a single-free parameter, 
+the fundamental length-scale $\ell_{\rm th}$ of the gravity theory under consideration, the GR limit 
+corresponding to $\ell_{\rm th} \rightarrow 0$.
+
+With this formulation of the ringdown, we use the two loudest merger-ringdown GW events, so far 
+observed by the LVK collaboration, notably GW150914 and GW200129, and Bayesian-inference techniques to 
+perform null tests. We find that GR is not violated, and we set upper limits, at $90\%$ credible level, 
+on the length-scale $\ell_{\rm th}$. In Table~\ref{tab:bound_summary}, we summarize our results, and compare 
+them with existing constraints.
 
@@
 \end{tabular}
-\caption{\hs{Mention it in the Introduction later, in a sort of `executive summary'.}}
+\caption{Summary of the upper limits, at $90\%$ credible level, 
+on the length-scale of the modified gravity theories under investigation. 
+They were obtained combining Bayesian-inference results from GW150914 and GW200129. 
+Current constraints on $\ell_{\rm th}$ are also listed.}
 \label{tab:bound_summary}
@@
 
-\ab{Unless otherwise specified, we will work in geometric units $G = 1 = c$.}
+The paper is organized as follows. In Sec.~\ref{sec:review_theories}, we briefly describe the four 
+higher-curvature modified gravity theories for which we peform the ringdown test. 
+In Sec.~\ref{sec:method} we build our parameterized IMR model for nonprecessing-spin compact-object 
+binaries making use of the ParSpec framework. After reviewing the Bayesian inference method, 
+in Sec.~\ref{sec:pe}, we motivate our selection of GW events from the LVK catalog, and also 
+discuss the range of validity of our analyses. In particular, we discuss the impact on 
+our results of the assumptions underlying the ParSpec framework, and the fact that 
+our modified gravity theories have to be interpreted as EFTs. In Sec.~\ref{sec:results}, 
+we present our results obtained by applying Bayesian analysis on the LVK data of 
+GW150914 and GW1200129, and discuss how we set the upper limits 
+on the fundamental length-scales $\ell_{\rm th}$. Finally, in Sec.~\ref{sec:conclusions} we 
+summarize our findings, and discuss how to make our framework more robust, in view 
+of stronger GW events in upcoming GW observational runs, by including  physical effects currently absent in our 
+study (e.g., precessing-spins and eccentricity). In the Appendix~\ref{app:map_details} 
+we provide details in calculating the nonGR QNM (complex) frequencies, when using ParSpec,  
+for the four modified gravity theories under consideration.
+
+Henceforth, unless otherwise specified, we work in geometric units $G = 1 = c$.
 
@@
 and $(5,5)$. Such a model was built by applying the post-adiabatic approximation~\cite{Nagar:2018gnk}
-to the multipolar spin-aligned effective-one-body (EOB) waveform model of Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv}
-(henceforth we refer to our baseline model as \SEOB{}\footnote{This waveform
+to the multipolar spin-aligned effective-one-body (EOB) waveform model of Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv} (henceforth we refer to our baseline model as \SEOB{}\footnote{This waveform
 model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA}

### 2022-04-20 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
draft intro + new refs

@@
 %
-using the neutron-star--black-hole binaries GW200105 and
+using the NSBH binaries GW200105 and
 GW200115~\cite{LIGOScientific:2021qlt} while Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, obtained
@@
 %
-by stacking the posteriors of $\ell_{\rm EdGB}$ from a selection of binary BHs (BBH)
+by stacking the posteriors of $\ell_{\rm EdGB}$ from a selection of BBHs 
 from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}~\footnote{These bounds
@@
 %
-by folding data from the X-ray observations of the isolated neutron star
+by folding data from the X-ray observations of the isolated NS 
 PSR~J0030+0451~\cite{Lommen:2000yt,NANOGrav:2017wvv} by
 NICER~\cite{Riley:2019yda,Miller:2019cac} and from the GW observation of the binary
-neutron star GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}.
+NS GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}.
 
@@
 %
-This type of parametrization\footnote{\hs{See also
+This type of parametrization~\footnote{See also
 Refs.~\cite{Glampedakis:2017dvb,Glampedakis:2019dqh,Silva:2019scu} and
-Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj,Kimura:2020mrh} for alternative parametrizations.}}
+Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj,Kimura:2020mrh} for alternative parametrizations.}
 was adopted, for instance, in Refs.~\cite{Gossan:2011ha,Meidam:2014jpa,Brito:2018rfr,Carullo:2018sfu,Ghosh:2021mrv}.
 
-The current LIGO-Virgo-KAGRA tests of BH ringdown (see Sec.VII.A
+The current LVK tests of BH ringdown (see Sec.VII.A
 of Ref.~\cite{LIGOScientific:2020tif} or Sec.VIII.A
@@
 In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by \redsout{using} the \redsout{other}
-length-scale associated with the remnant black hole (i.e., its source-frame mass
+length-scale associated with the remnant BH (i.e., its source-frame mass
 $M^{\rm s}_{\rm f}$\footnote{Throughout this paper, we maintain the convention of
@@
 As in Refs.~\cite{Brito:2018rfr,Ghosh:2021mrv}, we use an IMR BBH waveform
-model where the (complex\hs{-valued}) frequencies describing the remnant object
+model where the (complex-valued) frequencies describing the remnant object
 are left additionally free and estimated directly from the data.
@@
 infer the properties of the underlying GW signal; then, we identify the most promising
-events from the catalog of LIGO-Virgo-KAGRA GW observations to base our analyses on. Finally,
+events from the catalog of LVK GW observations to base our analyses on. Finally,
 we discuss how we can interpret our results after taking into account the region of validity of
@@
 
-\subsection{Event selection}
+\subsection{Events selection}
 
@@
 %
-The latest LIGO-Virgo-KAGRA GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
+The latest LVK GW catalog~\cite{LIGOScientific:2021djp} reported 90 observed
 signals not all of which are relevant for our BH ringdown analysis. In fact, in
@@
 %
-\hs{Here we explore the range $\varepsilon \in [0, 1]$, but following
+Here we explore the range $\varepsilon \in [0, 1]$, but following
 the Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} we quote our final results using
-$\varepsilon = 1/2$.}
+$\varepsilon = 1/2$. 
 % %
@@
 We say that a bound has been placed on $\ell_{\rm th}$, if most of the PDF $P(\ell_{\rm th} | d)$ support is in the interval
-$[0, \, \Lambda_{\rm EFT}(\hs{1/2}, \mathfrak{m})]$.
+$[0, \, \Lambda_{\rm EFT}(1/2, \mathfrak{m})]$.
 %
@@
 does have maximum support at $\gamma_{\rm EdGB} = 0$. This shows that our model is consistent with GR. 
-\hs{The right panel shows the PDFs in the range $0 \leqslant \gamma_{\rm EdGB} \leqslant 1$. Note how
+The right panel shows the PDFs in the range $0 \leqslant \gamma_{\rm EdGB} \leqslant 1$. Note how
 the curves are flat in this range for both events and when $N_{\rm max} = 1$.}
-}
 \label{fig:gamma_gb}
@@
 % \abcomm{Please update the paragraph below.}
-\hs{
-In this theory, we have considered only $N_{\rm max} = 0$. We found that the
-inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
-for which the ringdown portions of the larger than the inspiral-plunge part.
+In this theory, we have considered only $N_{\rm max} = 0$. We find that the
+inclusion of the spin corrections yields waveforms that for $\ell_{\rm qEFT} \gtrsim 80$~km, 
+for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence 
+has some problems in English. I do not udnerstand it.}
 %
@@
 which were essentially uniform, as our prior, and thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
-}
 %
@@
 modified gravity theories (EdGB, dCS, cubic, and quartic EFTs of GR) using
-observational data from the LIGO-Virgo-KAGRA's events GW150914 and GW200129.
+observational data from the LVK events GW150914 and GW200129.
 %
@@
 %
-In that case, it is dCS which is unconstrained \hs{with already observed GW
+In that case, it is dCS which is \ab{poorly constrained with current observed GW
 events}, while EdGB can be constrained, as shown in Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
 %
-\hscomm{I will a sentence here on Refs.~\cite{Alexander:2017jmt,Loutrel:2018ydv,Loutrel:2018rxs}.}
+\hscomm{I will add a sentence here on Refs.~\cite{Alexander:2017jmt,Loutrel:2018ydv,Loutrel:2018rxs}.}
 
@@
 
-\hscomm{TODO: add that we could try to parametrize the final black hole mass and spin estimates formulas we
+\hscomm{TODO: add that we could try to parametrize the final BH mass and spin estimates formulas we
 use at the moment~\cite{Hofmann:2016yih}. Maybe comment that a possible first attempt could follow~\cite{Buonanno:2007sv},
@@
 %
+
 This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open
@@
 %
+
 The authors would like to thank everyone at the frontline of the Covid-19

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: reading through intro; acronyms; new refs

@@
 
-The large number of GW observations has allowed to infer relevant astrophysical~\cite{LIGOScientific:2021aug} and cosmological~\cite{LIGOScientific:2021psn} information on the compact-object population in our local Universe, and also to probe General Relativity (GR) in the high-velocity, dynamical and strong-field regime of gravity~\cite{LIGOScientific:2021sio}.
-The latter complement tests of GR in the low-velocity, quasi-static or linear regimes available with Solar-System experiments~\cite{Will:2014kxa}, binary-pulsar~\cite{Wex:2014nva} and galactic center~\cite{GRAVITY:2018ofz,Do:2019txf,EventHorizonTelescope:2019ths} observations,
+The large number of GW observations has allowed us to infer relevant astrophysical~\cite{LIGOScientific:2021aug} and cosmological~\cite{LIGOScientific:2021psn} information on the compact-object population in our local Universe, and also to probe General Relativity (GR) in the high-velocity, dynamical and strong-field regime of gravity~\cite{LIGOScientific:2021sio}.
+The latter complement tests of GR in the low-velocity, quasi-static or linear regimes available with Solar-System experiments~\cite{Will:2014kxa}, binary-pulsar~\cite{Wex:2014nva,Kramer:2021jcw} and galactic-center~\cite{GRAVITY:2018ofz,Do:2019txf,EventHorizonTelescope:2019ths} observations,
 and cosmological measurements~\cite{Clifton:2011jh}.
@@
 Then, they \textit{merge}, forming a common apparent horizon.
-Subsequently, during the \textit{ringdown} stage, the newly formed remnant object settles down to a Kerr BH emitting quasi-normal modes (QNMs)~\cite{Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza}.
+Subsequently, during the \textit{ringdown} stage, the newly formed remnant object settles down to a Kerr BH emitting quasinormal modes (QNMs)~\cite{Vishveshwara:1970cc,Press:1971wr,Chandrasekhar:1975zza}.
 Because of the no-hair conjecture in GR~\cite{Carter:1971zc,Israel:1967wq,Hawking:1971vc,Robinson:1975bv}, the QNM (complex) frequencies of (electrically neutral) astrophysical BHs are only described by the BH's mass and spin.
@@
 They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the intermediate (plunge) and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow to set upper limit on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
-mass of the graviton; tests of the polarization of gravitational radiation~
-\cite{Will:2014kxa}, for which more than 
+mass of the graviton; tests of the polarization of gravitational radiation~\cite{Will:2014kxa}, for which more than
 two GW detectors are needed to set statistically significant bounds, and tests of the remnant properties~\cite{Meidam:2014jpa,Carullo:2018sfu,Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui}
@@
 ringdown, has attracted a lot of attention in the last twenty years.
-Reference~\cite{Dreyer:2003bv} proposed the idea of employing spectroscopy
+Reference~\cite{Dreyer:2003bv} proposed the idea of employing BH spectroscopy~\cite{Detweiler:1980gk}
 of the ringdown stage to rule out (or constrain) either modified theories of
@@
 testing the no-hair conjecture. Since then, many studies have quantified the accuracy
-with which the QNM (complex) frequencies can be measured for
-GW sources detectable with ground- and space-based detectors (see, e.g., Refs.~\cite{Berti:2005ys,Baibhav:2020tma,Bhagwat:2021kwv}). Several analyses~\cite{Carullo:2018sfu,
+with which the QNM frequencies can be measured for
+GW sources detectable with ground- and space-based detectors (see, e.g., Refs.~\cite{Berti:2005ys,Baibhav:2020tma,Bhagwat:2021kwv,Ota:2021ypb}). Several analyses~\cite{Carullo:2018sfu,
 Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui}
 have used the GW observations of the LIGO-Virgo-KAGRA (LVK) collaboration to set upper
-limits on deviations in the QNM (complex) frequencies of BHs in GR. Others have claimed 
+limits on deviations in the QNM frequencies of BHs in GR. Others have claimed
 the measurements of QNMs beyond the dominant $(2,2,0)$ mode~\cite{Capano:2021etf},
-or overtones --- for example the $(2,2,1)$ ymode~\cite{Isi:2019aib,Cotesta:2022pci,Isi:2022mhy}. These studies have been pursued either using a superposition 
+or overtones --- for example the $(2,2,1)$ mode~\cite{Isi:2019aib,Cotesta:2022pci,Isi:2022mhy}.
+%
+These studies have been pursued either using a superposition
 of damped sinusoids~\cite{Giesler:2019uxc,Carullo:2019flw}, in some cases augmemted with QNM amplitudes calibrated to
-numerical-relativity simulations, or with parameterized inspiral-merger-ringdown (IMR) 
-waveform models, where the QNM (complex) frequencies are not necessarily fixed 
+numerical-relativity (NR) simulations, or with parameterized inspiral-merger-ringdown (IMR)
+waveform models, where the QNM frequencies are not necessarily fixed
 to the GR values for BHs, but kept free~\cite{Brito:2018rfr,Ghosh:2021mrv}.
@@
 waveform model was employed in Refs.~\cite{Abbott:2020jks,LIGOScientific:2021sio} for theory-independent tests of the ringdown.
-More specifically, here we will focus on four modified gravity theories, Einstein-dilaton Gauss-Bonnet gravity, dynamical
-Chern-Simon gravity, cubic and quartic effective-field theories of GR, and 
-express the QNM (complex) frequencies using the parametrized ringdown spin-expansion coefficients (ParSpec) 
-of Ref.~\cite{Maselli:2019mjd}. In such a framework, the non-GR QNM frequencies are  
-recast as deviations from the GR QNM values, and are expressed in terms of a single-free parameter, 
+%
+More specifically, here we will focus on four modified gravity theories, Einstein-dilaton-Gauss-Bonnet gravity, dynamical
+Chern-Simon gravity, cubic and quartic effective-field theories (EFTs) of GR, and
+express the QNM frequencies using the parametrized ringdown spin-expansion coefficients (ParSpec)
+of Ref.~\cite{Maselli:2019mjd}.
+%
+In this framework, the non-GR QNM frequencies are
+recast as deviations from the GR QNM values, and are expressed in terms of a single free parameter,
 the fundamental length-scale $\ell_{\rm th}$ of the gravity theory under consideration, the GR limit
@@
 With this formulation of the ringdown, we use the two loudest merger-ringdown GW events, so far
-observed by the LVK collaboration, notably GW150914 and GW200129, and Bayesian-inference techniques to 
-perform null tests. We find that GR is not violated, and we set upper limits, at $90\%$ credible level, 
-on the length-scale $\ell_{\rm th}$. In Table~\ref{tab:bound_summary}, we summarize our results, and compare 
+observed by the LVK collaboration, notably GW150914 and GW200129, and use Bayesian-inference techniques to
+perform null tests. We find no indication that GR is violated and, when possible, we place upper limits, at $90\%$ credible level,
+on the length-scale $\ell_{\rm th}$ of each theory. In Table~\ref{tab:bound_summary}, we summarize our results, and compare
 them with existing constraints.
 
-\begin{table}[th]
+\begin{table}[t]
 \begin{tabular}{c | c c}
@@
 \hline
-EdGB        & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
-dCS         & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 38.7$~km \\
+EdGB        & $\ell_{\rm EdGB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
+dCS         & $\ell_{\rm dCS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm dCS} \leqslant 38.7$~km \\
 cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
@@
 study (e.g., precessing-spins and eccentricity). In the Appendix~\ref{app:map_details}
-we provide details in calculating the nonGR QNM (complex) frequencies, when using ParSpec,  
+we provide details in calculating the non-GR QNM frequencies, when using ParSpec,
 for the four modified gravity theories under consideration.
-
+%
 Henceforth, unless otherwise specified, we work in geometric units $G = 1 = c$.
@@
 %
-\begin{equation} \label{eq:action_sgb}
+\begin{align} \label{eq:action_sgb}
     S_{\rm EdGB} = \frac{1}{16 \pi}
@@
     \right]\,,
-\end{equation}
+    \nonumber \\
+\end{align}
 %
@@
 An accurate description of the merger is incorporated through calibration with
-numerical relativity (NR) simulations, as described in Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv}, along with
+NR simulations, as described in Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv}, along with
 information for the merger and ringdown phases, from BH perturbation theory.

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
updated theory discussion, in part. dcs

@@
 We confront the resultant waveform models against the two loudest
-gravitational-wave ringdown signals, so far, notably, GW150914 and GW200129.
+gravitational-wave ringdown signals observed so far, notably, GW150914 and GW200129.
 %
@@
 the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GWs signals \cite{LIGOScientific:2021djp} from mergers
-of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2020aai} and their mixture \cite{LIGOScientific:2021qlt}. These results have been confirmed
+of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki,LIGOScientific:2020aai} and their mixture \cite{LIGOScientific:2021qlt}. These results have been confirmed
 by independent analyses, which have also identified a few new GW signals~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq,Nitz:2021zwj,Olsen:2022pin}.
@@
     \left[
-    R - \tfrac{1}{2}(\nabla \varphi)^2
+    R - \tfrac{1}{2}(\partial \varphi)^2
     + \tfrac{1}{4} \ell^{2}_{\rm EdGB} f(\varphi) \, \mathcal{G}
-    \right]\,,
+    \right],
     \nonumber \\
@@
 where $g \equiv \textrm{det}(g_{\mu \nu})$ is the metric determinant, $R$ is the Ricci
-scalar, $\varphi$ is a dynamical scalar field that couples to the
-Gauss-Bonnet invariant
+scalar, $\varphi$ is a dynamical scalar field, with kinetic term $(\partial \varphi)^2 = g^{\mu\nu} \partial_{\mu} \varphi \partial_{\nu} \varphi$,
+which couples to the Gauss-Bonnet invariant
 %
@@
 In this case, the theory admits the same stationary, asymptotically flat BH
-solutions as GR and those of scalarized
+solutions as GR~\cite{Silva:2017uqg} and those of scalarized
 BHs~\cite{Doneva:2017bvd,Silva:2017uqg,Macedo:2019sem,Dima:2020yac,Herdeiro:2020wei,Berti:2020kgk}.
 %
-Examples include the Gaussian $f(\varphi) \propto \exp(-\varphi^2)$~\cite{Doneva:2017bvd} and
+Examples include Gaussian $f(\varphi) \propto \exp(-\varphi^2)$~\cite{Doneva:2017bvd} and
 the quadratic $f(\varphi) \propto \varphi^2$~\cite{Silva:2017uqg} coupling functions.
+
 BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
@@
 This charge is not an independent parameter, and depends on the BH's mass and spin,
-thus being a ``secondary hair''~\cite{Coleman:1991ku,Herdeiro:2015waa}.
+thus being a ``secondary hair''~\cite{Coleman:1991ku,Kanti:1995vq,Herdeiro:2015waa}.
 %
@@
 charges of binary components. This makes EdGB gravity testable with present GW
-observations of compact binaries where at least if one component is a BH.
+observations of compact binaries where at least one component is a BH.
 %
@@
 by stacking the posteriors of $\ell_{\rm EdGB}$ from a selection of BBHs
-from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}~\footnote{These bounds
+from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}\footnote{These bounds
 are, strictly speaking, valid only when the scalar field $\varphi$ is small (i.e., $\varphi \ll 1$), and
 take into account only the leading-order scalar field contribution arising from the dilatonic coupling.}.
-Secondly, the scalar field does influence the response of BHs to linearized perturbations and thus
-affects the BH QNM spectra.
+Secondly, the scalar field influences the response of BHs to linearized perturbations and thus
+affects the BH's QNM spectra.
 %
@@
 (i.e., the isospectrality~\cite{Chandrasekhar:1985kt}) for Schwarzschild BHs in GR.
-%
-
-The QNMs for nonrotating BHs in EdGB gravity were first computed in
-Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and were
-extended to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
+
+Using BH perturbation theory, the QNMs for nonrotating BHs in EdGB gravity
+were first computed in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn}
+and were extended to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
+%
+See also Refs.~\cite{Witek:2018dmd,Okounkova:2019zep} for NR studies.
 
@@
     \left[
-    R - \tfrac{1}{2}(\nabla \vartheta)^2
+    R - \tfrac{1}{2}(\partial \vartheta)^2
     + \tfrac{1}{4} \ell^{2}_{\rm dCS} \, \vartheta \, {}^{*}RR
@@
 %
-However, a coupling with $\vartheta$ can modify the field equations.
-%
-The coupling strength is set by the coupling constant $\ell_{\rm dCS}$, with
-dimensions of length.
-
-The theory admits as a solution, the garden-variety Schwarzschild BH of GR. This
-is not the case when rotation is included and the Kerr metric is not a solution of
-the theory~\cite{Jackiw:2003pm}.
+The Pontryagin density can, however, modify the field equation when coupled to $\vartheta$;
+the strength of the coupling set by $\ell_{\rm dCS}$, with dimensions of length.
+%
+% However, a coupling with $\vartheta$ can modify the field equations.
+% %
+% The coupling strength is set by the coupling constant $\ell_{\rm dCS}$, with
+% dimensions of length.
+
+The theory admits as a solution, the garden-variety Schwarzschild BH of GR.
+This is not the case when rotation is included and the Kerr metric is not a
+solution of the theory~\cite{Jackiw:2003pm}.
 %
@@
 $r^{-2}$ asymptotically, to which we can associate a scalar dipole
-charge~\cite{Yunes:2009hc,Konno:2009kg}.
-%
-As a consequence, the leading-scalar radiative channel of BBH to lose energy is quadrupolar,
-which affects the GW phase at 2PN order~\cite{Yagi:2011xp,Alexander:2017jmt}.
+charge~\cite{Yunes:2009hc,Konno:2009kg} and
+%
+the leading-order modification to the GW phase enters at 2PN~\cite{Yagi:2011xp}.
 %
 Deviations from GR at this PN order are constrained with present GW observations~\cite{LIGOScientific:2021sio}
-\ab{only at the level of $\sim 50\%$ (see the constraint on the 2PN parameter $\varphi_4$ in Fig.XXX of
-Ref.~\cite{LIGOScientific:2021sio}). Thus, dCS gravity is poorly constrained by
-analyses that rely on the inspiral portion of GWs when using current BBH observations are used~\cite{Nair:2019iur,Perkins:2021mhb}.}
+only at the level of $\sim 50\%$ (see the constraint on the 2PN parameter $\varphi_4$ in Fig.~6 of
+Ref.~\cite{LIGOScientific:2021sio}). Thus, so far, dCS gravity has remained
+unconstrained by works which use only on the inspiral portion of BBH GW signals~\cite{Nair:2019iur,Perkins:2021mhb}.
 %
@@
 NICER~\cite{Riley:2019yda,Miller:2019cac} and from the GW observation of the binary
-NS GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}.
+NS GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}, using
+equation-of-state independent relations between NS moment of inertia and tidal deformability~\cite{Yagi:2013bca,Yagi:2013awa,Gupta:2017vsl}.
 
@@
 %
-They were also extracted from numerical-relativity simulations of head-on BH collisions
-in Ref.~\cite{Okounkova:2019dfo}.
+They were also extracted from NR simulations of BH head-on collisions in Ref.~\cite{Okounkova:2019dfo}.
 
@@
 In addition, in the dimension-six case we further assume that $\lame = \lamo = 1$,
-leaving us with \redsout{$\ell =$} $\ell_{\rm cEFT}$ as our single free parameter.
+leaving us with $\ell_{\rm cEFT}$ as our single free parameter.
 %
@@
 %
-This leaves us with \redsout{$\ell =$} $\ell_{\rm qEFT}$ as our single free parameter.
+This leaves us with $\ell_{\rm qEFT}$ as our single free parameter.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
working on the appendix

@@
 %
-This type of parametrization~\footnote{See also
+This type of parametrization\footnote{See also
 Refs.~\cite{Glampedakis:2017dvb,Glampedakis:2019dqh,Silva:2019scu} and
@@
 %
-In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by \redsout{using} the \redsout{other}
+In Eq.~\eqref{eq:def_gamma} we made $\gamma$ dimensionless by the
 length-scale associated with the remnant BH (i.e., its source-frame mass
@@
 As in Refs.~\cite{Brito:2018rfr,Ghosh:2021mrv}, we use an IMR BBH waveform
-model where the (complex-valued) frequencies describing the remnant object
+model where the complex-valued frequencies describing the remnant object
 are left additionally free and estimated directly from the data.
@@
 \begin{align}
-    M_{\rm f}\, \omega &= \gamma \left [ \delta\omega^{(0)} \omega^{(0)} + \chi_{\rm f} \delta\omega^{(1)} \omega^{(1)} \right ]
+    M_{\rm f}\, \omega &= \gamma \left [ \delta\omega^{(0)} \omega^{(0)} + \chi_{\rm f}\, \delta\omega^{(1)} \omega^{(1)} \right ]
     + \sum_{j=0}^{N_{\rm max}} \chi^{j}_{\rm f}\, \omega^{(j)} \,,
 \\
-    \frac{\tau}{M_{\rm f}}   &= \gamma \left [ \delta\tau^{(0)} \tau^{(0)} + \chi_{\rm f} \delta\tau^{(1)} \tau^{(1)} \right ]
+    \frac{\tau}{M_{\rm f}}   &= \gamma \left [ \delta\tau^{(0)} \tau^{(0)} + \chi_{\rm f}\, \delta\tau^{(1)} \tau^{(1)} \right ]
     + \sum_{j=0}^{N_{\rm max}} \chi^{n}_{\rm f}\, \tau^{(j)}\,,
@@
 \hline
-EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
+EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
 dCS         & --                   & --                 &  --                  & --                 & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
@@
 %
-In non-GR theories, isospectrality is in general broken (see
+In beyond-GR theories, isospectrality is in general broken (see
 in Ref.~\cite{Hui:2021cpm} for a counterexample).
@@
 Moreover, and what is more relevant for our analysis, are their post-inspiral
-(merger-ringdown) SNRs which are both $\sim `6$ (see the columns for
+(merger-ringdown) SNRs which are both $\approx 6$ (see the columns for
 $\rho_{\text{post-insp}}$ in Table III of Ref.~\cite{LIGOScientific:2019fpa} and
@@
 remnant BH, suppresses scalar field's charge relatively to the initial binary
-components.~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
-Point this out in the conclusions after all specific theories are discussed.}
+components.
 %
@@
 
-We presented an unified framework to combine the ParSpec formalism introduced
+We presented an unified framework that combines the ParSpec formalism introduced
 to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
@@
 region of validity of the ParSpec framework, the coupling constant of dCS gravity is bound to
-$\ell_{\rm CS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
+$\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
 of GW150914 and GW200129.
 %
-In contrast, we could not place any constraint of the coupling constants in EdGB gravity $\ell_{\rm GB}$.
+In contrast, we could not place any constraint of the coupling constants in EdGB gravity $\ell_{\rm EdGB}$.
 %
@@
 perturbative bounds. If so, add explanation here.}
+
+~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
+Point this out in the conclusions after all specific theories are discussed.}
 
@@
 %
-\hs{Here, $\chi_{\rm eff}$ is the dimensionless effective-spin parameter, related to the individual spins $\chi_{i}$
-and masses $m_{i}$ of each binary component as $\chi_{\rm eff} \equiv (m_1 \chi_1 + m_2 \chi_2) / (m_1 + m_2)$.}
+Here, $\chi_{\rm eff}$ is the dimensionless effective-spin parameter, related to the individual spins $\chi_{i}$
+and masses $m_{i}$ of each binary component as $\chi_{\rm eff} \equiv (m_1 \chi_1 + m_2 \chi_2) / (m_1 + m_2)$.
 %
@@
 
-We start by considering EdGB gravity, for which the QNMs of nonrotating and
-slowly-rotating BHs where calculated in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk}
-and~\cite{Pierini:2021jxd}, respectively.
+We start by considering EdGB gravity and, in particular, focus on
+Refs.~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} to determine the
+ParSpec coefficients for this theory.
+% and~\cite{Pierini:2021jxd} for the QNMs of for which the QNMs of nonrotating and
+% slowly-rotating BHs where calculated in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk}
+% and~\cite{Pierini:2021jxd}, respectively.
 %
@@
 of the polar gravitational-led modes increases as the coupling constant
-$\ell_{\rm EdGB}$ is increased.
+$\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
+branch of QNMs was calculated in~\cite{Pierini:2021jxd}.
 %
@@
 For the nonrotating QNMs we used the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
-generated a new quartic in $\ell_{\rm EdCS}$ fit to the data valid for small
-values of the coupling constant [see, in particular, Eq.~(27) and Fig.~2 of~\cite{Blazquez-Salcedo:2016enn}].
+generated a new quartic fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
+values of the coupling constant [see, in particular, Eq.~(27) and Fig.~2 of Ref.~\cite{Blazquez-Salcedo:2016enn}].
 %
@@
 \begin{align}
-    M {\rm Re}(\sigma)_{\rm EdGB} &= M {\rm Re}(\sigma)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
+    M {\rm Re}(\sigma)_{\rm EdGB} &= M {\rm Re}(\sigma)_{\rm GR} \, \left( 1 + 0.0107 \, \gamma_{\rm EdGB}^4 \right),
     \\
-    M {\rm Im}(\sigma)_{\rm EdGB} &= M {\rm Im}(\sigma)_{\rm GR} \, \left[ 1 - 0.0044 (\ell_{\rm EdGB} / M)^4 \right].
+    M {\rm Im}(\sigma)_{\rm EdGB} &= M {\rm Im}(\sigma)_{\rm GR} \, \left( 1 - 0.0044 \, \gamma_{\rm EdGB}^4 \right).
 \end{align}
@@
 %
-The smallness of the numerical prefactors of $\ell_{\rm EdGB}^4$ are a consequence of the how weakly the QNMs
+The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ are a consequence of the how weakly the QNMs
 of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $(\ell_{\rm EdGB} / M)^4 \approx 0.3$.
@@
 The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
-which for consistency, with our previous discussion, we truncated at quartic-order in $\ell_{\rm EdGB}$.
-%
-Taken together, all use as our fitting expressions for the QNM is EdGB gravity
+which for consistency with our previous discussion, we truncated at quartic-order in $\gamma_{\rm EdGB}$.
+%
+Taken together, use as our fitting expressions for the QNM is EdGB gravity
 %
@@
 \begin{align}
-    M {\rm Re}(\sigma)_{\rm EdGB} &= \dots % {\rm Re}(\omega)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
+    M {\rm Re}(\sigma)_{\rm EdGB} &= {\rm Re}(\omega)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
     \\
@@
 Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
-this is the branch of QNMs we will select.
+this is the branch of QNMs we chose to work with.
 
@@
 \begin{equation}
-    M \omega_{\rm CS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+    M {\rm Re}(\omega)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
     \label{eq:omega_dsc_eg}
@@
 %
-and similarly for the imaginary part ${\rm Im}(\sigma_{\rm dCS}) =  - 1 / \tau_{\rm dCS}$.
+and similarly for the imaginary part, ${\rm Im}(\sigma)_{\rm dCS} =  - 1 / \tau_{\rm dCS}$.
 %
@@
 \begin{equation}
-    \kappa \zeta = (\ell_{\rm dCS} / M)^4 \,,
-\end{equation}
-%
-and $c_{i}$ are fitting coefficients which can be found in Ref.~\cite{Wagle:2021tam}, Table II.
+    \kappa \zeta = (\ell_{\rm dCS} / M)^4 = \gamma_{\rm dCS},
+\end{equation}
+%
+and $c_{i}$ (with $i=1, \dots, 6$) are fitting coefficients which can be found in
+Ref.~\cite{Wagle:2021tam},~Table II.
 
@@
 \begin{equation}
-p_{\rm dCS} = 4\,, \quad \delta \omega^{(0)}_{\rm dCS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm dCS} = 41.199\,.
+p_{\rm dCS} = 4\,, \quad \delta \omega^{(0)}_{\rm dCS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm dCS} = 41.199.
 \label{eq:cs_omega_coefs}
 \end{equation}
-
+%
 We can carry the same steps for $\tau_{\rm dCS}$ and find
@@
 \begin{equation}
-\delta \tau^{(0)}_{\rm dCS} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm dCS} = 794.66\,.
+\delta \tau^{(0)}_{\rm dCS} = 6.3619\,, \quad \delta \tau^{(1)}_{\rm dCS} = 794.66,
 \label{eq:cs_tau_coefs}
@@
 %
-which completes the set of fixed parameters beyond-GR parameters in the ringdown of the \pSEOB{} waveform model.
-%
-We remark that the alarmingly large values of $\delta \omega_{\rm dCS}^{(1)}$ and $\delta \tau_{\rm dCS}^{(1)}$
-are compensated by the assumptions that $(\ell_{\rm dCS} / M_{\rm f})^2$ and $\chi$ are much less than unity,
-which are the assumptions in Ref.~\cite{Wagle:2021tam}.
+which completes the set of fixed non-GR parameters in the ringdown of the \pSEOB{} waveform model for this theory.
+%
+As for the case of EdGB gravity, we remark that the alarmingly large values of
+$\delta \omega_{\rm dCS}^{(1)}$ and $\delta \tau_{\rm dCS}^{(1)}$ are
+compensated by the assumptions that $(\ell_{\rm dCS} / M_{\rm f})^2$ and $\chi$
+are much less than unity, which are the assumptions used in Ref.~\cite{Wagle:2021tam}
+to compute the QNMs.
 
@@
 The QNMs of slowly-rotating BHs in both cubic and quartic EFT of GR where calculated in Ref.~\cite{Cano:2021myl}.
+%
+For the cubic EFT, we use their Eq.~(67), particularizing to $\lame = \lamo = 1$. We further linearize that equation in
+$\chi$ and particularize $m=2$.
+%
+This process, shows that the mode labelled ``-'' is the least damped and it is the one we use.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
changes to appendices
more on appendix

@@
 
-For dCS gravity, we follow Ref.~\cite{Wagle:2021tam} which numerically calculated the QNMs of slowly-rotating BHs in this theory
-and found that the axial gravitational modes have their damping time increased as we
+For dCS gravity, we follow Ref.~\cite{Wagle:2021tam} which numerically calculated the QNMs, $\sigma_{\rm dCS}$,
+of slowly-rotating BHs in this theory and found that the axial gravitational modes have their damping time increased as we
 increase the Chern-Simons coupling $\ell_{\rm dCS}$ at fixed spin $\chi$ of the BH.
@@
 
-We can now proceed to determine $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$ as follows.
+We then proceed to determine $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$ as follows.
 %
@@
 \begin{equation}
-    M {\rm Re}(\omega)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+    M \, {\rm Re}(\sigma)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
     \label{eq:omega_dsc_eg}
@@
 %
-For the cubic EFT, we use their Eq.~(67), particularizing to $\lame = \lamo = 1$. We further linearize that equation in
-$\chi$ and particularize $m=2$.
+For the cubic EFT, we use their Eq.~(67), particularizing to $\lame = \lamo = 1$.
+%
+We further linearize that equation in $\chi$ and particularize $m=2$.
 %
 This process, shows that the mode labelled ``-'' is the least damped and it is the one we use.
+%
+Direct comparison with Eqs.~\eqref{eq:qnm_nongr_iso} results in,
+%
+\begin{align}
+    p_{\rm cEFT} = 4, \quad \delta \omega_{\rm cEFT}^{(0)} = - 0.5813, \quad \delta \tau_{\rm cEFT}^{(0)} = 2.6469,
+    \nonumber \\
+    \delta \omega_{\rm cEFT}^{(1)} = -3.8620, \quad \delta \tau_{\rm cEFT}^{(1)} = 265.12.
+\end{align}
+
+We proceed in the same away for the quartic EFT. Here we use Eq.~(68) (with
+$\epsilon_{1} = 1$ and $\epsilon_{2} = 0$) and Eq.~(70) of
+Ref.~\cite{Cano:2021myl},
+%
+In this case we found that both modes (``-'' and ``+'' in the notation of Ref.~\cite{Cano:2020cao}) make the
+fundamental QNM damp fast and we chose the ``-'' mode which decreases less the damping time.
+%
+We then find
+%
+\begin{align}
+    p_{\rm qEFT} = 6, \quad \delta \omega_{\rm qEFT}^{(0)} = -0.2114, \quad \delta \tau_{\rm qEFT}^{(0)} = -0.6070,
+    \nonumber \\
+    \delta \omega_{\rm qEFT}^{(1)} = -1.5263, \quad \delta \tau_{\rm qEFT}^{(1)} = 171.35.
+\end{align}
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
adding contour plot discussion to dcs section

@@
 
-\begin{figure}[t]
-\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
-\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
-remnant mass $M_{\rm f}$ for GW150914, using the same waveform model,
-but without (purple contours) and with the non-GR parameters
-different from zero (blue contours), for
-dCS gravity and $N_{\rm max}=0$ as an example.
-%
-The contours represent 90\% credible levels.
-%
-We see that the introduction of the non-GR parameters does not bias the
-inference on the source parameters.
-}
-\label{fig:corner_plot}
-\end{figure}
-
 The \pSEOB{} model, as described in Sec.~\ref{sec:review_pSEOB}, is an
@@
 
-\subsection{Einstein-dilaton-Gauss-Bonnet gravity}
-\label{sec:results_edgb}
-
-We start with EdGB gravity.
-%
-In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized PDFs of the
-coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
-(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
-%
-The bottom panel shows the joint posterior obtained by combining both events.
-%
-We see, for both events, the $N_{\rm max} = 0$ posteriors are
-characterized by a peak away from zero.
-%
-This does not mean that we are inferring a deviation from GR.
-%
-We recall that the deviations from GR in the ParSpec framework are controlled
-by the dimensionless parameter $\gamma$, which here reads,
-%
-\begin{equation}
-    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M_{f}}\right)^4\,.
-    \label{eq:def_gamma_gb}
-\end{equation}
-%
-As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm EdGB}$ does indeed have a posterior
-distribution with largest support at zero, indicating consistency between
-the underlying signal and GR.
-%
-We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
-displaces the posteriors distributions towards smaller values of $\ell_{\rm EdGB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
-and larger values of $\gamma_{\rm EdGB}$ (see Fig.~\ref{fig:gamma_gb}).
-
 \begin{figure}[t]
@@
 \end{figure}
+
+\subsection{Einstein-dilaton-Gauss-Bonnet gravity}
+\label{sec:results_edgb}
+
+We start with EdGB gravity.
+%
+In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized PDFs of the
+coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
+(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
+%
+The bottom panel shows the joint posterior obtained by combining both events.
+%
+We see, for both events, the $N_{\rm max} = 0$ posteriors are
+characterized by a peak away from zero.
+%
+This does not mean that we are inferring a deviation from GR.
+%
+We recall that the deviations from GR in the ParSpec framework are controlled
+by the dimensionless parameter $\gamma$, which here reads,
+%
+\begin{equation}
+    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M_{f}}\right)^4\,.
+    \label{eq:def_gamma_gb}
+\end{equation}
+%
+As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm EdGB}$ does indeed have a posterior
+distribution with largest support at zero, indicating consistency between
+the underlying signal and GR.
+%
+We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
+displaces the posteriors distributions towards smaller values of $\ell_{\rm EdGB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
+and larger values of $\gamma_{\rm EdGB}$ (see Fig.~\ref{fig:gamma_gb}).
 
@@
 We also note that since the CDF grows fast in approximate domain $\varepsilon = [0.2, 0.4]$,
-that a stronger, albeit at lower credibility,
+that a stronger, albeit at lower credible level,
 %
@@
 \ell_{\rm dCS} \leqslant 37.4~\textrm{km}
-% ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
 \quad \textrm{at 68\% credible level},
@@
 In Table~\ref{tab:summary_dcs} we summarize our findings of this section.
+
+\begin{figure}[t]
+\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
+\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
+remnant mass $M_{\rm f}$ for GW150914, using the same waveform model,
+but without (purple contours) and with the non-GR parameters
+different from zero (blue contours), for
+dCS gravity and $N_{\rm max}=0$.
+%
+The contours represent 90\% credible levels.
+%
+We see that the introduction of the non-GR parameters does not bias the
+inference on the source parameters as required by the ParSpec.
+}
+\label{fig:corner_plot}
+\end{figure}
 
@@
 
-\sout{In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_f$ and
-detector-frame remnant mass $(1 + z) M_{\rm f}$ for GW150914 for GR and the
-illustrative case of dCS gravity. We see that our waveform models does not
-introduce a substantial change to the GR estimates on this parameters, as
-required by the ParSpec expansion (see discussion in
-Sec.~\ref{sec:review_parspec}).}\agcomm{This reference to Fig.2 appears misplaced here.
+\hscomm{Alessandra, I moved the plot here as we discussed.}
+%
+In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_{\rm f}$ and
+remnant mass $M_{\rm f}$ for GW150914 for GR and dCS gravity.
+%
+We see that indeed our waveform models does not introduce substantial changes
+to the GR estimates on these parameters, as required by the ParSpec expansion
+(see discussion in Sec.~\ref{sec:review_parspec}).
+%
+We observed the same in all other theories we studied.
+
+% \agcomm{This reference to Fig.2 appears misplaced here.
 IMO, Fig 2.
@@
 %
-In that case, it is dCS which is \ab{poorly constrained with current observed GW
-events}, while EdGB can be constrained, as shown in Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+In that case, it is dCS gravity which cannot be constrained with current GW
+events, while EdGB can, as shown in Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
 %
@@
 
-We now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\ell_{\rm dCS}$, and
-gather the terms proportional to $\ell_{\rm dCS}$.
+We now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\gamma_{\rm dCS}$, and
+gather the terms proportional to $\gamma_{\rm dCS}$.
 %
@@
 \begin{align}
-    M \, \omega_{\rm dCS} &=
-    \left[ 0.3722 + 1.1945 (\ell_{\rm dCS} / M)^4 \right]
+    M \, \omega_{\rm dCS} =
+    \left( 0.3722 + 1.1945 \gamma_{\rm dCS}^4 \right)
+    + \left(0.1861 + 5.1828 \gamma_{\rm dCS}^4 \right) \, \chi,
     \nonumber \\
-    &\quad + \left[0.1861 + 5.1828 (\ell_{\rm dCS} / M)^4 \right] \, \chi\,,
     \label{eq:omega_dcs_interm}

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more rearrangements

@@
 We give a prescription on how to include in this waveform model the quasinormal mode frequencies
-calculated on a theory-by-theory basis. In particular, we focus on gravity theories that deviate
-from general relativity through higher-order curvature corrections, namely,
+calculated on a theory-by-theory basis. In particular, we focus on theories that deviate
+from general relativity by higher-order curvature corrections, namely,
 Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
@@
 Since the first detection of gravitational waves (GWs) from a binary black-hole (BBH) merger in 2015~\cite{LIGOScientific:2016aoc},
-the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GWs signals \cite{LIGOScientific:2021djp} from mergers
-of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki,LIGOScientific:2020aai} and their mixture \cite{LIGOScientific:2021qlt}. These results have been confirmed
+the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GWs signals~\cite{LIGOScientific:2021djp} from mergers
+of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki,LIGOScientific:2020aai} and their mixture~\cite{LIGOScientific:2021qlt}. These results have been confirmed
 by independent analyses, which have also identified a few new GW signals~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq,Nitz:2021zwj,Olsen:2022pin}.
@@
 Several null tests have been proposed to probe the nature of gravity with GW signals~\cite{TheLIGOScientific:2016src,Yunes:2016jcc,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks,LIGOScientific:2021sio}.
-They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the intermediate (plunge) and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow to set upper limit on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
+They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the plunge and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow to set upper limit on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
 mass of the graviton; tests of the polarization of gravitational radiation~\cite{Will:2014kxa}, for which more than
@@
 
+\subsection{Einstein-dilaton-Gauss-Bonnet gravity}
+\label{sec:results_edgb}
+
 \begin{figure}[t]
@@
 
-\begin{figure}[h]
+We start with EdGB gravity.
+%
+In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized PDFs of the
+coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
+(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
+%
+The bottom panel shows the joint posterior obtained by combining both events.
+%
+We see, for both events, the $N_{\rm max} = 0$ posteriors are
+characterized by a peak away from zero.
+%
+This does not mean that we are inferring a deviation from GR.
+%
+We recall that the deviations from GR in the ParSpec framework are controlled
+by the dimensionless parameter $\gamma$, which here reads,
+%
+\begin{equation}
+    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M_{f}}\right)^4\,.
+    \label{eq:def_gamma_gb}
+\end{equation}
+%
+As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm EdGB}$ does indeed have a posterior
+distribution with largest support at zero, indicating consistency between
+the underlying signal and GR.
+%
+We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
+displaces the posteriors distributions towards smaller values of $\ell_{\rm EdGB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
+and larger values of $\gamma_{\rm EdGB}$ (see Fig.~\ref{fig:gamma_gb}).
+
+\begin{figure}[t]
 \includegraphics[width=\columnwidth]{figs/edgb_gamma.pdf}
@@
 \end{figure}
-
-\subsection{Einstein-dilaton-Gauss-Bonnet gravity}
-\label{sec:results_edgb}
-
-We start with EdGB gravity.
-%
-In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized PDFs of the
-coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
-(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
-%
-The bottom panel shows the joint posterior obtained by combining both events.
-%
-We see, for both events, the $N_{\rm max} = 0$ posteriors are
-characterized by a peak away from zero.
-%
-This does not mean that we are inferring a deviation from GR.
-%
-We recall that the deviations from GR in the ParSpec framework are controlled
-by the dimensionless parameter $\gamma$, which here reads,
-%
-\begin{equation}
-    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M_{f}}\right)^4\,.
-    \label{eq:def_gamma_gb}
-\end{equation}
-%
-As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm EdGB}$ does indeed have a posterior
-distribution with largest support at zero, indicating consistency between
-the underlying signal and GR.
-%
-We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
-displaces the posteriors distributions towards smaller values of $\ell_{\rm EdGB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
-and larger values of $\gamma_{\rm EdGB}$ (see Fig.~\ref{fig:gamma_gb}).
 
@@
 
-\begin{table}[b]
-\begin{tabular}{l l c c c}
-\hline
-\hline
-$N_{\rm max}$ & Event &  EFT    & ParSpec & Constraint      \\
-              &       &  bound? & bound?  & ($\gm = M_{f}$) \\
-\hline
-  & GW150914 & No  & Yes & -- \\
-0 & GW200129 & No  & Yes & -- \\
-  & Combined & --  & Yes & -- \\
-\hline
-  & GW150914 & No  & Yes & -- \\
-1 & GW200129 & No  & Yes & -- \\
-  & Combined & --  & Yes & -- \\
-\hline
-\hline
-\end{tabular}
-\caption{Detailed summary of our results for EdGB gravity for GW150914, GW200129, and
-combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
-%
-We find that we cannot place any constraint on $\ell_{\rm EdGB}$ with our waveform model from either GW event.
-}
-\label{tab:summary_edgb}
-\end{table}
-
 As we have emphasized in Sec.~\ref{sec:remarks}, we must first check whether the
@@
 We summarize our findings in Table~\ref{tab:summary_edgb}.
+
+\begin{table}[h]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+$N_{\rm max}$ & Event &  EFT    & ParSpec & Constraint      \\
+              &       &  bound? & bound?  & ($\gm = M_{f}$) \\
+\hline
+  & GW150914 & No  & Yes & -- \\
+0 & GW200129 & No  & Yes & -- \\
+  & Combined & --  & Yes & -- \\
+\hline
+  & GW150914 & No  & Yes & -- \\
+1 & GW200129 & No  & Yes & -- \\
+  & Combined & --  & Yes & -- \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results for EdGB gravity for GW150914, GW200129, and
+combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+%
+We find that we cannot place any constraint on $\ell_{\rm EdGB}$ with our waveform model from either GW event.
+}
+\label{tab:summary_edgb}
+\end{table}
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more edits

@@
 % \abcomm{Please update the paragraph below.}
-In this theory, we have considered only $N_{\rm max} = 0$. We find that the
-inclusion of the spin corrections yields waveforms that for $\ell_{\rm qEFT} \gtrsim 80$~km,
-for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
-has some problems in English. I do not udnerstand it.}
+In this theory, we have considered only $N_{\rm max} = 0$.
+%
+\hs{We found that the inclusion of the spin corrections produced waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
+had a ringdown segment larger (sometimes seconds long) that the inspiral-plugne segment.}
+% for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
+% has some problems in English. I do not udnerstand it.}
 %
@@
 
-% -------------------------------------------------------------
-% \hs{Try to draw some conclusions that apply to all theories.}
-% -------------------------------------------------------------
-
-We presented an unified framework that combines the ParSpec formalism introduced
+We presented an unified framework that combines the ParSpec framework
 to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
@@
 observational data from the LVK events GW150914 and GW200129.
-%
-We found, in particular that, within the interpretation of our non-GR theories as EFTs and the
+
+We found, in particular, that within the interpretation these theories as EFTs and the
 region of validity of the ParSpec framework, the coupling constant of dCS gravity is bound to
@@
 %
-This dichotomy between these theories has an analogy with works that considered
+This dichotomy between the two theories has an analogy with works that considered
 the inspiral part of the GW signal alone.
@@
 %
-\hscomm{I will add a sentence here on Refs.~\cite{Alexander:2017jmt,Loutrel:2018ydv,Loutrel:2018rxs}.}
-
-Our work shows that there are theories of gravity (such as dCS) which can by-pass observational
-constraints from the inspiral phase alone, {\it yet} would not, if we
-analyze the ringdown.
-%
-We hope that our result thus serve as additional motivation for future work
-modeling the late-inspiral, merger and ringdown of coalescing BHs in modified
-gravity theories.
+% HS: changed my mind -- I think it would divert from the original flow.
+% \hscomm{I will add a sentence here on Refs.~\cite{Alexander:2017jmt,Loutrel:2018ydv,Loutrel:2018rxs}.}
+%
+We hope that our results serve as further motivation to address these
+challenging problems.
 
@@
 
-\hscomm{TODO: say that we could try to expand the waveform model to include modification to
-the inspiral part too; maybe through FTI~\cite{Mehta:2022pcn}?}
-
-\hscomm{TODO: add that we could try to parametrize the final BH mass and spin estimates formulas we
-use at the moment~\cite{Hofmann:2016yih}. Maybe comment that a possible first attempt could follow~\cite{Buonanno:2007sv},
-as done in~\cite{Jai-akson:2017ldo,Li:2020wse}. Say that ultimately we will need to informed by NR in beyond-GR.}
-
-\hscomm{I suspect that by construction the $N_{\rm max} = 1$ cases will often fail to satisfy our
-perturbative bounds. If so, add explanation here.}
+% \hscomm{TODO: say that we could try to expand the waveform model to include modification to
+% the inspiral part too; maybe through FTI~\cite{Mehta:2022pcn}?}
+
+% \hscomm{TODO: add that we could try to parametrize the final BH mass and spin estimates formulas we
+% use at the moment~\cite{Hofmann:2016yih}. Maybe comment that a possible first attempt could follow~\cite{Buonanno:2007sv},
+% as done in~\cite{Jai-akson:2017ldo,Li:2020wse}. Say that ultimately we will need to informed by NR in beyond-GR.}
+
+% HS: I did not add a comment on this, because of our discussion of how the N = 1 results will
+% not be "permanent" as the N = 0 one, until we have QNM results valid up to ~ 0.7
+% \hscomm{I suspect that by construction the $N_{\rm max} = 1$ cases will often fail to satisfy our
+% perturbative bounds. If so, add explanation here.}
 
@@
 and refer to Fig.~\ref{fig:corner_plot_all}}
+
+Our work shows that there are theories of gravity (such as dCS) can be unconstrained by studying the
+inspiral portion of GW events, {\it yet} can be constrained, if we analyze the ringdown.
+%
+Our results show that to fulfill the potential to test GR with GW observations,
+further work on modeling of the late-inspiral-(plunge)-merger and ringdown of
+coalescing BHs  (with NR simulations) and, complementary, the calculations of
+QNMs of rapidly-rotating BHs in modified gravity theories (with BH perturbation
+theory) are necessary.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
moving the large corner plot, added text related to the small one. Working on appendices

@@
 %
-As we will next, the situation is the opposite for dCS gravity.
+% As we will next, the situation is the opposite for dCS gravity.
 
@@
 %
-In Fig.~\ref{fig:corner_plot}, we show the final spin $\chi_{\rm f}$ and
-remnant mass $M_{\rm f}$ for GW150914 for GR and dCS gravity.
-%
-We see that indeed our waveform models does not introduce substantial changes
+As an additional check, to verify the robustness of our constraint, we show in
+Fig.~\ref{fig:corner_plot}, the final spin $\chi_{\rm f}$ and remnant mass
+$M_{\rm f}$ for GW150914 for GR and dCS gravity.
+%
+We see that our \pSEOB waveform model does not introduce substantial changes
 to the GR estimates on these parameters, as required by the ParSpec expansion
@@
 %
-We observed the same in all other theories we studied.
+In fact, we observed no bias on the estimation of $\Mf$ and $\chi_{\rm f}$
+for all theories considered here.
+%
+In Appendix~\ref{app:big_contour} we show how all other intrinsic parameter parameters
+remain unbiased.
 
@@
 \hs{We found that the inclusion of the spin corrections produced waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
-had a ringdown segment larger (sometimes seconds long) that the inspiral-plugne segment.}
+had a ringdown segment larger (sometimes seconds long) that the inspiral-plunge segment in the detectors frequency bands.}
 % for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
@@
 To avoid this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
-which were essentially uniform, as our prior, and thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
+which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
 %
@@
 %
-In contrast, we could not place any constraint of the coupling constants in EdGB gravity $\ell_{\rm EdGB}$.
+In contrast, we could not place any constraint of the coupling constants in
+EdGB gravity $\ell_{\rm EdGB}$.
 %
@@
 %
+This result also shows how the inclusion of theory-specific information into the ParSpec framework
+can result in different outcomes for different theories, even if they predict same exponent $p$.
+
 % HS: changed my mind -- I think it would divert from the original flow.
 % \hscomm{I will add a sentence here on Refs.~\cite{Alexander:2017jmt,Loutrel:2018ydv,Loutrel:2018rxs}.}
-%
-We hope that our results serve as further motivation to address these
-challenging problems.
 
@@
 theory) are necessary.
-
-\begin{figure*}[t]
-\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
-\caption{(Color online).~Corner plot showing that the inferred source binary parameters for GW150914,
-using the same waveform model \pSEOB, but with (purple contours) and without setting the non-GR parameters different
-from zero (blue contours), having as an illustrative example dCS gravity and $N_{\rm max}=0$.
-%
-Here, $\chi_{\rm eff}$ is the dimensionless effective-spin parameter, related to the individual spins $\chi_{i}$
-and masses $m_{i}$ of each binary component as $\chi_{\rm eff} \equiv (m_1 \chi_1 + m_2 \chi_2) / (m_1 + m_2)$.
-%
-All contours correspond to 90\% credible levels.
-%
-We see that the addition of the non-GR parameters does not introduce biases in the
-inference of the source parameters.
-%
-We found the same qualitative behavior in the posteriors distributions of the
-source binary parameters for the other modified gravity theories studied in the
-main text.
-%
-The same conclusions apply for the other GW event studied here, GW200129.
-}
-\label{fig:corner_plot_all}
-\end{figure*}
+%
+We hope that our results serve as further motivation to address these
+challenging, and outstanding, problems.
 
@@
 
+\section{Intrinsic binary parameters}
+\label{app:big_contour}
+
+In this Appendix, we show in Fig.~\ref{fig:corner_plot_all} a corner plot with all intrinsic binary parameters from our parameter estimation for GW150914
+using the \pSEOB{} waveform models for GR and dCS.
+%
+We see that median of the distribution is not affected substantially by the inclusion of the non-GR parameters.
+%
+That is the case for $\Mf$ and $\chi_{\rm f}$ is an underlying assumption of the ParSpec framework.
+%
+We qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
+
+\begin{figure*}[t]
+\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
+\caption{(Color online).~Corner plot showing that the inferred source binary parameters for GW150914,
+using the same waveform model \pSEOB, but with (purple contours) and without setting the non-GR parameters different
+from zero (blue contours), having as an illustrative example dCS gravity and $N_{\rm max}=0$.
+%
+Here, $\chi_{\rm eff}$ is the dimensionless effective-spin parameter, related to the individual spins $\chi_{i}$
+and masses $m_{i}$ of each binary component as $\chi_{\rm eff} \equiv (m_1 \chi_1 + m_2 \chi_2) / (m_1 + m_2)$.
+%
+All contours correspond to 90\% credible levels.
+%
+We see that the addition of the non-GR parameters does not introduce biases in the
+inference of the source parameters.
+%
+We found the same qualitative behavior in the posteriors distributions of the
+source binary parameters for the other modified gravity theories studied in the
+main text.
+%
+The same conclusions apply for the other GW event studied here, GW200129.
+}
+\label{fig:corner_plot_all}
+\end{figure*}
+
 \bibliography{paper_alt_theor_bounds}

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more work on the conclusions

@@
 %
-Put together this allowed us to use the \pSEOB~waveform model to test four
-modified gravity theories (EdGB, dCS, cubic, and quartic EFTs of GR) using
-observational data from the LVK events GW150914 and GW200129.
+The resulting \pSEOB~waveform model not bias (relative to GR) the inference of
+the intrinsic binary parameters as required by ParSpec (see, in particular, Fig.~\ref{fig:corner_plot} and
+Appendix~\ref{app:big_contour},~Fig.~\ref{fig:corner_plot_all}).
+%
+Put together this allowed us to test four modified gravity theories (EdGB, dCS,
+cubic, and quartic EFTs of GR) using observational data from the LVK events
+GW150914 and GW200129.
 
@@
 
-\agcomm{Mention that our alternate ringdown formalism does not bias estimates of GR quantities
-and refer to Fig.~\ref{fig:corner_plot_all}}
+% HS: done
+% \agcomm{Mention that our alternate ringdown formalism does not bias estimates of GR quantities
+% and refer to Fig.~\ref{fig:corner_plot_all}}
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
conclusions

@@
 
-We found, in particular, that within the interpretation these theories as EFTs and the
-region of validity of the ParSpec framework, the coupling constant of dCS gravity is bound to
+We found, that within the interpretation these theories as EFTs and the
+region of validity of the ParSpec framework, that the coupling constant of dCS gravity is bound as
 $\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
-of GW150914 and GW200129.
-%
-In contrast, we could not place any constraint of the coupling constants in
-EdGB gravity $\ell_{\rm EdGB}$.
-%
-This dichotomy between the two theories has an analogy with works that considered
-the inspiral part of the GW signal alone.
-%
-In that case, it is dCS gravity which cannot be constrained with current GW
-events, while EdGB can, as shown in Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
-%
-This result also shows how the inclusion of theory-specific information into the ParSpec framework
-can result in different outcomes for different theories, even if they predict same exponent $p$.
+of GW150914 and GW200129. This is the first GW-alone constrain on this theory.
+%
+In contrast, we could not place any bounds on the coupling constant of EdGB
+gravity $\ell_{\rm EdGB}$.
+
+This dichotomy between the two theories has a counterpart with works that considered
+the inspiral part of the GW signal alone~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
+%
+In those cases, it is dCS gravity which cannot be constrained with current GW
+events, while EdGB can.
+%
+We emphasize that both theories (and the cubic EFT of GR also studied here) all predict the same exponent $p$ in ParSpec.
+%
+Hence, our results show how the inclusion of theory-specific information into the ParSpec framework
+can result in different outcomes for different theories, even if they predict same value of $p$.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
future work

@@
 
-Let us discuss some avenues for future work \dots
+Let us discuss some avenues for future work.
+%
+First, we could implement a high-spin version of the GR fitting coefficients to the ParSpec formulas.
+%
+This has already been done in Ref.~\cite{Carullo:2021dui} extending the validity of the ParSpec formulas up to
+spins of $\chi_{\rm f} \approx 0.99$.
+%
+For the events analyzed here, the original fit by Ref.~\cite{Maselli:2019mjd}
+was sufficient, but it might not be the case with future GW events.
 
@@
 
-\agcomm{Mention that we do not use the high-spin version of the fits, and refer to the
-chif measurements Fig.~\ref{fig:corner_plot} (which should be near the text here).}
+% \agcomm{Mention that we do not use the high-spin version of the fits, and refer to the
+% chif measurements Fig.~\ref{fig:corner_plot} (which should be near the text here).}
 
@@
 We qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
+%
+We also remark that the fact that the posterior on $\chi_{\rm f}$ has most support around $\approx 0.7$ justifies our use
+of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small changes

@@
 \newcommand{\Fp}{F_+}
-\newcommand{\Mf}{M_f}
+\newcommand{\Mf}{M_{\rm f}}
 \newcommand{\cA}{\mathpzc{A}}
@@
 
-\hscomm{Alessandra, I moved the plot here as we discussed.}
+\hscomm{I moved the plot here as we discussed.}
 %
@@
 %
-We see that our \pSEOB waveform model does not introduce substantial changes
+We see that our \pSEOB~waveform model does not introduce substantial changes
 to the GR estimates on these parameters, as required by the ParSpec expansion
@@
 %
-\hs{We found that the inclusion of the spin corrections produced waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
-had a ringdown segment larger (sometimes seconds long) that the inspiral-plunge segment in the detectors frequency bands.}
+\hs{We found that by adding the spin corrections and for $\ell_{\rm qEFT} \gtrsim 80$~km, resulted in waveforms which
+had a ringdown segment larger (sometimes seconds long) that the inspiral-plunge segment in the detectors frequency bands,
+making the parameter estimation challenging.}
 % for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
@@
 %
-To avoid this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
+To overcome this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
 which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
@@
 Here, we consider only the fundamental QNM $(\ell, m, n) = (2, 2, 0)$ and
-hence we omit the QNM subscript ``$(2,2,0)$'' for brevity.
+hence we omit the QNM subscript ``$(2,2,0)$'' for brevity and, likewise, the
+subscript ``f'' for final spin and mass.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
future work, more refs

@@
 For the events analyzed here, the original fit by Ref.~\cite{Maselli:2019mjd}
-was sufficient, but it might not be the case with future GW events.
+was sufficient, but it might not be the case with upcoming GW observation campaigns.
+%
+Second, it would be important to incorporate additional effects, such as spin-precession and eccentricity
+to \pSEOB~(see e.g., Refs~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}).
 
@@
 
-~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
-Point this out in the conclusions after all specific theories are discussed.}
+% ~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
+% Point this out in the conclusions after all specific theories are discussed.}
 
@@
 %
-We hope that our results serve as further motivation to address these
-challenging, and outstanding, problems.
+We hope that our results can serve as further motivation to address these
+outstanding problems.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more edits in eft sections and appendix

@@
 
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
+\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm cEFT}$ for
+GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+The colors distinguish different $N_{\rm max}$ in the spin expansion.
+}
+\label{fig:cEFT_exec_sum}
+\end{figure}
+
 In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
@@
 \begin{equation}
-    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km} \quad \textrm{at 90\% credible level}\,.
+    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km}, \quad \textrm{at 90\% credible level}\,.
 \end{equation}
@@
 We summarize our results in Table~\ref{tab:summary_ceft}.
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm cEFT}$ for
-GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-%
-The colors distinguish different $N_{\rm max}$ in the spin expansion.
-}
-\label{fig:cEFT_exec_sum}
-\end{figure}
 
@@
 
-\begin{table}[b]
+\begin{table}[h]
 \begin{tabular}{l l c c c}
@@
 The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ are a consequence of the how weakly the QNMs
-of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $(\ell_{\rm EdGB} / M)^4 \approx 0.3$.
+of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $\gamma_{\rm EdGB} \approx 0.3$.
 
@@
 %
-Taken together, use as our fitting expressions for the QNM is EdGB gravity
-%
-\begin{subequations}
+The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$
+read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}.
+%
+These steps yield,
+%
 \begin{align}
-    M {\rm Re}(\sigma)_{\rm EdGB} &= {\rm Re}(\omega)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
-    \\
-    M {\rm Im}(\sigma)_{\rm EdGB} &= \dots % {\rm Im}(\omega)_{\rm GR} \, \left[ 1 - 0.0044 (\ell_{\rm EdGB} / M)^4 \right].
+    p_{\rm EdGB} = 4, \quad \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
+    \nonumber \\
+    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
 \end{align}
-\end{subequations}
-
-\dots
+
+%
+% Taken together, use as our fitting expressions for the QNM is EdGB gravity
+% %
+% \begin{subequations}
+% \begin{align}
+%     M {\rm Re}(\sigma)_{\rm EdGB} &= {\rm Re}(\omega)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
+%     \\
+%     M {\rm Im}(\sigma)_{\rm EdGB} &= \dots % {\rm Im}(\omega)_{\rm GR} \, \left[ 1 - 0.0044 (\ell_{\rm EdGB} / M)^4 \right].
+% \end{align}
+% \end{subequations}
+%
+% \dots
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more text to appendix

@@
 \begin{align}
-    M {\rm Re}(\sigma)_{\rm EdGB} &= M {\rm Re}(\sigma)_{\rm GR} \, \left( 1 + 0.0107 \, \gamma_{\rm EdGB}^4 \right),
+    M {\rm Re}(\sigma)_{\rm EdGB} &= M {\rm Re}(\sigma)_{\rm GR} \, \left( 1 + 0.0107 \, \gamma_{\rm EdGB} \right),
     \\
-    M {\rm Im}(\sigma)_{\rm EdGB} &= M {\rm Im}(\sigma)_{\rm GR} \, \left( 1 - 0.0044 \, \gamma_{\rm EdGB}^4 \right).
+    M {\rm Im}(\sigma)_{\rm EdGB} &= M {\rm Im}(\sigma)_{\rm GR} \, \left( 1 - 0.0044 \, \gamma_{\rm EdGB} \right).
 \end{align}
@@
 %
-These steps yield,
+These steps yield $p_{\rm EdGB} = 4$,
 %
 \begin{align}
-    p_{\rm EdGB} = 4, \quad \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
-    \nonumber \\
+     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
+\end{align}
+%
+for the $j=0$ coefficients and
+%
+\begin{equation}
     \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
-\end{align}
-
-%
+\end{equation}
+%
+for the $j=1$ coefficients.
+
 % Taken together, use as our fitting expressions for the QNM is EdGB gravity
@@
     M \, \omega_{\rm dCS} =
-    \left( 0.3722 + 1.1945 \gamma_{\rm dCS}^4 \right)
-    + \left(0.1861 + 5.1828 \gamma_{\rm dCS}^4 \right) \, \chi,
+    \left( 0.3722 + 1.1945 \gamma_{\rm dCS} \right)
+    + \left(0.1861 + 5.1828 \gamma_{\rm dCS} \right) \, \chi,
     \nonumber \\
@@
 compare against Eq.~\eqref{eq:qnm_nongr_iso}, to find
-%
-\begin{equation}
-p_{\rm dCS} = 4\,, \quad \delta \omega^{(0)}_{\rm dCS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm dCS} = 41.199.
+$p_{\rm dCS} = 4$,
+%
+\begin{equation}
+\delta \omega^{(0)}_{\rm dCS} = 3.1964\,, \quad \delta \omega^{(1)}_{\rm dCS} = 41.199.
 \label{eq:cs_omega_coefs}
@@
 $\delta \omega_{\rm dCS}^{(1)}$ and $\delta \tau_{\rm dCS}^{(1)}$ are
-compensated by the assumptions that $(\ell_{\rm dCS} / M_{\rm f})^2$ and $\chi$
+compensated by the assumptions that $\gamma_{dCS}$ and $\chi$
 are much less than unity, which are the assumptions used in Ref.~\cite{Wagle:2021tam}
@@
 %
-This process, shows that the mode labelled ``-'' is the least damped and it is the one we use.
-%
-Direct comparison with Eqs.~\eqref{eq:qnm_nongr_iso} results in,
+This process, shows that the mode labeled ``-'' is the least damped and it is the one we use.
+%
+Direct comparison with Eqs.~\eqref{eq:qnm_nongr_iso} results in $p_{\rm cEFT} = 4$,
 %
 \begin{align}
-    p_{\rm cEFT} = 4, \quad \delta \omega_{\rm cEFT}^{(0)} = - 0.5813, \quad \delta \tau_{\rm cEFT}^{(0)} = 2.6469,
+    \delta \omega_{\rm cEFT}^{(0)} = - 0.5813, \quad \delta \tau_{\rm cEFT}^{(0)} = 2.6469,
     \nonumber \\
@@
 %
-We then find
+We then find this time that $p_{\rm qEFT} = 6$,
 %
 \begin{align}
-    p_{\rm qEFT} = 6, \quad \delta \omega_{\rm qEFT}^{(0)} = -0.2114, \quad \delta \tau_{\rm qEFT}^{(0)} = -0.6070,
+    \delta \omega_{\rm qEFT}^{(0)} = -0.2114, \quad \delta \tau_{\rm qEFT}^{(0)} = -0.6070,
     \nonumber \\
@@
 \end{align}
+%
+As with the previous theories, the larger values of some of these parameters are compensated
+by the assumptions of small coupling and small spin used to calculate the QNM frequencies.
 

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more writing in the appendix

@@
 The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$
-read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}.
+read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
+and re-expand in small coupling and spin.
 %

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small changes

@@
 Regge-Wheeler-Zerilli gauge~\cite{Regge:1957td,Zerilli:1970se} and connect it with the transverse-traceless gauge
-used to described GWs (see e.g.~Ref.~\cite{Maggiore:2018sht}, Chapter~12),
+used to described GWs (see, for instance,~Ref.~\cite{Maggiore:2018sht}, Chapter~12),
 %
@@
 Second, it would be important to incorporate additional effects, such as spin-precession and eccentricity
-to \pSEOB~(see e.g., Refs~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}).
+to \pSEOB~(see, for instance, Refs~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}).
 

### 2022-04-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
some changes

@@
 Several null tests have been proposed to probe the nature of gravity with GW signals~\cite{TheLIGOScientific:2016src,Yunes:2016jcc,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks,LIGOScientific:2021sio}.
-They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the plunge and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow to set upper limit on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
+They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the plunge and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow us to set upper limits on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
 mass of the graviton; tests of the polarization of gravitational radiation~\cite{Will:2014kxa}, for which more than
@@
 
+\ab{We will treat the modified theories of gravity as EFTs, and focus on 
+finite-size effects (see, e.g., Ref.~\cite{Sennett:2019bpc}). Thus, for each gravity theory the fundamental lenght-scale 
+$\ell \lesssim GM/c^2$, where $M$ is the mass of the BH. This implies 
+that observable deviations from GR present in those theories arise from modifications 
+to the Kerr geometry of each individual BH. Those finite-size effects can manifest themselves in 
+the QNMs of the remnant produced by the merger, but also in the GW phasing of the inspiral through 
+corrections to the GR spin-induced quadrupole and Love numbers. However, here we will not consider the latter, 
+instead, we will only study the impact of finite-size effects on the QNMs of the 
+remnant.}
+
 We start by briefly reviewing the modified gravity theories we consider in this
@@
 only at the level of $\sim 50\%$ (see the constraint on the 2PN parameter $\varphi_4$ in Fig.~6 of
-Ref.~\cite{LIGOScientific:2021sio}). Thus, so far, dCS gravity has remained
-unconstrained by works which use only on the inspiral portion of BBH GW signals~\cite{Nair:2019iur,Perkins:2021mhb}.
+Ref.~\cite{LIGOScientific:2021sio}). \ab{So far, analyses that used only the inspiral portion of 
+the BBH GW signals were not able to set meaningful bounds on such deviation at 2PN order~\cite{Nair:2019iur,Perkins:2021mhb}.}
 %
@@
 
-In general \dots
-%
-\hscomm{Alessandra, can you include a short description of~\cite{Sennett:2019bpc} for the quartic EFT?}
+\ab{For the EFT of GR with dimension-eight operators, Ref.~\cite{Sennett:2019bpc} focused on the 
+orbital effects (i.e., the inspiral stage) and performed 
+Bayesian model selection using the two lowest-mass BBHs events of the second-observig run of 
+the LIGO-Virgo Collaboration, notably GW151226 and GW170608. They found that the 
+data disfavor the appearance of new physics on distance scales around $\ell_{\rm qEFT} \sim 150$ km.}
 

### 2022-04-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
some changes

@@
 \ab{For the EFT of GR with dimension-eight operators, Ref.~\cite{Sennett:2019bpc} focused on the 
-orbital effects (i.e., the inspiral stage) and performed 
+orbital effects (i.e., instead of finite-size effects) and performed 
 Bayesian model selection using the two lowest-mass BBHs events of the second-observig run of 

### 2022-04-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
some changes
changes

@@
 We find that while the Einstein-dilaton-Gauss-Bonnet theory cannot be
-constrained with these events, we can place upper bounds on the coupling
-constants of cubic- ($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order
+constrained with these events, we can place upper bounds on the \sout{coupling
+constants} \ab{fundamental length-scale} of cubic- ($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order
 ($\ell_{\rm qEFT} \leqslant 51.3$~km) effective-field-theories of general
@@
 \ab{We will treat the modified theories of gravity as EFTs, and focus on 
-finite-size effects (see, e.g., Ref.~\cite{Sennett:2019bpc}). Thus, for each gravity theory the fundamental lenght-scale 
-$\ell \lesssim GM/c^2$, where $M$ is the mass of the BH. This implies 
+finite-size effects (see, e.g., Ref.~\cite{Sennett:2019bpc}). Thus, for each gravity theory we impose that 
+the fundamental length-scale $\ell \lesssim GM/c^2$, where $M$ is the mass of the BH. This implies 
 that observable deviations from GR present in those theories arise from modifications 
@@
 
-Our last example of modified gravity theories are the so-called effective field
-theories (EFT) of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
+Our last example of modified gravity theories are the so-called 
+EFTs of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
 %
@@
 Next, in Sec.~\ref{sec:review_pSEOB}, we review our baseline
-parametrized inspiral(--plunge)-merger-ringdown (IMR) waveform
-model~\cite{Brito:2018rfr,Ghosh:2021mrv}, and explain how we extend
+parametrized IMR waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}, and explain how we extend
 it to include the ParSpec.
@@
 the series~\eqref{eq:kerr_expansion} truncated at $N_{\rm max} = 4$, reproduces with 1\% accuracy
-the GR QNMs for BH's spins $\chi \lesssim 0.7$.
+the GR QNMs for BH's spins $\chi_{\rm f} \lesssim 0.7$.
 %
@@
 In Ref.~\cite{Carullo:2021dui}, the fitting coefficients were calculated up to $N_{\rm max} = 9$,
-which extend the validity of the spin-expansion up to $\chi \lesssim 0.99$.
+which extend the validity of the spin-expansion up to $\chi_{\rm f} \lesssim 0.99$.
 %
@@
 and $(5,5)$. Such a model was built by applying the post-adiabatic approximation~\cite{Nagar:2018gnk}
-to the multipolar spin-aligned effective-one-body (EOB) waveform model of Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv} (henceforth we refer to our baseline model as \SEOB{}\footnote{This waveform
+to the multipolar spin-aligned EOB waveform model of Refs.~\cite{Bohe:2016gbl,Cotesta:2018fcv} (henceforth we refer to our baseline model as \SEOB{}\footnote{This waveform
 model is available in \texttt{LALSuite}~\cite{lalsuite} as the \texttt{SEOBNRv4HM\_PA}
@@
 
-\subsection{Interpretation of our results}
+\subsection{EFT interpretation of our results}
 \label{sec:remarks}
@@
 have placed a constraint on $\ell_{\rm th}$. First, as we have explained in Sec.~\ref{sec:review_theories}, all theories that we
-consider must be interpreted as an effective field theory, meaning that it should be
+consider must be interpreted as an EFT, meaning that it should be
 considered valid only below an energy scale, or equivalently, a length-scale.
@@
 %
-We see that the CDF curves for $\gm = M_{f}$ are above 90\% for $\varepsilon =
+We see that the CDF curves for $\gm = M_{\rm f}$ are above 90\% for $\varepsilon =
 1/2$ for both events, with and without including the $n = 1$ dCS corrections to
@@
 \begin{equation}
-    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm dCS}}{G M_{f}} \right)^{4}\,,
+    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm dCS}}{G M_{\rm f}} \right)^{4}\,,
 \end{equation}
@@
 \includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
-\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
+\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_{\rm f}$,
 remnant mass $M_{\rm f}$ for GW150914, using the same waveform model,
@@
 
-\hscomm{I moved the plot here as we discussed.}
 %
@@
 %
-In Appendix~\ref{app:big_contour} we show how all other intrinsic parameter parameters
-remain unbiased.
+\ab{For completness,} in Appendix~\ref{app:big_contour} we also 
+show how all other intrinsic parameter parameters remain unbiased.
 
@@
 %
-\hs{We found that by adding the spin corrections and for $\ell_{\rm qEFT} \gtrsim 80$~km, resulted in waveforms which
-had a ringdown segment larger (sometimes seconds long) that the inspiral-plunge segment in the detectors frequency bands,
-making the parameter estimation challenging.}
+\ab{Indeed, we find that when adding the spin corrections and for $\ell_{\rm qEFT} \gtrsim 80$~km, 
+the waveforms can have a ringdown segment larger (sometimes seconds long) than the inspiral-plunge segment in the detectors frequency band, making the parameter estimation challenging.} \abcomm{The reference to 80 km comes out of the blue.
+Doesn't it?
+Why did you refer to it?}
 % for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
@@
 \hline
-$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{\rm f}$) \\
               &       & bound? & bound?  &                            \\
@@
 \caption{Detailed summary of our results the quartic EFT of GR for GW150914, GW200129, and
-combined events using $\gm = M_{f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$. The quoted
+combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$. The quoted
 result correspond to 90\% credible values.
@@
 %
-The resulting \pSEOB~waveform model not bias (relative to GR) the inference of
-the intrinsic binary parameters as required by ParSpec (see, in particular, Fig.~\ref{fig:corner_plot} and
-Appendix~\ref{app:big_contour},~Fig.~\ref{fig:corner_plot_all}).
+The resulting \pSEOB~waveform model \ab{does} not bias (relative to GR) the inference of
+the intrinsic binary parameters, as required by ParSpec (see, in particular, Fig.~\ref{fig:corner_plot} and
+Fig.~\ref{fig:corner_plot_all} in Appendix~\ref{app:big_contour}),
 %
@@
 cubic, and quartic EFTs of GR) using observational data from the LVK events
-GW150914 and GW200129.
-
-We found, that within the interpretation these theories as EFTs and the
-region of validity of the ParSpec framework, that the coupling constant of dCS gravity is bound as
+GW150914 and GW200129. \ab{Our results are summarzied in Table~\ref{tab:bound_summary}.}
+
+\ab{In particular,} we found, that within the interpretation \ab{of} these theories as EFTs and the
+region of validity of the ParSpec framework, the \sout{coupling constant} \ab{fundamental length-scale} of dCS gravity is bound as
 $\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
@@
 %
-In contrast, we could not place any bounds on the coupling constant of EdGB
-gravity $\ell_{\rm EdGB}$.
-
+In contrast, we could not place any bounds on the \sout{coupling constant} \ab{length-scale} \abcomm{Maybe 
+this is common in the literature, but I would call it length-scale instead of coupling 
+constant. What do you think?} of EdGB gravity $\ell_{\rm EdGB}$.
+%
 This dichotomy between the two theories has a counterpart with works that considered
@@
 %
-In those cases, it is dCS gravity which cannot be constrained with current GW
-events, while EdGB can.
-%
-We emphasize that both theories (and the cubic EFT of GR also studied here) all predict the same exponent $p$ in ParSpec.
+\ab{Using data of the LVK BBHs, it was found that the posterior distributions for 
+deviations from GR were uninformative in dCS gravity, but not in EdGB gravity.} 
+We emphasize that both those theories (and the cubic EFT of GR also studied here) all predict the same exponent $p$ in ParSpec.
 %
 Hence, our results show how the inclusion of theory-specific information into the ParSpec framework
-can result in different outcomes for different theories, even if they predict same value of $p$.
+can result in different outcomes for different theories, even if they predict the same value of $p$.
 
@@
 Second, it would be important to incorporate additional effects, such as spin-precession and eccentricity
-to \pSEOB~(see, for instance, Refs~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}).
+to \pSEOB~(see, for instance, Refs.~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}). \ab{Third, it will be 
+interesting, to perfom tests of modified theories of gravity using IMR waveform models that include, during 
+the inspiral stage, finite-size effects induced by the non-GR geometry around the  holes --- 
+for example the ones due to spin-induced quadrupole, tidal deformability and absorbtion, and also 
+orbital effects due to non-GR gravitational interactions 
+between the holes. Those effects could be included using the flexible theory-independent 
+method~\cite{Mehta:2022pcn}, as done in Ref.~\cite{Sennett:2019bpc} or the 
+TIGER code~\cite{Li:2011cg,Agathos:2013upa}. However, setting bounds on deviations 
+from GR caused by orbital effects requires a different EFT interpretation than what we 
+adopted in Sec.~\ref{sec:remarks} (see also Sec. II C in Ref.~\cite{Sennett:2019bpc}). 
+Indeed, in this case one would need to analyze the data considering that the modified theory of 
+gravity is valid for $\ell \gtrsim  M$, but $\ell \lesssim R$, being $R$ the binary's separation. Fourth,
+to test the robustness of the results obtained in this paper, it will be very useful to employ NR waveforms 
+produced in some of the non-GR theories under consideration, as synthetic signals, and carry out 
+Bayesian analysis to recover the binary's parameters, including the non-GR ones during the ringdown. 
+As today, there are only a handful of such NR simulations~XXX. Last, but not least, it will be very 
+beneficial to calculate the QNMs (complex) frequencies of rapidly-rotating BHs in modified gravity theories 
+(with BH perturbation theory). This is a challenging problem, but certainly necessary, 
+also in the context of ParSpec, if higher spin ocrrections would need to be 
+included to make the framwork robust.}
 
@@
 
-Our work shows that there are theories of gravity (such as dCS) can be unconstrained by studying the
-inspiral portion of GW events, {\it yet} can be constrained, if we analyze the ringdown.
-%
-Our results show that to fulfill the potential to test GR with GW observations,
-further work on modeling of the late-inspiral-(plunge)-merger and ringdown of
-coalescing BHs  (with NR simulations) and, complementary, the calculations of
-QNMs of rapidly-rotating BHs in modified gravity theories (with BH perturbation
-theory) are necessary.
-%
-We hope that our results can serve as further motivation to address these
-outstanding problems.
+\sout{Our work shows that, with the GW signals so far observed by the LVK Collaboration, 
+there are theories of gravity (such as dCS) that can be unconstrained by studying the
+inspiral portion of GW events, {\it yet} {it} can be constrained, if we analyze the ringdown.}
+%
+\sout{Our results show that to fulfill the potential to test GR with \ab{future} GW observations,
+further work \ab{is needed} on modeling \sout{of} the late-inspiral-(plunge)-merger and ringdown of
+coalescing BHs  (with NR simulations) and, complementary,} 
+%
+\sout{We hope that our results can also serve as further motivation to address these
+outstanding problems.}
 
@@
 
-In this Appendix, we show how we determined the coefficients in the ParSpec
-and summarized in Table~\ref{tab:ref_theories_qnms},
-using QNM calculations found in the literature for the theories described in
-Sec.~\ref{sec:review_theories}.
-%
-Here, we consider only the fundamental QNM $(\ell, m, n) = (2, 2, 0)$ and
-hence we omit the QNM subscript ``$(2,2,0)$'' for brevity and, likewise, the
-subscript ``f'' for final spin and mass.
+\ab{Here, for the theories described in Sec.~\ref{sec:review_theories}, we 
+use QNM calculations from the literature and determine 
+the coefficients in the ParSpec, which we have summarized 
+in Table~\ref{tab:ref_theories_qnms}.}
+%
+We consider only the fundamental QNM $(\ell, m, n) = (2, 2, 0)$, 
+hence we omit the QNM subscript ``$(2,2,0)$'' for brevity and, likewise, 
+the subscript ``f'' for final BH's spin and mass.
 
@@
 
-We start by considering EdGB gravity and, in particular, focus on
+We start by considering EdGB gravity and focus on
 Refs.~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} to determine the
@@
 In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
-of the polar gravitational-led modes increases as the coupling constant
+of the polar gravitational-\sout{led}\ab{dominant} mode increases as the coupling constant
 $\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
-branch of QNMs was calculated in~\cite{Pierini:2021jxd}.
+branch of QNMs was calculated in Ref.~\cite{Pierini:2021jxd}.
 %
 Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
-this is the gravitational-led branch of QNMs we select.
-
-For the nonrotating QNMs we used the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
-generated a new quartic fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
-values of the coupling constant [see, in particular, Eq.~(27) and Fig.~2 of Ref.~\cite{Blazquez-Salcedo:2016enn}].
+this is the gravitational-led \abcomm{led or dominant?} branch of QNMs we select.
+
+For the nonrotating QNMs we use\sout{d} \abcomm{We are using present tense when 
+describing results in the paper, so I would suggest with stick with that consistently 
+in the Appendix.} the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
+generate a new quartic fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
+values of the coupling constant (see, in particular, Eq.~(27) and Fig.~2 of 
+Ref.~\cite{Blazquez-Salcedo:2016enn}).
 %
@@
 %
-The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ are a consequence of the how weakly the QNMs
+The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ \abcomm{the term above 
+is linear not quartic in $\gamma_{\rm EdGB}$. Do you mean $\ell_{\rm EdGB}^4$?} 
+are a consequence of \sout{the} how weakly the QNMs
 of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $\gamma_{\rm EdGB} \approx 0.3$.
@@
 The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
-which for consistency with our previous discussion, we truncated at quartic-order in $\gamma_{\rm EdGB}$.
-%
-The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$
+which for consistency with our previous discussion, we truncate at quartic-order in $\gamma_{\rm EdGB}$ \abcomm{$\ell_{\rm EdCS}^4$?}.
+%
+The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ \ab{can be}  
 read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
@@
 %
-These steps yield $p_{\rm EdGB} = 4$,
+These steps yield \ab{for} $p_{\rm EdGB} = 4$,
 %
@@
 
-For dCS gravity, we follow Ref.~\cite{Wagle:2021tam} which numerically calculated the QNMs, $\sigma_{\rm dCS}$,
-of slowly-rotating BHs in this theory and found that the axial gravitational modes have their damping time increased as we
-increase the Chern-Simons coupling $\ell_{\rm dCS}$ at fixed spin $\chi$ of the BH.
+For dCS gravity, we follow Ref.~\cite{Wagle:2021tam}, which numerically calculated the QNMs, $\sigma_{\rm dCS}$,
+of slowly-rotating BHs, \sout{in this theory} and found that \ab{for} the axial gravitational modes \ab{the} \sout{have their} damping time increases, as we
+increase the Chern-Simons coupling $\ell_{\rm dCS}$, at fixed spin $\chi$ of the BH.
 %
 Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
-this is the branch of QNMs we chose to work with.
+this is the branch of QNMs we choose to work with.
 
@@
 %
-Using the fitting formula Eq.~(54a) of~\cite{Wagle:2021tam}, namely,
-%
-\begin{equation}
-    M \, {\rm Re}(\sigma)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi)^{c_{5} + c_{6} \kappa \zeta},
+\ab{We use} \sout{Using} the fitting formula Eq.~(54a) of Ref.~\cite{Wagle:2021tam}, namely,
+%
+\begin{equation}
+    M \, {\rm Re}(\sigma)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi_{\rm f})^{c_{5} + c_{6} \kappa \zeta},
     \label{eq:omega_dsc_eg}
@@
 %
-and $c_{i}$ (with $i=1, \dots, 6$) are fitting coefficients which can be found in
-Ref.~\cite{Wagle:2021tam},~Table II.
-
-We now expand Eq.~\eqref{eq:omega_dsc_eg} to leading-orders in $\chi$ and $\gamma_{\rm dCS}$, and
+where $c_{i}$ (with $i=1, \dots, 6$) are fitting coefficients which can be found in 
+Table II of Ref.~\cite{Wagle:2021tam},
+
+We now expand Eq.~\eqref{eq:omega_dsc_eg} to leading orders in $\chi$ and $\gamma_{\rm dCS}$, and
 gather the terms proportional to $\gamma_{\rm dCS}$.
@@
 %
-where we made use of the numerical value of the coefficients $c_{i}$.
-%
-We find that (reassuringly) that the nonrotating GR part of the expression above agree with $\omega^{(0)}$ of Ref.~\cite{Maselli:2019mjd}
-to 0.5\% relative percent error. The same error estimate is larger ($\approx 20$\%) for the linear-in-spin coefficient;
-0.1861 in comparison to 0.1258 of Ref.~\cite{Maselli:2019mjd}.
-%
-We attribute this difference to Ref.~\cite{Wagle:2021tam} having fitted Eq.~\eqref{eq:omega_dsc_eg} to QNM data compute to linear-order in spin, whereas~\cite{Maselli:2019mjd}
+where we make use of the numerical values of the coefficients $c_{i}$.
+%
+We find that (reassuringly) the nonrotating GR part of the expression above agrees with $\omega^{(0)}$ of Ref.~\cite{Maselli:2019mjd} to 0.5\% relative \sout{percent} error.
+The same \sout{error} estimate \sout{is} \ab{leads to a} larger \ab{relative error} ($\approx 20$\%) for the linear-in-spin coefficient (i.e., 0.1861 in comparison to 0.1258 of Ref.~\cite{Maselli:2019mjd}).
+%
+We attribute this difference to Ref.~\cite{Wagle:2021tam} having fitted Eq.~\eqref{eq:omega_dsc_eg} to QNM data computed to linear-order in spin, whereas~\cite{Maselli:2019mjd}
 fitted Eq.~\eqref{eq:kerr_expansion} to Kerr QNM valid to all orders in spin.
@@
 %
-which completes the set of fixed non-GR parameters in the ringdown of the \pSEOB{} waveform model for this theory.
+which completes the set of fixed non-GR parameters in the ringdown of the \pSEOB{} 
+waveform model for this theory.
 %
@@
 %
-For the cubic EFT, we use their Eq.~(67), particularizing to $\lame = \lamo = 1$.
-%
-We further linearize that equation in $\chi$ and particularize $m=2$.
-%
-This process, shows that the mode labeled ``-'' is the least damped and it is the one we use.
+For the cubic EFT, we use their Eq.~(67), particularizing \ab{it} to $\lame = \lamo = 1$.
+%
+We further linearize that equation in $\chi$ and \sout{particularize} \ab{consider} $m=2$.
+%
+This process, shows that the mode labeled ``-'' is the least-damped \ab{mode}, and it is the one we use.
 %
@@
 %
-In this case we found that both modes (``-'' and ``+'' in the notation of Ref.~\cite{Cano:2020cao}) make the
-fundamental QNM damp fast and we chose the ``-'' mode which decreases less the damping time.
-%
-We then find this time that $p_{\rm qEFT} = 6$,
+In this case we find that both modes (``-'' and ``+'' in the notation of Ref.~\cite{Cano:2020cao}) make the
+fundamental QNM damp fast, and we choose the ``-'' mode which decreases less the damping time. \abcomm{Not clear. 
+Decreases less with respect to what? Do you mean it has a smaller damping time?}
+%
+\ab{This time we} then find \sout{this time} that $p_{\rm qEFT} = 6$,
 %
@@
 by the assumptions of small coupling and small spin used to calculate the QNM frequencies.
-
-\section{Intrinsic binary parameters}
+\
+\section{The estimation of  intrinsic binary parameters in General Relativity and modified theories of gravity}
 \label{app:big_contour}
 
-In this Appendix, we show in Fig.~\ref{fig:corner_plot_all} a corner plot with all intrinsic binary parameters from our parameter estimation for GW150914
-using the \pSEOB{} waveform models for GR and dCS.
-%
-We see that median of the distribution is not affected substantially by the inclusion of the non-GR parameters.
-%
-That is the case for $\Mf$ and $\chi_{\rm f}$ is an underlying assumption of the ParSpec framework.
-%
-We qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
+\ab{We show} in Fig.~\ref{fig:corner_plot_all} a corner plot \ab{for all the} intrinsic binary parameters from our parameter-estimation study of GW150914, using the \pSEOB{} waveform models for GR and dCS.
+%
+We see that \ab{the} median\ab{s} of the \ab{posterior distributions are} not affected substantially by the inclusion of the non-GR parameters.
+\ab{This is particularly important for the $\Mf$ and $\chi_{\rm f}$ parameters, since
+the ParSpec framework assumes that the non-GR theory induces small deviations from GR.} 
+%
+We \ab{obtain} qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
 %

### 2022-04-24 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small commit to merge

--- 2022-04-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
@@
 Several null tests have been proposed to probe the nature of gravity with GW signals~\cite{TheLIGOScientific:2016src,Yunes:2016jcc,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks,LIGOScientific:2021sio}.
-They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the plunge and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow us to set upper limits on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
+They include tests of GW generation~\cite{Arun:2006yw,Yunes:2009ke,Li:2011cg,Agathos:2013upa,Mehta:2022pcn}, where deviations in the post-Newtonian (PN) coefficients in the inspiral, and phenomenological coefficients in the plunge and merger stages can be bounded; tests of GW propagation~\cite{Will:1997bb}, which allow to set upper limit on coefficients entering generalized dispersion relations, including the Compton wavelength associated to the
 mass of the graviton; tests of the polarization of gravitational radiation~\cite{Will:2014kxa}, for which more than
@@
 
-\ab{We will treat the modified theories of gravity as EFTs, and focus on 
-finite-size effects (see, e.g., Ref.~\cite{Sennett:2019bpc}). Thus, for each gravity theory the fundamental lenght-scale 
-$\ell \lesssim GM/c^2$, where $M$ is the mass of the BH. This implies 
-that observable deviations from GR present in those theories arise from modifications 
-to the Kerr geometry of each individual BH. Those finite-size effects can manifest themselves in 
-the QNMs of the remnant produced by the merger, but also in the GW phasing of the inspiral through 
-corrections to the GR spin-induced quadrupole and Love numbers. However, here we will not consider the latter, 
-instead, we will only study the impact of finite-size effects on the QNMs of the 
-remnant.}
-
 We start by briefly reviewing the modified gravity theories we consider in this
@@
 only at the level of $\sim 50\%$ (see the constraint on the 2PN parameter $\varphi_4$ in Fig.~6 of
-Ref.~\cite{LIGOScientific:2021sio}). \ab{So far, analyses that used only the inspiral portion of 
-the BBH GW signals were not able to set meaningful bounds on such deviation at 2PN order~\cite{Nair:2019iur,Perkins:2021mhb}.}
+Ref.~\cite{LIGOScientific:2021sio}). Thus, so far, dCS gravity has remained
+unconstrained by works which use only on the inspiral portion of BBH GW signals~\cite{Nair:2019iur,Perkins:2021mhb}.
 %
@@
 
-\ab{For the EFT of GR with dimension-eight operators, Ref.~\cite{Sennett:2019bpc} focused on the 
-orbital effects (i.e., the inspiral stage) and performed 
-Bayesian model selection using the two lowest-mass BBHs events of the second-observig run of 
-the LIGO-Virgo Collaboration, notably GW151226 and GW170608. They found that the 
-data disfavor the appearance of new physics on distance scales around $\ell_{\rm qEFT} \sim 150$ km.}
+In general \dots
+%
+\hscomm{Alessandra, can you include a short description of~\cite{Sennett:2019bpc} for the quartic EFT?}
 
@@
 %
-The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ are a consequence of the how weakly the QNMs
+The small values of the numerical prefactors of $\gamma_{\rm EdGB}$ are a consequence of the how weakly the QNMs
 of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $\gamma_{\rm EdGB} \approx 0.3$.

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: cleaning edgb sections

--- 2022-04-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
@@
 We find that while the Einstein-dilaton-Gauss-Bonnet theory cannot be
-constrained with these events, we can place upper bounds on the \sout{coupling
-constants} \ab{fundamental length-scale} of cubic- ($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order
+constrained with these events, we can place upper bounds on the
+fundamental length-scale of cubic- ($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order
 ($\ell_{\rm qEFT} \leqslant 51.3$~km) effective-field-theories of general
@@
 by stacking the posteriors of $\ell_{\rm EdGB}$ from a selection of BBHs
-from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}\footnote{These bounds
+from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}\footnote{\hs{These bounds
 are, strictly speaking, valid only when the scalar field $\varphi$ is small (i.e., $\varphi \ll 1$), and
-take into account only the leading-order scalar field contribution arising from the dilatonic coupling.}.
+take into account only the leading-order scalar field interaction arising from original the dilatonic coupling, i.e.,
+$f(\varphi) \approx \varphi$ in Eq.~\eqref{eq:action_sgb}.
+This results in what is often referred to as shift-symmetric scalar-Gauss-Bonnet theory.
+In this theory, NSs do not have scalar monopole charge~\cite{Yagi:2015oca}, while BHs do~\cite{Yunes:2011we,Sotiriou:2013qea,Sotiriou:2014pfa}.}}.
 Secondly, the scalar field influences the response of BHs to linearized perturbations and thus
@@
 were first computed in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn}
-and were extended to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
-%
-See also Refs.~\cite{Witek:2018dmd,Okounkova:2019zep} for NR studies.
+and were extended \hs{(in the polar sector)} to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
+%
+See Ref.~\cite{Bryant:2021xdh} for a study in the geometrical optics limit ($\ell \gg 1$) and
+Refs.~\cite{Witek:2018dmd,Okounkova:2019zep} for NR studies.
 
@@
 NS GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}, using
-equation-of-state independent relations between NS moment of inertia and tidal deformability~\cite{Yagi:2013bca,Yagi:2013awa,Gupta:2017vsl}.
+equation-of-state independent relations between the NS moment of inertia and tidal deformability~\cite{Yagi:2013bca,Yagi:2013awa,Gupta:2017vsl}.
 
@@
 We start by considering EdGB gravity and focus on
-Refs.~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} to determine the
-ParSpec coefficients for this theory.
+Refs.~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} to determine the ParSpec coefficients for this theory.
 % and~\cite{Pierini:2021jxd} for the QNMs of for which the QNMs of nonrotating and
@@
 In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
-of the polar gravitational-\sout{led}\ab{dominant} mode increases as the coupling constant
+of the \hs{dominant axial gravitational-led} mode increases as the coupling constant
 $\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
-branch of QNMs was calculated in Ref.~\cite{Pierini:2021jxd}.
+polar-branch of QNMs was studied in Ref.~\cite{Pierini:2021jxd}.
 %
 Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
-this is the gravitational-led \abcomm{led or dominant?} branch of QNMs we select.
+\hs{we select the axial-parity branch of QNMs.}
 
@@
 %
-The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ \abcomm{the term above 
-is linear not quartic in $\gamma_{\rm EdGB}$. Do you mean $\ell_{\rm EdGB}^4$?} 
-are a consequence of \sout{the} how weakly the QNMs
+% <<<<<<< HEAD
+The small values of the numerical prefactors of $\gamma_{\rm EdGB}$ are a consequence of the how weakly the QNMs
+% =======
+% The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ \abcomm{the term above
+% is linear not quartic in $\gamma_{\rm EdGB}$. Do you mean $\ell_{\rm EdGB}^4$?}
+% are a consequence of \sout{the} how weakly the QNMs
+% >>>>>>> 72e1d3e2d4db50f80c67fc8bc13cab1708d40edb
 of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $\gamma_{\rm EdGB} \approx 0.3$.

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
removing highlighted text i agreed with

@@
 
-\ab{Here, for the theories described in Sec.~\ref{sec:review_theories}, we
+Here, for the theories described in Sec.~\ref{sec:review_theories}, we
 use QNM calculations from the literature and determine
 the coefficients in the ParSpec, which we have summarized
-in Table~\ref{tab:ref_theories_qnms}.}
+in Table~\ref{tab:ref_theories_qnms}.
 %
@@
 
-For the nonrotating QNMs we use\sout{d} \abcomm{We are using present tense when
-describing results in the paper, so I would suggest with stick with that consistently
-in the Appendix.} the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
-generate a new quartic fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
-values of the coupling constant (see, in particular, Eq.~(27) and Fig.~2 of
+For the nonrotating QNMs we use
+% HS: I agree.
+% \abcomm{We are using present tense when
+% describing results in the paper, so I would suggest with stick with that consistently
+% in the Appendix.}
+the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
+generate a new \hs{linear} fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
+values of the $\gamma_{\rm EdGB}$ (see, in particular, Eq.~(27) and Fig.~1 of
 Ref.~\cite{Blazquez-Salcedo:2016enn}).
@@
 The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
-which for consistency with our previous discussion, we truncate at quartic-order in $\gamma_{\rm EdGB}$ \abcomm{$\ell_{\rm EdCS}^4$?}.
-%
-The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ \ab{can be}
+which for consistency with our previous discussion, we truncate at \hs{leading-order in} $\gamma_{\rm EdGB}$
+% \abcomm{$\ell_{\rm EdCS}^4$?}.
+%
+\hs{We can expand the resulting formula} in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
 read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
@@
 
-\ab{We show} in Fig.~\ref{fig:corner_plot_all} a corner plot \ab{for all the} intrinsic binary parameters from our parameter-estimation study of GW150914, using the \pSEOB{} waveform models for GR and dCS.
-%
-We see that \ab{the} median\ab{s} of the \ab{posterior distributions are} not affected substantially by the inclusion of the non-GR parameters.
-\ab{This is particularly important for the $\Mf$ and $\chi_{\rm f}$ parameters, since
-the ParSpec framework assumes that the non-GR theory induces small deviations from GR.}
-%
-We \ab{obtain} qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
+% HS: I agree with all the changes below
+We show in Fig.~\ref{fig:corner_plot_all} a corner plot for all the intrinsic
+binary parameters from our parameter-estimation study of GW150914, using the
+\pSEOB{} waveform models for GR and dCS.
+%
+We see that the medians of the posterior distributions are not affected substantially by the inclusion of the non-GR parameters.
+%
+This is particularly important for the $\Mf$ and $\chi_{\rm f}$ parameters, since
+the ParSpec framework assumes that the non-GR theory induces small deviations from GR.
+%
+We obtain qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
 %

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more edits

@@
 We give a prescription on how to include in this waveform model the quasinormal mode frequencies
-calculated on a theory-by-theory basis. In particular, we focus on theories that deviate
-from general relativity by higher-order curvature corrections, namely,
+calculated on a theory-by-theory basis. In particular, we focus on theories that modify
+general relativity by higher-order curvature corrections, namely,
 Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
@@
 Since the first detection of gravitational waves (GWs) from a binary black-hole (BBH) merger in 2015~\cite{LIGOScientific:2016aoc},
-the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GWs signals~\cite{LIGOScientific:2021djp} from mergers
+the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GW events~\cite{LIGOScientific:2021djp} from mergers
 of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki,LIGOScientific:2020aai} and their mixture~\cite{LIGOScientific:2021qlt}. These results have been confirmed
@@
 cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
-quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km \\
+quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km\hs{$^{\ast}$} \\
 \hline \hline
@@
 They were obtained combining Bayesian-inference results from GW150914 and GW200129.
-Current constraints on $\ell_{\rm th}$ are also listed.}
+Current constraints on $\ell_{\rm th}$ are also listed.
+%
+\hs{Our result for the quartic EFT of GR is only in marginal tension with our hard cut-off scale for the
+validity of the theory and hence we do still quote it here. See Sec.~\ref{sec:results_qeft} for details.}
+}
 \label{tab:bound_summary}
@@
 %
-\ab{For completness,} in Appendix~\ref{app:big_contour} we also
+For completness, in Appendix~\ref{app:big_contour} we also
 show how all other intrinsic parameter parameters remain unbiased.
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
+\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined_corrected.pdf}
 \caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
+\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold_corrected.pdf}
 \caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
@@
 cubic, and quartic EFTs of GR) using observational data from the LVK events
-GW150914 and GW200129. \ab{Our results are summarzied in Table~\ref{tab:bound_summary}.}
-
-\ab{In particular,} we found, that within the interpretation \ab{of} these theories as EFTs and the
-region of validity of the ParSpec framework, the \sout{coupling constant} \ab{fundamental length-scale} of dCS gravity is bound as
+GW150914 and GW200129. Our results are summarized in Table~\ref{tab:bound_summary}.
+
+In particular, we found, that within the interpretation of these theories as EFTs and the
+region of validity of the ParSpec framework, the fundamental length-scale of dCS gravity is bound as
 $\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
@@
 %
-In contrast, we could not place any bounds on the \sout{coupling constant} \ab{length-scale} \abcomm{Maybe
+In contrast, we could not place any bounds on the \hs{fundamental} length-scale \abcomm{Maybe
 this is common in the literature, but I would call it length-scale instead of coupling
-constant. What do you think?} of EdGB gravity $\ell_{\rm EdGB}$.
+constant. What do you think?}~\hscomm{I agree.} of EdGB gravity $\ell_{\rm EdGB}$.
 %
@@
 %
-\ab{Using data of the LVK BBHs, it was found that the posterior distributions for
-deviations from GR were uninformative in dCS gravity, but not in EdGB gravity.}
+Using data of the LVK BBHs, it was found that the posterior distributions for
+deviations from GR were uninformative in dCS gravity, but not in EdGB gravity.
 We emphasize that both those theories (and the cubic EFT of GR also studied here) all predict the same exponent $p$ in ParSpec.
@@
 
-\sout{Our work shows that, with the GW signals so far observed by the LVK Collaboration,
-there are theories of gravity (such as dCS) that can be unconstrained by studying the
-inspiral portion of GW events, {\it yet} {it} can be constrained, if we analyze the ringdown.}
-%
-\sout{Our results show that to fulfill the potential to test GR with \ab{future} GW observations,
-further work \ab{is needed} on modeling \sout{of} the late-inspiral-(plunge)-merger and ringdown of
-coalescing BHs  (with NR simulations) and, complementary,}
-%
-\sout{We hope that our results can also serve as further motivation to address these
-outstanding problems.}
+% \sout{Our work shows that, with the GW signals so far observed by the LVK Collaboration,
+% there are theories of gravity (such as dCS) that can be unconstrained by studying the
+% inspiral portion of GW events, {\it yet} {it} can be constrained, if we analyze the ringdown.}
+% %
+% \sout{Our results show that to fulfill the potential to test GR with \ab{future} GW observations,
+% further work \ab{is needed} on modeling \sout{of} the late-inspiral-(plunge)-merger and ringdown of
+% coalescing BHs  (with NR simulations) and, complementary,}
+% %
+% \sout{We hope that our results can also serve as further motivation to address these
+% outstanding problems.}
 
@@
 In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
-of the \hs{dominant axial gravitational-led} mode increases as the coupling constant
+of the \hs{dominant \emph{axial} gravitational-led} mode increases as the coupling constant
 $\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
-polar-branch of QNMs was studied in Ref.~\cite{Pierini:2021jxd}.
+\emph{polar}-parity QNMs was studied in Ref.~\cite{Pierini:2021jxd}.
 %
 Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
-\hs{we select the axial-parity branch of QNMs.}
+\hs{we select the axial-parity branch of QNMs and
+%
+for consistency, we only consider the leading-order $j=0$ coefficients in EdGB gravity.}
 
@@
 
+\hscomm{There was an error here: I mixed the axial QNMs we used for the nonrotating coefficients, with the polar QNMs
+for which the spin-corrections were computed. Because it is inconsistent, I suggest changing opening paragraph with the highlighted text,
+and then remove the $N_{\rm max} = 1$ results from our EdGB plots. What do you think?}
+%
 The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
@@
 % \abcomm{$\ell_{\rm EdCS}^4$?}.
-%
+
+\hscomm{Could remove this part until the end of this section.}
 \hs{We can expand the resulting formula} in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
@@
 of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.
+%
+\hscomm{Should we say that this happens almost by ``construction''? That would be because \pSEOB{} waveform changes very little the inspiral
+and the final masses and spins are predicted according to a GR formula.}
 

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added bbh nr papers, changes to conclusions

@@
 \hs{Our result for the quartic EFT of GR is only in marginal tension with our hard cut-off scale for the
-validity of the theory and hence we do still quote it here. See Sec.~\ref{sec:results_qeft} for details.}
+validity of the theory and hence we do still quote it here. See Secs.~\ref{sec:remarks} and~\ref{sec:results_qeft}
+for details.}
 }
@@
 In particular, in the literature, we can already find fitting formulas relating
-the QNMs to the BHs mass, spin and coupling constant $\ell_{\rm th}$, the latter being
+the QNMs to the BHs mass, spin and length-scale $\ell_{\rm th}$, the latter being
 specific to each theory, up to $j=1$ in the spin expansion (see Table~\ref{tab:ref_theories_qnms}).
@@
 %
-We note that $\Lambda_{\rm EFT}$ has dimensions of length and hence can be compared to the coupling strength $\ell_{\rm th}$.
+We note that $\Lambda_{\rm EFT}$ has dimensions of length and hence can be compared to \hs{each theory's fundamental length-scale} $\ell_{\rm th}$.
 %
@@
 this is common in the literature, but I would call it length-scale instead of coupling
-constant. What do you think?}~\hscomm{I agree.} of EdGB gravity $\ell_{\rm EdGB}$.
+constant. What do you think?}~\hscomm{I agree. I introduced ``length-scale'' at a few other place in the text.} of EdGB gravity $\ell_{\rm EdGB}$.
 %
@@
 Second, it would be important to incorporate additional effects, such as spin-precession and eccentricity
-to \pSEOB~(see, for instance, Refs.~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}). \ab{Third, it will be
-interesting, to perfom tests of modified theories of gravity using IMR waveform models that include, during
-the inspiral stage, finite-size effects induced by the non-GR geometry around the  holes ---
-for example the ones due to spin-induced quadrupole, tidal deformability and absorbtion, and also
+to \pSEOB~(see, for instance, Refs.~\cite{Ossokine:2020kjp,Ramos-Buades:2021adz}).
+%
+Third, it will be
+interesting, to perform tests of modified theories of gravity using IMR waveform models that include, during
+the inspiral stage, finite-size effects induced by the non-GR geometry around the BHs ---
+for example the ones due to spin-induced quadrupole, tidal deformability and absorption, and also
 orbital effects due to non-GR gravitational interactions
-between the holes. Those effects could be included using the flexible theory-independent
+between the BHs. Those effects could be included using the flexible theory-independent
 method~\cite{Mehta:2022pcn}, as done in Ref.~\cite{Sennett:2019bpc} or the
@@
 from GR caused by orbital effects requires a different EFT interpretation than what we
-adopted in Sec.~\ref{sec:remarks} (see also Sec. II C in Ref.~\cite{Sennett:2019bpc}).
+adopted in Sec.~\ref{sec:remarks} (see also Sec.~IIC in Ref.~\cite{Sennett:2019bpc}).
 Indeed, in this case one would need to analyze the data considering that the modified theory of
-gravity is valid for $\ell \gtrsim  M$, but $\ell \lesssim R$, being $R$ the binary's separation. Fourth,
-to test the robustness of the results obtained in this paper, it will be very useful to employ NR waveforms
+gravity is valid for $\ell_{\rm th} \gtrsim  M$, but $\ell_{\rm th} \lesssim \mathcal{R}$, being $\mathcal{R}$ the binary's separation.
+%
+Fourth, to test the robustness of the results obtained in this paper, it will be very useful to employ NR waveforms
 produced in some of the non-GR theories under consideration, as synthetic signals, and carry out
 Bayesian analysis to recover the binary's parameters, including the non-GR ones during the ringdown.
-As today, there are only a handful of such NR simulations~XXX. Last, but not least, it will be very
+As today, there are only a small number of such BBH NR simulations, for a
+given theory~\cite{Healy:2011ef,Witek:2018dmd,Okounkova:2017yby,Hirschmann:2017psw,Okounkova:2020rqw,Okounkova:2020rqw,Silva:2020omi,East:2020hgw,East:2021bqk,Figueras:2021abd}.
+%
+Last, but not least, it will be very
 beneficial to calculate the QNMs (complex) frequencies of rapidly-rotating BHs in modified gravity theories
 (with BH perturbation theory). This is a challenging problem, but certainly necessary,
-also in the context of ParSpec, if higher spin ocrrections would need to be
-included to make the framwork robust.}
+also in the context of ParSpec, if higher spin corrections would need to be
+included to make the framework robust.
 
@@
 In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
-of the \hs{dominant \emph{axial} gravitational-led} mode increases as the coupling constant
+of the \hs{dominant \emph{axial} gravitational-led} mode increases as the length-scale
 $\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
@@
 read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
-and re-expand in small coupling and spin.
-%
-These steps yield \ab{for} $p_{\rm EdGB} = 4$,
+and re-expand in $\ell_{\rm EdGB}$ and $\chi$.
+%
+These steps yield for $p_{\rm EdGB} = 4$,
 %
@@
 For dCS gravity, we follow Ref.~\cite{Wagle:2021tam}, which numerically calculated the QNMs, $\sigma_{\rm dCS}$,
-of slowly-rotating BHs, \sout{in this theory} and found that \ab{for} the axial gravitational modes \ab{the} \sout{have their} damping time increases, as we
-increase the Chern-Simons coupling $\ell_{\rm dCS}$, at fixed spin $\chi$ of the BH.
+of slowly-rotating BHs, and found that for the axial gravitational modes the damping time increases, as we
+increase the Chern-Simons coupling $\ell_{\rm dCS}$, \hs{at constant BH spin.}
 %
@@
 %
-\ab{We use} \sout{Using} the fitting formula Eq.~(54a) of Ref.~\cite{Wagle:2021tam}, namely,
-%
-\begin{equation}
-    M \, {\rm Re}(\sigma)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi_{\rm f})^{c_{5} + c_{6} \kappa \zeta},
+Using the fitting formula Eq.~(54a) of Ref.~\cite{Wagle:2021tam}, namely,
+%
+\begin{equation}
+    M {\rm Re}(\sigma)_{\rm dCS} = c_{1} + c_{2} \kappa \zeta + (c_{3} + c_{4} \kappa \zeta) \, (1 - \chi_{\rm f})^{c_{5} + c_{6} \kappa \zeta},
     \label{eq:omega_dsc_eg}
@@
 \begin{align}
-    M \, \omega_{\rm dCS} =
+    M \omega_{\rm dCS} =
     \left( 0.3722 + 1.1945 \gamma_{\rm dCS} \right)
@@
 %
-We find that (reassuringly) the nonrotating GR part of the expression above agrees with $\omega^{(0)}$ of Ref.~\cite{Maselli:2019mjd} to 0.5\% relative \sout{percent} error.
-The same \sout{error} estimate \sout{is} \ab{leads to a} larger \ab{relative error} ($\approx 20$\%) for the linear-in-spin coefficient (i.e., 0.1861 in comparison to 0.1258 of Ref.~\cite{Maselli:2019mjd}).
-%
-We attribute this difference to Ref.~\cite{Wagle:2021tam} having fitted Eq.~\eqref{eq:omega_dsc_eg} to QNM data computed to linear-order in spin, whereas~\cite{Maselli:2019mjd}
-fitted Eq.~\eqref{eq:kerr_expansion} to Kerr QNM valid to all orders in spin.
+We find (reassuringly) that the nonrotating GR part of the expression above agrees with $\omega^{(0)}$ of Ref.~\cite{Maselli:2019mjd} to 0.5\% relative error.
+The same estimate leads to a larger relative error ($\approx 20$\%) for the linear-in-spin coefficient (i.e., 0.1861 in comparison to 0.1258 of Ref.~\cite{Maselli:2019mjd}).
+%
+We attribute this difference to Ref.~\cite{Wagle:2021tam} having fitted
+Eq.~\eqref{eq:omega_dsc_eg} to QNM data computed to linear-order in spin,
+whereas~\cite{Maselli:2019mjd} fitted Eq.~\eqref{eq:kerr_expansion} to Kerr QNM
+valid to all orders in spin.
 
@@
 %
-We can carry the same steps for $\tau_{\rm dCS}$ and find
+We can carry the same steps for $\tau_{\rm dCS} = - 1 / {\rm Im}(\sigma)_{\rm dCS}$ and find
 %
@@
 %
-As for the case of EdGB gravity, we remark that the alarmingly large values of
+We remark that the alarmingly large values of
 $\delta \omega_{\rm dCS}^{(1)}$ and $\delta \tau_{\rm dCS}^{(1)}$ are
-compensated by the assumptions that $\gamma_{dCS}$ and $\chi$
-are much less than unity, which are the assumptions used in Ref.~\cite{Wagle:2021tam}
+compensated by the assumptions that $\gamma_{\rm dCS}$ and $\chi$
+are much less than unity, which are indeed the assumptions used in Ref.~\cite{Wagle:2021tam}
 to compute the QNMs.

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
changes to qeft

@@
 %
-We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
-hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
-%
-As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_{\rm f}$ before $\varepsilon = 1/2$.
-%
-Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
-%
-\begin{equation}
-    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level}\,.
-\end{equation}
-%
-% \abcomm{Please update the paragraph below.}
+We find that while the Parspec bound is satisfied, the EFT bound is only marginally so,
+%
+As shown in Fig.~\ref{fig:qEFT_cdf}, the 90\% credible level is reached for $\varepsilon \approx 0.58$
+(in the case of GW15094) and for $\varepsilon \approx 0.64$ (in the case of GW200129).
+%
+Having in mind that the hard cut-off $\varepsilon = 1/2$ is not fundamental, but to keep consistency
+across our analysis, our final result
+%
+\begin{equation}
+    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level},
+\end{equation}
+%
+at 90\% credible level should be taken lightly.
+%
+However, we \emph{can} claim the validity of the bound above, but at a lower,
+68\% credible level.
+
+% We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
+% hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
+% %
+% As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_{\rm f}$ before $\varepsilon = 1/2$.
+% %
+% Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
+% %
+% \begin{equation}
+%     \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level}\,.
+% \end{equation}
+% %
+% % \abcomm{Please update the paragraph below.}
 In this theory, we have considered only $N_{\rm max} = 0$.
 %
-\ab{Indeed, we find that when adding the spin corrections and for $\ell_{\rm qEFT} \gtrsim 80$~km,
-the waveforms can have a ringdown segment larger (sometimes seconds long) than the inspiral-plunge segment in the detectors frequency band, making the parameter estimation challenging.} \abcomm{The reference to 80 km comes out of the blue.
+\ab{We find that the addition of spin corrections (while maintaining the same prior ranges on $\ell_{\rm qEFT}$ as
+used in the $N_{\rm max} = 0$ study)
+can result in waveforms that can have a ringdown segment larger (sometimes seconds long) than the inspiral-plunge segment in the detectors frequency band, making the parameter estimation challenging.} \abcomm{The reference to 80 km comes out of the blue.
 Doesn't it?
-Why did you refer to it?}
+Why did you refer to it?}~\hscomm{That was the upper prior limit for the GW150914 run.
+I modified the text to explain this.}
 % for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
@@
 We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
-can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 90\% credibility.
+can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at \hs{68\% credibility}.
 }
@@
 %
-The resulting \pSEOB~waveform model \ab{does} not bias (relative to GR) the inference of
+The resulting \pSEOB~waveform model does not bias (relative to GR) the inference of
 the intrinsic binary parameters, as required by ParSpec (see, in particular, Fig.~\ref{fig:corner_plot} and
@@
 of slowly-rotating BHs, and found that for the axial gravitational modes the damping time increases, as we
-increase the Chern-Simons coupling $\ell_{\rm dCS}$, \hs{at constant BH spin.}
+increase $\ell_{\rm dCS}$, \hs{at constant BH spin.}
 %
@@
 As with the previous theories, the larger values of some of these parameters are compensated
-by the assumptions of small coupling and small spin used to calculate the QNM frequencies.
+by the assumptions of weak coupling and small spin used to calculate the QNM frequencies.
 \

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small chenges and edits to highligthed text

@@
 
-\ab{We will treat the modified theories of gravity as EFTs, and focus on
+We will treat the modified theories of gravity as EFTs, and focus on
 finite-size effects (see, e.g., Ref.~\cite{Sennett:2019bpc}). Thus, for each gravity theory we impose that
-the fundamental length-scale $\ell \lesssim GM/c^2$, where $M$ is the mass of the BH. This implies
+the fundamental length-scale $\ell_{\rm th} \lesssim GM/c^2$, where $M$ is the mass of the BH. This implies
 that observable deviations from GR present in those theories arise from modifications
@@
 instead, we will only study the impact of finite-size effects on the QNMs of the
-remnant.}
+remnant.
 
@@
 only at the level of $\sim 50\%$ (see the constraint on the 2PN parameter $\varphi_4$ in Fig.~6 of
-Ref.~\cite{LIGOScientific:2021sio}). \ab{So far, analyses that used only the inspiral portion of
-the BBH GW signals were not able to set meaningful bounds on such deviation at 2PN order~\cite{Nair:2019iur,Perkins:2021mhb}.}
+Ref.~\cite{LIGOScientific:2021sio}). So far, analyses that used only the inspiral portion of
+the BBH GW signals were not able to set meaningful bounds on such deviation at 2PN order~\cite{Nair:2019iur,Perkins:2021mhb}.
 %
@@
 $\tilde{\cal C} = R_{\mu\nu\gamma\delta} \epsilon^{\mu\nu}{}_{\rho\sigma} R^{\rho\sigma\gamma\delta}$,
-and $(\lambda_{\rm o, e},\varepsilon_{i})$, $i=$~1, 2, 3, are dimensionless parameters.
+and both $\lambda_{\rm o, e}$ and $\varepsilon_{i}$ (with $i=1, 2, 3$) are dimensionless parameters.
 %
@@
 
-\ab{For the EFT of GR with dimension-eight operators, Ref.~\cite{Sennett:2019bpc} focused on the
+For the EFT of GR with dimension-eight operators, Ref.~\cite{Sennett:2019bpc} focused on the
 orbital effects (i.e., instead of finite-size effects) and performed
@@
 the LIGO-Virgo Collaboration, notably GW151226 and GW170608. They found that the
-data disfavor the appearance of new physics on distance scales around $\ell_{\rm qEFT} \sim 150$ km.}
+data disfavor the appearance of new physics on distance scales around $\ell_{\rm qEFT} \sim 150$ km.
 

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
comments on qEFT
footnote

@@
 are, strictly speaking, valid only when the scalar field $\varphi$ is small (i.e., $\varphi \ll 1$), and
-take into account only the leading-order scalar field interaction arising from original the dilatonic coupling, i.e.,
+take into account only the leading-order scalar field interaction arising from the original dilatonic coupling, i.e.,
 $f(\varphi) \approx \varphi$ in Eq.~\eqref{eq:action_sgb}.
@@
 combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$. The quoted
-result correspond to 90\% credible values.
+result correspond \hs{to 90\% credible values \emph{if} we allow for a more flexible cut-off $\varepsilon \lesssim 0.65$.
+The result is however robust under the hard cut-off of $\varepsilon = 1/2$ at 65\% credible level.}
 }

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
reformatted table

@@
 \begin{table*}[t]
-\begin{tabular}{c | c c c c c c c c c c}
-\hline
-\hline
-Theory      & $\omega^{(0)}_{220}$ & $\tau^{(0)}_{220}$ & $\omega^{(1)}_{220}$ & $\tau^{(1)}_{220}$ & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.
+% \begin{tabular}{c | c c c c c c c c c c}
+% \hline
+% \hline
+% Theory      & $\omega^{(0)}_{220}$ & $\tau^{(0)}_{220}$ & $\omega^{(1)}_{220}$ & $\tau^{(1)}_{220}$ & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.
 \\
-\hline
-GR          & 0.3737               & 11.2407            &  0.1258              & 0.2522             & --  & --                          & --                        & --                          & --                        & \cite{Maselli:2019mjd} \\
-\hline
-EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
-dCS         & --                   & --                 &  --                  & --                 & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
-cubic EFT   & --                   & --                 &  --                  & --                 & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
-quartic EFT & --                   & --                 &  --                  & --                 & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
+% \hline
+% GR          & 0.3737               & 11.2407            &  0.1258              & 0.2522             & --  & --                          & --                        & --                          & --                        & \cite{Maselli:2019mjd} \\
+% \hline
+% EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
+% dCS         & --                   & --                 &  --                  & --                 & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
+% cubic EFT   & --                   & --                 &  --                  & --                 & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
+% quartic EFT & --                   & --                 &  --                  & --                 & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
+% \hline
+% \hline
+% \end{tabular}
+%
+\begin{tabular}{c | c }
+\hline
+\hline
+Theory                  & GR~\cite{Maselli:2019mjd} \\
+\hline
+$\omega^{(0)}_{220}$    & 0.3737                    \\
+$\tau^{(0)}_{220}$      & 11.2407                   \\
+$\omega^{(1)}_{220}$    & 0.1258                    \\
+$\tau^{(1)}_{220}$      & 0.2522                    \\
+\hline
+\hline
+\end{tabular}
+\quad
+\begin{tabular}{c | c  c  c  c}
+\hline
+\hline
+Theory                        & EdGB ($p=4$)~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & dCS ($p=4$)~\cite{Wagle:2021tam} & cubic EFT ($p=4$)~\cite{Cano:2021myl} & quartic EFT ($p=6$)~\cite{Cano:2021myl} \\
+\hline
+$\delta\omega^{(0)}_{220}$    & 0.0107                                               & 3.1964                   & $-$0.5813                     & $-$0.2114                       \\
+$\delta\tau^{(0)}_{220}$      & 0.0044                                               & 6.3619                   & $-$0.2114                     & $-$0.6070                       \\
+$\delta\omega^{(1)}_{220}$    & $-$0.2480                                            & 41.199                   & $-$3.8620                     & $-$1.5263                       \\
+$\delta\tau^{(1)}_{220}$      & $-$1.1010                                            & 794.66                   & 265.12                        & 171.35                          \\
 \hline

### 2022-04-26 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
edgb appendix and conclusions

@@
 general relativity by higher-order curvature corrections, namely,
-Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
+Einstein-dilaton-Gauss-Bonnet and dynamical Chern-Simons theories, and cubic- and quartic-order
 effective-field-theories of general relativity.
@@
 
-The large number of GW observations has allowed us to infer relevant astrophysical~\cite{LIGOScientific:2021aug} and cosmological~\cite{LIGOScientific:2021psn} information on the compact-object population in our local Universe, and also to probe General Relativity (GR) in the high-velocity, dynamical and strong-field regime of gravity~\cite{LIGOScientific:2021sio}.
+The large number of GW observations has allowed us to infer relevant astrophysical~\cite{LIGOScientific:2021aug} and cosmological~\cite{LIGOScientific:2021psn} information on the compact-object population in our local Universe, and also to probe General Relativity (GR) in the high-velocity, dynamical and strong-field regime of gravity~\cite{Yunes:2016jcc,LIGOScientific:2021sio}.
 The latter complement tests of GR in the low-velocity, quasi-static or linear regimes available with Solar-System experiments~\cite{Will:2014kxa}, binary-pulsar~\cite{Wex:2014nva,Kramer:2021jcw} and galactic-center~\cite{GRAVITY:2018ofz,Do:2019txf,EventHorizonTelescope:2019ths} observations,
@@
 
-BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
+BHs in EdGB gravity have scalar hair, to which we can associate a monopole scalar charge,
 related to the asymptotic $r^{-1}$ fall-off of the scalar field, where $r$ is the distance from the BH.
@@
 %
-Since the scalar field is sourced by a curvature scalar, $Q$ is larger (smaller),
+Since the scalar field is sourced by a curvature scalar, the scalar charge is larger (smaller),
 the smaller (larger) the BH mass is.
@@
 %
-$\ell_{\rm EdGB} \leqslant 1.33$~km
+% $\ell_{\rm EdGB} \leqslant 1.33$~km
+\hs{$\ell_{\rm EdGB} \leqslant 7.1$~km}
 %
@@
 %
-$\ell_{\rm EdGB} \leqslant 1.7$~km,
+% $\ell_{\rm EdGB} \leqslant 1.7$~km,
+\hs{$\ell_{\rm EdGB} \leqslant 9.1$~km},
 %
@@
 This results in what is often referred to as shift-symmetric scalar-Gauss-Bonnet theory.
-In this theory, NSs do not have scalar monopole charge~\cite{Yagi:2015oca}, while BHs do~\cite{Yunes:2011we,Sotiriou:2013qea,Sotiriou:2014pfa}.}}.
+In this theory, NSs do not have scalar monopole charge~\cite{Yagi:2015oca}, while BHs do~\cite{Yunes:2011we,Sotiriou:2013qea,Sotiriou:2014pfa}.
+Finally, we take note constant $\alpha_{\rm EdGB}$ used in Refs.~\cite{Yagi:2011xp,Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} is related to $\ell_{\rm EdGB}$ as $\ell_{\rm EdGB} = 4 \pi^{1/4} |\alpha_{\rm EdGB}|^{1/2}$.
+\hscomm{I had to translate between notations and rewrote the bounds quoted for $\alpha_{\rm EdGB}$ in terms of our $\ell_{\rm EdGB}$.}
+}}.
 Secondly, the scalar field influences the response of BHs to linearized perturbations and thus
@@
 \begin{align} \label{eq:action_dcs}
-    S_{\rm dCS} = \frac{1}{16 \pi}
+    S_{\rm dCS} =
     \int \dV
     \left[
-    R - \tfrac{1}{2}(\partial \vartheta)^2
+    \hs{\tfrac{1}{16\pi}} R - \tfrac{1}{2}(\partial \vartheta)^2
     + \tfrac{1}{4} \ell^{2}_{\rm dCS} \, \vartheta \, {}^{*}RR
     \right],
-    \nonumber \\
 \end{align}
@@
 %
-As in scalar-Gauss-Bonnet theories, $\int \dV {}^{*}RR$ by itself is a boundary
-term~\cite{Jackiw:2003pm} that does not contribute to the field equations in
-four-dimensions.
+The Pontryagin density by itself, $\int \dV {}^{*}RR$, is a boundary
+term that does not contribute to the field equations in
+four-dimensions~\cite{Jackiw:2003pm}.
 %
@@
 \hline
-Theory                  & GR~\cite{Maselli:2019mjd} \\
+                        & GR~\cite{Maselli:2019mjd} \\
 \hline
@@
 \hline
-Theory                        & EdGB ($p=4$)~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & dCS ($p=4$)~\cite{Wagle:2021tam} & cubic EFT ($p=4$)~\cite{Cano:2021myl} & quartic EFT ($p=6$)~\cite{Cano:2021myl} \\
+                              & EdGB ($p=4$)~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & dCS ($p=4$)~\cite{Wagle:2021tam} & cubic EFT ($p=4$)~\cite{Cano:2021myl} & quartic EFT ($p=6$)~\cite{Cano:2021myl} \\
 \hline
@@
 %
-We note that $\Lambda_{\rm EFT}$ has dimensions of length and hence can be compared to \hs{each theory's fundamental length-scale} $\ell_{\rm th}$.
+We note that $\Lambda_{\rm EFT}$ has dimensions of length and hence can be compared to each theory's fundamental length-scale $\ell_{\rm th}$.
 %
@@
 \begin{equation}
-    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M_{f}}\right)^4\,.
+    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M^{\rm s}_{\rm f}}\right)^4\,.
     \label{eq:def_gamma_gb}
@@
 This shows that that the ``EFT bound'' given by Eq.~\eqref{eq:eft_bound} is
-never met at a significant credibility and thus that we cannot place a bound on
+never met to a significant credible level and thus that we cannot place a bound on
 $\ell_{\rm EdGB}$.
@@
 \begin{equation}
-    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm dCS}}{G M_{\rm f}} \right)^{4}\,,
+    \gamma_{\rm CS} = \left( \frac{c^2 \ell_{\rm dCS}}{G M^{\rm s}_{\rm f}} \right)^{4}\,,
 \end{equation}
@@
 \begin{equation}
-    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level},
+    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km},
+    %\quad \textrm{at 90\% credible level},
 \end{equation}
@@
 %
-\ab{We find that the addition of spin corrections (while maintaining the same prior ranges on $\ell_{\rm qEFT}$ as
-used in the $N_{\rm max} = 0$ study)
-can result in waveforms that can have a ringdown segment larger (sometimes seconds long) than the inspiral-plunge segment in the detectors frequency band, making the parameter estimation challenging.} \abcomm{The reference to 80 km comes out of the blue.
-Doesn't it?
-Why did you refer to it?}~\hscomm{That was the upper prior limit for the GW150914 run.
-I modified the text to explain this.}
+We find that the addition of spin corrections (while maintaining the same prior
+ranges on $\ell_{\rm qEFT}$ as used in the $N_{\rm max} = 0$ study) can result
+in waveforms that can have a ringdown segment larger (sometimes seconds long)
+than the inspiral-plunge segment in the detectors frequency band, making the
+parameter estimation challenging.
+% \abcomm{The reference to 80 km comes out of the blue. Doesn't it? Why did you refer to it?}~\hscomm{That was the upper prior limit for the GW150914 run. I modified the text to explain this.}
 % for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
@@
 result correspond \hs{to 90\% credible values \emph{if} we allow for a more flexible cut-off $\varepsilon \lesssim 0.65$.
-The result is however robust under the hard cut-off of $\varepsilon = 1/2$ at 65\% credible level.}
+However, the result is robust under the hard cut-off of $\varepsilon = 1/2$ at 65\% credible level.}
 }
@@
 %
-In contrast, we could not place any bounds on the \hs{fundamental} length-scale \abcomm{Maybe
-this is common in the literature, but I would call it length-scale instead of coupling
-constant. What do you think?}~\hscomm{I agree. I introduced ``length-scale'' at a few other place in the text.} of EdGB gravity $\ell_{\rm EdGB}$.
+In contrast, we could not place any bounds on the \hs{fundamental} length-scale
+% \abcomm{Maybe
+% this is common in the literature, but I would call it length-scale instead of coupling
+% constant. What do you think?}~\hscomm{I agree. I introduced ``length-scale'' at a few other place in the text.}
+of EdGB gravity $\ell_{\rm EdGB}$.
 %
@@
 Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
-\hs{we select the axial-parity branch of QNMs and
-%
-for consistency, we only consider the leading-order $j=0$ coefficients in EdGB gravity.}
-
+we select the axial-parity branch of QNMs.
+%
+% for consistency, we only consider the leading-order $j=0$ coefficients in EdGB gravity.}
+%
 For the nonrotating QNMs we use
@@
 the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
-generate a new \hs{linear} fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
+generate a new linear fit in $\gamma_{\rm EdGB}$ using numerical QNM data valid for small
 values of the $\gamma_{\rm EdGB}$ (see, in particular, Eq.~(27) and Fig.~1 of
@@
 % >>>>>>> 72e1d3e2d4db50f80c67fc8bc13cab1708d40edb
-of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $\gamma_{\rm EdGB} \approx 0.3$.
-
-\hscomm{There was an error here: I mixed the axial QNMs we used for the nonrotating coefficients, with the polar QNMs
-for which the spin-corrections were computed. Because it is inconsistent, I suggest changing opening paragraph with the highlighted text,
-and then remove the $N_{\rm max} = 1$ results from our EdGB plots. What do you think?}
-%
-The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
-which for consistency with our previous discussion, we truncate at \hs{leading-order in} $\gamma_{\rm EdGB}$
+of BHs in EdGB gravity deviate from their GR counterparts, even at moderately large values of $\gamma_{\rm EdGB} \approx 0.3$.
+
+% \hscomm{There was an error here: I mixed the axial QNMs we used for the nonrotating coefficients, with the polar QNMs
+% for which the spin-corrections were computed. Because it is inconsistent, I suggest changing opening paragraph with the highlighted text,
+% and then remove the $N_{\rm max} = 1$ results from our EdGB plots. What do you think?}
+%
+\hs{The spin-corrections to the \emph{polar} gravitational-led modes
+were calculated in Ref.~\cite{Pierini:2021jxd} [see, in particular, their Eqs.~(51)
+and~(52).]
+%
+For consistency with our previous discussion, we truncate these equations at
+leading-order in $\gamma_{\rm EdGB}$, but we emphasize that we are being inconsistent in
+mixing results valid for modes of different parities.
+%
+We still do so, simply to explore what the rotational corrections to EdGB gravity QNMs \emph{might}
+tells us in our ringdown analysis and the results of Ref.~\cite{Pierini:2021jxd} are our best guide
+available presently.}
 % \abcomm{$\ell_{\rm EdCS}^4$?}.
 
-\hscomm{Could remove this part until the end of this section.}
-\hs{We can expand the resulting formula} in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
+% \hscomm{Could remove this part until the end of this section.}
+%
+We can expand the resulting formula in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
 read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
@@
 \begin{align}
-     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
+     \delta \omega_{\rm EdGB}^{(0)} = 0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
 \end{align}
@@
 
-For dCS gravity, we follow Ref.~\cite{Wagle:2021tam}, which numerically calculated the QNMs, $\sigma_{\rm dCS}$,
-of slowly-rotating BHs, and found that for the axial gravitational modes the damping time increases, as we
-increase $\ell_{\rm dCS}$, \hs{at constant BH spin.}
+For dCS gravity, we follow Ref.~\cite{Wagle:2021tam}, which numerically calculated the QNMs
+of slowly-rotating BHs, and found that for the axial gravitational-led modes the damping time increases, as we
+increase $\ell_{\rm dCS}$, at constant BH spin.
 %
@@
 %
+\hs{Indeed, since \pSEOB{} introduces only minimal modifications to the
+inspiral and because the remnant BH parameters are estimated according GR
+predictions, the fact that only small biases are introduced on $\Mf$ and $\chi_{\rm f}$
+is, to some extend, expected.}
+%
 We obtain qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
@@
 %
-\hscomm{Should we say that this happens almost by ``construction''? That would be because \pSEOB{} waveform changes very little the inspiral
-and the final masses and spins are predicted according to a GR formula.}
+%
+% %
+% \hscomm{Should we say that this happens almost by ``construction''? That would be because \pSEOB{} waveform changes very little the inspiral
+% and the final masses and spins are predicted according to a GR formula.}
 

### 2022-04-26 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
trying to trim text

@@
 we provide details in calculating the non-GR QNM frequencies, when using ParSpec,
-for the four modified gravity theories under consideration.
+for the modified gravity theories under consideration.
 %
@@
 information to the ParSpec coefficients \emph{can lead to different interpretations
-of the final bounds on $\ell_{\rm th}$, even for different theories that predict the same
+of the bounds on $\ell_{\rm th}$, even for different theories that predict the same
 value of the exponent $p$.}
@@
 %
-In contrast, we could not place any bounds on the \hs{fundamental} length-scale
+In contrast, we could not place any bounds on the fundamental length-scale
 % \abcomm{Maybe

### 2022-04-26 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
trimming text, adjusting (trying to) fix plot positions

@@
 Here we explore the range $\varepsilon \in [0, 1]$, but following
-the Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} we quote our final results using
-$\varepsilon = 1/2$.
+Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} we quote our final
+results using $\varepsilon = 1/2$, \hs{but we stress that there is no
+fundamental justification for using this cut off.}
 % %
@@
 % %
-We say that a bound has been placed on $\ell_{\rm th}$, if most of the PDF $P(\ell_{\rm th} | d)$ support is in the interval
+
+Under these assumptions, we will say that a bound has been placed on $\ell_{\rm th}$, if most of the PDF $P(\ell_{\rm th} | d)$ support is in the interval
 $[0, \, \Lambda_{\rm EFT}(1/2, \mathfrak{m})]$.
@@
 
-\begin{figure}[t]
+We start with EdGB gravity.
+%
+In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized PDFs of the
+coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
+(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
+%
+The bottom panel shows the joint posterior obtained by combining both events.
+%
+We see, for both events, the $N_{\rm max} = 0$ posteriors are
+characterized by a peak away from zero.
+%
+This does not mean that we are inferring a deviation from GR.
+%
+We recall that the deviations from GR in the ParSpec framework are controlled
+by the dimensionless parameter $\gamma$, which here reads,
+%
+\begin{equation}
+    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M^{\rm s}_{\rm f}}\right)^4\,.
+    \label{eq:def_gamma_gb}
+\end{equation}
+%
+As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm EdGB}$ does indeed have a posterior
+distribution with largest support at zero, indicating consistency between
+the underlying signal and GR.
+%
+We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
+displaces the posteriors distributions towards smaller values of $\ell_{\rm EdGB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
+and larger values of $\gamma_{\rm EdGB}$ (see Fig.~\ref{fig:gamma_gb}).
+
+\begin{figure}[h]
 \includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
@@
 \end{figure}
-
-We start with EdGB gravity.
-%
-In Fig.~\ref{fig:edgb_exec_sum} we show the marginalized PDFs of the
-coupling constant $\ell_{\rm GB}$, for GW150914 (top panel) and GW200129
-(middle panel), with and without the spin corrections to the $(2,2,0)$ QNM.
-%
-The bottom panel shows the joint posterior obtained by combining both events.
-%
-We see, for both events, the $N_{\rm max} = 0$ posteriors are
-characterized by a peak away from zero.
-%
-This does not mean that we are inferring a deviation from GR.
-%
-We recall that the deviations from GR in the ParSpec framework are controlled
-by the dimensionless parameter $\gamma$, which here reads,
-%
-\begin{equation}
-    \gamma_{\rm EdGB} = \left(\frac{c^2 \ell_{\rm EdGB}}{ G M^{\rm s}_{\rm f}}\right)^4\,.
-    \label{eq:def_gamma_gb}
-\end{equation}
-%
-As shown in Fig.~\ref{fig:gamma_gb}, $\gamma_{\rm EdGB}$ does indeed have a posterior
-distribution with largest support at zero, indicating consistency between
-the underlying signal and GR.
-%
-We also observe that the inclusion of the spin corrections (i.e., the curves with $N_{\rm max} = 1$)
-displaces the posteriors distributions towards smaller values of $\ell_{\rm EdGB}$ (see Fig.~\ref{fig:edgb_exec_sum}),
-and larger values of $\gamma_{\rm EdGB}$ (see Fig.~\ref{fig:gamma_gb}).
 
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
 \includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
@@
 %
-We find that we cannot place any constraint on $\ell_{\rm EdGB}$ with our waveform model from either GW event.
+We find that we cannot place any bound on $\ell_{\rm EdGB}$ with our waveform model from either GW event.
 }
@@
 %
-For the cubic EFT, we use their Eq.~(67), particularizing \ab{it} to $\lame = \lamo = 1$.
-%
-We further linearize that equation in $\chi$ and \sout{particularize} \ab{consider} $m=2$.
-%
-This process, shows that the mode labeled ``-'' is the least-damped \ab{mode}, and it is the one we use.
+For the cubic EFT, we use their Eq.~(67), particularizing it to $\lame = \lamo = 1$.
+%
+We further linearize that equation in $\chi$ and consider the harmonic $m=2$.
+%
+This process, shows that the mode labeled ``-'' is the least-damped mode, and it is the one we use.
 %
@@
 %
-\ab{This time we} then find \sout{this time} that $p_{\rm qEFT} = 6$,
+This time we then find that $p_{\rm qEFT} = 6$,
 %

### 2022-04-26 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small changes

@@
 two GW detectors are needed to set statistically significant bounds, and tests of the remnant properties~\cite{Meidam:2014jpa,Carullo:2018sfu,Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui}
-during the post-merger stage. So far, none of these null tests have reported any deviation from GR.
+during in the post-merger. So far, none of these null tests have reported any deviation from GR.
 
@@
 contribution), with magnitude proportional to the difference between the
-charges of binary components. This makes EdGB gravity testable with present GW
+charges of binary components. This makes EdGB gravity testable with GW
 observations of compact binaries where at least one component is a BH.
 %
-More specifically, Ref.~\cite{Lyu:2022gdr} placed the bound
+Indeed, Ref.~\cite{Lyu:2022gdr} placed the bound
 %
@@
 %
-The coupling between scalar field and the Gauss-Bonnet invariant, which
-result in a coupling between scalar perturbations and gravitational
-perturbations of polar parity can, for example break the equivalence
+The coupling between scalar field and the Gauss-Bonnet invariant,
+results in a coupling between scalar perturbations and gravitational
+perturbations of polar parity which, for instance, breaks the equivalence
 between the QNM spectra of polar and axial gravitational perturbations~\cite{Glampedakis:2017rar,Lenzi:2021njy}
-(i.e., the isospectrality~\cite{Chandrasekhar:1985kt}) for Schwarzschild BHs in GR.
+(i.e., the isospectrality~\cite{Chandrasekhar:1985kt}) of Schwarzschild BHs in GR.
 
@@
 %
-The Pontryagin density by itself, $\int \dV {}^{*}RR$, is a boundary
+The variation of the Pontryagin density is a boundary
 term that does not contribute to the field equations in
@@
 %
-The Pontryagin density can, however, modify the field equation when coupled to $\vartheta$;
+However, the Pontryagin density can modify the field equations when coupled to $\vartheta$;
 the strength of the coupling set by $\ell_{\rm dCS}$, with dimensions of length.
@@
 in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}. We mark
-with vertical lines theh $90\%$ upper credible intervals.}
+with vertical lines the $90\%$ upper credible intervals.}
 \label{fig:edgb_exec_sum}
@@
 which is a major facility fully funded by the NSF.
-%
 
@@
 and the Virgo Collaboration, and Zenodo (https://zenodo.org/record/5172704).
-%
 
@@
 tells us in our ringdown analysis and the results of Ref.~\cite{Pierini:2021jxd} are our best guide
-available presently.}
+presently available.}
 % \abcomm{$\ell_{\rm EdCS}^4$?}.
@@
 %
-For the cubic EFT, we use their Eq.~(67), particularizing it to $\lame = \lamo = 1$.
-%
-We further linearize that equation in $\chi$ and consider the harmonic $m=2$.
-%
-This process, shows that the mode labeled ``-'' is the least-damped mode, and it is the one we use.
+For the cubic EFT, we use their Eq.~(67), in the particular case of $\lame = \lamo = 1$.
+%
+%
+We then linearize the resulting expression in $\chi$ and consider $m=2$ the harmonic.
+%
+\hscomm{Instead calling them ``$+$'' and ``$-$'' following the notation used in~\cite{Cano:2021myl},
+I call them axial/polar to follow our conventions.}
+%
+As an outcome, we find that the fundamental axial-parity QNM is the least damped one, and it is
+the one we use.
 %
@@
 %
-In this case we find that both modes (``-'' and ``+'' in the notation of Ref.~\cite{Cano:2020cao}) make the
-fundamental QNM damp fast, and we choose the ``-'' mode which decreases less the damping time. \abcomm{Not clear.
+In this case we find that both modes (``$-$'' and ``$+$'' in the notation of Ref.~\cite{Cano:2020cao}) make the
+fundamental QNM damp fast, and we choose the ``$-$'' mode which decreases less the damping time. \abcomm{Not clear.
 Decreases less with respect to what? Do you mean it has a smaller damping time?}

### 2022-04-26 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
cleaning eft appendix

@@
 
-The theory admits as a solution, the garden-variety Schwarzschild BH of GR.
+The theory admits as a solution the garden-variety Schwarzschild BH of GR.
 This is not the case when rotation is included and the Kerr metric is not a
@@
 %
-by folding data from the X-ray observations of the isolated NS
+by folding data from the X-ray observations of the pulsar
 PSR~J0030+0451~\cite{Lommen:2000yt,NANOGrav:2017wvv} by
@@
 NS GW170817~\cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki}, using
-equation-of-state independent relations between the NS moment of inertia and tidal deformability~\cite{Yagi:2013bca,Yagi:2013awa,Gupta:2017vsl}.
+equation-of-state independent relations between NS moment of inertia and tidal deformability~\cite{Yagi:2013bca,Yagi:2013awa,Gupta:2017vsl}.
 
@@
 perturbations couple to gravitational perturbations of axial parity, in contrast
-with EdGB gravity.
-%
-This leads to a breakdown of isospectrality. The QNM spectra of slowly-rotating BHs in dCS gravity was
-studied in Ref.~\cite{Srivastava:2021imr,Wagle:2021tam}.
+with EdGB gravity, resulting in a breakdown of isospectrality.
+%
+The QNM spectra of slowly-rotating BHs in dCS gravity was
+studied in Refs.~\cite{Srivastava:2021imr,Wagle:2021tam}.
 %
@@
     L^{(6)} &= \lame R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} R_{\gamma \delta}{}^{\mu\nu}
-    + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu}\,,
+    + \lamo R_{\mu\nu}{}^{\rho\sigma} R_{\rho\sigma}{}^{\gamma\delta} \tilde{R}_{\gamma \delta}{}^{\mu\nu},
     \label{eq:s_6}
@@
     + \varepsilon_{2} \tilde{\mathcal{C}}^{2}
-    + \varepsilon_{3} \mathcal{C} \tilde{\mathcal{C}}\,,
+    + \varepsilon_{3} \mathcal{C} \tilde{\mathcal{C}},
 \label{eq:s_8}
@@
 \hline
-$\omega^{(0)}_{220}$    & 0.3737                    \\
-$\tau^{(0)}_{220}$      & 11.2407                   \\
-$\omega^{(1)}_{220}$    & 0.1258                    \\
-$\tau^{(1)}_{220}$      & 0.2522                    \\
+$\omega^{(0)}$    & 0.3737                    \\
+$\tau^{(0)}$      & 11.2407                   \\
+$\omega^{(1)}$    & 0.1258                    \\
+$\tau^{(1)}$      & 0.2522                    \\
 \hline
@@
 \hline
-$\delta\omega^{(0)}_{220}$    & 0.0107                                               & 3.1964                   & $-$0.5813                     & $-$0.2114                       \\
-$\delta\tau^{(0)}_{220}$      & 0.0044                                               & 6.3619                   & $-$0.2114                     & $-$0.6070                       \\
-$\delta\omega^{(1)}_{220}$    & $-$0.2480                                            & 41.199                   & $-$3.8620                     & $-$1.5263                       \\
-$\delta\tau^{(1)}_{220}$      & $-$1.1010                                            & 794.66                   & 265.12                        & 171.35                          \\
+$\delta\omega^{(0)}$    & 0.0107                                               & 3.1964                   & $-$0.5813                     & $-$0.2114                       \\
+$\delta\tau^{(0)}$      & 0.0044                                               & 6.3619                   & $-$0.2114                     & $-$0.6070                       \\
+$\delta\omega^{(1)}$    & $-$0.2480                                            & 41.199                   & $-$3.8620                     & $-$1.5263                       \\
+$\delta\tau^{(1)}$      & $-$1.1010                                            & 794.66                   & 265.12                        & 171.35                          \\
 \hline
@@
 the theories under consideration, can be found in Table~I of Ref.~\cite{Maselli:2019mjd}.
+%
+\hscomm{I added the values of $p$ to the column headers to keep both columns with the same number of rows. I also
+removed the subscript 220 because we already said we consider only this mode.}
 }
@@
 Because QNMs of rotating BHs in modified gravity theories are not known to
-all spin values, we can expect that the $j=1$ coefficients to be susceptible to
-changes as calculations beyond-leading order in spin are accomplished in the future.
+all spin values, we can expect that the $j=1$ coefficients to change as
+calculations beyond-leading order in spin are accomplished in the future.
 %
@@
 results using $\varepsilon = 1/2$, \hs{but we stress that there is no
-fundamental justification for using this cut off.}
+fundamental justification for this choice.}
 % %
@@
 %
-Having in mind that the hard cut-off $\varepsilon = 1/2$ is not fundamental, but to keep consistency
+\hs{Having in mind that the cut off $\varepsilon = 1/2$ is not fundamental, but to keep consistency
 across our analysis, our final result
@@
 %
-at 90\% credible level should be taken lightly.
+at 90\% credible level should be taken lightly.}
 %
@@
 in waveforms that can have a ringdown segment larger (sometimes seconds long)
-than the inspiral-plunge segment in the detectors frequency band, making the
+than the inspiral-plunge segment in the detectors' frequency band, making the
 parameter estimation challenging.
@@
 
-\begin{table}[h]
+\begin{table}[t]
 \begin{tabular}{l l c c c}
@@
     \nonumber \\
-    \delta \omega_{\rm cEFT}^{(1)} = -3.8620, \quad \delta \tau_{\rm cEFT}^{(1)} = 265.12.
+    \delta \omega_{\rm cEFT}^{(1)} = -3.8620, \quad \delta \tau_{\rm cEFT}^{(1)} = 265.12,
 \end{align}
+%
+for this theory.
 
@@
 %
-In this case we find that both modes (``$-$'' and ``$+$'' in the notation of Ref.~\cite{Cano:2020cao}) make the
-fundamental QNM damp fast, and we choose the ``$-$'' mode which decreases less the damping time. \abcomm{Not clear.
-Decreases less with respect to what? Do you mean it has a smaller damping time?}
+In this case we find that both axial and polar modes reduce the damping time
+of the fundamental QNM mode relative to GR.
+%
+Hence, we choose the axial-parity mode for this which reduction is the smallest.
+% \abcomm{Not clear.
+% Decreases less with respect to what? Do you mean it has a smaller damping time?}
 %
@@
     \nonumber \\
-    \delta \omega_{\rm qEFT}^{(1)} = -1.5263, \quad \delta \tau_{\rm qEFT}^{(1)} = 171.35.
+    \delta \omega_{\rm qEFT}^{(1)} = -1.5263, \quad \delta \tau_{\rm qEFT}^{(1)} = 171.35,
 \end{align}
 %
-As with the previous theories, the larger values of some of these parameters are compensated
-by the assumptions of weak coupling and small spin used to calculate the QNM frequencies.
-\
+for this theory.
+%
+As in the case of the previous theories, the large values of some of these
+coefficients are compensated by the assumptions of weak coupling and small spin
+used to calculate the QNM frequencies.
+
 \section{The estimation of  intrinsic binary parameters in General Relativity and modified theories of gravity}
@@
 \hs{Indeed, since \pSEOB{} introduces only minimal modifications to the
-inspiral and because the remnant BH parameters are estimated according GR
+inspiral and because the remnant BH parameters are estimated according to GR
 predictions, the fact that only small biases are introduced on $\Mf$ and $\chi_{\rm f}$

### 2022-04-26 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
updates to plots and fig captions

@@
 $\delta\omega^{(1)}$    & $-$0.2480                                            & 41.199                   & $-$3.8620                     & $-$1.5263                       \\
-$\delta\tau^{(1)}$      & $-$1.1010                                            & 794.66                   & 265.12                        & 171.35                          \\
+$\delta\tau^{(1)}$      & $-$1.1014                                            & 794.66                   & 265.12                        & 171.35                          \\
 \hline
@@
 \includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
-\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm cEFT}$ for
+\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the cubic EFT of GR.
+We show our results for
 GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
 %
-The colors distinguish different $N_{\rm max}$ in the spin expansion.
+The colors distinguish different $N_{\rm max}$ in the spin expansion and, once more, the vertical
+lines mark the 90\% upper credible intervals.
 }
@@
 \includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined_corrected.pdf}
-\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
-GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the quartic EFT of GR.
+We show our results for GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+As there, we mark with the vertical lines the 90\% upper credible intervals.
 }
@@
 \begin{equation}
-    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
+    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.1014.
 \end{equation}
@@
 %
-Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm dCS}^{4} / (M^4 \kappa)$, and thus
-%
-\begin{equation}
-    \kappa \zeta = (\ell_{\rm dCS} / M)^4 = \gamma_{\rm dCS},
-\end{equation}
-%
+Here $\kappa = 1/(16 \pi)$, $\zeta = \ell_{\rm dCS}^{4} / (M_{\rm s}^4 \kappa)$, thus
+$\kappa \zeta = \gamma_{\rm dCS}$ and
+% %
+% \begin{equation}
+%     \kappa \zeta = (\ell_{\rm dCS} / M^{\rm s})^4 = \gamma_{\rm dCS},
+% \end{equation}
+% %
 where $c_{i}$ (with $i=1, \dots, 6$) are fitting coefficients which can be found in

### 2022-04-26 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
some more edits

@@
 have placed a constraint on $\ell_{\rm th}$. First, as we have explained in Sec.~\ref{sec:review_theories}, all theories that we
-consider must be interpreted as an EFT, meaning that it should be
+consider must be interpreted as an EFT, meaning that they should be
 considered valid only below an energy scale, or equivalently, a length-scale.
@@
 %
+\hscomm{I commented out the 68\% results for consistency with the other sections.}
+%
 This means that with our model's assumptions and using the remnant's source mass $M_{\rm f}$ to set the
@@
 \begin{equation}
-\ell_{\rm dCS} \leqslant 42.6~\textrm{km}
+\ell_{\rm dCS} \leqslant 41.9~\textrm{km}
 \quad \textrm{at 90\% credible level},
@@
 %
-We also note that since the CDF grows fast in approximate domain $\varepsilon = [0.2, 0.4]$,
-that a stronger, albeit at lower credible level,
-%
-\begin{equation}
-\ell_{\rm dCS} \leqslant 37.4~\textrm{km}
-\quad \textrm{at 68\% credible level},
-\end{equation}
-%
-can also be placed, when $N_{\rm max}=0$.
+% We also note that since the CDF grows fast in approximate domain $\varepsilon = [0.2, 0.4]$,
+% that a stronger, albeit at lower credible level,
+% %
+% \begin{equation}
+% \ell_{\rm dCS} \leqslant 37.4~\textrm{km}
+% \quad \textrm{at 68\% credible level},
+% \end{equation}
+% %
+% can also be placed, when $N_{\rm max}=0$.
 
@@
 \begin{equation}
-\ell_{\rm dCS} \leqslant 36.6~\textrm{km}
+\ell_{\rm dCS} \leqslant 35.8~\textrm{km}
 % 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
-\quad \textrm{at 90\% credible level},
+\quad \textrm{at 90\% credible level}.
 \end{equation}
-%
-and
-%
-\begin{equation}
-\ell_{\rm dCS} \leqslant 29.1~\textrm{km}
-% ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
-\quad \textrm{at 68\% credible level},
-\end{equation}
-%
-when $N_{\rm max}=0$.
-%
+% %
+% and
+% %
+% \begin{equation}
+% \ell_{\rm dCS} \leqslant 28.8~\textrm{km}
+% % ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
+% \quad \textrm{at 68\% credible level},
+% \end{equation}
+% %
+% when $N_{\rm max}=0$.
+% %
 These stronger bounds are a consequence of the larger support for $\ell_{\rm dCS} \lessapprox 15$~km
@@
 ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
-$\mathfrak{m} = M_{\rm f}$ and $\varepsilon = 1/2$.
+$\mathfrak{m} = M_{\rm f}$, $\varepsilon = 1/2$\hs{, and $N_{\rm max} = 0$.}
 %
@@
 
-\begin{table}[t]
+\begin{table}[h]
 \begin{tabular}{l l c c c}
@@
 result correspond \hs{to 90\% credible values \emph{if} we allow for a more flexible cut-off $\varepsilon \lesssim 0.65$.
-However, the result is robust under the hard cut-off of $\varepsilon = 1/2$ at 65\% credible level.}
+However, the result is robust for the cut off $\varepsilon = 1/2$, at 65\% credible level.}
 }

### 2022-04-27 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small change

@@
 of slowly-rotating BHs, and found that for the axial gravitational-led modes the damping time increases, as we
-increase $\ell_{\rm dCS}$, at constant BH spin.
+increase $\ell_{\rm dCS}$, at constant, small BH spin.
 %

### 2022-04-27 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
minor changes before submissiion to the LSC

@@
 cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
-quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km\hs{$^{\ast}$} \\
+quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km~\footnote{We notice that our result for the quartic EFT of GR is only in marginal tension with our hard cut-off scale for the
+validity of the theory, and hence we do still quote it here (see Secs.~\ref{sec:remarks} and~\ref{sec:results_qeft}
+for details).}
+\\
 \hline \hline
@@
 They were obtained combining Bayesian-inference results from GW150914 and GW200129.
-Current constraints on $\ell_{\rm th}$ are also listed.
-%
-\hs{Our result for the quartic EFT of GR is only in marginal tension with our hard cut-off scale for the
-validity of the theory and hence we do still quote it here. See Secs.~\ref{sec:remarks} and~\ref{sec:results_qeft}
-for details.}
-}
+Current constraints on $\ell_{\rm th}$ are also listed.}
 \label{tab:bound_summary}
@@
 % $\ell_{\rm EdGB} \leqslant 1.33$~km
-\hs{$\ell_{\rm EdGB} \leqslant 7.1$~km}
+$\ell_{\rm EdGB} \leqslant 7.1$~km
 %
@@
 % $\ell_{\rm EdGB} \leqslant 1.7$~km,
-\hs{$\ell_{\rm EdGB} \leqslant 9.1$~km},
+$\ell_{\rm EdGB} \leqslant 9.1$~km,
 %
 by stacking the posteriors of $\ell_{\rm EdGB}$ from a selection of BBHs
-from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}\footnote{\hs{These bounds
+from the GWTC-1 and GWTC-2 catalogs~\cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl}\footnote{These bounds
 are, strictly speaking, valid only when the scalar field $\varphi$ is small (i.e., $\varphi \ll 1$), and
-take into account only the leading-order scalar field interaction arising from the original dilatonic coupling, i.e.,
-$f(\varphi) \approx \varphi$ in Eq.~\eqref{eq:action_sgb}.
+they take into account only the leading-order scalar field interaction arising from the original dilatonic coupling 
+(i.e., $f(\varphi) \approx \varphi$ in Eq.~\eqref{eq:action_sgb}).
 This results in what is often referred to as shift-symmetric scalar-Gauss-Bonnet theory.
 In this theory, NSs do not have scalar monopole charge~\cite{Yagi:2015oca}, while BHs do~\cite{Yunes:2011we,Sotiriou:2013qea,Sotiriou:2014pfa}.
-Finally, we take note constant $\alpha_{\rm EdGB}$ used in Refs.~\cite{Yagi:2011xp,Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} is related to $\ell_{\rm EdGB}$ as $\ell_{\rm EdGB} = 4 \pi^{1/4} |\alpha_{\rm EdGB}|^{1/2}$.
-\hscomm{I had to translate between notations and rewrote the bounds quoted for $\alpha_{\rm EdGB}$ in terms of our $\ell_{\rm EdGB}$.}
-}}.
+Finally, we note that the constant $\alpha_{\rm EdGB}$ used in Refs.~\cite{Yagi:2011xp,Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} is related to $\ell_{\rm EdGB}$ as $\ell_{\rm EdGB} = 4 \pi^{1/4} |\alpha_{\rm EdGB}|^{1/2}$.}.
 Secondly, the scalar field influences the response of BHs to linearized perturbations and thus
@@
 were first computed in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn}
-and were extended \hs{(in the polar sector)} to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
+and were extended (in the polar sector) to leading-order in BH spin in Ref.~\cite{Pierini:2021jxd}.
 %
@@
     \left[
-    \hs{\tfrac{1}{16\pi}} R - \tfrac{1}{2}(\partial \vartheta)^2
+    \tfrac{1}{16\pi}\, R - \tfrac{1}{2}(\partial \vartheta)^2
     + \tfrac{1}{4} \ell^{2}_{\rm dCS} \, \vartheta \, {}^{*}RR
@@
 %
-We summarize each theory we have considered together with: the exponent $p$ at
+We summarize each theory we consider together with: the exponent $p$ at
 which their QNM-modification enters, the corresponding modifications to the
@@
 %
-We also included for comparison the GR coefficients, up to $j=1$, obtained in Ref.~\cite{Maselli:2019mjd}.
+We also include for comparison the GR coefficients, up to $j=1$, obtained in Ref.~\cite{Maselli:2019mjd}.
 %
@@
 %
-\hscomm{I added the values of $p$ to the column headers to keep both columns with the same number of rows. I also
-removed the subscript 220 because we already said we consider only this mode.}
 }
@@
 Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr} we quote our final
-results using $\varepsilon = 1/2$, \hs{but we stress that there is no
-fundamental justification for this choice.}
+results using $\varepsilon = 1/2$, but we stress that there is no
+fundamental justification for this choice.
 % %
@@
 %
-\hscomm{I commented out the 68\% results for consistency with the other sections.}
-%
 This means that with our model's assumptions and using the remnant's source mass $M_{\rm f}$ to set the
@@
 ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
-$\mathfrak{m} = M_{\rm f}$, $\varepsilon = 1/2$\hs{, and $N_{\rm max} = 0$.}
+$\mathfrak{m} = M_{\rm f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$.
 %
@@
 %
-\hs{Having in mind that the cut off $\varepsilon = 1/2$ is not fundamental, but to keep consistency
+Having in mind that the cut off $\varepsilon = 1/2$ is not fundamental, but to keep consistency
 across our analysis, our final result
@@
 %
-at 90\% credible level should be taken lightly.}
+at 90\% credible level should be taken lightly.
 %
@@
 We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
-can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at \hs{68\% credibility}.
+can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 68\% credibility.
 }
@@
 combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$. The quoted
-result correspond \hs{to 90\% credible values \emph{if} we allow for a more flexible cut-off $\varepsilon \lesssim 0.65$.
-However, the result is robust for the cut off $\varepsilon = 1/2$, at 65\% credible level.}
+result correspond to 90\% credible values \emph{if} we allow for a more flexible cut-off $\varepsilon \lesssim 0.65$.
+However, the result is robust for the cut off $\varepsilon = 1/2$, at 65\% credible level.
 }
@@
 In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
-of the \hs{dominant \emph{axial} gravitational-led} mode increases as the length-scale
+of the dominant \emph{axial} gravitational-led mode increases as the length-scale
 $\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
@@
 %
-\hs{The spin-corrections to the \emph{polar} gravitational-led modes
-were calculated in Ref.~\cite{Pierini:2021jxd} [see, in particular, their Eqs.~(51)
-and~(52).]
+The spin-corrections to the \emph{polar} gravitational-led modes
+were calculated in Ref.~\cite{Pierini:2021jxd} (see, in particular, their Eqs.~(51)
+and~(52)).
 %
@@
 We still do so, simply to explore what the rotational corrections to EdGB gravity QNMs \emph{might}
-tells us in our ringdown analysis and the results of Ref.~\cite{Pierini:2021jxd} are our best guide
-presently available.}
+tells us in our ringdown analysis and the results of Ref.~\cite{Pierini:2021jxd} are our best 
+presently available guide.  
 % \abcomm{$\ell_{\rm EdCS}^4$?}.
@@
 %
-\hscomm{Instead calling them ``$+$'' and ``$-$'' following the notation used in~\cite{Cano:2021myl},
-I call them axial/polar to follow our conventions.}
-%
 As an outcome, we find that the fundamental axial-parity QNM is the least damped one, and it is
@@
 %
-\hs{Indeed, since \pSEOB{} introduces only minimal modifications to the
-inspiral and because the remnant BH parameters are estimated according to GR
-predictions, the fact that only small biases are introduced on $\Mf$ and $\chi_{\rm f}$
-is, to some extend, expected.}
+Indeed, since \pSEOB{} introduces only minimal modifications to the plunge-merger 
+and because the remnant BH parameters are estimated according to GR
+predictions using the binary's component masses and spins, the fact that only small 
+biases are introduced on $\Mf$ and $\chi_{\rm f}$ is, to some extend, expected. 
 %

### 2022-04-27 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
tried to fix table footnote

@@
                longbibliography]{revtex4-1}
-
+\usepackage[flushleft]{threeparttable}
 \usepackage{epsfig}
@@
 \begin{table}[t]
+\begin{threeparttable}
 \begin{tabular}{c | c c}
@@
 cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
-quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km~\footnote{We notice that our result for the quartic EFT of GR is only in marginal tension with our hard cut-off scale for the
-validity of the theory, and hence we do still quote it here (see Secs.~\ref{sec:remarks} and~\ref{sec:results_qeft}
-for details).}
+quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km~\tnote{a}
 \\
@@
 Current constraints on $\ell_{\rm th}$ are also listed.}
+\begin{tablenotes}
+\item[a]{\footnotesize We notice that our result for the quartic EFT of GR is only in marginal tension with our hard cut-off scale for the
+validity of the theory, and hence we do still quote it here (see Secs.~\ref{sec:remarks} and~\ref{sec:results_qeft}
+for details)}
+\end{tablenotes}
 \label{tab:bound_summary}
+\end{threeparttable}
 \end{table}

### 2022-05-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: implemented Anuradha Gupta`s comments

@@
 two GW detectors are needed to set statistically significant bounds, and tests of the remnant properties~\cite{Meidam:2014jpa,Carullo:2018sfu,Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui}
-during in the post-merger. So far, none of these null tests have reported any deviation from GR.
+\redsout{during} \hs{in the post-merger}. So far, none of these null tests have reported any deviation from GR.
 
@@
 validity of the theory, and hence we do still quote it here (see Secs.~\ref{sec:remarks} and~\ref{sec:results_qeft}
-for details)}
+for details)\hs{.}}
 \end{tablenotes}
@@
 %
-where $p_j(\ell_{\rm th} | \mathcal{H})$ are the priors used for each observation, and $p(\ell_{\rm th} | \mathcal{H})$ is an overall prior.
+where $p_j(\ell_{\rm th} | \mathcal{H})$ are the priors used for each observation, \redsout{and} $p(\ell_{\rm th} | \mathcal{H})$ is an overall prior\hs{, and we assume that the value of $\ell_{\rm th}$ is shared among all events.}
 %
@@
 outline the main results. Whenever possible, we also combine results from
-multiple events to obtain the strongest possible bound on $\ell_{\rm th}$.
+\redsout{multiple} \hs{both} events to obtain the strongest possible bound on $\ell_{\rm th}$.
 
@@
 For completness, in Appendix~\ref{app:big_contour} we also
-show how all other intrinsic parameter parameters remain unbiased.
+show how all other intrinsic \redsout{parameter} parameters remain unbiased.
 

### 2022-05-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: cleaned commented out text / comments

@@
 \usepackage{microtype}
-
-% \usepackage{tikz}
 
@@
 
-% HS: temporary title. Feel free to add suggestions
 \title{Black-hole ringdown as a probe of higher-curvature gravity theories}
@@
 %
-% $\ell_{\rm EdGB} \leqslant 1.33$~km
 $\ell_{\rm EdGB} \leqslant 7.1$~km
@@
 %
-% $\ell_{\rm EdGB} \leqslant 1.7$~km,
 $\ell_{\rm EdGB} \leqslant 9.1$~km,
@@
 the strength of the coupling set by $\ell_{\rm dCS}$, with dimensions of length.
-%
-% However, a coupling with $\vartheta$ can modify the field equations.
-% %
-% The coupling strength is set by the coupling constant $\ell_{\rm dCS}$, with
-% dimensions of length.
 
@@
 luminosity distance $D_L$,
-% \abcomm{I changed to capital $d$ because later we call the
-% data ``d''.},
 right ascension $\alpha$ and declination $\delta$,
@@
 harmonics.
-%
-% --------------------------------
-% HS: maybe not necessary anymore:
-% \footnote{Note that we use $l$ to denote the angular dependence index and $\ell$ to denote the coupling constant in Sec.~\ref{sec:review_parspec}.}
-% --------------------------------
 %
@@
 %
-%\ag{Going back to the convention established above to use the index $k$ to now denote the $(l, m,0)$
-%mode,  the frequencies $\omega_k$ and damping times $\tau_k$ can be read off from the
-%real and imaginary parts of $\sigma_k$ respectively.}
-%
 The functions $\tilde{A}_{l m}(t)$ and $\tilde{\phi}_{l m}(t)$ are defined
@@
 We detail our results in Sec.~\ref{sec:results}.
-%
-% \hs{Alessandra, Abhirup, should we call this waveform differently to distinguish it from your previous papers?}
-%
-%In this paper, we will restrict ourselves to the $k=(2,2,0)$ QNM and corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
-Assuming a prior which is uniform on the beyond-GR parameters, $(\ell, \{\delta \omega_k^{(j)}\},\{\delta \tau_k^{(j)}\})$, we employ a Bayesian framework to stochastically sample over the parameter space using the \texttt{LALInference} algorithm.~\cite{lallsuite}.
-%
-%The bounds on these beyond-GR parameters, for specific cases of modified gravity theories outlined in Sec.~\ref{sec:review_theories}, are detailed in Sec.~\ref{sec:results}.
 
@@
 \begin{table*}[t]
-% \begin{tabular}{c | c c c c c c c c c c}
-% \hline
-% \hline
-% Theory      & $\omega^{(0)}_{220}$ & $\tau^{(0)}_{220}$ & $\omega^{(1)}_{220}$ & $\tau^{(1)}_{220}$ & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.
-\\
-% \hline
-% GR          & 0.3737               & 11.2407            &  0.1258              & 0.2522             & --  & --                          & --                        & --                          & --                        & \cite{Maselli:2019mjd} \\
-% \hline
-% EdGB        & --                   & --                 &  --                  & --                 & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
-% dCS         & --                   & --                 &  --                  & --                 & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
-% cubic EFT   & --                   & --                 &  --                  & --                 & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
-% quartic EFT & --                   & --                 &  --                  & --                 & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
-% \hline
-% \hline
-% \end{tabular}
-%
 \begin{tabular}{c | c }
@@
 \end{figure}
-
-% \begin{table*}[th]
-% \begin{tabular}{c | c c c c c c c c}
-% \hline
-% \hline
-% Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
-% \hline
-% EdGB      & 4 & 0.0107 & 0.0044 & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
-% dCS       & 4 & 3.1964 & 6.3619 & 41.199 & 794.66 &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm CS} \leqslant 34.5$~km \\
-% cEFT  & 4 & -0.5813  & 2.6469 & -3.8620 & 265.12 & \cite{Cano:2021myl} & \dots  & \dots \\
-% qEFT  & 6 & \dots  & \dots & \dots & \dots & \cite{Cano:2021myl} & $\ell_{\rm qEFT} = \dots$~km~\cite{Sennett:2019bpc}  & \dots \\
-% \hline
-% \hline
-% \end{tabular}
-% \caption{Summary of the quasinormal modes calculations.
-% %
-% We summarize each theory we have considered together with: the exponent $p$ at
-% which their QNM-modification enters, the corresponding modifications to the
-% oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
-% references from which we used the results from and the current best constraint
-% (if applicable).
-% %
-% In these cases, the dimensionless parameters $\lambda_{\rm e,o}$ are degenerate
-% with the length scale $\ell$.
-% %
-% }
-% \label{tab:ref_theories_qnms}
-% \end{table*}
 
@@
 GR become relevant in each of the theories described in
-Sec.~\ref{sec:review_theories}. %Hence,
-%
-%\begin{equation}
-%\bm{\lambda} = \{\ell\} \cup \{\bm{\theta}\}.
-%\label{eq:def_params}
-%\end{equation}
-
-% As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
-% constants in the cases of EdGB and dCS theories, but two in the cubic and
-% quartic EFTofGR.
-% %
-% We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
-% fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
-% %
+Sec.~\ref{sec:review_theories}.
 
@@
 $\mathcal{H}$.
-%
-%In some cases, we found it necessary to work with different prior ranges across
-%different events, within the context of a given theory.
-%
-%In this situation, when combining the posteriors we use chose as our overall
-%prior the widest one among the individual events.
 
@@
 $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes\footnote{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior.}}.
-%
-%The prior on $t_0$ is uniform and its range is informed by our detection pipelines.
 
@@
 We assume an uniform prior on $\ell_{\rm th}$ between appropriate ranges.
-% \sout{, say $\ell_{\rm th} \in [0, \ell_{\rm max}]$}.
 %
@@
 generality.
-%
-%The upper limit is chosen as to make sure that our marginalized posterior
-%distributions on $\ell$ do not rail against $\ell_{\rm max}$.
 
@@
 the analyses in Ref.~\cite{LIGOScientific:2021sio}.
-%
-%The only difference between the sampling configurations is that we do not
-%sample over the fractional deviations in the $(220)$ QNM frequencies and
-%damping times, but instead on $\ell$ while holding $\{\delta \omega_k^{(j)}\},$
-%and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions, summarized
-%in Table~\ref{tab:ref_theories_qnms}.
-%
 
@@
 fundamental justification for this choice.
-% %
-% In Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}, $\varepsilon = 1/2$ was used,
-% but here we explore $\varepsilon \in [0, 1]$ for generality.
-% %
 
@@
 \begin{equation}
-% \textrm{CDF}(\ell) \leqslant \textrm{CDF}(T_{\rm EFT}(\varepsilon; \, \mathfrak{m})).
 P(\ell_{\rm th} \leqslant \Lambda_{\rm EFT} | d) \leqslant 0.9,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% ----------------------------------------------------------
-% \hs{Convention: us 90\% credibility for the final bounds.}
-% ----------------------------------------------------------
-
-% -----------------
-% Explain threshold
-% -----------------
-
-% \hs{Note to ourselves: as mentioned in~\cite{Maselli:2019mjd}:
-% %
-% ``As customary in parametrized approaches, we focus on perturbative corrections by assuming $\gamma_{i} \delta \omega^{(n)} \ll 1$, $\gamma_{i} \delta \tau^{(n)} \ll 1$ and GR is recovered in the limit $\gamma_{i} \to 0$.''
-% We should check this \emph{in addition} to the small-coupling approximation to argue whether we placed a bound or not.
-% }
 
@@
 components.
-%
-% As we will next, the situation is the opposite for dCS gravity.
-
-% Let us place our results in a broader context. In particular, let us contrast
-% them against those of Ref.~\cite{Lyu:2022gdr} which placed the bound
-% %
-% $\ell_{\rm GB} \leqslant 1.33$~km
-% %
-% using the neutron star-black hole binaries GW200105 and GW200115~\cite{LIGOScientific:2021qlt}, and
-% of Refs.~\cite{Nair:2019iur,Perkins:2021mhb}, which placed the bound
-% %
-% $\ell_{\rm GB} \leqslant 1.7$~km,
-% %
-% by stacking the posterior of $\ell_{\rm GB}$ from a  selection of black hole binaries from the GWTC-1 and GWTC-2 catalogs
-% with at least one relatively low-mass binary component~\cite{}\footnote{These bounds
-% are, strictly speaking, valid only when the scalar field $\varphi$ is small, i.e., $\varphi \ll 1$, and
-% take into consideration only the leading-order scalar field contribution arising from the dilatonic coupling.}.
-% %
-% These works use the \emph{inspiral} portion of GW event only and a constraint
-% on EdGB gravity can be obtained because black holes in this theory carry a
-% monopole scalar charge which in turn can source dipolar scalar radiation,
-% that affects the GW phase at $-1$PN order, relative to the dominant GR contribution, and
-% is proportional to the difference between the charges of binary components.
-% %
-% Now, the magnitude of the scalar charge scales roughly with the inverse of the black hole's mass squared, that is,
-% smaller (larger) back holes carry large (smaller) scalar charges. Qualitatively, this is because the scalar field
-% is sourced by the Gauss-Bonnet curvature invariant, which is large for black holes with small masses.
-% %
-% Beyond-GR corrections to the inspiral are, by construction, not present in our
-% waveform model and constitutes a important ingredient to be added in forthcoming
-% versions of the model.
-% %
-% In addition to the larger mass (which suppresses the black hole's charge), the
-% QNM of EdGB gravity differ very little from GR as observed in~\cite{Blazquez-Salcedo:2016enn}.
-% %
-% Hence, here we have an example of a theory in which the inspiral portion of the signal
-% is more constraining then the ringdown portion of the signal.
-%
-% As we will next, the situation is the opposite for dCS gravity.
 
@@
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for dCS gravity.
-%
-% ~Posterior distribution function for the coupling constant $\ell_{\rm CS}$ for
-% GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-% %
-% In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
-% in spin QNM correction.
 %
@@
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for dCS gravity.
-% The cumulative distribution function evaluated at the
-% cut-off $\Lambda_{\rm EFT}(\varepsilon, \gm)$ as a function of the parameter $\varepsilon$ for both
-% $\gm = m_2$ (solid and dashed lines) and $\gm = M_{f}$ (dot-dashed and dotted lines) without
-% (blue lines) and with (orange lines) linear-in-spin QNM corrections.
-% The horizontal lines lay at 0.68 and 0.90.
 %
@@
 Finally, in the bottom panel, we show the combined result for both events.
-% \agcomm{Just a thought.  Since, Figs 3,6,8,10 and Figs.4,6,9,11 show the same basic thing,
-% should we have one description at the top of the section for each figure? We can follow this up
-% by what is special for each theory in each section? Currently, we are repeating a lot of the
-% language to describe these figures for each theory?}
 
@@
 observations alone}.
-%
-% We also note that since the CDF grows fast in approximate domain $\varepsilon = [0.2, 0.4]$,
-% that a stronger, albeit at lower credible level,
-% %
-% \begin{equation}
-% \ell_{\rm dCS} \leqslant 37.4~\textrm{km}
-% \quad \textrm{at 68\% credible level},
-% \end{equation}
-% %
-% can also be placed, when $N_{\rm max}=0$.
 
@@
 \ell_{\rm dCS} \leqslant 35.8~\textrm{km}
-% 43.9~\textrm{km}~( = \Lambda_{\rm EFT}(\tfrac{1}{2}, M_{f}) )
 \quad \textrm{at 90\% credible level}.
 \end{equation}
-% %
-% and
-% %
-% \begin{equation}
-% \ell_{\rm dCS} \leqslant 28.8~\textrm{km}
-% % ~( = \Lambda_{\rm EFT}(0.3, M_{f}) )
-% \quad \textrm{at 68\% credible level},
-% \end{equation}
-% %
-% when $N_{\rm max}=0$.
-% %
+%
 These stronger bounds are a consequence of the larger support for $\ell_{\rm dCS} \lessapprox 15$~km
@@
 \hline
-%       & GW150914 & Yes & Yes & $\ell_{\rm CS} \leqslant 46.5$~km \\
-% 0     & GW200129 & Yes & Yes & $\ell_{\rm CS} \leqslant 43.9$~km \\
-%       & Combined & Yes & Yes & \cellcolor{blue!10}$\ell_{\rm CS} \leqslant 34.5$~km \\
       & GW150914 & Yes & Yes & $\ell_{\rm dCS} \leqslant 41.9$~km \\
@@
 show how all other intrinsic \redsout{parameter} parameters remain unbiased.
-
-% \agcomm{This reference to Fig.2 appears misplaced here.
-IMO, Fig 2.
-has two purposes.
-1) to show that we do not need the high-spin version of the fits Carullo used, because our spin posteriors are well-localised around 0.7, and 2) to assure the reader that we were right in using the GR values of the final mass and spin in the ParSpec expansion, because introducing nonGR parameters has not ended up biasing our estimates of Mf-chif.
-I think both of these points can be addressed in the discussions section.
-That is also where we can put the other corner plot with the remaining intrinsic parameters.
-One side-advantage of this is that the figures would then also appear slightly later in the paper, as we had originally planned.}
-%
 
@@
     \ell_{\rm qEFT} \leqslant 51.3~\textrm{km},
-    %\quad \textrm{at 90\% credible level},
 \end{equation}
@@
 
-% We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
-% hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
-% %
-% As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_{\rm f}$ before $\varepsilon = 1/2$.
-% %
-% Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
-% %
-% \begin{equation}
-%     \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level}\,.
-% \end{equation}
-% %
-% % \abcomm{Please update the paragraph below.}
 In this theory, we have considered only $N_{\rm max} = 0$.
@@
 parameter estimation challenging.
-% \abcomm{The reference to 80 km comes out of the blue. Doesn't it? Why did you refer to it?}~\hscomm{That was the upper prior limit for the GW150914 run. I modified the text to explain this.}
-% for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
-% has some problems in English. I do not udnerstand it.}
 %
@@
   & Combined &     &      & \cellcolor{black!10}$\ell_{\rm qEFT} \leqslant 51.3$~km \\
-% \hline
-%   & GW150914 &  &     &    \\
-% 1 & GW200129 &  &     &    \\
-%   & Combined &  &     &    \\
 \hline
@@
 
-% \begin{figure}[t]
-% \includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
-% \caption{Posterior probability distribution on $\ell_{\rm CS}$ with GW200129.
-% The posterior shows that information was gained on this parameter relative to
-% the initial uniform prior distribution $\ell_{\rm CS} \in [0,\, 200]$~km.
-% %
-% The vertical lines represent two threshold for the validity of the theory as
-% an EFT.
-% %
-% The dotted line (labeled ``$m_2$'') at $\ell_{\rm CS} \approx 21.3$~km is
-% given by the median value of the secondary's mass $\varepsilon \, (G m_2 / c^2)$.
-% %
-% The dot-dashed line (labeled ``$M_{f}$'') at $\ell_{\rm CS} \approx 43.8$~km is
-% given by the median value of the remnant's mass $\varepsilon \, (G M_{f} / c^2)$.
-% %
-% For both, we used $\varepsilon = 0.5$.
-% %
-% If we take the latter as a length scale for the validity of dCS as an EFT, we
-% have place upper bound on $\ell_{\rm CS} \leqslant 43.8$~km, within the
-% approximation of our formalism.
-% }
-% \label{fig:dCS_bounds}
-% \end{figure}
-%
-% \begin{figure}[t]
-% \includegraphics[width=\columnwidth]{figs/dcs_gamma_GW200129.pdf}
-% \caption{Posterior probability distribution on $\gamma_{\rm CS}$ with GW200129.
-% The posterior shows that the parameter $\gamma$ [see Eq.~\eqref{eq:def_gamma}]
-% in dynamical Chern-Simons has a peak at zero, indicating consistency with GR.
-% }
-% \label{fig:dCS_gamma_plot}
-% \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 In contrast, we could not place any bounds on the fundamental length-scale
-% \abcomm{Maybe
-% this is common in the literature, but I would call it length-scale instead of coupling
-% constant. What do you think?}~\hscomm{I agree. I introduced ``length-scale'' at a few other place in the text.}
 of EdGB gravity $\ell_{\rm EdGB}$.
@@
 can result in different outcomes for different theories, even if they predict the same value of $p$.
-
-% HS: changed my mind -- I think it would divert from the original flow.
-% \hscomm{I will add a sentence here on Refs.~\cite{Alexander:2017jmt,Loutrel:2018ydv,Loutrel:2018rxs}.}
 
@@
 
-% \hscomm{TODO: say that we could try to expand the waveform model to include modification to
-% the inspiral part too; maybe through FTI~\cite{Mehta:2022pcn}?}
-
-% \hscomm{TODO: add that we could try to parametrize the final BH mass and spin estimates formulas we
-% use at the moment~\cite{Hofmann:2016yih}. Maybe comment that a possible first attempt could follow~\cite{Buonanno:2007sv},
-% as done in~\cite{Jai-akson:2017ldo,Li:2020wse}. Say that ultimately we will need to informed by NR in beyond-GR.}
-
-% HS: I did not add a comment on this, because of our discussion of how the N = 1 results will
-% not be "permanent" as the N = 0 one, until we have QNM results valid up to ~ 0.7
-% \hscomm{I suspect that by construction the $N_{\rm max} = 1$ cases will often fail to satisfy our
-% perturbative bounds. If so, add explanation here.}
-
-% ~\hscomm{This is a general `limitation' of ringdown test of higher-curvature theories in present detectors.
-% Point this out in the conclusions after all specific theories are discussed.}
-
-% \agcomm{Mention that we do not use the high-spin version of the fits, and refer to the
-% chif measurements Fig.~\ref{fig:corner_plot} (which should be near the text here).}
-
-% HS: done
-% \agcomm{Mention that our alternate ringdown formalism does not bias estimates of GR quantities
-% and refer to Fig.~\ref{fig:corner_plot_all}}
-
-% \sout{Our work shows that, with the GW signals so far observed by the LVK Collaboration,
-% there are theories of gravity (such as dCS) that can be unconstrained by studying the
-% inspiral portion of GW events, {\it yet} {it} can be constrained, if we analyze the ringdown.}
-% %
-% \sout{Our results show that to fulfill the potential to test GR with \ab{future} GW observations,
-% further work \ab{is needed} on modeling \sout{of} the late-inspiral-(plunge)-merger and ringdown of
-% coalescing BHs  (with NR simulations) and, complementary,}
-% %
-% \sout{We hope that our results can also serve as further motivation to address these
-% outstanding problems.}
-
-% -----------------------------------------------------------------------------
-% \hs{Say that the fact we spin correction look important reinforces the
-% importance of calculation QNMs of spinning black holes beyond-GR.}
-%
-% \hs{Say it is important to go beyond mode calculation and actually understand
-% how the QNM appear in the GW signal.}
-% -----------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------------
-% HS: we fixed p in our work. We could leave it free in future studies study.
-% This is similar to the 'number of dimensions'-like studies. Here it would
-% tells us quite generically what is the dimension of the modification to the
-% EH-action we include!
-% ------------------------------------------------------------------------------------
-
 % --------------------------
@@
 Refs.~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} to determine the ParSpec coefficients for this theory.
-% and~\cite{Pierini:2021jxd} for the QNMs of for which the QNMs of nonrotating and
-% slowly-rotating BHs where calculated in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk}
-% and~\cite{Pierini:2021jxd}, respectively.
 %
@@
 %
-% for consistency, we only consider the leading-order $j=0$ coefficients in EdGB gravity.}
-%
 For the nonrotating QNMs we use
-% HS: I agree.
-% \abcomm{We are using present tense when
-% describing results in the paper, so I would suggest with stick with that consistently
-% in the Appendix.}
 the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
@@
 %
-% <<<<<<< HEAD
 The small values of the numerical prefactors of $\gamma_{\rm EdGB}$ are a consequence of the how weakly the QNMs
-% =======
-% The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ \abcomm{the term above
-% is linear not quartic in $\gamma_{\rm EdGB}$. Do you mean $\ell_{\rm EdGB}^4$?}
-% are a consequence of \sout{the} how weakly the QNMs
-% >>>>>>> 72e1d3e2d4db50f80c67fc8bc13cab1708d40edb
 of BHs in EdGB gravity deviate from their GR counterparts, even at moderately large values of $\gamma_{\rm EdGB} \approx 0.3$.
 
-% \hscomm{There was an error here: I mixed the axial QNMs we used for the nonrotating coefficients, with the polar QNMs
-% for which the spin-corrections were computed. Because it is inconsistent, I suggest changing opening paragraph with the highlighted text,
-% and then remove the $N_{\rm max} = 1$ results from our EdGB plots. What do you think?}
-%
 The spin-corrections to the \emph{polar} gravitational-led modes
@@
 presently available guide.
-% \abcomm{$\ell_{\rm EdCS}^4$?}.
-
-% \hscomm{Could remove this part until the end of this section.}
-%
+
 We can expand the resulting formula in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
@@
 
-% Taken together, use as our fitting expressions for the QNM is EdGB gravity
-% %
-% \begin{subequations}
-% \begin{align}
-%     M {\rm Re}(\sigma)_{\rm EdGB} &= {\rm Re}(\omega)_{\rm GR} \, \left[ 1 + 0.0107 (\ell_{\rm EdGB} / M)^4 \right],
-%     \\
-%     M {\rm Im}(\sigma)_{\rm EdGB} &= \dots % {\rm Im}(\omega)_{\rm GR} \, \left[ 1 - 0.0044 (\ell_{\rm EdGB} / M)^4 \right].
-% \end{align}
-% \end{subequations}
-%
-% \dots
-
 \subsection{Dynamical Chern-Simons gravity}
@@
 $\kappa \zeta = \gamma_{\rm dCS}$ and
-% %
-% \begin{equation}
-%     \kappa \zeta = (\ell_{\rm dCS} / M^{\rm s})^4 = \gamma_{\rm dCS},
-% \end{equation}
-% %
+%
 where $c_{i}$ (with $i=1, \dots, 6$) are fitting coefficients which can be found in
@@
 Hence, we choose the axial-parity mode for this which reduction is the smallest.
-% \abcomm{Not clear.
-% Decreases less with respect to what? Do you mean it has a smaller damping time?}
 %
@@
 
-% HS: I agree with all the changes below
 We show in Fig.~\ref{fig:corner_plot_all} a corner plot for all the intrinsic
@@
 of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.
-%
-%
-% %
-% \hscomm{Should we say that this happens almost by ``construction''? That would be because \pSEOB{} waveform changes very little the inspiral
-% and the final masses and spins are predicted according to a GR formula.}
 

### 2022-05-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: Gregorio Carullo`s comments

@@
 % General:
-The detection of gravitational waves produced by coalescing compact binaries
-allows us to explore the dynamical, nonlinear regime of general relativity
-and to constrain modifications to it.
+\redsout{The detection of gravitational waves produced by coalescing compact binaries
+allows}
+\hs{Detections of gravitational waves from coalescing compact binaries allow}
+us to explore \hs{into} the dynamical, nonlinear regime of general relativity
+and \redsout{to} constrain modifications to it.
 %
@@
 % Main question:
-Can we use the ringdown to constrain deviations to general relativity,
+Can we use the ringdown to constrain deviations \redsout{to} \hs{from} general relativity,
 as predicted by several of its contenders?
@@
 %
-We give a prescription on how to include in this waveform model the quasinormal mode frequencies
+We give a prescription on how to include in this waveform model\hs{,} the quasinormal mode frequencies
 calculated on a theory-by-theory basis. In particular, we focus on theories that modify
 general relativity by higher-order curvature corrections, namely,
-Einstein-dilaton-Gauss-Bonnet and dynamical Chern-Simons theories, and cubic- and quartic-order
+Einstein-dilaton-Gauss-Bonnet\hs{,} \redsout{and} dynamical Chern-Simons theories, and cubic- and quartic-order
 effective-field-theories of general relativity.
@@
 % Main conclusion:
-We confront the resultant waveform models against the two loudest
-gravitational-wave ringdown signals observed so far, notably, GW150914 and GW200129.
+\redsout{We confront the resultant waveform models against the two loudest}
+\hs{We use this parametrized waveform model to measure the ringdown properties of}
+the two loudests \redsout{gravitational-wave} ringdown signals observed so far, \redsout{notably,} GW150914 and GW200129.
 %
@@
 $\delta\omega^{(j)}$, and $\delta\tau^{(j)}$ parameters, and then proceeded
-to use the posteriors on $\ell_{\rm th}$ to draw conclusions to any theory that predict
-corrections at a given $p$.
-%
-This is a important difference between our work and Ref.~\cite{Carullo:2021dui}.
-In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
+to use the posteriors on $\ell_{\rm th}$
+\hs{, considering up to $j=2$ in
+the GR deformation coefficients, and remaining agnostic about the underlying
+theory which would predict the modifications to the QNMs.}
+%
+\redsout{to draw conclusions to any theory that predict\hs{s}
+corrections at a given $p$.}
+%
+\redsout{This is a important difference between our work and Ref.~\cite{Carullo:2021dui}.
+In particular, as we will see in Sec.~\ref{sec:results},}
+\hs{We will see in Sec.~\ref{sec:results} that} adding theory-specific
 information to the ParSpec coefficients \emph{can lead to different interpretations
@@
 %
+\hs{We also thank Anuradha Gupta and Gregorio Carullo for comments on this work.}
+%
 We are grateful for the computational resources provided by the Max Planck

### 2022-05-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
minor changes + new text regarding Carullo's

@@
 % General:
-\redsout{The detection of gravitational waves produced by coalescing compact binaries
-allows}
-\hs{Detections of gravitational waves from coalescing compact binaries allow}
-us to explore \hs{into} the dynamical, nonlinear regime of general relativity
-and \redsout{to} constrain modifications to it.
-%
-Some of these gravitational-wave events have sufficiently high
+Detecting gravitational waves from coalescing compact binaries allows  
+us to explore the dynamical, nonlinear regime of general relativity
+and constrain modifications to it.
+%
+Some of the gravitational-wave events observed by the LIGO-Virgo Collaboration have sufficiently high
 signal-to-noise ratio in the merger, allowing us to probe the relaxation of the remnant black
@@
 % Main question:
-Can we use the ringdown to constrain deviations \redsout{to} \hs{from} general relativity,
+Can we use the ringdown to constrain deviations from general relativity,
 as predicted by several of its contenders?
@@
 %
-We give a prescription on how to include in this waveform model\hs{,} the quasinormal mode frequencies
+We give a prescription on how to include in this waveform model, the quasinormal mode frequencies
 calculated on a theory-by-theory basis. In particular, we focus on theories that modify
 general relativity by higher-order curvature corrections, namely,
-Einstein-dilaton-Gauss-Bonnet\hs{,} \redsout{and} dynamical Chern-Simons theories, and cubic- and quartic-order
+Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons theories, and cubic- and quartic-order
 effective-field-theories of general relativity.
@@
 % Main conclusion:
-\redsout{We confront the resultant waveform models against the two loudest}
-\hs{We use this parametrized waveform model to measure the ringdown properties of}
-the two loudests \redsout{gravitational-wave} ringdown signals observed so far, \redsout{notably,} GW150914 and GW200129.
+We use this parametrized waveform model to measure the ringdown properties of 
+the two loudests ringdown signals observed so far, GW150914 and GW200129.
 %
@@
 mass of the graviton; tests of the polarization of gravitational radiation~\cite{Will:2014kxa}, for which more than
-two GW detectors are needed to set statistically significant bounds, and tests of the remnant properties~\cite{Meidam:2014jpa,Carullo:2018sfu,Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui}
-\redsout{during} \hs{in the post-merger}. So far, none of these null tests have reported any deviation from GR.
+two GW detectors are needed to set statistically significant bounds, and tests of the remnant properties~\cite{Meidam:2014jpa,Carullo:2018sfu,Brito:2018rfr,Carullo:2019flw,Isi:2019aib,Ghosh:2021mrv,Carullo:2021dui} in the post-merger stage.
+So far, none of these null tests have reported any deviation from GR.
 
@@
 validity of the theory, and hence we do still quote it here (see Secs.~\ref{sec:remarks} and~\ref{sec:results_qeft}
-for details)\hs{.}}
+for details).}
 \end{tablenotes}
@@
 %
-\redsout{to draw conclusions to any theory that predict\hs{s}
-corrections at a given $p$.}
-%
-\redsout{This is a important difference between our work and Ref.~\cite{Carullo:2021dui}.
-In particular, as we will see in Sec.~\ref{sec:results},}
 \hs{We will see in Sec.~\ref{sec:results} that} adding theory-specific
@@
 %
-where $p_j(\ell_{\rm th} | \mathcal{H})$ are the priors used for each observation, \redsout{and} $p(\ell_{\rm th} | \mathcal{H})$ is an overall prior\hs{, and we assume that the value of $\ell_{\rm th}$ is shared among all events.}
+where $p_j(\ell_{\rm th} | \mathcal{H})$ are the priors used for each observation, \redsout{and} $p(\ell_{\rm th} | \mathcal{H})$ is an overall prior, and we assume that the value of $\ell_{\rm th}$ is shared among all events.
 %
@@
 outline the main results. Whenever possible, we also combine results from 
-\redsout{multiple} \hs{both} events to obtain the strongest possible bound on $\ell_{\rm th}$.
+both events to obtain the strongest possible bound on $\ell_{\rm th}$.
 
@@
 by setting $p=4$, \emph{but not} including theory-specific QNM information on $\delta \omega^{(j)}$ and $\delta \tau^{(j)}$. 
+\ab{Furthermore, Ref.~\cite{Carullo:2021dui} did not impose the EFT and ParSpec bounds that we imposed.} 
 %
@@
 %
-\hs{We also thank Anuradha Gupta and Gregorio Carullo for comments on this work.}
+We also thank Anuradha Gupta and Gregorio Carullo for comments on this manuscript. 
 %

### 2022-05-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
add ref

@@
 Our last example of modified gravity theories are the so-called
-EFTs of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
+EFTs of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,AccettulliHuber:2020dal,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
 %

### 2022-05-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
minor changes

@@
 $\delta\tau^{(0)}$      & 0.0044                                               & 6.3619                   & $-$0.2114                     & $-$0.6070                       \\
-$\delta\omega^{(1)}$    & $-$0.2480                                            & 41.199                   & $-$3.8620                     & $-$1.5263                       \\
+$\delta\omega^{(1)}$    & $-$0.2480                                            & 41.199                   & 6.4439                        & $-$1.5263                       \\
 $\delta\tau^{(1)}$      & $-$1.1014                                            & 794.66                   & 265.12                        & 171.35                          \\
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
+\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined_corrected.pdf}
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the cubic EFT of GR.
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold.pdf}
+\includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold_corrected.pdf}
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for the cubic EFT of GR.

### 2022-05-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
trying to adjust fig locations

@@
 
-In Fig.~\ref{fig:example_waveform} we show an illustrative waveform for GR (solid line; using the \texttt{SEOBNR} model) and in the cubic EFT of gravity (dashed line; using the \pSEOB{} model),
-including the leading-order $j = 0$ deformations to the fundamental QNM (see Table~\ref{tab:ref_theories_qnms}).
-%
-We choose binary parameters similar to GW150914,  but non-spinning, with detector-frame masses
-$m_1 = 39\msun$ and $m_2 = 31\msun$.
-%
-The top panel shows the $+$ GW polarization $h_{+}$ in both theories,
-while the bottom panel shows the amplitude $|h| = (h_{+}^2 + h_{\times}^2)^{1/2}$
-and instantaneous frequency $f$, all as functions of time $t$.
-%
-The signals are identical up to the merger, specifically, the time $t_\textrm{match}$
-defined in Sec.~\ref{sec:review_pSEOB}, after which they differ during the ringdown.
-%
-By construction, the ringdown lasts longer for the cubic EFT of GR waveform and
-with a smaller instantaneous frequency (see the bottom panel) due to the negative value of the
-$\delta\omega^{(0)}$ coefficient in this theory.
-
-\begin{figure}[t]
+\begin{figure}[hb]
 \includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
@@
 \end{figure}
+
+In Fig.~\ref{fig:example_waveform} we show an illustrative waveform for GR (solid line; using the \texttt{SEOBNR} model) and in the cubic EFT of gravity (dashed line; using the \pSEOB{} model),
+including the leading-order $j = 0$ deformations to the fundamental QNM (see Table~\ref{tab:ref_theories_qnms}).
+%
+We choose binary parameters similar to GW150914,  but non-spinning, with detector-frame masses
+$m_1 = 39\msun$ and $m_2 = 31\msun$.
+%
+The top panel shows the $+$ GW polarization $h_{+}$ in both theories,
+while the bottom panel shows the amplitude $|h| = (h_{+}^2 + h_{\times}^2)^{1/2}$
+and instantaneous frequency $f$, all as functions of time $t$.
+%
+The signals are identical up to the merger, specifically, the time $t_\textrm{match}$
+defined in Sec.~\ref{sec:review_pSEOB}, after which they differ during the ringdown.
+%
+By construction, the ringdown lasts longer for the cubic EFT of GR waveform and
+with a smaller instantaneous frequency (see the bottom panel) due to the negative value of the
+$\delta\omega^{(0)}$ coefficient in this theory.
 
@@
 %
-where $p_j(\ell_{\rm th} | \mathcal{H})$ are the priors used for each observation, \redsout{and} $p(\ell_{\rm th} | \mathcal{H})$ is an overall prior, and we assume that the value of $\ell_{\rm th}$ is shared among all events.
+where $p_j(\ell_{\rm th} | \mathcal{H})$ are the priors used for each observation, $p(\ell_{\rm th} | \mathcal{H})$ is an overall prior, and we assume that the value of $\ell_{\rm th}$ is shared among all events.
 %
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
 \includegraphics[width=\columnwidth]{figs/edgb_gamma.pdf}
@@
 
-We can compare this conclusion with that of Ref.~\cite{Carullo:2021dui}, which obtained $\ell_{\rm EdGB} \lesssim 35$~km,
-by setting $p=4$, \emph{but not} including theory-specific QNM information on $\delta \omega^{(j)}$ and $\delta \tau^{(j)}$.
+We can compare this conclusion with that of Ref.~\cite{Carullo:2021dui},
+\hs{which found that $p=4$ modifications (such as the case of EdGB gravity)
+are constrained to $\ell \lesssim 35$~km,}
+% which obtained $\ell_{\rm EdGB} \lesssim 35$~km,
+% by setting $p=4$,
+%
+\emph{but not} including theory-specific QNM information on $\delta \omega^{(j)}$ and $\delta \tau^{(j)}$.
 \ab{Furthermore, Ref.~\cite{Carullo:2021dui} did not impose the EFT and ParSpec bounds that we imposed.}
@@
 
+In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
+same way as already described for the EdGB and dCS theories.
+%
+We see that curves are very similar to those of dCS gravity for GW200129 (see
+bottom panel in Fig.~\ref{fig:cEFT_cdf}).
+%
+Moreover, we find that the EFT~\eqref{eq:eft_bound} and
+ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
+$\mathfrak{m} = M_{\rm f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$.
+%
+This allows us to place the combined bound of
+%
+\begin{equation}
+    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km}, \quad \textrm{at 90\% credible level}\,.
+\end{equation}
+%
+As also happened for our study for dCS, the find that, for
+the cubic EFT, the ParSpec bound is violated by the $N_{\rm max} = 1$ corrections to
+the QNMs, meaning that we cannot use this case to draw any meaningful
+constraint on this parameter.
+%
+We summarize our results in Table~\ref{tab:summary_ceft}.
+
 \begin{figure}[t]
@@
 \end{figure}
-
-In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
-same way as already described for the EdGB and dCS theories.
-%
-We see that curves are very similar to those of dCS gravity for GW200129 (see
-bottom panel in Fig.~\ref{fig:cEFT_cdf}).
-%
-Moreover, we find that the EFT~\eqref{eq:eft_bound} and
-ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
-$\mathfrak{m} = M_{\rm f}$, $\varepsilon = 1/2$, and $N_{\rm max} = 0$.
-%
-This allows us to place the combined bound of
-%
-\begin{equation}
-    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km}, \quad \textrm{at 90\% credible level}\,.
-\end{equation}
-%
-As also happened for our study for dCS, the find that, for
-the cubic EFT, the ParSpec bound is violated by the $N_{\rm max} = 1$ corrections to
-the QNMs, meaning that we cannot use this case to draw any meaningful
-constraint on this parameter.
-%
-We summarize our results in Table~\ref{tab:summary_ceft}.
 

### 2022-05-10 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: fig locs
hs: new refs and cleaned colored text

@@
 Our last example of modified gravity theories are the so-called
-EFTs of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,AccettulliHuber:2020dal,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
+EFTs of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,Cano:2019ore,Brandhuber:2019qpg,AccettulliHuber:2020dal,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
 %
@@
 $\delta\omega^{(j)}$, and $\delta\tau^{(j)}$ parameters, and then proceeded
-to use the posteriors on $\ell_{\rm th}$
-\hs{, considering up to $j=2$ in
+to use the posteriors on $\ell_{\rm th}$, considering up to $j=2$ in
 the GR deformation coefficients, and remaining agnostic about the underlying
-theory which would predict the modifications to the QNMs.}
+theory which would predict the modifications to the QNMs.
 %
@@
 
-\begin{figure}[hb]
+\begin{figure}[htb]
 \includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
@@
 Moreover, and what is more relevant for our analysis, are their post-inspiral
-(merger-ringdown) SNRs which are both $\approx 6$ (see the columns for
+(merger-ringdown) SNRs which are both $\approx 16$ (see the columns for
 $\rho_{\text{post-insp}}$ in Table III of Ref.~\cite{LIGOScientific:2019fpa} and
@@
 We summarize our findings in Table~\ref{tab:summary_edgb}.
-
-\begin{table}[b]
+%
+\begin{table}[h]
 \begin{tabular}{l l c c c}
@@
 We can compare this conclusion with that of Ref.~\cite{Carullo:2021dui},
-\hs{which found that $p=4$ modifications (such as the case of EdGB gravity)
-are constrained to $\ell \lesssim 35$~km,}
-% which obtained $\ell_{\rm EdGB} \lesssim 35$~km,
-% by setting $p=4$,
+which found that $p=4$ modifications (such as the case of EdGB gravity)
+are constrained to $\ell \lesssim 35$~km,
 %
 \emph{but not} including theory-specific QNM information on $\delta \omega^{(j)}$ and $\delta \tau^{(j)}$.
-\ab{Furthermore, Ref.~\cite{Carullo:2021dui} did not impose the EFT and ParSpec bounds that we imposed.}
+Furthermore, Ref.~\cite{Carullo:2021dui} did not impose the EFT bound that we imposed.
 %
@@
 For completness, in Appendix~\ref{app:big_contour} we also
-show how all other intrinsic \redsout{parameter} parameters remain unbiased.
+show how all other intrinsic parameters remain unbiased.
 
@@
 We summarize our results in Table~\ref{tab:summary_ceft}.
+%
+\begin{table}[b]
+\begin{tabular}{l l c c c}
+\hline
+\hline
+$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
+              &       & bound? & bound?  &                            \\
+\hline
+  & GW150914  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 38.2$~km \\
+0 & GW200129  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 42.5$~km \\
+  & Combined  &     &     &  \cellcolor{black!10}$\ell_{\rm cEFT} \leqslant 38.2$~km \\
+\hline
+  & GW150914  & Yes  & No  &  -- \\
+1 & GW200129  & Yes  & No  &  -- \\
+  & Combined  &      &     &  -- \\
+\hline
+\hline
+\end{tabular}
+\caption{Detailed summary of our results the cubic EFT of GR for GW150914, GW200129, and
+combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
+}
+\label{tab:summary_ceft}
+\end{table}
 
@@
 \end{figure}
-
-\begin{figure}[t]
+%
+\begin{figure}[h]
 \includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold_corrected.pdf}
@@
 \end{figure}
-
-\begin{table}[h]
-\begin{tabular}{l l c c c}
-\hline
-\hline
-$N_{\rm max}$ & Event & EFT    & ParSpec & Constraint ($\gm = M_{f}$) \\
-              &       & bound? & bound?  &                            \\
-\hline
-  & GW150914  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 38.2$~km \\
-0 & GW200129  & Yes & Yes &  $\ell_{\rm cEFT} \leqslant 42.5$~km \\
-  & Combined  &     &     &  \cellcolor{black!10}$\ell_{\rm cEFT} \leqslant 38.2$~km \\
-\hline
-  & GW150914  & Yes  & No  &  -- \\
-1 & GW200129  & Yes  & No  &  -- \\
-  & Combined  &      &     &  -- \\
-\hline
-\hline
-\end{tabular}
-\caption{Detailed summary of our results the cubic EFT of GR for GW150914, GW200129, and
-combined events using $\gm = M_{\rm f}$, $\varepsilon = 1/2$ and quoting only 90\% credible results.
-}
-\label{tab:summary_ceft}
-\end{table}
 

### 2022-05-10 papers/paper_alt_theor_bounds/arxiv_v1/paper_alt_theor_bounds.tex
hs: v1 of arXiv

--- 2022-05-10 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
@@
 \usepackage{txfonts}
-% \usepackage{newtxtext}
-% \usepackage{newtxmath}
 \usepackage{natbib}
@@
 \begin{figure}[htb]
-\includegraphics[width=\columnwidth]{figs/example_waveform_cubicEFT.pdf}
+\includegraphics[width=\columnwidth]{example_waveform_cubicEFT.pdf}
 \caption{(Color online). Gravitational-wave signal with GW150914-like parameters
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
+\includegraphics[width=\columnwidth]{edgb_posteriors_combined.pdf}
 \caption{(Color online).~Posterior distribution function on coupling constant $\ell_{\rm EdGB}$ in EdGB gravity
@@
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{figs/edgb_gamma.pdf}
+\includegraphics[width=\columnwidth]{edgb_gamma.pdf}
 \caption{(Color online).~Posterior distribution function on the dimensionless parameter $\gamma_{\rm EdGB}$,
@@
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{figs/edgb_cdf_varying_threshold.pdf}
+\includegraphics[width=\columnwidth]{edgb_cdf_varying_threshold.pdf}
 \caption{(Color online).~The CDF evaluated at the
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/dcs_posteriors_combined.pdf}
+\includegraphics[width=\columnwidth]{dcs_posteriors_combined.pdf}
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for dCS gravity.
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/dcs_cdf_varying_threshold.pdf}
+\includegraphics[width=\columnwidth]{dcs_cdf_varying_threshold.pdf}
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for dCS gravity.
@@
 \begin{figure}[t]
-\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
+\includegraphics[width=0.9\columnwidth]{GW150914_intrinsic_params_remnant.pdf}
 \caption{(Color online).~Corner plot showing that the inferred final spin $\chi_{\rm f}$,
@@
 %
-\begin{table}[b]
+\begin{table}[h]
 \begin{tabular}{l l c c c}
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined_corrected.pdf}
+\includegraphics[width=\columnwidth]{ceft_posteriors_combined.pdf}
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the cubic EFT of GR.
@@
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{figs/ceft_cdf_varying_threshold_corrected.pdf}
+\includegraphics[width=\columnwidth]{ceft_cdf_varying_threshold.pdf}
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_cdf}, but for the cubic EFT of GR.
@@
 
-In this theory, we have considered only $N_{\rm max} = 0$.
-%
-We find that the addition of spin corrections (while maintaining the same prior
-ranges on $\ell_{\rm qEFT}$ as used in the $N_{\rm max} = 0$ study) can result
-in waveforms that can have a ringdown segment larger (sometimes seconds long)
-than the inspiral-plunge segment in the detectors' frequency band, making the
-parameter estimation challenging.
-%
-To overcome this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
-which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
-%
-Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
-%
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined_corrected.pdf}
-\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the quartic EFT of GR.
-We show our results for GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
-%
-As there, we mark with the vertical lines the 90\% upper credible intervals.
-}
-\label{fig:qEFT_exec_sum}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold_corrected.pdf}
-\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
-We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
-can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 68\% credibility.
-}
-\label{fig:qEFT_cdf}
-\end{figure}
-
-\begin{table}[h]
+\begin{table}[b]
 \begin{tabular}{l l c c c}
@@
 \end{table}
+
+In this theory, we have considered only $N_{\rm max} = 0$.
+%
+We find that the addition of spin corrections (while maintaining the same prior
+ranges on $\ell_{\rm qEFT}$ as used in the $N_{\rm max} = 0$ study) can result
+in waveforms that can have a ringdown segment larger (sometimes seconds long)
+than the inspiral-plunge segment in the detectors' frequency band, making the
+parameter estimation challenging.
+%
+To overcome this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
+which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
+%
+Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
+%
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
+\caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the quartic EFT of GR.
+We show our results for GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
+%
+As there, we mark with the vertical lines the 90\% upper credible intervals.
+}
+\label{fig:qEFT_exec_sum}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
+\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
+We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
+can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 68\% credibility.
+}
+\label{fig:qEFT_cdf}
+\end{figure}
 

### 2022-05-10 papers/paper_alt_theor_bounds/arxiv_v1/paper_alt_theor_bounds.tex
hs: removed comment and continuous-line abstract for arxiv

@@
 %
-\hs{We will see in Sec.~\ref{sec:results} that} adding theory-specific
+We will see in Sec.~\ref{sec:results} that adding theory-specific
 information to the ParSpec coefficients \emph{can lead to different interpretations
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
+\includegraphics[width=\columnwidth]{qeft_posteriors_combined.pdf}
 \caption{(Color online).~Similar to Fig.~\ref{fig:edgb_exec_sum}, but for the quartic EFT of GR.
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
+\includegraphics[width=\columnwidth]{qeft_cdf_varying_threshold.pdf}
 \caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
@@
 \begin{figure*}[t]
-\includegraphics[width=0.9\textwidth]{figs/tmp_GW150914_intrinsic_params.pdf}
+\includegraphics[width=0.9\textwidth]{GW150914_intrinsic_params.pdf}
 \caption{(Color online).~Corner plot showing that the inferred source binary parameters for GW150914,
